\begin{abstract}
The preceding dictionary of literal factors isolates a positive-volume family
of prime--squarefree source cells on which the sampled orbit profile has a
uniform pointwise overlap with its carrier.  That geometric statement does
not by itself select a positive fraction of the
actual-coefficient-weighted carrier energy: a
bounded inherited coefficient may vanish on the compatible cells, and the
number of retained cofactors may concentrate on their complement.  We
solve the finite-atom selection problem exactly, before any coherent prime
sum or residual grouping is performed.

Let a good set have structural mass \(\delta\), let
\(|\zeta_m|\le C\), and let \(\kappa\) be the coefficient-weighted energy
divided by the total capacity \(C^2W\).  If \(\sigma\) is the fraction of
that energy on the good set, then
\[
 \sigma\ge
 \left(1-\frac{1-\delta}{\kappa}\right)_+.
\]
The threshold \(\kappa>1-\delta\), the inequality, and all endpoint cases
are sharp.  We also obtain the sharp bound in the presence of a good-cell
floor \(|\zeta_m|\ge\theta C\), including the optimal combination of the
local floor and the global capacity certificate.

Structural density is transported through source shapes, sampled-carrier
weights, and cofactor occupancy by the fractional-linear map
\[
 \mathsf T_\lambda(u)=\frac{\lambda u}{\lambda u+1-u}.
\]
Its odds multiply exactly, so successive distortion exponents add.  This
gives an explicit coverage ledger for the physical fixed-\(h_0\) packet
and identifies three sufficient routes: a coefficient floor plus balanced
occupancy, near-saturation of total coefficient capacity, or a finite
compatible cover of all active carrier energy.  None is supplied for the
full inherited coefficient class by an upper bound alone.

Finally, arbitrary diagonal phases leave every pre-terminal selection
quantity unchanged, while a two-atom collision in one full post-prime
output fiber---whose coordinates include \(s=d(m)r\)---already creates a
nontrivial kernel.  Thus phase distribution
cannot repair a magnitude deficit, and positive atomic coverage cannot be
pushed through terminal grouping without a new coherence estimate.  The
results close a sharp L0 selection calculation and give conditional L1
specializations; they prove no post-grouping lower bound, parity
improvement, or twin-prime statement.
\end{abstract}
