\section{Sharp selection from coefficient capacity}
\label{sec:capacity}

We first keep the structural weights fixed and ask what a coefficient
upper bound plus one scalar global energy statistic can force.

\begin{theorem}[Sharp capacity threshold]
\label{thm:tpc54-capacity}
Let \(0\le\delta\le1\), let \(|\zeta_m|\le C\), and suppose \(E>0\).
Then
\begin{equation}
 \boxed{\quad
 \sigma\ge
 \frac{\bigl(\kappa-(1-\delta)\bigr)_+}{\kappa}
 =\left(1-\frac{1-\delta}{\kappa}\right)_+ .
 \quad}
 \label{eq:tpc54-capacity-bound}
\end{equation}
For every admissible pair \((\delta,\kappa)\), the bound is attained by
coefficients whose squared modulus is constant separately on \(\cG\) and
\(\cM\setminus\cG\).  In particular, global information forces
\(\sigma>0\) if and only if
\begin{equation}
 \kappa>1-\delta.
 \label{eq:tpc54-positive-threshold}
\end{equation}
\end{theorem}

\begin{proof}
The bad set has capacity
\[
 E(\cM\setminus\cG)
 \le C^2W(\cM\setminus\cG)
 =C^2W(1-\delta).
\]
Since \(E=\kappa C^2W\), subtraction gives
\[
 E(\cG)\ge
 C^2W\bigl(\kappa-(1-\delta)\bigr).
\]
Combining this with \(E(\cG)\ge0\) and dividing by \(E\) proves
\eqref{eq:tpc54-capacity-bound}.

Assume first \(0<\delta<1\).  If \(0<\kappa\le1-\delta\), set
\[
 |\zeta_m|^2=0\quad(m\in\cG),
 \qquad
 |\zeta_m|^2=C^2\frac{\kappa}{1-\delta}
 \quad(m\notin\cG).
\]
Then \(E=\kappa C^2W\) and \(\sigma=0\).  If
\(1-\delta<\kappa\le1\), set
\[
 |\zeta_m|^2=C^2
 \quad(m\notin\cG),
 \qquad
 |\zeta_m|^2=C^2\frac{\kappa-1+\delta}{\delta}
 \quad(m\in\cG).
\]
This saturates the bad capacity and attains the positive branch of
\eqref{eq:tpc54-capacity-bound}.  For \(\delta=0\), necessarily
\(\sigma=0\); for \(\delta=1\), necessarily \(\sigma=1\).  These agree
with the formula and complete the endpoint cases.
\end{proof}

The equality mechanism is transparent.  On the zero branch it is enough
that all occupied energy fit on the bad set.  On the positive branch,
equality requires every positive-weight bad atom to be saturated; the
remaining prescribed energy is then placed on the good set.  No phase
condition occurs.

\begin{corollary}[Saturation-defect form]
\label{cor:tpc54-defect}
Write \(\epsilon:=1-\kappa\).  Then
\begin{equation}
 \sigma\ge\frac{(\delta-\epsilon)_+}{1-\epsilon}.
 \label{eq:tpc54-defect-bound}
\end{equation}
If \(\epsilon\le(1-\tau)\delta\) for some \(0\le\tau\le1\), then
\begin{equation}
 \sigma\ge\frac{\tau\delta}{1-\epsilon}
 \ge\tau\delta.
 \label{eq:tpc54-defect-tau}
\end{equation}
The condition \(\epsilon<\delta\) for a positive conclusion is sharp.
\end{corollary}

Thus ``large total energy'' is meaningful only relative to the capacity
of the complement.  A lower bound \(E\gg C^2W\) with an unspecified small
constant need not select a small good set: the exact requirement is
\(\kappa>1-\delta\).

\subsection{A local coefficient floor}

The other natural certificate is local rather than global.

\begin{theorem}[Sharp good-cell floor]
\label{thm:tpc54-floor}
Suppose
\begin{equation}
 |\zeta_m|\ge\theta C\quad(m\in\cG),
 \qquad |\zeta_m|\le C\quad(m\in\cM),
 \qquad 0<\theta\le1.
 \label{eq:tpc54-floor-hyp}
\end{equation}
If \(E>0\), then
\begin{equation}
 \boxed{\quad
 \sigma\ge
 \frac{\theta^2\delta}
      {\theta^2\delta+1-\delta}
 =\mathsf T_{\theta^2}(\delta).
 \quad}
 \label{eq:tpc54-floor-bound}
\end{equation}
The bound is sharp.
\end{theorem}

\begin{proof}
Write \(A=E(\cG)\) and \(B=E(\cM\setminus\cG)\).  The hypotheses give
\[
 A\ge\theta^2C^2\delta W,
 \qquad B\le C^2(1-\delta)W.
\]
Because \(A/(A+B)\) increases with \(A\) and decreases with \(B\), the
claimed bound follows.  Equality is obtained by taking
\(|\zeta_m|=\theta C\) on the good set and \(|\zeta_m|=C\) on the bad
set, with the evident endpoint interpretations.
\end{proof}

If both the actual value of \(\kappa\) and a good-cell floor are known,
neither certificate should be discarded.

\begin{theorem}[Optimal combined certificate]
\label{thm:tpc54-combined}
Under \eqref{eq:tpc54-floor-hyp}, a positive capacity level \(\kappa\) is
feasible only if \(\kappa\ge\theta^2\delta\).  For every feasible
\(\kappa\in(0,1]\cap[\theta^2\delta,1]\),
\begin{equation}
 \boxed{\quad
 \sigma\ge
 \frac{
  \max\{\theta^2\delta,\ \kappa-(1-\delta)\}}
 {\kappa}.
 \quad}
 \label{eq:tpc54-combined-bound}
\end{equation}
The bound is sharp for each \((\delta,\theta,\kappa)\).
\end{theorem}

\begin{proof}
The floor gives \(E(\cG)\ge\theta^2\delta C^2W\), while the bad-set
capacity argument gives
\(E(\cG)\ge(\kappa-(1-\delta))C^2W\).  Dividing their maximum by
\(E=\kappa C^2W\) proves the inequality.

If \(\kappa\le1-\delta+\theta^2\delta\), put exactly the floor energy on
the good set and distribute
\((\kappa-\theta^2\delta)C^2W\) uniformly over the bad set.  If
\(\kappa\ge1-\delta+\theta^2\delta\), saturate the bad set and distribute
the remaining \((\kappa-1+\delta)C^2W\) uniformly over the good set.
All squared amplitudes lie in \([0,C^2]\) and respect the floor, proving
sharpness.  The degenerate values \(\delta=0,1\) follow directly.
\end{proof}

After the floor is removed, the formula in
\cref{thm:tpc54-combined} extends to \(\theta=0\) and reduces to the
capacity law.
If \(\kappa\) is not specified, minimizing over all feasible values
recovers \cref{thm:tpc54-floor}.  If \(|\zeta_m|=C\) on every atom, then
\(\kappa=1\) and \(\sigma=\delta\) exactly.
