\section{The pre-terminal coverage ladder}
\label{sec:coverage-ladder}

\subsection{Finite weighted atoms}

Let \(\cM\) be a nonempty finite set, let \(w_m\ge0\), and write
\[
 W(S):=\sum_{m\in S}w_m,
 \qquad W:=W(\cM)>0.
\]
Atoms of zero weight may be deleted, so no result changes if one assumes
\(w_m>0\).  Fix a good set \(\cG\subseteq\cM\) and define its structural
fraction by
\begin{equation}
 \delta:=\frac{W(\cG)}{W}\in[0,1].
 \label{eq:tpc54-delta}
\end{equation}
For coefficients \(\zeta_m\in\C\), put
\begin{equation}
 E(S):=\sum_{m\in S}w_m|\zeta_m|^2,
 \qquad E:=E(\cM).
 \label{eq:tpc54-energy}
\end{equation}
Whenever \(E>0\), the actual good-energy fraction is
\begin{equation}
 \sigma:=\frac{E(\cG)}{E}.
 \label{eq:tpc54-sigma}
\end{equation}
These are atomic squared norms.  No sum of complex amplitudes has yet
occurred.

If \(|\zeta_m|\le C\) for a fixed \(C>0\), the total available capacity is
\(C^2W\).  We normalize the occupied capacity by
\begin{equation}
 \kappa:=\frac{E}{C^2W}\in(0,1].
 \label{eq:tpc54-kappa}
\end{equation}
The three numbers have different meanings: \(\delta\) is structural,
\(\kappa\) is global magnitude information, and \(\sigma\) is the desired
localized coefficient-energy fraction.

\subsection{The odds transform}

For \(\lambda\ge0\) and \(0\le u\le1\), set
\begin{equation}
 \mathsf T_\lambda(u)
 :=\frac{\lambda u}{\lambda u+1-u},
 \label{eq:tpc54-T-def}
\end{equation}
with the endpoint convention \(\mathsf T_0(1):=1\); thus
\(\mathsf T_0(u)=0\) for \(u<1\).  There is no joint continuous extension
at the exceptional corner \((0,1)\); the convention is only bookkeeping
and will not be used with a zero lower multiplier.

\begin{lemma}[Odds calculus]
\label{lem:tpc54-odds}
For \(0<u<1\) and \(\lambda>0\),
\begin{equation}
 \frac{\Tp{\lambda}{u}}{1-\Tp{\lambda}{u}}
 =\lambda\frac{u}{1-u}.
 \label{eq:tpc54-odds}
\end{equation}
Moreover, \(\mathsf T_\lambda\) is increasing in both variables and
\begin{equation}
 \mathsf T_\lambda\!\left(\mathsf T_\mu(u)\right)
 =\mathsf T_{\lambda\mu}(u)
 \label{eq:tpc54-composition}
\end{equation}
whenever the displayed expressions are defined by the stated endpoint
conventions.
\end{lemma}

\begin{proof}
Both identities follow by direct substitution.  Differentiation gives
\[
 \partial_u\mathsf T_\lambda(u)
 =\frac{\lambda}{(1-(1-\lambda)u)^2},
 \qquad
 \partial_\lambda\mathsf T_\lambda(u)
 =\frac{u(1-u)}{(1-(1-\lambda)u)^2},
\]
in the interior, proving monotonicity.  The ordinary endpoints follow by
one-variable limits, while the exceptional corner and the composition law
there are checked directly from the convention.
\end{proof}

The transform is the exact bookkeeping device for the rest of the paper.
If a change of weight decreases the good-to-bad odds by at most a factor
\(\lambda\), it changes the good fraction by \(\mathsf T_\lambda\).  A
chain of changes multiplies the odds factors, rather than adding an
artificial loss at each denominator.

\subsection{Five distinct levels}

For later reference we separate the following levels.

\begin{enumerate}[label=\textup{(C\arabic*)},leftmargin=2.8em]
 \item \emph{Geometric occupancy:} counting or prime--squarefree base
       mass on a compatible source box.
 \item \emph{Source base energy:} geometric mass reweighted by fixed
       logarithmic and smooth source shapes, but not by \(\zeta_m\).
 \item \emph{Sampled carrier energy:} source base energy reweighted by
       the coefficient-free sampled carrier.
 \item \emph{Lifted carrier energy:} sampled carrier energy repeated over
       the actual retained cofactors.
 \item \emph{Actual-coefficient carrier energy:} lifted carrier energy
       multiplied by \(|\zeta_m|^2\).
\end{enumerate}

Levels C1--C5 are all pre-terminal.  The coherent prime sum and the map
grouping \(s=d(m)r\) lie after this ladder.  Thus positivity permits exact
selection within the ladder, but not across the terminal boundary.
