\section{Endpoint ledger, conclusions, and next gate}
\label{sec:endpoint}

\subsection{Polynomial selection cost}

The odds formula makes the endpoint budget explicit.  Suppose, along a
sequence of scales,
\begin{align}
 \delta_{\rm geo}&=X^{-\nu+o(1)},
 &\lambda_{\rm src}&=X^{-\omega_{\rm src}+o(1)},
 \nonumber\\
 \lambda_{\rm car}&=X^{-\omega_{\rm car}+o(1)},
 &\lambda_{\rm cf}&=X^{-\omega_{\rm cf}+o(1)},
 \nonumber\\
 \theta&=X^{-\chi+o(1)},
 \label{eq:tpc54-polynomial-data}
\end{align}
with nonnegative exponents.  Put
\[
 \mathfrak a_X
 :=\theta^2\lambda_{\rm src}\lambda_{\rm car}\lambda_{\rm cf}.
\]
The elementary bound
\[
 \mathsf T_{\mathfrak a_X}(\delta_{\rm geo})
 \ge\frac{\mathfrak a_X\delta_{\rm geo}}{1+\mathfrak a_X}
\]
and \eqref{eq:tpc54-full-composition} give
\begin{equation}
 \sigma_X\ge
 X^{-(\nu+\omega_{\rm src}+\omega_{\rm car}
          +\omega_{\rm cf}+2\chi)+o(1)}.
 \label{eq:tpc54-selection-exponent}
\end{equation}
Thus the displayed sum is a sharp worst-case upper bound for the
polynomial selection cost; the actual odds can be better.  The factor two
on \(\chi\) is forced by squared energy.  No phase exponent appears.

The inherited TPC--52 ledger, with fixed cell scale and fixed positive
profile overlap, allows at most the nominal selection loss
\begin{equation}
 \boxed{\quad
 \nu+\omega_{\rm src}+\omega_{\rm car}
     +\omega_{\rm cf}+2\chi
 \le\frac1{400}.
 \quad}
 \label{eq:tpc54-endpoint-budget}
\end{equation}
At equality, an error already of size \(X^{-1/400+o(1)}\) need not be
absorbed without a constant-level comparison or an additional saving;
strict slack is the safe closure condition.  The fixed compatible boxes,
fixed nonzero shapes, fixed sampled-carrier ratio, and fixed overlap
\(\alpha_*\) used in the declared TPC--53 cell have zero positive
polynomial cost.  Under fixed-ratio coefficient and occupancy bounds, the
selection cost is therefore also zero.

If instead one uses the capacity route and such an exponent exists along
the chosen subsequence, define \(\varsigma\) by
\[
 \left(1-\frac{1-\delta_{{\rm cf},X}}{\kappa_X}\right)_+
 =X^{-\varsigma+o(1)}.
\]
The value \(\varsigma\) replaces the sum in
\eqref{eq:tpc54-endpoint-budget}.  If the left side is zero infinitely
often, or is smaller than \(X^{-A}\) for every fixed \(A>0\), this route
fails the endpoint gate.

A shrinking profile threshold would introduce its own exponent.  The
existing sampled approximation supports the fixed interior
\(\alpha_*>0\) regime; it should not be silently used as a relative-error
theorem at a polynomially vanishing threshold.

\subsection{Claim ledger}

The exact status is as follows.

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.25\textwidth}
                >{\raggedright\arraybackslash}p{0.62\textwidth}}
\toprule
Statement & Status \\
\midrule
Capacity threshold and extremizers & Unconditional finite-atom theorem
(L0). \\
Odds transport and composition & Unconditional sharp change-of-weight
theorem (L0). \\
Literal fixed-\(h_0\) carrier normalization & Exact specialization of the
TPC--53 pre-terminal carrier dictionary on the declared slice (L1
interface). \\
Compatible geometric/source box & Previously certified for fixed boxes;
not full actual-coefficient carrier-energy coverage. \\
Positive declared-slice \(\sigma_X\) & Conditional on actual occupancy,
balanced multiplicity plus a coefficient floor, capacity saturation, or a
finite compatible cover. \\
Post-grouping lower bound & Not proved; impossible uniformly on a selected
subspace containing both directions of a two-atom collision. \\
Parity or twin-prime consequence & Not claimed. \\
\bottomrule
\end{tabular}
\end{center}

In particular, the following implications remain forbidden:
geometric density does not imply actual-coefficient carrier energy; a unit-modulus source
factor does not imply full lifted coverage without occupancy control;
arbitrary cofactor multiplicity inside one selected packet does not imply
that the packet captures a fixed fraction of the full carrier; and a
pre-terminal lower bound does not commute with coherent prime summation or
residual grouping.

\subsection{The next gate}

The correct order of further work is now forced by the maps:
\begin{enumerate}[leftmargin=2.2em]
 \item select actual retained \((m,r)\)-fibers by one of the sharp
       certificates above;
 \item prove a two-sided or lower coherent-prime square while the source
       and cofactor labels remain separate;
 \item control collisions in the grouping \(s=d(m)r\);
 \item localize the resulting estimate to the literal fixed shift \(h_0\)
       and compare the residual Gram with the native affine Gram; and
 \item reconnect the controlled packet to the original ultra-tail defect.
\end{enumerate}

The immediate next paper takes the first step after selection: it keeps
the residual grouping explicit, rewrites fibers by \(s=d(m)r\), and asks
which exact divisor/cofactor structure can prevent the two-atom kernel
from being the relevant arithmetic behavior.  The present paper has made
that question quantitative, but has not answered it.

\medskip
\noindent\textbf{Conclusion.}
Given declared structural, capacity, and occupancy data, the abstract
finite-atom selection problem left by the literal factor dictionary has a
complete sharp answer.  A positive lifted structural fraction is selected
if it also has a local coefficient floor; alternatively, global
coefficient energy may saturate capacity beyond the complement threshold,
or a finite compatible cover may capture all active carrier energy.
Source, carrier, and cofactor distortions act multiplicatively on odds and
add at the exponent level.  These facts are exact before terminal
grouping.  The same exactness also shows why the result stops there: phases
are invisible before the sum, and collisions can cancel after it.
