\section{Phase blindness and the residual-grouping barrier}
\label{sec:grouping}

The selection theory is deliberately placed before the terminal map.  Two
elementary invariances show why this order cannot be reversed for free.

\subsection{Diagonal phases cannot repair magnitude coverage}

\begin{proposition}[Pre-terminal phase blindness]
\label{prop:tpc54-phase-blindness}
For arbitrary real phases \(\vartheta_m\), replace
\(\zeta_m\) by \(e^{i\vartheta_m}\zeta_m\).  Then
\(E(S)\), \(\delta\), \(\kappa\), and \(\sigma\) are unchanged for every
\(S\subseteq\cM\).  The same holds after orthogonal repetition over
retained labels \((m,r)\).
\end{proposition}

\begin{proof}
Every displayed quantity is a weighted sum of \(|\zeta_m|^2\), and
\(|e^{i\vartheta_m}\zeta_m|=|\zeta_m|\).  Repetition over orthogonal
coordinates only repeats the same diagonal squared modulus.
\end{proof}

Thus equidistribution, randomness, or oscillation of phases alone cannot
move pre-terminal energy onto a good cell.  Such information can become
relevant only when amplitudes are summed coherently later.

\subsection{A two-atom kernel after grouping}

Let \(\cU\) be a finite set of admissible post-prime input labels and let
the residual grouping map have the fiber form
\begin{equation}
 (Tz)_y=\sum_{u:\,q(u)=y}c_u z_u,
 \label{eq:tpc54-fiber-map}
\end{equation}
In the literal slice, one may take
\[
 u=(m,r,j,\gamma),\qquad
 q(u)=(\gamma,d(m)r,j),
\]
where the terminal prime \(p_u\) is admissible and satisfies
\(p_ur-mj=h_0\); the coefficient \(c_u\) includes
\(\mu(r)\Lambda(p_ur)\) and the already formed prime amplitude.  Thus
equality of \(d(m)r\) alone is not enough for a physical collision: the
other output coordinates and terminal constraint must also agree.  This
notation isolates only the linear-algebra issue and does not replace the
literal terminal formula of TPC--53.

\begin{theorem}[Two-atom collision obstruction]
\label{thm:tpc54-two-atom-kernel}
Suppose one output fiber contains distinct labels \(u_1,u_2\) with
\(c_{u_1}c_{u_2}\ne0\).  Then \(T\) has a nonzero vector supported on
that fiber in its kernel.  Consequently there is no constant \(c>0\)
such that
\begin{equation}
 \|Tz\|_2^2\ge c\sum_{u\in\cU}|z_u|^2
 \label{eq:tpc54-impossible-lower}
\end{equation}
for all coefficient arrays supported on any selected subspace containing
both coordinate directions.
\end{theorem}

\begin{proof}
Take
\[
 z_{u_1}=c_{u_2},\qquad z_{u_2}=-c_{u_1},
 \qquad z_u=0\quad(u\ne u_1,u_2).
\]
Then the only potentially nonzero output is
\(c_{u_1}c_{u_2}-c_{u_2}c_{u_1}=0\), while \(z\ne0\).  Scaling the vector
also meets any prescribed common upper bound on its coordinates.
\end{proof}

At a fixed source \(m\), the map \(r\mapsto d(m)r\) is injective, so the
literal pre-terminal \(r\)-square is exact.  Collisions, if present, can
arise only across different sources.  TPC--53 displays the actual order:
multiply by the
terminal weight, form the coherent prime sum, and only then group equal
values of \(s=d(m)r\).  Expanding the final squared norm produces cross
terms absent from \eqref{eq:tpc54-literal-energy}.

\begin{corollary}[Logical boundary of energy selection]
\label{cor:tpc54-selection-boundary}
If a selected compatible coordinate subspace contains both directions in
such a nonzero collision fiber, it has a kernel vector with compatible
input-energy fraction one.  Hence no uniform grouped lower bound holds on
that subspace.  A coverage statement alone gives no lower bound until one
checks how its selected support meets the physical collision fibers.  To
pass the boundary one must prove an estimate for the distinguished
arithmetic array---for example a coherent-prime lower square followed by
grouping stability---or restrict to a collision-free set of labels.
\end{corollary}

The theorem is a no-go for an \emph{automatic implication}, not evidence
that the physical coefficients actually choose a cancelling vector.  It
pinpoints the next missing estimate without assigning adversarial freedom
to a fixed arithmetic sequence.
