\section{Introduction}
\label{sec:introduction}

The TPC reduction studied in \citep{WangTPC25,WangTPC48,WangTPC50}
contains several logically different kinds of ``mass.''  A fixed
prime--squarefree source rectangle can contain a positive proportion of
the admissible rows.  Fixed smooth source shapes can give those rows a
positive proportion of a coefficient-free base energy.  The sampled
carrier and repetition over retained cofactors then change the row
weights.  Finally, the inherited coefficient \(\zeta_m\) may redistribute,
or completely remove, the carrier energy.  Conflating any two of these
statements turns a support theorem into an unjustified lower bound.

TPC--52 \citep{WangTPC52} proved a conditional pre-terminal profile
estimate once a fraction \(\sigma_X\) of the actual-coefficient carrier
energy lies on
compatible source fibers.  TPC--53 \citep{WangTPC53} supplied the literal
factor dictionary, exact atomic normalization, and a fixed compatible box
on which the sampled profile-to-carrier ratio is uniformly positive.  It
also exhibited the remaining obstruction: the inherited theory assumes
only \(|\zeta_m|\ll1\), and does not force the actual-coefficient carrier
energy or the cofactor multiplicity to visit that box.  The present paper
asks the narrow next question:

\begin{quote}
Given the structural size of a compatible set and only specified
information about coefficient capacity and cofactor occupancy, what is the
best possible lower bound for its actual-coefficient pre-terminal carrier
energy?
\end{quote}

This question is finite-dimensional.  Its answer is therefore exact, not
asymptotic.  The arithmetic work is to identify which weights occur in the
physical packet and which hypotheses the inherited papers actually
provide.

\subsection{Main results}

Our first result is a sharp capacity law.  Let \(W\) be total structural
mass, let the good set carry mass \(\delta W\), and suppose
\(|\zeta_m|\le C\).  If the coefficient energy is \(\kappa C^2W\), the bad set
can hold at most \((1-\delta)C^2W\).  Hence the good energy fraction obeys
\[
 \sigma\ge
 \frac{(\kappa-(1-\delta))_+}{\kappa}.
\]
Both regimes are attained: below the threshold one may place all energy
on bad atoms, while above it one first saturates every bad atom.  In terms
of the unsaturated capacity \(\epsilon=1-\kappa\), positive selection is
forced exactly when \(\epsilon<\delta\).

The second result describes changes of measure sharply.  If a multiplier
is at least \(n_-\) on good atoms and at most \(n_+\) on bad atoms, then a
good fraction \(u\) becomes at least
\[
 \mathsf T_{n_-/n_+}(u)
 =\frac{n_-u}{n_-u+n_+(1-u)}.
\]
The identity
\[
 \frac{\mathsf T_\lambda(u)}{1-\mathsf T_\lambda(u)}
 =\lambda\frac{u}{1-u}
\]
shows why independent losses multiply in odds coordinates.  Source-shape,
sampled-carrier, cofactor-occupancy, and coefficient-floor losses therefore
compose without the slack introduced by repeatedly discarding denominators.

Our third result is negative but operationally decisive.  All selection
quantities before the terminal map depend only on \(|\zeta_m|\), so
rowwise unit phases cannot change them.  After the terminal map, two
admissible inputs can collide only when their full output data agree; one
coordinate is \(s=d(m)r\).  Any such output fiber containing two nonzero
inputs has a one-dimensional cancellation direction.  A
pre-terminal lower bound therefore does not survive grouping merely by
positivity; one needs new information adapted to the distinguished
arithmetic coefficients.

\subsection{What is and is not arithmetic progress}

The sharp inequalities are unconditional L0 statements.  Their
specialization to the literal fixed-\(h_0\) carrier weights is also exact.
The earlier source-cell and profile-overlap certificates then give an L1
route under any one of several explicit additional hypotheses.  The full
inherited class currently supplies only a coefficient upper bound and an
arbitrary supported cofactor set.  It supplies neither a nonvanishing
coefficient floor, a near-capacity estimate, nor balanced cofactor
occupancy.  Consequently we do \emph{not} claim a positive coverage
constant for the full inherited packet.

Nothing here controls the coherent sum over the terminal prime, proves
stability of residual grouping, identifies the residual Gram matrix with
the native affine Gram matrix, or performs Fourier localization at a
moving shift.  Only the literal fixed shift \(h_0\) is physical.  In
particular, the paper contains no parity-breaking estimate and no
twin-prime consequence.

\subsection{Organization}

\Cref{sec:coverage-ladder} defines the selection variables and the exact
odds calculus.  \Cref{sec:capacity} proves the capacity and coefficient
floor theorems.  \Cref{sec:occupancy} treats reweighting, multiple stages,
and a finite-cover alternative.  \Cref{sec:physical} inserts the literal
prime--squarefree weights.  \Cref{sec:grouping} proves the phase-invariance
and grouping obstructions.  \Cref{sec:endpoint} records the polynomial
budget, claim level, and the next gate.
