\section{Sharp transport through source and cofactor weights}
\label{sec:occupancy}

The previous section treated a fixed base measure.  We now quantify how a
good fraction changes when the atoms are reweighted.

\subsection{An exact four-factor odds identity}

The sharp inequalities below are consequences of an exact identity that
also gives a necessary-and-sufficient average-data summary.

\begin{theorem}[Exact row--shape--amplitude--occupancy factorization]
\label{thm:tpc54-exact-odds-factorization}
Let \(q_m\ge0\) be reference row weights, let \(b_m\ge0\) be a fixed
base-energy multiplier, let \(|\zeta_m|\le C\), and let \(N_m\ge0\) be
an occupancy multiplier.  For \(A\in\{\cG,\cB\}\), where
\(\cB=\cM\setminus\cG\), set
\begin{align}
 Q_A&:=\sum_{m\in A}q_m,
 &\overline b_A&:=\frac{\sum_{m\in A}q_mb_m}{Q_A},
 \nonumber\\
 \vartheta_A&:=
 \frac{\sum_{m\in A}q_mb_m|\zeta_m|^2}
      {C^2\sum_{m\in A}q_mb_m},
 &\overline N_A&:=
 \frac{\sum_{m\in A}q_mb_m|\zeta_m|^2N_m}
      {\sum_{m\in A}q_mb_m|\zeta_m|^2}.
 \label{eq:tpc54-factor-averages}
\end{align}
Put \(\delta_0=Q_{\cG}/(Q_{\cG}+Q_{\cB})\), and define
\[
 F_A:=\sum_{m\in A}q_mb_m|\zeta_m|^2N_m,
 \qquad \sigma_N:=\frac{F_{\cG}}{F_{\cG}+F_{\cB}}.
\]
Assume, for both \(A=\cG,\cB\), that \(Q_A\), the base mass
\(\sum_Aq_mb_m\), the amplitude mass
\(\sum_Aq_mb_m|\zeta_m|^2\), and \(F_A\) are all positive.  Then
\begin{equation}
 \boxed{\quad
 \frac{\sigma_N}{1-\sigma_N}
 =\frac{\overline N_{\cG}}{\overline N_{\cB}}
  \frac{\vartheta_{\cG}}{\vartheta_{\cB}}
  \frac{\overline b_{\cG}}{\overline b_{\cB}}
  \frac{\delta_0}{1-\delta_0}.
 \quad}
 \label{eq:tpc54-exact-odds-factorization}
\end{equation}
The boundary cases are read directly from \(F_{\cG}\) and
\(F_{\cB}\): the selected fraction is zero if only the bad energy is
positive, one if only the good energy is positive, and undefined if both
vanish.
\end{theorem}

\begin{proof}
For either \(A\), the definitions telescope to
\[
 F_A=C^2Q_A\overline b_A\vartheta_A\overline N_A.
\]
Taking \(F_{\cG}/F_{\cB}\) proves
\eqref{eq:tpc54-exact-odds-factorization}.
\end{proof}

Thus \(\sigma_N\ge s\), for \(0<s<1\), is equivalent to the right side
of \eqref{eq:tpc54-exact-odds-factorization} being at least
\(s/(1-s)\).  Pointwise coefficient floors and occupancy bounds are
convenient sufficient conditions; the product of the good-to-bad weighted
average ratios is an exact necessary-and-sufficient summary.  All unit
phases have disappeared before any estimate is made.

Taking \(N_m\equiv1\) and writing
\[
 \delta_b:=\frac{\sum_{\cG}q_mb_m}{\sum_{\cM}q_mb_m},
 \qquad
 \sigma_b:=\frac{\sum_{\cG}q_mb_m|\zeta_m|^2}
                  {\sum_{\cM}q_mb_m|\zeta_m|^2},
\]
gives the exact amplitude identity
\begin{equation}
 \frac{\sigma_b}{1-\sigma_b}
 =\frac{\vartheta_{\cG}}{\vartheta_{\cB}}
  \frac{\delta_b}{1-\delta_b},
 \label{eq:tpc54-exact-amplitude-odds}
\end{equation}
Taking \(b_m\equiv1\) and \(|\zeta_m|\equiv C\) isolates the exact
energy-weighted occupancy ratio.

\subsection{Pointwise sharp transport}

\begin{theorem}[Sharp occupancy transport]
\label{thm:tpc54-transport}
 Let \(u_m\ge0\) have positive total mass and let
\(\delta=\sum_{\cG}u_m/\sum_{\cM}u_m\).  Let \(v_m\ge0\) satisfy
\begin{equation}
 v_m\ge v_->0\quad(m\in\cG),
 \qquad
 v_m\le v_+<\infty\quad(m\notin\cG),
 \qquad v_+>0,
 \label{eq:tpc54-multiplier-bounds}
\end{equation}
Assume \(\sum_m u_mv_m>0\).  Then the good fraction after reweighting is
\begin{equation}
 \delta_v:=\frac{\sum_{m\in\cG}u_mv_m}
                   {\sum_{m\in\cM}u_mv_m}
 \ge
 \mathsf T_{v_-/v_+}(\delta)
 =\frac{v_-\delta}{v_-\delta+v_+(1-\delta)}.
 \label{eq:tpc54-transport}
\end{equation}
The inequality is sharp.  If in addition \(v_-\le v_+\),
\(v_m\le v_+\) on \(\cG\) and \(v_m\ge v_-\) on its complement, the
corresponding sharp upper bound is
\begin{equation}
 \delta_v\le
 \frac{v_+\delta}{v_+\delta+v_-(1-\delta)}.
 \label{eq:tpc54-transport-upper}
\end{equation}
\end{theorem}

\begin{proof}
Put \(A=\sum_{\cG}u_mv_m\) and
\(B=\sum_{\cM\setminus\cG}u_mv_m\).  Then
\(A\ge v_-\delta\sum u_m\) and
\(B\le v_+(1-\delta)\sum u_m\).  Monotonicity of \(A/(A+B)\) gives the
 lower bound.  Equality is attained by taking \(v=v_-\) on \(\cG\) and
\(v=v_+\) on its complement.  Reversing the two inequalities proves and
sharpens the upper bound; equality there is attained by taking
\(v=v_+\) on \(\cG\) and \(v=v_-\) on its complement.
\end{proof}

Only a lower bound on good atoms and an upper bound on bad atoms are needed
for the lower estimate.  Very large good multipliers help rather than
hurt.  By contrast, a global upper bound with no good lower bound permits
complete loss of occupancy.

The exact factorization also gives a weaker-hypothesis version.  If
\(E_A=\sum_{m\in A}u_m|\zeta_m|^2>0\) and
\[
 \overline N_A
 =\frac{\sum_{m\in A}u_m|\zeta_m|^2N_m}{E_A},
\]
then, whenever both lifted masses are positive, the lifted odds are
exactly the unlifted odds multiplied by
\(\overline N_{\cG}/\overline N_{\cB}\).  If only the good lifted mass is
positive the lifted fraction is one; if only the bad lifted mass is
positive it is zero.  Hence pointwise bounds
\(N_m\ge n_-\) on good atoms and \(N_m\le n_+\) on bad atoms are not
necessary; they merely certify the corresponding average ratio.

\subsection{Exact composition of the coverage ladder}

Start with geometric weights \(q_m\) and good fraction
\(\delta_{\rm geo}\).  Let a fixed source-shape multiplier have ratio
\(\lambda_{\rm src}=a_-/a_+\), let the sampled-carrier multiplier have
ratio \(\lambda_{\rm car}=b_-/b_+\), and let the cofactor-occupancy
multiplier have ratio \(\lambda_{\rm cf}=n_-/n_+\), all in the sense of
\eqref{eq:tpc54-multiplier-bounds}.  Applying
\cref{thm:tpc54-transport,lem:tpc54-odds} gives
\begin{equation}
 \delta_{\rm lift}
 \ge
 \mathsf T_{\lambda_{\rm cf}}
  \!\left(\mathsf T_{\lambda_{\rm car}}
  \!\left(\mathsf T_{\lambda_{\rm src}}
  (\delta_{\rm geo})\right)\right)
 =\mathsf T_{\lambda_{\rm src}\lambda_{\rm car}\lambda_{\rm cf}}
  (\delta_{\rm geo}).
 \label{eq:tpc54-lifted-composition}
\end{equation}
If also \(|\zeta_m|\ge\theta C\) on the good set and
\(|\zeta_m|\le C\) everywhere, one more application yields
\begin{equation}
 \boxed{\quad
 \sigma\ge
 \mathsf T_{\theta^2\lambda_{\rm src}\lambda_{\rm car}\lambda_{\rm cf}}
  (\delta_{\rm geo}).
 \quad}
 \label{eq:tpc54-full-composition}
\end{equation}
Each stage, and the composition, is sharp in the unrestricted abstract
finite-atom class: take every good multiplier at its lower endpoint and
every bad multiplier at its upper endpoint.  Literal arithmetic factors
need not realize all these extremizers simultaneously.

Equation \eqref{eq:tpc54-full-composition} is stronger than multiplying a
good numerator by several lower bounds while repeatedly replacing the total
denominator by a global upper bound.  The odds coordinate keeps the exact
denominator at every stage.

If a coefficient floor is unavailable, define \(\kappa\) relative to the
already lifted base weights.  Then \cref{thm:tpc54-capacity} gives instead
\begin{equation}
 \sigma\ge
 \left(1-\frac{1-\delta_{\rm lift}}{\kappa}\right)_+.
 \label{eq:tpc54-lifted-capacity}
\end{equation}
This route needs no pointwise lower bound, but near-saturation becomes more
demanding when \(\delta_{\rm lift}\) is small.

\subsection{A finite-cover alternative}

Balance is sufficient, not logically necessary.  A second route is to
cover every active atom by finitely many compatible cells.

\begin{proposition}[Selection from a finite compatible cover]
\label{prop:tpc54-finite-cover}
Suppose \(E>0\) and the support of the coefficient-weighted atomic energy is contained in
\(\cG_1\cup\cdots\cup\cG_R\), where every \(\cG_j\) has the required
profile compatibility and \(R\) is independent of the scale.  Then some
cell satisfies
\begin{equation}
 \frac{E(\cG_j)}{E}\ge\frac1R.
 \label{eq:tpc54-cover-pigeonhole}
\end{equation}
The constant \(1/R\) is optimal.
\end{proposition}

\begin{proof}
Since the cover may overlap,
\(E\le\sum_{j=1}^R E(\cG_j)\).  One summand is therefore at least
\(E/R\).  Equality occurs for a partition into \(R\) cells of equal
energy.
\end{proof}

This proposition tolerates arbitrary source and cofactor concentration,
but its premise is stronger geometrically: the compatible cells must cover
the \emph{actual active support}, not merely one open positive-volume
subset of the ambient parameter box.
