\section{Specialization to the literal fixed-shift packet}
\label{sec:physical}

We now insert the exact factors identified in TPC--53.  This section does
not alter the inherited coefficient class.

\subsection{The physical structural weights}

Fix the literal shift \(h_0\ne0\), the opposite-row box \(\cQ\), the
orbit interval \(I\), and the direct residue class \(a\) used in the
TPC--53 sampled carrier.  Fix one complete source dyadic/residue cell
\(\cM_X^{\rm full}\) on this carrier slice and its compatible subset
\(\cM_X^{\rm good}\).  Thus ``full'' below means complete only on the
source side of the declared slice, not the whole TPC--48 residual packet.
For a source row
\(m=d_m\ell_m\), with \(\ell_m\) prime and \(d_m\) squarefree, remove the
inherited factor \(\zeta_m^{(1)}\) and define
\begin{equation}
 u_m:=
 \left|
  \mu(d_m)(\log\ell_m)\omega_D(d_m)
  \psi_L(\ell_m/L)
 \right|^2.
 \label{eq:tpc54-source-base-weight}
\end{equation}
All fixed residue and smooth-shape restrictions are understood as part of
the declared source cell.  Let \(\cI_X\) be the retained pre-terminal set
of pairs \((m,r)\), let
\(N_r(m)=\#\{r:(m,r)\in\cI_X\}\), and let
\(\mathscr B_X^M(m)\ge0\) be the sampled carrier norm of TPC--53.  The
pre-terminal carrier is identical for every retained \(r\) over the same
source row; neither \(\mu(r)\Lambda(pr)\) nor any terminal prime weight is
included at this stage.  The exact factorization is
\begin{equation}
 b_m:=u_m\mathscr B_X^M(m),
 \qquad N_m:=N_r(m),
 \qquad w_m:=b_mN_m.
 \label{eq:tpc54-literal-w}
\end{equation}
Delete zero-weight rows by putting
\begin{equation}
 \cA_X:=\{m\in\cM_X^{\rm full}:w_m>0\},
 \qquad \cG_X:=\cA_X\cap\cM_X^{\rm good}.
 \label{eq:tpc54-active-source}
\end{equation}
Consequently the actual-coefficient-weighted carrier energy is
\begin{equation}
 \mathscr C_X
 =\sum_{m\in\cA_X}
   w_m|\zeta_m^{(1)}|^2,
 \label{eq:tpc54-literal-energy}
\end{equation}
and, whenever \(\mathscr C_X>0\), the compatible carrier-energy fraction is
\begin{equation}
 \sigma_X
 =\frac{
   \sum_{m\in\cG_X}w_m|\zeta_m^{(1)}|^2}
  {\mathscr C_X}.
 \label{eq:tpc54-literal-sigma}
\end{equation}
These formulas are simply the repeated orthogonal carrier normalization
on \((m,r)\) before the terminal prime map
\citep{WangTPC52,WangTPC53}.  The residual coordinate is not yet grouped.

TPC--53 proves, on a fixed interior compatible source/orbit box, a
pointwise sampled comparison
\begin{equation}
 \mathscr P_X^M(m)\ge\alpha_*\mathscr B_X^M(m),
 \qquad \alpha_*>0,\qquad m\in\cG_X,
 \label{eq:tpc54-profile-pointwise}
\end{equation}
for all large \(X\).  Define the exact unseparated physical-profile
energies by
\begin{align}
 \mathscr Q_X
 &:=\sum_{m\in\cA_X}
 u_mN_r(m)|\zeta_m^{(1)}|^2\mathscr P_X^M(m),
 \label{eq:tpc54-physical-total-energy}\\
 \mathscr Q_{X,\rm good}
 &:=\sum_{m\in\cG_X}
 u_mN_r(m)|\zeta_m^{(1)}|^2\mathscr P_X^M(m).
 \label{eq:tpc54-physical-good-energy}
\end{align}
Therefore any lower bound for \(\sigma_X\) implies the pre-terminal
physical-profile estimate
\begin{equation}
 \mathscr Q_{X,\rm good}
 \ge \alpha_*\sigma_X\mathscr C_X.
 \label{eq:tpc54-selected-profile}
\end{equation}
This implication is pointwise and has no local-to-global normalization
gap.

\subsection{Three coefficient regimes}

Assume \(\mathscr C_X>0\), and let \(C_X>0\) be any certified upper bound
such that \(|\zeta_m^{(1)}|\le C_X\) on the declared full source slice.
With the active carrier weights \(w_m\), define
\begin{equation}
 \delta_{{\rm cf},X}
 :=\frac{\sum_{m\in\cG_X}w_m}
         {\sum_{m\in\cA_X}w_m},
 \qquad
 \kappa_X
 :=\frac{\mathscr C_X}
 {C_X^2\sum_{m\in\cA_X}w_m}.
 \label{eq:tpc54-physical-delta-kappa}
\end{equation}
The universal sharp capacity theorem gives the valid physical
specialization
\begin{equation}
 \boxed{\quad
 \sigma_X\ge
 \left(1-\frac{1-\delta_{{\rm cf},X}}{\kappa_X}
 \right)_+.
 \quad}
 \label{eq:tpc54-physical-capacity}
\end{equation}

More precisely, \cref{thm:tpc54-exact-odds-factorization} applies with
reference row weight one on \(\cM_X^{\rm full}\), fixed base multiplier
\(b_m=u_m\mathscr B_X^M(m)\), amplitude
\(\zeta_m^{(1)}\), and occupancy \(N_m=N_r(m)\).  It gives the exact
identity
\begin{equation}
 \frac{\sigma_X}{1-\sigma_X}
 =\frac{\overline N_{\rm good}}{\overline N_{\rm bad}}
  \frac{\vartheta_{\rm good}}{\vartheta_{\rm bad}}
  \frac{\overline b_{\rm good}}{\overline b_{\rm bad}}
  \frac{|\cM_X^{\rm good}|}
       {|\cM_X^{\rm full}\setminus\cM_X^{\rm good}|},
 \label{eq:tpc54-physical-exact-odds}
\end{equation}
whenever all four factors are nondegenerate.  This identity is the exact
dictionary: raw row occupancy, carrier/source shape, coefficient
magnitude, and cofactor occupancy are separate.  The boundary cases are
handled by the good and bad carrier energies, not by assigning infinite
ratios.

This formula separates three cases.

\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.6em]
 \item For the full inherited class, only
       \(|\zeta_m^{(1)}|\le C_X\) is known.  Provided
       \(\cA_X\setminus\cG_X\ne\varnothing\), the bounded class permits a
       coefficient that vanishes on every good row and has
       \(\sigma_X=0\).  If \(\cA_X=\cG_X\), instead
       \(\delta_{{\rm cf},X}=\sigma_X=1\) for every positive carrier
       energy.
 \item Suppose a quantitative provenance calculation on a fixed direct
       residue cell verifies
       \[
        0<c_X\le|\zeta_m^{(1)}|\quad(m\in\cG_X),
        \qquad |\zeta_m^{(1)}|\le C_X\quad(m\in\cA_X).
       \]
       Then
       \[
       \sigma_X\ge
       \mathsf T_{(c_X/C_X)^2}(\delta_{{\rm cf},X}).
       \]
       Abstract diagonal unit phases attached to these coefficients do not
       change the conclusion.  The Mellin factors in the literal
       dictionary remain in the provenance measure or layer phase; no
       favorable Mellin layer is selected and no signed-reassembly lower
       bound is inferred.  The displayed floor is an extra checkable
       quantitative hypothesis, not a consequence of qualitative
       nonvanishing and not a theorem about every bounded inherited
       coefficient \citep{WangTPC25,WangTPC50}.
 \item If \(|\zeta_m^{(1)}|=C_X\) on the declared active packet, then
       \(\sigma_X=\delta_{{\rm cf},X}\) exactly.  Even here, source-row
       density alone does not control \(\delta_{{\rm cf},X}\) if
       cofactor multiplicities concentrate on bad rows.
\end{enumerate}

Alternatively, without a coefficient floor, the single scalar estimate
\begin{equation}
 \kappa_X>1-\delta_{{\rm cf},X}
 \label{eq:tpc54-physical-saturation-route}
\end{equation}
forces positive selection.  The threshold cannot be weakened using only
the displayed data.

\subsection{What geometric information already supplies}

Assume explicitly that the compatible source box contains a fixed
positive-volume subrectangle on which the declared unary source shapes
\(\omega_D\) and \(\psi_L\) are bounded away from zero.  Under this
compatibility hypothesis, the fixed-modulus prime--squarefree count and
weighted asymptotic of TPC--50 give
\begin{equation}
 \delta_{{\rm src},X}
 :=\frac{\sum_{m\in\cM_X^{\rm good}}u_m}
         {\sum_{m\in\cM_X^{\rm full}}u_m}
 \gg1.
 \label{eq:tpc54-source-fraction}
\end{equation}
This is a source-base statement, not yet a carrier statement
\citep{WangTPC50,WangTPC53}.

On the fixed sampled carrier slice, the carrier lower bound on the good
box, the global fixed-shape upper bound, and uniform mask count can be
recorded as
\begin{equation}
 B_-S_X\le\mathscr B_X^M(m)\quad(m\in\cM_X^{\rm good}),
 \qquad
 \mathscr B_X^M(m)\le B_+S_X\quad(m\in\cM_X^{\rm full}),
 \label{eq:tpc54-carrier-two-sided}
\end{equation}
with \(S_X>0\) and fixed \(0<B_-\le B_+<\infty\).  These are the sampled
two-sided carrier data required from the declared TPC--53 box; if they are
not verified for a larger full source slice, they must be retained as an
explicit hypothesis.  Define
\begin{equation}
 \delta_{{\rm car},X}
 :=\frac{\sum_{m\in\cM_X^{\rm good}}
 u_m\mathscr B_X^M(m)}
 {\sum_{m\in\cM_X^{\rm full}}u_m\mathscr B_X^M(m)}.
 \label{eq:tpc54-carrier-fraction}
\end{equation}
Then
\begin{equation}
 \delta_{{\rm car},X}
 \ge\mathsf T_{B_-/B_+}(\delta_{{\rm src},X})\gg1.
 \label{eq:tpc54-carrier-transport}
\end{equation}
Neither statement yet gives the cofactor-lifted fraction
\(\delta_{{\rm cf},X}\).

For example, suppose one additionally proves, for some scalar
\(R_X^{\rm occ}>0\), the balanced-occupancy condition
\begin{equation}
 n_-R_X^{\rm occ}\le N_m\le n_+R_X^{\rm occ}
 \quad\text{on every positive-carrier full source row},
 \qquad 0<n_-\le n_+<\infty.
 \label{eq:tpc54-balanced-occupancy}
\end{equation}
Then the sharp transport theorem gives
\begin{equation}
 \delta_{{\rm cf},X}
 \ge
 \frac{n_-\delta_{{\rm car},X}}
 {n_-\delta_{{\rm car},X}+n_+(1-\delta_{{\rm car},X})}.
 \label{eq:tpc54-physical-occupancy}
\end{equation}
Together with a fixed nonzero coefficient floor, this yields
\(\sigma_X\gg1\) and hence \eqref{eq:tpc54-selected-profile}.  The
inherited supported-pair interface permits arbitrary finite cofactor
multiplicity and does not prove \eqref{eq:tpc54-balanced-occupancy}.

There are therefore three honest ways to finish this selection subgate:
prove direct actual occupancy \(\delta_{{\rm cf},X}\gg1\); prove a
product-like estimate such as \eqref{eq:tpc54-balanced-occupancy}; or
construct a fixed finite compatible cover of every nonzero active carrier
and apply \cref{prop:tpc54-finite-cover}.  TPC--53 proves openness of one
active compatible set, not the third global cover.

\begin{remark}[Carrier versus cofactor balance]
The carrier factor in the literal dictionary is independent of the real
Mellin-layer parameter and is uniformly two-sided on the declared fixed
sampled cell.  This can reduce \eqref{eq:tpc54-balanced-occupancy} to a statement
about \(N_r(m)\) after all relevant cell-uniformity constants are recorded.
It does not itself establish that statement.
\end{remark}
