\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Prime-Weighted Transfer for Centered Sieve Kernels: Large-Sieve Fixed Shifts and Power-Short Shift Means},
 pdfauthor={Liang Wang},
 pdfsubject={Weighted centered sieve kernels, multiplicative large sieve, and prime-supported factor boxes},
 pdfkeywords={sieve kernel, multiplicative large sieve, von Mangoldt function, Dirichlet character, rough product}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\F}{\mathbb F}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cE}{\mathcal E}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cL}{\mathcal L}
\newcommand{\cP}{\mathcal P}
\newcommand{\whG}{\widehat G}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\E}{\mathbb E}

\title{\textbf{Prime-Weighted Transfer for Centered Sieve Kernels:}\\
\textbf{Large-Sieve Fixed Shifts and Power-Short Shift Means}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let $Q=\prod_{w<p\le w^2}p$, let $G=(\Z/Q\Z)^\times$, and let $K_h^\circ$ be the centered local kernel for the conditions $ab+h\not\equiv0\pmod p$, $p\mid Q$.  We develop a weighted transfer theory for the associated factor-box form.  The exact character expansion and fully active shift Parseval identity remain valid for arbitrary complex coefficients, while conductor localization permits two different analytic inputs.

First, exact-conductor orthogonality gives coefficient-uniform complete-shift cancellation.  If $I,J$ have lengths $M,N<Q$ and the coefficients have modulus at most one, then the normalized complete fully-active-shift mean square is
\[
 \ll \frac1{\max\{M,N\}}+\frac1{w\log w}.
\]
The same asymptotic cancellation holds on every interval of $\lfloor Q^{1/\log w}\rfloor$ shift parameters, with an explicit deterministic completion error.  Second, the classical multiplicative large sieve gives, uniformly for $(h,Q)=1$, a fixed-shift estimate of the shape
\[
 |\cB_h(a,b)|
 \ll \sqrt{E_aE_b}
 \left\{
  \frac{\sqrt{MN}}w+(\log Q)(\sqrt M+\sqrt N)+\sqrt Q
 \right\},
\]
where $E_a,E_b$ are the coefficient energies on the $Q$-unit support.  Thus arbitrary bounded coefficients have fixed-shift cancellation whenever the two lengths are power-sized and $MN/Q\to\infty$.

For von Mangoldt factor coefficients, we combine the same conductor decomposition with Siegel--Walfisz at small conductor.  On dyadic boxes $I=(X,2X]$, $J=(Y,2Y]$ with $X=Q^{\lambda+o(1)}$ and $Y=Q^{\nu+o(1)}$, double von Mangoldt weights have complete and subpower-shift mean-square cancellation for every fixed $0<\lambda,\nu<1$.  At a prescribed shift, including $h=2$, the conclusion holds when $\lambda+\nu>1$.  Removing prime powers yields an asymptotic count of prime pairs $(p,q)$ for which $pq+h$ avoids the primes in the window defining $Q$.

The target $pq+h$ is only required to be rough with respect to this finite window.  We do not prove that it is prime, do not estimate $\Lambda(n)\Lambda(n+2)$, and do not obtain a twin-prime lower bound.  The ambient-volume condition $MN/Q\to\infty$ at a fixed shift is imposed by the present large-sieve argument and is not an asserted barrier.
\end{abstract}

\noindent\textbf{Keywords:} centered sieve kernel; multiplicative large sieve; von Mangoldt weight; Dirichlet character; fixed shift; rough product.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35; Secondary 11L40, 11N13.

\input{sections/introduction-scope}
\input{sections/weighted-kernel-large-sieve}
\input{sections/prime-weighted-applications}
\input{sections/certificates-boundaries}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
