\section{Exact certificate and conclusion}
\label{sec:certificate-conclusion}

The analytic arguments above are symbolic.  We include a deterministic
finite certificate to audit the identities and rational exponent
ledger most vulnerable to sign, gcd, normalization, or boundary
errors.  It does not test the zero-free region, estimate a M\"obius
shell asymptotically, or sample primes for evidential purposes.

\subsection{Certificate}

The standard-library script
\begin{center}
 \texttt{experiments/tpc24\_certificate.py}
\end{center}
uses \texttt{fractions.Fraction} throughout.  It represents
\(\log n\) on the formal prime basis and represents products of two
divisor coefficients as exact degree-two polynomials in those formal
logarithms.  It checks:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item the exact finite-model density
 \eqref{eq:model-density-identity} on four primitive row models;
 \item both calibrated-prefix identities
 \eqref{eq:prefix-indicator} and \eqref{eq:prefix-increment} on the
 same models;
 \item the direct physical zero kernel
 \eqref{eq:zero-kernel} against its exact gcd reparametrization
 \eqref{eq:zero-gcd-reparametrization} on four finite families;
 \item the coefficient split \eqref{eq:a-gd-split} on every tested
 coprime squarefree pair;
 \item the asymmetric three-cell inequality on an exact rational grid;
 \item the specialization from \((\beta;s,t)\) to
 \((\beta,\delta,\xi)\), including the rational crossing sample
 \eqref{eq:rational-passage-sample};
 \item the hard-failure response \eqref{eq:fixed-modulus-failure},
 which is required to be nonzero with the predicted formal
 \(\log p\)-coefficient.
\end{enumerate}

Independent ordinary and \texttt{python -O} runs perform \(55{,}084\)
exact checks and produce byte-identical JSON.  The hashes are
\begin{center}
\scriptsize
\begin{tabular}{@{}ll@{}}
\toprule
JSON SHA-256
&\nolinkurl{f638ca06fa641a570277b89b1ed17d81aeac2eaa264cf80d5a317378efbd0fc6}\\
source SHA-256
&\nolinkurl{7b9ce64a93c5abb24c02ca9da6ea763fa5fbd97192bc1fd700fe47a7887ad33d}\\
certificate digest
&\nolinkurl{c684a7c10e7cf3bd2cc46f2305af94d8452f018494d445ecdd3483325df6f50d}\\
\bottomrule
\end{tabular}
\end{center}
The JSON records explicitly that the projective-mass condition is a
hypothesis and that the mass-sensitive zero term has not been deleted.
Its flags for asymptotic evidence, full residual closure,
Hardy--Littlewood, twin primes, and a general parity breakthrough are
all false.

\subsection{Conclusion}

The old Poisson-short boundary is not a wall for every residual
component.  Once the object is organized as an exact calibrated-prefix
increment, the misleading long single channel cancels algebraically.
The remaining nonzero joint spectrum has a rectangular true-conductor
decomposition, whose certified saving is
\eqref{eq:eta-asymmetric}.  Its physical zero mode has a different
mechanism: the complete long M\"obius shell cancels the common endpoint
constant for small shared factor, while the off-diagonal row
determinant controls large shared factor.

This proves a genuine support advance.  The explicit region
\eqref{eq:special-passage-window} contains parameters with
\(S=R<J<T\), for example \eqref{eq:rational-passage-sample}.  The
advance is stronger than a numerical observation: the nonzero spectrum
has fixed-power saving, and the zero kernel has the pointwise theorem
\eqref{eq:pointwise-zero-shell}.

The paper also preserves the exact remaining boundary.  Pointwise
shell cancellation becomes a packet estimate with the actual absolute
row mass \(\cZ_1\).  Fixed-polylogarithmic projective mass yields the
full logarithmic closure \eqref{eq:polylog-full-closure}; a mean-zero
test function yields the soft-mass closure
\eqref{eq:mean-zero-full-closure}.  Generic soft mass and nonzero
physical mean leave the explicit term in
\eqref{eq:mass-sensitive-main-theorem}.  Calling that term negligible
would require a new row-averaged zero-mode estimate, not a change of
notation.

The next useful target is therefore precise: prove cancellation of the
small-\(g\) zero kernel against the actual separated row family, or
derive a fixed-polylog projective decomposition for the relevant
packet, and then attack the both-new square.  Neither step is supplied
here.  In particular, this one-sided passage is not a twin-prime
theorem and is not described as a general breach of parity.
