\section{Exact splicing, a failed shortcut, and scope}
\label{sec:splicing-scope}

\subsection{Where the mixed increment sits in the residual}

Let \(U\) contain every positive target in the selected orbit packet.
By \eqref{eq:full-residual-prefix},
\begin{equation}
 P_{m,U}(j)=
 \Lambda(mj+h)-\Lambda_R(mj+h)-\delta_H(m).
 \label{eq:full-calibrated-residual}
\end{equation}
For \(R\le S<T\le U\), the prefix has the exact decomposition
\begin{equation}
 P_{m,U}=P_{m,S}+L_{m;S,T}+L_{m;T,U}.
 \label{eq:three-piece-prefix}
\end{equation}
Therefore a two-row residual product expands into nine explicitly
labelled pieces.  The present theorem treats
\begin{equation}
 P_{m,S}L_{n;S,T}
 \qquad\text{and, by transposition,}\qquad
 L_{m;S,T}P_{n,S}.
 \label{eq:treated-two-pieces}
\end{equation}
It does not estimate \(L_{m;S,T}L_{n;S,T}\), either component
involving \(L_{\cdot;T,U}\), or the already studied base product
\(P_{m,S}P_{n,S}\).  Consequently
\eqref{eq:polylog-full-closure} is a closure of a genuine residual
increment, but not a closure of the complete residual correlation from
TPC-18 \citep{WangTPC18}.

The shell lower endpoint is also structural.  In
\eqref{eq:inner-endpoint-difference}, the main constant in
\(A_M(Y)\) disappears only because the long divisor variable is summed
over the difference \((S/g,T/g]\).  Replacing that shell by a single
modulus destroys the mechanism.

\subsection{Pointwise calibration at a fixed modulus is false}

The last warning has a finite counterexample.  For a cutoff \(R\),
define the centered response of the complete short prefix to one
modulus \(v\) by
\begin{equation}
 \Gamma_R(v;\Delta)=
 \sum_{u\le R}\frac{b_R(u)}u
 \left((u,v)\one_{(u,v)\mid\Delta}-1\right),
 \label{eq:fixed-modulus-response}
\end{equation}
temporarily suppressing row coprimality.  Choose a prime
\(R/2<p\le R\), put \(v=p\), and take \(p\mid\Delta\).  For every
\(u\le R\) other than \(u=p\), either \((u,p)=1\), in which case the
bracket vanishes, or \(b_R(u)=0\) for a nonsquarefree multiple of
\(p\).  Since only \(b=1\) occurs in \eqref{eq:lambda-def},
\begin{equation}
 \lambda'_R(p)=-\frac p{p-1},
 \qquad
 b_R(p)=\log p+\frac p{p-1}.
 \label{eq:prime-edge-coefficient}
\end{equation}
Thus
\begin{equation}
 \Gamma_R(p;\Delta)
 =\frac{p-1}{p}b_R(p)
 =\left(1-\frac1p\right)\log p+1
 \asymp\log R.
 \label{eq:fixed-modulus-failure}
\end{equation}
Bertrand's postulate supplies such a prime for every sufficiently
large \(R\).  Hence a uniform assertion
\(\Gamma_R(v;\Delta)=o(1)\) is false.  This does not contradict
\cref{thm:pointwise-zero-shell}: that theorem retains the full outer
M\"obius shell and uses cancellation between its two endpoints.

\subsection{What is unconditional, conditional, and still open}

The result has three logically different levels.

\begin{enumerate}[label=\textup{(\arabic*)}]
 \item The prefix, four-channel, recombination, and gcd identities are
 finite and exact.  So are the fixed-modulus counterexample and the
 exponent ledger.
 \item The nonzero conductor theorem and pointwise zero-shell theorem
 are proved without conjectural number-theoretic input for packets
 satisfying the displayed primitive, smoothness, no-wrap, and
 fixed-power-range interfaces.  They use the primitive
 multiplicative large sieve and the classical zero-free region for
 \(\zeta(s)\), not a Chowla or Elliott conjecture.
 \item Full logarithmic closure for general \(\widehat F(0)\ne0\)
 additionally uses the explicit fixed-projective-mass hypothesis
 \eqref{eq:polylog-projective-mass}.  Under only the generic soft mass,
 the honest conclusion is \eqref{eq:mass-sensitive-main-theorem}; the
 mean-zero test-function corollary
 \eqref{eq:mean-zero-full-closure} remains fully closed.
\end{enumerate}

In particular, nothing here proves a Hardy--Littlewood asymptotic, a
positive lower bound for prime pairs, the twin-prime conjecture, or a
general violation of the sieve parity barrier.  The phrase ``passage
beyond the Poisson boundary'' refers only to the support coordinate
\(T>J\) in the calibrated mixed increment.

\subsection{The next precise gates}

The theorem leaves several separable research problems.
\begin{enumerate}[label=\textup{(\roman*)}]
 \item Replace absolute use of \(\cZ_1\) in
 \eqref{eq:mass-sensitive-zero} by a row-averaged operator or
 Hilbert--Schmidt estimate for the small-\(g\) kernel.  Such an estimate
 would remove the fixed-projective-mass hypothesis without requiring
 pointwise fixed-modulus calibration, which
 \eqref{eq:fixed-modulus-failure} rules out.
 \item Treat the both-new square
 \(L_{m;S,T}L_{n;S,T}\).  It has two long legs and no calibrated short
 prefix, so the present one-sided algebra does not apply.
 \item Reassemble the remaining \(L_{\cdot;T,U}\) complement fibers.
 TPC-23 identifies their affine M\"obius parity cocycle; polynomially
 uniform cancellation over those growing fibers remains open
 \citep{WangTPC23}.
 \item Only after these analytic components have compatible bounds may
 one return to the global endpoint and positivity ledgers.  A
 prime-pair main term is a separate stage, not a consequence of mixed
 shell cancellation alone.
\end{enumerate}

Each gate has a valid negative fallback: failure of a proposed uniform
estimate can be recorded by an exact obstruction such as
\eqref{eq:fixed-modulus-failure}, without being presented as evidence
for or against the twin-prime conjecture.
