\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\hypersetup{
 pdftitle={Recovery-Decorrelation Uncertainty at the Coherent Mobius Gate: Weighted Phase Frames, Sharp Fourier Frontiers, and Equality-Slice Rigidity},
 pdfauthor={Liang Wang},
 pdfsubject={Sharp recovery-coherence tradeoffs for equality-preserving phase banks at an orbit-sliced Mobius gate},
 pdfkeywords={Mobius correlation, phase frame, exact recovery, coherence, Fourier bank, CRT alias, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cW}{\mathcal W}
\newcommand{\cX}{\mathcal X}
\newcommand{\cY}{\mathcal Y}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\op}{\operatorname{op}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\Ran}{\operatorname{Ran}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\ee}[1]{\exp(2\pi i #1)}

\title{\textbf{Recovery--Decorrelation Uncertainty}\\
\textbf{at the Coherent M\"obius Gate:}\\
\textbf{Weighted Phase Frames, Sharp Fourier Frontiers,}\\
\textbf{and Equality--Slice Rigidity}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC--39 constructs a minimally sampled additive phase bank that recovers
the equality alias exactly.  Its positive square energy nevertheless
contains the original equality energy, and its determinant phases are
constant across physical rows at a fixed alias.  A natural continuation
is to add row phases and try to decorrelate the surviving cross--row
M\"obius form.  We prove a sharp obstruction to every such
coefficient--blind positive--energy scheme.

Let \(\Phi=(\phi_{t\alpha})\in\C^{m\times R}\) have unimodular entries,
let \(w_t>0\) with \(\sum_tw_t=1\), and suppose coefficients \(a_t\)
recover the coherent row sum universally:
\[
 \sum_{t=1}^m a_t\phi_{t\alpha}=1
 \qquad(1\le\alpha\le R).
\]
Define the recovery amplification and normalized row Gram by
\[
 \cA=\sum_t\frac{|a_t|^2}{w_t},
 \qquad
 G=\Phi^*\diag(w)\Phi.
\]
Then the exact Loewner domination
\[
 \boxed{G\succeq\cA^{-1}\one\one^*}
\]
holds.  Consequently
\[
 \cA\,\lambda_{\max}(G)\ge R,
 \qquad
 \sum_{\alpha\ne\beta}\operatorname{Re}G_{\alpha\beta}
 \ge R^2/\cA-R.
\]
The first inequality is a recovery--decorrelation uncertainty law.  It is
sharp at every integer point of its Pareto frontier: taking any \(r\)
rows of the \(R\)-point Fourier matrix, including the constant row, gives
\(\cA=r\) and \(\lambda_{\max}(G)=R/r\).

The equality cases are rigid.  Unit amplification \(\cA=1\) is possible
only when all phase columns are identical, in which case
\(G=\one\one^*\) and no row decorrelation occurs.  Conversely, complete
row orthogonality \(G=I_R\) forces \(\cA\ge R\), with equality for the
full Fourier bank.  We also prove a pseudoinverse formula for the optimal
amplification, an \(L^2\)-stable approximate--recovery version, and exact
diagonal invariance for Hilbert--valued row atoms.

Tensoring an arbitrary row bank with the \(q=L+1\) alias bank of TPC--39
does not alter this tradeoff.  The alias factor has unit amplification;
on the equality slice the tensor Gram is exactly \(G\).  More general
coupled row--alias phases obey the same lower bound after restriction to
the zero--alias slice.  Thus determinant twisting leaves maximal row
coherence, while Fourier row decorrelation pays back exactly its gain in
recovery amplification and leaves the atomic diagonal unchanged.

At the prime--M\"obius endpoint this closes a method class, not the
arithmetic gate.  It proves that universal phase geometry and a positive
square--energy estimate cannot by themselves remove the fixed--alias
cross--row form.  It does not prove a two-- or four--M\"obius correlation
estimate, a parity breach, a Hardy--Littlewood asymptotic, or the twin--prime
conjecture.  Any continuation inside this framework must break at least
one of its hypotheses; concrete options include using the actual
arithmetic coefficients, retaining a signed nonpositive functional, or
proving an equivalent coefficient--specific dispersion theorem.
\end{abstract}

\noindent\textbf{Keywords:}
M\"obius correlation; exact recovery; phase frame; coherent mode; Fourier
bank; CRT alias; parity boundary.

\medskip
\noindent\textbf{MSC 2020:}
Primary 42C15, 15A18; Secondary 11L07, 11N35, 42A16.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/weighted-phase-banks}
\input{sections/recovery-coherence-theorem}
\input{sections/fourier-extremizers}
\input{sections/approximate-recovery}
\input{sections/alias-tensor}
\input{sections/physical-endpoint}
\input{sections/superwindow-comparison}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references,references-extra}
\endgroup

\end{document}
