\section{Exact certificate, logical boundaries, and next gate}
\label{sec:tpc27-certificate-scope}

This final section separates finite algebra, imported analytic input,
new analytic output, and statements that remain open.

\subsection{Reproducible finite certificate}

The standard-library script
\begin{center}
 \texttt{experiments/tpc27\_certificate.py}
\end{center}
uses exact rational arithmetic and formal prime-log variables.  It
checks the Ramanujan compatibility resolution, the truncated and
complete finite-model multiple identities, the formal prime-multiple
identity, the Ramanujan-square zero factorization, the exact primitive
orbit bridge \(P=Z+E\), the four-channel algebra, and both rational exponent
ledgers.  It contains no floating-point tolerance and uses an explicit
exception-based checker, so optimization cannot delete a test.

Both
\[
 \begin{gathered}
 \texttt{python experiments/tpc27\_certificate.py},\\
 \texttt{python -O experiments/tpc27\_certificate.py}
 \end{gathered}
\]
complete \(20{,}540\) exact checks and produce the same JSON file.
\begin{samepage}
The recorded hashes are
\begin{center}
\footnotesize
\begin{tabular}{@{}>{\bfseries}l l@{}}
Source SHA-256 & \texttt{59afa0a8f94bc208297478d1fcc41e85}\\[-0.15em]
& \texttt{6cf88351c03bae3ef0e51690676a8e3d}\\
JSON SHA-256 & \texttt{dd7033c1a170a6ba968d4bc478841e19}\\[-0.15em]
& \texttt{978a5cbb38401a9c7d64681889bd2a48}\\
Certificate digest & \texttt{ae5b89520111cf8be04cc193e85cd197}\\[-0.15em]
& \texttt{b8159cbed1b9e0421b9d8f2a1af0e6c4}
\end{tabular}
\end{center}
\end{samepage}
The certificate controls finite algebra only; it is not asymptotic or
prime-pair evidence.

\subsection{Dependency and status ledger}

\begin{center}
\small
\begin{tabular}{
 >{\raggedright\arraybackslash}p{0.30\textwidth}
 >{\raggedright\arraybackslash}p{0.18\textwidth}
 >{\raggedright\arraybackslash}p{0.40\textwidth}}
\toprule
Item & Status & Source or limitation\\
\midrule
Ramanujan-square zero factorization & exact, unconditional &
\Cref{thm:tpc27-Ramanujan-square}; finite sums only\\
Finite-model multiple density & exact, unconditional &
\Cref{prop:tpc27-model-multiple}; completeness uses \(kdH\le R\)\\
Uniform prime-multiple calibration & proved imported input &
Classical zero-free region in the polynomial modulus range used by
TPC-20 and TPC-24\\
Centered physical base zero & closed here &
Off-diagonal mask, small/large \(k\) split, and actual row
\(\ell^1\)-mass\\
Centered physical base nonzero spectrum & closed by transfer &
TPC-22 when \(S=R\), TPC-23 when \(S>R\), with the TPC-25--26
continuous physical transfer\\
Scalar channels \(EZ,ZE,EE\) & closed here &
Uniform endpoint calibration and the strict Poisson-short orbit bound\\
Sample \((3/20,31/50,7/20,39/100)\) & fully closed selected square &
Centered nonzero conductor margin \(7/100\), annular margin \(1/100\),
and arbitrary logarithmic saving in the calibrated conclusion\\
High-\(\beta\) sample of TPC-26 & base open &
Its lower cutoff already satisfies \(S/J=X^{61/1200+o(1)}\)\\
Ultra-long complement and full residual & open &
Requires new cancellation for affine two-point M\"obius families\\
Positivity or Hardy--Littlewood main term & open &
Not implied by a selected cancellation bound\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Why the interfaces cannot be silently dropped}

Three finite examples isolate the logical boundaries.  First, if a
bilinear form is \(\mathfrak B(x,y)=xy\), taking
\(Z_1=Z_2=0\) and \(E_1=E_2=1\) makes the centered square vanish but
the physical square equal one.  Thus a centered estimate does not
restore the scalar channels.  Second, on an even orbit the two legs
\(C(j)=(-1)^j/2\) each have mean zero, while the additive zero mode of
\(C(j)^2\) is \(1/4\).  Separate centering does not remove the joint
zero frequency.  Third, on the row diagonal,
\(c_k(0)=\varphi(k)\), so the large-modulus \(K_0^{-1}\) tail used in
\cref{thm:tpc27-pointwise-base-zero} disappears.  These examples
explain, respectively, the explicit \(EZ,ZE,EE\) restoration, zero
extraction before separation, and the off-diagonal mask.

\subsection{Next analytic gate}

The next step has two branches: prove a centered nonzero base theorem
for \(S>J\), or isolate a verifiable affine two-point M\"obius subfamily
in the reflected complement.  Failure can yield a precise barrier
theorem; success would still require a separate positivity and
main-term mechanism before twin primes.
