\section{Introduction}
\label{sec:tpc27-introduction}

The primitive M\"obius-tail program of TPC-20--26 rewrites a selected
fixed-shift prime-pair residual as a bilinear correlation of opened rows
\[
 m=\ell d,
 \qquad \ell\asymp L\text{ prime},
 \qquad d\asymp D,
 \qquad Q=LD,
 \qquad QJ\asymp X.
\]
The common residual divisor coefficient is
\begin{equation}
 a(u)=-\mu(u)\log u,
 \qquad
 b_R(u)=a(u)-\lambda'_R(u),
 \qquad
 \lambda'_R(u)=0\quad(u>R).
 \label{eq:tpc27-intro-coefficients}
\end{equation}
TPC-20 derives the exact four-channel centered kernel, TPC-21 closes
its multiplicative-character mean at nonzero additive frequency, and
TPC-22--23 close the corresponding connected fiber discrepancy in
explicit short-support regions
\citep{WangTPC20,WangTPC21,WangTPC22,WangTPC23}.  TPC-24--26 then use
endpoint calibration and exact-conductor estimates to pass selected
cutoffs across the old Poisson face
\citep{WangTPC24,WangTPC25,WangTPC26}.

There is a precise logical gap between those statements.  The scalar
packets displayed and estimated in TPC-22--23 are sums over
\(r\ne0\).  Their formulas do not estimate the additive zero term
retained by the TPC-20 two-scale completion.  Moreover, the physical
prefix used in TPC-26 is calibrated rather than merely centered.  Thus
one cannot infer a physical base estimate by replacing the words
``centered selected square'' with ``calibrated square.''  Two separate
operations are required:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item close the connected additive zero mode of the centered square;
 \item restore the scalar calibration channels without losing the
 natural scale.
\end{enumerate}
The present paper performs both operations for the actual physical
opened-row provenance.

\subsection{The exact zero-mode factorization}

For one row put
\begin{equation}
 Z_{m,S}(j)=
 \sum_{\substack{u\le S\\(u,mH)=1}}
 b_R(u)C_{m,u}(j),
 \qquad
 C_{m,u}(j)=\one_{u\mid mj+h}-\frac1u.
 \label{eq:tpc27-intro-centered-signal}
\end{equation}
If \(m\ne n\), the primitive complete-period average of
\(C_{m,u}C_{n,v}\) is
\begin{equation}
 \frac1{uv}
 \left(g\one_{g\mid m-n}-1\right),
 \qquad g=(u,v).
 \label{eq:tpc27-intro-connected-zero}
\end{equation}
The elementary Ramanujan identity
\begin{equation}
 g\one_{g\mid\Delta}-1
 =\sum_{\substack{k\mid g\\k>1}}c_k(\Delta)
 \label{eq:tpc27-intro-Ramanujan-identity}
\end{equation}
turns the two-divisor zero kernel into a sum of products of one-row
multiple densities:
\begin{equation}
 \boxed{
 K_S^0(m,n)=
 \sum_{k>1}c_k(m-n)B_{k,S}(m)B_{k,S}(n).}
 \label{eq:tpc27-intro-factorization}
\end{equation}
Here
\begin{equation}
 B_{k,S}(m)=
 \sum_{\substack{u\le S\\k\mid u\\(u,mH)=1}}
 \frac{b_R(u)}u.
 \label{eq:tpc27-intro-Bk}
\end{equation}
The row coprimality restrictions separate exactly; there is no
approximation in \eqref{eq:tpc27-intro-factorization}.

This factorization changes the nature of the problem.  It is not
necessary to estimate the centered two-divisor kernel by an operator
norm.  Instead, one calibrates each short one-row multiple density.
For squarefree \(k\) coprime to the row, the finite model satisfies an
exact identity
\begin{equation}
 \sum_{\substack{u\le R\\k\mid u\\(u,mH)=1}}
 \frac{\lambda'_R(u)}u
 =\frac{\mu(k)}{\varphi(k)}\rho_{M,H,R}(m)
 \label{eq:tpc27-intro-model-multiple}
\end{equation}
whenever \(kdH\le R\).  The corresponding prime coefficient has main
term
\begin{equation}
 \sum_{\substack{u\le S\\k\mid u\\(u,mH)=1}}
 \frac{a(u)}u
 =\frac{\mu(k)}{\varphi(k)}\rho_{P,H}(m)
 +O_A\!\left(
 \frac{\rho_{P,H}(m)(1+\log k)}
 {\varphi(k)(\log X)^A}\right).
 \label{eq:tpc27-intro-prime-multiple}
\end{equation}
Their difference is the already power-saving row drift
\[
 \delta_H(m)=\rho_{P,H}(m)-\rho_{M,H,R}(m)
 \ll \frac{\log\log(3X)}L.
\]

Choose \(K_0=X^\kappa\) below \(R^{1/2}\).  The identities above
control \(k\le K_0\).  For \(k>K_0\), the cofactor estimate
\begin{equation}
 |B_{k,S}(m)|\ll \frac{(\log X)^4}{k}
 \label{eq:tpc27-intro-large-B}
\end{equation}
and the off-diagonal relation \(m-n\ne0\) give
\begin{equation}
 \sum_{k>K_0}\frac{|c_k(m-n)|}{k^2}
 \ll X^{o(1)}K_0^{-1}.
 \label{eq:tpc27-intro-Ramanujan-tail}
\end{equation}
This proves the pointwise zero theorem
\begin{equation}
 K_S^0(m,n)
 \ll_A(\log X)^{-A}
 +L^{-2}(\log\log(3X))^3+X^{-\kappa+o(1)}.
 \label{eq:tpc27-intro-zero-theorem}
\end{equation}
The condition \(m\ne n\) is structural.  When \(m=n\), one has
\(c_k(0)=\varphi(k)\), and the large-\(k\) argument does not give
\eqref{eq:tpc27-intro-Ramanujan-tail}.

\subsection{From the centered base to the physical prefix}

TPC-24's exact calibration identity on the primitive orbit
\((j,H)=1\) is
\begin{equation}
 P_{m,S}(j)=Z_{m,S}(j)+E_S(m),
 \qquad
 E_S(m)=A_{mH}(S)-\rho_{P,H}(m).
 \label{eq:tpc27-intro-PZE}
\end{equation}
The classical zero-free region gives
\(E_S(m)\ll_A(\log X)^{-A}\), uniformly in the polynomial
row ranges used here.  Therefore
\begin{equation}
 P_{m,S}P_{n,S}
 =ZZ+EZ+ZE+EE.
 \label{eq:tpc27-intro-four-scalar-channels}
\end{equation}
The last three terms are bounded before spectral separation.  The
actual one-row absolute masses are \(O(Q)\), while
\[
 \sum_j|Z_{m,S}(j)|\,|F(j/J)|
 \ll (J+S)(\log(2X))^4.
\]
Thus the scalar channels have arbitrary logarithmic saving whenever
\(S\le JX^{-\eta_0}\).  This is precisely the strict Poisson-short
condition already required by the dynamic nonzero theorem.

For the \(ZZ\) term, physical frequency zero is extracted before
Mellin separation.  The new pointwise bound
\eqref{eq:tpc27-intro-zero-theorem} combines with the actual
\(O(Q^2)\) row-pair absolute mass.  Only the nonzero spectrum is then
sent through the applicable TPC-22 static or TPC-23 dynamic conductor
theorem.  The correct order is
\begin{equation}
 \boxed{
 \begin{gathered}
 \text{extract and factor the centered physical zero mode}\\
 \longrightarrow\ \text{calibrate its one-row multiples}\\
 \longrightarrow\ \text{separate the nonzero spectrum}\\
 \longrightarrow\ \text{restore }EZ,ZE,EE.
 \end{gathered}}
 \label{eq:tpc27-intro-order}
\end{equation}

\subsection{Consequences and boundary}

Write
\begin{equation}
 Q=X^{\beta+o(1)},
 \qquad J=X^{1-\beta+o(1)},
 \qquad S=X^{s+o(1)}.
 \label{eq:tpc27-intro-exponents}
\end{equation}
Under the inherited no-wrap, physical provenance, off-diagonal mask,
and fixed-margin hypotheses, the base closes when
\begin{equation}
 s<1-\beta,
 \qquad
 \eta_S(\beta,s)=
 \min\left\{
 1-\frac{3\beta}{2},
 \frac{\beta+1-4s}{2},
 \frac{3-\beta-6s}{4}
 \right\}>0.
 \label{eq:tpc27-intro-base-region}
\end{equation}
Combining this with the TPC-26 annular theorem closes a selected
calibrated square at an upper cutoff \(T=X^{t+o(1)}>J\) whenever its
annular minimax \(M_\beta(t)\) is positive.  The sample
\begin{equation}
 (\delta,\beta,s,t)=
 \left(\frac3{20},\frac{31}{50},\frac7{20},\frac{39}{100}\right)
 \label{eq:tpc27-intro-strict-sample}
\end{equation}
has centered nonzero conductor ledger margin \(7/100\) and annular
minimax margin \(1/100\); the complete calibrated conclusion has arbitrary
logarithmic saving.

This does not make the higher-\(\beta\) cutoff-stability sample of
TPC-26 into a closed square.  In that sample \(S>J\), so the inherited
base nonzero theorem is unavailable.  Nor does the argument estimate
the ultra-long complement after the upper cutoff.  It proves one
selected physical upper-bound/cancellation statement; it does not
produce positivity, a Hardy--Littlewood main term, twin primes, or a
general breach of sieve parity.

The paper is organized as follows.  \Cref{sec:tpc27-interface-bridge}
fixes the physical packet and the exact centered-to-calibrated bridge.
\Cref{sec:tpc27-Ramanujan-factorization} proves the zero-mode
factorization.  \Cref{sec:tpc27-multiple-calibration} proves the exact
model-multiple identity and its calibrated prime companion.
\Cref{sec:tpc27-base-zero-closure} obtains the pointwise and physical
zero theorems.  \Cref{sec:tpc27-nonzero-scalar} transfers the inherited
nonzero theorem and closes the scalar channels.
\Cref{sec:tpc27-passage-theorem} gives the base and upper-cutoff
closure, and \cref{sec:tpc27-certificate-scope} records the exact
certificate and strict scope.
