\begin{abstract}
Let \(F\) be the atomic-normalized missing-native incidence at one fixed
nonzero shift and write its Gram as
\[
 F^*F=I+R+E.
\]
Here \(R\) contains collisions already present at a common residual output
\((i,s)\), whereas \(E\) contains the unequal-residual cross terms created
when \(s\) is erased inside a complete native key \(i\).  This paper
resolves the exact algebra of mixed \(R/E\) operator words without asserting
an arithmetic cancellation estimate.

First, we decompose \(R=\sum_iR_i\) and \(E=\sum_iE_i\) over complete native
keys.  The matrix \(R_i\) is block diagonal in the residual partition at
\(i\), while \(E_i\) is strictly off block.  Consequently
\[
 \tr(E_iR_i^a)=0\qquad(a\ge0).
\]
In particular, the half-sector \(\tr(ER)\) in the full mixed
second-moment coefficient \(S_{2,1}=2\tr(ER)\) is not a one-key
phenomenon:
\[
 \tr(ER)=\sum_{i\ne j}\tr(E_iR_j).
\]
Its literal terms are two-key, two-row rectangles.  After the source-row
gauge is removed, their four target Möbius signs reduce to the two residual
signs on the unequal-residual edge.  The remaining complex coefficient is
a gauge-invariant cross-key holonomy.

Second, we give the exact cyclic sector formula for the coefficient
\(S_{k,b}\) of \(t^b\) in
\(\tr(R+tE)^k\).  The one-erasure sector is
\[
 S_{k,1}=k\tr(R^{k-1}E).
\]
On every same-residual edge the residual sign factor is one; after the
complete decorated walk is closed, all source-row gauges telescope.  The
remaining target-sign product is exactly the product of \(\mu(s)\) over
the odd-degree boundary of the multigraph of erasure-edge residual labels.
Thus the number of erasure edges alone does not decide whether the signs
freeze.

Third, although individual two-erasure words may be signed, their complete
even-moment sector is nonnegative:
\[
 S_{2q,2}\ge0.
\]
We prove this by diagonalizing \(R\) and identifying the coefficient with
the nonnegative divided difference of the odd increasing function
\(x^{2q-1}\).  Hence the quadratic erasure response cannot supply a negative
moment correction; any favorable signed response must enter through the
linear sector or higher sectors.  Local star compensation, cross-key
countermodels, determinant reindexing, and the remaining arithmetic and
shorted-reassembly gates are recorded explicitly.  The matrix and sector
identities are L0, their complete fixed-shift carrier and target-sign
identifications are L1, and every uniform Möbius saving remains an unproved
L2 input.
\end{abstract}
