\section{Separating countermodels}
\label{sec:countermodels}

The following finite-dimensional examples test the exact logical boundary
of the preceding identities.  They are not asserted to be realizations of
the full arithmetic carrier.

\begin{example}[One key can contain both defects but no local mixed trace]
\label{ex:one-key-both-defects}
Take one native key \(i\), three rows, amplitudes
\[
 f_i=(1,1,1),
\]
and residual classes
\[
 A_{i,a}=\{1,2\},\qquad A_{i,b}=\{3\}.
\]
Then \(R_i\) contains the edge \(1\leftrightarrow2\), while \(E_i\)
contains the edges \(1\leftrightarrow3\) and
\(2\leftrightarrow3\).  Both matrices are nonzero.  Nevertheless,
\[
 \tr(E_iR_i^a)=0
\]
for every \(a\ge0\), because \(R_i^a\) remains inside the two residual
blocks and \(E_i\) crosses them.  Thus the local vanishing theorem is not
the trivial assertion that one of the two matrices is zero.
\end{example}

\begin{example}[Two keys create the first mixed rectangle]
\label{ex:two-key-first-rectangle}
Take two rows and two native keys \(i,j\), with
\[
 f_i=2^{-1/2}(1,1),\qquad
 f_j=2^{-1/2}(1,1).
\]
At \(i\), give the two rows different residual labels; at \(j\), give them
the same residual label.  Each normalized row has total squared mass one.
The only nonzero off-diagonal entries are
\[
 (E_i)_{12}=\frac12,\qquad
 (R_j)_{12}=\frac12.
\]
Hence
\[
 \tr(E_iR_j)=\frac12\ne0.
\]
The full Gram is positive because it is assembled from the two key
incidences.  This disproves any inference from one-key vanishing to global
Hilbert--Schmidt orthogonality.
\end{example}

\begin{example}[Same support and magnitudes, opposite holonomy]
\label{ex:holonomy-phase}
Keep the preceding support and residual partitions, but put
\[
 f_i=2^{-1/2}(1,1),\qquad
 f_j=2^{-1/2}(1,e^{\mathrm i\theta}).
\]
Then
\[
 \tr(E_iR_j)=\frac12\cos\theta.
\]
At \(\theta=0\), \(R_j\) and \(E_i\) reinforce and the full defect has
off-diagonal entry one.  At \(\theta=\pi\), they cancel and the full defect
vanishes.  The two models have identical key support, residual partitions,
atomic magnitudes, and row masses.  Their difference is exactly the
rectangle holonomy.
\end{example}

\begin{example}[Zero global cross trace with a large local star]
\label{ex:global-cross-trace-zero}
Take the orthogonal direct sum of two copies of
\cref{ex:holonomy-phase}: use \(\theta=0\) on rows \(1,2\) and
\(\theta=\pi\) on rows \(3,4\).  The two cross traces are \(1/2\) and
\(-1/2\), so
\[
 \tr(ER)=0.
\]
On the first component the full defect has off-diagonal entry one, while
on the second it vanishes.  Therefore
\[
 s_1(H)=s_2(H)=1,\qquad \|H\|=1.
\]
Global rectangle cancellation gives no uniform local compensation.
\end{example}

\begin{example}[Erasure-edge parity is not sign parity]
\label{ex:E-count-parity}
Assign residual endpoint pairs
\[
 (a,b),(b,c)
\]
to two erasure edges.  Their sign is \(\mu(a)\mu(c)\), not identically one.
By contrast, the three erasure edges
\[
 (a,b),(b,c),(c,a)
\]
have sign one.  Thus evenness of the number of erasure edges is neither
necessary nor sufficient for an algebraically frozen target sign.
\end{example}

\begin{example}[Averaged second trace can miss a fixed obstruction]
\label{ex:normalized-trace}
Let \(H_r\) be the \(r\times r\) Hermitian matrix whose only nonzero block
is
\[
 \begin{pmatrix}0&1\\1&0\end{pmatrix}
\]
on the first two rows.  Then
\[
 \|H_r\|=1,\qquad
 \tr H_r^2=2,\qquad
 \frac1r\tr H_r^2\longrightarrow0.
\]
An averaged row or normalized moment estimate therefore cannot replace an
unnormalized operator certificate.
\end{example}

\begin{remark}[Scope of the countermodels]
The examples prove non-implications for the finite-dimensional interface.
They neither show that the actual fixed-shift carrier realizes the bad
phases nor show that it avoids them.  Deciding that question requires the
literal arithmetic weights and is L2.
\end{remark}
