\section{Introduction}
\label{sec:introduction}

TPC--61 identifies the exact atomic-normalized native Gram of the
missing-high carrier and splits its off-diagonal alias operator into
same-residual and unequal-residual parts \citep{WangTPC61}.  TPC--68 removes
the fixed source-row Möbius gauge, exposes the two-affine target signs, and
develops pair, star, Perron, and operator-walk certificates
\citep{WangTPC68}.  It also proves a decisive negative fact: on a
same-residual collision, the two target signs freeze.  Therefore the
same-residual operator has no cancellation coming from those signs alone.

The next question is not whether one can rename the unequal-residual terms
as a signed perturbation.  That is immediate.  The useful question is
\emph{where the first genuinely new sign survives after the full operator
product is expanded}.  A one-edge calculation does not answer it, because
operator moments join several collision edges through common source rows,
and the complete native key can change from edge to edge.

We write
\[
 R:=H_{\rm res},\qquad E:=H_{\rm erase},\qquad H=R+E.
\]
This notation is used only after the residual erasure map has been defined;
it must not be confused with the represented carrier or with that map.
The two defects act on the same active row space.  They are separated by
residual labels at the atomic output level, but they are not automatically
orthogonal as matrices on the source-row space.

\subsection{Main algebraic results}

The first result is a key-local decomposition.  For every complete native
key \(i\), the fixed-\((i,m)\) singleton property gives one normalized
amplitude \(f_i(m)\), or zero, for each source row.  The residual label
\(s_i(m)\) partitions the active rows at that key.  We construct
\[
 R=\sum_iR_i,\qquad E=\sum_iE_i,
\]
where \(R_i\) is block diagonal and \(E_i\) is off block with respect to
that partition.  It follows that
\[
 \tr(E_iP(R_i))=0
\]
for every polynomial \(P\).  The first mixed trace is therefore
\[
 \tr(ER)=\sum_{i\ne j}\tr(E_iR_j).
\]
Each term uses two rows and two distinct complete native keys.  Its four
literal amplitudes form a rectangle, and their product is invariant under
both row phases and output-key phases.  We call this product the
\emph{cross-key holonomy}.

The second result organizes every noncommutative mixed moment.  If
\[
 \tr(R+tE)^k=\sum_{b=0}^kt^bS_{k,b},
\]
then, for \(1\le b\le k\),
\[
 S_{k,b}
 =
 \frac{k}{b}
 \sum_{\substack{a_1+\cdots+a_b=k-b\\a_\nu\ge0}}
 \tr\!\left(
 E R^{a_1}E R^{a_2}\cdots E R^{a_b}
 \right).
\]
No commutativity is assumed.  This is a marked-erasure counting identity.
It gives \(S_{k,1}=k\tr(R^{k-1}E)\) and isolates the first mixed signed
sector.

The third result evaluates the signs in every decorated closed walk.  An
erasure edge has two unequal residual endpoints.  Form the multigraph whose
vertices are the integer residual labels and whose edges are these endpoint
pairs.  The complete product of target Möbius signs is
\[
 \prod_{\deg_E(s)\ {\rm odd}}\mu(s).
\]
All source-row gauges and all same-residual signs have disappeared
exactly.  Thus a residual Eulerian subgraph forces sign \(+1\), while a
nonempty residual boundary is the only place where the target signs can
remain algebraically nontrivial.

Finally, the complete exactly-two-erasure sector in every even trace is
nonnegative:
\[
 S_{2q,2}\ge0.
\]
This is not a heuristic positivity statement about individual decorated
walks.  It follows from the exact formula
\[
 S_{2q,2}
 =
 q\sum_{\alpha,\beta}|E_{\alpha\beta}|^2
 \frac{\lambda_\alpha^{2q-1}-\lambda_\beta^{2q-1}}
      {\lambda_\alpha-\lambda_\beta},
\]
where \(\lambda_\alpha\) are the eigenvalues of \(R\) and the diagonal
quotient has its derivative value.  The divided difference is nonnegative
because \(x^{2q-1}\) is increasing on the real line.

\subsection{What these results do and do not change}

The paper advances the operator interface in three ways.  It shows that the
first mixed second moment is necessarily cross-key; it reduces every closed
walk sign to a residual boundary; and it proves that the full quadratic
erasure response in an even moment cannot be negative.  These facts remove
several possible but incorrect proof shortcuts.

They do not estimate the resulting arithmetic sums.  In particular, this
paper proves none of the following:
\[
 \tr(R^{2q-1}E)=o(\text{absolute majorant}),\qquad
 \|R+E\|=X^{o(1)},\qquad
 \|C_N\|=o(1).
\]
It also proves no missing-mass saving, represented lower frame, parity
estimate, prime-pair theorem, or twin-prime conclusion.  The fixed shift is
never averaged and is not silently specialized to \(2\).

\subsection{Organization}

\Cref{sec:literal-interface} freezes the complete physical carrier.
\Cref{sec:key-local} proves the key-local diagonal/off-block decomposition.
\Cref{sec:mixed-words} gives the cyclic sector formula.
\Cref{sec:residual-boundary} proves the residual-boundary sign theorem.
\Cref{sec:cross-key} derives the exact two-key rectangle and its direct-cell
form.  \Cref{sec:quadratic-response} proves positivity of the quadratic
even-moment response.  \Cref{sec:local-star} separates local compensation
from global trace cancellation.  Countermodels and the conditional
arithmetic ledger follow, and the final section records L0, L1, L2, and
endpoint boundaries.
