\section{Key-local residual blocks and erasure links}
\label{sec:key-local}

This section proves that one erasure edge cannot close against powers of
the same native-key residual operator.  The conclusion is purely
finite-dimensional and uses the complete key rather than a reduced
collision cell.

\subsection{The residual partition at one native key}

For a native key \(i\), let
\[
 A_i:=\{m\in\cM_M:f_i(m)\ne0\}.
\]
For \(m\in A_i\), let \(s_i(m)\) denote the residual label of the unique
atom selected by \((i,m)\).  Extend \(f_i\) by zero to all of \(S_M\), and
put
\begin{equation}
 D_i:=\diag\bigl(|f_i(m)|^2\bigr)_{m\in\cM_M}.
 \label{eq:key-local-diagonal}
\end{equation}
Define two positive matrices by their entries:
\begin{align}
 (K_i)_{mn}
 &:=\overline{f_i(m)}f_i(n),
 \label{eq:key-native-Gram}\\
 (K_i^{\rm res})_{mn}
 &:=
 \one_{\{s_i(m)=s_i(n)\}}
 \overline{f_i(m)}f_i(n),
 \label{eq:key-residual-Gram}
\end{align}
where an indicator is zero if either amplitude vanishes.  Equivalently,
if
\[
 A_{i,s}:=\{m\in A_i:s_i(m)=s\},
\]
then \(K_i^{\rm res}\) is the orthogonal direct sum of the rank-one Grams
on the coordinate spaces \(\ell^2(A_{i,s})\).

\begin{definition}[Key-local defects]
\label{def:key-local-defects}
Set
\begin{equation}
 R_i:=K_i^{\rm res}-D_i,
 \qquad
 E_i:=K_i-K_i^{\rm res}.
 \label{eq:key-local-defects}
\end{equation}
\end{definition}

Thus \(R_i\) has the same-residual off-diagonal entries at \(i\), and
\(E_i\) has the unequal-residual entries at \(i\).  Both have zero
diagonal.

\begin{proposition}[Exact complete-key decomposition]
\label{prop:complete-key-decomposition}
On \(S_M\),
\begin{equation}
 \boxed{
 \sum_iD_i=I,\qquad
 R=\sum_iR_i,\qquad
 E=\sum_iE_i.}
 \label{eq:complete-key-decomposition}
\end{equation}
Every sum is over the actual complete native output keys.
\end{proposition}

\begin{proof}
For a fixed active row \(m\), the fixed-\((i,m)\) singleton property and
\eqref{eq:gauged-key-amplitude} give
\[
 \sum_i|f_i(m)|^2
 =
 \frac1{W_m}
 \sum_{\substack{w\in\cW_M\\m(w)=m}}|\beta_w|^2
 =1.
\]
This proves \(\sum_iD_i=I\).  Summing \(K_i^{\rm res}\) over \(i\) gives
the normalized residual Gram \(I+R\), because equality of both \(i\) and
\(s\) is precisely equality of the residual output.  Summing \(K_i\)
gives the native Gram \(I+R+E\).  Subtracting the diagonal identity proves
the other two formulas.
\end{proof}

\subsection{The local off-block theorem}

Let
\begin{equation}
 \mathscr P_i
 :=
 \bigoplus_s\ell^2(A_{i,s})
 \oplus\ell^2(A_i^c)
 \label{eq:residual-coordinate-partition}
\end{equation}
be the coordinate decomposition induced by residual labels at \(i\).
Relative to \(\mathscr P_i\), \(R_i\) is block diagonal.  The diagonal
blocks of \(E_i\), including the \(A_i^c\)-block, are zero.

\begin{theorem}[One-key mixed traces vanish]
\label{thm:one-key-mixed-trace}
For every complete native key \(i\) and every integer \(a\ge0\),
\begin{equation}
 \boxed{\tr(E_iR_i^a)=0.}
 \label{eq:one-key-mixed-trace}
\end{equation}
More generally,
\begin{equation}
 \tr(E_iP(R_i))=0
 \label{eq:polynomial-local-vanishing}
\end{equation}
for every polynomial \(P\).
\end{theorem}

\begin{proof}
Every power of the block-diagonal matrix \(R_i\) is block diagonal relative
to \(\mathscr P_i\).  The product of the strictly off-block matrix \(E_i\)
with a block-diagonal matrix has zero diagonal blocks and hence zero trace.
Linearity gives the polynomial statement.  The case \(a=0\) is simply
\(\tr E_i=0\).
\end{proof}

\begin{corollary}[The first mixed trace is cross-key]
\label{cor:first-mixed-cross-key}
One has
\begin{equation}
 \boxed{
 \tr(ER)=\sum_{\substack{i,j\\i\ne j}}\tr(E_iR_j).}
 \label{eq:first-mixed-cross-key}
\end{equation}
\end{corollary}

\begin{proof}
Expand \(E=\sum_iE_i\) and \(R=\sum_jR_j\).  The terms with \(i=j\)
vanish by \cref{thm:one-key-mixed-trace} with \(a=1\).
\end{proof}

\begin{remark}[Disjoint pair lists do not imply matrix orthogonality]
\label{rem:not-HS-orthogonal}
At one key, an atom pair cannot be simultaneously equal-residual and
unequal-residual.  This set-theoretic disjointness proves
\(\tr(E_iR_i)=0\).  It does not prove \(\tr(ER)=0\), because \(E_i\) and
\(R_j\) with \(i\ne j\) are matrices on the same row space and may occupy
the same row-pair entry.
\end{remark}

\subsection{Higher one-erasure words}

The local theorem removes only the word whose erasure edge and all residual
edges carry the same native key.  Indeed,
\begin{equation}
 \tr(ER^{k-1})
 =
 \sum_{i,j_1,\ldots,j_{k-1}}
 \tr(E_iR_{j_1}\cdots R_{j_{k-1}}).
 \label{eq:key-expansion-one-erasure}
\end{equation}
The term with \(j_1=\cdots=j_{k-1}=i\) vanishes.  Other key sequences need
not vanish, even if some adjacent keys agree.  Thus the one-erasure sector
of a longer moment is a cross-key polygon rather than a one-key ladder.

\begin{remark}[Why complete keys matter]
If side, external block, opposite row, \(\gamma\), or orbit time is removed
from \(i\), two different physical output coordinates can be placed in one
artificial local block.  The proof of
\eqref{eq:one-key-mixed-trace} would then concern the compressed model, not
the native Gram.  Conversely, splitting one actual key into coefficient-
dependent subkeys would manufacture orthogonality.  Neither operation is
allowed.
\end{remark}
