\section{Cyclic sectors of noncommutative mixed words}
\label{sec:mixed-words}

We now organize all words in \(R\) and \(E\) before using their arithmetic
entries.  The identities in this section hold for arbitrary finite square
matrices for which the displayed traces are defined.

\subsection{The erasure-count generating polynomial}

For integers \(k\ge1\) and \(0\le b\le k\), define
\begin{equation}
 S_{k,b}
 :=
 \sum_{\substack{\omega\in\{R,E\}^k\\|\omega|_E=b}}
 \tr(H_{\omega_1}\cdots H_{\omega_k}),
 \qquad H_R=R,\quad H_E=E.
 \label{eq:sector-definition}
\end{equation}
Equivalently,
\begin{equation}
 \tr(R+tE)^k
 =
 \sum_{b=0}^kt^bS_{k,b}.
 \label{eq:sector-generating-polynomial}
\end{equation}
The order of the letters is retained in
\eqref{eq:sector-definition}; no binomial commutativity is assumed.

\begin{theorem}[Exact cyclic erasure-sector formula]
\label{thm:cyclic-sector}
For \(1\le b\le k\),
\begin{equation}
 \boxed{
 S_{k,b}
 =
 \frac{k}{b}
 \sum_{\substack{a_1+\cdots+a_b=k-b\\a_\nu\ge0}}
 \tr\!\left(
 E R^{a_1}E R^{a_2}\cdots E R^{a_b}
 \right).}
 \label{eq:cyclic-sector-formula}
\end{equation}
Also \(S_{k,0}=\tr R^k\).
\end{theorem}

\begin{proof}
Mark one of the \(b\) occurrences of \(E\) in every word contributing to
\(S_{k,b}\).  This produces \(b\) marked copies of each linear word.  Rotate
a marked word so that its marked \(E\) is first.  The numbers of consecutive
\(R\)'s after the successive \(E\)'s form a weak composition
\[
 a_1+\cdots+a_b=k-b.
\]
Conversely, a weak composition and one of the \(k\) possible rotation
offsets reconstruct a marked linear word.  Trace cyclicity makes all
rotations have the displayed trace.  Therefore \(bS_{k,b}\) is \(k\)
times the sum over weak compositions, proving
\eqref{eq:cyclic-sector-formula}.  The counting remains valid for periodic
words because the marked occurrence and rotation offset are retained.
\end{proof}

\begin{corollary}[The one- and two-erasure sectors]
\label{cor:first-two-sectors}
For \(k\ge2\),
\begin{align}
 S_{k,1}
 &=\boxed{k\tr(ER^{k-1})},
 \label{eq:one-erasure-sector}\\
 S_{k,2}
 &=\boxed{
 \frac{k}{2}
 \sum_{a=0}^{k-2}
 \tr(E R^aE R^{k-2-a}).}
 \label{eq:two-erasure-sector}
\end{align}
\end{corollary}

The first two even expansions are
\begin{align}
 \tr(R+E)^2
 &=
 \tr R^2+2\tr(RE)+\tr E^2,
 \label{eq:second-moment-expansion}\\
 \tr(R+E)^4
 &=
 \tr R^4
 +4\tr(R^3E)
 +4\tr(R^2E^2)
 +2\tr(RERE)
 +4\tr(RE^3)
 +\tr E^4.
 \label{eq:fourth-moment-expansion}
\end{align}
The two distinct two-erasure necklaces in
\eqref{eq:fourth-moment-expansion} must not be merged before their traces
are evaluated.

\subsection{Key expansion of the one-erasure sector}

Combining \cref{prop:complete-key-decomposition,cor:first-two-sectors}
gives
\begin{equation}
 S_{k,1}
 =
 k
 \sum_{i,j_1,\ldots,j_{k-1}}
 \tr(E_iR_{j_1}\cdots R_{j_{k-1}}).
 \label{eq:key-expanded-linear-sector}
\end{equation}
By \cref{thm:one-key-mixed-trace}, the fully local term
\[
 \tr(E_iR_i^{k-1})
\]
vanishes.  Hence each surviving decorated contribution changes complete
native key at least once.  At \(k=2\) this forces two distinct keys exactly.
For \(k>2\), it produces cross-key polygons with one off-residual edge.

\begin{remark}[Sector control versus moment control]
A bound for \(S_{2q,1}\) alone is not a bound for
\(\tr(R+E)^{2q}\).  The zero-erasure sector, the nonnegative quadratic
sector proved in \cref{sec:quadratic-response}, and all higher sectors
remain.  Conversely, a bad estimate for one sector does not prove that the
full moment is large, because different sectors can cancel after \(t\) is
set to one.  A valid moment argument must state which sectors are bounded
absolutely and which are combined with their literal signs.
\end{remark}

\subsection{Decorated key words}

For later use, a decorated realization of a word consists of:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item a row path \(m_0,m_1,\ldots,m_k\);
 \item a complete native key \(i_\ell\) on each edge;
 \item the unique atoms \(w_{\ell,-}\), \(w_{\ell,+}\) at
       \((i_\ell,m_{\ell-1})\) and \((i_\ell,m_\ell)\); and
 \item the condition
       \[
       s(w_{\ell,-})=s(w_{\ell,+})
       \quad\Longleftrightarrow\quad \omega_\ell=R.
       \]
\end{enumerate}
The row path joins edges, but it does not identify their keys, atoms,
times, residual labels, sides, or \(\gamma\)-coordinates.  This distinction
is responsible for both the cross-key rectangles below and the absence of
a general telescope for literal complex weights.
