\section{The nonnegative quadratic response of even moments}
\label{sec:quadratic-response}

The residual-boundary formula shows that individual two-erasure
decorations can retain nontrivial signs.  Nevertheless, after all words
with exactly two \(E\)'s are assembled, the even-moment coefficient has a
definite sign.  This is a global matrix identity, not an arithmetic
estimate.

\subsection{Divided-difference formula}

\begin{theorem}[Nonnegative two-erasure sector]
\label{thm:quadratic-response}
Let \(R\) and \(E\) be finite Hermitian matrices.  For every integer
\(q\ge1\),
\begin{equation}
 \boxed{S_{2q,2}\ge0.}
 \label{eq:quadratic-response-positive}
\end{equation}
More precisely, choose an orthonormal eigenbasis
\((e_\alpha)\) with
\[
 Re_\alpha=\lambda_\alpha e_\alpha,
\qquad
 P_\alpha=e_\alpha e_\alpha^*,
\qquad
 R=\sum_\alpha\lambda_\alpha P_\alpha,
\]
where equal eigenvalues may occur at different indices, and put
\(E_{\alpha\beta}=\langle Ee_\beta,e_\alpha\rangle\).  Then
\begin{equation}
 \boxed{
 S_{2q,2}
 =
 q\sum_{\alpha,\beta}
 |E_{\alpha\beta}|^2
 \Phi_q(\lambda_\alpha,\lambda_\beta),}
 \label{eq:quadratic-divided-difference}
\end{equation}
where
\begin{equation}
 \Phi_q(x,y)
 :=
 \sum_{a=0}^{2q-2}x^{2q-2-a}y^a
 =
 \begin{cases}
 \displaystyle
 \frac{x^{2q-1}-y^{2q-1}}{x-y},&x\ne y,\\[8pt]
 (2q-1)x^{2q-2},&x=y.
 \end{cases}
 \label{eq:Phi-divided-difference}
\end{equation}
\end{theorem}

\begin{proof}
By \eqref{eq:two-erasure-sector},
\[
 S_{2q,2}
 =
 q\sum_{a=0}^{2q-2}
 \tr(E R^aE R^{2q-2-a}).
\]
In an eigenbasis of \(R\),
\[
 \tr(E R^aE R^{2q-2-a})
 =
 \sum_{\alpha,\beta}
 |E_{\alpha\beta}|^2
 \lambda_\beta^a
 \lambda_\alpha^{2q-2-a}.
\]
Summing over \(a\) gives
\eqref{eq:quadratic-divided-difference}.  The function
\[
 g_q(x)=x^{2q-1}
\]
is increasing on \(\mathbb R\), because
\[
 g_q'(x)=(2q-1)x^{2q-2}\ge0.
\]
Therefore every off-diagonal divided difference in
\eqref{eq:Phi-divided-difference} is nonnegative, and the diagonal value
is also nonnegative.  Each summand in
\eqref{eq:quadratic-divided-difference} is nonnegative.
\end{proof}

\begin{corollary}[Quantitative upper bound and equality cases]
\label{cor:quadratic-upper}
One has
\begin{equation}
 0\le S_{2q,2}
 \le
 \binom{2q}{2}
 \|R\|^{2q-2}\|E\|_{\rm HS}^2.
 \label{eq:quadratic-upper}
\end{equation}
For \(q=1\),
\[
 S_{2,2}=\|E\|_{\rm HS}^2.
\]
For \(q\ge2\), equality \(S_{2q,2}=0\) holds if and only if
\begin{equation}
 E=P_{\Ker R}EP_{\Ker R}.
 \label{eq:quadratic-zero-characterization}
\end{equation}
\end{corollary}

\begin{proof}
From the finite sum in \eqref{eq:Phi-divided-difference},
\[
 |\Phi_q(x,y)|
 \le(2q-1)\max\{|x|,|y|\}^{2q-2}.
\]
Insert this into \eqref{eq:quadratic-divided-difference} and use
\(q(2q-1)=\binom{2q}{2}\).  When \(q=1\), \(\Phi_1=1\).
For \(q\ge2\), the odd power \(x^{2q-1}\) is strictly increasing, so
\(\Phi_q(x,y)>0\) unless \(x=y=0\).  Hence the sum vanishes exactly when
every nonzero matrix entry of \(E\) lies inside the zero eigenspace of
\(R\).
\end{proof}

\subsection{Response interpretation}

Put
\begin{equation}
 \mathcal F_q(t):=\tr(R+tE)^{2q}.
 \label{eq:moment-response-function}
\end{equation}
Then
\begin{align}
 \mathcal F_q'(0)&=S_{2q,1}
 =2q\tr(ER^{2q-1}),
 \label{eq:first-response}\\
 \frac12\mathcal F_q''(0)&=S_{2q,2}\ge0.
 \label{eq:second-response}
\end{align}
Applying the theorem with \(R\) replaced by \(R+tE\) shows that
\(\mathcal F_q''(t)\ge0\) for every real \(t\).  Thus
\(\mathcal F_q\) is convex.  This is also consistent with the convexity of
the \(2q\)-th power of the Schatten \(2q\)-norm
\citep{Bhatia1997,HornJohnson2013}.

The conclusion is deliberately limited:
\begin{itemize}
 \item the linear response can have either sign;
 \item the complete quadratic response cannot be negative;
 \item sectors of order three and above can again be signed; and
 \item convexity in \(t\) does not by itself compare
       \(\mathcal F_q(1)\) with \(\mathcal F_q(0)\), because the initial
       derivative may be negative.
\end{itemize}

\subsection{Individual words need not be positive}

The positivity in \cref{thm:quadratic-response} occurs only after every
two-erasure word is assembled with its correct cyclic multiplicity.  For
example, take
\[
 R=\begin{pmatrix}1&0\\0&-1\end{pmatrix},
 \qquad
 E=\begin{pmatrix}0&1\\1&0\end{pmatrix}.
\]
Then
\[
 \tr(RERE)=-2,
\qquad
 \tr(R^2E^2)=2.
\]
At fourth order,
\[
 S_{4,2}
 =
4\tr(R^2E^2)+2\tr(RERE)
=4>0.
\]
Taking the alternating word alone would therefore give the wrong sign for
the full quadratic sector.

\subsection{Arithmetic meaning}

At the literal level, \eqref{eq:quadratic-response-positive} says that all
two-erasure residual-boundary signs and all complex coefficient phases,
after being summed over every word position and every decorated walk, form
a nonnegative total.  It supplies no smallness.  Indeed, the upper bound in
\eqref{eq:quadratic-upper} can be large.  The theorem closes only a proposed
mechanism: the complete quadratic sector cannot be invoked as a negative
correction that cancels the zero-erasure moment.

The first potentially favorable perturbative term is therefore the
cross-key linear response
\[
 S_{2q,1}=2q\tr(ER^{2q-1}),
\]
whose residual-boundary sign remains an L2 arithmetic problem.
