\section{Introduction}
\label{sec:tpc45-introduction}

The terminal obstruction in the present TPC chain is no longer a
formal sieve remainder.  TPC--43 represented the surviving equality
energy as
\begin{equation}
 Z_0(\varepsilon)
 =\cD_0+\sum_{\kappa>1}C_X(\kappa)\chi_\kappa(\varepsilon),
 \qquad
 Z_0(-\one)
 =\cD_0+\sum_{\kappa>1}\mu(\kappa)C_X(\kappa),
 \label{eq:tpc45-intro-Walsh-corner}
\end{equation}
where the second value is the literal four--M\"obius equality term,
not a random-model surrogate \citep{WangTPC43}.  TPC--44 proved that a
density-one set of high-prime environments remains admissible after
every sign
\begin{equation}
 p\le (\log X)^{501/500}
 \label{eq:tpc45-intro-old-cutoff}
\end{equation}
is overwritten arbitrarily, hence in particular by its physical value
\(-1\) \citep{WangTPC44}.  It also proved that degree two, vanishing
relative variance, and vanishing normalized influences do not select
the prescribed all--minus corner.  Thus a further abstract Boolean-cube
argument cannot by itself cross the next gate.

This paper returns to the coefficients that generated
\eqref{eq:tpc45-intro-Walsh-corner}.  The equality labels are
\begin{equation}
 u_{\alpha,j}
 =d_\alpha n_{\alpha,j}
 =d_\alpha(\ell_\alpha d_\alpha j+h),
 \label{eq:tpc45-intro-actual-label}
\end{equation}
with
\begin{align}
 Q&=X^{267/400+o(1)},
 &J&=X^{133/400+o(1)},
 \notag\\
 D_0&=X^{10049/52500+o(1)},
 &L_0:=Q/D_0
   &=X^{\lambda_L+o(1)},
   \qquad \lambda_L:=\frac{99979}{210000}.
 \label{eq:tpc45-intro-scales}
\end{align}
We also write
\begin{equation}
 \lambda_0:=1+\frac{10049}{52500}
 =\frac{62549}{52500}
 \label{eq:tpc45-intro-lambda0}
\end{equation}
for the exponent of the original fused labels.
Here \(m_\alpha=\ell_\alpha d_\alpha\asymp Q\),
\(\ell_\alpha\asymp L_0\), \(d_\alpha\asymp D_0\),
and \(j\asymp J\).  We retain every inherited mask, complex source
weight, and output coordinate.  No sign or equidistribution hypothesis
is imposed on those deterministic coefficients.

\subsection{The first positive result: a physical prime band}

Let \(N_-\) and \(N_+\) be the minimum and maximum positive equality
targets \(n_{\alpha,j}\), and let \(\ell_+\) be the largest active
source prime.  Define the packet-dependent band
\begin{equation}
 \cP_{\mathrm{bal}}
 :=\left\{p\text{ prime}:
   \sqrt{N_+}<p\le \frac{N_-}{\ell_+}\right\}.
 \label{eq:tpc45-intro-balanced-band}
\end{equation}
At the endpoint it occupies, up to fixed support margins, the exponent
window
\begin{equation}
 \frac12<\frac{\log p}{\log X}
 <1-\frac{99979}{210000}
 =\frac{110021}{210000};
 \label{eq:tpc45-intro-balanced-window}
\end{equation}
its width is
\begin{equation}
 \frac{5021}{210000}=0.0239095\ldots.
 \label{eq:tpc45-intro-band-width}
\end{equation}
This is a genuinely growing prime interval, not a finite set of
coordinates.

If \(p\in\cP_{\mathrm{bal}}\) divides an active target, write
\begin{equation}
 n_{\alpha,j}=pr,
 \qquad s=d_\alpha r.
 \label{eq:tpc45-intro-cofactor}
\end{equation}
The prime \(p\) is unique, \(r\ge\ell_+\), and
\begin{equation}
 \mu(u_{\alpha,j})=\mu(ps)=-\mu(s).
 \label{eq:tpc45-intro-sign-collapse}
\end{equation}
Thus setting every sign in \(\cP_{\mathrm{bal}}\) to its physical
value deletes that prime exactly from the character.  Equal residual
labels have at most
\begin{equation}
 O_h(\tau(s))=X^{o(1)}
 \label{eq:tpc45-intro-fiber-bound}
\end{equation}
preimages in a fixed Hilbert coordinate.  The proof is elementary but
uses the actual equation
\begin{equation}
 rp-d_\alpha j\ell_\alpha=h.
 \label{eq:tpc45-intro-determinant}
\end{equation}
After grouping collisions, the new diagonal is at most
\(X^{o(1)}\cD_0\).

Combining this descent with the robust-face theorem of TPC--44 yields
our principal de-randomization statement.  For a density
\(1-o(1)\) set of the remaining prime-sign environments, all signs in
the entire band \(\cP_{\mathrm{bal}}\) may be fixed simultaneously to
\(-1\), while all signs in \eqref{eq:tpc45-intro-old-cutoff} may still
be overwritten arbitrarily, and the resulting equality energy remains
within the inherited \(K_B=X^{1/400+o(1)}\) budget.  This is the first
step in this chain that physically freezes a growing large-prime band.
More generally, if \(R=X^{\theta+o(1)}\) and
\(z=(\log X)^A\), the sufficient frontier is
\begin{equation}
 (\lambda_L-\theta)_+
 +\lambda_0(1-1/A)<\frac1{400}.
 \label{eq:tpc45-intro-tradeoff}
\end{equation}
For example, retaining \(A=501/500\) and taking
\(R=\ell_+X^{-1/10000}\) extends the upper band exponent to
\begin{equation}
 1-\lambda_L+\frac1{10000}
 =\frac{55021}{105000}=0.5240095\ldots,
 \label{eq:tpc45-intro-budgeted-endpoint}
\end{equation}
with exact unused margin \(577/26302500\).  These statements do not
freeze the intervening or still larger primes.

\subsection{Two complementary large-prime normal forms}

The band theorem is most effective when the cofactor is at least the
source-prime length.  Two further exact statements locate what happens
on either side of that balance.

First, the touched residual labels satisfy
\begin{equation}
 s\le D_0\sqrt{N_+}
 =X^{\lambda_1+o(1)},
 \qquad
 \lambda_1
 =\frac12+\frac{10049}{52500}
 =\frac{36299}{52500}.
 \label{eq:tpc45-intro-short-label}
\end{equation}
For the touched component alone, TPC--44's Rankin projection argument
therefore admits every
\begin{equation}
 1<A<
 A_1^*:=\left(1-\frac1{400\lambda_1}\right)^{-1}
 =\frac{145196}{144671}.
 \label{eq:tpc45-intro-A-star}
\end{equation}
We choose \(A=1003/1000\).  The exact endpoint margin is
\begin{equation}
 \frac1{400}-\lambda_1\left(1-\frac{1000}{1003}\right)
 =\frac{30329}{70210000}>0.
 \label{eq:tpc45-intro-new-gap}
\end{equation}
This improves the robust low-prime cutoff of the shortened component
to \((\log X)^{1003/1000}\).  Untouched labels retain their original
size, so this larger cutoff is not asserted for the full packet.

Second, fix \(\eta>0\) and move to
\begin{equation}
 y=X^{267/400+\eta}.
 \label{eq:tpc45-intro-affine-threshold}
\end{equation}
Every equality label then contains either no prime above \(y\) or one
such prime, and fixed \((j,p)\) meets at most one source row in each
source system.  With all
lower signs placed at their physical values, the complete equality
packet becomes
\begin{equation}
 Z_0(-\one_{\le y},\varepsilon_{>y})
 =\left\|v_0+\sum_{p>y}\varepsilon_pv_p\right\|^2.
 \label{eq:tpc45-intro-affine-form}
\end{equation}
Thus the large-prime Walsh hypergraph is exactly a Gram graph: its
degree is at most two, and the general coefficient descent of TPC--44
reduces to correlations among the vectors \(v_p\).

Averaging, rather than fixing, the signs below \(y\) gives an even
sharper rough projection.  For explicitly lifted residual vectors
\(x_p\),
\begin{equation}
 \E_{\le y}Z_0(\varepsilon_{\le y},-\one_{>y})
 =\cD_0-\cD_H+
  \left\|\sum_{p>y}x_p\right\|^2,
 \qquad
 \cD_H=\sum_{p>y}\|x_p\|^2\le\cD_0.
 \label{eq:tpc45-intro-pure-Gram}
\end{equation}
The remaining off-diagonal collisions are exactly equal deleted-label
fibers.  Writing \(n=pr\), each atom on one such fiber lies on
\eqref{eq:tpc45-intro-determinant}.  When \(r\ll L_0\), the ambient
two-prime ladder has length \(O_h(1+L_0/r)\), and all atoms with the
same residual label have the same M\"obius sign.  On every realized
fiber, Cauchy--Schwarz is sharp for arbitrary deterministic
coefficients; the ambient ladder bound need not be attained.

\subsection{What is and is not proved}

The unconditional advances are structural and de-randomizing:
\begin{enumerate}[label=(\roman*),leftmargin=2.1em]
 \item the actual coefficients are expanded without an auxiliary sign
 assumption;
 \item a full mesoscopic band of prime signs is fixed physically at
 subpolynomial diagonal cost;
 \item the shortened component receives a stronger low-prime cutoff;
 \item the very-large-prime part becomes an exact affine Gram graph;
 \item the remaining small-cofactor obstruction is identified as a
 fixed-determinant, coefficient-specific synthesis estimate.
\end{enumerate}
We do \emph{not} prove the synthesis estimate in
\eqref{eq:tpc45-intro-pure-Gram}; we do not deduce the complete
physical equality bound; and we do not obtain a prime-pair asymptotic,
a parity breakthrough, or a bounded-gap statement.  The literature
audit in \cref{sec:tpc45-literature} explains a particularly precise
reason: the closest cited fixed-determinant theorem permits two arbitrary
arithmetic coefficient sequences, whereas the TPC packet has three
nonsmooth arithmetic slots after the descent.

\Cref{sec:tpc45-interface,sec:tpc45-incidence} reconstruct the actual
coefficient and incidence geometry.  The physical-band descent and its
sharp fiber estimate are proved in
\cref{sec:tpc45-cofactor-descent,sec:tpc45-balanced-compression}.
\Cref{sec:tpc45-residual-freezing} gives the two robust freezing
consequences.  The affine and rough Gram forms are derived in
\cref{sec:tpc45-affine-gram}; the fixed-determinant ladders and exact
support boundary appear in
\cref{sec:tpc45-determinant-ladders,sec:tpc45-boundaries}.
We compare the result with current analytic inputs in
\cref{sec:tpc45-literature}, state the next gate in
\cref{sec:tpc45-next-gate}, and close with a machine-checkable algebraic
certificate and claim ledger.
