\section{The next gate}
\label{sec:tpc45-next-gate}

The preceding descent separates three tasks that should not be merged
under the phrase ``M\"obius randomness.''  We formulate them at the
level of the actual coefficient packet.

\subsection{A block synthesis estimate}

Let \(\cF_{i,s}(R)\) denote one residual fiber of atom indices \(e\)
with cofactor \(r\asymp R\), and let \(b_{i,e}\) be the inherited
complex atom.  The
support argument gives
\begin{equation}
 \sum_{i,s}
 \left|\sum_{e\in\cF_{i,s}(R)}b_{i,e}\right|^2
 \ll_h X^{o(1)}\left(1+\frac{L_0}{R}\right)
 \sum_{i,e}|b_{i,e}|^2.
 \label{eq:tpc45-support-block-synthesis}
\end{equation}
The squared norm of the exact grouping operator is the actual maximal
fiber size.  Thus \eqref{eq:tpc45-support-block-synthesis} is sharp when
its ambient upper bound is replaced by that maximal size; the displayed
upper bound need not itself be attained.  A power improvement below the
actual support frontier must therefore use the source phases,
opposite-row masks, or cancellation between different residual labels.

The natural positive target is a coefficient-specific replacement
\begin{equation}
 \sum_{i,s}
 \left|\sum_{e\in\cF_{i,s}(R)}b_{i,e}\right|^2
 \ll X^{o(1)}\cB(R)
 \sum_{i,e}|b_{i,e}|^2,
 \label{eq:tpc45-target-block-Bessel}
\end{equation}
where \(\cB(R)\) is strictly smaller than \(1+L_0/R\) on at least one
new cofactor range.  Even a small power improvement would enlarge the
physical band in \cref{sec:tpc45-residual-freezing}.  Estimate
\eqref{eq:tpc45-target-block-Bessel} is a target, not an assumption used
in any unconditional theorem above.

\subsection{The very-large-prime Bessel gate}

For the low-averaged rough projection, the exact missing estimate is
\begin{equation}
 \boxed{
 \left\|\sum_{p>y}x_p\right\|^2
 \ll X^{o(1)}K_B
       \sum_{p>y}\|x_p\|^2.}
 \label{eq:tpc45-target-high-Bessel}
\end{equation}
Together with the identity in \cref{sec:tpc45-affine-gram}, this would
place that projected sector within the endpoint budget.  It would not
by itself fix the signs below \(y\).  For the complete physical affine
face, a sufficient pair of estimates is
\begin{align}
 \|v_0\|^2
 &\ll X^{o(1)}K_B\cD_0,
 \label{eq:tpc45-target-base-vector}\\
 \left\|\sum_{p>y}v_p\right\|^2
 &\ll X^{o(1)}K_B\cD_0.
 \label{eq:tpc45-target-physical-synthesis}
\end{align}
Indeed the triangle inequality then bounds
\(\|v_0-\sum_pv_p\|^2\).  The first line is a base-sector problem and
the second is the physical high-prime synthesis problem.  Neither
follows from the pure rough projection, because lower-sign averaging
deletes their cross terms.

\subsection{The required determinant input}

After dyadic decomposition in the cofactor and source variables, a
candidate analytic theorem would have to estimate the fixed equation
\begin{equation}
 rp-dj\ell=h
 \label{eq:tpc45-next-fixed-determinant}
\end{equation}
with all of the following features retained:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item \(p\) and \(\ell\) are prime;
 \item the cofactor and source-divisor signs contribute M\"obius
       weights rather than smooth cutoffs;
 \item the actual projective mask remains in the coefficient;
 \item \(h\) is fixed;
 \item the estimate is vector-valued and stable under the preceding
       physical prime restrictions; and
 \item the final normalization is the atomic energy, not the ambient
       number of integer solutions.
\end{enumerate}
The Bettin--Chandee fixed-determinant corollary reviewed here lacks one
of these arithmetic coefficient slots; see
\cref{sec:tpc45-literature}.  Proving a theorem with all six features is
the direct route to \eqref{eq:tpc45-target-block-Bessel}.  Proving it
after averaging \(h\), smoothing one arithmetic slot, or restricting to
a favorable cofactor block would still be a meaningful weaker theorem,
but it would have to be labelled accordingly.

\subsection{A reversible research program}

The exact descent leaves several logically independent doors.
\begin{enumerate}[label=\textbf{Door \Alph*.},leftmargin=3.7em]
 \item Prove a power saving over
 \eqref{eq:tpc45-support-block-synthesis} on one additional cofactor
 block and enlarge the unconditional physical band.
 \item Establish a three-arithmetic-weight, fixed-\(h\) determinant
 estimate strong enough for \eqref{eq:tpc45-target-high-Bessel}.
 \item First prove an averaged-shift or smoothed-slot analogue, thereby
 identifying which of fixed \(h\), the third coefficient, or the
 vector-energy normalization is the dominant obstruction.
 \item Construct an actual-mask coefficient packet saturating the
 support norm.  Such a result would be a sharp negative boundary for
 support-only methods, without asserting that the physical TPC
 coefficients themselves saturate it.
\end{enumerate}
The current paper completes the geometric reduction needed before any
of these analytic attacks.  Failure at one door does not invalidate the
physical-band theorem, and success in an averaged or smoothed model
must not be reported as success at the fixed physical endpoint.
