\section{Finite spectral meaning, certificate, and conclusion}
\label{sec:tpc21-certificate}

\subsection{Two finite dualities}

The word \emph{spectrum} has two finite meanings in this paper.  After
zero extension from \(\cU_q\) to \(\Z/q\Z\), the additive transform
\[
 r\longmapsto
 \sum_{\kappa\in\cU_q}D_q(\kappa)e_q(r\overline H\kappa)
\]
is the spectral coordinate of the observable \(D_q\) for translation
on the finite cycle \(\Z/q\Z\).  The multiplicative transform
\[
 \chi\longmapsto
 \sum_{\kappa\in\cU_q}D_q(\kappa)\overline{\chi(\kappa)}
\]
is Fourier analysis on the finite abelian group \(\cU_q\).  The former
couples directly to Poisson summation; the latter exposes the row
Dirichlet polynomials and the shared-\(g\) convolution.  The induced
character Gauss formula in \cref{prop:tpc21-induced-Gauss} is the exact
bridge between them.

These are literal spectra of finite group actions.  They do not assert
that zeros of the Riemann zeta function are eigenvalues of a dynamical
system, and no such interpretation is used anywhere in the proofs.

\subsection{Exact computational certificate}

The standard-library certificate is
\begin{center}
 \texttt{experiments/tpc21\_certificate.py}.
\end{center}
Run it from the paper directory with
\begin{verbatim}
python experiments/tpc21_certificate.py
python -O experiments/tpc21_certificate.py
\end{verbatim}
Both commands regenerate
\(\texttt{experiments/tpc21\_certificate.json}\).  The certificate performs
1,149 exact equality checks.  Pass/fail checks use
integers, rational arithmetic, and exact roots of unity in a finite
prime field; floating-point comparisons are not used for the proof
identities.  The certificate verifies:

\begin{enumerate}[label=\textup{(\roman*)}]
 \item compatible row-fiber totals and the unit-class mean;
 \item the squarefree lcm occupancy product;
 \item bilinear divisor-lattice M\"obius reassembly, centering, and the
 additive CRT lift;
 \item primitive-frequency loss of the outer M\"obius signs;
 \item multiplicative-character Parseval and the exact shared-\(g\)
 masked character convolution;
 \item the conductor-sensitive induced-character Gauss formula;
 \item the row-diagonal one-fiber spike and its centered energy; and
 \item the rational exponent-gain ledger.
\end{enumerate}

The generated JSON explicitly records that these finite checks are not
evidence for a twin-prime theorem, the residual-dispersion estimate, a
parity breakthrough, or an asymptotic prime-pair formula.  For the
archived version, the JSON SHA-256 is
\nolinkurl{21AB51D5A8775832D8C44D90B4E21917C11FADAD1F150B896D234835740D5F74},
and the script SHA-256 is
\nolinkurl{26268E848E0D66A3B50B6FD628E95D8AF6931DE3FA9FA31D55C722FB8BFB3CB3}.
The same hashes are recorded in the README.

\subsection{Conclusion}

TPC-20 left a Ramanujan mean packet and a centered CRT-fiber
discrepancy.  The first is now closed.  Reduced-class Poisson summation
identifies it with an ordinary smooth coprime-lattice discrepancy of
size \(O_F(\tau(Hq))\), and the full lcm arithmetic cost is summable.
The total mean is \(O_\eps(Q^2X^\eps)\), one complete orbit-length
factor below the natural scale.

For the discrepancy, deterministic row occupancy gives the genuine
normalization \(Q^2q^{-1/2}\), but its dyadic sum crosses the target
exactly at \(q\asymp J\).  It therefore does not penetrate the long-lcm
range.  The new exact normal forms explain what extra information is
needed.  Unmasked rank-one packets are divisor-lattice M\"obius
differences of cumulative row-fiber products.  Generic packets are
shared-factor convolutions of masked two-row Dirichlet-character sums,
and their nonprincipal multiplicative energy is the connected fourth
moment that remains to be bounded.

The row-diagonal spike shows why the order matters: a contribution may
be power-saving after the complete scalar orbit sum and still saturate
the raw fiber norm relative to its coefficient amplitude.  Thus generic
pruning cannot be removed inside a nonlinear norm merely by citing its
scalar negligibility.  This rules out a
tempting shortcut and leaves a quantitatively specified gain target,
\(\omega>(y-j)/2\), for the sufficient character-moment route.

Accordingly, this paper advances the short--short branch by one positive
closure and one exact reduction.  It does not estimate the long
connected character moment, control the large-divisor legs, prove the
full TPC-18 residual-dispersion statement, breach sieve parity, or
establish a fixed-shift Hardy--Littlewood asymptotic or a twin-prime
lower bound.
