\section{Introduction}
\label{sec:tpc21-introduction}

The symmetric M\"obius tail isolated in TPC-17 is reduced in TPC-18
to a primitive two-row residual correlation.  After diagonal,
same-source, near-determinant, and large-gcd pairs are removed by
elementary counting, a failed block forces a generic correlation at the
natural scale \(XQ\) \citep{WangTPC18}.  TPC-19 gives exact divisor and
Poisson normal forms for that correlation, but its four locally centered
channels cannot be estimated independently without losing their matching
\citep{WangTPC19}.  TPC-20 performs the matching first.  In the strict
single-leg range it completes the two one-divisor spectra and compresses
the remaining compatible short--short joint spectrum into one ordinary
finite Fourier transform on
\(\cU_q=(\Z/q\Z)^\times\) \citep{WangTPC20}.

The last compression has the exact split
\begin{equation}
 S_q(r)=\overline Z_q\,c_q(r)+\widehat D_q(r),
 \qquad
 \sum_{r\bmod q}|\widehat D_q(r)|^2
 =q\sum_{\kappa\in\cU_q}|D_q(\kappa)|^2.
 \label{eq:tpc21-intro-mean-discrepancy}
\end{equation}
TPC-20 deliberately leaves both terms on the right as analytic inputs.
The purpose of the present paper is to decide which part is elementary,
which part has additional row structure, and which part is still a new
arithmetic estimate.

\subsection{The mean packet closes absolutely}

Our first result removes one of the two inputs.  For \(M\ge1\), define
\begin{equation}
 \Delta_M(F;J)
 =\frac JM\sum_{r\ne0}c_M(r)
   \widehat F\!\left(\frac{rJ}{M}\right).
 \label{eq:tpc21-intro-delta}
\end{equation}
Reduced-class Poisson summation and ordinary M\"obius inversion give
\begin{equation}
 \Delta_M(F;J)
 =\sum_{(j,M)=1}F(j/J)
  -J\frac{\varphi(M)}M\widehat F(0),
 \qquad
 |\Delta_M(F;J)|\ll_F\tau(M).
 \label{eq:tpc21-intro-delta-bound}
\end{equation}
The estimate is uniform through the transition \(M\asymp J\); it is a
bounded smooth lattice discrepancy, not a long-modulus prime theorem.
The TPC-20 mean packet is exactly
\(\overline Z_q\Delta_{Hq}(F;J)\).  Under the standard separated-packet
bound \(\mathcal Z_1\ll Q^2X^\eps\), summing it absolutely over all
short--short lcm layers gives
\begin{equation}
 \sum_q|\cL_q^{\rm mean}|
 \ll_\eps Q^2X^\eps,
 \qquad
 Q^2X^\eps\asymp\frac{XQ}{J}X^\eps.
 \label{eq:tpc21-intro-mean-closure}
\end{equation}
Thus the mean is power-saving throughout the strict single-leg range.
No cancellation between moduli is used.

\subsection{What row occupancy proves, and where it stops}

The fiber vector is not completely arbitrary.  Because \(u\le R<L/2\),
fixing \(d\) and a row class modulo \(u\) confines the prime source
\(\ell\) to one progression containing \(O(L/u)\) integers.  Consequently
each fiber contains at most \(O(Q/u)\) rows on the \(u\)-side.  This gives
the unconditional estimate
\begin{equation}
 \lVert D_q\rVert_{2,\cU_q}
 \ll_\eps \frac{Q^2}{\sqrt q}X^\eps.
 \label{eq:tpc21-intro-occupancy}
\end{equation}
For \(q\asymp Y\), insertion into the TPC-20 restricted-frequency
inequality produces
\begin{equation}
 \sum_{q\asymp Y}|\cL_q^{\rm disc}|
 \ll_\eps Q^2\sqrt{JY}\,X^\eps.
 \label{eq:tpc21-intro-occupancy-scalar}
\end{equation}
Relative to \(XQ=Q^2J\), this saves a fixed power only when \(Y<J\)
by a fixed power.  That is precisely the region where the whole joint
period is already short.  Occupancy improves the abstract one-fiber
bound, but it does not cross the long-lcm boundary.

\subsection{Two provenance-preserving normal forms}

The original \(TT^*\) row weights have rank-one provenance before the
generic Schur mask is imposed.  For a separated bilinear packet, let
\(A_u^x(\kappa)\) and \(A_u^y(\kappa)\) be the two one-row sums in the
class \(m\kappa\equiv-h\pmod u\), and put
\begin{equation}
 B_s^x(\kappa)=\sum_{u\mid s}\vartheta_R(u)A_u^x(\kappa),
 \qquad
 B_s^y(\kappa)=\sum_{u\mid s}\vartheta_R(u)A_u^y(\kappa).
 \label{eq:tpc21-intro-prefixes}
\end{equation}
The unmasked lcm layer has the exact divisor-lattice formula
\begin{equation}
 Z_q^{x,y}(\kappa)
 =\sum_{s\mid q}\mu(q/s)
 B_s^x(\kappa\bmod s)B_s^y(\kappa\bmod s).
 \label{eq:tpc21-intro-divisor-reassembly}
\end{equation}
In the Hermitian case this is a M\"obius difference of cumulative
nonnegative energies.  CRT lifting then shows that on frequencies
coprime to \(q\), the outer lcm M\"obius signs all disappear.  This is
structure, but not automatic cancellation.

For the actual generic mask, multiplicative Fourier analysis is more
faithful.  Write \(q=gab\), \(u=ga\), \(v=gb\), with \(g,a,b\) pairwise
coprime.  If \(\chi=\chi_g\chi_a\chi_b\) is a character of
\(\cU_q\), the fiber transform is exactly a convolution over characters
\(\psi\) of the shared factor \(g\):
\begin{equation}
 \widehat Z_{u,v}^{\,\mathfrak m}(\chi)
 =\frac{\overline{\chi(-h)}}{\varphi(g)}
 \sum_{\psi\bmod g}
 \cB_{\mathfrak m}
 (\chi_g\chi_a\psi,\chi_b\overline\psi).
 \label{eq:tpc21-intro-character-convolution}
\end{equation}
Here \(\mathfrak m(m_1,m_2)\) is the generic Schur mask and
\(\cB_{\mathfrak m}\) is its masked two-row Dirichlet-character sum.
When \(\mathfrak m\equiv1\), the latter factors into two one-row
Dirichlet polynomials.  For the generic mask it does not.  Multiplicative
Parseval therefore identifies the exact surviving input as a masked
shared-factor character fourth moment.

\subsection{Why scalar unpruning cannot be put inside the norm}

The isolated short--short signal is \(O_\eps(X^\eps)\) pointwise.
Hence the TPC-18 tuple counts allow the degenerate row pairs to be
restored and removed at the level of the complete scalar correlation,
with fixed-power error.  It is tempting to restore the full Gram packet,
take its fiber \(L^2\) norm, and then subtract the degenerate scalar
terms.  This is invalid because the norm is nonlinear.

We make the failure exact.  A single row diagonal contributes to one
class \(\kappa_q\) only:
\begin{equation}
 Z_{q,m}^{\rm rowdiag}(\kappa)
 =|x_m|^2\Gamma_\vartheta(q)
  \one_{\{\kappa=\kappa_q\}},
 \label{eq:tpc21-intro-diagonal-spike}
\end{equation}
and its multiplicative Fourier magnitude is constant in every
nonprincipal frequency.  Thus a row
diagonal can saturate the one-fiber obstruction of TPC-20 even though
its summed physical correlation is already negligible.  The generic
mask must remain inside the connected character moment, or the
degenerate pieces must be removed before a nonlinear norm is applied.

The paper therefore makes a positive reduction without claiming a
parity breakthrough: the Ramanujan mean is closed, the arbitrary fiber
is replaced by an exact masked character object, and two insufficient
shortcuts are ruled out quantitatively.  The masked fourth moment and
the large-divisor legs remain open.

\subsection{Organization}

\Cref{sec:tpc21-interface} fixes the inherited packet and its generic
mask.  \Cref{sec:tpc21-mean-closure} closes the Ramanujan mean.
\Cref{sec:tpc21-occupancy-frontier} proves the occupancy frontier.
\Cref{sec:tpc21-divisor} gives the divisor-lattice reassembly and its
additive Fourier lift.  \Cref{sec:tpc21-character} derives the exact
shared-factor character gate.  \Cref{sec:tpc21-nonlinear} proves the
diagonal-spike obstruction and the scalar/norm distinction.
\Cref{sec:tpc21-technology} audits the remaining analytic interface,
and \Cref{sec:tpc21-certificate} records the exact finite certificate
and the conclusion.
