\section{Degenerate scalar savings do not commute with fiber energy}
\label{sec:tpc21-nonlinear}

The scalar unpruning statement in
\cref{prop:tpc21-scalar-unpruning} is linear: after exact spectral
reassembly, the excluded row-pair sums may be subtracted at fixed-power
cost.  The sufficient gate \eqref{eq:tpc21-inherited-gate} is nonlinear
because it takes a fiber \(L^2\) norm first.  We now show that moving the
degenerate removal through this norm is not merely unproved; it is false
as a formal implication.

Assume for this section that the packet is Hermitian,
\(y_\alpha=\overline{x_\alpha}\), and unmasked.  For a row \(m\) and
squarefree \(q\) with \((q,mH)=1\), let
\begin{equation}
 \kappa_q(m)\equiv-h\overline m\pmod q.
 \label{eq:tpc21-row-kappa}
\end{equation}
Define the lcm coefficient
\begin{equation}
 \Gamma_\vartheta(q)
 =\sum_{\substack{u,v\le R\\{}[u,v]=q}}
 \vartheta_R(u)\vartheta_R(v).
 \label{eq:tpc21-Gamma-theta}
\end{equation}
The divisor-lattice identity also gives
\begin{equation}
 \Gamma_\vartheta(q)
 =\sum_{s\mid q}\mu(q/s)
 \left|\sum_{\substack{u\mid s\\u\le R}}
 \vartheta_R(u)\right|^2.
 \label{eq:tpc21-Gamma-prefix}
\end{equation}

\begin{proposition}[A row diagonal is an exact one-fiber spike]
\label{prop:tpc21-row-diagonal-spike}
The contribution of the single row pair \((m,m)\) to the unmasked
aggregated \(q\)-fiber is
\begin{equation}
 \boxed{
 Z_{q,m}^{\rm rowdiag}(\kappa)
 =|x_m|^2\Gamma_\vartheta(q)
  \one_{\{\kappa=\kappa_q(m)\}}.}
 \label{eq:tpc21-row-diagonal-spike}
\end{equation}
If \(A=|x_m|^2\Gamma_\vartheta(q)\), then its centered fiber satisfies
\begin{align}
 \lVert D_{q,m}^{\rm rowdiag}\rVert_{2,\cU_q}^2
 &=|A|^2\left(1-\frac1{\varphi(q)}\right),
 \label{eq:tpc21-row-diagonal-L2}\\
 \widehat D_{q,m}^{\rm rowdiag}(r)
 &=A\left\{e_q(r\overline H\kappa_q(m))
       -\frac{c_q(r)}{\varphi(q)}\right\}.
 \label{eq:tpc21-row-diagonal-additive}
\end{align}
For every nonprincipal multiplicative character \(\chi\) of
\(\cU_q\),
\begin{equation}
 \left|\sum_{\kappa\in\cU_q}
 D_{q,m}^{\rm rowdiag}(\kappa)\overline{\chi(\kappa)}\right|
 =|A|.
 \label{eq:tpc21-row-diagonal-multiplicative}
\end{equation}
Thus the spike occupies every nonprincipal multiplicative mode with the
same magnitude and, when \(\varphi(q)>1\), retains order-\(A\) additive
discrepancy at every frequency coprime to \(q\).
\end{proposition}

\begin{proof}
For each \(u\mid q\), the row \(m\) belongs to exactly the class
\(\kappa_q(m)\bmod u\).  Hence every pair \(u,v\) with lcm \(q\)
contributes at the same joint class, proving
\eqref{eq:tpc21-row-diagonal-spike}.  Subtracting the unit-class mean
\(A/\varphi(q)\) and summing the two possible squared values gives
\eqref{eq:tpc21-row-diagonal-L2}.  The additive transform is immediate.
For a nonprincipal \(\chi\), the constant mean has zero transform, so
the transform is \(A\overline{\chi(\kappa_q(m))}\), of modulus
\(|A|\).
\end{proof}

\begin{proposition}[The scalar estimate supplies no fiberwise saving]
\label{prop:tpc21-nonlinear-noncommutation}
For every \(q\) with \(\Gamma_\vartheta(q)\ne0\) and
\(\varphi(q)>1\), the single-row diagonal satisfies the exact relative
identity
\begin{equation}
 \frac{\lVert D_{q,m}^{\rm rowdiag}\rVert_2}
 {|x_m|^2|\Gamma_\vartheta(q)|}
 =\left(1-\frac1{\varphi(q)}\right)^{1/2}.
 \label{eq:tpc21-no-fiberwise-saving}
\end{equation}
Consequently \cref{prop:tpc21-scalar-unpruning}, by itself, supplies no
coefficientwise small factor for the row-diagonal fiber array and no
bound for its sum of fiber norms.  In particular, that scalar estimate
does not justify restoring the full Gram fiber inside a norm, applying
the triangle inequality, and subtracting the degenerate scalar error
afterwards.  This statement does not assert that the actual summed
row-diagonal fiber norm is large; additional cancellation in
\(\Gamma_\vartheta(q)\) or among rows is not ruled out.
\end{proposition}

\begin{proof}
Identity \eqref{eq:tpc21-no-fiberwise-saving} is
\eqref{eq:tpc21-row-diagonal-L2} divided by the spike amplitude.
Its right-hand side tends to \(1\) as \(\varphi(q)\to\infty\), so the
fiber norm has no uniform relative saving at the coefficient level.
By contrast, the scalar estimate sums the diagonal along the physical
orbit and uses the row count \(LDJ\asymp X\).  It contains no estimate
for the coefficient array obtained after discarding the Poisson
weights and taking a fiber norm.  Thus the displayed triangle-inequality
inference does not follow from that scalar estimate.
\end{proof}

The correctly pruned off-diagonal object removes the row diagonal before
the norm.
For one fixed \(u,v\), put
\begin{equation}
 C_{u,v}^{\rm rowdiag}(\kappa)
 =\sum_{\substack{\alpha\in\cA\\
 m_\alpha\equiv-h\overline\kappa\ (q)}}x_\alpha y_\alpha,
 \qquad q=[u,v],
 \label{eq:tpc21-connected-diagonal-subtraction}
\end{equation}
with the summand restricted to rows admissible for both divisor legs.
Then
\(Z_{u,v}^{\ne}=Z_{u,v}^{1}-C_{u,v}^{\rm rowdiag}\)
contains only distinct rows.  Its centered norm is nonnegative and has
the multiplicative Parseval formula of
\cref{sec:tpc21-character}.  Subtracting a scalar self-energy from an
already squared raw norm would not give the same quantity and need not
remain nonnegative.

\begin{proposition}[Distinctness alone does not force fiber spread]
\label{prop:tpc21-offdiagonal-spike}
Even after row-diagonal subtraction, rank-one provenance and
off-diagonal support alone imply no uniform fiber saving.  Fix one
admissible divisor pair \(u,v\), put \(g=(u,v)\), \(q=[u,v]\), and take
one distinct compatible row pair \(m\ne n\) with \(g\mid m-n\).
If
\[
 A=\vartheta_R(u)\vartheta_R(v)x_my_n
\]
is its isolated \((u,v;m,n)\) amplitude, then the contribution is
\(A\) at exactly one joint class and zero elsewhere.  After centering,
its fiber \(L^2\) energy is exactly
\begin{equation}
 |A|^2\left(1-\frac1{\varphi(q)}\right).
 \label{eq:tpc21-offdiagonal-spike-energy}
\end{equation}
Consequently a saving must use the distribution and signs of the full
arithmetic row family, not only the labels \emph{Gram} or
\emph{off diagonal}.
\end{proposition}

\begin{remark}[The legitimate order]
\label{rem:tpc21-legitimate-order}
There are two legitimate routes.  One may retain the generic Schur mask
inside the exact character transform and estimate its connected moment.
Alternatively, one may reassemble the complete scalar spectrum first,
estimate its rank-one part without taking a lossy raw fiber norm, and
then subtract the scalar degenerate contributions using
\cref{prop:tpc21-scalar-unpruning}.  What is forbidden is to replace the
generic fiber by the unpruned fiber inside a nonlinear norm merely
because the excluded physical correlation is small.
\end{remark}
