\section{The quantitative character-moment gate}
\label{sec:tpc21-technology}

The preceding sections remove the deterministic mean and identify two
coefficient-independent bounds for the discrepancy.  This section
records the exact improvement still required in a long dyadic lcm block
and compares it with standard character and Kloosterman technology.

\subsection{The gain ledger}

Write
\begin{equation}
 q\asymp Y=X^{y+o(1)},\qquad
 J=X^{j+o(1)},\qquad
 Q=X^{\beta+o(1)},\qquad j=1-\beta.
 \label{eq:tpc21-exponent-notation}
\end{equation}
The occupancy estimate gives, up to logarithms,
\begin{equation}
 \sum_{q\asymp Y}
 \lVert D_q^{\mathfrak m}\rVert_{2,\cU_q}
 \ll Q^2\sqrt Y\,X^\eps.
 \label{eq:tpc21-occupancy-block-norm}
\end{equation}
Suppose a future arithmetic estimate improves this by a fixed power:
\begin{equation}
 \sum_{q\asymp Y}
 \lVert D_q^{\mathfrak m}\rVert_{2,\cU_q}
 \ll Q^2\sqrt Y\,X^{-\omega+\eps}.
 \label{eq:tpc21-future-character-gain}
\end{equation}

\begin{proposition}[Gain threshold for the sufficient norm route]
\label{prop:tpc21-required-gain}
The combination of \eqref{eq:tpc21-future-character-gain} with the
TPC-20 restricted-frequency inequality gives a fixed power saving
relative to \(XQ=Q^2J\) whenever
\begin{equation}
 \boxed{\qquad
 \omega>\frac{y-j}{2}
 \qquad}
 \label{eq:tpc21-required-gain}
\end{equation}
with a fixed margin.  At the maximal short--short denominator
\begin{equation}
 Y=R^2=X^{1-2\delta+o(1)},
 \label{eq:tpc21-maximal-Y}
\end{equation}
condition \eqref{eq:tpc21-required-gain} becomes
\begin{equation}
 \omega>\frac{\beta-2\delta}{2}.
 \label{eq:tpc21-top-required-gain}
\end{equation}
On the largest divisor slice,
\(\beta=\lambda+1/4-\delta/2\), this is
\begin{equation}
 \boxed{\qquad
 \omega>\frac{\lambda}{2}+\frac18-\frac{5\delta}{4}.
 \qquad}
 \label{eq:tpc21-profile-required-gain}
\end{equation}
These are requirements for this sufficient norm route, not lower bounds
on every possible scalar method.
\end{proposition}

\begin{proof}
Equations \eqref{eq:tpc21-inherited-gate} and
\eqref{eq:tpc21-future-character-gain} give
\[
 \sum_{q\asymp Y}|\cL_q^{\rm disc}|
 \ll Q^2\sqrt{JY}\,X^{-\omega+\eps}.
\]
After division by \(Q^2J\), the remaining factor is
\(X^{(y-j)/2-\omega+\eps}\).  This is power-saving precisely under
\eqref{eq:tpc21-required-gain} with a fixed margin.  Substitute
\(y=1-2\delta\), \(j=1-\beta\), and then the displayed largest-slice
value of \(\beta\).
\end{proof}

For the published TPC profile
\(\lambda=10/21-\sigma_0\), the right side of
\eqref{eq:tpc21-profile-required-gain} is
\[
 \frac{61}{168}-\frac{\sigma_0}{2}-\frac{5\delta}{4}.
\]
For the version-locked Li-v6 profile
\(\lambda=8/17-\sigma_0\), it is
\[
 \frac{49}{136}-\frac{\sigma_0}{2}-\frac{5\delta}{4}.
\]
The symbol \(\sigma_0\) here is the inherited profile margin, while
\(\omega\) denotes the new character-moment gain.  Neither displayed
gain is proved in this paper.

\subsection{What the ordinary character large sieve returns}

The classical multiplicative large sieve in primitive-character form is
recorded in \eqref{eq:tpc21-standard-character-large-sieve}; see also
\citet[Chapter~7]{IwaniecKowalski2004}.  Passing between all and primitive
characters costs only the usual divisor bookkeeping in the present
squarefree setting.

For a one-row TPC polynomial, the ambient length is \(N\asymp Q\) and
the coefficient energy is \(O(QX^\eps)\).  When \(U\le\sqrt Q\),
\eqref{eq:tpc21-standard-character-large-sieve} therefore has size
\(Q^2X^\eps\), the same normalization already supplied by deterministic
occupancy.  When \(U>\sqrt Q\), its \(U^2\) term is larger.  Applying
Cauchy--Schwarz to the shared-\(g\) convolution in
\cref{thm:tpc21-masked-shared-character} introduces a fourth
moment rather than removing this cost.  Thus the ordinary large sieve,
used without additional arithmetic structure, proves no
\(\omega>0\) in a block with \(Y>J\).

This comparison does not say that character methods are irrelevant.
It says that the required input must exploit the specific masked
convolution over the common factor \(g\), rather than apply the
one-polynomial large sieve independently to every factor.

\subsection{Why one-fraction black boxes do not yet apply}

The bilinear Kloosterman-fraction estimate of
\citet{DukeFriedlanderIwaniec1997} and the trilinear estimate of
\citet{BettinChandee2018} take separated coefficient sequences.  The
partially fixed-modulus preprint of \citet{Wright2026} retains an
analogous separability requirement.  The generic transform in
\cref{thm:tpc21-masked-shared-character} contains instead
\[
 \cB_{\mathfrak m}(\rho_1,\rho_2)
 =\sum_{\alpha_1,\alpha_2}
 x_{\alpha_1}y_{\alpha_2}
 \mathfrak m(\alpha_1,\alpha_2)
 \rho_1(m_1)\rho_2(m_2),
\]
where the determinant and gcd restrictions remain inside the two-row
coefficient.  Replacing this by a product of one-row polynomials would
delete the generic Schur mask before a nonlinear moment is taken, an
operation not justified by the scalar estimate; see
\cref{prop:tpc21-nonlinear-noncommutation}.

Likewise, the exceptional-spectrum large sieve of
\citet{Pascadi2026LargeSieve} requires a representing measure satisfying
its size and two-frequency concentration hypotheses.  The exact
character normal form derived here does not by itself verify those
hypotheses.  None of these cited results is used as a black-box estimate
for \eqref{eq:tpc21-future-character-gain}.

\subsection{Three defensible next routes}

The remaining short--short problem now has three explicit routes.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item Prove \eqref{eq:tpc21-future-character-gain} directly for the
 masked shared-\(g\) transform, with the gain ledger
 \eqref{eq:tpc21-required-gain}.
 \item Decompose the generic Schur mask into separated pieces with a
 fully controlled projective norm, then insert the exact parameters
 into one specified character or Kloosterman theorem.  Merely counting
 pieces is insufficient; the complete norm cost must retain a fixed
 margin after \eqref{eq:tpc21-required-gain}.
 \item Avoid the sufficient fiber norm and estimate the complete scalar
 spectral sum while preserving cancellation between the connected
 piece and the explicitly removable degenerate pieces.  This route must
 keep the scalar order of operations in
 \cref{rem:tpc21-legitimate-order}.
\end{enumerate}

Even a successful short--short estimate leaves the residual legs with
\(u>R\) or \(v>R\).  Closing the full TPC-18 residual would additionally
require uniform reassembly of the separated packets and all earlier
endpoint estimates.  Nothing in this ledger is a twin-prime lower bound, a
Hardy--Littlewood asymptotic, or a breach of the sieve parity barrier.
