\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\cA}{\mathcal A}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\cW}{\mathcal W}
\newcommand{\cY}{\mathcal Y}
\newcommand{\one}{\mathbf 1}
\newcommand{\Span}{\operatorname{span}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\rad}{\operatorname{rad}}

\hypersetup{
  pdftitle={Prime-Resolved Residual Fibers at a Fixed Shift: Exact Grouping SVD, Common Moebius Gauge, and Collision-Free Transversals},
  pdfauthor={Liang Wang},
  pdfsubject={Exact spectral and arithmetic structure of residual grouping in a literal fixed-shift prime-squarefree packet},
  pdfkeywords={residual grouping, fiber SVD, terminal prime, common Moebius gauge, determinant ladder, parity obstruction}
}

\title{\bfseries Prime-Resolved Residual Fibers at a Fixed Shift:\\
Exact Grouping SVD, Common M\"obius Gauge, and Collision-Free Transversals}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\input{sections/abstract}

\noindent\textbf{Keywords:} residual grouping; terminal-prime resolution;
fiber singular values; common M\"obius gauge; determinant ladders; parity
obstruction.

\medskip
\noindent\textbf{Convention.}
The shift \(h_0\ne0\), one left-hand source system, and one direct
residue/orbit slice are fixed.
All physical domain and output norms use the inherited counting-measure
atomic normalization.  Terminal weights are displayed in the operator and
are never absorbed into a redefined input norm.  A collision means equality
of the complete output key \((\gamma,s,j)\), not equality of \(s\) alone.
The raw sampled-profile normalization is the one used in TPC--53, not the
normalized \(1/(E_XJ)\) convention used in an earlier intermediate model.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 47A10; Secondary 11N36,
15A18, 46C05.

\input{sections/introduction}
\input{sections/literal-map}
\input{sections/fiber-svd}
\input{sections/arithmetic-fibers}
\input{sections/transversals}
\input{sections/physical-coherence}
\input{sections/endpoint-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
