\section{Finite certificate and reproducibility}
\label{sec:computation}

The analytic asymptotic imports the Guth--Maynard short-interval theorem
and the weighted transfer proved in TPC-12.  No finite computation can
verify those asymptotic inputs.  The included deterministic certificate
checks the exact new algebra and the resolution interfaces.

The script \texttt{experiments/radial\_mellin\_certificate.py} performs
the following checks.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item It enumerates a finite factor box and verifies the bijection
 $(m,n)\leftrightarrow(a,b,k)$, including reconstruction and injectivity
 of $(a/b,k)$.

 \item It compares the direct factor-pair transform with the compressed
 two-coordinate expansion at several pairs $(t,s)$.

 \item In every dyadic sector containing at least two distinct rays or
 radial indices, respectively, it computes the corresponding actual
 minimum log gap and verifies the lower bounds
 \eqref{eq:sector-ray-gap}--\eqref{eq:sector-radial-gap}.

 \item It evaluates the tensor Fourier-side Fej\'er quadratic form at
 admissible scale parameters and verifies that every off-diagonal multiplier
 is zero, leaving exactly $TS\sum|x_{a,b,k}|^2$.  It also checks the
 coefficient-recovery multipliers.

 \item It groups the same squared coefficients by $r=mn$ and verifies
 the exact identity
 $\cF_{h,D}=\sum_rA_D(r)(\Lambda(r+h)-1)^2$.

 \item It constructs the two extremal vectors in
 \cref{prop:energy-minimax}, confirming that identical total energy can
 place all mass either in the endpoint or in its complement.
\end{enumerate}

The companion unit tests repeat these identities at independent
parameter values.  Integer factorization and GCD data are exact;
floating-point tolerances occur only in logarithms and phases.  The
commands are
\begin{verbatim}
python experiments/radial_mellin_certificate.py
python -m unittest experiments.test_radial_mellin_certificate
\end{verbatim}
The saved JSON output is a regression certificate for finite identities,
not numerical evidence for a fixed-shift prime-pair or quadratic-prime
asymptotic.

\section{Conclusion and next analytic interface}
\label{sec:conclusion}

The coordinate omitted from the ratio-only factor-ray spectrum can be
restored exactly after the observable is augmented with GCD data; it is
not recovered from ratio-only samples.  The GCD--Mellin lift replaces each collapsed radial fibre by
the injective joint frequency
\[
 (\log(a/b),\log k).
\]
On $ab\asymp R$, its two resolution scales are $R$ and
$\sqrt{X/R}$; tensor Fej\'er kernels recover individual coefficients and
their energy exactly.  A tensor Montgomery--Vaughan argument supplies a
stable hard-rectangle asymptotic once both side lengths exceed their
reciprocal-gap scales by unbounded factors.  This constructs an exact
two-parameter diagonal unitary representation of the augmented
coefficient array; no intrinsic prime, logistic, or transfer-operator
spectrum is claimed.

The arithmetic effect is equally explicit.  Full radial dephasing
changes the ray energy into the pure product-center target-square
diagonal.  TPC-12's weighted exceptional-set transfer then yields the
short-shift asymptotic with error $O(HX\log^2X)$, removing the
$\log\log X$ cost of the same-ray two-target upper sieve.  The gain is
real, but it belongs to a new observable; the old ratio-only energy still
contains its coherent radial cross terms.

There is no corresponding fixed-shift breakthrough.  Exact inversion
reveals the arithmetic coefficients rather than estimating them.  The
$m=1$ slice is equivalent at natural precision to a weighted
Hardy--Littlewood correlation, and the cutoff-free $(6,1)$ ray
comparison is equivalent at natural precision to a weighted prime
number theorem for $6k^2+1$.
Retaining only total radial energy loses the endpoint label again, with
the exact minimax loss in \eqref{eq:energy-minimax}.  These are positive
and negative statements at matching normalizations.

The next honest interface is therefore not a smaller formal bandwidth or
the substitution $H=1$.  It is an arithmetic, label-preserving signed
observable that can distinguish an endpoint or a controlled family of
radial slices before squaring, together with an explicit source of
Type-II or dispersion cancellation not reducible to an upper-bound
sieve.  A viable next theorem may average an additional arithmetic
parameter while retaining a specified radial selector.  A negative
result would be equally informative if it proves that every proposed
average still factors through parity-blind local data.  In either case,
the endpoint and quadratic-ray equivalences above are mandatory tests.

No fixed-shift prime-pair asymptotic, twin-prime lower bound,
quadratic-prime theorem, new distribution level, or violation of sieve
parity has been obtained.
