\section{Parity-conditioned even shifts}
\label{sec:even-shifts}

Restricting the ensemble to even shifts requires its own local centering.
For $h\equiv0\pmod2$ and a product center $r$, put
\begin{equation}
 \eta_r^{(2)}(h)
 :=\Lambda(r+h)-2\one_{2\nmid r}.
 \label{eq:parity-centered-target}
\end{equation}
Define
\begin{equation}
 x^{(2)}_{a,b,k}(h;X,D)
 :=u(ak)\eta_{abk^2}^{(2)}(h)W(abk^2/X)
 \label{eq:even-radial-coefficient}
\end{equation}
and the fully radial parity-centered energy
\begin{equation}
 \cF^{(2)}_{h,D}(X)
 :=\sum_{(a,b)=1}\sum_{\substack{k\geq1\\ak>D}}
 |x^{(2)}_{a,b,k}(h;X,D)|^2.
 \label{eq:even-radial-energy}
\end{equation}
The associated joint signal is obtained by multiplying
$x^{(2)}_{a,b,k}$ by $(a/b)^{it}k^{is}$.

\begin{theorem}[Short even-shift radial energy]
\label{thm:short-even-radial-energy}
Let $G\in C_c^1((0,\infty))$ be nonnegative and nonzero.  Under
\eqref{eq:intro-parameter-range},
\begin{equation}
 \begin{aligned}
 \sum_{h\equiv0\ (2)}G(h/H)\cF^{(2)}_{h,D}(X)
 ={}&\frac14HX I_0(G)I_2(W)\log X\\
 &\times\bigl((\log X)^2-(\log D)^2\bigr)
 +O_{\eps,\eta,W,G}\bigl(HX(\log X)^2\bigr).
 \end{aligned}
 \label{eq:short-even-radial-energy}
\end{equation}
\end{theorem}

\begin{proof}
The coordinate bijection gives
\[
 \cF^{(2)}_{h,D}(X)
 =\sum_rA_D(r)|\eta_r^{(2)}(h)|^2.
\]
For odd $r$, the transferred target-square moment over even shifts is
\[
 \sum_{h\equiv0\ (2)}G(h/H)|\eta_r^{(2)}(h)|^2
 =HI_0(G)\log X+O(H)
\]
outside the same stretched-exponentially sparse set used in TPC-12.  For
even $r$, the target term is supported on powers of two.  Since
$r+h\asymp X$ on the shift support, only $O_G(1)$ such powers occur and
\[
 \sum_{h\equiv0\ (2)}G(h/H)|\eta_r^{(2)}(h)|^2
 \ll_G(\log X)^2.
\]
After multiplication by $A_D(r)$ and summation, these rows contribute
\[
 O_W(X(\log X)^4)=o(HX(\log X)^2)
\]
in the stated range.  The exceptional-set transfer applies to the odd
rows with the same $A_D$ ledger, and their $O(H)$ errors sum to
$O(H\cS_D)$.

It remains to sum the source squares on odd product centers.  TPC-12
proves
\begin{equation}
 \sum_{\substack{n>D,\ m\geq1\\2\nmid nm}}
 u(n)^2|W(mn/X)|^2
 =\frac14XI_2(W)
 \bigl((\log X)^2-(\log D)^2\bigr)
 +O_W(X\log X).
 \label{eq:odd-product-source-diagonal}
\end{equation}
The factor $1/2$ from odd $m$ multiplies the $1/2$ in the full source
diagonal.  Restricting $n$ to odd values changes only the lower-order
linear logarithm.  Multiplication by $H\log X$ and the transferred
exceptional error give \eqref{eq:short-even-radial-energy}.
\end{proof}

The normalized conditional average uses $2/H$ rather than $1/H$ because
only half of the shifts are sampled.  Accordingly, after conditional
normalization, the leading source coefficient is $1/2$; the
unnormalized sum in \eqref{eq:short-even-radial-energy} has coefficient
$1/4$.

All exact dephasing statements in
\cref{sec:two-dimensional-dephasing} apply coefficient by coefficient to
$x^{(2)}_{a,b,k}$.  For example, the even-shift version of the global
joint band has the right-hand side of
\eqref{eq:short-shift-global-band} with $1/2$ replaced by $1/4$ and the
same $O(TSHX(\log X)^2)$ error.

\begin{remark}[No selected even gap]
The support of $G(h/H)$ moves to infinity with $H$.  The theorem
conditions the growing ensemble on parity but contains no prescribed
even integer once $X$ is large.  In particular, it gives no information
about the single shift $h=2$.
\end{remark}
