\section{Introduction and scope}
\label{sec:introduction}

The factor-ray program has reached a precise coordinate bottleneck.
The ratio phase $(n/m)^{it}$ distinguishes primitive rays but is constant
along each ray.  If
\[
 n=ak,\qquad m=bk,\qquad (a,b)=1,
\]
then $(n/m)^{it}=(a/b)^{it}$ and the radial coordinate $k=(m,n)$
disappears.  TPC-10 had already used the full ratio--product two-Mellin
continuum for endpoint selection \citep{WangTPC10}; that pair of
variables is information-theoretically complete on a finite factor box.
TPC-11 then isolated the ratio coordinate, proved exact long-band
dephasing of the distinct ratios, and identified the remaining same-ray arithmetic
\citep{WangTPC11}.  TPC-12 evaluated the squared ray coefficients after
averaging the shift over
\[
 X^{2/15+\eps}\leq H\leq X
\]
by transferring the almost-all short-interval theorem of
\citet{GuthMaynard2026} through an unbounded divisor weight
\citep{WangTPC12}.  Its fixed-ray minimax theorem also showed that no
amount of ratio bandwidth can reconstruct the lost $k$-profile.

The next step should therefore restore the missing coordinate directly,
not formally set $H=1$.  Relative to the ratio-only signal, we observe
\begin{equation}
 (m,n)^{is}=k^{is}.
 \label{eq:intro-gcd-phase}
\end{equation}
It is important to distinguish this phase from a second product Mellin
phase such as $(mn/X)^{is}$.  Since $mn=abk^2$, the latter mixes the
primitive-ray product $ab$ with $k$; it is not transformed into
\eqref{eq:intro-gcd-phase} by a global linear change of the two old
frequency variables.  After a primitive ray is known, however, a
ray-dependent shift and rescaling recovers $\log k$ from the product
frequency.  Thus the GCD--Mellin coordinate is a new directly observed,
ray-adapted parametrization, but it is not richer than TPC-10's full
ratio--product continuum.

The classical Mellin transform is Fourier analysis on the multiplicative
group \citep{ButzerJansche1997}.  Our product-Fej\'er identities are
elementary tensor Fourier inversion, and the hard-rectangle estimate is
obtained by applying the one-dimensional Montgomery--Vaughan inequality
twice.  We do not claim a new general multidimensional Mellin,
Plancherel, or large-sieve theorem.  The novelty is the direct GCD lift
of this factor-ray coefficient system, its explicit anisotropic sector
gaps, and the arithmetic transfer for the resulting diagonal observable.

\subsection{The two-coordinate lift}

Throughout,
\[
 u(n)=\Lambda(n)-1,
 \qquad \eta(q)=\Lambda(q)-1,
\]
and $W\in C_c^1((0,\infty);\R)$ has support in a fixed interval
$[\alpha,\beta]\subset(0,\infty)$.  We extend
$\Lambda(q)=0$ for nonpositive integers $q$; in every asymptotic
application $X$ is large enough that the supported targets are positive.
Define
\begin{align}
 \cT^{\rad}_{h,D}(X;t,s)
 &:={}
 \sum_{\substack{n>D\\m\geq1}}
 u(n)\Lambda(mn+h)W(mn/X)(n/m)^{it}(m,n)^{is},
 \label{eq:intro-raw-radial-transform}\\
 \cM^{\rad}_{D}(X;t,s)
 &:={}
 \sum_{\substack{n>D\\m\geq1}}
 u(n)W(mn/X)(n/m)^{it}(m,n)^{is},
 \label{eq:intro-radial-model}\\
 \cR^{\rad}_{h,D}
 &:={}\cT^{\rad}_{h,D}-\cM^{\rad}_{D}.
 \label{eq:intro-centered-radial-transform}
\end{align}
The unique GCD decomposition gives
\begin{equation}
 \cR^{\rad}_{h,D}(X;t,s)
 =\sum_{\substack{a,b\geq1\\(a,b)=1}}
 \sum_{\substack{k\geq1\\ak>D}}
 x_{a,b,k}(h;X,D)(a/b)^{it}k^{is},
 \label{eq:intro-joint-expansion}
\end{equation}
where
\begin{equation}
 x_{a,b,k}(h;X,D)
 :=u(ak)\eta(abk^2+h)W(abk^2/X).
 \label{eq:intro-joint-coefficient}
\end{equation}
The frequency map
\[
 (a,b,k)\longmapsto
 \bigl(\log(a/b),\log k\bigr)
\]
is injective.  In dynamical language, it is the joint spectrum of two
commuting diagonal generators.  This is a finite-support unitary
representation attached to the factor coordinates; it is not a claim
that prime gaps or zeta zeros are eigenvalues of a physical or transfer
operator.

The corresponding fully separated energy is
\begin{align}
 \cF_{h,D}(X)
 &:={}
 \sum_{\substack{a,b\geq1\\(a,b)=1}}
 \sum_{\substack{k\geq1\\ak>D}}
 |x_{a,b,k}(h;X,D)|^2
 \label{eq:intro-radial-energy}\\
 &=\sum_{\substack{n>D\\m\geq1}}
 u(n)^2\eta(mn+h)^2|W(mn/X)|^2.
 \label{eq:intro-factor-pair-energy}
\end{align}
The second line follows from the same bijection.  It is the target-square
diagonal before any radial indices are combined.

\subsection{Main advances}

There are three distinct conclusions.

First, on the dyadic factor-ray sector $R\leq ab<2R$, primitive ratios
are separated at scale $R^{-1}$ and radial logarithms at scale
$\sqrt{R/X}$.  A tensor Fej\'er kernel therefore recovers every
coefficient and its squared norm exactly once the two scale parameters
separately satisfy
\[
 T_{\rm ray}\gg R,
 \qquad
 T_{\rm rad}\gg\sqrt{X/R}.
\]
Both inequalities are sharp up to constants along populated interior
sector families with adjacent rays or consecutive radial indices.  The relation
\[
 T_{\rm ray}T_{\rm rad}^2\asymp X
\]
is consequently a sectorwise resolution identity, not permission to
trade one missing coordinate bandwidth against the other.
For hard rectangles, an asymptotic requires both side lengths to exceed
the displayed reciprocal-gap scales by unbounded factors.

Second, the arithmetic average of \eqref{eq:intro-radial-energy} has a
smaller error than the ratio-only ray energy.  For nonnegative, nonzero
$G\in C_c^1((0,\infty))$, fixed $0<\eps<13/15$ and $0<\eta<1$, uniformly
for
\begin{equation}
 X^{2/15+\eps}\leq H\leq X,
 \qquad 1\leq D\leq X^{1-\eta},
 \label{eq:intro-parameter-range}
\end{equation}
we prove
\begin{equation}
 \begin{aligned}
 \sum_hG(h/H)\cF_{h,D}(X)
 ={}&\frac12HX I_0(G)I_2(W)\log X\\
 &\times\bigl((\log X)^2-(\log D)^2\bigr)
 +O\bigl(HX(\log X)^2\bigr),
 \end{aligned}
 \label{eq:intro-main-energy}
\end{equation}
where
\[
 I_0(G)=\int_0^\infty G(v)\,dv,
 \qquad
 I_2(W)=\int_0^\infty|W(v)|^2\,dv.
\]
The raw target has the same formula.  The $\log\log X$ loss in TPC-12
came from bounding $k\ne\ell$ on one ray by a two-target upper sieve.
Here those terms are geometrically absent.  A parity-centered average
over even shifts has coefficient $1/4$ and the same error order.

Third, exact reconstruction does not evaluate the recovered arithmetic
data.  The endpoint slice $m=1$ of \eqref{eq:intro-factor-pair-energy}
satisfies, for each fixed nonzero $h$,
\begin{equation}
 \cF_h^{\rm end}(X)
 =(\log X)^2
 \sum_n\Lambda(n)\Lambda(n+h)|W(n/X)|^2
 +O_{h,W}(X\log X).
 \label{eq:intro-endpoint-reduction}
\end{equation}
Thus the predicted fixed-even-shift asymptotic for this positive spectral
slice is equivalent to the corresponding weighted Hardy--Littlewood
prime-pair asymptotic.  The new coordinate reaches the boundary cleanly;
it does not cross it.

\subsection{Claim ledger}

\begin{center}
\begin{tabular}{@{}p{0.31\textwidth}p{0.27\textwidth}p{0.31\textwidth}@{}}
\toprule
Statement & Status here & What it does not imply\\
\midrule
Joint GCD--Mellin spectrum
 & Exact and injective on factor pairs
 & Not recovered from ratio-only data\\
Sector dephasing and reconstruction
 & Exact after stated filtering
 & No arithmetic coefficient is estimated\\
Short-shift radial energy
 & Unconditional in \eqref{eq:intro-parameter-range}
 & No prescribed shift is selected\\
Even-shift ensemble
 & Unconditional after parity centering
 & No conclusion for $h=2$\\
Fixed endpoint
 & Exact reduction \eqref{eq:intro-endpoint-reduction}
 & Its predicted asymptotic remains open\\
\bottomrule
\end{tabular}
\end{center}

No fixed-shift Hardy--Littlewood asymptotic, twin-prime lower bound,
prime number theorem for a fixed quadratic polynomial, new level of
distribution, or violation of the parity barrier is asserted.
