\section{Dyadic factor-ray sectors and joint spacing}
\label{sec:sector-geometry}

The two coordinates have different natural resolutions.  To see them
without mixing incompatible scales, let
\begin{equation}
 \cD_X:=\{2^j:j\in\Z_{\geq0},\ 2^j\leq\beta X\}
 \label{eq:dyadic-scales}
\end{equation}
and, for $R\in\cD_X$, define the hyperbolic sector
\begin{equation}
 \mathscr I_R(X):=
 \left\{(a,b,k):
 \begin{array}{l}
 (a,b)=1,\ R\leq ab<2R,\\
 \alpha X\leq abk^2\leq\beta X
 \end{array}
 \right\}.
 \label{eq:sector-index-set}
\end{equation}
Every coefficient supported by $W(abk^2/X)$ belongs to exactly one such
sector.  The cutoff $ak>D$ may remove indices but cannot worsen the
spacing.

\begin{lemma}[Explicit uniform lower gaps in one sector]
\label{lem:sector-joint-gaps}
Let $(a,b,k),(c,d,\ell)\in\mathscr I_R(X)$.  If $(a,b)\ne(c,d)$, then
\begin{equation}
 \left|\log\frac ab-\log\frac cd\right|
 \geq\delta_{\rm ray}(R),
 \qquad
 \delta_{\rm ray}(R):=2\arsinh\!\left(\frac1{4R}\right).
 \label{eq:sector-ray-gap}
\end{equation}
If $k\ne\ell$, then
\begin{equation}
 |\log k-\log\ell|
 \geq\delta_{\rm rad}(R,X),
 \qquad
 \delta_{\rm rad}(R,X)
 :=\log\!\left(1+\sqrt{\frac{R}{\beta X}}\right).
 \label{eq:sector-radial-gap}
\end{equation}
Uniformly for $1\leq R\leq\beta X$,
\begin{equation}
 \delta_{\rm ray}(R)^{-1}\asymp R,
 \qquad
 \delta_{\rm rad}(R,X)^{-1}\asymp_\beta\sqrt{X/R}.
 \label{eq:sector-gap-scales}
\end{equation}
\end{lemma}

\begin{proof}
For distinct reduced fractions, $|ad-bc|\geq1$.  The exact identity
\[
 2\sinh\!\left(
 \frac12\left|\log\frac{ad}{bc}\right|
 \right)
 =\frac{|ad-bc|}{\sqrt{abcd}}
\]
and $ab,cd<2R$ give
\[
 2\sinh\!\left(
 \frac12\left|\log\frac{a/b}{c/d}\right|
 \right)>\frac1{2R},
\]
which implies \eqref{eq:sector-ray-gap}.

Next, every supported radial index satisfies
\[
 k\leq\sqrt{\frac{\beta X}{ab}}
 \leq\sqrt{\frac{\beta X}{R}}.
\]
If $1\leq k<\ell$, then
\[
 \frac\ell k\geq1+\frac1k
 \geq1+\sqrt{\frac{R}{\beta X}},
\]
and \eqref{eq:sector-radial-gap} follows.  The final estimates use
$\arsinh y\asymp y$ and $\log(1+y)\asymp y$ for $0<y\leq1$, with fixed
$\beta$ absorbed into the constants.
\end{proof}

\begin{corollary}[The sectorwise resolution invariant]
\label{cor:sector-resolution-invariant}
The reciprocal gap scales obey
\begin{equation}
 \delta_{\rm ray}(R)^{-1}
 \delta_{\rm rad}(R,X)^{-2}\asymp_\beta X.
 \label{eq:sector-resolution-invariant}
\end{equation}
Thus the natural anisotropic resolution pair is
\begin{equation}
 T_{\rm ray}\asymp R,
 \qquad
 T_{\rm rad}\asymp\sqrt{X/R},
 \qquad
 T_{\rm ray}T_{\rm rad}^2\asymp X.
 \label{eq:anisotropic-resolution-pair}
\end{equation}
\end{corollary}

\begin{remark}[Separate inequalities, not a bandwidth trade]
The last product is only a compact way to record the two gap scales.
A very long radial window cannot distinguish two near-adjacent primitive
rays having the same $k$, and a very long ray window cannot distinguish
consecutive radial indices on one ray.  Exact dephasing below therefore
requires two separate threshold inequalities.
\end{remark}

\begin{remark}[Why the statement is sectorwise]
Without coefficient-side sectorization, all $ab\leq\beta X$ occur.
The worst primitive-ray gap is then of order $X^{-1}$, while the worst
radial gap is of order $X^{-1/2}$.  A single global rectangular band
therefore needs
\[
 T_{\rm ray}\asymp X,
 \qquad T_{\rm rad}\asymp\sqrt X,
\]
and has $T_{\rm ray}T_{\rm rad}^2\asymp X^2$.  One may instead filter
each known dyadic sector at its own scales, but one may not replace that
filter bank by one global band satisfying the smaller product law.
\end{remark}

\begin{remark}[Near-sharp populated interior families]
The pairs of primitive rays $(N,1)$ and $(N-1,1)$ have log gap
$N^{-1}+O(N^{-2})$.  On a fixed ray, consecutive radial indices $K$ and
$K-1$ have log gap $K^{-1}+O(K^{-2})$.  Choosing $N\asymp R$ and
$K\asymp\sqrt{X/R}$ along populated families with
$R\to\infty$ and $X/R\to\infty$ inside a nondegenerate hyperbolic shell
shows that both scales in \eqref{eq:sector-gap-scales} are sharp up to
constants for general supported coefficient systems.  A particular
empty or sparse sector may need only one of the two conditions, or
neither.
\end{remark}
