\section{The fixed canonical Mellin direction}
\label{sec:tpc51-canonical-direction}

The kernel theorems in \cref{sec:tpc51-continuous-kernels} allow the
coefficient density to vary.  The provenance-canonical representation
does not: a fixed physical shape has one fixed real-axis Mellin
transform.  On orthogonal atomic coordinates its envelope-to-output
ratio has an exact elementary formula.

\subsection{Wiener--Mellin mass and exact synthesis}

Let \(W\in C_c^\infty((0,\infty))\).  We use the normalization
\begin{align}
 \widetilde W(t)
 &:=\int_0^\infty W(x)x^{-it}\frac{dx}{x},
 \label{eq:tpc51-direction-Mellin-transform}\\
 W(x)
 &=\frac1{2\pi}\int_\R\widetilde W(t)x^{it}\,dt.
 \label{eq:tpc51-direction-Mellin-inversion}
\end{align}
For an integer \(B\ge0\), define the polynomially weighted
Wiener--Mellin mass
\begin{equation}
 A_B(W)
 :=\frac1{2\pi}\int_\R(1+|t|)^B
       |\widetilde W(t)|\,dt.
 \label{eq:tpc51-Wiener-Mellin-mass}
\end{equation}
Schwartz decay makes \(A_B(W)<\infty\).  If \(W\ne0\), then
\begin{equation}
 A_B(W)\ge A_0(W)\ge\|W\|_\infty>0
 \label{eq:tpc51-Wiener-lower}
\end{equation}
by \eqref{eq:tpc51-direction-Mellin-inversion}.

Fix samples \(x_1,\ldots,x_N>0\) and a coefficient vector
\(c=(c_1,\ldots,c_N)\in\C^N\).  Put
\begin{equation}
 v_t(c):=(c_nx_n^{it})_{n=1}^N.
 \label{eq:tpc51-canonical-phase-vector}
\end{equation}
The canonical synthesis and its order-\(B\) envelope are
\begin{align}
 \cS_Wc
 &:=\frac1{2\pi}\int_\R\widetilde W(t)v_t(c)\,dt,
 \label{eq:tpc51-direction-canonical-synthesis}\\
 \cE_B(W;c)
 &:=\frac1{2\pi}\int_\R(1+|t|)^B
     |\widetilde W(t)|\,\|v_t(c)\|_2\,dt.
 \label{eq:tpc51-canonical-envelope}
\end{align}

\begin{theorem}[Exact fixed-shape Mellin ledger]
\label{thm:tpc51-fixed-shape-identity}
\label{thm:tpc51-canonical-mellin-direction}
For every \(W\), every positive sample set, and every \(c\in\C^N\),
\begin{align}
 \cS_Wc&=(c_nW(x_n))_{n=1}^N,
 \label{eq:tpc51-fixed-shape-output}\\
 \cE_B(W;c)&=A_B(W)\|c\|_2.
 \label{eq:tpc51-fixed-shape-envelope}
\end{align}
Consequently, whenever \(\cS_Wc\ne0\), the canonical condition number
is exactly
\begin{equation}
 \boxed{
 \operatorname{cond}_{B,W}(c)
 :=\frac{\cE_B(W;c)}{\|\cS_Wc\|_2}
 =\frac{A_B(W)\|c\|_2}
 {\left(\sum_{n=1}^N|c_n|^2|W(x_n)|^2\right)^{1/2}}.}
 \label{eq:tpc51-fixed-shape-condition}
\end{equation}
\end{theorem}

\begin{proof}
Mellin inversion gives \eqref{eq:tpc51-fixed-shape-output}
coordinate by coordinate.  Since \(|x_n^{it}|=1\),
\(\|v_t(c)\|_2=\|c\|_2\) for every \(t\).  This proves
\eqref{eq:tpc51-fixed-shape-envelope} and then
\eqref{eq:tpc51-fixed-shape-condition}.
\end{proof}

The same proof works with orthogonal Hilbert atoms in place of the
standard coordinate vectors and with positive atomic weights absorbed
into \(c_n\).  It fails after nonorthogonal grouping unless the grouping
map is included in the object being estimated.

\subsection{Interior stability and the exact worst direction}

For a nonempty set \(I\subset\{1,\ldots,N\}\), let \(\C^I\) denote the
coefficient vectors supported on \(I\).

\begin{corollary}[Exact interior minimax]
\label{cor:tpc51-interior-minimax}
If \(W(x_n)\ne0\) for every \(n\in I\), then
\begin{equation}
 \sup_{0\ne c\in\C^I}
 \operatorname{cond}_{B,W}(c)
 =\frac{A_B(W)}{\min_{n\in I}|W(x_n)|}.
 \label{eq:tpc51-interior-minimax}
\end{equation}
In particular, if
\begin{equation}
 |W(x_n)|\ge\eta>0
 \qquad(n\in I),
 \label{eq:tpc51-interior-lower}
\end{equation}
then every canonical direction supported on \(I\) has condition number
at most \(A_B(W)/\eta\).

If \(W(x_{n_0})=0\) for some \(n_0\), then the coordinate vector
\(e_{n_0}\) is an exact kernel direction.  Moreover, after adjoining
any direction with nonzero output, the unrestricted condition number is
unbounded.
\end{corollary}

\begin{proof}
Formula \eqref{eq:tpc51-fixed-shape-condition} is bounded above by the
right side of \eqref{eq:tpc51-interior-minimax}; equality is attained by
a coordinate vector at which \(|W(x_n)|\) is minimal.  If
\(W(x_{n_0})=0\), then \eqref{eq:tpc51-fixed-shape-output} gives
\(\cS_We_{n_0}=0\).  Adding an arbitrarily large multiple of this kernel
vector to one fixed nonzero-output coefficient leaves a nonzero output
of fixed size while the envelope tends to infinity.
\end{proof}

Thus a fixed shape has no continuous-frame pathology on a declared
interior set where it is bounded away from zero.  The relevant condition
is lower physical mass, not a lower bound for every Mellin layer.

\subsection{Zeros and flat cutoff boundaries}

The opposite conclusion holds near a zero of the fixed physical shape.
This produces a canonical near kernel without changing the Mellin
coefficient measure.

\begin{proposition}[Finite-order zero obstruction]
\label{prop:tpc51-finite-zero-obstruction}
Let \(x_0>0\), let \(k\ge1\), and suppose
\begin{equation}
 W^{(j)}(x_0)=0\quad(0\le j<k),
 \qquad
 \sup_{x\in U}|W^{(k)}(x)|\le M_k
 \label{eq:tpc51-order-k-zero}
\end{equation}
on an interval \(U\) containing \(x_0\), where \(M_k>0\).  If
\(x_n\in U\), the interval between \(x_0\) and \(x_n\) lies in \(U\),
\(0<|x_n-x_0|\le\Delta\), and \(c=e_n\), then either
\(W(x_n)=0\), giving an exact kernel direction, or
\begin{equation}
 \operatorname{cond}_{B,W}(e_n)
 \ge \frac{k!\,A_B(W)}{M_k\Delta^k}.
 \label{eq:tpc51-order-k-condition}
\end{equation}
\end{proposition}

\begin{proof}
Taylor's theorem with integral remainder gives
\[
 |W(x_n)|\le\frac{M_k}{k!}|x_n-x_0|^k
 \le\frac{M_k}{k!}\Delta^k.
\]
If the left side is nonzero, insert this bound in
\eqref{eq:tpc51-fixed-shape-condition} with \(c=e_n\).  If it vanishes,
\eqref{eq:tpc51-fixed-shape-output} gives the stated exact kernel.
\end{proof}

\begin{corollary}[Flat-boundary super-polynomial obstruction]
\label{cor:tpc51-flat-boundary-obstruction}
\label{cor:tpc51-boundary-zero}
Suppose \(W\) extends smoothly by zero across a boundary point \(x_0>0\)
of its support.  If a sequence of samples satisfies
\begin{equation}
 0<|x_X-x_0|\le X^{-\sigma}
 \label{eq:tpc51-flat-boundary-distance}
\end{equation}
for some fixed \(\sigma>0\), then either \(W(x_X)=0\) along a
subsequence, producing exact kernel directions there, or, along every
subsequence on which \(W(x_X)\ne0\), for every \(A>0\),
\begin{equation}
 \operatorname{cond}_{B,W}(e_{x_X})
 \gg_{A,B,W,\sigma}X^A.
 \label{eq:tpc51-flat-boundary-superpower}
\end{equation}
Here \(e_{x_X}\) denotes the one-coordinate vector at that sample.
\end{corollary}

\begin{proof}
Every derivative of \(W\) vanishes at \(x_0\).  For a prescribed
\(A>0\), choose an integer \(k>A/\sigma\).  If
\(\sup_U|W^{(k)}|=0\) on a suitable interval \(U\), then \(W\) vanishes
there and the sample is an exact kernel for all sufficiently large
\(X\).  Otherwise apply \cref{prop:tpc51-finite-zero-obstruction} with
\(\Delta=X^{-\sigma}\).  Then \(\Delta^{-k}=X^{\sigma k}\ge X^A\),
and the fixed constant \(k!A_B(W)/M_k\) is absorbed into the implied
constant.
\end{proof}

The corollary is a worst-direction statement.  It does not say that a
boundary region carries a positive fraction of the physical atomic
energy.  A bounded-overlap partition and an aggregate lower-energy
estimate may discard such directions.  Conversely, an upper seminorm
bound alone cannot do so.

\subsection{Scope of the canonical identity}

The exact ledger above concerns a Mellin phase acting diagonally on
orthogonal atomic coordinates.  It does not commute a signed integral
through a layerwise nonlinear norm.  In particular, it does not by
itself compare a Banach profile of the form
\[
 \int C(\phi_\tau)^{1/2}\|B_\tau\|\,d|\nu|(\tau)
\]
with the norm of the signed reassembled physical coefficient.  Such a
comparison additionally requires either a coefficient-specific vector
frame or a reordering that performs canonical Mellin inversion before
the nonlinear large-sieve step.  No full TPC--48 profile closure is
asserted here.
