\section{Endpoint ledger, provenance labels, and open doors}
\label{sec:tpc51-endpoint}

We now place the abstract and arithmetic results at the inherited TPC
endpoint.  This section is a scope ledger: every gain is attached to
the operator on which it was actually proved.

\subsection{Zero polynomial cost on the abstract sampled quotient face}

The endpoint factorization inherited from TPC--50 is
\begin{equation}
 Q=X^{267/400+o(1)},
 \qquad J=X^{133/400+o(1)},
 \qquad QJ=X^{1+o(1)},
 \label{eq:tpc51-endpoint-QJ}
\end{equation}
and
\begin{equation}
 L=X^{99979/210000+o(1)},
 \qquad
 D=X^{10049/52500+o(1)}.
 \label{eq:tpc51-endpoint-LD}
\end{equation}
In particular the static-mask degree defect satisfies the upper bound
\begin{equation}
 \epsilon_X\ll X^{-\eta+o(1)},
 \qquad
 \eta:=\min\left\{\kappa_0,\frac{10049}{52500}\right\}>0.
 \label{eq:tpc51-endpoint-epsilon}
\end{equation}
For every fixed \(A>0\) and \(K\leq(\log X)^A\),
\begin{align}
 \epsilon_XR_K
 &\ll X^{-\eta+o(1)}=o(1),
 \label{eq:tpc51-endpoint-mask-loss}\\
 R_K(1+K)^{C_1}D^{-1/2+\delta}
 &\leq X^{-10049/105000+\varepsilon+o(1)}
 \label{eq:tpc51-endpoint-squarefree-loss}
\end{align}
for every fixed \(\varepsilon>0\), after choosing the corresponding
sufficiently small \(\delta>0\).  Thus the limiting exponent before the
arbitrarily small loss is \(10049/105000\); choosing
\(0<\varepsilon<10049/105000\) gives a fixed power saving for this
squarefree contribution alone.
Here \(\epsilon_X\) is the mask degree defect, \(\delta\in(0,1/2)\)
is the auxiliary exponent in the squarefree counting error, and
\(\varepsilon\) is the final arbitrarily small exponent slack.  These
three quantities are distinct; choosing \(\delta\) does not alter the
definition of \(\eta\).  The prime progression error is
smaller than every negative power of \(\log X\), even after multiplying
by a fixed polylogarithm.  Hence the lower bound in
\eqref{eq:tpc51-masked-lower-frame} remains a fixed positive constant.

\begin{corollary}[Abstract endpoint sampled-frame stability]
\label{cor:tpc51-endpoint-quotient-stability}
Fix an admissible fixed-modulus prime--squarefree row cell.  Let
\(\mathbf W=(W_1,\ldots,W_R)\) be a fixed finite scalar family on the
log box, let \(\mathbf A=(A_1,\ldots,A_R)\) be fixed positive
normalizations, and remove the exact limiting relations.  If the
resulting limiting normalized Gram has
\(\lambda_{\min}(G_\infty)=:\lambda_*>0\), then its sampled Gram and its
literal-mask sampled Gram have condition number
\begin{equation}
 O_{q,H,\cA,\mathbf W,\mathbf A,\lambda_*}(1).
 \label{eq:tpc51-abstract-fixed-endpoint-condition}
\end{equation}
Thus this fixed scalar-family problem has zero positive polynomial
sampling-and-mask loss.  Separately, for every fixed \(A>0\), the
retained log-Fourier bank with \(K\leq(\log X)^A\) has sampled
Hilbert-Gram condition number
\(O_{A,q,H,\cA}(1)\), while its displayed \(\ell^1\) quotient cost is at
worst \(R_K=X^{o(1)}\).  In both statements the source-row label is
retained.
\end{corollary}

\begin{proof}
The fixed-family assertion is
\cref{thm:tpc51-limit-gram,cor:tpc51-fixed-physical-family,cor:tpc51-masked-fixed-shapes};
its constants necessarily retain the
displayed family, normalization, and limiting-eigenvalue dependence.
The growing-bank and literal-mask assertions follow from
\cref{thm:tpc51-polylog-fourier-frame,thm:tpc51-masked-frame} together
with \eqref{eq:tpc51-endpoint-mask-loss}--
\eqref{eq:tpc51-endpoint-squarefree-loss}.
\end{proof}

The phrase ``zero polynomial loss'' does not mean zero constant loss,
does not suppress the dependencies in
\eqref{eq:tpc51-abstract-fixed-endpoint-condition}, and does not mean
that an actual TPC provenance operator has been identified with this
abstract family.  It says only that the declared sampled scalar family
or retained finite bank consumes no positive exponent.

\subsection{What the continuous no-go changes}

The universal kernel in \cref{thm:tpc51-smooth-kernel} makes one
possible future strategy inadmissible.  One may not introduce an
arbitrary \(L^2\) or signed \(L^1\) Mellin coefficient density and then
claim a lower frame merely because individual phases have unit modulus.
The correct alternatives are:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.6em]
 \item use the one provenance-fixed density and invert it exactly;
 \item pass to the quotient by the exact synthesis kernel and specify a
       quotient norm; or
 \item retain a separated finite bank and prove its sampled Gram bound.
\end{enumerate}
The present paper proves each alternative only on its declared model
domain.  It does not identify the actual orbit-translate provenance
with the finite scalar family or retained bank; that step is exactly
\cref{prop:tpc51-actual-bridge-criterion} and remains unverified.

The boundary obstruction also has two distinct meanings.  A uniform
coordinatewise diagonal bound fails when an allowed coordinate
approaches a zero, and then subdivision or energy selection is needed.
An aggregate fixed-family sampled Gram can nevertheless remain stable
when a shape has isolated zeros, provided its limiting
\(L^2(e^{x+y}dxdy)\) quotient classes remain independent.  Thus a
coordinatewise near kernel is not by itself an aggregate Gram
degeneracy, and weighted Mellin mass alone proves neither conclusion.

\subsection{Provenance and claim ledger}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.24\textwidth}
                >{\raggedright\arraybackslash}p{0.20\textwidth}
                >{\raggedright\arraybackslash}p{0.45\textwidth}}
\toprule
Object & Status & Exact meaning \\
\midrule
Continuous Mellin lower frame
& Disproved
& False for arbitrary signed smooth densities at every finite \(X\);
  the synthesis has a nonzero smooth kernel. \\
Canonical fixed density
& Exact
& Mellin inversion reconstructs the physical shape at the sampled
  rows; no inter-layer orthogonality is assumed. \\
Fixed finite scalar-shape quotient
& Proved on its abstract domain
& After exact redundancies are removed, limiting \(L^2\)-independence
  gives an \(O(1)\) sampled Gram condition number, with constants
  depending on the family and its limiting Gram. \\
Prime--squarefree log bank
& Proved
& Fixed modulus, nondegenerate interior block, degree
  \(K\leq(\log X)^A\), with standard PNT and squarefree counts. \\
Literal static-mask transfer
& Proved for the declared families
& One-sided row deletion costs \(O(\epsilon_XR_K)\); the source row is
  not coherently collapsed. \\
Actual orbit-translate provenance bridge
& Open
& Requires the uniform vector-valued Gram or relative-tail and
  weighted-envelope comparison in
  \cref{prop:tpc51-actual-bridge-criterion}; these are not verified. \\
Full TPC--48 profile comparison
& Open
& Its outer \(L^1(d|\nu|)\) occurs after a nonlinear layer norm and
  includes a coherent prime sum. \\
Fixed-shift prime pair / twins
& Not reached
& No parity-breaking estimate or \(L^2\) target correlation is asserted. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Why the full TPC--48 envelope does not follow}

For a fixed representation, the inherited profile has the schematic
form
\begin{equation}
 \mathfrak S_{\mathscr R}(\alpha)
 =\int C_{\rm LS}(\phi_\omega,H_0)^{1/2}
 \left(\sum_m\|B_{\omega,m}(\alpha)\|^2\right)^{1/2}
 d|\nu|(\omega),
 \label{eq:tpc51-profile-envelope-reminder}
\end{equation}
where, inside the Hilbert norm, the prime variable has already been
summed coherently.  The abstract frames proved here act on declared
opposite-row log families while retaining the other row and arithmetic
labels.  Before they can even be placed into the actual provenance
operator, \cref{prop:tpc51-actual-bridge-criterion} must be verified.
After that bridge, three further noncommutations would still prevent
\eqref{eq:tpc51-profile-envelope-reminder} from being replaced by the
physical atomic energy:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.6em]
 \item the outer total-variation integral is applied after the square
       root of a layer energy;
 \item \(C_{\rm LS}\) is a profile seminorm weight, not the norm of a
       canonical Mellin coefficient; and
 \item the coherent prime and residual maps need not intertwine with
       the opposite-row quotient projection.
\end{enumerate}
Minkowski proves an upper envelope in this order; the quotient theorem
does not reverse Minkowski.

\subsection{The next mathematical doors}

The remaining interfaces, in dependency order, are:
\begin{enumerate}[label=\textup{D\arabic*:},leftmargin=3.4em]
 \item \textbf{Actual-provenance bridge.}  For the genuine
 \(X\)-dependent Hilbert-valued orbit-translate family, verify a uniform
 normalized Gram or a uniform relative Fourier-tail estimate, and prove
 the weighted continuous-envelope comparison
 \eqref{eq:tpc51-actual-envelope-bridge}.  This is not a consequence of
 the fixed scalar-family theorem.
 \item \textbf{Coherent-prime square.}  At fixed source and cofactor,
 prove a square estimate for
 \(\sum_p A(p,r,m)\e(-pr\alpha)v_{p,r,m}\) that is stable under the
 canonical quotient projection, or give a sharp obstruction.
 \item \textbf{Residual grouping.}  Control the map grouping
 \(s=d(m)r\), including its maximal fiber multiplicity and any usable
 cancellation within a fiber.
 \item \textbf{Physical-shift localization.}  Compare the frozen
 completed family with the single physical intercept \(h_0\).
 \item \textbf{Native-Gram identification.}  Relate the residual
 low-sign Gram to the native affine physical Gram without discarding
 cross terms.
 \item \textbf{Parity-sensitive input.}  Only after the preceding
 Hilbert interfaces close would a genuinely new number-theoretic input
 be able to address a fixed-shift prime-pair lower bound.
\end{enumerate}

Failure at any one door would be informative: it would identify an
explicit operator or near-kernel rather than an unspecified appeal to
the parity barrier.  The abstract positive and translate-obstruction
results localize the first remaining door more sharply; they do not
assert that this actual-provenance door is already open.
