\section{The provenance-canonical synthesis interface}
\label{sec:tpc51-inherited-interface}

This section reconstructs the exact coefficient interface inherited from
TPC--25, TPC--36, and TPC--47--50
\citep{WangTPC25,WangTPC36,WangTPC47,WangTPC48,WangTPC49,WangTPC50}.
There are three different parameter spaces in that interface: a fixed finite
residue decomposition, a continuous real-axis Mellin decomposition, and a
later projective decomposition of the static mask.  Only the first two belong
to the provenance-canonical pre-mask cellization.  Keeping them separate is
essential: a terminal projective parameter from TPC--47/48 is not a physical
Mellin atom, and a lower-frame assertion for all of its possible signed
representations is false.

\subsection{Physical rows and the literal pre-mask coefficient}

Fix the physical shift $h_0\ne0$ and one source-compatible dyadic packet.
Let $\cA_1$ and $\cA_2$ be its two finite row systems.  A row is
\begin{equation}
 \rho=(\ell_\rho,d_\rho),
 \qquad
 m_\rho=\ell_\rho d_\rho\asymp Q,
 \label{eq:tpc51-row}
\end{equation}
where $\ell_\rho$ is prime, $d_\rho$ is squarefree, and the inherited
separation makes $m_\rho$ determine $\rho$.  The literal static mask is
\begin{equation}
 K_{\alpha\gamma}
 :=\one_{\ell_\alpha\ne\ell_\gamma}
   \one_{|m_\alpha-m_\gamma|>\Delta}
   \one_{(d_\alpha,d_\gamma)\le G},
 \qquad
 \Delta=QX^{-\kappa_0},\quad G=X^{\kappa_0}.
 \label{eq:tpc51-literal-mask}
\end{equation}
Before $K$ is decomposed, the joint multiplier has the form
\begin{equation}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)
 =K_{\alpha\gamma}\,
  \Xi_{\alpha,\gamma}(j)
  \mathcal W_{\alpha,\gamma}(j/J),
 \label{eq:tpc51-joint-multiplier}
\end{equation}
where $\Xi$ has a fixed orbit period and $\mathcal W$ is assembled from
fixed smooth row--orbit cutoffs.  On the left, the physical source
coefficient is
\begin{equation}
 \gamma_\alpha^{(1)}
 =\mu(d_\alpha)(\log\ell_\alpha)
  \omega_D^{(1)}(d_\alpha)
  \psi_L^{(1)}(\ell_\alpha/L)\zeta_\alpha^{(1)},
 \label{eq:tpc51-source-coefficient}
\end{equation}
with the symmetric formula on the right.  These are literal coefficients,
not arbitrary bounded row weights.

The large-prime residual vector at $h_0$ is
\begin{equation}
 \mathcal F_{h_0}^{\rm act,L}
 =\sum_{\substack{\gamma,j,m,p,r\\pr-mj=h_0}}
 \gamma_m^{(1)}\mathfrak A_{m,\gamma}^{\rm act}(j)
 \mu(r)\Lambda(pr)e_{\gamma,d(m)r}\otimes e_j.
 \label{eq:tpc51-physical-residual}
\end{equation}
It has actual coefficients at the physical intercept, but it belongs to the
low-sign-averaged residual Gram route rather than automatically to the native
affine physical Gram face.  Prime summation, residual grouping, and this Gram
identification will therefore remain downstream of the synthesis operator
defined below.

\subsection{Finite residue variables and continuous Mellin variables}

Let $H_0=O_{h_0}(1)$ be a common orbit-residue period.  A fixed residue
factor has the finite Fourier expansion
\begin{equation}
 \xi(d,j)
 =\sum_{a,b\bmod H_0}
   \widehat\xi_{H_0}(a,b)\e_{H_0}(ad+bj),
 \qquad
 \sum_{a,b\bmod H_0}|\widehat\xi_{H_0}(a,b)|\ll_{h_0}1.
 \label{eq:tpc51-finite-residue-Fourier}
\end{equation}
Equivalently one may first split the $O_{h_0}(1)$ physical residue cells.
Thus residue parameters are finite and of fixed complexity.  Direct cell
splitting uses a finite counting measure; Fourier implementation uses a
finite complex atomic measure.  Neither is a growing continuous frame.

The smooth separation is genuinely continuous.  For a fixed smooth shape
$W$ put
\begin{equation}
 \widetilde W(t)
 :=\int_0^\infty W(z)z^{-it}\,\frac{dz}{z}.
 \label{eq:tpc51-Mellin-transform}
\end{equation}
The function $\widetilde W$ is Schwartz.  For the four smooth factors in a
two-row packet, a representative provenance measure is
\begin{equation}
 \begin{split}
 \bm\tau&=(t_1,s_1,t_2,s_2)\in\R^4,\\
 d\nu_{\rm Mel}(\bm\tau)
 &:=(2\pi)^{-4}
   \widetilde W_1(t_1)\widetilde\Psi_1(s_1)
   \widetilde W_2(t_2)\widetilde\Psi_2(s_2)\,d\bm\tau.
 \end{split}
 \label{eq:tpc51-provenance-Mellin-measure}
\end{equation}
The evident product with further fixed smooth shapes gives the versions used
in later packets.  In particular, this is a specific complex Borel measure,
absolutely continuous with respect to Lebesgue measure, rather than a freely
chosen coefficient density.  Its polynomially weighted total variation is
finite at every fixed order.  The associated row phases are unitary: for
example,
\begin{equation}
 (\ell d)^{it}d^{is}=\ell^{it}d^{i(t+s)}.
 \label{eq:tpc51-unit-Mellin-row-phase}
\end{equation}

Combining the fixed residue variables with the required real Mellin
variables gives finite disjoint unions
\begin{equation}
 \Theta^{\rm can}_X
 :=\bigsqcup_{a\bmod H_0}\Theta_a,
 \qquad
 \Theta_a=F_a\times\R^{k_a},
 \label{eq:tpc51-canonical-parameter-space}
\end{equation}
where $F_a$ is fixed and finite and $k_a=O(1)$.  The corresponding
provenance measures are denoted by $\lambda_a$.  They are finite complex
atomic--continuous product measures obtained using the original Fourier and
Mellin normalizations.  With no null pairs or algebraic refactorizations
inserted, the canonical pre-mask identity is
\begin{align}
 &\gamma_\alpha^{(1)}
  \Xi_{\alpha,\gamma}(j)
  \mathcal W_{\alpha,\gamma}(j/J)
 \notag\\
 &\quad={}
 \sum_{a\bmod H_0}\one_{j\equiv a\!\!\!\pmod{H_0}}
 \int_{\Theta_a}
 u_{a,\tau}^{L}(\alpha)v_{a,\tau}(\gamma)
 \phi_{a,\tau}(j/J)\,d\lambda_a(\tau).
 \label{eq:tpc51-canonical-cellization}
\end{align}
There is one compact interval $I_0\subset\R$, independent of $X,a,\tau$,
such that $\phi_{a,\tau}\in C_c^\infty(I_0)$.  For every fixed $B$,
\begin{equation}
 \sum_{a\bmod H_0}\int_{\Theta_a}
 \|u_{a,\tau}^{L}\|_\infty
 \|v_{a,\tau}\|_\infty
 \|\phi_{a,\tau}\|_{C^B}\,d|\lambda_a|(\tau)
 \ll_{B,h_0}X^{o(1)}.
 \label{eq:tpc51-canonical-L1-seminorm-mass}
\end{equation}
This is an upper $L^1(d|\lambda|)$ projective-seminorm estimate.  It is not
a lower frame bound.

\subsection{Why mask parameters are not canonical Mellin cells}

Only after \eqref{eq:tpc51-canonical-cellization} is fixed does TPC--36
apply the specified mask representation
\begin{equation}
 K_{\alpha\gamma}
 =\int_{\Omega_{36}}p_\eta(\alpha)q_\eta(\gamma)
 \,d\nu_{36}(\eta),
 \qquad
 \int_{\Omega_{36}}
 \|p_\eta\|_\infty\|q_\eta\|_\infty\,d|\nu_{36}|(\eta)
 =X^{o(1)}.
 \label{eq:tpc51-specified-mask-representation}
\end{equation}
The parameter $\eta$ is a finite or finitely representable projective-mask
parameter.  It records same-source orthogonality, signed Ferrers separation,
and gcd compression.  It is not part of
$\Theta_X^{\rm can}$ and has no representation-independent physical
meaning by itself.

There may also be a further continuous Mellin variable when the smooth
terminal factor $\Lambda(pr)=(\log pr)\Phi_0(pr/X)$ is separated.  Its
measure is again fixed by the real-axis Mellin transform of the declared
terminal shape and has Schwartz weighted variation.  TPC--47 retains this
variable, the prime restriction, and $\mu(r)$ in $A_\omega(p,r,m)$ rather
than in the opposite-row pre-mask cell.  Accordingly it is a canonical
\emph{downstream} Mellin parameter, but it is not an element of
$\Theta_X^{\rm can}$ in \eqref{eq:tpc51-canonical-parameter-space}.  If it
is retained as an auxiliary coordinate, its measure is tensorized with
$\lambda_X$ only after the coefficientwise operator below has been formed.

The terminal symbol $\omega$ in TPC--47/48 combines a canonical pre-mask
cell $(a,\tau)$, a mask parameter $\eta$, and any terminal Mellin variables.
An individual $\omega$-layer therefore contains
$u_{a,\tau}^{L}p_\eta$ and $v_{a,\tau}q_\eta$, while the literal masked tensor
is recovered only after the complete signed $\eta$-integration.  Appending a
cancelling mask-layer pair changes layerwise quantities without changing the
physical multiplier.  Consequently no canonical cell statistic is assigned
to a terminal $\omega$.

\subsection{The coefficientwise physical Hilbert output}

Let $\cM_X$ be the finite set of supported source integers and let
$\mathcal I_X$ contain the supported pairs $(m,r)$ before coherent prime summation.
Let $\mathcal O_L$ be the opposite-row set, let $\cS_X$ contain the residual labels,
and put
\begin{equation}
 \mathcal J_X:=\{j\in\Z:j/J\in I_0\},
 \qquad
 \mathcal V_L:=\ell^2(\mathcal O_L\times\cS_X),
 \qquad
 \cH_X^{\rm coeff}
 :=\bigoplus_{(m,r)\in\mathcal I_X}
   \ell^2(\mathcal J_X;\mathcal V_L).
 \label{eq:tpc51-coefficient-Hilbert-space}
\end{equation}
The common compact support $I_0$ makes $\mathcal J_X$ finite for every
fixed $X$.  The direct sum deliberately retains $(m,r)$.  It therefore isolates the
residue/Mellin synthesis from the later coherent prime square and from the
grouping map $s=d(m)r$.

For $\theta=(a,\tau)\in\Theta_X^{\rm can}$ define the literal-mask layer
$k_{X,\theta}^{L}\in\cH_X^{\rm coeff}$ by
\begin{align}
 k_{X,\theta}^{L}(m,r,j)
 :={}&\one_{j\equiv a\!\!\!\pmod{H_0}}
 u_{a,\tau}^{L}(m)\phi_{a,\tau}(j/J)
 \notag\\
 &\times
 \sum_{\gamma\in\mathcal O_L}
 K_{m\gamma}v_{a,\tau}(\gamma)
 e_{\gamma,d(m)r}.
 \label{eq:tpc51-canonical-layer-vector}
\end{align}
Here $u_{a,\tau}^{L}(m)$ means the value at the unique row determined by
$m$.  No $p_\eta q_\eta$ mask layer occurs in
\eqref{eq:tpc51-canonical-layer-vector}.  Multiplying
\eqref{eq:tpc51-canonical-cellization} by the literal $K$ gives the exact
coefficientwise profile
\begin{align}
 G_{m,r}^{L}(j)
 &:={}
 \sum_{\gamma\in\mathcal O_L}
 \gamma_m^{(1)}\mathfrak A_{m,\gamma}^{\rm act}(j)
 e_{\gamma,d(m)r},
 \label{eq:tpc51-physical-vector-profile}\\
 G_X^{L}
 &=\sum_{a\bmod H_0}\int_{\Theta_a}
 k_{X,(a,\tau)}^{L}\,d\lambda_a(\tau)
 \quad\text{in }\cH_X^{\rm coeff}.
 \label{eq:tpc51-canonical-Bochner-reassembly}
\end{align}

For each $X$ the arithmetic and orbit supports are finite.  Strong
measurability and \eqref{eq:tpc51-canonical-L1-seminorm-mass} make
\eqref{eq:tpc51-canonical-Bochner-reassembly} a genuine Bochner integral.
The often-used phrase ``signed Bochner integral'' includes the complex case:
write the polar decomposition
\begin{equation}
 d\lambda_X(\theta)
 =\varepsilon_X(\theta)\,d\mu_X(\theta),
 \qquad
 \mu_X:=|\lambda_X|,
 \qquad
 |\varepsilon_X|=1\quad\mu_X\text{-a.e.},
 \label{eq:tpc51-polar-measure}
\end{equation}
where $\lambda_X=\bigoplus_a\lambda_a$.  Absorb the polar phase into
\begin{equation}
 A_{X,\theta}^{L}:=\varepsilon_X(\theta)k_{X,\theta}^{L}.
 \label{eq:tpc51-polar-layer}
\end{equation}

\subsection{Canonical synthesis, the actual direction, and the reduced Gram}

On its natural Bochner domain define
\begin{equation}
 \cS_X^{L}f
 :=\int_{\Theta_X^{\rm can}}
 f(\theta)A_{X,\theta}^{L}\,d\mu_X(\theta)
 \in\cH_X^{\rm coeff}.
 \label{eq:tpc51-canonical-synthesis}
\end{equation}
For example it is defined whenever
$\int |f(\theta)|\|A_{X,\theta}^{L}\|\,d\mu_X(\theta)<\infty$.
After the fixed projective weights are placed in the measure, the literal
physical coefficient is the distinguished direction
\begin{equation}
 \boxed{G_X^{L}=\cS_X^{L}\one.}
 \label{eq:tpc51-actual-direction}
\end{equation}
The coefficient function $\one$ is not a freely selected Mellin density; it
records the fixed provenance measure itself.

For the provenance measure at each fixed \(X\), this synthesis is a
bounded map from \(L^2(\mu_X)\).  Indeed, the finite residue part is
atomic, the physical output support is finite, the real Mellin phases
have unit modulus, and all remaining profile dependence grows at most
polynomially in the Mellin variables.  Since the density placed in
\(d\mu_X=d|\lambda_X|\) is Schwartz, one has
\begin{equation}
 \int_{\Theta_X^{\rm can}}
 \|A_{X,\theta}^L\|_{\cH_X^{\rm coeff}}^2\,d\mu_X(\theta)<\infty.
 \label{eq:tpc51-L2-synthesis-integrability}
\end{equation}
Cauchy--Schwarz therefore gives boundedness.  Its Gram operator is
\begin{equation}
 \Gamma_X^L:=(\cS_X^L)^*\cS_X^L,
 \label{eq:tpc51-Gram-operator}
\end{equation}
with integral kernel
\begin{equation}
 \cG_X^L(\theta,\theta')
 :=\langle A_{X,\theta'}^L,A_{X,\theta}^L\rangle_{\cH_X^{\rm coeff}}.
 \label{eq:tpc51-Gram-kernel}
\end{equation}
In particular,
\begin{equation}
 \|G_X^L\|_{\cH_X^{\rm coeff}}^2
 =\iint
 \cG_X^L(\theta,\theta')
 \,d\mu_X(\theta)d\mu_X(\theta').
 \label{eq:tpc51-actual-Gram-quadratic-form}
\end{equation}

For every fixed $X$, all index sets in
\eqref{eq:tpc51-coefficient-Hilbert-space} are finite, so the output space
is finite-dimensional, whereas
$L^2(\mu_X)$ has a non-atomic continuous Mellin component.  Hence
$\cS_X^L$ has an infinite-dimensional kernel.  A lower frame inequality on
all of $L^2(\mu_X)$ is therefore impossible for dimensional reasons.  The
correct coefficient space is the quotient
\begin{equation}
 \mathfrak Q_X^L
 :=L^2(\mu_X)/\ker\cS_X^L,
 \qquad
 \|[f]\|_{\mathfrak Q_X^L}
 :=\inf_{g\in\ker\cS_X^L}\|f+g\|_{L^2(\mu_X)},
 \label{eq:tpc51-quotient-space}
\end{equation}
or, equivalently, the reduced subspace
\begin{equation}
 \cK_X^L
 :=(\ker\cS_X^L)^\perp
 =\overline{\operatorname{ran}(\cS_X^L)^*}.
 \label{eq:tpc51-reduced-space}
\end{equation}
The reduced Gram is
\begin{equation}
 \Gamma_{X,\rm red}^L
 :=\Gamma_X^L|_{\cK_X^L}.
 \label{eq:tpc51-reduced-Gram}
\end{equation}
Its smallest positive spectral value is the exact finite-$X$ lower quotient
frame constant.  A useful asymptotic theorem must control this value on the
specified provenance subspace or must control the single actual direction
\eqref{eq:tpc51-actual-direction}; it must not replace the quotient by the
false full-space lower bound.

For later comparison with the inherited Minkowski argument, let
$w_B(\theta)\ge1$ be the fixed polynomial/seminorm weight produced by the
$C^B$ orbit profile.  Define the canonical displayed-representation envelope
\begin{equation}
 \cE_{1,B}^L(f)
 :=\int_{\Theta_X^{\rm can}}
 w_B(\theta)|f(\theta)|
 \|A_{X,\theta}^L\|_{\cH_X^{\rm coeff}}\,d\mu_X(\theta).
 \label{eq:tpc51-canonical-L1-envelope}
\end{equation}
The actual-direction condition number is
\begin{equation}
 \kappa_{\rm can,B}^L(X)
 :=\frac{\cE_{1,B}^L(\one)^2}
 {\|\cS_X^L\one\|_{\cH_X^{\rm coeff}}^2},
 \label{eq:tpc51-actual-condition-number}
\end{equation}
when the denominator is nonzero.  Proving
$\kappa_{\rm can,B}^L(X)=X^{o(1)}$, or the corresponding uniform reduced-Gram
bound on a declared finite provenance subspace, is a meaningful
representation-efficiency statement.  The existence of
$\ker\cS_X^L\ne\{0\}$ by itself is not a physical obstruction; a genuine
negative result must place the actual direction, or a required canonical
physical family, in a polynomial near-kernel.

\subsection{The full TPC--48 envelope is a different nonlinear object}

The terminal projective layer in TPC--48 has, after Fourier transformation
in the frozen intercept,
\begin{equation}
 B_{\omega,m}(\alpha)
 :=\sum_{p,r}A_\omega(p,r,m)\e(-pr\alpha)
 v_{\omega,p,r,m}.
 \label{eq:tpc51-inherited-row-vector}
\end{equation}
For fixed $m$, distinct residual labels separate the $r$-square, but at fixed
$(m,r)$ the $p$-sum remains coherent.  A fixed admissible global
representation $\mathscr R$ has the envelope
\begin{equation}
 \mathfrak S_{\mathscr R}(\alpha)
 :=\int
 C_{\rm LS}(\phi_\omega,H_0)^{1/2}
 \left(\sum_m\|B_{\omega,m}(\alpha)\|^2\right)^{1/2}
 \,d|\nu|(\omega).
 \label{eq:tpc51-full-profile-envelope}
\end{equation}
Its norm order is exactly:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.5em]
 \item the outer projective reassembly is $L^1(d|\nu|)$;
 \item the source-row aggregation inside each layer is $\ell^2$ in $m$;
 \item each summand uses the residual Hilbert norm; and
 \item the prime sum at fixed $(m,r)$ is formed before that norm is taken.
\end{enumerate}
Moreover $C_{\rm LS}^{1/2}$ is a profile seminorm weight, not a declared
Hilbert norm.  The pointwise infimum over admissible representations is not
integrated; annular arguments retain one fixed jointly measurable global
representation.  The resulting field is the completed frozen family, and
only its $h=h_0$ slice has literal physical provenance.

Thus \eqref{eq:tpc51-full-profile-envelope} is not the norm of
$\cS_X^L\one$, is not a finite-matrix nuclear norm, and is not the native
physical atomic diagonal
\begin{equation}
 \cD_0=\sum_i\sum_u|b_{i,u}|^2.
 \label{eq:tpc51-native-atomic-diagonal}
\end{equation}
The operator \eqref{eq:tpc51-canonical-synthesis} isolates only the
provenance-canonical residue/Mellin no-cancellation question before coherent
prime summation.  Even a subpower quotient condition number leaves the
coherent prime square, the map $s=d(m)r$, frozen-to-$h_0$ localization, and
the comparison with the native affine Gram face open.
