\section{Introduction}
\label{sec:tpc51-introduction}

The TPC reduction has reached a narrow but consequential question.  A
fixed-complexity residue/Mellin cell survives the literal static row
mask with zero polynomial loss \citep{WangTPC50}, whereas the completed
TPC--48 estimate is still expressed as a signed outer integral of
layerwise Hilbert norms \citep{WangTPC48}.  Can the latter integral be
replaced by the energy of the physically reassembled coefficient?
Calling this a ``frame problem'' is useful only after the domain of the
putative frame has been specified.  The continuous Mellin coefficient
space, the finite family of physical cutoff shapes, and the one
provenance-fixed coefficient density are three different domains.

This paper separates them.  The strongest naive statement is false for
an elementary dimensional reason: at every finite scale the physical
coefficient space is finite dimensional, while arbitrary smooth signed
Mellin densities form an infinite-dimensional space.  We give both an
abstract smooth kernel and an explicit differential kernel for the
phase dictionary.  Thus no amount of numerical conditioning evidence
can establish a lower Riesz bound on the full continuous parameter
space.

The negative theorem does not apply to one fixed Mellin density.
Mellin inversion recombines the unique transform density of a fixed
cutoff into the values of that cutoff at declared samples.  This gives
an exact formula, not a heuristic orthogonality assertion.  Separately,
for a fixed finite scalar family the remaining question is finite
dimensional: after exact redundancies are removed, its condition number
is controlled by the least eigenvalue of a normalized sampled Gram
matrix.  We prove that this eigenvalue is bounded away from zero for
every fixed limiting-independent scalar family on the
prime--squarefree dyadic row universe.  We also prove a uniform version
for a retained log-Fourier bank of polylogarithmic degree and show that
the literal static mask perturbs its lower bound by only
\(O(\varepsilon_X(2K+1)^2)\).  These statements do not by themselves
identify the genuine \(X\)-dependent, Hilbert-valued orbit-translate
family with a fixed scalar family.

\subsection{Main results}

The results are organized by the logical strength of their domains.

\begin{enumerate}[label=\textup{(R\arabic*)},leftmargin=3.2em]
 \item \textbf{Continuous-domain no-go.}
 Every integral synthesis from smooth densities on an interval into a
 finite-dimensional Hilbert space has a nonzero smooth kernel
 (\cref{thm:tpc51-smooth-kernel}).  For logarithmic phase samples the
 kernel is explicit (\cref{prop:tpc51-explicit-phase-kernel}), and
 neighboring atoms give arbitrarily large signed-measure condition
 number (\cref{prop:tpc51-neighbouring-atoms}).

 \item \textbf{Exact canonical direction.}
 For a fixed smooth shape, its weighted Mellin--Wiener envelope and its
 physical synthesis norm are given exactly by
 \cref{thm:tpc51-canonical-mellin-direction}.  A declared sample set
 satisfying \(\inf_n|W(x_n)|\geq\eta>0\) has
 \(O_{B,W,\eta}(1)\) condition number.  Coordinate samples approaching a finite-order zero
 incur the corresponding power loss, and a flat cutoff boundary can
 incur losses beyond every fixed power
 (\cref{cor:tpc51-boundary-zero}).

 \item \textbf{Finite quotient criterion.}
 For a fixed finite scalar shape family, the squared quotient condition number lies
 between the inverse least positive eigenvalue and the number of
 retained shapes times that inverse eigenvalue for its normalized Gram
 matrix
 (\cref{thm:tpc51-finite-gram-criterion}).  Weak convergence of sample
 measures and limiting linear independence therefore give an
 \(O(1)\) quotient frame
 (\cref{thm:tpc51-limit-gram}).

 \item \textbf{Arithmetic sampling.}
 The logarithmic empirical measures of admissible prime--squarefree
 rows converge unconditionally to
 \[
   d\nu(x,y)=e^{x+y}\,dx\,dy,
   \qquad 0\leq x,y\leq\log2,
 \]
 and their Fourier moments admit a quantitative fixed-modulus estimate
 (\cref{thm:tpc51-row-equidistribution}).  Consequently every fixed
 limiting-independent scalar family has a stable sampled Gram, and
 every log-Fourier bank of degree \(K\leq(\log X)^A\) obeys uniform
 Riesz bounds (\cref{thm:tpc51-polylog-fourier-frame}).

 \item \textbf{Literal-mask robustness for declared finite families.}
 If a zero--one mask deletes at most \(\varepsilon_X\) of the complete row
 universe in every source row, the lower bound of a two-dimensional
 degree-\(K\) bank changes by at most
 \(C\varepsilon_X(2K+1)^2\), uniformly in an arbitrary nonnegative weight
 on the other side (\cref{thm:tpc51-masked-frame}).  At the inherited
 endpoint this is \(o(1)\) for every fixed polylogarithmic degree.  The
 fixed finite scalar-family version has constants depending on that
 family.

 \item \textbf{Exact boundary and conditional bridge.}
 The positive result proves the abstract fixed finite scalar-family and
 retained finite-bank sampled frames.  Transfer to the actual
 coefficientwise pre-terminal provenance requires a uniform normalized
 Gram or uniform relative Fourier-tail theorem for the
 \(X\)-dependent Hilbert-valued orbit-translate family, together with a
 norm comparison from the actual weighted continuous envelope to that
 Hilbert energy.  \Cref{prop:tpc51-actual-bridge-criterion} records this
 criterion and the fact that it is not verified here.  The result also
 does not commute an outer \(L^1\) integral through the nonlinear
 TPC--48 layer norm and does not control the coherent prime square,
 residual grouping, physical-shift localization, or native affine
 Gram.
\end{enumerate}

\subsection{Three levels of assertion}

To prevent a local Hilbert-space lemma from being promoted into a
number-theoretic conclusion, we use the following ledger throughout.

\begin{description}[style=nextline,leftmargin=2.2em]
 \item[Level L0: exact algebra/analysis.]
 Kernels, Mellin inversion identities, Gram formulas, and finite-matrix
 perturbation bounds.  These statements do not use primes.
 \item[Level L1: arithmetic interface.]
 Fixed-modulus prime number theory, squarefree progression counts, and
 the inherited static-mask degree defect.  These prove the sampled
 quotient bounds on the stated row universe.
 \item[Level L2: target correlation.]
 A fixed-shift prime-pair or twin-prime estimate.  No result at this
 level is proved or inferred here.
\end{description}

In particular, no actual TPC provenance gate is called closed merely
from the abstract fixed-family theorem.  Any future use of that word
must first verify the bridge criterion in
\cref{prop:tpc51-actual-bridge-criterion}; it can never refer to the
parity problem or the full TPC determinant route here.

\subsection{Organization}

\Cref{sec:tpc51-inherited-interface} reconstructs the canonical
operator before the projective mask decomposition.
\Cref{sec:tpc51-continuous-kernels} proves the continuous-domain
obstructions.  \Cref{sec:tpc51-canonical-direction} treats the single
physical direction, and \cref{sec:tpc51-quotient-frames} gives the
finite quotient criterion.  \Cref{sec:tpc51-arithmetic-sampling}
proves the prime--squarefree sampling theorem.
\Cref{sec:tpc51-mask-robustness} transfers it through the literal mask.
The endpoint and open doors are given in \cref{sec:tpc51-endpoint}; the
reproducible finite certificate is described in
\cref{sec:tpc51-certificate}.
