\section{Finite canonical families and quotient frames}
\label{sec:tpc51-quotient-frames}

A physical decomposition may contain several fixed shapes.  Exact
duplicates should be removed algebraically, whereas nearly duplicate
shapes must be charged through a condition number.  This section gives
the finite-dimensional criterion that distinguishes the two cases.

\subsection{The normalized sampled Gram}

Let \(K\) be a compact metric space, let
\(W_1,\ldots,W_R\in C(K)\) be nonzero fixed shapes, and choose positive
normalization weights
\begin{equation}
 A_1,\ldots,A_R>0,
 \qquad
 D_A:=\diag(A_1,\ldots,A_R).
 \label{eq:tpc51-family-normalizations}
\end{equation}
For the Mellin application, \(K\) may be a compact logarithmic box and
\(A_r\) is the weighted Wiener--Mellin mass of the corresponding fixed
physical shape.  The abstract argument below uses only positivity of
the \(A_r\).

Fix samples \(x_1,\ldots,x_N\in K\) and positive weights
\(w_1,\ldots,w_N\).  Write
\begin{equation}
 M:=\sum_{n=1}^Nw_n
 \label{eq:tpc51-total-sample-mass}
\end{equation}
and define the physical sampled synthesis \(F:\C^R\to\C^N\) by
\begin{equation}
 (Fc)_n
 :=w_n^{1/2}\sum_{r=1}^Rc_rW_r(x_n).
 \label{eq:tpc51-family-synthesis}
\end{equation}
The declared canonical family envelope is
\begin{equation}
 \cE_{\mathrm{fam}}(c)
 :=M^{1/2}\sum_{r=1}^RA_r|c_r|
 =M^{1/2}\|D_Ac\|_1.
 \label{eq:tpc51-family-envelope}
\end{equation}
In the Mellin specialization this is exactly the envelope obtained by
separating the fixed shapes, applying Mellin inversion to each one, and
then using Minkowski's inequality.

Introduce the normalized matrix and Gram matrix
\begin{equation}
 \mathsf B:=M^{-1/2}FD_A^{-1},
 \qquad
 G:=\mathsf B^*\mathsf B.
 \label{eq:tpc51-normalized-Gram}
\end{equation}
Thus, with \(d=D_Ac\),
\begin{equation}
 \frac{\cE_{\mathrm{fam}}(c)}{\|Fc\|_2}
 =\frac{\|d\|_1}{\|\mathsf Bd\|_2}.
 \label{eq:tpc51-family-condition-reduction}
\end{equation}

If \(\ker\mathsf B\ne\{0\}\), the right side depends on the chosen
representative of one physical output.  The canonical quotient norm is
\begin{equation}
 \|[d]\|_{1,\mathrm q}
 :=\inf_{k\in\ker\mathsf B}\|d+k\|_1,
 \label{eq:tpc51-quotient-l1}
\end{equation}
and the quotient frame condition number is
\begin{equation}
 K_{\mathrm q}(\mathsf B)
 :=\sup_{\mathsf Bd\ne0}
 \frac{\|[d]\|_{1,\mathrm q}}{\|\mathsf Bd\|_2}.
 \label{eq:tpc51-quotient-condition}
\end{equation}
This removes exact algebraic redundancy; it does not remove a small
positive singular value.

\begin{theorem}[Exact normalized-Gram criterion]
\label{thm:tpc51-quotient-Gram}
\label{thm:tpc51-finite-gram-criterion}
Assume \(\mathsf B\ne0\), and let \(\sigma_+(\mathsf B)\) be its
smallest positive singular value.  If
\(\lambda_+(G)=\sigma_+(\mathsf B)^2\) denotes the smallest positive
eigenvalue of \(G\), then
\begin{equation}
 \boxed{
 \frac1{\lambda_+(G)}
 \le K_{\mathrm q}(\mathsf B)^2
 \le\frac{R}{\lambda_+(G)}.}
 \label{eq:tpc51-quotient-Gram-bounds}
\end{equation}
If \(G\) is positive definite, the quotient is trivial and
\eqref{eq:tpc51-quotient-Gram-bounds} bounds the condition number of the
displayed canonical family itself.
\end{theorem}

\begin{proof}
Let \(V=(\ker\mathsf B)^\perp\).  Every output has a unique
representative \(d_V\in V\), and
\[
 \|[d]\|_{1,\mathrm q}
 \le\|d_V\|_1
 \le\sqrt R\|d_V\|_2
 \le\frac{\sqrt R}{\sigma_+(\mathsf B)}
       \|\mathsf Bd\|_2.
\]
This proves the upper bound.  For the lower bound, take a unit right
singular vector \(v\in V\) belonging to \(\sigma_+(\mathsf B)\).
For every \(k\in\ker\mathsf B\), orthogonality gives
\(\|v+k\|_2\ge1\), and hence \(\|v+k\|_1\ge1\).  Therefore
\[
 \|[v]\|_{1,\mathrm q}\ge1,
 \qquad
 \|\mathsf Bv\|_2=\sigma_+(\mathsf B),
\]
which proves the lower bound.
\end{proof}

\begin{corollary}[Subpower quotient criterion]
\label{cor:tpc51-subpower-quotient}
For a family depending on \(X\), the two hypotheses
\begin{equation}
 R_X=X^{o(1)},
 \qquad
 \lambda_+(G_X)^{-1}=X^{o(1)}
 \label{eq:tpc51-subpower-Gram-hypotheses}
\end{equation}
imply
\begin{equation}
 K_{\mathrm q}(\mathsf B_X)^2=X^{o(1)}.
 \label{eq:tpc51-subpower-quotient-conclusion}
\end{equation}
Conversely, if \(\lambda_+(G_X)\le X^{-\sigma+o(1)}\) for a fixed
\(\sigma>0\), then
\(K_{\mathrm q}(\mathsf B_X)^2\ge X^{\sigma+o(1)}\).
\end{corollary}

The quotient criterion is stronger than necessary for one specified
physical coefficient.  For a fixed direction \(d_X\) with
\(\mathsf B_Xd_X\ne0\), it suffices to bound the single ratio
\begin{equation}
 \frac{\|[d_X]\|_{1,\mathrm q}^2}
      {d_X^*G_Xd_X};
 \label{eq:tpc51-one-direction-Rayleigh}
\end{equation}
no estimate of the least eigenvalue on unrelated coefficient directions
is then required.

\subsection{Duplicate and nearly duplicate shapes}

\begin{proposition}[Exact duplicate obstruction]
\label{prop:tpc51-duplicate-shapes}
If two shapes satisfy \(W_1(x_n)=W_2(x_n)\) at every sampled point,
then the unquotiented physical synthesis \(F\) has the nonzero kernel
direction \(c=e_1-e_2\).  Thus no lower bound for the displayed
envelope \eqref{eq:tpc51-family-envelope} can hold on all
representatives.  After quotienting by this direction, the duplicate
contributes no physical dimension.
\end{proposition}

This is an intrinsic redundancy of the chosen finite family.  It is
different from appending a null pair to a representation after the
canonical family has been fixed.

\begin{proposition}[Near-duplicate condition lower bound]
\label{prop:tpc51-near-duplicate-shapes}
For two shapes and the signed coefficient \(c=(1,-1)\),
\begin{equation}
 \frac{\cE_{\mathrm{fam}}(c)}{\|Fc\|_2}
 =\frac{M^{1/2}(A_1+A_2)}
 {\left(\sum_{n=1}^Nw_n
       |W_1(x_n)-W_2(x_n)|^2\right)^{1/2}}.
 \label{eq:tpc51-near-duplicate-exact}
\end{equation}
where the ratio is interpreted as \(+\infty\) if the denominator
vanishes.  In that case \(c\) is an exact sampled-kernel direction, as
in \cref{prop:tpc51-duplicate-shapes}.
In particular, if
\begin{equation}
 \left(\frac1M\sum_{n=1}^Nw_n
 |W_1(x_n)-W_2(x_n)|^2\right)^{1/2}
 \le\varepsilon,
 \label{eq:tpc51-near-duplicate-distance}
\end{equation}
then the unquotiented condition number in this direction is at least
\((A_1+A_2)/\varepsilon\).
\end{proposition}

\begin{proof}
Both assertions follow by evaluating
\eqref{eq:tpc51-family-synthesis} and
\eqref{eq:tpc51-family-envelope} at \(c=(1,-1)\).
\end{proof}

The lower bound can be polynomial even though both individual shapes
are perfectly nondegenerate.  Here is a Mellin-specific example.
Suppose \(K\) is contained in a fixed compact interval of
\((0,\infty)\), \(W_1(x)=W(x)\), and
\(W_2(x)=W(e^\delta x)\), where \(W\) is \(C^1\) on a fixed compact
interval containing every \(x_n\) and \(e^\delta x_n\).  For
\(|\delta|\le1\), the mean-value theorem in logarithmic coordinates
gives
\begin{equation}
 |W(e^\delta x_n)-W(x_n)|
 \le C_W|\delta|.
 \label{eq:tpc51-dilation-near-duplicate}
\end{equation}
If \(A_1=A_2=A_B(W)\), as happens for the weighted Mellin masses of
these two dilates, then
\begin{equation}
 \frac{\cE_{\mathrm{fam}}(1,-1)}
      {\|F(1,-1)\|_2}
 \gg_W |\delta|^{-1}.
 \label{eq:tpc51-dilation-condition}
\end{equation}
A separation \(|\delta|=X^{-\sigma+o(1)}\) therefore creates a genuine
polynomial loss.  A fixed dyadic separation gives only a fixed constant
and is not, by itself, an asymptotic obstruction.

\subsection{A positive limiting quotient theorem}

The preceding condition is directly verifiable for a fixed physical
family.  For each \(X\), let \(x_{n,X}\in K\) and \(w_{n,X}>0\), put
\(M_X=\sum_{n=1}^{N_X}w_{n,X}\), and define the probability measure
\begin{equation}
 \mu_X:=\frac1{M_X}\sum_{n=1}^{N_X}w_{n,X}\delta_{x_{n,X}}.
 \label{eq:tpc51-family-empirical-measure}
\end{equation}
Let \(F_X\), \(\mathsf B_X\), and \(G_X\) be the matrices defined
above for this sampled set.

\begin{theorem}[Positive limiting sampled frame]
\label{thm:tpc51-limiting-frame}
\label{thm:tpc51-limit-gram}
Let \(K\) be a compact metric space and let \(R\) be fixed.  Suppose
\(\mu_X\) converges weakly to a probability measure \(\mu\) on \(K\),
and suppose \(W_1,\ldots,W_R\in C(K)\) are linearly independent in
\(L^2(\mu)\).  Define
\begin{equation}
 (G_\infty)_{rs}
 :=\frac1{A_rA_s}
   \int_K\overline{W_r(x)}W_s(x)\,d\mu(x).
 \label{eq:tpc51-limiting-Gram}
\end{equation}
Then \(G_\infty\) is positive definite and
\begin{equation}
 G_X\longrightarrow G_\infty
 \quad\text{entrywise and in operator norm}.
 \label{eq:tpc51-Gram-convergence}
\end{equation}
Consequently, for all sufficiently large \(X\),
\begin{equation}
 \lambda_{\min}(G_X)
 \ge\frac12\lambda_{\min}(G_\infty)>0,
 \qquad
 K_{\mathrm q}(\mathsf B_X)^2
 \le\frac{2R}{\lambda_{\min}(G_\infty)}.
 \label{eq:tpc51-limiting-frame-bound}
\end{equation}
\end{theorem}

\begin{proof}
For \(u\in\C^R\),
\[
 u^*G_\infty u
 =\int_K\left|
   \sum_{r=1}^R\frac{u_r}{A_r}W_r(x)
  \right|^2d\mu(x).
\]
Linear independence makes this positive for \(u\ne0\), so
\(G_\infty\) is positive definite.  Each product
\(\overline{W_r}W_s\) is continuous on \(K\); weak convergence gives
entrywise convergence.  Since \(R\) is fixed, entrywise convergence
implies operator-norm convergence.  Weyl's eigenvalue inequality then
gives the first bound in \eqref{eq:tpc51-limiting-frame-bound}, and
\cref{thm:tpc51-quotient-Gram} gives the second.
\end{proof}

If the original family is linearly dependent in \(L^2(\mu)\), one must
first quotient by its fixed limiting relations, choose a basis of the
resulting image, and apply the theorem to that reduced family.  Merely
replacing \(\lambda_{\min}\) by the smallest positive eigenvalue of the
unreduced finite-\(X\) Gram can be misleading: an exact limiting
relation may appear at finite \(X\) as a small positive eigenvalue.

Weak convergence alone is also insufficient when the number of shapes
grows with \(X\).  A polylogarithmic Fourier bank requires a quantitative
sampling theorem uniform over that bank.  The present theorem provides
the fixed-family endpoint and the exact Gram criterion; any growing-bank
application must verify the additional uniformity explicitly.

Finally, the quotient frame concerns the canonical smooth-shape
reassembly on its declared atomic coordinates.  It neither estimates a
coherent prime sum inside one residual coordinate nor controls residual
grouping, frozen-to-physical localization, or identification with the
native affine Gram face.  In particular, it is not a closure theorem for
the full TPC--48 Banach envelope.
