\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={One-Sided Passage Beyond the Poisson Boundary: Shell-Averaged Zero Modes and Asymmetric Conductor Rectangles in a Primitive Mobius Tail},
 pdfauthor={Liang Wang},
 pdfsubject={Asymmetric mixed-shell estimates beyond the Poisson-short boundary},
 pdfkeywords={Mobius tail, Poisson boundary, zero mode, exact conductors, large sieve, mixed shell, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cI}{\mathcal I}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\cond}{\operatorname{cond}}
\newcommand{\lcm}{\operatorname{lcm}}

\title{\textbf{One-Sided Passage Beyond the Poisson Boundary:}\\
\textbf{Shell-Averaged Zero Modes and Asymmetric}\\
\textbf{Conductor Rectangles in a Primitive M\"obius Tail}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Fix \(h\in\mathbb Z\setminus\{0\}\), put \(H=\operatorname{rad}|h|\),
and let \(R=X^{1/2-\delta+o(1)}\) be the finite Ramanujan cutoff in the
matched divisor expansion of a primitive fixed-shift M\"obius
residual.  The earlier centered-block argument closes a square
\(u,v\le S\) under the condition that the common short prefix satisfies
\(HS<JX^{-\eta_0}\).  We keep that prefix on one row but attach on the
other row a new shell \(S<v\le T\), where \(T\) may exceed the
Poisson length \(J=X^{1-\beta+o(1)}\).  We write
\(Q=X^{\beta+o(1)}\), so that \(QJ\asymp X\).

The correct object is the exact calibrated-prefix increment.  If
\(P_{m,S}\) is the calibrated residual prefix and
\(L_{n;S,T}=P_{n,T}-P_{n,S}\), then pointwise
\[
 P_{m,S}L_{n;S,T}
 =\sum_{u\le S}\sum_{S<v\le T}
 b_R(u)a(v)\one_{u\mid mj+h}\one_{v\mid nj+h}
 -\delta_H(m)L_{n;S,T},
\]
where \(a(w)=-\mu(w)\log w\) and
\(b_R(w)=a(w)-\lambda'_R(w)\), with the inherited coprimality
conditions understood.  Thus the
apparently surviving long single channel cancels algebraically; the
remaining scalar drift satisfies
\(\delta_H(\ell d_0)\ll X^{o(1)}/L\).  The joint nonzero channel admits
an asymmetric exact-conductor rectangle.  If \(S=X^{s+o(1)}\),
\(T=X^{t+o(1)}\), and \(s\le t\), its certified saving is
\[
 \eta_{\rm asym}(\beta;s,t)=
 \min\left\{
 1-\frac{3\beta}{2},
 \frac{\beta+1-2s-2t}{2},
 \frac{3-\beta-s-5t}{4}
 \right\}.
\]

The additive zero frequency is not covered by the nonzero
Ramanujan--Gauss estimate.  We prove a separate shell theorem.  For
each off-diagonal row pair, split the shared factor
\(g=(u,v)\mid m-n\) at \(SX^{-\kappa}\), where \(0<\kappa<s\).
For small \(g\), uniform M\"obius calibration at the two endpoints
\(S/g\) and \(T/g\) cancels the common main constant.  For large
\(g\), divisibility of the nonzero row determinant gives a factor
\(X^\kappa/S\).  If \(\mathcal Z_1\) is the absolute row-pair mass,
then for every fixed \(A>0\) the resulting zero-mode bound is
\[
 \ll J\mathcal Z_1
 \left\{(\log X)^{-A}+X^\kappa S^{-1}X^{o(1)}\right\}.
\]
This mass factor is not hidden: the usual soft estimate
\(\mathcal Z_1\ll Q^2X^\varepsilon\) does not turn the first term into
logarithmic saving.  When \(\eta_{\rm asym}>0\) with fixed margins and
the stated interfaces hold, the explicit fixed-projective-mass
hypothesis \(\mathcal Z_1\ll Q^2(\log X)^K\) makes the entire
calibrated mixed increment
\(O_B(XQ(\log X)^{-B})\) for every fixed \(B>0\).  With only the soft
mass hypothesis, test functions with \(\widehat F(0)=0\) give
fixed-power closure; the displayed zero mode remains the sole
mass-sensitive term in general.

For \(S=R\) and \(T=RX^\xi\), the joint saving becomes
\[
 \min\left\{
 1-\frac{3\beta}{2},
 \frac{\beta+4\delta-1}{2}-\xi,
 \frac{6\delta-\beta-5\xi}{4}
 \right\}.
\]
Consequently there is a strict one-sided passage beyond \(T=J\) when
\[
 \frac12+\delta-\beta<\xi<
 \min\left\{
 \frac{\beta+4\delta-1}{2},
 \frac{6\delta-\beta}{5}
 \right\},
\]
provided \(\beta<2/3\), \(\beta<1/2+\delta\), and all inequalities
have fixed margins.  This is an incremental mixed-shell estimate,
not a closure of the full residual, a Hardy--Littlewood asymptotic, a
twin-prime lower bound, or a general breach of sieve parity.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; Poisson boundary;
mixed divisor shell; shell-averaged zero mode; exact conductors;
tensor large sieve; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11L07, 11L40.

\input{sections/introduction}
\input{sections/interface-prefixes}
\input{sections/asymmetric-four-channel}
\input{sections/zero-shell}
\input{sections/asymmetric-conductor}
\input{sections/exponent-passage}
\input{sections/splicing-scope}
\input{sections/certificate-conclusion}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
