\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cM}{\mathcal M}
\newcommand{\cN}{\mathcal N}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cT}{\mathcal T}
\newcommand{\one}{\mathbf 1}
\newcommand{\op}{\mathrm{op}}
\newcommand{\HS}{\mathrm{HS}}
\newcommand{\ee}[1]{e^{2\pi i #1}}

\hypersetup{
  pdftitle={Residue-Fiber Orthogonality at the Triple-Prime Mobius Gate: Canonical Hilbert Defects, Coherent Synthesis, and Exact Convolution Counterterms},
  pdfauthor={Liang Wang},
  pdfsubject={Exact separation of residue-fiber progression energy from the coherent physical Mobius gate},
  pdfkeywords={Mobius correlation, residue fiber, Hilbert space, Moore-Penrose projection, coherent synthesis, Dirichlet convolution, parity boundary}
}

\title{\bfseries Residue--Fiber Orthogonality at the Triple--Prime M\"obius Gate:\\
Canonical Hilbert Defects, Coherent Synthesis,\\
and Exact Convolution Counterterms}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
TPC--41 separated the terminal physical packet into a closed same--row
alias sector and a surviving cross--row four--M\"obius sector, while also
proving scalar logarithmic decorrelation in reduced residue classes for
almost all admissible triple--prime moduli.  We determine exactly how far
that input can propagate into the physical Hilbert output.  For every
fixed alias, terminal coefficient vectors belonging to distinct integers in the
same residue class are orthogonal.  Consequently the natural
Hilbert--valued residue energy is identically the already controlled atomic
diagonal; the remaining physical term is entirely the coherent synthesis
between distinct residue packets.  We give a canonical Moore--Penrose
factorization into the scalar-visible residue-synchronous sector and a
directional defect supported on its domain-orthogonal complement, prove
a sharp black-box obstruction for the latter, and reduce each projective
mask layer to an orbit--slope Bessel
form.  A second exact theorem rules out a different shortcut: completing
the localized Dirichlet convolution produces boundary faces whose sum is
the negative of the original local cell on the physical product window.
Thus the shifted-prime completion cancels against the source complement
rather than estimating the local packet.  These results do not prove the
remaining four--M\"obius cancellation or breach sieve parity; they replace
two broad proposed routes by one explicit cross--residue, orbit--slope
coefficient target.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; residue fiber;
Hilbert output; Moore--Penrose projection; coherent synthesis; Dirichlet
convolution; triple--prime CRT modulus; parity boundary.

\medskip
\noindent\textbf{Convention.}
All complex inner products are linear in the first argument.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11L40; Secondary 15A09,
42A16, 11N36.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/canonical-factorization}
\input{sections/residue-orthogonality}
\input{sections/coherent-synthesis}
\input{sections/hilbert-large-sieve}
\input{sections/projective-orbit-reduction}
\input{sections/convolution-counterterm}
\input{sections/quantitative-boundary}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\bibliographystyle{plainnat}
\bibliography{references}
\end{document}
