\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Calibrated Base Closure in a Primitive Mobius Tail: Ramanujan-Square Zero Modes and Passage Beyond the Poisson Length},
 pdfauthor={Liang Wang},
 pdfsubject={Closure of a calibrated base square in a primitive Mobius tail},
 pdfkeywords={Mobius tail, additive zero mode, Ramanujan sums, calibrated base, Poisson boundary, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cN}{\mathcal N}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cW}{\mathcal W}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\cond}{\operatorname{cond}}
\newcommand{\supp}{\operatorname{supp}}

\title{\textbf{Calibrated Base Closure in a Primitive M\"obius Tail:}\\
\textbf{Ramanujan-Square Zero Modes and Passage}\\
\textbf{Beyond the Poisson Length}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let \(P_{m,S}\) be the calibrated residual prefix in a primitive
opened row \(m=\ell d\), where \(\ell\asymp L\) is prime, \(d\) is
squarefree, and \(R\le S\).  Earlier exact-conductor estimates close
the retained nonzero additive spectrum of the centered selected square
when \(S\) is strictly below the Poisson length.  They do not, by their
displayed formulas, estimate the connected additive zero mode.  This
paper closes that missing base mode for the actual opened-row
provenance and then restores the calibrated physical square.

On the primitive orbit \((j,H)=1\), write
\[
 Z_{m,S}(j)=\sum_{\substack{u\le S\\(u,mH)=1}}
 b_R(u)\left(\one_{u\mid mj+h}-\frac1u\right),
 \qquad P_{m,S}=Z_{m,S}+E_S(m).
\]
For distinct rows \(m,n\), the complete-period zero kernel of
\(Z_{m,S}Z_{n,S}\) is
\[
 K_S^0(m,n)=
 \sum_{u,v\le S}\frac{b_R(u)b_R(v)}{uv}
 \left((u,v)\one_{(u,v)\mid m-n}-1\right),
\]
with the primitive row-coprimality restrictions understood.  The
identity
\[
 g\one_{g\mid\Delta}-1
 =\sum_{\substack{k\mid g\\k>1}}c_k(\Delta)
\]
factorizes it exactly as
\[
 K_S^0(m,n)=\sum_{k>1}c_k(m-n)B_{k,S}(m)B_{k,S}(n),
 \qquad
 B_{k,S}(m)=
 \sum_{\substack{u\le S\\k\mid u\\(u,mH)=1}}
 \frac{b_R(u)}u.
\]
For \(k\le X^\kappa\), an exact multiple-density identity for the
finite Ramanujan model and the classical uniform M\"obius calibration
give
\[
 B_{k,S}(m)=\frac{\mu(k)}{\varphi(k)}\delta_H(m)
 +O_A\!\left(\frac1{\varphi(k)(\log X)^A}\right),
 \qquad
 \delta_H(m)\ll \frac{\log\log(3X)}L.
\]
For \(k>X^\kappa\), the cofactor mass bound and \(m-n\ne0\) yield a
Ramanujan tail of size \(X^{-\kappa+o(1)}\).  Consequently, for every
fixed \(A>0\) and every fixed
\(0<\kappa<\min\{s,\tfrac12(\tfrac12-\delta)\}\),
\[
 K_S^0(m,n)
 \ll_A (\log X)^{-A}
 +L^{-2}(\log\log(3X))^3+X^{-\kappa+o(1)}.
\]

The actual physical row coefficients have \(O(Q)\) one-row absolute
mass.  Extracting frequency zero before Mellin separation therefore
closes the physical base zero mode.  Uniform endpoint calibration also
closes the three scalar channels \(EZ,ZE,EE\).  Combining these facts
with the inherited static or dynamic exact-conductor theorem proves
\[
 \mathcal Q_S^{\rm phys}
 \ll_B XQ(\log X)^{-B}
\]
throughout its strict Poisson-short base region.  Splicing this base
estimate with the annular cutoff-stability theorem closes the selected
calibrated square at certain \(T>J\).  In particular, the rational
sample
\[
 \delta=\frac3{20},\quad \beta=\frac{31}{50},\quad
 s=\frac7{20},\quad t=\frac{39}{100}
\]
is upgraded from conditional cutoff stability to a closed selected
truncated square.  The higher-\(\beta\) sample whose base already lies
beyond the Poisson length is not covered.  No ultra-long complement,
positivity statement, Hardy--Littlewood asymptotic, twin-prime theorem,
or general parity breakthrough is claimed.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; calibrated base;
additive zero mode; Ramanujan sum; Poisson boundary; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11L07, 11L40.

\input{sections/introduction}
\input{sections/interface-bridge}
\input{sections/ramanujan-factorization}
\input{sections/multiple-calibration}
\input{sections/base-zero-closure}
\input{sections/nonzero-scalar-reassembly}
\input{sections/passage-theorem}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
