\section{Finite certificate and reproducibility}
\label{sec:computation}

The proofs above are analytic.  A deterministic finite certificate is
included only to test the exact algebra that precedes the estimates.  It
does not test a prime-pair asymptotic.  The script
\texttt{experiments/factor\_ray\_certificate.py} performs the following
checks for a documented finite hyperbolic support.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item It enumerates every supported factor pair $(n,m)$ and groups it by
 the reduced fraction $(a,b)=(n/(n,m),m/(n,m))$.  At several real
 frequencies it compares the original factor-pair sum with the compressed
 ray sum.

 \item It computes all adjacent gaps between the ordered ray frequencies
 (and hence their global minimum), verifies the exact hyperbolic lower
 bound in \eqref{eq:exact-ratio-spacing}, and records the minimizing rays.

 \item It evaluates the hard-band quadratic form in two ways: directly
 from the factor pairs and from the compressed ray coefficients.  It also
 verifies that the Fej\'er multiplier is diagonal once the finite frequency
 bandwidth exceeds the reciprocal of the actual minimum ray gap.

 \item It counts the determinant layers permitted by the compact-Fourier
 support condition at a sequence of resolutions and verifies the endpoint classification
 $m=1$ versus $m\geq2$ under \eqref{eq:endpoint-support-hypothesis}.
\end{enumerate}

The companion unit test repeats the certificate at smaller parameter
values and uses exact rational arithmetic for the ray labels and
determinants.  Floating-point comparisons occur only in exponential and
logarithmic evaluations and are guarded by reported tolerances.  The
machine-readable output is
\texttt{experiments/data/factor-ray-certificate.json}.  Reproduction
requires only the Python standard library:
\begin{verbatim}
python experiments/factor_ray_certificate.py
python -m unittest experiments.test_factor_ray_certificate
\end{verbatim}
The saved output is a regression certificate for the identities, not
evidence for the fixed-$h$ statements explicitly excluded in
\cref{sec:introduction}.

\section{Conclusion and next boundary}
\label{sec:conclusion}

This paper closes one well-defined step in the factor-scale program.  A
complete large-factor prime-target residual is converted into a separated
exponential polynomial by grouping factor pairs along primitive ratio
rays.  At fixed shift this yields a hyperbolic Mellin large-sieve law, an
$X\log^4X$ ray-energy upper bound, density-one cancellation in long
frequency intervals, and exact Fej\'er diagonalization at the geometric
resolution $T\asymp X$.  None of these conclusions evaluates a prescribed
frequency.

Squaring first and averaging $h$ over a window of length at least $X$
adds arithmetic content.  The source diagonal admits an explicit
asymptotic evaluation;
the target square contributes $\log H$; and a two-linear-forms upper sieve
is sufficient for every same-ray off-diagonal.  The result is an
unconditional averaged-shift ray-energy asymptotic and its hard- and
smooth-band consequences.  The even-shift version records the
parity-conditioned local factor without selecting any individual even
shift.

The remaining fixed-shift obstruction is now explicit rather than hidden
in a generic appeal to the parity problem.  Spectral separation removes
different reduced ratios but leaves all radial indices $k$ coherent.
Their coefficients contain quadratic target correlations
$\Lambda(abk^2+h)\Lambda(ab\ell^2+h)$.  In the mesoscopic band, additional
interactions are organized by the determinant $ad-bc$.  At the factor
endpoint, a single smooth coherent functional recovers the weighted
Hardy--Littlewood quantity of \citet{HardyLittlewood1923}; hence an
absolute $o(X^2)$ fixed-shift band approximation, together with a
compatible filtered model and $o(X)$ tails, would already have substantial
prime-pair content.

The next honest target is therefore not to assert a fixed-$h$ diagonal
formula.  It is to find cancellation in one controlled weakening of the
determinant-layer or intra-ray forms: a shorter shift average, a balanced
ray sector, or an average over a bounded set of determinant layers.  Any
such theorem must be compared with the endpoint strength test before it is
interpreted arithmetically.  The classical sieve framework described by
\citet{IwaniecKowalski2004} remains the relevant boundary: no twin-prime
lower bound, Hardy--Littlewood asymptotic at $h=2$, or violation of sieve
parity is obtained here.
