\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\hypersetup{
 pdftitle={Coordinate-Face Reduction at the Coherent Mobius Gate: Physical Zero-Face Absorption, Jacobi Near-Isometry, and Three-Modulus Energy Localization},
 pdfauthor={Liang Wang},
 pdfsubject={Zero-coordinate removal and exact spectral localization for a coherent orbit-sliced Mobius gate},
 pdfkeywords={Mobius correlation, multiplicative characters, Jacobi sums, Chinese remainder theorem, orbit energy, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\F}{\mathbb F}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cU}{\mathcal U}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\cX}{\mathcal X}
\newcommand{\cY}{\mathcal Y}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\op}{\operatorname{op}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Coordinate--Face Reduction at the Coherent M\"obius Gate:}\\
\textbf{Physical Zero--Face Absorption, Jacobi Near--Isometry,}\\
\textbf{and Three--Modulus Energy Localization}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
The preceding product--slope analysis reduces an orbit--sliced prime--M\"obius
energy estimate to a weighted coherent multiplicative spectrum.  Three
possible obstructions remain entangled there: zero residue coordinates,
nonconstant complementary weights, and the proper coordinate faces of a
three--modulus completion.  We separate them exactly.

At the endpoint
\[
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
\]
choose a prime \(q\asymp J\) above the physical orbit support.  The part
of either orbit slice on which \(q\mid m_\alpha j+h\) satisfies
\[
 \boxed{
 V_{L,q\mid N}+V_{R,q\mid N}
 \ll X^{o(1)}(1+Q/q)Q^2
 \ll X^{o(1)}Q^3/J.}
\]
Thus every physical \(s=0\) or \(u=0\) residue face may be removed before
finite--field completion at exactly the inherited gate scale.  The same
holds for any fixed number of orbit--scale primes.

On the regular part, the raw ultra residue vector \(G\) has \(G(0)=0\).
Its punctured centering
\[
 \beta=\frac1{q-1}\sum_{U\ne0}G(U),\qquad
 g(0)=0,\qquad g(U)=G(U)-\beta\quad(U\ne0)
\]
is both additively centered and still vanishes at zero.  If
\(f=F-q^{-1}\sum_DF(D)\), then for \(a,s\ne0\)
\[
 \cC_{a,s}(F,G)
 =\cC_{a,s}(f,g)-\beta f(-h/a)+(q-1)\bar F\beta.
\]
Hence the centered core has zero complete-\(s\) trace, while every
centering correction is explicit and rank one in the complementary
\(s\)-coordinate.  For the actual dyadic
ultra weight, the standard zero--free--region estimate gives
\[
 |\beta|\ll_A (U/q)(\log X)^{-A}.
\]
Complete residue cycles of the complementary interval therefore cancel
exactly in the core; only its incomplete boundary, the mean corrections,
and alias weights remain.

We next diagonalize that nonconstant boundary.  If
\(c=w*_\times g\), then the two--character transform is a shifted Mellin
transform
\[
 C_\chi=\sum_{x\in\F_q^\times}c(x)\overline{\chi(x-h)}.
\]
The nonprincipal Jacobi matrix
\(
 K_{\chi,\psi}=J(\psi,\bar\chi)
\)
satisfies
\[
 \boxed{K^*K=KK^*=(q-1)^2I-q\,\mathbf1\mathbf1^*.}
\]
Its singular values are \(q-1\), with multiplicity \(q-3\), and \(1\),
with multiplicity one.  Equivalently,
\[
 \sum_{\chi\ne\mathbf1}|C_\chi|^2
 =\sum_{\psi\ne\mathbf1}
 |\widehat w(\psi)\widehat g(\psi)|^2
 -\frac q{(q-1)^2}
 \left|\sum_{\psi\ne\mathbf1}
 \widehat w(\psi)\widehat g(\psi)\psi(h)\right|^2.
\]
Thus the Jacobi layer is near--isometric, not an automatic source of
cancellation.  Nevertheless, for an interval weight \(w\),
P\'olya--Vinogradov saves the full uniform Cauchy factor in the unweighted
character average.  A sharp punctured character example shows that an
arbitrary nonconstant coherent weight may still saturate that factor.

Finally, we give an exact calculus for all eight character faces of three
pairwise coprime orbit--scale primes.  The faces are orthogonal over one
CRT period.  Their squared masses, by codimension, are
\[
 J^{-3},\qquad J^{-2},\qquad J^{-1},\qquad 1.
\]
The coherent union \(P\) of the seven proper faces obeys
\[
 \|P\|_\infty\ll J^{-1},\qquad
 \|P\|_2^2\asymp J^{-1},\qquad
 \|P\|_1\asymp1.
\]
Grouping a reciprocal dyadic block first by the integer determinant
\(F=su-N\) removes the apparent incomplete--box boundary: every face has
total absolute mass at most \(X^{o(1)}X/J^3\), while
\[
 \sum_{s,u}|P(su-N)|^2
 \ll X^{o(1)}X/J^4=o(1).
\]
The full face, however, remains \(1-O(J^{-1})\) on every exact equality
and retains the terminal M\"obius layer.  Closing the orbit gate still
requires either absorption of the exposed punctured-centering mean
corrections and principal outer boundary together with actual
nonprincipal spectral overlap, or a target-coupled, coefficient-weighted
shifted--fiber Bessel theorem for the unsplit raw physical output.  We
prove neither route, and claim no
parity breach, Hardy--Littlewood asymptotic, or twin--prime result.
\end{abstract}

\noindent\textbf{Keywords:}
M\"obius correlation; multiplicative character; Jacobi sum;
Chinese remainder theorem; orbit energy; parity boundary.

\medskip
\noindent\textbf{MSC 2020:}
Primary 11N35, 11N37; Secondary 11L40, 15A18, 15B05.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/physical-zero-faces}
\input{sections/punctured-centering}
\input{sections/two-character}
\input{sections/three-modulus}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
