\begin{abstract}
The literal fixed-shift residual map of a prime-squarefree orbit packet
first restricts the full pre-terminal array to the inherited terminal
equality support, multiplies a surviving input \((m,r,j,\gamma)\) by
\(\mu(r)\Lambda(mj+h_0)\), and then identifies inputs with the same
complete output key \((\gamma,d(m)r,j)\).  Positive pre-terminal energy
does not imply either terminal activation or survival under this
identification.  We determine the exact linear and arithmetic structure
of the internal grouping gate, keeping these two losses separate.

For a general weighted fiber-summing operator we compute every singular
value, its kernel, the Moore--Penrose inverse, and the canonical visible
projection.  Each active output fiber has exactly one visible direction;
all remaining directions are collision modes.  For a distinguished input,
the grouped energy is an exact energy-weighted average of explicit fiber
alignment coefficients.  Conditional on separate terminal activation and
downstream comparison gates, the remaining internal grouping statement is
a lower bound on the angle of the physical array from a known kernel, not
a uniform lower bound on the full coefficient space.

The fixed-shift arithmetic adds a more specialized fact.  Assume
\(h_0\ne0\), \(D=o(J)\), uniqueness of the declared row labels, and
sufficiently large \(X\).  If the terminal prime
\(p=(mj+h_0)/r\) is retained, then the refined key
\((\gamma,d(m)r,j,p)\) is injective on one declared source system.  Hence
after terminal restriction, residual grouping factors exactly into a
collision-free prime-resolved lift
and a final coherent sum over distinct terminal primes.  Determinant
ladders give the coefficient-blind upper bound
\(\ll_{h_0}X^{o(1)}(1+L/R)\) for the maximal fiber size on a cofactor block
\(r\asymp R\).  In the balanced range \(R\gg L\), whenever the block has
nonzero terminal diagonal energy, a rank-by-prime partition contains a
collision-free subpacket with at least an \(X^{-o(1)}\) fraction of that
energy.  This selection incurs no fixed positive-power loss inside that
block; it is not a lower bound for the unreduced coherent sum.

Finally, on the inherited coprime squarefree equality support only, the
source and cofactor signs combine as
\(\mu(d)\mu(r)=\mu(d r)\), so M\"obius contributes one common phase on a
residual fiber.  Any remaining cancellation belongs to the actual source,
mask, profile, and terminal amplitudes.  No lower bound for the full
fixed-shift coherent-prime square, parity improvement, or prime-pair
consequence is claimed.
\end{abstract}
