\section{Endpoint ledger, claim boundary, and the next gate}
\label{sec:endpoint-claims}

\subsection{The capacity cost at the inherited endpoint}

The declared row scales inherited from TPC--53 \citep{WangTPC53} are
\begin{equation}
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)},
 \qquad
 D=X^{10049/52500+o(1)}.
 \label{eq:tpc55-endpoint-scales}
\end{equation}
Therefore
\begin{equation}
 L=\frac QD
 =X^{99979/210000+o(1)}.
 \label{eq:tpc55-endpoint-L}
\end{equation}
On a cofactor block
\(R=X^{\theta_R+o(1)}\), the worst-case transversal-selection exponent
certified by
\cref{cor:tpc55-balanced-multiplicity} is
\begin{equation}
 \mu_{\rm cap}
 =\left(\frac{99979}{210000}-\theta_R\right)_+.
 \label{eq:tpc55-endpoint-capacity-cost}
\end{equation}
Thus every fixed balanced range \(R\gg L\) has
\begin{equation}
 M_X(R)=X^{o(1)},
 \qquad \mu_{\rm cap}=0.
 \label{eq:tpc55-balanced-zero-cost}
\end{equation}
This means that the rank cover has no fixed positive-power loss inside a
balanced block.  It is not a claim that terminal diagonal energy is
concentrated on, or even nonzero in, such a block.

At the older cofactor scale \(R\asymp J\), the coefficient-blind ladder
certificate gives the worst-case factor
\begin{equation}
 \frac LR
 =X^{15077/105000+o(1)}.
 \label{eq:tpc55-old-range-cost}
\end{equation}
The exponent in this support-only certificate exceeds the nominal endpoint
allowance \(X^{1/400+o(1)}\) by
\begin{equation}
 \frac{15077}{105000}-\frac1{400}
 =\frac{29629}{210000}>0.
 \label{eq:tpc55-old-range-deficit}
\end{equation}
Thus that certificate alone cannot close the endpoint budget at
\(R\asymp J\).  The actual physical multiplicity may be smaller; no matching
lower bound is asserted.  Primality can give logarithmic thinning but does
not improve this support-only power count.

\subsection{A complete loss ledger}

Suppose a parent physical atomic energy is first restricted to a declared
compatible packet with fraction
\begin{equation}
 X^{-\lambda_{\rm sel}+o(1)},
 \label{eq:tpc55-selection-loss}
\end{equation}
and then to the pre-terminal cofactor block
\begin{equation}
 \mathcal B_R^{\rm pre}
 :=\{u\in\cU^{\rm pre}:R\le r_u\le2R\},
 \qquad g_R^{\rm pre}:=g\one_{\mathcal B_R^{\rm pre}},
 \label{eq:tpc55-preterminal-block}
\end{equation}
with energy fraction
\begin{equation}
 X^{-\lambda_{\rm blk}+o(1)}.
 \label{eq:tpc55-block-loss}
\end{equation}
Suppose first that terminal activation on this full pre-terminal block
satisfies
\begin{equation}
 \delta_{\rm term}(g_R^{\rm pre})
 \ge X^{-\lambda_{\rm term}+o(1)}.
 \label{eq:tpc55-terminal-loss}
\end{equation}
The resulting terminal diagonal energy is then partitioned by the block
prime-rank classes of \cref{thm:tpc55-balanced-transversal}.  Selecting the
energy-rich collision-free rank costs at most the certified exponent
\(\mu_{\rm cap}\).  The selected-rank grouped energy therefore has the
formal lower exponent
\begin{equation}
 \lambda_{\rm sel}+\lambda_{\rm blk}
 +\mu_{\rm cap}+\lambda_{\rm term}.
 \label{eq:tpc55-selected-rank-ledger}
\end{equation}
This conclusion is relative to the selected post-terminal rank.  The order
is essential: terminal activation is established on the pre-terminal block
before the rank pigeonhole is applied to its terminal diagonal energy.  The
selected-rank statement does not return to the full output.

For the undeleted physical terminal vector of the same block, instead
suppose one proves
\begin{equation}
 \chi_{\rm grp}\ge X^{-\lambda_{\rm coh}+o(1)}.
 \label{eq:tpc55-coherence-loss}
\end{equation}
Then the exact factorization
\eqref{eq:tpc55-exact-gate-factorization} gives the combined exponent
\begin{equation}
 \lambda_{\rm sel}+\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm coh}.
 \label{eq:tpc55-full-output-ledger}
\end{equation}
Any later native-Gram comparison, frozen-family localization, boundary
truncation, or ultra-tail reconnection must add its own nonnegative loss.
To remain within the nominal TPC endpoint budget, the complete eventual
sum must satisfy
\begin{equation}
 \boxed{
 \lambda_{\rm sel}+\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm coh}+\lambda_{\rm loc}
 +\lambda_{\rm Gram}+\lambda_{\rm bdry}+\lambda_{\rm tail}
 \le\frac1{400}.}
 \label{eq:tpc55-full-endpoint-budget}
\end{equation}
At equality, a further error of size \(X^{-1/400+o(1)}\) need not be
absorbed; strict slack or a constant-level comparison is the safe closure
condition.

The present paper proves none of \(\lambda_{\rm blk}\),
\(\lambda_{\rm term}\), \(\lambda_{\rm coh}\), or the downstream losses
for the full inherited packet.  It proves \(\mu_{\rm cap}=0\) for the
coordinate-selection problem conditional on a declared balanced block with
nonzero terminal diagonal energy.

\subsection{Six-point physical audit}

The interfaces used above satisfy the following audit.
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3.2em]
 \item \emph{Literal coefficients.}
       The source coefficient, binary mask, four smooth profile factors,
       cofactor sign, and terminal amplitude are displayed in
       \eqref{eq:tpc55-source-coefficient},
       \eqref{eq:tpc55-mask},
       \eqref{eq:tpc55-four-factor-profile}, and
       \eqref{eq:tpc55-terminal-diagonal}.
 \item \emph{Fixed physical shift.}
       Every arithmetic equation uses the one fixed \(h_0\).  The frozen
       Fourier family is mentioned only to distinguish it from this map.
 \item \emph{Atomic normalization.}
       Domain, prime-resolved output, and grouped output all use inherited
       counting measure.  The terminal coefficient is not hidden in the
       norm.
 \item \emph{Canonical representation.}
       The map is the literal TPC--53 coordinate map.  No projective
       representation or favorable Mellin layer is selected.
 \item \emph{Actual support.}
       The full pre-terminal universe, terminal-admissible subset, and
       physically nonzero subset are separated in
       \eqref{eq:tpc55-preterminal-universe},
       \eqref{eq:tpc55-terminal-universe}, and
       \eqref{eq:tpc55-physical-active-set}.
 \item \emph{Endpoint budget.}
       The only unconditional selection exponent is the explicit
       \(\mu_{\rm cap}\) in \eqref{eq:tpc55-endpoint-capacity-cost}; all
       unproved losses remain visible in
       \eqref{eq:tpc55-full-endpoint-budget}.
\end{enumerate}

\subsection{Claim table}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.27\textwidth}
                >{\raggedright\arraybackslash}p{0.62\textwidth}}
\toprule
Statement & Status \\
\midrule
Weighted fiber SVD, kernel, pseudoinverse, and angle criterion
& Unconditional finite-dimensional theorem (L0).\\
Prime-resolved injection
& Exact on one declared fixed-\(h_0\) physical source system under the
  inherited \(D=o(J)\) row geometry (L1).\\
Determinant-ladder capacity
& Exact coefficient-blind upper bound on the declared squarefree terminal
  support (L1).\\
Balanced rank cover
& Canonical post-terminal cover and existence of a collision-free subpacket
  with an \(X^{-o(1)}\) fraction of nonzero block terminal diagonal energy;
  no block-occupancy estimate (L1).\\
Common M\"obius-gauge factorization
& Exact common product \,\(\mu(d)\mu(r)=\mu(s)\) on the inherited coprime
  squarefree support; no claim about the remaining complex amplitudes (L1).\\
Terminal activation
& Not proved for the full pre-terminal packet.\\
Full coherent output lower bound
& Not proved; exactly equivalent to a lower estimate for the displayed
  physical coherence/alignment together with terminal activation.\\
Parity or twin-prime consequence
& Not claimed.\\
\bottomrule
\end{tabular}
\end{center}

In particular, the following implications remain forbidden:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item subpower maximal multiplicity does not imply a lower bound for the
       unselected full sum;
 \item common M\"obius phase does not imply a sector condition for
       \(\zeta_m\) and the source/mask profile;
 \item a collision-free selected rank need not be a compatible smooth
       pre-terminal cell;
 \item refined-key, equivalently fixed \((s,j,p,\gamma)\), injectivity does
       not make fixed \((s,j,\gamma)\) injective, because different terminal
       primes are exactly the collision modes;
 \item the physical fixed-\(h_0\) prime synthesis is not the
       frozen-intercept Fourier \(p\)-sum; and
 \item a residual output norm is not automatically the native affine
       physical Gram face.
\end{enumerate}

\subsection{The next gate}

The next paper should keep one literal full fiber or one explicitly
declared cofactor block and study
\begin{equation}
 \sum_{u\in\cF_{\gamma,s,j}^{\rm phys}} b_u,
 \label{eq:tpc55-next-fiber-sum}
\end{equation}
with \(b_u\) given by
\eqref{eq:tpc55-remaining-fiber-amplitude}.  There are three honest doors:
\begin{enumerate}[label=\textbf{Door \Alph*.},leftmargin=3.8em]
 \item prove a deterministic sector, dominance, or restricted-Gram lower
       bound for the distinguished physical amplitudes on one nonempty
       literal regime;
 \item prove a two-sided coherent terminal-prime square after an explicitly
       labeled averaging or smoothing, then quantify exactly why that model
       does or does not localize back to fixed \(h_0\); or
 \item construct a literal admissible packet whose remaining amplitudes
       approach the collision kernel, giving a coefficient-specific
       saturation or no-go theorem for this route.
\end{enumerate}
An estimate for an arbitrary smooth proxy, a random-phase model, or an
averaged shift would be useful only under its own label.  It would not be
reported as a fixed-shift parity gain.

\paragraph{Conclusion.}
The residual-grouping obstruction is now explicitly identified at the
operator and support levels.  Under the declared hypotheses, the refined
terminal key is injective and the prime-resolved operator restricted to
terminal-admissible coordinates is a weighted coordinate embedding;
forgetting the terminal prime creates rank-one output fibers with an
explicit collision kernel.  Balanced fibers admit an optimal subpower
transversal cover, and the product of the two literal M\"obius signs is
common inside each fiber.  After terminal activation is controlled, the
remaining internal
grouping question is how the distinguished source--mask--prime amplitudes
align with the visible direction.  Fixed-shift localization, native-Gram
comparison, boundary control, and tail reconnection remain separate
downstream gates.  Every one of these steps is strictly upstream of a
parity-sensitive or twin-prime conclusion.
