\section{Introduction}
\label{sec:introduction}

The preceding two stages of this program placed the pre-terminal packet on
an exact physical normalization.  TPC--53 identified every literal source,
opposite-row, orbit, mask, and Mellin factor and proved a sampled interior
profile comparison.  TPC--54 then solved the abstract energy-selection
problem sharply: structural density, source shape, sampled carrier,
cofactor occupancy, and coefficient capacity can be tracked without moving
any of them through a nonlinear norm \citep{WangTPC53,WangTPC54}.  Both
results stop before the terminal map.  That stopping point is forced, not
cosmetic.

Fix one left source system, one direct row/orbit residue slice, and a
nonzero physical shift \(h_0\).  A retained pre-terminal coordinate has the
form
\[
 u=(m,r,j,\gamma),
 \qquad m=d(m)\ell(m),
\]
where \(\ell(m)\) is prime and \(d(m)\) is squarefree.  On the terminal
support the equation
\[
 p r-mj=h_0
\]
determines at most one prime \(p\).  The literal output coordinate is
\[
 y=q(u)=(\gamma,s,j),\qquad s=d(m)r.
\]
Consequently the physical terminal map is a weighted sum over the full
terminal fiber \(\cF_y^{\rm term}\).  If such a fiber contains two
nonzero input directions, the map has a kernel on the unrestricted
coefficient space.  This elementary obstruction was enough to disprove an
automatic passage from pre-terminal coverage to post-terminal energy, but
it did not describe the arithmetic fiber or the behavior of the
distinguished physical vector.

The present paper asks the next narrow question:
\begin{quote}
What is the exact spectral and arithmetic structure of a fixed-\(h_0\)
residual fiber, and which part of its terminal diagonal energy can be made
collision-free without claiming a lower bound for the unreduced coherent
sum?
\end{quote}

There are four answers.

\subsection{Prime resolution gives an exact desingularization}

The first answer changes the geometry of the question.  Adjoin the unique
terminal prime to the output key:
\[
 \widetilde q(u)=(\gamma,s,j,p_u),
 \qquad p_u=\frac{mj+h_0}{r}.
\]
Under \(h_0\ne0\), \(D=o(J)\), uniqueness of the declared row labels,
and sufficiently large \(X\), this refined map is injective on one
declared source system.  Indeed,
equality of \((s,j,p)\) gives equality of the fused squarefree label
\[
 d(m)(mj+h_0)=p s,
\]
and the fixed-coordinate label-injectivity argument of the large-prime
descent recovers the unique row \citep{WangTPC45}.  We also give the short
self-contained proof.  The fixed-shift terminal map therefore factors as
\[
 \boxed{\begin{aligned}
 \text{literal terminal map}
 &=\text{forget-}p\text{ synthesis}\\
 &\quad\circ\text{terminal-restricted collision-free lift}.
 \end{aligned}}
\]
Thus distinct points of one residual collision fiber necessarily carry
distinct terminal primes.  In the literal fixed-\(h_0\) representation,
``residual grouping'' and ``coherent terminal-prime synthesis'' are not two
independent many-to-one operations.  The former is precisely the last
operation that forgets the prime coordinate.  This statement concerns the
physical \(h_0\)-slice; it does not identify the different coherent
\(p\)-sum appearing after Fourier transformation of the completed frozen
intercept family in TPC--48 \citep{WangTPC48}.

\subsection{The grouping spectrum is completely explicit}

Let \(q:\cU\to\cY\) be any finite fiber map and
\[
 (Tz)_y=\sum_{q(u)=y}c_uz_u
\]
between Hilbert spaces with positive atomic weights \(a_u\) and \(b_y\).
Put
\[
 S_y=\sum_{q(u)=y}\frac{|c_u|^2}{a_u},
 \qquad \rho_y^2=b_yS_y.
\]
We prove that the nonzero singular values of \(T\) are exactly the
\(\rho_y\).  Every active fiber contributes one visible unit vector
\[
 (v_y)_u=\frac{\overline{c_u}}{a_u\sqrt{S_y}}
 \quad(q(u)=y)
\]
and a kernel of codimension one.  This gives the exact pseudoinverse,
minimum-norm representative of every output, and quotient norm.  On a
restricted subspace, a lower bound is equivalent to a positive principal
angle from this explicit kernel.

For one distinguished vector \(z\), define
\[
 \eta_y(z)=
 \frac{\left|\sum_{q(u)=y}c_uz_u\right|^2}
 {S_y\sum_{q(u)=y}a_u|z_u|^2}.
\]
Then \(0\le\eta_y\le1\), and the grouped norm is exactly
\[
 \|Tz\|_b^2
 =\sum_y\rho_y^2\eta_y(z)
       \sum_{q(u)=y}a_u|z_u|^2.
\]
After terminal activation has been proved and any downstream interface
gates required by the target correlation have been supplied, the remaining
internal grouping question is therefore an arithmetic lower bound for a
displayed alignment statistic.  There is no hidden spectral gap to infer
from multiplicity or positive diagonal energy alone.

\subsection{Balanced fibers admit a zero-cost transversal cover}

Fix \(y=(\gamma,s,j)\), write \(s=dr\), and hold \(d\mid s\) fixed.  The
admissible source prime \(\ell\) and terminal prime \(p\) lie on the exact
determinant ladder
\[
 rp-dj\ell=h_0.
\]
If \(g=(r,dj)\mid h_0\), all integral solutions are
\[
 p=p_0+\frac{dj}{g}t,
 \qquad
 \ell=\ell_0+\frac r g t.
\]
The inherited squarefree support has \((d,r)=1\), so \(g=(r,j)\mid h_0\).
On a source-prime interval of length \(O(L)\), the number of candidates for
this \(d\) is \(O_{h_0}(1+L/r)\).  Summing over \(d\mid s\) gives the
coefficient-blind upper bound
\[
 |\cF_y(R)|
 \ll_{h_0}\tau(s)\left(1+\frac LR\right)
 \qquad(r\asymp R),
\]
already implicit in the determinant-ladder boundary of TPC--45.  Since
\(\tau(s)=X^{o(1)}\) on the polynomial-size support, balanced cofactors
\(R\gg L\) give subpower multiplicity.

Order the terminal primes in each full fiber and put the \(k\)-th smallest
prime from every fiber into the \(k\)-th rank class.  These classes form a
deterministic, coefficient-independent partition into at most the maximal
fiber size many collision-free transversals.  If the terminal diagonal
energy of the block is nonzero, one class captures at least the reciprocal
of that number.  Hence a balanced block with nonzero terminal diagonal
energy contains a collision-free subpacket with an \(X^{-o(1)}\) fraction
of that energy.  The selector is post-terminal and need not be a smooth
Mellin cell.  More importantly, a large collision-free summand does not
lower-bound the sum of all rank classes: the omitted classes can still
cancel it.

\subsection{The M\"obius gauge is common, not random}

On the inherited coprime squarefree equality support,
\(d,r,s=dr\) are squarefree, \((d,r)=1\), and
\[
 \mu(d)\mu(r)=\mu(s).
\]
The source coefficient contains \(\mu(d)\), while the terminal multiplier
contains \(\mu(r)\).  Their product is therefore constant on a fixed
residual fiber.  This coherence was first isolated during the large-prime
cofactor descent \citep{WangTPC45}; here it is inserted into the complete
TPC--53 factor dictionary.  The opposite-row phase and opposite profile
are also common on a full \((\gamma,s,j)\)-fiber.  After those factors are
removed, only the actual source coefficient, source profile, mask support,
and positive-or-signed terminal shape remain in the fiber sum.

This is useful structural progress, but not a parity claim in the classical
sieve-theoretic sense \citep[Ch.~16]{FriedlanderIwaniec2010}.  The inherited
theory supplies no uniform sector bound for the remaining complex
amplitudes.  We prove sharp phase-cone and magnitude-dominance criteria,
and we prove that without either type of information the diagonal moduli
alone may still form an exact polygonal cancellation.

\subsection{Scope and order of the next gate}

We use the program's level labels in the following precise sense.
Level L0 consists of abstract finite-dimensional operator identities and
inequalities that do not assert their arithmetic hypotheses for the
literal packet.  Level L1 consists of exact structural statements proved
on the declared inherited fixed-\(h_0\) support, including the
prime-resolved injection and determinant-ladder upper bound.  Level L2
would require a quantitative estimate reconnected to the full physical
fixed-shift correlation, with activation, normalization, boundary, and
all downstream comparison gates controlled.  Nothing in this paper is
L2.

The balanced transversal theorem is L1 but selects a post-terminal
subpacket; it does not prove that the full physical output is large.  No
step identifies the residual low-sign Gram with the native affine Gram,
changes the physical shift, or estimates a twin-prime correlation.

The result does, however, alter the practical order of attack.  The next
paper need not search for an abstract lower bound for a many-to-one map.
After terminal activation and the remaining downstream interface
requirements are kept explicit, it should estimate the terminal-prime
coherence on one literal fiber or one declared rank interaction, with the
source, cofactor, fixed shift, and actual atomic normalization all retained.
