\section{Canonical collision-free transversals}
\label{sec:transversals}

The exact multiplicity bound can be converted into a selection theorem
without assigning free phases or changing the physical atomic weights.

\subsection{Rank coloring of the terminal primes}

Assume \(\cU_{h_0}^{\rm term}\ne\varnothing\).  For each nonempty terminal
output \(y=(\gamma,s,j)\), order its terminal-prime set
from \cref{cor:tpc55-fiber-prime-bijection}:
\begin{equation}
 p_1(y)<p_2(y)<\cdots<p_{n_y}(y),
 \qquad n_y=|\cF_y|.
 \label{eq:tpc55-prime-order}
\end{equation}
Let \(u_k(y)\) be the unique input with terminal prime \(p_k(y)\), and put
\begin{equation}
 M=\max_y n_y,
 \qquad
 \cS_k:=\{u_k(y):n_y\ge k\},
 \quad 1\le k\le M.
 \label{eq:tpc55-rank-transversals}
\end{equation}
The construction depends only on the physical terminal prime and a fixed
ordering rule, not on the coefficient values.

\begin{theorem}[Canonical prime-rank cover]
\label{thm:tpc55-prime-rank-cover}
The terminal-admissible input set is the disjoint union
\begin{equation}
 \cU_{h_0}^{\rm term}
 =\bigsqcup_{k=1}^{M}\cS_k,
 \label{eq:tpc55-rank-partition}
\end{equation}
and \(q|_{\cS_k}\) is injective for every \(k\).  Conversely, a partition
of the input coordinates into collision-free coordinate sets requires at
least \(M\) sets whenever a fiber of size \(M\) is present.  Thus the number
of rank classes is optimal.
\end{theorem}

\begin{proof}
Every input has one rank inside its fiber, proving the disjoint union.  A
fixed rank contributes at most one input to each fiber, so \(q\) is
injective there.  A fiber with \(M\) coordinates forces its members into
different collision-free sets, proving optimality.
\end{proof}

For any nonnegative atomic energy \(e_u\), write
\begin{equation}
 E_k=\sum_{u\in\cS_k}e_u,
 \qquad E=\sum_ue_u.
 \label{eq:tpc55-rank-energies}
\end{equation}

\begin{corollary}[Sharp energy capture]
\label{cor:tpc55-rank-energy-capture}
At least one rank class satisfies
\begin{equation}
 E_k\ge\frac EM.
 \label{eq:tpc55-rank-pigeonhole}
\end{equation}
The constant \(1/M\) is optimal for arbitrary nonnegative atomic data.
\end{corollary}

\begin{proof}
Sum the \(M\) rank energies.  Equality is possible when all \(E_k=E/M\).
\end{proof}

\subsection{Specialization to terminal diagonal energy}

Let
\begin{equation}
 x=D_{h_0}g,
 \qquad
 e_u=|x_u|^2
 =|\Lambda(p_ur_u)|^2|g_u|^2.
 \label{eq:tpc55-terminalized-array}
\end{equation}
On a collision-free rank class, grouping creates no cross term:
\begin{equation}
 \|\cT_{h_0}(g\one_{\cS_k})\|_2^2
 =\sum_{u\in\cS_k}|x_u|^2=E_k.
 \label{eq:tpc55-transversal-exact-energy}
\end{equation}

For a cofactor scale \(R\), define the exact terminal block
\begin{equation}
 \mathcal B_R
 :=\{u\in\cU_{h_0}^{\rm term}:R\le r_u\le2R\},
 \qquad
 g_R:=g\one_{\mathcal B_R},
 \label{eq:tpc55-terminal-block}
\end{equation}
and, using \eqref{eq:tpc55-cofactor-block}, its maximal fiber size
\begin{equation}
 \cF_y(R)=\cF_y\cap\mathcal B_R,
 \qquad
 M_X(R):=\max_y|\cF_y(R)|.
 \label{eq:tpc55-block-fibers}
\end{equation}
Within each nonempty \(\cF_y(R)\), order the terminal primes and let
\(\cS_k(R)\) contain the atom of block rank \(k\), whenever it exists.
Thus \(\{\cS_k(R):1\le k\le M_X(R)\}\) is the prime-rank cover applied
to \(\mathcal B_R\), rather than the restriction of a possibly different global
rank ordering.

\begin{theorem}[Balanced collision-free block subpacket]
\label{thm:tpc55-balanced-transversal}
Assume that every residual label \(s\) occurring in \(\mathcal B_R\) has
polynomial size in \(X\), and let \(g\) be a physical array such that
\(\cD_{h_0}(g_R)>0\).  There is a canonical family of
\begin{equation}
 M_X(R)\ll_{h_0,C_L}X^{o(1)}\left(1+\frac LR\right)
 \label{eq:tpc55-number-of-transversals}
\end{equation}
collision-free prime-rank classes covering every terminal-admissible atom in
that block.  At least one block rank class satisfies
\begin{equation}
 \boxed{
 \|\cT_{h_0}(g_R\one_{\cS_k(R)})\|_2^2
 \ge\frac{\cD_{h_0}(g_R)}{M_X(R)}.}
 \label{eq:tpc55-balanced-transversal-energy}
\end{equation}
In particular, if \(R\ge cL\), then conditional on nonzero block terminal
diagonal energy, the selected collision-free block subpacket incurs no
fixed positive-power loss relative to that block energy.
\end{theorem}

\begin{proof}
Combine \cref{prop:tpc55-fiber-capacity,thm:tpc55-prime-rank-cover}.
Apply \cref{cor:tpc55-rank-energy-capture} to the physical terminal
diagonal weights of \(g_R\) in \eqref{eq:tpc55-terminalized-array}, then use
\eqref{eq:tpc55-transversal-exact-energy}.
\end{proof}

This is a positive post-terminal selection result on a specified nonzero
block.  It says that the balanced block terminal diagonal admits a
coordinate subpacket with no fixed positive-power selection cost, on which
physical grouping is exactly isometric after the literal terminal
multiplier has been applied.  It does not assert that the block energy is
nonzero, compare that energy with pre-terminal or global energy, or say
that a preassigned rank captures it: the family is canonical, while the
choice of its energy-rich member may depend on \(g_R\).

\subsection{Why the selected lower bound does not return to the full sum}

Write
\begin{equation}
 X_k:=\cT_{h_0}(g\one_{\cS_k}),
 \qquad
 \cT_{h_0}g=\sum_{k=1}^{M}X_k.
 \label{eq:tpc55-rank-output-sum}
\end{equation}
The \(X_k\) occupy the same output coordinate system and are not
orthogonal.  Therefore \(\|X_k\|^2\le\|\sum_lX_l\|^2\) is false in
general.

For one selected class \(S=\cS_k\), put
\begin{equation}
 D_S=\sum_{u\in S}|x_u|^2,
 \qquad
 D_R=\sum_{u\notin S}|x_u|^2.
 \label{eq:tpc55-selected-complement-energy}
\end{equation}
Every remaining rank class is also collision-free.  The triangle and
Cauchy--Schwarz inequalities give the valid one-sided estimate
\begin{equation}
 \boxed{
 \|\cT_{h_0}g\|_2
 \ge
 \left(\sqrt{D_S}-\sqrt{(M-1)D_R}\right)_+.}
 \label{eq:tpc55-transversal-complement-bound}
\end{equation}
Indeed, the sum of the norms of the other \(M-1\) rank outputs is at most
\(\sqrt{M-1}\sqrt{D_R}\).  Unless the selected rank dominates its
complement at this scale or the inter-rank phases are controlled,
\eqref{eq:tpc55-transversal-complement-bound} can be zero.

The obstruction is real already for a two-atom fiber: two equal terminal
amplitudes with opposite remaining phases give positive diagonal energy in
both rank classes and zero full output.  Hence
\cref{thm:tpc55-balanced-transversal} cannot be upgraded by monotonicity.

\subsection{Selection versus the canonical quotient}

The rank class is a sparse coordinate representative of each occupied
fiber.  The minimum-norm representative from
\cref{thm:tpc55-pseudoinverse} instead distributes an output over all
fiber coordinates in proportion to \(\overline{c_u}/a_u\).  These solve
different problems:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item the pseudoinverse is canonical for reconstructing an already known
       grouped output;
 \item a rank transversal is canonical for eliminating collisions before
       a lower-bound argument; and
 \item neither construction supplies the phase relation among all rank
       outputs of the distinguished physical array.
\end{enumerate}

The rank selector is also a post-terminal arithmetic selector.  It need not
be representable by a fixed smooth source/Mellin box, and the present paper
does not move earlier profile estimates through it.  Any later analytic
use must verify stability of the relevant estimates on this exact subset or
work directly with the full coherence statistic below.
