\begin{abstract}
TPC--70 and TPC--71 reduce the first signed cross-key coefficient of the
missing-native Gram to a M\"obius sum on primitive cofactor coordinates.
The general divisor-lifted certificate of TPC--71 allows an arbitrary
finitely supported plane kernel and consequently contains diagonal
dilations, restricted Mertens sums, and an exact large-diagonal tail.  The
literal physical kernel has more structure.  Its common content is defined
canonically by \(q=(S_m,S_n)\), and its remaining coordinates
\(u=S_m/q\), \(v=S_n/q\) are coprime.  We prove that the support-faithful
zero completion is therefore supported on the primitive lattice.  Every
diagonal dilation \(K^{[d]}(x,y)=K(dx,dy)\) with \(d\ge2\) vanishes
identically, the exact diagonal tail is zero for every cutoff \(D\ge1\),
and the physical divisor lift collapses to ordinary two-dimensional Abel
summation at \(d=1\).

For one anchor \(\mathfrak a\), with
\(M(x)=\sum_{n\le x}\mu(n)\), the exact formula is
\[
 \mathfrak X_{\mathfrak a}
 =
 \mu(a_{\mathfrak a})\mu(b_{\mathfrak a})
 \sum_{x,y\ge1}
 M(x)M(y)\Delta_{12}K_{\mathfrak a}^{0}(x,y).
\]
We also aggregate all row pairs and anchors before taking absolute values,
obtaining a scalar trace kernel and a sharper weighted-plaquette
certificate for \(\operatorname{tr}(ER)\).  An
\(\ell^1\)-valued version retains every anchor and shows that a global
cost estimate, rather than uniform anchorwise little-oh notation, is
sufficient for trace-level summability.

The tail collapse does not make the variation problem disappear.  We
prove that mixed variation is exactly the coefficient mass in a unique
terminal-rectangle decomposition and that diagonal downsampling contracts
this norm.  More importantly, the physical sum depends only on values at
primitive sites.  Any analytic completion at nonprimitive sites gives the
same physical sum but may trade a smaller \(d=1\) variation against
nonzero higher diagonal slices and tail.  We define the resulting
completion gauge and prove its exact invariance and certificate.  The
canonical completion is tail-free, but it need not minimize its \(d=1\)
mixed variation within its completion class.  Elementary examples separate
tail freedom, low variation, signed cancellation, anchor summation, and
operator control.  Thus the auxiliary diagonal-tail gate for the
support-faithful zero extension is closed exactly, while the
mass-normalized completion and weighted-plaquette gates remain open.  No
operator saving, fixed-\(2\)
estimate, parity-breaking statement, or prime-pair conclusion is drawn.
\end{abstract}
