\section{Claim ledger and conclusion}
\label{sec:claim-boundary}

\subsection{Exact conclusions}

The paper proves the following.
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item The literal \(q\)-aggregated physical kernel has canonical support
       on the primitive lattice.
 \item Its support-faithful zero completion has no \(d\ge2\) diagonal
       slice and no exact diagonal tail for any \(D\ge1\).
 \item The anchored coefficient, scalar global trace kernel, and
       anchor-labelled kernel have exact ordinary \(d=1\) Abel identities.
 \item The weighted plaquette cost gives the coefficient-faithful,
       location-sensitive canonical certificate and can be aggregated
       before or after retaining anchor labels.
 \item Mixed variation equals the \(\ell^1\)-mass of the unique
       terminal-rectangle coefficients, and diagonal downsampling is
       contractive.
 \item The physical signed functional is invariant under analytic
       completion at nonprimitive sites.
 \item The complete divisor-variation cost of one completion is a valid
       certificate; its infimum is an exact analytic benchmark.
 \item Canonical zero completion is tail-free but need not be
       variation-optimal.
\end{enumerate}

\subsection{Statements not proved}

The paper does not prove:
\begin{itemize}
 \item that \(\cC_\square(K_{\mathfrak a}^{0})\) is small relative to
       \(\mathfrak W_{\mathfrak a}\);
 \item that the global cost in
       \eqref{eq:global-weighted-plaquette-target} is
       \(o(\mathfrak A_{\rm tr})\);
 \item a uniformly controlled low-cost analytic completion for the literal
       physical family;
 \item a fixed-power M\"obius saving for the physical first mixed trace;
 \item a direct two-corner representation of \(E_{m,n}\);
 \item an entrywise, row-star, Perron, or operator-norm saving;
 \item a represented lower frame, missing-mass estimate, or nuisance-angle
       estimate;
 \item closure of geometric short rays, physical endpoints, or the final
       packet tail;
 \item the strict endpoint inequality for one complete chain;
 \item any result using a property special to \(h_0=2\); or
 \item a parity-breaking, prime-pair, or twin-prime theorem.
\end{itemize}

\subsection{Audit levels}

\begin{center}
\begin{tabular}{@{}
 >{\raggedright\arraybackslash}p{0.27\textwidth}
 >{\raggedright\arraybackslash}p{0.48\textwidth}
 >{\raggedright\arraybackslash}p{0.14\textwidth}@{}}
\toprule
Result & Scope & Level\\
\midrule
Rectangle decomposition, downsampling, completion gauge &
All finite plane kernels and declared completion classes &
L0\\
Primitive support and diagonal-tail collapse &
Literal \(q\)-canonical fixed-\(h_0\) anchored kernel &
L1\\
Global scalar and anchor-labelled trace identities &
Complete actual anchor family, trace scope only &
L1\\
Mass-normalized weighted plaquette saving &
Required for the actual growing physical family &
Open L2\\
Trace-to-operator promotion &
Requires a new two-corner, row-local, or moment carrier &
Open L2\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Conclusion}

The auxiliary diagonal tail isolated in TPC--71 and carried as an open
certificate gate in TPC--72 is not present for the canonical primitive
zero completion.
That closure is exact and useful: it removes a cutoff, all growing-\(d\)
uniformity, and one possible source of endpoint loss.  The result does not
make the arithmetic easy.  It concentrates the canonical route in one
literal object,
\[
 \sum_{x,y}|M(x)M(y)|
 |\Delta_{12}K_{\mathfrak a}^{0}(x,y)|,
\]
and exposes analytic completion as a coupled variation-tail optimization,
not as free smoothing.  A natural next question is whether primitive
coordinates can be attached directly to the two-corner erasure entry.
The plane and represented branches remain available in parallel if that
door closes.
