\section{The canonical primitive physical datum}
\label{sec:physical-support}

We restate the literal input needed from TPC--70 and TPC--71.  No estimate
is made in this section.

\subsection{Rows, anchors, and erasure coordinates}

Fix a finite physical scale, one nonzero integer shift \(h_0\), two
distinct active rows \(m<n\) satisfying
\[
 (mn,h_0)=1,
\]
and squarefree row divisors
\[
 d_m\mid m,\qquad d_n\mid n,\qquad
 d_m=ga,\qquad d_n=gb,\qquad(a,b)=1.
\]
An active row \(r\) is a canonical source row with positive raw atomic
mass \(W_r\).  On the active row space, the atomic-normalized native Gram
has the inherited decomposition
\[
 G_{\rm nat}=I+R+E,
\]
where \(R\) retains common-output pairs with equal residual labels and
\(E\) retains those with unequal residual labels
\citep{WangTPC68}.  A complete native key retains the direct side,
external block, opposite row, \(\gamma\)-coordinate, physical time, and
every other orthogonal output label; equality of times alone is not used
as equality of keys.

For the row pair \((m,n)\), a complete same-residual anchor
\(\mathfrak a\) contains a complete key \(\iota_R\), its time \(j_R\), and
both active row corners
\[
 mj_R+h_0=P_mR_m,\qquad
 nj_R+h_0=P_nR_n,\qquad
 d_mR_m=d_nR_n.
\]
At an actual erasure key \(\iota_E\), with time \(j_E\), the corresponding
targets are
\[
 mj_E+h_0=Q_mS_m,\qquad
 nj_E+h_0=Q_nS_n,\qquad
 d_mS_m\ne d_nS_n.
\]
Here \(P_m,P_n,Q_m,Q_n\) are the literal largest-prime labels and
\(R_m,R_n,S_m,S_n\) their cofactors.  At a present corner, let
\(\beta_{\iota,r}\) denote the literal coefficient after every physical
mask and profile.  The residual-sign-free four-corner amplitude is
\begin{equation}
 \cA(\iota_E,\iota_R;m,n)
 =
 \frac{
 \overline{\beta_{\iota_E,m}}\beta_{\iota_E,n}
 \overline{\beta_{\iota_R,n}}\beta_{\iota_R,m}
 }{W_mW_n},
 \label{eq:literal-four-corner-amplitude}
\end{equation}
and is zero if a required corner is absent
\citep{WangTPC70}.

Every target and residual label used below lies on the inherited
squarefree physical support.  In particular, at an erasure key
\[
 mj_E+h_0=Q_mS_m,\qquad nj_E+h_0=Q_nS_n,
\]
and
\[
 \mu(mj_E+h_0),\ \mu(nj_E+h_0),\
 \mu(d_mS_m),\ \mu(d_nS_n)\in\{-1,1\}.
\]
The analogous nonvanishing conditions are retained at the
same-residual anchor.
Put
\[
 H=h_0(n-m).
\]
At an actual erasure key, the two target cofactors are \(S_m,S_n\).
Their canonical content and primitive coordinates are
\begin{equation}
 q=(S_m,S_n),\qquad S_m=qu,\qquad S_n=qv.
 \label{eq:canonical-erasure-coordinates}
\end{equation}
The determinant identity of TPC--70 \citep{WangTPC70} gives
\[
 q\mid |H|,
 \qquad
 nuQ_m-mvQ_n=H/q,
\]
and the unequal-residual condition is
\begin{equation}
 (u,v)\ne(b,a).
 \label{eq:excluded-anchor-direction}
\end{equation}
Every physical coordinate in \eqref{eq:canonical-erasure-coordinates}
satisfies
\begin{equation}
 (u,v)=1.
 \label{eq:physical-primitivity}
\end{equation}

Let \(k_{\mathfrak a,q}(u,v)\) be the TPC--70 complete literal ray sum of
\eqref{eq:literal-four-corner-amplitude} at these coordinates.  It contains
every physical time, complete native key, largest-prime condition,
endpoint, mask, profile, complex phase, and the four-corner normalization
\(1/(W_mW_n)\).  It is zero when the corresponding actual ray is absent.
Aggregate the exact contents before taking absolute values:
\begin{equation}
 k_{\mathfrak a}(u,v)
 =
 \one_{(u,v)\ne(b,a)}
 \sum_{q\mid|H|}k_{\mathfrak a,q}(u,v),
 \qquad (u,v)=1.
 \label{eq:primitive-anchor-datum}
\end{equation}
Different \(q\)-slices may cancel at the same primitive coordinate.
Accordingly,
\[
 \supp k_{\mathfrak a}
 \subseteq
 \bigcup_{q\mid|H|}\supp k_{\mathfrak a,q},
\]
and equality is not asserted.

\subsection{Canonical zero completion}

Write
\[
 \cP_2=\{(u,v)\in\N^2:(u,v)=1\}.
\]

\begin{definition}[Support-faithful completion]
\label{def:canonical-zero-completion}
The canonical physical zero completion of
\eqref{eq:primitive-anchor-datum} is
\begin{equation}
 K_{\mathfrak a}^{0}(u,v)
 =
 \begin{cases}
  k_{\mathfrak a}(u,v),&(u,v)\in\cP_2,\\
  0,&(u,v)\notin\cP_2,
 \end{cases}
 \qquad u,v\ge1.
 \label{eq:canonical-zero-completion}
\end{equation}
It is zero both at absent primitive rays and at every nonprimitive
coordinate.
\end{definition}

The superscript \(0\) denotes zero completion, not the removal of a
physical atom.  The same-residual direction \((b,a)\) is already absent
from the literal erasure datum.

\begin{theorem}[Literal primitive support]
\label{thm:literal-primitive-support}
For every physical anchor \(\mathfrak a\),
\begin{equation}
 \supp K_{\mathfrak a}^{0}\subseteq\cP_2.
 \label{eq:literal-primitive-support}
\end{equation}
The property is preserved by exact \(q\)-aggregation, finite sums over
anchors, and multiplication by anchor-dependent scalars.
\end{theorem}

\begin{proof}
Equation \eqref{eq:physical-primitivity} follows from the definition
\(q=(S_m,S_n)\).  Thus no actual ray has a nonprimitive coordinate.
Definition \ref{def:canonical-zero-completion} assigns zero to every
remaining site.  Pointwise sums and scalar multiplication cannot create
support outside \(\cP_2\).
\end{proof}

\begin{remark}[Canonical means support-faithful]
\label{rem:not-variation-minimal}
The completion is canonical because it inserts no coefficient at an
absent physical coordinate.  This does not say that it minimizes mixed
variation among all analytic completions.  That different optimization
problem is treated in \cref{sec:completion-gauge}.
\end{remark}

\subsection{The anchored signed coefficient}

Let
\[
 \varepsilon_{\mathfrak a}=\mu(a)\mu(b).
\]
The frozen-sign theorem of TPC--70 \citep{WangTPC70} gives the exact
anchored scalar
coefficient
\begin{equation}
 \boxed{
 \mathfrak X_{\mathfrak a}
 =
 \varepsilon_{\mathfrak a}
 \sum_{u,v\ge1}
 \mu(u)\mu(v)K_{\mathfrak a}^{0}(u,v).}
 \label{eq:anchored-physical-sum}
\end{equation}
The explicit coprimality condition may be omitted because
\eqref{eq:literal-primitive-support} already enforces it.  This is a
four-corner contribution to \(\tr(ER)\); it is not a two-corner entry of
the erasure operator.
