\section{The reduced physical gate}
\label{sec:physical-ledger}

The canonical physical branch now has no diagonal-cutoff choice.  Its
remaining trace-level problem is a weighted plaquette estimate.
From this point, let \(X\to\infty\) through one declared physical family.
The active rows, anchors, kernels, and reference scales all depend on
\(X\); the index is suppressed, and every \(o(\,\cdot\,)\) statement is
with respect to this limit.

\subsection{Reference masses}

For one anchor define the exact post-\(q\)-aggregation mass
\begin{equation}
 \mathfrak W_{\mathfrak a}
 =
 \sum_{u,v\ge1}|K_{\mathfrak a}^{0}(u,v)|.
 \label{eq:anchored-physical-mass}
\end{equation}
Absolute values occur after the exact \(q\)-sum.  This mass is neither the
sum of pre-aggregation ray masses nor automatically the raw global Gram
mass.  Let \(\mathfrak A_{\rm tr}>0\) be one explicitly declared physical
reference scale for the complete first mixed trace.

\begin{proposition}[Canonical physical closure criterion]
\label{prop:canonical-physical-criterion}
If
\begin{equation}
 \sum_{m<n}\sum_{\mathfrak a\in\cR_{m,n}}
 \cC_\square(K_{\mathfrak a}^{0})
 =
 o(\mathfrak A_{\rm tr}),
 \label{eq:global-weighted-plaquette-target}
\end{equation}
then
\begin{equation}
 \tr(ER)=o(\mathfrak A_{\rm tr}).
 \label{eq:trace-saving}
\end{equation}
The conclusion remains valid if the left side of
\eqref{eq:global-weighted-plaquette-target} is replaced by the sharper
\(\cC_\square(K_{\rm tr}^{0})\).
\end{proposition}

\begin{proof}
Use \eqref{eq:global-trace-certificate}.
\end{proof}

This is an exact sufficient condition, not a theorem that the physical
cost is small.  It allows a nonuniform anchor family because the
quantifier is global and the total cost is explicit.

\subsection{Completion route}

For each anchor choose a declared analytic completion
\[
 F_{\mathfrak a}
 \in
 \Ext_{U_{\mathfrak a},V_{\mathfrak a}}(k_{\mathfrak a})
\]
before any later operator extremizer is selected.  The general sufficient
condition is
\begin{equation}
 \sum_{m<n}\sum_{\mathfrak a\in\cR_{m,n}}
 \cC_{D_{\mathfrak a}}(F_{\mathfrak a})
 =
 o(\mathfrak A_{\rm tr}).
 \label{eq:completion-physical-target}
\end{equation}
Here variation and diagonal tail refer to the same completion.  A future
physical construction may, for example, move a common coordinate factor
into an existing \(q\)-label and fill only those nonprimitive sites
compatible with literal content data.  An arbitrary smooth interpolation
is an L0 analytic device until its coefficient norm, support, and
quantifier dependence are controlled.

\subsection{Exact stop rules}

The route has the following logically different outcomes.
\begin{enumerate}[label=\textup{(G\arabic*)},leftmargin=3.2em]
 \item If \eqref{eq:global-weighted-plaquette-target} fails by a proved
       lower obstruction on a nonnegligible physical family, only the
       canonical tail-free certificate is closed.
 \item To close the full completion route, one needs a lower obstruction
       for every declared admissible completion rule, or for the infimum
       in \eqref{eq:completion-gauge}, at the same physical mass scale.
 \item Failure of an ambient tail estimate closes only that ambient
       specialization.  The auxiliary diagonal tail of the canonical
       zero extension is already zero.
 \item A large zero-completion variation does not prove that the original
       signed sum is large.  Literal complex phases, a structured
       completion, or a different signed sector may still cancel.
 \item A completed estimate for \(\tr(ER)\) remains trace-level.  It does
       not imply an entrywise erasure bound, a row star, a Perron estimate,
       or an operator norm.
 \item The geometric short-ray mass, physical endpoint cells, represented
       lower frame, missing-mass comparison, nuisance shorting, and final
       boundary reconstruction are untouched.
\end{enumerate}

\subsection{Exponent interpretation}

The classical prime number theorem gives \(M(x)=o(x)\)
\citep{IwaniecKowalski2004}.  It does not by itself provide the fixed
polynomial saving required by the strict endpoint ledger.  For a coarse
anchorwise estimate, one would need quantitative control of
\[
 \mathfrak M(U_{\mathfrak a})
 \mathfrak M(V_{\mathfrak a})
 \cV_\square(K_{\mathfrak a}^{0})
\]
relative to the literal reference mass.  Calling \(M(x)=o(x)\) an endpoint
power saving would be incorrect.
