\section{Adaptive route from TPC--73 to TPC--82}
\label{sec:route-plan}

TPC--72 separated four live tasks: physical primitive-plane variation, a
genuine operator carrier, represented-frame closure, and final shorted
reassembly.  The present paper removes the auxiliary diagonal tail for the
support-faithful physical zero extension and turns the first task into a
completion and weighted-plaquette problem.  The next block will alternate
among the independent
branches rather than refine one branch indefinitely.

\subsection{Provisional sequence}

\begin{longtable}{@{}
 >{\raggedright\arraybackslash}p{0.12\textwidth}
 >{\raggedright\arraybackslash}p{0.26\textwidth}
 >{\raggedright\arraybackslash}p{0.54\textwidth}@{}}
\toprule
Paper & Door & Falsifiable target\\
\midrule
\endfirsthead
\toprule
Paper & Door & Falsifiable target\\
\midrule
\endhead
TPC--73 &
Primitive support &
Tail collapse, completion invariance, and the exact weighted plaquette
gate.\\
TPC--74 &
Direct two-corner carrier &
Reindex the literal erasure entry itself on primitive cofactor coordinates,
or prove that a required physical sector lacks such a canonical
reindexing.\\
TPC--75 &
Completion/coherence census &
Construct a \(q\)-compatible completion with controlled full cost, or give
an actual-carrier lower obstruction for the completion certificate.\\
TPC--76 &
Row-local observability &
Transfer anchored data to observable row stars with a quantified inverse,
while isolating orphan erasure edges.\\
TPC--77 &
Terminal activation &
Use literal moment-to-capacity estimates in a declared distinguished
coefficient scope; do not replace them by a uniform worst-row claim.\\
TPC--78 &
Represented determinant capacity &
Convert actual good-component determinant mass into a distinguished lower
frame, or close that certificate on an actual bad-energy family.\\
TPC--79 &
Operator aggregation &
Apply pair/star/Perron or complete moments only to the literal carrier
established in TPC--74--TPC--76.\\
TPC--80 &
Nuisance principal angle &
Express shorting loss through the angle between represented output and the
missing image of the represented kernel.\\
TPC--81 &
Compatible merge &
Test missing mass, represented frame, nuisance, boundaries, and all
fixed-power losses in one carrier and quantifier scope.\\
TPC--82 &
Ten-paper audit &
Classify exact advances, actual obstructions, unresolved L2 inputs,
fallbacks, and the strict endpoint status.\\
\bottomrule
\end{longtable}

\subsection{Dynamic branching rules}

The numbering describes dependencies, not guaranteed positive outcomes.
\begin{enumerate}[label=\textup{(R\arabic*)},leftmargin=3.2em]
 \item If TPC--75 proves that every admissible completion has excessive
       physical cost, the Abel branch is recorded as a negative certificate
       theorem and the signed effort moves to direct entries, literal
       phases, or higher one-erasure polygons.
 \item If the direct-entry carrier closes in TPC--74, it has priority over
       anchor observability because it also sees orphan erasure edges.
       Otherwise TPC--76 retains the exact observable/orphan decomposition.
 \item A positive trace theorem never substitutes for TPC--79.  Operator
       aggregation begins only after a two-corner, row-local, or
       complete-moment carrier exists.
 \item The activation and represented papers proceed independently of the
       primitive-plane branch.  Failure of one branch does not supply a
       hypothesis on the other.
 \item TPC--81 attempts a merge only if all inputs use literal
       coefficients, the same fixed \(h_0\), raw physical normalization,
       actual support, and one common uniform or distinguished coefficient
       scope.
 \item Any actual family forcing total fixed-power loss at least \(1/400\)
       closes the present endpoint implication, including equality.
\end{enumerate}

At every stage, success means a literal exponent improvement, closure of a
necessary interface, or an exact actual-carrier obstruction.  A numerical
trend, a smooth surrogate, a fixed anchor, or an averaged shift is not
reported as fixed-shift arithmetic progress.
