\begin{abstract}
The literal fixed-shift residual output is a coherent sum over distinct
terminal primes inside each complete fiber \(y=(\gamma,s,j)\).  TPC--56
extracted a constant-energy phase sector, but that post-terminal adaptive
selection did not lower-bound the undeleted output.  We develop a
phase-blind route that acts on no selected coordinates: the terminal
diagonal carried by actual singleton fibers is already an exact positive
part of the full grouped square.

For an arbitrary finite fiber system, let \(D\) be the diagonal energy,
\(G\) the undeleted grouped energy, and \(D_1\) the energy on fibers with
exactly one active coordinate.  We prove
\[
 G\ge D_1\ge(D-I_1)_+,
\]
where the rooted collision incidence is
\[
 I_1=\sum_u|x_u|^2\bigl(n_{q(u)}-1\bigr).
\]
More generally, rooted collision moments
\(I_r=\sum_u|x_u|^2\binom{n_{q(u)}-1}{r}\) give an exact finite
inclusion--exclusion formula for \(D_1\) and sharp Bonferroni bounds.  Thus
the sufficient estimate \(I_1\le(1-\delta)D\) yields the undeleted lower
square \(G\ge\delta D\), without a transversal, a phase sector, or a
monotonic return from a selected packet.  A core cofactor block can be used
directly: every collision partner lies in a fixed enlarged block.

For the literal bounded source class, write each terminal amplitude as
\(x_u=c_u\zeta_{m(u)}\) and form the baseline weighted row--fiber graph.
We compute the sharp coefficient-uniform singleton constant
\[
 \beta_X=\min_{m:W_m>0}\frac{W_{m,1}}{W_m}
 =\inf_{\substack{0<D(\zeta)\\|\zeta_m|\le C}}
   \frac{D_1^{\rm phys}(\zeta)}{D(\zeta)}.
\]
This identifies rowwise singleton occupancy, rather than unweighted global
abundance, as the exact uniform gate.

We then parameterize every literal collision.  Two colliding factorizations
have a unique factor exchange
\[
 d_1=ab,\quad d_2=ac,\quad r_1=ce,\quad r_2=be,
\]
with \(a,b,c,e\) pairwise coprime and squarefree, and satisfy
\[
 \frac{e}{(e,h_0)}\mid b\ell_1-c\ell_2.
\]
Same-divisor collisions disappear for \(r>\rad|h_0|L\); high-cofactor
cross-divisor collisions require an exchange of two comparable large
factors.  A fixed row pair and exchange pattern occupies one orbit residue
class.  Separately, after \((s,j,d)\) is fixed, the source and terminal
primes run along two nonproportional affine forms.

These results reduce singleton occupancy to a concrete weighted one-atom
versus two-atom incidence estimate with all source and terminal primes
retained.  The current carrier and coefficient
hypotheses do not prove a positive value of \(\beta_X\) or a positive
singleton proportion.  Terminal activation, a parity improvement, and a
twin-prime conclusion are not claimed.
\end{abstract}
