\section{Occupancy barrier, endpoint ledger, and the next gate}
\label{sec:tpc57-endpoint-claims}

The preceding sections give exact lower bounds once a positive fraction of
the terminal diagonal lies in singleton fibers of the complete physical
output.  They do not supply that fraction.  This section records why the
existing support bounds do not imply it, states the precise weighted
factor-exchange estimate still missing, and places that estimate in the
inherited \(1/400\) ledger.

\subsection{Why a multiplicity upper bound is not singleton occupancy}

The TPC--55 determinant-ladder argument gives an upper bound for the number
of terminal atoms in one residual fiber.  Such a bound is useful for a
post-terminal transversal cover, but it points in the wrong direction for
the undeleted singleton route.

\begin{proposition}[Sharp occupancy barrier]
\label{prop:tpc57-occupancy-barrier}
For every integer \(M\ge2\) and every \(E>0\), there is a finite fiber
system and a vector \(x\) such that
\begin{equation}
 D(x)=E,
 \qquad
 \max_y n_y(x)\le M,
 \qquad
 D_1(x)=G(x)=0.
 \label{eq:tpc57-bounded-degree-zero-singleton}
\end{equation}
Consequently no positive lower bound for \(D_1/D\), or for \(G/D\), follows
from a finite maximal-fiber bound alone.  The conclusion remains true when
the maximal degree is \(2\).
\end{proposition}

\begin{proof}
Use one fiber with two coordinates
\[
 x_{u_1}=\sqrt{E/2},
 \qquad
 x_{u_2}=-\sqrt{E/2}.
\]
Its active degree is \(2\), its singleton energy is zero, and its grouped
sum vanishes.  This is also the case \(D_0=I_0=E\) of
\cref{prop:tpc57-first-moment-sharpness}.
\end{proof}

The obstruction is not cancellation-specific.  Even if both coordinates
in every doubleton have the same phase, the singleton energy is still zero.
Thus replacing the grouped square by a random-phase heuristic would not
prove the required occupancy statement.  Likewise, terminal activation
\(\cD_R^{\rm core}>0\) says only that some terminal energy survives; it does
not say whether that energy lies in degree-one or multiple fibers.

The rowwise minimax theorem makes the same boundary coefficient-sensitive.
For a declared baseline carrier, the best constant uniform over the bounded
row-coefficient class is
\[
 \beta_X=\min_{m:W_m>0}\frac{W_{m,1}}{W_m}.
\]
If one positive-weight row has no structurally singleton edge, then
\(\beta_X=0\).  An upper bound on every fiber degree does not exclude this
case.  Conversely, \(\beta_X=0\) is only a failure of the uniform singleton
route; it is not a proof that the distinguished grouped vector vanishes.

\subsection{The current endpoint scales}

The literal scale dictionary inherited from TPC--53 and retained in
TPC--55--56 is
\begin{equation}
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)},
 \qquad
 D=X^{10049/52500+o(1)},
 \label{eq:tpc57-endpoint-QJD}
\end{equation}
and therefore
\begin{equation}
 L=Q/D=X^{99979/210000+o(1)}.
 \label{eq:tpc57-endpoint-L}
\end{equation}
For a dyadic cofactor block
\(r\asymp R=X^{\theta_R+o(1)}\), the inherited
coefficient-blind capacity bound is
\begin{equation}
 M_X(R)
 \ll X^{o(1)}\left(1+\frac LR\right),
 \qquad
 \mu_{\rm cap}
 =\left(\frac{99979}{210000}-\theta_R\right)_+.
 \label{eq:tpc57-capacity-exponent}
\end{equation}

The enlarged partner range \([R/2,4R]\) is the union of three dyadic
blocks with scales comparable to \(R\).  Hence
\begin{equation}
 \max_y d_y^+(R)
 \ll X^{o(1)}\left(1+\frac LR\right)
 \label{eq:tpc57-enlarged-capacity-bound}
\end{equation}
under the same polynomial-size residual-label hypothesis as TPC--55.  The
constant-factor enlargement changes no exponent.

At the older cofactor scale \(R\asymp J\), one has
\begin{equation}
 \frac LR
 =X^{15077/105000+o(1)},
 \qquad
 \mu_{\rm cap}=\frac{15077}{105000}.
 \label{eq:tpc57-old-cofactor-capacity}
\end{equation}
This support-only exponent exceeds the nominal endpoint allowance by
\begin{equation}
 \frac{15077}{105000}-\frac1{400}
 =\frac{29629}{210000}>0.
 \label{eq:tpc57-capacity-endpoint-deficit}
\end{equation}

The factor-exchange geometry also gives an exact support theorem in a much
higher cofactor regime: by
\cref{cor:tpc57-high-cofactor-full-singleton}, every core atom is a
singleton in its complete terminal fiber if
\begin{equation}
 R>48HLD^2,
 \qquad H=\rad|h_0|.
 \label{eq:tpc57-endpoint-high-cofactor-test}
\end{equation}
Here \(L>4D\) holds for all sufficiently large \(X\) at the declared
scales, and \(H=X^{o(1)}\) because \(h_0\) is fixed.  Let \(N_+\) denote
the inherited maximum positive target size.  The large-prime descent
imposes the stronger global range restriction \citep{WangTPC45}
\begin{equation}
 p>\sqrt{N_+},
 \qquad
 r=\frac{mj+h_0}{p}<\sqrt{N_+}=X^{1/2+o(1)}.
 \label{eq:tpc57-large-prime-r-ceiling}
\end{equation}
On the other hand,
\begin{equation}
 LD^2=X^{180371/210000+o(1)},
 \qquad
 \frac{\sqrt{N_+}}{HLD^2}
 =X^{-75371/210000+o(1)}.
 \label{eq:tpc57-high-cofactor-global-gap}
\end{equation}
Consequently no terminal atom in the inherited physical carrier can lie
in a block satisfying
\eqref{eq:tpc57-endpoint-high-cofactor-test} once \(X\) is large.  The
high-cofactor theorem is a valid structural boundary, but its physical
activation door is closed for the present packet.

For comparison, at the older scale \(R\asymp J\),
\begin{equation}
 \frac{R}{HLD^2}
 =X^{-55273/105000+o(1)}.
 \label{eq:tpc57-high-cofactor-endpoint-gap}
\end{equation}
Thus even before using the global ceiling, the old block misses the
threshold by a fixed positive power.

For \(R\gg L\), the capacity is only \(X^{o(1)}\); nevertheless a carrier
made entirely of doubletons still has zero singleton energy.  Thus moving
to a balanced block removes the positive-power multiplicity cost of a
transversal cover but does not prove the occupancy estimate needed here.
Primality may thin the ambient ladder by logarithmic factors; the existing
upper-bound sieve does not turn this support count into a weighted
degree-one lower bound.

\subsection{The exact missing weighted factor-exchange estimate}

The weakest first-moment statement needed for the distinguished vector is
not an unweighted count.  By
\eqref{eq:tpc57-exact-weighted-physical-incidence}, it is precisely
\begin{equation}
 \boxed{
 \sum_m|\zeta_m|^2
   \mathfrak J_{m,1}^{R,+}(\zeta)
 \le
 (1-\delta_R)
 \sum_m|\zeta_m|^2W_{m,R},
 \qquad
 \delta_R>0.}
 \label{eq:tpc57-exact-missing-weighted-estimate}
\end{equation}
Every pair counted on the left satisfies the full literal system
\begin{equation}
 \begin{gathered}
 u=(d\ell,r,j,\gamma),
 \qquad
 v=(d'\ell',r',j,\gamma),
 \qquad
 dr=d'r',\qquad u\ne v,\\
 pr-d\ell j=h_0,
 \qquad
 p'r'-d'\ell'j=h_0,\\
 R\le r\le2R,
 \qquad
 R/2\le r'\le4R,
 \end{gathered}
 \label{eq:tpc57-complete-factor-exchange-system}
\end{equation}
with both terminal primes, all squarefree/coprime conditions, the literal
mask, every profile cutoff, and the actual row coefficients retained.
The energy weight is attached to the root \(u\):
\begin{equation}
 |x_u|^2=|c_u|^2|\zeta_{m_u}|^2.
 \label{eq:tpc57-root-physical-weight}
\end{equation}
Neither the partner count nor the root count may replace this weight
without a separate comparison theorem.

The coefficient-independent baseline majorant gives the stronger sufficient
target
\begin{equation}
 \boxed{
 \sum_m|\zeta_m|^2J_{m,1}^{R,+}
 \le
 (1-\delta_R)
 \sum_m|\zeta_m|^2W_{m,R}.}
 \label{eq:tpc57-baseline-distinguished-target}
\end{equation}
A still stronger, coefficient-uniform rowwise target is
\begin{equation}
 J_{m,1}^{R,+}
 \le(1-\delta_R)W_{m,R}
 \qquad(m:W_{m,R}>0).
 \label{eq:tpc57-baseline-uniform-row-target}
\end{equation}
The implications are
\begin{equation}
 \eqref{eq:tpc57-baseline-uniform-row-target}
 \Longrightarrow
 \eqref{eq:tpc57-baseline-distinguished-target}
 \Longrightarrow
 \eqref{eq:tpc57-exact-missing-weighted-estimate}
 \Longrightarrow
 \cG_{h_0}(G_X^L)
 \ge\delta_R\cD_R^{\rm core}.
 \label{eq:tpc57-collision-target-hierarchy}
\end{equation}
On the admissible inherited carrier, no estimate in this chain is currently
proved asymptotically for the \(R\asymp J\) packet.
The first target is suitable for a theorem uniform over
the bounded coefficient class; the middle target may exploit the
distinguished coefficient energy; the last is the exact weakest target for
the first rooted-moment bridge.

If
\begin{equation}
 \delta_R=X^{-\lambda_{\rm sing}+o(1)},
 \label{eq:tpc57-singleton-loss-exponent}
\end{equation}
then \(\lambda_{\rm sing}\) is the singleton-occupancy loss.  Together with
the exact activation chain in
\eqref{eq:tpc57-prospective-activation-ledger}, a direct already-reassembled
fixed-\(h_0\) route must eventually satisfy
\begin{equation}
 \boxed{
 \lambda_{\rm sel}+\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm sing}
 +\lambda_{\rm Gram}+\lambda_{\rm bdry}+\lambda_{\rm tail}
 \le\frac1{400}.}
 \label{eq:tpc57-full-endpoint-budget}
\end{equation}
No separate coherence loss is inserted after the singleton estimate.  No
frozen-shift localization or projective-reassembly loss is inserted in the
direct physical route either.  If a different proof passes through those
interfaces, their losses must be restored explicitly.  At equality in
\eqref{eq:tpc57-full-endpoint-budget}, an error already of order
\(X^{-1/400+o(1)}\) need not be absorbable; strict slack or a closed
constant-level comparison is the safe endpoint condition.

\subsection{Six-point physical audit}

The proposed singleton bridge passes the following audit.
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3.2em]
 \item \emph{Literal coefficients.}
       The terminal amplitude is the exact
       \(x_u=(D_{h_0}G_X^L)_u\).  Its row-factorized form
       \(x_u=c_u\zeta_{m_u}\) retains the common output factor, source
       shapes, binary mask, profiles, cofactor sign, and shaped terminal
       logarithm.  The collision statistic is weighted by \(|x_u|^2\),
       not by a proxy counting measure.
 \item \emph{Fixed physical shift.}
       Both equations in
       \eqref{eq:tpc57-complete-factor-exchange-system} use the one specified
       \(h_0\).  No averaged or frozen intercept is introduced.
 \item \emph{Physical atomic normalization.}
       The pre-terminal, core terminal, collision, and grouped energies all
       use the inherited raw counting-measure atoms.  Repetitions in the
       cofactor label remain distinct, and the terminal multiplier is not
       hidden in a modified input norm.
 \item \emph{Canonical representation.}
       Collisions are defined by the complete output key
       \(q(u)=(\gamma,d_mr,j)\), with the terminal-prime coordinate resolved
       exactly as in TPC--55.  The core and enlarged block are deterministic
       cofactor ranges.  No favorable rank, phase sector, projective layer,
       or ambient prime ladder is selected.
 \item \emph{Actual active support.}
       The baseline terminal carrier and the physically active carrier are
       kept distinct.  The exact statistic
       \(\mathfrak J_{m,1}^{R,+}(\zeta)\) uses active degrees, while
       \(J_{m,1}^{R,+}\) is explicitly labeled as a support-only majorant.
       The enlarged-block lemma accounts for every full-output partner of a
       core root.
 \item \emph{Endpoint budget.}
       Block occupancy, terminal activation, and singleton occupancy have
       separate exponents.  Native-Gram, boundary, and tail losses remain
       visible in \eqref{eq:tpc57-full-endpoint-budget}.  No support-only
       multiplicity estimate is entered as a positive singleton fraction,
       and the high-cofactor support theorem is not used outside its literal
       range.
\end{enumerate}

\subsection{Claim table}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.29\textwidth}
                >{\raggedright\arraybackslash}p{0.60\textwidth}}
\toprule
Statement & Status \\
\midrule
Singleton floor and rooted collision expansion
& Unconditional finite-dimensional theorems (L0). \\
Core-to-full collision bridge
& Unconditional finite-dimensional lower bound for the undeleted grouped
  vector (L0). \\
Sharp rowwise minimax constant
& Exact finite weighted-graph theorem for the bounded row-coefficient class
  (L0). \\
Prime-resolved literal row/fiber representation
& Exact on the inherited fixed-\(h_0\) terminal support under the TPC--55
  injection and TPC--56 gauge factorization (L1). \\
Enlarged-block partner localization
& Exact factor-exchange consequence of \(dr=d'r'\) and
  \(d,d'\in[D,2D]\); no arithmetic occupancy assertion (L1). \\
High-cofactor full-fiber singleton exclusion
& Exact support theorem under \(R>48HLD^2\) (L1); the inherited
  \(r<X^{1/2+o(1)}\) ceiling makes this range physically empty. \\
Weighted physical incidence identity
& Exact specialization to the distinguished physical coefficient vector
  (L1). \\
Positive singleton fraction on a cofactor core
& Conditional on
  \eqref{eq:tpc57-exact-missing-weighted-estimate}; not proved. \\
Core block occupancy and terminal activation
& Separate hypotheses; not proved here. \\
Undeleted fixed-\(h_0\) residual lower square
& Follows conditionally from the preceding three gates; no unconditional
  asymptotic lower bound is claimed. \\
Native affine Gram, boundary, and tail reconnection
& Not proved. \\
Parity improvement or twin-prime consequence
& Not claimed. \\
\bottomrule
\end{tabular}
\end{center}

The level terminology is therefore conservative.  L0 denotes exact
finite-dimensional identities and extremal laws.  L1 denotes exact
specialization to the declared literal support and factor-exchange geometry.
An L2 advance would require a quantitative estimate such as
\eqref{eq:tpc57-exact-missing-weighted-estimate}, together with activation
and every downstream comparison needed to reconnect to the parent physical
correlation.  No result in the current paper is labeled L2.

\subsection{The next gate}

The factor-exchange localization leaves one closed structural shortcut and
four live analytic or negative routes.
\begin{enumerate}[label=\textbf{Door \Alph*.},leftmargin=3.8em]
 \item \emph{Closed high-cofactor shortcut.}
       The support theorem would give \(\delta_R=1\) above
       \(48HLD^2\), but
       \cref{eq:tpc57-large-prime-r-ceiling,eq:tpc57-high-cofactor-global-gap}
       show that the inherited carrier contains no such terminal atom.  This
       door is closed for the current packet.  Reopening it would require a
       different large-prime decomposition or physical carrier, not merely a
       new dyadic choice of \(R\).
 \item \emph{Distinguished weighted incidence.}
       Estimate the exact left side of
       \eqref{eq:tpc57-exact-missing-weighted-estimate}, retaining the root
       energy \(|c_u\zeta_{m_u}|^2\).  This is the weakest first-moment
       target and may exploit concentration of the actual coefficients away
       from collision-rich rows.
 \item \emph{Uniform row factor exchange.}
       Prove \eqref{eq:tpc57-baseline-uniform-row-target} by analyzing the
       coupled system \eqref{eq:tpc57-complete-factor-exchange-system} for
       each source row.  This would give a theorem uniform over the inherited
       bounded coefficient class, but is strictly stronger than Door B.
 \item \emph{Higher rooted moments.}
       If the first-moment truncation is too crude, define core-rooted
       moments with
       \(\binom{n_{q(u)}^{\rm phys}-1}{r}\).  The exact Bonferroni hierarchy
       of \cref{thm:tpc57-collision-moment-expansion} can then certify
       singleton energy through an odd higher truncation.  Each new moment
       requires its own weighted factor-exchange estimate.
 \item \emph{Saturation or route closure.}
       If none of the preceding estimates can hold, construct literal
       carriers for which the weighted singleton constant tends to zero, or
       prove that every available support-only estimate is saturated by
       collision-rich rows.  Such a theorem would close the singleton door
       without asserting cancellation of the distinguished full output.
\end{enumerate}

Door A records a closed structural boundary.  Door B is the economical live
analytic target.  The enlarged block shows that Door B is local in cofactor
scale, but the occupancy barrier shows that it is not a consequence of the
known ladder capacity bound.  A positive
estimate, together with core terminal activation, would give the first
undeleted fixed-\(h_0\) coherent lower square in this route; a sharp
negative estimate would identify precisely why singleton occupancy cannot
carry the endpoint argument.

\paragraph{Conclusion.}
The undeleted terminal square has an exact phase-blind floor: every unit of
core energy whose full physical fiber is a singleton survives unchanged.
All partners of a cofactor-core atom lie in one constant-factor enlarged
block, and the resulting obstruction is the explicit coefficient-weighted
factor-exchange incidence
\eqref{eq:tpc57-exact-missing-weighted-estimate}.  The high-cofactor regime
is disjoint from the inherited carrier; on its admissible cofactor range,
the current support theory bounds how many partners may occur but does not
show that a positive weighted fraction has none.  Terminal activation,
weighted singleton occupancy,
native-Gram comparison, boundary control, and tail reconnection therefore
remain separate gates, all strictly before any parity-sensitive or
twin-prime conclusion.
