\section{Introduction}
\label{sec:tpc57-introduction}

The preceding four stages separated the fixed-shift prime square into
auditable gates.  TPC--53 fixed the literal coefficient dictionary and raw
atomic normalization \citep{WangTPC53}.  TPC--54 separated pre-terminal
energy selection from actual terminal occupancy \citep{WangTPC54}.
TPC--55 identified the complete residual fiber and proved that adjoining
the terminal prime removes every collision before the final coherent sum
\citep{WangTPC55}.  TPC--56 then showed that a phase-adaptive pentant
contains a constant fraction of the terminal diagonal and has a uniformly
positive grouped square \citep{WangTPC56}.

The last result is exact, but it deliberately deletes four phase channels.
It therefore does not answer the undeleted question.  If
\begin{equation}
 x_{y,p}
 :=(D_{h_0}G_X^L)_{u(y,p)}
 \label{eq:tpc57-intro-amplitude}
\end{equation}
is the terminal amplitude indexed by the exact terminal prime \(p\) in the
full output fiber \(y=(\gamma,s,j)\), then the two physical energies are
\begin{equation}
 \cD_{h_0}(G_X^L)
 =\sum_y\sum_{p\in\cP_y^{\rm phys}}|x_{y,p}|^2,
 \qquad
 \cG_{h_0}(G_X^L)
 =\sum_y\left|\sum_{p\in\cP_y^{\rm phys}}x_{y,p}\right|^2.
 \label{eq:tpc57-intro-two-energies}
\end{equation}
The first quantity ignores interference; the second is the actual
undeleted grouped square.  Arbitrary phases can make one nonsingleton fiber
vanish.  Neither bounded multiplicity nor a large collision-free selected
rank prevents the omitted coordinates from cancelling it.

This paper opens a phase-blind door that does not delete any coordinate:
\begin{quote}
How much terminal diagonal energy already lies in fibers containing exactly
one active atom, and what arithmetic event prevents an atom from being such
a singleton?
\end{quote}
On a singleton fiber there is no interference to estimate.  Its grouped
square equals its diagonal exactly, while every other grouped square is
nonnegative.  Thus singleton energy embeds monotonically in the full
output even though a selected block or rank output does not.

\subsection{The rooted collision interface}

For a finite fiber map \(q:\cU\to\cY\), an array \(x\), and active
multiplicities
\begin{equation}
 n_y(x)=\#\{u\in q^{-1}(y):x_u\ne0\},
 \label{eq:tpc57-intro-active-multiplicity}
\end{equation}
write \(D\) for the diagonal energy, \(G\) for the grouped energy, and
\(D_1\) for the energy on fibers with \(n_y=1\).  The first rooted
collision incidence is
\begin{equation}
 I_1(x)
 =\sum_{u:x_u\ne0}|x_u|^2\bigl(n_{q(u)}(x)-1\bigr)
 =\sum_{\substack{u\ne v\\q(u)=q(v)}}|x_u|^2.
 \label{eq:tpc57-intro-rooted-incidence}
\end{equation}
We prove the sharp chain
\begin{equation}
 \boxed{G\ge D_1\ge(D-I_1)_+.}
 \label{eq:tpc57-intro-singleton-floor}
\end{equation}
The first inequality uses the undeleted output itself.  The second is the
first Bonferroni truncation of an exact collision-moment expansion.  Hence
the concrete estimate
\begin{equation}
 I_1(x)\le(1-\delta)D(x)
 \label{eq:tpc57-intro-needed-incidence}
\end{equation}
would imply \(G(x)\ge\delta D(x)\).  This is a genuine return to the full
fixed-\(h_0\) output, not a statement about a favorable subpacket.

The block version avoids another common logical error.  Let the root atom
lie in a cofactor core \(R\le r\le2R\), but count all of its collision
partners in the full active support.  Because the direct squarefree factor
always lies in \([D,2D]\), equality \(d_ur_u=d_vr_v\) forces every partner
into \(R/2\le r_v\le4R\).  Thus a core-block singleton estimate can be
proved from one fixed enlarged block and then enters the full output
directly.  No lower monotonicity of grouped norms is invoked.

\subsection{Why unweighted singleton counts are insufficient}

The inherited source hypothesis has the form
\begin{equation}
 x_u=c_u\zeta_{m(u)},
 \qquad |\zeta_m|\le C,
 \label{eq:tpc57-intro-row-factorization}
\end{equation}
where \(c_u\) contains every literal mask, profile, terminal, and common
fiber factor independent of \(\zeta_m\).  One source row may feed many
different fibers.  Therefore a large unweighted set of singleton atoms
does not give a coefficient-uniform energy proportion: the allowed source
energy can concentrate on rows meeting mostly nonsingleton fibers.

We encode the exact obstruction in a weighted bipartite graph.  Its left
vertices are source rows, its right vertices are baseline terminal fibers,
and its edges are baseline-nondegenerate terminal atoms with weights
\(|c_u|^2\).  If \(W_m\) is the total edge weight from row \(m\) and
\(W_{m,1}\) is the part ending in structurally singleton fibers, define
\begin{equation}
 \beta_X
 :=\min_{m:W_m>0}\frac{W_{m,1}}{W_m}.
 \label{eq:tpc57-intro-beta}
\end{equation}
The exact minimax theorem is
\begin{equation}
 \boxed{
 \inf_{\substack{0<D(\zeta)\\|\zeta_m|\le C}}
 \frac{D_1^{\rm phys}(\zeta)}{D(\zeta)}
 =\beta_X.}
 \label{eq:tpc57-intro-minimax}
\end{equation}
Thus a uniform Door-A theorem is equivalent to a rowwise weighted
occupancy statement.  If \(\beta_X=0\), singleton energy cannot by itself
give a coefficient-uniform positive fraction.  This does not say that the
full grouped energy vanishes, nor does it say that the distinguished source
coefficients concentrate on a minimizing row.

\subsection{Every collision is a factor exchange}

The arithmetic side is equally explicit.  Suppose two distinct terminal
atoms in one fiber have
\begin{equation}
 m_i=d_i\ell_i,
 \qquad
 d_1r_1=d_2r_2=s.
 \label{eq:tpc57-intro-collision-data}
\end{equation}
The inherited equality support makes \(s\) squarefree and
\((d_i,r_i)=1\).  Consequently there are unique pairwise coprime
squarefree integers \(a,b,c,e\) such that
\begin{equation}
 d_1=ab,
 \qquad d_2=ac,
 \qquad r_1=ce,
 \qquad r_2=be.
 \label{eq:tpc57-intro-factor-exchange}
\end{equation}
The two terminal equations become
\begin{equation}
 ce\,p_1-ab\ell_1j=h_0,
 \qquad
 be\,p_2-ac\ell_2j=h_0,
 \label{eq:tpc57-intro-exchange-equations}
\end{equation}
and force
\begin{equation}
 \boxed{
 \frac{e}{(e,h_0)}\mid b\ell_1-c\ell_2.}
 \label{eq:tpc57-intro-exchange-divisibility}
\end{equation}
This is not an ambient divisor model: the reverse statement retains every
literal carrier, primality, mask, cutoff, residue, and orbit condition.

The factor exchange gives deterministic sparsity.  Same-\(d\) collisions
are impossible for \(r>\rad|h_0|L\).  At large cofactor scale, a
cross-\(d\) collision must exchange two distinct comparable factors of
quantified size.  After the rows and exchange pattern are fixed,
simultaneous integrality occupies one residue class of \(j\).  In the
separate fixed-\((s,j,d)\) description, the source and terminal primes run
along two nonproportional affine forms.  These are the exact orbit and
two-point objects that a future upper-bound sieve would have to sum.

\subsection{What advances and what remains open}

The advance is a complete reduction of the phase-blind undeleted route:
\[
 \begin{gathered}
 \text{terminal activation}
 +\text{weighted rooted-collision deficit}
 \\
 \Longrightarrow
 \text{undeleted fixed-\(h_0\) lower square}.
 \end{gathered}
\]
All collisions in the numerator now have a unique factor-exchange and
orbit-ladder description.  The remaining estimate compares weighted
one-atom terminal energy with a weighted two-atom incidence sum, retaining
the two source primes and the two terminal primes in every collision.

The current TPC--53--56 hypotheses do not imply
\eqref{eq:tpc57-intro-needed-incidence}.  The retained carrier has no
declared product-density theorem, terminal activation is itself open, a
maximum-degree bound does not force any singleton, and the bounded source
class permits rowwise energy concentration.  An upper-bound sieve for the
two affine prime forms can estimate a numerator, but a positive proportion
requires a compatible lower denominator and uniform control of the carrier
and weights.  This is precisely where the next arithmetic input is needed.

\Cref{sec:tpc57-literal-interface} fixes the literal support and energies.
\Cref{sec:tpc57-singleton-theory} proves the finite collision-moment
theory.  \Cref{sec:tpc57-block-bridge} gives the full-output block bridge.
\Cref{sec:tpc57-row-minimax} proves the rowwise minimax theorem.
\Cref{sec:tpc57-factor-exchange} parameterizes every collision, and
\cref{sec:tpc57-orbit-reduction} resolves its orbit ladder.
\Cref{sec:tpc57-endpoint-claims} states the exact missing estimate and the
claim boundary.

The finite-fiber identities are unconditional mathematics (L0).  Their
specialization to the exact terminal-prime carrier and the factor-exchange
structure are literal fixed-shift interface results (L1).  No positive
singleton proportion, terminal-activation theorem, parity-sensitive sieve
gain, or twin-prime conclusion is asserted; the classical parity boundary
remains in force \citep{FriedlanderIwaniec2010}.
