\section{Introduction}
\label{sec:tpc47-introduction}

The preceding large-prime descent turns one part of the TPC equality
column into the determinant equation
\begin{equation}
 pr-mj=h_0,
 \label{eq:tpc47-opening-determinant}
\end{equation}
with the prime variable \(p\), a M\"obius-weighted cofactor \(r\), and
an actual source row \(m\).  Projective reassembly separates the
physical source--mask coefficient into those arithmetic variables and
a smooth orbit profile, up to a fixed progression in \(j\)
\citep{WangTPC36,WangTPC45}.  TPC--46 then proves an exact
mesoscopic shift gap when the Hilbert vector attached to
\((p,r,m)\) is independent of \(j\) \citep{WangTPC46}.  In the actual
residual output, the literal label \(s=d(m)r\) remains fixed for
fixed \((m,r)\), but the non-orbit coefficient vector over opposite
rows varies with \(j\); its coordinates are
\begin{equation}
 (\text{opposite row},j,s),\qquad s=d(m)r.
 \label{eq:tpc47-actual-output-coordinate}
\end{equation}
TPC--47 records that dependence by adjoining the literal \(e_j\)
factor and projecting it.  Before projection, an arbitrary dual orbit
field can restore the entire spectrum.

This paper does not assume that this coupling is smooth.  It applies a
bounded projection to the coupling itself.  The physical orbit
coordinate is embedded by zero extension into \(\ell^2(\Z)\).  In every
fixed opposite-row and residual-label fiber, we retain the full
residue-comb Fourier band
\begin{equation}
 \cB_\Omega^{(H_0)}
 :=\{\beta\in\T:
 \operatorname{dist}(\beta,H_0^{-1}\Z)\le\Omega\}.
 \label{eq:tpc47-low-orbit-band}
\end{equation}
This defines one canonical sector of the actual output Hilbert space;
it is not the choice of one term in a signed projective expansion.  The
source mask, the M\"obius cofactor, and the residual label remain
literal.

\subsection{The positive theorem}

The abstract kernel underlying the result is transparent.  Let
\(M_-\le m\le M_+\), let \(H_0\) be fixed, and consider one layer
\begin{equation}
 F_h=\sum_{p,r,m}\sum_{\substack{j\in\Z\\j\equiv a\!\!\pmod{H_0}}}
 A_{p,r,m}\phi(j/J)v_{p,r,m}\otimes e_j
 \one_{pr-mj=h},
 \label{eq:tpc47-intro-layer}
\end{equation}
where \(v_{p,r,m}\) is independent of \(j\).  If
\(\operatorname{supp}\widehat\phi\subset[-\Sigma,\Sigma]\), then
the orbit Fourier variable \(\beta\) changes the Poisson kernel from
\(m\alpha\) to \(m\alpha-\beta\).  The exact nonresonance interval is
therefore
\begin{equation}
 \boxed{
 \frac{\Omega+\Sigma/J}{M_-}
 <\|\alpha\|_{\T}<
 \frac{H_0^{-1}-\Omega-\Sigma/J}{M_+}.}
 \label{eq:tpc47-intro-gap}
\end{equation}
On this interval the shift Fourier transform of
\(\Pi_\Omega F\) vanishes identically.  The statement is vector valued,
uses no cancellation in \(p,r,m\), and is uniform over their
coefficients.

The actual orbit profiles are smooth rather than band limited.  We use
a fixed smooth cutoff in continuous Fourier space,
\begin{equation}
 \phi=\phi_{\le\Sigma}+\phi_{>\Sigma},
 \qquad
 \operatorname{supp}\widehat{\phi_{\le\Sigma}}
 \subset[-\Sigma,\Sigma].
 \label{eq:tpc47-intro-lowpass}
\end{equation}
Every Schwartz seminorm of the remainder is smaller than an arbitrary
negative power of \(\Sigma\), provided a sufficiently high but fixed
orbit seminorm of \(\phi\) is used.  TPC--36 controls the total signed
projective mass with every fixed orbit seminorm.  Hence the tails in
\eqref{eq:tpc47-intro-lowpass} can be summed over the \emph{entire}
actual projective representation.  No layer is selected and no
arithmetic coefficient is smoothed.

At the endpoint
\begin{equation}
 M_\pm=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},
 \label{eq:tpc47-intro-endpoint-scales}
\end{equation}
take
\begin{equation}
 \Omega=X^{1/400+o(1)}/J,
 \qquad \Sigma=X^{1/400+o(1)}.
 \label{eq:tpc47-intro-endpoint-bands}
\end{equation}
After a harmless \(X^\epsilon\) shrink at both ends,
\eqref{eq:tpc47-intro-gap} becomes
\begin{equation}
 \boxed{
 X^{-399/400+\epsilon}
 \le\|\alpha\|_{\T}\le
 X^{-267/400-\epsilon}.}
 \label{eq:tpc47-intro-endpoint-gap}
\end{equation}
The projected frozen shift family built from the literal physical
\(h_0\)-coefficient field has leakage \(O_{A,\epsilon}(X^{-A})\) on this
interval relative to any of the declared polynomial coefficient
envelopes.  Thus the orbit-frequency
gate is crossed on a growing sector whose time--bandwidth size is the
same \(X^{1/400+o(1)}\) scale as the endpoint TPC allowance.

\subsection{What the projection does and does not retain}

On one fixed opposite-row and residual-label fiber, let \(E_I\)
restrict the orbit coordinate to a physical interval of
\(N\asymp J\) integers.  The band projection satisfies
\begin{equation}
 \|\Pi_\Omega\|=1,
 \qquad
 \|\Pi_\Omega E_I\|_{\mathrm{HS}}^2
 =\operatorname{tr}(E_I^*\Pi_\Omega E_I)=2H_0N\Omega.
 \label{eq:tpc47-intro-shannon-number}
\end{equation}
Thus \(2H_0N\Omega\asymp X^{1/400+o(1)}\) is an exact trace identity,
not an informal count of Fourier modes.  Moreover, a nonzero
finite-orbit vector cannot have zero projection onto an open frequency
band: its Fourier transform is a nonzero trigonometric polynomial.
The projected sector is therefore genuinely nonempty whenever the
physical residual packet is nonzero.

There is nevertheless no useful uniform lower bound for the retained
mass.  Explicit finite-difference vectors \(y_n\), supported inside a
physical orbit window, satisfy
\begin{equation}
 \frac{\|\Pi_\Omega y_n\|_2}{\|y_n\|_2}
 \ll n^{1/4}\Omega^{1/2}(C_{H_0}\Omega)^n.
 \label{eq:tpc47-intro-small-mass}
\end{equation}
Consequently, the theorem controls a canonical actual-residual-output
sector but
does not control the orthogonal complement or the norm of the full
equality column.  This is a sharp distinction between a spectral
transfer theorem and a fixed-shift TPC estimate.

\subsection{Claim ledger}

The results are organized as follows.
\begin{enumerate}[leftmargin=2.2em]
 \item \Cref{sec:tpc47-interface} identifies the physical large-prime
       packet and its frozen-coefficient shift extension.
 \item \Cref{sec:tpc47-projector} constructs the literal fiberwise
       orbit projector, proves its exact trace, and records the
       commuting residual structure.
 \item \Cref{sec:tpc47-exact-transfer} proves
       \eqref{eq:tpc47-intro-gap}, including the fixed progression.
 \item \Cref{sec:tpc47-smooth-transfer} gives the low-pass/tail
       decomposition and quantitative leakage bounds.
 \item \Cref{sec:tpc47-actual-reassembly} transfers those bounds to the
       full actual source--mask coefficient packet.
 \item \Cref{sec:tpc47-endpoint} proves the rational endpoint ledger.
 \item \Cref{sec:tpc47-mass-frontier} proves nonvanishing but disproves
       a uniform retained-mass fraction.
 \item \Cref{sec:tpc47-boundaries} separates the remaining gates, and
       \cref{sec:tpc47-certificate} records the exact finite
       certificate and claim boundary.
\end{enumerate}

Only the column \(h=h_0\) in the frozen family is the inherited
physical equality column.  The other shifts keep its coefficient field
fixed in order to expose the spectrum.  We do not identify them with
TPC packets reconstructed at new physical shifts.  We also do not
deduce atomic normalization, alias unfolding, a deterministic
fixed-shift M\"obius estimate, a parity breach, or a prime-pair
asymptotic.
