\section{The retained-mass frontier}
\label{sec:tpc47-mass-frontier}

The projected sector is not the zero subspace on a physical orbit
window.  Nevertheless, the projector can retain an arbitrarily small
fraction of an ambient finite-orbit vector.  No such smallness is
asserted for the actual arithmetic packet.  Both operator-theoretic
statements are exact.

\subsection{Qualitative injectivity on every finite window}

\begin{theorem}[Finite-support injectivity]
\label{thm:tpc47-finite-support-injectivity}
Let \(0<\Omega<1/(2H_0)\).  If
\(y\in\Vv\widehat\otimes\ell^2(\Z)\) is finitely supported in the
orbit coordinate, then
\begin{equation}
 \Pi_{\Omega}^{(H_0)}y=0
 \quad\Longrightarrow\quad y=0.
 \label{eq:tpc47-finite-injectivity}
\end{equation}
Equivalently, for every finite interval \(I\), the compression
\begin{equation}
 E_I^*\Pi_{\Omega}^{(H_0)}E_I
 \label{eq:tpc47-positive-compression}
\end{equation}
is strictly positive definite.
\end{theorem}

\begin{proof}
Pair \(y\) with an arbitrary vector in \(\Vv\).  Its orbit Fourier
transform is a Laurent polynomial in \(z=\e(-\beta)\).  If the
projection is zero, this polynomial vanishes almost everywhere on every
open arc in \(\cB_{\Omega}^{(H_0)}\), hence identically.  Every scalar
pairing is zero, so all coefficients of \(y\) vanish.  Applying this to
\(E_Iy\) proves strict positivity of the compression.
\end{proof}

Thus a nonzero finitely supported residual packet always has a nonzero
projected component.  This is only a qualitative statement; the
smallest eigenvalue of \eqref{eq:tpc47-positive-compression} is not
bounded below uniformly in the window length.

\subsection{An exponentially thin finite-support family}

Let \(S\) be the unit shift on \(\ell^2(\Z)\),
\((Sy)_j=y_{j-H_0}\), and for \(n\ge1\) put
\begin{equation}
 f_n:=(I-S)^n e_0
 =\sum_{k=0}^n(-1)^k\binom nk e_{kH_0}.
 \label{eq:tpc47-difference-witness}
\end{equation}
Then
\begin{align}
 (\mathscr F_jf_n)(\beta)
 &=\bigl(1-\e(-H_0\beta)\bigr)^n,
 \label{eq:tpc47-difference-transform}\\
 \|f_n\|_2^2&=\binom{2n}{n}.
 \label{eq:tpc47-difference-norm}
\end{align}

\begin{theorem}[No uniform retained-mass bound]
\label{thm:tpc47-no-mass-lower-bound}
There is an absolute constant \(C\) such that, whenever
\(\pi H_0\Omega<1\),
\begin{equation}
 0<
 \frac{\|\Pi_{\Omega}^{(H_0)}f_n\|_2}{\|f_n\|_2}
 \le
 C n^{1/4}(H_0\Omega)^{1/2}
 (\pi H_0\Omega)^n.
 \label{eq:tpc47-thin-sector-bound}
\end{equation}
The support of \(f_n\) lies in an interval of length \(nH_0+1\), so
it may be translated into any physical orbit window of at least that
length.
\end{theorem}

\begin{proof}
Write \(\beta=\tau/H_0+u\) on one component of the comb, with
\(|u|\le\Omega\).  Then
\begin{equation}
 |1-\e(-H_0\beta)|
 =2|\sin(\pi H_0u)|
 \le2\pi H_0\Omega.
 \label{eq:tpc47-comb-witness-bound}
\end{equation}
There are \(H_0\) components, with total measure \(2H_0\Omega\).
Hence
\begin{equation}
 \|\Pi_{\Omega}^{(H_0)}f_n\|_2^2
 \le2H_0\Omega(2\pi H_0\Omega)^{2n}.
 \label{eq:tpc47-projected-witness-energy}
\end{equation}
The elementary central-binomial estimate
\begin{equation}
 \binom{2n}{n}\ge\frac{4^n}{2\sqrt n}
 \label{eq:tpc47-central-binomial-bound}
\end{equation}
and \eqref{eq:tpc47-difference-norm} now give
\eqref{eq:tpc47-thin-sector-bound}, after changing an absolute
constant.  Strict positivity follows from
\cref{thm:tpc47-finite-support-injectivity}.
\end{proof}

At the endpoint \(\Omega=X^{\kappa-\nu+o(1)}\), for any proposed
fixed power \(C_0\), choosing one fixed \(n\) large enough makes the
ratio in \eqref{eq:tpc47-thin-sector-bound} smaller than \(X^{-C_0}\)
for all large \(X\).  Thus there is no uniform polynomial inverse
\begin{equation}
 \|y\|_2\le X^{C_0}
 \|\Pi_{\Omega}^{(H_0)}y\|_2
 \label{eq:tpc47-forbidden-polynomial-inverse}
\end{equation}
on orbit windows of length \(J\).

\subsection{Consequences for the TPC gate}

The two theorems above establish the exact logical status of the
sector:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item it is nonzero on every nonzero finite-orbit vector, hence is not
       vacuous if the finite physical residual packet is nonzero;
 \item on ambient finite-orbit vectors it need not retain a fixed,
       logarithmic, or even polynomially bounded fraction of the norm;
       no corresponding smallness is asserted for the actual arithmetic
       packet; and
 \item the trace identity \eqref{eq:tpc47-time-bandwidth-trace} is an
       average spectral-size statement, not a lower bound for one
       arithmetic vector.
\end{enumerate}

There is also no coordinatewise domination.  For example,
\(\Pi_{\Omega}^{(H_0)}e_0\) is the sinc-comb sequence
\eqref{eq:tpc47-comb-sinc-kernel}; it has nonzero coordinates away from
zero although \(e_0\) does not.  Only the global Hilbert contraction
\begin{equation}
 \|\Pi_{\Omega}^{(H_0)}y\|_2\le\|y\|_2
 \label{eq:tpc47-global-contraction}
\end{equation}
is automatic.

\begin{remark}[Why arbitrary dual fields restore the obstruction]
\label{rem:tpc47-arbitrary-dual-field}
Before projection, modulation by \(\e(mj\alpha)\) is unitary in the
orbit coordinate.  An arbitrary dual vector may be oppositely
modulated to place its mass at any prescribed shift frequency.  The
full output unit ball therefore has no uniform gap derived solely from
smoothness of the source mask.  The theorem succeeds precisely because
it states and retains the orbit-band restriction.
\end{remark}
