\section{The inherited physical-coefficient sector}
\label{sec:tpc47-interface}

We record the exact object to which the orbit projection is applied.
The purpose is to prevent a low-frequency statement about a model
coefficient from being substituted for the actual source--mask field.

\subsection{The physical equality column}

Fix \(h_0\in\Z\setminus\{0\}\), and put \(H_0=|h_0|\).  A source row
is \(\rho=(\ell_\rho,d_\rho)\), with
\begin{equation}
 m_\rho=\ell_\rho d_\rho\asymp Q,
 \qquad
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)}.
 \label{eq:tpc47-row-scales}
\end{equation}
Let \(M_-\) and \(M_+\) be the minimum and maximum source integers on
the inherited dyadic row cell.  Thus
\begin{equation}
 0<M_-\le m_\rho\le M_+,
 \qquad
 M_-=X^{267/400+o(1)},
 \qquad
 M_+=X^{267/400+o(1)}.
 \label{eq:tpc47-physical-M-bounds}
\end{equation}
The prime \(\ell_\rho\) and squarefree \(d_\rho\) are uniquely
determined by \(m_\rho\) on the inherited row support.  Let
\(\cO_L\) and \(\cO_R\) be the opposite-row sets for the left and
right columns.  We treat the left column; every assertion has the
symmetric right-column form.

On one terminal block \(n\asymp X\), take the large-prime band
\begin{equation}
 \cP_{R_0}^{\sharp}
 =\left\{p\in\Pp:\sqrt{N_+}<p\le N_-/R_0\right\}.
 \label{eq:tpc47-large-prime-band}
\end{equation}
Writing \(n=pr\), TPC--45 proves that \(p\) is unique, that
\(R_0\le r<\sqrt{N_+}\), and that the physical residual label is
\begin{equation}
 s=d_\rho r.
 \label{eq:tpc47-residual-label}
\end{equation}
After zero atoms are removed, \(d_\rho,r,s\) are squarefree on the
equality column and \(\mu(s)=\mu(d_\rho)\mu(r)\)
\citep{WangTPC43,WangTPC45,WangTPC46}.

Let \(\gamma_\rho^{(1)}\) be the physical source coefficient,
\(\mathfrak A_{\rho,\gamma}^{\rm act}(j)\) the actual joint
source--mask multiplier, and
\begin{equation}
 \Lambda(n)=(\log n)\Phi_0(n/X).
 \label{eq:tpc47-terminal-weight}
\end{equation}
The left large-prime equality residual synthesis is
\begin{equation}
 \cF_{h_0}^{\rm act,L}
 =\sum_{\substack{\gamma\in\cO_L,\ j\in\Z,
                   \rho,\ p\in\cP_{R_0}^{\sharp},\ r\\
                   pr-m_\rho j=h_0}}
 \gamma_\rho^{(1)}
 \mathfrak A_{\rho,\gamma}^{\rm act}(j)
 \mu(r)\Lambda(pr)\,
 e_{\gamma,d_\rho r}\otimes e_j.
 \label{eq:tpc47-physical-vector}
\end{equation}
Every coefficient is set to zero off the inherited terminal and orbit
support.  Thus \eqref{eq:tpc47-physical-vector} is finitely supported
in \(j\), even though we have embedded it in \(\ell^2(\Z)\).
At \(h_0\) this vector is the negative of the TPC--45/46 synthesis,
\(-\sum_pUx_p\).  It contains literal actual atoms and coefficients,
but it belongs to the low-sign-averaged residual Gram route rather than
the native affine physical Gram face; the two cross-inner-product
structures need not agree.

Define
\begin{equation}
 \Vv_L:=\ell^2(\cO_L\times\cS),
 \qquad
 \Hh_L:=\Vv_L\widehat\otimes\ell^2(\Z),
 \label{eq:tpc47-output-Hilbert-space}
\end{equation}
where \(\cS\) contains the supported residual labels.  The right
space is defined symmetrically, and the full output is their orthogonal
sum.

\subsection{The frozen-coefficient shift family}

For \(h\in\Z\), define \(\cF_h^{\rm fr,L}\) by the right side of
\eqref{eq:tpc47-physical-vector} with the determinant equation replaced
by
\begin{equation}
 pr-m_\rho j=h,
 \label{eq:tpc47-frozen-determinant}
\end{equation}
while every row, support, residue factor, source coefficient, mask
coefficient, and residual label remains the one constructed for
\(h_0\).  Then
\begin{equation}
 \cF_{h_0}^{\rm fr,L}=\cF_{h_0}^{\rm act,L}.
 \label{eq:tpc47-frozen-physical-agreement}
\end{equation}
The family belongs to \(\ell^1(\Z;\Hh_L)\cap
\ell^2(\Z;\Hh_L)\), and its shift transform is
\begin{equation}
 \widehat{\cF}^{\rm fr,L}(\alpha)
 :=\sum_{h\in\Z}\cF_h^{\rm fr,L}\e(-h\alpha).
 \label{eq:tpc47-frozen-shift-transform}
\end{equation}

\begin{remark}[No local-shift provenance]
\label{rem:tpc47-no-local-provenance}
For \(h\ne h_0\), \(\cF_h^{\rm fr,L}\) is an algebraic extension of
one physical coefficient field.  Reconstructing TPC at physical shift
\(h\) would change eligible rows, residue data, the joint multiplier,
and possibly the residual label.  No uniform identification of those
objects is used or claimed.
\end{remark}

\subsection{Exact projective layers of the full coefficient}

TPC--36 proves the pointwise actual-multiplier representation, and
TPC--46 inserts the large-prime and Mellin separations.  Their combined
interface gives the following statement
\citep{WangTPC36,WangTPC46}.

\begin{proposition}[Inherited actual-coefficient reassembly]
\label{prop:tpc47-inherited-reassembly}
For each fixed integer \(B\ge0\), the full frozen left family is a
Bochner signed superposition of layers
\begin{equation}
 \cF_h^\omega
 =\sum_{p,r,m}\sum_{\substack{j\in\Z\\
                      j\equiv a_\omega\!\!\pmod{H_0}}}
 A_\omega(p,r,m)\phi_\omega(j/J)
 v_{\omega,p,r,m}\otimes e_j\,
 \one_{pr-mj=h},
 \label{eq:tpc47-projective-layer}
\end{equation}
where
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item the prime restriction and terminal Mellin factor are retained in
       \(A_\omega\);
 \item \(\mu(r)\) is retained in \(A_\omega\), while the literal
       source and mask coefficient is retained in its \(m\)-factor;
 \item \(v_{\omega,p,r,m}\in\Vv_L\) is independent of \(j\) and is
       supported on coordinates \((\gamma,d(m)r)\); and
 \item after multiplication by one common fixed compactly supported
       cutoff that equals one on the physical normalized orbit range,
       \(\phi_\omega\in C_c^\infty(\R)\), with
       \begin{equation}
       \int \mathfrak a_\omega
       \|\phi_\omega\|_{C^B}\,d|\nu|(\omega)
       \ll_{B,h_0}X^{o(1)}.
       \label{eq:tpc47-projective-seminorm-mass}
       \end{equation}
\end{enumerate}
Here \(\mathfrak a_\omega\) is the product of the declared sup-norm
weights in the arithmetic and opposite-row factors.  More strongly,
the construction is coefficientwise before the terminal sum: for every
supported \(m,r\),
\begin{align}
 &\sum_{\gamma\in\cO_L}
 \gamma_m^{(1)}\mathfrak A_{m,\gamma}^{\rm act}(j)
 e_{\gamma,d(m)r}
 \notag\\
 &\quad={}
 \sum_{a\bmod H_0}\one_{j\equiv a\!\!\pmod{H_0}}
 \int c_{\omega,a}(m)\phi_{\omega,a}(j/J)
 q_{\omega,a}^{m,r}\,d\nu_a(\omega),
 \label{eq:tpc47-coefficientwise-reassembly}
\end{align}
where
\begin{equation}
 q_{\omega,a}^{m,r}
 =\sum_{\gamma\in\cO_L}q_{\omega,a}(\gamma)
 e_{\gamma,d(m)r},
 \label{eq:tpc47-coefficientwise-output-vector}
\end{equation}
and the integral of
\(\|c_{\omega,a}\|_\infty
  \|q_{\omega,a}\|_\infty
  \|\phi_{\omega,a}\|_{C^B}\)
is \(X^{o(1)}\).  In particular,
\begin{equation}
 \cF_h^{\rm fr,L}=\int\cF_h^\omega\,d\nu(\omega)
 \label{eq:tpc47-full-layer-integral}
\end{equation}
exactly, with total signed projective mass \(X^{o(1)}\) at every fixed
orbit differentiability order.
\end{proposition}

\begin{proof}
The global row-mask theorem of TPC--36 separates the source row, the
opposite row, and a smooth orbit profile after splitting the fixed
residue cells.  Its fixed-column refinement may additionally split
\(m=\ell d\), but no such split is needed here.  Multiplication by the
source coefficient preserves \(X^{o(1)}\) projective mass.  Mellin
inversion separates \(\Lambda(pr)\), while the large-prime descent
inserts \(\mu(r)\) and the literal residual coordinate \(d(m)r\).
Grouping the opposite-row factor into \(v_{\omega,p,r,m}\) gives
\eqref{eq:tpc47-projective-layer}.  The inherited orbit factors are
smooth on a fixed normalized interval.  A common cutoff equal to one
there makes them compactly supported without changing a physical
coefficient and preserves every fixed seminorm estimate.  These are
exactly the claims in \eqref{eq:tpc47-projective-seminorm-mass} and
\eqref{eq:tpc47-coefficientwise-reassembly}.  Multiplication by the
terminal factors and summation over \((p,r,m)\) then gives
\eqref{eq:tpc47-full-layer-integral}.
\end{proof}

The signed integral in \eqref{eq:tpc47-full-layer-integral} must remain
intact.  Selecting a favorable \(\omega\) would not define a bounded
projection of the physical multiplier.  The orbit projection below is
instead a single orthogonal operator applied after the complete sum has
been reassembled.
