\begin{abstract}
TPC--63 separates a literal full incidence from its pair projection and
shows that a labeled multiscale completion is an isometry only after the
completed incidence has been chosen.  It leaves open a prior arrow: does a
pair-populated or multiscale repair preserve the true pre-terminal parent,
and what terminal lower constant remains after any added parent mass is
charged?

We answer that finite-scale representation question at one fixed nonzero
shift.  On blockwise full incidences we define the literal parent mass
\(P_m\), terminal-support mass \(H_m\), and shaped terminal energy
\(T_m\).  The least parent-complete pair relation is the projection of the
literal pre-terminal active incidence.  Such a relation is also
terminal-atomically faithful if and only if its terminal-active rectangle
 equals the literal terminal incidence.  When the test fails no
 parent-complete terminal-faithful pair-rectangular lift exists, and our
 canonical fallback retains the literal active hypergraph; when it passes,
 the exact excess parent mass is \(\Delta_m\).  This yields a canonical
 hybrid repair and
\[
 \widetilde P_m=P_m+\Delta_m,
 \qquad
 \mathfrak I_X=
 \begin{cases}
  +\infty,&\exists m:\ P_m=0<\widetilde P_m,\\
  \displaystyle\max_{m:P_m>0}\frac{\widetilde P_m}{P_m},
      &\text{otherwise},
 \end{cases}
\]
for a nonzero literal parent.  The
literal-active-hypergraph baseline has exactly zero parent inflation.  A logarithmic
number of block labels does not control \(\mathfrak I_X\): arbitrary
polynomial inflation can occur in one block.

True terminal activation factors, on positive rows, as
\[
 \frac{T_m}{\widetilde P_m}
 =\frac{H_m}{P_m}\,
  \frac{T_m}{H_m}\,
  \frac{P_m}{\widetilde P_m}.
\]
We give zero-safe conventions, sharp uniform row minima, exact
distinguished weighted averages, and the optimal transfer
\(\tau_{\rm rep}\ge\tau_{\rm hyp}/\mathfrak I_X\).  For a coefficient
vector satisfying a cap and an occupied-capacity lower bound, the threshold
data \(g_m=T_m/\widetilde P_m\ge\eta\) on a repaired-parent fraction
\(\delta_\eta\) give the sharp certificate
\[
 \frac{T(z)}{\widetilde P(z)}
 \ge
 \eta\left(1-\frac{1-\delta_\eta}{\kappa_X}\right)_+.
\]
The certified right-hand side is positive exactly when
\(\kappa_X>1-\delta_\eta\).

Finally, we state a denominator-compatible chain and charge parent inflation
once inside the effective terminal loss before applying the strict
\(1/400\) endpoint test.  No favorable bound for \(T_m/P_m\),
\(\delta_\eta\), \(\kappa_X\), physical label erasure, or a signed
fixed-shift kernel is proved.  The result is an L0/L1 activation-interface
theorem, not a parity estimate, a prime-pair lower bound, or a twin-prime
result.
\end{abstract}
