\section{True terminal activation and its three exact factors}
\label{sec:tpc64-activation-factorization}

We now compare the shaped terminal energy with the repaired parent, not
with a terminal-active parent chosen after the fact.  The distinction
produces three factors: literal support alignment, literal multiplier
intensity, and inverse parent inflation.  Only the first and third are
proportions.

\subsection{Zero-safe row factors}

Continue with \(P_m,H_m,T_m,\Delta_m,\widetilde P_m\) from
\cref{sec:tpc64-inflation-laws}.  The finite incidence definitions imply
\begin{equation}
 H_m=0\quad\Longrightarrow\quad T_m=0,
 \qquad
 P_m=0\quad\Longrightarrow\quad H_m=T_m=0.
 \label{eq:tpc64-zero-propagation}
\end{equation}
Define the support-alignment, multiplier-intensity, inverse-inflation, and
repaired-activation factors by
\begin{align}
 \alpha_m
 &:=
 \begin{cases}
  H_m/P_m,&P_m>0,\\
  0,&P_m=0,
 \end{cases}
 \label{eq:tpc64-support-alignment-factor}\\
 \vartheta_m
 &:=
 \begin{cases}
  T_m/H_m,&H_m>0,\\
  0,&H_m=0,
 \end{cases}
 \label{eq:tpc64-multiplier-intensity-factor}\\
 \rho_m
 &:=
 \begin{cases}
  P_m/\widetilde P_m,&\widetilde P_m>0,\\
  1,&\widetilde P_m=0,
 \end{cases}
 \label{eq:tpc64-inverse-inflation-factor}\\
 g_m
 &:=
 \begin{cases}
  T_m/\widetilde P_m,&\widetilde P_m>0,\\
  0,&\widetilde P_m=0.
 \end{cases}
 \label{eq:tpc64-repaired-row-activation}
\end{align}
With \(1/(+\infty):=0\), the row conventions give
\(\rho_m=\iota_m^{-1}\) on every row.  Thus
\(0\le\alpha_m,\rho_m\le1\), but there is no upper bound \(1\) on
\(\vartheta_m\).  Indeed, when \(H_m>0\),
\begin{equation}
 \vartheta_m
 =
 \sum_{k\in K_X}
 \sum_{\substack{u\in\mathcal U_{X,h,k}^{+}\\m(u)=m}}
 \frac{|c_u|^2}{H_m}\,|t_h(u)|^2.
 \label{eq:tpc64-intensity-weighted-average}
\end{equation}
It is a weighted average of squared literal multiplier magnitudes, not a
probability of terminal survival.  In particular, shaped logarithmic or
profile weights can make it larger than one.
On a row with a zero denominator, the displayed zero values are
bookkeeping conventions chosen to make the universal product identity
below valid.  They are not conditional probabilities and do not assign a
physical multiplier intensity to an empty support.

\begin{theorem}[Exact three-factor activation law]
\label{thm:tpc64-exact-three-factor-activation}
On every row for which all three raw denominators are positive,
\begin{equation}
 \boxed{
 \frac{T_m}{\widetilde P_m}
 =
 \frac{H_m}{P_m}\,
 \frac{T_m}{H_m}\,
 \frac{P_m}{\widetilde P_m}.}
 \label{eq:tpc64-three-raw-fractions}
\end{equation}
With the zero conventions
\eqref{eq:tpc64-support-alignment-factor}--
\eqref{eq:tpc64-repaired-row-activation}, the universal statement is
\begin{equation}
 \boxed{g_m=\alpha_m\vartheta_m\rho_m}
 \qquad(m\in\mathcal M_X).
 \label{eq:tpc64-three-factor-activation}
\end{equation}
More explicitly:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item if \(P_m,H_m,\widetilde P_m>0\), then
       \eqref{eq:tpc64-three-raw-fractions} holds by cancellation;
 \item if \(P_m>0\) but \(H_m=0\), then \(T_m=g_m=0\);
 \item if \(P_m=0<\widetilde P_m\), then the row is new-only,
       \(H_m=T_m=0\), and \(g_m=\rho_m=0\);
 \item if \(\widetilde P_m=0\), then all four row masses vanish,
       \(g_m=0\), and the harmless convention \(\rho_m=1\) agrees with
       the reciprocal of \(\iota_m=1\); the row contributes to no
       quadratic form.
\end{enumerate}
\end{theorem}

\begin{proof}
The regular identity is obtained by inserting \(H_m\) and \(P_m\) between
the numerator and denominator.  The remaining cases follow from
\eqref{eq:tpc64-zero-propagation} and
\(0\le P_m\le\widetilde P_m\).
\end{proof}

The factorization separates three logically independent tasks.
Parent-to-terminal support alignment controls \(\alpha_m\), the literal
shaped coefficient controls \(\vartheta_m\), and the chosen repair controls
\(\rho_m\).  Completing a relation can improve neither of the first two
factors, while a terminal-faithful rectangle can strictly reduce the third.

\subsection{Uniform and distinguished activation}

Define the literal-hypergraph and repaired-parent uniform constants by
\begin{align}
 \tau_{\mathrm{hyp}}
 &:=
 \inf_{\substack{z\in Z_X\\P(z)>0}}
       \frac{T(z)}{P(z)},
 \label{eq:tpc64-hypergraph-uniform-activation}\\
 \tau_{\mathrm{rep}}
 &:=
 \inf_{\substack{z\in Z_X\\\widetilde P(z)>0}}
       \frac{T(z)}{\widetilde P(z)}.
 \label{eq:tpc64-repaired-uniform-activation}
\end{align}
These are full-row constants.  They are not statements about one
distinguished physical vector.

\begin{theorem}[Sharp uniform row minima]
\label{thm:tpc64-uniform-activation-minima}
On the full row-coefficient space,
\begin{align}
 \boxed{
 \tau_{\mathrm{hyp}}
 =\min_{m:P_m>0}\frac{T_m}{P_m}
 =\min_{m:P_m>0}\alpha_m\vartheta_m,}
 \label{eq:tpc64-hypergraph-row-minimum}\\
 \boxed{
 \tau_{\mathrm{rep}}
 =\min_{m:\widetilde P_m>0}\frac{T_m}{\widetilde P_m}
 =\min_{m:\widetilde P_m>0}
       \alpha_m\vartheta_m\rho_m.}
 \label{eq:tpc64-repaired-row-minimum}
\end{align}
In particular, one new-only parent row forces
\(\tau_{\mathrm{rep}}=0\), and one literal row with
\(P_m>0=T_m\) forces both uniform constants to vanish.
\end{theorem}

\begin{proof}
For \(P(z)>0\),
\[
 \frac{T(z)}{P(z)}
 =
 \sum_{m:P_m>0}
 \frac{P_m|z_m|^2}{P(z)}\,\frac{T_m}{P_m}.
\]
This is a convex combination of the active literal row ratios.  A
minimizing row basis vector attains the minimum.  The same argument with
\(\widetilde P_m\) proves
\eqref{eq:tpc64-repaired-row-minimum}.  The two zero-row conclusions follow
from \eqref{eq:tpc64-zero-propagation}.
\end{proof}

For a fixed distinguished vector \(z_*\) satisfying
\(\widetilde P(z_*)>0\), put
\begin{equation}
 \tau_{\mathrm{rep},*}(X)
 :=\frac{T(z_*)}{\widetilde P(z_*)}.
 \label{eq:tpc64-distinguished-repaired-activation}
\end{equation}

\begin{theorem}[Exact distinguished weighted average]
\label{thm:tpc64-distinguished-activation-average}
The distinguished repaired activation is exactly
\begin{equation}
 \boxed{
 \tau_{\mathrm{rep},*}(X)
 =
 \sum_{m:\widetilde P_m>0}
 \frac{\widetilde P_m|z_{*,m}|^2}
      {\widetilde P(z_*)}\,
 g_m.}
 \label{eq:tpc64-distinguished-activation-average}
\end{equation}
The displayed coefficients are nonnegative and sum to one.  If also
\(P(z_*)>0\), then
\begin{equation}
 \tau_{\mathrm{hyp},*}(X)
 :=\frac{T(z_*)}{P(z_*)}
 =
 \sum_{m:P_m>0}
 \frac{P_m|z_{*,m}|^2}{P(z_*)}\,
 \alpha_m\vartheta_m.
 \label{eq:tpc64-distinguished-hypergraph-average}
\end{equation}
Neither distinguished identity implies the corresponding row minimum:
a distinguished vector may avoid a bad row, whereas a full-row statement
must test it.
\end{theorem}

\begin{proof}
Insert the definitions of \(T(z_*)\), \(\widetilde P(z_*)\), and \(g_m\).
The second formula is identical with \(P_m\) in place of
\(\widetilde P_m\).
\end{proof}

\subsection{Sharp transfer through parent inflation}

\begin{theorem}[Inflation-corrected activation transfer]
\label{thm:tpc64-inflation-corrected-activation}
Assume \(\mathfrak I_X<\infty\).  For every \(z\) with \(P(z)>0\),
\begin{equation}
 \boxed{
 \frac{T(z)}{\widetilde P(z)}
 \ge
 \frac1{\mathfrak I_X}\,
 \frac{T(z)}{P(z)}.}
 \label{eq:tpc64-pointwise-inflation-transfer}
\end{equation}
Consequently,
\begin{equation}
 \boxed{
 \tau_{\mathrm{rep}}
 \ge\frac{\tau_{\mathrm{hyp}}}{\mathfrak I_X}.}
 \label{eq:tpc64-uniform-inflation-transfer}
\end{equation}
For every \(a>0\) and \(L\ge1\), a one-row terminal-faithful model attains
simultaneously
\begin{equation}
 \tau_{\mathrm{hyp}}=a,\qquad
 \mathfrak I_X=L,\qquad
 \tau_{\mathrm{rep}}=\frac aL.
 \label{eq:tpc64-inflation-transfer-sharp-model}
\end{equation}
Thus the factor \(\mathfrak I_X^{-1}\) is sharp.
\end{theorem}

\begin{proof}
By \cref{thm:tpc64-exact-parent-inflation},
\(\widetilde P(z)\le\mathfrak I_XP(z)\).  A finite inflation constant
excludes new-only rows, so \(\widetilde P(z)>0\) if and only if
\(P(z)>0\), up to common zero rows.  Multiplying the parent domination by
the nonnegative number \(T(z)/(P(z)\widetilde P(z))\) proves
\eqref{eq:tpc64-pointwise-inflation-transfer}.  Taking the infimum and
using \eqref{eq:tpc64-hypergraph-uniform-activation} gives
\eqref{eq:tpc64-uniform-inflation-transfer}.

For sharpness, take one literal terminal-active atom with
\(|c|^2=1\) and \(|t_h|^2=a\), and add terminal-null parent mass \(L-1\).
Then
\[
 P_m=H_m=1,\qquad T_m=a,\qquad
 \widetilde P_m=L,
\]
which gives \eqref{eq:tpc64-inflation-transfer-sharp-model}.
\end{proof}

If \(\mathfrak I_X=+\infty\), there is no coefficient-uniform comparison
from the literal parent to the repaired parent.  Writing
\(\mathfrak I_X^{-1}=0\) makes
\eqref{eq:tpc64-uniform-inflation-transfer} formally true but
quantitatively empty; it is not an activation theorem.

The results of this section are exact finite-dimensional identities.  They
do not prove that \(\alpha_m\), \(\vartheta_m\), \(g_m\), or either
activation constant has a favorable lower bound on the physical carrier.
In particular, they contain no signed parity estimate and no prime-pair
consequence.
