\section{A sharp threshold-capacity certificate}
\label{sec:tpc64-capacity-certificate}

The rowwise minimax is the correct answer for a homogeneous
full-coefficient theorem.  A different exact certificate is available for
one coefficient vector, or for a declared class on which a quantitative
capacity lower bound is known.  This section gives that certificate with
its quantifiers exposed.

\subsection{Good rows and occupied repaired-parent capacity}

Use the repaired row masses \(\widetilde P_m\) and the unchanged terminal
masses \(T_m\).  Delete rows with
\(\widetilde P_m=0\), and assume that the remaining set
\begin{equation}
 \mathcal M_X^+
 :=\{m:\widetilde P_m>0\}
 \label{eq:tpc64-capacity-active-rows}
\end{equation}
is nonempty.  Put
\begin{equation}
 \widetilde W_X:=\sum_{m\in\mathcal M_X^+}\widetilde P_m
 \label{eq:tpc64-total-parent-capacity}
\end{equation}
and define the exact repaired-parent row activation
\begin{equation}
 g_m:=\frac{T_m}{\widetilde P_m}\ge0
 \qquad(m\in\mathcal M_X^+).
 \label{eq:tpc64-row-gain}
\end{equation}
There is no assertion that \(g_m\le1\): the literal shaped terminal
multiplier remains inside \(T_m\).

For a threshold \(\eta>0\), define
\begin{align}
 \mathcal G_\eta
 &:=\{m\in\mathcal M_X^+:g_m\ge\eta\},
 \label{eq:tpc64-threshold-good-rows}\\
 \delta_\eta
 &:=\frac{\sum_{m\in\mathcal G_\eta}\widetilde P_m}
              {\widetilde W_X}
 \in[0,1].
 \label{eq:tpc64-threshold-capacity-fraction}
\end{align}
Thus \(\delta_\eta\) is a structural fraction measured in the exact
repaired-parent denominator.  It is not the unweighted density of good
rows and is not an actual-coefficient energy fraction.

Let \(C_X>0\) be a declared coefficient bound and let \(z\) satisfy
\begin{equation}
 |z_m|\le C_X\qquad(m\in\mathcal M_X^+).
 \label{eq:tpc64-coefficient-cap}
\end{equation}
Whenever \(\widetilde P(z)>0\), its occupied capacity is
\begin{equation}
 \kappa_X(z;C_X)
 :=\frac{\widetilde P(z)}
 {C_X^2\widetilde W_X}
 \in(0,1].
 \label{eq:tpc64-occupied-parent-capacity}
\end{equation}
For a real number \(x\), write \(x_+:=\max\{x,0\}\).

\subsection{The exact threshold theorem}

\begin{theorem}[Sharp threshold-capacity lower bound]
\label{thm:tpc64-threshold-capacity}
Fix \(\eta>0\) and \(0<\kappa_X\le1\).  If a coefficient vector \(z\)
satisfies \eqref{eq:tpc64-coefficient-cap} and
\begin{equation}
 \widetilde P(z)
 \ge \kappa_X C_X^2\widetilde W_X>0,
 \label{eq:tpc64-capacity-lower-hypothesis}
\end{equation}
then
\begin{equation}
 \boxed{
 \frac{T(z)}{\widetilde P(z)}
 \ge
 \eta
 \left(
  1-\frac{1-\delta_\eta}{\kappa_X}
 \right)_+.}
 \label{eq:tpc64-threshold-capacity-bound}
\end{equation}
More generally, if only
\(\delta_\eta\ge\underline\delta_\eta\) is known, then the same conclusion
holds with \(\underline\delta_\eta\) in place of \(\delta_\eta\).

Using only \(\eta\), \(\delta_\eta\), the coefficient cap, and the
capacity lower bound, the right side of
\eqref{eq:tpc64-threshold-capacity-bound} is optimal.  In particular, it
is positive exactly when
\begin{equation}
 \boxed{\kappa_X>1-\delta_\eta.}
 \label{eq:tpc64-capacity-positive-threshold}
\end{equation}
\end{theorem}

\begin{proof}
Write
\begin{equation}
 E_{\rm good}(z)
 :=\sum_{m\in\mathcal G_\eta}
       \widetilde P_m|z_m|^2,
 \qquad
 E_{\rm bad}(z)
 :=\widetilde P(z)-E_{\rm good}(z).
 \label{eq:tpc64-good-bad-parent-energy}
\end{equation}
The coefficient cap and
\eqref{eq:tpc64-threshold-capacity-fraction} give
\[
 E_{\rm bad}(z)
 \le C_X^2(1-\delta_\eta)\widetilde W_X.
\]
Subtracting this from
\eqref{eq:tpc64-capacity-lower-hypothesis}, and also using
\(E_{\rm good}(z)\ge0\), yields
\[
 \frac{E_{\rm good}(z)}{\widetilde P(z)}
 \ge
 \left(
  1-\frac{1-\delta_\eta}{\kappa_X}
 \right)_+.
\]
Since \(T_m=g_m\widetilde P_m\) and
\(g_m\ge\eta\) on \(\mathcal G_\eta\),
\[
 T(z)
 =\sum_mg_m\widetilde P_m|z_m|^2
 \ge\eta E_{\rm good}(z),
\]
which proves \eqref{eq:tpc64-threshold-capacity-bound}.  Monotonicity in
\(\delta_\eta\) proves the version with a lower bound for that fraction.

For sharpness, normalize \(C_X=\widetilde W_X=1\) and prescribe
\(\delta\in[0,1]\), \(\kappa\in(0,1]\).  Take \(g_m=\eta\) on a good
part of parent capacity \(\delta\) and \(g_m=0\) on its complement.  If
\(0<\delta<1\) and \(\kappa\le1-\delta\), put zero coefficient energy on
the good part and constant squared coefficient
\(\kappa/(1-\delta)\) on the bad part.  The terminal quotient is zero.
If \(\kappa>1-\delta\), saturate the bad part at squared coefficient one
and put constant squared coefficient
\((\kappa-1+\delta)/\delta\) on the good part.  Then
\[
 \widetilde P(z)=\kappa,
 \qquad
 \frac{T(z)}{\widetilde P(z)}
 =\eta\frac{\kappa-1+\delta}{\kappa}.
\]
These are equality cases for the two branches.  When \(\delta=0\), take
only bad rows; when \(\delta=1\), take only good rows.  Constant squared
coefficient \(\kappa\) gives the required occupied capacity at both
endpoints.  Finite weighted rows realize all of these models, so the
bound cannot be improved from the stated data.
\end{proof}

The theorem also has the exact actual-capacity form
\begin{equation}
 \frac{T(z)}{\widetilde P(z)}
 \ge
 \eta
 \left(
  1-\frac{1-\delta_\eta}
           {\kappa_X(z;C_X)}
 \right)_+.
 \label{eq:tpc64-actual-capacity-bound}
\end{equation}
A certified lower bound for
\(\kappa_X(z;C_X)\) may then be substituted because the right side is
increasing in the capacity variable.

\subsection{Uniform and distinguished quantifiers}

For \(C_X>0\) and \(0<\kappa_X\le1\), let
\begin{equation}
 \mathfrak Z_X(C_X,\kappa_X)
 :=
 \left\{
 z:\ |z_m|\le C_X,\quad
 \widetilde P(z)\ge
 \kappa_XC_X^2\widetilde W_X
 \right\}.
 \label{eq:tpc64-capacity-restricted-class}
\end{equation}
Theorem \ref{thm:tpc64-threshold-capacity} is coefficient-uniform on this
declared restricted class.  It is not a theorem on the entire bounded
coefficient cube: that cube contains vectors with arbitrarily small
occupied capacity and, whenever bad rows exist, vectors supported entirely
on those rows.

\begin{proposition}[The full-space boundary]
\label{prop:tpc64-capacity-full-space-boundary}
On any homogeneous declared class \(\mathfrak Z_X\) containing a nonzero
multiple of each active row direction,
\begin{equation}
 \inf_{\substack{z\in\mathfrak Z_X\\\widetilde P(z)>0}}
 \frac{T(z)}{\widetilde P(z)}
 =\min_{m\in\mathcal M_X^+}g_m.
 \label{eq:tpc64-capacity-full-space-minimax}
\end{equation}
Consequently a favorable value of
\eqref{eq:tpc64-threshold-capacity-bound} for one distinguished physical
vector does not imply a full-space uniform terminal lower bound.
\end{proposition}

\begin{proof}
Every quotient is a convex combination of the \(g_m\), with weights
\(\widetilde P_m|z_m|^2/\widetilde P(z)\).  A permitted row direction
attains the minimum.
\end{proof}

For a distinguished vector \(z_*(X)\), all of
\(C_X\), \(\kappa_X(z_*;C_X)\), and the threshold \(\eta\) must concern
that same vector and the same repaired parent.  An averaged vector, an
adaptively selected coefficient, or a capacity estimate computed with
\(P_m\) instead of \(\widetilde P_m\) cannot be inserted into
\eqref{eq:tpc64-threshold-capacity-bound}.

\subsection{What the certificate does not supply}

The theorem is an implication from \(\delta_\eta\) and occupied capacity.
It proves neither input favorable.  In particular:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item a positive number of terminal-active rows does not lower-bound
       their \(\widetilde P_m\)-capacity;
 \item boundedness of the inherited coefficients does not imply
       \(\kappa_X>1-\delta_\eta\);
 \item positivity of each \(T_m\) does not give a fixed-power lower bound
       for \(g_m\); and
 \item the raw terminal form \(T\) still precedes label erasure, residual
       grouping, and the native physical reassembly map.
\end{enumerate}
Thus the threshold theorem is a sharp L0 capacity law and, after the
literal fixed-shift dictionary is verified, a conditional L1
certificate.  It is not a new prime-distribution or cancellation
estimate.
