\section{Result ledger, claim boundary, and the next arithmetic target}
\label{sec:tpc64-claim-boundary}

TPC--64 separates true terminal activation from two representation
effects: deletion of parent mass and inflation by terminal-null crossed
coordinates.  It supplies exact finite-scale tests and a sharp capacity
certificate.  It does not prove that the physical terminal incidence is
large.

\subsection{Result ledger}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.23\textwidth}
                >{\raggedright\arraybackslash}p{0.52\textwidth}
                >{\raggedright\arraybackslash}p{0.14\textwidth}}
\toprule
Object & Exact conclusion & Status\\
\midrule
Literal parent and terminal
& The full incidence gives exact row masses \(P_m,H_m,T_m\), raw block
  disintegration, and, on rows with \(P_m,H_m>0\), the factorization
  \(T_m/P_m=(H_m/P_m)(T_m/H_m)\).
& L0 theorem; L1 dictionary\\
\addlinespace
Uniform activation
& On a class containing every active row direction, the optimal constant
  is \(\min_{P_m>0}T_m/P_m\); one zero row kills it.
& L0 minimax\\
\addlinespace
Parent-faithful pair lift
& A pair lift exists exactly when the parent projection creates no
  terminal-active spurious cross.  The least faithful relation and the
  hypergraph alternative are explicit.
& L0 iff test\\
\addlinespace
Parent inflation
& A parent-complete, terminal-faithful populated rectangle has
  \(\widetilde P_m=P_m+\Delta_m\) while preserving \(T_m\).  The optimal
  domination is the largest row inflation; a new-only row makes it
  infinite.
& L0 theorem\\
\addlinespace
Canonical hybrid
& Pair-good blocks use their least parent-complete lift, pair-bad blocks
  retain the literal active incidence, and the literal-active-hypergraph baseline has
  exactly zero inflation.
& L0 construction\\
\addlinespace
Threshold capacity
& If \(g_m=T_m/\widetilde P_m\), then threshold capacity
  \(\delta_\eta\) and occupied capacity \(\kappa_X\) give the sharp lower
  bound
  \(\eta(1-(1-\delta_\eta)/\kappa_X)_+\).
& L0 sharp theorem\\
\addlinespace
Denominator chain
& Literal activation, inflation, represented transfer, reassembly, and
  downstream arrows compose only with the same vector, carrier, raw norm,
  and quantifier scope.
& L0 compatibility\\
\addlinespace
Endpoint
& Inflation is charged once inside
  \(\lambda_{\rm term}^{\rm eff}\); all distinct physical losses must sum
  strictly below \(1/400\).
& L0 ledger; L1 conditional\\
\bottomrule
\end{tabular}
\end{center}

\subsection{The L0/L1/L2 boundary}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.12\textwidth}
                >{\raggedright\arraybackslash}p{0.38\textwidth}
                >{\raggedright\arraybackslash}p{0.38\textwidth}}
\toprule
Level & Established here & Not licensed by that level\\
\midrule
L0
& Exact finite-incidence parent/terminal forms, faithful-lift criteria,
  inflation identities, rowwise minimax laws, capacity extremizers, and
  compatible-form composition.
& No counting, density, or lower-bound assertion for the declared prime
  candidates, and no assertion that any asymptotic constant is favorable.\\
\addlinespace
L1
& Conditional specialization to one fixed nonzero \(h_0\), the literal
  TPC coefficient field, one cofactor M\"obius sign, raw atomic norms, and
  the stated terminal predicate.
& No proof that every physical row activates, that
  \(\delta_\eta\) or \(\kappa_X\) passes the threshold, or that physical
  label erasure is bounded below.\\
\addlinespace
L2
& None.
& No signed fixed-shift cancellation estimate, no specialization to
  \(h_0=2\), no parity-barrier advance, no prime-pair lower bound, and no
  twin-prime consequence.\\
\bottomrule
\end{tabular}
\end{center}

\subsection{What is not proved}

The following statements remain absent.
\begin{enumerate}[leftmargin=2.3em]
 \item No favorable lower bound is proved for
       \(\delta_{\eta_X}\) at any fixed or polynomially shrinking
       threshold \(\eta_X\).
 \item The actual physical coefficient vector is not shown to satisfy
       \(\kappa_X>1-\delta_{\eta_X}\), let alone with an
       endpoint-quality quantitative margin.
 \item No bound
       \[
        \min_{m:P_m>0}\frac{T_m}{P_m}
        \ge X^{-\lambda+o(1)}
       \]
       is proved for the full coefficient class.  Finite-scale positivity
       of every row would still be weaker than such a bound.
 \item No subpower or endpoint-quality bound is proved for the parent
       inflation of a pair-populated repair.  The literal-active-hypergraph baseline
       avoids that inflation but may not satisfy a downstream demand for
       pair coordinates.
 \item The labeled terminal square is not shown to survive dyadic-label
       erasure, residual grouping, comparison with the native affine
       Gram, boundary reconnection, or the ultra-tail map.
 \item None of the nonnegative endpoint losses is newly shown to fit
       inside the strict total budget.
\end{enumerate}

The capacity theorem is therefore not evidence that
\(\delta_\eta\) or \(\kappa_X\) is favorable.  Likewise, failure of its
threshold is failure of that certificate; it does not prove that the
actual terminal ratio \(T(z)/\widetilde P(z)\) is small.

\subsection{The next genuinely arithmetic theorem}

The next layer must estimate the terminal incidence itself.  There are
two honest quantifier scopes.

\paragraph{Uniform row target.}
For a full-coefficient theorem, prove on the literal multiscale carrier
\begin{equation}
 \boxed{
 T_m
 \ge X^{-\lambda_{\rm row}+o(1)}\widetilde P_m
 \quad\text{for every }m\text{ with }\widetilde P_m>0,}
 \label{eq:tpc64-next-uniform-row-target}
\end{equation}
with one uniform remainder and an exponent compatible with
\eqref{eq:tpc64-strict-stop-rule}.  Expanded literally, this is a weighted
lower theorem for terminal candidates
\begin{equation}
 p=\frac{mj+h_0}{r}
 \label{eq:tpc64-next-prime-candidate}
\end{equation}
which pass the declared prime, cofactor, squarefree, coprimality, mask, and
profile tests on every active source row.  A positive average over rows
does not prove \eqref{eq:tpc64-next-uniform-row-target}.

\paragraph{Distinguished capacity target.}
For the actual physical vector \(z_*(X)\), one may instead prove, for a
declared \(\eta_X>0\),
\begin{align}
 \delta_{\eta_X}
 &=
 \frac{\sum_{m:g_m\ge\eta_X}\widetilde P_m}
      {\sum_m\widetilde P_m},
 \label{eq:tpc64-next-delta-target}\\
 \kappa_X(z_*;C_X)
 &=
 \frac{\widetilde P(z_*)}
      {C_X^2\sum_m\widetilde P_m},
 \label{eq:tpc64-next-kappa-target}
\end{align}
and establish the quantitative threshold
\begin{equation}
 \boxed{
 \eta_X
 \left(
 1-\frac{1-\delta_{\eta_X}}
          {\kappa_X(z_*;C_X)}
 \right)_+
 \ge X^{-\lambda_{\rm term,*}^{\rm eff}+o(1)}.}
 \label{eq:tpc64-next-distinguished-capacity-target}
\end{equation}
This gives a distinguished terminal arrow only.  It cannot be entered as
the uniform constant in
\eqref{eq:tpc64-next-uniform-row-target}.

The natural arithmetic work is therefore a weighted prime-candidate
census in the progressions
\(mj+h_0\equiv0\pmod r\), simultaneously with the literal row, orbit,
cofactor, and terminal windows.  A successful lower theorem advances the
L1 activation gate.  An explicit active row with \(T_m=0\), or a proved
endpoint-sized dilution, closes the corresponding uniform architecture
and is an honest negative result.

\paragraph{After activation.}
Only after one of the two targets above is proved should the next paper
seek a represented-reference Gram lower bound on precisely the same
terminal carrier.  Determinant-pair cancellation, physical reassembly,
boundary terms, and the tail remain later gates.

\paragraph{Conclusion.}
TPC--64 gives the exact meaning of true terminal activation relative to a
parent-faithful denominator.  Pair completion can preserve the numerator
while diluting that denominator; threshold capacity can recover a sharp
lower bound only when its two inputs pass a strict quantitative test.
Neither mechanism supplies the missing arithmetic incidence theorem.
The next progress must come from the literal terminal candidates, not
from a relabeling of their parent.
