\section{Canonical hybrid repair and the activation-inflation law}
\label{sec:tpc64-hybrid-repair}

The blockwise criterion permits a canonical repair without forcing a
pair-only model on blocks where pair projection is unfaithful.  Pair-good
blocks use their unique least parent-complete rectangle; pair-bad blocks
retain their literal active incidence.  All block labels remain orthogonal
until a separately declared physical erasure.

\subsection{Pair-good and hypergraph blocks}

Define
\begin{align}
 K_X^{\mathrm{pair}}
 &:=
 \left\{k\in K_X:
 \operatorname{TRect}_{h,k}(I_{\mathrm{pre},k})
 =\mathcal U_{X,h,k}^{+}\right\},
 \label{eq:tpc64-pair-good-blocks}\\
 K_X^{\mathrm{hyp}}
 &:=
 K_X\setminus K_X^{\mathrm{pair}}.
 \label{eq:tpc64-hypergraph-blocks}
\end{align}
For each block, define the canonical repaired parent incidence
\begin{equation}
 \mathcal V_{X,k}^{\mathrm{hyb}}
 :=
 \begin{cases}
  \operatorname{PRect}_k(I_{\mathrm{pre},k}),
     &k\in K_X^{\mathrm{pair}},\\[2mm]
  \mathcal U_{X,k}^{\mathrm{pre},+},
     &k\in K_X^{\mathrm{hyp}}.
 \end{cases}
 \label{eq:tpc64-canonical-hybrid-incidence}
\end{equation}
Write
\(
 \mathcal V^{\mathrm{hyb}}
 :=(\mathcal V_{X,k}^{\mathrm{hyb}})_{k\in K_X}
\)
for this populated parent family.
The external label \(k\) is retained even if two underlying ambient
coordinates would otherwise be written with the same tuple.

The literal hypergraph baseline and the hybrid parent spaces are
\begin{align}
 \mathcal H_X^{\mathrm{hyp}}
 &:=
 \bigoplus_{k\in K_X}^{\perp}
 \ell^2(\mathcal U_{X,k}^{\mathrm{pre},+}),
 \label{eq:tpc64-hypergraph-parent-space}\\
 \mathcal H_X^{\mathrm{hyb}}
 &:=
 \bigoplus_{k\in K_X}^{\perp}
 \ell^2(\mathcal V_{X,k}^{\mathrm{hyb}}).
 \label{eq:tpc64-hybrid-parent-space}
\end{align}
Their populated analyses use the same literal field:
\begin{align}
 (C_X^{\mathrm{hyp}}z)(k,u)
 &:=c_u z_{m(u)},
 \label{eq:tpc64-hypergraph-analysis}\\
 (C_X^{\mathrm{hyb}}z)(k,u)
 &:=c_u z_{m(u)}.
 \label{eq:tpc64-hybrid-analysis}
\end{align}
The formulas have different coordinate domains.  In particular,
\(C_X^{\mathrm{hyb}}\) populates the terminal-null spurious crosses on
pair-good blocks.  Merely embedding
\(\mathcal H_X^{\mathrm{hyp}}\) into a larger ambient space by zero
extension would not do so and would have no parent inflation.

\subsection{Exact hybrid identities}

Put
\begin{equation}
 \Delta_m^{\mathrm{hyb}}
 :=
 \sum_{k\in K_X^{\mathrm{pair}}}
 \Delta_{k,m}(I_{\mathrm{pre},k})
 \label{eq:tpc64-hybrid-added-parent-mass}
\end{equation}
and
\begin{equation}
 \widetilde P_m
 :=P_m+\Delta_m^{\mathrm{hyb}}.
 \label{eq:tpc64-hybrid-row-parent}
\end{equation}
The hybrid parent form is
\begin{equation}
 \widetilde{\mathcal P}_X(z)
 :=\|C_X^{\mathrm{hyb}}z\|_2^2
 =\sum_m\widetilde P_m|z_m|^2.
 \label{eq:tpc64-hybrid-parent-form}
\end{equation}

\begin{theorem}[Canonical hybrid repair]
\label{thm:tpc64-canonical-hybrid-repair}
For every \(z\in Z_X\),
\begin{align}
 \widetilde{\mathcal P}_X(z)
 &=
 \mathcal P_X(z)
 +\sum_m\Delta_m^{\mathrm{hyb}}|z_m|^2,
 \label{eq:tpc64-hybrid-parent-identity}\\
 \|D_{X,h}^{\mathcal V^{\mathrm{hyb}}}C_X^{\mathrm{hyb}}z\|_2^2
 &=\mathcal T_{X,h}(z).
 \label{eq:tpc64-hybrid-terminal-identity}
\end{align}
Thus the hybrid repair is parent-complete and terminal-atomic faithful on
every block.  Among all repairs which use a parent-complete
terminal-atomic faithful pair relation on every block in
\(K_X^{\mathrm{pair}}\) and retain the literal active incidence on every block in
\(K_X^{\mathrm{hyp}}\), it minimizes the parent weight row by row.

The literal-active-hypergraph choice has the stronger exact identities
\begin{equation}
 \boxed{
 \|C_X^{\mathrm{hyp}}z\|_2^2=\mathcal P_X(z),
 \qquad
 \|D_{X,h}^{\mathcal U^{\mathrm{pre},+}}C_X^{\mathrm{hyp}}z\|_2^2
 =\mathcal T_{X,h}(z).}
 \label{eq:tpc64-hybrid-hypergraph-zero-inflation}
\end{equation}
Hence the literal active hypergraph baseline has exactly zero parent inflation,
not merely zero fixed-power inflation.
\end{theorem}

\begin{proof}
On a pair-good block,
\eqref{eq:tpc64-block-parent-inflation-identity} and
\eqref{eq:tpc64-block-terminal-preservation} apply to
\(I_{\mathrm{pre},k}\).  On a hypergraph block both forms are the literal
ones by definition.  Orthogonality of the external block labels allows
the identities to be summed over \(k\), proving
\eqref{eq:tpc64-hybrid-parent-identity} and
\eqref{eq:tpc64-hybrid-terminal-identity}.  Rowwise minimality follows
from \eqref{eq:tpc64-rowwise-minimal-inflation} on every pair-good block.
For the literal-active-hypergraph choice, every block is the original
literal active coordinate set,
so exact block disintegration gives
\eqref{eq:tpc64-hybrid-hypergraph-zero-inflation}.
\end{proof}

No theorem requires using a pair rectangle on a pair-good block.  Within
populated incidence repairs retaining every literal parent atom, the
literal active hypergraph is the parent-minimal baseline.  The
hybrid construction records the least cost incurred when a downstream
argument explicitly requires pair coordinates on the blocks where such a
representation is faithful.

\subsection{Block count is not an inflation estimate}

Suppose the cofactor blocks lie in a fixed polynomial range.  Then the
dyadic choice has
\begin{equation}
 |K_X|=O(\log X)=X^{o(1)}.
 \label{eq:tpc64-logarithmic-block-count}
\end{equation}
This controls only the number of external labels.  It does not control
\(\Delta_m^{\mathrm{hyb}}\), or any ratio of repaired to literal parent
mass.  Parent inflation of arbitrary polynomial size can already occur
inside a single pair-good block.

For clarity, put
\begin{equation}
 \widetilde P_{k,m}^{\mathrm{hyb}}
 :=
 \begin{cases}
  P_{k,m}+\Delta_{k,m}(I_{\mathrm{pre},k}),
      &k\in K_X^{\mathrm{pair}},\\
  P_{k,m},&k\in K_X^{\mathrm{hyp}}.
 \end{cases}
 \label{eq:tpc64-hybrid-block-parent-weight}
\end{equation}
If a separate estimate proves, for one common finite \(I_X\),
\begin{equation}
 \widetilde P_{k,m}^{\mathrm{hyb}}
 \le I_XP_{k,m}
 \label{eq:tpc64-hybrid-blockwise-inflation-input}
\end{equation}
on every block and active row, then summing gives
\begin{equation}
 \widetilde P_m
 =\sum_k\widetilde P_{k,m}^{\mathrm{hyb}}
 \le I_X\sum_kP_{k,m}
 =I_XP_m.
 \label{eq:tpc64-blockwise-to-global-inflation}
\end{equation}
Indeed, \(P_{k,m}=0\) implies
\(\widetilde P_{k,m}^{\mathrm{hyb}}=0\): no pair with first coordinate
\(m\) then occurs in \(I_{\mathrm{pre},k}\), and a hypergraph block keeps
the same empty active row.  Thus
\eqref{eq:tpc64-hybrid-blockwise-inflation-input} also holds trivially on
every inactive row, justifying the sum over all \(k\).
No additional factor \(|K_X|\) is needed in this comparison.  Conversely,
\eqref{eq:tpc64-logarithmic-block-count} supplies no value of \(I_X\).
The label count and the parent-inflation bound are logically independent
data.

Erasing the external label \(k\), coherently grouping residual labels, or
mapping the terminal vector to a native physical output is a later map.
Neither \eqref{eq:tpc64-logarithmic-block-count} nor
\eqref{eq:tpc64-hybrid-hypergraph-zero-inflation} supplies a lower bound through
that map.  Its kernel and range-restricted Gram belong to the reassembly
gate, not to parent inflation.

\begin{remark}[Claim boundary]
\label{rem:tpc64-hybrid-claim-boundary}
All results in this section are exact finite-incidence statements.  Their
use with the literal multiplier
\eqref{eq:tpc64-literal-terminal-multiplier}, one fixed nonzero shift,
and the raw physical atom norm is an arithmetic-interface
specialization.  No estimate here proves that
\(T_m>0\), gives a polynomial terminal-activation lower bound,
specializes \(h\) to \(2\), estimates a signed parity kernel, or implies a
prime-pair statement.
\end{remark}
