\section{Exact parent-inflation laws}
\label{sec:tpc64-inflation-laws}

The terminal-faithfulness test does not by itself preserve the parent
denominator.  A pair rectangle may add coordinates which are terminal-null
but carry nonzero pre-terminal mass.  This section records that mass exactly.
All incidences, coefficients, and repairs are fixed before the row
coefficient vector is chosen.

\subsection{Repaired parent data}

Continue with the literal blocks, incidences, and row masses
\[
 \mathcal U_{X,k}^{\mathrm{pre},+},\qquad
 \mathcal U_{X,h,k}^{+},\qquad
 P_m,\ H_m,\ T_m
\]
from \cref{sec:tpc64-literal-parent}.  In particular, \(P_m,H_m,T_m\)
are not recomputed after a pair projection or terminal restriction.

Fix a populated parent enlargement
\(\widetilde{\mathcal U}_{X,k}^{\mathrm{pre},+}\) which preserves every
literal parent atom and is terminal-atomic faithful.  Thus
\begin{equation}
 \mathcal U_{X,k}^{\mathrm{pre},+}
 \subseteq\widetilde{\mathcal U}_{X,k}^{\mathrm{pre},+}
 \subseteq\{u\in\Omega_{X,k}:c_u\ne0\},
 \qquad
 \{u\in\widetilde{\mathcal U}_{X,k}^{\mathrm{pre},+}:
               t_h(u)c_u\ne0\}
 =\mathcal U_{X,h,k}^{+}.
 \label{eq:tpc64-parent-complete-terminal-faithful}
\end{equation}
The added-parent incidence
\begin{equation}
 \mathcal N_{X,k}
 :=\widetilde{\mathcal U}_{X,k}^{\mathrm{pre},+}
      \setminus\mathcal U_{X,k}^{\mathrm{pre},+}
 \label{eq:tpc64-new-parent-incidence}
\end{equation}
therefore satisfies
\begin{equation}
 t_h(u)c_u=0
 \qquad(u\in\mathcal N_{X,k}).
 \label{eq:tpc64-new-parent-terminal-null}
\end{equation}
For a pair lift, the first condition is parent completeness in the sense
of \cref{def:tpc64-parent-complete-terminal-faithful}.  For the canonical
hybrid repair, take
\(\widetilde{\mathcal U}_{X,k}^{\mathrm{pre},+}
=\mathcal V_{X,k}^{\mathrm{hyb}}\): this is the least admissible
parent-complete rectangle on a pair-good block and the literal active
incidence on a pair-bad block.  The results below use only
\eqref{eq:tpc64-parent-complete-terminal-faithful}, so they also apply to
any larger populated terminal-faithful repair.

For every source row \(m\), define only the genuinely new quantity
\begin{equation}
 \Delta_m
 :=\sum_{k\in K_X}
     \sum_{\substack{u\in\mathcal N_{X,k}\\m(u)=m}}
       |c_u|^2.
 \label{eq:tpc64-added-parent-mass}
\end{equation}
The populated repaired parent mass therefore obeys
\begin{equation}
 \widetilde P_m=P_m+\Delta_m.
 \label{eq:tpc64-repaired-parent-mass}
\end{equation}
In the canonical hybrid specialization,
\(\Delta_m=\Delta_m^{\mathrm{hyb}}\), and
\eqref{eq:tpc64-repaired-parent-mass} is exactly the previously defined
hybrid row parent \eqref{eq:tpc64-hybrid-row-parent}; no second hybrid
parent is being introduced.
All four quantities are nonnegative, and
\begin{equation}
 0\le H_m\le P_m\le\widetilde P_m.
 \label{eq:tpc64-row-mass-order}
\end{equation}
Terminal faithfulness means that the repair changes neither \(H_m\) nor
\(T_m\).  It changes only the parent against which terminal activation is
measured.

For \(z=(z_m)_{m\in\mathcal M_X}\in Z_X\), set
\begin{align}
 P(z)&:=\mathcal P_X(z)=\sum_mP_m|z_m|^2,
 &
 \Delta(z)&:=\sum_m\Delta_m|z_m|^2,
 \label{eq:tpc64-parent-added-forms}\\
 \widetilde P(z)&:=\sum_m\widetilde P_m|z_m|^2,
 &
 T(z)&:=\mathcal T_{X,h}(z)=\sum_mT_m|z_m|^2.
 \label{eq:tpc64-repaired-terminal-forms}
\end{align}
We assume throughout that \(P\) is not identically zero.  Rows on which
\(P_m=\widetilde P_m=0\) are harmless zero rows.

\subsection{The exact inflation constant}

The row inflation ratio is an extended nonnegative number.  We use the
convention
\begin{equation}
 \iota_m:=
 \begin{cases}
  \displaystyle\frac{\widetilde P_m}{P_m}
   =1+\frac{\Delta_m}{P_m},&P_m>0,\\[8pt]
  1,&P_m=\widetilde P_m=0,\\
  +\infty,&P_m=0<\widetilde P_m.
 \end{cases}
 \label{eq:tpc64-row-inflation-convention}
\end{equation}
A row in the last case is called a \emph{new-only parent row}.  Define
\begin{equation}
 \mathfrak I_X
 :=\sup_{\substack{z\in Z_X\\P(z)>0}}
       \frac{\widetilde P(z)}{P(z)}
 \in[1,+\infty].
 \label{eq:tpc64-global-inflation-constant}
\end{equation}
The supremum is taken on the full row-coefficient space.  A
range-restricted or distinguished coefficient class has its own constant
and must not be substituted for \(\mathfrak I_X\).

\begin{theorem}[Exact parent inflation and sharp domination]
\label{thm:tpc64-exact-parent-inflation}
For every coefficient vector,
\begin{equation}
 \boxed{\widetilde P(z)=P(z)+\Delta(z).}
 \label{eq:tpc64-exact-parent-inflation-identity}
\end{equation}
Moreover,
\begin{equation}
 \boxed{\mathfrak I_X=\max_{m\in\mathcal M_X}\iota_m}
 \label{eq:tpc64-inflation-row-maximum}
\end{equation}
with the conventions in
\eqref{eq:tpc64-row-inflation-convention}.  Consequently, the following
are equivalent:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item there is a finite \(C\) such that
       \(\widetilde P(z)\le C P(z)\) for every \(z\);
 \item the repair has no new-only parent row;
 \item \(\mathfrak I_X<\infty\).
\end{enumerate}
When these conditions hold, the least possible domination constant is
\(\mathfrak I_X\):
\begin{equation}
 \widetilde P(z)\le\mathfrak I_XP(z)
 \qquad(z\in Z_X).
 \label{eq:tpc64-sharp-parent-domination}
\end{equation}
For the separate literal-active-hypergraph baseline, which makes no
pair-rectangularization claim,
\(\Delta_m=0\), \(\widetilde P_m=P_m\), and
\(\mathfrak I_X=1\) exactly, consistently with
\eqref{eq:tpc64-hybrid-hypergraph-zero-inflation}.
\end{theorem}

\begin{proof}
Equation \eqref{eq:tpc64-exact-parent-inflation-identity} follows by
summing \eqref{eq:tpc64-repaired-parent-mass} against \(|z_m|^2\).
First suppose there is no new-only row.  Whenever \(P(z)>0\),
\begin{equation}
 \frac{\widetilde P(z)}{P(z)}
 =
 \sum_{\substack{m:P_m>0}}
 \frac{P_m|z_m|^2}{P(z)}\,\iota_m.
 \label{eq:tpc64-inflation-convex-combination}
\end{equation}
This is a convex combination of the active row ratios.  It is at most
their maximum, and a row basis vector attaining the maximum gives
equality.

Now suppose \(P_{m_1}=0<\widetilde P_{m_1}\).  Choose a row \(m_0\) with
\(P_{m_0}>0\) and put
\[
 z^{(\varepsilon)}:=e_{m_1}+\varepsilon e_{m_0}.
\]
Then
\[
 P(z^{(\varepsilon)})=\varepsilon^2P_{m_0}>0,
 \qquad
 \widetilde P(z^{(\varepsilon)})
 \ge\widetilde P_{m_1},
\]
so the quotient tends to \(+\infty\).  This proves
\eqref{eq:tpc64-inflation-row-maximum} and all three equivalences.  The
hypergraph statement is the case
\(\widetilde{\mathcal U}_{X,k}^{\mathrm{pre},+}
=\mathcal U_{X,k}^{\mathrm{pre},+}\) for every block.
\end{proof}

\begin{proposition}[Sharpness of the inflation law]
\label{prop:tpc64-inflation-sharpness}
For every prescribed \(L\in[1,\infty)\), there is a one-row,
one-block terminal-faithful repair with
\begin{equation}
 P_m=1,\qquad
 \Delta_m=L-1,\qquad
 \widetilde P_m=L,\qquad
 \mathfrak I_X=L.
 \label{eq:tpc64-prescribed-inflation-model}
\end{equation}
Thus neither the coefficient \(1\) in
\eqref{eq:tpc64-exact-parent-inflation-identity} nor the constant
\(\mathfrak I_X\) in \eqref{eq:tpc64-sharp-parent-domination} can be
improved under the stated hypotheses.
\end{proposition}

\begin{proof}
Take one literal parent atom of square mass \(1\) and one added
terminal-null parent atom of square mass \(L-1\), omitting the latter when
\(L=1\).  The repair is terminal-faithful because the added coordinate
has zero terminal multiplier.  All formulas are immediate.  An explicit
pair-rectangle realization, with arbitrarily large integral inflation, is
given in \cref{ex:tpc64-arbitrary-faithful-inflation}.
\end{proof}

The value \(\mathfrak I_X\) is a parent-denominator constant.  It is not
the number of dyadic labels, a terminal occupancy proportion, an erasure
norm, or a cancellation exponent.  In particular, an \(X^{o(1)}\) label
count places no bound on \(\mathfrak I_X\).
