\section{Introduction}
\label{sec:tpc64-introduction}

The fixed-shift program now has two distinct notions of ``completion.''
TPC--63 completes the logical provenance interface: a pair relation may be
rectangularized only after its literal full incidence has passed the
appropriate parent, terminal, or grouped-output test
\citep{WangTPC63}.  It also proves that retaining dyadic cofactor scales as
orthogonal labels costs only \(X^{o(1)}\) at the raw-energy level.  Neither
statement says that the chosen completed space has the same parent
denominator as the coefficientwise physical field of TPC--47
\citep{WangTPC47}.

That denominator matters.  Suppose a rectangle adds coordinates which are
terminal-null but carry nonzero pre-terminal coefficient.  Its terminal
numerator is unchanged, while its parent form is larger.  Parseval on the
enlarged space is exact but answers the wrong comparison unless the extra
parent mass is recorded.  Conversely, replacing the parent by the
terminal-active incidence deletes the very alignment defect which the
activation theorem is meant to estimate.  The present paper isolates this
missing arrow before any represented-Gram or signed-cancellation argument is
attempted.

For each dyadic block \(k\), let \(\mathcal U_{X,k}\) be the literal full
incidence and let
\[
 \mathcal U_{X,k}^{\mathrm{pre},+}
 =\{u:c_u\ne0\},
 \qquad
 \mathcal U_{X,h,k}^{+}
 =\{u:t_h(u)c_u\ne0\}.
\]
The literal row masses are
\begin{align}
 P_m&=\sum_{k}\sum_{\substack{u\in
       \mathcal U_{X,k}^{\mathrm{pre},+}\\m(u)=m}}|c_u|^2,
 \label{eq:tpc64-intro-parent-mass}\\
 H_m&=\sum_{k}\sum_{\substack{u\in
       \mathcal U_{X,h,k}^{+}\\m(u)=m}}|c_u|^2,
 \qquad
 T_m=\sum_{k}\sum_{\substack{u\in
       \mathcal U_{X,h,k}^{+}\\m(u)=m}}|t_h(u)c_u|^2.
 \label{eq:tpc64-intro-terminal-masses}
\end{align}
All three are fixed before the free row coefficient is chosen.  In the
physical specialization, \(t_h\) contains one inherited cofactor sign and
the literal smooth terminal multiplier.  It is not normalized to a
probability.

The first result is an exact existence theorem.  Put
\[
 I_{\mathrm{pre},k}
 :=\operatorname{pr}_{m,r}
   \mathcal U_{X,k}^{\mathrm{pre},+}.
\]
A pair relation which retains every literal parent atom and introduces no
terminal-active spurious cross exists exactly when
\begin{equation}
 \operatorname{TRect}_{h,k}(I_{\mathrm{pre},k})
 =\mathcal U_{X,h,k}^{+}.
 \label{eq:tpc64-intro-faithful-test}
\end{equation}
When it exists, \(I_{\mathrm{pre},k}\) is the unique least relation.  Its
parent is uninflated exactly when its pre-terminal rectangle is already the
literal active incidence.  Blocks which fail
\eqref{eq:tpc64-intro-faithful-test} admit no parent-complete faithful
pair-rectangular lift.  Our canonical fallback retains their literal active
incidence, giving a pair-good/hypergraph hybrid.

The second result measures the cost of every populated repair.  With
\(\Delta_m\) the structural, \(z\)-independent squared mass of new
terminal-null parent coordinates,
\begin{equation}
 \widetilde P_m=P_m+\Delta_m.
 \label{eq:tpc64-intro-inflated-parent}
\end{equation}
The optimal full-row comparison is the largest row inflation; a new-only row
makes the comparison infinite.  The literal-active-hypergraph realization has
\(\Delta_m=0\) identically.  This distinguishes parent inflation from the
Mellin-frame conditioning of TPC--51, the capacity saturation of TPC--54,
and the physical label-erasure loss of TPC--62
\citep{WangTPC51,WangTPC54,WangTPC62}.

The third result gives the correct activation quantity.  On rows with all
denominators positive,
\begin{equation}
 \frac{T_m}{\widetilde P_m}
 =\underbrace{\frac{H_m}{P_m}}_{\text{terminal-support alignment}}
  \underbrace{\frac{T_m}{H_m}}_{\text{literal multiplier intensity}}
  \underbrace{\frac{P_m}{\widetilde P_m}}_{\text{inverse inflation}}.
 \label{eq:tpc64-intro-three-factor}
\end{equation}
The paper extends this identity through all zero rows, proves the sharp
uniform and distinguished minimax laws, and shows that the loss
\(\mathfrak I_X^{-1}\) in passing from the literal hypergraph parent to the
repaired parent cannot be improved from representation data alone.

There remains an honest distinguished alternative inherited from the sharp
energy-selection interface of TPC--54.  If good rows
\(g_m=T_m/\widetilde P_m\ge\eta\) occupy a structural repaired-parent
fraction \(\delta_\eta\), while a coefficient vector occupies at least a
fraction \(\kappa_X\) of the available capped energy, then
\begin{equation}
 \frac{T(z)}{\widetilde P(z)}
 \ge
 \eta\left(1-\frac{1-\delta_\eta}{\kappa_X}\right)_+.
 \label{eq:tpc64-intro-capacity}
\end{equation}
We prove that this bound and the threshold
\(\kappa_X>1-\delta_\eta\) are sharp from the stated data.  The theorem
does not assert that either input is favorable on the physical vector.

The compatible endpoint chain uses the same carrier, row vector, raw norm,
and uniform or distinguished scope throughout TPC--47, TPC--51, TPC--54,
TPC--59, TPC--62, and TPC--63
\citep{WangTPC47,WangTPC51,WangTPC54,WangTPC59,WangTPC62,WangTPC63}.
If a literal terminal estimate is first proved relative to \(P\), parent
inflation is charged once in its effective loss.  If a direct estimate is
proved relative to \(\widetilde P\), it is not charged again.  Equality at
the inherited endpoint \(1/400\) is a stop, not a success.

\paragraph{Main results.}
The paper proves the following finite-scale statements.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item Exact literal parent, terminal-support, and shaped terminal forms,
       with block disintegration and raw atomic normalization.
 \item A necessary and sufficient parent-complete/terminal-faithful pair-lift
       criterion, its unique least relation, and the exact zero-inflation
       test.
 \item A canonical hybrid repair and an exact literal-active-hypergraph zero-inflation
       baseline.
 \item Exact parent-inflation identities, the optimal domination constant,
       and sharp arbitrary-inflation and zero-row countermodels.
 \item Zero-safe three-factor activation, uniform row minima,
       distinguished weighted averages, and sharp inflation-corrected
       transfer.
 \item The sharp threshold-capacity certificate
       \eqref{eq:tpc64-intro-capacity}, including all endpoint extremizers.
 \item A denominator-compatible five-arrow chain, a no-double-charge
       exponent ledger, and the strict \(1/400\) stop rule.
\end{enumerate}

The incidence and minimax theorems are L0.  Their use with one literal
fixed-shift coefficient field is L1 and remains conditional on an arithmetic
terminal-incidence estimate.  No L2 cancellation, parity, prime-pair, or
twin-prime conclusion is claimed.
