\section{The literal multiscale parent and its terminal field}
\label{sec:tpc64-literal-parent}

The multiscale construction must begin before pair projection.  This
section fixes the literal finite incidence, its raw parent form, and the
terminal form to which every later repair will be compared.  In
particular, neither a rectangular completion nor the terminal-active
support is used to define the parent.

\subsection{Finite arithmetic blocks and full incidences}

Fix \(X\ge 2\) and one integer
\begin{equation}
 h\in\mathbb Z\setminus\{0\}.
 \label{eq:tpc64-fixed-shift}
\end{equation}
The physical specialization will take \(h=h_0\), but no value of \(h_0\)
is selected here.  Let \(K_X\subset\mathbb Z\) be a finite set of block
labels.  For \(k\in K_X\), let
\(\mathcal R_{X,k}\subset\mathbb N\) be finite, with the
\(\mathcal R_{X,k}\) pairwise disjoint, and let
\begin{equation}
 \Omega_{X,k}\subseteq
 \mathcal M_X\times\mathcal R_{X,k}
 \times\mathcal J_X\times\Gamma_X
 \label{eq:tpc64-block-ambient}
\end{equation}
be a finite coefficient-independent ambient incidence.  Here
\(\mathcal M_X,\mathcal J_X\subset\mathbb N\) and \(\Gamma_X\) is a
finite auxiliary label set.  A point is written
\[
 u=(m,r,j,\gamma),\qquad
 m(u)=m,\quad r(u)=r,\quad j(u)=j,\quad\gamma(u)=\gamma.
\]
Allowing \(\Omega_{X,k}\) to be a subset of the displayed product permits
fixed residue, side, orbit, and support restrictions.  They are part of
the ambient arithmetic data and are fixed before a row coefficient is
chosen.

For every \(k\), let
\begin{equation}
 \mathcal U_{X,k}\subseteq\Omega_{X,k}
 \label{eq:tpc64-literal-full-incidence}
\end{equation}
be the literal full pre-terminal incidence on that block.  The word
\emph{full} means that all four labels are retained; it does not mean that
\(\mathcal U_{X,k}\) is a Cartesian product.  Attach a structural
coefficient
\begin{equation}
 c_u\in\mathbb C,\qquad u\in\Omega_{X,k},
 \label{eq:tpc64-structural-coefficient}
\end{equation}
containing every coefficient-free source, mask, opposite-row, residue,
and orbit factor preceding terminalization.  Both
\(\mathcal U_{X,k}\) and \(c_u\) are fixed independently of
\[
 z=(z_m)_{m\in\mathcal M_X}\in
 Z_X:=\mathbb C^{\mathcal M_X}.
\]
Thus a zero of \(z_m\) never deletes an atom from the structural support.

\subsection{The literal terminal multiplier}

For \(u=(m,r,j,\gamma)\), put
\begin{equation}
 n_h(u):=mj+h.
 \label{eq:tpc64-target-integer}
\end{equation}
If \(n_h(u)>0\) and \(r\mid n_h(u)\), define
\begin{equation}
 p_h(u):=\frac{n_h(u)}r\in\mathbb N.
 \label{eq:tpc64-prime-candidate}
\end{equation}
Otherwise \(p_h(u)\) is left undefined and the terminal indicator below
is zero.  Let
\(\mathbf 1_{\mathrm{term},h}(u)\in\{0,1\}\) be the conjunction of the
complete declared terminal conditions.  In the fixed-shift arithmetic
specialization these include
\begin{equation}
 n_h(u)>0,\qquad r\mid n_h(u),\qquad
 p_h(u)\in\mathbb P,
 \label{eq:tpc64-basic-terminal-tests}
\end{equation}
the declared prime and cofactor windows, and every inherited squarefree,
coprimality, literal-mask, and terminal-profile support condition.  No
test is allowed to depend on \(z\).

Let \(\Lambda_X:\mathbb N\to\mathbb C\) be the literal shaped terminal
weight and define
\begin{equation}
 t_h(u):=
 \mu(r(u))\Lambda_X(n_h(u))
 \mathbf 1_{\mathrm{term},h}(u).
 \label{eq:tpc64-literal-terminal-multiplier}
\end{equation}
The factor \(\mu(r)\) occurs once.  If the physical packet uses an
equivalent calibrated multiplier, that multiplier is inserted in
\eqref{eq:tpc64-literal-terminal-multiplier} without changing any argument
below.

\begin{definition}[Literal active incidences]
\label{def:tpc64-literal-active-incidences}
For \(k\in K_X\), define
\begin{align}
 \mathcal U_{X,k}^{\mathrm{pre},+}
 &:=
 \{u\in\mathcal U_{X,k}:c_u\ne0\},
 \label{eq:tpc64-pre-active-incidence}\\
 \mathcal U_{X,h,k}^{+}
 &:=
 \{u\in\mathcal U_{X,k}:t_h(u)c_u\ne0\}.
 \label{eq:tpc64-terminal-active-incidence}
\end{align}
\end{definition}

Both sets are coefficient-independent and
\begin{equation}
 \mathcal U_{X,h,k}^{+}
 \subseteq\mathcal U_{X,k}^{\mathrm{pre},+}.
 \label{eq:tpc64-active-incidence-inclusion}
\end{equation}
The inclusion may be strict.  Replacing the first set by the second in an
upstream parent form would discard terminal-null parent mass and make
activation circular.

\subsection{Raw parent, support-aligned, and terminal forms}

For \(m\in\mathcal M_X\) and \(k\in K_X\), define
\begin{align}
 P_{k,m}
 &:=
 \sum_{\substack{u\in\mathcal U_{X,k}^{\mathrm{pre},+}\\m(u)=m}}
 |c_u|^2,
 \label{eq:tpc64-block-parent-weight}\\
 H_{k,m}
 &:=
 \sum_{\substack{u\in\mathcal U_{X,h,k}^{+}\\m(u)=m}}
 |c_u|^2,
 \label{eq:tpc64-block-aligned-weight}\\
 T_{k,m}
 &:=
 \sum_{\substack{u\in\mathcal U_{X,h,k}^{+}\\m(u)=m}}
 |t_h(u)c_u|^2.
 \label{eq:tpc64-block-terminal-weight}
\end{align}
An empty sum is zero.  Aggregate the blocks by
\begin{equation}
 P_m:=\sum_{k\in K_X}P_{k,m},\qquad
 H_m:=\sum_{k\in K_X}H_{k,m},\qquad
 T_m:=\sum_{k\in K_X}T_{k,m}.
 \label{eq:tpc64-aggregate-row-weights}
\end{equation}
Then
\begin{equation}
 0\le H_m\le P_m,\qquad
 P_m=0\Longrightarrow H_m=T_m=0.
 \label{eq:tpc64-row-weight-order}
\end{equation}
There is no universal order between \(T_m\) and \(H_m\), because the
literal multiplier \(\lvert\Lambda_X\rvert^2\) remains in \(T_m\).

The corresponding quadratic forms on the original row-coefficient space
are
\begin{align}
 \mathcal P_X(z)
 &:=\sum_{m\in\mathcal M_X}P_m|z_m|^2,
 \label{eq:tpc64-literal-parent-form}\\
 \mathcal H_{X,h}(z)
 &:=\sum_{m\in\mathcal M_X}H_m|z_m|^2,
 \label{eq:tpc64-literal-aligned-form}\\
 \mathcal T_{X,h}(z)
 &:=\sum_{m\in\mathcal M_X}T_m|z_m|^2.
 \label{eq:tpc64-literal-terminal-form}
\end{align}
These are raw counting-measure forms.  Repeated cofactors, orbit points,
or auxiliary labels remain distinct orthogonal atoms.  In particular,
there is no division by a row multiplicity, cofactor multiplicity, or
terminal fiber size.

Equivalently, on the labeled spaces
\begin{equation}
 \mathcal H_X^{\mathrm{pre}}
 :=
 \bigoplus_{k\in K_X}^{\perp}
 \ell^2(\mathcal U_{X,k}^{\mathrm{pre},+}),
 \qquad
 \mathcal H_{X,h}^{\mathrm{term}}
 :=
 \bigoplus_{k\in K_X}^{\perp}
 \ell^2(\mathcal U_{X,h,k}^{+}),
 \label{eq:tpc64-literal-Hilbert-spaces}
\end{equation}
Write
\(
 \mathcal U^{\mathrm{pre},+}
 :=(\mathcal U_{X,k}^{\mathrm{pre},+})_{k\in K_X}
\)
for the literal parent family.
For any family \(\mathcal V=(\mathcal V_{X,k})_{k\in K_X}\) satisfying
\[
 \mathcal U_{X,h,k}^{+}\subseteq\mathcal V_{X,k}\subseteq\Omega_{X,k},
 \qquad k\in K_X,
\]
define the typed terminal operator
\[
 D_{X,h}^{\mathcal V}:
 \bigoplus_{k\in K_X}^{\perp}\ell^2(\mathcal V_{X,k})
 \longrightarrow \mathcal H_{X,h}^{\mathrm{term}},
 \qquad
 (D_{X,h}^{\mathcal V}a)(k,u):=t_h(u)a(k,u)
 \quad(u\in\mathcal U_{X,h,k}^{+}).
\]
Thus the operator domain changes with the populated parent incidence, while
the terminal codomain remains literal.  The literal analysis and terminal
maps are
\begin{align}
 (C_X^{\mathrm{lit}}z)(k,u)
 &:=c_u z_{m(u)},
 \label{eq:tpc64-literal-analysis-map}\\
 (D_{X,h}^{\mathcal U^{\mathrm{pre},+}}C_X^{\mathrm{lit}}z)(k,u)
 &:=t_h(u)c_u z_{m(u)}.
 \label{eq:tpc64-literal-terminal-map}
\end{align}
Thus
\begin{equation}
 \|C_X^{\mathrm{lit}}z\|_2^2=\mathcal P_X(z),
 \qquad
 \|D_{X,h}^{\mathcal U^{\mathrm{pre},+}}C_X^{\mathrm{lit}}z\|_2^2
 =\mathcal T_{X,h}(z).
 \label{eq:tpc64-literal-map-forms}
\end{equation}

\begin{proposition}[Exact block disintegration]
\label{prop:tpc64-exact-block-disintegration}
For every \(z\in Z_X\),
\begin{align}
 \mathcal P_X(z)
 &=\sum_{k\in K_X}
   \sum_m P_{k,m}|z_m|^2,
 \label{eq:tpc64-parent-block-disintegration}\\
 \mathcal T_{X,h}(z)
 &=\sum_{k\in K_X}
   \sum_m T_{k,m}|z_m|^2.
 \label{eq:tpc64-terminal-block-disintegration}
\end{align}
These are exact identities with constant one, independently of
\(|K_X|\).
\end{proposition}

\begin{proof}
The external block labels make the summands orthogonal, and the cofactor
blocks are disjoint.  Expanding the two raw squared norms in
\eqref{eq:tpc64-literal-map-forms} and regrouping first by \(k\) and then
by \(m\) gives the displayed identities.
\end{proof}

\subsection{The activation comparison is not yet an estimate}

The literal activation problem is the comparison of
\(\mathcal T_{X,h}\) with \(\mathcal P_X\), in one declared uniform or
distinguished coefficient scope.  If \(\mathcal P_X\equiv0\), there is no
parent-visible vector and no activation constant or exponent is assigned.
If \(\mathcal P_X\not\equiv0\), the definitions above do not assert that
every active parent row has \(T_m>0\), nor that any positive ratio has a
fixed-power lower bound.

Normalizing \(\mathcal T_{X,h}\) by
\(\mathcal H_{X,h}\), or declaring
\(\mathcal U_{X,h,k}^{+}\) to be the parent incidence, would delete the
parent-to-terminal-support alignment loss.  Such a terminal-active parent
cannot be substituted for \(\mathcal P_X\) in a chain whose upstream
reference is the literal pre-terminal form.
