\section{Sharp countermodels and zero tests}
\label{sec:tpc64-sharp-countermodels}

The exact formulas above separate identities from arithmetic lower bounds.
This section shows that the separation is necessary.  Every example is a
finite coefficient-independent incidence with raw counting-measure norms.
The examples are sharp models of the stated interfaces; they are not
asserted to occur inside the literal fixed-shift prime carrier.

\subsection{Faithful rectangles can have arbitrary parent inflation}

\begin{example}[Arbitrarily large faithful inflation]
\label{ex:tpc64-arbitrary-faithful-inflation}
Take one block \(k\), one row \(m\), one cofactor \(r\), one auxiliary
label \(\gamma_0\), and \(N\ge2\) base labels
\(j_0,\ldots,j_{N-1}\).  Let the declared ambient incidence contain
\[
 u_i:=(m,r,j_i,\gamma_0),\qquad 0\le i<N,
\]
with \(c_{u_i}=1\).  Let the literal pre-terminal incidence be
\[
 \mathcal U_{X,k}^{\mathrm{pre},+}=\{u_0\},
\]
and set
\[
 t_h(u_0)=1,\qquad t_h(u_i)=0\quad(1\le i<N).
\]
The literal parent pair relation is the singleton
\[
 I_{\mathrm{pre},k}=\{(m,r)\}.
\]
Its rectangle contains all \(N\) ambient points.  It is parent-complete
and terminal-atomic faithful because \(u_0\) is the only terminal-active
point.  Nevertheless,
\begin{equation}
 P_m=H_m=T_m=1,\qquad
 \Delta_m=N-1,\qquad
 \widetilde P_m=N.
 \label{eq:tpc64-arbitrary-inflation-data}
\end{equation}
Consequently,
\begin{equation}
 \mathfrak I_X=N,\qquad
 \tau_{\mathrm{hyp}}=1,\qquad
 \tau_{\mathrm{rep}}=\frac1N.
 \label{eq:tpc64-arbitrary-inflation-constants}
\end{equation}
The terminal field and retained pair are unchanged; only the populated
parent rectangle has grown.

Taking \(N=2\) and replacing the single terminal-null unit coefficient by
one of modulus \(\sqrt{L-1}\) realizes every real \(L\ge1\).  Thus
\cref{prop:tpc64-inflation-sharpness,thm:tpc64-inflation-corrected-activation}
are sharp at every admissible value of the constants.
\end{example}

\begin{corollary}[One block and logarithmic label count give no inflation
control]
\label{cor:tpc64-one-block-no-inflation-control}
For every fixed \(A>0\), there is a family of examples with
\begin{equation}
 |K_X|=1,\qquad
 \mathfrak I_X=X^{A+o(1)}.
 \label{eq:tpc64-one-block-polynomial-inflation}
\end{equation}
Hence even the stronger statement \(|K_X|=1\), and therefore the usual
\(|K_X|=O(\log X)=X^{o(1)}\), supplies no upper bound on parent inflation.
\end{corollary}

\begin{proof}
In \cref{ex:tpc64-arbitrary-faithful-inflation}, take
\(N=\lceil X^A\rceil\).  All points have the same cofactor and hence the
same external cofactor-block label.
\end{proof}

This also proves that parent inflation is not a disguised block-count
loss.  A polynomial loss may occur entirely inside one block.

\subsection{New-only rows and terminal-zero rows}

\begin{proposition}[New-only row no-go]
\label{prop:tpc64-countermodel-new-only-row}
There are terminal-faithful populated repairs with a row \(m_1\) satisfying
\begin{equation}
 P_{m_1}=H_{m_1}=T_{m_1}=0
 <\widetilde P_{m_1}.
 \label{eq:tpc64-countermodel-new-only-data}
\end{equation}
For every such repair,
\begin{equation}
 \mathfrak I_X=+\infty,
 \qquad
 \tau_{\mathrm{rep}}=0.
 \label{eq:tpc64-countermodel-new-only-death}
\end{equation}
Thus no finite literal-to-repaired parent domination and no positive
full-row repaired activation theorem can hold.
\end{proposition}

\begin{proof}
Take a literal terminal-active atom on a row \(m_0\), with unit parent and
terminal square.  Add to the declared repair a different pair on a row
\(m_1\) whose populated rectangle contains one coordinate \(v\) with
\(c_v=1\) and \(t_h(v)=0\), and declare \(v\) to be the only ambient
coordinate over that added pair.  The extra coordinate is terminal-null, so
terminal faithfulness is preserved, but
\eqref{eq:tpc64-countermodel-new-only-data} holds with
\(\widetilde P_{m_1}=1\).  The row convention and
\cref{thm:tpc64-exact-parent-inflation,thm:tpc64-uniform-activation-minima}
give \eqref{eq:tpc64-countermodel-new-only-death}.  Equivalently, the row
direction \(e_{m_1}\) has positive repaired parent and zero terminal
energy.
\end{proof}

The canonical least parent-complete relation does not insert an arbitrary
extra row.  The point of the proposition is that any larger populated
repair, change of row coordinates, or claimed comparison must prove that
new-only rows are absent; terminal faithfulness alone does not prove it.

\begin{proposition}[Terminal-zero row kill]
\label{prop:tpc64-countermodel-terminal-zero-row}
If a required row satisfies
\begin{equation}
 P_{m_0}>0,\qquad H_{m_0}=T_{m_0}=0,
 \label{eq:tpc64-countermodel-terminal-zero-data}
\end{equation}
then
\begin{equation}
 \tau_{\mathrm{hyp}}=\tau_{\mathrm{rep}}=0
 \label{eq:tpc64-countermodel-terminal-zero-death}
\end{equation}
for every parent-complete terminal-faithful repair on a full coefficient
class containing \(e_{m_0}\).  Enlarging the retained pair relation cannot
repair the zero without changing the terminal field.
\end{proposition}

\begin{proof}
The literal row direction has positive parent and zero terminal energy,
so \(\tau_{\mathrm{hyp}}=0\).  Terminal faithfulness leaves \(T_{m_0}\)
unchanged, while parent completeness gives
\(\widetilde P_{m_0}\ge P_{m_0}>0\).  The same direction therefore forces
\(\tau_{\mathrm{rep}}=0\).
\end{proof}

A distinguished vector can avoid either bad row by having zero coefficient
there.  That is a different quantifier and yields only the weighted average
in \cref{thm:tpc64-distinguished-activation-average}.

\subsection{The terminal-active-parent tautology}

\begin{example}[Deleting the alignment defect by redefining the parent]
\label{ex:tpc64-terminal-active-parent-tautology}
Fix \(L\ge1\).  On one row, take two literal pre-terminal atoms:
\[
 |c_{u_0}|^2=1,\quad t_h(u_0)=1,
 \qquad
 |c_{u_1}|^2=L-1,\quad t_h(u_1)=0,
\]
omitting \(u_1\) when \(L=1\).  Then
\begin{equation}
 P_m=L,\qquad H_m=T_m=1,
 \qquad
 \frac{T_m}{P_m}=\frac1L.
 \label{eq:tpc64-tautology-true-activation}
\end{equation}
If one replaces the literal parent by the terminal-active incidence
\(\{u_0\}\), the newly defined parent mass is \(H_m=1\), and the displayed
ratio becomes
\begin{equation}
 \frac{T_m}{H_m}=1.
 \label{eq:tpc64-tautology-false-parent-ratio}
\end{equation}
The apparent improvement can be arbitrarily large, but it is obtained by
deleting the literal terminal-null parent mass \(L-1\).  It is not a lower
bound relative to the original parent.
\end{example}

The example is the exact reason that multiplier intensity is not itself
terminal activation.  In the notation of
\cref{thm:tpc64-exact-three-factor-activation}, redefining the parent as
the terminal-active support silently replaces the alignment factor
\(\alpha_m=1/L\) by \(1\).

\subsection{Multiplier intensity is not a probability}

\begin{example}[Unbounded literal multiplier intensity]
\label{ex:tpc64-unbounded-multiplier-intensity}
Take one literal terminal-active atom with \(|c_u|^2=1\) and
\(|t_h(u)|=M\), where \(M>0\).  Then
\begin{equation}
 P_m=H_m=1,\qquad
 T_m=M^2,\qquad
 \vartheta_m=M^2.
 \label{eq:tpc64-unbounded-intensity-data}
\end{equation}
The number \(M\) is arbitrary.  Hence \(\vartheta_m\) is a shaped
multiplier intensity and can exceed \(1\) by an arbitrary factor.
\end{example}

Any argument which clips \(T_m/H_m\) at one, interprets it as a survival
probability, or removes the literal shaped weight changes the physical
quadratic form.

\subsection{A largest block can be chosen only after positivity}

For \(z\in Z_X\), define the nonnegative shaped energy on block \(k\) by
\begin{equation}
 T_k(z):=\sum_{m\in\mathcal M_X}T_{k,m}|z_m|^2.
 \label{eq:tpc64-block-terminal-form}
\end{equation}
Exact block disintegration gives
\begin{equation}
 T(z)=\sum_{k\in K_X}T_k(z).
 \label{eq:tpc64-terminal-block-sum}
\end{equation}

\begin{theorem}[Largest-block quantifier and sharpness]
\label{thm:tpc64-largest-block-after-positivity}
Assume \(1\le L_X:=|K_X|<\infty\).  For each fixed vector \(z\),
\begin{equation}
 \boxed{
 \max_{k\in K_X}T_k(z)\ge\frac{T(z)}{L_X}.}
 \label{eq:tpc64-largest-block-bound}
\end{equation}
The constant \(L_X^{-1}\) is sharp.  Consequently:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item if a prior theorem gives
       \[
        T(z)\ge X^{-\lambda+o(1)}P(z)
       \]
       for one fixed distinguished \(z\), and
       \(L_X=O(\log X)\), then some block \(k=k(z,X)\) satisfies the same
       fixed-power lower bound up to \(X^{o(1)}\);
 \item if \(T(z)=0\), every block energy is zero, so the largest-block
       step creates no activation;
 \item the maximizing block may depend on the row or coefficient vector,
       and \eqref{eq:tpc64-largest-block-bound} alone does not select one
       block supporting a coefficient-uniform lower bound.
\end{enumerate}
\end{theorem}

\begin{proof}
The maximum of \(L_X\) nonnegative numbers is at least their average.
Equality holds when all \(T_k(z)=T(z)/L_X\), proving sharpness.  The first
consequence uses \(L_X^{-1}=X^{-o(1)}\); the second is immediate from
nonnegativity.

For the last assertion, take two rows and two blocks.  Put
\[
 P_{m_1}=P_{m_2}=1,\qquad
 T_{1,m_1}=1,\quad T_{2,m_2}=1,
\]
with the two cross terms zero.  The total terminal form equals the parent
form, so its uniform activation constant is one.  On block \(1\), the row
direction \(e_{m_2}\) has zero energy; on block \(2\), the direction
\(e_{m_1}\) has zero energy.  Thus neither single block has a positive
full-row activation constant.
\end{proof}

The block theorem is therefore downstream of activation, not a source of
activation.  A logarithmic number of blocks costs no fixed power only
after a positive total terminal estimate has been proved in the same
coefficient scope.

\subsection{Claim boundary}

These countermodels prove non-implications for finite parent and terminal
interfaces.  They show that terminal faithfulness does not control parent
inflation, that label count does not control populated parent mass, that
zero rows kill uniform activation, and that block selection cannot create
positivity.  They do not show that the literal arithmetic carrier has a
bad row or large inflation.  Conversely, none of the exact identities in
this paper proves positive physical activation, signed M\"obius
cancellation, a fixed-shift parity estimate, or a prime-pair lower bound.
