\section{Finite certificate and conclusion}
\label{sec:computation-conclusion}

The accompanying script
\texttt{experiments/signed\_label\_certificate.py} is a deterministic
finite certificate.  It checks the following identities independently of
the asymptotic proofs:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the unitary-divisor shell coefficient
 $\sum_{a\parallel r,a>1}(\Lambda(a)-1)
 =\log\rad(r)-2^{\omega(r)}+1$ on a finite range;
 \item the bijection between factor pairs $(n,m)$ and coordinates
 $(a,b,k)$, including endpoint and radial masks;
 \item Vaughan's identity and the hard-packet values on the finite
 prime/semiprime witness;
 \item the identical divisor signatures of
 \begin{equation}
  p=101,\qquad s=11\cdot13=143,\qquad R=10,
  \label{eq:finite-null-witness}
 \end{equation}
 together with their separation by a balanced factor row;
 \item the exact finite-fiber minimax radius and the Hilbert-space
 shift-coordinate radius for sample weights.
\end{enumerate}
The script writes a JSON record with all parameters and residuals, and the
unit test recomputes every assertion.  The certificate does not test the
Guth--Maynard or unitary-divisor Titchmarsh inputs.

The two quantifier regimes may be summarized without implication arrows:
\begin{center}
\small
\begin{tabular}{
 >{\raggedright\arraybackslash}p{0.17\textwidth}
 >{\raggedright\arraybackslash}p{0.33\textwidth}
 >{\raggedright\arraybackslash}p{0.33\textwidth}}
\toprule
 & All orientations $b$ & Endpoint orientation $b=1$\\
\midrule
Fixed $h$ & Fixed coprime-shell law in \cref{thm:fixed-shell-law}
& Unresolved fixed prime-pair covariance\\
Growing mean in $h$ & Full bounded-mask transfer
& Endpoint corollaries in \cref{cor:endpoint-centered-mean,cor:raw-endpoint-mean}\\
\bottomrule
\end{tabular}
\end{center}

The main conclusions are therefore separated cleanly by quantifier.
At every fixed nonzero shift, one nontrivial exact radial shell has an
explicit asymptotic; at $h=2$ its leading coefficient is
$6/\pi^2-1/3$.  Under a growing short-shift average of length
$H\geq X^{2/15+\eps}$, every bounded shift-independent label mask is
controlled simultaneously, including the prime-pair endpoint and every
masked target-recentered Vaughan packet.  An exact minimax theorem then
locates the information missing from local divisor signatures, and a
balanced bilinear row detects the resulting prime/semiprime null direction.

What remains is analytic rather than representational: obtain a
fixed-shift asymptotic, or cancellation after subtracting its correct local
main term, for a sharply localized Type-II packet while retaining the
endpoint label.  The fixed-shell law, the full-mask short-shift theorem,
and the null-space witness provide three independently checkable footholds
for that next step.  None is a fixed-shift prime-pair asymptotic or a
breach of the parity barrier.
