\section{Exact signed selectors in the joint label space}
\label{sec:dual-selectors}

We record the bilinear form of the tensor-Fej\'er identity from TPC-13.  It
is the precise sense in which a signed label is retained before any shift
average.

Let $J$ be a finite index set with pairwise distinct joint frequencies
\begin{equation}
 \xi_j=(\lambda_j,\rho_j)\in\R^2,
 \qquad j\in J,
 \label{eq:abstract-joint-frequencies}
\end{equation}
and define
\begin{equation}
 \cO_x(t,s)=\sum_{j\in J}x_j e^{i(t\lambda_j+s\rho_j)}.
 \label{eq:abstract-observation}
\end{equation}
Use the normalized Fej\'er kernel
\begin{equation}
 \kappa(t)=\frac2\pi\left(\frac{\sin(t/2)}t\right)^2,
 \qquad
 \widehat\kappa(\xi)=(1-|\xi|)_+.
 \label{eq:fejer-kernel}
\end{equation}

\begin{proposition}[Exact dual-mask identity]
\label{prop:dual-mask-identity}
Let $T,S>0$ and suppose that, for every $i\ne j$,
\begin{equation}
 T|\lambda_i-\lambda_j|\geq1
 \quad\text{or}\quad
 S|\rho_i-\rho_j|\geq1.
 \label{eq:pairwise-mask-separation}
\end{equation}
For arbitrary coefficient and mask vectors $x,\omega\in\C^J$,
\begin{equation}
 \frac1{TS}\iint_{\R^2}
 \kappa(t/T)\kappa(s/S)
 \cO_x(t,s)\overline{\cO_\omega(t,s)}\,dt\,ds
 =\sum_{j\in J}x_j\overline{\omega_j}.
 \label{eq:dual-mask-identity}
\end{equation}
Conversely, if \eqref{eq:pairwise-mask-separation} fails for one pair,
\eqref{eq:dual-mask-identity} fails for some $x,\omega$ supported on that
pair.
\end{proposition}

\begin{proof}
Expanding the integral, the $(i,j)$ term is multiplied by
\[
 \widehat\kappa(T(\lambda_i-\lambda_j))
 \widehat\kappa(S(\rho_i-\rho_j)).
\]
The diagonal multiplier is $1$, and every off-diagonal multiplier vanishes
under \eqref{eq:pairwise-mask-separation}.  If that condition fails for one
pair, both multipliers are strictly positive; choosing $x$ and $\omega$ on
the pair leaves a nonzero cross term.
\end{proof}

For the factor coordinates \eqref{eq:gcd-coordinates}, use
\begin{equation}
 \lambda_{a,b,k}=\log(a/b),
 \qquad
 \rho_{a,b,k}=\log k.
 \label{eq:gcd-mellin-frequencies}
\end{equation}
The global gap bounds in TPC-13 permit
$T\asymp X$ and $S\asymp\sqrt X$.  Sectorwise filters use the smaller
anisotropic scales $T_R\asymp R$ and $S_R\asymp\sqrt{X/R}$ after each
sector is isolated.  We import those gap estimates; no new large-sieve
theorem is asserted here.

For a fixed shift $h$, set
\begin{equation}
 x_{a,b,k}(h;X,D)=
 \one_{ak>D}u(ak)\eta(abk^2+h)W(abk^2/X).
 \label{eq:arithmetic-joint-coefficient}
\end{equation}
For an arithmetic mask $\omega$, apply
\eqref{eq:dual-mask-identity} with dual vector $\overline\omega$.  It
recovers
\begin{equation}
 \sum_{a,b,k\geq1}x_{a,b,k}(h;X,D)
 \omega_{a,b,k}
 \label{eq:masked-linear-functional}
\end{equation}
without first replacing $x$ by $|x|^2$.  In particular,
\begin{align}
 \omega^{\rm end}_{a,b,k}&=\one_{b=k=1},
 \label{eq:endpoint-mask}\\
 \omega^{(k_0)}_{a,b,k}&=\one_{k=k_0},
 \label{eq:radial-layer-mask}\\
 \omega^{(a_0,b_0)}_{a,b,k}&=\one_{(a,b)=(a_0,b_0)}
 \label{eq:ray-mask}
\end{align}
select the endpoint, a radial layer, and a primitive ray, respectively.

\begin{proposition}[Commutation with translation averaging]
\label{prop:selector-translation-commutation}
Let the mask be independent of $h$.  Under
\eqref{eq:pairwise-mask-separation},
\begin{align}
 &\frac1H\sum_qG(q/H)
 \sum_jx_j(h_0+q)\overline{\omega_j}
 \notag\\
 &\quad={}
 \frac1{HTS}\sum_qG(q/H)
 \iint_{\R^2}\kappa(t/T)\kappa(s/S)
 \cO_{x(h_0+q)}(t,s)
 \overline{\cO_\omega(t,s)}\,dt\,ds.
 \label{eq:translation-mask-commutation}
\end{align}
\end{proposition}

\begin{proof}
All sums are finite and the Fej\'er kernels are integrable, so the assertion
is \cref{prop:dual-mask-identity} followed by Fubini's theorem.
\end{proof}

The proposition is an exact commuting-filter statement.  It does not make a
shift-dependent target mask legal.  If $\omega$ is allowed to inspect
$h$ and then retain only factorisations of $r+h$ favorable to primality,
the coefficient vector itself changes with the translated von Mangoldt
function and the short-interval transfer below does not apply.

The mask symbol $\omega_{a,b,k}$ is unrelated to the standard arithmetic
function $\omega(r)$ counting distinct prime divisors.  The context will
always distinguish them.
