\section{Why the positive theorems do not select a fixed prime pair}
\label{sec:fixed-shift-boundary}

There are two different losses in the preceding results.  The fixed-shift
law retains the shell $k=1$ but aggregates its orientations.  The full-mask
law retains every orientation but averages the shift.  Neither loss can be
reversed by an algebraic change of coordinates alone.

\subsection{One shift average does not recover one shift coordinate}

The following Hilbert-space calculation isolates the quantifier loss.
Let $Q$ be a finite shift set, let $w\in\C^Q\setminus\{0\}$, and observe
only
$A_w(z)=\langle z,w\rangle=\sum_{q\in Q}z_q\overline{w_q}$.

\begin{proposition}[Exact coordinate-recovery minimax]
\label{prop:shift-coordinate-minimax}
For $q_\ast\in Q$ and $B>0$,
\begin{align}
 &\inf_{\Phi:\C\to\C}
 \sup_{\|z\|_2\leq B}
 |z_{q_\ast}-\Phi(A_w(z))|
 \notag\\
 &\qquad={}
 B\left(
 1-\frac{|w_{q_\ast}|^2}{\|w\|_2^2}
 \right)^{1/2}.
 \label{eq:shift-coordinate-minimax}
\end{align}
\end{proposition}

\begin{proof}
As in \cref{thm:local-minimax}, the exact radius is $B$ times the norm of
the target functional on $\ker A_w$.  This is the distance from the
coordinate vector $e_{q_\ast}$ to $\operatorname{span}\{w\}$, which is
the right side of \eqref{eq:shift-coordinate-minimax}.  The orthogonal
projection also gives the optimal linear decoder, so allowing nonlinear
decoders does not reduce the radius.
\end{proof}

For the smooth weights in this paper,
\begin{equation}
 w_q=H^{-1}G(q/H),
 \qquad
 \|w\|_2^2\asymp_G H^{-1}.
 \label{eq:smooth-shift-vector}
\end{equation}
If the selected coordinate lies in the support, then
$|w_{q_\ast}|^2\ll_GH^{-2}$, and therefore the minimax radius is
\begin{equation}
 B\bigl(1-O_G(H^{-1})\bigr).
 \label{eq:smooth-shift-minimax-limit}
\end{equation}
If the coordinate lies outside the sampled window, then $w_{q_\ast}=0$
and the radius is exactly $B$.
On an unrestricted response ball, a growing smooth mean retains
asymptotically none of the stable information needed to recover one
coordinate.  Arithmetic prime-pair vectors are not arbitrary vectors, so
this proposition is not an impossibility theorem for twin primes.  It says
precisely why the averaged theorem, by itself, cannot be inverted at
$h=2$.

\subsection{Why the fixed shell does not isolate the endpoint}

At fixed $h$, the $k=1$ shell has the exact orientation decomposition
\begin{equation}
 \cK_h(X)=
 \sum_{\substack{a>1,\ b\geq1\\(a,b)=1}}
 u(a)\eta(ab+h)W(ab/X).
 \label{eq:fixed-shell-orientation-decomposition}
\end{equation}
The proof of \cref{thm:fixed-shell-law} first sums all orientations with
$ab=r$, producing the unitary-divisor coefficient
$\log\rad(r)-d^*(r)+1$.  Biao Wang's theorem estimates that aggregate.
It supplies no estimate uniform in a dual orientation mask and therefore
cannot be combined with the exact Fej\'er selector to retain only $b=1$.
For that mask the target is exactly
\begin{equation}
 \sum_a(\Lambda(a)-1)(\Lambda(a+h)-1)W(a/X),
 \label{eq:fixed-endpoint-boundary}
\end{equation}
the unresolved fixed-shift covariance.

The Hardy--Littlewood prime-pair conjecture predicts the local main-term
coefficient
\begin{equation}
 \sum_a(\Lambda(a)-1)(\Lambda(a+h)-1)W(a/X)
 \sim\bigl(\mathfrak S(h)-1\bigr)XI_0(W),
 \label{eq:expected-fixed-covariance}
\end{equation}
where $\mathfrak S(h)$ is the prime-pair singular series
\citep{HardyLittlewood1923}.  In particular,
$\mathfrak S(2)=2C_2$, with
\[
 C_2=\prod_{p>2}\left(1-\frac1{(p-1)^2}\right).
\]
Thus the expected $h=2$ covariance is
$(2C_2-1)XI_0(W)$, not zero.

This distinction is easy to lose: exact coordinate recovery is an
identity for a finite coefficient array, while an arithmetic asymptotic is
a norm estimate uniform over the selector needed for inversion.  The
former does not manufacture the latter.

\subsection{Sparse rays fall outside the natural-scale transfer}

The $\ell^2$ transfer is uniform over masks, but its absolute bound need
not be sharp at the natural size of every sparse mask.  Fix a primitive
orientation $(a_0,b_0)$.  Its product centers have the form
\begin{equation}
 r=a_0b_0k^2\asymp X,
 \label{eq:quadratic-ray-centers}
\end{equation}
so only $O_{a_0,b_0}(X^{1/2})$ centers occur.  The source coefficient has
\begin{equation}
 \|c_{a_0,b_0}\|_2
 \ll_{a_0,b_0,W}X^{1/4}\log X.
 \label{eq:quadratic-ray-coefficient-norm}
\end{equation}
Combining this with the global residual norm
\eqref{eq:translated-residual-l2} yields only
\begin{equation}
 \left|
 \sum_{r=a_0b_0k^2}c_{a_0,b_0}(r)
 \Delta_{X,H,h_0}(r)
 \right|
 \ll_A X^{3/4}(\log X)^{-A},
 \label{eq:sparse-ray-global-l2-bound}
\end{equation}
after renaming $A$.  For every fixed $A$, this is not $o(X^{1/2})$.
Thus the uniform theorem controls the full mask ball on the ambient
$X$-scale, but it does not give natural-scale cancellation on an
individual quadratic ray.  Such a result would require a restriction
estimate for the translated residual on sparse polynomial centers.

\subsection{The remaining fixed-shift gate}

The results can now be placed in a strict logical order:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item the joint GCD--Mellin coordinate preserves every finite factor
 label exactly;
 \item the fixed $k=1$ aggregate is evaluable at every prescribed
 $h\ne0$;
 \item all shift-independent signed labels are controllable after a
 growing short-shift mean;
 \item local divisor labels below the square-root gate possess an exact
 prime/semiprime null direction;
 \item a balanced bilinear row detects that direction, but estimating the
 corresponding fixed-$h$ arithmetic packet remains open.
\end{enumerate}

Accordingly, the next useful target is not another algebraic inversion.
It is a fixed-shift asymptotic, or cancellation after subtracting the
correct local main term, for a sufficiently localized Type-II packet with
enough uniformity to preserve the endpoint label.  Proving such an estimate
would be genuine analytic progress.  The present paper neither assumes nor
claims it.
