\section{Tensoring row phases with minimal alias tomography}
\label{sec:tpc40-alias-tensor}

We now combine the row theorem with the \(q=L+1\) quotient bank from
\cref{sec:tpc40-interface}.  The tensor calculation separates the
equality slice from the folded nuisance spectrum and shows that alias
tomography supplies no hidden row decorrelation.

\subsection{The separable product bank}

Let \(\Phi=(\phi_{t\alpha})\) be a weighted row phase bank with weights
\(w_t\), recovery coefficients \(a_t\), amplification \(\cA\), and Gram
\(G\).  Define
\begin{equation}
 \cY_{t,\nu}
 :=\sum_{\alpha=1}^{R}\sum_{k=-L}^{L}
 \phi_{t\alpha}\omega^{\nu k}x_{\alpha,k},
 \qquad
 0\le\nu<q.
 \label{eq:tpc40-product-measurements}
\end{equation}
Give the pair \((t,\nu)\) weight \(w_t/q\) and recovery coefficient
\begin{equation}
 \widetilde a_{t,\nu}=\frac{a_t}{q}.
 \label{eq:tpc40-product-recovery-coefficient}
\end{equation}

\begin{theorem}[Tensor recovery and amplification conservation]
\label{thm:tpc40-tensor-recovery}
The product bank recovers the coherent equality slice:
\begin{equation}
 \sum_{t,\nu}\widetilde a_{t,\nu}\cY_{t,\nu}
 =\sum_{\alpha=1}^{R}x_{\alpha,0}.
 \label{eq:tpc40-product-recovery}
\end{equation}
Its normalized recovery amplification is exactly
\begin{equation}
 \widetilde{\cA}=\cA,
 \label{eq:tpc40-product-amplification}
\end{equation}
and its complete row--alias Gram is
\begin{equation}
 \widetilde G=G\otimes H_q,
 \label{eq:tpc40-product-Gram}
\end{equation}
where \(H_q\) is given by
\eqref{eq:tpc40-interface-Hq}.  On the zero--alias coordinate block,
\begin{equation}
 \widetilde G\big|_{k=\ell=0}=G.
 \label{eq:tpc40-zero-alias-Gram}
\end{equation}
Consequently
\begin{equation}
 \boxed{
 \cA\,\lambda_{\max}
 \left(\widetilde G\big|_{k=\ell=0}\right)\ge R.}
 \label{eq:tpc40-tensor-tradeoff}
\end{equation}
\end{theorem}

\begin{proof}
The coefficient of \(x_{\alpha,k}\) in the left side of
\eqref{eq:tpc40-product-recovery} is
\[
 \left(\sum_ta_t\phi_{t\alpha}\right)
 \left(\frac1q\sum_{\nu=0}^{q-1}\omega^{\nu k}\right)
 =\one_{k=0}.
\]
Moreover,
\[
 \sum_{t,\nu}
 \frac{|\widetilde a_{t,\nu}|^2}{w_t/q}
 =\sum_t\frac{|a_t|^2}{w_t}=\cA.
\]
The Gram factorization follows by separating the two phase sums.  Since
zero is a singleton residue in \([-L,L]\), \((H_q)_{00}=1\), proving
\eqref{eq:tpc40-zero-alias-Gram}.  Apply the recovery--coherence theorem
on that block.
\end{proof}

The full tensor operator has a nuisance factor two.  If
\(\lambda_1,\ldots,\lambda_R\) are the eigenvalues of \(G\), then for
each nonzero \(\lambda_j\) the corresponding nonzero tensor eigenvalues are
\begin{equation}
 2\lambda_j\quad(L\text{ copies for each }j),
 \qquad
 \lambda_j\quad(1\text{ copy for each }j).
 \label{eq:tpc40-product-spectrum}
\end{equation}
Zeros arise from the folded alias kernel and, when \(G\) is singular, also
from the outer row bank.  Thus the full operator norm is
\(2\|G\|_{\op}\) when \(L\ge1\), but the relevant
equality--slice coherence is \(\|G\|_{\op}\).  We do not insert the
irrelevant factor two into the sharp recovery tradeoff.

\begin{corollary}[Partial Fourier tensor spectrum]
\label{cor:tpc40-partial-Fourier-tensor}
For an \(r\)-row partial Fourier extremizer, the product bank has
\begin{equation}
 \widetilde\cA=r,
 \label{eq:tpc40-partial-tensor-A}
\end{equation}
and nonzero scalar spectrum
\begin{equation}
 \frac{2R}{r}\quad(rL\text{ times}),
 \qquad
 \frac{R}{r}\quad(r\text{ times}).
 \label{eq:tpc40-partial-tensor-spectrum}
\end{equation}
The equality--slice eigenvalue is \(R/r\), and its product with the
recovery amplification is exactly \(R\).
\end{corollary}

\subsection{Coupled phases do not evade the zero slice}

Separable phases are not essential.  Let \(s\) index an arbitrary bank
with positive weights \(w_s\), and let
\begin{equation}
 \theta_{s,\alpha,k}\in\T
 \label{eq:tpc40-coupled-phase}
\end{equation}
depend jointly on row and alias.  Suppose coefficients \(a_s\) recover
the coherent equality slice universally:
\begin{equation}
 \sum_sa_s\theta_{s,\alpha,k}=\one_{k=0}
 \qquad
 (1\le\alpha\le R,\ -L\le k\le L).
 \label{eq:tpc40-coupled-recovery}
\end{equation}
Put \(\cA=\sum_s|a_s|^2/w_s\).

\begin{theorem}[Equality--slice rigidity for coupled banks]
\label{thm:tpc40-coupled-zero-slice}
Let
\begin{equation}
 G^{(0)}_{\alpha\beta}
 :=\sum_sw_s
 \overline{\theta_{s,\alpha,0}}\theta_{s,\beta,0}.
 \label{eq:tpc40-coupled-zero-Gram}
\end{equation}
Then
\begin{equation}
 \boxed{
 G^{(0)}\succeq\cA^{-1}\one\one^*,
 \qquad
 \cA\lambda_{\max}(G^{(0)})\ge R.}
 \label{eq:tpc40-coupled-zero-tradeoff}
\end{equation}
For arbitrary Hilbert atoms,
\begin{equation}
 \left\|\sum_{\alpha}x_{\alpha,0}\right\|^2
 \le
 \cA\sum_sw_s
 \left\|\sum_{\alpha,k}
 \theta_{s,\alpha,k}x_{\alpha,k}\right\|^2.
 \label{eq:tpc40-coupled-positive-dominance}
\end{equation}
\end{theorem}

\begin{proof}
Restrict \eqref{eq:tpc40-coupled-recovery} to \(k=0\).  The phase columns
\((\theta_{s,\alpha,0})_s\) form an exact weighted row bank with the same
recovery coefficients and amplification.  The Loewner theorem gives
\eqref{eq:tpc40-coupled-zero-tradeoff}.  The Hilbert--valued weighted
Cauchy inequality applied to the exact recovery gives
\eqref{eq:tpc40-coupled-positive-dominance}.
\end{proof}

Thus nonseparable coding, random row signs, and joint row--alias phase
design do not bypass the obstruction as long as recovery is universal and
the analytic step is a positive average of squared norms.  The no--go is
obtained by setting every nuisance alias to zero; no behavior away from
the target slice can repair it.

\subsection{The determinant bank is the unit--amplification endpoint}

For the TPC--39 determinant twists,
\begin{equation}
 \theta_{\nu,\alpha,k}=\omega^{\nu k}
 \label{eq:tpc40-determinant-phase}
\end{equation}
is independent of \(\alpha\).  On \(k=0\), every phase column is the same
constant vector.  Hence
\begin{equation}
 \cA=1,
 \qquad
 G^{(0)}=\one\one^*,
 \qquad
 \lambda_{\max}(G^{(0)})=R.
 \label{eq:tpc40-determinant-max-coherence}
\end{equation}
The survival of fixed--alias cross--row coherence in TPC--39 is therefore
the rigid equality case of the general theorem, not a defect of the
chosen proof of folded Parseval.
