\section{Exact certificate and claim ledger}
\label{sec:tpc40-certificate}

The structural proofs above are exact.  A companion standard--library
certificate checks their finite cyclic realizations using only integers,
\texttt{Fraction} arithmetic, modular character orthogonality, and exact
prime--order cyclotomic coordinates.  It does not use floating--point
eigenvalues or numerical tolerances.

\subsection{Certified identities}

The frozen certificate verifies:
\begin{enumerate}[label=(\roman*)]
 \item selected \(R\)-point DFT banks containing the constant frequency,
 including the exact recovery amplification \(A=r\), rank \(r\), spectrum
 \(R/r\), and product equality \(A\lambda=R\);
 \item balanced and unbalanced short--cycle residue banks, their bucket
 spectra, and equality in the product bound exactly for equal bucket
 sizes;
 \item all folded collisions and the spectrum \(2,1,0\), with
 multiplicities \(L,1,L\), for the minimal alias bank through the frozen
 range;
 \item the row--alias tensor spectrum
 \begin{equation}
  2R/r\quad(rL\text{ times}),
  \qquad
  R/r\quad(r\text{ times}),
  \label{eq:tpc40-certificate-tensor-spectrum}
 \end{equation}
 together with amplification conservation;
 \item exact Loewner Gram factorizations for deterministic root--of--unity
 phase banks; and
 \item the endpoint exponent identity
 \begin{equation}
  \frac{267}{400}-\frac1{400}
  =\frac{266}{400}=\frac{133}{200}.
  \label{eq:tpc40-certificate-endpoint-exponent}
 \end{equation}
\end{enumerate}

Running
\begin{quote}
\ttfamily
python experiments/tpc40\_certificate.py\\
python -O experiments/tpc40\_certificate.py
\end{quote}
produces byte--identical canonical JSON records.  The frozen run passes
\begin{equation}
 \boxed{2{,}230{,}446\text{ exact checks}.}
 \label{eq:tpc40-certificate-checks}
\end{equation}
It includes \(2{,}748\) selected DFT banks, \(4{,}081\) unbalanced bucket
compositions, \(19{,}656\) row--alias tensor cases, and \(300\) exact
cyclotomic Loewner cases.  Its certificate digest is
\begin{center}
\ttfamily\small
d925148e93bc0ecd57a3958bc6ffc0447f5116cfb0f188844e8b1c93b96020a0.
\end{center}
The SHA--256 hashes of the canonical JSON record and source are,
respectively,
\begin{center}
\ttfamily\small
94e68bc4884d80fcfc685edbee34f851c097bd49d425d31c47cd2b76ed751bd7,\\
2e15f17ced216acc300163e543d73d7b14878127b31478410983ff88aed6e2f3.
\end{center}

\subsection{What the certificate does not certify}

The computation verifies finite identities and implementation fidelity.
It is not statistical evidence for random M\"obius signs and not a test of
an asymptotic physical estimate.  The JSON claim ledger explicitly marks
as false any assertion that the certificate proves a twist--stable
physical bound, two-- or four--M\"obius cancellation, a parity breach, a
prime--pair asymptotic, or infinitely many twin primes.
