\section{Fourier extremizers and the sharp Pareto family}
\label{sec:tpc40-Fourier-extremizers}

The product lower bound is attained at every integer point between its two
endpoints.  The relevant cyclic bank uses rows of the \(R\)-point Fourier
matrix; replacing the \(R\)-point phases by a shorter modulus \(r\) gives a
different construction and introduces an integrality defect.

Let
\begin{equation}
 \zeta_R:=\exp(2\pi i/R).
 \label{eq:tpc40-Rth-root}
\end{equation}

\begin{theorem}[Partial-DFT extremizers]
\label{thm:tpc40-partial-DFT-extremizers}
Fix \(1\le r\le R\), choose any \(T\subset\mathbb Z/R\mathbb Z\) with
\(|T|=r\) and \(0\in T\), and let \(s\ge1\).  Put \(m=rs\), index the rows
by \((t,\ell)\in T\times\{1,\ldots,s\}\), and the columns by
\(\alpha\in\mathbb Z/R\mathbb Z\).  Define
\begin{equation}
 \Phi_{(t,\ell),\alpha}=\zeta_R^{t\alpha},
 \qquad w_{(t,\ell)}=\frac1{rs},
 \qquad
 a_{(t,\ell)}=\frac1s\one_{t=0}.
 \label{eq:tpc40-partial-DFT-bank}
\end{equation}
Then
\begin{equation}
 a^T\Phi=\one_R^T,
 \qquad
 A=r,
 \label{eq:tpc40-partial-DFT-recovery}
\end{equation}
and the Gram spectrum is
\begin{equation}
 \operatorname{spec}(G)
 =\left\{\frac Rr\ \text{with multiplicity }r,
          \quad0\ \text{with multiplicity }R-r\right\}.
 \label{eq:tpc40-partial-DFT-spectrum}
\end{equation}
In particular,
\begin{equation}
 A\lambda_{\max}(G)=r\frac Rr=R.
 \label{eq:tpc40-partial-DFT-Pareto-equality}
\end{equation}
Hence every pair
\begin{equation}
 (A,\lambda_{\max}(G))=\left(r,\frac Rr\right),
 \qquad1\le r\le R,
 \label{eq:tpc40-integer-Pareto-family}
\end{equation}
lies on the sharp Pareto boundary.
\end{theorem}

\begin{proof}
The only rows used by the recovery coefficient are the \(s\) copies of
the constant Fourier row.  Their coefficients sum to one, proving exact
recovery.  Moreover,
\[
 A=rs\cdot s\left|\frac1s\right|^2=r.
\]
The distinct rows selected from the unnormalized \(R\)-point Fourier
matrix are mutually orthogonal and each has squared norm \(R\).  Equal
replication therefore gives
\[
 G=\frac1r\sum_{t\in T}v_t^*v_t,
 \qquad (v_t)_\alpha=\zeta_R^{t\alpha},
\]
whose \(r\) nonzero eigenvalues are all \(R/r\).  Finally, the constant
column vector is an \(R/r\)-eigenvector because the zero Fourier row is
present.  The Pareto assertion follows from
\cref{thm:tpc40-weighted-Loewner}: a strict improvement in one coordinate
without worsening the other would make the product smaller than \(R\).
\end{proof}

The endpoint \(r=1\) is the completely coherent, unit-amplification bank;
\(r=R\) is the full DFT with \(G=I_R\) and \(A=R\).

\subsection{A continuous weighted boundary}

Assume \(R\ge2\).  The weighted model also realizes every real point of
the hyperbola between the endpoints.  For \(1<A_0\le R\), take the full \(R\)-point Fourier
matrix, put
\begin{equation}
 w_0=\frac1{A_0},
 \qquad
 w_t=\frac{A_0-1}{A_0(R-1)}\quad(1\le t<R),
 \qquad
 a=e_0,
 \label{eq:tpc40-continuous-Fourier-weights}
\end{equation}
where \(e_0\) selects the constant Fourier row.

\begin{corollary}[Continuous weighted Pareto boundary]
\label{cor:tpc40-continuous-weighted-boundary}
The bank in \eqref{eq:tpc40-continuous-Fourier-weights} satisfies
\begin{equation}
 A=A_0,
 \qquad
 \lambda_{\max}(G)=\frac R{A_0},
 \qquad
 A\lambda_{\max}(G)=R.
 \label{eq:tpc40-continuous-Pareto-pair}
\end{equation}
The missing endpoint \(A_0=1\), excluded from this \(R\)-row formula by
the strict positivity of all \(w_t\), is realized by the one-row constant
bank.
\end{corollary}

\begin{proof}
Writing \(F_R\) for the unnormalized Fourier matrix, one has
\(G=F_R^*WF_R\).  Since \(R^{-1/2}F_R\) is unitary, the eigenvalues of
\(G\) are \(Rw_t\).  For \(A_0\le R\), \(w_0\ge w_t\) for \(t\ne0\), so
the largest eigenvalue is \(R/A_0\).  Also
\(A=|a_0|^2/w_0=A_0\).
\end{proof}

For uniform rows, rational points in this continuous family can equally be
implemented by repeating Fourier rows in the corresponding proportions.

\subsection{The short-cycle bucket defect}

There is a tempting but inequivalent construction.  Take \(m=r\), use
phases modulo \(r\), and index the \(R\) columns consecutively:
\begin{equation}
 \Phi^{\rm short}_{t,\alpha}
 =\exp(2\pi i t\alpha/r),
 \qquad0\le t<r,\quad0\le\alpha<R,
 \label{eq:tpc40-short-cycle-bank}
\end{equation}
with uniform row weights and recovery \(a=e_0\).  Then \(A=r\), but
\begin{equation}
 G^{\rm short}_{\alpha\beta}
 =\one_{\alpha\equiv\beta\pmod r}.
 \label{eq:tpc40-short-cycle-Gram}
\end{equation}
Its nonzero eigenvalues are the sizes of the \(r\) residue buckets, hence
\begin{equation}
 \lambda_{\max}(G^{\rm short})
 =\left\lceil\frac Rr\right\rceil.
 \label{eq:tpc40-short-cycle-lambda}
\end{equation}
Therefore this balanced short-cycle bank lies on the sharp Pareto boundary
if and only if \(r\mid R\).  If \(r\nmid R\), the partial \(R\)-point DFT
bank of \cref{thm:tpc40-partial-DFT-extremizers} has the same amplification
\(r\) and the strictly smaller coherence radius \(R/r\).  Thus balance
within the short-cycle subclass does not by itself prove global Pareto
optimality.
