\section{Inherited equality slice and endpoint ledger}
\label{sec:tpc40-interface}

We restate only the part of TPC--39 needed to connect the finite phase
theorem to the physical packet.  All estimates below that refer to
M\"obius cancellation remain explicitly conditional.

\subsection{Rows and aliases}

On one retained packet,
\begin{equation}
 QJ\asymp X,
 \qquad
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)}.
 \label{eq:tpc40-interface-QJ}
\end{equation}
Let \(\mathscr A\) be its active row set, of cardinality
\begin{equation}
 R_{\rm row}:=|\mathscr A|\ll X^{o(1)}Q.
 \label{eq:tpc40-interface-row-count}
\end{equation}
The main finite theorems use an arbitrary integer \(R\); physical
specializations are stated for any selected \(R\)-row subpacket.  When a
dense packet with \(R=X^{o(1)}Q\) is invoked, that density is written as
an additional hypothesis rather than inferred from
\eqref{eq:tpc40-interface-row-count}.

Choose the three orbit--scale primes of TPC--39 and put
\begin{equation}
 M=q_1q_2q_3=X^{399/400+o(1)}.
 \label{eq:tpc40-interface-M}
\end{equation}
Every completed determinant lies in \(|F|\le B\), where \(B\asymp X\).
Define
\begin{equation}
 L=\left\lfloor\frac BM\right\rfloor,
 \qquad
 q=L+1,
 \qquad
 K_B=2L+1.
 \label{eq:tpc40-interface-alias}
\end{equation}
Then
\begin{equation}
 q\asymp K_B\asymp X^{1/400+o(1)},
 \qquad
 qM>B.
 \label{eq:tpc40-interface-alias-scale}
\end{equation}

For each row \(\alpha\), alias \(-L\le k\le L\), and any remaining
physical output index, gather the actual row coefficient, mask,
M\"obius atom, and cutoff into a Hilbert vector
\begin{equation}
 x_{\alpha,k}\in\cH.
 \label{eq:tpc40-interface-atoms}
\end{equation}
The raw alias column and equality output are
\begin{equation}
 \cZ_k=\sum_{\alpha\in\mathscr A}x_{\alpha,k},
 \qquad
 \cR_0=\cZ_0.
 \label{eq:tpc40-interface-columns}
\end{equation}
The finite theorems treat the \(x_{\alpha,k}\) as arbitrary.  This is
exactly what makes their later physical conclusion coefficient blind.

\subsection{Minimal alias tomography}

Let \(\omega=\ee{1/q}\).  The TPC--39 measurements are
\begin{equation}
 \cY_\nu
 =\sum_{k=-L}^{L}\omega^{\nu k}\cZ_k,
 \qquad 0\le\nu<q.
 \label{eq:tpc40-interface-Ynu}
\end{equation}
They recover equality with unit normalized amplification:
\begin{equation}
 \cZ_0=\frac1q\sum_{\nu=0}^{q-1}\cY_\nu.
 \label{eq:tpc40-interface-recovery}
\end{equation}
Their normalized Gram in the alias coordinate is
\begin{equation}
 (H_q)_{k\ell}
 =\one_{k\equiv\ell\pmod q}.
 \label{eq:tpc40-interface-Hq}
\end{equation}
Because \(q=L+1\), its scalar spectrum is
\begin{equation}
 2\quad(L\text{ times}),
 \qquad
 1\quad(1\text{ time}),
 \qquad
 0\quad(L\text{ times}).
 \label{eq:tpc40-interface-Hq-spectrum}
\end{equation}
The eigenvalue one belongs to the isolated zero alias.  The eigenvalues
two and zero belong to folded nuisance pairs; they must not be confused
with the equality--slice recovery constant.

\subsection{Energy budget and the surviving term}

Put
\begin{equation}
 B_0=Q^2J.
 \label{eq:tpc40-interface-B0}
\end{equation}
The inherited target is
\begin{equation}
 \|\cR_0\|^2
 \ll X^{o(1)}\frac{Q^3}{J},
 \label{eq:tpc40-interface-target}
\end{equation}
and the exact exponent identity is
\begin{equation}
 B_0K_B=X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc40-interface-budget}
\end{equation}
TPC--39 closes the complete terminal atomic diagonal at this scale.  The
unproved part is off diagonal.  At fixed alias it contains cross--row
terms, and between the folded aliases it contains a gap of size
\(qM\in(B,B+M]\).  The determinant phase \(\omega^{\nu k}\) is constant
in \(\alpha\), so no row cancellation follows from
\eqref{eq:tpc40-interface-Ynu}.

The purpose of the present paper is to decide whether an additional
coefficient--blind row phase can repair this last defect while preserving
\eqref{eq:tpc40-interface-recovery} at low amplification.  It cannot;
the exact obstruction is finite dimensional and independent of any
unproved statement about M\"obius correlations.
