\section{Literature interface and the arithmetic boundary}
\label{sec:tpc40-literature-boundary}

The phase banks considered here sit at an interface between two theories
with very different logical content.  Finite--frame and large--sieve
inequalities describe the geometry of the measurement map.  Results on
correlations of multiplicative functions describe cancellation in the
measured coefficients.  The former can optimize sampling, conditioning,
and erasure tolerance, but it cannot supply the latter.  This section
records the exact scope of the relevant literature so that no deterministic
frame statement is mistaken for the twist--stable M\"obius estimate left
open by TPC--39.

\subsection{What finite--frame geometry does prove}

Let \(v_1,\ldots,v_m\) be unit vectors in a \(d\)-dimensional complex
Hilbert space.  The first Welch bound gives, for \(m>d\),
\begin{equation}
 \max_{r\ne s}|\langle v_r,v_s\rangle|^2
 \ge \frac{m-d}{d(m-1)}.
 \label{eq:tpc40-Welch-bound}
\end{equation}
Equality requires the vectors to form an equiangular tight frame
\citep{Welch1974}.  Thus the Welch bound is a lower bound for worst--pair
coherence.  It is not, by itself, a theorem about a prescribed recovery
functional, and it does not say that deleting a measurement preserves
exact recovery.

The averaged analogue is the frame potential
\begin{equation}
 \operatorname{FP}(v_1,\ldots,v_m)
 :=\sum_{r,s=1}^{m}|\langle v_r,v_s\rangle|^2.
 \label{eq:tpc40-frame-potential}
\end{equation}
For \(m\ge d\),
\begin{equation}
 \operatorname{FP}(v_1,\ldots,v_m)\ge \frac{m^2}{d},
 \label{eq:tpc40-frame-potential-bound}
\end{equation}
with equality precisely at unit--norm tight frames
\citep{BenedettoFickus2003}.  This is the appropriate background when a
phase bank is optimized by total squared correlation rather than maximum
coherence.  Tightness minimizes a declared geometric energy; it does not
make structured arithmetic coefficients independent.

There is a necessary qualification in the present setting.  A minimally
sampled phase map on all \(2L+1\) alias coordinates has a nontrivial
kernel.  Consequently it has no finite condition number as an operator on
the full alias space.  A statement such as ``unit condition number'' is
valid only after the quotient, range, or recoverable subspace has been
specified.  The regular polygon bank is an exact Fourier system on its
folded quotient; that fact neither removes the folded kernel nor controls
the norm of a physical M\"obius synthesis.

The analytic large sieve supplies a complementary Bessel bound.  If
\(x_1,\ldots,x_R\) are separated modulo one by at least \(\delta\), then
for a trigonometric polynomial supported on an interval of \(N\) integers
one has, up to harmless endpoint conventions,
\begin{equation}
 \sum_{r=1}^{R}
 \left|\sum_n a_n\,\mathrm e(nx_r)\right|^2
 \ll (N+\delta^{-1})\sum_n|a_n|^2.
 \label{eq:tpc40-large-sieve-form}
\end{equation}
This is the separated--frequency form established sharply by
\citet{MontgomeryVaughan1973}.  It bounds the norm of an analysis operator
by the input \(\ell^2\)-mass.  It does not decrease that mass, and it does
not force cancellation between two M\"obius atoms.  In the TPC--39 folded
Parseval identity the equality column \(\|\mathscr Z_0\|^2\) is already a
positive summand.  No application of
\eqref{eq:tpc40-large-sieve-form} can erase this summand without an
additional arithmetic estimate.

The division of labor is therefore exact:
\begin{equation}
 \boxed{\text{frame geometry does not imply arithmetic decorrelation.}}
 \label{eq:tpc40-frame-arithmetic-boundary}
\end{equation}

\subsection{Nearby M\"obius theorems and their quantifiers}

Several deep results come close to one face of the physical gate, but each
changes at least one essential quantifier.

First, \citet{KlurmanMangerelTeravainen2023} prove small variance for sums
of a bounded multiplicative function in residue classes modulo \(q\), for
almost all \(q=o(x)\), with stronger exceptional--set conclusions in
special modulus families and an every--modulus conclusion under their
stated GRH hypothesis.  This is the closest existing theorem to the
large--modulus, short--progression geometry of the terminal packet.  It is
nevertheless a scalar residue--class variance theorem.  It does not
include the prescribed CRT modulus, the physical row mask, coherent row
synthesis, or the affine four--M\"obius form.  At the endpoint \(K=x/M\),
its schematic error
\begin{equation}
 \varepsilon\varphi(M)K^2
 \label{eq:tpc40-KMT-schematic-error}
\end{equation}
reaches the scalar diagonal scale \(MK\) only if
\(\varepsilon\ll K^{-1}x^{o(1)}\).  The available M\"obius savings are
logarithmic rather than this fixed power.  GRH changes the exceptional
modulus quantifier, not this missing factor.

Second, \citet{TeravainenWalker2025} prove a logarithmically averaged
two--point Elliott theorem on convex Bohr sets.  Their additive--character
lemma gives cancellation for two fixed affine forms twisted by a fixed
linear phase.  This is especially relevant conceptually because the
terminal two--M\"obius term can also be displayed as an affine correlation
with a phase.  In the present problem, however, the affine coefficients,
shifts, modulus, and rational phase denominator all move with \(X\); the
desired quantity is a natural square energy with row weights.  Moreover,
their higher--point statement generally gives a nontrivial bound away from
the trivial maximum, not a vanishing four--point correlation.  It therefore
cannot be substituted for the physical gate.

Third, the averaged Chowla theorem of
\citet{MatomakiRadziwillTao2015} obtains cancellation after averaging the
shift parameters.  It applies to correlations of arbitrary fixed order
and is the natural comparison for the two-- and four--point terms produced
after squaring.  The TPC shifts, by contrast, occupy a sparse,
algebraically prescribed family tied to one CRT modulus.  Shift--average
cancellation does not imply a uniform estimate on that family.  The
quantitative savings in that method are also logarithmic, not the
\(K^{-1}\)-scale saving demanded by the endpoint ledger.

Local Fourier results change a different quantifier.  The short--interval
Fourier--uniformity theorem of \citet{MatomakiRadziwillTao2020} averages
the origin of the interval while taking a supremum over linear phases.  Its
higher--order extension proves averaged local nilsequence and Gowers
uniformity \citep{MatomakiRadziwillTaoTeravainenZiegler2023}.  These are
among the strongest available tools for phase--uniform cancellation on
short intervals, but a contiguous interval with averaged origin is not a
length--\(K\) progression of step \(M\) at one specified large modulus.
Neither paper contains the row--synthesis norm required here.

For fixed shifts there are two further landmarks.  \citet{Tao2016} proves
the two--point Chowla--Elliott correlation with logarithmic averaging.
\citet{TaoTeravainen2019} obtain unweighted two--point Chowla cancellation
at almost all scales.  In both comparisons the affine data are fixed
before the asymptotic limit; the TPC data grow with \(X\), and the desired
bound must hold along the prescribed endpoint sequence with quantitative
uniformity.  A fixed--parameter or almost--all--scales theorem cannot be
promoted to that moving--parameter assertion.

Finally, classical uniform exponential--sum cancellation for one
M\"obius factor \citep{Davenport1937} and strong M\"obius orthogonality to
fixed nilsequences \citep{GreenTao2012} justify viewing a phase twist itself
as benign.  They do not survive the logical operation needed here: after
the physical norm is squared, the coefficient is a product of two or four
M\"obius values rather than a single M\"obius function against a
deterministic phase.

\subsection{The precise remaining upgrade}

The missing input is therefore not another conditioning theorem for the
finite Fourier bank.  It is a moving--parameter decorrelation estimate,
uniform over the prescribed CRT modulus \(M=M(X)\), the minimal phases
\(0\le\nu<q=q(X)\), the physical row family, and the terminal support.  It
must control a natural \(L^2\) synthesis containing both two-- and
four--M\"obius off--diagonal terms at the diagonal scale.  Existing results
instead average shifts, interval origins, moduli, or scales; use
logarithmic averages; keep the affine data fixed; or treat only one
multiplicative factor.

Accordingly, none of the cited theorems proves the twist--stable physical
estimate, a parity breach, a Hardy--Littlewood asymptotic, or the
twin--prime conjecture.  Their correct role is to identify the nearest
available inputs and, just as importantly, to expose the exact quantifier
upgrade that a positive continuation would have to supply.
