\section{The corrected route after phase--geometry closure}
\label{sec:tpc40-next-gate}

Within the declared class of unimodular banks, positive weights, universal
recovery, and positive square--energy estimation, the finite question is
now settled.  Exact recovery and row decorrelation satisfy a sharp
conservation law; enlarging a bank inside this class cannot change it.  The
remaining options must use information absent from an arbitrary Hilbert
column family or leave this class.

\subsection{What is unconditional}

This paper proves without a M\"obius hypothesis:
\begin{enumerate}[label=(\roman*)]
 \item the weighted Loewner domination for every exact recovery bank;
 \item the optimal pseudoinverse formula for recovery amplification;
 \item the sharp product law between recovery amplification and coherent
 row eigenvalue;
 \item rigidity at unit amplification and the exact cost of complete row
 orthogonality;
 \item all integer points of the sharp boundary, and its continuous
 weighted extension, realized by Fourier banks;
 \item stability under \(L^2\)-approximate recovery;
 \item diagonal invariance for Hilbert row atoms;
 \item tensor conservation for the minimal TPC--39 alias bank; and
 \item equality--slice rigidity for arbitrary coupled row--alias phases.
\end{enumerate}

These statements close the coefficient--blind positive phase--frame route.
They do not estimate the physical coefficient vector.

\subsection{Route C: coefficient--specific coherent--mode avoidance}

Let \(G\) be a row Gram arising from a convenient redundant phase bank,
and let \(v_{\rm phys}\) denote the actual vector of row--M\"obius
coefficients after all masks and reassembly.  A reusable positive theorem
would bound
\begin{equation}
 \|\Pi_{\rm coh}v_{\rm phys}\|^2
 \label{eq:tpc40-next-coherent-projection}
\end{equation}
at a scale smaller than the operator worst case, where
\(\Pi_{\rm coh}\) is the high--eigenvalue row subspace.  The present
no--go does not address such a coefficient--specific projection.  A proof
would have to exploit M\"obius/source signs, the row--gcd mask, or a
dispersion identity that is false for arbitrary atoms.

\subsection{Route S: a signed amplitude estimate}

The Loewner obstruction applies when the analytic step replaces the exact
recovery combination by a positive square energy.  One may instead retain
the signed or complex recovery functional before Cauchy.  At the level of
the original scalar shell, this means estimating the matched bilinear
polarization directly rather than controlling both column energies
separately.  Such a route can use cancellation between polarizations and
between phase measurements, but no coefficient--free frame inequality
supplies that cancellation.

The required theorem must be stated for the actual physical functional.
Calling it a consequence of Fourier orthogonality would merely reinsert
the target under another name.

\subsection{Route M: the explicit moving M\"obius correlation}

At the terminal layer, the remaining same--row term contains
\begin{equation}
 \mu(n)\mu(n+dM)
 \label{eq:tpc40-next-two-Mobius}
\end{equation}
for structured, scale--dependent \(d\), while cross--row expansion
contains an affine four--M\"obius form with the physical row weights.
An averaged theorem for a declared subfamily of rows, aliases, auxiliary
triples, or shifts would be genuine partial progress if it produces a
quantitative off--diagonal saving beyond the invariant atomic diagonal.

Nearby results average at least one different variable, use logarithmic
weights, keep the affine data fixed, or obtain only logarithmic savings.
They do not currently give the \(X^{-1/400}\)-scale improvement needed by
the endpoint packet.  The next arithmetic paper should therefore target a
specific sublayer and record its exact quantifiers rather than invoke a
generic ``M\"obius randomness'' principle.

\subsection{Route W: a new superwindow architecture}

One may abandon the orbit--prime coordinate constraints and construct a
composite no--wrap modulus closer to \(qM\).  This would require new
proofs of zero--face absorption, unit coordinate ranges, target synthesis,
and physical completion.  No--wrap alone does not imply suppression of the
equality coefficient: that coefficient and its synthesis norm must be
recomputed in the new architecture.  If they remain unsuppressed, as they
do in the fixed orbit--prime system of
\cref{sec:tpc40-superwindow}, a physical sign estimate still remains.

\subsection{Parity boundary}

The two-- and four--M\"obius terms are consistent with the classical
parity obstruction for sieve methods
\citep{HeathBrown1982Parity,IwaniecKowalski2004}.  Recovery--decorrelation
uncertainty neither proves that these correlations are large nor rules out
a coefficient--specific cancellation theorem.  It proves only that
universal positive phase geometry cannot be that theorem.  No parity
breach, Hardy--Littlewood asymptotic, or twin--prime conclusion follows.
