\section{Physical endpoint: what phase geometry can and cannot buy}
\label{sec:tpc40-physical-endpoint}

We now insert the finite tradeoff into the ledger of
\cref{sec:tpc40-interface}.  Every conclusion in this section is a method
statement.  It does not assert that the actual M\"obius vector saturates a
coherent eigenmode.

\subsection{The atomic diagonal is invariant}

For Hilbert row atoms \(x_1,\ldots,x_R\), a weighted phase bank has energy
\begin{align}
 \cE_{\Phi}(x)
 &:=\sum_tw_t\left\|\sum_\alpha
 \phi_{t\alpha}x_\alpha\right\|^2
 \notag\\
 &=\sum_{\alpha,\beta}
 G_{\alpha\beta}\langle x_\alpha,x_\beta\rangle.
 \label{eq:tpc40-physical-bank-energy}
\end{align}
Since \(|\phi_{t\alpha}|=1\) and \(\sum_tw_t=1\),
\begin{equation}
 G_{\alpha\alpha}=1.
 \label{eq:tpc40-physical-unit-diagonal}
\end{equation}
Therefore the atomic diagonal in \eqref{eq:tpc40-physical-bank-energy} is
always
\begin{equation}
 \boxed{\sum_{\alpha=1}^{R}\|x_\alpha\|^2,}
 \label{eq:tpc40-physical-diagonal-invariance}
\end{equation}
independently of the number or choice of row phases.  Phasing can only
redistribute the off--diagonal terms.

If the bank universally recovers the coherent row sum, the Loewner
theorem simultaneously gives
\begin{equation}
 \cE_{\Phi}(x)
 \ge\frac1\cA
 \left\|\sum_\alpha x_\alpha\right\|^2.
 \label{eq:tpc40-physical-energy-dominates-target}
\end{equation}
Thus an upper bound \(\cE_{\Phi}(x)\le\mathcal B\) yields only
\begin{equation}
 \left\|\sum_\alpha x_\alpha\right\|^2
 \le\cA\mathcal B.
 \label{eq:tpc40-physical-recovery-cost}
\end{equation}

\subsection{The diagonal--coherence dilemma}

In the TPC--39 terminal packet, the complete atomic diagonal already has
the endpoint size
\begin{equation}
 \cD_{\rm term}
 \ll X^{o(1)}B_0K_B
 =X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc40-physical-diagonal-target}
\end{equation}
Normalized row phasing does not reduce this quantity.  Consequently, a
coefficient--blind argument that bounds the whole bank energy only at the
diagonal scale and then invokes
\eqref{eq:tpc40-physical-recovery-cost} must keep
\begin{equation}
 \cA=X^{o(1)}
 \label{eq:tpc40-physical-subpolynomial-A}
\end{equation}
to retain the endpoint target.  But then every \(R\)-row subpacket obeys
\begin{equation}
 \lambda_{\max}(G)
 \ge\frac{R}{\cA}=R\,X^{-o(1)}.
 \label{eq:tpc40-physical-residual-coherence}
\end{equation}
Nearly the full coherent row mode remains.  Complete row orthogonality
would instead require \(\cA\ge R\), multiplying the already sharp
diagonal ledger by \(R\).

The partial Fourier extremizers make the conservation literal.  Using
\(r\) Fourier measurements reduces the coherent eigenvalue from \(R\) to
\(R/r\), but the recovery cost becomes \(r\).  Their product is \(R\),
and the diagonal in \eqref{eq:tpc40-physical-diagonal-invariance} does not
move.  No choice of \(r\) turns the known diagonal estimate into the
desired coherent estimate without additional arithmetic information.

\subsection{A measurement--dimension lower bound}

Every \(m\)-measurement row Gram has
\begin{equation}
 \rank G\le m,
 \qquad
 \tr G=R.
 \label{eq:tpc40-physical-rank-trace}
\end{equation}
Hence
\begin{equation}
 \lambda_{\max}(G)\ge\frac Rm.
 \label{eq:tpc40-physical-dimension-bound}
\end{equation}
Suppose, only for scale comparison, that a dense active packet has
\begin{equation}
 R=X^{o(1)}Q
 \label{eq:tpc40-physical-dense-packet}
\end{equation}
and that one attempts to reuse only
\(m\asymp K_B=X^{1/400+o(1)}\) joint phase slots.  Then
\begin{equation}
 \lambda_{\max}(G)
 \ge X^{266/400-o(1)}.
 \label{eq:tpc40-physical-266-bound}
\end{equation}
This exponent is a conditional dense--packet specialization of the exact
finite rank bound; it is not inferred from the row upper bound alone.

\subsection{The scoped no--go}

Combining the preceding results gives the following precise conclusion.

\begin{corollary}[Universal diagonal majorants pay the row dimension]
\label{cor:tpc40-physical-no-go}
Suppose an exact weighted phase bank satisfies the coefficient--blind
Bessel majorant
\begin{equation}
 \cE_{\Phi}(x)
 \le C\sum_{\alpha=1}^{R}\|x_\alpha\|^2
 \label{eq:tpc40-universal-Bessel-majorant}
\end{equation}
for every Hilbert space and every row family.  Then
\begin{equation}
 \boxed{
 C\ge\lambda_{\max}(G),
 \qquad
 \cA C\ge R.}
 \label{eq:tpc40-universal-Bessel-cost}
\end{equation}
Consequently its universal recovered bound is
\begin{equation}
 \left\|\sum_{\alpha=1}^{R}x_\alpha\right\|^2
 \le\cA C\sum_{\alpha=1}^{R}\|x_\alpha\|^2,
 \label{eq:tpc40-universal-recovered-Bessel}
\end{equation}
and the coefficient--blind constant in this route cannot be smaller than
\(R\).
\end{corollary}

\begin{proof}
It suffices to take the Hilbert space to be \(\C\).  Then
\eqref{eq:tpc40-universal-Bessel-majorant} is the matrix inequality
\(G\preceq CI_R\), so \(C\ge\lambda_{\max}(G)\).  Combine this with
\(\cA\lambda_{\max}(G)\ge R\).  The recovered estimate follows from
\eqref{eq:tpc40-physical-recovery-cost}.
\end{proof}

Thus a universal diagonal--only majorant cannot close the TPC--39 gate at
the same diagonal scale on a polynomially large row packet.  Unit or
subpolynomial recovery amplification leaves a polynomial coherent mode;
full decorrelation pays a polynomial recovery loss while preserving the
diagonal.

The corollary says nothing about a proof that uses the actual signs and
weights of \(x_{\alpha,k}\).  A coefficient--specific vector may have a
small projection onto the coherent eigenspace even when the operator norm
is large.  Proving precisely that statement would be genuine arithmetic
progress and is not ruled out here.
