\section{Comparison with the multiplicative superwindow door}
\label{sec:tpc40-superwindow}

TPC--39 isolates a second architecture: enlarge the multiplicative CRT
modulus until it exceeds the determinant window.  This removes aliases
without additive tomography, but it does not create M\"obius cancellation.
The endpoint scales quantify the granularity cost.

\subsection{The orbit--prime granularity gap}

The inherited multiplicative coordinates use primes
\(q_i\asymp J\), and their product is
\begin{equation}
 M=q_1q_2q_3=X^{399/400+o(1)}.
 \label{eq:tpc40-superwindow-M}
\end{equation}
The smallest no--wrap factor required after this product is only
\begin{equation}
 q=L+1\asymp\frac BM=X^{1/400+o(1)}.
 \label{eq:tpc40-superwindow-additive-factor}
\end{equation}
By contrast, an additional coordinate satisfying the same orbit--prime
range has size \(p_4\asymp J=X^{133/400+o(1)}\).  Its multiplicative
superwindow \(M_4=Mp_4\) obeys
\begin{equation}
 \frac{M_4}{B}
 \asymp\frac{p_4}{q}
 =X^{132/400+o(1)}.
 \label{eq:tpc40-superwindow-overshoot}
\end{equation}
Thus the fourth multiplicative coordinate overshoots the exact no--wrap
factor by \(X^{33/100+o(1)}\).  Additive quotient tomography is far more
granular: it implements the effective modulus \(qM>B\) using \(q\)
unimodular measurements.

Equation \eqref{eq:tpc40-superwindow-overshoot} is specific to the
inherited architecture in which every new multiplicative coordinate must
lie at the orbit scale.  It is not a theorem that every possible composite
superwindow has this cost; smaller factors would require a new zero--face,
unit--coordinate, and physical synthesis analysis.

\subsection{No--wrap is not arithmetic closure}

For a squarefree product \(R=\prod_{i=1}^{s}p_i\), the full target face
has equality coefficient
\begin{equation}
 A_R=\prod_{i=1}^{s}\left(1-\frac1{p_i-1}\right).
 \label{eq:tpc40-superwindow-equality-coefficient}
\end{equation}
With a fixed number of orbit--scale primes,
\begin{equation}
 A_R=1-O_s(J^{-1}).
 \label{eq:tpc40-superwindow-equality-unsuppressed}
\end{equation}
Hence a no--wrap modulus removes the alias copies but leaves the original
equality vector with asymptotic coefficient one.  Its dominant target
squared singular value is of order \(R\), as computed in TPC--38 and
compared with the alias count in TPC--39.  The superwindow therefore
trades alias multiplicity for multiplicative synthesis scale; it does not
weaken the equality M\"obius form.

The additive and multiplicative doors have complementary strengths.
Additive tomography reaches the exact no--wrap scale with optimal recovery
amplification, but the present theorem shows that a further universal row
phase cannot decorrelate for free.  A fourth multiplicative coordinate
removes aliases directly, but overresolves the window and retains the full
equality coefficient.  Both routes return to the same coefficient--specific
arithmetic boundary.
