\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Orbit-Sliced Gram Energy at the Q3 Gate: Gram-Copy Diagonal Closure, Collision Savings, and the Terminal Mobius Boundary},
 pdfauthor={Liang Wang},
 pdfsubject={An exact TT-star decomposition and an orbit-sliced energy reduction for the distinguished zero-frequency shell in a primitive Mobius residual},
 pdfkeywords={Mobius correlation, TT-star, Gram matrix, orbit energy, divisor incidence, zero frequency, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cE}{\mathcal E}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\op}{\operatorname{op}}

\title{\textbf{Orbit--Sliced Gram Energy at the \(Q^3\) Gate:}\\
\textbf{Gram--Copy Diagonal Closure, Collision Savings,}\\
\textbf{and the Terminal M\"obius Boundary}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
We continue the distinguished zero--frequency analysis of a matched
prime--M\"obius cutoff shell.  The preceding paper reduces the remaining
physical amplitude to two column energies \(E_L,E_R\) and shows that

\[
 E_L+E_R\ll X^{o(1)}Q^3
 \quad\Longrightarrow\quad
 |\mathcal S_{\rm sh}^{\rm all}|\ll X^{o(1)}Q^2.
\]

Here we perform the corresponding physical \(TT^*\) expansion.  Opening
the ultra divisor and the actual row-gcd projector gives an exact Gram
kernel.  If \(v_1,v_2\) are the two projector divisors, then

\[
 |\cG_L(\xi_1,\xi_2)|
 \ll X^{o(1)}\left(L+\frac{Q}{[v_1,v_2]}\right),
\]

with a symmetric right-hand statement.  This incidence gain degenerates
on the principal layer \(v_1=v_2=1\), so it is not itself the required
energy estimate.

We then isolate several unconditional pieces.  The whole Gram-copy
(same-input-row) diagonal satisfies

\[
 E_{L,\Delta}+E_{R,\Delta}\ll X^{o(1)}Q^2J^2.
\]

At \(Q=X^{267/400+o(1)}\) and \(J=X^{133/400+o(1)}\), this is
\(Q^3X^{-1/400+o(1)}\): the complete Gram-copy diagonal crosses the \(Q^3\)
gate with a genuine power margin.  The absolute target-collision mass
with \(m_1j_1=m_2j_2\) is smaller, \(O(X^{o(1)}Q^2J)\).  The absolute
shared-ultra mass with \(u_1=u_2>T\gg J\) is
\(O(X^{o(1)}Q^3J^2/T)\), saving the full factor \(T\) from the
absolute baseline but still missing the gate by \(J^2/T\).  On a fixed
row it forces the two orbit times to be equal.  More generally,

\[
 (mj+h,mj'+h)=(mj+h,j-j'),
\]

which is the two-time counterpart of the earlier two-row target-content
identity.

The main reduction is an orbit-sliced energy.  Put

\[
 Y^L_{\gamma,j}
 =\sum_\alpha\gamma_\alpha^{(1)}
   \mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\alpha}(j),
 \qquad
 V_L=\sum_{\gamma,j}|Y^L_{\gamma,j}|^2,
\]

and define \(V_R\) symmetrically.  Exact Cauchy--Schwarz gives

\[
 E_L+E_R\ll X^{o(1)}J(V_L+V_R).
\]

Consequently \(V_L+V_R\ll X^{o(1)}Q^3/J\) is sufficient for the former
\(Q^3\) gate.  Its orbit-sliced Gram-copy diagonal is only
\(O(X^{o(1)}Q^2J)\), smaller than
the allowance by \(X^{1/400+o(1)}\).  Thus the unresolved object is a
near-diagonal-scale, same-time averaged row correlation rather than the
original two-time column energy.

Finally, on the high--\(\beta\) endpoint packet, the divisor range in
each ultra increment contains the terminal value \(u=mj+h\); its
coefficient is zero when \(\mu(mj+h)=0\).  On this layer the row and
target signs fuse as
\(\mu(d)\mu(\ell dj+h)\), and \(TT^*\) produces an averaged four-M\"obius
row correlation.  An exact coherent zero-pair-diagonal model attains
\(E\asymp Q^3J^2\), proving that cardinality, equal-pair deletion, and
absolute envelopes alone cannot yield the desired \(Q^3\) bound.
This is a method obstruction, not a lower bound for the physical energy.
No affine Chowla estimate, prime-pair asymptotic, positivity theorem,
twin-prime theorem, or breach of sieve parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; \(TT^*\) dispersion;
Gram energy; orbit slicing; divisor collision; zero frequency; parity
boundary.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary 11B25,
11L07, 15A18.

\input{sections/introduction}
\input{sections/physical-interface}
\input{sections/exact-gram}
\input{sections/unconditional-blocks}
\input{sections/orbit-sliced-reduction}
\input{sections/terminal-barrier}
\input{sections/high-beta-roadmap}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
