\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\Vv}{\mathcal V}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cW}{\mathcal W}
\newcommand{\one}{\mathbf 1}
\newcommand{\e}{\mathrm e}
\newcommand{\rad}{\operatorname{rad}}

\hypersetup{
  pdftitle={Orbit-Band Projection and Mesoscopic Spectral Transfer for an Actual-Coefficient Determinant Sector},
  pdfauthor={Liang Wang},
  pdfsubject={A projected orbit-frequency theorem at the TPC large-prime determinant interface},
  pdfkeywords={Mobius function, determinant equation, orbit projection, shift spectrum, Poisson summation, parity problem}
}

\title{\bfseries Orbit-Band Projection and Mesoscopic\\
Spectral Transfer for an Actual-Coefficient\\
Determinant Sector}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The large-prime determinant sector in the twin-prime-correlation (TPC)
sequence has a smooth orbit variable but an output vector whose orbit
coordinate is not uniformly band limited.  This is the first of four
transfer gates left by the preceding shift-spectral analysis.  We act
on the literal residual output coordinate: after zero extension in the
physical orbit variable, let \(\Pi_\Omega\) be the fiberwise orthogonal
 Fourier projection onto the half-width-\(\Omega\) comb around
\(H_0^{-1}\mathbb Z/\mathbb Z\), leaving the opposite row and the
physical residual label \(s=d(m)r\) unchanged.
For a progression-restricted orbit profile with Fourier bandwidth
\(\Sigma\), we prove that the projected completed determinant packet
has the exact shift-spectral gap
\[
 \frac{\Omega+\Sigma/J}{M_-}<\|\alpha\|_{\mathbb T}
 <\frac{H_0^{-1}-\Omega-\Sigma/J}{M_+}.
\]
The theorem is Hilbert valued and permits arbitrary arithmetic
coefficients on the prime, cofactor, and source variables.  We then
apply a canonical comb cutoff to the complete vector-valued
actual TPC source--mask profile; the proved projective representation
is used only to estimate its complement.  The discarded tails have
 super-polynomially small leakage, so the projected frozen shift family
 built from the literal physical \(h_0\)-coefficient field inherits
 rapid decay throughout a slightly shrunken gap.  At the inherited TPC
endpoint, an orbit band with time--bandwidth size
\(X^{1/400+o(1)}\) retains the nonempty range
\[
 X^{-399/400+o(1)}<\|\alpha\|_{\mathbb T}
 <X^{-267/400+o(1)}.
\]
The projection is contractive, commutes with the residual M\"obius
unitary, and has exact physical-window trace \(2H_0N\Omega\) per
scalar non-orbit fiber.  It is
injective on every nonzero finitely supported orbit vector; however,
an explicit finite-difference family shows that no uniform fraction of
 the residual norm must lie in this band.  Thus an
 actual-residual-output sector with growing time--bandwidth trace crosses
 the orbit-frequency gate, while the
high-frequency complement, atomic normalization, alias unfolding, and
fixed-shift localization remain open.  At the physical intercept this
is the actual-coefficient residual synthesis, not the native affine
physical Gram face.  The shift family outside that intercept is
frozen-coefficient, and no fixed-shift TPC closure,
parity breach, or twin-prime conclusion is claimed.
\end{abstract}

\noindent\textbf{Keywords:} determinant equation; orbit-frequency
projection; shift spectrum; M\"obius correlation; Poisson summation;
time--bandwidth concentration; parity problem.

\medskip
\noindent\textbf{Convention.}
We write \(\e(x)=\exp(2\pi i x)\), identify
\(\T=\R/\Z\), and put
\(\|\alpha\|_{\T}=\min_{k\in\Z}|\alpha-k|\).
Fourier transforms on \(\R\) use
\(\widehat f(\xi)=\int_{\R}f(x)\e(-x\xi)\,dx\); the unitary
Fourier transform on \(\ell^2(\Z)\) is
\((\mathscr Fy)(\beta)=\sum_{j\in\Z}y_j\e(-j\beta)\).

\medskip
\noindent\textbf{MSC 2020:} Primary 11L07, 11N35; Secondary 42A38,
47B38, 11N36.

\input{sections/introduction}
\input{sections/physical-interface}
\input{sections/orbit-projector}
\input{sections/exact-transfer}
\input{sections/smooth-transfer}
\input{sections/actual-reassembly}
\input{sections/endpoint-ledger}
\input{sections/mass-frontier}
\input{sections/boundaries-next-gate}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
