\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Common-Target Content in a Primitive Mobius Tail: Row-Orbit Pruning, Cross-Factor Pruning, and the Coprime-Core Gate},
 pdfauthor={Liang Wang},
 pdfsubject={Unconditional pruning by the full common content of two affine targets in a primitive Mobius-tail residual},
 pdfkeywords={Mobius tail, target gcd, row-orbit incidence, cross-content, sparse fibers}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cE}{\mathcal E}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cK}{\mathcal K}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cW}{\mathcal W}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Common-Target Content in a Primitive M\"obius Tail:}\\
\textbf{Row--Orbit Pruning, Cross-Factor Pruning,}\\
\textbf{and the Coprime-Core Gate}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let
\[
 N_m(j)=mj+h,\qquad N_n(j)=nj+h
\]
be two positive affine targets in the primitive opened-row packet of
the preceding M\"obius-tail reduction.  The orbit length is
$J=X^{1-\beta+o(1)}$, the rows have size
$Q=X^{\beta+o(1)}$, and $QJ\asymp X$; $\mathscr D$ below denotes the
fixed packet data.  Previous reflected-incidence
bounds prune sectors with large common content in the selected
divisor variables.  They do not use the full target content
\[
 \cG_{m,n}(j):=(N_m(j),N_n(j)).
\]

On the primitive orbit we exploit the exact identity
\[
 \cG_{m,n}(j)=(N_m(j),m-n),
\]
so the full target gcd divides the row difference.  For a fixed row
pair, its exact values therefore range over only the divisors of
$|m-n|$.  Combining this divisor sparsity with the opened-row
$\ell^1$ mass gives, for each of the two mixed raw channels and the
both-ultra raw channel, the unconditional
bound
\[
 \cS_{\cG>Z}
 \ll_{\eps,h,\mathscr D}X^\eps
 \left(Q^2+\frac{JQ^2}{Z}\right)
 \ll_{\eps,h,\mathscr D}X^\eps
 \left(Q^2+\frac{XQ}{Z}\right).
\]
Thus $Z\ge X^\eta$ produces a fixed-power saving from the natural
scale $XQ$, with exponent
$\min\{\eta,1-\beta\}$ up to endpoint losses.

There is a second interpretation in the both-ultra channel.  If
\[
 N_m=rU,\qquad N_n=sV,
\]
put $g=(r,s)$, $e=(U,V)$ and write
$r=gr_0$, $s=gs_0$, $U=eU_0$, $V=eV_0$.  Then, without any
coprimality assumption between $g$ and $e$,
\[
 \cG_{m,n}(j)
 =ge(r_0,V_0)(s_0,U_0)\mid m-n.
\]
Consequently every sector with polynomially large cross-content
on the left is power-small.  This includes sectors with
$(r,s)=1$, which are outside the large reflected-content theorem.

At the high-$\beta$ sample $\beta=267/400$, take
$r,s=X^{1/4+o(1)}$, $(r,s)=X^{o(1)}$, and
$(U,V)=X^{2/5+o(1)}$.  The reflected lcm is
$X^{1/2+o(1)}>J$, while the preceding absolute-incidence method has
zero saving on this negligible-reflected-content cell.  The new
target-content estimate
has relaxed margin $133/400$: every fixed exponent below this value is
available.

The argument is absolute and uses neither M\"obius-sign cancellation
nor a Chowla--Elliott input.  It does not close the small-target-content
core or the complete ultra-long residual, and it yields no prime-pair
asymptotic.  It isolates the next gate as signed dispersion on the
small-target-content residual, with the fully coprime target sector as
its sharp model.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; common target
content; row--orbit incidence; cross-factor gcd; sparse fiber.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11B25, 11D45.

\input{sections/introduction}
\input{sections/physical-interface}
\input{sections/target-gcd-geometry}
\input{sections/row-orbit-pruning}
\input{sections/cross-content}
\input{sections/high-beta-ledger}
\input{sections/comparison-next-gate}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
