\section{Exact certificate, numerical diagnostic, and conclusion}
\label{sec:certificate-conclusion}

The proofs above are analytic and do not depend on computation.  The
accompanying package serves two more limited purposes: it checks every finite
normalization entering the operator, and it makes the difference between an
exact arithmetic identity and a finite Mangoldt experiment visible.

\subsection{The integer/rational certificate}

The reference certificate uses
\begin{equation}\label{eq:certificate-parameters}
 q=5\cdot7\cdot11=385,
 \qquad h=2.
\end{equation}
Here $\varphi(q)=240$,
\begin{equation}\label{eq:certificate-kappa}
 \kappa_q=\frac9{16},
 \qquad
 R_q=\varphi(q)\kappa_q=135.
\end{equation}
The program
\path{experiments/exact_transfer_certificate.py}
uses only integers and exact rational arithmetic from the standard library.
It verifies the following items.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item The pointwise inclusion-exclusion identity is checked for all
 $240^2=57{,}600$ unit pairs.
 \item For every $d\mid385$, the map $J_{2,d}(a)=-2a^{-1}$ is checked to be
 an involution.  Its fixed points, two-cycles, and exact $\pm1$ eigenspace
 dimensions are recorded.
 \item The direct vector $\mathsf P_{385,2}\beta$ is compared entry by entry
 with the involution-bundle formula \eqref{eq:involution-bundle} for a
 deterministic signed observable.
 \item The principal mode and the seven nonprincipal real quadratic modes of
 exact conductor $d\mid385$ are checked.  Their normalized multiplier
 magnitudes are exactly
 \begin{equation}\label{eq:certificate-multipliers}
  1,\ \frac13,\ \frac15,\ \frac19,\
  \frac1{15},\ \frac1{27},\ \frac1{45},\ \frac1{135},
 \end{equation}
 corresponding respectively to
 $d=1,5,7,11,35,55,77,385$.
 \item The row-main identity
 \begin{equation}\label{eq:certificate-row-main}
  \frac{mN}{\varphi(mq)}
  \sum_{\substack{b\in G_q\\(mb+h,q)=1}}\beta(b)
  =\frac{mN}{\varphi(m)}(\mathsf P_{q,h}\beta)(m)
 \end{equation}
 is verified exactly on every eligible test row.
 \item The reindexing \eqref{eq:AP-reindexing} is checked independently for
 an arbitrary integer target weight.  It is also checked for a formal von
 Mangoldt function represented as an integer coefficient vector in the
 independent basis $\{\log p\}$; no floating logarithm is used.
\end{enumerate}

The canonical payload SHA-256 is
\begin{center}
\small\ttfamily
030F20B495E68234CD3176795C1F3652D2F8792DE88C1BE49BC6A04F15FBCCFF.
\end{center}
The committed JSON file SHA-256 is
\begin{center}
\small\ttfamily
2EEE645F124CCDA3A50F4FB349550AC7195321EA5FC4410853142CD655E1E37E.
\end{center}
Regeneration is byte deterministic.  These hashes certify finite data and
code conventions, not the Bombieri--Vinogradov estimate.

\subsection{A separate finite Mangoldt diagnostic}

The optional NumPy script
\texttt{experiments/lambda\_transfer\_diagnostics.py} sieves the genuine
von Mangoldt function and computes each row twice: directly in $n$, and by
target arithmetic progressions modulo $mq$.  It then compares the common
row value with the exact rational local main term.  This is a sharp-box
diagnostic on $N<n\leq2N$, corresponding formally to $\cI_W=1$, rather than
an implementation of the smooth weight in the theorem.  A reference run takes
\begin{equation}\label{eq:floating-parameters}
 M=32,
 \quad N=2^{19},
 \quad X=MN=2^{24},
 \quad q=35,
 \quad h=2.
\end{equation}
There are $11$ eligible rows.  The reported quantities are shown in
\cref{tab:floating-diagnostic}.  The conductor-$d$ observables are the real
quadratic modes used by the script.

\begin{table}[ht]
\centering
\caption{Finite Mangoldt row diagnostic at \eqref{eq:floating-parameters}.}
\label{tab:floating-diagnostic}
\begin{tabular}{@{}rrrrr@{}}
\toprule
$d$ & $\sum_m|\text{main}_m|/X$
    & $\sum_m|\text{error}_m|/X$
    & RMS$/N$ & max$/N$\\
\midrule
$1$  & $2.6569\times10^{-1}$ & $7.1598\times10^{-4}$
     & $2.4501\times10^{-3}$ & $4.4714\times10^{-3}$\\
$5$  & $8.8565\times10^{-2}$ & $6.9698\times10^{-4}$
     & $3.0493\times10^{-3}$ & $8.0454\times10^{-3}$\\
$7$  & $5.3139\times10^{-2}$ & $5.4323\times10^{-4}$
     & $2.2140\times10^{-3}$ & $5.3955\times10^{-3}$\\
$35$ & $1.7713\times10^{-2}$ & $8.6667\times10^{-4}$
     & $2.8950\times10^{-3}$ & $4.7501\times10^{-3}$\\
\bottomrule
\end{tabular}
\end{table}

The largest discrepancy between the direct and progression computations is
$1.17\times10^{-10}$, at floating precision.  The second numeric column is
the finite supremum of the displayed row error over coefficients
$|\alpha_m|\leq1$, normalized by $X$.

This experiment is not a verification of
\cref{thm:operator-transfer}.  At the reference scale,
$2Mq/\sqrt X=0.546875$; the non-explicit logarithmic constant $B$ in the
asymptotic theorem is not instantiated.  Nor does a small error for four
finite modes say anything about the energy-bearing residual in
\eqref{eq:residual-energy}.  The floating output is therefore intentionally
separate from the canonical exact certificate.

\subsection{Reproducibility commands}

From the paper directory, the exact artifact and its zero-dependency test
runner are produced first; the floating smoke test additionally requires
NumPy:
\begin{verbatim}
python experiments/exact_transfer_certificate.py \
  --output experiments/data/exact-certificate.json
python experiments/test_exact_transfer_certificate.py
python experiments/test_lambda_transfer_diagnostics.py
\end{verbatim}
The test modules are also discoverable by \texttt{pytest}.  The floating
reference run is
\begin{verbatim}
python experiments/lambda_transfer_diagnostics.py \
  --m 32 --n 524288 --q 35 --h 2 \
  --conductors 1,5,7,35 \
  --output experiments/data/lambda-diagnostic.json
\end{verbatim}
Its output is not part of the exact certificate.

\subsection{Conclusion}

The paper advances the fixed-shift program by one controlled layer.  An
arbitrary second coefficient remains outside the one-sided
Bombieri--Vinogradov reduction, but a bounded low-period coefficient can be
passed through $\Lambda(mn+h)$ with an $\ell^1$ row error.  The leading term
is not merely a density: it is the exact finite operator
$\mathsf P_{q,h}$.  Its divisor-bundle involutions, conjugate-mode exchange,
higher conductor-exponent kernel, damping factors, and even trace moments
are all explicit.

The same result also draws a sharper boundary.  The actual modulus is $mq$,
the residue complexity costs $q$, and TPC-7 shows that the permitted
polylogarithmic periodic spaces miss asymptotically all of the
$\Lambda-1$ energy.  Thus the theorem genuinely reaches a prime target at a
prescribed $h$, including $h=2$, while stopping before the Type~II residual
that contains the fixed prime-pair difficulty.  That separation is the main
conclusion: a finite arithmetic dynamics survives the prime target exactly,
but it is not a substitute for the missing parity-sensitive estimate.
