\section{Introduction and exact scope}
\label{sec:introduction}

The transition from a rough target to a prime target changes the analytic
problem.  A finite sieve kernel can test the congruences
$mn+h\not\equiv0\pmod p$ for prescribed primes $p$, but primality is encoded
by the von Mangoldt weight $\Lambda(mn+h)$.  The preceding paper
\citep{WangTPCSix2026} made this distinction explicit: a one-sided
Bombieri--Vinogradov argument controls
\begin{equation}\label{eq:intro-one-sided}
 \sum_{M<m\leq2M}\alpha_m
 \sum_{n\geq1}\Lambda(mn+h)W(n/N),
 \qquad |\alpha_m|\leq1,
\end{equation}
in the Type~I range $M\leq x^{1/2}(\log x)^{-B}$, where $x=MN$.
Inserting an arbitrary bounded coefficient $\beta_n$ in the $n$-sum destroys
the direct reduction to one residue class modulo $m$.  The resulting form
leads to the unresolved bilinear/Type~II interface isolated there.

This paper treats a deliberately narrower coefficient class.  We suppose
that $\beta$ is periodic modulo a small integer $q$ and is supported on the
unit classes.  Splitting $n$ modulo $q$ turns each row into finitely many
prime sums in reduced residue classes modulo
\begin{equation}\label{eq:intro-combined-modulus}
 mq.
\end{equation}
The classical maximal Bombieri--Vinogradov theorem can then be applied after
two costs have been recorded: the level condition concerns $Mq$, and the
triangle inequality over the residue classes costs at most $q$.  Both costs
are harmless when
\begin{equation}\label{eq:intro-safe-range}
 q\leq(\log x)^C,
 \qquad
 2Mq\leq\frac{x^{1/2}}{(\log x)^B}.
\end{equation}
They are not harmless for a general power-sized period.

The principal point is not merely that a periodic coefficient can be
handled.  Its main term retains a finite operator.  For an odd $q$ with
$(q,h)=1$, put
\begin{equation}\label{eq:intro-local-operator}
 (\mathsf P_{q,h}\beta)(a)
 =\frac1{\varphi(q)}
  \sum_{\substack{b\in G_q\\(ab+h,q)=1}}\beta(b),
 \qquad
 G_q=(\Z/q\Z)^\times.
\end{equation}
The transfer theorem proved below has the rowwise main term
\begin{equation}\label{eq:intro-row-main}
 \frac{mN}{\varphi(m)}\left(\int_0^\infty W(t)\,dt\right)
 (\mathsf P_{q,h}\beta)(m).
\end{equation}
Thus the prime target does not average $\beta$ to a scalar.  It transports
the finite residue observable by $\mathsf P_{q,h}$.

\subsection{Results and logical status}

The paper contains four groups of statements.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item We determine $\mathsf P_{q,h}$ exactly.  After division by its row
 density
 \begin{equation}\label{eq:intro-kappa}
  \kappa_q=\prod_{p\mid q}\frac{p-2}{p-1},
 \end{equation}
 it is a self-adjoint Markov operator.  If a local character has conductor
 exponent at least two at some $p\mid q$, that mode is annihilated.  Every
 surviving nonprincipal mode has squarefree exact conductor $r$ and is
 exchanged with its conjugate with modulus
 \begin{equation}\label{eq:intro-damping}
  d(r)=\prod_{p\mid r}\frac1{p-2}.
 \end{equation}
 The phase is the arithmetic involution phase
 $(-1)^{\omega(r)}\overline{\chi(-h)}$.  This is the same exact multiplier
 that occurs in the rough centered kernel of
 \citet{WangTPCFive2026}.  The structural contribution here is to identify
 and prove the occurrence of this multiplier in the main term of the
 two-scale prime-target form.

 \item We prove an $\ell^1$ row-transfer theorem in the range
 \eqref{eq:intro-safe-range}.  It is uniform over all bounded unit-supported
 $q$-periodic coefficients and immediately gives coefficient-uniform
 bilinear forms.  The only analytic input is the classical maximal
 Bombieri--Vinogradov theorem
 \citep{Bombieri1965,Vinogradov1965,IwaniecKowalski2004}.

 \item We give exact character corollaries and add a Mangoldt weight in the
 $m$-coordinate.  Siegel--Walfisz then removes every nonprincipal periodic
 output mode.  This produces a two-prime/periodic-factor asymptotic in a
 strongly unbalanced Type~I range.  It does not make the periodic factor
 prime.

 \item We combine the transfer theorem with the finite-conductor
 energy-escape result of \citet{WangTPCSeven2026}.  Periods of size
 $(\log x)^C$ capture a vanishing proportion of the $L^2$ energy of
 $\Lambda-1$.  Therefore the present theorem cannot be specialized to the
 missing prime coefficient.  We record this as a strict theorem-interface
 statement, not as a universal impossibility result.
\end{enumerate}

The finite computations have the same separation.  An integer/rational
certificate verifies the local identities, conductor multipliers,
involutions, and exact arithmetic-progression reindexing.  A separate
floating-point experiment displays finite Mangoldt rows.  No analytic
theorem depends on either computation.

\subsection{Relation to known distribution results}

The estimate in this paper is an organized consequence of the standard
square-root level of distribution.  It is not a new
Bombieri--Vinogradov theorem.  Results beyond the square-root level are known
for special well-factorable weights and fixed residue structures
\citep{BombieriFriedlanderIwaniec1986,Maynard2025WellFactorable}; those
hypotheses do not directly cover the residue $mb+h$ modulo the moving
combined modulus $mq$ with an arbitrary periodic coefficient.

Much deeper cancellation estimates are known for isolated shifted-prime
character sums, beginning with earlier shifted-prime work and continuing
through stronger bounds of Kerr, as well as for general trace functions over
primes \citep{FriedlanderGongShparlinski2010,Kerr2021,
FouvryKowalskiMichel2014}.  Our object and purpose are different: the source
scale $m$ moves, the modulus is $mq$, arbitrary row coefficients are retained,
and the desired output is the complete finite operator $\mathsf P_{q,h}$.  We
make no priority claim for a new estimate of an isolated character sum.

An $L^2$ treatment using Barban--Davenport--Halberstam or variational forms
\citep{LewkoLewko2012} may reduce the elementary residue-splitting loss in
some ranges.  In the small-modulus regime, however, standard formulations
also contain terms that do not automatically yield the power-sized-period
version of our coefficient-uniform statement.  Such an extension is left as
an open analytic problem rather than inferred from an inapplicable mean
square bound.

\subsection{What is not proved}

For clarity, none of the following is a consequence of this paper.

\begin{itemize}
 \item There is no estimate with an arbitrary bounded second coefficient.
 \item There is no bound for the Vaughan Type~II hard packet identified in
 \citet{WangTPCSix2026}.
 \item There is no asymptotic for
 $\sum_n\Lambda(n)\Lambda(n+2)$ and no twin-prime lower bound.
 \item The parity obstruction is not broken.  The relevant limitations of
 finite sieve information remain those discussed in the asymptotic-sieve
 and parity literature \citep{FriedlanderIwaniec1998,Polymath2014}.
 \item The finite Markov spectrum below is not a spectral realization of
 the primes.  It is the exact Fourier form of a local congruence operator.
\end{itemize}

The gain is narrower but rigorous: one nontrivial second-coefficient class
crosses the prime target at a prescribed shift, and the surviving arithmetic
dynamics is computed exactly.
