\section{Modal transfer and a prime-weighted source}
\label{sec:modal-corollaries}

The operator theorem becomes especially transparent in character
coordinates.  Continue to use the Fourier convention
\eqref{eq:Fourier-convention}.  Combining
\cref{thm:operator-transfer,thm:exact-local-spectrum} gives the exact main
term
\begin{align}
 &\sum_m\alpha_m\sum_n\beta(n)\Lambda(mn+h)W(n/N)
 \notag\\
 &\quad=\kappa_qN\cI_W
 \sum_m\alpha_m\frac{m}{\varphi(m)}
 \sum_{\substack{\chi\in\wh G_q\\\chi\ \mathrm{surviving}}}
 B(\chi)c_h(\chi)\chi(m)
 +O_{A,C,h,W}\!\left(\frac{x}{(\log x)^A}\right).
 \label{eq:modal-transfer}
\end{align}
The sums over $m$ have the support and the range of
\cref{thm:operator-transfer}.

\subsection{One character mode}

\begin{corollary}[Primitive squarefree mode]
\label{cor:primitive-mode}
Let $q$ be odd and squarefree, let $\chi$ be primitive modulo $q$, and
suppose the hypotheses of \cref{thm:operator-transfer} hold.  Then
\begin{align}
 &\sum_m\alpha_m\sum_{n\geq1}
  \overline{\chi(n)}\Lambda(mn+h)W(n/N)
 \notag\\
 &\quad=
 \frac{\mu(q)\overline{\chi(-h)}}{\varphi(q)}
 N\cI_W
 \sum_m\alpha_m\frac{m}{\varphi(m)}\chi(m)
 +O_{A,C,h,W}\!\left(\frac{x}{(\log x)^A}\right).
 \label{eq:primitive-mode-transfer}
\end{align}
Here every Dirichlet character is extended by zero away from the unit
classes.  Replacing $\overline\chi$ by $\chi$ conjugates the phase and the
output character.
\end{corollary}

\begin{proof}
For a primitive character of squarefree modulus $q$,
$r_\chi=q$ and
\[
 \kappa_qc_h(\chi)
 =\prod_{p\mid q}\frac{p-2}{p-1}
  \frac{\mu(q)\overline{\chi(-h)}}{\prod_{p\mid q}(p-2)}
 =\frac{\mu(q)\overline{\chi(-h)}}{\varphi(q)}.
\]
Now apply \eqref{eq:modal-transfer}.
\end{proof}

This formula displays the arithmetic involution directly:
\begin{equation}\label{eq:mode-involution}
 \overline\chi(n)
 \quad\longmapsto\quad
 \overline{\chi(-h)}\chi(m).
\end{equation}
The scalar $\mu(q)/\varphi(q)$ is not a heuristic independence factor.  It
is the exact local main coefficient after the $q$ residue classes have been
passed through the prime target.

\begin{corollary}[Higher conductor-exponent annihilation]
\label{cor:higher-exponent-annihilation}
Let $\chi\in\wh G_q$ have local conductor exponent at least two at some
$p\mid q$.  Under the hypotheses of \cref{thm:operator-transfer},
\begin{equation}\label{eq:higher-mode-transfer}
 \sum_m\alpha_m\sum_{n\geq1}
 \overline{\chi(n)}\Lambda(mn+h)W(n/N)
 \ll_{A,C,h,W}\frac{x}{(\log x)^A}.
\end{equation}
\end{corollary}

The vanishing is a local algebraic cancellation in the leading term.  It is
not a zero-free-region statement about the $L$-function of $\chi$.

\subsection{Exact-conductor truncations}

For $1\leq R\leq\rad(q)$, define the surviving low-conductor part
\begin{equation}\label{eq:low-conductor-beta}
 \beta_{\leq R}(b)
 =\sum_{\substack{\chi\ \mathrm{surviving}\\r_\chi\leq R}}
 B(\chi)\overline{\chi(b)}.
\end{equation}
Its transferred main term is obtained from \eqref{eq:modal-transfer} by
restricting the same sum to $r_\chi\leq R$.  There is, however, a distinction
between exact conductor and actual integer period.

If \eqref{eq:low-conductor-beta} is retained as a function on $G_q$ and
extended by zero off the units modulo $q$, its period remains $q$ because of
the ambient unit cutoff.  The Bombieri--Vinogradov condition is then on
$Mq$.  If one instead starts with a primitive character of its genuine
modulus $r$, as in \cref{cor:primitive-mode}, the condition is on $Mr$.
This prevents a low exact-conductor label inside an enormous ambient CRT
space from being used to evade the combined-modulus boundary.

For a finite sum of primitive modes of possibly different genuine periods,
the proof applies term by term.  A sufficient polylogarithmic complexity
budget, with every $r_j$ odd and $(r_j,h)=1$, is
\begin{equation}\label{eq:mode-complexity-budget}
 \sum_j|\gamma_j|r_j\leq(\log x)^C,
 \qquad
 2M\max_j r_j\leq x^{1/2}(\log x)^{-B}.
\end{equation}
This is a convenient corollary of the residue-class proof, not an optimal
large-sieve statement.

\subsection{Adding a prime weight in the source coordinate}

The nonprincipal output modes in \eqref{eq:modal-transfer} need not vanish
for arbitrary $\alpha_m$: one may choose $\alpha_m$ to align with a character.
They do vanish after placing a prime weight on the $m$-coordinate.

\begin{corollary}[Prime source and periodic factor]
\label{cor:prime-source-periodic-factor}
Fix $\delta,A,C>0$, let $W_1,W_2\in C_c^1((0,\infty))$, and suppose
$\supp W_1\subset[1,2]$.  Let $q\geq3$ be odd with $(q,h)=1$, let
$\beta:G_q\to\C$ satisfy $\|\beta\|_\infty\leq1$, and extend $\beta$
$q$-periodically to the integers and by zero on nonunit residue classes.
Put $x=MN$ and assume
\begin{equation}\label{eq:prime-source-range}
 M\geq x^\delta,
 \qquad
 q\leq(\log M)^C,
 \qquad
 2Mq\leq\frac{x^{1/2}}{(\log x)^B},
\end{equation}
where $B=B(A,C,\delta,h,W_1,W_2)$ is sufficiently large.  Then
\begin{align}
 &\sum_{\substack{m,n\geq1\\(m,hq)=1}}
 \Lambda(m)W_1(m/M)\beta(n)
 \Lambda(mn+h)W_2(n/N)
 \notag\\
 &\quad=
 \kappa_q B(\one)MN
 \left(\int_0^\infty W_1(u)\,du\right)
 \left(\int_0^\infty W_2(v)\,dv\right)
 +O_{A,C,\delta,h,W_1,W_2}\!\left(\frac{x}{(\log x)^A}\right),
 \label{eq:prime-source-asymptotic}
\end{align}
where
\begin{equation}\label{eq:beta-unit-mean}
 B(\one)=\frac1{\varphi(q)}\sum_{b\in G_q}\beta(b).
\end{equation}
In particular, a unit-mean-zero periodic factor gives an arbitrary
logarithmic saving.
\end{corollary}

\begin{proof}
Apply \cref{thm:operator-transfer} with row coefficient
$\Lambda(m)W_1(m/M)$.  Dividing this coefficient by $O(\log x)$ first and
requesting one additional logarithmic saving justifies the application.
Substitute \eqref{eq:P-Fourier-formula} in the main term.

For the principal character, the prime number theorem and partial summation
give
\begin{equation}\label{eq:principal-prime-source}
 \sum_m\Lambda(m)W_1(m/M)\frac{m}{\varphi(m)}
 =M\int_0^\infty W_1(u)\,du
 +O_A\!\left(\frac{M}{(\log M)^A}\right).
\end{equation}
The factor $m/\varphi(m)$ may be replaced by $1$: on primes the difference
contributes $O_{W_1}(\log M)$, and higher prime powers contribute
$O_{W_1}(M^{1/2}(\log M)^2)$.

For every nonprincipal $\chi\in\wh G_q$, the Siegel--Walfisz theorem,
uniformly for $q\leq(\log M)^C$, gives
\begin{equation}\label{eq:nonprincipal-prime-source}
 \sum_m\Lambda(m)W_1(m/M)\frac{m}{\varphi(m)}\chi(m)
 \ll_{A,C,W_1}\frac{M}{(\log M)^A}.
\end{equation}
The rows inherit the condition $(m,hq)=1$.  Its excluded prime powers obey
the uniform bound
\begin{equation}\label{eq:excluded-prime-source-powers}
 \sum_{\substack{M<p^k\leq2M\\p\mid hq}}
 \Lambda(p^k)\frac{p}{p-1}
 \ll_h\log(2q),
\end{equation}
because a fixed prime contributes only $O(1)$ powers to a dyadic interval.
They are therefore absorbed in the same saving.  There are at most
$\varphi(q)\leq(\log M)^C$
surviving modes, while $|B(\chi)|,|c_h(\chi)|\leq1$.  Increasing the
Siegel--Walfisz saving absorbs their total.  Finally
$M\geq x^\delta$ makes $\log M$ comparable to $\log x$, proving
\eqref{eq:prime-source-asymptotic}.
\end{proof}

The range \eqref{eq:prime-source-range} is strongly unbalanced.  Ignoring
logarithmic factors, the combined-modulus condition says
\begin{equation}\label{eq:type-I-imbalance}
 N\gtrsim Mq^2.
\end{equation}
This is still a Type~I theorem.  The periodic factor has crossed the prime
target, but it has not become a second unrestricted prime weight.
