\begin{abstract}
Let \(P\) be a finite real symmetric nonnegative matrix with zero
diagonal, and let \(H=H^*\) be a scalar complex Hermitian matrix with
zero diagonal and \(|H_{ij}|\le P_{ij}\).  The familiar Perron
majorization
\[
 \|H\|\le\rho(|H|)\le\rho(P)
\]
does not identify when completion slack or complex phases make either
inequality strict.

For connected \(P\), let \(Pr=\rho(P)r\) with \(r_i>0\), write
\(H_{ij}=q_{ij}\phi_{ij}\), and set \(x_i=r_if_i\).  We prove the exact
two-sector ground-state identity
\[
\begin{split}
x^*(\rho I-\sigma H)x
=
\sum_{\{i,j\}}r_ir_j\bigl[
q_{ij}|f_i-\sigma\phi_{ij}f_j|^2
{}+{}&(P_{ij}-q_{ij})\\
&\cdot(|f_i|^2+|f_j|^2)
\bigr],
\end{split}
\]
for \(\sigma\in\{\pm1\}\).  Consequently,
\[
\|H\|=\rho(P)
\]
if and only if, for some sector \(\sigma\), every amplitude bound is
saturated and
\[
 H=\sigma DPD^*
\]
for a diagonal unitary \(D\).  In the saturated case this switching
condition is equivalent to
\[
 \Hol_\phi(C)=\sigma^{|C|}
\]
on every cycle.  Only a fundamental-cycle basis must be checked.  In
particular, every scalar phase pattern on a tree is switchable and
\(\|H\|=\rho(|H|)\); a tree can never create phase-frustration saving.

We express the positive and negative spectral defects as exact
Perron-weighted magnetic energies.  Fundamental-cycle defects give
explicit upper bounds, while any defective cycle gives a resistance
type lower bound.  The exact flux spectrum of \(C_n\) shows that small
holonomy defects produce quadratic, not linear, spectral loss.  We also
give the reducible equality criterion and the exact decomposition
\[
\rho(P)-\|H\|
=
\bigl[\rho(P)-\rho(|H|)\bigr]
+\bigl[\rho(|H|)-\|H\|\bigr].
\]

These results close the finite scalar Hermitian equality question in
the dominated zero-diagonal setting.
They neither show that the unarchived growing fixed-shift carrier has
defective dominant cycles nor provide a mass-normalized exponent
saving.  The Hermitian row graph used here is distinct from the sparse
completion incidence graph.
\end{abstract}
