\section{Introduction}

The fixed-shift completion hierarchy produces nonnegative matrices that
majorize the absolute entries of a scalar Hermitian carrier
\cite{WangTPC75}.  Its operator estimate ends with
\begin{equation}\label{eq:intro-chain}
 \|H\|\le\rho(|H|)\le\rho(P).
\end{equation}
TPC-78 classifies certain forest components of the \emph{completion
incidence program} \cite{WangTPC78}.  It does not answer when the
Hermitian inequality \eqref{eq:intro-chain} is strict, because the graph
governing that question has physical rows as vertices and post-summation
matrix entries as edges.

Two mechanisms can create slack.  First,
\(|H_{ij}|<P_{ij}\) leaves amplitude or completion slack.  Second,
even when \(P=|H|\), edge phases can be inconsistent around cycles.
These are different phenomena, and they must be separated before a
strict Perron comparison can be interpreted.

\paragraph{Main results.}
We derive an exact Perron ground-state transform that is simultaneously
valid for the positive and negative extremal sectors.  It yields a
necessary-and-sufficient equality theorem:
\[
 \|H\|=\rho(P)
 \quad\Longleftrightarrow\quad
 |H_\alpha|=P_\alpha,\quad
 H_\alpha=\sigma D_\alpha P_\alpha D_\alpha^*
\]
on a Perron-dominant connected component, for some
\(\sigma\in\{\pm1\}\).  In the saturated connected case, diagonal
switching is equivalent to a \(U(1)\) cycle-holonomy condition.

The two sectors matter.  Frustrating the positive Perron eigenvector
does not force operator-norm strictness if the negative sector still
saturates.  A signed triangle with total phase \(-1\) is the smallest
example.  Genuine phase saving requires both sectors to have a
positive defect.

\paragraph{Quantitative content.}
The ground-state identity is an exact magnetic Dirichlet energy.
It gives a variational formula, a fundamental-cycle upper certificate,
and a defective-cycle lower certificate in terms of Perron
conductances.  The flux cycle \(C_n\) is solved in closed form and
shows quadratic small-angle loss.  Thus finite strictness alone cannot
be upgraded to an asymptotic power saving.

\paragraph{Scope.}
The phase classification is scalar and Hermitian.  A general
real-linear completion block has no single \(U(1)\) phase.  A
matrix-valued block can saturate on a common invariant subspace without
having trivial matrix holonomy.  A non-Hermitian carrier requires
singular-vector or dilation arguments, while a nonsymmetric
nonnegative majorant need not bound the Euclidean operator norm by its
spectral radius.

\paragraph{Progress label.}
The identities are exact L0 spectral algebra and advance the L1
operator interface for a literal scalar Hermitian carrier.  They do not
provide the missing growing-carrier census or any fixed-\(h_0\)
arithmetic exponent estimate.

\paragraph{Organization.}
\Cref{sec:setup} defines the two-sector phases.
\Cref{sec:ground} proves the exact sum of squares.
\Cref{sec:equality} classifies saturation.
\Cref{sec:holonomy,sec:trees} give switching and tree consequences.
\Cref{sec:quantitative,sec:flux} prove weighted bounds and the cycle
model.  \Cref{sec:reducible} handles reducible majorants.
\Cref{sec:two-graphs,sec:countermodels,sec:boundary} record the
interface, counterexamples, and stop rules.
