\section{Literal carrier specialization and claim boundary}
\label{sec:boundary}

Let \(\widetilde H_X\) be a finite scalar Hermitian carrier with zero
diagonal, and let \(P_X\) be a finite real symmetric nonnegative
zero-diagonal matrix.  Earlier completion layers may supply such a
majorant, including the most complete all-content or provenance-aware
versions.  Once the entrywise inequality
\[
 |\widetilde H_X|\le P_X
\]
is checked on complete post-aggregation keys, the present equality
theorem applies to this pair without further heuristic assumptions.

\begin{proposition}[Literal Perron equality audit]\label{prop:literal}
Under the finite scalar, symmetric/Hermitian, and zero-diagonal
hypotheses above,
\[
 \|\widetilde H_X\|=\rho(P_X)
\]
if and only if some Perron-dominant connected component of \(P_X\)
simultaneously satisfies:
\begin{enumerate}[label=(\roman*),leftmargin=2.4em]
\item every edge majorant is tight,
\[
 (P_X)_{mn}=|(\widetilde H_X)_{mn}|;
\]
\item the exact entry phases are balanced or antibalanced on every
fundamental row cycle.
\end{enumerate}
\end{proposition}

\begin{proof}
This is \cref{thm:reducible,thm:holonomy}.
\end{proof}

The minimal archive records:
\begin{enumerate}[label=(A\arabic*),leftmargin=2.7em]
\item fixed \(h_0\), scale \(X\), complete row keys, and the common
global raw normalizer;
\item literal complex entries after every atomic/content sum and exact
zero test;
\item the chosen majorant and an entrywise slack table;
\item connected components, their Perron radii and positive
eigenvectors;
\item a spanning forest, chord list, both sector holonomies, and
Perron conductances;
\item separate amplitude and phase gaps from \eqref{eq:split};
\item interval-verified eigenvalue or cycle certificates and data
hashes.
\end{enumerate}

No such growing literal carrier census is included here.  Thus no claim
is made that a dominant component contains a defective cycle, that both
sectors have a uniform gap, or that the gap survives global
normalization.

\subsection*{Progress and stop rules}

\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.19\linewidth}
>{\raggedright\arraybackslash}p{0.71\linewidth}@{}}
\toprule
Level & Status\\
\midrule
L0: spectral algebra &
Exact for finite scalar Hermitian matrices.\\
L1: operator interface &
Advanced by complete equality and weighted cycle-defect certificates.\\
L2: fixed-\(h_0\) arithmetic &
Open; no uniform growing-carrier or mass-normalized estimate is proved.\\
\bottomrule
\end{tabular}
\end{center}

The branch stops as a phase-saving route if a Perron-dominant component
of the exact post-aggregation graph \(G_{|\widetilde H_X|}\) is a tree
or if any dominant component is balanced or antibalanced.  Frustrating
only one sector, thresholding an exact edge, or measuring a
pre-aggregation atom phase is insufficient.  Even a positive finite
gap must be bounded uniformly on the complete growing family and
connected to the physical scale.

The inherited exponent ledger permits total fixed-power loss strictly
below \(1/400\) and stops at loss at least \(1/400\), including
equality.  This paper adds no exponent loss by itself and proves no
exponent gain.  A cycle gap cannot be entered as an arithmetic saving
until a separate literal transfer theorem supplies its direction,
normalization, and carrier coverage.

\subsection*{Conclusion}

The Perron gap now has an exact decision procedure:
\[
\begin{array}{c}
\text{amplitude tightness on dominant components}\\
\downarrow\\
\text{positive and negative cycle-holonomy tests}\\
\downarrow\\
\begin{cases}
\text{one sector consistent} &\Rightarrow \text{Perron saturation},\\
\text{both sectors defective} &\Rightarrow \text{quantified strictness}.
\end{cases}
\end{array}
\]
This closes the finite scalar Hermitian equality gate.  The remaining
question is arithmetic: whether the literal fixed-shift growing carrier
contains sufficiently weighted, persistently defective dominant
cycles.
