\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Assembly and Concentration at a Fixed-Shift Type-II Gate: Cumulative Divisor Prefixes, Bilinear Distribution Frontiers, and TT* Dispersion},
 pdfauthor={Liang Wang},
 pdfsubject={Cumulative factorable wedges and phase-concentration normal forms for a fixed-shift prime-pair Type-II gate},
 pdfkeywords={prime correlations, factorable moduli, Ramanujan sums, Type II sums, phase concentration, TT star, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Imported input}
\crefname{assumption}{Imported input}{Imported inputs}
\Crefname{assumption}{Imported input}{Imported inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\T}{\mathbb T}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\e}{\mathrm e}

\title{\textbf{Assembly and Concentration at a Fixed-Shift Type-II Gate:}\\
\textbf{Cumulative Divisor Prefixes, Bilinear Distribution Frontiers,}\\
\textbf{and \texorpdfstring{$TT^*$}{TT*} Dispersion}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Fix $h\ne0$, let $W\in C_c^\infty((0,\infty);\R)$, and write
\[
 \Lambda_R(n)=\sum_{q\le R}\frac{\mu(q)}{\varphi(q)}c_q(n),
 \qquad r_R=\Lambda-\Lambda_R,
 \qquad R=X^{1/2-\delta}.
\]
TPC-16 isolated a three-scale fixed-shift Type-II packet with source
scale $L$, quotient scale $K$, and divisor label $D$, and proved
cancellation for one $D$-resolved packet near the $11/21$ factorable
boundary.  We replace that isolated slice by an assembled divisor
prefix and then sharpen the spectral description of what remains.

The published core uses Maynard's 2025 fixed-residue distribution
theorem.  For a dyadic source block, all divisor labels $d\le D_0$ are
summed at once through
\[
 \beta_{\le D_0}(k)=\sum_{\substack{d\mid k\\d\le D_0}}\mu(d).
\]
Under the three Maynard monomial conditions, the corresponding residual
packet has arbitrary logarithmic saving.  In particular, the whole prefix
$d\le X^{1/21-o(1)}$ is packaged directly near
$L=X^{10/21-o(1)}$, yielding an exact tail normal form.

An explicitly segregated extension imports Theorem~1.1 of Li's
currently unrefereed arXiv:2602.20917v6, revised 27 May 2026.  Its
signed bilinear estimate deletes the third Maynard monomial condition.
The resulting exponent polytope has vertex
\[
 (\log_XL,\log_XD_0)=\left(\frac8{17},\frac1{17}\right),
 \qquad \log_X(LD_0)=\frac9{17}.
\]
Thus, within the TPC-16 interface and using that version-locked imported
theorem, an entire prefix $d\le X^{1/17+o(1)}$ is removed near
$L=X^{8/17-o(1)}$.  The proof records why the target weight depends on
the source factor but not on $d$; arbitrary pair-dependent masks are
not covered.  The published Maynard layer remains intact under any
later revision of the preprint.

For the surviving dyadic block
\[
 \cH_{L,K}(\alpha,\beta)
 =\sum_{\ell,k}c_{\ell,k}\e(\alpha\ell+\beta k),
 \qquad LK\asymp X,
\]
we prove the explicit energy bound
\[
 \sum_{\ell,k}|c_{\ell,k}|^2\ll X(\log X)^3.
\]
Exact Nyquist Parseval makes every natural-size exceptional phase a
finite translation-spectral atom.  A flat-top reproducing formula shows
that failure at the distinguished zero phase forces quantitative energy
inside a polylogarithmically enlarged uncertainty cell.  Finally,
$TT^*$ reduces such failure to a positive off-diagonal correlation of
the residuals $r_R(\ell_1k+h)$ and $r_R(\ell_2k+h)$ of size
$\gg XL/(\log X)^2$ at a dyadic witness scale.  A sharp abstract
countermodel shows that band limitation, total residual energy, and
phase mean squares alone cannot exclude the zero mode.

No fixed-shift prime-pair asymptotic, twin-prime lower bound, new
distribution theorem, or breach of sieve parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} fixed-shift prime correlations; factorable
moduli; cumulative divisor prefixes; Ramanujan residuals; Type-II sums;
phase concentration; $TT^*$ dispersion; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N05, 11N13; Secondary
11N35, 11N37, 42A05.

\input{sections/introduction-ledger}
\input{sections/setup-interface}
\input{sections/distribution-transfer}
\input{sections/assembled-prefix}
\input{sections/published-maynard}
\input{sections/li-extension}
\input{sections/phase-energy}
\input{sections/planck-ttstar}
\input{sections/sharp-boundary}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
