\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Periodic Second Coefficients through a Prime Target: A Bombieri--Vinogradov Transfer, Arithmetic Involutions, and the Combined-Modulus Boundary},
 pdfauthor={Liang Wang},
 pdfsubject={An exact low-conductor coefficient-transfer law for a two-scale prime-target form},
 pdfkeywords={Bombieri--Vinogradov theorem, periodic coefficients, arithmetic involution, Dirichlet characters, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cE}{\mathcal E}
\newcommand{\cI}{\mathcal I}
\newcommand{\cK}{\mathcal K}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cT}{\mathcal T}
\newcommand{\cV}{\mathcal V}
\newcommand{\wh}{\widehat}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\tr}{\operatorname{tr}}

\title{\textbf{Periodic Second Coefficients through a Prime Target:}\\
\textbf{A Bombieri--Vinogradov Transfer,}\\
\textbf{Arithmetic Involutions,}\\
\textbf{and the Combined-Modulus Boundary}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let $x=MN$, let $h\ne0$ be fixed, and let $q\geq3$ be odd with
$(q,h)=1$.  For a bounded $q$-periodic function $\beta$ supported on the
unit classes modulo $q$, we study the two-scale prime-target form
\[
 \sum_{M<m\leq2M}\alpha_m
 \sum_{n\geq1}\beta(n)\Lambda(mn+h)W(n/N),
 \qquad |\alpha_m|\leq1.
\]
Allowing an arbitrary bounded second coefficient leads to the unresolved
bilinear/Type~II interface isolated in the preceding work.  In the
low-period range
\[
 q\leq(\log x)^C,
 \qquad
 2Mq\leq x^{1/2}(\log x)^{-B},
\]
we prove instead an exact coefficient-transfer law, with arbitrary logarithmic
saving, by a direct application of the classical maximal
Bombieri--Vinogradov theorem.  The main term is operator-valued:
\[
 N\!\int W\,
 \sum_m\alpha_m\frac{m}{\varphi(m)}
 (\mathsf P_{q,h}\beta)(m),
 \qquad
 (\mathsf P_{q,h}\beta)(a)
 =\frac1{\varphi(q)}
 \sum_{\substack{b\in(\Z/q\Z)^\times\\(ab+h,q)=1}}\beta(b).
\]
Thus the periodic coefficient is not replaced by its mean: it is transported
by an explicit finite arithmetic operator.

We determine this operator completely.  After row normalization it is a
self-adjoint Markov operator.  Character modes with a conductor divisible by
$p^2$ are annihilated.  A surviving character of exact squarefree conductor
$r$ is exchanged with its conjugate and multiplied by
\[
 (-1)^{\omega(r)}\overline{\chi(-h)}
 \prod_{p\mid r}(p-2)^{-1}.
\]
This is exactly the finite-conductor multiplier found for the centered rough
kernel in the preceding work, now transferred through the genuine prime
target $\Lambda(mn+h)$.  We also give the corresponding prime-weighted source
corollary and an exact finite certificate.

The analytic input is classical; no new level of distribution is asserted.
The modulus is $mq$, not $m$, and residue splitting costs the period $q$.
Moreover, the finite-conductor energy-escape theorem from the preceding paper
shows that polylogarithmic periodic spaces capture a vanishing proportion of
the $L^2$ energy of $\Lambda-1$.  Consequently one cannot substitute
$\beta=\Lambda-1$, and the result gives neither a fixed-shift prime-pair
asymptotic nor a twin-prime lower bound or a breach of the parity barrier.
\end{abstract}

\noindent\textbf{Keywords:} periodic coefficient; prime target;
Bombieri--Vinogradov theorem; arithmetic involution; finite-conductor
spectrum; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N13, 11N36; Secondary 11L40, 47A10.

\input{sections/introduction-scope}
\input{sections/local-operator}
\input{sections/prime-target-transfer}
\input{sections/modal-corollaries}
\input{sections/conductor-boundary}
\input{sections/certificate-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
