\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Content-Rich Reflected Fibers in a Primitive Mobius Tail: Long-Fiber Pruning, a Sparse Incidence Wedge, and the Primitive-Core Barrier},
 pdfauthor={Liang Wang},
 pdfsubject={Incidence closure of a content-rich sparse wedge in the reflected ultra-long Mobius complement},
 pdfkeywords={Mobius tail, divisor reflection, sparse fibers, incidence geometry, primitive lcm, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cI}{\mathcal I}
\newcommand{\cN}{\mathcal N}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cU}{\mathcal U}
\newcommand{\cW}{\mathcal W}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Content-Rich Reflected Fibers in a Primitive M\"obius Tail:}\\
\textbf{Long-Fiber Pruning, a Sparse Incidence Wedge,}\\
\textbf{and the Primitive-Core Barrier}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let $P_{m,T}$ be the calibrated divisor prefix at the upper cutoff of
a selected primitive opened-row packet, and let $U_0\asymp X$ contain
all positive targets on its physical support.  The preceding
conductor argument closes the truncated quadratic packet at $T$, but
does not estimate the ultra-long complement.  We begin from the exact
calibrated identity
\[
 P_{m,U_0}-P_{m,T}=C_{m;T,U_0},\qquad
 C_{m;T,U_0}(j)=
 \sum_{\substack{T<w\le U_0\\w\mid mj+h}}-\mu(w)\log w.
\]
It avoids a scalar-tail replacement whose available pointwise bounds
do not by themselves imply arbitrary logarithmic saving.  Expanding
the joint cutoff difference leaves three raw ultra channels and two
row-drift legs; the latter are power-small from the existing
$L^{-1}$ row factor.

Reflect a long divisor $w$ to $r=(mj+h)/w$.  For distinct primitive
rows $m,n$, dyadic complement variables
\[
 r\asymp A,\qquad s\asymp B,\qquad (r,s)\asymp G
\]
select, when compatible, one orbit class modulo $[r,s]$.  We prove the
fixed-row incidence estimate
\[
 \cN_{m,n}(A,B,G)
 \ll_{\eps,h}X^\eps
 \min\left\{J,\frac{AB}{G^2}+\frac JG\right\}.
\]
The first term is the pointwise divisor bound.  For the second, each
exact common content divides $h(m-n)$; after writing
$r=dr_1$, $s=ds_1$, the number of coprime primitive pairs is
$O(AB/d^2)$ and their orbit occupancy is
$O(1+Jd/(AB))$.  This argument neither removes the M\"obius signs nor
assumes that complement and quotient contents are coprime.

The actual opened-row coefficients have one-row $\ell^1$ mass
$O(Q)$.  Consequently every physical mixed or both-ultra dyadic block
satisfies
\[
 |\cS(A,B,G)|
 \ll_\eps Q^2X^\eps
 \min\left\{J,\frac{AB}{G^2}+\frac JG\right\}.
\]
Writing $q=[r,s]$ and $g=(r,s)$, this gives the unconditional
content-rich sparse wedge
\[
 q\ge J,\qquad \frac qg\le JX^{-\eta}
 \quad\Longrightarrow\quad
 \cS_{\rm rich}\ll_\eps XQX^{-\eta+\eps}.
\]
Here $q/g=(r/g)(s/g)$ is the primitive lcm after the shared content is
removed.  On the complementary long-fiber side $q\le Y\le J$, row
residue energy also gives
\[
 \cS_{q\le Y,\,(r,s)>D}
 \ll_\eps X^\eps\left\{
 \frac{XQ}{D}\log^2(2Y)+X\log^3(2Y)
 \right\}.
\]
Thus every polynomially large shared-content sector is power-small on
prescribed long-fiber scales as well.

At the high-$\beta$ sample
$\beta=267/400$, $T=X^{193/500+o(1)}$, the block
$A=B=X^{1/4}$, $G=X^{1/10}$ is genuinely sparse and has the exact
incidence margin $13/400$.

This closes a nonempty exponent region of the ultra-long geometry
without a Chowla or Elliott input.  It does not close the primitive sparse core,
the dense long-fiber region, the complete residual, positivity, a
Hardy--Littlewood asymptotic, twin primes, or the sieve parity problem.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; divisor
reflection; sparse fiber; incidence geometry; primitive lcm; sieve
parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11B25, 11D45.

\input{sections/introduction}
\input{sections/physical-interface}
\input{sections/calibrated-difference}
\input{sections/reflected-incidence}
\input{sections/weighted-wedge}
\input{sections/long-content-pruning}
\input{sections/high-beta-ledger}
\input{sections/primitive-boundary}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
