\section{Exact certificate and claim boundary}
\label{sec:tpc37-certificate}

The accompanying standard-library program is
\begin{center}
\texttt{experiments/tpc37\_certificate.py}.
\end{center}
It performs deterministic exact-arithmetic checks and writes the canonical
JSON archive
\begin{center}
\texttt{experiments/tpc37\_certificate.json}.
\end{center}
The same suite is run by
\begin{verbatim}
python experiments/tpc37_certificate.py
python -O experiments/tpc37_certificate.py
\end{verbatim}
so no check depends on Python \texttt{assert} semantics.

\subsection{Finite identities checked}

The certificate is divided according to the proof architecture:
\begin{enumerate}[label=(\roman*)]
 \item row-residue occupancy and the one-hit orbit bound behind
 \cref{thm:tpc37-one-prime-face};
 \item the punctured-centering identity
 \eqref{eq:tpc37-punctured-identity} and complete-cycle annihilation
 \eqref{eq:tpc37-complete-cycle-annihilation};
 \item exact Jacobi Gram and energy identities for several small prime
 fields;
 \item the eight-face CRT decomposition, orthogonality, individual norms,
 and proper-union norms for several triples of primes; and
 \item determinant periodization and representative joint- and
 two-coordinate ghost fibers.
\end{enumerate}
All roots of unity used in the Jacobi checks are represented symbolically;
the CRT suites use integers and rational numbers.  No floating-point
tolerance or random sample is used.  Finite enumeration verifies the
displayed algebra on the archived test families; it is not evidence for an
unproved asymptotic cancellation estimate.

\subsection{Reproducibility record}

The generated JSON records the per-family check counts, byte-for-byte
source SHA-256 values, and a certificate digest of the canonical payload.
The repository attributes require LF line endings, but the hashing
algorithm itself reads the archived bytes without further normalization.
For the archived run,
\begin{align}
 \text{certificate source SHA-256}\quad
 &\texttt{3c4565e36931c5fd42d689425cf9ece9b}
 \notag\\[-0.3em]
 &\texttt{ce5d4a376d0657e79cc3f6dab5ccaed},
 \label{eq:tpc37-certificate-source-hash}\\
 \text{JSON SHA-256}\quad
 &\texttt{2ce1c2938868bf07495fb521bb2227bc}
 \notag\\[-0.3em]
 &\texttt{2b2e4a11daeeb5d1d9389b4375fbe0fa},
 \label{eq:tpc37-certificate-json-hash}\\
 \text{certificate digest}\quad
 &\texttt{3aac4337fdfcee4cdbc013c73ac5ca56}
 \notag\\[-0.3em]
 &\texttt{2fdcd76a79037e20e4eba6f30ed08efa}.
 \label{eq:tpc37-certificate-digest}
\end{align}
These values make changes to the finite certificate auditable without
promoting the enumeration to a proof of the analytic theorems.

\subsection{Unconditional conclusions}

Subject only to the explicit inherited packet hypotheses in
\cref{sec:tpc37-inherited-interface}, this paper proves:
\begin{enumerate}[label=(\roman*)]
 \item physical absorption of one, or any fixed finite number of,
 zero-coordinate faces at \(X^{o(1)}Q^3/J\);
 \item the exact punctured-centering identities and corrections that are
 rank one in the complementary \(s\)-coordinate,
 together with complete-cycle annihilation;
 \item the standard superlogarithmic estimate for the exposed clean
 M\"obius mean;
 \item the weighted two-character formula, the exact rank-one Jacobi Gram
 defect, and the shifted multiplicative Parseval identities;
 \item the interval-weight average bound and the exact outer decomposition
 into an explicit principal boundary plus a nonprincipal spectrum, with a
 sufficient flatness criterion for the latter;
 \item a punctured sharp example showing that abstract centered data can
 retain the full coherent character scale;
 \item the orthogonal three-modulus face calculus and exact norms of the
 seven-face proper union;
 \item determinant-first \(\ell^1\) and \(\ell^2\) periodization;
 \item proper-face closure on the exact equality, the full-face scalar
 obstruction, and the sharp quadratic-to-coherent separation for
 arbitrary bounded unary weights.
\end{enumerate}
The finite-field flatness theorem is an implication, not a verification
of its hypothesis for the physical row coefficient.  Similarly,
\eqref{eq:tpc37-shift-fiber-bessel-gate} is displayed as a sufficient
next input and is not among the proved estimates.

\subsection{What is not proved}

Neither the manuscript nor the certificate proves:
\begin{enumerate}[label=(\roman*)]
 \item the regular or full physical coefficient gate
 \(V_L+V_R\ll X^{o(1)}Q^3/J\);
 \item \(\mathfrak K_{\rm Mell}(a)=X^{o(1)}\) for the actual outer
 convolution, the required aggregate nonprincipal spectral-overlap bound,
 or physical absorption of the exposed \(\beta_U\)-mean corrections and
 principal \(r_0\)-term;
 \item a diagonal-size estimate for the physical M\"obius Hadamard energy
 \eqref{eq:tpc37-physical-Hadamard-energy};
 \item the target-coupled, coefficient-weighted shifted-fiber Bessel input
 \eqref{eq:tpc37-shift-fiber-bessel-gate};
 \item uniform moving-shift incidence control sufficient to reassemble
 all aliases;
 \item a fixed-power saving from the clean M\"obius mean;
 \item an affine Chowla theorem or a new M\"obius-disjointness theorem;
 \item a breach of sieve parity or positivity;
 \item a Hardy--Littlewood prime-pair asymptotic; or
 \item infinitely many twin primes.
\end{enumerate}

The precise advance is a reduction theorem.  It closes the physical zero
faces and the proper faces on the exact equality, and diagonalizes the
nonconstant one-modulus boundary.  The full nonzero coordinate face is
the unique unsuppressed face on the exact equality.  Off the equality,
coherent reassembly of both the full face and the proper union remains a
coefficient-specific problem.
