\section{Endpoint ledger and the relocated coherent-face gates}
\label{sec:tpc37-next-gate}

The three routes above answer different questions and must not be merged
into a single cancellation claim.  This section records their exact
logical output at the endpoint and isolates two sufficient, but presently
unproved, continuations.

\subsection{What has been removed from the regular problem}

Let
\begin{equation}
 \mathfrak G_X:=X^{o(1)}\frac{Q^3}{J}
 \label{eq:tpc37-target-gate}
\end{equation}
denote the inherited target scale.  The reductions proved above have the
following consequences.
\begin{enumerate}[label=(\roman*)]
 \item By \cref{thm:tpc37-one-prime-face,cor:tpc37-finite-prime-faces},
 every physical row--time pair on which one of the chosen CRT primes
 divides the target contributes \(O(\mathfrak G_X)\).  Hence the modular
 analysis may begin with both complementary coordinates in the unit
 groups.
 \item By \cref{prop:tpc37-punctured-identity}, ordinary additive
 centering can be replaced by punctured centering without hiding a
 zero-residue coefficient.  The difference is an explicit term that is
 rank one in the complementary \(s\)-coordinate and contains the clean
 scalar \(\beta_U\); complete constant residue cycles
 vanish by \cref{prop:tpc37-complete-cycle-annihilation}.
 \item By \cref{thm:tpc37-Jacobi-near-unitary,thm:tpc37-shifted-Parseval},
 the nonconstant complementary weight is represented exactly by a
 Hadamard product of two Mellin spectra.  The Jacobi transform has only a
 rank-one defect and therefore supplies no generic cancellation.  For an
 interval, P\'olya--Vinogradov removes one uniform Cauchy factor only in
 the unweighted character average.
 \item By \cref{thm:tpc37-orthogonal-face-calculus,%
thm:tpc37-proper-union-norms}, the seven proper coordinate faces of three
 moduli form one explicit kernel \(P\), with one-period squared mass
 \(\asymp J^{-1}\).  Determinant-first grouping gives the fiberwise bound
 \eqref{eq:tpc37-proper-l2-periodization}, and on the exact equality the
 proper-face energy is \(O(\mathfrak G_X)\) by
 \eqref{eq:tpc37-equality-proper-closure}.
\end{enumerate}
None of these statements estimates the full regular output after all row,
orbit, dyadic, and alias sums are restored.  In particular, the
fiberwise \(L^2\) estimate for \(P\) is not a license to apply Cauchy
through a coherent sum; \cref{prop:tpc37-coherent-face-no-go} quantifies
the resulting polynomial loss for arbitrary bounded coefficients.

\subsection{The two surviving formulations}

The unsuppressed equality face and the coherent off-equality alias
reassembly can be attacked in two nonexclusive forms.

\paragraph{Outer spectral overlap.}
For one completed product--slope block, put
\(B_0=\sum_\ell b(\ell)\), \(c=w*_\times g\), and
\(r_0=B_0f(0)c(h)\).  The exact arithmetic object is
\begin{equation}
 \mathfrak S_q^{\rm full}(a,w,g)
 :=\frac{q^2}{q-1}|r_0|^2
 +\frac1{q-1}\sum_{\chi\ne\mathbf1}
 |\widetilde a(\chi)|^2|C_\chi(w,g)|^2,
 \label{eq:tpc37-outer-overlap-gate}
\end{equation}
where \(a=b*_{\times}f\) is the actual outer row convolution and
\[
 C_\chi(w,g)=
 \sum_{x\in\F_q^\times}(w*_{\times}g)(x)
 \overline{\chi(x-h)}.
\]
\Cref{thm:tpc37-Mellin-flatness-sufficient} bounds the nonprincipal sum
if the actual \(a\) obeys
\(\mathfrak K_{\rm Mell}(a)=X^{o(1)}\); it leaves \(r_0\) explicit.
That pointwise flatness hypothesis is stronger than necessary: an
aggregate estimate for the nonprincipal overlap, averaged over the
physical layers, would suffice, provided the principal \(r_0\)-term is
also controlled.  Neither input is proved here.

\paragraph{Shifted determinant fibers.}
Keeping the integer determinant \(F\) visible gives the alternative
target-coupled Hilbert-space input
\eqref{eq:tpc37-shift-fiber-bessel-gate}.  Its normalization is not
arbitrary: the direct period masses
\eqref{eq:tpc37-direct-face-period-ledger} imply
\begin{align}
 \text{full face:}\quad &Q^2J\,\mathcal K_X=Q^3/J,
 \notag\\
 \text{proper union:}\quad
 &Q^2J\,\mathcal K_X/J=Q^3/J^2.
 \label{eq:tpc37-two-fiber-ledgers}
\end{align}
Thus the target-coupled, coefficient-weighted Bessel input at the stated
normalization would close the full face and overclose the proper union.
The moving shift \(h_F=h+F\), and the dependence of the face on
\(N\bmod M\), prevent one from importing a fixed-\(h\) incidence estimate
without a new uniformity argument.

These are alternative sufficient inputs for the same desired physical
output; they are not asserted to be equivalent term by term.  The first
asks for avoidance of large Mellin channels after completion; the second
asks for almost-orthogonality between integer determinant fibers before
completion.  Failure of a pointwise flatness bound therefore does not
rule out a weighted-overlap or fiberwise theorem.

\subsection{A route tree with valid fallback results}

The next layer has three mathematically distinct outcomes.
\begin{description}[style=nextline,leftmargin=2.4em]
 \item[Positive overlap theorem.]
 Prove the required aggregate nonprincipal overlap bound using the actual
 row and truncated M\"obius coefficients, and separately absorb both the
 exposed \(\beta_U\)-mean corrections and the principal \(r_0\)-term in
 \eqref{eq:tpc37-outer-overlap-gate}.  This would close the completed
 finite-field coherent core; integer aliases and all normalization
 constants would still have to be checked in the physical reassembly.

 \item[Positive shifted-fiber theorem.]
 Prove the target-coupled input
 \eqref{eq:tpc37-shift-fiber-bessel-gate} uniformly for the moving shifts
 and actual coefficients.  This route directly absorbs the three-modulus
 alias count at its critical \(X^{1/400+o(1)}\) scale.

 \item[Scoped obstruction theorem.]
 Exhibit, within a precisely specified coefficient class, unavoidable
 concentration in the exceptional Mellin direction or unavoidable
 alignment between shifted fibers.  Such a theorem would rule out that
 proof mechanism at the claimed normalization, not establish a lower
 bound for a prime-pair correlation.
\end{description}

The present paper advances the program regardless of which branch is
viable: zero faces, artificial centering values, constant residue cycles,
and proper equality faces are no longer mixed into the unsuppressed
equality-face question.  The surviving gates are coefficient-specific and
have two exact norm formulations.

\subsection{Relation to the parity boundary}

The sharp examples in
\cref{prop:tpc37-punctured-character-witness,%
prop:tpc37-coherent-face-no-go} show that centering, support restrictions,
and periodic \(L^2\) sparsity alone do not force the needed coherent
cancellation.  This is consistent with the classical parity obstruction
for sieve methods \citep{HeathBrown1982Parity,IwaniecKowalski2004}.
It is not a new formulation or resolution of that obstruction.  A future
positive theorem would have to use arithmetic information in the actual
M\"obius-derived coefficient beyond the formal finite-field identities
proved here.
