\section{Physical excision of the zero coordinate faces}
\label{sec:tpc37-physical-zero-faces}

The complete product--slope spectrum is naturally formulated on
\(\mathbb F_q^\times\).  Before completing any integer variable modulo
\(q\), we remove the physical row--time pairs on which a complementary
factor can be zero modulo \(q\).  This order avoids confusing a coordinate
face of a modular relaxation with cancellation in the M\"obius
coefficient.

\subsection{The inherited orbit slice}

We use only the following properties of the physical packet.  The left
and right row sets have \(O(Q)\) elements.  A left row \(\alpha\) has a
distinct integer label
\begin{equation}
 m_\alpha=\ell_\alpha d_\alpha\asymp Q,
 \label{eq:tpc37-row-label}
\end{equation}
where the source label \(\ell_\alpha\) is prime, and a coefficient
satisfying
\begin{equation}
 \sum_\alpha |\gamma_\alpha^{(1)}|^2
 \ll X^{o(1)}Q.
 \label{eq:tpc37-left-row-energy}
\end{equation}
The symmetric estimate holds for the right coefficients.  The orbit set
\(\mathcal J\) is contained in a positive interval of diameter
\(O(J)\), and every \(j\in\mathcal J\) is \(O(J)\).  Put
\begin{equation}
 N_\alpha(j)=m_\alpha j+h.
 \label{eq:tpc37-target}
\end{equation}
The actual multiplier
\(\mathfrak A_{\alpha,\gamma}^{\rm act}(j)\) is bounded, and the ultra
increment
\begin{equation}
 C_m(j)=
 \sum_{\substack{T<u\le U_0\\u\mid mj+h}}
 -\mu(u)\log u
 \label{eq:tpc37-ultra-increment}
\end{equation}
satisfies
\begin{equation}
 |C_m(j)|\ll X^{o(1)}
 \label{eq:tpc37-ultra-envelope}
\end{equation}
uniformly on the packet.  Thus the left slice and its energy are
\begin{align}
 Y_{\gamma,j}^L
 &:=\sum_\alpha \gamma_\alpha^{(1)}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\alpha}(j),
 \label{eq:tpc37-left-slice}\\
 V_L&:=\sum_{\gamma,j}|Y_{\gamma,j}^L|^2.
 \label{eq:tpc37-left-energy}
\end{align}
The right objects are obtained by exchanging the two row systems.

At the high--\(\beta\) endpoint,
\begin{equation}
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
 \label{eq:tpc37-endpoint-scales}
\end{equation}
and the inherited source scales give
\begin{equation}
 D=o(J),\qquad J=o(L).
 \label{eq:tpc37-source-order}
\end{equation}

Choose a fixed constant \(K\) larger than the constants implicit in the
positive orbit support.  Bertrand's postulate supplies, for all
sufficiently large \(X\), a prime
\begin{equation}
 KJ<q<2KJ.
 \label{eq:tpc37-orbit-prime}
\end{equation}
After enlarging \(K\) once, we may and do arrange that
\begin{equation}
 \max\mathcal J<q,\qquad
 \max_\alpha d_\alpha<q<\min_\alpha\ell_\alpha,
 \qquad q\nmid h.
 \label{eq:tpc37-unit-coordinate-range}
\end{equation}
In particular, \(q\nmid m_\alpha jh\) on the physical support.

\subsection{One auxiliary prime}

Split the ultra increment by the target residue:
\begin{align}
 C_m^{\rm sing(q)}(j)
 &:=\mathbf 1_{q\mid mj+h}C_m(j),
 \label{eq:tpc37-singular-increment}\\
 C_m^{\rm reg(q)}(j)
 &:=\mathbf 1_{q\nmid mj+h}C_m(j).
 \label{eq:tpc37-regular-increment}
\end{align}
Let \(Y^{L,\rm sing(q)}\), \(Y^{L,\rm reg(q)}\), and their energies be
defined from \eqref{eq:tpc37-left-slice} by using the corresponding
increment.  Define the right versions symmetrically.

\begin{theorem}[Physical absorption of one zero-coordinate face]
\label{thm:tpc37-one-prime-face}
Under \eqref{eq:tpc37-row-label}--\eqref{eq:tpc37-unit-coordinate-range},
\begin{equation}
 \boxed{
 V_{L,\rm sing(q)}+V_{R,\rm sing(q)}
 \ll X^{o(1)}\left(1+\frac Qq\right)Q^2.}
 \label{eq:tpc37-one-prime-face-bound}
\end{equation}
Consequently, at \(q\asymp J\),
\begin{equation}
 \boxed{
 V_{L,\rm sing(q)}+V_{R,\rm sing(q)}
 \ll X^{o(1)}\frac{Q^3}{J}.}
 \label{eq:tpc37-one-prime-gate}
\end{equation}
\end{theorem}

\begin{proof}
For fixed \(j\), let
\begin{equation}
 \mathcal A_q(j)=\{\alpha:q\mid m_\alpha j+h\}.
 \label{eq:tpc37-row-residue-set}
\end{equation}
If \(q\mid j\), this set is empty because \(q\nmid h\).  Otherwise
\(m_\alpha\) lies in one residue class modulo \(q\).  The labels are
distinct and lie in an interval of length \(O(Q)\), so
\begin{equation}
 |\mathcal A_q(j)|\ll 1+\frac Qq.
 \label{eq:tpc37-fixed-time-row-count}
\end{equation}
Conversely, for fixed \(\alpha\), the congruence
\(m_\alpha j\equiv-h\pmod q\) selects one class of \(j\pmod q\).
The orbit interval has diameter smaller than \(q\), and hence
\begin{equation}
 \#\{j\in\mathcal J:\alpha\in\mathcal A_q(j)\}\le1.
 \label{eq:tpc37-fixed-row-time-count}
\end{equation}

For one fixed opposite row \(\gamma\), Cauchy--Schwarz,
\eqref{eq:tpc37-ultra-envelope}, and
\eqref{eq:tpc37-fixed-time-row-count} give
\begin{align}
 \sum_j|Y_{\gamma,j}^{L,\rm sing(q)}|^2
 &\ll X^{o(1)}\left(1+\frac Qq\right)
 \sum_j\sum_{\alpha\in\mathcal A_q(j)}
 |\gamma_\alpha^{(1)}|^2 \notag\\
 &\le X^{o(1)}\left(1+\frac Qq\right)
 \sum_\alpha|\gamma_\alpha^{(1)}|^2 \notag\\
 &\ll X^{o(1)}\left(1+\frac Qq\right)Q.
 \label{eq:tpc37-one-column-singular-energy}
\end{align}
There are \(O(Q)\) opposite rows.  Summing
\eqref{eq:tpc37-one-column-singular-energy} over \(\gamma\) proves the
left part of \eqref{eq:tpc37-one-prime-face-bound}; the right part is
symmetric.  Finally, \(Q/q\to\infty\) and \(q\asymp J\), proving
\eqref{eq:tpc37-one-prime-gate}.
\end{proof}

The terminology in the theorem is literal.  On opening an ultra divisor,
write
\begin{equation}
 su=N_\alpha(j).
 \label{eq:tpc37-complementary-factorization}
\end{equation}
For a prime \(q\),
\begin{equation}
 q\mid N_\alpha(j)
 \quad\Longleftrightarrow\quad
 q\mid s\ \text{or}\ q\mid u.
 \label{eq:tpc37-zero-face-equivalence}
\end{equation}
Thus \cref{thm:tpc37-one-prime-face} absorbs simultaneously the
\(s=0\) and \(u=0\) residue faces of the physical equality.  It does not
estimate these faces by first replacing the equality with a congruence.

\subsection{A fixed finite family of moduli}

The preceding argument is stable under the fixed number of primes used
in a CRT realization.
For every fixed \(r\), the prime number theorem supplies \(r\) distinct
primes in the same fixed dilate of \(J\) for all sufficiently large
\(X\); the scale separation in \eqref{eq:tpc37-source-order} then gives
\eqref{eq:tpc37-unit-coordinate-range} for each of them.

\begin{corollary}[Fixed finite face excision]
\label{cor:tpc37-finite-prime-faces}
Let \(q_1,\ldots,q_r\asymp J\) be distinct primes satisfying
\eqref{eq:tpc37-unit-coordinate-range}, where \(r\) is fixed independently
of \(X\), and put \(P=\prod_{i=1}^{r}q_i\).  Define
\begin{equation}
 C_m^{\rm sing(P)}(j)
 :=\mathbf 1_{(mj+h,P)>1}C_m(j).
 \label{eq:tpc37-multimodulus-singular-increment}
\end{equation}
Then
\begin{equation}
 \boxed{
 V_{L,\rm sing(P)}+V_{R,\rm sing(P)}
 \ll_r X^{o(1)}\frac{Q^3}{J}.}
 \label{eq:tpc37-multimodulus-face-bound}
\end{equation}
On the complementary row--time support, every factor \(s,u\) in
\eqref{eq:tpc37-complementary-factorization} is a unit modulo every
\(q_i\).
\end{corollary}

\begin{proof}
Partition the event \((N_\alpha(j),P)>1\) according to the first prime
\(q_i\) dividing the target.  Apply
\cref{thm:tpc37-one-prime-face} to each disjoint piece.  The square of the
sum of at most \(r\) pieces is at most \(r\) times the sum of their
squares.  Since \(r\) is fixed, this proves
\eqref{eq:tpc37-multimodulus-face-bound}.  The final assertion follows
from \(su=N_\alpha(j)\).
\end{proof}

\subsection{Reduction of the full energy}

For one prime, the exact pointwise decomposition is
\begin{equation}
 Y_{\gamma,j}^L
 =Y_{\gamma,j}^{L,\rm reg(q)}
 +Y_{\gamma,j}^{L,\rm sing(q)}.
 \label{eq:tpc37-slice-regular-singular-split}
\end{equation}
Therefore
\begin{equation}
 \boxed{
 V_L+V_R
 \le2\bigl(V_{L,\rm reg(q)}+V_{R,\rm reg(q)}\bigr)
 +2\bigl(V_{L,\rm sing(q)}+V_{R,\rm sing(q)}\bigr).}
 \label{eq:tpc37-full-energy-reduction}
\end{equation}
The same statement holds for the fixed finite family in
\cref{cor:tpc37-finite-prime-faces}.  Hence a bound of size
\(X^{o(1)}Q^3/J\) for the regular energy implies the same bound for the
full energy.  The theorem proved here supplies the singular term in this
reduction; it does not supply the regular estimate.

At the endpoint,
\begin{equation}
 \frac Qq=X^{67/200+o(1)},\qquad
 \frac{Q^3}{J}=X^{167/100+o(1)}.
 \label{eq:tpc37-face-endpoint-ledger}
\end{equation}
In particular, the zero-coordinate faces fit the required ledger without
using a sign estimate.  The terminal factorization \(s=1\), \(u=N_\alpha(j)\)
remains in the regular part whenever \(q\nmid N_\alpha(j)\); no terminal
M\"obius cancellation is asserted.
