\section{Exact certificate and claim boundary}
\label{sec:tpc35-certificate-scope}

The accompanying standard-library certificate is
\begin{center}
 \texttt{experiments/tpc35\_certificate.py}.
\end{center}
It uses integers, \texttt{Fraction}, and hand-written Gaussian-rational
arithmetic.  It contains no floating-point calculation, random input,
true division, or Python \texttt{assert} statement.  Running
\begin{verbatim}
python experiments/tpc35_certificate.py
python -O experiments/tpc35_certificate.py
\end{verbatim}
performs the same checks and regenerates byte-identical JSON.

\subsection{Finite checks}

The archived run performs \(141{,}803\) exact checks.

\begin{table}[H]
\centering
\caption{Exact finite checks in the TPC-35 certificate.}
\label{tab:tpc35-certificate-counts}
\small
\begin{tabular}{@{}lr@{}}
\toprule
Check family & Count \\
\midrule
Aspect-ratio Gram, Hilbert--Schmidt, and tight-frame identities
 & \(1{,}260\) \\
Same-source block identity and Rayleigh lower bound
 & \(1{,}311\) \\
General and primitive ultra-CRT compatibility and occupancy
 & \(95{,}535\) \\
Short-orbit congruence operator
 & \(393\) \\
Incomplete multiplicity saturation
 & \(18{,}414\) \\
Product-slope character spectrum over \(q=3,5\)
 & \(194\) \\
Three/four-modulus alias ladder
 & \(8{,}736\) \\
CRT lift and normalized non-tensorization
 & \(1{,}338\) \\
Integer-line intersection, Schur count, and sharp pencil
 & \(14{,}618\) \\
Source constraints
 & \(4\) \\
\midrule
Total & \(141{,}803\) \\
\bottomrule
\end{tabular}
\end{table}

The Gram suite constructs the matrices \(M_j\) entry by entry, forms
\(\sum_jM_j^*M_j\), and compares it to
\eqref{eq:tpc35-G-exact}.  It checks the complete eigenvalue-free
operator and Hilbert--Schmidt inequalities and exact tight-frame
sharpness using integer Hadamard phases.  The same-source suite checks
\eqref{eq:tpc35-block-O} and the \(rt\), rather than \(r^2t\), subtraction
in \eqref{eq:tpc35-block-op-lower} through an exact Rayleigh witness.

The CRT suite enumerates the general criterion
\eqref{eq:tpc35-general-compatibility}, the primitive specialization
\eqref{eq:tpc35-primitive-compatibility}, the least-common-multiple joint
class, and exact interval occupancy.  It includes the explicit
\(h=2,u_1=u_2=4,m_1=1,m_2=3\) counterexample to the incorrectly swapped
coprimality hypothesis.  The short-orbit suite compares the direct
singular norm with the maximum time degree in
\eqref{eq:tpc35-short-orbit-norm}.

The projective suite checks the three pigeonhole ranges and the continuous
envelope algebra with rational arithmetic.  The product-slope suite uses
Gaussian rationals to verify every transform, energy, principal and
nonprincipal formula for all centered test functions in finite exact
families over \(q=3,5\).  It also verifies the single-character example
attaining the factor \(q-1\).  The alias suite checks exact floor counts
for the lcm fibers and the rational exponent ledger.  The CRT-lift suite
compares both pointwise centered correlations and normalized rms values.
The integer-line suite verifies intersection formulas, solution steps,
point and line multiplicities, Schur row sums, and a sharp common-point
pencil.

\subsection{Reproducibility values}

The archived outputs have:
\begin{align}
 \text{normalized source SHA-256}\quad
 &\texttt{7e08d1d29dc88e40b9653176b06336ba}
 \notag\\[-0.2em]
 &\texttt{2ed879db33fb080e2c697e79b94e948e},
 \label{eq:tpc35-source-hash}\\
 \text{JSON SHA-256}\quad
 &\texttt{02dea583a12f7078ee15ae8205f7e8d0}
 \notag\\[-0.2em]
 &\texttt{787f92c5c858c80a525396534357c134},
 \label{eq:tpc35-json-hash}\\
 \text{certificate digest}\quad
 &\texttt{26b282b0b8a989e792524dc12ab1a6ed}
 \notag\\[-0.2em]
 &\texttt{8215204fc36a0ef4493ab28982a7dae5}.
 \label{eq:tpc35-certificate-digest}
\end{align}
Line endings are normalized before the source hash is taken.  The
certificate digest hashes the canonical JSON payload before its digest
field is appended.

\subsection{What is proved and what remains open}

The unconditional abstract results are the equal-deletion and
same-source Gram identities and lower bounds, the saturation of the
residue-multiplicity certificate, the exact product-slope character
spectrum, the CRT alias identity and threshold, proper-coordinate
non-tensorization, the merge--complete cost ledger, the short-orbit
operator identity, and the ambient integer-incidence bound.  The
unconditional physical result is the same-ultra estimate
\eqref{eq:tpc35-shared-ultra-bound}, together with terminal equality on
that block.

Finite enumeration certifies algebra, finite incidence, and rational
bookkeeping.  It does not prove:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item asymptotic divisor, coefficient, or smooth-weight envelopes;
 \item a lower bound for either physical orbit-Gram norm;
 \item that the physical uniform operator gate is false;
 \item an upper or lower bound for the actual correlation from the
 multiplicity saturation theorem;
 \item suppression of bad multiplicative characters for the physical
 coefficient vector;
 \item a complete separable product--slope decomposition of the actual
 orbit-sliced mask with total cost \(X^{o(1)}\);
 \item a joint three-modulus dispersion or diagonal-scale alias-fiber
 estimate;
 \item control of the distinct-ultra cross terms;
 \item cancellation in the terminal four-M\"obius row correlation;
 \item the coefficient-specific orbit gate
 \eqref{eq:tpc35-coefficient-gate};
 \item the inherited \(Q^3\) column-energy or scalar-shell gate;
 \item an affine Chowla theorem, M\"obius disjointness theorem, or breach
 of sieve parity;
 \item positivity or a Hardy--Littlewood prime-pair asymptotic; or
 \item infinitely many twin primes.
\end{enumerate}

The paper therefore advances the proof program in a deliberately bounded
way: two tempting uniform shortcuts are shown to saturate in their stated
abstract classes, one coherent product-slope operator is exactly
diagonalized, the first orbit-scale alias depth compatible with the
diagonal budget is identified, and
one physical divisor block is improved.  The next unproved input is
coefficient-sensitive cancellation in
\eqref{eq:tpc35-signed-spectral-target}, or a joint CRT theorem strong
enough to imply it after physical reassembly.  This scoped boundary is
consistent with the classical parity phenomenon in sieve theory
\citep{HeathBrown1982Parity}; it is not a parity-breaking theorem.
