\section{The inherited orbit-sliced gate}
\label{sec:tpc35-inherited-gate}

We use the physical notation and proved estimates of TPC-32--TPC-34
\citep{WangTPC32,WangTPC33,WangTPC34}.  They are restated to separate theorems about
the actual M\"obius kernel from the abstract route diagnostics below.

\subsection{Rows, orbit, and ultra increment}

Fix \(h\in\Z\setminus\{0\}\), put \(H=\operatorname{rad}|h|\), and work
on a dyadic packet with
\begin{equation}
 Q=LD,\qquad QJ\asymp X,\qquad R\le T<U_0\asymp X.
 \label{eq:tpc35-scales}
\end{equation}
The inherited source-compatible packet also satisfies, for a fixed
\(0<\delta<1/2\),
\begin{equation}
 R=X^{1/2-\delta+o(1)},\qquad
 D\le R^{1/2+o(1)},\qquad
 L>\max\{2R,2|h|\}.
 \label{eq:tpc35-source-separation}
\end{equation}
A row is
\begin{equation}
 \alpha=(\ell_\alpha,d_\alpha),\qquad
 m_\alpha=\ell_\alpha d_\alpha\asymp Q,
 \label{eq:tpc35-row}
\end{equation}
where \(\ell_\alpha\asymp L\) is prime, \(d_\alpha\asymp D\) is
squarefree, and \((d_\alpha,H)=1\).  The scale separation in
\eqref{eq:tpc35-source-separation} makes the integer \(m_\alpha\)
determine the row label \(\alpha\) uniquely.  There are \(O(Q)\) rows.
The two physical coefficient systems obey
\begin{align}
 \sum_\alpha|\gamma_\alpha^{(i)}|&\ll X^{o(1)}Q,
 \label{eq:tpc35-row-l1}\\
 \sum_\alpha|\gamma_\alpha^{(i)}|^2&\ll X^{o(1)}Q,
 \qquad i=1,2.
 \label{eq:tpc35-row-l2}
\end{align}
The logarithm in the original \(L^2\) bound is absorbed into \(X^{o(1)}\).

For \(j\) in an interval of length \(O(J)\), put
\begin{equation}
 N_\alpha(j)=m_\alpha j+h\asymp X.
 \label{eq:tpc35-target}
\end{equation}
The inherited packet and its terminal horizon are chosen so that
\begin{equation}
 T<\min_{\alpha,j}N_\alpha(j)
 \le \max_{\alpha,j}N_\alpha(j)<U_0.
 \label{eq:tpc35-terminal-range}
\end{equation}
This is the terminal-range condition of TPC-34; in particular, the full
target \(N_\alpha(j)\) is one of the ultra divisors retained below.
Every divisor \(w\mid N_\alpha(j)\) on the physical support satisfies
\begin{equation}
 (w,m_\alpha jH)=1.
 \label{eq:tpc35-divisor-primitivity}
\end{equation}
In particular \((w,j)=(w,h)=(w,m_\alpha)=1\).

The actual bounded multiplier is
\begin{equation}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)
 =\one_{\ell_\alpha\ne\ell_\gamma}
  \one_{|m_\alpha-m_\gamma|>QX^{-\kappa_0}}
  \one_{(d_\alpha,d_\gamma)\le X^{\kappa_0}}
  \Xi_{\alpha,\gamma}(j)\cW_{\alpha,\gamma}(j/J),
 \label{eq:tpc35-actual-multiplier}
\end{equation}
where the periodic and smooth factors are uniformly bounded.  Define
\begin{equation}
 a_R(u)=-\mu(u)\log u,\qquad
 C_m(j)=\sum_{\substack{T<u\le U_0\\u\mid mj+h}}a_R(u).
 \label{eq:tpc35-ultra-increment}
\end{equation}
Divisor bounds give \( |C_m(j)|\ll X^{o(1)}\), uniformly on the packet.

\subsection{Orbit slicing and Gram decomposition}

The left orbit slices and their energy are
\begin{align}
 Y_{\gamma,j}^L
 &:=\sum_\alpha\gamma_\alpha^{(1)}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\alpha}(j),
 \label{eq:tpc35-left-slice}\\
 V_L&:=\sum_{\gamma,j}|Y_{\gamma,j}^L|^2.
 \label{eq:tpc35-left-energy}
\end{align}
The right objects exchange the two row systems:
\begin{align}
 Y_{\alpha,j}^R
 &:=\sum_\gamma\gamma_\gamma^{(2)}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\gamma}(j),
 \label{eq:tpc35-right-slice}\\
 V_R&:=\sum_{\alpha,j}|Y_{\alpha,j}^R|^2.
 \label{eq:tpc35-right-energy}
\end{align}
TPC-34 proves that
\begin{equation}
 V_L+V_R\ll X^{o(1)}\frac{Q^3}{J}
 \label{eq:tpc35-orbit-gate}
\end{equation}
is sufficient for the inherited scalar shell estimate.  It also proves
the complete input--copy diagonal bound
\begin{equation}
 V_{L,\Delta}+V_{R,\Delta}\ll X^{o(1)}Q^2J.
 \label{eq:tpc35-orbit-diagonal}
\end{equation}

For each \(j\), let
\begin{equation}
 (M_j^L)_{\gamma,\alpha}
 =\mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\alpha}(j),
 \qquad
 G_L^{\rm orb}=\sum_j(M_j^L)^*M_j^L.
 \label{eq:tpc35-left-Gram}
\end{equation}
Write \(G_L^{\rm orb}=D_L^{\rm orb}+O_L^{\rm orb}\), with \(D\) the
entrywise diagonal, and define the right objects symmetrically.  Then
\begin{equation}
 V_L=\langle G_L^{\rm orb}\gamma^{(1)},\gamma^{(1)}\rangle.
 \label{eq:tpc35-coefficient-Gram}
\end{equation}
The previously displayed uniform sufficient condition is
\begin{equation}
 \|O_L^{\rm orb}\|_{\op}+\|O_R^{\rm orb}\|_{\op}
 \ll X^{o(1)}\frac{Q^2}{J},
 \label{eq:tpc35-uniform-op-gate}
\end{equation}
and a Hilbert--Schmidt sufficient interface has squared scale
\begin{equation}
 \|O_L^{\rm orb}\|_{\HS}^2+\|O_R^{\rm orb}\|_{\HS}^2
 \ll X^{o(1)}\frac{Q^4}{J^2}.
 \label{eq:tpc35-uniform-HS-gate}
\end{equation}
Neither estimate is inherited as a theorem.

The direct coefficient--specific sufficient condition already identified
in TPC-34 is
\begin{equation}
 |V_{L,\ne}|+|V_{R,\ne}|
 \ll X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc35-coefficient-gate}
\end{equation}
It is stronger than logically necessary, because only the upper bound for
their sum is needed, but it is much weaker than controlling every vector
as in \eqref{eq:tpc35-uniform-op-gate}.  The role of this paper is to show
why the two convenient uniform routes saturate in broad abstract classes
and to identify a complete finite-model spectrum that could feed into
\eqref{eq:tpc35-coefficient-gate} after a separate physical reassembly
lemma; we do not claim to discover the coefficient gate for the first
time.

\subsection{Endpoint scales}

At the high--\(\beta\) packet,
\begin{equation}
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)}.
 \label{eq:tpc35-high-beta-scales}
\end{equation}
The underlying source and row scales are
\begin{equation}
 L=X^{99979/210000+o(1)},\qquad
 D=X^{10049/52500+o(1)}.
 \label{eq:tpc35-high-beta-LD}
\end{equation}
In particular,
\begin{equation}
 D=o(Q),\qquad J=o(Q),\qquad DJ=o(Q^2),\qquad D\le X/T
 \label{eq:tpc35-endpoint-consequences}
\end{equation}
for sufficiently large \(X\).
The basic identities used repeatedly below are
\begin{align}
 QJ&=X^{1+o(1)},
 &\frac{Q}{J^2}&=X^{1/400+o(1)},
 \label{eq:tpc35-basic-ledger-one}\\
 \frac{T}{J}&=X^{107/2000+o(1)},
 &\frac{J^2}{T}&=X^{279/1000+o(1)}.
 \label{eq:tpc35-basic-ledger-two}
\end{align}
Every assertion involving these exponents is an endpoint accounting
statement; it does not replace a uniform estimate on the full parameter
range.
