\section{Introduction}
\label{sec:tpc35-introduction}

The matched residual chain now has a sharply localized unresolved object.
TPC-32 isolates a distinguished zero--frequency shell, TPC-33 converts it
to two physical column energies, and TPC-34 performs the corresponding
\(TT^*\) expansion and orbit slicing
\citep{WangTPC32,WangTPC33,WangTPC34}.  After closing the complete
Gram--copy diagonal, the remaining sufficient estimate is
\begin{equation}
 V_L+V_R\ll X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc35-intro-orbit-gate}
\end{equation}
Its proved diagonal is \(O(X^{o(1)}Q^2J)\).  At the endpoint
\begin{equation}
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
 \label{eq:tpc35-intro-scales}
\end{equation}
the ratio between the allowance in \eqref{eq:tpc35-intro-orbit-gate}
and that diagonal is only
\begin{equation}
 \frac{Q^3/J}{Q^2J}=\frac{Q}{J^2}
 =X^{1/400+o(1)}.
 \label{eq:tpc35-intro-margin}
\end{equation}
Thus a useful next step must distinguish a genuine near--diagonal
mechanism from a norm inequality whose worst direction is irrelevant to
the physical coefficients.

This paper audits three routes suggested at the end of TPC-34:
uniform Gram norms, one--modulus projective Plancherel, and multi--modulus
or integer incidence.  The purpose is not to manufacture a stronger
claim from a larger formalism.  It is to prove exactly which pieces close,
which abstract information is insufficient, and what signed quantity a
future theorem must control.

\subsection{Uniform Gram norms: an exact aspect--ratio calculation}

The operator and Hilbert--Schmidt conditions in TPC-34 were stated only as
convenient sufficient interfaces.  We show that they cannot follow from
the broad data used by a sign--blind majorant.  In the equal--deletion
phase model, let
\[
 A=\mathbf1\mathbf1^*-I_n,\qquad
 M_j=AD_j,\qquad 1\le j\le t<n,
\]
where the diagonal entries of every \(D_j\) have modulus one.  If \(R\)
is the \(t\times n\) phase matrix, then the off--diagonal part of
\(\sum_jM_j^*M_j\) is not merely bounded by a frame expression: it is
exactly
\begin{equation}
 O=(n-2)(R^*R-tI_n).
 \label{eq:tpc35-intro-exact-O}
\end{equation}
Rank and trace alone therefore give
\begin{align}
 \|O\|_{\op}
 &\ge(n-2)\max\{t,n-t\},
 \label{eq:tpc35-intro-op-lower}\\
 \|O\|_{\HS}^2
 &\ge(n-2)^2nt(n-t).
 \label{eq:tpc35-intro-hs-lower}
\end{align}
The bounds are attained by a partial Fourier matrix.  At
\(n\asymp Q,t\asymp J\), their scales are \(Q^2\) and \(Q^4J\), whereas
the previous sufficient gates ask for \(Q^2/J\) and \(Q^4/J^2\).
A block calculation shows that deleting every pair from the same prime
source does not change this conclusion at the abstract scale.

The quantifier is essential.  These theorems concern a class retaining
only cardinality, unit--phase, and deletion data.  The physical matrix has
additional gcd projectors, near--row deletion, smooth weights, M\"obius
zeros, and a distinguished coefficient vector.  Entry deletion is not an
order operation for a Hermitian off--diagonal matrix.  We therefore do
\emph{not} prove that the physical operator is large or that its uniform
gate is false.  We prove that the listed coarse data cannot prove that it
is small.

\subsection{From projective averages to a multiplicative spectrum}

TPC-33 proves an exact projective Plancherel identity over
\(\F_q\).  Its incomplete integer implementation is controlled by maximum
residue multiplicities.  We normalize that right--hand side by the
pointwise Cauchy scale and prove the universal lower bound
\begin{equation}
 \mathscr R_q\ge\min\{J_0,S_0\}^{-1/2}.
 \label{eq:tpc35-intro-projective-saturation}
\end{equation}
Balanced nonzero-residue sets attain this scale up to constants.  This is
a saturation theorem for that specific
residue--multiplicity certificate; it is not a lower bound for the actual
correlation energy and not a no--go theorem for all projective methods.

The positive result is an exact diagonalization of a complete, separable
coherent product--slope operator.  If
\[
 R_s(a)=\sum_D f(D)g\bigl(s^{-1}(aD+h)\bigr),\qquad
 (Tb)(j,s)=\sum_{\ell\ne0}b(\ell)R_s(\ell j),
\]
then multiplicative characters diagonalize \(T\):
\begin{equation}
 \sum_{j,s}|Tb(j,s)|^2
 =\frac1{q-1}\sum_\chi
 |\widehat b(\bar\chi)|^2\cE_\chi,
 \qquad
 \|T\|_{\op}^2=\max_\chi\cE_\chi.
 \label{eq:tpc35-intro-character-spectrum}
\end{equation}
The projective second moment is the average of the same
\(\cE_\chi\).  Hence the passage from independent slope averaging to one
coherent coefficient vector is precisely an average--versus--maximum
problem in multiplicative character space.  The factor \(q-1\) can be
attained by a single--character finite model.  At \(q\asymp J\), it is
exactly the energy factor that the one--modulus route fails to supply.
Applying this identity to the physical orbit energy would additionally
require a controlled decomposition of its \(j\)-dependent mask and
incomplete ranges into complete separable layers.  That reassembly lemma
is not proved here.

\subsection{The critical CRT ladder}

For an integer affine determinant \(F\) with \(|F|\le B\asymp X\),
simultaneous congruences modulo \(q_1,\ldots,q_r\) leave the exact aliases
\[
 F=k\,[q_1,\ldots,q_r],
 \qquad |k|\le B/[q_1,\ldots,q_r].
\]
Taking pairwise coprime orbit--scale moduli \(q_i\asymp J\) gives
\begin{equation}
 \frac{X}{J^r}
 =X^{1-r(133/400)+o(1)}.
 \label{eq:tpc35-intro-alias-ladder}
\end{equation}
Three moduli are the first to reach the margin in
\eqref{eq:tpc35-intro-margin}; four are the first to make the ambient
box strictly no--wrap.  The numerical match
\begin{equation}
 \frac{X}{J^3}=\frac{Q}{J^2}=X^{1/400+o(1)}
 \label{eq:tpc35-intro-critical-match}
\end{equation}
is exact at exponent level.

It is only a route ledger.  We prove two reasons why separate one--modulus
estimates cannot simply be multiplied.  First, a function lifted from one
CRT coordinate has exactly the same normalized projective rms at the
product modulus as it had at that one prime.  Second, the specified
strategy of merging moduli to a single modulus \(P\) and then completing
the \(J\)-long orbit incurs costs whose product obeys the bookkeeping
inequality
\begin{equation}
 (1+X/P)(1+P/J)\ge X/J\asymp Q.
 \label{eq:tpc35-intro-coverage-law}
\end{equation}
A viable three--modulus theorem must therefore keep the coordinates joint
and suppress their principal and proper--coordinate faces in the actual
coefficient direction.

\subsection{A physical gain and the remaining boundary}

Opening both ultra increments inside the orbit--sliced energy, we bound
the block in which the two copies use the same divisor \(u>T\):
\begin{equation}
 \cV_{L,u=}+\cV_{R,u=}
 \ll X^{o(1)}Q^2J(1+Q/T).
 \label{eq:tpc35-intro-physical-ultra}
\end{equation}
At the endpoint it is \(O(X^{o(1)}Q^3J/T)\).  This is a true theorem for
the physical mask and coefficient system.  It is one factor \(J\) smaller
than the analogous two--time block in TPC-34, and it saves the full \(T\)
from the orbit--sliced absolute baseline.  It nevertheless exceeds the
required \(Q^3/J\) by \(J^2/T\).

We also record the exact short--orbit incidence operator and an ambient
integer--line Schur bound.  They explain why congruence uniqueness is
valuable but does not by itself control how many different divisor atoms
can land at the same orbit time.

\subsection{Claim boundary and organization}

The conclusions are route diagnostics and exact finite spectral
identities.  They do not establish the coefficient--specific physical
off--diagonal estimate.  In particular, this paper proves no suppression
of all bad multiplicative characters, no controlled complete separable
decomposition of the physical mask, no joint three--modulus dispersion
theorem, no affine Chowla estimate, no positivity statement, no
Hardy--Littlewood prime--pair asymptotic, no infinitely many twin primes,
and no breach of sieve parity.

\Cref{sec:tpc35-inherited-gate} restates the physical interface.
\Cref{sec:tpc35-uniform-gram} proves the aspect--ratio theorems.
\Cref{sec:tpc35-projective-saturation} proves one--modulus saturation.
\Cref{sec:tpc35-product-spectrum} gives the exact character spectrum.
\Cref{sec:tpc35-crt-alias} develops the CRT ladder and non--tensorization.
\Cref{sec:tpc35-physical-ultra} proves the physical same--ultra estimate.
\Cref{sec:tpc35-integer-incidence} treats short--orbit and integer
incidence.  The final two sections give the endpoint ledger, next gate,
certificate, and exact claim boundary.
