\section{Saturation of the residue-multiplicity projective route}
\label{sec:tpc35-projective-saturation}

TPC-33 proves an exact determinant--fiber second moment over
\(\F_q\) and extends it to incomplete integer slope sets by grouping
elements into residue classes.  We now measure the strongest normalized
factor that this specific multiplicity bound can certify.  This should not
be confused with a lower bound on the correlations being estimated.

\subsection{Normalization}

Let \(q\) be prime and let \(\cJ,\cS\) be finite integer sets, with no
element divisible by \(q\).  Write
\begin{equation}
 J_0=|\cJ|,\qquad S_0=|\cS|,
 \label{eq:tpc35-set-sizes}
\end{equation}
and define
\begin{equation}
 \nu_{\cA}(r)=\#\{a\in\cA:a\equiv r\pmod q\},\qquad
 \nu_{\cA}^*=\max_{r\in\F_q^\times}\nu_{\cA}(r).
 \label{eq:tpc35-residue-multiplicity}
\end{equation}
The incomplete projective estimate in TPC-33 has, after suppressing the
common coefficient and function norms, the right--hand side
\[
 q\nu_{\cJ}^*\nu_{\cS}^*.
\]
The pointwise Cauchy bound summed over the \(J_0S_0\) slope pairs has
scale \(J_0S_0\).  We therefore define the squared certificate factor
\begin{equation}
 \mathscr R_q^2(\cJ,\cS)
 :=\frac{q\nu_{\cJ}^*\nu_{\cS}^*}{J_0S_0}.
 \label{eq:tpc35-certificate-factor}
\end{equation}
This is not the ``rms loss relative to complete residue averaging'' used
in TPC-33.  It is a different normalization: the ratio of that
multiplicity right--hand side to the total pointwise Cauchy scale.

\subsection{Universal lower bound and balanced-set sharpness}

\begin{theorem}[Incomplete multiplicity saturation]
\label{thm:tpc35-multiplicity-saturation}
For every prime \(q\) and every nonempty pair \(\cJ,\cS\) as above,
\begin{equation}
 \boxed{
 \mathscr R_q^2(\cJ,\cS)
 \ge\frac1{\min\{J_0,S_0\}},
 \qquad
 \mathscr R_q(\cJ,\cS)
 \ge\min\{J_0,S_0\}^{-1/2}.}
 \label{eq:tpc35-multiplicity-lower}
\end{equation}
Conversely, if \(M:=\min\{J_0,S_0\}\ge2\), there are a prime \(q\) and
balanced nonzero-residue sets of those cardinalities for which
\begin{equation}
 \boxed{
 \mathscr R_q^2(\cJ,\cS)<\frac4M.}
 \label{eq:tpc35-balanced-sharpness}
\end{equation}
Thus the exponent in \eqref{eq:tpc35-multiplicity-lower} is sharp for
this certificate.
\end{theorem}

\begin{proof}
By symmetry assume \(J_0\le S_0\).  Pigeonhole gives
\begin{equation}
 \nu_{\cA}^*\ge
 \max\left\{1,\frac{|\cA|}{q-1}\right\}.
 \label{eq:tpc35-pigeonhole}
\end{equation}
There are three ranges.

If \(q\le J_0\), apply the second term of
\eqref{eq:tpc35-pigeonhole} to both sets:
\[
 \mathscr R_q^2
 \ge\frac{q}{(q-1)^2}\ge\frac1q\ge\frac1{J_0}.
\]
If \(J_0<q\le S_0\), use \(\nu_{\cJ}^*\ge1\) and
\(\nu_{\cS}^*\ge S_0/(q-1)\):
\[
 \mathscr R_q^2\ge\frac{q}{J_0(q-1)}\ge\frac1{J_0}.
\]
Finally, if \(q>S_0\), both multiplicities are at least one and
\[
 \mathscr R_q^2\ge\frac{q}{J_0S_0}>\frac1{J_0}.
\]
This proves \eqref{eq:tpc35-multiplicity-lower}.

For sharpness, Bertrand's postulate supplies a prime
\(J_0<q\le2J_0\).  Choose \(\cJ\) with one element in each of \(J_0\)
distinct nonzero residue classes, so \(\nu_{\cJ}^*=1\).  Distribute the
\(S_0\) elements of \(\cS\) as evenly as possible among the \(q-1\)
nonzero classes.  Then
\[
 \nu_{\cS}^*\le\frac{S_0}{q-1}+1.
\]
Integer representatives with these residue multiplicities plainly
exist.  Therefore
\[
 \mathscr R_q^2
 \le\frac{q}{J_0(q-1)}+\frac{q}{J_0S_0}
 <\frac2{J_0}+\frac2{S_0}
 \le\frac4{J_0},
\]
which proves \eqref{eq:tpc35-balanced-sharpness}.
\end{proof}

\begin{remark}[The continuous proxy]
The algebraic envelope
\[
 \Phi(q)=\frac1q+\frac1{J_0}+\frac1{S_0}
 +\frac{q}{J_0S_0}
\]
is minimized at \(q=\sqrt{J_0S_0}\), with value
\((J_0^{-1/2}+S_0^{-1/2})^2\).  This is a useful continuous ledger and is
checked by the certificate.  It is not asserted to be an exact
coefficient-one upper bound for an interval after its zero residue class
has been removed.
\end{remark}

\begin{remark}[What is saturated]
The theorem lower--bounds the best right--hand side factor available from
maximum residue multiplicities.  The actual projective correlation may
be zero even when \(\mathscr R_q\) is large.  A method using cancellation
between residue classes, weights adapted to the coefficient vector, more
than one modulus jointly, or a direct integer large--sieve estimate is not
covered by the theorem; those belong to the broader large--sieve framework
\citep{Bombieri1965,IwaniecKowalski2004}.
\end{remark}

\subsection{Endpoint consequence}

In the orbit--slope application, \(J_0\asymp J\), while the other
physical slope range may be shorter or longer.  Since
\(\min\{J_0,S_0\}\le J_0\), even the most optimistic amplitude factor
certified by the one--modulus multiplicity right--hand side cannot improve
on \(J^{-1/2}\), or \(J^{-1}\) at energy level.  Applied optimistically to
the orbit--sliced absolute scale \(Q^3J\), it reaches only
\begin{equation}
 Q^3J\cdot J^{-1}=Q^3.
 \label{eq:tpc35-one-modulus-ledger}
\end{equation}
The desired energy is \(Q^3/J\).  With a common denominator \(2000\),
\begin{equation}
 Q^3J=X^{4670/2000+o(1)},\qquad
 Q^3=X^{4005/2000+o(1)},\qquad
 \frac{Q^3}{J}=X^{3340/2000+o(1)}.
 \label{eq:tpc35-projective-exponent-ledger}
\end{equation}
Thus this certificate misses exactly one further factor \(J\) at energy
level.  The next section identifies that factor as a possible
average--to--maximum loss in multiplicative character space.
