\section{Aspect-ratio obstructions to uniform Gram gates}
\label{sec:tpc35-uniform-gram}

We first ask whether the uniform conditions
\eqref{eq:tpc35-uniform-op-gate}--\eqref{eq:tpc35-uniform-HS-gate}
could follow from the most visible geometry: \(n\) input rows, \(t\) orbit
times, bounded phases, and deletion of the equal row.  The answer is no
for that abstract information class.  The calculation is exact and is a
frame identity rather than a probabilistic counterexample.
TPC-34 already gives one coherent constant-phase witness at the
sign-blind scale \citep{WangTPC34}.  The theorem below upgrades that
witness to rank--trace lower bounds valid for every unit-phase
equal-deletion frame and identifies the sharp Fourier case.

\subsection{Equal-row deletion}

Let \(n\ge3\), \(1\le t<n\), and let
\begin{equation}
 A=\mathbf1\mathbf1^*-I_n.
 \label{eq:tpc35-equal-deletion-A}
\end{equation}
For \(1\le j\le t\), choose phases \(c_{j\alpha}\in\C\) with
\(|c_{j\alpha}|=1\), and put
\begin{equation}
 D_j=\operatorname{diag}(c_{j1},\ldots,c_{jn}),\qquad
 M_j=AD_j.
 \label{eq:tpc35-phase-matrices}
\end{equation}
Let \(R=(c_{j\alpha})_{j,\alpha}\in\C^{t\times n}\), define
\begin{equation}
 G=\sum_{j=1}^tM_j^*M_j,
 \label{eq:tpc35-abstract-Gram}
\end{equation}
and let \(O=G-\operatorname{diag}G\).

\begin{theorem}[Exact equal-deletion Gram identity]
\label{thm:tpc35-equal-deletion-Gram}
With the preceding notation,
\begin{align}
 G&=tI_n+(n-2)R^*R,
 \label{eq:tpc35-G-exact}\\
 \operatorname{diag}G&=(n-1)tI_n,
 \label{eq:tpc35-G-diagonal}\\
 &\boxed{O=(n-2)(R^*R-tI_n).}
 \label{eq:tpc35-O-exact}
\end{align}
Consequently
\begin{equation}
 \boxed{
 \|O\|_{\op}\ge(n-2)\max\{t,n-t\},}
 \label{eq:tpc35-O-op-lower}
\end{equation}
and
\begin{equation}
 \boxed{
 \|O\|_{\HS}^2\ge(n-2)^2nt(n-t).}
 \label{eq:tpc35-O-HS-lower}
\end{equation}
Both lower bounds are equalities when \(R\) consists of any \(t\) rows of
an \(n\times n\) complex Fourier matrix.
\end{theorem}

\begin{proof}
Writing \(J_n=\mathbf1\mathbf1^*\), one has
\begin{equation}
 A^2=(J_n-I_n)^2=I_n+(n-2)J_n.
 \label{eq:tpc35-A-square}
\end{equation}
Moreover,
\[
 \sum_{j=1}^tD_j^*J_nD_j=R^*R.
\]
This proves \eqref{eq:tpc35-G-exact}.  Every diagonal entry of \(R^*R\)
is \(t\), which gives \eqref{eq:tpc35-G-diagonal} and
\eqref{eq:tpc35-O-exact}.

Let \(\lambda_1,\ldots,\lambda_n\) be the eigenvalues of \(R^*R\).
They are nonnegative,
\begin{equation}
 \operatorname{rank}(R^*R)\le t,
 \qquad
 \sum_i\lambda_i=\operatorname{tr}(R^*R)=nt.
 \label{eq:tpc35-R-rank-trace}
\end{equation}
Because \(t<n\), zero is an eigenvalue, so
\(\|R^*R-tI\|_{\op}\ge t\).  The largest eigenvalue is at least \(n\),
since at most \(t\) nonzero eigenvalues have sum \(nt\).  Hence the same
norm is at least \(n-t\), proving \eqref{eq:tpc35-O-op-lower}.

For the Hilbert--Schmidt norm, Cauchy--Schwarz on the nonzero eigenvalues
gives
\[
 \sum_i\lambda_i^2\ge\frac{(nt)^2}{t}=n^2t.
\]
Therefore
\begin{align*}
 \|R^*R-tI\|_{\HS}^2
 &=\sum_i(\lambda_i-t)^2\\
 &=\sum_i\lambda_i^2-2t(nt)+nt^2\\
 &\ge nt(n-t),
\end{align*}
which proves \eqref{eq:tpc35-O-HS-lower}.

For \(t\) Fourier rows, \(RR^*=nI_t\).  Thus the eigenvalues of \(R^*R\)
are \(n\) with multiplicity \(t\) and zero with multiplicity \(n-t\),
giving equality throughout.
\end{proof}

\begin{corollary}[Aspect-ratio gap]
\label{cor:tpc35-aspect-ratio-gap}
If \(n\asymp Q\), \(t\asymp J\), and \(J=o(Q)\), then every matrix in
the model satisfies
\begin{equation}
 \|O\|_{\op}\gg Q^2,
 \qquad
 \|O\|_{\HS}^2\gg Q^4J.
 \label{eq:tpc35-abstract-scales}
\end{equation}
Relative to \eqref{eq:tpc35-uniform-op-gate} and
\eqref{eq:tpc35-uniform-HS-gate}, these scales are larger by factors
\(J\) and \(J^3\), respectively.
\end{corollary}

\begin{proof}
Since \(n-t\asymp Q\), the operator lower bound is
\(\gg n(n-t)\asymp Q^2\).  The Hilbert--Schmidt lower bound is
\[
 (n-2)^2nt(n-t)\asymp n^4t\asymp Q^4J.
\]
The ratios to \(Q^2/J\) and \(Q^4/J^2\) are \(J\) and \(J^3\).
\end{proof}

\subsection{Same-source block deletion}

The physical mask also deletes row pairs sharing the same prime source.
The following block model shows that this deletion does not, by itself,
remove the aspect--ratio effect.

Suppose \(n=kr\) and partition the coordinates into \(k\) blocks of size
\(r\).  Put
\begin{equation}
 B=\bigoplus_{g=1}^kJ_r,
 \qquad A=J_n-B.
 \label{eq:tpc35-block-deletion-A}
\end{equation}
Thus \(A_{\alpha\beta}=0\) when the two coordinates lie in the same
source block.  Retain the phase matrices \(D_j\) and \(R\) above; let
\(R_g\in\C^{t\times r}\) be the columns of \(R\) in block \(g\).

\begin{theorem}[Exact same-source block formula]
\label{thm:tpc35-block-Gram}
Assume \(n\ge2r\).  For \(M_j=AD_j\), let
\(G=\sum_jM_j^*M_j\) and \(O=G-\operatorname{diag}G\).  Then
\begin{equation}
 A^2=(n-2r)J_n+rB,
 \label{eq:tpc35-block-A-square}
\end{equation}
and
\begin{equation}
 \boxed{
 O=(n-2r)(R^*R-tI_n)
 +r\bigoplus_{g=1}^k(R_g^*R_g-tI_r).}
 \label{eq:tpc35-block-O}
\end{equation}
If \(t<n\), then
\begin{equation}
 \boxed{
 \|O\|_{\op}
 \ge (n-2r)(n-t)-rt}
 \label{eq:tpc35-block-op-lower}
\end{equation}
whenever the right-hand side is positive.
\end{theorem}

\begin{proof}
The block relations
\[
 J_n^2=nJ_n,\qquad J_nB=BJ_n=rJ_n,\qquad B^2=rB
\]
give \eqref{eq:tpc35-block-A-square}.  Conjugating by \(D_j\) and
summing gives
\[
 G=(n-2r)R^*R+r\bigoplus_gR_g^*R_g.
\]
Every diagonal entry equals \(t(n-r)\), yielding
\eqref{eq:tpc35-block-O}.

Choose a unit eigenvector \(x\) for the largest eigenvalue \(\lambda\) of
\(R^*R\).  As in \eqref{eq:tpc35-R-rank-trace}, \(\lambda\ge n\).
Writing \(x=\bigoplus_gx_g\), positivity gives
\begin{align*}
 \langle Ox,x\rangle
 &=(n-2r)(\lambda-t)
 +r\sum_g\bigl(\|R_gx_g\|_2^2-t\|x_g\|_2^2\bigr)\\
 &\ge(n-2r)(n-t)-rt.
\end{align*}
If this number is positive, it is bounded above by \(\|O\|_{\op}\).
\end{proof}

In the corresponding exponent-scale block model,
\[
 n=QX^{o(1)},\qquad r=DX^{o(1)},\qquad t=JX^{o(1)}.
\]
The inherited source separation
\eqref{eq:tpc35-source-separation} and endpoint scales
\eqref{eq:tpc35-high-beta-LD} imply \(D=o(Q)\), \(J=o(Q)\), and
\(D J=o(Q^2)\).  Hence the right side of
\eqref{eq:tpc35-block-op-lower} has exponent scale \(Q^2X^{o(1)}\).
The same-source deletion alone therefore does not supply the factor \(J\)
required by the uniform operator gate.

\subsection{What the obstruction does and does not prove}

\begin{corollary}[Coarse-data method boundary]
\label{cor:tpc35-uniform-method-boundary}
No argument valid for every equal-deletion phase model
\eqref{eq:tpc35-phase-matrices}, using only \(n,t\), unit-modulus phase
envelopes, and equal-row deletion, can certify the uniform scales in
\eqref{eq:tpc35-uniform-op-gate} or
\eqref{eq:tpc35-uniform-HS-gate} when \(n\asymp Q,t\asymp J\to\infty\).
The same conclusion holds after same-source deletion for the block class
above whenever the right side of \eqref{eq:tpc35-block-op-lower} is
\(\asymp Q^2\).
\end{corollary}

The corollary is a quantifier statement about an abstract majorant class.
It does not say that the actual \(O_L^{\rm orb}\) or \(O_R^{\rm orb}\)
has size \(Q^2\).  The physical entries contain arithmetic zeros, an
opened gcd projector, near--row deletion, smooth weights, and M\"obius
coefficients.  Nor may one infer a physical lower bound by deleting
entries from the abstract \(O\): an off--diagonal Hermitian matrix has no
entrywise monotonicity for its operator norm.  The calculation instead
forces the next proof to use some information absent from the broad
phase model.  The physical vector \(\gamma^{(i)}\) in
\eqref{eq:tpc35-coefficient-Gram} is the most economical such information.
