\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\hypersetup{
 pdftitle={Additive Quotient Tomography of the Identity Bucket: Minimal Fourier Recovery, Folded Parseval, and the Twist-Stable Mobius Gate},
 pdfauthor={Liang Wang},
 pdfsubject={Exact additive recovery of the zero alias in an orbit-sliced Mobius energy gate},
 pdfkeywords={Mobius correlation, additive character, quotient tomography, CRT completion, folded Parseval, alias recovery, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cN}{\mathcal N}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cW}{\mathcal W}
\newcommand{\cY}{\mathcal Y}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\op}{\operatorname{op}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\ee}[1]{\exp(2\pi i #1)}

\title{\textbf{Additive Quotient Tomography of the Identity Bucket:}\\
\textbf{Minimal Fourier Recovery, Folded Parseval,}\\
\textbf{and the Twist--Stable M\"obius Gate}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC--38 showed that a three--modulus multiplicative completion identifies
the recombined output with the joint--alias sum, not its original equality
column.  Multiplicative
characters cannot distinguish those aliases because every one lies in the
same ratio bucket.  We construct the missing coefficient--free recovery
map on the additive quotient of that bucket.

Let \(M\) be the three--modulus CRT product, let \(|F|\le B\), and put
\[
 L=\left\lfloor\frac BM\right\rfloor,
 \qquad q=L+1,
 \qquad \omega=\ee{1/q}.
\]
Then \(qM>B\), and on the full determinant window
\[
 \one_{M\mid F}\frac1q\sum_{\nu=0}^{q-1}
 \ee{\nu F/(qM)}
 =\one_{qM\mid F}
 =\one_{F=0}.
\]
Full/proper face recombination is essential in this identity: the additive
average alone does not remove determinants with \(M\nmid F\).  For arbitrary
Hilbert columns \(\mathscr Z_k\), \(-L\le k\le L\), define
\[
 \mathscr Y_\nu=\sum_{k=-L}^{L}\omega^{\nu k}\mathscr Z_k.
\]
The quotient projector gives the exact recovery formula with unit normalized
amplification
\[
 \mathscr Z_0=\frac1q\sum_{\nu=0}^{q-1}\mathscr Y_\nu,
 \qquad
 \|\mathscr Z_0\|^2\le
 \frac1q\sum_{\nu=0}^{q-1}\|\mathscr Y_\nu\|^2.
\]

We prove the Hilbert--valued folded Parseval identity
\[
 \frac1q\sum_{\nu=0}^{q-1}\|\mathscr Y_\nu\|^2
 =\|\mathscr Z_0\|^2+
 \sum_{r=1}^{L}\|\mathscr Z_r+\mathscr Z_{r-q}\|^2.
\]
The normalized scalar alias--index tomography Gram has eigenvalues \(2,1,0\), with
multiplicities \(L,1,L\), respectively.  Its kernel consists precisely of
antisymmetric folded alias pairs and does not intersect the equality
column.  Thus the minimal bank is weaker than a raw alias trace or a full
Gram estimate while still recovering the one column required by the
physical problem.

The number \(q=L+1\) is optimal.  Even allowing arbitrary nonzero phase
nodes and complex recovery weights, no bank of at most \(L\) phase
measurements recovers the central coefficient of every Laurent polynomial
supported on \([-L,L]\).  The regular \(q\)-gon attains this lower bound and
also minimizes the normalized noise amplification.  Under positive
weights, every minimally sampled optimal rule is a rotation of this
regular polygon with equal weights.  Deleting any one twist from the
minimal bank destroys coefficient--free exact recovery.

For the orbit--sliced prime--M\"obius interface, the twist is
\(\ee{\nu(su-N)/(qM)}\).  At the endpoint,
\[
 q\asymp 1+X/M=X^{1/400+o(1)},
 \qquad
 Q^2Jq=X^{o(1)}Q^3/J.
\]
Consequently, a square--average bound of this target size for the
recombined twisted outputs would close the inherited equality gate with no
additional alias loss.  The corresponding full/proper fields have exactly
the same coefficient masses as their untwisted versions.  However, folded
Parseval retains the original equality energy as a positive summand, and
the terminal expansion retains affine four--M\"obius correlations.

We therefore prove an exact, minimally sampled equality projector and a
new twist--stable conditional route, not the required M\"obius energy
estimate.  No affine Chowla theorem, parity breach, Hardy--Littlewood
asymptotic, or twin--prime theorem is claimed.
\end{abstract}

\noindent\textbf{Keywords:}
M\"obius correlation; additive character; quotient tomography; CRT
completion; folded Parseval; alias recovery; parity boundary.

\medskip
\noindent\textbf{MSC 2020:}
Primary 11L07, 11N35; Secondary 15A18, 42A16, 42C15.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/quotient-projector}
\input{sections/folded-parseval}
\input{sections/minimality-conditioning}
\input{sections/completion-comparison}
\input{sections/twisted-physical-gate}
\input{sections/terminal-boundary}
\input{sections/partial-random-banks}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
