\section{Exact certificate and claim ledger}
\label{sec:tpc41-certificate}

The proofs above are analytic and exact.  A companion standard--library
certificate checks the finite cyclic and convolution identities using
integers, rational arithmetic, modular character orthogonality, and formal
prime--logarithm vectors.  It uses no floating point, random draws, or
optimization--sensitive \texttt{assert} statements.

\subsection{Certified identities}

The frozen certificate verifies:
\begin{enumerate}[label=(\roman*)]
 \item the minimal alias Gram, its \(2,1,0\) spectrum and folded bucket
 decomposition for a declared range of \(L\);
 \item the full \((2L+1)\)-point DFT identity \(H=I\);
 \item exact same--row energy decompositions and the sharp inequality
 \(|\cS_{\rm same}|\le\cD\) on exhaustive small integer atom families;
 \item the allowed alias pairs in
 \eqref{eq:tpc41-physical-alias-pairs};
 \item the nonproportional determinant implication on exhaustive finite
 admissible row--modulus models;
 \item the formal convolution identity
 \(\Lambda*\mu*\mathbf1=\Lambda\) through the frozen integer range; and
 \item all endpoint exponent identities, including
 \begin{equation}
  3\frac{133}{400}=\frac{399}{400},
  \qquad
  1-\frac{399}{400}=\frac1{400},
  \qquad
  2\frac{267}{400}+\frac{133}{400}+\frac1{400}
  =\frac{167}{100}.
  \label{eq:tpc41-certificate-exponents}
 \end{equation}
\end{enumerate}

Running
\begin{quote}
\ttfamily
python experiments/tpc41\_certificate.py\\
python -O experiments/tpc41\_certificate.py
\end{quote}
produces byte--identical canonical JSON records.  The frozen run passes
\begin{equation}
 \boxed{4{,}358{,}451\text{ exact checks}.}
 \label{eq:tpc41-certificate-checks}
\end{equation}
It includes \(80\) minimal and \(80\) full alias Grams,
\(81{,}375\) real and \(3{,}250\) Gaussian--integer atom vectors,
\(80{,}400\) allowed ordered alias pairs, \(693{,}840\) affine
determinants, and the formal convolution through \(n=10{,}000\).
The certificate digest is
\begin{center}
\ttfamily\small
e10174e2448d5323afb586d5855112e596ea7e134cd5899f216ef3a916748fc4.
\end{center}
The SHA--256 hashes of the canonical JSON record and source are,
respectively,
\begin{center}
\ttfamily\small
a12acada9747cb53acf1a5bdc7c763ede4ace5254cc7ce084145c596ada4c107,\\
b08c52e25f8c59105017cb9e602039e7030d4671456be9eb77a22d36b84f54f0.
\end{center}

\subsection{What the certificate does not certify}

The computation does not verify the asymptotic theorem of
\citet{KlurmanMangerelTeravainen2023}, the prime number theorem, the
Mertens zero--free--region estimate, or the multiplicative large sieve;
these are cited analytic inputs.  It is not numerical evidence for random
M\"obius signs.  Its JSON claim ledger explicitly marks as false any claim
that it proves the physical four--M\"obius estimate, a parity breach, a
prime--pair asymptotic, or the twin--prime conjecture.
