\section{The completed convolution shadow and its boundary defect}
\label{sec:tpc41-convolution}

There is a second reason not to attack the expanded four--M\"obius form
term by term.  In an idealized scalar completion, the divisor--row
coefficient collapses exactly under Dirichlet convolution.

Let \(*\) denote Dirichlet convolution, let \(\Lambda\) be the von
Mangoldt function, and let \(\mathbf 1(n)=1\).

\begin{proposition}[Full divisor completion]
\label{prop:tpc41-full-convolution}
For every \(n\ge1\),
\begin{equation}
 \boxed{
 (\Lambda*\mu*\mathbf1)(n)=\Lambda(n).}
 \label{eq:tpc41-full-convolution}
\end{equation}
Consequently, for every finitely supported scalar weight depending only on
the product \(n=\ell dj\), the fully completed model satisfies
\begin{equation}
 \sum_{\ell,d,j}
 \Lambda(\ell)\mu(d)
 \mu(\ell dj+h)W(\ell dj)
 =\sum_n\Lambda(n)\mu(n+h)W(n).
 \label{eq:tpc41-completed-shifted-prime}
\end{equation}
\end{proposition}

\begin{proof}
M\"obius inversion gives \(\mu*\mathbf1=\delta_1\), the identity for
Dirichlet convolution.  Associativity gives
\(\Lambda*(\mu*\mathbf1)=\Lambda\).  Grouping the finite triple sum by
\(n=\ell dj\) proves \eqref{eq:tpc41-completed-shifted-prime}.
\end{proof}

The right side of \eqref{eq:tpc41-completed-shifted-prime} is the shifted
prime--M\"obius correlation studied on average over \(h\) by
\citet{Lichtman2022} and in the broader Hardy--Littlewood--Chowla setting
by \citet{LichtmanTeravainen2022}.  In particular, known results give
qualitative cancellation for almost all shifts once the shift range is
sufficiently larger than a power of \(\log X\).

This identity does not apply unchanged to the physical packet.  A single
projective layer contains a truncated coefficient of the shape
\begin{equation}
 \sum_{\ell dj=n}
 b_\gamma(\ell)f_\gamma(d)\eta_\gamma(j/J),
 \label{eq:tpc41-truncated-convolution}
\end{equation}
where the factors are restricted to prescribed dyadic ranges and inherit
the opposite--row mask.  Even before that mask, the natural model is a
localized convolution
\begin{equation}
 \Lambda_{L_0}*\mu_{D_0}*\mathbf1_{\cJ},
 \label{eq:tpc41-localized-convolution}
\end{equation}
where the subscripts denote restriction to the inherited source dyadic
scales \(L_0,D_0\) and orbit interval \(\cJ\).  It is not
\(\Lambda*\mu*\mathbf1\).  The difference between
\eqref{eq:tpc41-localized-convolution} and an appropriate localized
\(\Lambda\) term is a boundary defect whose Hilbert norm has not been
estimated here.

Two upgrades would be required to turn the identity into a physical
theorem:
\begin{enumerate}[label=(\roman*)]
 \item a localization theorem controlling the dyadic and mask boundary
 defect with power strong enough for
 \eqref{eq:tpc41-Hilbert-equality-target}; and
 \item a vector--valued shifted--prime estimate uniform in the opposite
 row and projective layer, rather than an average over the external shift
 \(h\).
\end{enumerate}
The exact convolution collapse is therefore a route marker.  It shows
that part of the apparent fourfold structure is created by truncation,
but writing the completion is not itself a bound for the truncation
error.

There is one further asymmetry.  At alias \(k=0\),
\((d_\alpha,m_\alpha j+h)=1\), so the two M\"obius values can sometimes be
fused multiplicatively.  At \(k\ne0\), the condition
\((d_\alpha,h+kM)=1\) is not automatic.  Any fusion argument must either
remain on the equality alias or explicitly control these new gcd faces.
