\section{Inherited physical interface}
\label{sec:tpc41-interface}

We restate only the terminal data from TPC--36 and TPC--39 needed in the
new arguments.  All estimates in this section are inherited; the
row--diagonal theorem in the next section is abstract and independent of
their derivation.

\subsection{Rows and endpoint scales}

Fix \(h\in\Z\setminus\{0\}\).  A retained physical row is
\begin{equation}
 \alpha=(\ell_\alpha,d_\alpha),
 \qquad
 \ell_\alpha\asymp L_0,
 \qquad
 d_\alpha\asymp D_0,
 \qquad
 m_\alpha=\ell_\alpha d_\alpha\asymp Q,
 \qquad
 L_0D_0=Q,
 \qquad
 QJ\asymp X,
 \label{eq:tpc41-interface-row}
\end{equation}
where the source separation makes \(m_\alpha\) determine \(\alpha\).
The two source coefficient systems obey
\begin{equation}
 \sum_\alpha|\gamma_\alpha^{(i)}|^2
 \ll X^{o(1)}Q,
 \qquad i=1,2.
 \label{eq:tpc41-interface-source-l2}
\end{equation}
The orbit variable \(j\) ranges through \(O(J)\) positive integers.

Choose three distinct auxiliary primes \(q_1,q_2,q_3\asymp J\) with
\begin{equation}
 \max\cJ<q_i,
 \qquad
 \max_\alpha d_\alpha<q_i<\min_\alpha\ell_\alpha,
 \qquad
 q_i\nmid h,
 \label{eq:tpc41-interface-primes}
\end{equation}
and put
\begin{equation}
 M=q_1q_2q_3.
 \label{eq:tpc41-interface-M}
\end{equation}
The physical regular packet has \((m_\alpha j+h,M)=1\); this property is
unchanged after adding any multiple of \(M\).

At the optimized endpoint,
\begin{equation}
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)},
 \qquad
 M=X^{399/400+o(1)}.
 \label{eq:tpc41-interface-endpoint}
\end{equation}
If every completed determinant satisfies \(|F|\le B\asymp X\), define
\begin{equation}
 L=\left\lfloor\frac BM\right\rfloor,
 \qquad
 q=L+1,
 \qquad
 \cI_B=\{-L,\ldots,L\},
 \qquad
 K_B=2L+1.
 \label{eq:tpc41-interface-aliases}
\end{equation}
Then
\begin{equation}
 K_B=X^{1/400+o(1)}
 =X^{o(1)}\frac{Q}{J^2}.
 \label{eq:tpc41-interface-alias-scale}
\end{equation}
With \(B_0=Q^2J\), the endpoint ledger is
\begin{equation}
 \boxed{
 B_0K_B
 =X^{o(1)}\frac{Q^3}{J}
 =X^{167/100+o(1)}.}
 \label{eq:tpc41-interface-key-ledger}
\end{equation}

\subsection{Terminal atoms and physical coefficients}

For \(k\in\cI_B\), set
\begin{equation}
 n_{\alpha,j,k}=m_\alpha j+h+kM
 \label{eq:tpc41-interface-target}
\end{equation}
and, on the positive terminal support,
\begin{equation}
 b_{\alpha,j,k}
 =-\mu(n_{\alpha,j,k})
   \log(n_{\alpha,j,k})\Phi_0(n_{\alpha,j,k}).
 \label{eq:tpc41-interface-b}
\end{equation}
It is zero outside that support.  The left terminal output at fixed alias
has coordinates
\begin{equation}
 [\mathscr T_k^L]_{\gamma,j}
 =\sum_\alpha c^L_{\alpha,\gamma,j}b_{\alpha,j,k},
 \qquad
 c^L_{\alpha,\gamma,j}
 =\gamma_\alpha^{(1)}
  \mathfrak A_{\alpha,\gamma}^{\rm act}(j).
 \label{eq:tpc41-interface-left-output}
\end{equation}
The right output is obtained by interchanging the two row systems.  The
actual multiplier contains the row separation, gcd, residue, and smooth
masks and satisfies
\begin{equation}
 \sup_{\alpha,\gamma,j}
 |\mathfrak A_{\alpha,\gamma}^{\rm act}(j)|
 \ll X^{o(1)}.
 \label{eq:tpc41-interface-multiplier}
\end{equation}
In particular, the shift \(kM\) changes the terminal atom, not the
inherited row--time multiplier.

The source coefficient \(\gamma_\alpha^{(1)}\) includes the factor
\(\mu(d_\alpha)\).  Consequently a cross--row expansion with
\(\alpha\ne\beta\) contains \(\mu(d_\alpha)\mu(d_\beta)\) in addition to
the two target M\"obius factors.  We will retain the compact notation
\(c^L\) until that expansion is needed.

\subsection{The inherited diagonal theorem}

Define the left and right atomic diagonals by
\begin{align}
 \cD_L
 &=\sum_{\gamma,j}\sum_{\alpha,k}
   |c^L_{\alpha,\gamma,j}|^2|b_{\alpha,j,k}|^2,
 \label{eq:tpc41-interface-DL}\\
 \cD_R
 &=\sum_{\alpha,j}\sum_{\gamma,k}
   |c^R_{\gamma,\alpha,j}|^2|b_{\gamma,j,k}|^2.
 \label{eq:tpc41-interface-DR}
\end{align}
TPC--39 proves
\begin{equation}
 \boxed{
 \cD_L+\cD_R
 \ll X^{o(1)}Q^2JK_B
 =X^{o(1)}\frac{Q^3}{J}.}
 \label{eq:tpc41-interface-diagonal-bound}
\end{equation}
This estimate uses the row \(\ell^2\) ledger and bounded physical masks;
it does not use M\"obius cancellation.  The new point is that it controls
more than the literal atomic diagonal after the alias Gram is taken into
account.

Finally, TPC--39 proves terminal row--alias injectivity: for every fixed
\(j\), the map
\begin{equation}
 (\alpha,k)\longmapsto m_\alpha j+h+kM
 \label{eq:tpc41-interface-injectivity}
\end{equation}
is injective.  This follows from \((j,M)=1\), source separation, and
\begin{equation}
 \max_{\alpha,\beta}|m_\alpha-m_\beta|<M,
 \label{eq:tpc41-interface-row-gap}
\end{equation}
which is automatic at \eqref{eq:tpc41-interface-endpoint}.
