\section{Introduction}
\label{sec:tpc41-introduction}

The TPC programme has progressively separated geometric losses from the
arithmetic cancellation that would be needed at a prime--pair endpoint.
TPC--34 isolates an orbit--sliced Gram operator; TPC--36 gives an exact
soft projective reassembly of the physical row mask; TPC--37 and TPC--38
localize the relevant CRT face and identify its identity bucket; and
TPC--39 recovers the equality alias by a minimal additive Fourier bank
\citep{WangTPC34,WangTPC36,WangTPC37,WangTPC38,WangTPC39}.  TPC--40 then
proves that universal row phasing cannot decorrelate the equality mode at
unit recovery cost \citep{WangTPC40}.

The endpoint left by these papers has two superficially similar types of
terms.  If a physical row \(\alpha\) and an alias \(k\) contribute a
terminal atom
\begin{equation}
 b_{\alpha,j,k}
 =-\mu(m_\alpha j+h+kM)
   \log(m_\alpha j+h+kM)
   \Phi_0(m_\alpha j+h+kM),
 \label{eq:tpc41-intro-terminal-atom}
\end{equation}
then expansion of the folded square produces
\begin{enumerate}[label=(\roman*)]
 \item same--row products with \(\alpha=\beta\) and \(k\ne k'\), which
 look like a long--gap two--M\"obius correlation; and
 \item cross--row products with \(\alpha\ne\beta\), which also retain
 the two source factors \(\mu(d_\alpha)\mu(d_\beta)\) and are therefore
 four--M\"obius expressions.
\end{enumerate}
The first purpose of this paper is to show that these are not two versions
of the same analytic difficulty.

\subsection{The row--diagonal closure}

Let \(k\) range over an alias interval, let \(y\) denote an output
coordinate, and consider measurements
\begin{equation}
 Y_{t,y}=\sum_{\alpha,k}\theta_{t,k}c_{\alpha,y}b_{\alpha,y,k},
 \qquad
 \sum_tw_t=1,
 \qquad |\theta_{t,k}|=1.
 \label{eq:tpc41-intro-measurement}
\end{equation}
The normalized alias Gram is
\begin{equation}
 H_{kk'}=\sum_tw_t\overline{\theta_{t,k}}\theta_{t,k'}.
 \label{eq:tpc41-intro-H}
\end{equation}
If \(\cD\) is the atomic diagonal, the exact contribution from
\(\alpha=\beta\) obeys
\begin{equation}
 \boxed{
 \cE_{\rm same}\le\lambda_{\max}(H)\cD,
 \qquad
 |\cE_{\rm same}-\cD|
 \le\|H-I\|_{\op}\cD.}
 \label{eq:tpc41-intro-general-closure}
\end{equation}
This elementary Gram fact has a decisive endpoint consequence.  For the
minimal bank of TPC--39, \(H\) is a direct sum of one scalar block and
two--by--two all--ones blocks.  Therefore
\begin{equation}
 \cE_{\rm same}\le2\cD,
 \qquad
 |\cE_{\rm same}-\cD|\le\cD.
 \label{eq:tpc41-intro-minimal-closure}
\end{equation}
The apparently difficult two--M\"obius sum is just an inner product inside
each folded pair and is absorbed by \(2|uv|\le|u|^2+|v|^2\).  A full
alias DFT has \(H=I\) and deletes it exactly.

Since the atomic diagonal was already proved to have size
\begin{equation}
 \cD_L+\cD_R
 \ll X^{o(1)}Q^2JK_B
 =X^{o(1)}\frac{Q^3}{J},
 \label{eq:tpc41-intro-diagonal-scale}
\end{equation}
the entire same--row sector is closed.  This removes a false arithmetic
gate rather than proving a special case of Chowla's conjecture.

\subsection{The remaining four--M\"obius form}

For the minimal bank put
\begin{equation}
 u_{\alpha,j,0}=b_{\alpha,j,0},
 \qquad
 u_{\alpha,j,r}=b_{\alpha,j,r}+b_{\alpha,j,r-q}
 \quad(1\le r\le L),
 \label{eq:tpc41-intro-folded-atoms}
\end{equation}
where \(q=L+1\).  After the row diagonal is removed, the left terminal
remainder is exactly
\begin{equation}
 \cF_L
 =\sum_{\gamma,j}\sum_{a=0}^{L}
   \sum_{\alpha\ne\beta}
   c^L_{\alpha,\gamma,j}
   \overline{c^L_{\beta,\gamma,j}}
   u_{\alpha,j,a}\overline{u_{\beta,j,a}},
 \label{eq:tpc41-intro-four-form}
\end{equation}
with a symmetric right form \(\cF_R\).  The necessary and sufficient
one--sided endpoint input, after the already proved diagonal estimate, is
\begin{equation}
 \boxed{
 \operatorname{Re}(\cF_L+\cF_R)
 \ll X^{o(1)}Q^2JK_B.}
 \label{eq:tpc41-intro-true-gate}
\end{equation}
An absolute--value estimate would be stronger than required.

Every expanded row pair contains two nonproportional affine forms in the
orbit variable \(j\).  Nevertheless, their slopes and intercepts grow with
\(X\), the coefficients depend on the shared opposite row, and the target
is an aggregate Hilbert norm.  Existing fixed--form Chowla theorems do not
provide the required uniformity.  We therefore also give an exact vector
compression that writes a terminal column as
\begin{equation}
 \mathscr T_k^L
 =-\sum_r\mu(r+h+kM)\mathbf G_k(r),
 \label{eq:tpc41-intro-Hilbert-compression}
\end{equation}
where \(\mathbf G_k(r)\) takes values in the physical output Hilbert space.
This formulation exposes the missing theorem without expanding into four
M\"obius factors.

\subsection{A positive scalar arithmetic step}

The physical vector gate remains open, but the scalar CRT shadow admits a
strict coefficient--specific saving with a sharpened exceptional--set
specialization.  Write
\begin{equation}
 Y=X^{133/400},
 \qquad M\asymp Y^3,
 \qquad K_M=X/M\asymp X^{1/400}.
 \label{eq:tpc41-intro-scalar-scales}
\end{equation}
We specialize the almost--all--moduli theorem of
\citet{KlurmanMangerelTeravainen2023} to products of three primes in
disjoint admissible intervals.  Its rank--one character subtraction is
then removed on average over this sparse family by a maximal
multiplicative large sieve.  For any fixed \(0<\theta<1/200\), almost all
of the resulting moduli satisfy
\begin{equation}
 \boxed{
 \sum_{a\bmod M}^{*}
 \left|\sum_{\substack{n\le X\\n\equiv a\pmod M}}\mu(n)\right|^2
 \ll \frac{XK_M}{(\log X)^\theta}.}
 \label{eq:tpc41-intro-raw-variance}
\end{equation}
The coefficient--blind scale is \(XK_M\), so
\eqref{eq:tpc41-intro-raw-variance} is genuine arithmetic cancellation.
The diagonal scale is only \(X\), however; a factor
\(K_M/(\log X)^\theta\) remains.  Moreover, this scalar residue--class
energy contains neither the physical row synthesis nor the shared masks
in \eqref{eq:tpc41-intro-four-form}.

The distinction is central to the claim boundary.  Classical
Barban--Davenport--Halberstam theory already implies logarithmic savings
for almost all moduli in this scalar range.  Our arithmetic contribution
is the explicit admissible triple--prime specialization, its stronger
exceptional--density ledger, and transfer to the terminal weight.  The
paper also removes the same--row alias sector from the selected folded
physical gate.  It does not control the
cross--row four--M\"obius form, cross the sieve parity barrier
\citep{HeathBrown1982Parity}, prove a prime--pair asymptotic, or imply
infinitely many twin primes.

\subsection{Organization}

\Cref{sec:tpc41-interface} fixes the inherited scales and terminal packet.
\Cref{sec:tpc41-row-diagonal,sec:tpc41-banks} prove the general Gram
identity and its minimal/full Fourier consequences.
\Cref{sec:tpc41-physical-four,sec:tpc41-hilbert} isolate the exact
four--M\"obius remainder and its Hilbert compression.
\Cref{sec:tpc41-triple-prime,sec:tpc41-weighted} prove the raw
triple--prime progression theorem and its smooth--weight transfer.
\Cref{sec:tpc41-convolution,sec:tpc41-literature,sec:tpc41-next-gate}
compare ideal convolution completion, known arithmetic inputs, and the
next physical gate.  The exact finite certificate is recorded in
\cref{sec:tpc41-certificate}.
