\section{Minimal folding and full Fourier deletion}
\label{sec:tpc41-banks}

We now specialize \cref{thm:tpc41-row-diagonal-closure} to the two phase
banks naturally attached to the alias interval
\(\cI_B=\{-L,\ldots,L\}\).

\subsection{The minimal equality--recovery bank}

Put \(q=L+1\), \(\omega=\ee{1/q}\), and
\begin{equation}
 \theta_{\nu,k}=\omega^{\nu k},
 \qquad 0\le\nu<q,
 \qquad w_\nu=q^{-1}.
 \label{eq:tpc41-minimal-bank}
\end{equation}
Its alias Gram is
\begin{equation}
 H_{k,k'}
 =\frac1q\sum_{\nu=0}^{q-1}\omega^{\nu(k'-k)}
 =\one_{k\equiv k'\pmod q}.
 \label{eq:tpc41-minimal-H}
\end{equation}
The residue bucket \(0\) consists only of \(\{0\}\), while bucket
\(r\), \(1\le r\le L\), is
\begin{equation}
 \{r,r-q\}.
 \label{eq:tpc41-folded-pairs}
\end{equation}
Thus \(H\) is the direct sum of \([1]\) and \(L\) copies of the
two--by--two all--ones matrix.

\begin{corollary}[Sharp minimal--bank row closure]
\label{cor:tpc41-minimal-row-closure}
For the bank \eqref{eq:tpc41-minimal-bank},
\begin{equation}
 \operatorname{spec}(H)
 =\{2\ (L\text{ times}),\ 1\ (1\text{ time}),\ 0\ (L\text{ times})\}.
 \label{eq:tpc41-minimal-spectrum}
\end{equation}
Consequently
\begin{equation}
 \boxed{
 0\le\cE_{\rm same}\le2\cD,
 \qquad
 |\cS_{\rm same}|\le\cD.}
 \label{eq:tpc41-minimal-row-bounds}
\end{equation}
Both constants are sharp in the unrestricted atom class.
\end{corollary}

\begin{proof}
The spectrum follows from the block decomposition.  Hence
\(\lambda_{\max}(H)=2\) and \(\|H-I\|_{\op}=1\), and
\cref{thm:tpc41-row-diagonal-closure} applies.  Equal atoms on one folded
pair attain the first constant; opposite atoms attain the absolute value
in the second.
\end{proof}

There is also a direct form of the second inequality:
\begin{equation}
 \cS_{\rm same}
 =2\operatorname{Re}
 \sum_{y,\alpha}\sum_{r=1}^{L}
 |c_{\alpha,y}|^2
 b_{\alpha,y,r}\overline{b_{\alpha,y,r-q}}.
 \label{eq:tpc41-minimal-direct-S}
\end{equation}
Every nonzero alias belongs to exactly one pair in
\eqref{eq:tpc41-folded-pairs}.  Applying
\(2|uv|\le|u|^2+|v|^2\) within each pair proves
\begin{equation}
 |\cS_{\rm same}|
 \le\sum_{y,\alpha}\sum_{k\ne0}
 |c_{\alpha,y}|^2|b_{\alpha,y,k}|^2
 \le\cD.
 \label{eq:tpc41-minimal-direct-bound}
\end{equation}
This makes explicit why the gap
\begin{equation}
 r-(r-q)=q,
 \qquad qM\in(B,B+M],
 \label{eq:tpc41-long-gap}
\end{equation}
does not create a two--point Chowla requirement.

\subsection{The full alias DFT}

Let \(K_B=2L+1\), \(\zeta=\ee{1/K_B}\), and instead take
\begin{equation}
 \theta_{\nu,k}=\zeta^{\nu k},
 \qquad0\le\nu<K_B,
 \qquad w_\nu=K_B^{-1}.
 \label{eq:tpc41-full-bank}
\end{equation}
Since distinct \(k,k'\in[-L,L]\) remain distinct modulo \(K_B\),
\begin{equation}
 H=I_{K_B}.
 \label{eq:tpc41-full-H}
\end{equation}

\begin{corollary}[Exact full--DFT deletion]
\label{cor:tpc41-full-deletion}
For the full bank,
\begin{equation}
 \boxed{
 \cE_{\rm same}=\cD,
 \qquad \cS_{\rm same}=0.}
 \label{eq:tpc41-full-deletion}
\end{equation}
Thus every same--row unequal--alias product is deleted before any
arithmetic estimate.
\end{corollary}

More strongly, inserting \(H=I\) into the full expansion gives
\begin{equation}
 \cE^{\rm full}
 =\sum_{k=-L}^{L}\sum_y
  \left|\sum_\alpha c_{\alpha,y}b_{\alpha,y,k}\right|^2.
 \label{eq:tpc41-full-fixed-alias-energy}
\end{equation}
Hence the full DFT deletes every product with \(k\ne k'\), including
cross--row products.  Its only off--diagonal terms are the fixed--alias
row correlations parameterized by the Hilbert columns in
\cref{sec:tpc41-hilbert}.

The full bank uses \(2L+1\) measurements instead of \(L+1\).  Since both
are \(\asymp K_B\), this changes no endpoint exponent.  The minimal bank
is optimal for recovering the equality column, while the full bank is the
cleaner sufficient object if one wants to remove all alias cross terms.

\subsection{Physical endpoint consequence}

Apply \cref{cor:tpc41-minimal-row-closure} first to the left coordinates
\(y=(\gamma,j)\) and then to the symmetric right coordinates.  Using
\eqref{eq:tpc41-interface-diagonal-bound} gives
\begin{equation}
 \boxed{
 \cE_{{\rm same},L}+\cE_{{\rm same},R}
 \ll X^{o(1)}Q^2JK_B
 =X^{o(1)}\frac{Q^3}{J}.}
 \label{eq:tpc41-physical-same-row-closed}
\end{equation}
In particular, the complete weighted signed sector built from the terminal
products
\begin{equation}
 \mu(n_{\alpha,j,r})\mu(n_{\alpha,j,r-q})
 \label{eq:tpc41-physical-two-mobius}
\end{equation}
that survive minimal folding is already absorbed at the physical target
scale.  This does not bound any individual long--shift correlation.  It is
an unconditional theorem about the actual terminal packet, not a
heuristic randomness assertion.
