\section{A general row--diagonal identity}
\label{sec:tpc41-row-diagonal}

We first separate alias geometry from arithmetic.  The theorem below is
valid for arbitrary complex atoms and arbitrary output coordinates.

Let \(\cY,\cR,\cK,\cT\) be finite index sets.  Think of \(y\in\cY\) as
an output coordinate, \(\alpha\in\cR\) as a physical row,
\(k\in\cK\) as an alias, and \(t\in\cT\) as a phase measurement.  Let
\begin{equation}
 Y_{t,y}
 =\sum_{\alpha\in\cR}\sum_{k\in\cK}
   \theta_{t,k}c_{\alpha,y}b_{\alpha,y,k},
 \label{eq:tpc41-general-Y}
\end{equation}
where \(|\theta_{t,k}|=1\).  Give the measurements weights \(w_t>0\)
with \(\sum_tw_t=1\), and define
\begin{align}
 H_{k,k'}
 &=\sum_{t\in\cT}w_t
   \overline{\theta_{t,k}}\theta_{t,k'},
 \label{eq:tpc41-general-H}\\
 \cE
 &=\sum_{t\in\cT}w_t\sum_{y\in\cY}|Y_{t,y}|^2,
 \label{eq:tpc41-general-energy}\\
 \cD
 &=\sum_{y,\alpha,k}|c_{\alpha,y}|^2|b_{\alpha,y,k}|^2.
 \label{eq:tpc41-general-D}
\end{align}
The matrix \(H\) is positive semidefinite and has unit diagonal.

\begin{theorem}[Row--diagonal Gram closure]
\label{thm:tpc41-row-diagonal-closure}
The sector of \(\cE\) with equal physical rows is exactly
\begin{equation}
 \boxed{
 \cE_{\rm same}
 =\sum_{y,\alpha}|c_{\alpha,y}|^2
   b_{\alpha,y}^{*}Hb_{\alpha,y},}
 \label{eq:tpc41-same-exact}
\end{equation}
where \(b_{\alpha,y}=(b_{\alpha,y,k})_{k\in\cK}\).  Hence
\begin{equation}
 0\le\cE_{\rm same}
 \le\lambda_{\max}(H)\cD.
 \label{eq:tpc41-same-lambda}
\end{equation}
If \(\cS_{\rm same}\) denotes the part with equal rows but unequal
aliases, then
\begin{equation}
 \cS_{\rm same}=\cE_{\rm same}-\cD
 \label{eq:tpc41-same-off-exact}
\end{equation}
and
\begin{equation}
 \boxed{
 |\cS_{\rm same}|
 \le\|H-I\|_{\op}\cD.}
 \label{eq:tpc41-same-off-bound}
\end{equation}
No sign, independence, or cancellation property of the atoms is used.
\end{theorem}

\begin{proof}
Expanding \eqref{eq:tpc41-general-energy} and averaging the phases gives
\begin{equation}
 \cE
 =\sum_y\sum_{\alpha,\beta}\sum_{k,k'}
 \overline{c_{\alpha,y}}c_{\beta,y}
 \overline{b_{\alpha,y,k}}H_{k,k'}b_{\beta,y,k'}.
 \label{eq:tpc41-general-expanded}
\end{equation}
Restricting to \(\alpha=\beta\) proves
\eqref{eq:tpc41-same-exact}.  Positivity of \(H\) and the Rayleigh
quotient give \eqref{eq:tpc41-same-lambda}.  Since \(H_{k,k}=1\), the
alias diagonal in \eqref{eq:tpc41-same-exact} is precisely \(\cD\), so
the remainder is \eqref{eq:tpc41-same-off-exact}.  Finally,
\[
 |b^*(H-I)b|\le\|H-I\|_{\op}\|b\|_2^2
\]
for each \((\alpha,y)\); summing with the nonnegative weights
\(|c_{\alpha,y}|^2\) proves \eqref{eq:tpc41-same-off-bound}.
\end{proof}

\begin{remark}[Why this is stronger than termwise arithmetic]
\label{rem:tpc41-no-mobius-needed}
If the entries of \(b\) contain M\"obius values, the off--alias sector is
visually a two--M\"obius correlation.
\Cref{thm:tpc41-row-diagonal-closure} bounds its \emph{whole signed
quadratic form} by the diagonal.  It does not assert cancellation in any
individual shift correlation, and none is required for the phase energy.
\end{remark}

\begin{corollary}[Uniform bounded--Gram criterion]
\label{cor:tpc41-bounded-Gram}
For any family of banks with
\(\sup\lambda_{\max}(H)<\infty\), the same--row sector is controlled by
the atomic diagonal with a uniform constant.  If \(H=I\), every unequal
alias term with \(\alpha=\beta\) vanishes identically.
\end{corollary}

The hypothesis that the phase depends only on \((t,k)\) is important.
For a coupled phase \(\theta_{t,\alpha,k}\), one obtains a separate alias
Gram \(H^{(\alpha)}\) for every fixed row.  Exact recovery alone does not
force \(\lambda_{\max}(H^{(\alpha)})=O(1)\); the recovery--coherence
uncertainty of TPC--40 explains why this cannot be assumed for free.
