\section{Bounded--variation transfer to terminal weights}
\label{sec:tpc41-weighted}

The terminal atom contains a smooth cutoff and a logarithm.  We extend the
raw prefix theorem to such weights without invoking a separate smooth
version of the short--progression theorem.

Let \(0<c<C<\infty\) be fixed.  For a function \(W\) supported on
\([c,C]\), write
\begin{equation}
 \|W\|_{\mathrm{BV}}
 :=\|W\|_\infty+\Var_{[c,C]}(W).
 \label{eq:tpc41-BV-norm}
\end{equation}
The proof of \cref{thm:tpc41-raw-triple-prime} is uniform for
\(x\asymp X\).  Below, \(e_{n\bmod M}\) denotes the standard basis vector
when \((n,M)=1\) and the zero vector otherwise.

\begin{theorem}[Weighted raw progression theorem]
\label{thm:tpc41-weighted-raw}
Under the hypotheses of \cref{thm:tpc41-raw-triple-prime}, let
\(W_X\) be any family supported in \([c,C]\) with
\(\|W_X\|_{\mathrm{BV}}\ll1\).  Then, for all but
\(o(|\mathfrak M_X|)\) moduli,
\begin{equation}
 \boxed{
 \sum_{a\bmod M}^{*}
 \left|
  \sum_{n\equiv a\pmod M}\mu(n)W_X(n/X)
 \right|^2
 \ll\frac{XK_M}{(\log X)^\theta}.}
 \label{eq:tpc41-weighted-raw}
\end{equation}
The exceptional set may be chosen uniformly for any fixed finite
collection of such weights.
\end{theorem}

\begin{proof}
Retain \(\eps=(\log X)^{-\theta}\) and choose
\begin{equation}
 R=\lceil\eps^{-1/2}\rceil.
 \label{eq:tpc41-grid-R}
\end{equation}
Take an \(R\)-point grid on \([cX,CX]\).  Apply the proof of
\cref{thm:tpc41-raw-triple-prime} at every grid endpoint.  The union of
the KMT exceptional sets is still zero density, since the extra factor
\(R\) is logarithmic and
\eqref{eq:tpc41-KMT-exception-ratio} decays faster than every logarithm.
Summing the character energies over the grid and applying Markov costs the
same factor \(R\), but
\begin{equation}
 \frac{R(\log X)^C}{\eps K}=o(1).
 \label{eq:tpc41-grid-character-Markov}
\end{equation}
Thus, outside a zero--density set, every grid prefix vector has squared
norm \(\ll\eps XK_M\).

Between adjacent endpoints, an interval has length \(O(X/R)\), so each
residue class contains at most \(O(K_M/R+1)\) integers.  Its
coefficient--blind residue energy is therefore
\begin{equation}
 \ll M(K_M/R+1)^2
 \ll\frac{XK_M}{R^2}
 \ll\eps XK_M,
 \label{eq:tpc41-short-block-energy}
\end{equation}
because \(K_M/R\to\infty\).  The raw prefix vector consequently has
norm \(O((\eps XK_M)^{1/2})\) uniformly throughout \([cX,CX]\).

Abel summation in the Hilbert space
\(\ell^2((\Z/M\Z)^\times)\) now gives
\begin{equation}
 \left\|
  \sum_n\mu(n)W_X(n/X)e_{n\bmod M}
 \right\|_2
 \le \|W_X\|_{\mathrm{BV}}
 \sup_{cX\le t\le CX}
 \left\|\sum_{n\le t}\mu(n)e_{n\bmod M}\right\|_2.
 \label{eq:tpc41-Hilbert-Abel}
\end{equation}
Squaring proves \eqref{eq:tpc41-weighted-raw}.
\end{proof}

Let \(\Phi\) be a fixed smooth function supported on a compact subinterval
of \((0,\infty)\), and put
\begin{equation}
 W_X(t)=\frac{\log(Xt)}{\log X}\Phi(t).
 \label{eq:tpc41-terminal-W}
\end{equation}
Its bounded--variation norm is uniform.  Therefore
\cref{thm:tpc41-weighted-raw} gives
\begin{equation}
 \sum_{a\bmod M}^{*}
 \left|
  \sum_{n\equiv a\pmod M}
  \mu(n)\log n\,\Phi(n/X)
 \right|^2
 \ll
 \frac{XK_M(\log X)^2}{(\log X)^\theta}.
 \label{eq:tpc41-terminal-log-weight}
\end{equation}
This matches the scalar shape of the terminal atom
\eqref{eq:tpc41-interface-b} after a harmless normalization of its fixed
cutoff.

\begin{remark}[What transfers, and what does not]
\label{rem:tpc41-weighted-boundary}
The theorem controls the full reduced residue vector with a common scalar
weight.  Any unweighted subset of residue coordinates inherits the bound
by positivity.  The actual TPC output, however, assigns row--dependent
coefficients to a Hilbert coordinate indexed by the opposite row and
orbit time.  Neither coordinatewise restriction nor
\eqref{eq:tpc41-terminal-log-weight} supplies the vector inequality
\eqref{eq:tpc41-Hilbert-equality-target}.
\end{remark}
