\begin{abstract}
TPC--73 isolated an analytic completion gate on the primitive cofactor
plane, and TPC--74 attached that plane to every off-diagonal entry of the
normalized missing-native Gram.  We make the remaining completion
infimum exactly decidable.  On every finite rectangle, a linear operator
\(A_D\) has norm \(\|A_DF\|_1\) equal to the full low-diagonal
plaquette cost plus exact high-diagonal tail.  If \(R\) is primitive
restriction, we prove attainment and the strong complex dual identity
\[
 \min_{RF=k}\|A_DF\|_1
 =
 \max_{\substack{A_D^*z=R^*\lambda\\\|z\|_\infty\le1}}
 \operatorname{Re}\langle\lambda,k\rangle .
\]
The gauge is a quotient seminorm with nullspace \(R(\ker A_D)\); a
low-cost completion and a dual obstruction witness are exact
alternatives, and the physical M\"obius functional is one feasible dual
direction.

For a finite Hermitian row family, let \(\gamma_{mn}\) be the optimal
cost of the fixed post-\(q\) direct-entry kernel.  When admissible completions
factor over unordered row pairs, we prove the exact matrix-optimization identity
\[
 \inf_{\boldsymbol F}\rho(P(\boldsymbol F))
 =
 \rho(Q^\gamma),
 \qquad
 Q^\gamma_{mn}=\gamma_{mn}.
\]
Thus Hermitian reversal alone creates no joint optimization gain.  We
also derive a strong dual for fixed weighted-Schur aggregation under an
arbitrary declared affine coupling rule at fixed finite stacked data;
this is where shared \(q\)-compatibility creates a genuine joint gate.
Uniformity over a growing coefficient class remains a separate minimax
problem.

Finally, every completion majorant is bounded below by the
absolute-entry Perron radius of the gauged direct-entry matrix.  A
zero-diagonal symmetric Hadamard construction has
\(\|H\|=O(N^{-1/2})\) while \(\rho(|H|)\to1\), proving that failure of
all absolute-value completion certificates need not mean failure of
signed operator cancellation.  These are exact certificate/obstruction
results, not a physical saving; no fixed-\(2\), parity-breaking,
prime-pair, or twin-prime conclusion is asserted.
\end{abstract}
