\section{Claim ledger and conclusion}
\label{sec:claim-boundary}

\subsection{Exact conclusions}

This paper proves:
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=2.8em]
 \item an exact finite linear analysis operator whose \(\ell^1\)-norm is
       the complete divisor--variation completion cost;
 \item primal and dual attainment, with no duality gap, for every feasible
       finite complex completion problem, together with the exact
       infeasible/unbounded alternative;
 \item the quotient-seminorm identity
       \(\ker\gamma=R(\ker A)\);
 \item exact dual obstruction witnesses and the arithmetic M\"obius
       witness as one feasible dual direction;
 \item the factorization
       \(\inf_{\boldsymbol F}\rho(P(\boldsymbol F))=\rho(Q^\gamma)\)
       for independent unordered row
       pairs;
 \item the universal completion sandwich
       \[
       \|H\|=\|\widetilde H\|
       \le\rho(|\widetilde H|)
       \le\rho(Q^\gamma)\le\rho(P^0);
       \]
 \item a fixed-weight Hermitian row-Schur strong dual;
 \item a strong dual for every declared finite affine shared rule at
       fixed stacked data and fixed positive Schur weight;
 \item a literal \(q\)-provenance content lift for the TPC--74 direct
       kernels; and
 \item deterministic countermodels separating certificate failure from
       signed cancellation failure.
\end{enumerate}

\subsection{Statements not proved}

The paper does not prove:
\begin{itemize}
 \item that \(\gamma_{mn}\) is small relative to the actual raw entry
       mass on a growing physical family;
 \item that the content lift is uniformly cheaper than the canonical zero
       completion;
 \item a row-sum, weighted-Schur, or Perron saving for \(Q^\gamma_X\);
 \item that \(\rho(|H_X|)=o(1)\), or any fixed-power decay;
 \item that a finite numerical SOCP certificate persists asymptotically;
 \item that an obstruction for one shared rule covers all completion
       rules;
 \item cancellation in the same-residual sector or the full signed
       matrix;
 \item closure of the represented frame, missing-mass comparison,
       nuisance shorting, endpoints, or final boundary reconstruction;
 \item the strict \(1/400\) endpoint inequality;
 \item a result special to \(h_0=2\); or
 \item a parity-breaking, prime-pair, or twin-prime theorem.
\end{itemize}

\subsection{Audit levels}

\begin{center}
\begin{tabular}{p{0.30\textwidth}p{0.48\textwidth}l}
\toprule
Result & Scope & Level\\
\midrule
Analysis normal form, strong duality, quotient gauge &
All feasible finite linear \(\ell^1\) systems, with infeasibility alternative & L0\\
Independent-edge Perron factorization &
All finite Hermitian-compatible product classes & L0\\
Affine shared-rule dual &
Every fixed-data finite real-linear coupling & L0\\
Hadamard Perron-floor separation &
Finite symmetric matrices of order \(2^r\) & L0\\
Direct-entry gauge and content lift &
Complete literal TPC--74 missing-high carrier & L1\\
Normalized completion saving &
Complete growing physical row-pair family & Open L2\\
Perron decay and physical reassembly &
One common carrier and coefficient scope & Open\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Conclusion}

The analytic completion gate is no longer an open-ended interpolation
problem.  At every declared finite scale,
\[
 \min_{RF=k}\|A_DF\|_1
 =
 \max_{\substack{A_D^*z=R^*\lambda\\\|z\|_\infty\le1}}
 \Real\langle\lambda,k\rangle.
\]
A construction and an obstruction are exact primal--dual certificates
for the same number.  On the complete TPC--74 direct-entry carrier, the
independent optimal values form one symmetric matrix \(Q^\gamma\), and
its Perron radius is exactly the best separated completion majorant.

This closes two conceptual gaps.  First, a failed completion search can
now be replaced by a rigorous obstruction rather than a heuristic
negative claim.  Second, Hermitian reversal is not blamed for a joint
gap it does not create; any such gap must be traced to an explicitly
shared rule.  The Hadamard separation then supplies the correct stop
rule: a large absolute-Perron obstruction closes the completion
certificate, but it leaves a signed-moment route open.

The next task is therefore concrete.  Analyze the literal divisor-poset
content lift and its dual flow on the actual carrier.  If the
actual-carrier absolute Perron floor is already nonnegligible, stop that
route and change architecture.  If the lift improves the complete row
matrix above that unavoidable floor, the result is immediately compatible
with the same raw normalization and fixed-shift operator chain.
