\section{Introduction}
\label{sec:introduction}

The primitive-plane program has reached a precise optimization boundary.
The divisor lift of TPC--71 \citep{WangTPC71} converts a coprime
two-variable M\"obius sum into diagonal slices.  TPC--73
\citep{WangTPC73} proves that the support-faithful physical kernel has no
auxiliary slices with \(d\ge2\), and that every nonprimitive analytic
completion preserves the primitive physical functional.  Its complete
certificate cost is nevertheless a coupled sum of low-diagonal
plaquette variation and a high-diagonal tail.  TPC--74
\citep{WangTPC74} then constructs the missing interface for the gauged
perturbation \(\widetilde H=U_dHU_d\):
\[
 \widetilde H_{mn}
 =
 \sum_{(u,v)=1}\mu(u)\mu(v)L_{mn}^{0}(u,v)
\]
for every actual off-diagonal row pair of the normalized missing-native
Gram.  A completion certificate can therefore be asked entry by entry
and aggregated into a nonnegative Hermitian majorant.

Three logical gaps remain if the completion infimum is left only as a
definition.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.7em]
 \item A failed search for a smooth or \(q\)-compatible completion is not
       a proof that no cheaper completion exists.
 \item Separate entrywise optimizers need not define one admissible rule
       when a fixed finite stacked family is required to share parameters
       across row pairs.
 \item Even an exact lower obstruction for every absolute-value
       completion majorant may obstruct only that certificate
       architecture, not the signed matrix itself.
\end{enumerate}
The purpose of this paper is to close all three logical gaps at the
finite-dimensional level.

\subsection{Main results}

Fix a finite rectangle and a diagonal cutoff \(D\).  The full TPC--73
cost is a finite sum of absolute values of linear functionals of the
completion.  We stack those functionals, with their literal weights, into
one operator \(A_D\).  If \(R\) is restriction to the primitive lattice,
then
\[
 \cC_D(F)=\|A_DF\|_1,
 \qquad
 \gamma_D(k)=\min_{RF=k}\|A_DF\|_1.
\]
Our first result is an exact strong dual over the underlying real spaces:
\[
 \gamma_D(k)
 =
 \max
 \left\{
 \Real\langle\lambda,k\rangle:
 A_D^*z=R^*\lambda,\ \|z\|_\infty\le1
 \right\}.
\]
The formula treats complex literal coefficients without discarding their
phases.  It also proves attainment on both sides.  Any feasible
\((\lambda,z)\) gives a rigorously checkable lower obstruction, while an
optimal completion gives a matching upper certificate.

The second result identifies the geometry of the optimum.  The map
\(k\mapsto\gamma_D(k)\) is a seminorm on the primitive data space, with
\[
 \ker\gamma_D=R(\ker A_D).
\]
It is therefore a norm on the corresponding quotient.  This removes a
common ambiguity: zero completion cost is possible exactly when the
prescribed primitive datum is the trace of a zero-analysis completion,
not merely when one chosen interpolation happens to have small
variation.

The third result treats the complete direct-entry family.  For
independent unordered row-pair completion classes, define the symmetric
matrix
\[
 Q^\gamma_{mn}
 =
 \begin{cases}
  \gamma_{mn},&m\ne n,\\
  0,&m=n.
 \end{cases}
\]
Then
\[
 \|H\|=\|\widetilde H\|
 \le \rho(|\widetilde H|)
 \le \rho(Q^\gamma)
 =
 \inf_{\boldsymbol F}\rho(P(\boldsymbol F)).
\]
The last equality is exact.  Each edge minimum can be attained
simultaneously, and Perron monotonicity leaves no hidden joint gain.
Hence a genuine joint gate cannot be attributed to Hermitian reversal
alone.  It appears only when one declares additional cross-edge
constraints, such as a shared \(q\)-compatible rule or a
finite stacked-data parametrization.  We give the exact primal and dual
for every such finite affine coupled rule; uniformity over a growing
coefficient class remains a separate minimax problem.

\subsection{What this advances}

The paper converts an open-ended search problem into an exact decision
problem.  At a declared finite scale and within a declared completion
class, exactly one numerical value controls both sides:
\[
 \text{best completion cost}
 =
 \text{strongest dual obstruction}.
\]
This is a real theoretical advance at the interface level.  It does not
show that the value is small on the growing physical carrier.  Nor does
it identify a classical Mertens estimate sufficient for that smallness.

The absolute-entry Perron floor makes the limitation sharper.  We give a
deterministic symmetric family for which the signed operator norm tends
to zero but the absolute-entry spectral radius tends to one.  Thus a
large dual obstruction can close the entire Abel--completion--Perron
route while a different signed-moment route remains viable.

\subsection{Organization}

\Cref{sec:finite-normal-form} writes the divisor--variation cost as one
finite linear analysis norm.  \Cref{sec:primal-dual} proves strong
duality and attainment.  \Cref{sec:quotient-witnesses} develops the
quotient geometry and physical witness.  \Cref{sec:hermitian-family}
proves the exact independent-edge Perron theorem.
\Cref{sec:coupled-rules} handles shared affine rules.
\Cref{sec:countermodels} records the necessary non-substitution laws.
\Cref{sec:physical-gate} returns to the literal fixed-shift carrier, and
\cref{sec:claim-boundary} gives the claim ledger and next decision.
