\section{The literal fixed-shift completion gate}
\label{sec:physical-gate}

\subsection{Inherited carrier}

We now specialize only to the physical object proved in TPC--74
\citep{WangTPC74}.  Fix one nonzero shift \(h_0\), one external block,
and the actual TPC--61/TPC--68 missing-high carrier.  The two direct sides
are combined through their proved orthogonal direct sum.  Every key
retains its side, block, opposite row, profile, time, mask, endpoint, and
remaining native output labels.

For an active unordered row pair \(m<n\), write
\[
 \Delta_{mn}=h_0(n-m)
\]
and let \(L_{mn,q}(u,v)\) be the literal \(q\)-resolved direct-entry
kernel of TPC--74.  Its post-content aggregation is
\[
 L_{mn}(u,v)
 =
 \sum_{q\mid|\Delta_{mn}|}L_{mn,q}(u,v).
\]
Before optimizing, choose a finite rectangle \(B_{mn}\) containing the
union of the primitive supports of all \(L_{mn,q}\) and every declared
lifted nonprimitive site.  Fix \(D_{mn}\ge1\), and set
\[
 B_{nm}=B_{mn}^{\mathsf T},
 \qquad
 D_{nm}=D_{mn}.
\]
These choices are used in \(\gamma_{mn}\), \(Q^\gamma\), \(P^0\), and
\(P^{\rm lift}\); changing them changes the optimization problem.
Prescribe
\begin{equation}
 k_{mn}(u,v)=L_{mn}(u,v)
 \qquad((u,v)=1),
 \label{eq:physical-primitive-data}
\end{equation}
including zero at every absent primitive site.  Only nonprimitive sites
are completion variables.

Here \(\gamma_{mn}\) is the pair-dependent optimum formed after exact
\(q\)-aggregation of this fixed literal datum.  In contrast,
\(F^{\rm lift}_{mn}\) below is a candidate informed by retained
pre-aggregation \(q\)-provenance.  It is not a slice-by-slice
absolute-value optimization.

The normalization inside every \(L_{mn,q}\) remains
\[
 \frac1{\sqrt{W_M(m)W_M(n)}},
 \qquad
 W_M(m)=\sum_{w:m(w)=m}|\beta_w|^2,
\]
where the sum uses both orthogonal sides on the declared block.
This is the \(W_m\) notation used in TPC--74.
Nonprimitive fill values are not physical atoms and never enter \(W_M\).

\subsection{Three exact majorants}

Let \(F^0_{mn}\) be the canonical zero completion.  Let
\(\gamma_{mn}\) be the exact unrestricted analytic optimum from
\cref{eq:completion-gauge}.  TPC--74 and
\cref{thm:Perron-floor} give
\begin{equation}
 \|H\|=\|\widetilde H\|
 \le\rho(|\widetilde H|)
 \le\rho(Q^\gamma)
 \le\rho(P^0).
 \label{eq:physical-majorant-hierarchy}
\end{equation}
Every matrix in this chain refers to the same literal row set, complete
keys, raw masses, and fixed \(h_0\).

There is also a canonical provenance-preserving candidate that was not
available before the \(q\)-resolved direct-entry representation.
Write a site uniquely as
\[
 (x,y)=(du,dv),
 \qquad
 d=(x,y),\quad(u,v)=1.
\]
Define the content lift, inside \(B_{mn}\), by
\begin{equation}
 F^{\rm lift}_{mn}(du,dv)
 =
 \sum_{\substack{r\mid|\Delta_{mn}|\\d\mid r}}
 L_{mn,r}(u,v).
 \label{eq:content-lift}
\end{equation}
The sum is zero when no such \(r\) exists.

\begin{proposition}[Literal content lift]
\label{prop:literal-content-lift}
The kernel \(F^{\rm lift}_{mn}\) is a legal completion of
\eqref{eq:physical-primitive-data}.  It uses only actual
\(q\)-slices with \(q\mid|\Delta_{mn}|\), introduces no physical mass,
and respects Hermitian reversal:
\[
 F^{\rm lift}_{nm}(v,u)
 =
 \overline{F^{\rm lift}_{mn}(u,v)}.
\]
\end{proposition}

\begin{proof}
At a primitive site \(d=1\), \eqref{eq:content-lift} gives
\[
 F^{\rm lift}_{mn}(u,v)
 =
 \sum_{r\mid|\Delta_{mn}|}L_{mn,r}(u,v)
 =
 k_{mn}(u,v).
\]
Thus the primitive restriction is correct, including absent-ray zeros.
Every nonprimitive value is only a sum of already existing literal
content slices.  It is not inserted into the physical key set or row
mass, and \eqref{eq:content-lift} is a declared analytic copying rule,
not a physical movement or identity between atoms.  Finally, TPC--74 gives
\[
 L_{nm,r}(v,u)=\overline{L_{mn,r}(u,v)};
\]
the divisor set of \(|\Delta_{mn}|\) is unchanged by reversal.
\end{proof}

Let \(P^{\rm lift}\) be the symmetric matrix of the full costs
\(\cC_{D_{mn}}(F^{\rm lift}_{mn})\).  Then
\begin{equation}
 \rho(Q^\gamma)
 \le
 \min\{\rho(P^0),\rho(P^{\rm lift})\}.
 \label{eq:lift-upper-bound}
\end{equation}
No ordering between \(P^0\) and \(P^{\rm lift}\) is asserted.
The lift may reduce the \(d=1\) plaquette term while increasing higher
diagonal terms or the tail.

\subsection{Exact positive and negative outcomes}

Let \(X\to\infty\) through one declared physical family, with all objects
above indexed by \(X\).

\paragraph{Positive separated outcome.}
If one proves
\[
 \rho(Q^\gamma_X)\le\eta_X<1,
\]
then the normalized missing-native Gram
\[
 G_{{\rm nat},X}=I+H_X
\]
obeys
\[
 U_{d,X}G_{{\rm nat},X}U_{d,X}
 =
 I+\widetilde H_X.
\]
The two Grams are unitarily equivalent, so
\[
 1-\eta_X
 \le\lambda_{\min}(G_{{\rm nat},X})
 \le\lambda_{\max}(G_{{\rm nat},X})
 \le1+\eta_X.
\]
This is a deterministic implication.  The hypothesis is not proved
here.

\paragraph{Negative separated outcome.}
For each edge, a dual witness gives the nonnegative lower bound
\[
 W_{mn}
 =
 \left|
 [\lambda_{mn},k_{mn}]_{\mathbb R}
 \right|
 \le\gamma_{mn};
\]
changing the common sign of \((\lambda_{mn},z_{mn})\) makes this absolute
value a feasible dual objective.
Set \(W_{nm}=W_{mn}\) and \(W_{mm}=0\).  Then
\[
\rho(W)\le\rho(Q^\gamma).
\]
Thus a nonnegligible actual-carrier lower bound for \(\rho(W)\) closes the
broad independent absolute-completion route at that scale.  It still
does not lower-bound \(\|H\|\).

\paragraph{Shared-rule outcome.}
For a declared affine \(q\)-compatible rule at one fixed finite stacked
datum,
\cref{thm:coupled-rule-dual} gives the exact fixed-\(c\) value and its
obstruction.  A witness for one \(c\) does not close the Perron infimum;
one needs a bound uniform over positive \(c\), a direct nonnegative
matrix floor, or an exact evaluation of the resulting Collatz problem.
Nor does the single-datum theorem supply a rule uniform over a growing
coefficient class; that requires the additional minimax quantifier in
\cref{rem:fixed-data-coupling}.

\subsection{Remaining physical gates}

Even a successful missing-native estimate must still be combined on one
carrier with:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.7em]
 \item terminal activation and the represented lower frame;
 \item missing-mass comparison and nuisance shorting;
 \item geometric endpoint and packet-boundary terms; and
 \item the complete fixed-power loss ledger.
\end{enumerate}
If the accumulated loss reaches \(1/400\), including equality, the
current strict endpoint implication stops.  None of the completion
identities changes that budget.

\subsection{TPC--76 decision}

TPC--75 leaves two rigorously separated next doors.
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.6em]
 \item Analyze the literal content lift
       \eqref{eq:content-lift} on the divisor poset and compare its exact
       KKT/dual flow with the zero completion.
 \item If an actual absolute-Perron floor is already nonnegligible, pivot
       to a signed full-\(H\) moment or a hybrid direct/anchor
       architecture, because no entrywise absolute completion can cross
       that floor.
\end{enumerate}
The first route is the default theoretical next step; the second is an
explicit kill-criterion fallback rather than an overclaim that
cancellation has failed.
