\section{Exact primal--dual completion theorem}
\label{sec:primal-dual}

We first state the theorem for arbitrary finite spaces.  This separates the
convex fact from the arithmetic realization of \(A_D\).

\begin{theorem}[Strong completion duality]
\label{thm:strong-completion-duality}
Let \(\cX,\cY,\cK\) be finite-dimensional complex spaces, regarded as
real spaces with the pairing \([\cdot,\cdot]_{\mathbb R}\).  Let
\[
 A:\cX\to\cY,\qquad R:\cX\to\cK
\]
be complex-linear maps, and define
\[
 \gamma(k)
 =
 \inf\{\|AF\|_1:RF=k\},
\]
with value \(+\infty\) when the constraint is infeasible.  Then
\begin{equation}
 \boxed{
 \gamma(k)
 =
 \sup_{\substack{A^*z=R^*\lambda\\\|z\|_\infty\le1}}
 [\lambda,k]_{\mathbb R}.}
 \label{eq:strong-dual}
\end{equation}
If \(k\in\Ran R\), both the primal minimum and the dual maximum are
attained.  If \(k\notin\Ran R\), the dual is unbounded above.
\end{theorem}

\begin{proof}
The real Fenchel conjugate of the complex \(\ell^1\)-norm is
\[
 \bigl(\|\cdot\|_1\bigr)^*(z)
 =
 \begin{cases}
  0,&\|z\|_\infty\le1,\\
  +\infty,&\|z\|_\infty>1.
 \end{cases}
\]
Indeed, each complex coordinate is a two-dimensional Euclidean block and
\[
 \sup_y\{[z,y]_{\mathbb R}-|y|\}
 \]
is finite exactly when \(|z|\le1\).

For the equality constraint use the Lagrangian
\[
 \cL(F,\lambda)
 =
 \|AF\|_1+[\lambda,k-RF]_{\mathbb R}.
\]
The infimum over \(F\) is finite precisely when there is
\(z\in\cY\) satisfying
\[
 \|z\|_\infty\le1,
 \qquad
 A^*z=R^*\lambda.
\]
In that case the infimum equals \([\lambda,k]_{\mathbb R}\); otherwise it
is \(-\infty\).  This gives the displayed dual.  Finite-dimensional
Fenchel--Rockafellar duality, applied on the nonempty affine space
\(\{F:RF=k\}\), gives equality whenever \(k\in\Ran R\)
\citep{Rockafellar1970}.

For completeness, primal attainment does not require coercivity on all
of \(\cX\).  Quotient the feasible direction space \(\ker R\) by
\(\ker A\cap\ker R\), choose a linear complement, and restrict there.
The induced map into \(\Ran A\) is injective, so its norm controls the
complement variable.  A minimizing sequence is therefore bounded modulo
the cost-free direction, and has a convergent representative.

For dual attainment, restrict \(\lambda\) to
\((\ker R^*)^\perp\).  On that subspace \(R^*\) is injective and
\(A^*z=R^*\lambda\), \(\|z\|_\infty\le1\), bounds \(\lambda\).
The resulting feasible set is closed and bounded, hence compact.
Adding a vector in \(\ker R^*\) does not change the objective for
\(k\in\Ran R\).

If \(k\notin\Ran R\), choose
\(\lambda_0\in(\Ran R)^\perp\) with
\([\lambda_0,k]_{\mathbb R}>0\).  Then
\(R^*\lambda_0=0=A^*0\), so
\((t\lambda_0,0)\) is dual feasible for every \(t>0\), and its objective
tends to \(+\infty\).
\end{proof}

\begin{corollary}[Exact certificate/obstruction alternative]
\label{cor:certificate-obstruction}
Suppose \(k\in\Ran R\) and \(\varepsilon\ge0\).  Exactly one of the
following strict alternatives can occur:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.6em]
 \item there is \(F\) with \(RF=k\) and \(\|AF\|_1\le\varepsilon\);
 \item there are \(\lambda,z\) with
       \(A^*z=R^*\lambda\), \(\|z\|_\infty\le1\), and
       \([\lambda,k]_{\mathbb R}>\varepsilon\).
\end{enumerate}
If the optimum equals \(\varepsilon\), the primal and dual optimizers
meet at equality rather than satisfying the strict second alternative.
\end{corollary}

\begin{proof}
Both optima equal \(\gamma(k)\) by
\cref{thm:strong-completion-duality}.  Compare this common value with
\(\varepsilon\).
\end{proof}

\begin{remark}[What is checkable]
A proposed completion is verified by the equality \(RF=k\) and a direct
evaluation of \(\|AF\|_1\).  A proposed obstruction is verified by one
adjoint equality and one coordinatewise unit-ball inequality.  Neither
certificate requires trusting an optimizer or a numerical convergence
diagnostic.
\end{remark}

\begin{corollary}[KKT certificate]
\label{cor:KKT-certificate}
For feasible \(k\), a primal--dual feasible quadruple
\((F,\lambda,z,k)\) is optimal if and only if
\begin{equation}
 [z,AF]_{\mathbb R}=\|AF\|_1.
 \label{eq:KKT-saturation}
\end{equation}
Equivalently, coordinatewise,
\[
 z_\nu=
 \frac{(AF)_\nu}{|(AF)_\nu|}
 \quad\text{when }(AF)_\nu\ne0,
 \qquad
 |z_\nu|\le1
 \quad\text{when }(AF)_\nu=0.
\]
\end{corollary}

\begin{proof}
Primal and dual feasibility give
\[
 [\lambda,k]_{\mathbb R}
 =
 [R^*\lambda,F]_{\mathbb R}
 =
 [A^*z,F]_{\mathbb R}
 =
 [z,AF]_{\mathbb R}
 \le\|AF\|_1.
\]
Equality is exactly simultaneous optimality by strong duality.  Equality
in each complex coordinate support inequality gives the stated phase
condition.
\end{proof}

\begin{remark}[LP versus second-order cone form]
For real kernels the absolute values give a linear program after the
usual positive/negative epigraph split.  For complex kernels, each
constraint \(|z_j|\le1\) is a two-dimensional second-order cone.
Thus the exact finite problem is an SOCP in general and an LP only in the
real specialization.  No asymptotic conclusion follows merely from
solving either finite program.
\end{remark}

\begin{corollary}[TPC--73 gauge dual]
\label{cor:tpc73-gauge-dual}
For the operator \(A_D\) in
\cref{def:analysis-operator} and primitive restriction \(R\),
\begin{equation}
 \boxed{
 \gamma_D(k)
 =
 \max_{\substack{A_D^*z=R^*\lambda\\\|z\|_\infty\le1}}
 \Real\langle\lambda,k\rangle.}
 \label{eq:tpc73-gauge-dual}
\end{equation}
\end{corollary}

\begin{proof}
Use \cref{prop:exact-normal-form,thm:strong-completion-duality}.  Here
\(R\) is surjective, so both optima are finite and attained for every
\(k\in\cK\).
\end{proof}
