\section{Introduction and scope}\label{sec:introduction}

This paper makes one specific transition: from an exact finite Fourier
description of a centered Chinese-remainder pair kernel to asymptotic
cancellation on genuinely power-short factor boxes.  The character-sum input
is classical.  The new point is its conductor-by-conductor assembly against
the exact multipliers and shift Parseval identity of the companion paper
\citep{WangCenteredKernels2026}.  In particular, we do not prove a new
P\'olya--Vinogradov or Burgess estimate.

Let
\begin{equation}\label{eq:intro-Q-G-kappa}
 Q=\prod_{w<p\le w^2}p,
 \qquad
 G=(\Z/Q\Z)^\times,
 \qquad
 g=\varphi(Q),
 \qquad
 \kappa=\prod_{p\mid Q}\frac{p-2}{p-1}.
\end{equation}
For integer intervals $I,J$ of the same length $L<Q$, and for $(h,Q)=1$,
write
\begin{equation}\label{eq:intro-box-form}
 \cB_h(I,J)
 =\sum_{\substack{m\in I,\ n\in J\\(mn,Q)=1}}
 \left\{
  \kappa^{-1}\one_{(mn+h,Q)=1}-1
 \right\}.
\end{equation}
Thus the coefficient on the unit support is identically one.  Arbitrary
bounded coefficients are not included in the theorems below.  The centering
in \eqref{eq:intro-box-form} is the exact complete-group centering, not an
empirical centering chosen from the observed box.

\subsection{Main results}

Fix $0<\eta<1$ and put
\begin{equation}\label{eq:intro-power-short-length}
 L=\left\lceil Q^{1-\eta}\right\rceil.
\end{equation}
Uniformly in the locations of $I$ and $J$, we prove
\begin{equation}\label{eq:intro-complete-shift-result}
 \frac1{L^2}
 \left(
  \frac1g\sum_{\ell\in G}|\cB_{2\ell}(I,J)|^2
 \right)^{1/2}
 =o(1)
 \qquad (w\to\infty).
\end{equation}
This is a complete fully-active-shift mean: $(\ell,Q)=1$ ensures that every
prime in the window is active for $h=2\ell$.  It is not a conclusion for
each shift separately.

The complete average can be sampled on a much shorter interval.  Let $\cL$
be any interval of
\begin{equation}\label{eq:intro-short-shift-length}
 H=\left\lfloor Q^{1/\log w}\right\rfloor
\end{equation}
consecutive integers and set
$H_Q=\#\{\ell\in\cL:(\ell,Q)=1\}$.  Then, again for every fixed
$0<\eta<1$ and uniformly in the locations of all three intervals,
\begin{equation}\label{eq:intro-short-shift-result}
 \frac1{L^2}
 \left(
  \frac1{H_Q}
  \sum_{\substack{\ell\in\cL\\(\ell,Q)=1}}
  |\cB_{2\ell}(I,J)|^2
 \right)^{1/2}
 =o(1).
\end{equation}
Although $H=Q^{o(1)}$, this remains an averaged theorem and does not select a
prescribed member of $\cL$.

For the prescribed local shift, the result is necessarily stated separately.
For every fixed $0<\eta<4/5$,
\begin{equation}\label{eq:intro-fixed-shift-result}
 \frac{\cB_2(I,J)}{L^2}=o(1),
\end{equation}
uniformly in the locations of $I,J$.  The range comes from choosing a
conductor cutoff $R=Q^\alpha$ with
\begin{equation}\label{eq:intro-cutoff-compatibility}
 \eta<\alpha<4(1-\eta):
\end{equation}
after choosing such an $\alpha$, one fixes a sufficiently large Burgess
parameter so that the slightly stronger finite-parameter upper inequality
also holds.  Low conductors are treated by Burgess and high conductors by the exact kernel
multiplier.  We make no assertion at $\eta=1$ or $\eta=4/5$, and neither
strict range is claimed to be optimal or to be a barrier for other methods.

There is also a finite algebraic result of a different kind.  We construct a
nonnegative shifted-divisor square which majorizes the relevant local
residue-avoidance indicator and has every nonconstant one-prime Fourier mode
equal to zero.  Its remaining nonconstant spectrum lies on two-prime
conductors.  This construction explains both what an ordinary same-window
divisor square cannot change on the unit group and what cross-prime coupling
can change.  It is a finite spectral design, not a prime-detecting sieve
asymptotic.

\subsection{Where the power saving comes from}

For a character $\chi\in\widehat G$, let $q_\chi$ be the product of the local
primes on which $\chi$ is nontrivial.  Since $Q$ is squarefree, $\chi$ is
induced from a primitive character of conductor exactly $q_\chi$.  The
companion calculation gives, for $\chi\ne\one$, an exact kernel coefficient
of modulus
\begin{equation}\label{eq:intro-exact-multiplier}
 d(\chi)=\prod_{p\mid q_\chi}\frac1{p-2},
\end{equation}
together with an exact diagonal Parseval formula after averaging the fully
active shifts \citep{WangCenteredKernels2026}.  Reduction to the primitive
conductor converts each rough interval transform into ordinary incomplete
character sums.  P\'olya--Vinogradov, as presented for example in
\citep[Section~9.4]{MontgomeryVaughan2007}, gives a useful intermediate
power-short range.  The final ranges in all three main statements use the
Burgess estimate for squarefree, hence cubefree, conductors
\citep{Burgess1962,Burgess1963II}.  At high conductor,
\eqref{eq:intro-exact-multiplier} itself supplies the decay.  The contribution
here is this division of labor and the resulting exponents for the particular
CRT pair kernel, not any strengthening of those classical character-sum
theorems.

The distinction from earlier sifted character sums is worth recording.
Schlage-Puchta inserted a sifting device into a character sum in a specific
application \citep{SchlagePuchta2006}; Puchta's short character sums over
primes use a large-sieve inequality for prime-supported coefficients together
with the Selberg sieve \citep{Puchta2003}.  Our sums instead have constant
coefficients on the $Q$-unit support and a two-variable centered periodic
kernel.  Those works provide important methodological context, but their
prime-supported conclusions are neither inputs to nor consequences of
\eqref{eq:intro-complete-shift-result}--\eqref{eq:intro-fixed-shift-result}.

Low-conductor exceptional behavior also plays a central role in general
Bombieri--Vinogradov theories for multiplicative functions
\citep{GranvilleShao2018,GranvilleShao2019}.  Those theorems concern
distribution in arithmetic progressions, averaged over moduli, under
Siegel--Walfisz and related hypotheses.  Here the modulus $Q$ is one fixed
squarefree product, the averaging in \eqref{eq:intro-complete-shift-result}
is over local shifts, and the exact conductor weight comes from the kernel.
Consequently, the present theorem is not a Bombieri--Vinogradov theorem for a
new multiplicative function.

The congruence $mn\equiv-h\pmod q$ also places the problem near the literature
on modular hyperbolas; see the survey \citep{Shparlinski2012}.  Our condition,
however, is a product of exclusions at the primes dividing $Q$, followed by
exact CRT centering.  We use its specialized character factorization and do
not claim a new point-count estimate for a modular hyperbola.

Finally, factorability has a precise meaning in results on primes in
arithmetic progressions.  The large-modulus work of
\citet{BombieriFriedlanderIwaniec1986} and its extensions use structured
averages that are far more than a formal factorization of one squarefree
integer.  Maynard's fixed-residue-class theorem uses moduli
with suitably placed divisors, whereas the well-factorable theorem averages
prime-progression errors with suitably well-factorable modulus weights
\citep{Maynard2025FixedResidue,Maynard2025WellFactorable}.  Neither condition
is supplied merely by writing $Q$ as a product of primes.  Our shift average
is not a well-factorable modulus average, and \eqref{eq:intro-fixed-shift-result}
contains none of the prime-sensitive dispersion or Type~II input in those
works.

\subsection{Selberg form and strict boundary of the claims}

The nonnegative shifted-divisor square is motivated by the algebraic form of
Selberg sieve weights; standard sieve theory and modern smoothing questions
are treated in \citep{FriedlanderIwaniec2010,GranvilleKoukoulopoulosMaynard2021}.
Our use is deliberately finite: coefficients are chosen so that specified
Fourier modes of a local function vanish exactly.  We do not optimize an
asymptotic upper- or lower-bound sieve, and the label ``Selberg-form'' does not
turn the weight into a detector of primes.

More generally, every asymptotic box result in this paper concerns the
coefficient-one periodic expression \eqref{eq:intro-box-form}; the separate
quadratic design is a finite local weight.  There is no von Mangoldt function
$\Lambda$, no prime-supported coefficient sequence, and no Type~II estimate
for such a sequence.  An ambient estimate $o(L^2)$ is also not a positive main term on
the prime-pair scale.  Classical sieve parity remains a separate obstruction
\citep{HeathBrown1982}, and prime-producing asymptotic sieve arguments require
additional information absent here \citep{FriedlanderIwaniec1998}.  Therefore
none of \eqref{eq:intro-complete-shift-result}--\eqref{eq:intro-fixed-shift-result},
nor the finite quadratic design, implies or provides evidence for the
twin-prime conjecture.  The paper's claim is narrower: classical incomplete
character-sum tools, combined with an exact CRT kernel, now reach power-short
unweighted rough boxes and expose several concrete prime-sensitive interfaces
that this local model does not control.
