\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cU}{\mathcal U}
\newcommand{\cV}{\mathcal V}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\e}{\mathrm e}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\diag}{\operatorname{diag}}
\newcommand{\Span}{\operatorname{span}}

\hypersetup{
  pdftitle={Diagonal Mellin Reassembly on Actual Orbit Fibers: Scalar Saturation, Profile Overlap, and an Interior TPC Bridge},
  pdfauthor={Liang Wang},
  pdfsubject={Actual-direction Mellin stability for label-preserving orbit fibers and sharp support-grazing obstructions},
  pdfkeywords={Mellin inversion, orbit fibers, profile overlap, scalar Gram saturation, prime squarefree sampling, static mask, parity problem}
}

\title{\bfseries Diagonal Mellin Reassembly on Actual Orbit Fibers:\\
Scalar Saturation, Profile Overlap,\\
and an Interior TPC Bridge}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The preceding twin-prime-correlation reduction proved stable sampled
frames for fixed scalar Mellin families but left open their transfer to
the actual, growing family of row-dependent orbit translates.  We show
that two different questions were hidden in that gap.  If the orbit
label is discarded, a cluster of \(r+1\) normalized scalar translates
has Gram eigenvalue at most \(O_r(J^{-2r})\).  Thus the unreduced scalar
family has no uniform lower frame, and on an interior
translate-independent window its exact dimension is of order \(J\), so
no polylogarithmic scalar bank can preserve the energy of every vector in
that exact span with uniform relative error.

The physical coefficientwise space does not discard the orbit label.
It retains \((m,r,j,\gamma)\) as orthogonal coordinates before coherent
prime summation and residual grouping.  On those coordinates we prove
an exact \(q\)-factor diagonal Mellin identity.  For fixed
\(W_1,\ldots,W_q\in C_c^\infty((0,\infty))\), base coefficients \(c_i\),
and positive samples \(x_{i,\nu}\), its weighted canonical envelope and
physical output satisfy
\[
 \cE_B(\mathbf W;c)=A_B(\mathbf W)\|c\|_2,
 \qquad
 \|\cS_{\mathbf W}c\|_2^2
 =\sum_i|c_i|^2\prod_{\nu=1}^q|W_\nu(x_{i,\nu})|^2.
\]
Consequently the actual-direction condition number is exactly
\[
 \frac{\cE_B(\mathbf W;c)^2}{\|\cS_{\mathbf W}c\|_2^2}
 =\frac{A_B(\mathbf W)^2}{\Theta(\mathbf W;c)},
\]
where \(\Theta\) is the nonnegative physical profile-to-carrier ratio.
This bypasses a lower-frame assertion for arbitrary Mellin densities or
for the entire growing scalar family.

 We then give a conditional criterion for evaluating its sampled actual
instantiation \(\Theta_X^{\rm act}\) on a
literal prime--squarefree row universe.  The declared factors include
\(W(c_\beta e^{x+y}t)\) and
\(\Psi(c'_\beta e^yt)\), with the normalized source parameter
\(\beta\) in a fixed compact set.  If the continuous profile-to-carrier
ratio has a uniform lower bound \(\rho_*>0\), and if the displayed
profiles and weights satisfy an exact coordinatewise dictionary with one
complete nondegenerate row cell, fixed-modulus row sampling, orbit Riemann
sampling, and the literal-mask degree estimate give
\[
 \Theta_X^{\rm act}\ge \rho_*/2
\]
uniformly for arbitrary source concentration and arbitrary finite retained
cofactor support.  Hence the
canonical coefficientwise pre-terminal direction has \(O(1)\) condition
number on every such uniformly active direct cell.  Under the same exact
dictionary and nondegeneracy hypotheses, we verify the required
regularity-to-carrier normalization and projected-reference lower bound and
deduce polylogarithmic row-log Fourier compressibility of the retained
Hilbert-valued orbit field; this does not compress the orbit labels.

The overlap hypothesis is essential.  Two fixed smooth bumps whose
scaled supports graze can make \(\Theta_X^{\rm act}\) smaller than every power of
\(X\), while the canonical layer envelope remains of carrier size.  The
resulting super-polynomial near-kernel concerns the distinguished actual
direction, not an arbitrary signed density.  Thus the paper proves an exact
diagonal identity and a conditional coefficientwise Mellin bridge on
uniformly active interior packets.  Support grazing is a sharp obstruction
to the overlap route, but the paper does not verify the exact-profile
dictionary or uniform overlap for every inherited packet.  Coherent prime
summation, residual grouping, localization
to the physical shift, native-Gram identification, and every
parity-sensitive conclusion remain open.
\end{abstract}

\noindent\textbf{Keywords:} Mellin inversion; orbit fibers; profile
overlap; scalar Gram saturation; Hilbert-valued sampling;
prime--squarefree rows; static mask; sieve parity.

\medskip
\noindent\textbf{Convention.}
All Hilbert spaces are complex.  Every Mellin contour is the real axis.
Direct residue cells are formed before the literal static mask, and the
mask is formed before any signed projective representation.  Constants
may depend on the fixed smooth shapes, residue moduli, and derivative
order, but not on \(X\).  We write \(\e^z:=\exp z\),
\(\e(z):=\exp(2\pi iz)\), and \(\e_q(z):=\e(z/q)\).

\medskip
\noindent\textbf{MSC 2020:} Primary 42A38, 46C05; Secondary 11N35,
42B35, 15A18.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/scalar-saturation}
\input{sections/diagonal-mellin}
\input{sections/profile-overlap}
\input{sections/actual-bridge}
\input{sections/fourier-compressibility}
\input{sections/grazing-boundary}
\input{sections/endpoint-claims}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
