\begin{abstract}
The fixed-shift completion program contains two formally different
sources of information.  A direct channel synthesizes corrections in
the target entry space; an anchor channel records lower-dimensional or
four-corner structure.  These channels cannot be combined merely
because their labels overlap.  One must construct a literal anchor
synthesis into the same target.

We study the resulting finite-dimensional convex problem.  Let
\(S_A:X_A\to K\) and \(S_D:X_D\to K\) be anchor and direct synthesis
maps, assume \(S_D\) is surjective, and assume the coefficient variables
form a verified separable direct sum with additive cost
\(p_A(x)+p_D(y)\).  Write
\[
 \alpha(v)=\inf_{S_Ax=v}p_A(x),
 \qquad
 \delta(k)=\min_{S_Dy=k}p_D(y),
\]
and \(V_A=\Ran S_A\).  The direct cost left after declaring anchor
directions free is the orphan quotient gauge
\[
 \delta_{\rm orph}(\pi k)
 =\inf_{v\in V_A}\delta(k-v).
\]
If \(\cB_A,\cB_D\) are the polar feasibility sets induced by the two
coefficient norms, then
\[
 \delta_{\rm orph}(\pi k)
 =
 \max_{\lambda\in\cB_D,\ S_A^*\lambda=0}
 [\lambda,k]_{\R}.
\]

The genuinely hybrid cost is instead
\[
 h(k)=\min_{v\in V_A}\{\alpha(v)+\delta(k-v)\}.
\]
We prove the exact dual intersection formula
\[
 h(k)
 =
 \max_{\lambda\in\cB_A\cap\cB_D}
 [\lambda,k]_{\R}
\]
and the hierarchy
\[
 \delta_{\rm orph}(\pi k)\le h(k)\le\delta(k).
\]
For a fixed datum,
\[
 h(k)=\delta(k)
 \quad\Longleftrightarrow\quad
 N_D(k)\cap\cB_A\ne\varnothing,
\]
where \(N_D(k)\) is the face of direct norming functionals.  In
particular, a direct norming functional annihilating the anchor range
certifies that the anchor channel cannot help.  Globally, the anchor
channel is redundant exactly when
\(\alpha(v)\ge\delta(v)\) for all \(v\in V_A\).

The results give a precise test for whether two previously separate
completion mechanisms yield a real saving, only a quotient floor, or
no interaction at all.  They do not construct the required physical
anchor synthesis or prove that its literal fixed-shift coefficients
cross any arithmetic endpoint.
\end{abstract}
