\section{Claim boundary, stop certificates, and next gate}
\label{sec:boundary}

\subsection*{What is proved}

For any finite literal, separable, surjective-direct common-target
packet, this paper proves:
\begin{enumerate}[label=(C\arabic*),leftmargin=2.7em]
\item exact direct, orphan, and hybrid dual formulas;
\item the hierarchy
\(\delta_{\rm orph}\le h\le\delta\);
\item a necessary-and-sufficient fixed-datum no-improvement test;
\item an orphan norming functional as a strong sufficient local stop
certificate;
\item a necessary-and-sufficient global redundancy test;
\item matched decomposed primal--dual gaps.
\end{enumerate}

\subsection*{What is not proved}

We do not prove that the previously available anchor observables admit
a canonical synthesis into the direct two-corner target.  We do not
prove that the literal fixed-\(h_0\) anchor polar ball removes every
direct norming functional, that strict saving occurs on a positive
density of carriers, or that the inherited total exponent-loss ledger
closes strictly below \(1/400\).  We do not convert a support-only or
averaged-family result into fixed-\(h_0\) parity progress.

\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.19\linewidth}
>{\raggedright\arraybackslash}p{0.71\linewidth}@{}}
\toprule
Level & Status\\
\midrule
L0: model algebra &
Exact for finite real-linear common-target synthesis.\\
L1: interface &
Advanced by exact quotient/hybrid separation and equality certificates.\\
L2: arithmetic &
Open; the literal anchor synthesis and fixed-\(h_0\) transfer estimate
are not supplied.\\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Branch stop certificates}

At a fixed datum, a verified witness
\[
 \lambda\in N_D(k)\cap\cB_A
\]
rigorously proves no anchor improvement.  A primal--dual hybrid pair
alone only brackets \(h(k)\).  A certified strict saving requires, for
example, a direct lower bound \(L_D\) and a hybrid upper bound \(U_H\)
with \(L_D>U_H\), or exact evaluation of both values.  Solver failure
proves neither alternative.  Globally, \(\alpha\ge\delta\) on \(V_A\)
stops the anchor branch entirely.  If a physical common-target map is
not yet constructed, the gate remains open; only a proof of
incompatibility supports a negative transfer theorem.

\subsection*{Endpoint loss ledger and next gate}

The inherited fixed-power ledger allows total exponent loss strictly
smaller than \(1/400\) and stops at loss at least \(1/400\), including
equality.  The exact finite-dimensional identities here add no exponent
loss by themselves, but a physical synthesis dictionary, carrier
restriction, and reassembly theorem may do so.  A strict hybrid gauge
gap is not an exponent gain until a separate transfer theorem proves
its direction, scale, and common global normalization.

The next structural question is orthogonal: when a Hermitian physical
matrix is bounded entrywise by a nonnegative Perron majorant, exactly
when do complex phases allow the Perron bound to be saturated?  That
phase-consistency problem requires cycle holonomy and must be kept
separate from the incidence and orphan-quotient graphs studied here.

\subsection*{Conclusion}

The anchor channel has now been placed on an exact decision tree:
\[
\begin{array}{c}
\text{construct a literal common-target synthesis}\\
\downarrow\\
\delta_{\rm orph}\le h\le\delta\\
\downarrow\\
\begin{cases}
\text{norming charge survives} &\Rightarrow \text{no improvement},\\
\text{dual face is cut} &\Rightarrow \text{certifiable hybrid saving}.
\end{cases}
\end{array}
\]
This identifies both a usable route and a rigorous stopping mechanism.
The remaining difficulty is no longer hidden in the convex program: it
is the construction and arithmetic prevalence of the physical channel.
