\section{Introduction}

The completion program now has two mature but separate interfaces.
Direct primitive-entry completion has an exact quotient gauge and
primal--dual certificates \cite{WangTPC75,WangTPC77}; sparse forest
components admit additional closed reductions \cite{WangTPC78}.
Separately, anchor or lower-content constructions organize four-corner
and provenance information.  The next logical question is whether an
anchor channel can lower the direct completion cost.

That question is ill posed until both channels land in one target
space.  An observation map out of the direct target, a shared divisor
label, or a four-corner trace is not yet a vector that can be subtracted
from a two-corner direct entry.  The missing object is a synthesis map
\[
 S_A:X_A\longrightarrow K
\]
into the same \(K\) used by the direct synthesis
\(S_D:X_D\to K\).  Once this map exists, three different values appear:
\begin{enumerate}[label=(\roman*),leftmargin=2.4em]
\item the direct cost \(\delta(k)\);
\item the direct cost on the quotient \(K/\Ran S_A\), where anchor
directions are declared free;
\item the hybrid cost \(h(k)\), where using an anchor direction incurs
its actual coefficient cost.
\end{enumerate}
Confusing (ii) and (iii) can manufacture a saving that is not physically
available.

\paragraph{Main results.}
We compute the duals of all three values.  The quotient floor uses
direct charges annihilating the anchor range.  The hybrid cost uses the
intersection of the anchor and direct polar balls.  This immediately
gives
\[
 \delta_{\rm orph}\le h\le\delta,
\]
but the important content is the equality theory.  A fixed datum gets
no hybrid improvement exactly when a direct norming functional is also
anchor feasible.  A norming functional that annihilates the entire
anchor range is a particularly strong no-improvement certificate.
Globally, the anchor channel is redundant exactly when it is never
cheaper than the direct channel on its own range.

\paragraph{Relation to the previous layer.}
TPC-78 reduces the cost of evaluating a direct component.  The present
paper changes the admissible synthesis family: it asks whether a second
family can share the load.  Thus it advances a different gate.  Forest
closed forms can be inserted into \(\delta\), but they do not construct
\(S_A\) or prove that the intersection of polar balls yields a strict
physical gain.

\paragraph{Scope and progress label.}
All theorems are exact finite-dimensional convex analysis over complex
spaces viewed as real spaces.  They are L0 convex-algebraic results that
advance the L1 interface.  No literal arithmetic construction of
\(S_A\), no carrier-density bound, and no fixed-\(h_0\) endpoint saving
is assumed or claimed.

\paragraph{Organization.}
\Cref{sec:setup,sec:pure} define the two synthesis gauges.
\Cref{sec:orphan} derives the quotient floor.
\Cref{sec:hybrid} proves hybrid duality.
\Cref{sec:equality} gives fixed-datum and global equality tests.
\Cref{sec:stability} gives matched certificates.
\Cref{sec:countermodels} separates observation from synthesis and
quotient from hybrid cost.  \Cref{sec:physical,sec:boundary} state the
literal transfer requirements and endpoint stop rule.
