\section{Requirements for a literal fixed-shift transfer}
\label{sec:physical}

Fix one nonzero physical shift \(h_0\).  A valid specialization at scale
\(X\) must archive the following common-target diagram:
\[
\begin{array}{ccc}
 X_{A,X} & \xrightarrow{\ S_{A,X}\ } & K_X\\
 && \uparrow S_{D,X}\\[-0.3em]
 && X_{D,X}.
\end{array}
\]
The arrows must be literal coefficient assemblies.  A trace,
restriction, aggregate, or four-corner observation into another space
does not fill the top arrow.

\begin{definition}[Physical hybrid packet]\label{def:packet}
A physical packet to which the intersection formula applies consists
of:
\begin{enumerate}[label=(H\arabic*),leftmargin=2.7em]
\item one fixed \(h_0\) and one target key set \(K_X\);
\item literal maps \(S_{A,X},S_{D,X}\), including all provenance and
content lifts before exact summation, with \(S_{D,X}\) surjective onto
\(K_X\);
\item coefficient norms \(p_{A,X},p_{D,X}\) derived from the same raw
atomic measure;
\item the datum \(k_X\) in the same units and orientation as both
synthesis maps;
\item a verified separable coefficient space
\(X_{A,X}\oplus X_{D,X}\) with cost \(p_{A,X}+p_{D,X}\);
\item primal coefficients and a dual charge with both polar constraints
verified;
\item a separately proved arithmetic inequality connecting the physical
quantity of interest to \(\delta_X,h_X\), or their difference.
\end{enumerate}
\end{definition}

If anchor and direct channels share or couple native variables, the
packet is not separable and \(\cB_A\cap\cB_D\) need not be its dual
ball.  One must instead construct the literal joint synthesis, joint
coefficient norm, and its single polar ball; none of the intersection
formulas may be applied until an exact separable reparameterization is
proved.

\begin{proposition}[Common-target necessity]\label{prop:common-target}
Suppose anchor data are available only through an observation
\(T_X:K_X\to Y_X\).  The values \(T_Xk_X\), the direct gauge
\(\delta_X\), and a norm on \(Y_X\) do not in general determine a
hybrid value on \(K_X\).  A synthesis \(R_X:Y_X\to K_X\), or a direct
coefficient map from anchor variables into \(K_X\), is necessary.
\end{proposition}

\begin{proof}
\Cref{ex:obs} gives two sections of the same observation with distinct
target ranges and therefore potentially distinct hybrid gauges.  The
input data listed in the statement cannot distinguish them.
\end{proof}

\begin{remark}[Majorization direction]
Convex duality computes a finite value; it does not decide whether that
value upper-bounds, lower-bounds, or equals a physical bad-set mass.
The direction and every scale factor must be proved from the literal
arithmetic assembly.  A saving in \(h_X\) is not an endpoint saving
until this bridge is supplied.
\end{remark}

The minimal reproducible census records, for each \(X\), the dimensions
and hashes of all native arrays, exact output keys, ranks and actual
supports of both synthesis maps, the values
\[
 \delta_{{\rm orph},X}(\pi k_X),
 \qquad
 h_X(k_X),
 \qquad
 \delta_X(k_X),
\]
and their globally normalized gaps.  Numerical feasibility tolerances
must be reported separately from exact support and exact adjoint
constraints.
