\section{Common-target synthesis model}
\label{sec:setup}

Let \(K,X_A,X_D\) be finite-dimensional real or complex vector spaces;
complex spaces are regarded as real vector spaces when taking duals.
Pair each space with its real dual using \([\lambda,k]_{\R}\); after
choosing Hermitian coordinates in the complex case this is
\(\Real\langle\lambda,k\rangle\).

Let
\[
 S_A:X_A\to K,
 \qquad
 S_D:X_D\to K
\]
be real-linear maps.  Assume \(S_D\) is surjective.  Let \(p_A,p_D\)
be norms on the coefficient spaces, and write \(p_A^\circ,p_D^\circ\)
for their polar norms.  The real adjoints are defined by
\[
 [S_A^*\lambda,x]_{\R}=[\lambda,S_Ax]_{\R},
 \qquad
 [S_D^*\lambda,y]_{\R}=[\lambda,S_Dy]_{\R}.
\]

\begin{definition}[Polar feasibility sets]\label{def:balls}
Define
\begin{align}
 \cB_A
 &=
 \{\lambda\in K^*:p_A^\circ(S_A^*\lambda)\le1\},
 \label{eq:BA}\\
 \cB_D
 &=
 \{\lambda\in K^*:p_D^\circ(S_D^*\lambda)\le1\}.
 \label{eq:BD}
\end{align}
\end{definition}

Because \(S_D^*\) is injective, \(\cB_D\) is compact.  The set
\(\cB_A\) may be unbounded along the annihilator of \(\Ran S_A\), but
\(\cB_A\cap\cB_D\) is compact.

\begin{definition}[Anchor range and orphan quotient]\label{def:orphan}
Let
\[
 V_A=\Ran S_A,
 \qquad
 \pi:K\to Q_{\rm orph}:=K/V_A
\]
be the anchor-visible subspace and its quotient map.  A class
\(\pi k\) is called the \emph{orphan part} of \(k\): it is the part no
anchor synthesis can change.
\end{definition}

The term ``orphan'' is algebraic.  It does not assert that a physical
carrier is absent; it says only that the chosen literal map \(S_A\)
does not synthesize that quotient direction.

\begin{remark}[Observation is not synthesis]\label{rem:obs}
A map \(T:K\to Y\) measures or aggregates a target.  It does not define
a map \(Y\to K\).  A right inverse, section, or reconstruction operator
must be specified and proved compatible with the physical coefficients
before its range may be called \(V_A\).
\end{remark}
