\begin{abstract}
The preceding diagonal Mellin reduction isolated an exact-profile
dictionary and a positive profile-overlap condition as two application
hypotheses.  We discharge the first hypothesis, exactly and
coordinatewise, for one explicitly declared representative packet from
the prime--squarefree opened-row provenance.  The packet is formed before
coherent prime summation and before the many-to-one grouping
\(s=d(m)r\).  Its orbit multiplier is the literal four-factor product
\[
 W_1(mj/X)\Psi_1(d(m)j/K)
 W_2(m_\gamma j/X)\Psi_2(d_\gamma j/K).
\]
After direct residue splitting, every factor is assigned to one of four
places: the source coefficient, the coefficient-free opposite-row
factor, the literal static mask, or the real-axis Mellin measure.  The
opposite-row logarithmic base weight in the left residual route is
exactly \(1\), not \((\log\ell_\gamma)^2\); its fixed unary shape remains
in both profiles and its unit phase remains in the Mellin layer.  The
single physical prime logarithm remains in the source coefficient.  The
resulting carrier and physical coordinate
identities hold with equality for every \(X\), with all factors of
\(2\pi\), residue amplitudes, cofactor repetitions, and global phases
accounted for.  Thus the exact-profile assumption of the preceding paper
is a theorem on this declared direct packet.

We next replace the remaining qualitative overlap hypothesis by a
deterministic support certificate.  In normalized variables
\(x=\log(\ell_\gamma/L)\), \(y=\log(d_\gamma/D)\), and \(t=j/J\), the
opposite-row factors have arguments
\[
 c_X\e^{x+y}t,\qquad c'_X\e^yt,
 \quad c_X=LDJ/X,\quad c'_X=DJ/K=1.
\]
If at one reachable normalized point the carrier---including the fixed
unary shape and retained residue amplitude---is nonzero and all four
physical cutoffs lie strictly inside their nonzero sets, then fixed
compact source, opposite-row, and orbit boxes can be
selected on which the profile-to-carrier ratio has an explicit positive
lower bound.  The selected opposite-row and orbit boxes have fixed
positive geometric density, literal-mask deletion is \(o(1)\), and the
extraction has zero positive polynomial cost at the \(1/400\) endpoint.
Once this explicit certificate is verified, the preceding sampled
theorem yields an \(O(1)\) canonical Mellin condition number for that
named retained-label subpacket.

This is not a statement about the whole inherited packet.  An arbitrary
bounded source factor \(\zeta_m\) can vanish on every selected compatible
source box and concentrate all actual source energy on its complement.
Hence
positive geometric density does not imply a positive good-carrier
fraction.  We prove the corresponding sharp obstruction and give a
sufficient fixed-nonzero-source criterion for positive source-row energy
coverage.  Positive coverage after cofactor repetition additionally
follows under a balanced-fiber condition, which is not proved here.
Coherent prime summation, residual grouping, fixed-shift
localization, native-Gram identification, and every parity-sensitive or
twin-prime conclusion remain open.
\end{abstract}
