\section{Endpoint ledger, limitations, and next gates}
\label{sec:tpc53-endpoint}

At the inherited endpoint,
\begin{equation}
 \begin{aligned}
 Q&=X^{267/400+o(1)},&
 J&=X^{133/400+o(1)},&
 \kappa_0&=\frac1{400},\\
 D&=X^{10049/52500+o(1)},&
 V&=X^{23/120+o(1)}.
 \end{aligned}
 \label{eq:tpc53-endpoint-scales}
\end{equation}
The hard divisor boundary has the strict margin
\begin{equation}
 \frac{23}{120}-\frac{10049}{52500}
 =\frac9{35000}>0.
 \label{eq:tpc53-hard-cutoff-margin}
\end{equation}
Moreover \(L=Q/D\) and
\begin{equation}
 \left(\frac{267}{400}-\frac{10049}{52500}\right)
 -\frac{10049}{52500}
 =\frac{59783}{210000}>0.
 \label{eq:tpc53-L-over-D-margin}
\end{equation}
Hence \(2D\le V\) and \(L>4D\) for all sufficiently large \(X\), each
with a fixed power margin.  Together with the certified unary and
residue support, the selected packet is genuinely nondegenerate; no
endpoint loss is hidden in these conditions \citep{WangTPC50}.

The costs of the present extraction are:
\begin{enumerate}[label=\textup{(E\arabic*)},leftmargin=3em]
 \item a fixed number of direct row and orbit residue cells;
 \item fixed compact source, opposite-row, and orbit boxes;
 \item row sampling error \(o(1)\) at fixed modulus;
 \item orbit sampling error \(O(J^{-1})\); and
 \item literal-mask deletion
 \[
 O\!\left(L^{-1+o(1)}+D^{-1+o(1)}
          +X^{-1/400+o(1)}\right).
 \]
\end{enumerate}
Every Mellin transform belongs to a fixed Schwartz library and has
finite weighted variation.  Since the support certificate gives a fixed
\(\rho_*>0\), only qualitative \(o(1)\) sampling is required.  Thus the
local dictionary-and-overlap bridge has zero positive polynomial cost
and spends none of the \(1/400\) allowance.

This zero cost applies to the \emph{selected} packet.  It does not say
that deleting the complement costs zero actual energy.  Under arbitrary
bounded \(\zeta_m^{(1)}\) or arbitrary cofactor multiplicity, the
complement may carry all of the lifted carrier energy by
\cref{prop:tpc53-zeta-obstruction}.  A full-packet statement must prove a
positive \(\sigma_X\), partition all nonzero energy into finitely many
compatible cells, or bound the unselected complement by another method.

\subsection{Exact claim ledger}

\begin{description}[leftmargin=3.2em,style=nextline]
 \item[Proved exactly (L0).]
 The exact four-factor Mellin allocation and lifted atomic norm.  Also,
 the reachable-support equivalence, explicit compact-box lower bound,
 and source-concentration obstruction.
 \item[Proved on the literal selected packet (L1).]
 The exact TPC--52 profile dictionary with \(e=0\), fixed positive
 geometric row--orbit density, sampled masked overlap, and an \(O(1)\)
 canonical condition number in the retained-label pre-terminal space.
 \item[Conditional subgate.]
 Positive coverage of the full lifted carrier follows from a nonvanishing
 source factor plus balanced carrier multiplicities, or from any direct
 proof that \(\sigma_X\gg1\).
 \item[Not proved (L2).]
 A coherent-prime lower square, a fixed-\(h_0\) arithmetic lower bound,
 a parity-sensitive estimate, or a twin-prime theorem.
\end{description}

\subsection{Dependency order after this paper}

The remaining interfaces should not be permuted:
\begin{enumerate}[label=\textup{(O\arabic*)},leftmargin=3em]
 \item determine whether compatible cells capture a controlled fraction
 of the full actual carrier energy, including cofactor multiplicity;
 \item prove, or sharply delimit, a coherent prime square at fixed
 \((m,r)\) that is stable under the certified carrier projection;
 \item control the many-to-one grouping \(s=d(m)r\) and its cancellation;
 \item localize a completed frozen shift family back to the single
 physical intercept \(h_0\); and
 \item compare the residual low-sign Gram with the native affine
 physical Gram without deleting its cross terms.
\end{enumerate}

The present paper advances the first physical-interface line by replacing
an abstract factor dictionary with an exact one and replacing an unnamed
overlap assumption with a finite support certificate.  It does not move
any downstream operation through a norm and does not hint at a resolution
of the parity problem.
