\section{Geometric coverage versus actual energy coverage}
\label{sec:tpc53-energy}

Let \(\cM_X^{\rm full}\) be a complete fixed-modulus source dyadic cell,
and suppose the compatible cell \(\mathfrak B_0\) contains a fixed
positive-volume source rectangle.  Let \(\cM_X^{\rm good}\) be the rows
whose normalized parameters lie in that rectangle.  Fixed-modulus prime
and squarefree counting then gives
\begin{equation}
 |\cM_X^{\rm good}|\asymp|\cM_X^{\rm full}|,
 \label{eq:tpc53-source-geometric-density}
\end{equation}
but the actual coefficient contains \(\zeta_m^{(1)}\), for which the
inherited interface assumes only an upper bound.

For the repeated lifted packet, define the fiber carrier multiplier
\begin{equation}
 \mathfrak n_X(m)
 :=\sum_{r:(m,r)\in\cI_X}\mathscr B_X^M(m)
 =N_r(m)\mathscr B_X^M(m),
 \label{eq:tpc53-fiber-multiplier}
\end{equation}
where \(N_r(m)\) is the retained cofactor multiplicity.  The good-carrier
fraction in the full lifted packet is
\begin{equation}
 \sigma_X
 :=\frac{\displaystyle
   \sum_{m\in\cM_X^{\rm good}}|a_m|^2\mathfrak n_X(m)}
  {\displaystyle
   \sum_{m\in\cM_X^{\rm full}}|a_m|^2\mathfrak n_X(m)}
 \label{eq:tpc53-good-carrier-fraction}
\end{equation}
when the denominator is positive.

\begin{proposition}[Sharp coefficient-concentration obstruction]
\label{prop:tpc53-zeta-obstruction}
Assume the full packet has at least one source row outside
\(\cM_X^{\rm good}\) on which the fixed source shapes and fiber
multiplier are nonzero.  In the coefficient class
\(|\zeta_m^{(1)}|\le1\), one may have
\begin{equation}
 |\cM_X^{\rm good}|\asymp|\cM_X^{\rm full}|
 \qquad\text{but}\qquad \sigma_X=0.
 \label{eq:tpc53-zero-energy-coverage}
\end{equation}
Thus no positive lower bound for \(\sigma_X\) follows from geometric
density, row sampling, or profile overlap alone.
\end{proposition}

\begin{proof}
Set \(\zeta_m^{(1)}=0\) on every good row and on any unwanted bad row,
and set it equal to one on one nonzero bad row.  This respects the only
stated coefficient hypothesis.  The numerator of
\eqref{eq:tpc53-good-carrier-fraction} is zero and the denominator is
positive.
\end{proof}

Even a unit-modulus \(\zeta_m^{(1)}\) does not by itself control
\(\sigma_X\) if \(N_r(m)\) is allowed to concentrate arbitrarily on bad
rows.  This is a second, logically independent coverage obstruction.

There is a clean sufficient repair.  Let the fixed source unary shapes
be bounded below on the good box, and suppose
\begin{equation}
 |\zeta_m^{(1)}|\ge\zeta_0>0
 \quad(m\in\cM_X^{\rm good}),
 \qquad |\zeta_m^{(1)}|\le C
 \quad(m\in\cM_X^{\rm full}).
 \label{eq:tpc53-source-nondegeneracy}
\end{equation}

\begin{proposition}[Source-energy coverage]
\label{prop:tpc53-source-energy-coverage}
Under \eqref{eq:tpc53-source-nondegeneracy}, fixed-modulus
admissibility, uniform lower bounds for the source shapes on the good
box, and uniform upper bounds for them on the full box, there is a constant
\(c_{\rm src}>0\) such that
\begin{equation}
 \frac{\sum_{m\in\cM_X^{\rm good}}|a_m|^2}
      {\sum_{m\in\cM_X^{\rm full}}|a_m|^2}
 \ge c_{\rm src}+o(1).
 \label{eq:tpc53-source-energy-fraction}
\end{equation}
If, in addition, for some \(A_X>0\) and fixed
\(0<n_-\le n_+<\infty\),
\begin{equation}
 n_-A_X\le\mathfrak n_X(m)\le n_+A_X
 \quad\text{on every nonzero full source row},
 \label{eq:tpc53-balanced-fibers}
\end{equation}
then
\begin{equation}
 \sigma_X\ge\frac{n_-}{n_+}c_{\rm src}+o(1)>0.
 \label{eq:tpc53-positive-good-fraction}
\end{equation}
\end{proposition}

\begin{proof}
On the good box, the lower bounds for the fixed source shapes and
\(\zeta_m^{(1)}\), together with the fixed-modulus prime number theorem
and squarefree counting, give
\[
 \sum_{m\in\cM_X^{\rm good}}|a_m|^2
 \gg LD\log L.
\]
The inherited upper bounds and Chebyshev's estimate give
\(\sum_{m\in\cM_X^{\rm full}}|a_m|^2\ll LD\log L\).
This proves \eqref{eq:tpc53-source-energy-fraction}.  Multiplying the
good numerator by the lower bound in
\eqref{eq:tpc53-balanced-fibers} and the full denominator by the upper
bound gives \eqref{eq:tpc53-positive-good-fraction}.
\end{proof}

Condition \eqref{eq:tpc53-balanced-fibers} is not proved by the present
paper.  It is a transparent sufficient condition for turning source-row
coverage into coverage after cofactor repetition.  Alternatively, a
direct estimate of \eqref{eq:tpc53-good-carrier-fraction} may replace
both \eqref{eq:tpc53-source-nondegeneracy} and
\eqref{eq:tpc53-balanced-fibers}.
