\section{Introduction}
\label{sec:tpc53-introduction}

TPC--52 separated a misleading scalar-frame problem from the actual
label-preserving Mellin synthesis.  On the retained coefficient space it
proved that the conditioning of the provenance-fixed direction is
governed by a nonnegative physical profile-to-carrier ratio, rather than
by a lower frame for every signed Mellin density
\citep{WangTPC52}.  Its actual application deliberately retained two
hypotheses: a coordinatewise dictionary identifying the abstract profile
with the literal opened-row coefficient, and a uniform positive overlap
of the physical cutoffs.  Neither may be inferred merely from bounded
smoothness.

The first gap is bookkeeping, but bookkeeping at this interface is
mathematics.  There are three different row roles in the provenance
chain.  The original symmetric opened-row packet has two physical row
coefficients.  After large-prime descent, a left residual packet has one
source coefficient and one coefficient-free opposite output row.  After
residual grouping, different pairs \((m,r)\) may share the same physical
label \(s=d(m)r\).  Moving a prime logarithm between the first two roles,
or declaring \((m,r)\) orthogonal after the third operation, changes the
norm being estimated.

This paper fixes one representative four-factor packet and prints its
factor allocation in full.  No unidentified \(\mathcal W\) remains in
the main theorem.  The allocation converts the exact-profile dictionary
of TPC--52 from an assumption into an equality on the named packet.

The second gap is geometric.  For arbitrary fixed smooth tests, the
nonzero sets of \(W\) and \(\Psi\) need not overlap every reachable
scaled orbit.  We therefore do not assert that the full parameter box is
uniformly active.  Instead we prove a necessary-and-sufficient strict
support criterion for a nonempty active interior and a quantitative
rectangle certificate for a compact subpacket.  This certificate is
finite-dimensional and deterministic; it contains no prime-pair input.

\subsection{Main results}

The conclusions are as follows.

\begin{enumerate}[label=\textup{(R\arabic*)},leftmargin=3.2em]
 \item \textbf{Exact literal dictionary.}
 On one complete nondegenerate direct left packet, with no independent
 opposite-row pruning, we take
 \[
 a_m=\gamma_m^{(1)},\qquad
 \omega_{\gamma,X}=1,\qquad
 M_X(m,\gamma)=K_{m\gamma}.
 \]
 The fixed opposite unary shape is placed in both the carrier and
 physical profiles, its unit phase is kept in the layer phase, and the
 direct residue amplitudes are placed in both profiles.  The absolute
 Mellin transforms and every factor
 \((2\pi)^{-1}\) are placed in the positive provenance measure.  All
 remaining row and orbit powers have modulus one.  The two coordinate
 identities required in TPC--52 then hold exactly for every retained
 \((a,m,r,j,\gamma)\).

 \item \textbf{Atomic normalization.}
 The exact squared norm is
 \[
 \sum_{m,r,j,\gamma}
 |\gamma_m^{(1)}|^2K_{m\gamma}|R(q_\gamma)|^2|\xi_a|^2
 \prod_{\nu=1}^4|U_{\nu}(z_{\nu})|^2,
 \qquad \mathbf U=(W_1,\Psi_1,W_2,\Psi_2).
 \]
 It is the norm of a pre-terminal orthogonal lift.  The terminal factor
 \(\mu(r)\Lambda(pr)\), coherent prime sum, and collision map
 \(s=d(m)r\) are absent.  We prove no equality with the final
 TPC--48 output norm or native affine Gram.

 \item \textbf{Reachable-support certificate.}
 A strict point at which the carrier and all four physical factors are
 nonzero generates compact source, opposite-row, and orbit boxes with
 explicit overlap
 \[
 \rho_*
 \ge
 \frac{r_0^2\prod_{\nu=1}^4w_{\nu,0}^2}{H_0b_+}
 \left(\int_{\cQ}\e^{x+y}\,dx\,dy\right)|I|>0.
 \]
 Conversely, positive continuous profile energy implies such a strict
 point.  Thus the active parameter set is relatively open and its compact subsets
 are uniformly active.  A grazing limit of active parameters can lose
 its lower bound at the boundary.

 \item \textbf{A sampled interior bridge.}
 The row box has limiting geometric mass
 \[
 (\e^{x_+}-\e^{x_-})(\e^{y_+}-\e^{y_-})>0,
 \]
 while one orbit residue class contributes
 \( |I|/H_0+O(J^{-1})\).  Fixed-modulus prime and squarefree sampling,
 together with the literal-mask degree estimate, transfers the explicit
 continuous overlap to the sampled packet.  The canonical actual
 direction therefore has \(O(1)\) condition number on that subpacket.

 \item \textbf{Geometric density is not energy coverage.}
 If only \(|\zeta_m|\ll1\) is known, the source weight may vanish on
 every selected active box.  We give an exact construction with positive
 geometric density but zero good-carrier fraction.  If instead the
 remaining source factor is bounded below on a compatible fixed cell, the
 standard fixed-modulus row asymptotics yield a positive source-energy
 fraction for that declared finite cell decomposition.
\end{enumerate}

\subsection{Claim level}

The factor identities and support criterion are Level L0 exact algebra
and analysis.  Their application to the literal complete row cell and
static mask is a Level L1 physical-interface theorem.  No coherent prime
square, fixed-\(h_0\) arithmetic lower bound, parity-breaking estimate,
Hardy--Littlewood asymptotic, or twin-prime conclusion is obtained.  In
particular, selecting a positive-density interior subpacket is not a
substitute for proving that it carries a positive fraction of the full
actual energy.

\subsection{Organization}

\Cref{sec:tpc53-literal-packet} defines the packet and its correct norm.
The exact factor allocation is proved in
\cref{sec:tpc53-dictionary}.  The support criterion and explicit box
certificate are in \cref{sec:tpc53-support}.  We transfer them to the
sampled prime--squarefree packet in \cref{sec:tpc53-sampled}.  The
source-energy obstruction and its sufficient repair are treated in
\cref{sec:tpc53-energy}.  Endpoint costs and the remaining gates are
audited in \cref{sec:tpc53-endpoint}.
