\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Orbit-Scale CRT Compression and Uniform Gram Obstructions: Product-Slope Character Spectrum, Three-Modulus Alias Reduction, and a Coefficient-Specific Gate},
 pdfauthor={Liang Wang},
 pdfsubject={Exact route diagnostics for an orbit-sliced Mobius energy gate},
 pdfkeywords={Mobius correlation, Gram matrix, projective Plancherel, multiplicative characters, Chinese remainder theorem, aliasing, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\F}{\mathbb F}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cL}{\mathcal L}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cU}{\mathcal U}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\cX}{\mathcal X}
\newcommand{\op}{\operatorname{op}}
\newcommand{\HS}{\operatorname{HS}}
\newcommand{\lcm}{\operatorname{lcm}}

\title{\textbf{Orbit--Scale CRT Compression and Uniform Gram Obstructions:}\\
\textbf{Product--Slope Character Spectrum, Three--Modulus Alias Reduction,}\\
\textbf{and a Coefficient--Specific Gate}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
The preceding paper reduces a distinguished zero--frequency shell to an
orbit--sliced row energy
\[
 V_L+V_R\ll X^{o(1)}Q^3/J,
\]
whose proved diagonal is only \(O(X^{o(1)}Q^2J)\).  Here we decide how
far three natural routes can reach and identify the first
coefficient--sensitive spectral quantity for the TPC-34 orbit--sliced
product--slope interface.

First, for the abstract equal--row deletion model

\[
 A=\mathbf1\mathbf1^*-I_n,\qquad M_j=AD_j,
\]

with \(t<n\) unit--phase observations, the off--diagonal Gram matrix is
exactly

\[
 O=(n-2)(R^*R-tI_n).
\]

Consequently

\[
 \|O\|_{\rm op}\ge(n-2)\max\{t,n-t\},\qquad
 \|O\|_{\rm HS}^2\ge(n-2)^2nt(n-t),
\]

with equality at the Fourier tight--frame scale.  A block version survives
same--source deletion.  Thus cardinality, unit phases, and these deletions
alone cannot certify the much smaller uniform operator or
Hilbert--Schmidt gates proposed previously.  This is an abstract
information obstruction, not a lower bound for the physical masked Gram
matrix.

Second, we prove that the residue--multiplicity implementation of one--prime
projective Plancherel saturates at a normalized rms factor
\(\min\{J_0,S_0\}^{-1/2}\), with balanced residue sets attaining this scale
up to constants.  We then diagonalize a complete, separable coherent
product--slope sum.  For centered
\(f,g:\mathbb F_q\to\mathbb C\), its exact singular spectrum is indexed by
multiplicative characters.  Projective Plancherel controls the average
character energy, whereas a coherent weight sees its maximum; the possible
average--to--maximum loss is exactly \(q-1\).  This selects a
coefficient--specific finite-model interface rather than a uniform norm
gate.  A controlled decomposition of the actual physical mask into such
complete separable layers is not proved here.

Third, simultaneous orbit--scale congruences have an exact alias ladder.
For \(r\) pairwise coprime moduli \(q_i\asymp J\) and an affine determinant
\(F\) of size \(O(X)\), the number of possible aliases is
\(O(1+X/J^r)\).  At

\[
 Q=X^{267/400+o(1)},\quad
 J=X^{133/400+o(1)},\quad
 T=X^{193/500+o(1)},
\]

three moduli leave \(X/J^3=X^{1/400+o(1)}=Q/J^2\), exactly the allowance
above the orbit diagonal, while four moduli are the first orbit--scale
choice giving strict no--wrap.  We prove, however, that CRT coordinates do
not automatically tensorize: data supported on one coordinate reproduce
the one--prime normalized rms exactly.  The specified
merge--then--complete strategy also obeys the bookkeeping inequality
\((1+X/P)(1+P/J)\ge X/J\asymp Q\).

On the physical side, the same--ultra block of the orbit--sliced energy
satisfies

\[
 \cV_{L,u=}+\cV_{R,u=}
 \ll X^{o(1)}Q^2J(1+Q/T)
 \ll X^{o(1)}Q^3J/T.
\]

This removes one orbit factor from the earlier two--time estimate and saves
the full factor \(T\), but it still misses the orbit gate by \(J^2/T\).
The outcome is a precise next target: a joint three--modulus theorem that
suppresses low--coordinate CRT modes in the actual coefficient direction,
or an equivalent bound for the bad multiplicative--character mass,
together with the missing complete separable reassembly lemma.  No such
physical coefficient estimate or reassembly is proved here.  We claim no
affine Chowla theorem, parity breach, Hardy--Littlewood asymptotic, or
twin--prime result.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; orbit energy; Gram
matrix; projective Plancherel; multiplicative character; CRT aliasing;
parity boundary.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary 11L07,
11A07, 15A18.

\input{sections/introduction}
\input{sections/inherited-gate}
\input{sections/uniform-gram}
\input{sections/projective-saturation}
\input{sections/product-slope-spectrum}
\input{sections/crt-alias}
\input{sections/physical-ultra}
\input{sections/integer-incidence}
\input{sections/ledger-next-gate}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
