\begin{abstract}
Sparse provenance completion reduces, component by component, to
\[
  \Gamma(b,C)=\min_{\theta\in\C^J}\|b+C\theta\|_1.
\]
The preceding incidence decomposition identifies the exact nonzero
bipartite graph but does not by itself solve a nontrivial component.  We
solve the forest-supported complex-scalar case to the extent permitted
by its intrinsic defect.

First, a variable leaf and its adjacent analysis row can be erased
without changing the value.  Second, for a matrix with forest support
and nonzero edge coefficients,
\[
  \rank_{\C} C=\nu(G),
\]
where \(\nu(G)\) is the maximum matching number.  Consequently a
row-saturating matching is exactly the graph-theoretic condition for
zero completion cost for every datum.  After exhaustive variable-leaf
erasure, every surviving variable has degree at least two, the variables
are matchable, and each connected core satisfies
\[
 \dim_{\C}\Ker C^*
 =|I|-|J|
 =1+\sum_{j\in J}\bigl(\deg(j)-2\bigr).
\]
Thus a core has one complex obstruction precisely when every surviving
variable has degree two.

For any one-defect component, if \(\Ker C^*=\C\alpha\), we obtain the
closed formula
\[
 \Gamma(b,C)=
 \frac{|\langle\alpha,b\rangle|}{\|\alpha\|_\infty},
\]
together with explicit primal and dual optimizers and the complete
optimal-residual face.  On a degree-two tree, \(\alpha\) is recovered by
edgewise phase transport.  For branching cores we give an exact
matching-based reduction to a complex second-order cone program having
only \(\dim\Ker C^*\) variables.  We also prove an exact
column-dominant pivot rule and additive or fractional lower bounds from
balanced Hall-circuit motifs.

These results convert a large sparse completion problem into closed
forms on defect-one trees and auditable low-dimensional programs on the
remaining cores.  They are algebraic and convex-analytic interface
theorems.  No estimate here proves that the literal fixed-shift
arithmetic matrix has forest support, that its motif scores are
non-negligible, or that any global endpoint budget is crossed.
\end{abstract}

