\section{The exact defect of a pruned tree core}
\label{sec:core-defect}

Let a nontrivial connected pruned core contain \(p\) analysis rows and
\(q\) variables.  Every variable now has degree at least two.

\begin{lemma}[All surviving variables are matchable]\label{lem:var-match}
Every set \(S\subseteq J\) of variables in a pruned tree core satisfies
\[
 |N(S)|\ge |S|+1.
\]
In particular, a matching saturates every variable.
\end{lemma}

\begin{proof}
The subgraph induced by \(S\cup N(S)\) is a forest.  Because every edge
incident to a variable of \(S\) remains inside this induced graph and
every such variable has degree at least two,
\[
 2|S|
 \le |E(S,N(S))|
 \le |S|+|N(S)|-1.
\]
The stated inequality follows.  Hall's theorem then supplies a
matching saturating \(J\).
\end{proof}

\begin{theorem}[Pruned-core defect identity]\label{thm:defect}
For a connected pruned tree core,
\begin{equation}\label{eq:defect}
 \rank_{\C}C=q,
 \qquad
 d:=\dim_{\C}\Ker C^*
 =p-q
 =1+\sum_{j\in J}\bigl(\deg(j)-2\bigr).
\end{equation}
\end{theorem}

\begin{proof}
\Cref{lem:var-match,thm:forest-rank} give \(\rank C=q\), hence
\(\dim\Ker C^*=p-q\).  The tree identity
\[
 p+q-1=|E|=\sum_{j\in J}\deg(j)
\]
rearranges to the last equality in \eqref{eq:defect}.
\end{proof}

\begin{corollary}[One-defect topology]\label{cor:one-defect-topology}
A nontrivial pruned tree core has \(d=1\) if and only if every variable
has degree two.  Each unit of excess degree
\(\deg(j)-2\) adds one complex dual degree of freedom.
\end{corollary}

Thus branching is measured exactly.  A degree-three variable is not a
minor perturbation of the scalar case: it creates at least a
two-complex-dimensional dual feasible section.  An isolated analysis
row is treated separately as the degenerate \(p=1,q=0\) core and has
value \(|b_i|\).

\begin{remark}[Combinatorics versus coefficients]
The dimension formula is coefficient-independent only because forest
support prevents determinant cancellation.  It does not say that the
value \(\Gamma(b,C)\) is coefficient-independent.  Even at defect one,
the transported charge and its pairing with \(b\) retain all literal
edge magnitudes and phases.
\end{remark}

