\section{A column-dominant exact pivot}
\label{sec:dominance}

Variable leaves are maximally sparse pivots.  A larger class of exact
\(\ell^1\) eliminations is available when one coefficient dominates the
rest of its column.

\begin{theorem}[Column-dominant pivot elimination]\label{thm:pivot}
Choose a row \(r\in I\) and variable \(j\in J\) with \(c_{rj}\ne0\).
Assume
\begin{equation}\label{eq:dominance}
 |c_{rj}|\ge\sum_{i\ne r}|c_{ij}|.
\end{equation}
For \(i\ne r\) and \(k\ne j\), define
\begin{equation}\label{eq:pivot-data}
 b'_i=b_i-\frac{c_{ij}}{c_{rj}}b_r,
 \qquad
 c'_{ik}=c_{ik}-\frac{c_{ij}}{c_{rj}}c_{rk}.
\end{equation}
Then
\begin{equation}\label{eq:pivot-equality}
 \Gamma(b,C)=\Gamma(b',C'),
\end{equation}
where \(C'\) deletes row \(r\) and column \(j\) after the update.
There exists an optimizer whose \(r\)-th residual is zero.  If
\eqref{eq:dominance} is strict, every optimizer has zero \(r\)-th
residual.
\end{theorem}

\begin{proof}
Fix all variables \(k\ne j\), and let
\[
 u_i=b_i+\sum_{k\ne j}c_{ik}\theta_k.
\]
Write \(\theta_j=-u_r/c_{rj}+\delta\).  The objective becomes
\[
 |c_{rj}\delta|
 +\sum_{i\ne r}
 \left|u_i-\frac{c_{ij}}{c_{rj}}u_r+c_{ij}\delta\right|.
\]
The triangle inequality bounds this below by its value at \(\delta=0\)
plus
\[
 \left(|c_{rj}|-\sum_{i\ne r}|c_{ij}|\right)|\delta|.
\]
Thus \(\delta=0\) is always optimal under \eqref{eq:dominance}, and is
forced under strict dominance.  Substitution at \(\delta=0\) produces
\eqref{eq:pivot-data} and \eqref{eq:pivot-equality}.
\end{proof}

\begin{proposition}[Matched dual lift]\label{prop:dual-lift}
Under \eqref{eq:dominance}, every dual feasible \(z'\) for the reduced
program lifts by
\begin{equation}\label{eq:dual-lift}
 z_i=z'_i\ (i\ne r),
 \qquad
 z_r=
 -\frac{1}{\overline{c_{rj}}}
 \sum_{i\ne r}\overline{c_{ij}}z'_i.
\end{equation}
The lift satisfies \(|z_r|\le1\), \(C^*z=0\), and
\([z,b]_{\R}=[z',b']_{\R}\).
\end{proposition}

\begin{proof}
The bound follows from \(\|z'\|_\infty\le1\) and
\eqref{eq:dominance}.  Formula \eqref{eq:dual-lift} is exactly the
\(j\)-column balance equation.  Substitution shows that every other
column balance is the corresponding reduced equation, while the
objective identity follows from the update of \(b'\).
\end{proof}

A component that can be exhausted by successive pivots satisfying
\eqref{eq:dominance} is \emph{dominance-peelable}.  The theorem and its
dual lift then give an exact recursion with matched upper and lower
certificates.  A variable leaf is the special case in which every
off-pivot entry of column \(j\) is zero.  An analysis leaf is not such a
case unless its incident column also satisfies the dominance inequality.

