\section{Exact reduction of a branching core}
\label{sec:higher-defect}

Let a connected pruned tree core have \(p\) rows, \(q\) variables, and
defect \(d=p-q\ge1\).  By \cref{lem:var-match}, choose a matching that
saturates all variables.  Let \(M\subset I\) be its \(q\) matched rows
and \(U=I\setminus M\) the \(d\) unmatched rows.  Write \(C_M\) and
\(C_U\) for the corresponding row restrictions.

\begin{theorem}[Defect-dimensional dual reduction]\label{thm:reduced-socp}
The square matrix \(C_M\) is invertible.  Define
\[
 K:\C^U\longrightarrow\C^I,
 \qquad
 (K\xi)_U=\xi,
 \qquad
 (K\xi)_M=-(C_M^*)^{-1}C_U^*\xi.
\]
Then \(K\) is an isomorphism from \(\C^U\) onto \(\Ker C^*\), and
\begin{equation}\label{eq:reduced-socp}
 \boxed{\displaystyle
 \Gamma(b,C)
 =
 \max_{\xi\in\C^U}
 \left\{
 [K\xi,b]_{\R}:\|K\xi\|_\infty\le1
 \right\}.}
\end{equation}
Thus a branching tree core reduces exactly to a complex
second-order-cone program in \(d\) complex variables.
\end{theorem}

\begin{proof}
The matching is the unique perfect matching of the forest subgraph on
\(M\sqcup J\); otherwise the symmetric difference of two perfect
matchings would contain a cycle.  Hence
\(\det C_M\) is, up to sign, the product of its matched nonzero entries.
It is nonzero.

Writing \(z=(z_M,z_U)\), the balance equation is
\[
 C_M^*z_M+C_U^*z_U=0.
\]
After setting \(z_U=\xi\), invertibility gives the displayed formula
for \(z_M\), uniquely.  Substitution into \eqref{eq:dual} proves
\eqref{eq:reduced-socp}.  Each constraint
\(|(K\xi)_i|\le1\) is a two-dimensional second-order-cone constraint.
\end{proof}

\begin{remark}[What the reduction does and does not close]
At \(d=1\), \eqref{eq:reduced-socp} is a disk and reduces to
\cref{thm:one-defect}.  At \(d>1\), it is an intersection of complex
ellipsoidal cylinders.  The theorem removes all redundant primal
variables and exposes the exact intrinsic dimension, but it does not
replace a genuinely multidimensional feasible body by a fictitious
single scalar.
\end{remark}

\begin{proposition}[Exact a posteriori certificate]\label{prop:reduced-gap}
For any primal trial \(\theta\) and reduced dual trial \(\xi\) with
\(\|K\xi\|_\infty\le1\), set
\[
 U(\theta)=\|b+C\theta\|_1,
 \qquad
 L(\xi)=[K\xi,b]_{\R}.
\]
Then
\[
 L(\xi)\le\Gamma(b,C)\le U(\theta),
 \qquad
 0\le U(\theta)-L(\xi).
\]
Equality is a complete optimality certificate.
\end{proposition}

This certificate is stable under the component sum of TPC-77: upper
and lower values add, so the global gap is the sum of component gaps.

\begin{remark}[Exact min--sum remains available]
Rooting a general tree also yields an exact convex min--sum recursion.
For real data and real scalar variables the messages are
piecewise-linear.  For genuinely complex data they are generally
curved cone-representable functions.  We use
\eqref{eq:reduced-socp} as the canonical finite certificate because it
does not suggest a nonexistent coordinatewise-median formula.
\end{remark}

