\section{Introduction}

The completion layers developed in
\cite{WangTPC75,WangTPC77} separate a fixed-shift physical assembly from
a finite convex program.  After immutable coordinates and exact zero
columns are removed and the actual incidence graph is split into
connected components, the active algebraic problem is
\begin{equation}\label{eq:intro-program}
 \Gamma(b,C)
 =
 \min_{\theta\in\C^J}
 \sum_{i\in I}
 \left|b_i+\sum_{j\in J}c_{ij}\theta_j\right|.
\end{equation}
For an arbitrary matrix, the primal--dual certificate of TPC-77 is the
right stopping point.  The purpose of this paper is to identify what
becomes exactly solvable when the \emph{actual} nonzero support of \(C\)
is a forest.

There are three distinct questions.
\begin{enumerate}[label=(Q\arabic*),leftmargin=2.7em]
\item When does the parameter family cancel every datum?
\item If cancellation is impossible, how many independent obstructions
remain and when is there a closed formula?
\item When the obstruction space is multidimensional, what exact
reduction and lower certificates survive?
\end{enumerate}
Forest support answers all three without genericity assumptions on the
nonzero coefficients.  Its decisive feature is not merely sparsity.
Every matching minor contains a unique determinant monomial, so no
coefficient cancellation can destroy its rank.  This converts matching
theory \cite{LovaszPlummer1986,Schrijver2003} into an exact algebraic
test.

\paragraph{Main results.}
Variable leaves can be removed exactly.  Forest rank equals maximum
matching size.  Once variable-leaf pruning stops, a connected core has
defect
\[
 d=\dim_{\C}\Ker C^*
   =1+\sum_{j}(\deg(j)-2).
\]
The case \(d=1\) has a complete closed solution, including both
optimizers and the entire optimal residual face.  Higher defect is not
hidden behind a scalar surrogate: it is reduced exactly to a
\(d\)-complex-variable second-order cone problem.  In parallel, a
column-dominant pivot gives a different exact elimination rule, and
balanced local charges give checkable dual-packing lower bounds.

\paragraph{What is genuinely new at this layer.}
Component decomposition alone says that independent pieces add.
Here we determine the value of every defect-one forest piece in closed
form and give a structural zero test for every forest piece.  We also
isolate the exact branching statistic that measures the dimension of
the unsolved core.  This is a real reduction of the completion
interface, not a relabeling of the previous dual program.

\paragraph{Scope.}
The forest theorems use nonzero complex-scalar entries \(c_{ij}\).
TPC-77 allowed general real-linear maps \(\C\to\C\); a nonzero
real-linear leaf block need not be surjective, so those results do not
extend verbatim.  Moreover, forest topology says nothing about how
frequently a literal fixed-shift arithmetic assembly realizes a given
motif, or how large the corresponding datum score is.  Those are later
arithmetic-transfer questions.  We keep them outside every theorem
below.

\paragraph{Organization.}
\Cref{sec:setup} records the primal--dual normal form.
\Cref{sec:leaf-rank} proves leaf erasure and the matching-rank theorem.
\Cref{sec:core-defect} identifies the pruned-core defect.
\Cref{sec:one-defect,sec:degree-two} give the closed solution and phase
transport.  \Cref{sec:dominance} proves a second exact pivot rule.
\Cref{sec:higher-defect,sec:motifs} treat branching cores and dual
packings.  \Cref{sec:countermodels,sec:physical-boundary} state the
failure modes and the physical claim boundary.

