\section{Variable-leaf erasure and forest rank}
\label{sec:leaf-rank}

\begin{theorem}[Exact variable-leaf erasure]\label{thm:leaf-erasure}
Suppose \(j\in J\) is adjacent to exactly one row \(i\in I\), with
\(c_{ij}\ne0\).  Let \(C'\) and \(b'\) be obtained by deleting row
\(i\) and column \(j\).  Then
\[
 \Gamma(b,C)=\Gamma(b',C').
\]
If deletion disconnects the remaining graph, the right-hand side is
the sum of the resulting component values.
\end{theorem}

\begin{proof}
Fix all variables except \(\theta_j\).  Because column \(j\) appears
only in row \(i\), choosing
\[
 \theta_j
 =
 -\frac{b_i+\sum_{k\ne j}c_{ik}\theta_k}{c_{ij}}
\]
sets the \(i\)-th residual to zero and changes no other residual.
Minimizing over the remaining variables proves the equality.
Equivalently, the \(j\)-th dual balance equation is
\(\overline{c_{ij}}z_i=0\), so every dual feasible vector has
\(z_i=0\).
\end{proof}

\begin{definition}[Variable-leaf pruning]\label{def:pruning}
Repeatedly erase a variable leaf and its adjacent analysis row by
\cref{thm:leaf-erasure}; also erase every isolated variable produced by
the operation.  The surviving forest is called a \emph{pruned core}.
\end{definition}

Every erasure preserves the total value, irrespective of the order.
Different orders may label the surviving components differently, but
all yield exact residual programs.

\begin{theorem}[Forest structural rank]\label{thm:forest-rank}
Let the actual support of \(C\) be a forest and suppose every supported
entry is nonzero.  Then
\begin{equation}\label{eq:forest-rank}
 \rank_{\C}C=\nu(G(C)).
\end{equation}
\end{theorem}

\begin{proof}
For every matrix, a nonzero \(r\times r\) minor supplies a size-\(r\)
matching through one nonzero determinant term.  Hence
\(\rank C\le\nu(G(C))\).

Conversely, take a matching of size \(r\) and the submatrix on its
incident rows and columns.  The matching gives one nonzero determinant
monomial.  If another determinant monomial were nonzero, the two
perfect matchings of this induced bipartite graph would have a
nonempty alternating cycle in their symmetric difference.  That is
impossible in a forest.  The determinant is therefore, up to sign, the
product of the matched nonzero entries and is nonzero.  Thus
\(\rank C\ge r\).  Maximize over matchings.
\end{proof}

\begin{corollary}[Uniform zero-cost test]\label{cor:zero-test}
For a forest-supported \(C\), the following are equivalent:
\begin{enumerate}[label=(\roman*),leftmargin=2.5em]
\item \(\Gamma(b,C)=0\) for every \(b\in\C^I\);
\item \(C\) has full row rank;
\item \(G(C)\) has a matching saturating every analysis row;
\item variable-leaf pruning erases every analysis row.
\end{enumerate}
\end{corollary}

\begin{proof}
The first two statements are equivalent to \(\Ran C=\C^I\), and
\cref{thm:forest-rank} gives the equivalence with (iii).

If pruning erases all rows, repeated use of
\cref{thm:leaf-erasure} gives zero value for every datum, hence (iv)
implies (i).  Conversely, if a nonempty pruned core remains, every
surviving variable has degree at least two.  On a connected core with
\(p\) rows and \(q\) variables, the tree identity gives
\[
 p+q-1=|E|\ge2q,
\]
so \(p\ge q+1\).  Such a core has no row-saturating matching.  Hence
(iii) implies (iv): indeed, when a variable leaf \(j\) adjacent to
\(i\) is erased, any row-saturating matching can first be modified to
use \((i,j)\) (freeing the edge formerly incident to \(i\)), and then
restricted to the remaining graph.  Row saturation is therefore
preserved at every pruning step.
\end{proof}

\begin{remark}[Datum-specific cancellation]\label{rem:specific-zero}
The graph test is uniform in \(b\).  For one particular datum,
\[
 \Gamma(b,C)=0
 \quad\Longleftrightarrow\quad
 -b\in\Ran C,
\]
even when no row-saturating matching exists.  Topology alone cannot
decide this datum-specific equality.
\end{remark}
