\section{Hall-circuit motifs and dual packings}
\label{sec:motifs}

The reduced program is exact, but a lower bound may be certified
without solving it globally.  The correct local objects are balanced
charges, not merely dense-looking subgraphs.

\begin{definition}[Row Hall circuit]\label{def:hall-circuit}
A nonempty row set \(S\subseteq I\) is a \emph{row Hall circuit} when
\[
 |N(S)|<|S|
\]
and no proper nonempty subset of \(S\) has this property.  Here
\(N(S)\) contains \emph{every} variable adjacent to a row of \(S\).
\end{definition}

\begin{theorem}[Canonical circuit charge]\label{thm:circuit-charge}
Assume \(G(C)\) is a forest and \(S\) is a row Hall circuit.  Then
\[
 |N(S)|=|S|-1,
 \qquad
 \dim_{\C}\Ker C_{S,N(S)}^*=1.
\]
Every nonzero generator \(g^S\) of this kernel has
\(g_i^S\ne0\) for all \(i\in S\).  Extending \(g^S\) by zero outside
\(S\) gives a global balanced charge \(C^*g^S=0\).  Consequently
\begin{equation}\label{eq:motif-score}
 \Gamma(b,C)\ge
 \frac{|\langle g^S,b_S\rangle|}
      {\|g^S\|_\infty}.
\end{equation}
\end{theorem}

\begin{proof}
For each \(i\in S\), minimality gives
\(|N(S\setminus\{i\})|\ge|S|-1\), while
\(N(S\setminus\{i\})\subseteq N(S)\).  Hence
\(|N(S)|=|S|-1\).

Every proper row subset is matchable, whereas \(S\) is not.  The
forest-rank theorem therefore gives row rank \(|S|-1\) for
\(C_{S,N(S)}\), so its left kernel is one dimensional.  If a generator
vanished at \(i\), its restriction would give a nonzero left-kernel
vector on the proper set \(S\setminus\{i\}\), contradicting its full
row rank.  The zero extension is globally balanced because \(N(S)\)
contains all columns incident to \(S\).  Normalize it to
\(\ell^\infty\)-norm one, rotate its phase to make the pairing with
\(b\) nonnegative, and apply \eqref{eq:dual}.
\end{proof}

The insistence on the full neighbor set is essential.  A charge
balanced only against columns drawn inside a picture of the motif may
fail the global equation at an incident boundary column.

\begin{theorem}[Disjoint and fractional motif packing]\label{thm:packing}
Let \(g^1,\ldots,g^m\in\Ker C^*\).
\begin{enumerate}[label=(\alph*),leftmargin=2.4em]
\item If their row supports are pairwise disjoint and
\(\|g^s\|_\infty=1\), then
\begin{equation}\label{eq:disjoint-pack}
 \Gamma(b,C)\ge
 \sum_{s=1}^m|\langle g^s,b\rangle|.
\end{equation}
\item More generally, if
\begin{equation}\label{eq:capacity}
 \sum_{s=1}^m|g_i^s|\le1
 \qquad(i\in I),
\end{equation}
then the same lower bound \eqref{eq:disjoint-pack} holds.
\end{enumerate}
\end{theorem}

\begin{proof}
For each \(s\), choose \(\omega_s\in\C\), \(|\omega_s|=1\), so that
\(\langle \omega_s g^s,b\rangle\) is nonnegative real.  The sum
\[
 z=\sum_s\omega_s g^s
\]
is balanced.  Disjoint support in (a), or the capacity inequality in
(b), gives \(\|z\|_\infty\le1\).  Its dual objective is the stated sum.
\end{proof}

\begin{remark}[Certificate, not prevalence]
\Cref{thm:packing} is useful only after actual balanced motifs and their
literal datum scores have been exhibited.  Counting an ambient graph
motif, replacing an exact zero by a tolerance, or ignoring incident
columns does not produce a feasible charge.  Moreover, a large abstract
packing has arithmetic force only if its global raw normalization is
kept and its physical carrier set has the required size.
\end{remark}

