\section{Literal fixed-shift census and claim boundary}
\label{sec:physical-boundary}

The exact theorems become a physical certificate only after a literal
assembly has been archived.  Fix one nonzero physical shift \(h_0\).
For each truncation or scale \(X\), the required record is:
\begin{enumerate}[label=(P\arabic*),leftmargin=2.7em]
\item the native input and output keys, with no collapsed or missing
carrier labels;
\item the literal baseline vector \(b_X\) and completion matrix \(C_X\);
\item the exact nonzero support after all algebraic sums;
\item the decomposition into fixed rows, zero columns, and actual
connected components;
\item for every forest component, its matching, pruning trace, defect,
transported charge or reduced matrix \(K\);
\item matched primal and dual values, with numerical tolerances recorded
separately from graph adjacency;
\item the common global raw atomic normalizer, whether it is already
absorbed into \(b_X,C_X\), and every component contribution under that
single convention.
\end{enumerate}

\begin{proposition}[Auditable forest census identity]\label{prop:census}
For any archived finite literal program, let \(\cF_X\) be its actual
forest components and \(\cU_X\) its remaining components.  Then
\begin{equation}\label{eq:census}
 \Gamma(b_X,C_X)
 =
 \|b_{X,\mathrm{fix}}\|_1
 +\sum_{S\in\cF_X}\Gamma_S
 +\sum_{S\in\cU_X}\Gamma_S.
\end{equation}
Every zero-prunable forest term and every defect-one forest term in
\eqref{eq:census} is exactly computable by this paper.  Every other
forest term admits the defect-reduced interval of this paper.  Every
remaining term, including a nonforest component, retains the matched
TPC-77 primal--dual interval.
\end{proposition}

\begin{proof}
This is the exact component factorization of TPC-77, followed by
\cref{thm:leaf-erasure,cor:zero-test,thm:one-defect,thm:reduced-socp}
on the forest terms.  No thresholding or change of normalization occurs.
\end{proof}

No literal fixed-\(h_0\) dataset is included in this paper.  Therefore
we make no numerical statement about the frequency of forest
components, the distribution of their defects, or the normalized size
of their scores.

\subsection*{Progress labels}

\begin{center}
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.20\linewidth}
>{\raggedright\arraybackslash}p{0.70\linewidth}@{}}
\toprule
Label & Status after this paper\\
\midrule
L0: model algebra &
Exact for the finite complex-scalar forest program.\\
L1: interface/certificate &
Advanced: forest rank, pruning, defect-one values, reduced SOCPs, and
motif packings are now exact and auditable.\\
L2: fixed-\(h_0\) arithmetic &
Not advanced here: no density, cancellation, or endpoint estimate for
literal arithmetic coefficients is proved.\\
\bottomrule
\end{tabular}
\end{center}

\subsection*{Endpoint loss ledger and stop rule}

The inherited arithmetic ledger permits a \emph{total fixed-power
exponent loss strictly smaller than \(1/400\)}.  Equality is not enough:
the route stops once accumulated certified losses reach or exceed
\(1/400\).  The exact finite-dimensional reductions in this paper add
zero exponent loss by themselves, but they also prove no arithmetic
gain.  Any downstream dictionary, carrier restriction, approximation,
or reassembly loss must be entered in the same ledger.

In particular, neither a component gauge nor a motif-packing lower
score is a \(1/400\) gain without a separate literal transfer theorem
that proves the direction, scale, and global raw normalization.  If
that transfer incurs total loss at least \(1/400\), or reduces to an
unproved parity-sensitive correlation, this branch must be recorded as
an L1 interface result or a negative transfer result rather than an L2
advance.

\subsection*{Conclusion}

Forest sparsity creates an exact hierarchy:
\[
\begin{split}
\text{variable-leaf pruning}
&\longrightarrow \text{uniform zero test},\\
\text{degree-two core}
&\longrightarrow \text{one-obstruction closed form},\\
\text{branching core}
&\longrightarrow \text{defect-dimensional SOCP},\\
\text{balanced motifs}
&\longrightarrow \text{additive dual lower certificates}.
\end{split}
\]
This closes a substantial finite-dimensional subgate of sparse
provenance completion.  It does not identify the needed physical
carriers or prove a parity-breaking arithmetic estimate.  That precise
separation is the basis for the next transfer layer.
