\section{Exact certificate, dependencies, and scope}
\label{sec:tpc29-certificate-scope}

\subsection{Finite exact certificate}

The standard-library script
\begin{center}
\texttt{experiments/tpc29\_certificate.py}
\end{center}
uses exception-based checks in both ordinary and optimized Python.  It
verifies the finite algebra underlying the paper by independent direct
and structured computations:

\begin{enumerate}[label=\textup{(\roman*)}]
 \item generalized-CRT compatibility, uniqueness of the orbit class,
 and finite-window occupancy for primitive row and modulus pairs;
 \item direct triple enumeration versus CRT enumeration for the
 dyadic incidence count, together with an explicit-constant finite
 version of \eqref{eq:tpc29-incidence-bound};
 \item direct versus CRT long-fiber bookkeeping, including the exact
 factorization $[r,s]=d(r/d)(s/d)$ for $d=(r,s)$;
 \item the calibrated prefix identity
 \eqref{eq:tpc29-exact-cutoff} and the five-term joint identity
 \eqref{eq:tpc29-five-term-identity}, using formal prime-log vectors
 rather than floating-point logarithms;
 \item the rational exponent formula
 \eqref{eq:tpc29-sparse-saving}, its boundary cases, and the exact
 high-$\beta$ margins in
 \eqref{eq:tpc29-high-sparse-margin}--\eqref{eq:tpc29-high-saving};
 \item explicit negative scope flags for every prime-pair, positivity,
 full-residual, and parity claim not proved here.
\end{enumerate}

The incidence regression checks a finite inequality with its explicit
arithmetic multiplicity constant.  It does not assign constant one to
the asymptotic $\ll$ symbol.  Nor does finite enumeration prove an
asymptotic M\"obius estimate.  Ordinary and optimized Python both
complete $37{,}265$ recorded top-level exact checks and regenerate
byte-identical JSON.  The reproducibility values are
\begin{itemize}
 \item source SHA-256:
 \nolinkurl{13de31994c18d36f30975121daf485d8aca2f738f5a48dfc31e297130ed136c6};
 \item JSON SHA-256:
 \nolinkurl{0cbe83d578f39246542d6b0480db3d4a3d9b02ed23036dd9f569671dd5e2242d};
 \item certificate digest:
 \nolinkurl{5c2858662e76278cf3e8b4f1e26a4ac024e3b863ca21a3be8866dcf921a162b1}.
\end{itemize}
The source hash normalizes newlines to LF; the final value hashes the
canonical sorted payload before the digest field is inserted.

\subsection{Dependency ledger}

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.34\textwidth}
                >{\raggedright\arraybackslash}p{0.20\textwidth}
                >{\raggedright\arraybackslash}p{0.37\textwidth}}
\toprule
Input or statement & Status & Use \\
\midrule
Opened-row $\ell^1/\ell^2$ provenance
& Imported & TPC-25; physical pair mass and row residue energy. \\
\addlinespace
Calibrated prefix and $L^{-1}$ drift
& Imported definition and bound & TPC-28; exact cutoff difference used here. \\
\addlinespace
Selected truncated closure at $T$
& Imported & TPC-28; locates the new complement, not used to prove the
incidence bounds. \\
\addlinespace
Cutoff difference, CRT fiber, incidence theorem
& Proved here & Finite identity and elementary divisor-incidence
geometry. \\
\addlinespace
Sparse content-rich and long large-content closure
& Proved here & Absolute physical estimates; no M\"obius cancellation
input. \\
\addlinespace
Fixed-form logarithmic Elliott theorem
& External benchmark & Explains the fixed-fiber result but is not used
in either main closure theorem. \\
\addlinespace
Primitive reflected-family dispersion
& Open & Required for the remaining small-content signed core. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Claims deliberately excluded}

The following statements are not consequences of this paper:
\begin{itemize}
 \item closure of every sparse fiber or every long fiber;
 \item closure of the complete ultra-long cutoff difference;
 \item closure of the full TPC-18 residual or every endpoint packet;
 \item a positive lower bound, a Hardy--Littlewood asymptotic, or
 infinitely many twin primes;
 \item a general violation of the sieve parity barrier;
 \item polynomially uniform two-point Chowla or Elliott cancellation.
\end{itemize}

The positive conclusion is narrower and exact: large shared content
closes a complete long-fiber sector and a nonempty sparse incidence
wedge in exponent space.  The remaining core is explicitly identified
rather than treated as random.
