\section{Introduction and claim ledger}
\label{sec:tpc29-introduction}

The primitive residual program separates a fixed-shift prime-pair
correlation into opened row packets before confronting the remaining
M\"obius signs.  TPC-23 identified the exact affine fibers produced by
reflecting divisors beyond a dynamic cutoff \citep{WangTPC23}.  TPC-26
then treated a finite annular difference jointly, and TPC-28 closed a
source-compatible selected square through an upper cutoff $T$, even
though its base already exceeds the Poisson length
\citep{WangTPC26,WangTPC28}.  The resulting statement is a rigorous
truncated-packet estimate.  The terms with a divisor larger than $T$
remain.

The present paper removes a new, explicitly defined part of that
remainder.  It does not ask for cancellation on any individual
M\"obius fiber.  Instead it exploits the common content of the two
reflected divisors.  If
\[
 r\mid mj+h,\qquad s\mid nj+h,
\]
then $(r,s)$ divides $h(m-n)$.  In the primitive physical packet it is
coprime to $h$, hence divides the nonzero row difference.  A large
shared content therefore has two simultaneous effects: it restricts
the row pair and reduces the number of primitive modulus pairs.  These
effects are strong enough to close two nonempty scale regions without
using the signs of $\mu$.

\subsection{The new results}

The proof has four layers.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item We retain the calibrated prefix and take its exact cutoff
 difference.  If $U_0$ contains all physical targets, then
 \begin{equation}
  P_{m,U_0}-P_{m,T}=C_{m;T,U_0}
  \label{eq:tpc29-intro-cutoff-difference}
 \end{equation}
 with no scalar centering error.  The joint difference has three raw
 ultra channels and two power-small row-drift legs.

 \item For a fixed off-diagonal row pair and dyadic divisor scales
 $A,B,G$, we prove
 \begin{equation}
  \cN_{m,n}(A,B,G)
  \ll_{\eps,h}X^\eps
  \min\left\{J,\frac{AB}{G^2}+\frac JG\right\}.
  \label{eq:tpc29-intro-incidence}
 \end{equation}
 The estimate is a count with multiplicity.  It therefore applies
 after inserting arbitrary signs and all physical support selectors.

 \item The opened-row $\ell^1$ provenance converts
 \eqref{eq:tpc29-intro-incidence} into a physical block bound.  In the
 sparse range $q=[r,s]\ge J$, every fixed $\eta>0$ gives
 \begin{equation}
  \frac{q}{(r,s)}\le JX^{-\eta}
  \quad\Longrightarrow\quad
  \cS_{\rm rich}\ll_\eps XQX^{-\eta+\eps}.
  \label{eq:tpc29-intro-sparse-wedge}
 \end{equation}
 Thus a short fiber is useful only after the number of primitive
 modulus pairs is also controlled.

 \item In the long-fiber region $q\le Y\le J$, an independent
 row-residue argument removes every block with common content
 $d=(r,s)>D$:
 \begin{equation}
  \cS_{q\le Y,\,d>D}
  \ll_\eps X^\eps
  \left\{
   \frac{XQ}{D}\log^2(2Y)+X\log^3(2Y)
  \right\}.
  \label{eq:tpc29-intro-long-pruning}
 \end{equation}
 For $D\ge X^\eta$ this has a fixed-power saving relative to $XQ$.
\end{enumerate}

These two closure regions share the same mechanism but cover different
fiber lengths.  The long theorem uses the $J/q$ occupancy and row
residue energy.  The sparse theorem keeps the unavoidable $+1$ in the
occupancy and compensates for it by requiring the primitive lcm
$q/(r,s)$ to be short.

At the TPC-28 high-$\beta$ sample,
\[
 \beta=\frac{267}{400},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
\]
the dyadic choice
\[
 A=B=X^{1/4},\qquad G=X^{1/10}
\]
has lcm exponent $2/5$ and primitive-lcm exponent $3/10$.  It is
sparse by $27/400$ and the new incidence saving is exactly $13/400$.
This $13/400$ is unrelated to the smaller $13/1600$ conductor margin
that closed the TPC-28 base.

\subsection{What remains}

The theorem does not estimate every short fiber.  When $(r,s)=1$ and
$[r,s]\ge J$, the exponent delivered by
\eqref{eq:tpc29-intro-incidence} is exactly the natural exponent.  A
new signed estimate after summing the growing family is still needed.
Nor does \eqref{eq:tpc29-intro-long-pruning} remove the long fibers
with small content.  Their affine slopes grow polynomially with the
row scale, whereas the fixed-form logarithmic Elliott theorem has no
uniform rate that can be summed over the physical family
\citep{Tao2016}.

No conclusion below concerns positivity, a prime-pair main term, or
infinitely many twin primes.  Even a future closure of every ultra
channel would still have to be reassembled with the full TPC-18
endpoint and block ledger before the residual-dispersion target was
reached \citep{WangTPC18}.

\subsection{Organization}

\Cref{sec:tpc29-interface} fixes the physical packet.
\Cref{sec:tpc29-calibrated-difference} proves the exact joint cutoff
identity and removes the row drifts.
\Cref{sec:tpc29-reflected-incidence} derives the reflected fibers and
the incidence bound.  \Cref{sec:tpc29-weighted-wedge} proves the
physical sparse theorem, while \cref{sec:tpc29-long-content} proves
the long-fiber companion theorem.  \Cref{sec:tpc29-high-beta} gives
the rational sample.  \Cref{sec:tpc29-primitive-boundary} identifies
the remaining signed gate, and \cref{sec:tpc29-certificate-scope}
records the certificate and exact scope.
