\section{Claim boundary and next gate}
\label{sec:claim-boundary}

\begin{theorem}[Audited conclusion]
\label{thm:audited-conclusion}
For the actual high-\(\beta\) TPC-32 coefficient at one fixed
nonzero \(h_0\), the distinguished zero mode is exactly a coherent
linear functional of the nonzero determinant frequencies.  Averaging
over the complete actual zero set gives the unique
minimum-\(\ell^2\) kernel within the zero-set-averaged class and
recovers the sharp bound
\[
 |Z_X|^2\le s_XD_X.
\]
Positive-density zero-arc padding also gives
\eqref{eq:physical-low-frequency}; at the critical row the triangular
filter reduces the missing pointwise input to
\(R_X=X^{133/600+\varepsilon}\) for sufficiently small fixed
\(\varepsilon>0\).  For any exceptional set,
\cref{thm:exceptional-ledger} gives the exact sufficient
multiplier-weighted return condition.
\end{theorem}

\begin{proof}
Combine
\cref{thm:literal-interface,thm:low-frequency-reduction,thm:critical-window,thm:exceptional-ledger}.
\end{proof}

\paragraph{What is proved.}
The finite reconstruction, optimizer, zero-arc filter, sharp support
inequality, low-window reduction, and exceptional-frequency ledger
are exact \(\Lzero\) results.  Their application to the padded literal
determinant coefficient and its inherited energy envelope is
\(\Lone\).  The correction from ``nonzero frequencies are
irrelevant'' to ``a short low-frequency coherent reassembly is the
remaining gate on the zero-mode branch'' is therefore rigorous.

\paragraph{What is not proved.}
There is no new \(\Ltwo\) estimate for the coherent sum, no lower
bound for \(D_X\), no fixed-shift Chowla theorem, and no transfer from
averaged shifts or generic frequencies.  The paper proves no parity
breakthrough, no prime-pair lower bound, and no twin-prime result.
Nothing is specialized to \(h_0=2\).

\paragraph{Two independent ledgers.}
If a later theorem proves
\[
 |Z_X|\le X^{-\eta_Z+o(1)}Q_X^2,\qquad
 D_X\ge X^{-\lambda_D+o(1)}Q_X^3J_X^2,
\]
then the TPC-82 flatness transfer uses
\[
 \lambda_D\le2\eta_Z.
\]
Separately, every fixed-power degradation actually entering the full
physical comparison must be counted once in
\[
 \Lambda_{\rm phys}<\frac1{400}.
\]
Equality in the second ledger stops the route; the first ledger is
not another copy of the \(1/400\) budget.

\paragraph{Stop rules.}
The tail condition
\((k-\tfrac12)\rho>1-\beta+\eta_Z\) is strict when a fixed-power
reserve is claimed.  If the padding has \(H_X/q_X\to0\), its filter
loss must be recalculated.  If \(k\) grows with \(X\), its constants
must be audited.  An almost-all-frequency input is insufficient unless
its multiplier-weighted exceptional contribution is returned.  A
resonant or short-fiber sector cannot be deleted.

\paragraph{Next gate.}
The positive route on the zero-mode branch is now precise: estimate the literal
low-frequency multiplier sum, or its fixed-\(h_0\)
determinant-character-twisted affine M\"obius expansion.  A
logarithmically averaged or
almost-all-scale theorem may be used only after a quantitative
Tauberian and quantifier transfer to the same growing packet.  The
next paper audits that transfer.
