\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={The Large-Divisor Prime-Pair Defect at Almost All Shifts: Uniform Small-Divisor Transfer, Fourier Coordinates, and Finite-Conductor Energy Escape},
 pdfauthor={Liang Wang},
 pdfsubject={An almost-all-shift closure theorem for the exact large-divisor defect in a prime-pair correlation},
 pdfkeywords={prime pairs, von Mangoldt correlation, Bombieri--Vinogradov theorem, almost-all shifts, Fourier correlation, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cH}{\mathcal H}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cV}{\mathcal V}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\e}{\mathrm e}

\title{\textbf{The Large-Divisor Prime-Pair Defect}\
\textbf{at Almost All Shifts:}\
\textbf{Uniform Small-Divisor Transfer, Fourier Coordinates,}\
\textbf{and Finite-Conductor Energy Escape}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
For a cutoff $D$, write the von Mangoldt function as the exact sum of its
short source-divisor part and its complementary defect,
\[
 a_D(n)=-\sum_{\substack{d\mid n\\d\le D}}\mu(d)\log d,
 \qquad
 r_D(n)=\Lambda(n)-a_D(n).
\]
The preceding paper in this series isolated
\[
 \cT_{h,>D}(X)=\sum_{X<n\le2X}r_D(n)\Lambda(n+h)
\]
as the complete large-divisor remainder left after a
Bombieri--Vinogradov evaluation of the prime-pair correlation.  For a fixed
nonzero even shift, estimating this remainder by $o(X)$ is equivalent to the
expected Hardy--Littlewood asymptotic and is therefore open.

Here the quantifier on the shift is changed and nothing else is removed from
the defect.  We first prove, uniformly for
$1\le |h|\le 2X^{1-\eps}$, that the short-divisor correlation with
$D=X^{1/2}(\log X)^{-B}$ equals
$\mathfrak S(h)X+O_A(X(\log X)^{-A})$.  Combining this uniform transfer with
the averaged Hardy--Littlewood theorem of Matom\"aki, Radziwi\l\l, and Tao
shows that, whenever
\[
 X^{8/33+\eps}\le H\le X^{1-\eps},
\]
the full defect satisfies
\[
 \cT_{h,>D}(X)=O_{A,\eps}(X(\log X)^{-A})
\]
for all but $O_{A,\eps}(H(\log X)^{-A})$ shifts in every permitted window of
length $2H$.  The deep almost-all prime-pair theorem is an external input;
the contribution here is the uniform defect transfer and its exact
interpretation.  Fixed $h$, in particular $h=2$, is not controlled.

We place the result in additive Fourier coordinates: the defect correlations
are matrix coefficients of the integer translation representation and their
global square sum is an exact weighted Fourier energy.  This is a spectral
identity, not a new dispersion estimate.  Finally, if $V_q$ denotes the
space of $q$-periodic functions on $(N,2N]$, we prove uniformly for
$q\le N^{1-\delta}$ that
\[
 \|P_{V_q}(\Lambda-1)\|_2^2
 \ll_\delta N\frac q{\varphi(q)}
 \ll_\delta N\log\log(3q),
\]
whereas $\|\Lambda-1\|_2^2\sim N\log N$.  Thus sublinear finite-conductor
models capture a vanishing proportion of the prime fluctuation's linear
$L^2$ energy.  This is a periodic-approximation boundary, not an
impossibility theorem for nonlocal sieve or Type~II methods.  No fixed-shift
prime-pair lower bound is proved.
\end{abstract}

\noindent\textbf{Keywords:} prime-pair defect; von Mangoldt correlation;
almost-all shifts; Bombieri--Vinogradov theorem; Fourier translation;
finite-conductor approximation.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N36; Secondary 11N13, 11N35, 42A38,
47B15.

\input{sections/introduction-scope}
\input{sections/uniform-small-divisor}
\input{sections/almost-all-closure}
\input{sections/spectral-density}
\input{sections/finite-conductor-barriers}
\input{sections/computations-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
