\section{Reduction of the complete frozen actual-coefficient family}
\label{sec:tpc48-actual-reduction}

We now apply \cref{thm:tpc48-common-profile-large-sieve} to the full
signed representation \eqref{eq:tpc48-signed-reassembly}.  No orbit
band and no projective layer is selected.

\subsection{The row-square normal form}

For one projective layer, define
\begin{equation}
 B_{\omega,m}(\alpha)
 :=\sum_{p,r}A_\omega(p,r,m)\e(-pr\alpha)
 v_{\omega,p,r,m}\in\Vv_{\mathrm L}.
 \label{eq:tpc48-row-vector}
\end{equation}
The arithmetic sum is finite.  Fourier transformation in the frozen
determinant intercept gives the exact identity
\begin{equation}
 \widehat{\cF^\omega}(\alpha)
 =\sum_{\substack{j\in\Z\\j\equiv a_\omega\!\!\pmod{H_0}}}
 \phi_\omega(j/J)
 \left(\sum_mB_{\omega,m}(\alpha)\e(mj\alpha)\right)
 \otimes e_j.
 \label{eq:tpc48-layer-shift-transform}
\end{equation}

\begin{proposition}[Exact residual square at fixed source]
\label{prop:tpc48-residual-square}
For fixed \(\omega,m,\alpha\), put
\begin{equation}
 B_{\omega,m,r}(\alpha)
 :=\sum_pA_\omega(p,r,m)\e(-pr\alpha)
 v_{\omega,p,r,m}.
 \label{eq:tpc48-inner-prime-sum}
\end{equation}
Then
\begin{equation}
 \boxed{
 \|B_{\omega,m}(\alpha)\|^2
 =\sum_r\|B_{\omega,m,r}(\alpha)\|^2.}
 \label{eq:tpc48-residual-square}
\end{equation}
\end{proposition}

\begin{proof}
For fixed \(m\), the vector
\(B_{\omega,m,r}(\alpha)\) is supported on the residual coordinate
\(s=d(m)r\).  Distinct supported cofactors \(r\) give distinct labels
and hence orthogonal coordinate subspaces.  The prime sum at one fixed
\(r\) remains coherent, which is why no \(p\)-square decomposition is
claimed.
\end{proof}

This identity localizes the remaining arithmetic task: one must control
the prime exponential sum inside each residual coordinate and then the
outer square sum over \(m,r\).

\subsection{A representation-independent projective envelope}

Let \(C_{\rm LS}(\phi,H_0)\) denote the least admissible constant
\(C_{\phi,H_0}\) in
\eqref{eq:tpc48-common-profile-large-sieve}.  For an admissible signed
representation \(\mathscr R\) of the actual coefficient, set
\begin{equation}
 \mathfrak S_{\mathscr R}(\alpha)
 :=\int C_{\rm LS}(\phi_\omega,H_0)^{1/2}
 \left(\sum_m\|B_{\omega,m}(\alpha)\|^2\right)^{1/2}
 d|\nu|(\omega),
 \label{eq:tpc48-representation-envelope}
\end{equation}
and define
\begin{equation}
 \mathfrak S_{\rm pr}(\alpha)
 :=\inf_{\mathscr R}\mathfrak S_{\mathscr R}(\alpha),
 \label{eq:tpc48-projective-envelope}
\end{equation}
where the infimum ranges over all inherited admissible
coefficientwise representations described in
\cref{sec:tpc48-interface}.  The set is nonempty by TPC--36/47.  This
definition does not estimate the envelope; it makes the reduction
independent of one chosen representation.  It is used only pointwise.
For integration we keep one fixed global representation, thereby
avoiding any measurability assertion for an infimum over an uncountable
representation class.

The proof of \cref{thm:tpc48-common-profile-large-sieve} shows that
\(C_{\rm LS}(\phi,H_0)^{1/2}\) is controlled by one fixed finite-order
\(C^B\)-seminorm once the common compact support is fixed.  For every
fixed admissible representation, the layer data are jointly
measurable and Bochner integrable; consequently
\(\mathfrak S_{\mathscr R}\) is a measurable extended-valued function.
Finiteness almost everywhere is part of admissibility.  If one works
with a broader representation class, all pointwise bounds remain valid
with value \(+\infty\), while the annular application below explicitly
requires a finite envelope.

\begin{theorem}[All-band reduction of the actual frozen family]
\label{thm:tpc48-actual-reduction}
Let \(t=\|\alpha\|_\T\ge0\), and assume
\eqref{eq:tpc48-large-sieve-no-wrap}.  Then the complete left frozen
family built from the literal \(h_0\)-coefficient field satisfies
\begin{equation}
 \boxed{
 \|\widehat{\cF}^{\rm fr,\mathrm L}(\alpha)\|
 \le
 \left(\frac{J}{H_0}D_J(t;K)\right)^{1/2}
 \mathfrak S_{\rm pr}(\alpha).}
 \label{eq:tpc48-actual-reduction}
\end{equation}
The same argument gives the right-side estimate with its corresponding
support cardinality and envelope.  Denote the preceding left envelope
by \(\mathfrak S_{\rm pr,\mathrm L}\) and its right analogue by
\(\mathfrak S_{\rm pr,\mathrm R}\).  On the orthogonal left--right sum,
the valid combined envelope is
\((\mathfrak S_{\rm pr,\mathrm L}^2+
\mathfrak S_{\rm pr,\mathrm R}^2)^{1/2}\), with the larger of the two
large-sieve prefactors if their supports differ.
Equivalently, for every band count \(L\),
\begin{equation}
 \left(
 \sum_{k\bmod L}
 \|\Pi_k\widehat{\cF}^{\rm fr,\mathrm L}(\alpha)\|^2
 \right)^{1/2}
 \le
 \left(\frac{J}{H_0}D_J(t;K)\right)^{1/2}
 \mathfrak S_{\rm pr}(\alpha).
 \label{eq:tpc48-actual-all-band-square-function}
\end{equation}
\end{theorem}

\begin{proof}
Apply \cref{thm:tpc48-common-profile-large-sieve} to
\eqref{eq:tpc48-layer-shift-transform}.  Minkowski's integral
inequality and the exact signed identity
\eqref{eq:tpc48-signed-reassembly} give
\eqref{eq:tpc48-actual-reduction} with
\(\mathfrak S_{\mathscr R}\) for every admissible representation.
Take the infimum.  Equation
\eqref{eq:tpc48-actual-all-band-square-function} is the exact
orthogonal resolution \eqref{eq:tpc48-projector-resolution}.
\end{proof}

The theorem controls the complete orbit output, not a selected band,
and it incurs no cover-count factor.  Its right side is a projective
row-square envelope rather than the physical atomic diagonal.  No
bound relating those two quantities is assumed.

\subsection{Residual grouping}

On the active residual space, let \(C\) be the grouping map from
TPC--47.  It acts on the non-orbit factor, commutes with every \(\Pi_k\)
and \(U_{m\alpha}\), and satisfies \(\|C\|^2=\rho_{\rm res}\).
Consequently
\begin{equation}
 \|C\widehat{\cF}^{\rm fr,\mathrm L}(\alpha)\|
 \le\rho_{\rm res}^{1/2}
 \left(\frac{J}{H_0}D_J(t;K)\right)^{1/2}
 \mathfrak S_{\rm pr}(\alpha).
 \label{eq:tpc48-grouped-actual-bound}
\end{equation}
At \(h_0\), this grouping recovers the corresponding large-prime
component of the actual equality column under the inherited global
sign convention.  It neither restores the base component nor converts
the residual Gram route into the native affine physical face.
