\section{Tube statistics and sharpness ledgers}
\label{sec:tpc48-tube-statistics}

The pointwise channel load of \cref{thm:tpc48-channel-norm} is a
worst-case quantity.  A separate two-dimensional calculation records
the exact average incidence geometry.  It is useful precisely because
it also shows what averaging does \emph{not} prove.

Let \(E\subset\T\) be measurable and let \(\cM\subset\Z\) contain
\(K\) distinct integers.  Define
\begin{equation}
 \cL_E(\alpha,\beta)
 :=\sum_{m\in\cM}\one_E(\beta-m\alpha).
 \label{eq:tpc48-two-dimensional-load}
\end{equation}

\begin{theorem}[Exact first and second tube moments]
\label{thm:tpc48-tube-moments}
With normalized Haar measure on \(\T^2\),
\begin{align}
 \int_{\T^2}\cL_E(\alpha,\beta)\,d\alpha\,d\beta
 &=K|E|,
 \label{eq:tpc48-tube-first-moment}\\
 \int_{\T^2}\cL_E(\alpha,\beta)^2\,d\alpha\,d\beta
 &=K|E|+K(K-1)|E|^2.
 \label{eq:tpc48-tube-second-moment}
\end{align}
\end{theorem}

\begin{proof}
Translation invariance gives
\(\int_\T\one_E(\beta-m\alpha)\,d\beta=|E|\), proving the first
identity after summing over \(m\).  For the second, expand the square.
The \(K\) diagonal terms contribute \(K|E|\).  If \(m\ne n\), the map
\begin{equation}
 (\alpha,\beta)\longmapsto
 (\beta-m\alpha,\beta-n\alpha)
 \label{eq:tpc48-pair-torus-map}
\end{equation}
is a surjective continuous homomorphism of compact tori and therefore
pushes normalized Haar measure to normalized Haar measure.  Each
ordered off-diagonal pair consequently contributes \(|E|^2\).
\end{proof}

For one critical quotient cell \(E=\cC_k\), \(|E|=1/L\), so
\begin{equation}
 \mathbb E_{\alpha,\beta}\cL_E=\frac KL,
 \qquad
 \mathbb E_{\alpha,\beta}\cL_E^2
 =\frac KL+\frac{K(K-1)}{L^2}.
 \label{eq:tpc48-critical-cell-moments}
\end{equation}
For dense \(K\asymp M\) and critical \(L\asymp J\), the mean load is
\begin{equation}
 \frac KL\asymp\frac MJ=X^{67/200+o(1)}.
 \label{eq:tpc48-average-critical-load}
\end{equation}
This records the same \(K/L\) geometric density scale as the
coarse-edge model in \eqref{eq:tpc48-dense-load}.  It is not a
fixed-\(\alpha\) estimate.

\begin{remark}[What the moment identity does not average]
The variable \(\beta\) in \eqref{eq:tpc48-two-dimensional-load} is
free.  The theorem does not give a second moment for the one-variable
channel count at a fixed orbit frequency, for
\(R_L(\alpha;\cM)\), or for the literal source-mask coefficient.
Nor may one insert an additional independent restriction
\(\beta\in\cC_q\) and retain the same formula without a new
calculation.  The exact two-dimensional moments are an incidence
ledger, not an arithmetic cancellation theorem.
\end{remark}

\subsection{The conserved phase-space product}

TPC--47 used \(L_{47}=X^{\nu-\kappa+o(1)}\) bands at its mesoscopic
resolution.  The corresponding dense coarse-edge load was
\begin{equation}
 \frac M{L_{47}}
 =X^{\mu-\nu+\kappa+o(1)}
 =X^{27/80+o(1)},
 \label{eq:tpc48-tpc47-load}
\end{equation}
and the product satisfied
\begin{equation}
 L_{47}\frac M{L_{47}}=M.
 \label{eq:tpc48-tpc47-phase-product}
\end{equation}
At the present critical resolution,
\begin{equation}
 L\frac ML=M
 \label{eq:tpc48-critical-phase-product}
\end{equation}
as well.  The additional factor \(X^\kappa\) in \(L\) removes the
mesoscopic \(\kappa\)-loss from the resolved channel load and restores
the exact \(X^{-1}\) tube scale, but it cannot remove the intrinsic
\(M/J=X^{\mu-\nu}\) density of source slopes per critical cell.

There are therefore two complementary sharpness statements:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item arbitrary independent orbit inputs recover the full factor
       \(K\) after channel collapse, by
       \cref{thm:tpc48-unrestricted-barrier};
 \item common-profile inputs have the smaller factor \(D_J(t;K)\),
       and consecutive slope clusters attain it up to constants, by
       \cref{prop:tpc48-large-sieve-sharpness}.
\end{enumerate}
Each inherited projective layer lies inside the second class.  The
fully reassembled coefficient is instead a signed projective integral
controlled through \(\mathfrak S_{\mathscr R}\); no theorem in this
paper says that it either saturates or improves the common-profile
frontier.
