\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\E}{\mathbb E}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\cA}{\mathcal A}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cP}{\mathcal P}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\one}{\mathbf 1}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\sfk}{\operatorname{sf}}

\hypersetup{
  pdftitle={Annealed Multiplicative Closure at the Four-Mobius Gate: Prime-Sign Orthogonality, Product-Fiber Rigidity, and the Deterministic Walsh Corner},
  pdfauthor={Liang Wang},
  pdfsubject={Exact random-multiplicative diagonalization and Walsh compression of the triple-prime Mobius endpoint},
  pdfkeywords={Mobius correlation, random multiplicative function, Rademacher signs, Walsh spectrum, Hilbert energy, parity boundary}
}

\title{\bfseries Annealed Multiplicative Closure at the Four--M\"obius Gate:\\
Prime--Sign Orthogonality, Product--Fiber Rigidity,\\
and the Deterministic Walsh Corner}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
TPC--42 reduced the surviving triple--prime endpoint to a coherent
orbit--slope energy containing one source and one target M\"obius value
per row.  We deform all of those values by one common prime--sign field,
rather than attaching independent row phases.  For the zero alias, the
source divisor and target affine value fuse into a squarefree integer
label.  The inherited scale separation $D=o(J)$ makes these labels
injective across physical rows, and prime--sign orthogonality then makes
the complete left--plus--right Hilbert energy equal its atomic diagonal
in expectation, with no projective separation.  For the full alias trace,
the corresponding squarefree--kernel fibers have only $X^{o(1)}$
multiplicity; hence the annealed trace is still at the endpoint diagonal
scale.  Boolean hypercontractivity gives fixed high moments, and, for
each fixed prescribed dyadic packet sequence, almost every global random
multiplicative field closes every sufficiently large packet.  At the
distinguished all--minus prime corner the random
model is exactly the M\"obius function.  We give an exact Walsh expansion
there: every four--M\"obius cross row collapses to one M\"obius value of a
squarefree symmetric--difference kernel.  A sharp Walsh example shows
that annealed diagonalization alone cannot control this specified corner.
Thus the declared randomized multiplicative terminal model is closed,
while the remaining
deterministic problem is an explicit corner de--randomization theorem,
not a claim of four--M\"obius cancellation or a breach of sieve parity.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; random multiplicative
function; Rademacher prime signs; product fiber; Walsh spectrum; Hilbert
energy; triple--prime endpoint; parity boundary.

\medskip
\noindent\textbf{Convention.}
All complex inner products are linear in the first argument.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11K65; Secondary 42C10,
60E15, 11N36.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/prime-sign-model}
\input{sections/product-fiber-geometry}
\input{sections/annealed-trace}
\input{sections/zero-alias-rigidity}
\input{sections/hypercontractive-moments}
\input{sections/walsh-corner}
\input{sections/sharp-boundaries}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\small
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
