\begin{abstract}
The cross-key erasure analysis at one fixed nonzero shift reduces the first
genuinely signed native coefficient to a primitive cofactor-plane sum
\[
 \sum_{\substack{u\le U,\ v\le V\\(u,v)=1}}
 \mu(u)\mu(v)K(u,v),
\]
after complete native masks, prime-line fibers, and literal complex
amplitudes have been retained in \(K\).  The sign is frozen along each
prime-line parameter, so cancellation, if present, must occur across the
\((u,v)\)-plane.

We give an exact analytic certificate for this plane.  First,
\[
 \one_{(u,v)=1}\mu(u)\mu(v)=\mu(uv).
\]
M\"obius inversion of the coprimality condition then yields the diagonal
divisor lift
\[
 \sum_{d\ge1}\mu(d)
 \sum_{\substack{a,b\ge1\\(a,d)=(b,d)=1}}
 \mu(a)\mu(b)K(da,db).
\]
For
\[
 M_d(x)=\sum_{\substack{n\le x\\(n,d)=1}}\mu(n),
\]
two-dimensional Abel summation converts the \(d\)-term exactly into
\[
 \sum_{x,y}M_d(x)M_d(y)
 \Delta_{12}K^{[d]}(x,y).
\]
Consequently, truncation at \(d\le D\) is controlled by restricted Mertens
envelopes times zero-extended mixed variation, while the remaining diagonal
tail is at most \(\|K\|_\infty UV/D\).

The prime number theorem implies \(M_d(x)=o(x)\) for every fixed \(d\).
It follows unconditionally that kernel families satisfying
\(\cV_\square(K^{[d]})=O_d(\|K\|_\infty)\) for every fixed \(d\)
have \(o(\|K\|_\infty UV)\) cancellation.  In particular, the unweighted
primitive rectangle cancels.
We also prove projective bounded-variation and Banach-valued versions.

For the literal fixed-shift carrier, the excluded same-residual direction
is one primitive-plane site and is already absent from the erasure kernel.
The exact plane certificate bounds each anchored
cross-key rectangle sum and hence the linear mixed trace
\(\operatorname{tr}(ER)\).  It is not an entrywise bound for the erasure
operator.  What remains unproved is stated without compression:
mass-normalized variation for the actual prime-line kernel, a small diagonal
tail at the physical scale, summability over the growing anchor family, an
operator-level bridge, and the represented/missing shorted reassembly.
Sign-selected hard masks show that bounded amplitude alone cannot replace
these hypotheses.  Thus the paper proves a regular-kernel cancellation
theorem and isolates, but does not claim to solve, the fixed-shift parity
interface.
\end{abstract}
