\section{Claim ledger and next decisions}
\label{sec:claim-ledger}

\subsection{What is proved}

\paragraph{L0: finite and analytic statements.}
The following results are unconditional:
\begin{itemize}
 \item the primitive sign collapse
 \(\one_{(u,v)=1}\mu(u)\mu(v)=\mu(uv)\);
 \item the exact diagonal divisor lift
 \eqref{eq:exact-diagonal-lift};
 \item the zero-extended two-dimensional Abel identity
 \eqref{eq:double-abel};
 \item fixed-\(d\) restricted Mertens cancellation from the prime number
 theorem;
 \item the exact master certificate
 \eqref{eq:master-certificate} and ambient tail
 \eqref{eq:ambient-tail};
 \item the anisotropic one-direction certificates and the exact
 boundary/interior/short-ray decomposition;
 \item unconditional \(o(UV)\) cancellation for kernels whose fixed-d
 mixed variation is \(O_d(\|K\|_\infty)\); and
 \item the projective-BV and Banach-valued certificates.
\end{itemize}

\paragraph{L1: fixed-shift identification.}
On the complete squarefree physical carrier inherited from TPC--70,
\eqref{eq:physical-plane-coefficient} identifies every anchored cross-key
rectangle sum \(\mathfrak X_{\mathfrak a}\) with the primitive-plane
transform of the complete aggregate kernel \(K^\circ_{\mathfrak a}\).
Their exact sum gives \(\operatorname{tr}(ER)\).  The common erasure
content \(q\) is sign-free, the sign is frozen on every affine time ray,
and the same-residual direction is one excluded primitive-plane site,
already zero in the literal erasure kernel.
Combining this L1 dictionary with the L0 analytic theorem gives the
anchored and global mixed-trace majorants
\eqref{eq:literal-anchor-certificate}--%
\eqref{eq:linear-sector-plane-certificate}.

\subsection{What remains L2-open}

No theorem in this paper proves:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item bounded or saving mixed variation for the actual prime-line kernel;
 \item a diagonal tail small relative to actual atomic mass;
 \item uniform restricted-Mertens input for a growing divisor cutoff;
 \item summability of anchored certificates at the physical trace scale;
 \item a direct-entry, row-local, or growing-moment bridge from the
 anchored trace problem to an operator bound;
 \item control of the same-residual part of the native defect;
 \item a fixed-power missing-mass saving;
 \item the represented activated-range lower frame;
 \item a small nuisance shorting penalty; or
 \item the boundary and tail estimates needed for the final physical
 implication.
\end{enumerate}

\subsection{Endpoint ledger}

Any future composition must use one denominator-compatible ledger.  A
schematic safe form is
\[
 \Lambda_{\rm tot}
 =
 \lambda_{\rm sel}+\lambda_{\rm occ}+\lambda_{\rm blk}
 +\lambda_{\rm term}^{\rm eff}
 +\lambda_{\rm sing}+\lambda_H+\lambda_{\rm aff}
 +\lambda_{\rm reasm}+\lambda_{\rm bdry}+\lambda_{\rm tail}
 <\frac1{400}.
\]
The effective terminal loss already contains whichever inflation or
capacity route is used; it must not be charged twice.  Subpower divisor
counts and a bounded number of exact relabelings cost zero exponent, but
any polynomial variation, row-aggregation, or tail loss must be entered
literally.  Equality at \(1/400\) is failure for the strict endpoint.

\subsection{Next-step decision tree}

The present paper leaves four testable branches.
\begin{enumerate}[label=\textup{(\Roman*)}]
 \item \textbf{Direct physical variation.}  Compute
 \(\Delta_{12}(K^\circ_{\mathfrak a})^{[d]}\) from the literal ray masks.
 If the
 jumps telescope or are confined to a small boundary, feed the resulting
 majorant into \eqref{eq:trace-plane-certificate}.
 \item \textbf{Smooth plus discrepancy.}  Decompose
 \[
 K^\circ=K_{\rm reg}+K_{\rm rough}.
 \]
 Apply the proved theorem to \(K_{\rm reg}\), and formulate a separate
 arithmetic discrepancy estimate for \(K_{\rm rough}\).  Both parts must
 retain the actual normalization.
 \item \textbf{Trace-to-operator bridge.}  Construct either a direct
 two-corner primitive kernel for entries of \(E\), a row-local anchor
 certificate, or a complete growing-moment estimate.  A small global
 \(\operatorname{tr}(ER)\) is not enough.
 \item \textbf{Certificate failure.}  If actual mixed variation is too
 large, record the exact offending masks and abandon this certificate.
 Possible alternatives include a direct affine-correlation estimate,
 a multi-modulus dispersion, or a growing-moment route.  Failure of the
 BV certificate is not a no-cancellation theorem.
\end{enumerate}

\subsection{No endpoint claim}

The paper does not specialize \(h_0\) to \(2\), does not improve a
fixed-shift parity estimate, and proves no prime-pair lower bound.  In
particular, it does not prove or imply the twin-prime conjecture.  The
genuine advance is narrower: the paper identifies an unconditionally
cancellative regular comparison class and the explicit physical variation,
tail, anchor-summability, and trace-to-operator gates needed to connect the
literal kernel to that class.
