\section{Introduction}
\label{sec:introduction}

The signed missing-native route separates two questions which are often
blurred.  The first is algebraic: after a residual label is erased, where
does a nontrivial M\"obius sign actually survive?  TPC--68 shows that
same-residual collisions freeze the target signs
\citep{WangTPC68}.  TPC--69 then expands the residual and erasure operators
in noncommutative words and proves that the complete two-erasure sector in
every even moment is nonnegative \citep{WangTPC69}.  The first useful signed
door is therefore the linear erasure sector or a higher, genuinely mixed
sector.

TPC--70 opens the linear sector at the level of one two-key rectangle
\citep{WangTPC70}.  Its primitive coordinates have two decisive features.
The common contents belong to divisor sets determined by
\(H=h_0(n-m)\), while the remaining erasure direction is a coprime pair
\((u,v)\).  More importantly, the surviving sign
\[
 \mu(a)\mu(b)\mu(u)\mu(v)
\]
is constant along the affine time parameter of each prime ray.  There is no
time-randomness left to average on that ray.  Any cancellation must join
different primitive directions.

The present paper asks the next narrow question:

\begin{quote}
\emph{Which deterministic regularity of the exact primitive-plane kernel is
sufficient to force cancellation, using only the prime number theorem?}
\end{quote}

The answer begins with a small identity that changes the geometry of the
problem:
\[
 \one_{(u,v)=1}\mu(u)\mu(v)=\mu(uv).
\]
The apparently rough coprimality boundary can be opened by a diagonal
divisor lift.  At each fixed divisor \(d\), the resulting signs separate
again into two copies of the M\"obius function restricted to integers
coprime to \(d\).  Two-dimensional Abel summation then transfers all
cancellation into their partial sums and all geometric irregularity into
the mixed variation of the dilated kernel.

\subsection{Main results}

Let \(K\) be supported on
\([1,U]\times[1,V]\).  Write
\[
 K^{[d]}(a,b)=K(da,db)
\]
and extend it by zero outside its finite rectangle.  If
\[
 \cV_\square(K^{[d]})
 =
 \sum_{a,b\ge1}
 \left|
 K^{[d]}(a,b)-K^{[d]}(a+1,b)-K^{[d]}(a,b+1)
 +K^{[d]}(a+1,b+1)
 \right|,
\]
and define
\[
 \mathfrak M_d(X)=
 \max_{1\le x\le X}
 \left|\sum_{\substack{n\le x\\(n,d)=1}}\mu(n)\right|,
 \qquad
 \cT_D(K)\le \|K\|_\infty UV/D.
\]
Then the exact master bound proved below is
\begin{align}
\left|
\sum_{\substack{u\le U,\ v\le V\\(u,v)=1}}
\mu(u)\mu(v)K(u,v)
\right|
\le{}&
\sum_{d\le D}
\mathfrak M_d(U/d)\mathfrak M_d(V/d)
\cV_\square(K^{[d]})
\notag\\
&+\cT_D(K),
\label{eq:intro-master}
\end{align}
The formula before absolute values is exact.

For fixed \(d\), the prime number theorem gives
\(\mathfrak M_d(X)=o(X)\).  Hence if
\[
 \cV_\square(K^{[d]})\ll_d\|K\|_\infty
\]
for every fixed \(d\), then the left side of
\eqref{eq:intro-master} is
\[
 o(\|K\|_\infty UV)
\]
as \(\min(U,V)\to\infty\).  This includes constant rectangles,
finite projective sums of one-dimensional bounded-variation weights, and
smooth rescaled kernels with uniformly bounded rectangular variation.

The result is deliberately normalized by ambient area.  The physical
prime-line kernel may be sparse, and its relevant denominator is an actual
anchored rectangle mass rather than \(\|K\|_\infty UV\).  We therefore retain
the right side of \eqref{eq:intro-master} as a literal majorant for each
anchored sum and then sum those majorants in the exact trace formula.  This
produces three explicit arithmetic gates:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item a mixed-variation bound after every low diagonal dilation;
 \item a diagonal-divisor tail small relative to actual physical mass; and
 \item summability over the growing row-and-anchor family at the physical
 trace scale.
\end{enumerate}
None is silently identified with the smooth-kernel corollary.
Moreover, a small mixed trace is not an operator bound.  An entrywise,
row-local, or growing-moment bridge remains a separate theorem.

\subsection{What this does not prove}

The exact physical kernel contains prime-line solvability, terminal masks,
native-key coincidences, finite endpoints, and complex amplitudes.  Those
features can create many jumps in \((u,v)\).  We do not prove that its mixed
variation is bounded, or even smaller than its actual mass by a power.  We
also do not replace a row-pair estimate by a uniform operator estimate.
Existing fixed-form and averaged Chowla technology does not automatically
provide those missing interfaces; the coefficient and averaging mismatch
was audited in TPC--33 \citep{WangTPC33}.

Accordingly, the paper proves no fixed-\(2\) estimate, no parity-breaking
statement, and no prime-pair or twin-prime theorem.  Its contribution is a
positive theorem for regular primitive-plane kernels and an exact,
falsifiable certificate for the irregular physical kernel.

\subsection{Organization}

\Cref{sec:primitive-interface} records the literal plane inherited from
TPC--70.  \Cref{sec:divisor-lift} proves the coprimality collapse and
diagonal lift.  \Cref{sec:double-abel} gives the exact Abel identity and
restricted Mertens input.  \Cref{sec:master-certificate} proves the master
truncation theorem.  \Cref{sec:smooth-kernels} develops unconditional
regular-kernel consequences.  \Cref{sec:physical-gate} transfers the bound
back to anchored and global mixed-trace certificates.  Countermodels and the
literature boundary follow before the final L0/L1/L2 ledger.
