\section{Relation to existing M\"obius-correlation results}
\label{sec:literature-boundary}

The present theorem uses only one-variable Mertens cancellation after a
full two-dimensional average and a diagonal divisor lift.  It should not
be confused with a theorem for a prescribed pair of affine forms.

For fixed nonproportional affine forms, logarithmically averaged two-point
Chowla is known \citep{Tao2016LogChowla}.  Averaged unweighted results are
also available when an additional shift or coefficient is averaged
\citep{MatomakiRadziwillTao2015}.  Those theorems are powerful but do not
directly control the literal kernel here, whose coefficients can grow with
the physical scale and whose prime-line and native-key masks select a
restricted subset of the cofactor plane.

TPC--33 records the detailed mismatch \citep{WangTPC33}.  The unresolved
physical requirements include:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item growing affine coefficients and row-dependent primitive coordinates;
 \item a fixed dyadic physical shell rather than only logarithmic averaging;
 \item complete prime-line, endpoint, and native-key masks;
 \item actual complex weights and row normalization;
 \item uniformity over all active row pairs; and
 \item an operator-scale saving compatible with the endpoint ledger.
\end{enumerate}

\Cref{thm:regular-kernel-cancellation} avoids the fixed-form Chowla barrier
because it assumes regularity in two independent cofactor directions.
If the kernel collapses onto a thin prescribed affine graph, its
zero-extended mixed variation can be as large as its length, and the theorem
does not manufacture a saving.  This is the correct behavior: the family
of prescribed affine directions contains open two-point M\"obius
correlations.

The classical parity obstruction for sieve methods remains relevant
\citep{HeathBrown1982Parity}.  The divisor lift is not a parity-breaking
sieve.  It is an exact reindexing followed by prime-number-theorem
cancellation under a deterministic regularity hypothesis.  Whether the
literal physical kernel satisfies that hypothesis is precisely the new
arithmetic gate.
