\section{Return to the fixed-shift mixed trace}
\label{sec:physical-gate}

We now apply the deterministic theorem to the exact anchored kernel in
\eqref{eq:physical-plane-coefficient}.  This section states certificates,
not estimates for the physical kernel.  The object being bounded is kept
explicit: it is an anchored four-corner scalar contributing to
\(\operatorname{tr}(ER)\), not a two-corner matrix entry of \(E\).

\subsection{One same-residual anchor}

Assume that \(K^\circ_{\mathfrak a}\) is supported on
\([1,U_{\mathfrak a}]\times[1,V_{\mathfrak a}]\).  Define
\begin{align}
 \cB_{\mathfrak a}(D)
 ={}&
 \sum_{d\le D}
 \mathfrak M_d(U_{\mathfrak a}/d)
 \mathfrak M_d(V_{\mathfrak a}/d)
 \cV_\square\bigl((K^\circ_{\mathfrak a})^{[d]}\bigr)
\notag\\
 &+\cT_D(K^\circ_{\mathfrak a}).
\label{eq:physical-anchor-majorant}
\end{align}

\begin{proposition}[Literal anchored certificate]
\label{prop:literal-anchor-certificate}
For every \(D\ge1\),
\begin{equation}
 \boxed{
 |\mathfrak X_{\mathfrak a}|
 \le
 \cB_{\mathfrak a}(D).}
\label{eq:literal-anchor-certificate}
\end{equation}
For the literal erasure kernel the excluded site is already zero.  If an
enlarged bookkeeping kernel is used, removing that site changes only the
\(d=1\) variation, by at most
\(4|\widehat K_{\mathfrak a}(b,a)|\).
\end{proposition}

\begin{proof}
The prefactor \(\mu(a)\mu(b)\) in
\eqref{eq:physical-plane-coefficient} has modulus one.  Apply
\cref{thm:master-certificate} and then
\cref{lem:anchor-diagonal-visibility}.
\end{proof}

\subsection{The exact global trace certificate}

\begin{corollary}[Linear mixed-sector majorant]
\label{cor:linear-mixed-sector-majorant}
For every choice of anchorwise cutoffs \(D_{\mathfrak a}\ge1\),
\begin{align}
 |\operatorname{tr}(ER)|
 &\le
 2\sum_{m<n}
 \sum_{\mathfrak a\in\cR_{m,n}}
 \cB_{\mathfrak a}(D_{\mathfrak a}),
\label{eq:trace-plane-certificate}\\
 |S_{2,1}|
 &\le
 4\sum_{m<n}
 \sum_{\mathfrak a\in\cR_{m,n}}
 \cB_{\mathfrak a}(D_{\mathfrak a}),
\label{eq:linear-sector-plane-certificate}
\end{align}
where \(S_{2,1}=2\operatorname{tr}(ER)\) is the full linear erasure
coefficient in \(\operatorname{tr}(R+tE)^2\).
\end{corollary}

\begin{proof}
Use the exact anchor expansion
\eqref{eq:trace-by-primitive-anchors}, the triangle inequality, and
\cref{prop:literal-anchor-certificate}.  The second formula uses the
definition of \(S_{2,1}\).
\end{proof}

\begin{remark}[Normalization is already present]
Every \(K_{\mathfrak a,q}\) is built from a four-corner amplitude divided
by \(W_mW_n\).  No further factor
\(\sqrt{W_mW_n}\) is introduced in
\eqref{eq:physical-anchor-majorant}.  Doing so would double-normalize the
rectangle scalar and would not turn it into an entry of \(E\).
\end{remark}

\subsection{The three trace-level physical gates}

\Cref{cor:linear-mixed-sector-majorant} separates the remaining work at
the level it actually controls.

\paragraph{Gate A: low-diagonal variation.}
For every relevant anchor and every low \(d\), one must control
\[
 \cV_\square\bigl((K^\circ_{\mathfrak a})^{[d]}\bigr).
\]
The kernel contains the actual prime-ray incidence and every native mask.
Replacing it by a smooth envelope proves a theorem for the envelope, not
for the literal coefficient, unless the replacement error is separately
bounded.

\paragraph{Gate B: diagonal tail relative to actual anchored mass.}
The ambient estimate
\[
 \cT_D(K^\circ_{\mathfrak a})
 \le
 \|K^\circ_{\mathfrak a}\|_\infty
 U_{\mathfrak a}V_{\mathfrak a}/D
\]
may be too large for a sparse carrier.  It must be compared with an actual
anchored reference scale, for example
\[
 \cA_{\mathfrak a}
 =
 \sum_{u,v}|K^\circ_{\mathfrak a}(u,v)|,
\]
or directly within the global physical trace ledger.

\paragraph{Gate C: growing-anchor summability.}
A saving for every fixed anchor does not imply a saving after summing the
growing family
\[
 \bigcup_{m<n}\cR_{m,n}.
\]
One needs
\[
 \sum_{m<n}\sum_{\mathfrak a\in\cR_{m,n}}
 \cB_{\mathfrak a}(D_{\mathfrak a})
 =
 o(\cA_{\rm tr})
\]
at the declared trace reference scale \(\cA_{\rm tr}\).  Fixed-anchor
little-oh notation without uniform domination is insufficient.

\subsection{Boundary, long-ray interior, and short-ray tail}

The diagonal tail \(\cT_D\) should not be confused with the geometric
short-ray tail.  For each anchor, split the primitive support disjointly
into
\[
 \Omega_{\rm bd}\sqcup\Omega_{\rm int}\sqcup\Omega_{\rm short}.
\]
Here \(\Omega_{\rm bd}\) contains small \(u\) or small \(v\);
\(\Omega_{\rm int}\) contains cells on which both cofactor coordinates
grow and the affine ray has many admissible time positions; and
\(\Omega_{\rm short}\) contains directions whose ray length is \(O(1)\).
Let the corresponding zero-extended kernels be
\[
 K_{\rm bd},\qquad K_{\rm int},\qquad K_{\rm short}.
\]
Then the exact triangle decomposition gives
\begin{equation}
 |\cS(K^\circ_{\mathfrak a})|
 \le
 \|K_{\rm bd}\|_{\ell^1}
 +\|K_{\rm short}\|_{\ell^1}
 +\cB_D(K_{\rm int}).
\label{eq:boundary-interior-short}
\end{equation}
Thus a sufficient anchored closure consists of
\[
 \|K_{\rm bd}\|_{\ell^1}
 +\|K_{\rm short}\|_{\ell^1}
 =o(\cA_{\mathfrak a})
\]
together with a mass-normalized variation--tail certificate for the
interior.  Having only one time point on each short ray does not make the
sum over all such directions small; its literal total mass must be
estimated.

If only one of \(u,v\) is large in an intermediate sector, the anisotropic
certificate \cref{prop:anisotropic-certificate} can be applied instead of
discarding the sector.  Its one-direction variation must still be verified
for the complete hard mask.

\subsection{Why the \texorpdfstring{\(q\)}{q}-sum is not a fourth sign source}

The common erasure content \(q\mid |H|\) disappears from
\eqref{eq:frozen-primitive-sign}.  It remains inside
\(K_{\mathfrak a,q}\) through ray geometry and weights.  Therefore:
\begin{itemize}
 \item cancellation among \(q\)-slices can occur only through their literal
 complex amplitudes;
 \item applying the triangle inequality before
 \eqref{eq:aggregate-q-kernel} may lose that cancellation; and
 \item the divisor bound \(\tau(|H|)=|H|^{o(1)}\) controls only
 multiplicity, not M\"obius parity.
\end{itemize}

\subsection{The trace-to-operator bridge is open}

A small value of \(\operatorname{tr}(ER)\) is not a norm bound for \(E\),
for \(R+E\), or for the missing-native Gram.  Global cancellation among
anchors can coexist with large row-local defects.  In particular,
\cref{prop:literal-anchor-certificate} gives no entrywise domination of
\(E\), so the star and Perron certificates of TPC--68 cannot be invoked
directly.

An operator-level continuation needs at least one genuinely new bridge:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item a direct primitive reindexing of the two-corner entries \(E_{m,n}\);
 \item row-local anchored sums that dominate the relevant stars;
 \item or uniform control of complete growing mixed moments, without
 reducing them to the single global trace.
\end{enumerate}
This is an L2 interface, not a consequence of two-dimensional Abel
summation.

\subsection{Reassembly remains separate}

Even an operator-level missing-native bound would control only one branch.
The same-residual defect, total missing mass, represented lower frame, and
the nuisance shorting term remain separate.  In the full reassembly notation
of TPC--68,
\[
 G_{\rm sh}=G_{\rm dir}-C_N.
\]
No plane estimate implies \(\|C_N\|=o(1)\), and no missing-native estimate
supplies the represented lower bound.  These arrows must be verified on
the same carrier and with the same normalization.
