\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Four-Channel Compression in a Primitive Mobius Tail: Centered Divisor Kernels, a Single-Leg Completion Wedge, and CRT-Fiber Discrepancy},
 pdfauthor={Liang Wang},
 pdfsubject={Exact matched Fourier compression of the primitive residual-dispersion gate},
 pdfkeywords={Mobius tail, Ramanujan model, centered divisor kernel, CRT fibers, Poisson summation, Kloosterman fractions, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{Conditional input}{Conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\ee}[1]{\exp(2\pi i #1)}
\newcommand{\eql}[2]{e_{#1}\!\left(#2\right)}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cV}{\mathcal V}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Four-Channel Compression in a Primitive M\"obius Tail:}\\
\textbf{Centered Divisor Kernels, a Single-Leg Completion Wedge,}\\
\textbf{and CRT-Fiber Discrepancy}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC-19 shows that the primitive residual correlation left by TPC-18
cannot be estimated by centering the prime--prime, prime--model, model--prime,
and model--model channels separately.  We give the missing common
algebraic reduction and then sharpen its long-period spectral gate.

Let \(P_m\) and \(M_m\) be the locally calibrated prime and finite
Ramanujan-model signals on a primitive affine row \(mj+h\), put
\(H=\rad|h|\), and set \(Z_m=P_m-M_m\).  For a finite target horizon
\(U\), we prove the
pointwise identity
\[
 Z_m(j)=\eps_U(m)+
 \sum_{\substack{u\le U\\(u,mH)=1}}
 b_R(u)\left(\one_{u\mid mj+h}-\frac1u\right),
 \qquad b_R(u)=-\mu(u)w_R(u),
\]
where \(w_R(u)>0\) is explicit.  A uniform M\"obius calibration
theorem gives \(\eps_U(m)\ll_A \rho_{P,H}(m)(\log U)^{-A}\) throughout
every fixed polynomial row range.  Thus the full
\(PP-PM-MP+MM\) product has one coefficient and one centered divisor
kernel, up to an arbitrarily logarithmically small scalar defect.  Its
primitive-conditional centered-kernel \((u,v)\)-zero mode is
\[
 \frac{b_R(u)b_R(v)}{uv}
 \bigl((u,v)\one_{(u,v)\mid m_1-m_2}-1\bigr),
\]
so the zero mode of every coprime divisor pair vanishes termwise in the
matched channel.

For \(g=(u,v)\), \(u=ga\), \(v=gb\), and
\(l=[u,v]=gab\), we compute every Fourier coefficient of the primitive
centered kernel on its true period \(Hl\).  When
the two divisor congruences are compatible, all four phases align and
the coefficient contains the exact multiplier
\[
 B_{g,a,b}(r)=g-\one_{b\mid r}-\one_{a\mid r}+\one_{l\mid r}.
\]
This yields a two-scale Poisson theorem.  If
\(H\max(u,v)\le JX^{-\eta}\), the two single-indicator spectra and the
constant spectrum complete with arbitrary power accuracy even when
the joint period \(Hl\) is long.  For all \(u,v\le R=X^{1/2-\delta}\),
the strict-margin range in which every single and constant spectrum
completes is
\(Q\le X^{1/2+\delta-\eta_0}\), substantially wider than the
\(Q\le X^{2\delta-\eta_0}\) range obtained by completing the whole
joint period at once.  In the genuinely remaining low-frequency
joint packet, however, \(B_{g,a,b}(r)=g\); centering supplies no further
nonzero-frequency cancellation.

Finally, compatible row pairs are aggregated by their joint CRT class
\(\kappa\bmod l\).  The three inverse phases of TPC-19 compress exactly
to the ordinary finite Fourier transform of a single fiber vector
\(Z_l(\kappa)\).  Splitting that vector into its unit-class mean and
discrepancy produces an explicit Ramanujan bias and an exact Parseval
identity for the fiber variance.  For this chosen compatible
short--short packet, the remaining inputs are a bound for the explicit
Ramanujan mean and a quantitative estimate for this modulus-dependent
fiber discrepancy, or a norm-controlled low-rank substitute.  The cited
large-sieve and Kloosterman-fraction theorems do not automatically
provide those inputs for the sharp M\"obius row weights, and the
large-divisor legs remain outside this reduction.  No residual-dispersion estimate,
fixed-shift Hardy--Littlewood asymptotic, twin-prime theorem, or breach
of sieve parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius tail; centered divisor kernel;
determinant spectrum; Chinese remainder theorem; Poisson summation;
CRT fibers; Ramanujan sums; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11N05, 11L07, 11L20.

\input{sections/introduction}
\input{sections/interface}
\input{sections/matched-recombination}
\input{sections/uniform-calibration}
\input{sections/kernel-fourier}
\input{sections/single-leg-completion}
\input{sections/fiber-compression}
\input{sections/technology-boundary}
\input{sections/certificate-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
