\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Factor-Ray Dephasing of a Prime-Target Residual: A Hyperbolic Mellin Large Sieve, Averaged-Shift Energy, and the Intra-Ray Boundary},
 pdfauthor={Liang Wang},
 pdfsubject={Continuous Mellin energy laws and exact arithmetic boundaries for a prime-target residual},
 pdfkeywords={Mellin mean square, Montgomery--Vaughan inequality, shifted primes, Selberg sieve, factor rays, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cE}{\mathcal E}
\newcommand{\cI}{\mathcal I}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\arsinh}{\operatorname{arsinh}}

\title{\textbf{Factor-Ray Dephasing of a Prime-Target Residual:}\\
\textbf{A Hyperbolic Mellin Large Sieve, Averaged-Shift Energy,}\\
\textbf{and the Intra-Ray Boundary}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Put $u(n)=\Lambda(n)-1$, fix a real-valued
$W\in C_c^1((0,\infty))$, and consider the large-source-factor transform
\[
 \cT_{h,D}(X;t)=
 \sum_{\substack{n>D\\m\geq1}}
 u(n)\Lambda(mn+h)W(mn/X)(n/m)^{it}.
\]
The target-free form $\cM_D$, obtained by replacing $\Lambda(mn+h)$ by
$1$, is the first-moment model under a long smooth average of the shift.
We study the centered transform $\cR_{h,D}=\cT_{h,D}-\cM_D$.

Writing uniquely $n=ak$, $m=bk$, $(a,b)=1$, compresses every equal-ratio
class into a primitive factor ray.  The resulting frequencies
$\log(a/b)$ have spacing at least
\[
 \delta_X=2\arsinh\!\left(\frac{1}{2\beta X}\right)
\]
when $\supp W\subset[\alpha,\beta]$.  The generalized Hilbert inequality
of Montgomery and Vaughan therefore gives, for every fixed shift and every
$T\geq1$,
\[
 \int_{-T}^{T}|\cR_{h,D}(X;t)|^2dt
 =2T\cE_{h,D}(X)+O_W(X\cE_{h,D}(X)),
\]
where $\cE_{h,D}$ is the exact squared ray energy.  A raywise Cauchy
ledger proves $\cE_{h,D}\ll X(\log X)^4$.  Consequently every prescribed
fixed integer shift has mean-square $o(X^2)$ per Mellin
frequency on bands whose length grows faster than $(\log X)^4$.  This is
frequency-density cancellation, not a fixed-frequency asymptotic.
With a normalized Fej\'er kernel, distinct rays are removed exactly once
$T\delta_X\geq1$.

The ray energy itself becomes arithmetically evaluable after squaring first
and then averaging the shift.  For nonnegative
$G\in C_c^1((0,\infty))$, $X\leq H\leq X^C$, and
$1\leq D\leq X^{1-\eps}$, we prove
\begin{align*}
 \sum_hG(h/H)\cE_{h,D}(X)
 ={}&\frac12HX I_0(G)I_2(W)\log H\\
 &\times\bigl((\log X)^2-(\log D)^2\bigr)\\
 &+O\!\left(HX(\log X)^2\log\log(3X)\right).
\end{align*}
The diagonal $\Lambda^2$ term supplies the extra logarithm.  Every
same-ray off-diagonal target correlation is handled only by a two-linear-
forms Selberg upper sieve and an explicit $O(X\log^2X)$ source-ray ledger.
This yields a genuine hard-band asymptotic for $T/X\to\infty$ and an exact
Fej\'er-band asymptotic already at $T\asymp X$.

Finally, a determinant-layer formula identifies the unresolved
mesoscopic band, and a fixed smooth endpoint selector shows that an
$o(X^2)$ fixed-shift band error, together with a compatible filtered model
and $o(X)$ Fourier tails, would recover the $m=1$ Hardy--Littlewood
functional.  Equal-ratio compression never
separates the terms $\Lambda(abk^2+h)$ on one ray.  Thus no fixed-shift
prime-pair asymptotic, twin-prime lower bound, new level of distribution,
or breach of the parity barrier is claimed.
\end{abstract}

\noindent\textbf{Keywords:} prime-target residual; Mellin mean square;
Montgomery--Vaughan inequality; factor rays; averaged shifts; Selberg
upper-bound sieve; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N13, 11N36; Secondary 11M06,
42A05.

\input{sections/introduction-scope}
\input{sections/ray-geometry}
\input{sections/fixed-shift-dephasing}
\input{sections/averaged-ray-energy}
\input{sections/band-corollaries}
\input{sections/determinant-boundary}
\input{sections/endpoint-strength}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
