\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\E}{\mathbb E}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cF}{\mathcal F}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cU}{\mathcal U}
\newcommand{\one}{\mathbf 1}
\newcommand{\Pminus}{P^{-}}
\newcommand{\Pplus}{P^{+}}

\hypersetup{
  pdftitle={Large-Prime Cofactor Descent for a Four-Mobius Walsh Energy},
  pdfauthor={Liang Wang},
  pdfsubject={Actual-coefficient large-prime descent for the TPC equality packet},
  pdfkeywords={Mobius function, parity problem, large prime factor, Walsh spectrum, Gram matrix, determinant equation, Type II estimate}
}

\title{\bfseries Large--Prime Cofactor Descent\\
for a Four--M\"obius Walsh Energy}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The ``four--M\"obius gate'' is the nonnegative equality energy left
after expanding two source and two target M\"obius factors in a
fixed-shift prime-pair decomposition.  Earlier papers in the
twin-prime-correlation (TPC) sequence represented this energy as a
Walsh polynomial but left its deterministic all--minus corner
unresolved.  We study that corner for the actual labels
\(u=d(\ell d j+h)\).  If a prime in the global band
\(\sqrt{N_+}<p\le N_-/R\) divides a target, then
\(\ell d j+h=pr\) with \(r\ge R\), and setting its sign to \(-1\)
replaces \(u=p(dr)\) by \(dr\) exactly.  Equal descended labels have
maximal multiplicity
\(\rho_R\le X^{o(1)}(1+L_0/R)\); the actual multiplicity, rather than
this ambient upper bound, is the exact squared norm of the grouping
map.  Combining the descent with robust Walsh-face compression yields
an unconditional band/cutoff tradeoff.  In particular, the cutoff
\((\log X)^{501/500}\) survives while the physical band reaches
exponent \(55021/105000=0.5240095\ldots\), and the touched component
alone admits \((\log X)^{1003/1000}\).  At
\(y=X^{267/400+\eta}\), the complementary very-high-prime sector has
an exact affine Gram form; low-sign averaging gives a second, pure Gram
synthesis over equal residual labels.  The remaining collisions lie on
the fixed-determinant ladders \(rp-dj\ell=h\) and have coherent physical
M\"obius sign.  The closest dispersion and Kloosterman-fraction results
reviewed here do not supply the resulting fixed-\(h\), three-weight,
vector-valued interface.  No M\"obius cancellation estimate, parity
breach, prime-pair asymptotic, or twin-prime theorem is claimed.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; parity problem;
large prime factor; cofactor descent; Walsh spectrum; Gram synthesis;
determinant equation.

\medskip
\noindent\textbf{Convention.}
The shift \(h\ne0\) is fixed.  All packets and prime sets at one scale
are finite.  Constants may depend on the fixed dyadic supports and on
\(h\), but not on \(X\).  We use \(P^+(1)=1\) and
\(P^-(1)=+\infty\).

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N36; Secondary 42C10,
11L07, 60E15.

\input{sections/introduction}
\input{sections/actual-interface}
\input{sections/prime-incidence}
\input{sections/cofactor-descent}
\input{sections/balanced-compression}
\input{sections/residual-freezing}
\input{sections/affine-gram}
\input{sections/determinant-ladders}
\input{sections/sharp-boundaries}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
