\section{Conclusion and the next gate}
\label{sec:conclusion}

The present fixed-shift reduction has three rigorously separated layers.

First, the primitive shell admits a row-local prime density.  Below the
quarter scale, maximal Bombieri--Vinogradov controls every bounded
source-factor row mask after this centering.  The complete row-centered residual
still has coefficient $\delta_h$, equal to $1/6$ at $h=2$.  When
$\delta_hI_0(W)\ne0$, its logarithmic main term is not an artifact of using the
wrong mean; it is forced into the post-quarter aggregate.

Second, the finite Heath--Brown model realizes the local factors as an
actual translation spectrum.  Its rational eigenfrequencies are finite,
its autocorrelation is the truncated singular series, and it matches the
two prime--model cross terms required here through
Bombieri--Vinogradov.  Subtracting it removes the Hardy--Littlewood local
main term without assuming the Hardy--Littlewood conjecture.

Third, the Ramanujan residual is calibrated on the full
quotient-independent Type-I row ball used here, up to
$Q=X^{1/2-\delta}$.  Vaughan's identity therefore leaves one explicit
hard packet with both factor variables beyond the Type-I cutoff.  The
logical endpoint is exact:
\[
 \text{weighted Hardy--Littlewood at admissible even }h, I_0(W)\ne0
 \quad\Longleftrightarrow\quad
 \cB_{h,\delta}(X)=o(X).
\]
This equivalence is the result of the reduction, not an estimate asserted
by it.

The next analytic target is correspondingly narrow.  One may seek a
power- or logarithmic-saving estimate for dyadic pieces of
$\cB_{h,\delta}$ after retaining the Ramanujan subtraction, perhaps first
under an additional average over one factor, a sparse set of shifts, or a
restricted family of bilinear masks.  Any such theorem must be checked at
the natural $X$ scale and against the correct singular-series center.
Failure at that stage would itself locate which bilinear corridor or mask
class supports the obstruction.

No argument here proves a fixed-shift prime-pair asymptotic, a twin-prime
lower bound, a level of distribution beyond one half, or a breach of the
sieve parity barrier.  The advance is a sharper interface: the local
factor is explicit, the required Type-I row ball is closed at a prescribed
shift, and the remaining fixed-shift task is a single named bilinear residual
rather than an unspecified appeal to ``more cancellation.''
