\section{Fixed-shift closure of the full Type-I row ball}
\label{sec:fixed-typei-closure}

The model is useful because its complete-period mean agrees exactly with
the prime mean in every row whose modulus is visible at resolution $Q$.
For $F\in C_c^1((0,\infty))$, define
\begin{align}
 R_{m,h;Q}(X;F)
 &=\sum_{j\geq1}r_Q(mj+h)F(mj/X),
 \label{eq:ordinary-TypeI-row}\\
 R^{\log}_{m,h;Q}(X;F)
 &=\sum_{j\geq1}(\log j)r_Q(mj+h)F(mj/X).
 \label{eq:log-TypeI-row}
\end{align}

\begin{theorem}[Full bounded Type-I row masks]
\label{thm:full-bounded-TypeI-rows}
Fix $h\ne0$, $F\in C_c^1((0,\infty))$, and $\eta>0$.  Let
$M\leq Q$ and suppose
\begin{equation}
 Q\leq\frac{X^{1/2}}{(\log X)^{B}},
 \qquad
 MQ\leq X^{1-\eta}.
 \label{eq:TypeI-row-parameter-range}
\end{equation}
For every $A>0$, if $B=B(A,h,F,\eta)$ is sufficiently large, then
uniformly over all coefficient vectors $|\alpha_m|\leq1$,
\begin{align}
 \sup_{|\alpha_m|\leq1}
 \left|\sum_{m\leq M}\alpha_mR_{m,h;Q}(X;F)\right|
 &\ll_{A,h,F,\eta}X(\log X)^{-A},
 \label{eq:full-bounded-TypeI-row-closure}\\
 \sup_{|\alpha_m|\leq1}
 \left|\sum_{m\leq M}\alpha_mR^{\log}_{m,h;Q}(X;F)\right|
 &\ll_{A,h,F,\eta}X(\log X)^{-A}.
 \label{eq:full-bounded-log-TypeI-row-closure}
\end{align}
The masks may depend on $X,M,Q$ and on the source row $m$, but not on the
quotient $j$.
\end{theorem}

\begin{proof}
First assume $(m,h)=1$.  Maximal Bombieri--Vinogradov and smooth partial
summation give
\begin{align}
 \sum_{j\geq1}\Lambda(mj+h)F(mj/X)
 &=\frac X{\varphi(m)}I_0(F)+E_m,
 \label{eq:prime-TypeI-row-main}\\
 \sum_{m\leq M}|E_m|
 &\ll_{A,h,F}X(\log X)^{-A},
 \label{eq:prime-TypeI-row-BV-error}
\end{align}
after increasing the requested exponent.  On the other hand,
\cref{lem:HB-complete-row-mean,lem:HB-incomplete-row-error} give
\begin{equation}
 \sum_{j\geq1}\Lambda_Q(mj+h)F(mj/X)
 =\frac X{\varphi(m)}I_0(F)+E_m^{(Q)},
 \qquad
 |E_m^{(Q)}|\ll_FQ(\log(2Q))^2.
 \label{eq:model-TypeI-row-main}
\end{equation}
Thus the local main terms cancel row by row, not merely after the $m$ sum.

If $(m,h)>1$, the common local mean is zero.  A von Mangoldt value
$\Lambda(mj+h)$ forces $mj+h$ to be a power of one of the finitely many
primes dividing $h$.  Summed over all $m\leq M$, these exceptional rows
contribute $O_{h,F,\eps}(X^\eps)$: for each relevant prime power one counts
only divisors of a fixed integer.  The model rows still have mean zero by
\cref{lem:HB-complete-row-mean}, and
\[
 \sum_{j\geq1}\Lambda_Q(mj+h)F(mj/X)=E_m^{(Q)},
 \qquad |E_m^{(Q)}|\ll_FQ(\log(2Q))^2
\]
by \cref{lem:HB-incomplete-row-error}.

Taking the supremum over the masks is now harmless.  The preceding
reduced and nonreduced row estimates give
\begin{equation}
 \sup_{|\alpha_m|\leq1}
 \left|\sum_{m\leq M}\alpha_mR_{m,h;Q}(X;F)\right|
 \ll_A X(\log X)^{-A}+MQ(\log(2Q))^2+X^\eps.
 \label{eq:TypeI-row-two-errors}
\end{equation}
The last two terms are absorbed by the power saving in
\eqref{eq:TypeI-row-parameter-range}.

For the logarithmic row, partial summation in maximal
Bombieri--Vinogradov gives, when $(m,h)=1$,
\begin{align*}
 \sum_{j\geq1}(\log j)\Lambda(mj+h)F(mj/X)
 &={}
 \frac1{\varphi(m)}
 \int_0^\infty\log(t/m)F(t/X)\,dt+E_m^{\log},\\
 \sum_{m\leq M}|E_m^{\log}|
 &\ll_A X(\log X)^{-A}.
\end{align*}
This main term equals the one in \eqref{eq:HB-log-row-lattice-error},
because $\rho_h(m)/m=1/\varphi(m)$.  The prime part loses at most one
power of $\log X$ in obtaining the displayed error.  The model lattice error is
\eqref{eq:HB-log-row-lattice-error}; after summing over $m$ it is
$O(MQ(\log(2XQ))^3)$.  Again the fixed power $X^{-\eta}$ absorbs every
prescribed logarithmic factor.  On nonreduced rows, the same prime-power
argument as above costs only an additional factor $O(\log X)$, while the
model has zero mean and obeys the same logarithmic lattice bound.  This proves
\eqref{eq:full-bounded-log-TypeI-row-closure}.
\end{proof}

\begin{corollary}[The power-separated calibration]
\label{cor:power-separated-TypeI-calibration}
Fix $0<\delta<1/2$ and take
\begin{equation}
 Q=\lfloor X^{1/2-\delta}\rfloor.
 \label{eq:chosen-Q}
\end{equation}
Then \cref{thm:full-bounded-TypeI-rows} holds with
$M\leq Q$, since $MQ\leq Q^2\leq X^{1-2\delta}$.
\end{corollary}

This is a fixed-shift full dual-ball statement, but only in the row
variable.  Allowing a mask $\alpha_{m,j}$ that varies arbitrarily with the
quotient would permit it to inspect $mj+h$ and select the target primes.
Neither Bombieri--Vinogradov nor the theorem above permits that target-
adaptive operation.
