\section{Canonical scalar factorization and the directional defect}
\label{sec:tpc42-canonical}

We first isolate the finite-dimensional statement behind any attempted
scalar-to-Hilbert upgrade.  The result is independent of M\"obius
cancellation and makes the relevant quantifiers explicit.

Let \(\cA\) be a finite set of residue labels.  For every \(a\in\cA\),
let \(\cI_a\) be a nonempty finite fiber, and put
\begin{equation}
 \mathscr X=\bigoplus_{a\in\cA}\C^{\cI_a}.
 \label{eq:tpc42-fiber-domain}
\end{equation}
Choose a nonzero weight vector
\(w_a=(w_{a,i})_{i\in\cI_a}\) on each fiber.  Define the weighted scalar
collapse
\begin{equation}
 (P_wx)_a
 =\sum_{i\in\cI_a}x_{a,i}\overline{w_{a,i}},
 \qquad
 P_w:\mathscr X\longrightarrow\ell^2(\cA).
 \label{eq:tpc42-weighted-collapse}
\end{equation}
Let \(\Hh\) be a Hilbert space and let
\(G_{a,i}\in\Hh\).  The corresponding vector synthesis is
\begin{equation}
 T_Gx=\sum_{a\in\cA}\sum_{i\in\cI_a}x_{a,i}G_{a,i}.
 \label{eq:tpc42-vector-synthesis}
\end{equation}

The Moore--Penrose inverse and the orthogonal projection onto
\((\ker P_w)^\perp\) are explicit:
\begin{align}
 (P_w^\dagger z)_{a,i}
 &=\frac{z_aw_{a,i}}{\|w_a\|_2^2},
 \label{eq:tpc42-P-dagger}\\
 \Pi_w:=P_w^\dagger P_w,
 \qquad
 (\Pi_wx)_{a,i}
 &=\frac{w_{a,i}}{\|w_a\|_2^2}
   \sum_{j\in\cI_a}x_{a,j}\overline{w_{a,j}}.
 \label{eq:tpc42-P-projection}
\end{align}
Thus every synthesis has the canonical decomposition
\begin{equation}
 \boxed{
 T_G=(T_GP_w^\dagger)P_w+T_G(I-\Pi_w).}
 \label{eq:tpc42-canonical-splitting}
\end{equation}
The first term is visible to a scalar progression theorem.  The second
term is the directional defect: it acts on data whose weighted sum is
zero in every residue fiber.

\begin{theorem}[Exact scalar-factorization criterion]
\label{thm:tpc42-factorization-criterion}
The following statements are equivalent.
\begin{enumerate}[label=(\roman*)]
 \item There is a finite constant \(C\) such that
 \begin{equation}
  \|T_Gx\|_{\Hh}\le C\|P_wx\|_2
  \qquad(x\in\mathscr X).
  \label{eq:tpc42-black-box-lift}
 \end{equation}
 \item \(\ker P_w\subseteq\ker T_G\).
 \item The directional defect vanishes:
 \begin{equation}
  T_G(I-\Pi_w)=0.
  \label{eq:tpc42-defect-vanishes}
 \end{equation}
 \item There are vectors \(V_a\in\Hh\) such that
 \begin{equation}
  G_{a,i}=\overline{w_{a,i}}V_a
  \qquad(a\in\cA,\ i\in\cI_a).
  \label{eq:tpc42-fiber-synchronous-atoms}
 \end{equation}
\end{enumerate}
When these conditions hold,
\begin{equation}
 T_G=BP_w,
 \qquad
 Be_a=V_a,
 \qquad
 \inf C=\|B\|_{\op}=\|T_GP_w^\dagger\|_{\op}.
 \label{eq:tpc42-optimal-factor-constant}
\end{equation}
\end{theorem}

\begin{proof}
Inequality \eqref{eq:tpc42-black-box-lift} forces \(T_Gx=0\) whenever
\(P_wx=0\), proving (i)\(\Rightarrow\)(ii).  Since \(I-\Pi_w\) is the
orthogonal projection onto \(\ker P_w\), conditions (ii) and (iii) are
equivalent.  On a fixed fiber, (ii) says that the linear map
\begin{equation}
 (x_i)_{i\in\cI_a}\longmapsto\sum_i x_iG_{a,i}
 \label{eq:tpc42-one-fiber-map}
\end{equation}
vanishes on the kernel of
\(x\mapsto\sum_i x_i\overline{w_{a,i}}\).  A linear map with this kernel
property is a vector multiple of that scalar functional, which is exactly
\eqref{eq:tpc42-fiber-synchronous-atoms}.  Conversely,
\eqref{eq:tpc42-fiber-synchronous-atoms} gives
\begin{equation}
 T_Gx=\sum_a(P_wx)_aV_a=BP_wx.
 \label{eq:tpc42-factor-through-P}
\end{equation}
This proves all equivalences.  Because \(P_wP_w^\dagger=I\), every
factorization \(T_G=BP_w\) has \(B=T_GP_w^\dagger\); its operator norm is
the optimal constant.
\end{proof}

For the unweighted progression collapse, \(w_{a,i}=1\), the criterion
says that a universal scalar lift exists precisely when all Hilbert atoms
inside the same residue fiber are equal.  Pairwise orthogonality, proved
for the physical atoms in \cref{sec:tpc42-residue-orthogonality}, lies at
the opposite extreme.

\begin{corollary}[Sharp orthogonal-fiber defect]
\label{cor:tpc42-orthogonal-fiber-defect}
Fix one unweighted fiber \(\cI_a\) of cardinality \(\rho_a\), and suppose
that \((G_{a,i})_{i\in\cI_a}\) are pairwise orthogonal.  Their canonical
scalar-synchronous representative is
\begin{equation}
 \overline G_a=\frac1{\rho_a}\sum_{i\in\cI_a}G_{a,i}.
 \label{eq:tpc42-fiber-mean}
\end{equation}
Then
\begin{align}
 \sum_{i\in\cI_a}\|\overline G_a\|^2
 &=\frac1{\rho_a}
   \sum_{i\in\cI_a}\|G_{a,i}\|^2,
 \label{eq:tpc42-synchronous-energy}\\
 \sum_{i\in\cI_a}\|G_{a,i}-\overline G_a\|^2
 &=\left(1-\frac1{\rho_a}\right)
   \sum_{i\in\cI_a}\|G_{a,i}\|^2.
 \label{eq:tpc42-sharp-defect-energy}
\end{align}
Both identities are exact.
\end{corollary}

\begin{proof}
Orthogonality gives
\begin{equation}
 \left\|\sum_iG_{a,i}\right\|^2=\sum_i\|G_{a,i}\|^2.
 \label{eq:tpc42-orthogonal-sum-norm}
\end{equation}
This proves \eqref{eq:tpc42-synchronous-energy}.  The usual least-squares
identity
\begin{equation}
 \sum_i\|G_{a,i}-\overline G_a\|^2
 =\sum_i\|G_{a,i}\|^2-\rho_a\|\overline G_a\|^2
 \label{eq:tpc42-mean-square-identity}
\end{equation}
then gives \eqref{eq:tpc42-sharp-defect-energy}.
\end{proof}

Thus, on a fiber of multiplicity \(\rho_a\), only the fraction
\(1/\rho_a\) of the Hilbert--Schmidt coefficient energy lies in the
canonical sector through which a scalar residue sum factors.  The
remaining fraction is not small when \(\rho_a\) grows.

\begin{remark}[Quantifier boundary]
\label{rem:tpc42-factorization-boundary}
\Cref{thm:tpc42-factorization-criterion} characterizes an implication
that is uniform for every scalar array \(x\).  Its failure does not say
that the one arithmetic array formed by the actual M\"obius values has a
large directional defect after synthesis.  Proving that this particular
array avoids the coherent defect would be a coefficient-specific
arithmetic theorem.  What the criterion rules out is deriving such a
theorem solely from a scalar residue norm by a coefficient-blind tensor or
Moore--Penrose argument.
\end{remark}
