\section{Exact certificate and claim ledger}
\label{sec:tpc42-certificate}

The arguments above are analytic or exact finite-dimensional identities.
The companion standard-library certificate checks the finite identities
with integers, Gaussian integers, rational arithmetic, and exact finite
Dirichlet convolutions.  It uses no floating point, random draws, or
optimization-sensitive assertion.

\subsection{Certified identities}

Run from the paper directory
\begin{verbatim}
python experiments/tpc42_certificate.py
python -O experiments/tpc42_certificate.py
\end{verbatim}
The two commands produce byte-identical canonical JSON.  The frozen run
passes
\begin{equation}
 \boxed{178{,}226\ \text{exact checks}.}
 \label{eq:tpc42-certificate-count}
\end{equation}
It verifies:
\begin{enumerate}[label=(\roman*)]
 \item injectivity of the row-to-residue map on every declared finite
 orbit slice;
 \item fixed-alias orthogonality for distinct products in one residue
 fiber, including nonunit fibers, the exact packed diagonal, and the
 cross-residue coherent
 decomposition;
 \item the corresponding minimal-folded orthogonality, packed energy,
 coherent energy, and ordered cross-residue identity;
 \item the \(1/\rho\) synchronous energy and
 \(1-1/\rho\) canonical defect of orthogonal fibers, together with the
 sharp zero-scalar countermodels;
 \item the three-face convolution identity, the physical-window
 counterterm, outer-prime uniqueness, prime-power support separation, and
 exact coefficient-energy factorization through the frozen range; and
 \item every endpoint rational-exponent identity, including
 \(Q/K_B=X^{o(1)}J^2\).
\end{enumerate}

The certificate digest is
\begin{verbatim}
c2860f5d7c679224a5ff4edd417cb956a3cb49e3c7addc434e23dd7b4b8c50bf
\end{verbatim}
The SHA--256 hashes of the canonical JSON record and source are,
respectively,
\begin{verbatim}
1f6d7defff20b4ee8dfd4cd75b86c39eb08492a7a021e6e569dabc5aeebaf51a
57e1438392c88e8523bd5e038f580f179cdcddb7f0590776507e2956202c9c52
\end{verbatim}

\subsection{What the certificate does not certify}

The finite checks do not verify the prime number theorem, the
multiplicative large sieve, the TPC--41 scalar progression theorem, or any
asymptotic inherited from the previous papers.  They do not test M\"obius
randomness and are not numerical evidence for cancellation in
\eqref{eq:tpc42-next-four-mobius}.  The hard-cell convolution model checks
an exact coefficient identity; it does not model every physical mask.

In particular, the JSON record marks as false any interpretation that it
proves the orbit--slope Bessel target, a fixed affine Chowla estimate, a
parity breach, a prime-pair asymptotic, or the twin-prime conjecture.  Its
purpose is reproducibility of the exact structural reductions and their
claim boundary.
