\section{The coherent residue-synthesis defect}
\label{sec:tpc42-coherent-synthesis}

The identities of the preceding section interchange the usual roles of
progression and output coordinates.  A scalar progression estimate sums
down a fixed residue fiber.  The physical norm keeps that direction
orthogonal and instead sums across distinct residues at each orbit-time
coordinate.

\subsection{The sharp deterministic overlap bound}

For a fixed left alias define the active row overlap
\begin{equation}
 R_{k,L}
 :=\max_{\gamma,j}
 \#\{\alpha:
 c^L_{\alpha,\gamma,j}b_{\alpha,j,k}\ne0\}.
 \label{eq:tpc42-fixed-k-overlap}
\end{equation}
For the folded bank, let
\begin{equation}
 R_{\rm fold,L}
 :=\max_{\gamma,j,s}
 \#\{\alpha:
 c^L_{\alpha,\gamma,j}u_{\alpha,j,s}\ne0\}.
 \label{eq:tpc42-folded-overlap}
\end{equation}
Both are at most the inherited active row count and hence
\begin{equation}
 R_{k,L}+R_{\rm fold,L}\ll X^{o(1)}Q.
 \label{eq:tpc42-overlap-Q}
\end{equation}
Define the right overlaps symmetrically.

\begin{proposition}[Deterministic coherent synthesis]
\label{prop:tpc42-deterministic-synthesis}
One has
\begin{align}
 \|\mathscr T_k^L\|^2
 &\le R_{k,L}\cD_{k,L},
 \label{eq:tpc42-fixed-k-overlap-bound}\\
 \cE_{\rm fold,L}
 &\le R_{\rm fold,L}\cE_{\rm same,L}.
 \label{eq:tpc42-folded-overlap-bound}
\end{align}
The constants are sharp for abstract packets with the declared overlap
numbers.
\end{proposition}

\begin{proof}
Fix \((\gamma,j)\).  By
\eqref{eq:tpc42-distinct-rows-distinct-residues}, the nonzero row terms at
this coordinate occupy distinct target residues.  Cauchy--Schwarz gives
\begin{equation}
 \left|\sum_a[\mathbf V_{k,a}^L]_{\gamma,j}\right|^2
 \le R_{k,L}\sum_a
 |[\mathbf V_{k,a}^L]_{\gamma,j}|^2.
 \label{eq:tpc42-coordinate-Cauchy}
\end{equation}
Sum over \((\gamma,j)\) and use
\eqref{eq:tpc42-fixed-k-packed-diagonal}.  The same argument at every
\((\gamma,j,s)\), followed by
\eqref{eq:tpc42-folded-packed-energy}--
\eqref{eq:tpc42-folded-coherent-synthesis}, proves the folded bound.
Equality in coordinatewise Cauchy is possible when all active residue
contributions have the same phase and modulus, proving abstract
sharpness.
\end{proof}

For nonzero packet families \((V_a)\), write their coherent quotient as
\begin{equation}
 \mathfrak C(V)
 :=\frac{\|\sum_aV_a\|^2}{\sum_a\|V_a\|^2}.
 \label{eq:tpc42-coherent-quotient}
\end{equation}
The proposition gives \(\mathfrak C\le X^{o(1)}Q\) without arithmetic
cancellation.  The uniform diagonal-normalized equality-column route has
the sufficient benchmark
\begin{equation}
 \mathfrak C(\mathbf V_{0,\bullet}^L\oplus
             \mathbf V_{0,\bullet}^R)
 \ll X^{o(1)}K_B.
 \label{eq:tpc42-equality-required-coherence}
\end{equation}
Indeed, the inherited fixed-alias diagonal estimate is
\begin{equation}
 \cD_{0,L}+\cD_{0,R}\ll X^{o(1)}Q^2J.
 \label{eq:tpc42-equality-diagonal}
\end{equation}
The deterministic bound therefore gives only
\begin{equation}
 \|\mathscr T_0^L\|^2+\|\mathscr T_0^R\|^2
 \ll X^{o(1)}Q^3J,
 \label{eq:tpc42-equality-coherent-scale}
\end{equation}
whereas the target is
\begin{equation}
 K_BQ^2J
 =X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc42-equality-target-scale}
\end{equation}
Thus the gap between the deterministic overlap bound and this sufficient
endpoint benchmark is
\begin{equation}
 \boxed{\frac Q{K_B}=X^{o(1)}J^2.}
 \label{eq:tpc42-exact-J2-defect}
\end{equation}

For the complete minimal-folded route, the packed energy is already
\(O(X^{o(1)}Q^2JK_B)\) by
\eqref{eq:tpc42-packed-vector-target}.  The corresponding uniform
diagonal-normalized positive route has the sufficient benchmark of an
\(X^{o(1)}\)-scale coherent quotient after summing over buckets.  The
universal overlap estimate loses \(Q\).  The
logically weakest continuation remains the signed one-sided estimate
\eqref{eq:tpc42-inherited-gate}; it need not bound the absolute value of
every cross-residue inner product.

\subsection{A sharp scalar-blind countermodel}

The following model incorporates the exact orthogonality direction of the
physical packet.  It shows that even perfect scalar cancellation in every
residue does not control the coherent synthesis between residues.

\begin{theorem}[Zero scalar variance with maximal coherent defect]
\label{thm:tpc42-scalar-blind-countermodel}
For every integer \(R\ge1\), there is a two-point atom fiber over each of
\(R\) residues such that:
\begin{enumerate}[label=(\roman*)]
 \item the two Hilbert atoms in every residue fiber are orthogonal;
 \item the scalar sum in every residue is zero;
 \item every Hilbert coordinate has overlap \(R\); and
 \item the coherent synthesis quotient is exactly \(R\).
\end{enumerate}
More explicitly, let \(e_+,e_-\) be an orthonormal basis of \(\C^2\),
put
\begin{equation}
 G_{a,+}=e_+,
 \qquad
 G_{a,-}=e_-,
 \qquad
 x_{a,+}=1,
 \qquad
 x_{a,-}=-1
 \label{eq:tpc42-countermodel-atoms}
\end{equation}
for \(1\le a\le R\).  Then
\begin{align}
 (Px)_a&=x_{a,+}+x_{a,-}=0,
 \label{eq:tpc42-countermodel-scalar-zero}\\
 V_a&=x_{a,+}G_{a,+}+x_{a,-}G_{a,-}=e_+-e_-,
 \label{eq:tpc42-countermodel-packets}\\
 \sum_a\|V_a\|^2&=2R,
 &
 \left\|\sum_aV_a\right\|^2&=2R^2.
 \label{eq:tpc42-countermodel-sharpness}
\end{align}
\end{theorem}

The coefficient kernel in this model may be taken constant, so its
bounded projective norm is one.  Thus low projective complexity does not
remove the obstruction.  In particular, any universal estimate of the
form
\begin{equation}
 \left\|\sum_aV_a\right\|^2
 \le C\left(
 K_B\sum_a\|V_a\|^2+\|Px\|_2^2
 \right)
 \label{eq:tpc42-impossible-scalar-lift}
\end{equation}
must have
\begin{equation}
 C\ge\frac R{K_B}.
 \label{eq:tpc42-countermodel-lower-bound}
\end{equation}
On an abstract dense endpoint packet with \(R=X^{o(1)}Q\), this saturates
the same \(J^2\) ratio relative to the sufficient benchmark in
\eqref{eq:tpc42-exact-J2-defect}.

There are in fact two independent reasons why the scalar theorem of
TPC--41 cannot be inserted as a black box.  First, that theorem concerns
the complete scalar sum in a residue class; a fixed physical alias keeps
only the integers represented by \(r=m_\alpha j\), and scalar cancellation
is not hereditary under such a deletion.  Second, even a hypothetical
zero scalar sum on the exact represented subset is compatible with the
maximal vector defect in
\cref{thm:tpc42-scalar-blind-countermodel}.  The first issue is support;
the second is Hilbert geometry.

\begin{remark}[Arithmetic claim boundary]
\label{rem:tpc42-countermodel-boundary}
The countermodel is not asserted to be realized by the actual M\"obius
values on the TPC packet.  It proves that scalar residue variance,
residue-fiber orthogonality, bounded projective norm, and the deterministic
row ledgers do not logically imply the required physical estimate.  A
theorem exploiting the actual source signs \(\mu(d_\alpha)\), the target
signs \(\mu(m_\alpha j+h+kM)\), or an averaged auxiliary modulus remains
possible and is precisely the coefficient-specific continuation.
\end{remark}
