\section{Localized convolution completion is an exact counterterm}
\label{sec:tpc42-convolution-counterterm}

The full identity
\(
 \Lambda*\mu*\one=\Lambda
\)
does not make one dyadic factorization cell an approximation to
\(\Lambda\).  In the present scales the precise opposite statement holds:
the complementary divisor faces sum to the negative of the local cell on
the physical product window.  We formulate this before inserting any
arithmetic estimate.

\subsection{The three-face identity}

Let \(\delta_1\) denote the identity for Dirichlet convolution.  Let
\(\lambda_L\) be any finitely supported arithmetic function, let
\(\mu_D\) be any finitely supported truncation of \(\mu\), and let
\(u_J\) be any finitely supported orbit cutoff.  In the physical
specialization,
\begin{equation}
 \lambda_L(p)=(\log p)w_L(p/L_0)
 \quad(p\ \text{prime}),
 \qquad
 \mu_D(d)=\mu(d)w_D(d/D_0),
 \qquad
 u_J(j)=w_J(j/J),
 \label{eq:tpc42-counterterm-physical-functions}
\end{equation}
and \(\lambda_L\) vanishes away from the prime source interval.  Define
\begin{align}
 A&:=\lambda_L*\mu_D*u_J,
 \label{eq:tpc42-counterterm-A}\\
 B_D&:=\lambda_L*(\mu-\mu_D)*\one,
 \label{eq:tpc42-counterterm-BD}\\
 B_J&:=\lambda_L*\mu_D*(\one-u_J).
 \label{eq:tpc42-counterterm-BJ}
\end{align}
The complements in \eqref{eq:tpc42-counterterm-BD} and
\eqref{eq:tpc42-counterterm-BJ} need not be finitely supported.  Every
convolution value at a fixed integer is nevertheless a finite divisor
sum.

\begin{theorem}[Exact three-face completion]
\label{thm:tpc42-three-face-completion}
For every positive integer \(n\),
\begin{equation}
 \boxed{A(n)+B_D(n)+B_J(n)=\lambda_L(n).}
 \label{eq:tpc42-three-face-identity}
\end{equation}
\end{theorem}

\begin{proof}
Using \(\mu*\one=\delta_1\) and associativity gives
\begin{align*}
 A+B_D+B_J
 &=\lambda_L*
 \bigl[
   \mu_D*u_J+(\mu-\mu_D)*\one
   +\mu_D*(\one-u_J)
 \bigr]\\
 &=\lambda_L*(\mu*\one)
 =\lambda_L*\delta_1
 =\lambda_L.
\end{align*}
\end{proof}

The ordering of the two boundary terms is deliberate.  For hard
cutoffs, \(B_D\) first takes the complementary \(d\)-range with all
\(j\), while \(B_J\) retains the physical \(d\)-range and takes the
complementary \(j\)-range.  Thus there is no overlap ambiguity.  Smooth
cutoffs give the same identity with a weighted partition.

\subsection{The physical-window counterterm}

Assume that, for fixed positive dyadic constants,
\begin{equation}
 \operatorname{supp}\lambda_L\subset[c_LL_0,C_LL_0],
 \quad
 \operatorname{supp}\mu_D\subset[c_DD_0,C_DD_0],
 \quad
 \operatorname{supp}u_J\subset[c_JJ,C_JJ],
 \label{eq:tpc42-counterterm-supports}
\end{equation}
where
\begin{equation}
 L_0D_0J\asymp X,
 \qquad
 D_0J\longrightarrow\infty.
 \label{eq:tpc42-counterterm-product-scale}
\end{equation}
There are fixed \(0<c_X<C_X\) such that the local convolution \(A\) is
supported in
\begin{equation}
 W_X=[c_XX,C_XX]\cap\N.
 \label{eq:tpc42-counterterm-window}
\end{equation}
For all sufficiently large \(X\), this window is disjoint from
\(\operatorname{supp}\lambda_L\).

\begin{corollary}[The boundary is the negative local cell]
\label{cor:tpc42-physical-window-counterterm}
On the physical product window,
\begin{equation}
 \boxed{
  \one_{W_X}(B_D+B_J)=-\one_{W_X}A.}
 \label{eq:tpc42-physical-window-counterterm}
\end{equation}
Consequently,
\begin{align}
 \|B_D+B_J\|_{\ell^2(W_X)}
 &=\|A\|_{\ell^2(W_X)},
 \label{eq:tpc42-counterterm-norm-equality}\\
 \|B_D\|_{\ell^2(W_X)}^2
 +\|B_J\|_{\ell^2(W_X)}^2
 &\ge \frac12\|A\|_{\ell^2(W_X)}^2.
 \label{eq:tpc42-counterterm-face-energy}
\end{align}
In particular, at least one of the two boundary faces has squared norm at
least \(\|A\|_{\ell^2(W_X)}^2/4\).
\end{corollary}

\begin{proof}
Restrict \eqref{eq:tpc42-three-face-identity} to \(W_X\), where
\(\lambda_L\) vanishes.  This proves
\eqref{eq:tpc42-physical-window-counterterm} and
\eqref{eq:tpc42-counterterm-norm-equality}.  The inequality
\(\|x+y\|^2\le 2\|x\|^2+2\|y\|^2\) proves
\eqref{eq:tpc42-counterterm-face-energy}.
\end{proof}

The counterterm statement is unchanged by terminal multiplication and
Hilbert postcomposition.

\begin{proposition}[Arbitrary Hilbert multiplier]
\label{prop:tpc42-counterterm-Hilbert-multiplier}
This proposition concerns the grouped-product scalarization; it does not
identify a representation-dependent physical mask with a function of
the grouped product \(n\).
Let \(\Hh\) be a Hilbert space and let
\(v:W_X\to\Hh\) be arbitrary.  All sums below are finite.  Then
\begin{equation}
 \boxed{
 \sum_{n\in W_X}(B_D+B_J)(n)v(n)
 =-\sum_{n\in W_X}A(n)v(n).}
 \label{eq:tpc42-counterterm-Hilbert-multiplier}
\end{equation}
This remains true for each admissible alias after taking, on the positive
terminal support,
\begin{equation}
 v(n)=
 \mu(n+h+kM)\log(n+h+kM)
 \Phi_0(n+h+kM)z(n),
 \qquad z(n)\in\Hh.
 \label{eq:tpc42-counterterm-terminal-multiplier}
\end{equation}
\end{proposition}

\begin{proof}
Multiply the pointwise identity
\eqref{eq:tpc42-physical-window-counterterm} by \(v(n)\) and sum.
No boundedness or regularity of \(v\) is required because \(W_X\) is
finite.
\end{proof}

Thus an estimate for the combined boundary output in
\eqref{eq:tpc42-counterterm-Hilbert-multiplier} is exactly an estimate for
the original localized output.  Completion has not replaced the local
gate by a smaller error.

\subsection{Why the completed \texorpdfstring{\(\Lambda\)}{Lambda} term cancels}

The same calculation locates the apparent shifted-prime term.  Since
\(f*\mu*\one=f\) for every arithmetic function \(f\),
\begin{equation}
 \boxed{
 \Lambda=(\Lambda-\lambda_L)+A+B_D+B_J.}
 \label{eq:tpc42-full-Lambda-decomposition}
\end{equation}
Indeed, the first term is
\((\Lambda-\lambda_L)*\mu*\one\), while the other three terms are the
three-face expansion of \(\lambda_L*\mu*\one\).

\begin{corollary}[Source-complement cancellation]
\label{cor:tpc42-source-complement-cancellation}
On the physical window one has the two separate identities
\begin{align}
 \one_{W_X}(\Lambda-\lambda_L)&=\one_{W_X}\Lambda,
 \label{eq:tpc42-source-complement-Lambda}\\
 \one_{W_X}(A+B_D+B_J)&=0.
 \label{eq:tpc42-source-complement-cancellation}
\end{align}
Thus, after multiplication by any grouped-product Hilbert multiplier and
summation, the completed \(\Lambda\) contribution is carried entirely by
the source-complement term, while the three local faces cancel among
themselves.  Equivalently, moving the local cell to the other side leaves
\(A=-(B_D+B_J)\).
\end{corollary}

This is an algebraic obstruction, not a statement that shifted-prime
estimates are weak.  Even a perfect bound for the completed \(\Lambda\)
term or its source-complement copy gives no estimate for one local face:
the second identity in
\eqref{eq:tpc42-source-complement-cancellation} only cancels the three
faces collectively.

\subsection{Compatibility with projective mask layers}

The actual row mask is representation-dependent, so it cannot simply be
inserted as a function of the grouped product \(n\) in
\eqref{eq:tpc42-three-face-identity}.  After the product-ready
fixed-column projective separation inherited from TPC--36, however, each
scalarized layer has the form
\begin{equation}
 A_\rho=B_\rho*F_\rho*E_\rho,
 \label{eq:tpc42-counterterm-projective-layer}
\end{equation}
where the three functions carry the source, divisor, and orbit weights of
that layer.  There is then a layerwise version of the same obstruction.

\begin{proposition}[Unique layerwise completion]
\label{prop:tpc42-layerwise-counterterm}
Put
\begin{equation}
 C_\rho=F_\rho*E_\rho,
 \qquad
 R_\rho=\delta_1-C_\rho.
 \label{eq:tpc42-layerwise-remainder}
\end{equation}
Then \(R_\rho\) is the unique arithmetic function for which
\(C_\rho+R_\rho=\delta_1\), and
\begin{equation}
 A_\rho+B_\rho*R_\rho=B_\rho.
 \label{eq:tpc42-layerwise-completion}
\end{equation}
Consequently, on any window \(W\) disjoint from
\(\operatorname{supp}B_\rho\),
\begin{equation}
 \boxed{
  \one_W(B_\rho*R_\rho)=-\one_WA_\rho.}
 \label{eq:tpc42-layerwise-counterterm}
\end{equation}
\end{proposition}

\begin{proof}
The uniqueness of \(R_\rho\) is immediate from
\eqref{eq:tpc42-layerwise-remainder}.  Associativity gives
\[
 A_\rho+B_\rho*R_\rho
 =B_\rho*(C_\rho+R_\rho)
 =B_\rho*\delta_1
 =B_\rho.
\]
Restriction to \(W\) proves
\eqref{eq:tpc42-layerwise-counterterm}.
\end{proof}

A low projective reassembly mass controls the cost of summing the layers;
it does not make the exact counterterms in
\eqref{eq:tpc42-layerwise-counterterm} small.  Moreover, the scalar
convolution in \eqref{eq:tpc42-counterterm-projective-layer} has already
summed the orbit variable.  The physical output retains its
\((\gamma,j)\) coordinates, so the scalar completion identity does not by
itself define an inverse on that Hilbert coordinate space.  The results of
this section therefore rule out a small-boundary shortcut; they do not
supply, or disprove, the remaining physical cancellation theorem.
