\section{Introduction}
\label{sec:tpc42-introduction}

The terminal gate left by TPC--41 has two descriptions that initially
appear close.  The physical description is a Hilbert norm of row sums
whose cross terms contain four M\"obius factors.  The scalar description
is a short-progression variance over reduced residue classes modulo an
admissible triple-prime number \(M\), for which TPC--41 proves a
logarithmic saving on almost all such
moduli \citep{WangTPC41,KlurmanMangerelTeravainen2023}.  This paper proves
that the two descriptions point in transverse directions.

Fix an alias and write the terminal column as
\begin{equation}
 \mathscr T_k
 =-\sum_r\mu(r+h+kM)\mathbf G_k(r),
 \qquad
 \mathbf G_k(r)\in\ell^2\{(\gamma,j)\}.
 \label{eq:tpc42-intro-column}
\end{equation}
If \(r\ne r'\) but \(r\equiv r'\pmod M\), then
\begin{equation}
 \boxed{\mathbf G_k(r)\perp\mathbf G_k(r').}
 \label{eq:tpc42-intro-fiber-orthogonality}
\end{equation}
Indeed, a shared orbit coordinate would force
\((m_\alpha-m_\beta)j\) to be divisible by \(M\); the admissibility of
the auxiliary primes and the no--wrap row window then force the two rows
to be identical.  Hence the vector energy obtained by packing terms in
the same residue class is exactly the atomic diagonal, without using any
M\"obius cancellation.

This is an orthogonality swap.  Arrange the physical atoms in a grid with
orbit time \(j\) as the horizontal coordinate and target residue modulo
\(M\) as the vertical coordinate.  Along a fixed \(j\), distinct rows
occupy distinct residues and the physical output adds them coherently.
Along a fixed residue, distinct products occupy disjoint \(j\)-coordinates
and are orthogonal.  Scalar progression variance measures the vertical
direction, whereas the surviving physical gate is the horizontal
coherent synthesis.

The minimal folded bank admits the exact version
\begin{equation}
 \cE_{\rm fold,L}
 =\sum_s\left\|\sum_a\mathbf W^L_{s,a}\right\|^2,
 \qquad
 \cE_{\rm same,L}
 =\sum_{s,a}\|\mathbf W^L_{s,a}\|^2,
 \label{eq:tpc42-intro-packed-energies}
\end{equation}
where \(s\) is a folded alias bucket and \(a\) a residue class.  Their
difference is precisely the cross--residue form
\begin{equation}
 \operatorname{Re}\cF_L
 =\operatorname{Re}
  \sum_s\sum_{a\ne b}
  \langle\mathbf W^L_{s,a},\mathbf W^L_{s,b}\rangle,
 \label{eq:tpc42-intro-cross-residue}
\end{equation}
and similarly on the right.  Thus the progression-direction vector
variance is already closed by the theorem of TPC--41; what remains is
not an unproved Hilbert extension of that scalar statement.
The exact packet sums here run over all residues modulo \(M\).  The
scalar TPC--41 theorem acts only on the unit-residue sector, so nonunit
packets remain outside that scalar input unless an independently justified
regular pruning makes them vanish.

\subsection{The canonical scalar-visible sector}

There is nevertheless a precise sense in which any scalar progression
theorem can be postcomposed into a Hilbert space.  On the sector addressed
by that scalar theorem, let \(R_M\) be the weighted residue aggregation
operator, let \(A_M\) synthesize the corresponding physical coefficient
vectors, and set
\begin{equation}
 P_M=R_M^\dagger R_M,
 \label{eq:tpc42-intro-P}
\end{equation}
where \(R_M^\dagger\) is the Moore--Penrose inverse.  Then
\begin{equation}
 \boxed{
 A_M\mu
 =A_MR_M^\dagger(R_M\mu)
  +A_M(I-P_M)\mu.}
 \label{eq:tpc42-intro-canonical-split}
\end{equation}
The first term is the maximal canonical sector visible to the scalar
progression vector and obeys every bounded Bessel postcomposition of the
TPC--41 estimate.  The second term is a uniquely defined directional
defect.  An operator factors through \(R_M\) if and only if it vanishes
on this defect space.
For TPC--41 this canonical split is applied to the unit-residue sector;
any nonunit physical packets sit outside that scalar domain and must be
carried separately.

This distinction is sharp.  On one residue fiber, universal control of
a Hilbert synthesis by the scalar fiber sum is possible if and only if
all coefficient columns on that fiber are equal.  The actual physical
columns lie at the opposite geometric extreme: they are pairwise
orthogonal.  For an unweighted fiber of multiplicity \(\rho\), only the
fraction \(1/\rho\) of their Hilbert--Schmidt energy lies in the common
fiber mode, while \(1-1/\rho\) lies in the scalar-invisible complement.
This rules out a black-box deduction from scalar variance plus
coefficient energy.  It does not rule out a coefficient-specific theorem
for the actual M\"obius vector.

TPC--36 adds a useful positive reduction.  Each projective mask layer
factors its opposite-row coordinate, so its Hilbert norm is exactly an
orbit-time Bessel form.  The next arithmetic input can therefore be
stated for a restricted family of row slopes and orbit weights, rather
than for arbitrary Hilbert coefficients.

\subsection{The localized convolution counterterm}

A second proposed route was to compare the local coefficient
\(\lambda_L*\mu_D*u_J\) with the completed identity
\(\Lambda*\mu*\one=\Lambda\).  We prove that its natural boundary is not
a small error.  With
\begin{equation}
 A=\lambda_L*\mu_D*u_J,
 \quad
 B_D=\lambda_L*(\mu-\mu_D)*\one,
 \quad
 B_J=\lambda_L*\mu_D*(\one-u_J),
 \label{eq:tpc42-intro-three-faces}
\end{equation}
one has the pointwise identity
\begin{equation}
 A+B_D+B_J=\lambda_L.
 \label{eq:tpc42-intro-counterterm-identity}
\end{equation}
The physical product window is of size \(L_0D_0J\asymp X\), disjoint
from the source support \(L_0=o(X)\).  Consequently
\begin{equation}
 \boxed{B_D+B_J=-A}
 \label{eq:tpc42-intro-counterterm}
\end{equation}
pointwise on that window, after any Hilbert-valued postcomposition
depending only on the grouped product \(n\).  The full shifted-prime
contribution is
cancelled exactly by the source-complement term.  For the natural
unmasked hard cell we further prove
\begin{equation}
 \frac{X}{\log X}\ll\|A\|_2^2\ll X^{1+o(1)},
 \qquad
 A(n)\Lambda(n)=0,
 \label{eq:tpc42-intro-boundary-size}
\end{equation}
so the local cell and the von Mangoldt comparator have disjoint support.
The conclusion is about the completion strategy, not a lower bound for
the signed physical four--M\"obius output.

\subsection{What advances}

The present results move the endpoint in three ways.  First, they prove
that vectorizing the scalar progression direction introduces no hidden
arithmetic gain: for the actual packet that direction is exactly
diagonal.  Second, they replace the vague scalar-to-Hilbert gap by the
canonical operator \(A_M(I-P_M)\) and then identify its actual
cross--residue geometry.  Third, they close the local-completion route as
a standalone shortcut by an exact counterterm theorem.  The remaining
positive problem is a coefficient-specific orbit--slope dispersion
estimate.  No individual affine Chowla estimate, parity breach,
Hardy--Littlewood prime-pair asymptotic, or twin-prime conclusion is
claimed.

The paper is organized as follows.  \Cref{sec:tpc42-interface} records
the inherited endpoint.  The next three sections develop the canonical
factorization, the residue-fiber identities, and coherent synthesis.  The
Hilbert large-sieve section records the exact positive scope of
dimension-free postcomposition, followed by the projective orbit
reduction.  The two
convolution sections prove the counterterm and its quantitative hard-cell
form.  The final sections compare the literature, state the next target,
and freeze an exact certificate and claim ledger.
