\section{Sparse families, dense shifts, and the exact selection loss}
\label{sec:tpc42-literature-boundary}

We place the preceding operator statement against three neighboring
parts of the literature.  The purpose is not to claim a new general
large sieve, but to identify which existing average can actually select
an admissible TPC modulus or shift.

\subsection{Sparse moduli: what is already available}

Large--sieve and Bombieri--Vinogradov theory for sparse sets of moduli is
well established.  Baier's general sparse large sieve requires
quantitative distribution of the modulus set in arithmetic progressions
\citep{Baier2006SparseLargeSieve}.  Baier and Zhao prove, among other
results, a Barban--Davenport--Halberstam theorem for a well--distributed
set \(\mathcal S\) satisfying a divisor--slice stability condition and
\begin{equation}
 |\mathcal S(Q)|\gg Q^{1/2},
 \qquad Q\le x^{1-\varepsilon};
 \label{eq:tpc42-baier-zhao-cardinality-range}
\end{equation}
see \citet[Theorem~1]{BaierZhao2006}.  These hypotheses are substantive,
not consequences of cardinality alone.

For the three disjoint prime intervals used here,
\begin{equation}
 |\mathfrak M_X|
 \asymp\frac{M_0}{(\log X)^3},
 \qquad M_0=X^{399/400},
 \label{eq:tpc42-literature-family-density}
\end{equation}
so the numerical size condition in
\eqref{eq:tpc42-baier-zhao-cardinality-range} is more than satisfied,
and \(M_0\le X^{1-\varepsilon}\) for every fixed
\(0<\varepsilon<1/400\).  A direct invocation would still require a
proof that this exact three--interval product family is well distributed
and satisfies the divisor--slice hypothesis.  There is also a
quantifier issue: the cited formulation starts from one fixed set of
natural numbers, whereas the three prime intervals here move with \(X\).
One must either embed the moving slices in a fixed set or verify that the
proof is uniform for this scale--dependent family; a finite dyadic
decomposition is also needed if the product window crosses dyadic
boundaries.  Moreover, the cited
Barban--Davenport--Halberstam theorem concerns the scalar prime error.
The standard sparse large sieve likewise acts on one common scalar
coefficient sequence.  Neither statement permits the modulus--dependent
within--fiber physical coefficient field encoded by \(T_G\) and its
canonical projector to be inserted into that scalar sequence for free.

Two further comparisons prevent an inflated novelty claim.  Iwaniec
obtains true--order large--sieve estimates for prime moduli when the
common scalar coefficients are supported on integers without small prime
factors \citep{Iwaniec2022PrimeModuli}; this is not a theorem for products
of three primes with moving Hilbert coefficients.  As a recent comparison
for factorable moduli, \citet{Li2026LargeModuli} proves prime
mean--value theorems for bilinear modulus forms up to \(x^{9/17}\) and
trilinear modulus forms up to \(x^{17/32}\).  Those results concern scalar
prime distribution and their trilinear exponent is far below
\(399/400\).  Accordingly, we claim neither a first sparse
triple--prime BDH theorem nor a new general almost--prime--modulus large
sieve.

\subsection{An exact density--loss lemma}

The elementary loss incurred by restricting a dense average is already
decisive at the present logarithmic density.

\begin{lemma}[Sharp restriction threshold]
\label{lem:tpc42-density-loss}
Let \(\Omega_X\) be a finite ambient family, let
\(\mathcal S_X\subseteq\Omega_X\) have relative density
\(\delta_X=|\mathcal S_X|/|\Omega_X|\), and let
\(E_X:\Omega_X\to[0,\infty)\).  Then
\begin{equation}
 \frac1{|\mathcal S_X|}\sum_{s\in\mathcal S_X}E_X(s)
 \le
 \delta_X^{-1}
 \frac1{|\Omega_X|}\sum_{s\in\Omega_X}E_X(s).
 \label{eq:tpc42-exact-density-loss}
\end{equation}
The factor \(\delta_X^{-1}\) is best possible without additional
information on the placement of \(\mathcal S_X\).
\end{lemma}

\begin{proof}
Positivity gives
\(\sum_{s\in\mathcal S_X}E_X(s)
\le\sum_{s\in\Omega_X}E_X(s)\), which is
\eqref{eq:tpc42-exact-density-loss} after division.  Equality in the loss
is attained by a function supported on \(\mathcal S_X\).
\end{proof}

For the family in \eqref{eq:tpc42-literature-family-density},
\(\delta_X\asymp(\log X)^{-3}\) inside a fixed--proportion dyadic modulus
window.  Therefore a dense nonnegative estimate
\begin{equation}
 \frac1{|\Omega_X|}\sum_{s\in\Omega_X}E_X(s)
 \ll \frac{\mathsf T_X}{(\log X)^A}
 \label{eq:tpc42-dense-average-saving}
\end{equation}
implies only
\begin{equation}
 \frac1{|\mathfrak M_X|}\sum_{M\in\mathfrak M_X}E_X(M)
 \ll \frac{\mathsf T_X}{(\log X)^{A-3}}.
 \label{eq:tpc42-triple-family-threshold}
\end{equation}
Thus \(A>3\) is the exact black--box threshold for a residual logarithmic
saving, \(A\ge3+\sigma\) is needed for a prescribed
\((\log X)^{-\sigma}\) saving, and a qualitative
\(o(\mathsf T_X)\) conclusion on the sparse family requires a dense bound
\(o(\mathsf T_X/(\log X)^3)\).
The same calculation applies to any nonnegative average of the canonical
Hilbert defect.  It is a selection threshold, not an estimate for that
defect.

\subsection{What dense shift estimates do and do not select}

The averaged Chowla theorem of
\citet{MatomakiRadziwillTao2015} averages over full boxes of integer
shifts.  Polynomial variants also exist: \citet{Frantzikinakis2018}
treats independent polynomial shifts in a qualitative uniform--density
framework.  These results are important prior art for product--shaped
shift parameters.  A prime--restricted parameter box is a zero--density
subset of the full integer box, so a qualitative dense convergence
statement alone cannot select it.  Stronger exceptional--set theorems
must, however, be considered separately.

For shifted primes, the comparison can be made numerical.  If
\(H=X^{\vartheta}\), \(0<\vartheta<1\), then
\citet[Theorem~1.1]{Lichtman2022} proves, for every \(\eta>0\),
\begin{equation}
 \sum_{h\le H}
 \left|\sum_{p\le X}\mu(p+h)\right|
 \ll_{\vartheta,\eta}
 \frac{H\pi(X)}{(\log X)^{1/3-\eta}}.
 \label{eq:tpc42-lichtman-dense-saving}
\end{equation}
Restricting this nonnegative sum to a prescribed shift set of relative
density \((\log X)^{-3}\) loses \((\log X)^3\) by
\cref{lem:tpc42-density-loss}.  The resulting average is bounded only by
\(\pi(X)(\log X)^{8/3+\eta}\), not by \(o(\pi(X))\).  In exponent language,
the available dense saving is \(1/3-\eta\), while black--box selection of
the triple--prime subset requires a saving strictly greater than \(3\):
the deficit of this particular first--moment bound is \(8/3+\eta\).
This calculation is not a limitation of Lichtman's full result.

Indeed, \citet[Theorem~6.3]{Lichtman2022} proves a much sharper
exceptional--set statement.  Write \(\log_2 X=\log\log X\) and suppose
\(\log H/\log_2 X\to\infty\).  For fixed \(h_2,\ldots,h_k\le H\),
\(g_1=\mu\), and fixed \(1\)-bounded \(g_2,\ldots,g_k\), the
shifted-prime correlation is \(o(\pi(X))\) for
all but
\begin{equation}
 O_K\bigl(H(\log X)^{-K}\bigr)
 \label{eq:tpc42-lichtman-exceptional-set}
\end{equation}
values of \(h_1\le H\), for every \(K>0\).  Consequently, taking \(K>3\)
does select a good shift from any prescribed scalar shift set of size
\(\gg H/(\log X)^3\).  Corollary~1.5 of the same paper gives the
corresponding arbitrary logarithmic exceptional saving for fixed-order
scalar M\"obius tuples.  Thus selection of a triple--prime subset in a
pure scalar shifted-prime problem is already available and is not the
TPC--42 gap.

The hybrid theorem of \citet{LichtmanTeravainen2022}, in its stated
parameter ranges, further inserts fixed M\"obius shifts and fixed prime
offsets and obtains cancellation for almost all choices of one shift
once \(H\ge(\log X)^{\ell+\varepsilon}\).  What neither theorem supplies
is one estimate uniform over the TPC family of coefficient fields:
the modulus changes the residue fibers and their canonical projector,
and every nonzero alias changes the terminal argument.  The row slopes,
projective masks, and retained Hilbert coordinates are additional
structure absent from the scalar theorem even when they are held fixed;
they may also vary if a regular subpacket is reselected with the modulus.
In particular, a scalar good shift chosen for one fixed
collection of \(g_j\) does not bound the nonnegative moving quantity
\(\|T_{G_M}(I-\Pi_{w,M})\mu\|_{\Hh}^{2}\) averaged over \(M\).

\subsection{The claim boundary}

The positive result of \cref{sec:tpc42-hilbert-large-sieve} is exactly a
dimension--free postcomposition of the scalar residue vector already
proved in TPC--41.  Its useful new role in the present paper is to
transfer, simultaneously, the inherited estimate through every
residue--synchronous Bessel synthesis and to locate the within--fiber
directional defect, whose physical synthesis appears as cross--residue
coherence.  It is
not a vector extension of the arithmetic theorem of
Klurman--Mangerel--Ter\"av\"ainen, and it does not prove a new sparse
modulus or sparse shift mean--value theorem.  Conversely,
\cref{lem:tpc42-density-loss} shows exactly what a future route must add:
either direct information on the declared triple--prime family, or more
than three powers of logarithmic saving in a nonnegative ambient average
of that same canonical defect, before it can be selected by restriction
alone.  Scalar shift estimates, even with a smaller exceptional set, are
not such a defect estimate.
