\section{The remaining uniform gate and a stepwise roadmap}
\label{sec:barriers-roadmap}

The dynamic theorem and complement theorem meet at a precise boundary.
Inside \(u,v\le S\), exact-conductor averaging supplies a fixed-power
saving.  Outside, divisor reflection exposes affine M\"obius
correlations.  This section records the order of operations needed to
continue and the conclusions that are not available.

\subsection{A quantitative form of the next gate}

For a compatible complement pair, define the sharp fiber sum
\begin{align}
 \cM_{m_1,m_2;r,s}(W;S)
 :={}&\sum_t W\left(\frac{j_0+[r,s]t}{J}\right)
 \mu(U_{r,s}(t))\mu(V_{r,s}(t))
 \notag\\
 &\times\log U_{r,s}(t)\log V_{r,s}(t)
 \one_{U_{r,s}(t)>S}\one_{V_{r,s}(t)>S}.
 \label{eq:sharp-affine-fiber}
\end{align}
The smooth weight \(W\) ranges over a fixed family with uniformly
bounded support and derivative seminorms.  The
forms and their nonzero determinant are given by
\cref{thm:affine-complement-fiber}.  The fiber has length
\begin{equation}
 \asymp 1+\frac{J}{[r,s]}.
 \label{eq:fiber-length}
\end{equation}

Tao's theorem controls \eqref{eq:sharp-affine-fiber} when every
coefficient is fixed, the average is cumulative logarithmic, and the
limit is taken before the coefficients grow.  The TPC packet instead
requires all of the following simultaneously:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item \(m_i\asymp Q=X^{\beta+o(1)}\) and complement divisors as large
 as \(X/S\);
 \item a prescribed smooth dyadic window of length \(J\), not merely a
 cumulative \(dt/t\) average;
 \item a rate strong enough to sum the row pairs, complement pairs,
 determinant-content refinements, and separated smooth packets;
 \item a separate treatment of the sparse range \([r,s]\gtrsim J\),
 where a fiber has at most \(O(1)\) orbit points and no one-fiber
 asymptotic can create cancellation.
\end{enumerate}

The next useful theorem would therefore be a \emph{uniform affine
M\"obius dispersion estimate}, not a pointwise appeal to randomness.
One possible sufficient interface is the following.

\begin{assumption}[Dyadic affine-fiber dispersion]
\label{ass:uniform-affine-dispersion}
After inserting the actual row weights and generic row-pair mask, every
dyadic block of compatible complement moduli with
\([r,s]\le JX^{-\kappa}\) has total contribution from
\eqref{eq:sharp-affine-fiber} at most
\begin{equation}
 XQ(\log X)^{-B}
 \label{eq:uniform-affine-gate}
\end{equation}
for arbitrarily prescribed \(B>0\), uniformly over the separated
weights.  The complementary sparse blocks admit the same total bound
after using their exact determinant and incidence geometry rather than
a one-fiber asymptotic.
\end{assumption}

This is deliberately an input, not a theorem of the present paper.  It
keeps the two M\"obius signs together and specifies the growing
parameters, sharp averaging, coefficient summation, and sparse regime
that a usable result must cover.

\subsection{Why several shortcuts fail}

\begin{enumerate}[label=\textup{(\arabic*)}]
 \item \emph{Taking absolute values fiber by fiber.}
 \Cref{prop:absolute-nogo} gives natural-scale mass already on
 \(r=s=1\).  The two M\"obius signs are the mechanism, not a nuisance
 that can be discarded.

 \item \emph{Replacing the reflected sign by \(\mu(r)\).}
 The exact coefficient is \(\mu(n/r)\); see
 \eqref{eq:exact-complement}.  The Liouville rewriting introduces the
 global target phase \(\lambda(n)\) and a squarefree quotient cutoff.
 It does not turn the coefficient into an ordinary short-divisor
 M\"obius sum.

 \item \emph{Assuming the two determinant contents are coprime.}
 In a mixed large--short term, both the complement gcd and the
 quotient--short-divisor gcd divide \(m_1-m_2\), but they may overlap
 when the target has a square factor.  Declaring them coprime silently
 deletes valid nonsquarefree targets.

 \item \emph{Applying TPC-22 with an arbitrarily large cutoff.}
 The dynamic conductor ledger loses its margin at the explicit faces
 in \eqref{eq:etaS}, and TPC-20's Fourier-channel reduction loses the
 strict Poisson-short condition at \(S\asymp J\).  Beyond those faces,
 additional cancellation between joint and single spectra or a new
 quotient-variable argument is required.

 \item \emph{Using logarithmic Elliott as a black box for the full
 packet.}
 \Cref{cor:slow-window} is intentionally ineffective.  It supplies no
 bound uniform over polynomially many forms, and logarithmic averaging
 cannot simply be removed by partial summation.
\end{enumerate}

\subsection{A staged continuation}

The exact reductions suggest the following sequence of independent
tasks.

\begin{enumerate}[label=\textup{Stage \arabic*:},leftmargin=6.2em]
 \item Push the dynamic cutoff to the largest certified \(S\) on each
 row slice, using \cref{thm:dynamic-closure}.  This has been completed
 here for the full square \(u,v\le S\).

 \item Split the remaining both-ultra terms by the complement modulus
 \(q=[r,s]\), and the mixed terms by their complementary--short
 modulus.  Preserve the row mask, the exact affine determinant
 \(h(m_1-m_2)/(r,s)\), and the corresponding mixed gcd content.

 \item In \(q\ll J\), seek a quantitative version of two-point
 M\"obius cancellation that is uniform in the polynomial coefficients
 generated by the complement fibers.  A logarithmically averaged or
 averaged-row theorem would already be publishable if its precise
 range exceeds the current slow diagonal window.

 \item In \(q\gtrsim J\), use sparse incidence geometry, the equation
\begin{equation}
 m_2U r-m_1V s=h(m_2-m_1),
 \label{eq:sparse-incidence-equation}
\end{equation}
 and the generic determinant/gcd pruning.  A theorem here need not
 solve an individual two-point Chowla problem because each fiber is
 short; it must instead save after summing the family.

 \item Recombine the long and sparse complement blocks with the mixed
 \(Z^{\le S}Z^{>S}\) terms.  Only after this scalar recombination may
 one restore all separated packets and the earlier TPC-18 endpoint
 pieces.

 \item A full residual-dispersion estimate would still be an analytic
 upper/cancellation theorem.  Converting it into a positive
 Hardy--Littlewood main term or an infinite twin-prime conclusion is a
 separate parity-sensitive step.
\end{enumerate}

Each stage has a useful fallback.  Failure of a uniform estimate can
be recorded as a sharp exponent boundary or a componentwise no-go;
success in a logarithmic, averaged-row, or shorter-parameter regime is
still a rigorous intermediate theorem.

\subsection{Status table}

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.42\textwidth}
                >{\raggedright\arraybackslash}p{0.47\textwidth}}
\toprule
Object & Status after this paper\\
\midrule
Ramanujan mean for \(b_R(u)\one_{u\le S}\)
& Closed absolutely by \cref{thm:dynamic-mean}.\\
\addlinespace
Centered connected packet \(u,v\le S\)
& Closed with fixed-power saving in
  \cref{thm:dynamic-closure,cor:closed-strip}.\\
\addlinespace
Mixed and both-large pieces newly included in
\eqref{eq:new-support-pieces}
& Closed; these are genuine coefficients beyond \(R\).\\
\addlinespace
Remaining terms with \(u>S\) or \(v>S\)
& Exact complement-fiber form proved; polynomially uniform estimate
  open.\\
\addlinespace
Every fixed complement fiber and fixed finite complement truncation
& Closed only in cumulative logarithmic average by
  \cref{prop:fixed-fiber-log,cor:finite-complement-log}.\\
\addlinespace
Full TPC-18 residual and all endpoint reassembly
& Not proved.\\
\addlinespace
Hardy--Littlewood asymptotic, twin-prime lower bound, or a general
parity breakthrough
& Not claimed and not implied.\\
\bottomrule
\end{tabular}
\end{center}
