\section{Conductor rectangularization at a dynamic cutoff}
\label{sec:dynamic-conductor}

We now prove that the centered part of the selected packet extends
from \(u,v\le R\) to \(u,v\le S\).  Every step is performed before
summing different lcm decompositions; there is no global character
rectangle shared by all divisor pairs.

\subsection{Pairwise coordinates and compatibility energy}

For one squarefree pair, use \eqref{eq:gab}.  Since \(g,a,b\) are
pairwise coprime,
\begin{equation}
 \mathfrak X(q)\simeq\mathfrak X(u)\times\mathfrak X(b),
 \qquad \chi\longmapsto(\alpha,\gamma),
 \label{eq:product-characters}
\end{equation}
and
\begin{equation}
 \cond\chi=(\cond\alpha)(\cond\gamma).
 \label{eq:product-conductors}
\end{equation}
The global principal character is exactly the pair of coordinate
principals.

Put
\begin{equation}
 c_{m,n}^{(g)}
 =x_my_n\mathfrak m(m,n)\one_{m\equiv n\pmod g}.
 \label{eq:compatibility-matrix}
\end{equation}
Character orthogonality on the shared factor gives the exact pairwise
transform
\begin{equation}
 \widehat Z_{u,v}^{\,\times}(\chi)
 =\overline{\chi(-h)}
 \sum_{m,n}c_{m,n}^{(g)}\alpha(m)\gamma(n).
 \label{eq:pair-rectangularization}
\end{equation}
There is no residual \(1/\varphi(g)\), and the character on the second
row is not conjugated.  This is the TPC-22 rectangularization, whose
proof is purely finite-group algebra and is unchanged by \(u,v>R\).

\begin{proposition}[Compatibility energy is cutoff-independent]
\label{prop:compatibility-energy}
Under \eqref{eq:row-energy}--\eqref{eq:mask},
\begin{equation}
 \boxed{
 \sum_{g\le S}\sum_{m,n}|c_{m,n}^{(g)}|^2
 \ll_\eps Q^2X^\eps.}
 \label{eq:compatibility-energy}
\end{equation}
No comparison \(S<L/2\) is required.
\end{proposition}

\begin{proof}
The mask removes \(m=n\).  Hence
\[
 \sum_{g\le S}\sum_{m,n}|c_{m,n}^{(g)}|^2
 \le\sum_{m\ne n}|x_m|^2|y_n|^2
       \sum_{g\mid m-n}1.
\]
The last multiplicity is at most \(\tau(|m-n|)\ll_\eps X^\eps\),
independently of \(S\).  Apply \eqref{eq:row-energy}.
\end{proof}

The row-pair-only nature of the mask is used here and below.  If the
mask changed with \(u,v,q\), the same matrix would no longer be tested
over the ambient character moduli, and the tensor step would not follow.

\subsection{The two estimates for one conductor cell}

We recall the weighted exact-conductor large sieve in the normalization
needed here.  If \(w\asymp W\) runs over squarefree moduli, \(a_n\) is
supported on an interval of length \(N\), and exact conductors lie in a
dyadic block \(f\asymp F\), then
\begin{equation}
 \sum_{w\asymp W}\frac1{\varphi(w)}
 \sum_{\substack{\chi\in\mathfrak X(w)\\\cond\chi\asymp F}}
 \left|\sum_na_n\chi(n)\right|^2
 \ll_\eps X^\eps\left(F+\frac NF\right)
 \sum_n|a_n|^2.
 \label{eq:exact-conductor-LS}
\end{equation}
The block \(F=1\) contains conductor one.  The proof writes \(w=fd\),
applies the primitive multiplicative large sieve at the true conductor
\(f\), and sums the inducing factors \(d\); it is uniform in the
ambient modulus \(W\).  This is Theorem~4.1 of TPC-22
\citep{WangTPC22}, derived there from the primitive multiplicative
large sieve \citep[Chapter~7]{IwaniecKowalski2004}.

Put
\begin{equation}
 \cK_Q(F)=F+\frac QF.
 \label{eq:KQ}
\end{equation}
For \(q=gab\asymp Y\), \(ga,gb\le S\), let
\(\cE_{Y,S}(F_1,F_2)\) be the sum of the squared transforms
\eqref{eq:pair-rectangularization}, weighted by
\begin{equation}
 \frac{|\vartheta_{R,S}(ga)\vartheta_{R,S}(gb)|^2}{\varphi(gab)},
 \label{eq:cell-weight}
\end{equation}
over all pairwise-coprime \(g,a,b\), coordinate characters with
\(\cond\alpha\asymp F_1\), \(\cond\gamma\asymp F_2\), and all
inherited admissibility conditions.  This is a sum of pair energies,
not the norm of a fictitious common projection.

\begin{theorem}[Dynamic tensor conductor energy]
\label{thm:dynamic-tensor-energy}
Uniformly for \(Y\le S^2\) and \(1\le F_i\le S\),
\begin{equation}
 \boxed{
 \cE_{Y,S}(F_1,F_2)
 \ll_\eps Q^2X^\eps
 \cK_Q(F_1)\cK_Q(F_2).}
 \label{eq:dynamic-tensor-energy}
\end{equation}
\end{theorem}

\begin{proof}
Fix \(g\), enlarge the nonnegative sum by dropping divisibility and
coprimality restrictions among the ambient moduli, and apply
\eqref{eq:exact-conductor-LS} in the \(m\)-coordinate.  Its
Hilbert-valued form permits the entire \(n\)-coordinate to remain as a
vector.  Apply the same theorem in the \(n\)-coordinate.  This gives
\[
 X^\eps\cK_Q(F_1)\cK_Q(F_2)
 \sum_{m,n}|c_{m,n}^{(g)}|^2.
\]
Sum in \(g\), use \cref{prop:compatibility-energy}, and absorb the
dyadic and divisor-pair multiplicities into \(X^\eps\).  The soft
coefficient bound \eqref{eq:b-soft} is the only property of
\(\vartheta_{R,S}\) used.
\end{proof}

Let \(\cL_{u,v}^{F_1,F_2}\) denote the scalar functional
\eqref{eq:dynamic-scalar-packet} formed from the
\((F_1,F_2)\)-coordinate-character projection of the unweighted
centered pair \(D_{u,v}\); the dynamic divisor coefficients are
inserted externally below.  Define the pair-separated cell sum
\begin{equation}
 \mathfrak L_{Y,S}(F_1,F_2)
 =
 \sum_{\substack{g,a,b\ {\rm pairwise\ coprime}\\
                  ga,gb\le S,\ gab\asymp Y}}
 |\vartheta_{R,S}(ga)\vartheta_{R,S}(gb)|
 |\cL_{ga,gb}^{F_1,F_2}|.
 \label{eq:dynamic-cell-definition}
\end{equation}
The inherited restricted-frequency norm route, licensed by
\eqref{eq:no-wrap} and the polynomial tail-mass assumption, gives
\begin{equation}
 \mathfrak L_{Y,S}(F_1,F_2)
 \ll_\eps QX^\eps
 \sqrt{JY\cK_Q(F_1)\cK_Q(F_2)}.
 \label{eq:dynamic-norm-route}
\end{equation}

There is a second estimate.  If a character modulo the squarefree
\(q\) has exact conductor \(f\mid q\), its additive transform at every
nonzero frequency factors into a primitive Gauss sum of size
\(\sqrt f\) and a Ramanujan sum modulo \(q/f\).  Summing that Ramanujan
factor against the smooth Fourier weight gives
\begin{equation}
 \sum_{r\ne0}|c_d(r)|
 \left|\widehat F\left(\frac{rJ}{Hq}\right)\right|
 \ll_{F,H} \frac{Hq}{J}\tau(d).
 \label{eq:Ramanujan-frequency}
\end{equation}
The zero frequency must remain excluded.  Resolving exact conductors
before this sum and applying \cref{thm:dynamic-tensor-energy} gives
\begin{equation}
\mathfrak L_{Y,S}(F_1,F_2)
 \ll_\eps QF_1F_2X^\eps
 \sqrt{\cK_Q(F_1)\cK_Q(F_2)}.
 \label{eq:dynamic-Gauss-route}
\end{equation}
This is exactly the all-frequency argument of Lemmas~6.1--6.2 and
Theorem~6.3 of TPC-22 \citep{WangTPC22}: replacing \(R\) by \(S\)
changes only the ambient ranges \(q\le S^2\) and \(F_i\le S\).  The
Ramanujan-frequency sum in \eqref{eq:Ramanujan-frequency} cancels the
Poisson normalization, while the two primitive Gauss factors and
Cauchy--Schwarz contribute \(F_1F_2\).

Combining the two estimates for the same scalar cell proves the dynamic
cell bound
\begin{equation}
 \boxed{
 \mathfrak L_{Y,S}(F_1,F_2)
 \ll_\eps QX^\eps
 \sqrt{\cK_Q(F_1)\cK_Q(F_2)}
 \min\{\sqrt{JY},F_1F_2\}.}
 \label{eq:dynamic-cell-bound}
\end{equation}
The omitted block \((F_1,F_2)=(1,1)\) is the principal mean already
treated in \cref{thm:dynamic-mean}; one-sided principal coordinate
cells remain in \eqref{eq:dynamic-cell-bound}.  Linearity and the
pairwise triangle inequality give the formal reassembly
\begin{equation}
 \sum_{q\asymp Y}|\cL_{q,S}^{\rm disc}|
 \le
 \sum_{\substack{F_1,F_2\\(F_1,F_2)\ne(1,1)}}
 \mathfrak L_{Y,S}(F_1,F_2)
 +O_A(X^{-A}\cZ_1),
 \label{eq:dynamic-cell-reassembly}
\end{equation}
where the final term is the inherited polynomial Fourier-tail error.

\begin{remark}[What was needed to cross \(R\)]
\label{rem:no-L2S}
Neither the character algebra nor the energy estimates require
\(L>2S\).  The inherited condition \(L>2R\) belongs to the row/source
construction.  For a target divisor \(u>R\), the necessary primitivity
is supplied by \eqref{eq:target-coprime}.  The genuinely new analytic
restriction is the Poisson-short condition \eqref{eq:S-single-leg}.
\end{remark}
