\begin{abstract}
The preceding fixed-shift analysis identifies an actual unit-diagonal residual
Gram and proves subpower reduced-cell codegree for every fixed row pair, but
does not control its global smallest eigenvalue. We open a determinant route
on the literal full-output matrix. For every square full-column minor, repeated
degree-one peeling factors off exactly all pivots found by the iterative
degree-one rule. A residual core without a perfect matching has zero
determinant. If the core admits a perfect matching, normalizing that matching
to the identity makes every other determinant term a vertex-disjoint family
of directed alternating cycles; diagonal gauge leaves only the
cycle-holonomy parameters. If
\(\mathcal A_\phi=\operatorname{per}(I+|E|)-1\) is the total absolute activity
of the nonempty cycle families, \(P_{\mathrm{for}}\) is the product of the
forced-pivot magnitudes, and \(P_\phi\) is the core matching-pivot product,
then
\[
 |\det T|
 \ge
 P_{\mathrm{for}}P_\phi(1-\mathcal A_\phi)_+.
\]
We next aggregate rather than select minors. For a synthesis matrix \(B\) with
\(r\) unit columns and Gram \(K=B^*B\), Cauchy--Binet and the trace constraint
give, for \(r\ge2\), the sharp conversion
\[
 \mathfrak D(B):=\sum_{|Y_0|=r}|\det B_{Y_0}|^2=\det K,
 \qquad
 \lambda_{\min}(K)
 \ge
 \left(\frac{r-1}{r}\right)^{r-1}\mathfrak D(B)
 \ge e^{-1}\mathfrak D(B).
\]
The case \(r=1\) is exact with constant one.
Thus certified determinant mass transfers to the physical Gram without the
dimension-exponential norm penalty of a one-minor estimate. The theorem is
sharp, but the route is not automatically sufficient: a path-Gram family has
a uniform spectral gap while its determinant decays exponentially. The
remaining arithmetic task for this certificate is to lower-bound the
determinant mass of every actual full-support collision component, or the
corresponding certified-minor mass; a global determinant-mass lower bound is
a stronger sufficient condition. A direct spectral or signed-reassembly
argument remains an independent route. No such physical lower bound, parity
improvement, or prime-pair conclusion is claimed.
\end{abstract}
