\section{Conclusions, stop rules, and the next door}

\subsection{What is now exact}
The determinant route has four exact layers.
\begin{enumerate}[label=(\arabic*)]
\item Every square actual minor factors into the pivots exposed by iterative
degree-one peeling and a nonpeelable residual core. A residual core without
a perfect matching has zero determinant.
\item If the residual core admits a declared perfect matching, all possible
cancellation is encoded by vertex-disjoint alternating-cycle families and
their gauge-invariant holonomies.
\item Dominant-matching activity gives a literal, phase-safe determinant
certificate. It makes no randomness assumption.
\item Cauchy--Binet aggregates every full minor, and unit diagonal converts
that determinant mass to the Gram gap with the sharp fixed-dimension factor
\(c_r\); the bound \(c_r\ge e^{-1}\) is uniform in the dimension.
\end{enumerate}

Consequently, if the literal physical matrix satisfies
\[
 \mathfrak D_X
 :=
 \sum_{\substack{Y_0\subseteq\mathcal Y_X^{\mathrm{full}}\\
                  |Y_0|=|\mathcal M_X^{\mathrm{act}}|}}
 |\det (B_X)_{Y_0,\mathcal M_X^{\mathrm{act}}}|^2
 \ge X^{-\lambda_{\det}+o(1)},
\]
then its represented Gram has the same fixed-power exponent:
\[
 \beta_X\ge e^{-1}X^{-\lambda_{\det}+o(1)}.
\]
The determinant-to-gap conversion is L0; identifying \(B_X\) with the literal
fixed-\(h_0\) carrier is L1. Proving the displayed physical lower bound would
be L2, and remains open.
The sharper componentwise version requires only
\[
 \min_{C\in\mathscr C_X}\mathfrak D_C
 \ge X^{-\lambda_{\det}+o(1)},
\]
uniformly over all actual components, and gives the same conclusion by
\cref{cor:tpc67-componentwise-determinant-gap}; it avoids the irrelevant
product over mutually orthogonal collision components. This is likewise an
unproved L2 premise.

\subsection{What remains unavailable}
TPC-66's reduced pair-codegree theorem does not supply:
\begin{itemize}
\item a full-output Hall matching involving every active row;
\item lower bounds for matching pivots or their products;
\item a bound below one for the activity of an actual core;
\item control of long alternating cycles or \(\gamma\)-multiplicity;
\item a polynomial lower bound for \(\mathfrak D_X\), or, more usefully, a
uniform lower bound for \(\min_C\mathfrak D_C\) or for the corresponding
worst-component certified-minor mass.
\end{itemize}
Deleting difficult rows, replacing full outputs by reduced cells, or selecting
a generic coefficient filling would change the quantifier and is not allowed.

\subsection{Stop rules}
The following failures have different force.
\begin{enumerate}[label=(\roman*)]
\item A full-support Hall deficiency forces
\(\mathfrak D_X=0\). More generally, \(\mathfrak D_X=0\) is equivalent to
a genuine kernel for the represented map, even when the support satisfies
Hall's condition.
\item \(\mathcal A_\phi\ge1\) kills only the chosen
dominant-matching certificate. The same minor may still be nonsingular.
\item A small global product
\(\mathfrak D_X=\prod_C\mathfrak D_C\) alone is not a stop: many orthogonal
components can make that product exponentially small while every component
gap is good. Failure of one chosen certified-minor family gives a stop only
for that family. The present determinant conversion is genuinely too weak at
the desired fixed-power scale only if the \emph{actual} worst-component mass
\(\min_C\mathfrak D_C\), or the actual mass of the single connected component
under study, is proved to be \(X^{-\omega(1)}\). Even then it does not show
that the Gram gap is small. The connected path countermodel proves the latter
distinction sharply.
\end{enumerate}

\subsection{Route update for TPC-68}
The determinant door is now fully specified but still needs new physical
matching, pivot, and cycle-activity input. The next independent door is the
signed native/reassembly map, where the common residual M\"obius gauge has
already been removed and genuine two-affine signs first reappear. TPC-68
should isolate exact pair, star, and operator cancellation certificates there,
test them against the actual full-output normalization, and state a hard stop
if only support or generic-phase information is available. No parity,
fixed-\(2\), prime-pair, or twin-prime conclusion follows from the present
paper.
