\section{Exact decomposition by full-support collision components}
\label{sec:tpc67-componentwise}

The determinant mechanisms in the preceding sections can be tested one
actual collision component at a time, but the components must then be
reassembled with the correct quantifier.  This is an exact orthogonal
decomposition of the full matrix \(B_X\), not permission to retain only a
favorable component.

\subsection{The full-support row collision graph}

Define the row collision graph \(\mathscr G_X^{\mathrm{full}}\) on
\(\mathcal M_X^{\mathrm{act}}\) by
\begin{equation}
 m\sim n
 \quad\Longleftrightarrow\quad
 m\ne n
 \ \text{ and there is }y\in\mathcal Y_X^{\mathrm{full}}
 \text{ with }
 (B_X)_{y,m}(B_X)_{y,n}\ne0.
 \label{eq:tpc67-full-row-collision-graph}
\end{equation}
Let \(\mathscr C_X\) be its connected components.  Isolated active rows
are included as one-vertex components.  For \(C\in\mathscr C_X\), put
\begin{equation}
 \mathcal Y_C
 :=
 N_X^{\mathrm{full}}(C)
 =
 \{y:(B_X)_{y,m}\ne0
       \text{ for some }m\in C\},
 \label{eq:tpc67-component-output-set}
\end{equation}
and define the literal component matrix
\begin{equation}
 B_C:=B_X[\mathcal Y_C,C]:
 \ell^2(C)\longrightarrow\ell^2(\mathcal Y_C).
 \label{eq:tpc67-component-matrix}
\end{equation}

\begin{lemma}[Disjoint output support of distinct components]
\label{lem:tpc67-component-output-disjointness}
If \(C,C'\in\mathscr C_X\) and \(C\ne C'\), then
\begin{equation}
 \mathcal Y_C\cap\mathcal Y_{C'}=\varnothing.
 \label{eq:tpc67-disjoint-component-outputs}
\end{equation}
Moreover,
\begin{equation}
 \mathcal Y_X^{\mathrm{full}}
 =\bigsqcup_{C\in\mathscr C_X}\mathcal Y_C.
 \label{eq:tpc67-full-output-component-partition}
\end{equation}
\end{lemma}

\begin{proof}
If \(y\) belonged to both output sets, it would support nonzero entries
from rows \(m\in C\) and \(n\in C'\).  Then \(m\sim n\) in
\(\mathscr G_X^{\mathrm{full}}\), contradicting the assumption that the
rows lie in different components.  Every full output has a nonzero entry
by \eqref{eq:tpc67-full-output-set}, so it belongs to the output set of
the component containing that row.
\end{proof}

\begin{proposition}[Exact block diagonalization]
\label{prop:tpc67-exact-component-blocks}
After permutation of full-output and active-row coordinates,
\begin{align}
 B_X
 &=
 \bigoplus_{C\in\mathscr C_X}B_C,
 \label{eq:tpc67-B-component-sum}\\
 K_X=B_X^*B_X
 &=
 \bigoplus_{C\in\mathscr C_X}K_C,
 \qquad
 K_C:=B_C^*B_C.
 \label{eq:tpc67-K-component-sum}
\end{align}
Every column of every \(B_C\) still has norm one.
\end{proposition}

\begin{proof}
By \cref{lem:tpc67-component-output-disjointness}, a row in \(C\) has no
nonzero matrix entry in \(\mathcal Y_{C'}\) for \(C'\ne C\).  This proves
the first orthogonal direct-sum identity.  Taking the Gram gives the
second.  Component restriction removes no output touched by a column in
\(C\), so the unit-column identity
\eqref{eq:tpc67-unit-columns} remains unchanged.
\end{proof}

\subsection{Componentwise lower-frame and kernel reduction}

For each component put
\begin{equation}
 \beta_C:=\lambda_{\min}(K_C)
          =\sigma_{\min}(B_C)^2.
 \label{eq:tpc67-component-beta}
\end{equation}

\begin{theorem}[Exact componentwise lower-frame law]
\label{thm:tpc67-componentwise-lower-frame}
For \(x=\bigoplus_Cx_C\),
\begin{equation}
 \|B_Xx\|^2
 =
 \sum_{C\in\mathscr C_X}\|B_Cx_C\|^2.
 \label{eq:tpc67-component-energy-identity}
\end{equation}
Consequently,
\begin{align}
 \boxed{
 \beta_X
 =\min_{C\in\mathscr C_X}\beta_C,}
 \label{eq:tpc67-global-beta-minimum}\\
 \ker B_X
 &=
 \bigoplus_{C\in\mathscr C_X}\ker B_C,
 \label{eq:tpc67-kernel-component-sum}\\
 \dim\ker B_X
 &=
 \sum_{C\in\mathscr C_X}\dim\ker B_C.
 \label{eq:tpc67-nullity-component-sum}
\end{align}
In particular, \(B_X\) is injective if and only if every component matrix
\(B_C\) is injective.
\end{theorem}

\begin{proof}
Equation \eqref{eq:tpc67-component-energy-identity} is the squared-norm
identity for the orthogonal direct sum in
\eqref{eq:tpc67-B-component-sum}.  It gives the lower bound
\[
 \|B_Xx\|^2
 \ge
 \left(\min_C\beta_C\right)\sum_C\|x_C\|^2.
\]
Conversely, a unit vector supported on a component attaining the minimum
shows equality in \eqref{eq:tpc67-global-beta-minimum}.  The kernel and
nullity formulas follow from the same direct sum.
\end{proof}

Thus a component with a very good lower frame cannot compensate for one
singular component.  An isolated active row has \(\beta_C=1\), but this
does not raise the minimum if another component is bad.

\subsection{Support and rank defects factor componentwise}

For \(C\in\mathscr C_X\), define the local support Hall defect and literal
rank defect
by
\begin{align}
 \mathfrak h_C^{\mathrm{supp}}
 &:=
 \max_{S\subseteq C}
 \bigl(|S|-|N_X^{\mathrm{full}}(S)|\bigr)_+,
 \label{eq:tpc67-component-support-defect}\\
 \mathfrak h_C^{\mathrm{act}}
 &:=
 \max_{S\subseteq C}
 \left(
 |S|-\rank B_X[N_X^{\mathrm{full}}(S),S]
 \right).
 \label{eq:tpc67-component-actual-defect}
\end{align}

\begin{proposition}[Componentwise defect accounting]
\label{prop:tpc67-component-Hall-accounting}
The two global defects satisfy
\begin{align}
 \mathfrak h_X^{\mathrm{supp}}
 &=
 \sum_{C\in\mathscr C_X}
 \mathfrak h_C^{\mathrm{supp}},
 \label{eq:tpc67-support-defect-sum}\\
 \mathfrak h_X^{\mathrm{act}}
 &=
 \sum_{C\in\mathscr C_X}
 \mathfrak h_C^{\mathrm{act}}
 =
 \sum_{C\in\mathscr C_X}\dim\ker B_C.
 \label{eq:tpc67-actual-defect-sum}
\end{align}
Hence ordinary full-support Hall holds globally if and only if it holds
inside every component, and the literal full-rank condition from
\cref{thm:tpc67-actual-Hall-kernel} holds globally if and only if it holds
inside every component.
\end{proposition}

\begin{proof}
For \(S\subseteq\mathcal M_X^{\mathrm{act}}\), write
\(S_C=S\cap C\).  The component output sets are disjoint, so
\[
 |S|-|N_X^{\mathrm{full}}(S)|
 =
 \sum_C
 \left(
 |S_C|-|N_X^{\mathrm{full}}(S_C)|
 \right).
\]
Allowing \(S_C=\varnothing\) gives zero contribution, so maximizing the
positive deficiency independently in each component proves
\eqref{eq:tpc67-support-defect-sum}.  The rank-defect identity follows either
by the same block-rank calculation or from
\cref{thm:tpc67-actual-Hall-kernel,thm:tpc67-componentwise-lower-frame}.
\end{proof}

For \(C\in\mathscr C_X\), let \(r_C=|C|\) and define its literal full
determinant mass by
\begin{equation}
 \mathfrak D_C
 :=
 \sum_{\substack{I_C\subseteq\mathcal Y_C\\|I_C|=r_C}}
 |\det B_C[I_C]|^2.
 \label{eq:tpc67-component-determinant-mass}
\end{equation}

\begin{proposition}[Exact determinant-mass product]
\label{prop:tpc67-determinant-mass-product}
The full determinant mass factors as
\begin{equation}
 \boxed{
 \mathfrak D_X
 =
 \prod_{C\in\mathscr C_X}\mathfrak D_C.}
 \label{eq:tpc67-determinant-mass-factorization}
\end{equation}
Consequently \(\mathfrak D_X>0\) if and only if
\(\mathfrak D_C>0\) for every component.
\end{proposition}

\begin{proof}
Consider a full row set
\(I\subseteq\mathcal Y_X^{\mathrm{full}}\) with \(|I|=r_X\), and put
\(I_C=I\cap\mathcal Y_C\).  In the block matrix
\eqref{eq:tpc67-B-component-sum}, its determinant can be nonzero only if
\[
 |I_C|=r_C
 \qquad(C\in\mathscr C_X).
\]
Indeed, if one block is assigned fewer than \(r_C\) output rows, that
block cannot have full column rank; because the total numbers of selected
rows and columns agree, an excess in another block cannot repair this
deficit.  When all equalities hold, permutation to component order gives
\[
 |\det B_X[I]|^2
 =
 \prod_C|\det B_C[I_C]|^2.
\]
Summing independently over the \(I_C\)'s proves
\eqref{eq:tpc67-determinant-mass-factorization}.  This is a block-support
factorization; it does not reprove the preceding quantitative
Cauchy--Binet lower inequality.
\end{proof}

\begin{corollary}[Componentwise determinant conversion]
\label{cor:tpc67-componentwise-determinant-gap}
With \(c_r\) as in
\eqref{eq:tpc67-sharp-determinant-constant},
\begin{equation}
 \boxed{
 \beta_X
 \ge
 \min_{C\in\mathscr C_X}
 c_{r_C}\mathfrak D_C
 \ge
 e^{-1}\min_{C\in\mathscr C_X}\mathfrak D_C.}
 \label{eq:tpc67-componentwise-determinant-gap}
\end{equation}
More generally, suppose that for each component \(C\) a family
\(\mathscr I_C^{\mathrm{cert}}\) of literal full-column component minors has
certified lower bounds
\[
 I_C\in\mathscr I_C^{\mathrm{cert}},
 \qquad
 |\det B_C[I_C]|\ge\eta_C(I_C).
\]
Then
\begin{equation}
 \beta_X
 \ge
 \min_{C\in\mathscr C_X}
 c_{r_C}
 \sum_{I_C\in\mathscr I_C^{\mathrm{cert}}}\eta_C(I_C)^2.
 \label{eq:tpc67-componentwise-certified-mass}
\end{equation}
\end{corollary}

\begin{proof}
Every \(B_C\) has \(r_C\) unit columns by
\cref{prop:tpc67-exact-component-blocks}.  Cauchy--Binet gives
\(\mathfrak D_C=\det K_C\).  Apply
\cref{thm:tpc67-sharp-determinant-gap} to each component Gram and combine
the result with
\eqref{eq:tpc67-global-beta-minimum}.  Retaining only the certified
nonnegative component-minor summands proves the last formula.
\end{proof}

\begin{remark}[Why the componentwise conversion matters]
\label{rem:tpc67-componentwise-versus-product}
The global identity
\(\mathfrak D_X=\prod_C\mathfrak D_C\) can be exponentially smaller than
every individual component mass when the number of components grows.
Equation~\eqref{eq:tpc67-componentwise-determinant-gap} pays no such
gratuitous product: a uniform lower frame needs the worst component, not
the product of all component determinants.  This improvement is exact only
for the full-support coordinate components above; it does not authorize an
arbitrary row partition or deletion.
\end{remark}

\subsection{Full components are the mandatory scope}

The reduced projection
\((\gamma,s,j)\mapsto(s,j)\) can join two rows that occupy disjoint
\(\gamma\)-coordinates.  Therefore the reduced collision graph can merge
several components of \(\mathscr G_X^{\mathrm{full}}\).  It may be used as
an arithmetic supergraph, but it is not the graph whose connected
components produce the canonical coordinate block decomposition
\eqref{eq:tpc67-B-component-sum}.  In particular, reduced-cell codegree
does not alter the identities
\eqref{eq:tpc67-global-beta-minimum} or
\eqref{eq:tpc67-determinant-mass-factorization}.

\begin{remark}[No favorable-component selection]
\label{rem:tpc67-no-component-deletion}
The component partition is determined by the full actual nonzero support
after all active rows have been included and before a test vector is
chosen.  Passing to components is lossless because
\eqref{eq:tpc67-component-energy-identity} retains every summand.  A
uniform physical theorem must prove the desired estimate in every
component: the global lower frame is the minimum of the local constants,
the global kernel is their direct sum, and the determinant mass is their
product.  Deleting a singular or poorly conditioned component would
change the coefficient space and is not an L1 theorem for the original
physical map.

All results in this section are exact finite-dimensional L0 statements
for \(B_X\).  Their L1 content is solely that \(B_X\), its support graph,
and its components are the literal fixed-\(h_0\), full-output objects
from \cref{sec:tpc67-physical-minor-interface}.  No componentwise
positivity, polynomial determinant mass, parity gain, or prime-pair
conclusion is asserted.
\end{remark}
