\section{Forced peeling and the actual alternating-cycle core}
\label{sec:tpc67-forced-core}

This section is finite-dimensional.  Let
\[
 T=(t_{y,m})_{y\in\mathcal Y_0,\ m\in\mathcal M}
\]
be a square matrix, where
\(|\mathcal Y_0|=|\mathcal M|=r\).  In the arithmetic application \(T\)
is a full-column minor of the literal physical synthesis matrix: its rows
are actual full output coordinates and its columns are all active physical
rows.  None of the arguments below replaces those coefficients by generic
fillings.

The bipartite support graph \(\mathcal H(T)\) has parts
\(\mathcal M\) and \(\mathcal Y_0\), with \(m\sim y\) precisely when
\(t_{y,m}\ne0\).  We use the convention that the determinant of the empty
matrix is one.

\subsection{Exact two-sided degree-one peeling}

A degree-one vertex on either side of \(\mathcal H(T)\) forces its unique
incident edge in every nonzero determinant monomial.  Iterating this
observation gives an exact factorization, not merely a support reduction.

\begin{theorem}[Two-sided forced-peeling factorization]
\label{thm:tpc67-forced-peeling}
Choose any iterative procedure with the following rule.  Whenever the
current bipartite support graph has a degree-one vertex, delete that vertex,
its unique neighbor, and their incident edge.  Let
\(\mathcal P_{\mathrm{for}}\) be the ordered set of deleted edges, and let
\(T_{\mathrm{core}}\) be the square matrix left after the deletions.
Then there is a sign
\(\varepsilon_{\mathrm{for}}\in\{-1,1\}\) such that
\begin{equation}
 \boxed{
 \det T
 =
 \varepsilon_{\mathrm{for}}
 \left(\prod_{e\in\mathcal P_{\mathrm{for}}}t_e\right)
 \det T_{\mathrm{core}}.}
 \label{eq:tpc67-forced-factorization}
\end{equation}
If a zero-degree vertex occurs at any stage, then
\(\det T=0\).  Otherwise the final core is empty or every one of its
bipartite vertices has degree at least two.
\end{theorem}

\begin{proof}
Suppose first that a column vertex \(m\) has the unique neighbor \(y\).
Laplace expansion down column \(m\) gives
\[
 \det T=(-1)^{\iota(y)+\iota(m)}t_{y,m}
 \det T_{\widehat y,\widehat m},
\]
where the hats mean that the indicated row and column have been removed.
The same formula follows by expansion across a row when the degree-one
vertex is on the output side.  Iterating these identities proves
\eqref{eq:tpc67-forced-factorization}; all Laplace signs are absorbed into
\(\varepsilon_{\mathrm{for}}\).

A zero row or zero column makes the current determinant zero and hence,
through the preceding exact expansions, makes \(\det T=0\).  If no such
vertex occurs, termination without another degree-one vertex leaves either
the empty matrix or minimum degree at least two on both sides.
\end{proof}

\begin{remark}[Order and scope]
\label{rem:tpc67-peeling-order}
The factorization is valid for every chosen peeling order; no uniqueness of
the residual core is needed.  If the support admits a perfect matching,
every peeled edge belongs to every perfect matching of the current graph,
and the residual support again admits a perfect matching.  If no perfect
matching remains, its determinant is zero.  Thus order dependence cannot
turn a singular minor into a certified nonsingular one.
\end{remark}

\subsection{Normalization by one core matching}

Assume from now on that \(T_{\mathrm{core}}\) is nonempty and that its
support admits a perfect matching
\[
 \phi:V\longrightarrow\mathcal Y_{\mathrm{core}},
\]
where \(V\) indexes the core columns.  Reorder the core output rows so that
row \(i\) is \(\phi(i)\), and put
\begin{equation}
 p_i:=t_{\phi(i),i}\ne0,
 \qquad
 D_\phi:=\diag(p_i)_{i\in V}.
 \label{eq:tpc67-matching-pivots}
\end{equation}
The matching-normalized matrix is
\begin{equation}
 N_\phi
 :=
 \bigl(t_{\phi(i),j}\bigr)_{i,j\in V}D_\phi^{-1}
 =I+E_\phi,
 \label{eq:tpc67-matching-normalization}
\end{equation}
where
\begin{equation}
 (E_\phi)_{i,i}=0,
 \qquad
 (E_\phi)_{i,j}
 =
 \frac{t_{\phi(i),j}}{p_j}
 \quad(i\ne j).
 \label{eq:tpc67-normalized-offmatching-entry}
\end{equation}
Consequently,
\begin{equation}
 |\det T|
 =
 \left(\prod_{e\in\mathcal P_{\mathrm{for}}}|t_e|\right)
 \left(\prod_{i\in V}|p_i|\right)
 |\det(I+E_\phi)|.
 \label{eq:tpc67-full-core-normalization}
\end{equation}
The ratios in \eqref{eq:tpc67-normalized-offmatching-entry}, rather than the
unnormalized entry magnitudes alone, are the numerical data that control
the remaining cancellation.

\subsection{Exact alternating-cycle expansion}

Let \(\mathcal D_\phi\) be the directed graph on \(V\) having the arc
\(i\to j\) exactly when \(i\ne j\) and
\((E_\phi)_{i,j}\ne0\).  The arc \(i\to j\) represents the off-matching
bipartite edge joining row \(\phi(i)\) to column \(j\).  A directed cycle
\[
 C=(i_1\to i_2\to\cdots\to i_k\to i_1)
\]
therefore lifts to a bipartite cycle alternating, for each \(\nu\), the
off-matching and matching edges
\[
 \phi(i_\nu)\!-\!i_{\nu+1}
 \qquad\text{and}\qquad
 \phi(i_\nu)\!-\!i_\nu.
\]
Define its normalized complex weight by
\begin{equation}
 w_\phi(C)
 :=
 \prod_{\nu=1}^{k}(E_\phi)_{i_\nu,i_{\nu+1}},
 \qquad i_{k+1}:=i_1.
 \label{eq:tpc67-cycle-weight}
\end{equation}

Let \(\mathfrak F_\phi\) be the set of all nonempty families
\(\mathcal F\) of pairwise vertex-disjoint simple directed cycles in
\(\mathcal D_\phi\), and put
\[
 w_\phi(\mathcal F):=\prod_{C\in\mathcal F}w_\phi(C),
 \qquad
 |V(\mathcal F)|:=\sum_{C\in\mathcal F}|C|.
\]

\begin{theorem}[Determinant terms are disjoint alternating-cycle families]
\label{thm:tpc67-cycle-family-expansion}
There is a weight-preserving bijection between the nonidentity nonzero
permutation terms in \(\det(I+E_\phi)\) and the families in
\(\mathfrak F_\phi\).  Explicitly,
\begin{equation}
 \boxed{
 \det(I+E_\phi)
 =
 1+
 \sum_{\mathcal F\in\mathfrak F_\phi}
 (-1)^{|V(\mathcal F)|-|\mathcal F|}
 w_\phi(\mathcal F).}
 \label{eq:tpc67-exact-cycle-family-expansion}
\end{equation}
\end{theorem}

\begin{proof}
Expand the determinant over permutations of \(V\).  Because the diagonal
of \(E_\phi\) is zero, every fixed point of a permutation contributes the
diagonal entry one, while every moved vertex \(i\) contributes the arc
\(i\to\sigma(i)\).  The restriction of a permutation to its moved vertices
is uniquely a family of pairwise vertex-disjoint cycles of length at least
two.  Conversely, such a family, extended by the identity off its vertices,
is a unique permutation with a nonzero term.

A cycle of length \(k\) has permutation sign \((-1)^{k-1}\).
Multiplication over the cycles gives the sign
\[
 (-1)^{\sum_{C\in\mathcal F}(|C|-1)}
 =
 (-1)^{|V(\mathcal F)|-|\mathcal F|},
\]
and its matrix-entry product is \(w_\phi(\mathcal F)\).  This proves both
the bijection and \eqref{eq:tpc67-exact-cycle-family-expansion}.
\end{proof}

\begin{corollary}[Acyclic normalized core]
\label{cor:tpc67-acyclic-core}
If \(\mathcal D_\phi\) has no directed cycle, then
\[
 \det(I+E_\phi)=1
\]
and the chosen matching is the only perfect matching of the core support.
In particular, all possible determinant cancellation is confined to the
directed alternating-cycle families.
\end{corollary}

\begin{proof}
The sum in \eqref{eq:tpc67-exact-cycle-family-expansion} is empty.  The same
permutation--cycle correspondence shows that a second perfect matching
would produce a nonempty directed cycle family.
\end{proof}

\subsection{Diagonal similarity and the holonomy dimension}

For a diagonal unitary matrix
\[
 S=\diag(e^{i\theta_i})_{i\in V},
\]
the transformation
\begin{equation}
 I+E_\phi
 \longmapsto
 S^{-1}(I+E_\phi)S
 =
 I+S^{-1}E_\phi S
 \label{eq:tpc67-diagonal-similarity}
\end{equation}
preserves the determinant and every entry magnitude.  It changes an arc
phase by
\[
 \arg(E_{i,j})\longmapsto
 \arg(E_{i,j})-\theta_i+\theta_j,
\]
while every directed-cycle product
\eqref{eq:tpc67-cycle-weight} is unchanged.

Write
\[
 \mathcal E_{\mathrm{off}}
 :=
 \{(i,j):i\ne j,\ (E_\phi)_{i,j}\ne0\},
 \qquad q_\phi:=|\mathcal E_{\mathrm{off}}|,
\]
and let \(c_\phi\) be the number of weakly connected components of
\(\mathcal D_\phi\), isolated vertices included.

\begin{proposition}[Gauge reduction to chord phases]
\label{prop:tpc67-holonomy-dimension}
There is a diagonal unitary similarity for which the weights on a spanning
forest of the underlying weak graph are positive real.  Hence, after entry
magnitudes are fixed, at most
\begin{equation}
 \boxed{
 q_\phi-|V|+c_\phi}
 \label{eq:tpc67-holonomy-count}
\end{equation}
arc phases remain.  All phase dependence of the determinant factors through
these residual chord phases, and every directed alternating-cycle weight is
a gauge-invariant holonomy.
\end{proposition}

\begin{proof}
Choose one root in each weak component and a spanning forest containing
\(|V|-c_\phi\) directed arcs after their orientations are forgotten.
Starting at the roots, choose the vertex phases recursively so that the
selected arc joining each new vertex to the preceding tree is positive
real.  A forest imposes no inconsistent phase equation.  The selected
\(|V|-c_\phi\) phases have thereby been removed from the
\(q_\phi\) off-diagonal phases, leaving at most
\(q_\phi-|V|+c_\phi\).  Diagonal similarity preserves the determinant, and
the vertex phases telescope around every directed cycle, proving the last
assertion.
\end{proof}

\begin{remark}[L0 status and nonduplication with TPC--66]
\label{rem:tpc67-forced-core-L0}
The peeling factorization, matching normalization, exact cycle-family
expansion, and gauge count are L0 matrix theorems.  TPC--66 proved a
support-rank hierarchy, an exact formula on forest Gram graphs, and a
single uniform-cycle obstruction \citep{WangTPC66}.  The present result
does not repeat those statements: it factors an arbitrary square minor down
to its nonpeelable matching core and describes \emph{all} of that core's
determinant monomials by disjoint alternating-cycle families.

An L1 application must use an actual full-output minor, all active physical
rows, its literal nonzero pivots, and its literal coefficient ratios.
Nothing here proves that such a minor exists, that its forced-pivot product
is polynomially large, or that its residual holonomies are favorable.
\end{remark}
