\section{The literal full-output minor interface}
\label{sec:tpc67-physical-minor-interface}

TPC--65 identifies the represented lower-frame constant with the smallest
eigenvalue of the actual activated row Gram, and TPC--66 identifies the
literal row columns and their support geometry
\citep{WangTPC65,WangTPC66}.  We now fix the matrix on which every
determinant in this paper is computed.  The output coordinate remains the
complete physical key \((\gamma,s,j)\); no reduced-cell quotient is made
in the matrix definition.

\subsection{All active rows and all full outputs}

Fix \(X\), one nonzero shift \(h_0\), one declared source system, and all
external block, direct-residue, orbit, mask, profile, and endpoint data
before choosing a row vector.  Let \(\mathcal U_X\) be the actual nonzero
terminal atoms in this fixed scope.  For \(u\in\mathcal U_X\), write
\[
 a_u:=t_{h_0}(u)c_u\ne0
\]
for its literal coefficient, and retain its declared maps \(m(u)\), \(r(u)\),
\(j(u)\), and \(\gamma(u)\), together with the inherited row factor \(d_{m(u)}\).
Define
\[
 T_m:=\sum_{\substack{u\in\mathcal U_X\\m(u)=m}}|a_u|^2.
\]
Let
\[
 \mathcal M_X^{\mathrm{act}}
 :=\{m:T_m>0\}
\]
be the complete set of terminal-active physical rows.  For a full output
\[
 y=(\gamma,s,j),
\]
write the literal coherently summed row coefficient as
\begin{equation}
 a_{y,m}
 :=
 \sum_{\substack{u\in\mathcal U_X:\ q(u)=y\\m(u)=m}}
 a_u,
 \qquad
 q(u)=(\gamma(u),d_{m(u)}r(u),j(u)).
 \label{eq:tpc67-literal-full-row-entry}
\end{equation}
Every summand and every zero in
\eqref{eq:tpc67-literal-full-row-entry} belongs to the fixed physical
carrier.  On the declared source system, the row-singleton theorem of
TPC--66 says that the displayed sum is either empty or contains one
literal terminal atom.  In particular,
\begin{equation}
 T_m=\sum_y|a_{y,m}|^2
 \qquad(m\in\mathcal M_X^{\mathrm{act}}).
 \label{eq:tpc67-row-terminal-mass}
\end{equation}

Define the complete actual output set
\begin{equation}
 \mathcal Y_X^{\mathrm{full}}
 :=
 \{(\gamma,s,j):
   a_{(\gamma,s,j),m}\ne0
   \text{ for at least one }m\in\mathcal M_X^{\mathrm{act}}\}.
 \label{eq:tpc67-full-output-set}
\end{equation}
It contains every nonzero full output coordinate generated by every
active row.  Put
\[
 r_X:=|\mathcal M_X^{\mathrm{act}}|.
\]
If \(r_X=0\), the represented gate is empty and no lower-frame or
determinant constant is assigned.  Henceforth assume \(r_X\ge1\).

\begin{definition}[Literal normalized full-output matrix]
\label{def:tpc67-literal-B}
The matrix
\begin{equation}
 B_X:\ell^2(\mathcal M_X^{\mathrm{act}})
 \longrightarrow
 \ell^2(\mathcal Y_X^{\mathrm{full}})
 \label{eq:tpc67-B-map}
\end{equation}
has entries
\begin{equation}
 (B_X)_{y,m}:=\frac{a_{y,m}}{\sqrt{T_m}}.
 \label{eq:tpc67-normalized-B-entry}
\end{equation}
Its actual normalized Gram and lower-frame constant are
\begin{equation}
 K_X:=B_X^*B_X,
 \qquad
 \beta_X:=\lambda_{\min}(K_X)
          =\sigma_{\min}(B_X)^2.
 \label{eq:tpc67-full-Gram-and-beta}
\end{equation}
\end{definition}

Every column of \(B_X\) has norm one:
\begin{equation}
 \sum_{y\in\mathcal Y_X^{\mathrm{full}}}
 |(B_X)_{y,m}|^2=1.
 \label{eq:tpc67-unit-columns}
\end{equation}
If \(z\) is an original row coefficient vector and
\(x_m=\sqrt{T_m}z_m\), then the represented quotient relative to terminal
energy is
\[
 \frac{\|B_Xx\|^2}{\|x\|^2}.
\]
Thus \(\beta_X\) is exactly the TPC--65 activated-range constant on all
active rows, not the lower constant of a selected collision-free packet.

\subsection{Full minors and determinant mass}

Fix arbitrary orderings of
\(\mathcal M_X^{\mathrm{act}}\) and
\(\mathcal Y_X^{\mathrm{full}}\).  For
\(I\subseteq\mathcal Y_X^{\mathrm{full}}\) with \(|I|=r_X\), let
\begin{equation}
 B_X[I]
 :=
 \bigl((B_X)_{y,m}\bigr)_{
       y\in I,\ m\in\mathcal M_X^{\mathrm{act}}}
 \label{eq:tpc67-full-square-minor}
\end{equation}
be the square row restriction using every active physical row.  Define
\begin{align}
 \mathfrak d_X(I)
 &:=|\det B_X[I]|^2,
 \label{eq:tpc67-one-minor-mass}\\
 \mathfrak D_X
 &:=
 \sum_{\substack{I\subseteq\mathcal Y_X^{\mathrm{full}}\\|I|=r_X}}
 \mathfrak d_X(I).
 \label{eq:tpc67-full-determinant-mass}
\end{align}
The sum is zero when
\(|\mathcal Y_X^{\mathrm{full}}|<r_X\).  The adjective \emph{full}
means that a minor uses all active columns and literal full-output rows.
It does not mean that every output coordinate is retained in one square
minor.  The sum in \eqref{eq:tpc67-full-determinant-mass}, rather than an
adaptively chosen minor, is the canonical determinant mass.

\begin{proposition}[Actual rank criterion]
\label{prop:tpc67-actual-rank-criterion}
The following are equivalent:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item \(\mathfrak D_X>0\);
 \item at least one literal full minor \(B_X[I]\) is nonsingular;
 \item \(B_X\) has full column rank;
 \item \(\ker B_X=\{0\}\);
 \item \(K_X\) is positive definite, equivalently \(\beta_X>0\).
\end{enumerate}
\end{proposition}

\begin{proof}
The determinant mass is a finite sum of nonnegative numbers, so it is
positive exactly when one full minor is nonzero.  The ordinary rank-by-
minors criterion gives the equivalence with full column rank.  Finally,
\(\ker(B_X^*B_X)=\ker B_X\), which proves the last two equivalences.
No quantitative Cauchy--Binet lower inequality is used here.
\end{proof}

The later determinant-mass section will relate
\(\mathfrak D_X\) quantitatively to the lower spectrum.  We do not
anticipate or reprove that inequality in the interface.

\subsection{Support Hall defect versus the literal rank defect}

Let \(\mathscr H_X^{\mathrm{full}}\) be the bipartite support graph of
\(B_X\).  Its left vertices are
\(\mathcal M_X^{\mathrm{act}}\), its right vertices are
\(\mathcal Y_X^{\mathrm{full}}\), and
\[
 m\sim y
 \quad\Longleftrightarrow\quad
 (B_X)_{y,m}\ne0.
\]
For \(S\subseteq\mathcal M_X^{\mathrm{act}}\), let
\[
 N_X^{\mathrm{full}}(S)
 :=
 \{y:\text{there is }m\in S\text{ with }m\sim y\},
\]
and write
\[
 B_{X,S}
 :=
 B_X[
 N_X^{\mathrm{full}}(S),S]
 :
 \ell^2(S)\longrightarrow
 \ell^2(N_X^{\mathrm{full}}(S)).
\]
Define the support Hall defect and the literal rank defect:
\begin{align}
 \mathfrak h_X^{\mathrm{supp}}
&:=
 \max_{S\subseteq\mathcal M_X^{\mathrm{act}}}
 \bigl(|S|-|N_X^{\mathrm{full}}(S)|\bigr)_+,
 \label{eq:tpc67-support-Hall-defect}\\
 \mathfrak h_X^{\mathrm{act}}
 &:=
 \max_{S\subseteq\mathcal M_X^{\mathrm{act}}}
 \bigl(|S|-\rank B_{X,S}\bigr).
 \label{eq:tpc67-actual-Hall-defect}
\end{align}
Here \(x_+:=\max\{x,0\}\).  The first depends only on the full support.
The second uses the literal complex entries and is therefore an actual,
rather than generic, rank defect; despite the inherited symbol
\(\mathfrak h_X^{\mathrm{act}}\), it is not called a Hall defect.

\begin{theorem}[Literal rank-defect--kernel equivalence]
\label{thm:tpc67-actual-Hall-kernel}
One has
\begin{equation}
 \boxed{
 \mathfrak h_X^{\mathrm{supp}}
 \le
 \mathfrak h_X^{\mathrm{act}}
 =
 \dim\ker B_X
 =
 \dim\ker K_X.}
 \label{eq:tpc67-Hall-kernel-identity}
\end{equation}
Consequently the following are equivalent:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item \(\ker B_X=\{0\}\);
 \item for every \(S\subseteq\mathcal M_X^{\mathrm{act}}\),
       \(\rank B_{X,S}=|S|\);
 \item \(\mathfrak h_X^{\mathrm{act}}=0\);
 \item \(\mathfrak D_X>0\).
\end{enumerate}
Ordinary Hall inequalities
\begin{equation}
 |N_X^{\mathrm{full}}(S)|\ge|S|
 \qquad(S\subseteq\mathcal M_X^{\mathrm{act}})
 \label{eq:tpc67-ordinary-Hall}
\end{equation}
are necessary for these conditions but are not sufficient for the one
literal coefficient array.
\end{theorem}

\begin{proof}
Since
\(\rank B_{X,S}\le|N_X^{\mathrm{full}}(S)|\),
the first inequality in
\eqref{eq:tpc67-Hall-kernel-identity} follows.  The nullity of
\(B_{X,S}\) is
\[
 |S|-\rank B_{X,S}
 =
 \dim\{x\in\ker B_X:\supp x\subseteq S\},
 \]
and is therefore at most \(\dim\ker B_X\).  Taking
\(S=\mathcal M_X^{\mathrm{act}}\) gives equality, proving the middle
identity.  The Gram has the same kernel as \(B_X\).
The equivalences now follow from
\cref{prop:tpc67-actual-rank-criterion}.  A violation of
\eqref{eq:tpc67-ordinary-Hall} forces a positive support defect and hence
a kernel.  Conversely, cycle cancellation can give an actual kernel even
when all cardinal Hall inequalities hold, as already demonstrated at L0
in TPC--66.
\end{proof}

\subsection{Why reduced-cell codegree is auxiliary}

Let
\begin{equation}
 \pi:\mathcal Y_X^{\mathrm{full}}\longrightarrow
 \mathcal Y_X^{\mathrm{red}},
 \qquad
 \pi(\gamma,s,j)=(s,j).
 \label{eq:tpc67-full-to-reduced-projection}
\end{equation}
The TPC--66 arithmetic codegree bounds the number of reduced cells
\((s,j)\) in which a fixed pair of rows can meet.  This is useful for
locating possible nonzero Gram summands, but \(\pi\) can identify many
orthogonal \(\gamma\)-coordinates.  In particular:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=3em]
 \item a square matrix indexed by reduced cells is not a row restriction
       of \(B_X\);
\item a matching in the projection of the \emph{actual} full-support graph
       to distinct reduced cells has a support lift: choose one nonzero
       full coordinate over each matched incidence, and distinct reduced
       cells force the chosen full coordinates to be distinct.  This lift
       gives a support matching, not a numerical determinant lower bound,
       because other permutation terms may cancel it.  By contrast, a
       matching in the larger arithmetic supergraph used for the TPC--66
       codegree count need not have any literal nonzero lift;
 \item reduced Hall deficiency need not imply full Hall deficiency,
       because one reduced cell can have many full-output lifts; and
 \item reduced pair codegree does not determine
       \(\mathfrak D_X\), \(\ker B_X\), or \(\beta_X\).
\end{enumerate}
All full minors, neighborhoods, ranks, and kernels in this paper are
therefore computed before applying \(\pi\).  Reduced-cell codegree may
prune the list of possible full collisions; it never replaces their
literal \(\gamma\)-multiplicity or coefficient values.

\subsection{L1 quantifier ledger}
\label{subsec:tpc67-interface-ledger}

The arithmetic interface has the following fixed order of quantifiers.
\begin{enumerate}[label=\textup{(L1.\arabic*)},leftmargin=4em]
 \item Fix \(h_0\ne0\), \(X\), the source system, all multiscale/direct
       cells, residue and orbit classes, masks, profiles, and literal
       terminal support.
 \item Form the actual nonzero entries
       \eqref{eq:tpc67-literal-full-row-entry}, then retain
       \emph{every} row with \(T_m>0\) and every full output touched by
       those rows.
 \item Normalize columns only by their physical terminal masses \(T_m\).
       No fiber degree, row multiplicity, or reduced-cell multiplicity is
       absorbed into the norm.
 \item Construct the full support graph, all full minors, determinant
       mass, literal ranks and nullity, and support components from this fixed
       matrix, before testing any coefficient vector.
 \item Evaluate a lower-frame statement uniformly on the complete active
       row space.  A row with an inconvenient collision pattern is not
       deleted, and a favorable minor or component is not substituted for
       the full physical map.
\end{enumerate}

These are exact finite-\(X\) definitions and L0 matrix equivalences,
specialized at L1 to the literal fixed-\(h_0\) carrier.  They prove no
positive exposure lower bound, no polynomial lower bound for
\(\mathfrak D_X\) or \(\beta_X\), no parity estimate, and no prime-pair
conclusion.
