\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Soft Projective Reassembly of the Physical Row Mask: Orthogonal GCD Compression, Optimal Ferrers Separation, and Coherent Product-Slope Spectra},
 pdfauthor={Liang Wang},
 pdfsubject={A signed reassembly theorem and coherent spectral boundary for an orbit-sliced Mobius energy gate},
 pdfkeywords={Mobius correlation, projective tensor norm, Ferrers matrix, multiplicative characters, orbit energy, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\F}{\mathbb F}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cU}{\mathcal U}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\cX}{\mathcal X}
\newcommand{\cY}{\mathcal Y}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\op}{\operatorname{op}}
\newcommand{\pinf}{\pi_{\infty}}
\newcommand{\pplus}{\pi_{+}}

\title{\textbf{Soft Projective Reassembly of the Physical Row Mask:}\\
\textbf{Orthogonal GCD Compression, Optimal Ferrers Separation,}\\
\textbf{and Coherent Product--Slope Spectra}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
The preceding orbit--sliced analysis leaves a concrete interface question:
can the actual row-pair multiplier be reassembled into separable layers at
only \(X^{o(1)}\) cost, without destroying the product slope that carries
the multiplicative spectrum?  We answer the static part affirmatively and
locate the next obstruction exactly.

For a finite kernel \(K\), let \(\pinf(K)\) be its bounded projective norm.
The physical row mask is
\[
 \mathfrak m_{\rm act}(\alpha,\gamma)
 =\one_{\ell_\alpha\ne\ell_\gamma}
  \one_{|m_\alpha-m_\gamma|>\Delta}
  \one_{(d_\alpha,d_\gamma)\le G}.
\]
The same-source deletion has projective cost at most \(2\).  The near-row
deletion is a finite interval kernel and has cost \(O(\log(2Q))\).  For the
gcd threshold, an orthogonal random-sign compression of the exact divisor
projector gives
\[
 \pinf\!\left(\one_{(d,e)\le G}\right)
 \le(3+2\sqrt2)^{\omega_*},
 \qquad
 \omega_*:=\max_{\text{physical }d}\omega(d).
\]
Consequently
\[
 \boxed{
 \pinf(\mathfrak m_{\rm act})
 \ll\log(2Q)(3+2\sqrt2)^{\omega_*}=X^{o(1)}.}
\]
Together with the previously proved finite-residue and Mellin
separations, this closes the static controlled-multiplier boundary in the
retained TPC-32 factorization.  It is a projective-complexity theorem, not
an operator-norm bound for the physical Gram matrix.

Fixing the opposite row gives a stronger product-ready form.  The gcd and
same-source conditions become unary weights, while the near-row cutoff is
a difference of two Ferrers kernels.  After splitting the \(O_h(1)\)
fixed orbit residue cells, finite Fourier inversion therefore decomposes
each physical column exactly into
\[
 b_\rho(\ell)f_\rho(d)\eta_\rho(j)
\]
with \(O(D)\) discrete layers but total signed projective and orbit-seminorm
cost \(X^{o(1)}\); in particular \(b_\rho\) is independent of \(j\) and of
the complementary factor \(s\).  The logarithmic cost is optimal:
for \(T_n=(\one_{k\le r})\),
\[
 \pinf(T_n)\asymp\log(2n),
 \qquad
 \pplus(T_n)=n.
\]
Thus signed Fourier reassembly is essential, whereas positive or
raw column-by-column rectangle splitting is polynomially expensive.

Termwise additive-frequency separation of the product phase is costly.
For
\(A_r(x,y)=e_q(rxy)\) on \(\F_q^\times\), \(r\ne0\),
\[
 \boxed{
 \pinf(A_r)=\frac{(q-2)\sqrt q+1}{q-1}\asymp\sqrt q.}
\]
By contrast the multiplication kernel
\(\one_{xy=a}\) has projective cost exactly \(1\).  Expanding that kernel
additively and reassembling its frequencies absolutely manufactures a
\(\sqrt q\) amplitude loss, which at \(q\asymp J\) is precisely one factor
\(J\) in energy.

Finally, we diagonalize the coherent complementary-factor sum.  For the
TPC-35 product--slope operator \(T\) and an arbitrary weight \(w\),
\[
 \sum_j\left|\sum_sw(s)(Tb)(j,s)\right|^2
 =\frac1{q-1}\sum_\chi|\widehat b(\bar\chi)|^2
 \left|\sum_sw(s)\widehat R_s(\chi)\right|^2.
\]
If \(f,g\) are additively centered and \(w=1\), then
\[
 \sum_sR_s(a)=qg(0)f(-h/a),
\]
so complete \(s\)-coherence collapses to a residue-zero boundary trace.
Nevertheless the factor \(q-1\) from Cauchy in \(s\) is sharp in the
abstract centered nonprincipal class.  The remaining physical gate is
therefore not static-mask separation: it is the joint control of
incomplete \(s\)-weights, integer aliases, and the actual M\"obius
coefficient mass in the resulting character spectrum.  We prove no
coefficient-specific orbit gate, affine Chowla theorem, parity breach,
Hardy--Littlewood asymptotic, or twin--prime result.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; projective tensor norm;
Ferrers matrix; multiplicative character; orbit energy; parity boundary.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary 11L07,
15A18, 15B05.

\input{sections/introduction}
\input{sections/physical-interface}
\input{sections/projective-toolkit}
\input{sections/global-mask}
\input{sections/fixed-column}
\input{sections/optimality-boundaries}
\input{sections/coherent-spectrum}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
