\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cW}{\mathcal W}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\e}{\mathrm e}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\supp}{\operatorname{supp}}

\hypersetup{
  pdftitle={Fixed-Complexity Cell Survival and Sharp Concentration Obstructions for the TPC Static Mask},
  pdfauthor={Liang Wang},
  pdfsubject={Canonical pre-mask cellization, weighted survival, and sharp anti-concentration criteria},
  pdfkeywords={weighted mask survival, residue cells, Mellin separation, anti-concentration, projective tensor norm, parity problem}
}

\title{\bfseries Fixed-Complexity Cell Survival and\\
Sharp Concentration Obstructions\\
for the TPC Static Mask}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The preceding twin-prime-correlation (TPC) reduction left a precise
finite-dimensional question: does the literal static row mask retain
enough of the squared mass of the residue/Mellin cells to compare a
bounded-projective envelope with an atomic diagonal?  We first remove a
representation ambiguity.  Weighted survival is canonically attached
to a \emph{pre-mask} cell---the fixed-period residue and real-axis
Mellin factors are separated before the Fourier--Ferrers--gcd
representation of the static mask is introduced.  It is not an
invariant of an arbitrary final projective layer.

For a binary mask \(M\) and a nonzero right weight \(b\), let

\[
 \eta_M(b)=\max_\alpha
 \frac{\sum_{\gamma:M(\alpha,\gamma)=0}|b_\gamma|^2}
      {\|b\|_2^2}.
\]

We prove the exact minimax identity

\[
 \inf_{a\ne0}\delta_w(M;a,b)=1-\eta_M(b).
\]

For the TPC mask, the necessary-and-sufficient quantity \(\eta_M\) is
bounded by three explicit
anti-concentration numbers measuring mass on a single prime-source
fibre, in a determinant window of width
\(\Delta=QX^{-\kappa_0}\), and on a large-gcd fibre.  These are the
geometric sufficient quantities used below; they are individually
sharp, whereas their sum need not be necessary because the deleted
sets may overlap.

We then unpack the actual fixed-complexity provenance.  An identified
nondegenerate direct opposite-row cell has a fixed smooth dyadic shape,
a fixed admissible residue set, and unit-modulus residue and real-axis
Mellin phases.
Fixed-modulus prime and squarefree counts give uniformly

\[
 \operatorname{Flat}(b)=O(1).
\]

Together with the complete-row degree theorem, this yields

\[
 \delta_w(M;a,b)
 =1-O\!\left(L^{-1+o(1)}+D^{-1+o(1)}
                 +X^{-\kappa_0+o(1)}\right)
 =1-o(1)
\]

for every nonzero weight \(a\) on the other row, however sparse.
Hence, on this identified separated row-output face, the TPC--36 representation
has only \(X^{o(1)}\) projective-to-atomic energy distortion: the
active-cell survival gate consumes no polynomial part of the
\(1/400\) endpoint allowance.  An abstract finite-family selection
lemma gives the same survival conclusion for energetic cells under an
explicit aggregate lower-frame hypothesis, while controlling their
aggregate discarded cell energy.  It is not a frame theorem for the
signed continuous Mellin reassembly.

The distinction from the upper-only inherited interface is sharp.
Concentration on a same-source fibre, a near-product block, or a
large-gcd block produces polynomially large packets with zero survival;
adding one admitted neighbor gives positive survival as small as the
inverse packet size.  Such selectors require growing or shrinking
complexity and are not generated by the literal fixed-period,
fixed-shape, real-axis Mellin provenance.  The paper does not compare
the full signed TPC--48 profile envelope with the physical atomic
diagonal, prove a Mellin frame lower bound, control the coherent prime
square, group residual labels, or localize the frozen family back to
the physical shift.  No parity-barrier breach or twin-prime conclusion
is claimed.
\end{abstract}

\noindent\textbf{Keywords:} weighted mask survival; residue cells;
Mellin separation; anti-concentration; projective tensor norm;
determinant equations; sieve parity.

\medskip
\noindent\textbf{Convention.}
All finite weights may be complex; survival depends only on their
moduli.  Zero cells are deleted.  Constants may depend on the fixed
shift, fixed residue moduli, and fixed smooth shapes, but never on the
real Mellin parameters or on \(X\).

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 46B28; Secondary 11N37,
15A18, 42A10.

\input{sections/introduction}
\input{sections/canonical-interface}
\input{sections/exact-concentration}
\input{sections/frame-selection}
\input{sections/physical-cell-survival}
\input{sections/sharp-obstructions}
\input{sections/endpoint-boundaries}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
