\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\E}{\mathbb E}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cW}{\mathcal W}
\newcommand{\one}{\mathbf 1}
\newcommand{\e}{\mathrm e}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\sfk}{\operatorname{sf}}

\hypersetup{
  pdftitle={Mesoscopic Shift-Spectral Gaps and Tensor-Normalization Barriers for Three-Coefficient Determinant Packets},
  pdfauthor={Liang Wang},
  pdfsubject={Shift spectral structure and atomic-energy barriers at the TPC determinant interface},
  pdfkeywords={Mobius function, determinant equation, shift spectrum, Poisson summation, Bohr transform, tensor norm, parity problem}
}

\title{\bfseries Mesoscopic Shift--Spectral Gaps and\\
Tensor--Normalization Barriers for\\
Three--Coefficient Determinant Packets}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The large-prime reduction in the twin-prime-correlation (TPC) sequence
admits scalar projective layers of the form \(pr-mj=h\), with separated
arithmetic weights on the prime \(p\), a M\"obius cofactor \(r\), and
an actual source variable \(m\), while the orbit variable \(j\) is
smooth up to a fixed residue-class selector.  The physical Hilbert
dual later recouples these variables.  We separate three
questions that are lost if this is described
only as a ``third-coefficient problem.''  First, multiplicative
synthesis and Cauchy--Schwarz close the scalar fixed-shift form, and a
Fourier--Bohr lift also closes the residual label \(s=d(m)r\), at the
Cartesian tensor-energy scale.  That scale is the sum of the atomic
diagonals over all shifts, not the physical diagonal at one shift;
flat boxes and an explicit fixed-shift construction show that the two
normalizations may differ by a polynomial factor.  Second, Poisson
summation in the smooth orbit slot gives the exact kernel
\(K_m(\alpha)=J\sum_k\widehat w(J(k-m\alpha))\).  Band-limited orbit
weights therefore produce a genuine shift-spectral gap between the
geometric envelope and the first sampling aliases.  At the TPC endpoint
this gap is \(X^{-1+o(1)}<\|\alpha\|<X^{-267/400+o(1)}\); corresponding
band-pass averages vanish, and low-pass averages have an exact main
term.  Restriction to any fixed orbit progression preserves this
exponent gap.  Third, weighted shift averaging leaves the exact
fiber-grouping norm unchanged when numerator and diagonal use the same
weights.
Moreover, sparse TPC alias sampling folds the full shift spectrum, and
the currently proved collision-free local-label range does not reach
the Poisson scale.  Thus the paper proves a deterministic spectral
advance and identifies atomic normalization, orbit-output coupling, alias
folding, and fixed-shift localization as separate remaining gates.  No
fixed-shift TPC closure, parity breach, or twin-prime conclusion is
claimed.
\end{abstract}

\noindent\textbf{Keywords:} determinant equation; shift spectrum;
M\"obius correlation; Poisson summation; Fourier--Bohr transform;
tensor normalization; parity problem.

\medskip
\noindent\textbf{Convention.}
We write \(\e(x)=\exp(2\pi i x)\), identify
\(\T=\R/\Z\), and put
\(\|\alpha\|_{\T}=\min_{k\in\Z}|\alpha-k|\).
All arithmetic supports at one scale are finite.  Fourier transforms on
\(\R\) use
\(\widehat f(\xi)=\int_{\R}f(x)\e(-x\xi)\,dx\).

\medskip
\noindent\textbf{MSC 2020:} Primary 11L07, 11N35; Secondary 42A38,
46B28, 11N36.

\input{sections/introduction}
\input{sections/tpc-interface}
\input{sections/determinant-model}
\input{sections/tensor-closure}
\input{sections/bohr-parseval}
\input{sections/shift-spectrum}
\input{sections/poisson-averages}
\input{sections/atomic-boundaries}
\input{sections/alias-localization}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
