\section{Finite dynamics, exact certificate, and conclusion}
\label{sec:tpc20-certificate-conclusion}

The word \emph{spectrum} in this paper has a finite and literal
dynamical meaning.  For each divisor pair, translation
\begin{equation}
 \tau:j\longmapsto j+1
 \qquad\text{on }\Z/(H[u,v])\Z
 \label{eq:tpc20-cyclic-shift}
\end{equation}
is a finite measure-preserving dynamical system.  Its Koopman
characters are \(e_{H[u,v]}(rj)\), and the coefficients computed in
\cref{thm:tpc20-four-channel-coefficients} are exactly the spectral coordinates
of the centered local divisor observable.  The Poisson step couples
these finite cyclic spectra to the smooth orbit window, while
\cref{thm:tpc20-fiber-DFT} reorganizes the compatible row weights on a
single CRT fiber.  This terminology does not assert a spectral
realization of the zeros of the Riemann zeta function.

\subsection{Exact computational certificate}

The standard-library Python certificate is located at
\begin{center}
 \texttt{experiments/tpc20\_certificate.py}.
\end{center}
Run it from the paper directory with
\begin{verbatim}
python experiments/tpc20_certificate.py
python -O experiments/tpc20_certificate.py
\end{verbatim}
Both commands regenerate the deterministic file
\texttt{experiments/tpc20\_certificate.json}.  The proof checks use
integers, \texttt{fractions.Fraction}, formal prime-log polynomials, and
finite prime fields containing roots of the exact required orders.
They verify independently sampled instances of:
\begin{enumerate}[label=\textnormal{(\roman*)}]
 \item the pointwise four-channel recombination into the single
 coefficient \(b_R\), including its scalar calibration term;
 \item the primitive complete-period zero mode and its termwise
 disappearance for every coprime divisor pair;
 \item the full four-term Fourier formula, the aligned multiplier
 \(B_{g,a,b}\), its frequency counts and exact energy, and the kernel
 Plancherel identity;
 \item the CRT-fiber parametrization, finite Fourier transform,
 Parseval formula, and mean--discrepancy decomposition;
 \item the squarefree sign migration, completion exponent ledger, and
 the convolution identity underlying the uniform calibration theorem.
\end{enumerate}
The certificate is a regression test for finite algebra; it is not
numerical evidence for the unproved fiber-discrepancy estimate.  Its
JSON therefore records
\begin{center}
 \texttt{twin\_prime\_evidence = false},\qquad
 \texttt{residual\_dispersion\_evidence = false},\\
 \texttt{asymptotic\_evidence = false}.
\end{center}
Its diagnostic scope also excludes a parity-barrier breakthrough.

At the version archived with this paper, the generated JSON has
SHA-256
\begin{center}
 \texttt{0F994F32950AC68B8249D2F90E7074176106C122A2AE53268370F03584B7C12B},
\end{center}
and the script has SHA-256
\begin{center}
 \texttt{55D9FA7DD4277C541ABE39C53231453F7F6A9107DEF40103F5227373B53E0174}.
\end{center}

\subsection{Conclusion}

TPC-20 supplies the matched reduction that TPC-19 left open.  The
prime--prime, prime--model, model--prime, and model--model channels combine
pointwise into one centered divisor kernel with one residual
coefficient.  A uniform M\"obius theorem makes the finite calibration
defect arbitrarily logarithmically small throughout polynomial row
ranges, and \cref{cor:tpc20-calibration-negligible} makes it negligible
at packet scale under its explicit packet hypotheses, which hold for the
separated packets in the single-leg range.  The resulting
primitive-conditional zero mode is connected, and the zero mode of
every coprime divisor pair vanishes before any triangle inequality is
applied.

The exact Fourier calculation then separates genuinely different
period scales.  Completing the two single legs at periods \(Hu\) and
\(Hv\), rather than artificially at \(H[u,v]\), identifies uniform
single-leg completion up to
\(Q\le X^{1/2+\delta-\eta_0}\), beyond the older whole-joint-period
completion range \(Q\le X^{2\delta-\eta_0}\).  This removes two spurious long
spectra.  It does not cancel the surviving joint packet: on its low
nonzero frequencies the aligned multiplier equals \(g=(u,v)\).

Finally, the apparent triple inverse phase of TPC-19 is one ordinary
DFT after compatible row pairs are grouped by their joint CRT class.
The transform splits exactly into a Ramanujan mean packet and a fiber
discrepancy, with Parseval identifying the full discrepancy energy.
For this chosen compatible short--short packet, the remaining
obligations are concrete: prove the weighted restricted-frequency fiber
gate (or an explicitly normed low-rank substitute) for the actual sharp
M\"obius row weights, and separately control the Ramanujan mean.  The
cited separated Kloosterman-fraction and frequency-concentration
results do not automatically provide either input.  The large-divisor
legs remain outside this reduction.

Thus this paper advances the route by an exact common-channel
compression, a wider unconditional single-leg completion range, and a
sharply formulated coefficient gate.  It does not estimate the full TPC-18
residual, prove a fixed-shift Hardy--Littlewood asymptotic or a
twin-prime lower bound, breach the sieve parity barrier, or realize
zeta zeros as dynamical eigenvalues.
