\section{CRT-fiber compression and the exact remaining gate}
\label{sec:tpc20-fiber-compression}

We now compress the compatible joint inverse phases.  Throughout this
section the row and orbit weights have first been separated as in the
smooth-separation step of the TPC interface, so that the same function
\(F(j/J)\) occurs for every row pair in one packet.  The separated row
weights are absorbed into coefficients \(z_{m_1,m_2}\).  The argument is
exact for each separated packet; the usual rapidly convergent
superposition may be restored afterwards.

Fix \(u,v\) with \((uv,H)=1\), put \(q=[u,v]\), and let
\(\mathscr R_{u,v}\) be any finite set of row pairs such that
\((u,m_1)=(v,m_2)=1\) for every
\((m_1,m_2)\in\mathscr R_{u,v}\), including any generic pruning
independent of \(j\).  Retain only the compatible pairs
\(g\mid m_1-m_2\).

\begin{lemma}[Compatible row residues are CRT fibers]
\label{lem:tpc20-row-fiber-bijection}
The map which assigns to a compatible row pair its joint class
\(\kappa\bmod q\) takes values in
\begin{equation}
 \mathcal U_q=(\mathbb Z/q\mathbb Z)^{\times}.
 \label{eq:tpc20-unit-fibers}
\end{equation}
Conversely, a class \(\kappa\in\mathcal U_q\) determines the unique
compatible pair of row residue classes
\begin{equation}
 m_1\equiv-h\overline\kappa\pmod u,
 \qquad
 m_2\equiv-h\overline\kappa\pmod v.
 \label{eq:tpc20-row-residue-from-kappa}
\end{equation}
Thus compatible pairs of row residue classes are in bijection with
\(\mathcal U_q\).
\end{lemma}

\begin{proof}
The forward statement is
\cref{lem:tpc20-primitive-compatibility}.  Conversely,
\eqref{eq:tpc20-row-residue-from-kappa} makes
\(m_i\kappa\equiv-h\) in the required modulus.  The two resulting
classes are units and are compatible by construction.  Inversion modulo
\(u\) and \(v\) shows uniqueness.
\end{proof}

Define the fiber coefficient
\begin{equation}
 Z_{u,v}(\kappa)
 =\sum_{\substack{(m_1,m_2)\in\mathscr R_{u,v}\\
 m_1\equiv-h\overline\kappa\ (\bmod u)\\
 m_2\equiv-h\overline\kappa\ (\bmod v)}}
 z_{m_1,m_2},
 \qquad \kappa\in\mathcal U_q,
 \label{eq:tpc20-fiber-coefficient}
\end{equation}
and its joint phase packet
\begin{equation}
 S_{u,v}(r)
 =\sum_{\kappa\in\mathcal U_q}
 Z_{u,v}(\kappa)e_q(r\overline H\kappa).
 \label{eq:tpc20-fiber-DFT}
\end{equation}

\begin{theorem}[Triple inverse phases compress to one DFT]
\label{thm:tpc20-fiber-DFT}
The sum over compatible row pairs of the joint Poisson phase is exactly
\(S_{u,v}(r)\).  If \(u\) and \(v\) are squarefree, as they are on both
the \(\lambda'_R\)- and \(b_R\)-supports, then in the coordinates
\(u=ga\), \(v=gb\) the integers \(g,a,b\) are pairwise coprime and each
summand may equivalently be written as
\begin{align}
 e_q(r\overline H\kappa)
 ={}&e_g\!\left(-hr\overline H\,\overline{m_1}\,
                 \overline{ab}\right)
 e_a\!\left(-hr\overline H\,\overline{m_1}\,
                 \overline{gb}\right)
 \notag\\
 &\times
 e_b\!\left(-hr\overline H\,\overline{m_2}\,
                 \overline{ga}\right).
 \label{eq:tpc20-three-phase-factorization}
\end{align}
with a modulus-one factor interpreted as \(1\).
Thus the three displayed inverse phases are the CRT factorization of one
ordinary Fourier character, not three independent spectra.  Moreover,
\begin{equation}
 \boxed{
 \sum_{r\bmod q}|S_{u,v}(r)|^2
 =q\sum_{\kappa\in\mathcal U_q}|Z_{u,v}(\kappa)|^2.}
 \label{eq:tpc20-fiber-parseval}
\end{equation}
\end{theorem}

\begin{proof}
The first assertion follows by grouping the row pairs according to the
bijection in \cref{lem:tpc20-row-fiber-bijection}.  Under the stated
squarefree hypothesis, the factorization in
\eqref{eq:tpc20-three-phase-factorization} is CRT factorization of the
character modulo the pairwise coprime moduli \(g,a,b\), followed by
\(m_i\kappa\equiv-h\) in the appropriate factors.  Finally,
\(r\mapsto r\overline H\) permutes the frequencies modulo \(q\), so
ordinary finite-group Parseval proves \eqref{eq:tpc20-fiber-parseval}.
\end{proof}

All pairs \((u,v)\) with the same least common multiple may be combined
before estimation.  In the single-leg range of
\cref{cor:tpc20-whole-single-range}, let \(\vartheta_R(u)\) denote either
the finite-model coefficient \(\lambda'_R(u)\), or the matched
short--short residual coefficient \(b_R(u)\one_{u\le R}\), and put
\begin{equation}
 Z_q(\kappa)
 =\sum_{\substack{u,v\le R\\\operatorname{lcm}(u,v)=q}}
 \vartheta_R(u)\vartheta_R(v)Z_{u,v}(\kappa),
 \label{eq:tpc20-aggregated-fiber}
\end{equation}
where an inadmissible row-modulus pair contributes zero.  Define
\begin{equation}
 S_q(r)=\sum_{\kappa\in\mathcal U_q}
 Z_q(\kappa)e_q(r\overline H\kappa).
 \label{eq:tpc20-aggregated-DFT}
\end{equation}
Then the compatible long-joint contribution at this denominator is
\begin{equation}
 \mathcal L_q
 =\frac{J}{Hq}\sum_{r\ne0}
 c_H(r)\widehat F\!\left(\frac{rJ}{Hq}\right)S_q(r).
 \label{eq:tpc20-long-q-packet}
\end{equation}
This formula is a normal form for the chosen short--short joint
remainder.  In the residual application it does not include the
large-divisor legs \(u>R\) or \(v>R\).

\begin{theorem}[Ramanujan mean and fiber discrepancy]
\label{thm:tpc20-mean-discrepancy}
Put
\begin{equation}
 \overline Z_q
 =\frac1{\varphi(q)}\sum_{\kappa\in\mathcal U_q}Z_q(\kappa),
 \qquad
 D_q(\kappa)=Z_q(\kappa)-\overline Z_q.
 \label{eq:tpc20-fiber-mean-discrepancy}
\end{equation}
Then
\begin{equation}
 S_q(r)
 =\overline Z_q c_q(r)
 +\sum_{\kappa\in\mathcal U_q}
 D_q(\kappa)e_q(r\overline H\kappa),
 \label{eq:tpc20-DFT-mean-split}
\end{equation}
and
\begin{equation}
 \boxed{
 \sum_{r\bmod q}
 |S_q(r)-\overline Z_qc_q(r)|^2
 =q\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|^2.}
 \label{eq:tpc20-discrepancy-parseval}
\end{equation}
Since \((H,q)=1\), the deterministic part of
\eqref{eq:tpc20-long-q-packet} is the one-modulus Ramanujan packet
\begin{equation}
 \mathcal L_q^{\mathrm{mean}}
 =\overline Z_q\frac{J}{Hq}\sum_{r\ne0}
 c_{Hq}(r)\widehat F\!\left(\frac{rJ}{Hq}\right).
 \label{eq:tpc20-Ramanujan-mean-packet}
\end{equation}
\end{theorem}

\begin{proof}
Insert \(Z_q=\overline Z_q+D_q\) in
\eqref{eq:tpc20-aggregated-DFT}.  The Fourier transform of the constant
function on \(\mathcal U_q\) is \(c_q(r\overline H)=c_q(r)\).  Parseval
applied to \(D_q\), extended by zero off \(\mathcal U_q\), gives
\eqref{eq:tpc20-discrepancy-parseval}.  Multiplicativity of Ramanujan
sums for coprime moduli gives \(c_H(r)c_q(r)=c_{Hq}(r)\).
\end{proof}

\begin{proposition}[Restricted-frequency fiber bound]
\label{prop:tpc20-restricted-fiber-bound}
Fix \(\epsilon>0\) and suppose
\begin{equation}
 J\ge 4HX^\epsilon.
 \label{eq:tpc20-no-frequency-wrap}
\end{equation}
Write \(\mathcal L_{q,\le N}^{\mathrm{disc}}\) for the discrepancy
part of \eqref{eq:tpc20-long-q-packet} truncated at
\begin{equation}
 0<|r|\le N_{q,\epsilon}=X^\epsilon\frac{Hq}{J},
 \label{eq:tpc20-fiber-window}
\end{equation}
Then
\begin{equation}
 \boxed{
 |\mathcal L_{q,\le N}^{\mathrm{disc}}|
 \ll_{H,F,\epsilon}
 X^{\epsilon/2}\sqrt{\frac JH}
 \left(\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|^2\right)^{1/2}}
 \label{eq:tpc20-restricted-fiber-bound}
\end{equation}
and, for every \(A>0\),
\begin{equation}
 \mathcal L_q^{\mathrm{disc}}
 =\mathcal L_{q,\le N}^{\mathrm{disc}}
 +O_{A,F,H,\epsilon}\!\left(
 X^{-A}\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|\right).
 \label{eq:tpc20-fiber-tail-error}
\end{equation}
Let \(\mathcal Q\) be a family of long denominators and assume, for some
fixed \(C_0\), the explicit polynomial mass bound
\begin{equation}
 \sum_{q\in\mathcal Q}\sum_{\kappa\in\mathcal U_q}
 |D_q(\kappa)|\ll X^{C_0}.
 \label{eq:tpc20-fiber-tail-mass}
\end{equation}
Then a sufficient discrepancy input is
\begin{equation}
 \sum_{q\in\mathcal Q}
 \left(\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|^2\right)^{1/2}
 \ll X^{-\epsilon}\frac{XQ}{\sqrt J}(\log X)^{-B},
 \label{eq:tpc20-fiber-gate}
\end{equation}
with the harmless power of \(X^\epsilon\) adjusted as needed.  This
controls only the discrepancy packets; the Ramanujan mean packets in
\eqref{eq:tpc20-Ramanujan-mean-packet} remain separate.
\end{proposition}

\begin{proof}
Rapid decay of \(\widehat F\), the trivial bound
\[
 \left|\sum_{\kappa\in\mathcal U_q}
 D_q(\kappa)e_q(r\overline H\kappa)\right|
 \le\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|,
\]
and summation of the Fourier tail give
\eqref{eq:tpc20-fiber-tail-error}.  Under
\eqref{eq:tpc20-no-frequency-wrap}, the retained positive and negative
integers occupy distinct classes modulo \(q\).  Cauchy-Schwarz,
\(|c_H(r)|\ll_H1\), and
\eqref{eq:tpc20-discrepancy-parseval} give
\begin{align*}
 |\mathcal L_{q,\le N}^{\mathrm{disc}}|
 &\ll_H\frac{J}{Hq}N_{q,\epsilon}^{1/2}
 \left(q\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|^2\right)^{1/2}\\
 &\ll_H X^{\epsilon/2}\sqrt{\frac JH}
 \left(\sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|^2\right)^{1/2}.
\end{align*}
Summation over \(q\) proves the sufficient gate after choosing the
epsilon bookkeeping with the required margin.  Equation
\eqref{eq:tpc20-fiber-tail-mass} makes the summed tails negligible by
taking \(A>C_0+B+1\) in \eqref{eq:tpc20-fiber-tail-error}.
\end{proof}

The Ramanujan mean has a revealing interaction with the transverse
M\"obius sign.  The following identity applies to each fixed
squarefree \((u,v)\)-summand before the lcm aggregation in
\eqref{eq:tpc20-aggregated-fiber}; it is not an estimate.

\begin{proposition}[Migration of the transverse sign]
\label{prop:tpc20-sign-migration}
Assume \(q=gab\) is squarefree with \(g,a,b\) pairwise coprime.  Put
\begin{equation}
 d_g=(r,g),\qquad d_a=(r,a),\qquad d_b=(r,b).
 \label{eq:tpc20-frequency-contents}
\end{equation}
Then
\begin{equation}
 \boxed{
 \mu(a)\mu(b)c_{gab}(r)
 =\mu(g/d_g)\mu(d_a)\mu(d_b)
  \varphi(d_gd_ad_b).}
 \label{eq:tpc20-sign-migration}
\end{equation}
In particular,
\begin{equation}
 (r,gab)=1
 \quad\Longrightarrow\quad
 \mu(a)\mu(b)c_{gab}(r)=\mu(g).
 \label{eq:tpc20-coprime-sign-migration}
\end{equation}
Thus fiber-uniformity of a fixed squarefree \((u,v)\)-summand does not
preserve its transverse M\"obius sign; on frequencies coprime to \(q\),
that sign is transferred to the associated determinant content
\(g=(u,v)\).  No single-\(g\) conclusion is asserted after summing over
all decompositions of \(q\).
\end{proposition}

\begin{proof}
For squarefree \(q\),
\[
 c_q(r)=\mu\!\left(\frac{q}{(q,r)}\right)\varphi((q,r)).
\]
Factor this formula over the pairwise coprime integers \(g,a,b\).  Since
\(\mu(a)\mu(a/d_a)=\mu(d_a)\), and similarly for \(b\), one obtains
\eqref{eq:tpc20-sign-migration}.
\end{proof}

\begin{proposition}[Sharp algebraic no-go for arbitrary fibers]
\label{prop:tpc20-fiber-nogo}
CRT compression alone implies neither uniform pointwise decay of the
restricted discrepancy transform nor a restricted-frequency saving for
arbitrary fiber vectors.  Indeed, if an admissible coefficient
vector is supported on one class \(\kappa_0\in\mathcal U_q\), say
\(Z_q=A\one_{\{\kappa_0\}}\), then
\begin{equation}
 |S_q(r)|=|Z_q(\kappa_0)|
 \qquad\text{for every }r.
 \label{eq:tpc20-one-fiber-saturation}
\end{equation}
Moreover its mean-zero discrepancy transform is
\begin{equation}
 \widehat D_q(r)
 =A\left(
 e_q(r\overline H\kappa_0)-\frac{c_q(r)}{\varphi(q)}
 \right).
 \label{eq:tpc20-one-fiber-discrepancy}
\end{equation}
If \(\varphi(q)>1\) and \((r,q)=1\), then
\begin{equation}
 |\widehat D_q(r)|
 \ge |A|\left(1-\frac1{\varphi(q)}\right).
 \label{eq:tpc20-one-fiber-discrepancy-lower}
\end{equation}
Thus a nonempty retained window, which contains the coprime frequency
\(r=1\), can still carry order-\(|A|\) discrepancy.
Its uncentered Fourier energy is exactly \(q|A|^2\), distributed
uniformly over all \(q\) frequencies.  A useful improvement of
\eqref{eq:tpc20-restricted-fiber-bound} requires an arithmetic bound for
the actual row-fiber discrepancy, or a separable low-rank decomposition
whose coefficient cost is controlled.
\end{proposition}

\begin{proof}
For a one-fiber vector,
\(S_q(r)=Z_q(\kappa_0)e_q(r\overline H\kappa_0)\).  This proves
\eqref{eq:tpc20-one-fiber-saturation} and equality in the corresponding
Parseval identity.  Subtracting the unit-class mean gives
\eqref{eq:tpc20-one-fiber-discrepancy}.  When \((r,q)=1\),
\(c_q(r)=\mu(q)\), so the reverse triangle inequality proves
\eqref{eq:tpc20-one-fiber-discrepancy-lower}.
\end{proof}

\begin{remark}[Why a generic additive large sieve does not close the gate]
\label{rem:tpc20-generic-large-sieve-nogo}
For denominators \(q\asymp Q_0\), the relevant dual length is
\(N\asymp HQ_0/J\), whereas generic Farey spacing costs \(Q_0^2\).
Thus the standard large-sieve constant \(N+Q_0^2\) is dominated by
\(Q_0^2\) in the present low-frequency regime.  Likewise, existing
bilinear or trilinear Kloosterman bounds require a separated coefficient
array and do not accept an arbitrary modulus-dependent vector
\(Z_q(\kappa)\).  The exact new gate is therefore a quantitative
equidistribution or controlled-rank theorem for the actual
prime-M\"obius row fibers, together with control or matching of the
explicit Ramanujan mean packet.
\end{remark}

\begin{remark}[Scope of the compression]
\label{rem:tpc20-fiber-scope}
The compression theorem applies to a separated compatible joint packet.
In the intermediate range of
\cref{cor:tpc20-whole-single-range}, it describes the only nonzero
spectrum left in the chosen short--short block after single-leg
completion.  It does not by itself estimate that packet, control the
large-divisor legs of the common residual coefficient, or prove the
all-modulus primitive residual-dispersion target.
\end{remark}
