\section{Introduction}
\label{sec:tpc20-introduction}

TPC-18 reduces a failed symmetric fixed-shift tail block to a primitive,
generic two-row correlation of the residual
\(
 r_R=\Lambda-\Lambda_R
\), where
\[
 \Lambda_R(n)=\sum_{q\le R}\frac{\mu(q)}{\varphi(q)}c_q(n)
\]
and the row determinant is \(h(m_1-m_2)\)
\citep{WangTPC18}.  TPC-19 then gives exact divisor and Poisson normal
forms for this correlation \citep{WangTPC19}.  It also records a crucial
negative fact: the centered model--model channel can have a nonzero
complete-period mean on a primitive, distinct-source row pair.  A proof
cannot therefore estimate
\[
 PP,\qquad PM,\qquad MP,\qquad MM
\]
independently after taking absolute values.  Either additional
oscillation over the whole row family or a genuinely matched spectral
argument is required.

The first purpose of this paper is to carry out that matching at the
algebraic level.  Let \(P_m\) and \(M_m\) denote the locally calibrated
prime and finite-model signals on the row \(mj+h\), and put
\(Z_m=P_m-M_m\).  The four products above are exactly the expansion of
\(Z_{m_1}Z_{m_2}\).  We prove that, on every finite target horizon, this
difference has one common centered-divisor representation
\begin{equation}
 Z_m(j)=\eps_U(m)+
 \sum_u b_R(u)C_{m,u}(j),
 \qquad
 C_{m,u}(j)=\one_{u\mid mj+h}-\frac1u.
 \label{eq:tpc20-intro-common-kernel}
\end{equation}
Here
\(
 b_R(u)=-\mu(u)w_R(u)
\)
is the actual residual coefficient found in TPC-19, not the coefficient
of only one of the four channels.  The scalar \(\eps_U(m)\) is not
discarded formally: we prove a uniform M\"obius calibration theorem
which makes it arbitrarily logarithmically small for every polynomial
row range.  Consequently the \((u,v)\)-term of the matched centered
kernel has the primitive-conditional connected zero mode
\begin{equation}
 \frac{b_R(u)b_R(v)}{uv}
 \left((u,v)\one_{(u,v)\mid m_1-m_2}-1\right).
 \label{eq:tpc20-intro-connected-mode}
\end{equation}
The zero mode of every \((u,v)=1\) term vanishes before any estimate is
made.

The second purpose is to resolve the apparent three-phase complexity of
the long-lcm Poisson spectrum.  Write
\[
 g=(u,v),\qquad u=ga,\qquad v=gb,\qquad q=[u,v]=gab.
\]
For compatible divisor congruences, all four centered Fourier terms
align on the common period \(Hq\), where \(H=\rad|h|\).  Their exact
multiplier is
\begin{equation}
 B_{g,a,b}(r)
 =g-\one_{b\mid r}-\one_{a\mid r}+\one_{q\mid r}.
 \label{eq:tpc20-intro-B}
\end{equation}
This alignment has two consequences.  First, the joint, two single, and
constant terms should not all be completed at the longest period.  The
single terms have periods \(Hu\) and \(Hv\).  Completing those shorter
periods yields a strict-margin range
\begin{equation}
 Q\le X^{1/2+\delta-\eta_0}
 \label{eq:tpc20-intro-new-wedge}
\end{equation}
for completing all single and constant terms across
\(u,v\le R=X^{1/2-\delta}\), compared with
\(Q\le X^{2\delta-\eta_0}\) when the full joint period is completed at
once.  The compatible joint packet is retained.  Second, on its
genuinely remaining low nonzero frequencies,
the multiplier in \eqref{eq:tpc20-intro-B} is exactly \(g\).  The
matched algebra has removed the spurious single spectra, but it has not
created cancellation in the surviving joint packet.

The third purpose is to identify that packet without inverse-phase
notation obscuring its coefficient.  Compatible row residue pairs are
parametrized by one unit class \(\kappa\bmod q\).  After aggregating the
actual row weights on these fibers, the joint phase is the ordinary DFT
\begin{equation}
 S_q(r)=\sum_{\kappa\in(\Z/q\Z)^\times}
 Z_q(\kappa)e_q(r\overline H\kappa).
 \label{eq:tpc20-intro-fiber-dft}
\end{equation}
The three inverse phases displayed in TPC-19 are precisely the CRT
factorization of this one character.  Splitting \(Z_q\) into its
unit-class mean and discrepancy gives
\[
 S_q(r)=\overline Z_qc_q(r)+\widehat D_q(r)
\]
and the exact identity
\begin{equation}
 \sum_{r\bmod q}|\widehat D_q(r)|^2
 =q\sum_{\kappa\in(\Z/q\Z)^\times}|D_q(\kappa)|^2.
 \label{eq:tpc20-intro-fiber-parseval}
\end{equation}
Thus, for this chosen compatible short--short packet, the remaining
gates are a quantitative theorem for the actual prime--M\"obius row
weights across CRT fibers and a separate bound for the explicit
Ramanujan mean packet.  The large-divisor legs \(u>R\) or \(v>R\)
remain outside this reduction.  The fiber gate is not an unspecified
need for cancellation among three unrelated inverse phases.

These reductions are rigorous progress, but they do not supply the
required estimates for this packet.  A coefficient concentrated on one CRT fiber
saturates Parseval.  At the opposite extreme, a uniform fiber vector
produces an explicit Ramanujan bias, and on coprime frequencies its
transverse M\"obius sign migrates to the determinant content.  The cited
bilinear and trilinear Kloosterman-fraction estimates apply only after a
separable coefficient reduction, while the current fiber vector is a
modulus-dependent joint array
\citep{DukeFriedlanderIwaniec1997,BettinChandee2018,Wright2026}.
Pascadi's frequency-concentration theorem gives a powerful abstract
interface once a representing measure satisfying its size and
two-frequency conditions has been constructed; it does not prove those
conditions for the sharp coefficient here \citep{Pascadi2026LargeSieve}.

The organization is as follows.  \Cref{sec:tpc20-interface} fixes the
primitive row geometry.  \Cref{sec:tpc20-recombination} proves the
common four-channel coefficient, and
\cref{sec:tpc20-uniform-calibration} controls its scalar calibration
defect uniformly and proves packet-scale negligibility under explicit
packet hypotheses, which are satisfied for the separated packets in the
single-leg range.  \Cref{sec:tpc20-kernel-fourier} computes the complete
Fourier kernel.  \Cref{sec:tpc20-single-leg} proves the new completion
wedge and its sharp smoothness boundary.
\Cref{sec:tpc20-fiber-compression} gives the fiber DFT, Ramanujan mean,
variance identity, and no-go results.  Current technology is audited in
\cref{sec:tpc20-technology-boundary}; the exact certificate and conclusion
are in \cref{sec:tpc20-certificate-conclusion}.
