\section{Technology interfaces and the coefficient gate}
\label{sec:tpc20-technology-boundary}

TPC-18 produces the primitive two-row residual correlation, and TPC-19
separates its direct determinant-frequency and long-lcm Poisson
interfaces \citep{WangTPC18,WangTPC19}.  The results above improve the
second interface in two exact ways: the four centered channels are placed
on one Fourier lattice before estimation, and the compatible triple
inverse phase is compressed to the single fiber transform
\eqref{eq:tpc20-aggregated-DFT}.  This section records how several cited
estimates interface with those reductions, and which
hypothesis on the chosen prime--M\"obius fiber vector is still missing.

\subsection{The frequency-concentration interface}

A particularly flexible input relevant here is the exceptional-spectrum
large sieve of \citet{Pascadi2026LargeSieve}.  Put
\(\mathbb T=\R/\Z\).  In its notation, for
\(\alpha,\beta\in\mathbb T\), put
\begin{equation}
 T_N(\alpha,\beta)
 =\min_{t\in\Z_{\ge1}}\bigl(t+N\lVert t\alpha\rVert_{\mathbb T}
                         +N\lVert t\beta\rVert_{\mathbb T}\bigr),
 \qquad
 \mathcal I_N(\nu)
 =\iint T_N(\alpha,\beta)\,
       d|\nu|(\alpha)d|\nu|(\beta).
 \label{eq:tpc20-Pascadi-functional}
\end{equation}
Theorem~5.2 of that paper treats a coefficient
\(a_n=f(n/N)\check\nu(n)\).  Suppressing its standard smooth-cutoff,
parameter, and cusp-normalization hypotheses, the theorem gives
\begin{equation}
 \sum_{\lambda_j<1/4}X^{2\theta_j}
 \left|\sum_{n\asymp N}a_n\rho_{j\mathfrak a}(a_0n)\right|^2
 \ll_\epsilon
 (qa_0NX)^{2\epsilon}
 \left(1+\frac{a_0N}{q}\right)\mathcal A^2,
 \label{eq:tpc20-Pascadi-bound}
\end{equation}
provided, in particular,
\begin{align}
 \mathcal A
 &\gg \lVert a\rVert_2
 +\frac{\sqrt{(a_0,q)}N}{\sqrt{q+a_0N}}|\nu|(\mathbb T),
 \label{eq:tpc20-Pascadi-size-gate}\\
 X
 &\ll \max\!\left(1,\frac q{a_0N}\right)
       \max\!\left(1,\frac{\mathcal A^2}
                           {\mathcal I_N(\nu)}\right).
 \label{eq:tpc20-Pascadi-concentration-gate}
\end{align}
Thus this result is an interface theorem, not a black-box estimate for
an arbitrary determinant sequence.  Before it can be used here one must
derive one common spectral coefficient from the matched four-channel
kernel, identify its spectral level \(q\), length \(N\), scalar
\(a_0\), and exceptional parameter \(X\), construct a representing
measure \(\nu\), and verify both
\eqref{eq:tpc20-Pascadi-size-gate} and
\eqref{eq:tpc20-Pascadi-concentration-gate}.  In particular, the
spectral level called \(q\) in \eqref{eq:tpc20-Pascadi-bound} must not
be identified with either the row scale or the fiber modulus merely
because the same letter is traditionally used.  Applying the theorem
separately to the joint, two single, and constant channels is not a
substitute: the intervening triangle inequalities would discard the
matching encoded by \eqref{eq:tpc20-compatible-Khat}.  The coefficient
presented to the large sieve must be the combined coefficient whenever
more than one channel survives on the block under consideration.

There is a sharp positive benchmark.  Theorem~1.7 of
\citet{Pascadi2026LargeSieve} applies to the smooth difference
coefficient
\[
 \sum_{h_1\ell_1-h_2\ell_2=n}
 \Phi_1(h_1/H_0)\Phi_2(h_2/H_0)
 e(h_1\alpha_1+h_2\alpha_2),
\]
subject to its stated spectral-level and parameter conditions, including
the regime in which the level is at least of order \(L^2\).  It does not
cover the sharp coefficient isolated in TPC-19, where \(\omega_D\) is a
\(1\)-bounded smooth cutoff supported on \(d\asymp D\):
\begin{equation}
 A_{\ell_1,\ell_2}(n)
 =\sum_{\ell_1d_1-\ell_2d_2=n}
 \mu(d_1)\mu(d_2)\omega_D(d_1)\omega_D(d_2).
 \label{eq:tpc20-sharp-determinant-coefficient}
\end{equation}
Indeed, if
\[
 M_\ell(\alpha)
 =\sum_d\mu(d)\omega_D(d)e(-\ell d\alpha),
\]
then
\(\widehat A_{\ell_1,\ell_2}
 =M_{\ell_1}\overline{M_{\ell_2}}\).  The natural representing measure
has density \(\widehat A_{\ell_1,\ell_2}\), and hence total variation
\begin{equation}
 V_{\ell_1,\ell_2}
 =\int_{\mathbb T}|M_{\ell_1}(\alpha)M_{\ell_2}(\alpha)|\,d\alpha
 \ll D
 \label{eq:tpc20-natural-measure-variation}
\end{equation}
by Parseval and Cauchy--Schwarz.  Indeed,
\(\lVert M_\ell\rVert_2^2\le\sum_{d\asymp D}|\omega_D(d)|^2\ll D\).
In the formal smooth-benchmark scaling
\(N\asymp LD\), spectral level \(q\asymp L^2\), \(a_0=1\), and
\(L>2D\), retaining \(\mathcal A=D^{1+o(1)}\) would already require
\(V_{\ell_1,\ell_2}=D^{o(1)}\), together with the independent
two-frequency condition
\eqref{eq:tpc20-Pascadi-concentration-gate}.  Neither estimate follows
from \eqref{eq:tpc20-natural-measure-variation}.

Davenport's uniform M\"obius exponential-sum estimate, in the form
recalled by \citet{GreenTao2008}, gives arbitrary logarithmic saving in
\(\sup_\alpha|\sum_{d\leq D}\mu(d)e(d\alpha)|\).  After partial
summation it also handles a standard smooth dyadic cutoff.  This is a
one-frequency \(L^\infty\) statement.  It does not bound the product
variation in \eqref{eq:tpc20-natural-measure-variation} at the scale
required above and does not control the two-frequency functional
\(\mathcal I_N\).  Consequently it does not verify Pascadi's two gates
for \eqref{eq:tpc20-sharp-determinant-coefficient}.

\subsection{What one-fraction estimates do and do not import}

The classical bilinear estimate of
\citet{DukeFriedlanderIwaniec1997} controls a single Kloosterman
fraction \(e(a\overline m/n)\) with a separated coefficient
\(\alpha_m\beta_n\).  The trilinear estimate of
\citet{BettinChandee2018} admits a further separated coefficient
\(\nu_a\), and the recent preprint \citet{Wright2026} treats a useful
partially fixed denominator while retaining the same essential
one-fraction and separability requirements.  The latter is presently a
version-sensitive, non-peer-reviewed preprint, so only its explicitly
stated current hypotheses may be used.  These results can therefore
be invoked on a dyadic slice only after the slice has been reduced to
their precise phase and coefficient forms and all of their size
hypotheses have been checked.  They are not estimates for an arbitrary
two-dimensional array indexed by a modulus and a residue class.

The compression in \cref{thm:tpc20-fiber-DFT} supplies the needed
single phase, but not the needed coefficient separation.  After
aggregation, the relevant vector is
\[
 (q,\kappa)\longmapsto D_q(\kappa),
 \qquad \kappa\in\mathcal U_q.
\]
Replacing \(\kappa\) by its inverse may display the phase as one
Kloosterman fraction, but it simultaneously replaces the coefficient
by \(D_q(\overline m)\); the joint dependence on \(q\) and \(m\)
remains.  Likewise, Theorem~1 of \citet{BlomerMilicevic2015} averages
complete Kloosterman sums over their modulus \(c\), with a residue weight
modulo \(q_0\), a smooth \(c/X\) weight, and a cost measured by
the \(\ell^1\)-norm of the \(q_0\)-Mellin transform of that residue
weight.  It is not a direct estimate for the one-modulus fiber transform
\(S_q(r)\).  The identity \eqref{eq:tpc20-aggregated-DFT} alone does not
convert the fiber vector into that weighted-modulus average.
None of the cited results is a separate \emph{long-lcm Poisson spectrum}
theorem: Poisson summation gives the exact normal form, while the
arithmetic estimate of its coefficient array is an additional step.

The obstruction may be quantified.  On a dyadic modulus block
\(q\asymp Q_0\), choose representatives \(0\leq\kappa<2Q_0\), extend
\(D_q(\kappa)\) by zero outside \(\kappa\in\mathcal U_q\), and define
the separable projective cost
\begin{equation}
 \mathfrak R_\pi(D;Q_0)
 =\inf_{D_q(\kappa)=\sum_\nu x_\nu(q)y_\nu(\kappa)}
   \sum_\nu\lVert x_\nu\rVert_2\lVert y_\nu\rVert_2.
 \label{eq:tpc20-projective-rank-cost}
\end{equation}
A direct termwise use of a separated bilinear or trilinear theorem pays
the decomposition cost in
\eqref{eq:tpc20-projective-rank-cost}.  Small Hilbert-space norm or
Parseval energy does not by itself imply a sufficiently small projective
cost.  Thus ``one phase'' is a necessary structural reduction, whereas
controlled projective rank is an additional arithmetic input.

\subsection{A defensible next gate}

For a family \(\mathcal Q\) of long denominators, set
\begin{equation}
 \mathfrak V(\mathcal Q)
 =\sum_{q\in\mathcal Q}q
   \sum_{\kappa\in\mathcal U_q}|D_q(\kappa)|^2.
 \label{eq:tpc20-total-fiber-variance}
\end{equation}
By \eqref{eq:tpc20-discrepancy-parseval}, this is exactly the complete
frequency energy of the discrepancy transforms.  It is not yet a
restricted-frequency saving: the one-fiber example in
\cref{prop:tpc20-fiber-nogo} retains an order-one coprime-frequency
discrepancy after its mean is removed.  The direct next proof obligation is
therefore the weighted \(\ell^1_q\ell^2_\kappa\) estimate stated in
\eqref{eq:tpc20-fiber-gate}, or a stronger variance estimate that implies
it with a fixed margin.  This route uses the exact restricted-frequency
bound in \cref{prop:tpc20-restricted-fiber-bound} and requires no claim
that any cited Kloosterman theorem accepts the fiber array.

An alternative low-rank route must do all three of the following on each
dyadic block: exhibit an explicit decomposition in
\eqref{eq:tpc20-projective-rank-cost}; substitute the actual block
parameters into one specified theorem of
\citet{DukeFriedlanderIwaniec1997}, \citet{BettinChandee2018}, or
\citet{Wright2026}; and prove that the imported bound multiplied by the
full decomposition cost is below the TPC-18 obstruction scale with a
fixed margin.  Low rank without this norm and parameter ledger is not a
valid transfer theorem.  In either route the explicit Ramanujan mean
packet \eqref{eq:tpc20-Ramanujan-mean-packet} remains a separate term;
fiber discrepancy estimates do not cancel it.

Finally, no estimate in this paper is taken from the January 2026
withdrawn preprint entitled \emph{Bilinear forms with Kloosterman
fractions and applications}.  Its withdrawal notice reports a missing
factor in the claimed bound, and it is intentionally given no
bibliographic entry here.  The unconditional boundary is therefore as
follows: the results audited above supply rigorous smooth and separated
benchmarks, while neither the sharp frequency-concentration gates nor
the actual fiber-variance/projective-rank gate is proved here or supplied
by those results.  In
particular, the results above do not establish cancellation of the full
TPC-18 residual, a fixed-shift prime-pair asymptotic, a twin-prime lower
bound, or a breach of the sieve parity barrier.
