\begin{abstract}
The distinguished zero determinant frequency in a fixed-shift
prime--M\"obius packet is controlled by a ratio, not by an amplitude
estimate alone.  If \(a_X=(A_{C_X}(n))_n\) is the literal determinant
coefficient, the required quantity is
\[
 \mathfrak F_{h_0}(X)
 =\frac{|\sum_n A_{C_X}(n)|^2}
        {\sum_n|A_{C_X}(n)|^2}.
\]
Earlier work isolated the threshold
\(\mathfrak F_{h_0}(X)\le X^{1/400+o(1)}\) and an amplitude target
\(|\sum_n A_{C_X}(n)|\ll X^{o(1)}Q_X^2\), but did not supply the
matching lower bound for the denominator.

This paper gives an exact transfer architecture for that missing
denominator.  A represented synthesis \(\cA_X\), a literal missing
synthesis \(\cM_X\), and their reassembly
\(\cB_X=\cA_X+\cM_X\) yield coefficient-specific and uniform energy
survival bounds from a normalized missing-Gram Perron certificate.
An explicit determinant-binning map \(\cJ_X\), a verified restricted
lower modulus \(s_X\), and the dictionary defect
\(r_X=a_X-\cJ_X\cB_Xz_X\) then give
\[
 \|a_X\|_2^2\ge
 \left(
 s_X\sqrt{\delta_{{\rm reasm},X}\Gamma_{{\rm pre},X}}
 -\frac{\|r_X\|_2}{\sqrt{D_{{\rm raw},X}}}
 \right)_+^2D_{{\rm raw},X}.
\]
At the high-row scales
\(Q_X=X^{267/400+o(1)}\) and
\(J_X=X^{133/400+o(1)}\), an amplitude exponent
\(\eta_Z\) and an energy-loss exponent \(\lambda_D\) give
\[
 \mathfrak F_{h_0}(X)
 \le X^{1/400+\lambda_D-2\eta_Z+o(1)}.
\]
For this exponent transfer, the sharp recorded-bounds condition is
\(2\eta_Z\ge\lambda_D\), with genuine robustness only under strict
inequality.  It is not claimed to be necessary for the physical
packet when the recorded exponents are nonoptimal.

Two sharp countermodels show why this bridge is not formal:
unsigned support and energy do not determine the zero mode, and raw
atomic mass can disappear completely inside one determinant bin.
Accordingly, the results are exact L0 algebra and a conditional L1
arithmetic interface.  They do not prove determinant-energy survival
for the physical packet, a full-block cover, a fixed-shift
Hardy--Littlewood asymptotic, twin primes, or a breach of the parity
barrier.
\end{abstract}
