\section{Reproducible audit, claim boundary, and next gate}
\label{sec:audit}

The transfer is useful only if every object can be checked against the
literal packet.  We record a minimum archive.

\subsection{Carrier and dictionary census}

For each audited scale \(X\), archive:
\begin{enumerate}[label=(A\arabic*),leftmargin=2.7em]
\item the fixed value \(h_0\), the exact \(Q_X,J_X,C_X\), and the
version of every upstream identity;
\item the complete ordered native key sets
\(\cK_X,\cY_X,\cN_X\), including field names, integer ranges,
orientations, contents, provenance labels, and cryptographic hashes;
\item the exact sparse arrays of \(\cA_X,\cM_X,\cB_X\), before
thresholding, together with dimensions, ranks, and actual nonzero
supports;
\item the literal coefficient \(z_X\), the actual determinant
coefficient \(a_X\), and a direct exact check of
\(r_X=a_X-\cJ_X\cB_Xz_X\);
\item the determinant label \(\nu_X\), every multiplier
\(\tau_X(y)\), every fiber cardinality, and the sparse matrix of
\(\cJ_X\);
\item the single global \(D_{{\rm raw},X}\), with its atomic measure
and units; no block-renormalized replacement;
\item \(G_{\cM,X}\), its exact active diagonal
\(D_{\cM,X}\), the normalized residual \(R_{\cM,X}\), the majorant
\(P_X\), an entrywise proof of \(|R_{\cM,X}|\le P_X\), and a certified
bound for \(\rho(P_X)\);
\item the quantities \(\eta_X,\chi_X,\Gamma_{{\rm pre},X}\),
\(\Xi_X(z_X)\), \(\delta_{{\rm sharp},X}\), and
\(\delta_{{\rm reasm},X}\);
\item the defining constraints for \(E_X\), an exact proof that
\(\cB_Xz_X\in E_X\), and a certified lower bound for \(s_X\);
\item the exact values \(Z_X,D_X,\mathfrak D_{h_0}(X)\), and
\(\mathfrak F_{h_0}(X)\), followed by the complete polynomial-loss
ledger of \cref{cor:lambda-D}.
\end{enumerate}

Exact integer, rational, algebraic, or interval certificates should be
used whenever feasible.  Floating-point tolerances are reported
separately and never used to change the exact support.  A regression
over finitely many \(X\) may motivate an exponent, but it does not
prove the asymptotic inequalities in
\cref{thm:literal-flatness-transfer}.

\subsection{Six mandatory physical checks}

Before any L1 claim, answer all six questions:
\begin{enumerate}[label=(C\arabic*),leftmargin=2.7em]
\item Are the coefficients literal physical coefficients rather than
majorant, trace, or averaged-family coefficients?
\item Is the same prescribed nonzero \(h_0\) retained in every map?
\item Is the atomic normalization global and physical?
\item Is the representation canonical, or has every multiplicity in a
nonminimal representation been restored?
\item Is the support the actual exact post-aggregation support?
\item Does the endpoint ledger keep every fixed-power loss explicit
and obey the strict \(1/400\) stop rule?
\end{enumerate}
Failure of any check returns the result to L0.

\subsection{Decision protocol}

The next arithmetic decision is a deliberate trichotomy.

\begin{enumerate}[label=\textbf{Route \Alph*.},leftmargin=3.5em]
\item Construct the literal dictionary with \(r_X=0\), and prove
\[
 s_X,\ \delta_{{\rm reasm},X},\ \Gamma_{{\rm pre},X}
 \ge X^{-o(1)},
 \qquad
 D_{{\rm raw},X}\ge X^{-o(1)}Q_X^3J_X^2.
\]
Then \eqref{eq:natural-energy-required} follows and the remaining
independent task is the zero-mode amplitude estimate.
\item Prove an amplitude gain
\(\eta_Z>0\).  Then a determinant-energy loss
\(\lambda_D\le2\eta_Z\) is admissible, subject to the separate strict
endpoint ledger.
\item Show that the required lower bound for \(D_X\), after exact
expansion, contains an unresolved fixed-shift signed correlation of
the same strength as a Chowla/parity input.  Then record a negative
transfer theorem and stop this route rather than rename the missing
arithmetic as a completion lemma.
\end{enumerate}

\subsection{Claim table}

\begin{center}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.31\textwidth}
                    >{\raggedright\arraybackslash}p{0.27\textwidth}
                    >{\raggedright\arraybackslash}p{0.31\textwidth}@{}}
\toprule
Statement & Status here & Missing physical input\\
\midrule
Missing-Gram energy bound
& Exact L0 theorem
& Literal \(\cM_X\) and asymptotic certificate statistics\\
\addlinespace
Uniform reassembly
& Exact conditional L0 theorem
& Positive \(\delta_{{\rm reasm},X}\) at physical scale\\
\addlinespace
Determinant-energy lower bound
& Exact conditional L1 implication
& Literal \(\cJ_X\), lower modulus, and small \(r_X\)\\
\addlinespace
Condition \(2\eta_Z\ge\lambda_D\)
& Exact criterion for this exponent transfer
& Bounds for the actual numerator and denominator\\
\addlinespace
Matched-shell saving
& Conditional inherited implication
& All hypotheses of \cref{thm:literal-flatness-transfer}\\
\addlinespace
\(\cB_{h_0,\delta}(X)=o(X)\)
& Conditional full-block implication
& Exact cover, normalization sum, and uniform packet estimates\\
\addlinespace
Fixed-shift prime-pair asymptotic or twin primes
& Not proved
& L2 arithmetic closure and all inherited bridges\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Conclusion}

The new point is not a hidden cancellation theorem.  It is an exact
factorization of the remaining inference:
\[
\boxed{
\begin{array}{c}
\text{literal completion}\\
\Downarrow\ \text{Gram survival}\\
\text{pre-bin energy}\\
\Downarrow\ \text{restricted binning + dictionary}\\
\text{determinant energy}\\
\Downarrow\ \text{independent zero-mode estimate}\\
\text{zero-frequency flatness}.
\end{array}}
\]
The first two downward arrows are now governed by explicit,
falsifiable constants.  The final arithmetic inputs remain open.
That separation prevents exact finite algebra from being mislabeled
as fixed-shift parity progress while leaving a precise route for a
genuine future advance.
