\section{The literal fixed-shift packet}
\label{sec:literal-packet}

All spaces in the finite algebra below are complex Hilbert spaces with
their standard inner products, linear in the first variable.  The
same statements hold over real spaces.  The index \(X\) is suppressed
when no ambiguity is possible.

\begin{definition}[Complete native packet]
\label{def:complete-packet}
A complete native packet at scale \(X\) consists of:
\begin{enumerate}[label=(P\arabic*),leftmargin=2.7em]
\item one fixed nonzero integer \(h_0\), not averaged over a family;
\item a finite native key set \(\cK_X\), including all row, orbit,
content, divisor, orientation, source, and endpoint labels used by
the construction;
\item a coefficient space \(\cH_X=\C^{\cK_X}\) and the literal
physical coefficient \(z_X\in\cH_X\);
\item a pre-bin key set \(\cY_X\) and literal maps
\[
 \cA_X,\cM_X:\cH_X\longrightarrow\C^{\cY_X},
 \qquad
 \cB_X:=\cA_X+\cM_X;
\]
\item a determinant key set \(\cN_X\), an exact determinant label
\(\nu_X:\cY_X\to\cN_X\), and all literal scalar multipliers attached
to the aggregation;
\item the actual post-aggregation coefficient
\(a_X=(A_{C_X}(n))_{n\in\cN_X}\), with exact zeros retained until the
aggregation has been performed;
\item one global raw atomic energy \(D_{{\rm raw},X}>0\), computed
before block deletion, renormalization, thresholding, or selection.
\end{enumerate}
\end{definition}

The words ``represented'' and ``missing'' describe provenance, not
sign.  Thus \(\cM_X\) already includes its literal signs and phases;
reassembly is \(\cA_X+\cM_X\), never an unsigned union of supports.
Similarly, \(D_{{\rm raw},X}\) is not recomputed on the represented
support.  Per-component normalizers can conceal an arbitrarily large
deleted mass and are therefore inadmissible for the physical transfer.

\begin{definition}[Exact determinant binning]
\label{def:binning}
Let \(\tau_X(y)\in\C\) be the archived multiplier on a pre-bin key
\(y\in\cY_X\).  Define
\begin{equation}
 (\cJ_Xu)(n)
 :=
 \sum_{\substack{y\in\cY_X\\ \nu_X(y)=n}}
 \tau_X(y)u(y),
 \qquad n\in\cN_X.
 \label{eq:literal-binning}
\end{equation}
The sum is taken over every native pre-bin key in the fiber.  The
dictionary residual is
\begin{equation}
 r_X:=a_X-\cJ_X\cB_Xz_X.
 \label{eq:dictionary-residual}
\end{equation}
\end{definition}

If the proposed carrier is literally the physical coefficient, then
\(r_X=0\) by exact finite arithmetic.  If only a model, restriction,
or surrogate carrier has been constructed, \eqref{eq:dictionary-residual}
does not vanish automatically.  The residual is the correct location
for that discrepancy.

\begin{remark}[Actual support]
The support of a synthesis map is its exact nonzero support after
literal coefficient aggregation.  A geometrically available edge,
a thresholded numerical entry, or a union of possible carriers is not
an actual edge.  In particular, a spectral radius computed on an
ambient support is not the Perron constant used below unless it is
proved to majorize the normalized Gram on the actual active
coordinates.
\end{remark}

\begin{remark}[No change of target]
The completion maps take values in the pre-bin space
\(\C^{\cY_X}\), while the arithmetic coefficient lives in
\(\C^{\cN_X}\).  An observation on another quotient, a four-corner
trace, or a common-target gauge does not define \(\cJ_X\).  The
determinant map and every aggregation multiplier must be constructed
explicitly.
\end{remark}

For reference, write
\begin{equation}
 Z_X=\langle a_X,\bm 1\rangle,
 \qquad
 D_X=\|a_X\|_2^2,
 \qquad
 \mathfrak D_{h_0}(X)=\frac{D_X}{Q_X^3J_X^2}.
 \label{eq:packet-statistics}
\end{equation}
These are physical, post-aggregation statistics.  None is replaced by
the corresponding statistic of \(\cA_Xz_X\),
\(\cB_Xz_X\), or an unsigned majorant.
