\section{Final claim boundary}
\label{sec:claim-boundary}

\begin{theorem}[Post-bin mass--energy equivalence]
\label{thm:final-equivalence}
For the actual TPC-32 coefficient
\[
 A_X=A_{\lfloor J_X\rfloor}
\]
at one fixed nonzero \(h_0\), with
\(N_{0,X}=J_XQ_X^2\), the following are equivalent:
\begin{align}
 M_X&\ge X^{-o(1)}N_{0,X},
\label{eq:final-mass}\\
 D_X&\ge
 X^{-o(1)}\frac{N_{0,X}^2}{Q_X}.
\label{eq:final-energy}
\end{align}
More generally, a mass loss \(\mu\) certifies energy loss
\(2\mu\), and an energy loss \(\lambda\) certifies mass loss
\(\lambda\).  The energy hypothesis also forces
\[
 S_X\ge X^{-\lambda-o(1)}Q_X.
\]
The mass-to-energy exponent is sharp under the verified support
envelope.  The reverse mass and support exponents are sharp whenever
\(X^{-\lambda}Q_X\to\infty\), in particular throughout the relevant
endpoint range \(\lambda<1/400\).
\end{theorem}

\begin{proof}
This is
\cref{thm:two-sided-transfer,cor:subpower-equivalence} together with
the extremizers of
\cref{prop:sharp-mass-energy,prop:sharp-energy-mass}.
\end{proof}

The theorem reduces one literal energy question to one literal
post-bin mass question.  It does not estimate either quantity from
below.  In particular, the TPC-32 absolute majorant and every
pre-bin/raw absolute mass remain upper data only.

\paragraph{Explicit exclusions.}
This paper proves no lower bound for \(M_X\) or \(D_X\), no estimate
for the distinguished zero mode \(Z_X\), no fixed-shift M\"obius
cancellation theorem, and no result specialized to \(h_0=2\).  It
does not prove a breach of sieve parity, a Hardy--Littlewood
asymptotic, a prime-pair lower bound, or the twin-prime conjecture.
Its complete contribution is the sharp \(\Lone\) equivalence and its
stop rules.

\paragraph{Next gate.}
The next positive task is to prove the following lower bound directly
for the literal post-bin mass:
\[
 M_X\ge X^{-o(1)}N_{0,X}.
\]
The alternative is an exact obstruction showing that the physical
fiber geometry permits a fixed-power or complete post-bin mass loss.
Either outcome must be stated for the same \(h_0\), actual support,
and global normalization.  The full-route loss remains subject to
\eqref{eq:strict-loss-boundary}.
