\section{The exponent and endpoint audit}
\label{sec:endpoint-audit}

\subsection{What exponent enters the energy ledger}

Suppose a future argument proves
\[
 M_X\ge X^{-\mu+o(1)}N_{0,X}.
\]
\Cref{thm:two-sided-transfer} certifies the determinant-energy loss
\begin{equation}
 \lambda_D\le2\mu
\label{eq:lambda-from-mu}
\end{equation}
in the notation
\[
 D_X\ge
 X^{-\lambda_D+o(1)}
 \frac{N_{0,X}^2}{Q_X}.
\]
This is a one-way certified upper bound on the loss exponent; the
actual energy may be larger.  Conversely, an independently proved
energy loss \(\lambda_D\) certifies a post-bin mass loss at most
\(\lambda_D\).

The TPC-82 zero-slack ledger compares this energy loss with a
distinguished-zero-mode gain \(\eta_Z\):
\begin{equation}
 2\eta_Z\ge\lambda_D.
\label{eq:zero-slack-import}
\end{equation}
Thus, if the mass route is the only energy input and there are no
additional energy losses, the sufficient compatibility condition is
\[
 \eta_Z\ge\mu.
\]
If an auxiliary squared-energy loss \(\lambda_{\rm aux}\) is present,
the recorded condition becomes
\[
 2\eta_Z\ge2\mu+\lambda_{\rm aux}.
\]
The present paper proves none of these lower or cancellation
hypotheses; it only identifies their exact transfer.

\subsection{The strict physical loss rule}

The \(1/400\) appearing at the high-row TPC-32 flatness endpoint is
not an allowance that may be reused for mass, energy, dictionary, or
cover losses.  In the full physical comparison, every fixed-power
loss must be derived in the same literal carrier and counted once.
Writing their complete sum as \(\Lambda_{\rm phys}\), the operational
rule remains
\begin{equation}
\boxed{
 \Lambda_{\rm phys}<\frac1{400}
 \quad\text{to continue};\qquad
 \Lambda_{\rm phys}\ge\frac1{400}
 \quad\text{to stop}.}
\label{eq:strict-loss-boundary}
\end{equation}
Equality is in the stopping case.  An open term cannot be assigned
zero loss, and \eqref{eq:lambda-from-mu} cannot be counted twice under
both the mass and energy names.

\subsection{The L0/L1/L2 ledger}

\begin{definition}[Stage labels]
\label{def:stage-labels}
\begin{enumerate}[label=(\arabic*),leftmargin=2.2em]
\item \(\Lzero\) is finite algebra independent of the physical
carrier.
\item \(\Lone\) is an exact interface retaining the fixed nonzero
\(h_0\), literal coefficient, complete native aggregation, actual
support, global normalization, and original quantifiers.
\item \(\Ltwo\) is a new asymptotic arithmetic estimate for that
literal growing carrier, strong enough to reduce a positive exponent
in the physical ledger.
\end{enumerate}
\end{definition}

\begin{proposition}[Stage classification of this paper]
\label{prop:stage-classification}
\Cref{thm:mass-energy-sandwich} is an exact \(\Lzero\) theorem.
\Cref{thm:two-sided-transfer,cor:subpower-equivalence} form an exact
\(\Lone\) equivalence for the actual TPC-32 matched coefficient.  This
paper proves no unconditional \(\Ltwo\) estimate.
\end{proposition}

\begin{proof}
The finite theorem uses no arithmetic.  The transfer inserts the
verified literal support and singleton bounds while preserving every
item in \cref{def:stage-labels}(2).  However, neither
\eqref{eq:mass-lower-mu} nor
\eqref{eq:energy-lower-lambda} is proved here for any growing
physical packet.  Hence no new asymptotic lower bound is available to
enter the \(\Ltwo\) ledger.
\end{proof}

\begin{remark}[What would count as the next advance]
A proof of
\[
 M_X\ge X^{-o(1)}N_{0,X}
\]
for the actual fixed-\(h_0\) coefficient would, by
\cref{cor:subpower-equivalence}, close the natural determinant-energy
gate.  A lower bound for a raw majorant, an averaged shift, a selected
subsequence of cutoffs, or a renormalized component would not.
\end{remark}
