\section{Introduction}
\label{sec:introduction}

The TPC-81 transfer architecture isolates the determinant energy
\[
 D_X=\sum_n|A_{C_X}(n)|^2
\]
as one of the two remaining arithmetic statistics in the matched
fixed-shift route \citep{WangTPC81}.  TPC-82 then records the
zero-slack relation between energy survival and distinguished
zero-mode cancellation \citep{WangTPC82}.  A lower bound for \(D_X\)
is not presently known at the natural scale.  Before returning to the
more elaborate pre-bin completion machinery, it is useful to ask a
strictly post-bin question:
\begin{quote}
How much of the determinant energy problem is already equivalent to
survival of the actual post-bin \(\ell^1\) mass?
\end{quote}

For the literal coefficient, the answer is exact and asymmetric.  A
lower \(\ell^1\) mass with loss \(\mu\) yields an energy lower bound
with loss \(2\mu\).  Conversely, an energy lower bound with loss
\(\lambda\) yields an \(\ell^1\) lower bound with the same loss
\(\lambda\).  At subpower resolution, the two survival statements
are equivalent.  This uses only two physical upper bounds already
proved in TPC-32: the determinant support has size \(O(Q_X)\), and a
single determinant bin has amplitude at most
\(X^{o(1)}N_{0,X}/Q_X\) \citep{WangTPC32}.

The result is elementary, but it closes a useful interface.  It
replaces the broad question ``does the energy survive binning?'' by
the equivalent subpower question ``does a natural amount of
\(\ell^1\) mass survive after binning?''  This is not a replacement
of arithmetic by norm interpolation.  TPC-32 supplies only the upper
bound
\[
 M_X\ll X^{o(1)}N_{0,X};
\]
the matching lower bound remains open.  Moreover, \(M_X\) is formed
after all literal atoms with the same determinant have been summed.
A large raw absolute mass gives no such lower bound.

The paper has five main conclusions.
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item We prove the sharp universal inequalities
\[
 M^2/S\le D\le LM
\]
for a finite complex sequence, including all equality cases.
\item We insert the actual TPC-32 support and singleton bounds at
\(C_X=\lfloor J_X\rfloor\), obtaining the two-sided exponent
transfer.
\item We prove that natural determinant energy forces a quantitatively
large actual support.  Thus energy cannot survive at its natural
scale on a subpower-small fraction of the available determinant
range.
\item We give extremizing model sequences showing that the factors
\(2\mu\), \(\lambda\), and the support exponent cannot be improved
from the stated data.
\item We separate the actual post-bin mass from every pre-bin or raw
absolute majorant and give exact cancellation counterexamples.
\end{enumerate}

The distinction from the distinguished zero frequency is equally
important.  The mass
\[
 M_X=\sum_n|A_X(n)|
\]
forgets the phases between different determinant bins.  The zero
mode
\[
 Z_X=\sum_n A_X(n)
\]
depends on those phases.  Two sequences can have identical
\((S,L,M,D)\) and opposite zero-mode behavior.  Therefore the present
equivalence advances the energy side only; it neither proves nor
models zero-frequency cancellation.

All physical statements keep one prescribed \(h_0\ne0\), the actual
coefficient \(A_{C_X}\), the complete matched aggregation, and the
global TPC-32 normalization.  No assertion is specialized to
\(h_0=2\).
