\section{Why raw and pre-bin masses cannot be substituted}
\label{sec:non-substitution}

The distinction between a post-bin coefficient and an atomic
majorant is exact.  Let \(\cY_X\) be a native pre-bin key set, let
\(\nu_X:\cY_X\to\Z\) be the determinant label, and write the literal
atomic contribution as \(b_X(y)\).  In the simplest unit-multiplier
model,
\begin{equation}
 A_X(n)=
 \sum_{\substack{y\in\cY_X\\\nu_X(y)=n}}b_X(y).
\label{eq:atomic-binning}
\end{equation}
The same discussion applies with archived multipliers absorbed into
\(b_X(y)\).

Define the fiberwise absolute majorant and raw absolute mass by
\begin{equation}
 A_X^+(n)=
 \sum_{\substack{y\in\cY_X\\\nu_X(y)=n}}|b_X(y)|,
 \qquad
 M_{{\rm raw},X}=\sum_{y\in\cY_X}|b_X(y)|.
\label{eq:raw-majorant}
\end{equation}
Then
\begin{equation}
 M_X=\sum_n|A_X(n)|
 \le\sum_nA_X^+(n)
 =M_{{\rm raw},X}.
\label{eq:one-way-raw}
\end{equation}

\begin{proposition}[No reverse raw-mass inequality]
\label{prop:no-raw-reverse}
There is no positive universal constant \(c\) such that
\[
 M_X\ge c\,M_{{\rm raw},X}
\]
for all literal determinant aggregations, even when the raw support,
raw absolute values, determinant fiber, and global normalization are
fixed.
\end{proposition}

\begin{proof}
Put two atoms in the same determinant fiber and take their
contributions to be \(1\) and \(-1\).  Then
\[
 M_{{\rm raw},X}=2,\qquad A_X(n)=0,\qquad M_X=D_X=0.
\]
Scaling both atoms makes the raw mass arbitrarily large while the
post-bin coefficient remains zero.
\end{proof}

\begin{corollary}[Majorants give upper bounds only]
\label{cor:majorant-upper-only}
The two TPC-32 majorant statistics
\[
 \sum_nA_{C_X}^+(n)
 \quad\text{and}\quad
 \max_nA_{C_X}^+(n)
\]
validly imply upper bounds for \(M_X\) and \(L_X\).  They do not
imply a lower bound for \(M_X\), \(D_X\), or \(S_X\).
\end{corollary}

\begin{proof}
The upper implications follow from
\(|A_X(n)|\le A_{C_X}^+(n)\).  The counterexample in
\cref{prop:no-raw-reverse} rules out every positive reverse
implication.
\end{proof}

\begin{remark}[No channelwise renormalization]
The cancellation in \cref{prop:no-raw-reverse} occurs before the
post-bin statistics are measured.  Renormalizing each atom, channel,
triplet, or component separately would erase that cancellation and
change the coefficient.  The only allowed \(M_X\) is the norm of the
already aggregated \(A_X\) in the original global normalization.
\end{remark}

\subsection{Mass and energy do not control the zero mode}

Let
\[
 Z_X=\sum_nA_X(n)
\]
be the distinguished zero-frequency coefficient.

\begin{proposition}[Identical norm data, different zero modes]
\label{prop:norms-not-zero-mode}
For every even \(S\) and every \(L>0\), there are two sequences with
identical \((S,L,M,D)\) but zero modes of magnitudes \(SL\) and
\(0\), respectively.
\end{proposition}

\begin{proof}
On a support of size \(S\), take
\[
 a_n=L
\]
for every coordinate and take
\[
 b_n=(-1)^nL.
\]
Both sequences satisfy
\[
 \#\supp=S,\qquad
 \|\cdot\|_\infty=L,\qquad
 \|\cdot\|_1=SL,\qquad
 \|\cdot\|_2^2=SL^2.
\]
The first zero mode is \(SL\), while the second is zero.
\end{proof}

\begin{remark}[No flatness theorem]
\Cref{prop:norms-not-zero-mode} shows that even exact knowledge of
all four post-bin statistics in \eqref{eq:SLMD} does not prove the
TPC-32 distinguished-frequency flatness condition.  The current
paper concerns energy survival, not cancellation among determinant
bins.
\end{remark}

\subsection{Observation versus premise}

Numerically observing \(M_X\) or \(D_X\) on a finite cutoff is useful
for locating possible loss.  It is not a growing-\(X\) lower bound.
Likewise, an exact upper bound for the raw majorant is not evidence
that the post-bin mass is close to that upper bound.  A valid
arithmetic input must be stated directly for \(M_X\) or \(D_X\) with
the fixed \(h_0\), the literal coefficient, and the original
quantifiers.
