\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Zero Before Separation in a Primitive Mobius Tail: Provenance-Weighted Closure and the Principal Row-Mode Boundary},
 pdfauthor={Liang Wang},
 pdfsubject={Physical zero-mode closure in a primitive Mobius tail},
 pdfkeywords={Mobius tail, zero mode, projective mass, principal row mode, congruence skeleton, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cI}{\mathcal I}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\supp}{\operatorname{supp}}

\title{\textbf{Zero Before Separation in a Primitive M\"obius Tail:}\\
\textbf{Provenance-Weighted Closure and the}\\
\textbf{Principal Row-Mode Boundary}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC-24 proves pointwise arbitrary-logarithmic cancellation for the
physical additive zero mode of a calibrated one-sided divisor shell,
but its abstract packet theorem retains an additional fixed-projective-
mass hypothesis.  We return here to the actual primitive opened-
\(d\) packet before smooth row--orbit separation.  Its row coefficient
has the provenance
\(\mu(d)(\log\ell)\), up to fixed bounded cutoffs, where
\(m=\ell d\), \(\ell\asymp L\) is prime, \(d\asymp D\), and
\(Q=LD\).  Extracting Poisson frequency zero first turns the original
row-dependent smooth orbit weight into a uniformly bounded integral.
Chebyshev's estimate then gives
\[
 \sum_{\substack{\ell\asymp L\\ \ell\ \mathrm{prime}}}
 (\log\ell)\sum_{d\asymp D}|\mu(d)|\ll LD=Q,
\]
so the physical zero-mode row-pair mass is \(O(Q^2)\), without a
projective decomposition and without an \(X^\varepsilon\) loss.

Combining this zero-before-separation principle with the pointwise shell
kernel of TPC-24 yields, for \(S=X^{s+o(1)}\), every
\(0<\kappa<s\), and every fixed \(A>0\),
\[
 |\mathcal Z^0_{S,T}|
 \ll JQ^2\{(\log X)^{-A}+X^{-s+\kappa+o(1)}\}.
\]
Consequently the fixed-projective-mass condition in TPC-24 is automatic
for the actual opened-\(d\) one-sided packet.  Under the remaining
inherited row, no-wrap, Fourier-tail, and conductor interfaces, and
when
\[
 \eta_{\rm asym}(\beta;s,t)=
 \min\left\{1-\frac{3\beta}{2},
 \frac{\beta+1-2s-2t}{2},
 \frac{3-\beta-s-5t}{4}\right\}>0
\]
with fixed margin, the calibrated mixed increment has arbitrary
logarithmic saving for a general nonzero-mean fixed smooth test within
the factorable provenance class; no mean-zero hypothesis on the fixed
physical test is needed.  This closes the mass gate for that
specific physical packet, not for arbitrary abstract row arrays.

We also prove that the distinction is necessary.  Soft row
\(L^2\) energy, a divisor-independent off-diagonal mask, and an
entrywise kernel bound smaller than every fixed logarithmic power do
not imply a packet saving.  A dense constant row mode saturates the
natural scale while obeying all three interfaces.  The same coherent
direction occurs in the exact M\"obius algebra: for
\(H=1\), \(R=S=2\), \(T=3\), and prime rows larger than \(3\),
the raw kernel equals \(\kappa_0=((\log2-2)\log3)/6\) on every
distinct row pair.  After off-diagonal masking its matrix is
\[
 \kappa_0(\mathbf1\mathbf1^{\mathsf T}-I).
\]
Thus a direct Hilbert--Schmidt upgrade has no dimension gain.  Finally,
in a prime-row no-long-wrap model we decompose the whole kernel into
residue-class constant spaces modulo the shared factor \(g\).  This
gives an exact congruence skeleton and a deflated operator bound, while
also showing precisely which extra row-balance statistics a future
both-new-shell argument would have to control.  Nothing here proves a
Hardy--Littlewood asymptotic, a twin-prime lower bound, or a general
breach of the sieve parity barrier.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; physical zero
mode; row provenance; principal row mode; congruence skeleton;
projective mass; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11L07, 11L40.

\input{sections/introduction}
\input{sections/provenance}
\input{sections/zero-first}
\input{sections/one-sided-closure}
\input{sections/energy-boundary}
\input{sections/congruence-skeleton}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
