\section{The assembled-prefix theorem}
\label{sec:assembly}

We now pass from one dyadic divisor label to a complete initial
segment.  We give a direct sharp-prefix proof: the coefficient
$\one_{d\le D_0}$ is inserted into the bilinear distribution theorem
itself.  This packages the cumulative statement without endpoint loss
or dependence on a choice of dyadic partition.

\begin{theorem}[Cumulative divisor-prefix cancellation]
\label{thm:assembled-prefix}
Fix $h\ne0$, $0<\delta<1/2$, and $\eta>0$.  Let $L,K,D_0$ satisfy
\begin{align}
 &LK\asymp_W X,
 \qquad L>2R,
 \qquad 1\le D_0<R,
 \qquad D_0\le V,
 \qquad K>2V,
 \label{eq:assembly-geometry}\\
 &(L,D_0)\in\mathfrak R_\eta,
 \qquad LD_0R\le X^{1-\eta},
 \label{eq:assembly-analysis}
\end{align}
where $\mathfrak R_\eta$ is any signed bilinear distribution profile
with property $\mathrm{BD}_h$.  Then, for every $A>0$,
\begin{equation}
 \cC_{L,K}(D_0)
 \ll_{A,h,W,\psi,\delta,\eta}X(\log X)^{-A}.
 \label{eq:assembled-prefix-bound}
\end{equation}
\end{theorem}

\begin{proof}
Start from the opened expression \eqref{eq:opened-prefix-block}.  We
first remove source prime powers $\ell=p^a$, $a\ge2$.  On the support,
$j\asymp_W K/d$, and \eqref{eq:pointwise-residual} gives, for every
fixed $\eps>0$,
\begin{align}
 &\sum_{\substack{p^a\asymp L\\a\ge2}}
 \Lambda(p^a)
 \sum_{d\le D_0}\sum_{j\asymp K/d}
 |r_R(p^adj+h)|
 \notag\\
 &\hspace{6em}\ll_{W,\eps}
 L^{1/2+\eps}K(\log(2D_0))X^\eps
 \ll_{W,\eps}X^{1+2\eps}L^{-1/2}\log X.
 \label{eq:assembled-source-powers}
\end{align}
Put $\rho_0=1/2-\delta>0$.  Since
$L>2R=X^{\rho_0+o(1)}$, choosing $\eps<\rho_0/8$ makes the last
quantity $O(X^{1-\rho_0/4})$.  Thus it has a fixed power saving.
We may therefore restrict $\ell$ to primes.  In particular,
$\ell>R>|h|$ for all sufficiently large $X$.

For fixed $\ell,d$, apply the row decomposition
\eqref{eq:row-decomposition} with
\begin{equation}
 F_{\ell,X}(u)
 =W(u)\psi\!\left(\frac{Xu}{\ell K}\right).
 \label{eq:assembly-row-weight}
\end{equation}
The family is uniformly supported and uniformly $C^1$ by
$LK\asymp_WX$, and
\[
 F_{\ell,X}(\ell dj/X)
 =W(\ell dj/X)\psi(dj/K).
\]

On the reduced rows $(\ell d,h)=1$, the aggregate prime-progression
error is $O_A(X(\log X)^{-A})$ by
\cref{lem:one-factor-smooth-transfer}, with
\begin{equation}
 a_\ell=\Lambda(\ell)\psi(\ell/L)\one_{\ell\,\mathrm{prime}},
 \qquad
 b_d=\mu(d)\one_{d\le D_0}.
 \label{eq:assembly-separated-coefficients}
\end{equation}
The logarithm in $a_\ell$ is absorbed by requesting one additional
logarithmic power.

It remains to check the nonreduced rows.  Since $\ell>|h|$ is prime,
$(\ell d,h)>1$ implies $(d,h)>1$.  If $p\mid(d,h)$, every integer
$\ell dj+h$ is divisible by $p$; a nonzero von Mangoldt value therefore
forces
\begin{equation}
 \ell dj+h=p^\nu.
 \label{eq:nonreduced-prime-power-equation}
\end{equation}
For each of the finitely many $p\mid h$, only $O_{h,W}(1)$ exponents
occur at scale $X$, while the number of ordered factorizations
$\ell d\mid p^\nu-h$ is $O_{h,\eps}(X^\eps)$.  Hence the total prime
part of the nonreduced rows is $O_{h,W,\eps}(X^\eps)$.  Their continuous
prime mean and complete finite-model mean both vanish.  Indeed,
$\mu(d)\ne0$ makes $d$ squarefree, every divisor of $d$ lies below
$R$, and the local factor at $p\mid(d,h)$ is $1-1=0$.

The finite-row lattice leakage in \eqref{eq:row-decomposition} is
$O(R(\log(2R))^2)$ per ordered pair $(\ell,d)$.  Summing the outer
weights gives
\begin{equation}
 \ll LD_0R(\log X)^3
 \ll X^{1-\eta}(\log X)^3.
 \label{eq:assembled-leakage}
\end{equation}

Finally consider the cutoff drift.  For prime $\ell>R$, squarefree
$d<R$, and $\ell\nmid d$, all divisors of $\ell d$ below $R$ divide
$d$.  Consequently
\begin{equation}
 \Delta_{h,R}(\ell d)=
 \begin{cases}
 \displaystyle\frac{d}{\varphi(d)(\ell-1)},&(d,h)=1,\\[0.7em]
 0,&(d,h)>1.
 \end{cases}
 \label{eq:assembled-drift-formula}
\end{equation}
After insertion into the continuous term of
\eqref{eq:row-decomposition}, its total absolute value is
\begin{align}
 &\ll_W X
 \sum_{\ell\asymp L}
 \frac{\Lambda(\ell)}{\ell(\ell-1)}
 \sum_{d\le D_0}\frac{\mu(d)^2}{\varphi(d)}
 \notag\\
 &\hspace{6em}\ll_W \frac XL(\log(2D_0))^2.
 \label{eq:assembled-drift-total}
\end{align}
This again has a fixed power saving because $L>2R$.  The source powers,
reduced prime errors, nonreduced rows, leakage, and drift are therefore
all $O_A(X(\log X)^{-A})$, after shrinking fixed power margins if
necessary.
\end{proof}

The conclusion has an exact and useful tail formulation.

\begin{corollary}[Exact tail normal form]
\label{cor:tail-normal-form}
Under the hypotheses of \cref{thm:assembled-prefix},
\begin{equation}
 \cH^{\mathrm{HB}}_{L,K}
 =\cT_{L,K}(D_0,V)
 +O_{A,h,W,\psi,\delta,\eta}
   \bigl(X(\log X)^{-A}\bigr)
 \label{eq:tail-normal-form}
\end{equation}
for every $A>0$.
\end{corollary}

\begin{proof}
Combine the exact coefficient split
\eqref{eq:exact-prefix-tail-split} with
\eqref{eq:assembled-prefix-bound}.
\end{proof}

\begin{remark}[What the normal form does and does not do]
The tail coefficient
\[
 \beta_{(D_0,V]}(k)
 =\sum_{\substack{d\mid k\\D_0<d\le V}}\mu(d)
\]
is signed.  Equation \eqref{eq:tail-normal-form} compresses the unknown
part to a shorter divisor interval, but supplies neither positivity nor
cancellation inside that interval.  In particular, it is not a
prime-pair lower bound and does not evade the parity obstruction.
\end{remark}
