\section{Finite certificate, maze exits, and conclusion}
\label{sec:computation}

The companion script
\begin{center}
\texttt{experiments/tpc17\_certificate.py}
\end{center}
performs four deterministic checks:
\begin{enumerate}
 \item it solves the Maynard and Li boundary intersections over exact
 rational arithmetic and verifies the gap $9/17-11/21=2/357$;
 \item it verifies the explicit monomial and $\delta$ ledgers at a
 sample interior point;
 \item it checks
 $\beta_V=\beta_{\le D_0}+\beta_{(D_0,V]}$ on a finite range; and
 \item it tests exact Nyquist Parseval and the $TT^*$ diagonal/off-diagonal
 identity on a deterministic finite matrix.
\end{enumerate}
The generated JSON file records all inputs and residual errors.  These
checks certify algebra and implementation only.  They are not evidence
for an unproved prime-pair asymptotic and are not used in any proof.

The resulting maze has three mathematically distinct exits.

\begin{center}
\small
\begin{tabular}{p{0.18\textwidth}p{0.34\textwidth}p{0.37\textwidth}}
\toprule
Route & Target & Honest stopping result \\
\midrule
Tail route & Estimate a nontrivial subrange of
$\beta_{(D_0,V]}$ by additional factor shape or cancellation &
A larger exact prefix, or a theorem identifying which tail shapes are
inaccessible to current distribution inputs \\
Dispersion route & Prove $o(XL)$ for the averaged two-form correlation
\eqref{eq:offdiagonal-correlation} &
A zero-phase cancellation theorem on a restricted corridor, or a sharp
lower-bound obstruction for existing $TT^*$ information \\
Hybrid route & Use divisor-tail structure before the $TT^*$ expansion &
A determinant-resolved normal form combining $d>D_0$ with
$h(\ell_1-\ell_2)$, even if the final cancellation remains open \\
\bottomrule
\end{tabular}
\end{center}

The paper therefore advances on two fronts.  Analytically, it packages
the factorable divisor slices as a complete initial segment and
compresses the unresolved Vaughan coefficient to an exact tail.
Spectrally, it turns a possible distinguished zero-mode failure into a
sparse uncertainty-cell concentration and then into one explicit
off-diagonal two-form correlation.  The countermodel proves that the
phase mean-square ledgers available here, even together with pointwise
and total-energy bounds, do not close that gate.

The next useful theorem must consequently exploit arithmetic structure
in either the Möbius tail or the determinant-resolved residual pair.
This is a narrower and more falsifiable target than the original
fixed-shift correlation, but it remains well short of a twin-prime or
general Hardy--Littlewood theorem.
