\section{Bilinear distribution inputs and a one-factor smooth transfer}
\label{sec:distribution-transfer}

Write
\begin{equation}
 E_\pi(t;q,h)=\pi(t;q,h)-\frac{\pi(t)}{\varphi(q)}
 \qquad ((q,h)=1).
 \label{eq:pi-error}
\end{equation}
The two imported theorems used below have different logical strengths.
Maynard controls the absolute double sum in a three-inequality region;
Li controls a signed bilinear sum in a larger two-inequality region.
We first formulate the common consequence actually needed by the
assembled packet.

\begin{definition}[Signed bilinear distribution profile]
Fix $\eta>0$.  A set $\mathfrak R_\eta$ of pairs $(L,D)$ has property
$\mathrm{BD}_h$ if, for every fixed $A,C>0$, every pair of sequences
$a_\ell,b_d$ satisfying
\[
 |a_\ell|\le(\log X)^C,
 \qquad |b_d|\le(\log X)^C,
\]
and every $t\asymp X$, one has
\begin{equation}
 \sum_{\substack{\ell\le2L,\ d\le D\\(\ell d,h)=1}}
 a_\ell b_d E_\pi(t;\ell d,h)
 \ll_{A,C,h,\eta}t(\log t)^{-A}
 \label{eq:bd-profile}
\end{equation}
uniformly for $(L,D)\in\mathfrak R_\eta$.  The profile is understood
with a fixed power margin, so replacing $X$ by $t\asymp X$ is harmless.
\end{definition}

The log-bounded formulation is deliberate.  It is the common
consequence of the two imported inputs needed by this paper.  Li's
signed theorem permits the stronger class of divisor-bounded
coefficients, whereas Maynard's absolute unweighted estimate does not
by itself permit arbitrary pointwise divisor weights.

\subsection{The published and version-locked profiles}

Maynard's theorem \citep[Theorem~1.1]{Maynard2025I} implies
$\mathrm{BD}_h$ on
\begin{equation}
 \mathfrak R^{\mathrm M}_\eta
 =\left\{(L,D):
 DL^2\le X^{1-\eta},\quad
 D^{12}L^7\le X^{4-\eta},\quad
 D^{20}L^{19}\le X^{10-\eta}
 \right\}.
 \label{eq:maynard-profile}
\end{equation}
Here the orientation in Maynard's notation is
$(Q_1,Q_2)=(D,2L)$; its three conditions are asymmetric.
Indeed, his theorem bounds the sum of the absolute values of
$E_\pi(t;d\ell,h)$ over the two factor ranges.  Hence log-bounded
separated coefficients can be inserted after requesting additional
logarithmic saving.

The newer input is the following exact version of the result used here.

\begin{assumption}[Li v6 bilinear theorem]
\label{input:li-v6}
Theorem~1.1 in version~6 of \citet{Li2026v6} states that, for fixed
$h\ne0$ and arbitrary
divisor-bounded complex sequences $a_{q_1},b_{q_2}$,
\begin{equation}
 \sum_{\substack{q_1\le Q_1,\ q_2\le Q_2\\(q_1q_2,h)=1}}
 a_{q_1}b_{q_2}E_\pi(t;q_1q_2,h)
 \ll_A t(\log t)^{-A}
 \label{eq:li-v6-theorem}
\end{equation}
provided, with a fixed positive margin,
\begin{equation}
 Q_1^2Q_2\le t^{1-\eta},
 \qquad
 Q_1^7Q_2^{12}\le t^{4-\eta}.
 \label{eq:li-v6-conditions}
\end{equation}
The cited document is an unrefereed preprint revised 27 May 2026; no
part of its proof is reproduced or independently certified here.
\end{assumption}

For Li the orientation is instead $(Q_1,Q_2)=(2L,D)$.  Absorbing fixed
factors into the power margin gives $\mathrm{BD}_h$ on
\begin{equation}
 \mathfrak R^{\mathrm L}_\eta
 =\left\{(L,D):
 DL^2\le X^{1-\eta},\quad
 D^{12}L^7\le X^{4-\eta}
 \right\}.
 \label{eq:li-profile}
\end{equation}
The superscript $\mathrm L$ always denotes the version-locked Li input,
not a theorem proved in this paper.

\begin{remark}[Why other large-modulus theorems are not inserted]
Maynard's $3/5$ well-factorable theorem \citep{Maynard2025II} applies to
collapsed modulus weights possessing triple well-factorability.  The
specific coefficient $\Lambda(\ell)\mu(d)$ with an independently
resolved source factor has no such property in general.  Replacing it
by a factorable sieve weight would change the exact Vaughan packet.
Likewise, splitting a general $d$ into several independent factors
fails for a divisor label that is itself a large prime.  We therefore do
not promote a well-factorable or trilinear theorem to the present packet.
\end{remark}

\subsection{Smooth von Mangoldt transfer}

The signed nature of \eqref{eq:li-v6-theorem} requires the test weight to
preserve separated coefficients.  The following lemma records the exact
allowable dependence.

\begin{lemma}[One-factor-dependent smooth transfer]
\label{lem:one-factor-smooth-transfer}
Let $(L,D)$ belong to a $\mathrm{BD}_h$ profile.  For every $\ell\le2L$,
let $F_{\ell,X}\in C_c^1((0,\infty))$ belong to a family with a common
compact support and a common $C^1$ bound.  Let
$|a_\ell|,|b_d|\le(\log X)^C$.  Then
\begin{align}
 &\sum_{\substack{\ell\le2L,\ d\le D\\(\ell d,h)=1}}
 a_\ell b_d
 \left[
 \sum_{j\ge1}\Lambda(\ell dj+h)
 F_{\ell,X}(\ell dj/X)
 -\frac{X}{\varphi(\ell d)}I_0(F_{\ell,X})
 \right]
 \notag\\
 &\hspace{8em}\ll_{A,C,h,\eta,\mathcal F}X(\log X)^{-A}
 \label{eq:smooth-lambda-transfer}
\end{align}
for every fixed $A>0$, where $\mathcal F$ denotes the common support
and $C^1$ bounds of the weight family.
\end{lemma}

\begin{proof}
We give the transfer in detail because the one-factor restriction is
essential.  First retain only target primes.  Put
\begin{equation}
 \omega_{\ell,X}(t)
 = (\log t)F_{\ell,X}((t-h)/X).
 \label{eq:stieltjes-weight}
\end{equation}
The support lies in one fixed interval $t\asymp X$, and
\begin{equation}
 |\omega_{\ell,X}'(t)|\ll\frac{\log X}{X}
 \label{eq:weight-derivative}
\end{equation}
uniformly in $\ell$.  Stieltjes partial summation makes the difference
between the prime progression sum and its global-prime counterpart
equal to
\begin{equation}
 -\int
 E_\pi(t;\ell d,h)\omega_{\ell,X}'(t)\,dt.
 \label{eq:stieltjes-error}
\end{equation}
There are no endpoint terms after extending the compactly supported
weight by zero.

After summing \eqref{eq:stieltjes-error} over $\ell,d$, fix $t$ inside
the integral.  The coefficient
\begin{equation}
 a_{\ell,t}=a_\ell\omega_{\ell,X}'(t)
 \label{eq:t-dependent-source-coefficient}
\end{equation}
still depends only on $\ell$, while $b_d$ depends only on $d$.
Write
\[
 a_{\ell,t}=\frac{\log X}{X}\widetilde a_{\ell,t},
 \qquad |\widetilde a_{\ell,t}|\le(\log X)^{C'}
\]
using \eqref{eq:weight-derivative}.  The $\mathrm{BD}_h$ estimate
applies pointwise to $\widetilde a_{\ell,t}$ and $b_d$, uniformly in
$t$.  Its $t\asymp X$ scale is multiplied by $(\log X)/X$; integrating
over an interval of length $O(X)$ restores the final $X$ scale and
loses only one fixed logarithmic power.  Increasing the requested
saving absorbs that loss.

The global prime sum satisfies, uniformly over the same family,
\begin{equation}
 \sum_p(\log p)F_{\ell,X}((p-h)/X)
 =XI_0(F_{\ell,X})+O(X\exp(-c\sqrt{\log X})).
 \label{eq:global-pnt-family}
\end{equation}
The accumulated error is negligible because standard divisor estimates
give
\begin{equation}
 \sum_{\ell\le2L,\ d\le D}
 \frac{|a_\ell b_d|}{\varphi(\ell d)}
 \ll_C(\log X)^{C'}.
 \label{eq:inverse-totient-weight}
\end{equation}

It remains to restore target prime powers.  If $p^\nu\asymp X$,
$\nu\ge2$, and $p^\nu\equiv h\pmod{\ell d}$, then
$\ell d\mid p^\nu-h$.  Hence the total number of ordered pairs is
bounded by a fixed divisor function, and
\begin{equation}
 \sum_{\substack{p^\nu\asymp X\\\nu\ge2}}
 (\log p)\tau_3(|p^\nu-h|)^{C'}
 \ll_{C',\eps}X^{1/2+\eps}.
 \label{eq:target-prime-powers}
\end{equation}
This is absorbed by any prescribed logarithmic saving.  Combining the
prime, global-main-term, and prime-power estimates proves
\eqref{eq:smooth-lambda-transfer}.
\end{proof}

\begin{remark}[Forbidden pair dependence]
The proof does not allow an arbitrary family $F_{\ell,d,X}$.  In the
signed Li layer, the Stieltjes derivative of such a family would create
a genuinely pair-dependent coefficient, outside
\eqref{eq:li-v6-theorem}.  The packet used below is admissible because
its weight has the exact form
\begin{equation}
 F_{\ell,X}(u)
 =W(u)\psi\!\left(\frac{Xu}{\ell K}\right),
 \qquad
 F_{\ell,X}(\ell dj/X)
 =W(\ell dj/X)\psi(dj/K),
 \label{eq:one-factor-weight-identity}
\end{equation}
which is independent of $d$ once $\ell$ is fixed.  The product ledger
$LK\asymp_WX$ supplies a common compact support and common $C^1$ bound.
\end{remark}
