\section{Exact finite certificate}
\label{sec:tpc44-certificate}

The companion script
\begin{center}
\texttt{experiments/tpc44\_certificate.py}
\end{center}
uses only Python's standard library and exact integer, rational, and
Gaussian--integer arithmetic.  It performs no random sampling.  The
frozen finite regressions verify:
\begin{enumerate}[label=(\roman*)]
 \item the low--high label split and projected diagonal identity;
 \item the pointwise robust face inequality for every finite sign
 assignment in several exhaustive Gram packets;
 \item the smooth physical sector after high--prime averaging;
 \item the exact forward and reverse Walsh layers and their Parseval
 ledgers;
 \item the coefficient recurrence, physical invariance, and product
 formula in \cref{thm:tpc44-correlation-product};
 \item the kernel projection bound and low--restriction energy estimate;
 \item the conditional face increments and likelihood ratios; and
 \item every formula in the rough degree--two obstruction, for a finite
 family of \(R\) and \(\lambda\).
\end{enumerate}
The script also checks the rational endpoint ledger
\begin{equation}
 \lambda_0=\frac{62549}{52500},
 \qquad
 \frac{\lambda_0}{501}=\frac{62549}{26302500},
 \qquad
 \frac1{400}-\frac{\lambda_0}{501}
 =\frac{12829}{105210000}>0,
 \label{eq:tpc44-certificate-ledger}
\end{equation}
and scans its own syntax tree to exclude floating--point literals,
random imports, true division, and optimization--sensitive
\texttt{assert} statements.

The frozen run performs \(15{,}677\) exact checks.  Its canonical
certificate digest is
\begin{center}
\texttt{24b7eb3f19af7a2c8a016672020ee593578463857f1d7fe3dabedd7e59b57433}.
\end{center}
The certified source SHA--256 is
\begin{center}
\texttt{1bc866f4e7981b3beea6fd4682fc702bef7cc28b949c192a628e1582d69a5da1},
\end{center}
and the canonical JSON SHA--256 is
\begin{center}
\texttt{bc0f83c2ba177f395a4c6b22a2d5c5bf1773249134149a4fbce4326bb2e7d7ea}.
\end{center}
Normal and optimized Python executions produce byte--identical JSON.

Finite computation certifies only finite algebra and combinatorics.  It
does not certify the asymptotic Rankin argument, maximal order of
\(\omega\), Bonami--Beckner inequality, Borel--Cantelli lemma, inherited
TPC diagonal bound, or any physical M\"obius cancellation.  In
particular, the certificate is not numerical evidence for twin primes
or for the unproved high--prime gate.
