\section{The inherited equality--Walsh interface}
\label{sec:tpc44-interface}

We isolate exactly the part of TPC--43 used here.  The left and right
output coordinates are combined into one finite index set \(i\).  For
each \(i\),
\begin{equation}
 S_i(\varepsilon)=\sum_{u\in\mathcal U_i}b_{i,u}\chi_u(\varepsilon),
 \qquad
 Z_0(\varepsilon)=\sum_i|S_i(\varepsilon)|^2,
 \label{eq:tpc44-coordinate-packet}
\end{equation}
where every \(u\) is squarefree and the nonzero labels in a fixed
\(\mathcal U_i\) are pairwise distinct.  The characters are
\begin{equation}
 \chi_u(\varepsilon)=\prod_{p\mid u}\varepsilon_p.
 \label{eq:tpc44-character}
\end{equation}
All coefficients and label sets are deterministic after the inherited
TPC packet has been fixed.

The atomic diagonal is
\begin{equation}
 \cD_0:=\sum_i\sum_{u\in\mathcal U_i}|b_{i,u}|^2.
 \label{eq:tpc44-diagonal}
\end{equation}
Pairwise label distinctness within each coordinate and Walsh
orthogonality give
\begin{equation}
 \E Z_0=\cD_0.
 \label{eq:tpc44-mean-diagonal}
\end{equation}
If \(\cD_0=0\), every coefficient vanishes and all statements below are
trivial.  We henceforth suppose \(\cD_0>0\).

Expanding the squared norms and grouping equal squarefree
symmetric--difference kernels gives real coefficients \(C(\kappa)\)
such that
\begin{align}
 Z_0(\varepsilon)
 &=\cD_0+F(\varepsilon),
 \label{eq:tpc44-Z-F}\\
 F(\varepsilon)
 &=\sum_{\kappa>1}C(\kappa)\chi_\kappa(\varepsilon),
 \label{eq:tpc44-F-spectrum}\\
 Z_0(-\one)
 &=\cD_0+\sum_{\kappa>1}\mu(\kappa)C(\kappa),
 \label{eq:tpc44-physical-corner}\\
 V:=\|F\|_2^2
 &=\operatorname{Var}(Z_0)
 =\sum_{\kappa>1}|C(\kappa)|^2.
 \label{eq:tpc44-variance-parseval}
\end{align}
Every prime in these formulas belongs to the finite support of the
labels.  We extend \(C\) by zero to all other squarefree integers and set
\(C(1)=0\).

At the physical equality alias the labels have the more specific form
\begin{equation}
 u_{\alpha,j}
 =d_\alpha n_{\alpha,j,0}
 =d_\alpha(\ell_\alpha d_\alpha j+h),
 \label{eq:tpc44-physical-label}
\end{equation}
where \(h\ne0\) is fixed,
\begin{align}
 \ell_\alpha d_\alpha&\asymp Q,
 &Q&=X^{267/400+o(1)},
 \notag\\
 j&\asymp J,
 &J&=X^{133/400+o(1)},
 \label{eq:tpc44-endpoint-scales}\\
 d_\alpha&\asymp D_0,
 &D_0&=X^{10049/52500+o(1)}.
 \notag
\end{align}
The notation \(D_0\) for the divisor scale is distinct from the
calligraphic energy \(\cD_0\).  Since \(QJ\asymp X\),
\begin{equation}
 u_{\alpha,j}
 \le X^{\lambda_0+o(1)},
 \qquad
 \lambda_0=1+\frac{10049}{52500}
 =\frac{62549}{52500}.
 \label{eq:tpc44-label-size}
\end{equation}
The equality endpoint budget and inherited diagonal estimate are
\begin{equation}
 K_B=X^{1/400+o(1)},
 \qquad
 \cD_0\ll X^{o(1)}Q^2J,
 \label{eq:tpc44-endpoint-budget}
\end{equation}
and the desired physical conclusion would be
\begin{equation}
 Z_0(-\one)\ll X^{o(1)}K_BQ^2J.
 \label{eq:tpc44-physical-target}
\end{equation}

For later comparison, Boolean hypercontractivity
\citep{Bonami1970,Beckner1975,Harper2019HighMoments} gives a soft variance
bound.  Put
\begin{equation}
 d_X:=\max_{i,u\in\mathcal U_i}\omega(u).
 \label{eq:tpc44-label-degree}
\end{equation}
The maximal order of \(\omega\) and \eqref{eq:tpc44-label-size} imply
\begin{equation}
 d_X\le(\lambda_0+o(1))\frac{\log X}{\log\log X}.
 \label{eq:tpc44-degree-bound}
\end{equation}
Applying the \(L^4\) inequality to each \(S_i\), then Minkowski to
\(Z_0=\sum_i|S_i|^2\), yields
\begin{equation}
 V^{1/2}\le\|Z_0\|_2
 \le3^{d_X}\cD_0=X^{o(1)}\cD_0.
 \label{eq:tpc44-soft-variance}
\end{equation}
This estimate is useful after a structural compression; by itself it
does not evaluate \(F\) at one prescribed corner.
