\section{Introduction and main results}
\label{sec:tpc44-introduction}

The terminal obstruction isolated in TPC--42 is a coherent Hilbert
energy with one source and one target M\"obius value in each row
\citep{WangTPC42}.  TPC--43 replaced \(\mu\) by one globally consistent
Rademacher multiplicative field and proved exact annealed
diagonalization at the equality alias \citep{WangTPC43}.  The same paper
compressed every unequal row pair into a squarefree Walsh kernel:
\begin{equation}
 Z_0(\varepsilon)
 =\cD_0+\sum_{\kappa>1}C_X(\kappa)\chi_\kappa(\varepsilon),
 \qquad
 Z_0(-\one)
 =\cD_0+\sum_{\kappa>1}\mu(\kappa)C_X(\kappa).
 \label{eq:tpc44-intro-walsh}
\end{equation}
Here \(Z_0\ge0\), \(\E Z_0=\cD_0\), and \(Z_0(-\one)\) is the literal
physical equality energy.  The subscript \(X\) is suppressed below.

The difficulty is now extremely specific.  Annealed estimates describe
most vertices of the prime cube, whereas the arithmetic problem asks
for one prescribed vertex.  A small exceptional set may contain that
vertex at every scale.  The present paper does not try to hide this
quantifier gap.  Instead it asks how many prime coordinates can be made
adversarial before the annealed endpoint is lost.

\subsection{Uniform control of an entire small--prime face}

Every nonzero equality atom has a squarefree label \(u\).  Split it at
\(z\ge2\) as
\begin{equation}
 u=u_{\le z}u_{>z},
 \qquad
 \Pplus(u_{\le z})\le z<\Pminus(u_{>z}),
 \label{eq:tpc44-intro-label-split}
\end{equation}
with the usual conventions for the factor \(1\).  Let
\begin{equation}
 \nu_z:=\#\{u_{\le z}:u\text{ occurs as an equality label}\}.
 \label{eq:tpc44-intro-nu}
\end{equation}
This is an actual packet complexity, not the cardinality
\(2^{\pi(z)}\) of the entire small--prime cube.

The first main theorem is the following robust face estimate; its
abstract version is proved in \cref{sec:tpc44-robust-face}.

\begin{theorem}[Robust small--prime face]
\label{thm:tpc44-intro-robust-face}
For every \(z\ge2\) and \(L\ge1\),
\begin{equation}
 \Pp_{\varepsilon_p:p>z}\!\left(
  \sup_{\sigma\in\{-1,1\}^{\{p\le z\}}}
  Z_0(\sigma,\varepsilon_{>z})
  >L\nu_z\cD_0
 \right)
 \le L^{-1}.
 \label{eq:tpc44-intro-face-probability}
\end{equation}
In particular, some high--prime environment satisfies
\begin{equation}
 \sup_{\sigma}Z_0(\sigma,\varepsilon_{>z})\le\nu_z\cD_0.
 \label{eq:tpc44-intro-face-existence}
\end{equation}
\end{theorem}

The supremum is inside the probability.  Thus the theorem first selects
one high--prime environment and then allows every small--prime sign to be
changed, jointly and adversarially.  It is stronger than proving a tail
bound for each fixed small--prime assignment separately.

At the TPC endpoint the labels obey
\begin{equation}
 u\le X^{\lambda_0+o(1)},
 \qquad
 \lambda_0=1+\frac{10049}{52500}
 =\frac{62549}{52500}.
 \label{eq:tpc44-intro-lambda}
\end{equation}
A Rankin count of possible projected labels yields the quantitative
advance.

\begin{theorem}[A mildly superlogarithmic frozen block]
\label{thm:tpc44-intro-quantitative-face}
Put
\begin{equation}
 z_X=(\log X)^{501/500},
 \qquad
 L_X=\exp\!\left(\frac{\log X}{\sqrt{\log\log X}}\right).
 \label{eq:tpc44-intro-z-L}
\end{equation}
Then
\begin{equation}
 \nu_{z_X}
 \le X^{62549/26302500+o(1)}
 \label{eq:tpc44-intro-nu-bound}
\end{equation}
and, for all sufficiently large \(X\),
\begin{equation}
 L_X\nu_{z_X}\le K_B,
 \qquad K_B=X^{1/400+o(1)}.
 \label{eq:tpc44-intro-budget}
\end{equation}
Consequently
\begin{equation}
 \Pp_{>z_X}\!\left(
  \sup_{\sigma_{p\le z_X}}
  Z_0(\sigma,\varepsilon_{>z_X})
  >K_B\cD_0
 \right)
 \le
 \exp\!\left(-\frac{\log X}{\sqrt{\log\log X}}\right).
 \label{eq:tpc44-intro-quantitative-probability}
\end{equation}
\end{theorem}

In particular, the signs at all primes \(p\le z_X\) may be overwritten
by \(-1\), exactly as required by \(\mu\).  The theorem does not set the
remaining high--prime signs to \(-1\).

\subsection{Exact descents and the remaining gate}

Let \(F=Z_0-\cD_0\), extend \(C(\kappa)\) by zero, and list the active
primes as \(p_1<\cdots<p_R\).  For squarefree \(m\), define
\begin{equation}
 C_r(m):=\sum_{a\mid p_1\cdots p_r}\mu(a)C(am),
 \qquad (m,p_1\cdots p_r)=1.
 \label{eq:tpc44-intro-Cr}
\end{equation}
Then setting the first \(r\) signs to \(-1\) is exactly
\begin{equation}
 F(-\one_{\le p_r},\varepsilon_{>p_r})
 =\sum_{(m,p_1\cdots p_r)=1}C_r(m)\chi_m(\varepsilon).
 \label{eq:tpc44-intro-restricted-F}
\end{equation}
If \(E_r\) is the sum of \(|C_r(m)|^2\) over squarefree \(m\) coprime to
\(p_1\cdots p_r\), coefficient pairing gives
\begin{equation}
 E_r=(1-\theta_r)E_{r-1},
 \qquad -1\le\theta_r\le1,
 \label{eq:tpc44-intro-energy-step}
\end{equation}
and hence the exact identity
\begin{equation}
 \boxed{
 |F(-\one)|^2
 =\operatorname{Var}(Z_0)
  \prod_{r=1}^{R}(1-\theta_r).}
 \label{eq:tpc44-intro-coefficient-product}
\end{equation}
This is a restriction identity, not a probabilistic estimate.

There is also a nonnegative face transport.  Average the first \(r\)
prime signs while keeping every later one equal to \(-1\), and call the
result \(A_r\).  When \(Z_0(-\one)>0\),
\begin{equation}
 \frac{Z_0(-\one)}{\cD_0}
 =\prod_{r=1}^{R}(1+\delta_r),
 \qquad -1\le\delta_r\le1.
 \label{eq:tpc44-intro-face-product}
\end{equation}
Under the energy--biased probability
\(d\QZ=(Z_0/\cD_0)dU\), each factor is a conditional likelihood:
\begin{equation}
 1+\delta_r
 =2\QZ\!\left(
  \varepsilon_{p_r}=-1
  \mid
  \varepsilon_{p_{r+1}}=\cdots=\varepsilon_{p_R}=-1
 \right).
 \label{eq:tpc44-intro-likelihood}
\end{equation}
If \(Z_0(-\one)=0\), the desired upper endpoint is automatic.  Thus the
nontrivial endpoint selection is exactly a cumulative boundary--path
problem.

The distinction between local and cumulative control is essential.  In
\cref{sec:tpc44-sharp-obstruction} we construct a degree--two Gram
energy with all nonconstant kernels \(z\)-rough for which
\begin{equation}
 \frac{\operatorname{Var}Z}{(\E Z)^2}\longrightarrow0,
 \qquad
 \max_r|\delta_r|\longrightarrow0,
 \qquad
 \sum_r\delta_r^2\longrightarrow0,
 \label{eq:tpc44-intro-small-local}
\end{equation}
but \(Z(-\one)/\E Z\to\infty\).  Therefore neither a second moment nor
small primewise defects can finish the physical corner.  The remaining
positive target is a one--sided cumulative estimate for the actual
\(C_X(\kappa)\), after the small primes have been folded exactly.

\subsection{Claim boundary and organization}

The paper proves a partial de--randomization: inside a density--one set
of high--prime environments, a growing mildly superlogarithmic block can
be overwritten by the physical signs.  It does not prove that the
all--minus high--prime environment is typical, that the product in
\eqref{eq:tpc44-intro-coefficient-product} is \(X^{o(1)}\), or that the
rough tail cancels.  In particular, it proves no fixed--shift Chowla
estimate, no breach of the sieve parity barrier, no Hardy--Littlewood
prime--pair asymptotic, and no infinitude of twin primes.

\Cref{sec:tpc44-interface} records the inherited interface.
\Cref{sec:tpc44-prime-martingales} gives the exact Walsh martingales.
\Cref{sec:tpc44-robust-face,sec:tpc44-quantitative-cutoff} prove the
uniform face theorem and its endpoint exponent.  The two exact descents
are developed in
\cref{sec:tpc44-coefficient-descent,sec:tpc44-face-transport}.
\Cref{sec:tpc44-sharp-obstruction} gives the sharp obstruction.
\Cref{sec:tpc44-literature,sec:tpc44-next-gate} compare the result with
the literature and state the next coefficient--specific gate.  The
finite certificate is described in \cref{sec:tpc44-certificate}.
