\section{Literature boundary}
\label{sec:tpc44-literature}

The prime--by--prime conditioning in
\cref{sec:tpc44-prime-martingales,sec:tpc44-face-transport} is the Walsh
analogue of a finite reverse martingale.  Its differences group the
coefficient spectrum by the least prime factor.  Hypercontractive moment
bounds for Rademacher multiplicative functions, such as Probability
Result~2.3 of \citet{Harper2019HighMoments}, control such polynomials in
the annealed model.  They do not, by themselves, control a prescribed
vertex of the cube.  The robust face theorem uses the additional Gram
representation and injective equality labels, rather than a stronger
generic moment inequality.

General low--influence principles also have a different quantifier.
The invariance theorem of
\citet[Theorem~3.18]{MosselODonnellOleszkiewicz2010} is distributional
under bounded--degree and low--influence hypotheses.  Even when those
hypotheses hold, the theorem describes typical product--space inputs,
not the all--minus input.  The obstruction in
\cref{thm:tpc44-rough-obstruction} makes this distinction explicit: its
degree is two and its normalized influences vanish, yet its specified
corner diverges.

Small--bias spaces provide a finite derandomization of Walsh averages.
\citet[Theorem~3.2]{NaorNaor1993} construct such spaces with a logarithmic
randomness seed.  Applied to
\(
 F(\varepsilon)=\sum C(\kappa)\chi_\kappa(\varepsilon)
\), the direct conclusion has the form
\begin{equation}
 |\E_{\varepsilon\in\mathcal S}F(\varepsilon)|
 \le\epsilon\sum_\kappa|C(\kappa)|.
 \label{eq:tpc44-small-bias-l1}
\end{equation}
It therefore needs an \(\ell^1\) coefficient estimate and locates some
good sign vector; it does not identify the physical vector.  Classical
Riesz--product results, for example \citet[Theorem~1.2]{Peyriere1975},
concern singularity of limiting product measures and likewise do not
bound a specified finite corner.

Strong theorems for unweighted rough numbers do not supply the missing
signed estimate.  \citet[Theorem~1.1]{GorodetskyRoughVariance} proves a
variance asymptotic for the indicator of integers without small prime
factors in averaged short intervals.  This controls spatially averaged
roughness, not
\begin{equation}
 \sum_{\kappa}\mu(\kappa)C_X(\kappa)
 \label{eq:tpc44-weighted-mobius-sum}
\end{equation}
for a signed, packet--dependent coefficient.  Large--small prime
duality \citep{Alladi1977} and recent effective least--prime identities
such as \citet[Theorem~1.1]{Tenenbaum2026} exploit special divisor or
harmonic weights.  No corresponding convolution identity has been
proved for \(C_X\).

M\"obius orthogonality to fixed--complexity structured sequences is a
second possible route.  For instance, \citet[Theorem~1.1]{GreenTao2012}
give arbitrary logarithmic saving against polynomial nilsequences of
fixed complexity.  The present \(C_X(\kappa)\) is scale dependent and is
not known to be a fixed--complexity nilsequence, a bounded sum of such
sequences, or a member of an analogous class.  We therefore cite that
theorem as a route boundary, not as a black box that applies here.

The closest classical diagnosis is the sieve parity problem.  The
asymptotic sieve of \citet[Theorem~1]{FriedlanderIwaniec1998} obtains a
prime conclusion only after an explicit bilinear axiom is added to
local--density and remainder information.  In a broad modern sieve
framework, \citet[Theorem~2.1]{FordMaynard2024} show that insufficient
Type--II information allows sequences satisfying nontrivial Type--I and
Type--II estimates while still failing to force primes.  Their
theorems do not apply literally to the generally signed \(C_X\), but
they support the route map: rough--kernel counting alone cannot control
\eqref{eq:tpc44-weighted-mobius-sum}; a coefficient--specific bilinear
estimate or an equally strong arithmetic substitute is needed.

To avoid an accidental application of an unrelated theorem, we record
the current negative information.  The coefficient \(C_X\) is real but
generally signed, packet and mask dependent, and changes with \(X\).  It
is not known to be multiplicative, nonnegative, low degree, uniformly
low influence, \(\ell^1\)-small, smooth, divisor--convolutional, a fixed
nilsequence, or controlled in a Type--II norm.  The results cited in this
section diagnose possible inputs; none proves the remaining physical
corner estimate.
