\section{Introduction and strict scope}
\label{sec:introduction-scope}

For a nonzero integer $h$ and $X\ge2$, put
\begin{equation}\label{eq:intro-pair-correlation}
 \cC_h(X)=\sum_{X<n\le2X}\Lambda(n)\Lambda(n+h),
\end{equation}
with the convention $\Lambda(t)=0$ for $t\le0$.  The Hardy--Littlewood
prediction is
\begin{equation}\label{eq:intro-hl-prediction}
 \cC_h(X)\sim\mathfrak S(h)X
\end{equation}
for each fixed even $h$, where
\begin{equation}\label{eq:intro-singular-series}
 \mathfrak S(h)=
 \begin{cases}
 \displaystyle
 2\prod_{p>2}\left(1-\frac1{(p-1)^2}\right)
 \prod_{\substack{p\mid h\\p>2}}\frac{p-1}{p-2},&2\mid h,\\[1.3ex]
 0,&2\nmid h.
 \end{cases}
\end{equation}
Even an $o(X)$ error in \eqref{eq:intro-hl-prediction} is not known for any
single nonzero even shift; the case $h=2$ would imply the twin-prime
conjecture.  This paper does not alter that fixed-shift fact.

The elementary identity
\begin{equation}\label{eq:intro-mobius-log}
 \Lambda(n)=-\sum_{d\mid n}\mu(d)\log d
\end{equation}
gives, for every $1\le D\le2X$, the exact decomposition
\begin{align}
 a_D(n)&=-\sum_{\substack{d\mid n\\d\le D}}\mu(d)\log d,
 \label{eq:intro-short-weight}\\
 r_D(n)&=\Lambda(n)-a_D(n)
       =-\sum_{\substack{d\mid n\\d>D}}\mu(d)\log d,
 \label{eq:intro-defect-weight}\end{align}
and hence
\begin{equation}\label{eq:intro-exact-split}
 \cC_h(X)=\cC_{h,\le D}(X)+\cT_{h,>D}(X),
\end{equation}
where
\begin{align}
 \cC_{h,\le D}(X)
 &=\sum_{X<n\le2X}a_D(n)\Lambda(n+h),
 \label{eq:intro-short-correlation}\\
 \cT_{h,>D}(X)
 &=\sum_{X<n\le2X}r_D(n)\Lambda(n+h).
 \label{eq:intro-large-defect}
\end{align}
The terminology \emph{source divisor} refers to a divisor introduced by
expanding the first von Mangoldt factor in \eqref{eq:intro-mobius-log}.

TPC-6 proved for each fixed nonzero even $h$ that classical
Bombieri--Vinogradov theory
evaluates \eqref{eq:intro-short-correlation} at
$D=X^{1/2}(\log X)^{-B}$, and consequently that
\eqref{eq:intro-hl-prediction} is equivalent to
$\cT_{h,>D}(X)=o(X)$ \citep{WangTPCSix2026}.  That equivalence named the
missing object but supplied no estimate for it.  The present paper retains
the same complete remainder and changes the topology in the shift variable:
pointwise control is replaced by control outside a set of asymptotic density
zero in each sufficiently long shift window.

\subsection{Main contributions and provenance}
\label{subsec:intro-contributions}

The logical inputs and outputs are separated as follows.
\begin{enumerate}[label=\textbf{R\arabic*.},leftmargin=3.2em]
 \item We prove a singular-series coefficient estimate uniform for
 $1\le|h|\le z^K$.  Together with the maximal
 Bombieri--Vinogradov theorem, it yields
 \[
  \cC_{h,\le D}(X)
  =\mathfrak S(h)X+O_A(X(\log X)^{-A})
 \]
 simultaneously for all $1\le|h|\le2X^{1-\eps}$.  The analytic ingredients
 are classical; the point is the uniformity needed for the growing shift
 window.
 \item We use the averaged Hardy--Littlewood theorem of
 \citet[Theorem~1.3(i)]{MatomakiRadziwillTao2019}.  It gives the same main
 term for the full correlation outside
 $O_{A,\eps}(H(\log X)^{-A})$ shifts when
 $H\ge X^{8/33+\eps}$.  Subtraction proves that the \emph{same full defect}
 from TPC-6 is small at almost all such shifts.  The exponent $8/33$ and the
 deep prime-correlation estimate are entirely due to those authors; we do
 not claim a new circle-method, dispersion, or Type~II estimate.
 \item We record the exact Fourier representation of the defect and its
 Plancherel energy.  This gives a rigorous translation-dynamical interface,
 but the identity alone contains no cancellation estimate.
 \item We prove a finite-conductor energy-escape theorem.  Periodic
 functions of every modulus $q\le N^{1-\delta}$ capture only
 $O_\delta(\log\log(3q)/\log N)$ of the $L^2$ energy of $\Lambda-1$.  This
 quantifies a linear periodic-approximation boundary and does not extend to
 arbitrary nonlinear or nonlocal information.
\end{enumerate}

Earlier almost-all-shift prime-pair results culminated, for the present
purpose, in the theorem of Matom\"aki, Radziwi\l\l, and Tao, which improved
the shift-window threshold from $X^{1/3+\eps}$ to
$X^{8/33+\eps}$ \citep{Mikawa1991,MatomakiRadziwillTao2019}.  Our result is
not a further improvement of that threshold.  It transfers their theorem to
the exact large-source-divisor coordinate singled out by the preceding
operator and sieve analysis.

\subsection{What is not claimed}
\label{subsec:intro-not-claimed}

For clarity, none of the following is asserted.
\begin{enumerate}[label=\textbf{B\arabic*.},leftmargin=3.2em]
 \item The exceptional set is not shown to avoid any prescribed shift.
 In particular, it may contain $h=2$ for every $X$.
 \item No individual dyadic layer of \eqref{eq:intro-defect-weight} is shown
 to be small.  Cancellation may occur between different divisor scales.
 \item The Fourier identity is not a spectral gap, an operator
 isomorphism, or an estimate for a fixed Fourier coefficient.
 \item The finite-conductor theorem concerns orthogonal approximation by a
 single periodic linear space.  It is not a universal parity-barrier theorem
 and does not rule out growing bilinear, dispersion, automorphic, or other
 nonlocal methods.
 \item No lower bound for twin primes, no fixed-shift asymptotic, and no new
 level of distribution for the primes is proved.
\end{enumerate}
