\section{Translation dynamics and additive spectral coordinates}
\label{sec:spectral-density}

The shift variable has an exact and elementary dynamical realization.  This
section records it in order to distinguish the resulting identity from the
analytic estimate imported in \cref{thm:MRT-averaged-HL}.

Put $\e(x)=\exp(2\pi i x)$.  For a finitely supported sequence
$f:\Z\to\C$, define
\begin{equation}\label{eq:additive-Fourier-transform}
 \widehat f(\theta)=\sum_{n\in\Z}f(n)\e(n\theta),
 \qquad \theta\in\T=\R/\Z.
\end{equation}

\begin{proposition}[Exact Fourier representation of correlations]
\label{prop:exact-correlation-spectrum}
Let $f,g:\Z\to\R$ be finitely supported and set
\begin{equation}\label{eq:generic-shift-correlation}
 C_h(f,g)=\sum_{n\in\Z}f(n)g(n+h).
\end{equation}
Then
\begin{align}
 C_h(f,g)
 &=\int_{\T}
   \overline{\widehat f(\theta)}\widehat g(\theta)
   \e(-h\theta)\,d\theta,
 \label{eq:correlation-Fourier-coefficient}\\
 \sum_{h\in\Z}|C_h(f,g)|^2
 &=\int_{\T}|\widehat f(\theta)|^2
                  |\widehat g(\theta)|^2\,d\theta.
 \label{eq:correlation-Plancherel}
\end{align}
Equivalently, if $U^h g(n)=g(n+h)$ is the unitary integer-translation
representation on $\ell^2(\Z)$, then
\begin{equation}\label{eq:translation-matrix-coefficient}
 C_h(f,g)=\langle f,U^h g\rangle_{\ell^2(\Z)}.
\end{equation}
\end{proposition}

\begin{proof}
Expand the integrand in \eqref{eq:correlation-Fourier-coefficient}.  Fourier
orthogonality retains exactly the pairs $t=n+h$.  Formula
\eqref{eq:correlation-Plancherel} is Parseval applied to the Fourier
coefficients in \eqref{eq:correlation-Fourier-coefficient}, and
\eqref{eq:translation-matrix-coefficient} is the definition of $U^h$.
\end{proof}

For the defect application, let $Y=2X^{1-\eps}$ and define
\begin{align}
 f_{X,D}(n)&=r_D(n)\one_{X<n\le2X},
 \label{eq:defect-Fourier-sequence}\\
 g_{X,Y}(t)&=\Lambda(t)\one_{X-Y<t\le2X+Y}.
 \label{eq:prime-Fourier-sequence}
\end{align}
For every $|h|\le Y$,
\begin{equation}\label{eq:defect-as-matrix-coefficient}
 \cT_{h,>D}(X)
 =C_h(f_{X,D},g_{X,Y})
 =\langle f_{X,D},U^h g_{X,Y}\rangle.
\end{equation}
Thus the complete defect is an inverse Fourier coefficient of
\begin{equation}\label{eq:defect-spectral-product}
 \overline{\widehat f_{X,D}(\theta)}
 \widehat g_{X,Y}(\theta).
\end{equation}
The global energy identity is
\begin{equation}\label{eq:defect-global-Fourier-energy}
 \sum_{h\in\Z}|C_h(f_{X,D},g_{X,Y})|^2
 =\int_{\T}|\widehat f_{X,D}(\theta)|^2
             |\widehat g_{X,Y}(\theta)|^2\,d\theta.
\end{equation}

\begin{remark}[Identity versus estimate]
Neither \eqref{eq:defect-spectral-product} nor
\eqref{eq:defect-global-Fourier-energy} shows that a coefficient is small.
The analytic content in \cref{thm:complete-defect-almost-all} comes from
Bombieri--Vinogradov for the short divisor coordinate and from the theorem
of Matom\"aki, Radziwi\l\l, and Tao for the full correlation.  Parseval does
not replace those inputs.
\end{remark}

\begin{remark}[A triangular family, not a fixed mixing system]
Both vectors in \eqref{eq:defect-as-matrix-coefficient}, the cutoff $D$, and
the window grow with $X$.  Therefore
\cref{cor:fixed-Lp-closure} is a statement about a triangular family of
translation matrix coefficients.  It is not a mixing theorem for one fixed
pair of vectors, a spectral gap for $U$, or a spectral isomorphism with a
logistic map.
\end{remark}

\subsection{Why density convergence does not select a fixed shift}
\label{subsec:density-does-not-select}

The topology in \cref{cor:fixed-Lp-closure} deliberately forgets a set of
vanishing relative size.  Evaluation at one coordinate is not uniformly
continuous in that topology.

\begin{proposition}[Fixed-coordinate spike]
\label{prop:fixed-coordinate-spike}
Let $\cH_X\subset\Z$ be finite sets with $|\cH_X|\to\infty$, all containing
a fixed integer $h_\ast$.  Define
\begin{equation}\label{eq:spike-sequence}
 s_X(h)=\one_{h=h_\ast}.
\end{equation}
Then, for every fixed $1\le p<\infty$,
\begin{equation}\label{eq:spike-Lp-vanishing}
 \left(\frac1{|\cH_X|}\sum_{h\in\cH_X}|s_X(h)|^p\right)^{1/p}
 =|\cH_X|^{-1/p}\longrightarrow0,
\end{equation}
while $s_X(h_\ast)=1$ for every $X$.
\end{proposition}

Consequently, no abstract passage from \eqref{eq:fixed-Lp-closure} to a
bound at $h=2$ is possible.  In fact the allowance
$O(H(\log X)^{-A})$ in \eqref{eq:complete-defect-exceptions} grows without
bound in the permitted power-sized windows, so the exceptional set may
contain any preassigned finite collection of shifts at every scale.
