\begin{abstract}
The fixed-shift packet developed in TPC--47--TPC--62 eventually uses a
finite retained relation \(\cI_X\) of source rows and cofactors.  The
earlier residual formulas, however, quantify over already supported
\((m,r)\)-pairs, while the later coefficient space rectangularizes the
relation across orbit and opposite-row labels.  No displayed theorem had
identified that pair relation with the literal full incidence from which
the physical terminal operator is built.  Consequently, a favorable
cofactor-exposure estimate cannot be inferred from the inherited interface
without a circular support assumption.

We repair this logical provenance interface at one fixed nonzero shift.  For an arbitrary
finite literal incidence, we prove exact criteria for when pair projection
and rectangular completion preserve the pre-terminal raw form, the
terminal atomic map, or the grouped physical operator.  The three criteria
are different.  We construct the unique minimal terminal-faithful pair
relation when it exists, identify the spurious-cross obstruction when it
does not, and show that the full incidence hypergraph is then the canonical
replacement.  Applied to the native very-high carrier, this gives a
coefficient-independent maximal eligible relation, an effective-core
identity, and the exact row factorization
\[
 \frac{W_R^{\cI}(m)}{W_H(m)}
 =\alpha_m\theta_m,
\]
with an explicit zero-alignment convention.
It separates terminal-support alignment from retained-relation completion
and yields sharp uniform and distinguished exposure constants.

For the literal single-band provenance
\(\sqrt{N_+}<p\le N_-/R_0\), intersection with the critical very-high
face \(p>y\) is confined to
\(R_0\le r<N_+/y\), up to one fixed-ratio transition window.  At
\(y\asymp Q\), the balanced band, and in fact every band certified by the
inherited freezing inequality, has \(R_0\gg J\) and is eventually
disjoint from the critical face.  Retuning to \(R_0\asymp J\) makes the
old coefficient-blind freezing loss equal to
\(15077/105000>1/400\).  Even after an independently justified retuning,
every omitted full dyadic block below the top window makes the inherited
Brun--Titchmarsh harmonic certificate yield zero fixed-power saving.  A
new multiscale construction or a weighted largest-prime-factor/terminal
distribution theorem is therefore necessary for this support-only exposure
branch.  The result is an L1 provenance-completion criterion and a sharp closure of two support-only
certificates; it is not a fixed-shift parity estimate, a prime-pair lower
bound, or a twin-prime result.
\end{abstract}
