\section{Endpoint ledger and route decisions}
\label{sec:tpc63-endpoint-decisions}

The preceding results settle a provenance question and close one
support-only certificate.  They do not supply a new favorable exponent.
This section records exactly how those facts enter the inherited endpoint
calculus.

\subsection{What the single-band calculation certifies}

The critical row and cofactor scales remain
\begin{equation}
 \theta_Q=\frac{267}{400},
 \qquad
 \theta_J=\frac{133}{400},
 \qquad
 \lambda_L=\frac{99979}{210000}.
 \label{eq:tpc63-critical-scale-exponents}
\end{equation}
The balanced inherited band has lower cofactor threshold
\(R_0=X^{\lambda_L+o(1)}\), whereas the critical high face has ceiling
\(R_{\max}=X^{\theta_J+o(1)}\).  Since
\begin{equation}
 \lambda_L-\theta_J
 =\frac{15077}{105000}>\frac1{400},
 \label{eq:tpc63-balanced-band-gap}
\end{equation}
the balanced band, and in fact every band certified by the inherited
freezing inequality, is eventually disjoint from the critical high face.
Retuning \(R_0\) down to the top critical scale makes the first inherited
freezing loss equal to the left side of
\eqref{eq:tpc63-balanced-band-gap}, already beyond the entire endpoint
budget.  Thus the old simultaneous band/freezing certificate is closed
before exposure is estimated.

If a different theorem permits such a retuned band, every full omitted
dyadic block below its cofactor window still faces a second obstruction: the
available support-cardinality/Brun--Titchmarsh harmonic argument cancels
its best possible cofactor saving.  More precisely, if
\(\eta_H\le\theta_J\) is its effective-exposure exponent, then
\begin{equation}
 \sigma_{\rm cof}^{\rm card}(\eta_H)
 :=\eta_H-\theta_J\le0,
 \qquad
 \boxed{\sup_{\eta_H\le\theta_J}
        \bigl(\sigma_{\rm cof}^{\rm card}(\eta_H)\bigr)_+=0.}
 \label{eq:tpc63-cardinality-certified-saving}
\end{equation}
Here \(x_+:=\max\{x,0\}\).  Thus the certificate has no positive
fixed-power saving.
It cannot satisfy the strict sufficient condition
\begin{equation}
 \sigma_M>\lambda_{\rm rep}+\nu_M,
 \qquad \lambda_{\rm rep},\nu_M\ge0.
 \label{eq:tpc63-restricted-product-test}
\end{equation}
This kills the specified harmonic certificate on the full omitted blocks.
Together with \eqref{eq:tpc63-balanced-band-gap}, it does
not prove that the actual weighted missing mass has exponent zero, and it
does not kill a weighted distribution estimate, a signed estimate, or the
exact shorted-Gram route.

By contrast, the labeled completion in
\cref{thm:tpc63-exact-labelled-completion} has exact raw-energy constant
one and only \(O(\log X)=X^{o(1)}\) external labels.  Its bookkeeping
exponent is exactly zero.  The erasure map is a different gate.  If its
actual range-restricted lower constant is
\begin{equation}
 \eta(\cE_a;S_X)
 \ge X^{-\lambda_{\rm erase}+o(1)},
 \label{eq:tpc63-erasure-loss-input}
\end{equation}
then \(\lambda_{\rm erase}\) is charged once inside the physical
reassembly loss.  Neither \(L_X\) nor
\(\lambda_{\rm erase}\) may be charged again under another name.

\subsection{The strict complete ledger}

Retaining the module names of TPC--61--TPC--62, every nonnegative
fixed-power loss on the actual physical chain must occur once in
\begin{equation}
 \boxed{
 \begin{aligned}
 \Lambda_{\rm tot}:={}&
 \lambda_{\rm sel}+\lambda_{\rm occ}
 +\lambda_{\rm blk}+\lambda_{\rm term}
 +\lambda_{\rm sing}\\
 &+\lambda_H+\lambda_{\rm aff}
 +\lambda_{\rm reasm}
 +\lambda_{\rm bdry}+\lambda_{\rm tail}.
 \end{aligned}}
 \label{eq:tpc63-complete-endpoint-ledger}
\end{equation}
The endpoint gate is
\begin{equation}
 \boxed{\Lambda_{\rm tot}<\frac1{400}.}
 \label{eq:tpc63-strict-endpoint-budget}
\end{equation}
Here \(\lambda_{\rm reasm}\) includes every genuine loss from labeled
represented output to the declared physical output, including
\(\lambda_{\rm erase}\) when erasure is a mandatory factor.  Exact
provenance identities, set partitions, canonical relabelings, and the
logarithmic block count cost zero.  The quantities \(\sigma_M\) and
\(\nu_M\) determine whether a chosen mass--degree certificate makes
reassembly perturbative; they are not extra summands in
\eqref{eq:tpc63-complete-endpoint-ledger}.

All estimates in the ledger must hold for the same fixed \(h_0\), the same
literal carrier, the same raw atomic normalization, and the same uniform
or distinguished coefficient scope.  Equality at \(1/400\) is rejected
unless a separate leading-constant argument recovers a strict final
inequality.  No such constant-level recovery is proved here.

\subsection{Decision tree with exact kill rules}

The next attack should follow the order below.
\begin{enumerate}[label=\textbf{Gate \arabic*.},leftmargin=4.4em]
 \item \emph{Pair faithfulness.}  Apply the pre-terminal, terminal, and
       grouped rectangularization tests to the literal full incidence.  If
       pair projection creates a terminal-active spurious cross, retain the
       full incidence hypergraph; do not force a pair-only model.
 \item \emph{Alignment first.}  Compute the parent-to-terminal
       alignment mass \(W_A(m)\).  A row with
       \(W_A(m)=0<W_H(m)\) kills a uniform activation theorem on every
       coefficient class containing that row.  Enlarging the retained pair
       relation cannot repair this zero.
 \item \emph{Relation completion.}  On aligned mass, compute the exact
       completion ratio.  Passing to \(\cI_X^{\max}\) removes only the
       relation-induced defect; it does not improve the alignment ratio.
 \item \emph{Labeled multiscale realization.}  Retain every nonempty
       cofactor block as an orthogonal label.  This passes the raw-energy
       gate exactly, but each newly included block still needs its own
       literal coefficient and terminal compatibility theorem.
 \item \emph{Erasure kernels.}  Identify the actual upstream range \(S_X\)
       and compute \(S_X\cap\Ker\cE_a\).  A nonzero intersection kills the
       full-coefficient lower bound for that declared physical
       composition.  A kernel in the ambient labeled space but outside
       \(S_X\) does not kill the composition.
 \item \emph{Weighted exposure or exact shorting.}  The single-band
       inherited freezing certificate is incompatible with the critical
       face by \eqref{eq:tpc63-balanced-band-gap}.  After any independently
       justified retuning, the cardinality proof is still closed by
       \eqref{eq:tpc63-cardinality-certified-saving}.  Either prove a new
       weighted terminal/largest-prime-factor estimate, or use the exact
       signed or shorted-Gram route.  Do not rename label count as missing
       mass saving.
 \item \emph{Represented and downstream chain.}  Only after activation,
       represented native transfer, and reassembly are quantified in one
       scope should boundary and tail arrows be attached and
       \eqref{eq:tpc63-strict-endpoint-budget} tested.
\end{enumerate}

The exact deaths and surviving pivots can be summarized as follows.
\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.29\textwidth}
                >{\raggedright\arraybackslash}p{0.31\textwidth}
                >{\raggedright\arraybackslash}p{0.29\textwidth}}
\toprule
Observed event & What is killed & Honest pivot\\
\midrule
No pair-only terminal-faithful relation exists
& Pair-rectangular completion of the literal incidence.
& Retain the full incidence hypergraph.\\
\addlinespace
The inherited freezing inequality certifies the single band
& Its intersection with the critical high face: the certified band is
  eventually empty.
& Prove a new band/freezing theorem or realize a genuinely multiscale
  carrier.\\
\addlinespace
Retuning the old band to \(R_0\asymp J\)
& The inherited sufficient freezing route: its first loss already exceeds
  \(1/400\).
& A new coefficient-sensitive freezing estimate is required.\\
\addlinespace
\(W_A(m_0)=0<W_H(m_0)\) on a required row
& Uniform parent-to-terminal activation on a class containing that row.
& A justified distinguished class may avoid the row; otherwise reopen the
  terminal carrier.\\
\addlinespace
The canonical completion ratio is one but \(W_A/W_H\) is small
& The assertion that relation completion alone repairs exposure.
& Prove terminal alignment or a weighted alignment theorem.\\
\addlinespace
\(S_X\cap\Ker\cE_a\ne\{0\}\)
& Uniform lower transfer through that actual erasure composition.
& Change the physical representation, restrict to a justified
  distinguished vector, or estimate a different exact shorted map.\\
\addlinespace
Best possible positive-part cardinality saving is zero
& The support-cardinality/harmonic proof of the strict product test.
& Weighted distribution, signed cancellation, or exact shorting.\\
\addlinespace
A necessary proved loss reaches \(1/400\)
& The stated endpoint exponent route without constant-level recovery.
& Change the architecture; do not absorb the loss into \(X^{o(1)}\).\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Forbidden substitutions}

None of these gates is repaired by specializing \(h_0\) to \(2\),
averaging over shifts, deleting a coefficient-dependent zero, normalizing
raw atoms by fiber size, choosing phases after seeing the coefficient
vector, or replacing the literal active support by its terminal image.
Those operations change either the object or the quantifier.  Their
conclusions cannot be entered into
\eqref{eq:tpc63-complete-endpoint-ledger} for the present fixed carrier.
