\section{Maximal eligibility and exact row exposure}
\label{sec:exposure-factorization}

The incidence calculus separates two questions which were previously hidden
inside the phrase ``retained pair.''  First, does a native high atom pass all
terminal tests other than membership in the pair relation?  Second, if it
does, is its recovered pair retained?  This section disintegrates the two
questions before any residual or native grouping.  All sets are fixed before
the row coefficient is chosen.

\subsection{The relation-free admissible high carrier}

Let \(\cW_H(y)\) be the complete nonzero native very-high carrier on one
fixed side and direct residue slice.  Every \(w\in\cW_H(y)\) canonically
recovers
\begin{equation}
 m(w),\qquad j(w),\qquad
 n(w)=m(w)j(w)+h_0,\qquad
 p(w)=\Pplus(n(w))>y,\qquad
 r(w)=\frac{n(w)}{p(w)}.
 \label{eq:exposure-recovered-labels}
\end{equation}
Write its literal amplitude as
\begin{equation}
 b_w(\zeta)=\beta_w\zeta_{m(w)},
 \label{eq:exposure-literal-amplitude}
\end{equation}
where \(\beta_w\) contains every coefficient-free source, mask, orbit,
opposite-row, and shaped terminal factor.  No free atom phase is inserted.

Remove only the retained-pair membership test from the complete terminal
admission predicate.  Let
\begin{equation}
 A_X(w)\in\{0,1\}
 \label{eq:exposure-nonrelation-predicate}
\end{equation}
be the conjunction of all remaining declared tests: terminal-prime and
orbit scope, nonvanishing terminal weight, squarefree and coprimality
conditions, literal mask and profile support, and every further
terminal-only condition.  Define
\begin{align}
 \cW_A(y)&:=\{w\in\cW_H(y):A_X(w)=1\},
 \label{eq:exposure-admissible-high-carrier}\\
 \cI_X^{\max}
 &:=\{(m(w),r(w)):w\in\cW_A(y)\}.
 \label{eq:exposure-maximal-eligible-relation}
\end{align}
The superscript ``max'' refers only to removal of the retained-pair test.
It does not enlarge any other literal support.  Under the exact
terminal--Walsh coordinate injection, \(\cI_X^{\max}\) is the pair
projection of the coefficient-free terminal incidence.  Identifying it
with the residual projection \(\cI_X^{\rm res}\) from
\cref{def:audit-residual-incidences} additionally requires equality of the
two declared support systems; this equality is not inferred from their
common scales.

Let \(\cI_X\subseteq\cM_X\times\N\) be any declared finite,
coefficient-independent pair relation and put
\begin{equation}
 \cI_m:=\{r:(m,r)\in\cI_X\},
 \qquad
 \cI_X^{\rm eff}:=\cI_X\cap\cI_X^{\max}.
 \label{eq:exposure-effective-core}
\end{equation}
Its represented high carrier and its full missing complement are
\begin{align}
 \cW_R^{\cI}
 &:=\{w\in\cW_A(y):(m(w),r(w))\in\cI_X\},
 \label{eq:exposure-represented-carrier}\\
 \cW_M^{\cI}
 &:=\cW_H(y)\setminus\cW_R^{\cI}.
 \label{eq:exposure-missing-carrier}
\end{align}
Thus \(\cW_M^{\cI}\) includes both non-relation failure and failure of a
different terminal test.  In the identical-support specialization of
TPC--60/61, \(A_X=1\) on \(\cW_H\), so only the first mechanism remains
\citep{WangTPC60,WangTPC61}.

\begin{proposition}[Effective core and the eligibility lattice]
\label{prop:exposure-effective-core}
For every declared relation \(\cI_X\),
\begin{equation}
 \boxed{
 \cW_R^{\cI}
 =\cW_R^{\cI_X^{\rm eff}}.}
 \label{eq:exposure-effective-core-identity}
\end{equation}
If \(\cI_X\subseteq\cJ_X\), then
\begin{equation}
 \cW_R^{\cI}\subseteq\cW_R^{\cJ}.
 \label{eq:exposure-relation-monotonicity}
\end{equation}
Moreover, \(\cI_X^{\max}\) is the unique least pair relation which
represents every atom of \(\cW_A(y)\).  Any superset of
\(\cI_X^{\max}\) gives the same represented carrier
\(\cW_A(y)\).
\end{proposition}

\begin{proof}
Membership in \(\cW_R^{\cI}\) requires both \(A_X(w)=1\) and
\((m(w),r(w))\in\cI_X\).  The first condition already places the recovered
pair in \(\cI_X^{\max}\), proving
\eqref{eq:exposure-effective-core-identity}.  Relation inclusion gives
\eqref{eq:exposure-relation-monotonicity}.  Finally, every relation which
represents all of \(\cW_A\) must contain the pair of every one of its
atoms, hence must contain their projection \(\cI_X^{\max}\).  Conversely,
that projection represents every admissible atom by definition.
\end{proof}

The proposition is a maximal-support identity.  It is not a statement that
\(\cW_A\) has positive mass relative to \(\cW_H\), and it is not a theorem
that the inherited relation equals \(\cI_X^{\max}\).

\subsection{Two realized measures and the exact factorization}

For a source row \(m\), define finite positive measures on \(\N\) by
\begin{align}
 \nu_m^H(r)
 &:=\sum_{\substack{w\in\cW_H(y)\\
                    m(w)=m,\ r(w)=r}}|\beta_w|^2,
 \label{eq:exposure-native-high-measure}\\
 \nu_m^A(r)
 &:=\sum_{\substack{w\in\cW_A(y)\\
                    m(w)=m,\ r(w)=r}}|\beta_w|^2.
 \label{eq:exposure-admissible-high-measure}
\end{align}
Put
\begin{align}
 W_H(m)&:=\nu_m^H(\N),
 &W_A(m)&:=\nu_m^A(\N),
 \label{eq:exposure-high-admissible-row-weights}\\
 W_R^{\cI}(m)&:=\nu_m^A(\cI_m),
 &W_M^{\cI}(m)&:=W_H(m)-W_R^{\cI}(m).
 \label{eq:exposure-represented-missing-row-weights}
\end{align}
All weights use raw counting-measure atoms.  In particular, neither
\(\nu_m^H\) nor \(\nu_m^A\) is divided by a row, orbit, cofactor, or native
fiber multiplicity.

For every row with \(W_H(m)>0\), define the alignment factor
\begin{equation}
 \alpha_m:=\frac{W_A(m)}{W_H(m)}\in[0,1].
 \label{eq:exposure-alignment-factor}
\end{equation}
When \(W_A(m)>0\), define the relation-completion factor
\begin{equation}
 \theta_m(\cI)
 :=\frac{\nu_m^A(\cI_m)}{W_A(m)}\in[0,1];
 \label{eq:exposure-completion-factor}
\end{equation}
when \(W_A(m)=0\), put \(\theta_m(\cI):=0\).

\begin{theorem}[Exact alignment--completion factorization]
\label{thm:exposure-exact-factorization}
For every native-high active row,
\begin{equation}
 \boxed{
 \frac{W_R^{\cI}(m)}{W_H(m)}
 =\alpha_m\theta_m(\cI).}
 \label{eq:exposure-alpha-theta-factorization}
\end{equation}
Consequently,
\begin{equation}
 W_R^{\cI}(m)>0
 \quad\Longleftrightarrow\quad
 W_A(m)>0
 \quad\text{and}\quad
 \cI_m\cap\supp\nu_m^A\ne\varnothing.
 \label{eq:exposure-positive-row-criterion}
\end{equation}
For the canonical maximal relation,
\begin{equation}
 \theta_m(\cI_X^{\max})=1
 \quad\text{whenever }W_A(m)>0,
 \qquad
 \frac{W_R^{\max}(m)}{W_H(m)}=\alpha_m.
 \label{eq:exposure-maximal-relation-value}
\end{equation}
Thus maximal relation completion removes only relation-induced missing
mass; it does not remove the alignment defect \(1-\alpha_m\).
\end{theorem}

\begin{proof}
If \(W_A(m)>0\), substitute
\(W_R^{\cI}(m)=\nu_m^A(\cI_m)\) and insert \(W_A(m)\) between numerator
and denominator.  If \(W_A(m)=0\), both sides of
\eqref{eq:exposure-alpha-theta-factorization} vanish by convention.  A
positive finite measure charges \(\cI_m\) precisely when that set meets
its support, proving \eqref{eq:exposure-positive-row-criterion}.  Finally,
\(\cI_X^{\max}\) contains every pair in \(\supp\nu_m^A\), which gives
\eqref{eq:exposure-maximal-relation-value}.
\end{proof}

Under identical support one has \(\nu_m^A=\nu_m^H\) and
\(\alpha_m=1\).  Then \eqref{eq:exposure-alpha-theta-factorization}
reduces exactly to the TPC--61 realized-cofactor formula
\begin{equation}
 \frac{W_R^{\cI}(m)}{W_H(m)}
 =\frac{\nu_m^H(\cI_m)}{\nu_m^H(\N)}.
 \label{eq:exposure-identical-support-specialization}
\end{equation}
The specialization is useful only after identical support itself has been
proved for the declared packet.

\subsection{Sharp uniform and distinguished constants}

For a row-coefficient vector \(\zeta\), let
\begin{align}
 \cD_H(\zeta)
 &:=\sum_mW_H(m)|\zeta_m|^2,
 \label{eq:exposure-DH}\\
 \cD_R^{\cI}(\zeta)
 &:=\sum_mW_R^{\cI}(m)|\zeta_m|^2,
 \qquad
 \cD_M^{\cI}(\zeta)
 :=\cD_H(\zeta)-\cD_R^{\cI}(\zeta).
 \label{eq:exposure-DR-DM}
\end{align}

\begin{theorem}[Uniform and distinguished exposure minimax]
\label{thm:exposure-uniform-distinguished-minimax}
Assume the declared uniform coefficient class contains a nonzero multiple
of each active row direction.  If \(\cD_H\) is not identically zero, then
\begin{align}
 \inf_{\cD_H(\zeta)>0}
 \frac{\cD_R^{\cI}(\zeta)}{\cD_H(\zeta)}
 &=\min_{m:W_H(m)>0}\alpha_m\theta_m(\cI),
 \label{eq:exposure-uniform-minimum}\\
 \sup_{\cD_H(\zeta)>0}
 \frac{\cD_M^{\cI}(\zeta)}{\cD_H(\zeta)}
 &=\max_{m:W_H(m)>0}
   \bigl(1-\alpha_m\theta_m(\cI)\bigr).
 \label{eq:exposure-uniform-maximum}
\end{align}
For one distinguished physical vector \(\zeta_*\) with
\(\cD_H(\zeta_*)>0\), the exact represented fraction is instead
\begin{equation}
 \boxed{
 \rho_*(X)
 :=\frac{\cD_R^{\cI}(\zeta_*)}{\cD_H(\zeta_*)}
 =\sum_{m:W_H(m)>0}
 \frac{W_H(m)|\zeta_{*,m}|^2}{\cD_H(\zeta_*)}
 \alpha_m\theta_m(\cI).}
 \label{eq:exposure-distinguished-average}
\end{equation}
\end{theorem}

\begin{proof}
By \cref{thm:exposure-exact-factorization}, each quotient is a convex
combination of the row values \(\alpha_m\theta_m(\cI)\), with weights
\(W_H(m)|\zeta_m|^2/\cD_H(\zeta)\).  It is bounded below by their minimum,
and concentration on a minimizing coordinate attains that value after a
harmless scalar rescaling into the declared class.  Apply the same argument
to \(1-\alpha_m\theta_m\) for the missing quotient.  Keeping the literal
weights of \(\zeta_*\) gives \eqref{eq:exposure-distinguished-average}.
\end{proof}

At one finite scale, coefficient-uniform positive exposure is therefore
equivalent to
\begin{equation}
 \min_{m:W_H(m)>0}\alpha_m\theta_m(\cI)>0.
 \label{eq:exposure-finite-positive-uniform}
\end{equation}
A scale-uniform constant requires the infimum of this minimum over all
large \(X\) to be positive.  The much stronger fixed-power missing-mass
target requires
\begin{equation}
 \max_{m:W_H(m)>0}
 \bigl(1-\alpha_m\theta_m(\cI)\bigr)
 \le X^{-\sigma+o(1)}
 \label{eq:exposure-power-target}
\end{equation}
for some \(\sigma>0\).  Mere rowwise nonemptiness proves neither statement.

\subsection{The sharp support no-go and its scope}

\begin{corollary}[Finite-relation insufficiency]
\label{cor:exposure-finite-relation-no-go}
The inherited hypotheses ``\(\cI_X\) is finite and fixed before
\(\zeta\)'' do not imply a positive value in
\eqref{eq:exposure-uniform-minimum}, even under identical support.  They
also do not imply \eqref{eq:exposure-power-target}.
\end{corollary}

\begin{proof}
The stated hypotheses permit an otherwise active row \(m_0\) for which
\(\cI_{m_0}\cap\supp\nu_{m_0}^A=\varnothing\).  Under identical support,
\(\alpha_{m_0}=1\), but \(\theta_{m_0}=0\).  Hence the exact minimum is
zero and the exact maximum missing fraction is one.  This is an admissible
model of the displayed interface, not an assertion that the literal
upstream construction necessarily chooses such a row.
\end{proof}

The distinguished route is logically different.  It may survive a bad row
when \(\zeta_{*,m}=0\) there, but the upper bound
\(|\zeta_{*,m}|\ll1\) alone supplies no lower bound for
\eqref{eq:exposure-distinguished-average}.  Likewise, defining
\(\cI_X^{\max}\) from support gives the exact value \(\theta_m=1\), but
does not prove \(\alpha_m>0\), parent-to-high activation, or any
post-grouping lower bound.

The lattice and factorization theorems are L0 finite-incidence statements.
Their use with \eqref{eq:exposure-recovered-labels}, the literal
\(\beta_w\), one fixed \(h_0\), and the raw native atomic norm is an L1
physical-interface specialization.  The support no-go closes only an
inference from opaque finite relations.  It neither lower-bounds actual
missing mass nor estimates the signed parity kernel, and it has no L2
prime-pair consequence.
