\section{Introduction}
\label{sec:introduction}

The fixed-shift route preceding this paper has reached a precise but
unresolved reassembly problem.  TPC--59 decomposes the literal Walsh
carrier into base, represented high, and missing high coordinates;
TPC--60 identifies the exact shorted-Gram and kernel tests for restoring
the missing high image; TPC--61 disintegrates its raw mass into realized
row cofactor measures; and TPC--62 arranges all available closure
certificates in the correct quantifier order
\citep{WangTPC59,WangTPC60,WangTPC61,WangTPC62}.  The favorable
mass--degree route would require, in matching scope,
\begin{equation}
 \cD_M(z)\le X^{-\sigma_M+o(1)}\cD_{\rm ref}(z),
 \qquad
 \sigma_M>\lambda_{\rm rep}+\nu_M.
 \label{eq:intro-mass-degree-target}
\end{equation}
The first inequality is not a formal consequence of the definitions.  It
depends on which cofactors the inherited relation \(\cI_X\) actually
retains on every active row.

That relation has an unresolved provenance.  TPC--47 and TPC--48 begin
with literal sums over already supported \((p,r,m,j)\)-atoms and prove
coefficientwise signed reassembly and fixed-row \(r\)-orthogonality
\citep{WangTPC47,WangTPC48}.  TPC--51 first names a set
\(\cI_X\) containing the supported \((m,r)\)-pairs; TPC--52 and
TPC--53 then form a direct sum over that relation, and TPC--54 explicitly
permits arbitrary finite cofactor multiplicity
\citep{WangTPC51,WangTPC52,WangTPC53,WangTPC54}.  None of those displayed
interfaces supplies a set-builder membership rule or a row-completion
theorem.  TPC--61 therefore correctly proves that the finite-relation
hypothesis alone implies no positive exposure, but leaves open whether the
literal upstream incidence repairs that defect.

This paper opens precisely that box.  Its first point is conceptual but
mathematically exact: a pair relation and a full four-label incidence are
not interchangeable.  If
\[
 \cU\subseteq\cM\times\cR\times\cJ\times\Gamma
\]
is the literal incidence and \(I=\pr_{m,r}\cU\), then the later lifted
space uses the rectangular completion
\[
 \Rect(I)=\{(m,r,j,\gamma):(m,r)\in I,
                 j\in\cJ,\ \gamma\in\Gamma\}.
\]
It may contain spurious crosses.  Some crosses are harmless because the
terminal predicate kills them; some alter the raw parent form but not the
terminal map; and some alter even the grouped physical operator.  We give
sharp finite-scale if-and-only-if tests for all three cases.

The second point is an exact repair.  Removing the retained-pair test from
the literal terminal predicate defines a coefficient-independent eligible
universe and its maximal pair projection \(\cI_X^{\max}\).  Every declared
relation selects the same native-high carrier as its effective core
\(\cI_X\cap\cI_X^{\max}\).  This selector identity is not an identity for a
rectangular terminal operator, which still requires the terminal-faithfulness
test.  On the native high carrier we further separate
the alignment mass \(W_A\), which passes every non-relation terminal test,
from the amount retained by \(\cI_X\).  This produces an exact two-gate
factorization and the correct uniform/distinguished minimax laws.  Setting
\(\cI_X=\cI_X^{\max}\) eliminates only relation-induced missing mass.  It
does not prove parent-to-terminal activation, nor may the terminal-active
support be substituted retroactively for the parent support.

The third point decides what the old one-band support can and cannot do.
On the large-prime band of TPC--45/47,
\begin{equation}
 \sqrt{N_+}<p\le N_-/R_0,
 \label{eq:intro-old-prime-band}
\end{equation}
every represented atom has \(r\ge R_0\).  On the critical very-high face
of TPC--59, \(p>y\asymp Q\) implies
\begin{equation}
 r<N_+/y\asymp J.
 \label{eq:intro-critical-cofactor-ceiling}
\end{equation}
The exact comparison is stronger than a mere top-window localization.  The
balanced inherited threshold has exponent \(99979/210000>133/400\), and
every band satisfying the inherited freezing inequality remains
polynomially above the critical ceiling.  Its intersection with the
critical face is therefore empty.  If one independently retunes
\(R_0\asymp J\) to create a top-window intersection, the old
coefficient-blind freezing loss is \(15077/105000>1/400\).  Moreover, if
the unseen lower blocks are then treated by the TPC--61 ladder and
Brun--Titchmarsh certificate, their full cardinality exactly cancels the
available cofactor exponent.  These are genuine negative theorems for two
specified certificates, not evidence that the actual weighted missing
mass is large.

The resulting fork is useful.  One may prove a new coefficient-specific
band/freezing theorem and then seek a weighted distribution theorem for
its low-cofactor complement, or canonically realize a multiscale relation
and separately pay for the enlarged parent/label-reassembly gates.  Either
route is now falsifiable.
Neither route is described as progress on the fixed-\(h=2\) parity kernel
until a genuinely signed arithmetic estimate on the literal carrier has
been proved.

\paragraph{Main results.}
The paper proves the following finite-scale statements.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.7em]
 \item Exact pre-terminal, terminal-atomic, and grouped-operator
       rectangularization criteria, including explicit spurious-cross
       witnesses.
 \item A unique least terminal-faithful pair relation when pair-only
       completion is possible, and a sharp criterion requiring the full
       incidence hypergraph when it is not.
 \item The maximal-eligible relation, effective-core identity, monotonicity
       lattice, exact alignment/completion factorization, and sharp
       uniform/distinguished exposure constants.
 \item Exact cofactor-window inclusions, the disjointness of every band
       certified by the inherited freezing inequality from the critical
       face, and the over-budget cost of the top-scale retuning.
 \item A zero-saving theorem for the full omitted dyadic blocks under the
       inherited support-cardinality/harmonic certificate, even after an
       independently justified retuning.
 \item A labeled multiscale completion with zero fixed-power bookkeeping
       cost, together with the proof that erasing its labels is a separate
       reassembly map.
\end{enumerate}

All exact support and operator statements are L0.  Their specialization to
one literal fixed shift, coefficient field, and raw atomic norm is L1.  No
new L2 cancellation or prime-distribution lower bound is claimed.
