\section{The inherited support and the missing provenance arrow}
\label{sec:provenance-audit}

We first state exactly what is inherited and what is not.  This section is
not a historical survey: it fixes the logical hypotheses used in every
later theorem.

\subsection{The literal residual atom set}

Fix one side and one direct residue cell.  A source row is uniquely encoded
by
\begin{equation}
 m=d_m\ell_m\asymp Q,
 \qquad
 Q=X^{267/400+o(1)},
 \qquad
 j\asymp J=X^{133/400+o(1)}.
 \label{eq:audit-scales}
\end{equation}
The physical shift \(h_0\ne0\) is fixed.  On the TPC--47 residual sector,
an eligible atom has the determinant relation
\begin{equation}
 pr-mj=h_0,
 \qquad
 p\in\cP_{R_0}^{\sharp}
 :=\{p\in\Pp:\sqrt{N_+}<p\le N_-/R_0\},
 \label{eq:audit-band-determinant}
\end{equation}
together with the inherited row, orbit, opposite-row, terminal, mask,
squarefree, and coprimality restrictions.  Write
\(\Lambda_X(n):=(\log n)\Phi_0(n/X)\) for \(n>0\), zero-extended to
\(\Z\), for the inherited smooth terminal weight.  Thus \(\Lambda_X\) is
not the von Mangoldt function.  The literal coefficient is
\begin{equation}
 \gamma_m^{(1)}\mathfrak A_{m,\gamma}^{\rm act}(j)
 \mu(r)\Lambda_X(pr),
 \qquad s=d_mr.
 \label{eq:audit-literal-coefficient}
\end{equation}
The large prime is unique and every occurring cofactor obeys
\begin{equation}
 R_0\le r<\sqrt{N_+}
 \label{eq:audit-cofactor-range}
\end{equation}
\citep{WangTPC45,WangTPC47}.

Remove only the bounded row coefficient \(\zeta_m\) from
\(\gamma_m^{(1)}\), retaining every fixed source shape and logarithmic
factor.  Let \(c_{m,j,\gamma}\) denote the remaining coefficient-free
pre-terminal factor.  The structural support is defined using
\(c_{m,j,\gamma}\ne0\), not using \(c_{m,j,\gamma}\zeta_m\ne0\).  Thus it
is fixed before the coefficient vector is chosen.

\begin{definition}[Literal eligible and active residual incidences]
\label{def:audit-residual-incidences}
Let \(\cE_X^{\rm res}\) be the finite set of tuples
\(e=(m,r,p,j,\gamma)\) satisfying
\eqref{eq:audit-band-determinant} and every declared structural support
condition.  Let
\begin{equation}
 \cA_X^{\rm res}
 :=\{e\in\cE_X^{\rm res}:
      c_{m,j,\gamma}\mu(r)\Lambda_X(pr)\ne0\}
 \label{eq:audit-active-residual-incidence}
\end{equation}
and define its pair projection
\begin{equation}
 \cI_X^{\rm res}:=\pr_{m,r}\cA_X^{\rm res}.
 \label{eq:audit-residual-pair-projection}
\end{equation}
\end{definition}

This is a genuine coefficient-independent finite relation, but its
definition is a projection of the full residual incidence.  It is not a
row-completion theorem and, by itself, it is not an identification with the
later native high carrier.

\subsection{What reassembly preserves}

TPC--47 proves a coefficientwise signed Bochner reassembly for every
already supported \((m,r)\), and TPC--48 proves an exact orthogonal
\(r\)-square at fixed \(m\) before residual grouping
\citep{WangTPC47,WangTPC48}.  Both statements preserve the relation
\(\cI_X^{\rm res}\).  They neither select a favorable pair nor add a
missing one.  More explicitly, at fixed \(m\), distinct cofactors occupy
the distinct residual coordinates \(d_mr\), so
\begin{equation}
 \left\|\sum_r B_{m,r}\right\|^2
 =\sum_r\|B_{m,r}\|^2
 \label{eq:audit-fixed-row-r-square}
\end{equation}
whenever the vectors are evaluated in the ungrouped residual-label space.
An empty fixed-row cofactor fiber is compatible with this identity.

The orbit projector acts in the \(j\)-factor, and the all-band tiling acts
on the same orbit-frequency quotient.  Neither operator creates a new
\((m,r)\)-label.  By contrast, the later map
\begin{equation}
 (\gamma,d_mr,j)\longmapsto(\gamma,j)
 \label{eq:audit-residual-erasure}
\end{equation}
groups different residual labels and is not norm-monotone from below.
Support preservation before that map is therefore not a lower reassembly
estimate after it.

\subsection{Where the pair relation becomes opaque}

The coefficient spaces of TPC--51 and TPC--52 introduce a finite relation
\(\cI_X\) described only as containing the supported pairs before coherent
prime summation.  TPC--53 uses the rectangular lifted space
\begin{equation}
 \bigoplus_{(m,r)\in\cI_X}
 \ell^2(\cJ_{X,a};\ell^2(\cO_X\times\cS_X)),
 \label{eq:audit-rectangular-space}
\end{equation}
and its exact factor dictionary is valid for any declared finite retained
set.  TPC--54 then keeps only the multiplicity
\begin{equation}
 N_r(m)=\#\{r:(m,r)\in\cI_X\}
 \label{eq:audit-row-multiplicity}
\end{equation}
and explicitly leaves balanced occupancy unproved
\citep{WangTPC51,WangTPC52,WangTPC53,WangTPC54}.

The displayed interfaces therefore do not prove any of
\begin{align}
 \cI_m\cap\supp\nu_m&\ne\varnothing
       &&\text{on every native-high active row},
 \label{eq:audit-unproved-intersection}\\
 \inf_m\frac{\nu_m(\cI_m)}{\nu_m(\N)}&>0,
 \label{eq:audit-unproved-positive-exposure}\\
 \sup_m\frac{\nu_m(\cI_m^c)}{\nu_m(\N)}
 &\le X^{-\sigma+o(1)}
       &&\text{for some \(\sigma>0\)}.
 \label{eq:audit-unproved-power-exposure}
\end{align}
The statement is a logical non-implication.  It does not assert that the
actual arithmetic relation has a bad row.

\begin{proposition}[Support-preservation boundary]
\label{prop:audit-support-preservation-boundary}
Under the displayed TPC--47/48 interface, \(\cI_X^{\rm res}\) is finite,
is preserved by coefficientwise signed reassembly and orbit-band tiling,
and has the fixed-row orthogonality \eqref{eq:audit-fixed-row-r-square}.
Those statements do not imply any of
\eqref{eq:audit-unproved-intersection}--
\eqref{eq:audit-unproved-power-exposure} for an independently specified
native-high measure family \((\nu_m)\).
\end{proposition}

\begin{proof}
Finiteness follows from the finite row, orbit, terminal, and opposite-row
supports.  The residual label is \(d_mr\); at fixed \(m\), its injectivity
in \(r\) gives \eqref{eq:audit-fixed-row-r-square}.  The coefficientwise
identities in TPC--47/48 are indexed by the already supported pair and hence
do not alter its projection.  For the non-implication, take one source row,
let \(\cI_m^{\rm res}=\{r_0\}\), and let an otherwise admissible native-high
measure be \(\nu_m=\delta_{r_1}\) with \(r_1\ne r_0\).  Every stated
finite-support and orthogonality property remains true, while
\(\nu_m(\cI_m^{\rm res})=0<\nu_m(\N)\).  This model witnesses
insufficiency of the displayed hypotheses only.
\end{proof}

The next sections replace the opaque arrow by a full-incidence calculus.
That calculus will show exactly when a pair projection is faithful and
exactly which extra theorem would be needed to identify it with the native
high support.
