\section{Conclusions, dependency graph, and the next gate}

\subsection{What advanced}
The paper proves three kinds of results.
\begin{enumerate}[label=(\arabic*)]
\item \textbf{Literal row geometry.} A fixed physical row is a singleton in
each residual output fiber. The active normalized row Gram therefore has
diagonal exactly one.
\item \textbf{Arithmetic pair geometry.} Summing the TPC-57 exchange patterns
for a fixed pair of distinct rows gives
\[
 C_{m,n}^{\rm red}(R)
 \le X^{o(1)}\left(1+\frac JR\right).
\]
At \(R\asymp J\), fixed row pairs have subpower reduced codegree even though a
single output fiber can retain polynomial degree.
\item \textbf{Lower-frame support calculus.} Private energy, the absolute
comparison matrix, forests, stars, and unique matchings give exact positive
certificates. Cycle holonomy proves the sharp boundary of support-only data.
\end{enumerate}

This is a real structural advance from the TPC-65 abstract Gram: the unknown
matrix is now a unit-diagonal Gram whose reduced-cell pair codegrees are
subpower on the critical block. The full decorated support and the global row
collision graph may still be large. This is not yet an endpoint lower bound.

\subsection{What remains open}
No result here proves:
\begin{itemize}
\item that every relevant row is nonempty or has positive private energy;
\item a fixed-power diffuseness bound for \(\rho_m(R)\);
\item a favorable bound for the aggregate collision spectral radius or for
cycle holonomies;
\item a polynomial lower bound for the physical smallest singular value;
\item a native/reassembly signed estimate, parity improvement, or prime-pair
lower bound.
\end{itemize}

The exact matrix/support statements are L0. The fixed-\(h_0\) row singleton,
factor exchange, CRT spacing, divisor thinning, and critical pair-codegree
bound are L1 on the declared literal carrier. No theorem specializes to
\(h_0=2\) through any property special to that shift, and no theorem reaches
L2.

\subsection{Route update for TPC-67}
The next paper should not seek M\"obius randomness in the residual Gram:
the row/output gauge removes that sign. The smallest next gate is global
geometry on the full collision skeleton, using only the pair thinning that
has actually been proved:
\begin{enumerate}[label=(\roman*)]
\item quantify Hall deficiency and uniquely matched minors on the actual
critical incidence;
\item bound the nonpeelable collision core, alternating cycles, and
cycle-holonomy dimension;
\item combine pair codegree, right degree, and actual row-energy diffuseness
through Cauchy--Binet or trace/minor identities.
\end{enumerate}
If these mechanisms yield only exponentially small determinant bounds, that is
a route stop for uniform closure but still a precise negative theorem. If they
give a polynomially conditioned minor or a strict comparison-matrix margin,
the route advances to reassembly. Signed two-affine cancellation remains a
separate later door.
