\section{Sharp route-separation models}

These models are finite-dimensional or coefficient-blind diagnostics. They do
not contradict the literal arithmetic theorems.

\begin{example}[Large candidate exposure, empty terminal support]
Take any number of congruence candidates in
\eqref{eq:tpc66-row-exposure-upper}, but let the terminal prime indicator or a
literal mask delete every candidate. Then the actual row energy is zero. An
upper census cannot be reversed into activation.
\end{example}

\begin{example}[Many cells, no diffuseness]
For \(N\ge2\) and \(0<\varepsilon<1\), let a unit column have squared magnitudes
\[
 1-\varepsilon,\quad
 \frac{\varepsilon}{N-1},\ldots,\frac{\varepsilon}{N-1}
\]
on \(N\) cells. Its support grows with \(N\), while its cell concentration is
\(\rho=1-\varepsilon\). Exposure cardinality alone gives no decay of \(\rho\).
\end{example}

\begin{example}[Pair codegree one, arbitrary global rank loss]
Let \(N\) unit columns all be supported on the same single output. Every
distinct pair has codegree one, yet the Gram is the all-ones matrix and has
rank one. Subpower pair codegree is not a global lower-frame theorem when the
row collision degree is unbounded.
\end{example}

\begin{example}[Same support data, different pair geometry]
The normalized columns
\[
 2^{-1/2}(1,1),\quad2^{-1/2}(1,1)
\]
have a kernel, whereas
\[
 2^{-1/2}(1,1),\quad2^{-1/2}(1,-1)
\]
are orthogonal. Exposure, pair codegree, output degrees, and entry magnitudes
are identical. The relative phase is missing support data.
\end{example}

\begin{example}[\(\gamma\)-decoration does not equal reduced codegree]
Let two rows share one reduced cell and let its \(\gamma\)-space have dimension
\(G\ge2\). If both decorated vectors are nonzero in all \(G\) coordinates, the raw
full-key support intersection is \(G\), while the reduced codegree is one.
Their normalized overlap can be any number in \([0,1]\). Thus raw
\(\gamma\)-multiplicity and Gram-relevant cell codegree are different objects.
\end{example}

\begin{example}[Private-energy bound is sharp]
For \(0\le\delta\le1\), take two normalized columns
\[
 v_1=(\sqrt\delta,0,\sqrt{1-\delta}),\qquad
 v_2=(0,\sqrt\delta,\sqrt{1-\delta}).
\]
Each row has private energy \(\delta\), and the Gram eigenvalues are
\(\delta\) and \(2-\delta\). Hence the private-output lower bound equals the
true smallest eigenvalue.
\end{example}

The cycle-holonomy section supplies the strongest combined no-go: even bounded
row support, output degree, collision degree, pair codegree, Hall matching, and
fixed magnitudes do not determine whether the lower frame is positive.
