\section{Introduction}

TPC-65 reduced the represented-reference question to the smallest eigenvalue
of an actual row Gram on the terminal range \citep{WangTPC65}. Its literal
matrix entries are residual-fiber correlations. That result closed the carrier
and normalization problem, but deliberately left two arithmetic questions:
how often are two physical rows exposed to the same output, and can those
collisions create a small singular direction?

This paper answers the first question at the critical cofactor scale and
develops exact support-level tests for the second. The starting observation is
simple but decisive. For the physical key
\[
 q(m,r,j,\gamma)=(\gamma,d_mr,j),
\]
fixing \(m\) and \(q\) fixes \(r\), \(j\), and \(\gamma\), and the terminal
prime is then fixed by \(pr-mj=h_0\). Thus a row never coherently sums two of
its own terminal atoms inside one output coordinate. The normalized physical
row Gram has unit diagonal. Its off-diagonal graph is the entire problem.

The arithmetic result uses, but does not rebrand, the factor-exchange and CRT
identities of TPC-57 \citep{WangTPC57}. Those identities treat one fixed
exchange pattern. Here the rows are fixed and all admissible exchange factors
are summed. A divisor-thinning argument leaves only \(X^{o(1)}\) factors, and
the CRT modulus is at least the root cofactor \(R\). Consequently the reduced
pair codegree is
\[
 C_{m,n}^{\rm red}(R)
 \le X^{o(1)}\left(1+\frac JR\right).
\]
At \(R\asymp J\) this is subpower uniformly in the distinct row pair. This is
not the older fiber-degree estimate: the same skeleton can have high right
degree and low left pair codegree.

Pairwise sparsity is not yet a lower frame. We therefore prove a hierarchy of
exact finite-dimensional results. Private output energy gives a sharp positive
lower bound. The absolute overlap matrix gives the optimal phase-blind
comparison bound and its weighted Collatz--Wielandt form. On forests, all edge
phases are gauge, giving an exact spectral-radius formula and a sharp star law.
At the support level, Hall deficiency is a universal rank obstruction, while a
unique-matching minor is a universal injectivity certificate. Ordinary Hall
matching lies strictly between them: it gives only generic full rank and does
not settle the one literal coefficient array.

The boundary is a cycle. A degree-two, codegree-one support pattern with fixed
entry magnitudes can be singular or nonsingular depending on one cycle
holonomy. This proves that exposure, bounded degrees, bounded codegrees, Hall
matching, and magnitude data do not determine the physical lower frame. The
next arithmetic gate is therefore global: combine the proved reduced-cell
pair thinning with actual full-output diffuseness and expansion, or control
the remaining holonomy. It is not legitimate to infer such control from
support counts.

\subsection*{Claim levels}
The support and matrix theorems are L0. The row-singleton dictionary,
factor-exchange summation, CRT spacing, and divisor bound are unconditional L1
statements on one literal fixed-\(h_0\) carrier. A positive exposure lower
bound, polynomial diffuseness, global smallest-singular-value estimate,
fixed-\(h_0=2\) parity estimate, or twin-prime conclusion would be L2 and is
not proved here.
