\section{Divisor-thin reduced codegree of a fixed row pair}
\label{sec:tpc66-pair-codegree}

The determinant-ladder bound of TPC--55 controls how many rows can enter
one residual output \citep{WangTPC55}.  That is a right-degree estimate.
The present section proves a different statement: after two source rows
are fixed, the number of reduced residual cells in which they can meet is
much smaller on a critical cofactor block.  The proof sums the
factor-exchange and simultaneous-CRT description of TPC--57 over every
exchange cofactor that can occur \citep{WangTPC57}.

\subsection{Reduced collision cells}

Work on one declared source system and one fixed direct residue/orbit
slice of the literal terminal carrier.  Fix \(h_0\ne0\).  Source rows
have their inherited unique factorizations
\begin{equation}
 m_i=d_i\ell_i,\qquad
 d_i\in[D,2D],\qquad
 \ell_i\in[L,2L]\cap\mathbb P,
 \qquad i=1,2,
 \label{eq:tpc66-two-row-factorizations}
\end{equation}
where the \(d_i\) are squarefree.  A terminal atom on row \(m_i\) has
cofactor \(r_i\), terminal prime \(p_i\), and satisfies
\begin{equation}
 r_ip_i-m_ij=h_0.
 \label{eq:tpc66-two-terminal-equations-short}
\end{equation}
The literal equality support also has
\[
 d_i,r_i,d_ir_i\ \hbox{squarefree},
 \qquad (d_i,r_i)=1.
\]
Every prime, residue, mask, profile, and endpoint restriction remains
part of the carrier.
Let \(\mathcal J_X\) denote the retained orbit interval and fix
\(C_J\ge1\), independent of the rows and \(X\), such that
\[
 \operatorname{diam}(\mathcal J_X)\le C_JJ.
\]

For \(R>0\) and two distinct rows \(m_1\ne m_2\), define
\(\mathcal C^{\mathrm{red}}_{m_1,m_2}(R)\) to be the set of pairs
\((s,j)\) for which there are opposite labels \(\gamma_1,\gamma_2\) and two
literal terminal atoms
\[
 u_i=(m_i,r_i,j,\gamma_i),\qquad d_ir_i=s,\qquad i=1,2,
\]
with \(R\le r_1\le2R\).  Put
\begin{equation}
 c^{\mathrm{red}}_{m_1,m_2}(R)
 :=\left|\mathcal C^{\mathrm{red}}_{m_1,m_2}(R)\right|.
 \label{eq:tpc66-reduced-codegree}
\end{equation}
Thus each row must be genuinely exposed over the reduced cell, but the two
opposite labels need not agree and are not counted with multiplicity. This
stronger reduced codegree contains the set of arithmetic cells that can
contribute to the row-pair Gram entry. It is not the cardinality of the
intersection of the two full \((\gamma,s,j)\)-supports.
The definition is rooted at \(m_1\) and may be asymmetric.  The symmetric
intersection in which both cofactors lie in \([R,2R]\) is a subset of this
rooted set, in either ordering.

\subsection{Exact factor exchange and the simultaneous orbit class}

The following lemma records the fixed-row consequences of the
factor-exchange normal form.  It is included to make the subsequent
summation transparent.

\begin{lemma}[Fixed-row exchange equations and determinant]
\label{lem:tpc66-fixed-row-exchange}
Let \((s,j)\in\mathcal C^{\mathrm{red}}_{m_1,m_2}(R)\).  There are unique
positive, pairwise coprime, squarefree integers \(a,b,c,e\) such that
\begin{equation}
 d_1=ab,\qquad d_2=ac,\qquad
 r_1=ce,\qquad r_2=be,\qquad
 s=abce.
 \label{eq:tpc66-factor-exchange}
\end{equation}
For fixed rows, \(a=(d_1,d_2)\), \(b=d_1/a\), and \(c=d_2/a\) are fixed;
only \(e\) can vary.  The two terminal equations are
\begin{align}
 ce\,p_1-ab\ell_1j&=h_0,
 \label{eq:tpc66-exchange-terminal-one}\\
 be\,p_2-ac\ell_2j&=h_0,
 \label{eq:tpc66-exchange-terminal-two}
\end{align}
and imply
\begin{align}
 e(cp_1-bp_2)
 &=aj(b\ell_1-c\ell_2),
 \label{eq:tpc66-exchange-identity}\\
 \frac{e}{(e,h_0)}
 &\mid b\ell_1-c\ell_2.
 \label{eq:tpc66-exchange-divisibility}
\end{align}
Moreover,
\begin{equation}
 b\ell_1-c\ell_2\ne0.
 \label{eq:tpc66-nonzero-row-difference}
\end{equation}
\end{lemma}

\begin{proof}
The unique squarefree factor exchange is the one from TPC--57:
the prime factors of \(s\) are partitioned according to whether they
belong to both \(d_i\), only \(d_1\), only \(d_2\), or both \(r_i\).
Substitution in the two copies of
\eqref{eq:tpc66-two-terminal-equations-short} gives
\eqref{eq:tpc66-exchange-terminal-one} and
\eqref{eq:tpc66-exchange-terminal-two}; subtracting them gives
\eqref{eq:tpc66-exchange-identity}.

On the literal carrier, \((m_i,r_i)=1\).  Reducing the two terminal
equations modulo \(r_i\) therefore gives
\[
 j\equiv-h_0(ab\ell_1)^{-1}\pmod{ce},
 \qquad
 j\equiv-h_0(ac\ell_2)^{-1}\pmod{be}.
 \]
Compatibility modulo the common factor \(e\) is equivalent to
\(e\mid h_0(b\ell_1-c\ell_2)\), which is
\eqref{eq:tpc66-exchange-divisibility}.  Finally, equality in
\eqref{eq:tpc66-nonzero-row-difference} would give
\(m_1=ab\ell_1=ac\ell_2=m_2\), contrary to the hypothesis.
\end{proof}

\begin{proposition}[Exact CRT class and two terminal-prime forms]
\label{prop:tpc66-crt-and-prime-forms}
Fix the two distinct rows and an admissible exchange cofactor \(e\) arising
from \cref{lem:tpc66-fixed-row-exchange}; in particular, \(e\) is squarefree,
\((e,abc)=1\), and it satisfies
\eqref{eq:tpc66-exchange-divisibility}.  The two orbit congruences are
compatible and determine one residue class
\begin{equation}
 j\equiv j_e\pmod{bce}.
 \label{eq:tpc66-joint-crt-class}
\end{equation}
Consequently an orbit interval of diameter at most \(C_JJ\) contains at
most
\begin{equation}
 1+\left\lfloor\frac{C_JJ}{bce}\right\rfloor
 \label{eq:tpc66-fixed-e-orbit-count}
\end{equation}
simultaneously integral times.

Writing \(j=j_e+bce\,q\), the two terminal candidates are
\begin{equation}
 p_1(q)=p_{1,e}+ab^2\ell_1q,\qquad
 p_2(q)=p_{2,e}+ac^2\ell_2q.
 \label{eq:tpc66-two-prime-forms}
\end{equation}
They are nonproportional: their cross determinant is
\begin{equation}
 (ac^2\ell_2)p_{1,e}-(ab^2\ell_1)p_{2,e}
 =
 -\frac{ah_0}{e}(b\ell_1-c\ell_2)\ne0.
 \label{eq:tpc66-two-prime-cross-determinant}
\end{equation}
\end{proposition}

\begin{proof}
The two moduli are \(ce\) and \(be\).  Since \(b,c,e\) are pairwise
coprime, their gcd and least common multiple are respectively \(e\) and
\(bce\).  The compatibility condition is precisely
\eqref{eq:tpc66-exchange-divisibility}, so the Chinese remainder theorem
gives \eqref{eq:tpc66-joint-crt-class}.  The spacing bound gives
\eqref{eq:tpc66-fixed-e-orbit-count}.

Substituting \(j=j_e+bce\,q\) in
\eqref{eq:tpc66-exchange-terminal-one} and
\eqref{eq:tpc66-exchange-terminal-two} gives
\eqref{eq:tpc66-two-prime-forms}.  At \(q=0\), multiply the first
terminal equation by \(c\ell_2\), the second by \(b\ell_1\), and
subtract.  This gives
\[
 e(c^2\ell_2p_{1,e}-b^2\ell_1p_{2,e})
 =-h_0(b\ell_1-c\ell_2).
 \]
Multiplication by \(a\), followed by
\eqref{eq:tpc66-nonzero-row-difference}, proves
\eqref{eq:tpc66-two-prime-cross-determinant}.
\end{proof}

\subsection{Summing every exchange cofactor}

\begin{theorem}[Divisor-thin rooted fixed-row-pair codegree]
\label{thm:tpc66-divisor-thin-pair-codegree}
Assume that, for one fixed \(A>0\), all row and orbit labels are at most
\(X^A\), while \(h_0\ne0\) is fixed.  Uniformly over distinct literal
source rows,
\begin{align}
 c^{\mathrm{red}}_{m_1,m_2}(R)
 &\le
 \sum_{\substack{e\ge1\ {\rm squarefree}\\
          (e,abc)=1\\
          e/(e,h_0)\mid b\ell_1-c\ell_2\\
          R\le ce\le2R}}
 \left(
 1+\left\lfloor\frac{C_JJ}{bce}\right\rfloor
 \right)
 \label{eq:tpc66-exact-codegree-sum}\\
 &\ll_{h_0,C_J}
 X^{o(1)}
 \left(1+\frac JR\right).
 \label{eq:tpc66-codegree-main-bound}
\end{align}
The \(o(1)\) is uniform over the declared row pair.
\end{theorem}

\begin{proof}
For fixed rows, \(a,b,c,\ell_1,\ell_2\) are fixed.  Put
\[
 N_{12}:=b\ell_1-c\ell_2\ne0.
 \]
For every admissible \(e\), let \(\delta=(e,h_0)\).  Since \(e\) is
squarefree, \(\delta\) is one of the \(O_{h_0}(1)\) divisors of
\(\operatorname{rad}|h_0|\), while
\[
 e/\delta\mid N_{12}
 \]
by \eqref{eq:tpc66-exchange-divisibility}.  The map
\(e\mapsto(\delta,e/\delta)\) is injective.  Hence
\begin{equation}
 \#\{e:e\ {\rm squarefree},\ e/(e,h_0)\mid N_{12}\}
 \le
 \tau(\operatorname{rad}|h_0|)\tau(|N_{12}|)
 =X^{o(1)},
 \label{eq:tpc66-number-of-exchange-cofactors}
\end{equation}
uniformly, by the standard divisor bound and the polynomial size of
\(N_{12}\).

For each \(e\), \cref{prop:tpc66-crt-and-prime-forms} gives at most
\eqref{eq:tpc66-fixed-e-orbit-count} possible times.  Every literal
primality, residue, mask, profile, and endpoint condition only deletes
such times, proving \eqref{eq:tpc66-exact-codegree-sum}.  On the root
block, \(ce=r_1\ge R\), and therefore
\[
 bce=br_1\ge R.
 \]
Each summand in \eqref{eq:tpc66-exact-codegree-sum} is consequently
\(O_{C_J}(1+J/R)\).  Combining this with
\eqref{eq:tpc66-number-of-exchange-cofactors} proves
\eqref{eq:tpc66-codegree-main-bound}.
\end{proof}

\begin{corollary}[Critical-block pair linearity]
\label{cor:tpc66-critical-pair-linearity}
If \(R/J=X^{o(1)}\) and \(J/R=X^{o(1)}\), in particular if
\[
 R\asymp J=X^{133/400+o(1)},
 \]
then, uniformly over distinct active rows,
\begin{equation}
 \boxed{
 c^{\mathrm{red}}_{m_1,m_2}(R)=X^{o(1)}.}
 \label{eq:tpc66-critical-subpower-codegree}
\end{equation}
\end{corollary}

\begin{proof}
Insert \(J/R=X^{o(1)}\) in
\eqref{eq:tpc66-codegree-main-bound}.
\end{proof}

\subsection{Asymmetry with the right-fiber degree}

The low pair codegree does not say that one residual output has low
multiplicity.  TPC--55 proves, on a cofactor range comparable to \(R\),
\begin{equation}
 \Delta_R^{\mathrm{fib}}
 :=
 \max_y
 \#\{u:q(u)=y,\ r_u\asymp R\}
 \ll
 X^{o(1)}
 \left(1+\frac LR\right).
 \label{eq:tpc66-right-fiber-degree}
\end{equation}
The same bound applies to the reduced cell \((s,j)\) obtained by
forgetting \(\gamma\): before the opposite-label masks are imposed, the
candidate rows are already the source/terminal-prime solutions of the
fixed-\((s,j,d)\) determinant ladder, and allowing the existence of some
\(\gamma\) does not create an additional arithmetic solution.  Opposite
labels only decorate or delete such a row.
The constant-factor saturation \(r_u\in[R/2,4R]\) changes no exponent.
At the inherited endpoint,
\[
 L=X^{99979/210000+o(1)},
 \qquad
 R\asymp J=X^{133/400+o(1)},
 \]
so
\begin{equation}
 \Delta_R^{\mathrm{fib}}
 \le
 X^{15077/105000+o(1)},
 \qquad
 \max_{m_1\ne m_2}
 c^{\mathrm{red}}_{m_1,m_2}(R)
 =X^{o(1)}.
 \label{eq:tpc66-degree-codegree-asymmetry}
\end{equation}
Thus the literal reduced incidence may have polynomially large right
degree while remaining subpower-linear from the viewpoint of every fixed
left row pair.

\subsection{A four-cycle consequence}

Let \(\mathscr G_R^{\mathrm{red}}\) be the bipartite graph whose left
vertices are source rows and whose right vertices are reduced cells
\((s,j)\); join \(m\) to \((s,j)\) when a literal terminal atom on row
\(m\), with \(r\in[R,2R]\), occurs over that cell for at least one
\(\gamma\).  Write
\[
 I_m(R):=\{(s,j):m\sim(s,j)\},\qquad
 H_m(R):=|I_m(R)|,
 \]
and let \(d_R(s,j)\) be the right degree.  Put
\[
 C_R:=\max_{m\ne n}|I_m(R)\cap I_n(R)|,
 \qquad
 \Delta_R:=\max_{(s,j)}d_R(s,j).
 \]

\begin{corollary}[Rooted four-cycle bound]
\label{cor:tpc66-four-cycle-bound}
The number \(\mathfrak C_4(m;R)\) of unoriented four-cycles of
\(\mathscr G_R^{\mathrm{red}}\) containing a fixed left vertex \(m\)
satisfies
\begin{align}
 \mathfrak C_4(m;R)
 &=
 \sum_{n\ne m}
 \binom{|I_m(R)\cap I_n(R)|}{2}
 \label{eq:tpc66-four-cycle-identity}\\
 &\le
 \frac{\max\{C_R-1,0\}}{2}
 \sum_{(s,j)\in I_m(R)}
 \bigl(d_R(s,j)-1\bigr)
 \label{eq:tpc66-four-cycle-incidence-bound}\\
 &\le
 \frac{\max\{C_R-1,0\}}{2}
 H_m(R)(\Delta_R-1).
 \label{eq:tpc66-four-cycle-degree-bound}
\end{align}
At \(R\asymp J\),
\begin{equation}
 \mathfrak C_4(m;R)
 \le
 H_m(R)\,
 X^{15077/105000+o(1)}.
 \label{eq:tpc66-critical-four-cycle-bound}
\end{equation}
\end{corollary}

\begin{proof}
A four-cycle through \(m\) is uniquely a second row \(n\ne m\) together
with two distinct common reduced cells, proving
\eqref{eq:tpc66-four-cycle-identity}.  For
\(0\le c\le C_R\),
\[
 \binom c2\le\frac{\max\{C_R-1,0\}}{2}c.
\]
Moreover, double-counting the ordered pairs consisting of a cell
incident to \(m\) and another row incident to that cell gives
\[
 \sum_{n\ne m}|I_m(R)\cap I_n(R)|
 =
 \sum_{(s,j)\in I_m(R)}(d_R(s,j)-1).
 \]
These two identities prove
\eqref{eq:tpc66-four-cycle-incidence-bound}; the maximal right-degree
bound gives \eqref{eq:tpc66-four-cycle-degree-bound}.  Finally use
\cref{cor:tpc66-critical-pair-linearity} and
\eqref{eq:tpc66-degree-codegree-asymmetry}.
\end{proof}

\begin{remark}[Literal scope and the \(\gamma\)-boundary]
\label{rem:tpc66-codegree-scope}
Every result in this section is L1: it is an unconditional upper
statement on one literal fixed-\(h_0\) terminal carrier, using the actual
squarefree factor exchange and the actual orbit congruences.  The
argument does not enlarge the carrier; omitted primality, mask, profile,
residue, or endpoint tests can only reduce the counted set.

The reduction from \((\gamma,s,j)\) to \((s,j)\) is deliberate.  The raw
full-support intersection is
\[
 \sum_{(s,j)\in\mathcal C^{\mathrm{red}}_{m_1,m_2}(R)}
 \#\{\gamma:
   b_{(\gamma,s,j),m_1}b_{(\gamma,s,j),m_2}\ne0\},
 \]
and the inner multiplicity can be polynomially large.  Therefore
\eqref{eq:tpc66-critical-subpower-codegree} is not a subpower theorem
for raw \(\gamma\)-decorated support.  Its role is to bound the number of
arithmetic cells contributing to one row-pair Gram entry after the
opposite-label coordinates are combined with their literal weights.
No lower exposure, coefficient diffuseness, signed cancellation,
smallest-eigenvalue estimate, parity improvement, or prime-pair
conclusion is asserted.
\end{remark}
