\section{Certificates, comparison ledger, and boundaries}\label{sec:certificates-boundaries}

\subsection{Exact reproducibility certificate}

The directory \texttt{experiments/} contains a pure standard-library Python
implementation of the finite witness in \cref{sec:finite-barriers}.  It uses
integers and \texttt{Fraction} objects only; there is no floating-point
arithmetic, random sampling, external primality library, or fitted parameter.
The retained certificate is
\begin{center}
 \path{experiments/data/exact-certificate.json}.
\end{center}
Its SHA-256 digest is
\begin{center}
\small
\texttt{0C6BDAC0FDBD5BAB3308AAA907F361D9903B5A88406F6F466B621490C9AB7004}.
\end{center}
The main exact entries are summarized in \cref{tab:certificate-summary}.

\begin{table}[ht]
\centering
\caption{Exact finite witness retained in the certificate.}
\label{tab:certificate-summary}
\begin{tabular}{@{}ll@{}}
\toprule
quantity & exact value\\
\midrule
$Q,h$ & $385,2$\\
square target & $148996=2^2\cdot193^2$\\
prime target & $149381$\\
common factor residue & $(1,384)\pmod{385}$\\
common target residue & $1\pmod{385}$\\
$\kappa_Q$ & $9/16$\\
common $K_{Q,2}^{\circ}$ & $7/9$\\
$L_{\rm prime}(v)$ & $-1$\\
$L_\lambda(v)$ & $2$\\
prime minimax lower bound & $1/2$\\
Liouville minimax lower bound & $1$\\
Lucas witness & $3$\\
\bottomrule
\end{tabular}
\end{table}

Running
\begin{verbatim}
python exact_defect_certificate.py --output data/exact-certificate.json
python -m unittest -v test_exact_defect_certificate.py
\end{verbatim}
recomputes the JSON object and verifies byte-for-byte equality with the
tracked file.  The tests cover the two factorizations, the complete Lucas
certificate, CRT pushforward equality, all three prime-window signatures,
the exact centered-kernel value, both functional gaps, and both minimax
bounds.

\begin{remark}[What the certificate certifies]\label{rem:certificate-scope}
The certificate is a proof aid for a finite algebraic witness.  It is not
numerical evidence that a growing-window defect is small or large, and no
asymptotic theorem depends on extrapolating its values.
\end{remark}

\subsection{What is already known for neighboring sums}

The target-prime form changes character when the coefficient geometry
changes.  Three nearby statements should not be confused.
\begin{enumerate}[label=\textbf{K\arabic*.},leftmargin=3.2em]
 \item The complete unweighted hyperbolic sum can be rewritten as a shifted
 divisor problem:
 \[
  \sum_{mn+h\le X}\Lambda(mn+h)
  =\sum_{k\le X}\Lambda(k)\tau(k-h)
 \]
 up to the elementary boundary convention.  Strong uniform asymptotics for
 this type of sum are known \citep[Theorem~1.1]{AssingBlomerLi2021}; see
 also \citet{Fouvry1985}.  We make no novelty claim for it.
 \item The one-sided form with arbitrary $\alpha_m$ and no $\beta_n$ is
 controlled by Bombieri--Vinogradov in the exact modulus range
 \eqref{eq:one-sided-bv-range}; this is
 \cref{thm:one-sided-bv-type-I}.  Inserting a free second coefficient
 sequence destroys the direct arithmetic-progression reduction.
 \item A balanced dyadic form
 \[
  \sum_{m\sim M}\sum_{n\sim N}
  \alpha_m\beta_n\Lambda(mn+h)
 \]
 with broad coefficient classes is a genuinely different Type~II or
 dispersion problem.  No theorem in this paper estimates it at a prescribed
 shift.
\end{enumerate}

Likewise, the generalized Chen theorem recorded in
\citet[Theorem~25.11]{FriedlanderIwaniec2010} supplies many primes $p$ for which
$p-h$ has at most two prime factors, in an appropriate fixed-even-shift
formulation.  It does not allocate the mass between the prime and exact
semiprime sectors.  This is a classical near-miss, not a corollary of the CRT
nullspace theorem.

\subsection{A strict ledger of implications}

The results proved here have the following one-way relationships:
\begin{equation}\label{eq:implication-ledger}
\begin{gathered}
\text{finite CRT kernel}
\quad+\quad
\text{TPC-5 conductor estimates}
\quad\Longrightarrow\quad
\text{rough-target main term},\\
\text{Bombieri--Vinogradov}
\quad\Longrightarrow\quad
\text{one-sided target-prime Type~I range},\\
\text{full fixed-shift prime-pair asymptotic}
\quad\Longleftrightarrow\quad
\text{large-divisor tail cancellation in \cref{thm:large-source-tail-equivalence}}.
\end{gathered}
\end{equation}
The first two lines do not combine automatically, because they control
different weights and different coefficient norms.  The last line is an
exact equivalence, not a proof of either side.

The unresolved form produced by Vaughan's identity in
\cref{subsec:compact-vaughan-ledger} has the multiplicative-surface geometry
\begin{equation}\label{eq:hard-surface}
 \ell k-mn=h.
\end{equation}
Finite target roughness only records whether the right side of $mn+h$ meets
selected residue classes.  It gives neither cancellation between the two
factorizations in \eqref{eq:hard-surface} nor positivity for a prime target.

\subsection{Strict boundary of the claims}

For clarity, none of the following is asserted.
\begin{enumerate}[label=\textbf{B\arabic*.},leftmargin=3.2em]
 \item We do not prove that $mn+h$ is prime for any infinite family of
 factor pairs, and do not prove a lower bound for
 $\Lambda(m)\Lambda(n)\Lambda(mn+h)$.
 \item We do not estimate $\sum_n\Lambda(n)\Lambda(n+2)$ beyond the exact
 decomposition of \cref{thm:large-source-tail-equivalence}.  The large-divisor tail
 is the unsolved content.
 \item The one-sided Bombieri--Vinogradov theorem has no arbitrary second
 coefficient sequence.  Calling it a balanced Type~II estimate would be
 false.
 \item Vaughan's and Heath--Brown's identities are algebraic decompositions.
 Merely naming their Type~I/II packets supplies no estimate for those packets.
 \item The periodic-minorant and nullspace theorems concern a fixed finite
 period.  They are not universal impossibility theorems for analytic number
 theory and do not rule out increasing resolution or nonlocal input.
 \item No spectral isomorphism between the logistic map and a prime-target
 operator is claimed.  The dynamics used here consists of finite arithmetic
 shifts, congruence graph involutions, and their exact Fourier spectra.
\end{enumerate}

\subsection{Conclusion}

Within the present framework, two elementary exact identities separate the
finite rough term from the target von Mangoldt term and decompose a finite
divisor truncation into congruence involutions.  Classical
Bombieri--Vinogradov theory evaluates the one-sided Type~I range up to
$X^{1/2}(\log X)^{-B}$.  In the additive ledger, the standard main-term
calculation for that signed truncation yields the full formal pair
singular-series constant; the complementary fixed-shift tail remains
unestimated.

The negative theorems explain why this remainder cannot be replaced by a
fixed periodic prime minorant or inferred from finite CRT spectra.  Within
the present divisor/operator framework, a next advance would require a
genuinely nonlocal estimate---for example a
coefficient-stable Type~II or dispersion theorem for a specified portion of
\eqref{eq:hard-surface}.  Any such theorem must state its coefficient class,
scale, averaging variable, and fixed-shift quantifier explicitly.
