\section{Introduction and scope}\label{sec:introduction}

The preceding papers in this series moved from periodic prime-sieve words to
centered two-factor kernels.  Complete finite correlations recover the local
Hardy--Littlewood product, character decomposition identifies the exact local
modes, classical incomplete-character estimates transfer those modes to
power-short boxes, and a multiplicative-large-sieve argument permits von
Mangoldt weights on the two factor coordinates
\citep{WangTPCOne2026,WangTPCTwo2026,WangTPCThree2026,WangTPCFour2026,WangTPCFive2026}.
The last result counts prime factors $p,q$ for which $pq+h$ avoids a growing
finite set of primes.  It does not make $pq+h$ prime.

Throughout, $\Lambda(t)$ and $\one_{\Pp}(t)$ are extended by zero for
nonpositive integers $t$.

This paper studies that missing target-prime interface.  There are two
different transitions, and conflating them obscures the parity problem:
\begin{enumerate}[label=\textbf{T\arabic*.},leftmargin=3.2em]
 \item replace the local target indicator $\one_{(mn+h,Q)=1}$ by
 $\Lambda(mn+h)$;
 \item connect a two-factor target-prime form back to the additive
 correlation $\sum_n\Lambda(n)\Lambda(n+h)$.
\end{enumerate}
The first transition is a kernel and bilinear-form comparison.  The second requires an
exact convolution ledger and estimates for the resulting bilinear packets.
Neither follows from a topological conjugacy, an ordinary spectral limit, or
the finite character expansion alone.

\subsection{The exact rough-to-prime defect}

Let $Q$ be odd and squarefree, put
\[
 G=(\Z/Q\Z)^\times,
 \qquad
 \delta_Q=\frac{\varphi(Q)}Q,
 \qquad
 \kappa_Q=\prod_{p\mid Q}\frac{p-2}{p-1},
\]
and suppose $(h,Q)=1$.  On factor coordinates which are $Q$-units, define
\[
 K_{Q,h}(m,n)=\one_{(mn+h,Q)=1},
 \qquad
 K_{Q,h}^{\circ}=\kappa_Q^{-1}K_{Q,h}-1.
\]
For finite coefficient sequences $a=(a_m)$ and $b=(b_n)$ write
\begin{align}
 A_0&=\sum_m a_m,& B_0&=\sum_n b_n,\label{eq:intro-masses}\\
 \cB_{Q,h}(a,b)&=\sum_{m,n}a_mb_nK_{Q,h}^{\circ}(m,n),\label{eq:intro-centered-form}\\
 \cP_h(a,b)&=\sum_{m,n}a_mb_n\Lambda(mn+h).\label{eq:intro-prime-target-form}
\end{align}
The pointwise defect
\begin{equation}\label{eq:intro-defect}
 D_{Q,h}(m,n)
 =\Lambda(mn+h)-\delta_Q^{-1}K_{Q,h}(m,n)
\end{equation}
gives the exact identity
\begin{equation}\label{eq:intro-exact-bridge}
 \cP_h(a,b)
 =\frac{\kappa_Q}{\delta_Q}
  \{A_0B_0+\cB_{Q,h}(a,b)\}
  +\cD_{Q,h}(a,b),
 \qquad
 \cD_{Q,h}(a,b)=\sum_{m,n}a_mb_nD_{Q,h}(m,n).
\end{equation}
Here
\begin{equation}\label{eq:intro-local-factor}
 \frac{\kappa_Q}{\delta_Q}
 =\prod_{p\mid Q}\frac{p(p-2)}{(p-1)^2}.
\end{equation}
Thus the preceding centered-kernel estimates control the first brace in
\eqref{eq:intro-exact-bridge}; they do not estimate $\cD_{Q,h}$.  The
identity is useful precisely because it prevents a local roughness theorem
from being silently relabeled as a target-prime theorem.

\subsection{Main results}

The paper records the following exact identities, standard analytic
consequences, and finite-information obstructions.  No new level of
distribution or parity-breaking estimate is claimed; the contribution is
their joint formulation within the finite-dynamics framework.
\begin{enumerate}[label=\textbf{R\arabic*.},leftmargin=3.2em]
 \item We resolve the finite truncation
 \[
  \Lambda_{\le R}(N)
  =-\sum_{\substack{d\mid N\\d\le R}}\mu(d)\log d
 \]
 into exact congruence layers.  For $(d,h)=1$, the layer
 $mn\equiv-h\pmod d$ is the graph of the involution
 $x\mapsto-hx^{-1}$ on $(\Z/d\Z)^\times$.  We give its complete
 Dirichlet-character expansion and show that its spectrum is contained in
 $\{+1,-1\}$.
 \item This comparison locates a structural loss.  The actual squarefree
 $d$-layer has norm $\log d/\varphi(d)$, and the absolute norms over the
 prime-modulus subfamily contribute $\sim\log R$.  Because different layers
 act on different spaces, this is not the divergence of a single operator.
 It says precisely that the summable scalar majorant used for the centered
 rough kernel cannot be transplanted verbatim; cancellation between moduli
 is neither excluded nor estimated.
 \item We prove a one-sided Bombieri--Vinogradov Type~I theorem for
 $\sum_m\alpha_m\sum_n\Lambda(mn+h)$, uniformly for $|\alpha_m|\le1$
 when the modulus variable lies in the classical range
 $m\le x^{1/2}(\log x)^{-B}$.
 This is a direct consequence of the classical theorem, not a new level of
 distribution.
 \item Applying the same input to the exact M\"obius--logarithm expansion of
 $\sum_n\Lambda(n)\Lambda(n+h)W(n/X)$ evaluates all coprime source divisors
 through $X^{1/2}(\log X)^{-B}$.  The main term of this signed truncation
 equals the full formal pair singular-series constant.  The
 Hardy--Littlewood asymptotic is then equivalent, by the exact divisor
 ledger, to cancellation of the complementary large-divisor
 M\"obius--prime tail; that tail may still be of order $X$.
 \item We prove that a nonnegative observable periodic in the two factor
 coordinates cannot be a nonzero pointwise minorant for target primality on
 all sufficiently large pairs.  We also give a nullspace theorem: modulo any
 fixed odd $Q$, two nonnegative point masses can have identical finite CRT,
 character, and centered-kernel data (the last at $\operatorname{rad}(Q)$)
 while their targets have opposite primality and Liouville values.
 \item At $Q=5\cdot7\cdot11$ we supply a deterministic integer certificate.
 The locally indistinguishable targets are the square $148996$ and the prime
 $149381$; the latter is accompanied by a Lucas certificate.
\end{enumerate}

The positive analytic result in R3 is deliberately one-sided.  It can place
a prime weight on one factor and on the target in an unbalanced range, but it
does not permit an arbitrary second factor coefficient.  In particular, the
two true statements
\[
 \sum_{m,n}\Lambda(m)\Lambda(n)K_{Q,h}(m,n)
 \quad\hbox{and}\quad
 \sum_{m,n}\Lambda(m)\Lambda(mn+h)
\]
cannot be intersected to infer a theorem for
\begin{equation}\label{eq:intro-triple-lambda}
 \sum_{m,n}\Lambda(m)\Lambda(n)\Lambda(mn+h).
\end{equation}
The missing covariance is displayed explicitly in
\cref{sec:small-divisor-interface}.

\subsection{Position relative to known results}

The Bombieri--Vinogradov input used below is classical
\citep{Bombieri1965,Vinogradov1965,IwaniecKowalski2004}.  Vaughan's identity
is used only as an exact ledger; a generalized Heath--Brown identity would
produce more multilinear packets but would not estimate them
\citep{Vaughan1977,HeathBrownVaughan1982}.  The asymptotic sieve of
\citet{FriedlanderIwaniec1998} is an important positive comparison: in its
axiomatic setting, additional M\"obius-weighted bilinear information can
break the parity barrier.  The recent general framework of
\citet{FordMaynard2024} likewise quantifies Type~I/II requirements within
its stated class of nonnegative sequences.  We do not turn either framework
into a theorem for \eqref{eq:intro-triple-lambda}.

There are also stronger theorems for differently averaged objects.  Uniform
Titchmarsh divisor results evaluate complete unweighted hyperbolic sums such
as $\sum_{mn+h\le X}\Lambda(mn+h)$ with strong errors
\citep[Theorem~1.1]{AssingBlomerLi2021}; see also \citet{Fouvry1985}.
They do not provide a balanced dyadic rectangle estimate with arbitrary
factor coefficients.  Chen's original theorem represents every sufficiently
large even integer as a prime plus a $P_2$-number \citep{Chen1973}.  A
generalized fixed-linear-form theorem
\citep[Theorem~25.11]{FriedlanderIwaniec2010} implies, for each fixed
admissible even $h$, a lower bound for primes $p$ with $p-h\in P_2$.
Here $P_2$ means at most two prime factors and therefore includes the prime
case; this theorem does not isolate $p=qr+h$ with $q,r$ both prime.  These
are neighboring achievements, not consequences of our finite identities.

\subsection*{What is not claimed}

We do not estimate the large-divisor tail isolated below, prove
\eqref{eq:intro-triple-lambda}, obtain a lower bound for twin primes, or prove
a new Bombieri--Vinogradov, dispersion, or Type~II theorem.  The finite
nullspace and periodic-minorant results concern fixed local resolution.  They
do not exclude growing moduli, bilinear information, automorphic input,
additive-combinatorial methods, or any other nonlocal argument.  Conversely,
the exact rewriting of an open correlation as one remainder is not presented
as an independently easier conjecture.
