\section{Exact certificate, dependencies, and scope}
\label{sec:tpc30-certificate}

\subsection{Finite exact certificate}

The standard-library script
\begin{center}
\texttt{experiments/tpc30\_certificate.py}
\end{center}
uses exception-based checks in ordinary and optimized Python.  It
verifies the finite algebra underlying the paper by independent direct
and structured computations:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the primitive identity
 \[
 (mj+h,nj+h)=(mj+h,m-n),
 \]
 together with an explicit nonprimitive counterexample;
 \item exact-$c$ orbit layers, direct occupancy in finite windows
 $\cI$ of length $O_{\mathscr D}(J)$, and the fixed-row large-content
 inequality
 \[
 \#\{j\in\cI:(j,h)=1,\ \cG_{m,n}(j)>Z\}
 \le\tau(|m-n|)\left(1+\frac JZ\right);
 \]
 \item the four-factor identity
 \[
 (rU,sV)
 =(r,s)(U,V)(r/(r,s),V/(U,V))
              (s/(r,s),U/(U,V));
 \]
 \item the explicit finite row-residue inequality
 \[
 \cR_c\le K_c\|\gamma^{(1)}\|_2\|\gamma^{(2)}\|_2,
 \]
 where $K_c$ is the largest row occupancy of a residue class;
 \item the central rational high-$\beta$ ledger, including the old zero
 saving and the relaxed margin $133/400$;
 \item metadata regression assertions recording each full-residual,
 positivity, prime-pair, and parity claim deliberately excluded here.
\end{enumerate}

The four-factor regression exhausts all $65{,}536$ quadruples
$1\le r,s,U,V\le16$ and separately checks $116$ affine-target
factorizations.  Ordinary and optimized Python both complete
$773{,}361$ recorded top-level exact checks and regenerate
byte-identical JSON.  The subcounts are
\begin{itemize}
 \item $441{,}578$ primitive target-gcd identity checks;
 \item $1{,}924$ exact-content occupancy checks;
 \item $1{,}135$ fixed-row large-content checks;
 \item $197{,}313$ exact four-factor checks;
 \item $131{,}301$ row-residue energy checks;
 \item $90$ rational high-$\beta$ ledger checks;
 \item $20$ scope and nonoverlap metadata regression assertions.
\end{itemize}
The reproducibility values are
\begin{itemize}
 \item source SHA-256:
 \nolinkurl{f4813d6e89163098187fe1ce585934b354a384a09b7ca4332e3fad42d1a78610};
 \item JSON SHA-256:
 \nolinkurl{c466cd747c726d51074c0d8967a950ee0bcfb3e8a4658fcb8d3a81e52615c2e9};
 \item certificate digest:
 \nolinkurl{8c52338642c27d2c4dafd6807cb8cc56d52888ae16b27cd9aeda880ccc10f64d}.
\end{itemize}
The source hash normalizes source newlines to LF; the certificate
digest hashes the canonical sorted payload before the digest field is
inserted.

These computations certify finite identities, explicit finite
inequalities, and rational arithmetic.  They do not prove an
asymptotic M\"obius estimate.  In particular, finite enumeration is
not used as evidence that the high-$\beta$ cell contains a positive
amount of mass.

\subsection{Dependency ledger}

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.34\textwidth}
                >{\raggedright\arraybackslash}p{0.20\textwidth}
                >{\raggedright\arraybackslash}p{0.37\textwidth}}
\toprule
Input or statement & Status & Use \\
\midrule
Opened-row $\ell^1/\ell^2$ provenance
& Imported & TPC-25; pair mass and the auxiliary exact-layer energy. \\
\addlinespace
Calibrated cutoff difference and pointwise divisor envelopes
& Imported & TPC-28--TPC-29; defines the three raw channels. \\
\addlinespace
Primitive target-gcd divisibility
& Inherited geometry & TPC-18; sharpened here to the exact opened-row
identity and orbit class. \\
\addlinespace
Fixed-row large-content occupancy and weighted tail theorem
& Proved here & Gives the $Q^2+XQ/Z$ physical estimate. \\
\addlinespace
Exact four-factor decomposition and cross-factor pruning
& Elementary identity; pruning proved here & Reaches quotient-rich and
cross-rich sectors. \\
\addlinespace
TPC-29 reflected-content theorems
& Imported for comparison & Establishes strict nonoverlap of the
high-$\beta$ sample. \\
\addlinespace
Fixed-form logarithmic Elliott theorem
& External benchmark & Not used in any positive estimate here. \\
\addlinespace
Signed determinant-family dispersion
& Open & Proposed next input for the present route. \\
\bottomrule
\end{tabular}
\end{center}

\subsection{Claims deliberately excluded}

The following statements are not consequences of this paper:
\begin{itemize}
 \item cancellation or closure on every small-target-gcd fiber;
 \item closure of the complete ultra-long cutoff difference or the
 full TPC-18 residual;
 \item an effective polynomially uniform Chowla--Elliott theorem;
 \item a positive lower bound, a Hardy--Littlewood asymptotic, or
 infinitely many twin primes;
 \item a general violation or weakening of the sieve parity barrier.
\end{itemize}
The positive conclusion is narrower: within the retained three-channel
physical packet, every polynomially large full-target-content sector
is power-small, including quotient-rich and cross-rich sectors that
are invisible to reflected content alone.
The remaining small-target-content residual is not solved; its fully
coprime sector is identified as the sharp model.
