\section{Comparison, the coprime core, and the next gate}
\label{sec:tpc30-comparison}

\subsection{The inherited identity and the new estimate}

TPC-18 already observed that, on a primitive common orbit, the gcd of
two affine targets divides the source-row difference
\citep{WangTPC18}.  The Euclidean step behind
\eqref{eq:tpc30-target-gcd-identity} is therefore inherited.  The
present additions are:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the exact identity for the actual composite opened rows
 $m=\ell d$ and their physical primitive support;
 \item the fixed-row large-content occupancy
 \eqref{eq:tpc30-fixed-row-large-content};
 \item the weighted family estimate
 \eqref{eq:tpc30-main-content-bound} for all three raw channels;
 \item the exact four-factor identity
 \eqref{eq:tpc30-four-factor-identity} and its application to
 quotient-rich and cross-rich divisor sectors.
\end{enumerate}
Thus there is no claim that the Euclidean gcd observation was unknown.
The contribution within the present reduction is the physical
family-level pruning bound obtained by placing that observation before
divisor-variable separation.

\subsection{Strict separation from the TPC-29 regions}

Write
\[
 q=[r,s],\qquad g=(r,s).
\]
TPC-29 proves power saving in the two regions
\begin{align}
 q\le J,\qquad &g>X^\eta,
 \label{eq:tpc30-old-long-region}\\
 q\ge J,\qquad &q/g\le JX^{-\eta}.
 \label{eq:tpc30-old-sparse-region}
\end{align}
The new theorem depends instead on the full target content
\[
 \cG=gexy.
\]
It is independent of whether $q$ is below or above $J$.  In
particular, the high-$\beta$ block in
\cref{sec:tpc30-high-beta} has $q>J$, $g=X^{o(1)}$, and $q/g>J$, so neither
\eqref{eq:tpc30-old-long-region} nor
\eqref{eq:tpc30-old-sparse-region} applies.  Its large quotient
content $e$ nevertheless makes it power-small here.

The result is also distinct from deleting near-diagonal rows.  The
condition $\cG>Z$ implies that $m-n$ has a large divisor; it does not
imply that $|m-n|$ is small.  The high-$\beta$ cell is compatible with
$|m-n|=X^{\beta+o(1)}$, far from the near-row range.

\subsection{The small-content residual}

After applying \cref{thm:tpc30-common-target-pruning} with a fixed
threshold $X^\eta$, what remains satisfies
\begin{equation}
 \boxed{
 \cG_{m,n}(j)\le X^\eta.}
 \label{eq:tpc30-small-content-core}
\end{equation}
The sharp model is the fully coprime target sector
\begin{equation}
 (N_m(j),N_n(j))=1.
 \label{eq:tpc30-coprime-target-core}
\end{equation}
There
\[
 g=e=x=y=1
\]
for every selected factorization.  Neither shared content nor a
repartition of the same factors supplies a power saving.

For a reflected pair, compatibility still gives
\[
 g\mid m-n.
\]
The normalized row determinant
\begin{equation}
 \Delta_0=\frac{m-n}{g}
 \label{eq:tpc30-normalized-determinant}
\end{equation}
is therefore an integer.  The next useful decomposition is by the
number of allowed values of $\Delta_0$ in translated windows or residue
classes, not by another neighborhood of $\Delta_0=0$.  Near-row windows
have already been removed in the earlier pipeline; the genuinely new
question concerns macroscopically separated rows whose normalized
determinants occupy a thin additive spectrum.

An absolute estimate for one thin determinant class would not by
itself close \eqref{eq:tpc30-small-content-core}: summing all residue
classes absolutely restores the natural scale.  For the present
strategy, the next proposed gate is a signed family estimate that
recombines these classes while retaining
part of the single-class saving.  It must also preserve the two mixed
channels and the both-ultra channel from the exact cutoff difference.
Fixed-form logarithmically averaged Elliott cancellation
\citep{Tao2016} is a useful benchmark, but it supplies neither an
effective rate nor the required uniformity in the polynomially
growing slopes, divisor families, rows, and masks.

\subsection{Staged route after this paper}

The resulting route is deliberately modular:
\begin{enumerate}[label={\textup{TPC-\arabic*:}},start=31]
 \item prove determinant-entropy bounds for translated windows and
 individual normalized-determinant residue cells inside
 \eqref{eq:tpc30-small-content-core};
 \item seek signed dispersion across those cells, exploiting the
 factorable row source rather than only an arbitrary bounded mask;
 \item reassemble the mixed and both-ultra channels without separating
 away the cancellation encoded by the exact cutoff difference;
 \item return to the complete residual and endpoint packets only after
 the family estimate is uniform on the physical parameter box.
\end{enumerate}
Failure at any one of these stages would still identify a sharp
method boundary.  None of these future interfaces is assumed in the
theorems of the present paper.

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.42\textwidth}
                >{\raggedright\arraybackslash}p{0.47\textwidth}}
\toprule
Object & Status \\
\midrule
Primitive target-gcd Euclidean geometry
& Inherited from TPC-18 and restated exactly for opened rows. \\
\addlinespace
Selected truncated packet through $T$
& Closed under the TPC-28 physical conductor interfaces. \\
\addlinespace
Large reflected content and content-rich sparse wedge
& Closed in TPC-29. \\
\addlinespace
Large full-target content $\,\cG>Z$
& Power-saving bound proved here by
\cref{thm:tpc30-common-target-pruning}. \\
\addlinespace
Large quotient or normalized cross-content
& Power-saving bound proved here by
\cref{cor:tpc30-cross-factor-pruning}. \\
\addlinespace
Small full-target-content and fully coprime core
& Open; next determinant-entropy and signed-dispersion gate. \\
\addlinespace
Complete residual, positivity, prime-pair main term, or parity breach
& Not proved and not implied. \\
\bottomrule
\end{tabular}
\end{center}
