\section{The high-\texorpdfstring{$\beta$}{beta} cross-content cell}
\label{sec:tpc30-high-beta}

We now insert the target-content theorem into the exact parameter
sample closed through the selected cutoff in TPC-28.  The inherited
exponents are
\begin{equation}
 \beta=\frac{267}{400},\qquad
 \jmath=1-\beta=\frac{133}{400},\qquad
 t=\frac{193}{500}.
 \label{eq:tpc30-high-parameters}
\end{equation}
Thus
\begin{equation}
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
 \label{eq:tpc30-high-scales}
\end{equation}
and every reflected complement variable lies below
\begin{equation}
 \frac XT=X^{307/500+o(1)}.
 \label{eq:tpc30-reflected-ceiling}
\end{equation}

\subsection{A reflected pair with negligible common content}

In the both-ultra channel choose
\begin{equation}
 r,s=X^{1/4+o(1)},\qquad
 g=(r,s)=X^{o(1)}.
 \label{eq:tpc30-high-reflected-cell}
\end{equation}
The reflected lcm and its primitive part have exponents
\begin{align}
 [r,s]&=X^{1/2+o(1)},\label{eq:tpc30-high-lcm}\\
 \frac{[r,s]}{(r,s)}
 &=X^{1/2+o(1)}.\label{eq:tpc30-high-primitive-lcm}
\end{align}
Hence the fiber is sparse by
\begin{equation}
 \frac12-\frac{133}{400}
 =\boxed{\frac{67}{400}}.
 \label{eq:tpc30-high-sparse-margin}
\end{equation}
However, the TPC-29 absolute-incidence saving on this cell is
\begin{equation}
 \left(\frac{133}{400}-\frac12\right)_+
 =\boxed{0}.
 \label{eq:tpc30-old-zero-saving}
\end{equation}
Its content-rich sparse condition also fails because the primitive
lcm in \eqref{eq:tpc30-high-primitive-lcm} is larger than $J$ by a
fixed power.  The long-fiber theorem does not apply because
$[r,s]>J$.

Since each target is $X^{1+o(1)}$, the two co-divisors have size
\begin{equation}
 U,V=X^{3/4+o(1)}>T.
 \label{eq:tpc30-high-quotient-size}
\end{equation}
Impose the quotient-content condition
\begin{equation}
 e=(U,V)=X^{2/5+o(1)}.
 \label{eq:tpc30-high-quotient-content}
\end{equation}
Then
\begin{equation}
 U/e,\ V/e=X^{7/20+o(1)}.
 \label{eq:tpc30-high-reduced-quotients}
\end{equation}
To give the exponent cell a literal meaning, for fixed $\delta>0$ let
$\mathscr B_\delta(X)$ be the expanded both-ultra subfamily on which
\begin{align}
 X^{1/4-\delta}<r,s&\le X^{1/4+\delta},
 &g&\le X^\delta,
 \label{eq:tpc30-high-delta-reflected}\\
 X^{3/4-\delta}<U,V&\le X^{3/4+\delta},
 &X^{2/5-\delta}<e&\le X^{2/5+\delta}.
 \label{eq:tpc30-high-delta-quotient}
\end{align}
A sequence of dyadic blocks has the exponents displayed in
\eqref{eq:tpc30-high-reflected-cell},
\eqref{eq:tpc30-high-quotient-size}, and
\eqref{eq:tpc30-high-quotient-content} precisely when it belongs to
$\mathscr B_\delta(X)$ eventually for every fixed $\delta>0$.  By
\cref{prop:tpc30-four-factor-content}, every term in
$\mathscr B_\delta(X)$ satisfies $\cG_{m,n}(j)\ge e$ and hence lies in
the event
\begin{equation}
 \cG_{m,n}(j)>X^{2/5-\delta}.
 \label{eq:tpc30-high-target-event}
\end{equation}

\begin{corollary}[High-\texorpdfstring{$\beta$}{beta}
cross-content relaxed margin]
\label{cor:tpc30-high-cross-content}
For every fixed $\eta_0<133/400$, there is a $\delta_0>0$ such that,
for every fixed $0<\delta<\delta_0$, the expanded physical both-ultra
subsum $\cS_{\rm high,cross}(\delta)$ over
$\mathscr B_\delta(X)$ satisfies
\begin{equation}
 \boxed{
 |\cS_{\rm high,cross}(\delta)|
 \ll_{\delta,\eta_0,h,\mathscr D}XQX^{-\eta_0}.}
 \label{eq:tpc30-high-cross-bound}
\end{equation}
Equivalently, as $\delta\to0$, the supremal relaxed exponent in this
ledger is $133/400$; the endpoint itself is not asserted.
\end{corollary}

\begin{proof}
Choose $\delta_0$ small enough that
\begin{equation}
 \delta_0<\min\left\{\frac25-\eta_0,\frac{67}{1600}\right\}.
 \label{eq:tpc30-high-delta-choice}
\end{equation}
The second restriction also gives
$q/g=rs/g^2\ge X^{1/2-4\delta}>J$ and hence $q>J$ for all sufficiently
large $X$, so the strict separation from the TPC-29 regions is uniform
on this window.
On $\mathscr B_\delta(X)$ use
\cref{cor:tpc30-cross-factor-pruning} with
$Z=X^{2/5-\delta}$.  The two terms in
\eqref{eq:tpc30-main-content-bound}, relative to $XQ$, save
\begin{equation}
 1-\beta=\frac{133}{400},
 \qquad
 \frac25-\delta.
 \label{eq:tpc30-high-two-savings}
\end{equation}
The first is $133/400+o(1)$ at the inherited physical scale, and both
exponents exceed $\eta_0$ for all sufficiently large $X$.  This proves
the claimed bound.  Letting $\delta\to0$ gives the stated relaxed
margin.
\end{proof}

\subsection{Consistency checks}

The block is a support-compatible formal exponent cell.  First,
$1/4<307/500$, so both reflected variables obey
\eqref{eq:tpc30-reflected-ceiling}; and
$3/4>193/500$, so both co-divisors are genuinely beyond the selected
cutoff.  Second, the necessary divisibility $e\mid m-n$ is compatible
with the row scale because
\begin{equation}
 \frac{267}{400}-\frac25
 =\boxed{\frac{107}{400}}>0.
 \label{eq:tpc30-high-row-content-gap}
\end{equation}
On the optional macroscopically separated row subcell
$|m-n|=X^{\beta+o(1)}$, the reduced target difference
$(N_m-N_n)/e=((m-n)j)/e$ and each reduced product have exponent
\begin{align}
 \left(\frac{267}{400}-\frac25\right)
 +\frac{133}{400}
 &=\frac35,
 \label{eq:tpc30-high-row-orbit-balance}\\
 \frac14+\frac7{20}
 &=\frac35.
 \label{eq:tpc30-high-factor-balance}
\end{align}
Thus, on that subcell, the row--orbit and factorization ledgers agree.

Nor is this cell a relabeling of the TPC-29 reflected-content cell.
Moving the quotient gcd into both reflected variables would produce
the exponent
\begin{equation}
 \frac14+\frac25=\frac{13}{20}
 >\frac{307}{500},
 \label{eq:tpc30-high-not-reflected}
\end{equation}
above the reflected ceiling, while the reduced co-divisor exponent
$7/20$ lies below $t=193/500$.  The quotient content therefore crosses
the selected cutoff and cannot be absorbed into the old reflected
variables while preserving their channel roles.

\begin{table}[H]
\centering
\caption{Exact ledger for the high-$\beta$ cross-content cell.}
\label{tab:tpc30-high-ledger}
\begin{tabular}{@{}lll@{}}
\toprule
Quantity & Exact value & Role \\
\midrule
Orbit exponent $\jmath$ & $133/400$ & natural fiber length \\
Reflected exponent & $1/4$ & each of $r,s$ \\
Reflected lcm exponent & $1/2$ & sparse by $67/400$ \\
Old incidence saving & $0$ & primitive reflected core \\
Co-divisor exponent & $3/4$ & both-ultra support \\
Quotient-content exponent & $2/5$ & new full-target input \\
Reduced co-divisor exponent & $7/20$ & after removing $e$ \\
Row/content compatibility gap & $107/400$ & $e$ can divide $m-n$ \\
Relaxed margin & $133/400$ & every smaller fixed exponent is available \\
\bottomrule
\end{tabular}
\end{table}

The corollary is an upper bound for this support-compatible formal block.
It does not assert that the block is nonempty for every $X$, or that
it carries a positive proportion of the original residual.
