\section{Conclusion and the next analytic target}
\label{sec:conclusion}

The factor-scale coordinate separates four levels of information that are
easy to conflate.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item The zero Mellin mode admits the complete divisor collapse
 \(
  \sum_{d\mid r}(\Lambda(d)-1)=\log r-\tau(r)
 \)
 and hence a fixed-shift Titchmarsh evaluation.

 \item Coarse two-sided localization is still possible: after deleting
 every row with $m\leq Y$ or $n\leq Y$, the leading aggregate survives
 whenever $\log Y=o(\log X)$.  This is the bulk theorem
 \cref{thm:bulk-persistence}.

 \item Fine localization is available on the Type~I side.  Maximal
 Bombieri--Vinogradov evaluates an arbitrary fixed smooth window in
 $\log(n/m)$, uniformly in its moving center, as long as the modulus
 factor satisfies $n\leq X^{1/2}(\log X)^{-B}$.

 \item Fine localization of the complete long tail cannot be read from a
 fixed finite list of Mellin samples and a norm bound.  The exact error is
 a best exponential-polynomial approximation distance, and divisor-power
 fibres realize explicit blind directions.
\end{enumerate}

In spectral language, $u=\log(n/m)$ is the coordinate of the multiplicative
dilation flow and $e^{itu}$ is its character.  The zero mode is the
scale-invariant aggregate, derivatives at zero are generator moments, and
a local window requires a frequency superposition.  This is a precise use
of spectral coordinates; it does not identify zeta zeros, prime gaps, or
any other arithmetic data with dynamical eigenvalues.

The first Taylor derivatives explain why complete nonzero-Mellin control is
harder than the zero mode.  Already $D_1$ and $D_2$ contain shifted
two-von-Mangoldt convolution coefficients.  Even symmetrization removes
the former but leaves the latter.  At the strongest endpoint, the exact
sinc-squared filter recovers the $m=1$ fixed-prime-pair layer, showing that
an all-frequency theorem of the predicted strength would be equivalent to
the weighted Hardy--Littlewood assertion.

The most concrete next analytic target is therefore intermediate between
the results proved here and that endpoint.  One may seek a continuum-band
mean-square estimate for the complete large-factor transform,
\begin{equation}\label{eq:next-band-target}
 \int_{|t|\leq T}
 \left|
  \sum_{\substack{n>D\\m\geq1}}
  (\Lambda(n)-1)\Lambda(mn+h)W(mn/X)(n/m)^{it}
  -\cM_{h,D}(X;t)
 \right|^2dt,
\end{equation}
with an explicit model $\cM_{h,D}$ and a range $T=T(X)$ that grows.
Together with a compatible inverse transform for $\cM_{h,D}$ and control
of the weighted tail $|t|>T$---or, alternatively, for a band-limited
window---\eqref{eq:scale-center-Plancherel} would turn such an estimate into
an $L^2$ theorem over scale centers.  Averaging the shift $h$, enlarging
the window width, or restricting the frequency band are honest weaker
targets if the fixed-shift form \eqref{eq:next-band-target} proves
inaccessible.

Nothing in the present argument supplies signed Type~II cancellation,
pointwise localization of the complete tail, a fixed-shift prime-pair
asymptotic, a twin-prime lower bound, a new level of distribution, or a
parity-barrier breakthrough.  The advance is instead a sharp map: two
regions of rigorous localization, an exact finite-information boundary,
and an explicit identification of the arithmetic object that the next
layer must control.
