\begin{abstract}
The critical-cutoff analysis of TPC--59 separates the complete high-prime
Walsh face into coordinates represented by the terminal census and
high coordinates absent from that image.  Restoring the latter is not a
monotone operation: their native output may cancel the already represented
affine vector.  We formulate this reassembly problem on the literal finite
row-coefficient space at one fixed nonzero shift.

For linear maps \(A,M:\cK\to\cH\), representing respectively the
represented affine output and the missing-high correction, put \(B=A+M\)
and
\[
 \delta_{\rm reasm}
 =\inf_{Az\ne0}\frac{\|Bz\|^2}{\|Az\|^2}.
\]
The denominator does not see \(N=\Ker A\), while \(B(N)=M(N)\) can cancel
the full output.  We prove that the exact quotient is obtained only after
shorting \(B^*B\) against these nuisance directions.  If \(S=N^\perp\),
\(B_1=B|_S\), \(B_0=B|_N\), and \(P\) projects onto
\(B(N)^\perp\), then
\[
 \delta_{\rm reasm}
 =\inf_{s\in S\setminus\{0\}}
   \frac{\|PB_1s\|^2}{\|A s\|^2}.
\]
Equivalently, it is the least generalized eigenvalue of the pair
\((Q,A_S^*A_S)\), where the shorted numerator is
\[
 Q=B_1^*B_1-B_1^*B_0(B_0^*B_0)^\dagger B_0^*B_1.
\]
This yields the exact finite-dimensional positivity test
\(\Ker(A+M)\subseteq\Ker A\), an anti-diagonal image test, and a rank
kill criterion.  A naive compression to \(N^\perp\) is shown by sharp
examples to overestimate the transfer.

We also give a distinguished-vector signed-defect identity and a sharp
raw-mass certificate.  If each native output receives at most
\(d_{\rm miss}\) missing atoms, then
\[
 \|Mz\|^2\le d_{\rm miss}\cD_{\rm miss}(z).
\]
Consequently a missing-mass saving \(X^{-\sigma_{\rm miss}}\)
automatically defeats a fiber-degree cost \(X^{\mu_{\rm miss}}\) under
the strict exponent inequality
\(\sigma_{\rm miss}>\mu_{\rm miss}\), relative to the represented
output.  At exponent equality, finer constant or subpower information
decides whether this certificate still has zero fixed-power cost.
The terminal image and its complement are identified on the same physical
Walsh carrier and raw normalization.  No positive bound for the resulting
arithmetic constant is proved.  Thus the work closes the L0 linear-algebra
interface and the L1 fixed-shift dictionary, but proves no parity
improvement, prime-pair asymptotic, or twin-prime consequence.
\end{abstract}
