\section{Claims, limitations, and the next arithmetic gate}
\label{sec:tpc60-claims-next}

\subsection{Result ledger}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.23\textwidth}
                >{\raggedright\arraybackslash}p{0.50\textwidth}
                >{\raggedright\arraybackslash}p{0.17\textwidth}}
\toprule
Object & Exact conclusion & Status\\
\midrule
Three physical maps
& One row-coefficient space and one fixed \(h_0\) support
  \(B_X=A_X+M_X\), with raw atomic
  \(\cD_0=\cD_B+\cD_R+\cD_M\).
& L1 identity\\
\addlinespace
Prime-resolved alias
& Same-prime represented and missing vectors have disjoint support;
  only base--missing interaction and unequal-prime aliasing remain.
& L1 identity\\
\addlinespace
Uniform reassembly quotient
& Exact nuisance elimination, shorted-Gram generalized eigenvalue,
  and effective least singular value.
& L0 theorem\\
\addlinespace
Uniform zero test
& \(\delta(A,M)>0\) exactly when
  \(\Ker(A+M)\subseteq\Ker A\); a dimension excess kills it.
& L0 theorem\\
\addlinespace
Distinguished-vector defect
& Exact signed identity
  \(\|Bz\|^2-\|Az\|^2=\mathfrak X(z)\).
& L0 identity\\
\addlinespace
Raw mass--degree bridge
& \(\|Mz\|^2\le d_{\rm miss}\cD_{\rm miss}(z)\), with a sharp
  reverse-triangle certificate.
& L0 theorem\\
\addlinespace
Missing reason partition
& Definitional ordered first-failure partition; the inherited-support
  theorem makes the automatic pseudo-failure layers empty on the common
  literal carrier.
& L1 definitional partition plus inherited-support theorem\\
\addlinespace
Identical-support specialization
& Missing high atoms are exactly those whose complementary pair
  \((m,r)\) is outside \(\cI_X\).
& Conditional L1 identity\\
\addlinespace
Localization
& One represented dyadic block or one missing failure layer retains an
  \(X^{-o(1)}\) fraction of its branch.
& L1, \(\lambda_{\rm part}=0\)\\
\addlinespace
Endpoint certificate
& A route that pays the full residual determinant-ladder capacity incurs
  exponent at least \(15077/105000+\xi\), far above \(1/400\); this is not
  a lower bound for the actual native degree.
& Route-specific no-go\\
\bottomrule
\end{tabular}
\end{center}

\subsection{What is not proved}

The following statements do not follow from this paper:
\begin{enumerate}[leftmargin=2.3em]
 \item \(\cD_M=o(\cD_R)\), either rowwise or for the distinguished
       coefficient vector;
 \item a polynomial lower bound for \(\delta(A_X,M_X)\);
 \item a favorable sign for the base--missing or unequal-prime cross terms;
 \item \(\lambda_{\rm reasm}=0\) for the physical TPC family;
 \item a positive fixed-\(h_0\) parity gain, a prime-pair lower bound, a
       prime-pair asymptotic, or a twin-prime consequence.
\end{enumerate}
The first-failure partition can identify where missing mass lies, but does
not make that mass small.  The same-prime orthogonality deletes one class
of cross terms, but different primes still alias at the native output.  A
finite-scale positive eigenvalue is numerical scouting evidence unless its
scale dependence is controlled.

\subsection{The next ordered attack}

The next paper should not introduce another abstract angle.  The exact
reassembly theorem leaves a concrete arithmetic decision tree.

\begin{enumerate}[leftmargin=2.3em]
 \item \emph{Rowwise census.}  Compute or bound the literal weights
 \begin{equation}
  W_R(m),\qquad W_M(m),\qquad
  \frac{W_R(m)}{W_R(m)+W_M(m)}
  \label{eq:tpc60-next-row-census}
 \end{equation}
 on every active row.  If an active missing-only row occurs, record the
 exact death of the uniform represented-mass route.

 \item \emph{Cofactor-defect estimate.}  Under the identical-support
 specialization, replace the vague terminal failure by the single event
 \begin{equation}
  (m,r)\notin\cI_X.
  \label{eq:tpc60-next-cofactor-defect}
 \end{equation}
 Estimate its coefficient-weighted mass relative to the represented
 affine reference, not merely its unweighted cardinality.

 \item \emph{Restricted native degree.}  Factor the missing map through
 residual keys and estimate its norm on the actual coefficient image.
 The ambient bound \(X^{o(1)}Q\) is too large, while the residual ladder
 bound alone does not survive erasure of \(s\).  A successful argument
 must prove either a smaller restricted degree exponent or destructive
 phase cancellation inside the missing map itself.

 \item \emph{Shorted kernel audit.}  Assemble the literal matrices
 \(A_X,M_X\) at finite scales and test
 \begin{equation}
  \Ker(A_X+M_X)\subseteq\Ker A_X,
  \qquad
  \dim\bigl((\Ker A_X)^\perp\bigr)
  \le\dim\cH_{\rm out}
       -\rank\!\left(B_X|_{\Ker A_X}\right).
  \label{eq:tpc60-next-kernel-audit}
 \end{equation}
 Repeated exact failure closes the uniform door.  Repeated numerical
 success does not prove an asymptotic lower singular value, but it can
 identify the correct subspace for a theorem.

 \item \emph{Signed fallback.}  If the uniform door is killed, retain the
 physical distinguished vector and estimate
 \begin{equation}
  -2\operatorname{Re}
    \langle A_X\zeta_*,M_X\zeta_*\rangle
  \label{eq:tpc60-next-signed-cross-term}
 \end{equation}
 using the exact base--missing and unequal-prime decomposition.  This is a
 legitimate narrower route, provided it is not relabeled uniform.
\end{enumerate}

The mass--degree route advances automatically at zero fixed-power cost when
its arithmetic saving strictly beats the degree plus all
represented-reference losses, as in
\eqref{eq:tpc60-common-reference-threshold}.  At equality, the finer test
\eqref{eq:tpc60-equality-subpower-test} decides whether this certificate
still closes at subpower cost.  If every provable lower bound already
spends the remaining \(1/400\) slack, the correct result is a route-closure
theorem, not an adjusted normalization.

\paragraph{Conclusion.}
TPC--59 exposed a high Walsh boundary omitted by the represented terminal
census.  The present paper closes the corresponding interface: it writes
the physical maps on one coefficient space, identifies the precise
same-prime simplification, eliminates invisible coefficient directions by
shorting the full Gram, and gives sharp kernel and mass--degree
certificates.  The route has therefore moved from an unspecified
\emph{off-carrier restoration} to a finite list of falsifiable arithmetic
tasks.  It has not crossed the parity barrier.
