\section{Endpoint audit and the reassembly ledger}
\label{sec:tpc60-endpoint-ledger}

The exact constants above identify the reassembly problem.  We now compare
the available coefficient-blind degree certificate with the endpoint
budget and state the admissible ways to close the new gate.

\subsection{Critical-cutoff exponent dictionary}

Assume that \(y\) is very-high admissible and write
\begin{equation}
 \frac yQ=X^{\xi+o(1)},
 \qquad 0\le\xi<\frac{133}{400}.
 \label{eq:tpc60-xi-cutoff}
\end{equation}
At \(\xi=0\), admissibility retains the constant-scale requirement
\(y\ge C_{\rm vh}Q\) for a sufficiently large support-dependent constant;
the exponent identity alone is not enough.  The displayed range is the one
in which a polynomially nonempty cofactor scale remains compatible.
The compatible cofactor ceiling is
\begin{equation}
 r\le\frac{N_+}{y}
 =X^{\theta_c(\xi)+o(1)},
 \qquad
 \theta_c(\xi):=\frac{133}{400}-\xi.
 \label{eq:tpc60-compatible-cofactor-ceiling}
\end{equation}
The inherited source-prime and divisor exponents are
\begin{equation}
 \lambda_L
 :=\frac{267}{400}-\frac{10049}{52500}
 =\frac{99979}{210000},
 \qquad
 \lambda_D:=\frac{10049}{52500}.
 \label{eq:tpc60-LD-exponents}
\end{equation}
Thus the residual label \(s=d_mr\) obeys
\begin{equation}
 s\le
 X^{\lambda_D+\theta_c(\xi)+o(1)}
 =X^{110021/210000-\xi+o(1)}.
 \label{eq:tpc60-residual-label-ceiling}
\end{equation}

Let \(R=X^{\theta_R+o(1)}\) be any compatible dyadic cofactor block, so
\begin{equation}
 0\le\theta_R\le\theta_c(\xi).
 \label{eq:tpc60-compatible-thetaR}
\end{equation}
The determinant-ladder estimate
\eqref{eq:tpc60-residual-degree-bound} supplies the coefficient-blind
capacity exponent
\begin{equation}
 \mu_{\rm cap}(R)
 :=\lambda_L-\theta_R.
 \label{eq:tpc60-capacity-exponent}
\end{equation}
It satisfies
\begin{equation}
 \boxed{
 \mu_{\rm cap}(R)
 \ge\frac{15077}{105000}+\xi,}
 \label{eq:tpc60-capacity-floor}
\end{equation}
and hence
\begin{equation}
 \boxed{
 \mu_{\rm cap}(R)-\frac1{400}
 \ge\frac{29629}{210000}+\xi.}
 \label{eq:tpc60-capacity-budget-gap}
\end{equation}
At the critical choice \(\xi=0\), the lower floor is approximately
\(0.143590\), whereas the entire endpoint allowance is \(0.0025\).

This calculation must be interpreted in the correct direction.
\(\mu_{\rm cap}\) is the exponent of an ambient \emph{upper} bound for a
fiber size; it is not a proved energy loss and does not say that actual
fibers attain that size.  It does show that a crude route which pays the
complete ambient degree through coloring, a coefficient-blind transversal,
or Cauchy--Schwarz cannot fit inside the \(1/400\) ledger.  That
support-only closure is therefore unavailable.  A successful argument must
use actual missing-mass sparsity, restricted-range geometry, or signed
phase information.

\subsection{Three admissible reassembly certificates}

The following routes preserve the physical coefficient vector and the
fixed shift.

\begin{enumerate}[leftmargin=2.3em]
 \item \emph{Shorted-Gram route.}  Prove directly that
 \begin{equation}
  \lambda_{\min}\left(
   R_S^{-1/2}Q R_S^{-1/2}
  \right)
  \ge X^{-\lambda_{\rm reasm}+o(1)}.
  \label{eq:tpc60-route-shorted-Gram}
 \end{equation}
 This is the optimal coefficient-uniform statement.  Before estimating an
 eigenvalue, apply the exact kernel and dimension kill tests.

 \item \emph{Signed distinguished-vector route.}  For the physical
 coefficient vector \(\zeta_*\), prove
 \begin{equation}
  \mathfrak X(\zeta_*)
  \ge-\left(1-X^{-\lambda_{\rm reasm,*}+o(1)}\right)
       \|A_X\zeta_*\|^2.
  \label{eq:tpc60-route-signed}
 \end{equation}
 This may remain open after the uniform gate is killed, but it cannot be
 promoted to a uniform claim.

 \item \emph{Mass--degree route.}  Prove a common-reference saving
 \(\sigma\), a represented loss \(\lambda_{\rm rep}\), and a native degree
 exponent \(\mu_{\rm miss}\) satisfying
 \begin{equation}
  \sigma>\mu_{\rm miss}+\lambda_{\rm rep}.
  \label{eq:tpc60-route-mass-degree}
 \end{equation}
 Then \cref{thm:tpc60-pointwise-mass-degree} yields
 \(\lambda_{\rm reasm}=0\) for a uniform scope, or
 \(\lambda_{\rm reasm,*}=0\) for the distinguished-vector scope.  At
 equality of exponents,
 finer constant or subpower control must verify
 \eqref{eq:tpc60-equality-subpower-test}; the exponent comparison alone is
 inconclusive.
\end{enumerate}

The angle certificate of
\cref{prop:tpc60-uniform-angle-certificate} is a fourth presentation of the
 signed route.  Orthogonal full represented-affine and missing output
 ranges, \(\Ran A\perp\Ran M\), give the
safe special case \(\delta(A,M)\ge1\), but the fixed-\(h_0\) maps here do
not currently satisfy such an orthogonality theorem.

\subsection{Complete ledger}

The prospective fixed-shift chain remains
\begin{equation}
 \begin{aligned}
 \cD_{\rm up}
 &\longrightarrow\cE_{\rm par}
 \longrightarrow\cE_{\cR}
 \longrightarrow\cD_{\cR}^{\rm term}
 \longrightarrow\cD_H^{\rm rep}
 \longrightarrow\cD_{k_*}\\
 &\longrightarrow\cG_H
 \longrightarrow\cN_H
 \longrightarrow\cN_{\rm aff}^{\rm rep}
 \xrightarrow{\rm reassembly}
 \cN_{\rm slice}^{\rm full}
 \xrightarrow{\rm boundary/tail}
 \text{parent arithmetic target}.
 \end{aligned}
 \label{eq:tpc60-full-transfer-chain}
\end{equation}
Every arrow is a different assertion.  TPC--60 replaces the displayed
reassembly arrow by the exact constant \(\delta(A_X,M_X)\); it does not
estimate that constant from below for the arithmetic family.

If all arrows eventually receive polynomial lower bounds, the energy loss
is
\begin{equation}
 \boxed{
 \begin{aligned}
 \Lambda_{\rm tot}:={}&
 \lambda_{\rm sel}+\lambda_{\rm occ}
 +\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm sing}\\
 &+\lambda_H+\lambda_{\rm aff}
 +\lambda_{\rm reasm}
 +\lambda_{\rm bdry}+\lambda_{\rm tail}.
 \end{aligned}}
 \label{eq:tpc60-complete-ledger}
\end{equation}
The endpoint requirement is the strict inequality
\begin{equation}
 \boxed{
 \Lambda_{\rm tot}<\frac1{400}.}
 \label{eq:tpc60-strict-endpoint}
\end{equation}
For a distinguished-vector chain, \(\lambda_{\rm reasm}\) in
\eqref{eq:tpc60-complete-ledger} is replaced consistently by
\(\lambda_{\rm reasm,*}\).  The two exponents are never interchanged: a
pointwise certificate cannot be entered as a uniform one.
Equality is rejected unless leading constants and all remainders are
quantified.  The cutoff \(y\asymp Q\) is a feasibility choice and is not an
additive energy loss.  TPC--59 proves
\(\lambda_{\rm blk}=0\) only after represented high-face activation and
with its distinguished-block scope.  The new identity
\(\lambda_{\rm part}=0\) is a diagnostic finite/logarithmic partition and
does not replace either reassembly exponent in its matching version of
\eqref{eq:tpc60-complete-ledger}.

\subsection{Stop rules}

The current route must stop or change scope under any of the following
events.
\begin{enumerate}[leftmargin=2.3em]
 \item A literal vector satisfies \(A_X\zeta\ne0\) and
       \(B_X\zeta=0\); then the uniform reassembly gate is exactly dead.
 \item An active row satisfies \(W_R(m)=0<W_H(m)\); then uniform
       represented raw-mass transfer is exactly zero.
 \item A necessary proved loss by itself reaches \(1/400\), or the sum of
       necessary losses reaches it without a constant-level endpoint
       argument.
 \item The only available proof pays the full ambient capacity exponent in
       \eqref{eq:tpc60-capacity-floor}; then that proof architecture exceeds
       the endpoint allowance even at the critical cutoff.
\end{enumerate}
None of these events may be repaired by changing \(h_0\), averaging shifts,
renormalizing atoms by their fiber sizes, deleting coefficient-dependent
zeros, or selecting represented and missing vectors independently.  Such
operations define different problems.
