\section{Introduction}
\label{sec:tpc60-introduction}

The large-prime branch of the TPC program begins with an exact Walsh
expansion, resolves a unique very-high prime, transports the resulting
atoms through residual fibers, and finally recombines them into the native
affine output at a fixed physical shift \(h_0\ne0\)
\citep{WangTPC45,WangTPC53,WangTPC57,WangTPC58}.  TPC--59 makes a necessary
correction to that chain.  Its largest-prime census injects the retained
terminal atoms into the high Walsh carrier, but it need not cover the full
carrier.  With the notation of that paper,
\begin{equation}
 \cD_0
 =\cD_{\rm base}+\cD_{\rm miss}
  +\cD_H^{\rm rep}.
 \label{eq:tpc60-inherited-three-part-diagonal}
\end{equation}
Here \(\cD_H^{\rm rep}\) is the represented high diagonal, while
\(\cD_{\rm miss}\) is high Walsh mass outside the terminal image
\citep{WangTPC59}.

This distinction survives the final grouping.  Let \(g_{\rm rep}\) be the
native affine vector built from the base column and the represented high
column, and let \(h_{\rm miss}\) be the output of the missing high
coordinates.  The full physical vector is
\begin{equation}
 g_{\rm full}=g_{\rm rep}+h_{\rm miss}.
 \label{eq:tpc60-full-sum-intro}
\end{equation}
There is no inequality
\(\|g_{\rm full}\|\ge\|g_{\rm rep}\|\): the omitted vector can be
destructively aligned.  Nor does small raw missing mass by itself solve the
problem, because many small missing atoms may enter one native output with
the same phase.

The purpose of this paper is to identify exactly what must be proved at
this reassembly arrow.  The answer contains a subtle quotient.  Two row
coefficient vectors may have the same represented output while having
different missing output.  Therefore the full map need not descend to the
quotient by the kernel of the represented map.  The correct uniform
constant minimizes over that entire kernel fiber.  In matrix language this
is a shorted operator, or equivalently a generalized Schur complement
\citep{AndersonTrapp1975,BenIsraelGreville2003}.

\subsection{The three questions}

Fix finite-dimensional Hilbert spaces \(\cK\) and \(\cH\), and linear maps
\begin{equation}
 A,M:\cK\longrightarrow\cH,
 \qquad B:=A+M.
 \label{eq:tpc60-abstract-maps-intro}
\end{equation}
The TPC specialization is:
\begin{itemize}[leftmargin=2em]
 \item \(A\) is the base plus represented-high affine map;
 \item \(M\) is the missing-high native grouping;
 \item \(B\) is the full declared affine output on the same fixed slice.
\end{itemize}
We answer three separate questions.

\begin{enumerate}[leftmargin=2.2em]
 \item What is the optimal coefficient-uniform ratio
 \begin{equation}
  \delta_{\rm reasm}
  :=\inf_{Az\ne0}\frac{\|Bz\|^2}{\|Az\|^2}?
  \label{eq:tpc60-delta-intro}
 \end{equation}
 \item What exact kernel, image, or rank condition kills that uniform gate?
 \item What arithmetic estimate on missing raw mass and native fiber degree
       is sufficient for a distinguished-vector or uniform lower transfer?
\end{enumerate}

These questions must not be conflated.  A distinguished physical vector
can reassemble safely even when the uniform constant vanishes.  Conversely,
the qualitative kernel condition can hold while the least ratio tends to
zero with \(X\).  Finally, a raw atomic estimate does not determine the
sign of the represented--missing cross term.

\subsection{Main results}

Let
\begin{equation}
 N:=\Ker A,
 \qquad S:=N^\perp,
 \qquad W:=B(N)=M(N),
 \label{eq:tpc60-NSW-intro}
\end{equation}
and let \(P_W^\perp\) denote the orthogonal projection onto \(W^\perp\).
The first result is the exact nuisance-elimination formula
\begin{equation}
 \boxed{
 \delta_{\rm reasm}
 =\inf_{s\in S\setminus\{0\}}
   \frac{\|P_W^\perp Bs\|^2}{\|As\|^2}.}
 \label{eq:tpc60-main-short-formula-intro}
\end{equation}
Thus the effective map is not \(B|_S\), but its projection away from the
output that can be generated freely by \(N\).  We derive the equivalent
shorted-Gram and least-singular-value formulas and prove
\begin{equation}
 \boxed{
 \delta_{\rm reasm}>0
 \quad\Longleftrightarrow\quad
 \Ker B\subseteq\Ker A.}
 \label{eq:tpc60-main-kernel-intro}
\end{equation}
The equivalence is finite-dimensional.  It is an exact L0 statement; it
does not assert the condition for the TPC coefficient family.

For the literal missing atomic lift, let \(\cF_i^{\rm miss}\) be the
missing atoms entering native output \(i\), and put
\begin{equation}
 d_{\rm miss}:=\max_i|\cF_i^{\rm miss}|,
 \qquad
 \cD_{\rm miss}(z)
 :=\sum_i\sum_{u\in\cF_i^{\rm miss}}|m_u(z)|^2.
 \label{eq:tpc60-degree-diagonal-intro}
\end{equation}
Then the grouping operator has squared norm \(d_{\rm miss}\), and hence
\begin{equation}
 \|Mz\|^2\le d_{\rm miss}\cD_{\rm miss}(z).
 \label{eq:tpc60-mass-degree-intro}
\end{equation}
Together with the reverse triangle inequality this gives the sharp
certificate
\begin{equation}
 \frac{\|Bz\|^2}{\|Az\|^2}
 \ge
 \left(
  1-\sqrt{\frac{d_{\rm miss}\cD_{\rm miss}(z)}{\|Az\|^2}}
 \right)_+^2.
 \label{eq:tpc60-pointwise-certificate-intro}
\end{equation}
We exhibit a family saturating the threshold: \(d_{\rm miss}=n\), raw
missing mass \(1/n\), and exact cancellation of a unit represented output.

\subsection{Claim boundary and route position}

The paper deliberately stops at the first honest boundary.
The shorted-Gram theorem, signed-defect identity, and mass--degree estimate
are L0.  Their construction from the complete high Walsh carrier,
the represented terminal image, and its complement at one fixed \(h_0\)
is L1.  No estimate here proves that the missing-mass saving exceeds the
fiber-degree cost, that the effective map is injective uniformly in \(X\),
or that the distinguished physical vector avoids cancellation.  Those are
new arithmetic gates.

Accordingly, no statement in this paper is an L2 parity advance.  In
particular, we prove neither a positive fixed-\(h_0\) prime-pair lower bound
nor an asymptotic for twin primes.  The value of the result is diagnostic:
it replaces an informal ``restore the omitted coordinates'' arrow by an
optimal constant, an exact zero test, and two quantitatively auditable
routes to positivity.
