\section{Kernel, anti-diagonal, and rank kill tests}
\label{sec:tpc60-kernel-tests}

The shorted formula gives an exact qualitative test at each finite scale.
It also shows why qualitative injectivity is weaker than the polynomial
lower bound needed by an endpoint argument.

\begin{theorem}[Exact positivity test]
\label{thm:tpc60-exact-positivity-test}
For finite-dimensional \(\cK,\cH\) and \(A\ne0\), the following are
equivalent:
\begin{enumerate}[label=\textup{\(\roman*\)},leftmargin=2.6em]
 \item \(\delta(A,M)>0\);
 \item \(PB_S:S\to W^\perp\) is injective;
 \item \(\Ker(A+M)\subseteq\Ker A\);
 \item there is no \(z\in\cK\) with \(Az\ne0\) and
       \((A+M)z=0\).
\end{enumerate}
\end{theorem}

\begin{proof}
By \cref{cor:tpc60-effective-singular-value}, positivity is equivalent to
injectivity of \(PB_S\) on \(S\).  If that map is not injective, there is
\(s\in S\setminus\{0\}\) with \(B_Ss\in W=\Ran B_N\).  Choose \(k\in N\)
so that \(B_Nk=-B_Ss\).  Then \(z=s+k\in\Ker B\), while
\(Az=A_Ss\ne0\).  Conversely, any \(z=s+k\in\Ker B\setminus\Ker A\)
has \(s\ne0\) and \(PB_Ss=-PB_Nk=0\).  This proves all equivalences.
\end{proof}

\begin{corollary}[Dimension kill criterion]
\label{cor:tpc60-dimension-kill}
If
\begin{equation}
 \dim S>\dim\cH-\rank B_N,
 \label{eq:tpc60-dimension-kill}
\end{equation}
then \(\delta(A,M)=0\).
\end{corollary}

\begin{proof}
The codomain \(W^\perp\) of \(PB_S\) has dimension
\(\dim\cH-\rank B_N\).  Under \eqref{eq:tpc60-dimension-kill}, that map
cannot be injective.
\end{proof}

For the TPC specialization this supplies a finite-scale kill test which can
be checked exactly from the literal matrices.  If it fires, no uniform
loss exponent \(\lambda_{\rm reasm}\) exists on the declared coefficient
class: the ratio is exactly zero, not merely poorly estimated.  If it does
not fire, no quantitative asymptotic lower bound follows automatically.

\subsection{The pair-image formulation}

Define the coupled represented--missing map
\begin{equation}
 J:\cK\longrightarrow\cH\oplus\cH,
 \qquad Jz:=(Az,Mz),
 \label{eq:tpc60-coupled-AM-map}
\end{equation}
and its actual feasible pair image
\begin{equation}
 \cF_{A,M}:=\Ran J.
 \label{eq:tpc60-feasible-pair-image}
\end{equation}
The physical sum map is
\begin{equation}
 D_+(g,h):=g+h.
 \label{eq:tpc60-pair-sum-map}
\end{equation}
When \(\cF_{A,M}\ne\{0\}\), put
\begin{equation}
 \delta_{\rm pair}
 :=\inf_{(g,h)\in\cF_{A,M}\setminus\{0\}}
   \frac{\|g+h\|^2}{\|g\|^2+\|h\|^2}.
 \label{eq:tpc60-pair-angle}
\end{equation}
Here \(\cF_{A,M}\) carries the norm inherited from the Hilbert direct sum
\(\cH\oplus\cH\).

\begin{proposition}[Anti-diagonal test]
\label{prop:tpc60-anti-diagonal-test}
One has
\begin{equation}
 \delta_{\rm pair}
 =\sigma_{\min}\!\left(D_+|_{\cF_{A,M}}\right)^2,
 \qquad 0\le\delta_{\rm pair}\le2,
 \label{eq:tpc60-pair-singular-value}
\end{equation}
and
\begin{align}
 \delta_{\rm pair}>0
 &\Longleftrightarrow
 \cF_{A,M}\cap\{(g,-g):g\in\cH\}=\{(0,0)\}
 \label{eq:tpc60-pair-antidiagonal}\\
 &\Longleftrightarrow
 \Ker(A+M)\subseteq\Ker A.
 \notag
\end{align}
Furthermore
\begin{equation}
 \boxed{\delta(A,M)\ge\delta_{\rm pair}.}
 \label{eq:tpc60-delta-ge-pair}
\end{equation}
\end{proposition}

\begin{proof}
The first identity is the Rayleigh quotient of \(D_+^*D_+\) on the actual
pair image.  Its kernel is the anti-diagonal.  If
\(Jz=(g,-g)\ne(0,0)\), then \(Bz=0\) and \(Az=g\ne0\); the converse is
immediate.  Finally, for \(Az\ne0\),
\[
 \frac{\|Bz\|^2}{\|Az\|^2}
 \ge
 \frac{\|Bz\|^2}{\|Az\|^2+\|Mz\|^2}
 \ge\delta_{\rm pair}.
\]
Taking the infimum proves \eqref{eq:tpc60-delta-ge-pair}.
\end{proof}

The pair formulation is often convenient for an exact matrix computation,
but it must use \(\Ran J\), not an independently chosen product of the
represented and missing ranges.  Enlarging the feasible set to
\(\Ran A\times\Ran M\) can manufacture an anti-diagonal pair which no
physical coefficient vector produces.

\subsection{Qualitative and quantitative separation}

\begin{example}[The kernel test has no quantitative content]
\label{ex:tpc60-kernel-no-quantitative}
Let \(A=I\) and \(M=-(1-\varepsilon)I\), where
\(0<\varepsilon<1\).  Then \(B=\varepsilon I\), so
\begin{equation}
 \Ker B=\Ker A=\{0\},
 \qquad
 \delta(A,M)=\varepsilon^2.
 \label{eq:tpc60-epsilon-example}
\end{equation}
The exact kernel test passes for every \(\varepsilon>0\), but the constant
can be arbitrarily small.  For an \(X\)-dependent family, injectivity at
each finite \(X\) does not imply a polynomial lower bound.
\end{example}

\begin{example}[Equal raw size, opposite reassembly]
\label{ex:tpc60-same-mass-opposite-phase}
Let \(A=I\) and \(M=\pm tI\), with \(t\ge0\).  In both cases
\begin{equation}
 \|Mz\|^2=t^2\|Az\|^2,
 \label{eq:tpc60-same-raw-mass}
\end{equation}
but
\begin{equation}
 \delta(A,tI)=(1+t)^2,
 \qquad
 \delta(A,-tI)=(1-t)^2.
 \label{eq:tpc60-opposite-phase-constants}
\end{equation}
Thus the missing norm alone cannot distinguish constructive from
destructive interference.
\end{example}

\begin{example}[Pointwise success does not imply a uniform gate]
\label{ex:tpc60-pointwise-not-uniform}
Return to \cref{ex:tpc60-naive-compression-fails}.  The distinguished
vector \(z_*=(1,0)\) satisfies
\begin{equation}
 \frac{\|Bz_*\|^2}{\|Az_*\|^2}=1,
 \label{eq:tpc60-distinguished-success-example}
\end{equation}
while the uniform constant is zero because \((1,-1)\) cancels exactly.
Any distinguished-vector claim must therefore remain explicitly labeled
as such.
\end{example}

\subsection{Scale-dependent interpretation}

For a family \((A_X,M_X)\), call \(\lambda_{\rm reasm}\ge0\) an admissible
uniform loss exponent if
\begin{equation}
 \delta(A_X,M_X)
 \ge X^{-\lambda_{\rm reasm}+o(1)}.
 \label{eq:tpc60-uniform-loss-exponent}
\end{equation}
If the exact kernel test fails along an unbounded sequence of scales, no
such finite exponent exists on that coefficient class.  If the test passes,
\eqref{eq:tpc60-uniform-loss-exponent} is still a separate quantitative
assertion.  For one distinguished physical vector \(\zeta_*(X)\), the
analogous ratio
\begin{equation}
 \delta_*(X)
 :=\frac{\|B_X\zeta_*(X)\|^2}{\|A_X\zeta_*(X)\|^2}
 \label{eq:tpc60-distinguished-ratio}
\end{equation}
is a different object and may remain positive after the uniform gate is
killed.
