\section{Exact certificate, logical status, and conclusion}
\label{sec:tpc26-certificate-scope}

The analytic estimates in this paper are symbolic.  A deterministic
finite certificate is included to audit the exact annular algebra,
gcd normalization, and rational ledger identities most vulnerable to
sign or boundary errors.

\subsection{Certificate}

The standard-library script

\begin{center}
 \texttt{experiments/tpc26\_certificate.py}
\end{center}

uses \texttt{fractions.Fraction} and formal prime-log vectors.  It
checks:

\begin{enumerate}[label=\textup{(\arabic*)}]
 \item the exact identity
 \(P_TP_T-P_SP_S\) against the raw annular joint lattice and both
 negative drift terms on finite symbolic prefix data;
 \item the partition of the raw annulus into the two mixed rectangles
 and the both-new square;
 \item the direct finite both-new zero kernel against the
 \((g,c,d)\) normal form in \cref{lem:tpc26-both-new-gcd};
 \item the coefficient identity
 \eqref{eq:tpc26-agd-split} as an equality of formal logarithm vectors;
 \item CRT compatibility and the joint zero density
 \([u,v]^{-1}\one_{(u,v)\mid m-n}\) on finite primitive examples;
 \item the sharp minimax regional witnesses and boundary continuity on
 an exact rational grid;
 \item the strict \(1/100\) passage sample; and
 \item every source, support, row, and conductor margin in the
 \(\beta>2/3\) sample, including the saving \(33/8000\).
\end{enumerate}

Independent ordinary and \texttt{python -O} runs are required to
perform the same exact checks and generate byte-identical JSON.  The
repository README records the final JSON, source, and certificate
hashes after the source audit.  The archived JSON carries false flags
for full residual closure, positivity, a Hardy--Littlewood asymptotic,
twin primes, and a general parity breakthrough.

The certificate does not test the classical zero-free region, the
primitive multiplicative large sieve, any asymptotic M\"obius
cancellation, or the truth of a prime-pair conjecture.  It is regression
control for finite algebra and rational exponent arithmetic.

\subsection{What is proved directly and what is inherited}

The following parts are finite or elementary within the stated
physical packet:

\begin{enumerate}[label=\textup{(\roman*)}]
 \item the calibrated prefix identity and exact annular recombination;
 \item the both-new gcd normal form;
 \item the division of the physical annular zero mode into mixed,
 transpose, both-new, and two single-density drift terms;
 \item the physical \(O(Q^2)\) absolute row-pair mass once the
 TPC-25 provenance lemma is imported;
 \item the symmetric pairwise character coordinates; and
 \item the exact relaxed-box minimax and the two rational samples.
\end{enumerate}

The pointwise small-\(g\) zero estimate imports the uniform M\"obius
calibration proved in TPC-24 from the classical zero-free region.  The
nonzero spectrum imports the exact-conductor large-sieve mechanism of
TPC-22--24.  The smooth transfer and row norms import the physical
provenance established in TPC-25.  No conjectural Chowla or Elliott
input is used in the cutoff theorem.

The role of the present paper is to prove that those inherited tools
remain compatible after the three new support regions are first
recombined into one annular joint object, and to optimize their
symmetric conductor ledger exactly.

\subsection{Status table}

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.42\textwidth}
                >{\raggedright\arraybackslash}p{0.47\textwidth}}
\toprule
Object & Status after this paper\\
\midrule
Both-new physical zero mode on \((S,T]^2\)
& Closed with arbitrary logarithmic saving by endpoint calibration,
  determinant divisibility, and actual \(O(Q^2)\) row mass.\\
\addlinespace
Raw annular joint nonzero spectrum
& Closed with fixed-power saving whenever \(M_\beta(t)>0\).\\
\addlinespace
Physical cutoff difference
\(\cQ_T^{\rm phys}-\cQ_S^{\rm phys}\)
& Closed with arbitrary logarithmic saving when \(s>0\),
  \(M_\beta(t)>0\), and all inherited interfaces hold with fixed
  margins.\\
\addlinespace
Selected calibrated square through \(T>J\)
& Closed only when the matching \(S\)-cutoff base estimate is also
  available.\\
\addlinespace
High-\(\beta\) sample with \(\beta>2/3\)
& Annular cutoff stability proved inside actual opened-row geometry;
  no base-square closure imported.\\
\addlinespace
Ultra-long \((T,U]\) complement
& Not estimated; exact affine two-point M\"obius fibers remain.\\
\addlinespace
Full TPC-18 residual and endpoint reassembly
& Not proved.\\
\addlinespace
Hardy--Littlewood, positivity, twin primes, or general parity breach
& Not claimed and not implied.\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Conclusion}

The both-new square is not blocked by the principal row mode found in
TPC-25.  That mode arose when a shell coefficient was frozen before
its full endpoint structure was used.  In the complete annulus the
small-\(g\) main constants cancel, and the large-\(g\) layers are sparse
divisors of the nonzero row determinant.

The successful order is

\begin{equation}
 \boxed{
 \begin{gathered}
 \text{form the quadratic cutoff difference}
 \ \longrightarrow\
 \text{recombine the entire raw annulus}\\
 \longrightarrow\
 \text{extract physical zero}
 \ \longrightarrow\
 \text{separate and resolve only the nonzero spectrum}.
 \end{gathered}}
 \label{eq:tpc26-order}
\end{equation}

This closes a real missing component.  Conditional on an independent
matching calibrated base estimate, it pushes the whole selected
truncated square through an upper cutoff \(T>J\); that base estimate is
not supplied here.  The exact minimax also shows that the annular
conductor mechanism itself survives beyond \(\beta=2/3\), though that
fact must not be transferred automatically to the base square or the
complete residual.

The next wall is qualitatively different.  Divisor reflection in the
ultra-long complement places two growing affine M\"obius signs on the
same short fiber.  A future advance must obtain polynomially uniform
two-point cancellation, exploit sparse incidence after summing the
family, or find another exact recombination.  Success would close one
more analytic residual block; it would still not by itself produce a
positive prime-pair main term.
