\section{Physical cutoff stability and truncated-square closure}
\label{sec:tpc26-cutoff-stability}

We now combine the exact annular identity, physical zero theorem, and
sharp nonzero conductor ledger.

\subsection{The nonzero physical packet}

Let

\[
 (\cQ_T^{\rm phys}-\cQ_S^{\rm phys})^{\ne0}
\]

denote the sum of all nonzero additive frequencies of the raw annular
joint lattice in \eqref{eq:tpc26-annular-identity}, after the two drift
terms have been set aside.

\begin{theorem}[Nonzero annular conductor theorem]
\label{thm:tpc26-nonzero-annulus}
Assume the primitive physical interface of
\cref{sec:tpc26-interface-recombination}, the divisor-independent
off-diagonal mask, the no-wrap margin \eqref{eq:tpc26-no-wrap}, and
fixed-power support \(T\le X^{C_T}\).  Write
\[
 Q=X^{\beta+o(1)},\qquad
 T=X^{t+o(1)},\qquad
 \frac12\le\beta<1,
\]
with \(1-\beta\) bounded below by a fixed positive margin, and suppose

\begin{equation}
 M_\beta(t)>0
 \label{eq:tpc26-positive-ledger}
\end{equation}

with a fixed margin.  Then there is a fixed \(\eta>0\) such that

\begin{equation}
 \boxed{
 |(\cQ_T^{\rm phys}-\cQ_S^{\rm phys})^{\ne0}|
 \ll_{\mathscr D}XQX^{-\eta}.}
 \label{eq:tpc26-nonzero-bound}
\end{equation}

One may take any sufficiently small fixed \(\eta\) below the conductor
margin \(M_\beta(t)\) and the principal-mean margin \(1-\beta\), after
the auxiliary \(X^\eps\) losses are chosen.
\end{theorem}

\begin{proof}
For one Mellin component, decompose the nonprincipal spectrum into
dyadic denominator and coordinate-conductor cells.  Apply
\cref{thm:tpc26-cell-bound} to each cell and
\cref{prop:tpc26-sharp-minimax} to its exponents.  The fixed positive
margin absorbs the logarithmically many cells and the row-energy
factor in \eqref{eq:tpc26-transfer-l2}.  The global principal cell is
\eqref{eq:tpc26-principal-mean}, which is below \(XQ=Q^2J\) by the
fixed power \(J=X^{1-\beta+o(1)}\).  The physical Fourier tail is
arbitrarily power-saving by \cref{lem:tpc26-automatic-tail}.  Finally,
integrate the Mellin components using the weighted moments in
\cref{lem:tpc26-physical-transfer}.  The fixed \(H_0\)-residue cells
change only the implied constant.
\end{proof}

\subsection{Main cutoff theorem}

We use the fixed-data convention \(\mathscr D\) introduced in
\cref{sec:tpc26-interface-recombination}.

\begin{theorem}[Physical annular cutoff stability]
\label{thm:tpc26-cutoff-stability}
Retain the hypotheses of \cref{thm:tpc26-nonzero-annulus}.  Assume

\begin{equation}
 S=X^{s+o(1)},
 \qquad s>0,
 \qquad
 M_\beta(t)>0
 \label{eq:tpc26-main-hypotheses}
\end{equation}

with fixed margins.  Then, for every fixed \(B>0\),

\begin{equation}
 \boxed{
 \cQ_T^{\rm phys}-\cQ_S^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}.}
 \label{eq:tpc26-cutoff-stability}
\end{equation}

The same theorem applies to a finite bounded-overlap reassembly of
physical dyadic, content, sign, and fixed-residue cells; its fixed
polylogarithmic cost is absorbed by choosing the zero-mode calibration
exponent afterward.
\end{theorem}

\begin{proof}
Use \cref{prop:tpc26-annular-identity}.  The nonzero raw annular joint
term has a fixed-power saving by
\cref{thm:tpc26-nonzero-annulus}.  The physical zero contribution
together with the two separately bounded full drifts has arbitrary
logarithmic saving by \cref{cor:tpc26-zero-log-saving}.  A fixed-power
saving is smaller than any
prescribed negative power of \(\log X\) for sufficiently large \(X\),
which proves \eqref{eq:tpc26-cutoff-stability}.  Finite cell reassembly
costs only a fixed power of \(\log X\).
\end{proof}

\begin{remark}[What the theorem closes]
\label{rem:tpc26-cutoff-vs-value}
The theorem controls a cutoff difference.  It does not estimate
\(\cQ_S^{\rm phys}\) and therefore does not by itself estimate
\(\cQ_T^{\rm phys}\).  This distinction is essential in the
high-\(\beta\) sample \eqref{eq:tpc26-high-sample}, where both \(S\)
and \(T\) exceed \(J\).
\end{remark}

\begin{corollary}[Selected truncated-square closure]
\label{cor:tpc26-truncated-square}
In addition to the hypotheses of
\cref{thm:tpc26-cutoff-stability}, suppose the same physical
\(S\)-cutoff packet satisfies

\begin{equation}
 \cQ_S^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}
 \label{eq:tpc26-base-input}
\end{equation}

for every fixed \(B>0\).  Then

\begin{equation}
 \boxed{
 \cQ_T^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}.}
 \label{eq:tpc26-truncated-square}
\end{equation}

The estimate \eqref{eq:tpc26-base-input} is an independent calibrated
base input.  TPC-22--23 provide centered selected-square estimates, but
the scalar terms required to pass from those centered packets to the
present \(P_{m,S}P_{n,S}\) packet are not proved in this paper.
Accordingly, this corollary is conditional even in the strict sample
\eqref{eq:tpc26-old-sample}.
\end{corollary}

\begin{proof}
Apply the triangle inequality to

\[
 \cQ_T^{\rm phys}
 =\cQ_S^{\rm phys}
 +(\cQ_T^{\rm phys}-\cQ_S^{\rm phys})
\]

and use \eqref{eq:tpc26-base-input} and
\eqref{eq:tpc26-cutoff-stability}.
\end{proof}

\begin{corollary}[Vanishing physical zero functional]
\label{cor:tpc26-zero-free-test}
If
\[
 \vartheta_{H_0}(\alpha,\gamma)
 \widehat{\cW}_{\alpha,\gamma}(0)=0
\]
for every retained row pair and residue cell, then the raw annular
physical zero term vanishes.  The separately bounded full drifts remain.
Under the same conductor hypotheses, some fixed \(\eta'>0\) satisfies

\begin{equation}
 \cQ_T^{\rm phys}-\cQ_S^{\rm phys}
 \ll XQX^{-\eta'}.
 \label{eq:tpc26-power-saving-test}
\end{equation}
\end{corollary}

This last statement is optional extra cancellation.  The main theorem
does not assume it.

\subsection{The next analytic wall}

Let \(U\asymp X\) contain the complete target support.  The theorem
does not estimate

\begin{equation}
 L_{m;T,U}
 =\sum_{\substack{T<u\le U\\u\mid mj+h}}a(u).
 \label{eq:tpc26-ultra-long}
\end{equation}

TPC-23 reflects a divisor \(u>T\) to a complement \(r<(mj+h)/T\).
For fixed complement divisors \(r,s\), the two quotient variables are
affine forms whose determinant is

\begin{equation}
 \frac{h(m-n)}{(r,s)}\ne0.
 \label{eq:tpc26-affine-determinant}
\end{equation}

The remaining coefficient is a two-point product of M\"obius signs.
Taking absolute values already has natural-scale mass on the unit
complement fiber, while the known logarithmically averaged fixed-form
theorem has neither the required polynomial uniformity nor the sharp
dyadic averaging \citep{Tao2016,WangTPC23}.  Continuing beyond \(T\)
therefore requires a uniform affine-M\"obius dispersion theorem, a
sparse incidence theorem, or a new exact recombination.  It is not a
formal consequence of \cref{thm:tpc26-cutoff-stability}.
