\section{Introduction}
\label{sec:tpc26-introduction}

The primitive M\"obius-tail program of TPC-18--25 reorganizes a
fixed-shift prime-pair residual into dyadic opened rows

\[
 m=\ell d,
 \qquad \ell\asymp L\text{ prime},
 \qquad d\asymp D,
 \qquad Q=LD,
 \qquad QJ\asymp X.
\]

TPC-18 isolates the generic off-diagonal row correlation, TPC-19--20
derive its exact divisor and joint-Poisson normal forms, TPC-21 closes
the Ramanujan mean, and TPC-22--23 control a selected square of divisor
coordinates by exact-conductor large-sieve estimates
\citep{WangTPC18,WangTPC19,WangTPC20,WangTPC21,WangTPC22,WangTPC23}.
TPC-24 then lets one new divisor leg pass beyond the old Poisson length,
and TPC-25 removes the remaining projective-mass hypothesis for the
actual opened-\(d\) packet by extracting physical frequency zero before
smooth row--orbit separation \citep{WangTPC24,WangTPC25}.

The object left between those results is elementary to state.  For a
calibrated residual prefix \(P_{m,W}\), put

\begin{equation}
 L_{m;S,T}=P_{m,T}-P_{m,S},
 \qquad R\le S<T.
 \label{eq:tpc26-intro-L}
\end{equation}

The quadratic cutoff difference expands as

\begin{align}
 P_{m,T}P_{n,T}-P_{m,S}P_{n,S}
 ={}&P_{m,S}L_{n;S,T}
 +L_{m;S,T}P_{n,S}
 +L_{m;S,T}L_{n;S,T}.
 \label{eq:tpc26-intro-three-pieces}
\end{align}

The first two pieces are the one-sided increments of TPC-24--25.  The
third is the both-new square.  Estimating the three terms separately,
however, hides a more useful exact identity.  The present paper first
recombines the whole left side of
\eqref{eq:tpc26-intro-three-pieces}, before either divisor leg is
centered, Mellin-separated, or sent through a Fourier channel.

\subsection{Joint before separation}

Let

\[
 a(u)=-\mu(u)\log u,
 \qquad b_R(u)=a(u)-\lambda'_R(u),
 \qquad \lambda'_R(u)=0\quad(u>R).
\]

The calibrated prefix identity of TPC-24 is

\begin{equation}
 P_{m,W}(j)=
 \sum_{\substack{u\le W\\u\mid mj+h}}b_R(u)-\delta_H(m).
 \label{eq:tpc26-intro-prefix}
\end{equation}

Because \(S\ge R\), every new coefficient is \(b_R(u)=a(u)\).  Direct
subtraction gives

\begin{align}
 &P_{m,T}(j)P_{n,T}(j)-P_{m,S}(j)P_{n,S}(j)
 \notag\\
 &\quad=
 \sum_{\substack{u,v\le T\\\max\{u,v\}>S}}
 b_R(u)b_R(v)
 \one_{u\mid mj+h}\one_{v\mid nj+h}
 \notag\\
 &\qquad\quad
 -\delta_H(m)L_{n;S,T}(j)
 -\delta_H(n)L_{m;S,T}(j).
 \label{eq:tpc26-intro-annular-identity}
\end{align}

The first term is one raw joint lattice on the annulus

\[
 \{(u,v):u,v\le T,\ \max\{u,v\}>S\}.
\]

It contains both mixed orientations and the both-new square.  More
importantly, it contains no single-indicator Poisson channel.  The two
remaining terms are explicit row drifts, smaller by \(L^{-1}\) on the
physical packet.  This order of operations is the structural reason
that the nonzero spectrum may be treated with a symmetric conductor
box even when \(T>J\).

\subsection{The new zero-mode theorem}

The mixed parts of the annulus inherit the pointwise shell theorem of
TPC-24.  For the new shell--shell corner, the zero kernel is

\begin{equation}
 K^{\square,0}_{S,T}(m,n)
 =
 \sum_{\substack{S<u,v\le T\\
                  (u,mH)=(v,nH)=1}}
 \frac{a(u)a(v)}{[u,v]}
 \one_{(u,v)\mid m-n}.
 \label{eq:tpc26-intro-square-zero}
\end{equation}

Writing \(g=(u,v)\), \(u=gc\), and \(v=gd\) makes
\((g,c,d)\) pairwise coprime on the squarefree support.  If
\(g\le SX^{-\kappa}\), the innermost \(d\)-sum is the difference of
two complete M\"obius calibrations at \(T/g\) and \(S/g\); their common
main constant cancels.  If \(g>SX^{-\kappa}\), the off-diagonal
condition gives \(g\mid m-n\ne0\).  We obtain

\begin{equation}
 \boxed{
 K^{\square,0}_{S,T}(m,n)
 \ll_{A,\kappa}
 (\log X)^{-A}+X^{-s+\kappa+o(1)}}
 \label{eq:tpc26-intro-zero-bound}
\end{equation}

for \(S=X^{s+o(1)}\), every fixed \(A>0\), and every
\(0<\kappa<s\).  TPC-25 proves that the actual prime--M\"obius row
coefficients have \(O(Q^2)\) absolute pair mass before smooth
separation.  Consequently \eqref{eq:tpc26-intro-zero-bound} closes the
physical annular zero mode without a mean-zero test, a row-balance
hypothesis, or a new projective norm.

\subsection{A sharp symmetric conductor ledger}

At nonzero additive frequency the annular restriction only reduces the
nonnegative conductor energy.  Enlarge it to \(u,v\le T\), resolve the
two exact coordinate conductors, and combine the restricted-frequency
norm route with the induced-Gauss route.  Write

\begin{equation}
 Q=X^{\beta+o(1)},\qquad J=X^{1-\beta+o(1)},
 \qquad T=X^{t+o(1)}.
 \label{eq:tpc26-intro-exponents}
\end{equation}

For a denominator cell \(Y=X^{y+o(1)}\) and conductor cells
\(F_i=X^{f_i+o(1)}\), put

\[
 k_i=\max\{f_i,\beta-f_i\}.
\]

The two saving exponents are

\begin{equation}
 \eta_A=\frac{\beta+1-y-k_1-k_2}{2},
 \qquad
 \eta_B=1-f_1-f_2-\frac{k_1+k_2}{2}.
 \label{eq:tpc26-intro-etaAB}
\end{equation}

Here \(y\le2t\) and \(0\le f_i\le t\).  We compute the exact relaxed-
box minimax

\begin{equation}
 M_\beta(t)=
 \inf_{0\le f_1,f_2\le t}
 \max\{\eta_A(2t,f_1,f_2),\eta_B(f_1,f_2)\}.
 \label{eq:tpc26-intro-minimax}
\end{equation}

For \(1/2\le\beta<1\), it is the continuous piecewise-linear
function

\begin{equation}
 M_\beta(t)=
 \begin{cases}
 1-\beta-t,
 &0\le t\le(1-\beta)/2,\\[2pt]
 \dfrac{3-3\beta-2t}{4},
 &(1-\beta)/2\le t\le\beta/2,\\[5pt]
 \dfrac{3-\beta-6t}{4},
 &\beta/2\le t\le(3\beta-1)/2,\\[5pt]
 \dfrac{\beta+1-4t}{2},
 &t\ge(3\beta-1)/2.
 \end{cases}
 \label{eq:tpc26-intro-sharp-ledger}
\end{equation}

The previous low--low lower bound \(1-3\beta/2\) is not an exact
minimax face when \(t<\beta/2\).  In the region \(t>1-\beta\), some
positive interval survives for every

\begin{equation}
 \frac35<\beta<1.
 \label{eq:tpc26-intro-beta-range}
\end{equation}

This is a statement about the annular conductor problem, not about the
base square or the complete residual.  The equality witnesses in the
relaxed box need not all occur arithmetically; the minimax remains a
valid sufficient bound because the arithmetic cells form a subset.

\subsection{Main consequence and exact scope}

Let \(\mathcal Q_W^{\rm phys}\) be the selected physical quadratic
packet formed with \(P_{m,W}P_{n,W}\), the same row family, the same
smooth orbit weight, and the same divisor-independent off-diagonal mask
at both cutoffs.  Under the primitive opened-row interfaces and fixed
positive margins, the main theorem gives

\begin{equation}
 \boxed{
 \mathcal Q_T^{\rm phys}-\mathcal Q_S^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}}
 \label{eq:tpc26-intro-main}
\end{equation}

for every fixed \(B>0\), whenever \(M_\beta(t)>0\).  Here
\(\mathscr D\) denotes the fixed shift, residue, smoothness, no-wrap,
and source data.  The smooth Fourier tail is proved negligible for the
actual provenance rather than retained as an independent packet
hypothesis.

If an independent matching calibrated \(S\)-cutoff estimate is
available, \eqref{eq:tpc26-intro-main} closes the selected calibrated
square through \(T\).  This implication is stated separately: cutoff
stability alone does not estimate its initial value, and the scalar
reassembly from the earlier centered base packet is not proved here.

The first rational sample satisfies \(S<J<T\) and has conductor saving
\(1/100\).  A second sample has \(\beta=267/400>2/3\) and saving
\(33/8000\).  It lies inside the published opened-\(d\) row geometry,
but both annular endpoints are already beyond \(J\), so it establishes
only beyond-face cutoff stability.

Nothing in the paper estimates \(L_{\cdot;T,U}\), the ultra-long
complement identified in TPC-23.  That complement consists of growing
two-point affine M\"obius fibers; known fixed-form logarithmic results
do not supply the required polynomially uniform rate
\citep{Tao2016,WangTPC23}.  Global endpoint reassembly, positivity,
the prime-pair main term, Hardy--Littlewood, twin primes, and a general
breach of the parity barrier therefore remain outside the conclusion.
