\section{Physical zero before separation}
\label{sec:tpc26-physical-zero}

We now insert the arithmetic kernel into the actual opened-\(d\)
packet.  The order matters: physical additive frequency zero is taken
while the row-dependent orbit weight is still one bounded smooth
function.

\subsection{The fixed local factor}

Because every effective joint modulus is coprime to \(H_0=|h|\), the
fixed periodic factor may be split into finitely many residue cells.
For one row pair define its zero-frequency local average by

\begin{equation}
 \vartheta_{H_0}(\alpha,\gamma)
 =\frac1{H_0}
 \sum_{\substack{r\bmod H_0\\(r,H)=1}}
 \Xi_{\alpha,\gamma}(r).
 \label{eq:tpc26-local-average}
\end{equation}

It is uniformly bounded.  The zero Fourier functional of the smooth
orbit amplitude is

\begin{equation}
 \widehat{\cW}_{\alpha,\gamma}(0)
 =\int_{\R}\cW_{\alpha,\gamma}(t)\,dt,
 \qquad
 \sup_{\alpha,\gamma}
 |\widehat{\cW}_{\alpha,\gamma}(0)|\ll1.
 \label{eq:tpc26-row-zero-integral}
\end{equation}

Thus, for one row pair, the raw annular zero contribution has the
explicit form

\begin{equation}
 J\,\vartheta_{H_0}(\alpha,\gamma)
 \widehat{\cW}_{\alpha,\gamma}(0)
 K^{\rm ann,0}_{S,T}(m_\alpha,m_\gamma).
 \label{eq:tpc26-one-pair-physical-zero}
\end{equation}

All factors preceding the kernel are uniformly bounded.  When
\(\Xi\equiv1\), the local average reduces to the familiar fixed
primitive density; the proof does not require that special case.

\subsection{The provenance-weighted theorem}

Let \(\cZ^{\rm ann,0}_{S,T}\) denote the physical zero-frequency
contribution of the raw annular joint lattice in
\eqref{eq:tpc26-annular-identity}, including the local factor
\eqref{eq:tpc26-local-average}, but excluding the two separately
displayed drift terms.

\begin{theorem}[Physical annular zero theorem]
\label{thm:tpc26-physical-zero}
Retain the physical provenance
\eqref{eq:tpc26-row-provenance}, the off-diagonal mask
\eqref{eq:tpc26-mask}, and the hypotheses of
\cref{thm:tpc26-both-new-zero}.  Then, for every fixed \(A>0\) and
\(0<\kappa<s\),

\begin{equation}
 \boxed{
 |\cZ^{\rm ann,0}_{S,T}|
 \ll_{A,\kappa,\mathscr D}
 JQ^2\left\{
 (\log X)^{-A}+X^{-s+\kappa+o(1)}
 \right\}.}
 \label{eq:tpc26-physical-zero-bound}
\end{equation}

After the zero contribution is combined with the two separately
bounded \emph{full} drift contributions,

\begin{equation}
 |\cZ^{\rm cutoff,0}_{S,T}|
 \ll
 JQ^2\left\{
 (\log X)^{-A}+X^{-s+\kappa+o(1)}
 +L^{-1}X^\eps
 \right\}.
 \label{eq:tpc26-full-zero-bound}
\end{equation}
\end{theorem}

\begin{proof}
By \cref{cor:tpc26-annular-raw-zero}, each retained row pair has raw
zero kernel bounded by the braces in
\eqref{eq:tpc26-physical-zero-bound}.  Delete the bounded mask and the
bounded local and smooth zero factors.  The actual row provenance gives

\[
 \sum_{\alpha,\gamma}
 |\gamma_\alpha^{(1)}\gamma_\gamma^{(2)}
 \mathfrak m(\alpha,\gamma)|
 \le
 \left(\sum_\alpha|\gamma_\alpha^{(1)}|\right)
 \left(\sum_\gamma|\gamma_\gamma^{(2)}|\right)
 \ll Q^2
\]

by \eqref{eq:tpc26-row-l1}.  Multiplication by the orbit length \(J\)
proves the first assertion.  The second follows from
\cref{lem:tpc26-drift-bound}.
\end{proof}

\begin{corollary}[Arbitrary logarithmic zero saving]
\label{cor:tpc26-zero-log-saving}
Assume \(s>0\) and \(\lambda_0>0\) with fixed margins.  For every fixed
\(B>0\), choose \(\kappa<s\), the auxiliary \(\eps<\lambda_0\), and
then the calibration exponent \(A\).  Since \(JQ^2\asymp XQ\),

\begin{equation}
 \boxed{
 \cZ^{\rm cutoff,0}_{S,T}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}.}
 \label{eq:tpc26-zero-log-saving}
\end{equation}
\end{corollary}

No mean-zero condition is imposed on the fixed physical test.  The
conclusion is a provenance theorem for the actual opened-\(d\) packet;
it is not inferred from the abstract soft row-energy bound alone.

\subsection{Transfer to the nonzero interface}

Only after the zero frequency is removed do we separate the smooth
row--orbit factors.  First split the fixed periodic multiplier into its
\(O_h(1)\) residue cells:

\begin{equation}
 \Xi_{\alpha,\gamma}(j)
 =\sum_{\varrho\bmod H_0}
 \Xi_{\alpha,\gamma}(\varrho)
 \one_{j\equiv\varrho\pmod{H_0}}.
 \label{eq:tpc26-fixed-residue-split}
\end{equation}

On a fixed cell, the bounded row-pair coefficient
\(\Xi_{\alpha,\gamma}(\varrho)\) is absorbed into the generic mask.
It remains divisor-independent, bounded, and supported off the row
diagonal.  The extra congruence changes the Poisson period by only the
fixed factor \(H_0\), and hence changes none of the conductor exponents.
The following is the precise form of the TPC-25 transfer lemma needed
below.

\begin{lemma}[Continuous physical transfer]
\label{lem:tpc26-physical-transfer}
For every fixed residue cell \(\varrho\bmod H_0\), the physical
coefficient--weight product has the continuous projective
representation

\begin{equation}
 \gamma_\alpha^{(1)}\gamma_\gamma^{(2)}
 \cW_{\alpha,\gamma}(j/J)
 =
 \int_{\R^4}
 x_{\boldsymbol\tau}(\alpha)
 y_{\boldsymbol\tau}(\gamma)
 \Phi_{\boldsymbol\tau}(j/J)
 \,d\nu(\boldsymbol\tau).
 \label{eq:tpc26-continuous-transfer}
\end{equation}

For every fixed integer \(M\ge0\), it may be chosen so that

\begin{align}
 \int_{\R^4}(1+|\boldsymbol\tau|)^M
 \|x_{\boldsymbol\tau}\|_2
 \|y_{\boldsymbol\tau}\|_2
 \,d|\nu|(\boldsymbol\tau)
 &\ll_M Q\log(2L),
 \label{eq:tpc26-transfer-l2}\\
 \int_{\R^4}(1+|\boldsymbol\tau|)^M
 \|x_{\boldsymbol\tau}\|_1
 \|y_{\boldsymbol\tau}\|_1
 \,d|\nu|(\boldsymbol\tau)
 &\ll_M Q^2.
 \label{eq:tpc26-transfer-l1}
\end{align}

The row scales, target primitivity, and divisor-independent generic mask
are unchanged.  Every fixed orbit seminorm grows at most polynomially
in \(\boldsymbol\tau\), and summing the \(O_h(1)\) residue cells followed
by dominated convergence restores the original physical packet after
componentwise estimates.
\end{lemma}

\begin{proof}
Mellin inversion separates each fixed smooth factor depending on
\(m_\alpha j/X\), on the normalized opened-divisor argument
\((d/D)(j/J)\), or on the corresponding second-row variables.
Unit-modulus Mellin phases do not change the row norms
\eqref{eq:tpc26-row-l2}.  Schwartz decay gives every weighted moment of
the Mellin measure.  The \(\ell^1\) statement is
\eqref{eq:tpc26-row-l1} before integration.  Differentiating the orbit
phases produces a polynomial in \(\boldsymbol\tau\), which is absorbed
by a higher Schwartz moment.  The generic mask depends only on the row
pair and therefore remains outside the integral.  These are precisely
the transfer steps established for the same physical provenance in
TPC-25 \citep{WangTPC25}.
\end{proof}

\begin{lemma}[The physical Fourier tail is automatic]
\label{lem:tpc26-automatic-tail}
Fix \(0<\omega<\eps_0\), where the no-wrap margin below is
\(J\ge4HX^{\eps_0}\).  For every prescribed \(A>0\), repeated
integration by parts in the fixed smooth orbit weight makes the total
annular frequency range

\begin{equation}
 |r|>X^\omega Hq/J
 \label{eq:tpc26-tail-range}
\end{equation}

contribute \(O_{A,\mathscr D}(X^{-A}Q^2)\) after all row, divisor,
fixed-residue, and Mellin integrations.
\end{lemma}

\begin{proof}
Work first with one residue cell and one Mellin component.  For a
squarefree pair \((u,v)\) in the annulus, put \(q=[u,v]\), and let
\(Z_{u,v;\boldsymbol\tau}(\xi)\) be its unweighted row fiber on the
joint unit class \(\xi\bmod q\).  Thus

\begin{equation}
 \sum_{\xi\in\cU_q}
 |Z_{u,v;\boldsymbol\tau}(\xi)|
 \le
 \|x_{\boldsymbol\tau}\|_1
 \|y_{\boldsymbol\tau}\|_1,
 \label{eq:tpc26-tail-row-fiber-mass}
\end{equation}

because the bounded row-pair mask only deletes or attenuates terms.
After the fixed \(H_0\)-cell is imposed, the Poisson formula has the
same shape as the primitive formula, with its fixed modulus changed by
an \(O_h(1)\) factor.  We use the normalization \(Hq\) below; replacing
\(H\) by that fixed modulus changes only the implied constant.

The absolute tail functional for this Mellin component is bounded by

\begin{align}
 \mathscr T^{\rm ann}_{\omega}(\boldsymbol\tau)
 :={}&
 \sum_{\substack{u,v\le T\\\max\{u,v\}>S}}
 |b_R(u)b_R(v)|\frac{J}{Hq}
 \sum_{|r|>X^\omega Hq/J}|c_H(r)|
 \left|
 \widehat\Phi_{\boldsymbol\tau}
 \left(\frac{rJ}{Hq}\right)
 \right|
 \notag\\
 &\hspace{9em}\times
 \sum_{\xi\in\cU_q}
 |Z_{u,v;\boldsymbol\tau}(\xi)|.
 \label{eq:tpc26-physical-tail-functional}
\end{align}

This pairwise majorant also dominates a tail formed after lcm or
conductor aggregation, by the triangle inequality.  For every
\(N\ge2\), the Fourier transforms in the physical smooth family satisfy

\[
 |\widehat\Phi_{\boldsymbol\tau}(y)|
 \ll_N(1+|\boldsymbol\tau|)^N(1+|y|)^{-N}.
\]

Write \(a_q=J/(Hq)\).  An integral comparison, with the first lattice
point treated separately when \(X^\omega/a_q<1\), gives uniformly in
\(q\)

\begin{equation}
 a_q
 \sum_{|r|>X^\omega/a_q}
 (1+a_q|r|)^{-N}
 \ll_N X^{-\omega(N-1)}.
 \label{eq:tpc26-tail-lattice-cancellation}
\end{equation}

This is the required cancellation of the Poisson prefactor
\(J/(Hq)\) against the frequency-lattice spacing; no factor \(q/J\)
remains.  Since \(H\) is fixed, \(|c_H(r)|\ll_H1\).  Moreover, the
fixed-power support and the soft divisor-coefficient bound give a fixed
constant \(C_{\rm div}\) such that

\begin{equation}
 \sum_{u,v\le T}|b_R(u)b_R(v)|
 \ll X^{C_{\rm div}}.
 \label{eq:tpc26-tail-divisor-mass}
\end{equation}

All lcm labels merely repartition these pairs, and the number and total
variation of the fixed \(H_0\)-residue cells are \(O_h(1)\).  Combining
\eqref{eq:tpc26-tail-row-fiber-mass}--
\eqref{eq:tpc26-tail-divisor-mass} yields

\begin{equation}
 \mathscr T^{\rm ann}_{\omega}(\boldsymbol\tau)
 \ll_{N,\mathscr D}
 X^{C_{\rm div}-\omega(N-1)}
 (1+|\boldsymbol\tau|)^N
 \|x_{\boldsymbol\tau}\|_1
 \|y_{\boldsymbol\tau}\|_1.
 \label{eq:tpc26-tail-component-bound}
\end{equation}

Choose \(N\) so that
\(\omega(N-1)>A+C_{\rm div}\), integrate against \(d|\nu|\), and use
\eqref{eq:tpc26-transfer-l1} with the \(N\)-th weighted moment.  Finally
sum the \(O_h(1)\) residue cells.  This proves

\[
 \int_{\R^4}
 \mathscr T^{\rm ann}_{\omega}(\boldsymbol\tau)
 \,d|\nu|(\boldsymbol\tau)
 \ll_{A,\mathscr D}X^{-A}Q^2,
\]

as claimed.
\end{proof}
