\section{Exact finite certificate and claim ledger}
\label{sec:tpc39-certificate}

The script \nolinkurl{experiments/tpc39_certificate.py} is a deterministic
finite certificate for the algebraic identities in this paper.  It uses only
integers and exact rational Hilbert vectors.  Roots of unity are never
approximated: every phase average is evaluated by exact cyclic
orthogonality.  The script has no random input, floating--point literal,
true--division node, external package, or Python \texttt{assert}; every check
therefore remains active under \texttt{python -O}.

The certificate exhaustively checks declared finite ranges for:
\begin{enumerate}[label=(\roman*)]
 \item isolation of the zero alias at the sharp cyclic modulus \(q=L+1\),
 and separation of all aliases only at \(q=2L+1\);
 \item exact zero recovery and a null witness after deleting any one twist;
 \item Hilbert--valued folded Parseval, collision--Gram entries, ranks,
 traces, eigenvectors, and all multiplicities in
 \eqref{eq:tpc39-general-spectrum};
 \item the finite divisibility--indicator obstruction from
 \cref{thm:tpc39-divisibility-rigidity}; and
 \item the exact variance formulas for continuous Haar phases, the
 collision--free \((2L+1)\)-grid, and the folded minimal \((L+1)\)-grid,
 using exact character moments and complete finite product--space
 enumeration.
\end{enumerate}

Running
\begin{verbatim}
python experiments/tpc39_certificate.py
python -O experiments/tpc39_certificate.py
\end{verbatim}
produces byte--identical canonical JSON records.  The frozen run passes
\(2{,}305{,}056\) exact checks.  Its certificate digest is
\begin{center}
\nolinkurl{31ed18b3158a0aa3228441d96b04d5a7d3cb8096d669dfae0d28a5339baef633}.
\end{center}
The SHA--256 hashes of the source and canonical JSON record are, respectively,
\begin{center}
\nolinkurl{3527cf3d4c011df887965924b3500b4b9a645eded46e59afabb51a979282f764},\\
\nolinkurl{2bcce40bea2e82e8a5da849aea44af79ef0c8662b8a21f8883449979206aa7d3}.
\end{center}
The JSON also records representative rational energies and explicit Boolean
claim boundaries.

The certificate is evidence for finite algebra and implementation fidelity;
it is not evidence for an asymptotic M\"obius estimate.  In particular, its
claim ledger marks the twist--stable physical bound, uniform alias--column
bound, parity breach, Hardy--Littlewood asymptotic, and twin--prime theorem as
false.
