\section{Divisibility completions and the alias--synthesis trade}
\label{sec:tpc39-completion-comparison}

The quotient projector can be compared with the multi--completion route
proposed in TPC--38.  The comparison explains both why a superwindow
modulus is unavoidable and why additive phases are a distinct
implementation of it.

\subsection{Exact rigidity of linear divisibility recovery}

For a positive integer \(m\), put
\begin{equation}
 d_m(F)=\one_{m\mid F},
 \qquad |F|\le B.
 \label{eq:tpc39-divisibility-column}
\end{equation}
Repeated moduli in a linear combination are combined into one aggregate
coefficient \(a_m\).

\begin{theorem}[Identity--bucket divisibility rigidity]
\label{thm:tpc39-divisibility-rigidity}
Suppose a finite family satisfies
\begin{equation}
 \sum_m a_m d_m(F)=\one_{F=0}
 \qquad(|F|\le B).
 \label{eq:tpc39-divisibility-recovery}
\end{equation}
Then
\begin{equation}
 a_m=0\quad(1\le m\le B),
 \qquad
 \sum_{m>B}a_m=1.
 \label{eq:tpc39-divisibility-rigidity}
\end{equation}
Conversely, \eqref{eq:tpc39-divisibility-rigidity} is sufficient.
\end{theorem}

\begin{proof}
Evaluate \eqref{eq:tpc39-divisibility-recovery} at each
\(1\le n\le B\):
\begin{equation}
 0=\sum_{m\mid n}a_m.
 \label{eq:tpc39-divisibility-triangular}
\end{equation}
At \(n=1\) this gives \(a_1=0\).  Increasing induction on \(n\) then
gives \(a_n=0\), since every proper divisor coefficient has already
vanished.  At \(F=0\), all divisibility columns equal one, so the remaining
coefficients sum to one.  If \(m>B\), then \(d_m=\one_{F=0}\) on the
window, proving the converse.
\end{proof}

Thus no linear combination of window--internal completion indicators can
recover exact equality.  Every effective coefficient in an exact rule is
already attached to a no--wrap modulus.  This is a no--go for that
particular coefficient class, not for phase measurements or for relations
among the actual physical columns.

\subsection{How quotient tomography implements no--wrap recovery}

The projector in \cref{thm:tpc39-additive-quotient-identity} may be written
as
\begin{equation}
 \one_{M\mid F}\frac1q\sum_{\nu\bmod q}
 \ee{\nu F/(qM)}
 =\one_{qM\mid F}.
 \label{eq:tpc39-phase-implements-superwindow}
\end{equation}
Therefore it does not contradict
\cref{thm:tpc39-divisibility-rigidity}: the effective modulus \(qM\) is
larger than \(B\).  What is new is its implementation.  Instead of
introducing \(qM\) as an additional multiplicative CRT face modulus, we
retain the three--prime recombination at \(M\) and resolve its quotient by
\(q\) additive phase measurements.  Each phase has unit modulus, so it
does not change the scalar face masses.

\subsection{A finite alias--synthesis conservation law}

For comparison, let
\begin{equation}
 R=\prod_{i=1}^{s}p_i
 \label{eq:tpc39-general-CRT-R}
\end{equation}
be a squarefree CRT modulus with a fixed number \(s\) of odd prime
factors.  The full target--synthesis calculation of TPC--38 gives the
exact largest squared singular value
\begin{equation}
 \Lambda_C(R)
 =\prod_{i=1}^{s}
 \frac{p_i(p_i-2)^2}{(p_i-1)^2}
 =R\prod_{i=1}^{s}
 \left(1-\frac1{p_i-1}\right)^2.
 \label{eq:tpc39-full-synthesis-R}
\end{equation}
The joint alias count in the window is
\begin{equation}
 K_R=1+2\left\lfloor\frac BR\right\rfloor.
 \label{eq:tpc39-alias-count-R}
\end{equation}

\begin{proposition}[Alias--synthesis conservation]
\label{prop:tpc39-alias-synthesis-conservation}
If \(s\) is fixed and \(\min_i p_i\to\infty\), then
\begin{equation}
 \boxed{
 \Lambda_C(R)K_R\asymp R+B.}
 \label{eq:tpc39-alias-synthesis-conservation}
\end{equation}
In particular, coefficient--blind full synthesis cannot make both the
modulus cost and the joint alias count smaller than the determinant scale.
\end{proposition}

\begin{proof}
The product in \eqref{eq:tpc39-full-synthesis-R} is bounded above and
below by positive constants and tends to one.  Also
\(RK_R\asymp R+B\).
\end{proof}

This is a finite spectral trade, not a lower bound for the M\"obius
physical output.  Directly increasing \(R\) reduces aliases in inverse
proportion to the dominant full synthesis scale.  Additive quotient
tomography keeps \(R=M\) in the multiplicative face calculus and pays
instead for a bank of
\begin{equation}
 q=L+1\asymp1+B/M
 \label{eq:tpc39-phase-bank-size}
\end{equation}
structured outputs.  The recovery functional has unit normalized
amplification, but
an arithmetic theorem uniform or square--averaged over this bank is still
required.  Neither implementation is coefficient--free evidence of a
power saving.
