\section{The corrected continuation after quotient tomography}
\label{sec:tpc39-next-gate}

The equality--recovery problem is now algebraically closed.  The surviving
question is whether the physical coefficient system admits the required
twist--stable energy estimate.

\subsection{What is unconditional}

The paper proves, without a M\"obius hypothesis:
\begin{enumerate}[label=(\roman*)]
 \item the exact quotient identity
 \eqref{eq:tpc39-additive-quotient-identity};
 \item exact recovery of \(\mathscr Z_0\) from \(L+1\) recombined twists
 with unit normalized recovery amplification;
 \item Hilbert--valued folded Parseval and the complete tomography
 spectrum for every \(L<r\le2L+1\);
 \item minimality of the \(L+1\) sample count among arbitrary phase nodes
 and complex weights;
 \item optimal noise amplification and rigidity of positive minimal
 rules;
 \item the deletion no--go, the random estimator identity, and the exact
 relation to raw trace and alias Gram gates;
 \item rigidity of exact recovery by pure divisibility indicators;
 \item the finite alias--synthesis conservation law;
 \item terminal row--alias injectivity and, under the inherited deterministic
 multiplier ledger, closure of its complete atomic diagonal at the target
 scale.
\end{enumerate}

These results repair the logical gap in TPC--38: there is now an explicit
linear functional that converts a structured family of congruence
completions into exact equality.

\subsection{Route T: the minimal recombined bank}

The canonical minimal--bank continuation isolated here is precisely
\cref{ass:tpc39-minimal-twist-energy}:
\begin{equation}
 \frac1q\sum_{\nu\bmod q}\|\mathscr Y_\nu\|^2
 \ll X^{o(1)}B_0K_B.
 \label{eq:tpc39-next-route-T}
\end{equation}
This tests only the \(q=L+1\) Fourier directions needed for equality.
It allows arbitrary energy in the antisymmetric folded kernel
\eqref{eq:tpc39-minimal-kernel}.  It is therefore the smallest exact
tomographic gate constructed in this paper.

The terminal analysis shows what must be proved: the atomic diagonal is
already acceptable, while fixed--alias cross--row terms, the equality
column, and \(qM\)-gap folded correlations remain.  A useful proof would
have to exploit the actual M\"obius/source coefficients, not only additive
orthogonality in the alias index.

\subsection{Route F: twist--stable full/proper fields}

The stronger face formulation
\eqref{eq:tpc39-twist-stable-C}--\eqref{eq:tpc39-twist-stable-P} is closer
to the finite CRT architecture.  The twist leaves every coefficient mass
unchanged, so no new period factor appears on the input side.  What is
unknown is whether the coherent physical synthesis respects those scalar
ledgers uniformly or in square average over \(\nu\).

A theorem on all admissible coefficient fields would imply Route F, but
would be unnecessarily strong.  The present target is only a single
regular polygon orbit of the two prescribed fields.

\subsection{Route S: direct superwindow completion}

The divisibility rigidity theorem says that exact recovery by completion
indicators requires a modulus larger than \(B\).  One may therefore enlarge
the multiplicative CRT modulus itself until there are no aliases.  Within
the fixed--factor--count, large--prime regime of the conservation law
\eqref{eq:tpc39-alias-synthesis-conservation}, the dominant full synthesis
scale then grows to the determinant scale.  This is an
alternative physical architecture, not a consequence of the additive
route.  Optimizing the factorization of such a superwindow modulus and its
zero--face range is left to a subsequent layer.

\subsection{Viable outcomes for the next paper}

\begin{description}[style=nextline,leftmargin=1.8em]
 \item[Positive twist--stable theorem.]
 Prove \eqref{eq:tpc39-next-route-T}, or the stronger face estimates, for
 the actual packet.  This would close the equality--recovery stage at the
 inherited energy scale; it would still feed into the remaining scalar
 prime--pair reductions rather than by itself prove a prime--pair
 asymptotic.

 \item[Partial arithmetic theorem.]
 Prove the required estimate for a terminal sublayer, a restricted family
 of rows, or an averaged choice of the auxiliary triple.  The exact
 injectivity and diagonal ledger make any genuine off--diagonal saving
 separately visible and publishable.

 \item[Scoped twist obstruction.]
 Show that a declared class of additive dispersion, large--sieve, or
 positivity--preserving estimates cannot reach
 \eqref{eq:tpc39-next-route-T}.  Such a theorem would rule out that method
 class, not prove that the physical M\"obius form is large.
\end{description}

\subsection{Parity boundary}

The surviving terminal form contains two-- and four--M\"obius
correlations.  This is compatible with the classical parity obstruction
for sieve methods \citep{HeathBrown1982Parity,IwaniecKowalski2004}.
Quotient tomography neither proves nor disproves a parity--breaking
estimate.  It proves that equality recovery itself is no longer an
undefined step: the remaining statement is the explicit twist--stable
physical energy theorem in \eqref{eq:tpc39-next-route-T}.
