\section{Partial, redundant, and random twist banks}
\label{sec:tpc39-partial-random}

The minimal regular polygon is exact but has no redundant measurement.
This section records what is lost under partial sampling and what random
sampling can provide.

\subsection{The nonzero bank restores the alias loss}

Remove the zero column and define
\begin{equation}
 \mathscr Y_\nu^*
 :=\sum_{\substack{-L\le k\le L\\k\ne0}}
 \omega^{\nu k}\mathscr Z_k.
 \label{eq:tpc39-nonzero-twisted-bank}
\end{equation}
The untwisted nonzero aggregate required by the two--sum route of TPC--38
is
\begin{equation}
 \mathscr Y_0^*
 =\sum_{k\ne0}\mathscr Z_k.
 \label{eq:tpc39-nonzero-untwisted-sum}
\end{equation}
Since \(\nu=0\) is one member of the bank,
\begin{equation}
 \boxed{
 \|\mathscr Y_0^*\|^2
 \le (q-1)\left(
 \frac1q\sum_{\nu=0}^{q-1}\|\mathscr Y_\nu^*\|^2
 \right).}
 \label{eq:tpc39-nonzero-bank-qminusone-loss}
\end{equation}
Indeed, additive orthogonality gives
\(\sum_{\nu=0}^{q-1}\mathscr Y_\nu^*=0\).  Cauchy applied to the other
\(q-1\) values then yields
\(q\|\mathscr Y_0^*\|^2\le(q-1)\sum_\nu\|\mathscr Y_\nu^*\|^2\),
which is the displayed bound.  The factor \(q-1\asymp K_B\) is sharp:
the nonzero residue coefficients parametrize every zero--mean bank list.
Thus applying Parseval only to the nonzero aliases and then returning to
the one untwisted aggregate recreates the same endpoint order as the finite
alias loss.  The gain in \cref{thm:tpc39-exact-Hilbert-recovery} comes
from averaging the \emph{completed outputs themselves}, with the zero
column included and isolated by the quotient projector.

\subsection{Redundant cyclic banks}

Every integer \(r>L\) gives the exact recovery formula
\begin{equation}
 Z_0=\frac1r\sum_{\nu=0}^{r-1}Y_\nu^{(r)},
 \label{eq:tpc39-redundant-recovery}
\end{equation}
because the zero residue class remains a singleton.  The spectrum in
\cref{thm:tpc39-tomography-spectrum} quantifies the redundancy for
\(L<r\le2L+1\).  At \(r=2L+1\), all aliases are separated and the bank
energy is the raw trace in \eqref{eq:tpc39-full-DFT-Parseval}; this is
strictly stronger than necessary for equality recovery.

Using \(r>L+1\) may be helpful if an analytic argument has a small number
of exceptional twists.  Exact recovery from an arbitrary retained subset
is still governed by the moment system
\eqref{eq:tpc39-moment-system}; sample count alone does not control its
conditioning.  Clustered nodes may make the recovery weights large, while
the complete regular polygon has the optimal amplification proved in
\cref{prop:tpc39-optimal-conditioning}.

\subsection{Random phase averaging}

Let \(\theta_1,\ldots,\theta_m\) be independent and uniform on
\([0,1)\), and define
\begin{equation}
 \widehat Z_0
 :=\frac1m\sum_{j=1}^{m}
 \sum_{k=-L}^{L}\ee{k\theta_j}Z_k.
 \label{eq:tpc39-random-estimator}
\end{equation}

\begin{proposition}[Exact random mean--square error]
\label{prop:tpc39-random-MSE}
For every finite Hilbert column family,
\begin{align}
 \mathbb E\widehat Z_0&=Z_0,
 \label{eq:tpc39-random-unbiased}\\
 \mathbb E\|\widehat Z_0-Z_0\|^2
 &=\frac1m\sum_{\substack{-L\le k\le L\\k\ne0}}
 \|Z_k\|^2.
 \label{eq:tpc39-random-MSE}
\end{align}
\end{proposition}

\begin{proof}
The expectation of \(\ee{k\theta}\) is \(\one_{k=0}\), proving
\eqref{eq:tpc39-random-unbiased}.  Independence reduces the variance of
the sample mean by \(m\), and orthogonality in one sample removes all
terms with distinct nonzero frequencies, proving
\eqref{eq:tpc39-random-MSE}.
\end{proof}

Random sampling is always unbiased.  It becomes quantitatively useful only
when a nonzero--alias trace is available.  Without that input, it gives no
coefficient--free deterministic recovery.  The structured regular polygon
is exceptional: it obtains zero error with only \(L+1\) samples by exact
algebra rather than probabilistic concentration.

\subsection{Partial control is not enough}

The deletion no--go in \cref{cor:tpc39-deletion-no-go} has an analytic
consequence.  Bounds for all but one member of the minimal bank, no matter
how strong, do not control \(Z_0\) in the abstract column class.  A proof
of the physical route must therefore do one of the following:
\begin{enumerate}[label=(\roman*)]
 \item control the complete minimal bank in square average;
 \item add redundancy and solve the resulting stable moment system after
 deleting the exceptional twists; or
 \item estimate each exceptional output separately.
\end{enumerate}
This finite issue should be settled before any exceptional--frequency
argument is used in the M\"obius analysis.
