\section{Twisted face fields and the physical recovery gate}
\label{sec:tpc39-physical-gate}

We now return the quotient algebra to the inherited physical interface.
Every statement that estimates a physical output is isolated as a
conditional input.

\subsection{Unimodular twists preserve the face ledgers}

For \(0\le\nu<q\), set
\begin{align}
 C_{\nu,N}(F)
 &:=\ee{\nu F/(qM)}C_N(F),
 \label{eq:tpc39-twisted-C-field}\\
 P_{\nu,N}(F)
 &:=\ee{\nu F/(qM)}P_N(F).
 \label{eq:tpc39-twisted-P-field}
\end{align}
The twist depends only on the determinant.  In particular,
\begin{align}
 |C_{\nu,N}(F)|&=|C_N(F)|,
 &|P_{\nu,N}(F)|&=|P_N(F)|,
 \label{eq:tpc39-twist-preserves-pointwise-mass}\\
 \sum_{|F|\le B}|C_{\nu,N}(F)|^2
 &=\sum_{|F|\le B}|C_N(F)|^2,
 &
 \sum_{|F|\le B}|P_{\nu,N}(F)|^2
 &=\sum_{|F|\le B}|P_N(F)|^2.
 \label{eq:tpc39-twist-preserves-field-mass}
\end{align}
The one--period identities from TPC--38 therefore imply, uniformly in
unit targets and twists,
\begin{align}
 \sum_{|F|\le B}|C_{\nu,N}(F)|^2
 &\ll K_B+1,
 \label{eq:tpc39-full-window-mass}\\
 \sum_{|F|\le B}|P_{\nu,N}(F)|^2
 &\ll \frac{K_B+1}{J},
 \label{eq:tpc39-proper-window-mass}
\end{align}
at the orbit--scale three--prime endpoint.  Partial periods at the two
ends only change the absolute constants.

These scalar identities do not transfer automatically through the
coherent physical synthesis.  They show that adding the phase bank does
not worsen the coefficient norm in the proposed face--field estimate.

\subsection{A canonical minimal--bank square--energy condition}

Recall \(\mathscr Y_\nu\) from
\eqref{eq:tpc39-Ynu}.  The exact analytic input tailored to the minimal
tomography bank is the following.

\begin{assumption}[Minimal twist--bank energy]
\label{ass:tpc39-minimal-twist-energy}
The actual regular--subpacket outputs satisfy
\begin{equation}
 \boxed{
 \frac1q\sum_{\nu=0}^{q-1}\|\mathscr Y_\nu\|^2
 \ll X^{o(1)}B_0K_B.}
 \label{eq:tpc39-minimal-twist-energy}
\end{equation}
\end{assumption}

\begin{theorem}[Conditional equality closure]
\label{thm:tpc39-conditional-equality-closure}
Under \cref{ass:tpc39-minimal-twist-energy},
\begin{equation}
 \|\mathscr R_0\|^2
 \ll X^{o(1)}B_0K_B.
 \label{eq:tpc39-conditional-equality-bound}
\end{equation}
At the endpoint this is
\begin{equation}
 \|\mathscr R_0\|^2
 \ll X^{o(1)}Q^3/J.
 \label{eq:tpc39-conditional-endpoint-gate}
\end{equation}
\end{theorem}

\begin{proof}
Use \eqref{eq:tpc39-condition-one-recovery},
\(\mathscr Z_0=\mathscr R_0\), and
\eqref{eq:tpc39-interface-key-ledger}.
\end{proof}

This is an exact sufficient implication, but it is not an analytic weakening
of the original target.  Indeed,
\eqref{eq:tpc39-minimal-folded-Parseval} shows that the hypothesis is
stronger than the desired conclusion because its left side contains
\(\|\mathscr R_0\|^2\) as a positive summand.  Its value is to specify a
finite structured family of completed outputs to which additive-dispersion
methods could be applied, not to lower the required cancellation by algebra
alone.

\subsection{A face--separated sufficient input}

A formulation closer to the TPC--37 prescribed--field proposal is
\begin{assumption}[Twist--stable full/proper fields]
\label{ass:tpc39-twist-stable-faces}
The outputs in \eqref{eq:tpc39-Ynu-C} and
\eqref{eq:tpc39-Ynu-P} satisfy
\begin{align}
 \frac1q\sum_{\nu=0}^{q-1}\|\mathscr Y_\nu^C\|^2
 &\ll X^{o(1)}B_0K_B,
 \label{eq:tpc39-twist-stable-C}\\
 \frac1q\sum_{\nu=0}^{q-1}\|\mathscr Y_\nu^P\|^2
 &\ll X^{o(1)}B_0\frac{K_B}{J}.
 \label{eq:tpc39-twist-stable-P}
\end{align}
\end{assumption}

\begin{proposition}[Face stability implies the minimal gate]
\label{prop:tpc39-face-stability-implies-minimal}
\Cref{ass:tpc39-twist-stable-faces} implies
\cref{ass:tpc39-minimal-twist-energy}.
\end{proposition}

\begin{proof}
For each \(\nu\),
\[
 \|\mathscr Y_\nu^C+\mathscr Y_\nu^P\|^2
 \le2\|\mathscr Y_\nu^C\|^2+2\|\mathscr Y_\nu^P\|^2.
\]
Average and use \(J\to\infty\).
\end{proof}

Uniform estimates for every \(\nu\) with the corresponding right sides
are stronger sufficient conditions.  They would incur no extra factor
\(q\), because the final recovery uses an average.  On the other hand,
the two untwisted estimates proposed in TPC--37 are only the case
\(\nu=0\).  They do not imply either twist--stable assumption.  The
two--column obstruction from TPC--38, or the deletion witness in
\cref{cor:tpc39-deletion-no-go}, supplies abstract counterexamples.

\subsection{Why this is smaller than an all--field theorem}

An all--field Bessel estimate stable under arbitrary determinant
restrictions would control every field
\(\kappa_N(F)\), hence in particular all
\(C_{\nu,N},P_{\nu,N}\).  The minimal twist bank asks only for the
\(2q\) explicit fields in
\eqref{eq:tpc39-twisted-C-field}--\eqref{eq:tpc39-twisted-P-field}, or
more weakly for their \(q\) recombinations.  It discards the
\(L\)-dimensional antisymmetric kernel in
\eqref{eq:tpc39-minimal-kernel}.  It is therefore a genuinely smaller
operator test than the hereditary all--field theorem isolated in TPC--38.

It is not known whether the actual product--slope and projective
reassembly methods are stable under this bank.  Establishing precisely
that stability is the new physical gate.
