\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Conductor-Rectangularized Fibers in a Primitive Mobius Tail: Tensor Large Sieve, Gauss Complementarity, and Selected Short-Short Closure},
 pdfauthor={Liang Wang},
 pdfsubject={Exact conductor rectangularization and closure of a selected short-short connected fiber discrepancy},
 pdfkeywords={Mobius tail, Dirichlet characters, exact conductors, large sieve, Gauss sums, Ramanujan sums, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\cond}{\operatorname{cond}}

\title{\textbf{Conductor-Rectangularized Fibers}\
\textbf{in a Primitive M\"obius Tail:}\
\textbf{Tensor Large Sieve, Gauss Complementarity,}\
\textbf{and Selected Short--Short Closure}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC-21 leaves the selected short--short part of a primitive M\"obius
residual correlation as a connected multiplicative-character moment on
unit fibers modulo squarefree least common multiples.  Its shared-factor
formula appears to couple the two row variables through a character
convolution.  We prove that this convolution has an exact pairwise
rectangularization.  If
\[
 g=(u,v),\qquad u=ga,\qquad v=gb,\qquad q=gab,
\]
then, for the actual row-pair mask, character orthogonality converts the
shared-\(g\) average into the compatibility condition
\(m\equiv n\pmod g\), and the remaining character coordinates form the
Cartesian product
\(\mathfrak X(u)\times\mathfrak X(b)\).  The global conductor is the
product of the two coordinate conductors.  This identity is applied
separately to every lcm divisor pair; no common rectangular coordinate
across different pairs is asserted.

For coefficients on an interval of length \(N\), we derive from the
primitive character large sieve the weighted exact-conductor estimate
\[
 \sum_{\substack{s\asymp S\\s\ {\rm squarefree}}}\frac1{\varphi(s)}
 \sum_{\substack{\chi\ (\bmod s)\\\cond\chi\asymp F}}
 \left|\sum_n a_n\chi(n)\right|^2
 \ll_\eps X^\eps\left(F+\frac NF\right)\sum_n|a_n|^2.
\]
It includes conductor one and hence retains induced principal modes.
Tensorization estimates an arbitrary masked coefficient matrix; no
rank-one factorization or deletion of the determinant--gcd pruning is
used.  A second estimate exploits the exact induced Gauss factor at all
additive frequencies.  The Ramanujan factor \(c_{q/f}(r)\) is summed
against the rapidly decaying Fourier weight without imposing
\((r,q)=1\).

Writing \(Q=X^{\beta+o(1)}\),
\(R=X^{1/2-\delta+o(1)}\), and splitting coordinate conductors at
\(Q^{1/2}\), the tensor-norm and direct-Gauss estimates are
complementary.  Every conductor block has a fixed-power saving whenever
\[
 1-4\delta<\beta<\min\left\{\frac23,6\delta\right\}.
\]
Subject to the inherited no-wrap and polynomial tail-mass hypotheses,
either the row-occupancy range or the hybrid range above, together with
the strict single-leg condition \(\beta<1/2+\delta\), closes the connected
discrepancy for the actual row-pair-only generic mask in the selected
short--short packet of TPC-20--21, including the two inherited parameter
profiles stated below.
Combining with the Ramanujan-mean closure of TPC-21 closes that selected
packet.  We do not treat either large-divisor leg, reassemble the full
residual-dispersion argument, prove a prime-pair asymptotic, or breach the
sieve parity barrier.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius tail; CRT fibers; Dirichlet
characters; exact conductors; multiplicative large sieve; induced Gauss
sums; Ramanujan sums; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11L05, 11L07, 11L40.

\input{sections/introduction}
\input{sections/interface}
\input{sections/rectangularization}
\input{sections/exact-conductor-sieve}
\input{sections/tensor-energy}
\input{sections/gauss-complementarity}
\input{sections/exponent-closure}
\input{sections/barriers-scope}
\input{sections/certificate-conclusion}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
