\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Square-Root Normal Forms for a Fixed-Shift Type-II Gate: Recentered Ramanujan Rows, a Near-11/21 Factorable Wedge, and a Cross-Spectral Angular Criterion},
 pdfauthor={Liang Wang},
 pdfsubject={A square-root normal form and a factorable subpacket estimate for a fixed-shift prime-pair Type-II gate},
 pdfkeywords={prime correlations, Ramanujan sums, Vaughan identity, Bombieri-Vinogradov theorem, large moduli, Type II sums, translation spectrum, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\T}{\mathbb T}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\e}{\mathrm e}

\title{\textbf{Square-Root Normal Forms for a Fixed-Shift}\\
\textbf{Type-II Gate: Recentered Ramanujan Rows,}\\
\textbf{a Near-\texorpdfstring{$11/21$}{11/21} Factorable Wedge, and}\\
\textbf{a Cross-Spectral Angular Criterion}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Fix $h\ne0$, let $W\in C_c^\infty((0,\infty);\R)$, and put
\[
 \Lambda_R(n)=\sum_{q\le R}\frac{\mu(q)}{\varphi(q)}c_q(n),
 \qquad r_R=\Lambda-\Lambda_R,
 \qquad R=X^{1/2-\delta}.
\]
TPC-15 reduced the weighted fixed-shift prime-pair problem to a broad
Vaughan Type-II packet by using only rows of modulus at most $R$.  We
resolve two further layers of that packet.

First, the complete-period mean of $j\mapsto\Lambda_R(mj+h)$ is computed
for every $m$, including $m>R$.  The prime progression density minus this
model mean is the explicit cutoff drift
\[
 \Delta_{h,R}(m)=
 \sum_{\substack{q\mid m\\q>R}}
 \frac{\mu(q)c_q(h)}{\varphi(q)}.
\]
The aggregate drift is small, although it is generally nonzero row by
row.  Maximal Bombieri--Vinogradov after this recentering moves the
resolved source-row wall from $R$ to
\[
 M=X^{1/2}\exp(-\sqrt{\log X}).
\]
An asymmetric Vaughan identity then gives the square-root normal form
\[
 \sum_n\Lambda(n)\Lambda(n+h)W(n/X)
 =\mathfrak S(h)XI_0(W)-
 \sum_{\substack{\ell>M\\k>1}}
 \Lambda(\ell)r_R(\ell k+h)W(\ell k/X)
 +O_A(X(\log X)^{-A}).
\]
Thus the left unbalanced wing is closed up to the classical square-root
distribution wall.  The right wing is not removed: a fixed-$k$ slice is
itself a two-linear-form Hardy--Littlewood problem.

Second, opening the original coefficient
$\beta_V(k)=\sum_{d\mid k,d\le V}\mu(d)$ reveals the true progression
modulus $q=\ell d$.  All terms with $\ell d\le R$ are peeled off.  On the
remaining three-scale region, Maynard's fixed-residue theorem for
factorable moduli transfers to an actual hard subpacket.  In particular,
for $\delta>1/42$ with a fixed interior margin, a smooth packet near
\[
 D=X^{1/21},\qquad L=X^{10/21},\qquad K=X^{11/21}
\]
is $o(X)$.  This deletes one nonempty $D$-resolved wedge, not a whole
$(L,K)$ block.

Finally, we prove
\[
 \sum_n r_R(n)^2F(n/X)
 =X\log(X/R)I_0(F)+O_{F,\delta}(X),
\]
so the calibrated residual remains large in energy.  The hard packet is
an exact translation matrix coefficient and a specified Fourier
coefficient of a cross-spectrum.  Explicit norm bounds turn the missing
estimate into a quantitative angular-decorrelation corridor, while phase
averages enjoy unconditional power cancellation.  No fixed-shift
prime-pair asymptotic, twin-prime lower bound, new level of distribution,
or breach of sieve parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} fixed-shift prime correlations; Ramanujan
sums; Vaughan identity; Bombieri--Vinogradov theorem; factorable moduli;
Type-II sums; translation spectrum; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N05, 11N13; Secondary
11N35, 11N37, 42A05.

\input{sections/introduction-scope}
\input{sections/finite-row-drift}
\input{sections/recentered-typei}
\input{sections/asymmetric-vaughan}
\input{sections/dyadic-corridor}
\input{sections/factorable-wedge}
\input{sections/energy-cross-spectrum}
\input{sections/phase-masks-boundary}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
