\begin{abstract}
The low-sign average and the physical all-minus corner of a
large-prime Walsh packet produce two different Gram forms.  The former
resolves the low residual label \(s\); the latter erases \(s\) inside each
native output coordinate.  We identify the missing map exactly.  On the
canonical low-Walsh coefficient space it is the signed fiber sum
\[
 (\Eop_\mu z)_i=\sum_t\mu(t)z_{i,t},
\]
or, after the physical M\"obius gauge has already been absorbed, the
unsigned erasure \((\Eop_1A)_i=\sum_sA_{i,s}\).  Its quadratic defect is
the complete signed off-diagonal exchange form.  Each active output
fiber has one bright direction and a dark space of codimension one.
Thus any support-only lower comparison fails as soon as two residual
labels share a native output; this obstruction is sharp and is not
removed by terminal-prime singleton incidence.

For the actual coefficient image \(E=\Ran T\), we prove that the optimal
uniform native comparison is the least eigenvalue of the compression of
\(\Eop_\mu^*\Eop_\mu\) to \(E\).  We give its exact generalized-Gram and
Moore--Penrose forms, a dimension kill test, and the necessary
fixed-carrier convention.  At one fixed nonzero shift \(h_0\), the
terminal residual vector from the preceding prime-fiber construction is
identified coordinate by coordinate with the gauged high-Walsh lift.
The complete native affine column on the declared slice then factors through
two independent gates: a residual-label alias constant and a base--high
affine noncancellation constant.  Neither constant is proved positive at the
endpoint.  The endpoint very-high face also lies in a smaller cofactor band
than the inherited \(R\asymp J\) packet, so its activation requires a
separate relocation/occupancy theorem.  The results are exact L0 linear
algebra and L1 interface closure; they do not give a parity improvement or a
twin-prime conclusion.
\end{abstract}
