\section{High-block transfer and completion of the affine face}
\label{sec:tpc58-affine-completion}

The preceding residual construction and the native affine column use two
equivalent M\"obius conventions.  We first align them exactly.  This is
essential: the terminal amplitudes of TPC--56 and TPC--57 already contain
the residual sign, whereas the canonical Walsh lift stores that sign in the
evaluation operator \citep{WangTPC45,WangTPC56,WangTPC57}.

\subsection{The sign-compatible high block}

Let \(i\) denote one native output coordinate, including its side, opposite
row, and orbit time.  For a squarefree low label \(s\), define the canonical
high Walsh coefficient
\begin{equation}
 z_{H;i,s}
 :=-
 \sum_{\substack{p\in\cP_y\\sp\text{ is an active equality label at }i}}
 b_{i,sp}.
 \label{eq:tpc58-canonical-high-coefficient}
\end{equation}
The minus sign is the fixed physical value of the high character.  Let
\begin{equation}
 (C_{\mu,H}z)_i
 :=\sum_s\mu(s)z_{i,s},
 \qquad
 (U_\mu z)_{i,s}:=\mu(s)z_{i,s}.
 \label{eq:tpc58-high-erasure-and-gauge}
\end{equation}
Both operators act on raw counting-measure spaces.  Put
\begin{equation}
 h:=C_{\mu,H}z_H.
 \label{eq:tpc58-native-high-vector}
\end{equation}
By the definition of the TPC--45 vectors \(v_p\),
\begin{equation}
 \boxed{
 h=-\sum_{p\in\cP_y}v_p.}
 \label{eq:tpc58-high-vector-vp}
\end{equation}

For the same very-high-prime carrier, let
\begin{equation}
 A_{i,s}
 :=\sum_{u:q(u)=(i,s)}x_u
 \label{eq:tpc58-tpc57-residual-amplitude}
\end{equation}
be the undeleted TPC--57 residual amplitude.  Here the side tag in \(i\)
is suppressed from the notation \(q(u)\).  Finally define the unsigned
erasure
\begin{equation}
 (C_1A)_i:=\sum_sA_{i,s}.
 \label{eq:tpc58-unsigned-erasure}
\end{equation}

\begin{proposition}[Exact gauge alignment]
\label{prop:tpc58-exact-gauge-alignment}
On the identical fixed-\(h_0\), very-high-prime carrier,
\begin{equation}
 \boxed{
 A=U_\mu z_H,
 \qquad
 C_1A=C_{\mu,H}z_H=h,
 \qquad
 \|A\|_2=\|z_H\|_2.}
 \label{eq:tpc58-gauge-alignment}
\end{equation}
Equivalently, \(C_{\mu,H}=C_1U_\mu\).  In particular, no second
M\"obius sign is to be applied to the already physical amplitudes \(A\).
\end{proposition}

\begin{proof}
Write an active high equality label as \(sp\), with \(s=d_mr\).  The
stripped TPC--45 atom has the displayed leading minus sign, while the
terminal multiplier in TPC--56 and TPC--57 contributes
\(\mu(d_m)\mu(r)=\mu(s)\).  Thus, after summing all terminal primes with
the same \((i,s)\),
\[
 A_{i,s}
 =-\mu(s)\sum_p b_{i,sp}
 =\mu(s)z_{H;i,s}.
\]
This proves the first identity.  Summing over \(s\) proves the second,
and the third follows because \(U_\mu\) is diagonal unitary.
\end{proof}

Let \(z_0\) be the no-high part of the canonical Walsh lift, so that
\((z_0)_{i,u}=b_{i,u}\) when \(u_{>y}=1\).  Then
\begin{equation}
 C_{\mu,0}z_0=v_0,
 \qquad
 C_{\mu,H}z_H=h,
 \qquad
 C_\mu(z_0\oplus z_H)=v_0+h.
 \label{eq:tpc58-full-affine-erasure}
\end{equation}
Consequently the complete native affine energy is
\begin{equation}
 \boxed{
 \cN_{\rm aff}:=\|v_0+h\|_2^2
 =\left\|v_0-\sum_pv_p\right\|_2^2.}
 \label{eq:tpc58-native-affine-energy}
\end{equation}

\subsection{The restricted high-transfer constant}

For coefficient-uniform statements, fix once and for all a baseline
carrier independent of the bounded row coefficient vector
\(\zeta=(\zeta_m)\).  Remove atoms whose baseline factor is identically
zero, but do not remove an atom merely because a particular
\(\zeta_m\) vanishes.  On this fixed carrier, let
\begin{equation}
 T_H:\mathcal K_X\longrightarrow\cH_H,
 \qquad
 T_H\zeta=z_H(\zeta),
 \qquad
 E_H:=\Ran T_H,
 \label{eq:tpc58-high-coefficient-map}
\end{equation}
where \(\mathcal K_X\) is the finite row-coefficient space and
\(\cH_H\) is the canonical high-label Hilbert space.  The exact literal
factorization \(x_u=c_u\zeta_{m(u)}\) makes \(T_H\) linear.  For the
coefficient-uniform gate, assume \(E_H\ne\{0\}\) and define
\begin{equation}
 \alpha_H
 :=\inf_{\substack{z\in E_H\\z\ne0}}
 \frac{\|C_{\mu,H}z\|_2^2}{\|z\|_2^2}.
 \label{eq:tpc58-alpha-H}
\end{equation}
If \(E_H=\{0\}\), the declared high carrier is inactive for the whole
coefficient class.  The pointwise identities above still hold, but no
least-eigenvalue constant \(\alpha_H\) is assigned and the two-stage lower
chain has no nonzero high input.

\begin{proposition}[Optimal high-block transfer]
\label{prop:tpc58-optimal-high-transfer}
Let \(P_{E_H}\) be the orthogonal projection onto \(E_H\).  Then
\begin{equation}
 \boxed{
 \alpha_H
 =\lambda_{\min}\!\left(
 P_{E_H}C_{\mu,H}^{*}C_{\mu,H}P_{E_H}\big|_{E_H}
 \right).}
 \label{eq:tpc58-alpha-H-eigenvalue}
\end{equation}
Moreover,
\begin{equation}
 \alpha_H>0
 \quad\Longleftrightarrow\quad
 E_H\cap\Ker C_{\mu,H}=\{0\}.
 \label{eq:tpc58-alpha-H-kernel-test}
\end{equation}
In particular,
\begin{equation}
 \dim E_H>\rank C_{\mu,H}
 \quad\Longrightarrow\quad
 \alpha_H=0.
 \label{eq:tpc58-alpha-H-dimension-test}
\end{equation}
The same value is obtained if the infimum is restricted to any bounded
coefficient cube containing a nonzero scalar multiple of every direction
in \(\mathcal K_X\).
\end{proposition}

\begin{proof}
The quadratic form of the compressed positive operator in
\eqref{eq:tpc58-alpha-H-eigenvalue} is exactly
\(\|C_{\mu,H}z\|_2^2\) on \(E_H\).  The Rayleigh--Ritz principle therefore
gives the first assertion.  In finite dimension its least eigenvalue is
zero exactly when the restriction of \(C_{\mu,H}\) to \(E_H\) has a
nonzero kernel.  Rank--nullity proves
\eqref{eq:tpc58-alpha-H-dimension-test}.  Finally, every nonzero
coefficient vector can be multiplied by a sufficiently small positive
scalar to enter the bounded cube, and the quotient
\eqref{eq:tpc58-alpha-H} is homogeneous of degree zero.
\end{proof}

For the distinguished coefficient vector alone, no uniform coefficient
class is needed.  Whenever \(z_H\ne0\), set
\begin{equation}
 \alpha_H(\zeta)
 :=\frac{\|h(\zeta)\|_2^2}{\|z_H(\zeta)\|_2^2}.
 \label{eq:tpc58-distinguished-alpha-H}
\end{equation}
This number is an identity, not an estimated lower bound.

\subsection{The affine-separation constant}

Let
\begin{equation}
 B_0:\mathcal K_X\longrightarrow\cH_{\rm out},
 \qquad B_0\zeta=v_0(\zeta),
 \label{eq:tpc58-base-map}
\end{equation}
denote the no-high native map on the same declared coefficient class, and
define the coupled map
\begin{equation}
 J_{\rm aff}:\mathcal K_X
 \longrightarrow\cH_{\rm out}\oplus\cH_{\rm out},
 \qquad
 J_{\rm aff}\zeta
 :=\bigl(B_0\zeta,C_{\mu,H}T_H\zeta\bigr).
 \label{eq:tpc58-coupled-affine-map}
\end{equation}
Both entries are therefore driven by the same coefficient vector.  Let
\begin{equation}
 \cF_{\rm aff}:=\Ran J_{\rm aff}
 \subset\cH_{\rm out}\oplus\cH_{\rm out}.
 \label{eq:tpc58-affine-pair-image}
\end{equation}
For the uniform affine gate assume \(\cF_{\rm aff}\ne\{0\}\).  If this
image is zero, the declared native affine column vanishes identically; no
restricted minimum \(\delta_{\rm aff}\) is assigned and no positive lower
transfer is available on that class.
Define the physical sum map
\begin{equation}
 D_+(b,g):=b+g
 \label{eq:tpc58-affine-sum-map}
\end{equation}
and the optimal affine-separation constant
\begin{equation}
 \delta_{\rm aff}
 :=\inf_{\substack{(b,g)\in\cF_{\rm aff}\\(b,g)\ne(0,0)}}
 \frac{\|b+g\|_2^2}{\|b\|_2^2+\|g\|_2^2}.
 \label{eq:tpc58-delta-aff}
\end{equation}
Thus \(0\le\delta_{\rm aff}\le2\).  Notice that this is the raw physical
constant.  Dividing \(D_+\) by \(\sqrt2\) would produce a normalized
principal-angle constant, but it would also change the physical norm.

\begin{proposition}[Exact affine kernel test]
\label{prop:tpc58-affine-kernel-test}
One has
\begin{equation}
 \boxed{
 \delta_{\rm aff}
 =\sigma_{\min}\!\left(D_+\big|_{\cF_{\rm aff}}\right)^2,}
 \label{eq:tpc58-delta-aff-singular-value}
\end{equation}
where the domain has the orthogonal-sum norm.  Hence
\begin{equation}
 \delta_{\rm aff}>0
 \quad\Longleftrightarrow\quad
 \cF_{\rm aff}\cap
 \{(g,-g):g\in\cH_{\rm out}\}=\{(0,0)\}.
 \label{eq:tpc58-delta-aff-kernel-test}
\end{equation}
The equivalence uses that \(\cF_{\rm aff}\) is a nonzero finite-dimensional
linear subspace, and hence closed; it is not asserted for an arbitrary
nonclosed admissible set.
In particular,
\begin{equation}
 \dim\cF_{\rm aff}>\dim\cH_{\rm out}
 \quad\Longrightarrow\quad
 \delta_{\rm aff}=0.
 \label{eq:tpc58-delta-aff-dimension-test}
\end{equation}
\end{proposition}

\begin{proof}
The quotient in \eqref{eq:tpc58-delta-aff} is the squared Rayleigh
quotient of \(D_+|_{\cF_{\rm aff}}\).  This proves
\eqref{eq:tpc58-delta-aff-singular-value}.  Its kernel is the anti-diagonal
\(\{(g,-g)\}\), which proves the second assertion.  The last follows from
rank--nullity because \(D_+\) maps into \(\cH_{\rm out}\).
\end{proof}

\begin{theorem}[Two-stage residual-to-affine transfer]
\label{thm:tpc58-two-stage-affine-transfer}
Assume \(E_H\ne\{0\}\) and
\(\cF_{\rm aff}\ne\{0\}\).  For every coefficient vector in the declared
baseline class,
\begin{equation}
 \boxed{
 \cN_{\rm aff}(\zeta)
 \ge
 \delta_{\rm aff}\,\alpha_H\,
 \|z_H(\zeta)\|_2^2.}
 \label{eq:tpc58-two-stage-affine-transfer}
\end{equation}
Equivalently, using the TPC--57 residual vector \(A=U_\mu z_H\),
\begin{equation}
 \cN_{\rm aff}(\zeta)
 \ge
 \delta_{\rm aff}\,\alpha_H\,\|A(\zeta)\|_2^2.
 \label{eq:tpc58-two-stage-tpc57-transfer}
\end{equation}
For one distinguished vector the same conclusion holds with the pointwise
ratios \(\alpha_H(\zeta)\) and
\begin{equation}
 \delta_{\rm aff}(\zeta)
 :=\frac{\|v_0(\zeta)+h(\zeta)\|_2^2}
 {\|v_0(\zeta)\|_2^2+\|h(\zeta)\|_2^2},
 \label{eq:tpc58-distinguished-delta-aff}
\end{equation}
whenever their denominators are nonzero.
\end{theorem}

\begin{proof}
By definition of \(\delta_{\rm aff}\),
\[
 \|v_0+h\|_2^2
 \ge\delta_{\rm aff}
 \bigl(\|v_0\|_2^2+\|h\|_2^2\bigr)
 \ge\delta_{\rm aff}\|h\|_2^2.
\]
By \eqref{eq:tpc58-alpha-H},
\[
 \|h\|_2^2
 =\|C_{\mu,H}z_H\|_2^2
 \ge\alpha_H\|z_H\|_2^2.
\]
Multiplication proves \eqref{eq:tpc58-two-stage-affine-transfer}, and
\cref{prop:tpc58-exact-gauge-alignment} gives
\eqref{eq:tpc58-two-stage-tpc57-transfer}.  The distinguished statement is
the same chain with the two defining identities inserted pointwise.
\end{proof}

\subsection{Two independent sharp obstructions}

\begin{theorem}[Sharp independence of the two transfer gates]
\label{thm:tpc58-two-independent-no-go}
Neither stage in \cref{thm:tpc58-two-stage-affine-transfer} follows from
positivity at the other stage.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item A residual packet may have positive energy, with every terminal-prime
       fiber a singleton, while its native high vector is zero.
 \item A native high vector may be nonzero while the complete affine vector
       is zero.
\end{enumerate}
Both statements are sharp finite-dimensional assertions with raw counting
measure.
\end{theorem}

\begin{proof}
Both examples use one common coefficient space \(\mathcal K_X=\C\), so the
two affine entries are genuinely coupled rather than selected independently.

For (i), take one native coordinate \(i\), two distinct residual labels
\(s_1,s_2\), and one terminal atom in each residual fiber.  Let \(z_d\ne0\)
be the dark vector
\[
 (z_d)_{i,s_1}=\overline{\mu(s_1)},
 \qquad
 (z_d)_{i,s_2}=-\overline{\mu(s_2)},
 \qquad C_{\mu,H}z_d=0.
\]
Define \(T_H\zeta=\zeta z_d\) and, for a fixed nonzero
\(g\in\cH_{\rm out}\), define \(B_0\zeta=\zeta g\).  Then
\(E_H=\operatorname{span}\{z_d\}\), so \(\alpha_H=0\), whereas
\[
 \cF_{\rm aff}=\operatorname{span}\{(g,0)\},
 \qquad \delta_{\rm aff}=1.
\]
Thus a strictly positive affine gate does not prevent total loss at native
erasure, even with singleton terminal-prime fibers.

For (ii), choose a bright vector \(z_b\) with
\(C_{\mu,H}z_b=g\ne0\), and set
\(T_H\zeta=\zeta z_b\), \(B_0\zeta=-\zeta g\).  Then
\[
 \alpha_H=\frac{\|g\|_2^2}{\|z_b\|_2^2}>0,
 \qquad
 \cF_{\rm aff}=\operatorname{span}\{(-g,g)\},
 \qquad \delta_{\rm aff}=0.
\]
Hence a positive high-transfer gate does not prevent exact base--high
cancellation.  These are complete finite-dimensional coupled-map models;
they do not assert that either bad direction occurs in the distinguished
arithmetic image.
\end{proof}

The last sentence is part of the theorem boundary.  In particular, a dark
direction on the unrestricted coordinate space is not evidence that the
distinguished arithmetic coefficient occupies it.  Conversely, an upper
bound for fiber multiplicity does not bound its angle away from that dark
space.
