\section{Canonical residual erasure and its exact spectrum}
\label{sec:tpc58-erasure-spectrum}

This section isolates the finite-dimensional linear algebra of forgetting a
low label after its M\"obius phase has been restored.  No arithmetic
distribution statement is used.  The distinction between a canonical
coefficient array and its erased physical image is essential: the first is
unique in its declared orthogonal basis, whereas the second generally has a
large dark space.

\subsection{The block erasure operator}

Let \(\mathcal I\) be a finite set.  For each \(i\in\mathcal I\), let
\(\mathcal T_i\) be a nonempty finite label set of size \(k_i\), and put
\begin{equation}
 \mathcal Z:=\bigoplus_{i\in\mathcal I}\C^{\mathcal T_i},
 \qquad
 \mathcal Y:=\C^{\mathcal I}.
 \label{eq:tpc58-erasure-spaces}
\end{equation}
Both spaces carry their raw counting-measure inner products.  Attach a
possibly complex unit gauge
\begin{equation}
 \bm\mu_i=(\mu_{i,t})_{t\in\mathcal T_i},
 \qquad |\mu_{i,t}|=1,
 \label{eq:tpc58-unit-mobius-gauge}
\end{equation}
and define the erasure operator
\begin{equation}
 (C_\mu z)_i:=\sum_{t\in\mathcal T_i}\mu_{i,t}z_{i,t}.
 \label{eq:tpc58-erasure-operator}
\end{equation}
The classical squarefree M\"obius choice is real, but allowing a unitary
gauge makes the conjugation in the spectral projector visible.

For each fiber define
\begin{equation}
 \Pi_i z_i
 :=\frac{\overline{\bm\mu_i}}{k_i}
       \sum_{t\in\mathcal T_i}\mu_{i,t}z_{i,t}.
 \label{eq:tpc58-bright-projector}
\end{equation}
Thus \(\Pi_i\) is the orthogonal projector onto
\(\operatorname{span}\{\overline{\bm\mu_i}\}\), not in general onto
\(\operatorname{span}\{\bm\mu_i\}\).

\begin{theorem}[Exact erasure spectrum]
\label{thm:tpc58-exact-erasure-spectrum}
Let \(C_{\mu,i}:\C^{\mathcal T_i}\to\C\) denote the \(i\)-th block of
\(C_\mu\).  Then
\begin{align}
 C_{\mu,i}^*C_{\mu,i}&=k_i\Pi_i,
 \label{eq:tpc58-fiber-erasure-spectrum}\\
 C_\mu^*C_\mu&=\bigoplus_{i\in\mathcal I}k_i\Pi_i,
 \label{eq:tpc58-global-erasure-spectrum}\\
 \Ker C_\mu
 &=\bigoplus_{i\in\mathcal I}
   \left\{z_i:\sum_{t\in\mathcal T_i}\mu_{i,t}z_{i,t}=0\right\}.
 \label{eq:tpc58-exact-dark-space}
\end{align}
In particular,
\begin{equation}
 \rank C_\mu=|\mathcal I|,
 \qquad
 \dim\Ker C_\mu=\sum_{i\in\mathcal I}(k_i-1).
 \label{eq:tpc58-erasure-rank-nullity}
\end{equation}
The nonzero singular value on the \(i\)-th fiber is \(\sqrt{k_i}\).
\end{theorem}

\begin{proof}
In the standard coordinate convention the row of \(C_{\mu,i}\) is
\(\bm\mu_i^{\mathsf T}\), so
\begin{equation}
 C_{\mu,i}^*C_{\mu,i}
 =\overline{\bm\mu_i}\,\bm\mu_i^{\mathsf T}.
 \label{eq:tpc58-rank-one-outer-product}
\end{equation}
Its range is the line spanned by \(\overline{\bm\mu_i}\), and
\(\|\bm\mu_i\|^2=k_i\) by
\eqref{eq:tpc58-unit-mobius-gauge}.  This proves
\eqref{eq:tpc58-fiber-erasure-spectrum}.  Distinct fibers have disjoint
domain and range coordinates, hence the direct-sum identity
\eqref{eq:tpc58-global-erasure-spectrum}.  Each nonzero row has rank one,
and its kernel has dimension \(k_i-1\), which proves the remaining claims.
\end{proof}

\begin{remark}[The hypotheses behind the scalar \(k_i\)]
\label{rem:tpc58-erasure-weight-scope}
For a nonzero general row \(g_i=(g_{i,t})_t\), the exact identity is
\begin{equation}
 C_i^*C_i
 =\overline g_i g_i^{\mathsf T}
 =\|g_i\|^2\Pi_{\operatorname{span}(\overline g_i)}.
 \label{eq:tpc58-general-erasure-row}
\end{equation}
Thus the eigenvalue is \(k_i\) only when all \(k_i\) gauges have unit
modulus.  In particular, nonsquarefree labels carrying M\"obius value zero
cannot be counted among the \(k_i\) active unit-gauge labels.  Also, when
the numbers \(k_i\) vary, there is no global scalar \(k\) for which
\(C_\mu^*C_\mu=k\Pi\).
\end{remark}

\begin{proposition}[Sharp ambient obstruction]
\label{prop:tpc58-sharp-ambient-obstruction}
The best lower erasure constant on the entire canonical space is
\begin{equation}
 \alpha_{\rm amb}
 :=\inf_{0\ne z\in\mathcal Z}
   \frac{\|C_\mu z\|^2}{\|z\|^2}
 =
 \begin{cases}
  1,&k_i=1\text{ for every }i,\\
  0,&k_i\ge2\text{ for at least one }i.
 \end{cases}
 \label{eq:tpc58-sharp-ambient-constant}
\end{equation}
Both alternatives are sharp.
\end{proposition}

\begin{proof}
If every \(k_i=1\), then \(C_\mu\) is diagonal with unit-modulus entries
and is therefore unitary.  If \(k_i\ge2\), choose distinct labels
\(t,u\in\mathcal T_i\), set
\begin{equation}
 z_{i,t}=\mu_{i,u},
 \qquad z_{i,u}=-\mu_{i,t},
 \label{eq:tpc58-two-label-dark-vector}
\end{equation}
and set every other coordinate to zero.  This is a nonzero vector in
\(\Ker C_\mu\), so the infimum vanishes.
\end{proof}

The complex conjugation in
\eqref{eq:tpc58-bright-projector} is not cosmetic.  For example, if
\begin{equation}
 C=[\,1\ \ i\,],
 \label{eq:tpc58-complex-gauge-counterexample}
\end{equation}
then \(\Ran C^*=\operatorname{span}\{(1,-i)\}\).  Projecting instead onto
\(\operatorname{span}\{(1,i)\}\) reverses both off-diagonal signs and does
not give \(C^*C\).  Likewise, the row \([\,1\ \ 0\,]\) has two displayed
coordinates but nonzero eigenvalue one, not two; this is the smallest
counterexample to omitting the unit-gauge condition.

\subsection{Canonical aggregation is not physical uniqueness}

We record the exact sense in which the residual coordinate system is
canonical.  For each \(i\), let
\begin{equation}
 \mathcal T_i=\mathcal T_i^0\mathbin{\dot\cup}\mathcal S_i
 \label{eq:tpc58-canonical-label-partition}
\end{equation}
be a declared disjoint partition into no-high labels and residual labels.
For \(t\in\mathcal T_i^0\) let \(b_{i,t}\in\C\), and for
\(s\in\mathcal S_i\) let \(\mathcal P_{i,s}\) be a finite set with
coefficients \(b_{i,s,p}\).  Put
\begin{equation}
 B_{i,s}:=\sum_{p\in\mathcal P_{i,s}}b_{i,s,p},
 \qquad
 z_{i,t}:=b_{i,t},
 \qquad
 z_{i,s}:=-B_{i,s}.
 \label{eq:tpc58-canonical-residual-vector}
\end{equation}
Define
\begin{align}
 \cD_0
 &:=\sum_i\left(
      \sum_{t\in\mathcal T_i^0}|b_{i,t}|^2
      +\sum_{s\in\mathcal S_i}\sum_{p\in\mathcal P_{i,s}}
       |b_{i,s,p}|^2\right),
 \label{eq:tpc58-ambient-diagonal}\\
 \cD_H
 &:=\sum_i\sum_{s\in\mathcal S_i}
      \sum_{p\in\mathcal P_{i,s}}|b_{i,s,p}|^2,
 \label{eq:tpc58-high-diagonal}\\
 \cG_{\rm res}
 &:=\sum_i\sum_{s\in\mathcal S_i}|B_{i,s}|^2.
 \label{eq:tpc58-abstract-residual-grouped-energy}
\end{align}

\begin{proposition}[Canonical residual identity]
\label{prop:tpc58-canonical-residual-identity}
For the coefficient vector in
\eqref{eq:tpc58-canonical-residual-vector},
\begin{equation}
 \boxed{
 \cR_{\rm low}:=\|z\|^2
 =\cD_0-\cD_H+\cG_{\rm res}.}
 \label{eq:tpc58-canonical-low-energy}
\end{equation}
Equivalently,
\begin{equation}
 \cR_{\rm low}
 =\cD_0+2\operatorname{Re}
   \sum_i\sum_{s\in\mathcal S_i}
   \sum_{\substack{p,q\in\mathcal P_{i,s}\\p<q}}
   b_{i,s,p}\overline{b_{i,s,q}},
 \label{eq:tpc58-residual-signed-offdiagonal}
\end{equation}
after fixing any order on each finite prime set.
\end{proposition}

\begin{proof}
The declared partition
\eqref{eq:tpc58-canonical-label-partition} is orthogonal in
\(\mathcal Z\).  Hence
\[
 \|z\|^2
 =\sum_i\sum_{t\in\mathcal T_i^0}|b_{i,t}|^2
  +\sum_i\sum_{s\in\mathcal S_i}|B_{i,s}|^2,
\]
which is exactly
\eqref{eq:tpc58-canonical-low-energy}.  Expanding every \(|B_{i,s}|^2\)
and cancelling its diagonal contribution against \(-\cD_H\) gives
\eqref{eq:tpc58-residual-signed-offdiagonal}.
\end{proof}

The vector \(z\) is unique as the coefficient vector in the fixed
orthonormal coordinate family \((i,t)\).  This statement requires the
partition in \eqref{eq:tpc58-canonical-label-partition} to have been fixed
first; it neither recovers the separate coefficients inside a sum
\(B_{i,s}\) nor makes \(z\) unique from \(C_\mu z\).  Its support is the
smallest subset of this particular orthonormal coordinate family that
represents \(z\), but the fixed baseline label bank need not be minimal for
one realized coefficient vector.  Indeed,
\begin{equation}
 b_{i,s,p}=1,
 \qquad b_{i,s,q}=-1
 \label{eq:tpc58-cancelled-residual-counterexample}
\end{equation}
gives \(z_{i,s}=0\), even though two baseline atoms occur.  At the physical
erasure level, the one-fiber vectors \((1,0)\) and \((0,1)\) have the same
image under \([\,1\ \ 1\,]\).  Thus ``canonical'', ``minimal'', and
``physically identifiable'' are three different assertions.

\subsection{The signed native off-diagonal}

Put
\begin{equation}
 (v_0)_i:=\sum_{t\in\mathcal T_i^0}\mu_{i,t}b_{i,t},
 \qquad
 w_i:=\sum_{s\in\mathcal S_i}\mu_{i,s}B_{i,s}.
 \label{eq:tpc58-vzero-and-w}
\end{equation}
Then the erasure of the canonical residual vector is
\begin{equation}
 \boxed{C_\mu z=v_0-w.}
 \label{eq:tpc58-erased-affine-difference}
\end{equation}
The exact coordinate expansion is
\begin{align}
 \|C_\mu z\|^2
 ={}&\|z\|^2
 +2\operatorname{Re}\sum_i
   \sum_{\substack{t,u\in\mathcal T_i^0\\t<u}}
   \mu_{i,t}\overline{\mu_{i,u}}
   b_{i,t}\overline{b_{i,u}}
 \notag\\
 &+2\operatorname{Re}\sum_i
   \sum_{\substack{s,r\in\mathcal S_i\\s<r}}
   \mu_{i,s}\overline{\mu_{i,r}}
   B_{i,s}\overline{B_{i,r}}
 \notag\\
 &-2\operatorname{Re}\sum_i
   \sum_{\substack{t\in\mathcal T_i^0\\s\in\mathcal S_i}}
   \mu_{i,t}\overline{\mu_{i,s}}
   b_{i,t}\overline{B_{i,s}}.
 \label{eq:tpc58-complete-signed-offdiagonal}
\end{align}
Thus erasure restores all unequal-low-label cross terms.  The mixed
no-high/residual terms have a minus sign, while the no-high/no-high and
residual/residual terms have a plus sign.  For a complex gauge the factor is
\(\mu_{i,t}\overline{\mu_{i,u}}\); it cannot be replaced by a formal
\(\mu(tu)\) without additional coprimality and reality hypotheses.

If
\begin{equation}
 (v_p)_i
 :=\sum_{\substack{s\in\mathcal S_i\\p\in\mathcal P_{i,s}}}
   \mu_{i,s}b_{i,s,p},
 \label{eq:tpc58-individual-high-vectors}
\end{equation}
then \(w=\sum_pv_p\) and
\begin{equation}
 \boxed{
 \|v_0-w\|^2
 =\|v_0\|^2+\sum_p\|v_p\|^2
  +2\operatorname{Re}\sum_{p<q}\langle v_p,v_q\rangle
  -2\operatorname{Re}\sum_p\langle v_0,v_p\rangle.}
 \label{eq:tpc58-affine-signed-expansion}
\end{equation}
No positive lower comparison with \(\|z\|^2\) follows from the diagonal
terms alone.  The minimal sharp example is
\begin{equation}
 C=[\,1\ \ 1\,],
 \qquad z=(1,-1),
 \qquad \|z\|^2=2,
 \qquad \|Cz\|^2=0.
 \label{eq:tpc58-sharp-native-cancellation}
\end{equation}
The restricted-range analysis in the next section identifies exactly what
additional coefficient geometry is needed to exclude this dark direction.
