\section{Transport boundaries, the signed native exchange, and the endpoint ledger}
\label{sec:tpc58-transport-ledger}

The exact transfer theorem does not make either restricted-range constant
positive.  This section explains why the two preceding papers do not supply
that positivity, identifies the literal signed quadratic form that would
supply it, and records the complete endpoint charge.

\subsection{Why the adaptive phase sector does not transport}

TPC--56 extracts a constant-energy subpacket after the terminal phases have
been observed.  Its selector is a genuine coordinate projection once it is
chosen, but it is not a coefficient-independent pre-terminal criterion
\citep{WangTPC56}.  More basically, squared norms are not monotone under
putting the deleted coordinates back into a coherent sum.

\begin{proposition}[Sharp adaptive nontransport]
\label{prop:tpc58-adaptive-nontransport}
There is no constant \(c>0\) for which the grouped energy of the undeleted
residual packet, or the complete native affine energy of the declared
slice, is bounded below by
\(c\) times the grouped energy of every phase-adaptively selected terminal
subpacket.  This failure already occurs in one two-atom residual fiber.
\end{proposition}

\begin{proof}
Take two terminal coordinates in one residual fiber with amplitudes \(1\)
and \(-1\).  They lie in distinct phase sectors.  A sector containing either
coordinate has terminal diagonal and selected grouped energy equal to one,
whereas restoring the other coordinate makes the undeleted grouped amplitude
zero.  After a common phase rotation avoiding sector boundaries, the two
antipodal amplitudes occupy distinct members of the five equal sectors of
TPC--56.  Since the
native and affine maps are downstream of this already vanishing undeleted
residual amplitude, no positive lower bound for either downstream quantity
can follow.  The zero lower endpoint is attained, so the obstruction is
sharp.
\end{proof}

The proposition does not weaken the TPC--56 selected-square theorem.  It
states that the selected theorem may enter a physical chain only if the same
selection is realized before terminal primality and is preserved by every
later operation, or if a separate lower-reassembly theorem is proved.  No
such realization is assumed here.

\subsection{What the singleton theorem does and does not preserve}

TPC--57 instead works with the undeleted residual packet.  For
\(y=(i,s)\), let
\begin{equation}
 A_{i,s}:=\sum_{u\in\cF_y^{\rm term}}x_u,
 \qquad
 \cG_{\rm res}:=\sum_{i,s}|A_{i,s}|^2.
 \label{eq:tpc58-residual-grouped-energy}
\end{equation}
Its singleton theorem applies to the first grouping
\begin{equation}
 \{\text{terminal primes}\}\longrightarrow(i,s).
 \label{eq:tpc58-first-grouping}
\end{equation}
The native high column applies the different, second grouping
\begin{equation}
 (i,s)\longrightarrow i,
 \qquad
 H_i:=\sum_sA_{i,s}.
 \label{eq:tpc58-second-grouping}
\end{equation}

\begin{proposition}[Singleton survival stops at the residual label]
\label{prop:tpc58-singleton-stops-at-residual}
If a terminal-prime fiber \(y=(i,s)\) is a physical singleton, then its
energy survives the first grouping exactly.  Even if every active first-stage
fiber is a singleton, however, there is no positive support-only lower bound
for
\begin{equation}
 \cN_H:=\sum_i|H_i|^2
 \label{eq:tpc58-native-high-energy}
\end{equation}
in terms of \(\cG_{\rm res}\).
\end{proposition}

\begin{proof}
The first assertion is the identity
\(\left|\sum_{u\in\cF_y}x_u\right|^2=|x_u|^2\) on a singleton.  For the
second, take one native output \(i\), two distinct residual labels
\(s_1,s_2\), and one terminal atom in each residual fiber.  Choose their
already physical amplitudes to be
\(A_{i,s_1}=1\) and \(A_{i,s_2}=-1\).  Then
\(\cG_{\rm res}=2\), while \(H_i=0\) and \(\cN_H=0\).  Thus perfect
singleton occupancy at the first grouping does not control the second
grouping.
\end{proof}

Accordingly, the singleton exponent of TPC--57 and the native high-transfer
exponent below are separate entries.  The factor-exchange theorem of
TPC--57 studies collisions with equal \(s\); the new native gate consists of
cross terms with unequal \(s\).

\subsection{The exact signed native exchange}

Return to the literal fixed-\(h_0\) amplitudes
\begin{equation}
 x_u=c_u\zeta_{m(u)},
 \qquad
 q(u)=(i,s(u)),
 \qquad
 s(u)=d_{m(u)}r_u,
 \label{eq:tpc58-literal-terminal-factorization}
\end{equation}
where \(i\) contains the side, opposite row, and orbit time.  Every active
atom satisfies
\begin{equation}
 p_ur_u-m(u)j_u=h_0.
 \label{eq:tpc58-fixed-shift-equation}
\end{equation}
Choose any fixed total order on the finite residual-label set in each native
fiber.

\begin{proposition}[Exact native exchange identity]
\label{prop:tpc58-native-exchange-identity}
The difference between the native high energy and the residual grouped
energy is
\begin{align}
 \cN_H-\cG_{\rm res}
 &=2\operatorname{Re}
   \sum_i\sum_{s<t}A_{i,s}\overline{A_{i,t}}
 \label{eq:tpc58-native-exchange-residual}\\
 &=2\operatorname{Re}
   \sum_i\sum_{s<t}
   \sum_{\substack{u:q(u)=(i,s)}}
   \sum_{\substack{v:q(v)=(i,t)}}
   c_u\overline{c_v}\,
   \zeta_{m(u)}\overline{\zeta_{m(v)}}.
 \label{eq:tpc58-native-exchange-atoms}
\end{align}
In every summand of \eqref{eq:tpc58-native-exchange-atoms}, both atoms
satisfy \eqref{eq:tpc58-fixed-shift-equation}, but
\begin{equation}
 d_{m(u)}r_u=s\ne t=d_{m(v)}r_v.
 \label{eq:tpc58-unequal-residual-condition}
\end{equation}
Hence the same-residual factor-exchange divisibility from TPC--57 is not
available for this sum.
\end{proposition}

\begin{proof}
Expanding the square in \eqref{eq:tpc58-second-grouping} gives
\[
 |H_i|^2
 =\sum_s|A_{i,s}|^2
  +2\operatorname{Re}\sum_{s<t}A_{i,s}\overline{A_{i,t}}.
\]
Summing over \(i\) proves \eqref{eq:tpc58-native-exchange-residual}.
Substitution of \eqref{eq:tpc58-literal-terminal-factorization} proves
\eqref{eq:tpc58-native-exchange-atoms}.  The index condition \(s<t\)
implies \eqref{eq:tpc58-unequal-residual-condition}.  In contrast, the
factor-exchange identity begins with equality of the two residual products,
so its hypothesis fails here.
\end{proof}

The absence of the factor-exchange divisibility does not say that
\eqref{eq:tpc58-native-exchange-atoms} is large or negative.  It says that a
new signed estimate is required.  An absolute pair count is generally too
coarse because the desired information is one-sided spectral control.

To state the exact target, assume the high coefficient map is nonzero and let
\begin{equation}
 R_H:=T_H^*T_H,
 \qquad
 N_H:=T_H^*C_{\mu,H}^*C_{\mu,H}T_H,
 \label{eq:tpc58-high-Gram-pair}
\end{equation}
so that \(\Ran R_H\ne\{0\}\), and on \(\Ran R_H\) define
\begin{equation}
 \Theta_H
 :=R_H^{\dagger/2}(N_H-R_H)R_H^{\dagger/2}.
 \label{eq:tpc58-high-relative-defect}
\end{equation}

\begin{corollary}[Exact negative-spectrum gate]
\label{cor:tpc58-negative-spectrum-gate}
For \(0<\delta\le1\), the uniform estimate
\begin{equation}
 \cN_H(\zeta)\ge\delta\,\cG_{\rm res}(\zeta)
 \qquad\text{for every }\zeta
 \label{eq:tpc58-uniform-native-high-lower}
\end{equation}
is equivalent to
\begin{equation}
 \lambda_{\min}(\Theta_H)\ge-1+\delta.
 \label{eq:tpc58-negative-spectrum-condition}
\end{equation}
Equivalently, the signed exchange form must satisfy
\begin{equation}
 2\operatorname{Re}
 \sum_i\sum_{s<t}A_{i,s}\overline{A_{i,t}}
 \ge-(1-\delta)\cG_{\rm res}
 \label{eq:tpc58-exchange-form-target}
\end{equation}
for every coefficient vector.  Only the negative spectrum must be
controlled; no upper bound for the positive exchange is required.
\end{corollary}

\begin{proof}
On \(\Ran R_H\), the generalized native Gram is
\[
 R_H^{\dagger/2}N_HR_H^{\dagger/2}=I+\Theta_H.
\]
The Rayleigh--Ritz principle makes
\eqref{eq:tpc58-uniform-native-high-lower} equivalent to
\eqref{eq:tpc58-negative-spectrum-condition}.  The identity in
\cref{prop:tpc58-native-exchange-identity} gives the equivalent form
\eqref{eq:tpc58-exchange-form-target}.
\end{proof}

For a distinguished coefficient vector, the weakest pointwise target is
just \eqref{eq:tpc58-exchange-form-target} for that vector.  Proving it
uniformly over the bounded row-coefficient cube is stronger and is exactly
the positivity of the restricted constant \(\alpha_H\).

\subsection{The strict endpoint ledger}

Let \(\cD_{\rm par}\) be the raw parent atomic energy on one declared
carrier.  The endpoint very-high cutoff forces the smaller cofactor range
\eqref{eq:tpc58-compatible-cofactor-ceiling}, so first suppose that a lower
relocation transfer from the inherited parent packet into a compatible
cofactor band has been proved.  Suppose further that selection,
cofactor-block occupancy, terminal activation, and the undeleted TPC--57
singleton bridge have given
\begin{equation}
 \cG_{\rm res}
 \ge
 X^{-(\lambda_{\rm reloc}+\lambda_{\rm sel}+\lambda_{\rm blk}
      +\lambda_{\rm term}+\lambda_{\rm sing})+o(1)}
 \cD_{\rm par}.
 \label{eq:tpc58-upstream-residual-lower}
\end{equation}
Here \(\lambda_{\rm reloc}\ge0\) records the parent-to-compatible-band
loss and is not absorbed silently into \(\lambda_{\rm blk}\).  This is a
conditional input: TPC--57 neither proves this relocation nor proves the
remaining occupancy and activation transfers asymptotically.  On the
inherited \(R\asymp J\) carrier, the fixed-\(\eta\) very-high face is in
fact empty for all sufficiently large \(X\).

Assume also
\begin{equation}
 \alpha_H\ge X^{-\lambda_H+o(1)},
 \qquad
 \delta_{\rm aff}\ge X^{-\lambda_{\rm aff}+o(1)},
 \label{eq:tpc58-two-Gram-losses}
\end{equation}
with nonnegative exponents.  Boundary restriction and tail reconstruction,
if available as lower transfers, are assigned losses
\(\lambda_{\rm bdry}\) and \(\lambda_{\rm tail}\).

\begin{proposition}[Conditional endpoint propagation]
\label{prop:tpc58-endpoint-propagation}
Under the preceding lower-transfer hypotheses, the prospective final
physical quantity satisfies
\begin{equation}
 \cN_{\rm final}
 \ge X^{-\Lambda_{\rm tot}+o(1)}\cD_{\rm par},
 \label{eq:tpc58-prospective-final-lower}
\end{equation}
where
\begin{equation}
 \boxed{
 \begin{aligned}
 \Lambda_{\rm tot}
 :={}&\lambda_{\rm reloc}+\lambda_{\rm sel}+\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm sing}\\
 &+\lambda_H+\lambda_{\rm aff}
 +\lambda_{\rm bdry}+\lambda_{\rm tail}.
 \end{aligned}}
 \label{eq:tpc58-total-endpoint-exponent}
\end{equation}
Thus the safe endpoint requirement is
\begin{equation}
 \boxed{\Lambda_{\rm tot}<\frac1{400}.}
 \label{eq:tpc58-strict-endpoint-budget}
\end{equation}
At equality, a separate closed constant-level comparison and quantified
control of every \(o(1)\) term are required; equality of formal exponents
alone does not absorb an error of size
\(X^{-1/400+o(1)}\cD_{\rm par}\).
\end{proposition}

\begin{proof}
Apply \cref{thm:tpc58-two-stage-affine-transfer} to
\eqref{eq:tpc58-upstream-residual-lower}, then multiply the two assumed
Gram transfers and the downstream boundary and tail transfers.  Polynomial
loss exponents add, giving \eqref{eq:tpc58-total-endpoint-exponent}.  If
\(\Lambda_{\rm tot}<1/400\), the main lower scale dominates an additive
\(X^{-1/400+o(1)}\cD_{\rm par}\) error by a fixed power.  When the two
exponents are equal, the unspecified constants and \(o(1)\) terms decide
the sign, so exponent bookkeeping alone is insufficient.
\end{proof}

For the direct already-reassembled fixed-\(h_0\) route, no frozen-shift
localization or projective-reassembly exponent is inserted.  If another
route passes through a completed frozen family or a signed projective
decomposition, its localization and lower-reassembly losses must be restored
in \eqref{eq:tpc58-total-endpoint-exponent}.  It is convenient to record
\begin{equation}
 \lambda_{\rm Gram}:=\lambda_H+\lambda_{\rm aff},
 \label{eq:tpc58-Gram-loss-split}
\end{equation}
but the two terms must remain separately auditable because their kernels are
independent.
