\section{Barriers, order of operations, and strict scope}
\label{sec:barriers-scope}

The positive theorem depends on several exact choices.  This section
separates them from tempting but invalid shortcuts.

\subsection{A low-conductor repetition no-go}

The exact-conductor decomposition is not optional.  Set
\(S\asymp N^{1/2}\), fix a nonprincipal primitive character
\(\chi_0\bmod f_0\) of fixed squarefree conductor \(f_0>1\), and
induce it to squarefree moduli \(s=f_0d\asymp S\).  Take
\[
 a_n=\overline{\chi_0(n)}\one_{1\le n\le N}.
\]
Restrict \(d\) to primes in a fixed dyadic interval, excluding the
finitely many divisors of \(f_0\).  The prime number theorem and direct
inclusion--exclusion give
\[
 \left|\sum_na_n\chi_s(n)\right|
 =\sum_{\substack{n\le N\\(n,f_0d)=1}}1
 =N\frac{\varphi(f_0d)}{f_0d}+O(\tau(f_0d))
 \gg_{f_0}N.
\]
Consequently the weighted sum over these \(d\asymp S/f_0\) has size
\begin{equation}
 \gg \frac{N^2}{f_0\log S}.
 \label{eq:induced-repetition-lower}
\end{equation}
An estimate treating these characters as primitive at ambient scale
would have only \(N^{3/2+o(1)}\) on the
right.  This is an operator obstruction to the false large sieve, not a
lower bound for the actual TPC scalar packet.

\subsection{Four orders that cannot be interchanged}

\begin{enumerate}[label=\textup{(\roman*)}]
 \item \emph{Divisor pair before rectangular coordinates.}
 Different \((u,v)\) with the same lcm use different products
 \(\mathfrak X(u)\times\mathfrak X(v/(u,v))\).  A common global
 \((F_1,F_2)\)-coordinate is not defined.

 \item \emph{Exact conductor before the Ramanujan frequency sum.}
 Inside one dyadic block, \(c_{q/(f_1f_2)}(r)\) still depends on the
 exact conductors.  We first apply \eqref{eq:exact-direct-bound} at
 exact \(f_1,f_2\), then pay the divisor-soft dyadic reassembly.

 \item \emph{Remove zero frequency before
 \cref{lem:Ramanujan-Fourier}.}
 If \(r=0\) were included, \(c_s(0)=\varphi(s)\) would destroy
 \eqref{eq:Fourier-multiples} when \(e>K\).  The selected Poisson packet
 already has \(r\ne0\).

 \item \emph{Keep the mask before nonlinear energy.}
 Estimate \eqref{eq:compatibility-energy} uses the actual off-diagonal
 support.  Deleting the mask before squaring would restore \(m=n\), for
 which every shared factor divides the difference.
\end{enumerate}

\subsection{Why this is not a projective-mask theorem}

Some mask components admit inexpensive separated representations, but
the divisor-gcd cutoff does not automatically have a sufficiently small
naive projective norm.  The tensor proof avoids the issue:
\(c_{m,n}^{(g)}\) is arbitrary.  It does require the same matrix while
the output moduli vary for fixed \(g\).  A mask depending on \(u,v\) or
\(q\) is therefore not covered without a new argument.

The large shared-factor and moment-diagonal bounds obtainable directly
from TPC-21 remain useful cross-checks, but they are not needed to
manufacture the saving here.  The power saving comes from product
coordinates, the weighted conductor large sieve, and the complementary
induced-Gauss estimate.

\subsection{Closed and open objects}

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.41\textwidth}
                >{\raggedright\arraybackslash}p{0.48\textwidth}}
\toprule
Object & Status after TPC-22\\
\midrule
Ramanujan mean of the selected short--short packet
& Closed in TPC-21 and imported through
  \eqref{eq:imported-mean-bound}.\\
\addlinespace
Connected discrepancy of the same packet, with the actual
row-pair-only generic mask
& Closed in the parameter regions of
  \cref{thm:main-closure}.\\
\addlinespace
One-sided residual terms with \(u>R\) or \(v>R\)
& Not represented by \eqref{eq:lcm-fiber}; open.\\
\addlinespace
Uniform restoration of all earlier normal-form pieces and endpoint
terms in the full TPC-18 residual
& Not proved by the selected-packet estimate; open.\\
\addlinespace
Hardy--Littlewood asymptotic, twin-prime lower bound, or parity breach
& Not claimed and not implied.\\
\bottomrule
\end{tabular}
\end{center}

The phrase \emph{selected short--short closure} always refers to the
first two rows of this table.  It is not an abbreviation for the full
residual-dispersion theorem.

\subsection{Parity}

The character tensor supplies cancellation in a previously unresolved
analytic norm.  It does not alter the sign-insensitivity of the
underlying upper-bound sieve and does not produce a positive lower bound
for prime pairs.  Nothing here distinguishes an actual prime-pair main
term from every parity-compatible surrogate at the final sieve stage.
The theorem is a rigorous advance inside the TPC normal form, not a
claim to have crossed the classical parity barrier.
