\section{Exact finite certificate and conclusion}
\label{sec:certificate-conclusion}

The proofs above are symbolic.  A deterministic finite certificate is
included to audit the identities most vulnerable to normalization or
coordinate errors.  It is not numerical evidence for an unproved
asymptotic and is not used to replace any analytic estimate.

\subsection{Certificate design}

The script
\[
 \texttt{experiments/tpc22\_certificate.py}
\]
uses only the Python standard library.  Roots of unity are represented
exactly in \(\mathbf F_{61}\), whose multiplicative group contains the
orders needed for the squarefree test moduli.  Rational exponent
calculations use \texttt{fractions.Fraction}.

The primary model is
\[
 q=30,\qquad (u,v)=(10,15),\qquad (g,a,b)=(5,2,3),
\]
together with the reversed divisor pair.  The certificate checks:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item the shared-\(g\) convolution and
 \eqref{eq:exact-rectangularization} character by character;
 \item both product-coordinate choices and exact conductor
 multiplication;
 \item the identification of the global principal character with the
 joint principal coordinate, while retaining one-sided principal modes;
 \item the induced-character Gauss formula at every residue frequency,
 including frequencies not coprime to \(q\);
 \item the exact rational low--low, high--high, and mixed ledger;
 \item the two actual-tail profile endpoint intervals, gains, and
 arithmetic endpoint-stability thresholds.
\end{enumerate}

Hard-failure variants deliberately omit compatibility, replace
\(b=v/g\) by \(v\), omit the shared \(g\)-character, retain an extra
\(1/\varphi(g)\), or delete a one-sided principal block.  Each altered
formula is required to disagree with the exact model.  The ordinary and
\texttt{python -O} runs must produce byte-identical JSON, so correctness
does not depend on Python assertions.  All flags for a twin-prime
result, Hardy--Littlewood asymptotic, full residual closure, or parity
breakthrough are set to false.

The archived run performs \(346\) exact checks.  Its JSON and source
SHA-256 hashes are, respectively,
\begin{center}
\nolinkurl{772aa4a68009d2ffb7960f2d27db287e52c7a80aa7cd915293e4fc8dea3fa934}

\nolinkurl{2cc5e3fcdab3a51950f60c726ba8d64a96542c5fde115ac32545834be54e2964}
\end{center}
The certificate digest is
\begin{center}
\nolinkurl{c93ff8e6755ab0db536621e3b2c2b3f8332950da0a5784f60138912a2159fab8}.
\end{center}

\subsection{Conclusion}

The shared-factor character convolution left by TPC-21 is not an
irreducible fourth-moment obstruction.  Pairwise character
orthogonality turns it into an arbitrary compatibility matrix tested by
two independent character coordinates.  Exact conductor resolution
then exposes two complementary estimates:
\[
 Q\sqrt{JY\cK_Q(F_1)\cK_Q(F_2)}
\]
from the inherited norm route, and
\[
 QF_1F_2\sqrt{\cK_Q(F_1)\cK_Q(F_2)}
\]
from the direct induced-Gauss route.  Neither dominates everywhere, but
their conductor cells cover the complete selected short--short range in
the stated profiles with a fixed power margin.

This closes one concrete analytic gate and removes the arbitrary-fiber
obstruction for the actual generic mask in that packet.  The remaining
route to the full fixed-shift problem still includes the large-divisor
legs and global residual reassembly, followed eventually by the
classical parity obstruction.  Those are separate problems; no claim
about them is encoded in the present closure theorem.
