\section{A weighted exact-conductor large sieve}
\label{sec:exact-conductor-sieve}

The primitive multiplicative large sieve states that, for coefficients
on an interval of length \(N\),
\begin{equation}
 \sum_{f\le T}\frac f{\varphi(f)}
 \sum_{\chi^*\ (\bmod f)}^*
 \left|\sum_na_n\chi^*(n)\right|^2
 \ll (T^2+N)\sum_n|a_n|^2
 \label{eq:primitive-large-sieve}
\end{equation}
\citep[Chapter~7]{IwaniecKowalski2004}.  We need a normalization that
keeps the exact conductor while the ambient modulus varies.

\begin{theorem}[Weighted exact-conductor large sieve]
\label{thm:exact-conductor-large-sieve}
Let \(a_n\) be supported on an interval of length at most \(N\).  Let
\(s\asymp S\) run over squarefree moduli, and let
\(\cond\chi\asymp F\) denote a dyadic exact-conductor block, with the
block \(F=1\) containing only conductor one.  If all parameters are at
most \(X^{O(1)}\), then
\begin{equation}
 \boxed{
 \sum_{\substack{s\asymp S\\s\ {\rm squarefree}}}
 \frac1{\varphi(s)}
 \sum_{\substack{\chi\in\mathfrak X(s)\\\cond\chi\asymp F}}
 \left|\sum_na_n\chi(n)\right|^2
 \ll_\eps X^\eps
 \left(F+\frac NF\right)\sum_n|a_n|^2.}
 \label{eq:exact-conductor-large-sieve}
\end{equation}
The implied constant is uniform in the location of the coefficient
interval and in \(S\).
\end{theorem}

\begin{proof}
First suppose \(F>1\).  If \(\chi\bmod s\) has exact conductor \(f\),
then \(s=fd\), \((f,d)=1\), and the squarefree hypothesis makes the
factorization unique.  For the inducing primitive character
\(\chi^*\bmod f\),
\begin{equation}
 \chi(n)=\chi^*(n)\one_{(n,d)=1}.
 \label{eq:induced-zero-extension}
\end{equation}
For fixed \(d\), set \(a_n^{(d)}=a_n\one_{(n,d)=1}\).  The conditions
\(s\asymp S\), \(f\asymp F\) confine \(d\) to
\(d\asymp S/F\), up to a bounded dyadic refinement.  Moreover
\begin{equation}
 \frac1{\varphi(fd)}
 =\frac1{fd}\frac f{\varphi(f)}\frac d{\varphi(d)}
 \ll_\eps \frac{X^\eps}{S}\frac f{\varphi(f)}.
 \label{eq:exact-conductor-weight}
\end{equation}
Dropping coprimality and range restrictions only enlarges the
nonnegative sum.  Applying \eqref{eq:primitive-large-sieve} in \(f\)
for each \(d\) gives
\[
 \frac{X^\eps}{S}(F^2+N)\sum_n|a_n^{(d)}|^2
 \le \frac{X^\eps}{S}(F^2+N)\sum_n|a_n|^2.
\]
There are \(O(S/F)\) possible \(d\), so the total is
\[
 \ll X^\eps \frac{F^2+N}{F}\sum_n|a_n|^2,
\]
which is \eqref{eq:exact-conductor-large-sieve}.

For \(F=1\), the only character modulo \(s\) is the principal character
induced from modulus one.  By Cauchy--Schwarz,
\[
 \left|\sum_{(n,s)=1}a_n\right|^2
 \le N\sum_n|a_n|^2.
\]
The standard dyadic estimate
\(\sum_{s\asymp S}1/\varphi(s)\ll_\eps X^\eps\) then gives
\[
 \ll X^\eps N\sum_n|a_n|^2,
\]
which is bounded by the right side of
\eqref{eq:exact-conductor-large-sieve} with \(F=1\).
\end{proof}

\begin{remark}[Why conductor one matters]
\label{rem:conductor-one}
A fixed primitive character is repeated on every ambient modulus to
which it induces, with an additional coprimality cutoff as in
\eqref{eq:induced-zero-extension}.  Thus a principle treating all
nonprincipal characters as primitive characters of size \(S\) is
false.  The factor \(F+N/F\) retains low-conductor repetition.  In the
two-dimensional application, blocks with \(F_1=1<F_2\) or
\(F_2=1<F_1\) are genuine connected modes and must not be deleted.
\end{remark}

The theorem also has a Hilbert-valued form.  If \(a_n\) takes values in
a finite-dimensional Hilbert space \(\mathcal H\), then
\begin{equation}
 \sum_{s\asymp S}\frac1{\varphi(s)}
 \sum_{\cond\chi\asymp F}
 \left\|\sum_na_n\chi(n)\right\|_{\mathcal H}^2
 \ll_\eps X^\eps\left(F+\frac NF\right)
 \sum_n\|a_n\|_{\mathcal H}^2.
 \label{eq:Hilbert-exact-conductor}
\end{equation}
Expand in an orthonormal basis, apply
\cref{thm:exact-conductor-large-sieve} coordinatewise, and sum.
