\section{Introduction}
\label{sec:introduction}

After smooth separation, one-leg completion, and compression of the
compatible inverse phases, TPC-20 represents a selected short--short
piece of a primitive M\"obius residual correlation by one finite Fourier
transform on each unit fiber modulo a squarefree least common multiple
\citep{WangTPC18,WangTPC20}.  TPC-21 closes the constant, or
Ramanujan-mean, mode and identifies the centered part exactly as a
nonprincipal multiplicative-character energy \citep{WangTPC21}.

That energy retains the provenance of both rows, but its initial form
appears coupled.  If
\[
 g=(u,v),\qquad u=ga,\qquad v=gb,\qquad q=[u,v]=gab,
\]
then \(g,a,b\) are pairwise coprime and TPC-21 obtains
\begin{equation}
 \widehat Z_{u,v}^{\,\mathfrak m,\times}(\chi)
 =\frac{\overline{\chi(-h)}}{\varphi(g)}
 \sum_{\psi\in\mathfrak X(g)}
 \cB_{\mathfrak m}^{u,v}
 \bigl((\chi_g\psi)\boxtimes\chi_a,
       \overline\psi\boxtimes\chi_b\bigr).
 \label{eq:intro-shared-convolution}
\end{equation}
The actual generic row-pair mask \(\mathfrak m\) cannot be discarded
merely to factor \(\cB_{\mathfrak m}\) into two Dirichlet polynomials.

The first observation here is that the convolution is exactly
rectangular.  Character orthogonality gives
\begin{equation}
 \frac1{\varphi(g)}\sum_{\psi\bmod g}
 \cB_{\mathfrak m}^{u,v}
 \bigl((\chi_g\psi)\boxtimes\chi_a,
       \overline\psi\boxtimes\chi_b\bigr)
 =\sum_{m,n}c_{m,n}\one_{m\equiv n\ (g)}
   (\chi_g\boxtimes\chi_a)(m)\chi_b(n),
 \label{eq:intro-rectangularization}
\end{equation}
where \(c_{m,n}=x_my_n\mathfrak m(m,n)\).  Since \(q=ub\) and
\((u,b)=1\),
\begin{equation}
 \mathfrak X(q)\simeq\mathfrak X(u)\times\mathfrak X(b),
 \label{eq:intro-product-coordinates}
\end{equation}
and the two exact conductors multiply to \(\cond\chi\).  The shared
factor remains, correctly, as compatibility inside an arbitrary matrix.

The coordinates in \eqref{eq:intro-product-coordinates} depend on
\((u,v)\).  Different lcm decompositions of the same \(q\) do not share
one common rectangle.  We therefore split by divisor pair first, use
triangle or Cauchy over at most \(3^{\omega(q)}\) pairs, and only then
rectangularize.  The cost is \(X^{o(1)}\).

\subsection{Two complementary conductor estimates}

For coefficients on an interval of length \(N\), the primitive large
sieve \citep[Chapter~7]{IwaniecKowalski2004} gives the weighted estimate
\begin{equation}
 \sum_{\substack{s\asymp S\\s\ {\rm squarefree}}}\frac1{\varphi(s)}
 \sum_{\substack{\chi\ (\bmod s)\\\cond\chi\asymp F}}
 \left|\sum_na_n\chi(n)\right|^2
 \ll_\eps X^\eps
 \left(F+\frac NF\right)\sum_n|a_n|^2.
 \label{eq:intro-exact-conductor-LS}
\end{equation}
Conductor one is included, so repeated induced principal characters are
not silently removed.  Applying this estimate in both coordinates of
\eqref{eq:intro-rectangularization} works for an arbitrary matrix and
does not require a rank-one decomposition of the mask.

The second route uses the exact induced Gauss sum.  If
\(f=\cond\chi\mid q\), \(d=q/f\), and \(q\) is squarefree, then
\begin{equation}
 |G_q(\chi;r\overline H)|
 =\begin{cases}
   \sqrt f\,|c_d(r)|,&(r,f)=1,\\
   0,&(r,f)>1.
  \end{cases}
 \label{eq:intro-induced-Gauss}
\end{equation}
No condition \((r,q)=1\) is imposed.  Rapid Fourier decay gives
\begin{equation}
 \sum_{r\ne0}|c_d(r)|
 \left|\widehat F\left(\frac{rJ}{Hq}\right)\right|
 \ll_{F,H,\eps}X^\eps\frac qJ\tau(d),
 \label{eq:intro-Ramanujan-weight}
\end{equation}
which cancels the Poisson normalization \(J/q\).  The direct-Gauss
route is strongest at low coordinate conductor, while the inherited
fiber-norm route is strongest at high conductor.

\subsection{The saving ledger}

Write
\[
 Q=X^{\beta+o(1)},\quad J=X^{1-\beta+o(1)},\quad
 Y=X^{y+o(1)},\quad F_i=X^{f_i+o(1)},
\]
and put \(k_i=\max\{f_i,\beta-f_i\}\).  Relative to
\(Q^2J=XQ\), the two routes save
\begin{align}
 \eta_A&=\frac{\beta+1-y-k_1-k_2}{2},
 \label{eq:intro-eta-A}\\
 \eta_B&=1-f_1-f_2-\frac{k_1+k_2}{2}.
 \label{eq:intro-eta-B}
\end{align}
Since \(f_i\le1/2-\delta\) and \(y\le1-2\delta\), a low--low,
high--high, and mixed split gives
\begin{equation}
 \eta_*(\beta,\delta)
 =\min\left\{
  1-\frac{3\beta}{2},
  \frac{\beta+4\delta-1}{2},
  \frac{6\delta-\beta}{4}
 \right\}.
 \label{eq:intro-eta-star}
\end{equation}
This certified lower bound is positive in the strict region
\begin{equation}
 1-4\delta<\beta<\min\left\{\frac23,6\delta\right\}.
 \label{eq:intro-hybrid-region}
\end{equation}
It is not claimed to be the exact minimax of the two estimates.

For \(\beta<2\delta\) with a fixed margin, TPC-21 occupancy already
closes every \(Y\le R^2\); equality has no top-block power margin.  In
the two actual inherited tail profiles, \(\beta\) ranges from
\(\log_X(LD_0)\) to \(\log_X(LR^{1/2})\).  The entire interval lies in
\eqref{eq:intro-hybrid-region} in the strict ranges proved below.

\subsection{Scope and organization}

We close the centered discrepancy for the actual row-pair-only generic
mask in the selected short--short packet of TPC-20--21.  With the
already closed mean, this closes that selected packet.  We do not treat
either residual leg with a divisor exceeding \(R\), prove the full
TPC-18 residual-dispersion target, obtain a prime-pair asymptotic, or
breach sieve parity.

\Cref{sec:interface} fixes the packet.  \Cref{sec:rectangularization}
proves the pairwise identity.  \Cref{sec:exact-conductor-sieve} proves
\eqref{eq:intro-exact-conductor-LS}; \cref{sec:tensor-energy} tensorizes
it with the mask retained.  \Cref{sec:gauss-complementarity} proves the
all-frequency Gauss route, and \cref{sec:exponent-closure} completes the
conductor and profile ledger.  The final sections record barriers,
certification, and strict non-results.
