\begin{abstract}
TPC--76 reduces every fixed-row-pair provenance completion problem to
\[
 \Gamma(b,C)
 =
 \min_{\theta\in\C^J}\|b+C\theta\|_1,
 \qquad
 b=A_DF^0,\qquad
 C=A_DB_{\boldsymbol L}.
\]
The formula is exact, but it does not say which parts of a literal
carrier interact or how a finite optimum can be independently checked.
This paper closes that sparse finite-dimensional layer.

We first separate zero columns, immutable rows, and active coordinates.
Let \(\cG_C\) be the bipartite graph on active analysis rows and active
filter variables, with \(i\sim j\) exactly when the fully assembled
coefficient \(C_{ij}\) is nonzero. If
\((I_s,J_s)\) are its connected components, then
\[
 \Gamma(b,C)
 =
 \|b_{\rm fix}\|_1
 +
 \sum_s
 \gamma_s,\qquad
 \gamma_s
 =
 \min_{\theta_s}\|b_s+C_s\theta_s\|_1.
\]
This is an exact factorization, not a sparsity heuristic. Its dual
factors over the same components:
\[
 \gamma_s
 =
 \max_{\substack{\|z_s\|_\infty\le1\\C_s^*z_s=0}}
 \operatorname{Re}\langle z_s,b_s\rangle .
\]

For every trial fill \(\theta_s\) and exact dual-feasible charge \(z_s\),
the quantities
\[
 U_s=\|b_s+C_s\theta_s\|_1,\qquad
 L_s=\operatorname{Re}\langle z_s,b_s\rangle
\]
satisfy \(L_s\le\gamma_s\le U_s\), and their gaps add exactly. Equality
is equivalent to phase saturation of the residual. Thus each reported
finite value can carry a matched fill/charge certificate.

We also compare \(\cG_C\) with the ambient
filter--site--analysis tripartite graph. The ambient graph gives a safe
coarse block decomposition, whereas exact cancellations in
\(C=A_DB_{\boldsymbol L}\) may produce additional splitting. Thresholded
floating support is not admissible for this purpose.

The specialization preserves the complete literal fixed-\(h_0\)
carrier and its original global raw masses. No archived literal
coefficient census exists in the preceding papers, so no numerical
physical census is invented here. The results are L0 component theorems
and an L1 certificate protocol, not an L2 saving, Perron decay,
fixed-\(2\), prime-pair, or twin-prime conclusion.
\end{abstract}
