\section{Claim ledger and next gate}
\label{sec:claim-boundary}

\subsection{Exact conclusions}

The paper proves:
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=2.8em]
 \item exact and distinct deletion rules for zero columns, immutable
       rows, and range-solvable blocks;
 \item exact primal factorization over the connected components of the
       assembled nonzero graph of \(C\);
 \item exact dual factorization over the same components, including the
       fixed-row phases;
 \item componentwise and global matched fill/charge bounds with an
       additive certified gap;
 \item phase saturation as the exact zero-gap condition;
 \item a proof that the ambient tripartite graph is a safe coarse
       decomposition and that the actual \(C\)-graph refines it;
 \item Hermitian transport of the component census;
 \item an exact fixed-shift specialization to every finite literal
       TPC--76 provenance program; and
 \item a reproducible archive protocol that distinguishes literal,
       validated, rounded, and toy inputs.
\end{enumerate}

\subsection{Statements not proved}

The paper does not prove:
\begin{itemize}
 \item a numerical census for a literal coefficient table that was not
       archived by the preceding papers;
 \item that most actual components are small or cheap;
 \item a mass-normalized component saving;
 \item decay of complete row sums or Perron radius;
 \item that edgewise components factor the row matrix;
 \item a single filter uniform over a growing coefficient class;
 \item that a failed solver run is a dual obstruction;
 \item that thresholded floating support equals literal support;
 \item closure of represented-frame, activation, missing-mass,
       nuisance, endpoint, or reconstruction gates;
 \item the strict endpoint budget below \(1/400\);
 \item a statement special to \(h_0=2\); or
 \item a parity-breaking, prime-pair, or twin-prime theorem.
\end{itemize}

\subsection{Audit levels}

\begin{center}
\begin{tabular}{p{0.29\textwidth}p{0.49\textwidth}l}
\toprule
Result & Scope & Level\\
\midrule
Deletion and graph factorization &
All finite affine \(\ell^1\) programs on complex coordinates with
real-linear \(C\) & L0\\
Dual and gap certificates &
All exact finite component blocks & L0\\
Ambient refinement theorem &
All finite factorizations \(C=AB\) & L0\\
Literal fixed-\(h_0\) protocol &
Complete TPC--76 carrier when its coefficient table is supplied & L1\\
Actual growing-carrier census &
Complete literal coefficient family & Open L1\\
Normalized/Perron saving &
Complete growing row family & Open L2\\
Physical reassembly and endpoint &
One common carrier and coefficient scope & Open\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Next decision}

The next useful question is structural rather than larger-scale
numerics. Once a component is isolated, can its optimum or obstruction
be read from a small exact motif? Candidate motifs include a surjective
block, an immutable leaf, a one-dimensional quotient, a tree of
incidences, and disjoint dual-charge packings. TPC--78 is planned to
investigate exact motif reduction and to identify which local patterns
can or cannot generate a nonzero cost.

\subsection{Endpoint ledger}

Component certification changes no downstream implication. Terminal
activation, represented-frame recovery, missing-mass comparison,
nuisance shorting, endpoint cells, and packet reconstruction remain
open. If cumulative fixed-power loss reaches \(1/400\), including
equality, the current route stops.

\subsection{Conclusion}

The provenance completion gauge is no longer a black-box finite
program. Its exact assembled incidence matrix
\[
 C=A_DB_{\boldsymbol L}
\]
determines a canonical coordinate graph, and every connected component
carries its own attained primal and dual problem. Immutable costs,
component optima, and certificate gaps add without approximation.

The distinction between the ambient tripartite graph and the actual
product graph is essential. The former is safe for early coarse
blocking; the latter is required for maximal exact deletion because
complex paths can cancel. The distinction between a solver vector and a
certificate is equally essential: only an exact annihilating charge
provides a lower obstruction.

This advances the L1 route by making every future finite carrier census
auditable. It does not supply the missing literal dataset, an
asymptotic component law, or a physical saving. Those remain separate
gates.
