\section{Countermodels and non-substitution laws}
\label{sec:countermodels}

\subsection{A connected ambient graph need not be actual}

\Cref{ex:ambient-cancellation} already shows that two nonzero paths can
cancel in \(AB\). Support multiplication in the Boolean semiring gives
only an upper envelope for actual complex support.

\subsection{A zero column need not be a zero fill direction}

Let
\[
 A=\begin{pmatrix}1&-1\end{pmatrix},
 \qquad
 B=\begin{pmatrix}1\\1\end{pmatrix}.
\]
The nonzero kernel direction \(B\theta=(\theta,\theta)\) is annihilated
by \(A\). Deleting the column from the cost program is valid, but
deleting it from an exported analytic completion changes the fill.

\subsection{Small stationarity residual is not a lower bound}

Take \(C=[1]\), \(b=1\), and a real trial charge
\(z=\varepsilon\) with \(0<\varepsilon\le1\). Its apparent objective is
\(\varepsilon\), but
\(C^*z=\varepsilon\ne0\). The true optimum is zero because
\(\theta=-1\). Indeed,
\[
 [z,b+C\theta]_{\mathbb R}
 =
 \Real\!\bigl(\varepsilon(1+\theta)\bigr)
\]
is unbounded below along real \(\theta\) when the erroneous
stationarity term is separated. A tiny residual is not a tiny
certificate error without a parameter bound.

\subsection{Component factorization does not factor Perron radius}

Let
\[
 Q^{(1)}
 =
 \begin{pmatrix}0&1&0\\1&0&0\\0&0&0\end{pmatrix},
 \qquad
 Q^{(2)}
 =
 \begin{pmatrix}0&0&0\\0&0&1\\0&1&0\end{pmatrix}.
\]
Each has spectral radius \(1\), whereas
\[
 \rho(Q^{(1)}+Q^{(2)})=\sqrt2\ne2.
\]
Adding certified edge-component costs is exact entrywise; adding their
Perron radii is not.

\subsection{Pairwise components can merge under a shared rule}

Consider two scalar edge problems
\[
 |t|,\qquad |1-t|.
\]
With independent variables each graph is a separate zero-cost
component. A shared variable \(t\) connects the stacked rows into one
component and the combined optimum is \(1\). Thus a pairwise incidence
census cannot be promoted after the fact to a shared-filter result.

\subsection{Finite sparsity is not asymptotic smallness}

One immutable row with coefficient \(A_X\) forms a component of size
one and contributes \(|A_X|\). Its graph remains maximally sparse even
when \(|A_X|\) is comparable to the full raw mass. Component counts and
normalized component cost are different statistics.

\subsection{Rounded support can create false disconnection}

For
\[
 C_\varepsilon=
 \begin{pmatrix}1&\varepsilon\\0&1\end{pmatrix},
 \qquad \varepsilon\ne0,
\]
the actual graph is connected. Thresholding \(\varepsilon\) to zero
splits it. Any certificate assembled from the false blocks is a theorem
about the thresholded matrix, not about \(C_\varepsilon\).
