\section{Introduction}
\label{sec:introduction}

The completion route has reached a finite but nontrivial optimization
problem. TPC--75 \citep{WangTPC75} proves strong duality for arbitrary
nonprimitive completions. TPC--76 \citep{WangTPC76} restricts the free
values to literal content-flow directions and obtains
\[
 \gamma_D^{\rm prov}(\boldsymbol L)
 =
 \min_\theta
 \|A_D(F^0+B_{\boldsymbol L}\theta)\|_1.
\]
Set
\[
 b=A_DF^0,\qquad C=A_DB_{\boldsymbol L}.
\]
The remaining finite question is the distance of \(-b\) from
\(\Ran C\) in complex \(\ell^1\).

The matrix \(C\), however, is highly structured. A filter variable first
copies literal \(q\)-slice amplitudes onto permitted nonprimitive sites;
the divisor--variation operator then sends those sites to low
plaquettes and high-tail coordinates. Many formal variables vanish,
many analysis rows are immutable, and some groups cannot interact.
Ignoring this structure obscures both computation and proof.

\subsection{Why the product \texorpdfstring{\(C=AB\)}{C=AB} is the correct graph}

It is tempting to draw a graph from the support of
\(B_{\boldsymbol L}\) and the stencil of \(A_D\). That graph is useful,
but it is not necessarily sharp. For fixed analysis row \(i\) and
filter column \(j\),
\[
 C_{ij}
 =
 \sum_k(A_D)_{ik}(B_{\boldsymbol L})_{kj}.
\]
Distinct site contributions can cancel exactly. The maximal
support-based decomposition therefore uses the nonzero entries of the
assembled \(C\), after all literal sums and signs are fixed. The
tripartite graph will be proved to give a safe coarser partition.

\subsection{Main advance}

The paper proves four exact statements.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.8em]
 \item immutable coordinates and cost-null variables have different
       deletion rules;
 \item the actual incidence graph of \(C\) block-diagonalizes the affine
       \(\ell^1\) distance exactly;
 \item the same components factor the strong dual, including the fixed
       rows; and
 \item matched primal and dual data give a locally and globally
       checkable gap certificate.
\end{enumerate}
These statements turn a monolithic solver output into a sum of
independent mathematical claims.

\subsection{What is deliberately absent}

The previous TPC papers define the literal carrier symbolically but do
not archive a table of all active \(L_{mn,q}\) coefficients on a
declared growing block. Consequently this paper proves the exact census
protocol but does not fabricate a numerical census. Even a completed
finite census would remain L1: asymptotic normalized component mass,
row sums, Perron decay, shared-rule uniformity, and physical reassembly
would still be open.

\subsection{Organization}

\Cref{sec:normal-form} fixes the realified complex normal form.
\Cref{sec:deletion} proves exact deletion rules.
\Cref{sec:components} gives primal component factorization.
\Cref{sec:dual-certificates} gives the dual and gap certificates.
\Cref{sec:ambient-graph} compares actual and ambient graphs.
\Cref{sec:physical-census} states the literal fixed-shift protocol.
\Cref{sec:countermodels} records non-substitution examples, and
\cref{sec:claim-boundary} gives the claim ledger.
