\section{Literal fixed-shift specialization and census protocol}
\label{sec:physical-census}

\subsection{Frozen physical data}

Fix one nonzero \(h_0\), one declared external block, both orthogonal
direct sides, and the complete TPC--74 missing-high keys. For every
active unordered row pair \(e=\{m,n\}\), freeze
\[
 \Delta_{mn}=h_0(n-m)\ne0,
\]
the literal slices \(L_{mn,q}\), the rectangle \(B_{mn}\), the cutoff
\(D_{mn}\), and all complete native key labels. Form
\[
 F^0_{mn}
 \quad\text{from}\quad
 k_{mn}=\sum_{q\mid|\Delta_{mn}|}L_{mn,q},
\]
and form \(B_{\boldsymbol L,mn}\) only from the actual directions
\(d\mid q\mid|\Delta_{mn}|\).

The normalization remains
\[
 \frac1{\sqrt{W_mW_n}},
\]
where \(W_m,W_n\) are the global raw masses of all actual atoms on both
direct sides. Analytic copies, graph vertices, and component counts do
not enter these masses.

\begin{corollary}[Literal edge decomposition]
\label{cor:literal-edge-decomposition}
With
\[
 b_{mn}=A_{D_{mn}}F^0_{mn},
 \qquad
 C_{mn}=A_{D_{mn}}B_{\boldsymbol L,mn},
\]
the provenance gauge satisfies
\[
 \gamma^{\rm prov}_{mn}
 =
 \|(b_{mn})_{\rm fix}\|_1
 +
 \sum_s\gamma_{mn,s},
\]
and every \(\gamma_{mn,s}\) has the exact matched certificate of
\cref{thm:gap-certificate}.
\end{corollary}

\begin{proof}
All data are finite and have exactly the TPC--76 affine form. Apply
\cref{thm:primal-factorization,thm:dual-factorization}.
\end{proof}

\subsection{Verified archive format}

A finite census is reproducible only if it archives:
\begin{enumerate}[label=\textup{(C\arabic*)},leftmargin=3.4em]
 \item the object identity: \(h_0,m,n,\Delta_{mn},B_{mn},D_{mn}\),
       both-side block labels, complete-key identifiers, and raw
       \(W_m,W_n\);
 \item the literal \(q\)-slice table and exact or validated
       \(F^0,B_{\boldsymbol L},A_D,C=A_DB_{\boldsymbol L}\);
 \item the exact-zero policy, immutable-row ledger, zero-column ledger,
       and component index sets;
 \item for every component,
       \(\theta_s,y_s,z_s,U_s,L_s\), together with checks of
       \(y_s=b_s+C_s\theta_s\),
       \(C_s^*z_s=0\), \(\|z_s\|_\infty\le1\), and the saturation defect
       \(U_s-L_s\); phase saturation is required only when zero gap and
       optimality are claimed;
 \item the fixed-row cost and total certified gap;
 \item the Hermitian reverse checksum and assembled entry
       \(Q^{\rm prov}_{mn}\); and
 \item an input-certification statement distinguishing literal
       coefficients from a rounded surrogate.
\end{enumerate}

\begin{remark}[No invented census]
TPC--74 through TPC--76 provide symbolic exact formulas but no archived
complete literal coefficient table for a growing physical carrier.
Therefore the present paper proves the protocol and factorization
theorems but reports no numerical physical component counts. A census
of a toy or rounded instance would be labelled as such, not as the
literal L1 carrier.
\end{remark}

\subsection{Matrix boundary}

For independent unordered edges, the component sums assemble the
entries of \(Q^{\rm prov}\), after which the TPC--76 Perron majorant
applies. Components within one edge add to that edge cost. They do not
imply
\[
 \rho\!\left(\sum_sQ^{(s)}\right)
 =
 \sum_s\rho(Q^{(s)}),
\]
nor a direct-sum decomposition of the row matrix.

If a parameter is shared across edges, blocks, coefficient samples, or
scales, one must first stack the entire coupled affine problem and build
one global \(C\). A shared column can connect several edge blocks.
Pairwise components cannot be reused as a universal-filter theorem.
