\begin{abstract}
TPC-73--TPC-81 close a sequence of exact primitive-support,
direct-entry, convex-dual, provenance, sparse-incidence,
complex-scalar forest, anchor--direct, and scalar-spectral interfaces.
We audit those nine
papers together with the present synthesis as a ten-paper block.  The
audit separates finite algebra and graph theory (\(\Lzero\)), literal
fixed-shift transfer (\(\Lone\)), and new asymptotic arithmetic input
(\(\Ltwo\)).  Every unconditional theorem in the audited block lies at
\(\Lzero\) or \(\Lone\); none proves a new \(\Ltwo\) estimate.

The exact surviving architecture passes through the actual
determinant coefficient
\[
 a_X=(A_{C_X}(n))_n,\qquad
 Z_X=\sum_n A_{C_X}(n),\qquad
 D_X=\sum_n|A_{C_X}(n)|^2.
\]
Completion geometry reaches \(D_X\) only after a literal
determinant-binning map, a positive lower modulus on a verified
subspace, and a controlled dictionary residual.  It does not control
the distinguished zero mode \(Z_X\).  At the critical scales
\[
 Q_X=X^{267/400+o(1)},\qquad
 J_X=X^{133/400+o(1)},
\]
the hypotheses
\[
 |Z_X|\le X^{-\eta_Z+o(1)}Q_X^2,\qquad
 D_X\ge X^{-\lambda_D+o(1)}Q_X^3J_X^2
\]
give the flatness bound
\[
 \frac{|Z_X|^2}{D_X}
 \le X^{1/400+\lambda_D-2\eta_Z+o(1)}.
\]
Within this two-exponent transfer ledger, the sharp recorded-bounds
compatibility condition is \(2\eta_Z\ge\lambda_D\).  For the current
transfer route the present zero-mode target has \(\eta_Z=0\), so the
sufficient ledger condition requires natural energy,
\(\lambda_D=0\).
Support, absolute completion cost, raw energy, anchor quotient
geometry, and scalar holonomy cannot supply these two arithmetic
inputs without additional literal maps and estimates.  We prove
no-teleportation and nonidentifiability statements, give
branch-specific kill rules, and reduce the next block to three honest
routes: determinant-energy survival, distinguished-zero-frequency
cancellation, or a negative transfer theorem.  These routes concern
the TPC-32 matched-shell flatness gate; the exact TPC-18 full-block
cover and uniform remainder control remain an independent downstream
gate.  The paper proves no
fixed-shift Chowla estimate, parity breach, prime-pair lower bound, or
twin-prime conclusion.
\end{abstract}
