\section{Audit levels and the literal packet}
\label{sec:audit-levels}

\begin{definition}[The three levels]
\label{def:levels}
We use the following labels.
\begin{enumerate}[label=(\arabic*),leftmargin=2.2em]
\item An \(\Lzero\) result is a finite-dimensional algebraic,
convex-dual, combinatorial, graph-theoretic, or spectral theorem.  It
may be exact and new, but it neither depends on nor automatically
applies to the growing arithmetic carrier.
\item An \emph{\(\Lone\)-typed conditional interface} has hypotheses
that preserve one fixed nonzero \(h_0\), the complete physical keys,
literal coefficients, actual active support, one global raw atomic
normalization, and the original quantifier range, and it states how
an \(\Lzero\) object connects to the actual growing carrier.  Its
arithmetic hypotheses may remain open.  A \emph{verified physical
\(\Lone\) application} additionally checks every literal packet item
and every non-arithmetic interface hypothesis for the carrier under
study.  Neither label asserts an open asymptotic estimate.
\item An \(\Ltwo\) result proves a new asymptotic estimate for that
literal growing fixed-\(h_0\) carrier, strong enough to reduce a
positive exponent in the final physical loss ledger.
\end{enumerate}
\end{definition}

\begin{remark}[Interface progress versus gate closure]
An \(\Lone\)-typed interface may identify the right statistic without
bounding it.  Thus ``advances the \(\Lone\) interface'' and ``closes
the \(\Lone\) quantitative gate'' are different statements.  Only the
latter can feed an exponent ledger, and it becomes \(\Ltwo\) only
when the bound is a genuinely new arithmetic estimate.
\end{remark}

\begin{definition}[Literal physical packet]
\label{def:literal-packet}
At scale \(X\), a literal physical packet contains:
\begin{enumerate}[label=(P\arabic*),leftmargin=2.7em]
\item a fixed integer \(h_0\ne0\), not averaged or selected after the
estimate;
\item the complete native key set \(\cK_X\), including every row,
orientation, orbit, divisor, content, source, endpoint, and
provenance label used by the construction;
\item the literal coefficient \(z_X\in\C^{\cK_X}\), with all signs,
phases, units, and multiplicities;
\item the exact synthesis maps under discussion, with their genuine
domains, targets, and active nonzero support after coefficient
aggregation;
\item the determinant labels and every multiplier used in the final
binning map;
\item the actual post-aggregation coefficient
\[
 a_X=(A_{C_X}(n))_{n\in\cN_X},
\]
with \(C_X=\lfloor J_X\rfloor\) in the TPC-32 matched-shell
specialization,
with cancellations performed only after all native contributions
have been assembled;
\item one global raw atomic energy \(D_{{\rm raw},X}>0\), computed
before deletion, thresholding, block selection, or local
renormalization; and
\item the original uniformity and quantifier range needed by the
physical conclusion.
\end{enumerate}
\end{definition}

\begin{definition}[Actual support]
\label{def:actual-support}
The actual support of a literal map or coefficient is the set of
nonzero entries after exact aggregation with the physical signs and
phases.  It is not the union of geometrically possible edges, a
thresholded numerical graph, or an ambient incidence pattern.
\end{definition}

\begin{proposition}[Promotion test]
\label{prop:promotion-test}
An \(\Lzero\) theorem is promoted to a verified physical \(\Lone\)
application only after
all items of \cref{def:literal-packet} used by the theorem have been
verified.  Omitting any one of fixed \(h_0\), a native key, actual
support, the global raw normalizer, or the required uniformity leaves
the result at \(\Lzero\) as a physical application, although a
correctly quantified conditional statement may still be
\(\Lone\)-typed.
\end{proposition}

\begin{proof}
Each omitted datum permits two physical packets to have the same
reduced model but different target coefficients or normalizations.
For example, deleting a native key changes a determinant fiber,
replacing actual support by ambient support changes component and
spectral data, and local renormalization can hide arbitrary deleted
raw mass.  Therefore the reduced theorem does not identify the
physical statistic.  Verification of the full list supplies the
needed typing; it does not by itself supply an asymptotic bound.
\end{proof}

\begin{definition}[Closed interface and closed arithmetic gate]
\label{def:closed-gates}
An interface is \emph{closed} when the source, target, map, norm,
normalization, and quantifiers are explicit and the asserted
identity or inequality is proved.  An arithmetic gate is closed only
when its required bound is established on the literal packet with the
stated asymptotic strength.  A finite exact formula for an unknown
quantity closes an interface but not necessarily its arithmetic gate.
\end{definition}

This terminology is used throughout the table in
\cref{sec:stage-ledger}.  It prevents an exact optimization identity
from being reported as cancellation, and it prevents a numerical
certificate on a truncated carrier from being reported as a uniform
asymptotic theorem.
