\section{Final claim boundary}
\label{sec:claim-boundary}

\begin{theorem}[Ten-paper completion-to-flatness audit]
\label{thm:final-audit}
The joint unconditional content of TPC-73--TPC-81 and the present
paper is the following.
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item Exact \(\Lzero\) certificate theories are available for
primitive support, direct completion, provenance lifts, sparse
components, complex-scalar forest/motif reductions, common-target
anchor--direct duality for separable variables with additive physical
cost, and scalar Perron/holonomy defects.
\item Exact \(\Lone\)-typed interfaces identify the conditions under
which those theories can be attached to a literal fixed-\(h_0\)
carrier; a verified physical application additionally requires the
literal packet checks of \cref{prop:promotion-test}.
\item TPC-81 gives an exact conditional passage from pre-bin
completion survival to determinant energy, with every loss and the
dictionary residual displayed.
\item The current TPC-32 matched-shell transfer ledger has two
explicit arithmetic inputs:
determinant-energy survival with exponent \(\lambda_D\) and
distinguished-zero-mode cancellation with exponent \(\eta_Z\).
Their transfer ledger closes only under
\[
 2\eta_Z\ge\lambda_D.
\]
\item Neither input is established by the audited block.  Therefore
the block proves no \(\Ltwo\) fixed-shift arithmetic estimate.
\end{enumerate}
\end{theorem}

\begin{proof}
Items (i)--(ii) are
\cref{thm:typed-dependency,thm:stage-audit}.  Item (iii) is
\cref{thm:dictionary-energy-audit}.  Item (iv) is
\cref{thm:zero-slack-audit}, and item (v) follows from
\cref{rem:tpc81-conditional-status}.
\end{proof}

\begin{corollary}[What remains genuinely arithmetic]
\label{cor:genuine-arithmetic-gate}
At the present critical scales, the unresolved positive core of the
TPC-32 matched-shell flatness gate is
\begin{equation}
\boxed{
\text{determinant-energy survival}
\quad+\quad
\text{distinguished-zero-mode cancellation},
\qquad
2\eta_Z\ge\lambda_D.}
\label{eq:final-core}
\end{equation}
Completion, quotient, and scalar-spectral geometry can quantify
interfaces entering the first term, but they do not by themselves
prove either term.  This is not the whole prime-pair route: even
closure of this gate leaves the independent TPC-18 exact full-block
cover and uniform remainder control open.
\end{corollary}

\begin{proof}
The determinant-energy crosswalk is
\eqref{eq:dictionary-energy-audit}; zero-mode nonidentifiability is
\cref{prop:unsigned-nonidentifiability}; and the endpoint comparison
is \eqref{eq:zero-slack-audit}.
\end{proof}

The advance of this audit is therefore not a claimed approach to a
proved prime-pair theorem.  It is a reduction of a diffuse collection
of completion heuristics to two typed, quantitative arithmetic
questions at the matched-shell gate, together with exact
branch-specific certificates for when the algebraic mechanisms cannot
answer them.  The downstream full-block gate remains separate.

\paragraph{Explicit exclusions.}
This paper does not prove determinant-energy survival,
distinguished-zero-frequency cancellation, a fixed-shift Chowla
estimate, a breach of sieve parity, a fixed-shift
Hardy--Littlewood asymptotic, a prime-pair lower bound, or the
twin-prime conjecture.  It does not specialize its conclusions to
\(h_0=2\).  The parity problem remains a genuine arithmetic boundary,
not a conclusion of the present finite-dimensional analysis
\citep{HeathBrown1982Parity,IwaniecKowalski2004}.

\paragraph{Operational conclusion.}
Route I is worth continuing while either the literal dictionary or a
direct determinant-energy analysis can preserve natural-scale energy,
or while Route II supplies enough compensating zero-mode gain.  Route
II counts only at the actual
distinguished frequency and fixed \(h_0\).  If both routes are shown
to require the same unresolved Chowla-like correlation, Route III is
a mathematically complete negative-transfer outcome.  In every
case, the complete fixed-power loss remains subject to the strict
rule
\[
 \Lambda_{\rm phys}<\frac1{400};
 \qquad
 \Lambda_{\rm phys}\ge\frac1{400}
 \ \Longrightarrow\ \text{stop},
\]
with equality included in the stopping case.
