\section{Introduction}
\label{sec:introduction}

The purpose of a route audit is not to make a long proof program look
closer to its final conjecture than it is.  It is to identify which
interfaces have become exact, which quantities still require
arithmetic information, and which apparent shortcuts are type errors.
That distinction is especially important in a fixed-shift problem.
An estimate averaged over shifts, frequencies, or carrier families
may be deep, yet it does not automatically control one prescribed
nonzero \(h_0\).  Likewise, a finite-dimensional completion theorem can
be completely rigorous while remaining silent about the signed
coefficient to which it is intended to apply.

TPC-73--TPC-80 develop a chain of exact algebraic tools
\citep{WangTPC73,WangTPC74,WangTPC75,WangTPC76,WangTPC77,WangTPC78,WangTPC79,WangTPC80}.
The preceding TPC-72 audit isolated the missing direct two-corner
operator bridge and imposed the strict physical loss rule
\(\Lambda_{\rm phys}<1/400\) \citep{WangTPC72}.  TPC-74 closes that
direct entry bridge, while TPC-73--TPC-80 close or sharpen a sequence
of \(\Lzero/\Lone\) certificate subgates.  Their quantitative
aggregation on the small growing physical carrier remains open.
TPC-81 then asks for the first time in this block how those tools could
reach the determinant coefficient and the distinguished zero
frequency used in the matched-shell argument
\citep{WangTPC81,WangTPC32,WangTPC33}.  The answer is both useful and
restrictive.  Completion can contribute a lower bound for pre-bin
energy, but determinant aggregation can erase that energy.  Even if
determinant energy survives, its unsigned size does not cancel the
zero mode.  The two tasks must be recorded separately.

This paper is the tenth item in the block.  Its main outputs are as
follows.

\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item We give formal definitions of \(\Lzero,\Lone,\Ltwo\) and audit
TPC-73--TPC-81 against them.  The block contains substantial exact
\(\Lzero\) structure and several \(\Lone\) transfer interfaces, but no
completed \(\Ltwo\) arithmetic estimate.
\item We write the typed dependency graph.  The sparse incidence
graph of TPC-77/78, the common-target quotient of TPC-79, the scalar
Hermitian row graph of TPC-80, and the determinant coefficient space
of TPC-81 are distinct objects.  Shared labels do not identify them.
\item We isolate a no-teleportation principle: without an explicit
literal synthesis or intertwining map, a theorem on one of those
objects supplies no determinant-energy or zero-frequency estimate.
\item We restate the exact anchor--direct and scalar-holonomy
interfaces and record their application conditions.  In particular,
the orphan quotient is not the physical hybrid cost, trees supply no
phase-frustration saving, and one sector gap does not give norm
strictness.
\item We crosswalk the TPC-81 reassembly and determinant-dictionary
inequalities into one conditional energy-survival statement.  Every
factor in that statement is visible; none is silently declared to be
\(X^{o(1)}\).
\item We prove the recorded-bounds zero-slack compatibility condition
\[
 2\eta_Z\ge\lambda_D.
\]
Equality reaches the TPC-32 flatness threshold but leaves no
fixed-power reserve.  It is not permission to spend another
\(1/400\).
\item We give two exact nonidentifiability examples and a three-route
decision tree with hard stop rules.  These permit a clean negative
paper if the two remaining inputs reduce to a fixed-shift
Chowla-type correlation, rather than disguising that correlation as
a consequence of completion geometry.
\end{enumerate}

The distinction between structural and arithmetic progress is
standard in spirit.  Sieve parity and multiplicative correlations
are not resolved by unsigned support information
\citep{HeathBrown1982Parity,IwaniecKowalski2004}.  Strong averaged
correlation theorems provide essential comparison points
\citep{MatomakiRadziwillTao2015,Tao2016LogChowla}, but they do not
become a theorem for the literal distinguished frequency and fixed
\(h_0\) without a separate localization argument.

Our convention is deliberately strict.  The actual coefficient is
formed with all native keys, literal signs and phases, exact
post-aggregation support, and one global raw normalization.  An
ambient support, an unsigned envelope, a fitted reduced space, or a
componentwise renormalization may be a diagnostic, but it is not the
physical input.  This strictness turns several vague obstacles into
finite checklists and makes the remaining arithmetic gate precise.
