\section{The TPC-73--TPC-81 stage ledger}
\label{sec:stage-ledger}

\begingroup
\small
\hbadness=10000
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.12}
\begin{longtable}{@{}p{0.075\linewidth}p{0.34\linewidth}
 p{0.135\linewidth}p{0.355\linewidth}@{}}
\toprule
Paper & Exact closure & Highest verified stage & Open gate \\
\midrule
\endfirsthead
\toprule
Paper & Exact closure & Highest verified stage & Open gate \\
\midrule
\endhead
TPC-73 &
Canonical primitive support, zero completion, and exact disappearance
of every \(d\ge2\) diagonal slice. &
\(\Lone\) local carrier identity. &
The actual \(d=1\) mixed variation and a complete operator bound.
\\
TPC-74 &
Literal normalized two-corner primitive-plane entry for the
missing-native Gram, termwise Abel majorants, and a Perron majorant
interface. &
\(\Lone\) exact entry representation. &
A small \(\rho(P_X)\), including the actual row, star, and operator
summations.
\\
TPC-75 &
Strong duality for the completion gauge, quotient seminorms,
obstruction witnesses, and an independent row-pair Perron floor. &
\(\Lzero\), with \(\Lone\) typing. &
A small optimum on the growing carrier and any genuinely coupled
minimax problem.
\\
TPC-76 &
Divisor-poset zeta lift and inversion, provenance-compatible affine
classes, diagonal filtration, and reduced dual problems. &
\(\Lzero/\Lone\) interface. &
An actual lift whose literal growing optimum gives an asymptotic
saving.
\\
TPC-77 &
Factorization over components of the actual nonzero incidence graph,
componentwise primal--dual certificates, and a manifest schema. &
\(\Lzero\), advancing \(\Lone\). &
A complete scale-uniform literal census and a quantitative bound on
its component optima.
\\
TPC-78 &
For complex-scalar incidence maps: forest leaf erasure, matching
rank, defect reduction, a one-defect closed form, a reduced SOCP, and
motif dual packings. &
\(\Lzero\). &
Proof that the actual carrier is covered by the claimed forests or
motifs, with acceptable aggregate cost.
\\
TPC-79 &
Exact orphan quotient and hybrid duality, together with fixed-datum
and global equality tests. &
\(\Lzero\), with an \(\Lone\) admissibility test. &
Common physical target, separable variables, correct coefficient
prices, and an actual strict saving.
\\
TPC-80 &
Scalar Hermitian Perron saturation, switching/holonomy
classification, sector defects, and weighted defect bounds. &
\(\Lzero\), advancing \(\Lone\) diagnostics. &
The actual scalar row graph, quantitative defects in both sectors,
and treatment of any block-valued carrier.
\\
TPC-81 &
Exact completion/reassembly-to-determinant-energy transfer and the
zero-mode/energy exponent ledger. &
\(\Lone\)-typed conditional interface; no verified physical
specialization. &
A small dictionary residual, determinant-energy survival, and
distinguished-zero-mode cancellation.
\\
\midrule
Block &
Exact support, completion, quotient, sparse, forest, hybrid, scalar
spectral, and arithmetic-transfer interfaces. &
\(\Lzero/\Lone\); no \(\Ltwo\). &
No new fixed-\(h_0\) asymptotic cancellation estimate has been
proved.
\\
\bottomrule
\end{longtable}
\endgroup

\begin{theorem}[Stage audit]
\label{thm:stage-audit}
Every unconditional theorem in TPC-73--TPC-81 is an \(\Lzero\) or
\(\Lone\) statement in the sense of \cref{def:levels}.  None supplies
even the current target
\begin{equation}
 |Z_X|\le X^{o(1)}Q_X^2,
\label{eq:missing-zero-baseline}
\end{equation}
let alone
\begin{equation}
 |Z_X|\le X^{-\eta+o(1)}Q_X^2
 \quad\text{for some fixed \(\eta>0\),}
\label{eq:missing-zero-saving}
\end{equation}
or a polynomially adequate lower bound for the literal determinant
energy \(D_X\).  Consequently this ten-paper block contains no
completed \(\Ltwo\) fixed-shift arithmetic estimate.
\end{theorem}

\begin{proof}
TPC-73 and TPC-74 identify literal primitive pieces and entries, but
leave their growing operator aggregation open
\citep{WangTPC73,WangTPC74}.  TPC-75--TPC-80 are exact finite
optimization, incidence, reduction, quotient, or scalar spectral
theorems; their physical conclusions are conditional on an actual
manifest and quantitative hypotheses
\citep{WangTPC75,WangTPC76,WangTPC77,WangTPC78,WangTPC79,WangTPC80}.
TPC-81 constructs the exact crosswalk to \(D_X\) and \(Z_X\), but
states energy survival and zero-mode cancellation as hypotheses
\citep{WangTPC81}.  None of these papers proves
\eqref{eq:missing-zero-baseline}, \eqref{eq:missing-zero-saving}, or
the determinant-energy lower bound
used in \cref{sec:endpoint-ledger}.  By
\cref{def:levels}, no \(\Ltwo\) estimate is present.
\end{proof}

\begin{corollary}[No arithmetic relabeling]
\label{cor:no-arithmetic-relabeling}
The labels ``exact'', ``optimal'', ``dual certificate'', and
``spectral gap'' in the audited block describe their stated
\(\Lzero/\Lone\) objects.  They cannot be relabeled as a fixed-shift
M\"obius saving, a parity-breaking estimate, or a prime-pair theorem.
\end{corollary}

\begin{proof}
Those arithmetic statements require an \(\Ltwo\) estimate for the
literal coefficient.  \Cref{thm:stage-audit} shows that such an
estimate is not among the premises or conclusions audited here.
\end{proof}
