\section{Unified hard stop rules}
\label{sec:stop-rules}

The following rules apply before any claim is promoted.

\begin{enumerate}[label=\textbf{S\arabic*.},leftmargin=3.3em]
\item If the shift is averaged, optimized, or replaced by a moving
\(h\), stop the fixed-\(h_0\) claim.
\item If a native key is deleted, actual support is replaced by
ambient support, or the raw normalizer is recomputed locally, stop the
\(\Lone\) transfer.
\item If an observation, trace, or four-corner scalar is treated as a
synthesis vector without a proved section into the same target, stop
the TPC-79 combination.
\item If a block or operator-valued carrier is treated as a scalar
Hermitian graph, stop the TPC-80 application.
\item If a numerical solver fails to improve a value but supplies no
verified dual witness or exact normer, do not call the outcome an
obstruction.
\item When transferring raw or pre-bin energy, if it has not passed
through the literal \(\cJ_X\) and a verified lower modulus or residual
estimate, do not call it determinant energy.  This does not prohibit
a direct arithmetic expansion or estimate of \(D_X\).
\item If a dispersion estimate excludes or averages the distinguished
frequency, do not call it zero-frequency control.
\item If \(2\eta_Z<\lambda_D\), stop the present TPC-32 endpoint
transfer.
\item If the complete physical fixed-power \emph{loss} is
\(\ge1/400\), stop; equality also stops.
\item If the TPC-18 full-block cover and its uniform remainder bounds
are unverified, do not infer a fixed-shift Hardy--Littlewood,
prime-pair, or twin-prime conclusion.
\end{enumerate}

\begin{proposition}[Scope of a stop certificate]
\label{prop:scope-stop}
A stop rule invalidates only the claim or branch named in that rule.
It does not prove that every representation, every analytic method,
or the underlying number-theoretic conjecture is impossible.
\end{proposition}

\begin{proof}
Each rule identifies a missing hypothesis of a specified implication.
Failure of that hypothesis blocks the implication, not all possible
implications with different hypotheses.
\end{proof}

\begin{remark}[Equality conventions]
There are two equalities with different logical roles.  Equality
\(2\eta_Z=\lambda_D\) reaches the conditional flatness threshold but
has zero fixed-power robustness.  Equality
\(\Lambda_{\rm phys}=1/400\) fails the strict full physical loss rule
and therefore stops.  Neither equality may be described as spare
margin.
\end{remark}

\begin{remark}[Evidence archive]
A future literal census should archive the native manifest, the
post-aggregation nonzero graph, every connected component, the
primal and dual certificate residuals, the scalarization proof where
used, all determinant fibers, the lower-modulus subspace, and the
global raw normalizer.  Numerical evidence is useful for choosing a
branch, but promotion requires exact or interval-certified bounds
uniform in the stated asymptotic range.
\end{remark}
