\section{The complete-universe extension of the static-mask formula}
\label{sec:tpc49-static-mask}

The inherited active TPC packet may be pruned by smooth and residue
weights, and no lower row count is part of the TPC--45/47 interface.
We therefore separate two statements.  This section first analyzes the
complete-universe extension on which the literal static-mask formula
\eqref{eq:tpc49-actual-static-mask} is defined.  It then states the
weighted condition needed to transfer the conclusion to a pruned active
cell.

\subsection{The ambient row universe}

Fix \(H\ge1\) and \(\kappa_0>0\).  Let \(L,D\to\infty\) with \(X\),
assume \(L,D\le X^C\) for some fixed \(C\), and let
\begin{equation}
 \cR(L,D;H)
 :=\left\{(\ell,d):
 L<\ell\le2L, \ell\in\Pp,
 D<d\le2D, \mu^2(d)=1, (d,H)=1
 \right\}.
 \label{eq:tpc49-complete-row-universe}
\end{equation}
Assume \(L>4D\), as is more than satisfied by the inherited endpoint
separation.  Put \(N=|\cR(L,D;H)|\).  The prime number theorem and the
elementary squarefree count in fixed coprime residue conditions give
\begin{equation}
 N\asymp_H\frac{LD}{\log L}=X^{o(1)}LD.
 \label{eq:tpc49-complete-row-count}
\end{equation}
Only this two-sided order estimate is used; see, for example,
\citep[Chapter~1]{IwaniecKowalski2004}.  The row product
\(m=\ell d\) is injective: if \(\ell d=\ell'd'\) and
\(\ell\ne\ell'\), then the prime \(\ell\) divides
\(d'<2D<\ell\), a contradiction.

Use the same row universe on the two sides and define
\(M_X(\alpha,\gamma)\) by the literal static formula
\eqref{eq:tpc49-actual-static-mask}, with
\begin{equation}
 Q=LD,
 \qquad \Delta=QX^{-\kappa_0},
 \qquad G=X^{\kappa_0}.
 \label{eq:tpc49-complete-mask-scales}
\end{equation}

\begin{theorem}[Uniform degree of the complete static mask]
\label{thm:tpc49-static-degree}
Uniformly in every row on either side,
\begin{equation}
 \deg_{M_X}(\alpha)
 \ge(1-\epsilon_X)N,
 \qquad
 \epsilon_X
 \ll_H
 L^{-1+o(1)}+D^{-1+o(1)}+X^{-\kappa_0+o(1)}.
 \label{eq:tpc49-static-min-degree}
\end{equation}
In particular \(\epsilon_X=o(1)\) whenever \(L,D\to\infty\).
\end{theorem}

\begin{proof}
Fix \(\alpha=(\ell,d)\).  The forbidden rows lie in the union of three
sets.

For the same-source deletion \(\ell_\gamma=\ell\), there are \(O_H(D)\)
choices.  Dividing by \eqref{eq:tpc49-complete-row-count} gives
\begin{equation}
 \frac{O_H(D)}N\ll_H\frac{\log L}{L}=L^{-1+o(1)}.
 \label{eq:tpc49-same-source-degree}
\end{equation}

For the near-row deletion, injectivity of the integer label \(m_\gamma\)
gives at most \(2\Delta+1\) rows.  Hence
\begin{equation}
 \frac{2\Delta+1}{N}
 \ll_H X^{-\kappa_0}\log L+\frac{\log L}{LD}
 =X^{-\kappa_0+o(1)}+(LD)^{-1+o(1)}.
 \label{eq:tpc49-near-row-degree}
\end{equation}

Finally, if \((d,d_\gamma)>G\), the gcd is a divisor
\(g\mid d\) with \(g>G\).  For each opposite source prime, the number
of possible \(d_\gamma\) is at most
\begin{align}
 \sum_{\substack{g\mid d\\g>G}}
 \left(\frac{2D}{g}+1\right)
 &\le \tau(d)\left(\frac{2D}{G}+1\right).
 \label{eq:tpc49-gcd-bad-divisor-count}
\end{align}
Here we used \(g^{-1}\le G^{-1}\) and at most \(\tau(d)\) divisors.
Since \(\tau(d)=D^{o(1)}=X^{o(1)}\) under the declared polynomial
scale bound, multiplication by the
\(O(L/\log L)\) source primes and division by \(N\) yield
\begin{equation}
 \frac{\#\{\gamma:(d,d_\gamma)>G\}}N
 \ll_H X^{-\kappa_0+o(1)}+D^{-1+o(1)}.
 \label{eq:tpc49-gcd-bad-degree}
\end{equation}
The union bound proves \eqref{eq:tpc49-static-min-degree}.  The formula
is symmetric, so the column estimate is identical.
\end{proof}

\begin{corollary}[Density and a perfect matching]
\label{cor:tpc49-static-density-matching}
The number of admitted entries is
\begin{equation}
 \|M_X\|_{S_2}^2
 =\#\{(\alpha,\gamma):M_X(\alpha,\gamma)=1\}
 =(1+O(\epsilon_X))N^2.
 \label{eq:tpc49-static-Frobenius}
\end{equation}
For all sufficiently large \(X\), the admitted bipartite graph has a
perfect matching.
\end{corollary}

\begin{proof}
Sum the row degrees for the first statement.  For large \(X\), both the
minimum row degree and minimum column degree exceed \(N/2\).  The empty
set is trivial.  If \(0<|S|\le N/2\), any vertex in \(S\) has more than
\(N/2\) neighbors, so \(|\Gamma(S)|>|S|\).  If \(|S|>N/2\), a right
vertex without a neighbor in \(S\) would have all its more than \(N/2\)
neighbors in the complement of \(S\), whose size is less than \(N/2\),
a contradiction.  Hall's condition follows.
\end{proof}

\subsection{A specified explicit complete-mask comparison}

Fix one explicit representation \(\mathscr R_{36}\) furnished by the
proof of the TPC--36 static-mask theorem, using same-source
orthogonality, signed Ferrers separation, and global gcd compression.
That construction, rather than the infimum alone in
\eqref{eq:tpc49-inherited-mask-cost}, gives a fixed-representation bound.
Define
\begin{equation}
 \omega_*^{\rm comp}
 :=\max_{\substack{D<d\le2D\\ \mu^2(d)=1,\ (d,H)=1}}\omega(d),
 \label{eq:tpc49-complete-omega}
\end{equation}
where \(\omega(d)\) counts the distinct prime divisors of \(d\).  Then
\begin{equation}
 P_{\mathscr R_{36}}(M_X)
 \ll \log(2Q)(3+2\sqrt2)^{\omega_*^{\rm comp}}=X^{o(1)}.
 \label{eq:tpc49-explicit-mask-cost}
\end{equation}
Indeed, every fixed-base exponential in \(\omega_*^{\rm comp}\) is
\(D^{o(1)}=X^{o(1)}\).

\begin{theorem}[Soft atomic cost for the complete-universe extension]
\label{thm:tpc49-static-soft}
For all sufficiently large \(X\), on
\(\cR(L,D;H)\times\cR(L,D;H)\),
\begin{equation}
 \frac{\cE_{\mathscr R_{36}}(M_X;\one,\one)^2}
 {\|M_X\|_{S_2}^2}
 \le
 \frac{P_{\mathscr R_{36}}(M_X)^2}
 {1-\epsilon_X}
 =X^{o(1)}.
 \label{eq:tpc49-static-canonical-soft}
\end{equation}
Consequently
\begin{equation}
 r_{\rm nuc}(M_X)=X^{o(1)}.
 \label{eq:tpc49-static-intrinsic-soft}
\end{equation}
\end{theorem}

\begin{proof}
For uniform weights, the minimum-degree bound gives
\(\delta_w\ge1-\epsilon_X\).  Apply
\cref{thm:tpc49-weighted-transfer} to the specified explicit
representation and then use \eqref{eq:tpc49-explicit-mask-cost}.
The intrinsic infimum is no larger.
\end{proof}

This theorem concerns the complete static \(0\)-\(1\) mask.  It does
not say that every coefficient supported by the mask has soft nuclear
rank, nor that the full multiplier
\eqref{eq:tpc49-joint-multiplier} has a weighted lower density on every
active residue/Mellin cell.

\begin{corollary}[A criterion for a pruned weighted cell]
\label{cor:tpc49-pruned-cell}
Suppose a retained opposite-row weight \(b\) on the complete universe
satisfies
\begin{equation}
 \epsilon_X\operatorname{Flat}(b)=o(1).
 \label{eq:tpc49-flat-cell-hypothesis}
\end{equation}
Then for every nonzero source weight \(a\),
\begin{equation}
 \frac{\cE_{\mathscr R_{36}}(M_X;a,b)^2}
 {\|D_aM_XD_b\|_{S_2}^2}
 \le X^{o(1)}.
 \label{eq:tpc49-flat-cell-conclusion}
\end{equation}
\end{corollary}

This is a checkable sufficient condition for a separated TPC cell.
The current inherited interface does not supply
\eqref{eq:tpc49-flat-cell-hypothesis}; it is a new active-cell task.

\subsection{A support-class obstruction inside the same mask}

Let \(\sigma\) be the perfect matching from
\cref{cor:tpc49-static-density-matching} and define
\begin{equation}
 P_\sigma(\alpha,\gamma)=\one_{\gamma=\sigma(\alpha)}.
 \label{eq:tpc49-matching-packet}
\end{equation}
Then \(P_\sigma\) is supported entirely where \(M_X=1\).

\begin{theorem}[Sharp actual-mask-support witness]
\label{thm:tpc49-mask-support-witness}
The packet \eqref{eq:tpc49-matching-packet} satisfies
\begin{equation}
 \|P_\sigma\|_{\pi,\infty}=1,
 \qquad
 \|P_\sigma\|_{S_1}=N,
 \qquad
 \|P_\sigma\|_{S_2}^2=N,
 \qquad
 r_{\rm nuc}(P_\sigma)=N.
 \label{eq:tpc49-matching-witness-data}
\end{equation}
At the inherited endpoint,
\begin{equation}
 N=X^{267/400+o(1)}.
 \label{eq:tpc49-matching-witness-endpoint}
\end{equation}
Thus actual-mask support plus bounded projective cost
\(X^{o(1)}\) cannot control arbitrary supported coefficients at atomic
scale.
\end{theorem}

\begin{proof}
The matrix is a permutation, so
\cref{prop:tpc49-permutation-sharp} applies.  The endpoint row count is
\(N=X^{o(1)}LD=X^{267/400+o(1)}\).
\end{proof}

The witness deliberately zeros all other admitted entries.  It is not
the literal multiplier \(\gamma_m\mathfrak A_{m,\gamma}^{\rm act}(j)\),
and no claim is made that the physical prime/cofactor packet realizes
it.  Constructing a polynomial family of literal matching atoms would
require arithmetic information about \(mj+h_0\) and its eligible large
prime factor; that information is precisely outside the present gate.
