\section{Claim boundary and the next gate}
\label{sec:tpc49-boundaries}

\subsection{What is proved}

The present paper establishes the following reusable conclusions.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item On every genuinely Hilbertized coefficient face, the optimal
       projective-to-atomic energy loss is exactly the nuclear
       participation rank.
 \item A fixed signed representation has an independent cancellation
       condition number; appending null pairs proves that it cannot be
       omitted.
 \item The TPC--36 bounded projective norm transfers to the Hilbert
       envelope with the sharp weighted-density factor
       \(\delta_w^{-1}\).
 \item On the complete dyadic row universe, the complete-universe
       extension of the literal static-mask formula has density
       \(1-o(1)\), a perfect matching, and only soft distortion for the
       specified explicit representation.
 \item The admitted support nevertheless contains a permutation packet
       with full row-count distortion.  Thus support-only methods and
       bounded projective complexity alone are sharply insufficient for
       arbitrary supported coefficients.
 \item If the entire endpoint allowance is assigned to the isolated
       Hilbertized face, its exact ledger is
       \(2\chi+\rho\le1/400\), while the computable density route gives
       the sufficient target
       \(2\varpi+\theta\le1/400\).
\end{enumerate}

The static-mask result is not merely an abstract norm restatement.  It
removes one possible polynomial obstruction on the complete row model
and replaces a vague ``projective-to-atomic'' request by two measurable
quantities: nuclear effective rank and representation efficiency.

\subsection{What is not proved}

None of the following is asserted.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item The inherited active row packet is not assumed to equal the
       complete universe \eqref{eq:tpc49-complete-row-universe}.  The
       current interface gives row-count upper bounds, not weighted
       lower density or flatness.
 \item The support-class matching packet is not the literal physical
       multiplier, and the product kernel is not the literal residual
       prime/cofactor coefficient.
 \item The full Banach profile envelope
       \(\mathfrak S_{\mathscr R}(\alpha)\) is not identified with a
       matrix nuclear norm.  In particular, no
       \(\mathfrak S_{\mathscr R}^2\ll X^{o(1)}\cD_0\) theorem is claimed.
 \item No cancellation of the coherent \(p\)-sum, no
       \(X^{o(1)}\) residual grouping bound, and no removal of the
       TPC--48 coarse-edge collision factor is proved.
 \item No sparse-alias unfolding or Fourier localization of the
       completed frozen field to the physical shift \(h_0\) is proved.
       Only \(h_0\) has literal physical provenance.
 \item The residual Gram route is not identified with the native affine
       physical face.
 \item No fixed-shift Chowla estimate, parity-barrier breach,
       Hardy--Littlewood asymptotic, bounded-gap theorem, or twin-prime
       conclusion follows.
\end{enumerate}

\subsection{Four next doors}

The reduction leaves four logically separate continuations.
\begin{description}[leftmargin=2.8em,style=nextline]
 \item[Door A: active-cell weighted survival.]
 Prove \(\delta_w\ge X^{-1/400+o(1)}\), or a stronger subpower bound,
 for the literal residue/Mellin cells that actually enter
 \eqref{eq:tpc49-inherited-envelope}.  This requires lower information
 about the retained opposite-row mass, not another sup-norm estimate.

 \item[Door B: representation-frame efficiency.]
 Replace the Minkowski \(L^1(d|\nu|)\) reassembly by a Bessel/frame
 estimate, or prove a quantitative no-cancellation lower Gram bound for
 the specified layers.  This controls \(c_{\mathscr R}\).

 \item[Door C: the coherent prime square.]
 Estimate, averaged over \(m,r\), the internal sum
 \begin{equation}
 \sum_{m,r}\left\|
 \sum_pA_\omega(p,r,m)\e(-pr\alpha)
 v_{\omega,p,r,m}
 \right\|^2
 \label{eq:tpc49-next-prime-square}
 \end{equation}
 relative to the literal prime-atomic square.  This is arithmetic and
 remains independent of the static mask result.

 \item[Door D: localization and grouping.]
 Control the residual map \(s=d(m)r\), the ultra-low shift interval,
 sparse aliases, and inversion at \(h_0\).  This door is downstream of
 the first three.
\end{description}

Door A is now a particularly sharp next experiment: failure can be
certified by an actual weighted cell of large nuclear rank, while
success spends a precisely quantified part of the \(1/400\) budget.
Door B admits an equally meaningful negative outcome if the specified
layer Gram matrix has an unavoidable polynomial condition number.  No
failure at either door invalidates the exact static-mask theorem or the
other continuation routes.
