\section{Deterministic certificate and reproducibility boundary}
\label{sec:tpc49-certificate}

The repository contains the exact-arithmetic script
\begin{center}
\texttt{experiments/tpc49\_certificate.py}.
\end{center}
It produces \texttt{tpc49\_certificate.json} and checks finite models
of the identities used in the paper.  No floating-point arithmetic or
random sampling is used.

The certificate performs the following tasks.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item It verifies the normalized Rademacher rank-one representation of
       \(I_n\) for \(1\le n\le8\), its exact bounded projective mass,
       and the permutation nuclear/Frobenius ledger.
 \item It constructs complete dyadic row universes for several finite
       parameter sets, evaluates the literal three-factor static mask,
       exhausts every forbidden row type, checks the degree union bound,
       and finds a perfect matching by a deterministic augmenting-path
       algorithm.
 \item It verifies that the matching packet lies entirely in admitted
       actual-mask positions and has exact distortion equal to the row
       count.
 \item It checks the product-delta permutation on several prime fields
       and the exact Gram identity
       \(A_rA_r^*=qI-J\) in a finite cyclotomic surrogate over prime
       fields with compatible roots of unity.
 \item It verifies the dense Hadamard recursion, row sums, Gram matrix,
       number of admitted entries, and the resulting exact singular-value
       ledger through its two invariant subspaces.
 \item It checks all rational endpoint exponent differences, including
       \(133/400-1/400=33/100\) and
       \(267/400-1/400=133/200\).
\end{enumerate}

The computation is a regression certificate, not a proof of the
asymptotic row count, the nuclear theorem, or any arithmetic estimate.
Those proofs are given in the text.  In particular, the certificate
does not search for literal prime/cofactor matching atoms and does not
test a twin-prime assertion.

The committed record contains \(298{,}427\) exact checks.  Its two
release digests are
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
semantic & \nolinkurl{20c576cf7e27e0cec91cce677395a02110b857f1db53dd161f2cc12068bac3a4}\\
source & \nolinkurl{4176a42c73c01d0b68532e1dfde30974f61f162309dcd5e001a087c0fcd9e580}
\end{tabular}
\end{center}

The generated JSON records the check count, all exact finite parameters,
a canonical semantic digest of the result payload, and the SHA--256
hash of the normalized source.  Re-running the script must reproduce
both hashes before a release PDF is accepted.
