\section{Endpoint ledger and the isolated-face Door-B threshold}
\label{sec:tpc49-endpoint}

Write the inherited exponents as
\begin{equation}
 \mu:=\frac{267}{400},
 \qquad
 \nu:=\frac{133}{400},
 \qquad
 \kappa:=\frac1{400},
 \qquad
 \mu+\nu=1.
 \label{eq:tpc49-endpoint-exponents}
\end{equation}
Thus the source-row scale is \(Q=X^{\mu+o(1)}\), the orbit scale is
\(J=X^{\nu+o(1)}\), and the inherited determinant-packet energy
allowance is \(X^{\kappa+o(1)}\)
\citep{WangTPC45,WangTPC47,WangTPC48}.

\subsection{The exact isolated-face budget criterion}

Suppose one finite Hilbertized coefficient face has
\begin{equation}
 c_{\mathscr R}(T)=X^{\chi+o(1)},
 \qquad
 r_{\rm nuc}(T)=X^{\rho+o(1)}.
 \label{eq:tpc49-endpoint-condition-exponents}
\end{equation}
By \cref{prop:tpc49-fixed-representation-ledger}, the fixed
representation loses the exact energy exponent
\begin{equation}
 2\chi+\rho.
 \label{eq:tpc49-exact-loss-exponent}
\end{equation}
If the entire \(X^{\kappa+o(1)}\) allowance is assigned to this isolated
Hilbertized face, then the face fits that budget exactly when
\begin{equation}
 \boxed{2\chi+\rho\le\frac1{400}}
 \label{eq:tpc49-endpoint-exact-condition}
\end{equation}
up to the declared \(o(1)\) convention.  This is not a
necessary-and-sufficient criterion for full TPC--48 closure.  If the remaining
coefficient-specific collision, prime-square, grouping, and localization
operations consume a combined exponent \(\lambda_{\rm other}\ge0\), the
corresponding multiplicative ledger instead requires
\begin{equation}
 2\chi+\rho+\lambda_{\rm other}\le\frac1{400}.
 \label{eq:tpc49-full-budget-ledger}
\end{equation}
Those other losses are not estimated in this paper.

For an optimal Hilbert projective representation, \(\chi=0\), so the
isolated-face criterion is \(r_{\rm nuc}\le X^{1/400+o(1)}\).  For a
named bounded-projective representation with
\begin{equation}
 P_{\mathscr R}=X^{\varpi+o(1)},
 \qquad
 \delta_w=X^{-\theta+o(1)},
 \label{eq:tpc49-density-ledger-exponents}
\end{equation}
\cref{thm:tpc49-weighted-transfer} gives the sufficient condition
\begin{equation}
 2\varpi+\theta\le\frac1{400}.
 \label{eq:tpc49-density-sufficient-condition}
\end{equation}
When \(P_{\mathscr R}=X^{o(1)}\), the clean target is
\begin{equation}
 \delta_w\ge X^{-1/400+o(1)}.
 \label{eq:tpc49-density-threshold}
\end{equation}
This density condition is minimax-sharp by permutations, but is only
sufficient for a specified coefficient matrix.  The exact criterion for
the isolated face remains \eqref{eq:tpc49-endpoint-exact-condition}.

\subsection{Model costs at the endpoint}

The following table uses the energy convention throughout.
\begin{center}
\begin{tabular}{@{}p{0.38\textwidth}p{0.25\textwidth}p{0.24\textwidth}@{}}
\toprule
face or model & effective energy loss & excess over \(X^{1/400}\) \\
\midrule
complete-universe static-mask formula model
 & \(X^{o(1)}\)
 & none in this model \\
signed Ferrers mask, \(n=X^{O(1)}\)
 & \(\asymp(\log n)^2=X^{o(1)}\)
 & none \\
product permutation, prime \(q\asymp J\)
 & \(X^{133/400+o(1)}\)
 & \(X^{33/100+o(1)}\) \\
actual-mask-support matching, \(N=QX^{o(1)}\)
 & \(X^{267/400+o(1)}\)
 & \(X^{133/200+o(1)}\) \\
dense-slope common-profile collision at the TPC--48 coarse edge
 & \(X^{67/200+o(1)}\)
 & \(X^{133/400+o(1)}\) \\
\bottomrule
\end{tabular}
\end{center}

The first line is the positive theorem
\eqref{eq:tpc49-static-canonical-soft} for the complete-universe
extension of the literal formula.  It
is not a theorem for an arbitrarily pruned active joint multiplier.  The
matching line is supported inside the literal static-mask graph but
uses artificial coefficient values.  The product-permutation line is a
completed finite-field model.  Neither is a lower bound for the literal
prime/cofactor coefficient.

The last line is a different obstruction.  TPC--48 proves that common
orbit profiles improve unrestricted slope synthesis, yet a dense
consecutive-slope model at the coarse edge still has collision factor
\begin{equation}
 X^{\mu-\nu+o(1)}=X^{67/200+o(1)}.
 \label{eq:tpc49-inherited-collision}
\end{equation}
The present static-mask theorem does not cancel that factor.  Nuclear
distortion and determinant-slope collision are separate multiplicative
ledgers.

\subsection{What a full active-cell theorem would have to say}

For a separated residue/Mellin cell of the actual joint multiplier, a
usable theorem may take either of two forms:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.4em]
 \item a weighted admission and specified-representation efficiency estimate satisfying
       \eqref{eq:tpc49-density-sufficient-condition}; or
 \item a direct singular-value estimate satisfying
       \eqref{eq:tpc49-endpoint-exact-condition}, possibly by
       \cref{cor:tpc49-approximate-rank}.
\end{enumerate}
The former can use \cref{cor:tpc49-degree-flatness} after proving
opposite-row flatness of the literal active weight.  The latter could
exploit coefficient-specific low effective rank even when admitted
density is small.

After the individual cells are controlled, one still needs a frame or
no-cancellation theorem for their signed \(L^1(d|\nu|)\) reassembly.
Orthogonality of formal layers is not enough under Minkowski by
\cref{prop:tpc49-orthogonal-layers}.  Finally, the coherent prime square
inside \eqref{eq:tpc49-row-vector} and the completed-to-\(h_0\)
normalization must be treated separately.  These are arithmetic and
localization inputs, not missing steps in the nuclear calculation.
