\section{The inherited coefficient interface}
\label{sec:tpc49-interface}

We first state exactly which TPC objects motivate the finite-dimensional
theory.  This section imports definitions, not an atomic comparison.

\subsection{Rows and the literal static mask}

On one source-compatible dyadic packet, a row is
\begin{equation}
 \alpha=(\ell_\alpha,d_\alpha),
 \qquad m_\alpha=\ell_\alpha d_\alpha\asymp Q,
 \qquad Q=LD,
 \label{eq:tpc49-row-definition}
\end{equation}
where \(\ell_\alpha\asymp L\) is prime and
\(d_\alpha\asymp D\) is squarefree.  The inherited separation makes
\(m_\alpha\) determine the row on the active packet.  TPC--36 defines
\begin{equation}
 \mathfrak m_{\rm act}(\alpha,\gamma)
 =\one_{\ell_\alpha\ne\ell_\gamma}
  \one_{|m_\alpha-m_\gamma|>\Delta}
  \one_{(d_\alpha,d_\gamma)\le G},
 \label{eq:tpc49-actual-static-mask}
\end{equation}
with
\begin{equation}
 \Delta=QX^{-\kappa_0},
 \qquad G=X^{\kappa_0},
 \qquad \kappa_0>0.
 \label{eq:tpc49-pruning-scales}
\end{equation}
The literal joint multiplier is
\begin{equation}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)
 =\mathfrak m_{\rm act}(\alpha,\gamma)
  \Xi_{\alpha,\gamma}(j)
  \cW_{\alpha,\gamma}(j/J).
 \label{eq:tpc49-joint-multiplier}
\end{equation}
Here \(\Xi\) is fixed-period in \(j\) and \(\cW\) contains smooth
cutoffs.  After splitting the fixed residue classes and applying the
inherited Mellin separation, the full multiplier has an exact signed
projective representation with every fixed orbit seminorm having
\(X^{o(1)}\) total variation \citep{WangTPC36}.

For a finite kernel \(K:\cI\times\cJ\to\C\), the relevant TPC--36
norm is
\begin{equation}
 \|K\|_{\pi,\infty}
 :=\inf_{K=\int p_\omega q_\omega\,d\nu(\omega)}
 \int \|p_\omega\|_\infty
       \|q_\omega\|_\infty\,d|\nu|(\omega).
 \label{eq:tpc49-bounded-projective-norm}
\end{equation}
The exact static-mask theorem gives
\begin{equation}
 \|\mathfrak m_{\rm act}\|_{\pi,\infty}
 \ll \log(2Q)(3+2\sqrt2)^{\omega_*}
 =X^{o(1)},
 \label{eq:tpc49-inherited-mask-cost}
\end{equation}
where \(\omega_*\) is the maximum number of prime factors of an active
row divisor.  This is an unconditional identity and upper bound on the
declared packet.  It is not a nuclear-norm or Gram estimate.

\subsection{The physical atomic diagonal}

TPC--45 writes the literal stripped equality atoms as
\(b_{i,u}\), where \(i\) records an output row and an orbit time and
\(u\) is the squarefree equality label.  Its atomic diagonal is
\begin{equation}
 \cD_0:=\sum_i\sum_u|b_{i,u}|^2.
 \label{eq:tpc49-physical-atomic-diagonal}
\end{equation}
At the all-minus prime-sign point the associated Walsh polynomial
recovers the literal physical equality columns \citep{WangTPC45}.  The
quantity \(\cD_0\) is therefore tied to one fixed physical shift and to
the native atomic indexing.  It is not the Cartesian energy of an
arbitrary completed determinant family.

After large-prime descent, the left residual synthesis at the physical
shift \(h_0\) has the form
\begin{equation}
 \cF_{h_0}^{\rm act,L}
 =\sum_{\substack{\gamma,j,m,p,r\\pr-mj=h_0}}
 \gamma_m^{(1)}
 \mathfrak A_{m,\gamma}^{\rm act}(j)
 \mu(r)\Lambda(pr)
 e_{\gamma,d(m)r}\otimes e_j.
 \label{eq:tpc49-physical-residual}
\end{equation}
It uses literal coefficients, but belongs to the low-sign-averaged
residual Gram route rather than the native affine physical face
\citep{WangTPC45,WangTPC47}.

\subsection{The frozen projective row-square}

TPC--47/48 freezes every coefficient constructed at \(h_0\) and
replaces the determinant equation by \(pr-mj=h\) for arbitrary
\(h\in\Z\).  Only \(h=h_0\) has physical provenance.  One exact
projective layer is
\begin{equation}
 \cF_h^\omega
 =\sum_{p,r,m}
  \sum_{j\equiv a_\omega\!\!\pmod{H_0}}
 A_\omega(p,r,m)\phi_\omega(j/J)
 v_{\omega,p,r,m}\otimes e_j\,
 \one_{pr-mj=h}.
 \label{eq:tpc49-projective-layer}
\end{equation}
The complete frozen family is the signed Bochner integral of all such
layers.  Fourier transformation in \(h\) defines
\begin{equation}
 B_{\omega,m}(\alpha)
 :=\sum_{p,r}A_\omega(p,r,m)
   \e(-pr\alpha)v_{\omega,p,r,m}.
 \label{eq:tpc49-row-vector}
\end{equation}
At fixed \(m\), distinct \(r\) have orthogonal residual labels, but the
inner \(p\)-sum remains coherent.  For a fixed admissible global
representation \(\mathscr R\), TPC--48 introduces
\begin{equation}
 \mathfrak S_{\mathscr R}(\alpha)
 :=\int C_{\rm LS}(\phi_\omega,H_0)^{1/2}
 \left(\sum_m\|B_{\omega,m}(\alpha)\|^2\right)^{1/2}
 d|\nu|(\omega).
 \label{eq:tpc49-inherited-envelope}
\end{equation}
Its pointwise infimum over admissible representations is
\(\mathfrak S_{\rm pr}\).  The infimum is not integrated; the annular
theorem retains one fixed measurable global representation
\citep{WangTPC48}.

Three differences from a finite matrix nuclear norm must remain visible:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.4em]
 \item \(C_{\rm LS}^{1/2}\) is a profile seminorm weight, not a declared
       Hilbert norm;
 \item the \(p\)-sum in \eqref{eq:tpc49-row-vector} is taken before the
       square; and
 \item \(\mathfrak S_{\mathscr R}(\alpha)\) belongs to a completed
       frozen field, whereas \(\cD_0\) belongs to one physical slice.
\end{enumerate}
The finite theory below applies exactly to Hilbertized coefficient
faces and supplies a criterion for each separated mask cell.  A full
comparison of \eqref{eq:tpc49-inherited-envelope} with
\eqref{eq:tpc49-physical-atomic-diagonal} needs additional theorems and
is not silently imported.
