\section{Introduction}
\label{sec:tpc49-introduction}

The all-band theorem of TPC--48 leaves a precise normalization problem.
The frozen residual determinant family built from the literal
\(h_0\)-coefficient field satisfies, schematically,
\begin{equation}
 \|\widehat{\cF}^{\rm fr}(\alpha)\|
 \le \mathsf L(\alpha)^{1/2}
      \mathfrak S_{\rm pr}(\alpha),
 \label{eq:tpc49-inherited-reduction-schematic}
\end{equation}
where \(\mathsf L\) is an explicit common-profile large-sieve factor
and \(\mathfrak S_{\rm pr}\) is the pointwise infimum of signed
projective row-square envelopes \citep{WangTPC48}.  The inherited TPC
denominator, however, is the physical atomic diagonal at one fixed
determinant shift.  A small bounded-projective norm for the row mask is
not by itself a comparison between these two quantities.  TPC--36
already warned that its
\(\ell^\infty\widehat\otimes_\pi\ell^\infty\) norm is a Schur-multiplier
complexity, not a Gram estimate \citep{WangTPC36}.

This paper isolates the finite-dimensional core of that mismatch.  It
has two logically independent parts.

First, once a coefficient face has genuinely been Hilbertized, the
optimal rank-one envelope is not mysterious: it is exactly the nuclear
norm.  The atomic diagonal is the squared Frobenius norm.  Their squared
ratio
\begin{equation}
 r_{\rm nuc}(T)
 :=\frac{\|T\|_{S_1}^2}{\|T\|_{S_2}^2}
 \label{eq:tpc49-intro-nuclear-rank}
\end{equation}
is the correct effective-rank invariant.  Algebraic rank gives a valid
upper bound, but can be very crude.  Stable rank gives no upper bound at
all.  Moreover, a fixed signed representation may be arbitrarily worse
than the optimal nuclear decomposition, because large cancelling layer
pairs do not change the coefficient tensor.  Thus every fixed-envelope
theorem needs two inputs: intrinsic nuclear effective rank and a
representation-efficiency estimate.

Second, the bounded projective norm of TPC--36 does become useful after
one measures how much weighted mass survives the mask.  For
\(A=D_aKD_b\), set
\begin{equation}
 \delta_w(A\mid K)
 :=\frac{\|A\|_{S_2}^2}
 {\|a\|_2^2\|b\|_2^2}.
 \label{eq:tpc49-intro-weighted-density}
\end{equation}
We prove the sharp transfer
\begin{equation}
 r_{\rm nuc}(A)
 \le \frac{\|K\|_{\pi,\infty}^2}{\delta_w(A\mid K)}.
 \label{eq:tpc49-intro-density-transfer}
\end{equation}
The factor \(\delta_w^{-1}\) is unavoidable in the class controlled
only by bounded projective cost and admitted density: a permutation
matrix has projective cost one and attains equality.

The complete-universe extension of the static TPC mask formula has
considerably more structure.  On the complete dyadic row universe, the
three deleted
sets---same source prime, near source product, and large row gcd---have
uniformly vanishing relative degree.  The mask is therefore
\(1-o(1)\) dense.  A specified explicit TPC--36 representation has soft
projective mass, so this complete-universe formula model has only
\(X^{o(1)}\)
projective-to-atomic distortion.  This is a positive conclusion: the
complete static mask does not account for a remaining polynomial loss.

There is an equally important negative conclusion.  The same dense
admitted graph has a perfect matching.  A permutation packet supported
only on that matching has projective cost one and nuclear effective
rank equal to the full row count.  It obeys the actual mask support but
does not equal the literal joint multiplier.  Consequently neither
support nor bounded projective complexity can replace a
coefficient-specific weighted-density or frame theorem.

\subsection{Main results}

The paper proves the following statements.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item The Hilbert projective infimum equals the nuclear norm, and the
       exact energy distortion is \(r_{\rm nuc}\); see
       \cref{thm:tpc49-Hilbert-projective}.
 \item For every fixed representation \(\mathscr R\), the distortion
       factors exactly as
       \begin{equation}
       \frac{\cE_{\mathscr R}(T)^2}{\|T\|_{S_2}^2}
       =c_{\mathscr R}(T)^2r_{\rm nuc}(T).
       \label{eq:tpc49-intro-exact-ledger}
       \end{equation}
       No bound uniform over all exact signed representations is
       possible.
 \item Bounded projective cost transfers to weighted atomic energy by
       \eqref{eq:tpc49-intro-density-transfer}, for both optimal and
       specified representations; see
       \cref{thm:tpc49-weighted-transfer}.
 \item On a complete dyadic TPC row cell, the complete-universe extension
       of the literal static-mask formula has minimum degree
       \((1-o(1))N\) and specified-representation
       distortion \(X^{o(1)}\); see
       \cref{thm:tpc49-static-degree,thm:tpc49-static-soft}.
 \item The actual-mask support contains a sharp permutation packet,
       while the completed product kernel of TPC--36 gives the same
       obstruction at orbit-scale modulus.  Ferrers separation costs
       only \(\asymp(\log n)^2\) in energy.
 \item If the entire isolated-face endpoint allowance is assigned here
       and
       \(c_{\mathscr R}=X^{\chi+o(1)}\) and
       \(r_{\rm nuc}=X^{\rho+o(1)}\), the exact face-budget condition is
       \(2\chi+\rho\le1/400\).
\end{enumerate}

\subsection{What is not identified}

The nuclear identity applies to a finite Hilbert tensor.  The full
TPC--48 quantity \(\mathfrak S_{\mathscr R}\) also contains a
\(C_{\rm LS}^{1/2}\)-weighted profile norm and an \(L^1(d|\nu|)\)
reassembly.  We do not declare that Banach profile envelope to be a
nuclear norm.  Nor do we replace its completed coherent prime square by
the fixed-\(h_0\) physical diagonal.  Those operations would conflate
the present mask theorem with prime cancellation, shift localization,
and residual grouping.

The result is therefore a genuine but scoped advance.  It supplies the
correct invariant and closes the complete static-mask model at soft
cost; it also proves why the remaining coefficient-specific input
cannot be inferred from support alone.  It does not prove a
fixed-shift Chowla estimate, a parity-barrier breach, or a prime-pair
asymptotic.

\subsection{Organization}

\Cref{sec:tpc49-interface} records the inherited coefficient interface.
\Cref{sec:tpc49-Hilbert-geometry} proves the nuclear identity and the
fixed-representation ledger.  \Cref{sec:tpc49-weighted-transfer}
establishes the weighted mask theorem.  \Cref{sec:tpc49-static-mask}
proves the complete-row degree theorem and the matching boundary.
\Cref{sec:tpc49-models} computes sharp model families.
\Cref{sec:tpc49-endpoint} inserts the TPC exponents, and
\cref{sec:tpc49-boundaries,sec:tpc49-certificate} state the next gate
and the deterministic certificate.
