\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Canonical Determinant Cells in a Primitive Mobius Tail: Support-Cardinality Bounds, All-Content Cell Pruning, and the Residue-Cell Zero-Mode Gate},
 pdfauthor={Liang Wang},
 pdfsubject={Unconditional pruning of canonical normalized-determinant windows and residue cells in a primitive Mobius-tail residual},
 pdfkeywords={Mobius tail, normalized determinant, translated window, residue cell, Schur test, dispersion gate}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\ee}[1]{e^{2\pi i #1}}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cS}{\mathcal S}
\newcommand{\cW}{\mathcal W}

\title{\textbf{Canonical Determinant Cells in a Primitive M\"obius Tail:}\\
\textbf{Support--Cardinality Bounds, All--Content Cell Pruning,}\\
\textbf{and the Residue--Cell Zero--Mode Gate}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let
\[
 N_m(j)=mj+h,\qquad N_n(j)=nj+h
\]
be two positive affine targets in the primitive opened-row packet of
the preceding M\"obius-tail reduction.  The row and orbit scales are
$Q=X^{\beta+o(1)}$ and $J=X^{1-\beta+o(1)}$, with $QJ\asymp X$.
For each off-diagonal row--orbit triple define the full target content
and the canonical normalized determinant by
\[
 c=(N_m(j),N_n(j)),\qquad
 \Delta^\#=\frac{m-n}{c}.
\]
The first quantity is factorization-independent, and the primitive
target identity makes $\Delta^\#$ an integer.  If
$U=N_m(j)/c$ and $V=N_n(j)/c$, then
\[
 (U,V)=1,\qquad mV-nU=h\Delta^\#.
\]
Thus $\Delta^\#$ is the determinant of the canonically reduced target
pair, rather than the determinant attached to one selected divisor
factorization.

For exact content $c$ and an allowed set $\Omega_c\subset\Z$, let
\[
 \cH_c(\Omega_c)
 =\#\{\delta\in\Omega_c:|\delta|\ll Q/c\}.
\]
The difference graph $m-n=c\delta$ has both degrees at most
$\cH_c(\Omega_c)$.  A Schur estimate, the physical row $\ell^2$
bound, and the single orbit class modulo $c$ give, for each of the
three retained raw channels,
\[
 \left|\cS\bigl(c\le Z,\ \Delta^\#\in\Omega_c\bigr)\right|
 \ll_{\eps,h,\mathscr D}
 X^\eps Q\log(2L)
 \sum_{c\le Z}\left(1+\frac Jc\right)
 \cH_c(\Omega_c).
\]
This is an unconditional capacity bound for every canonical
determinant spectrum.  It gives power saving whenever the displayed
orbit-weighted support count is polynomially smaller than $JQ$; the
explicit cases below include translated windows far from the row
diagonal and individual normalized-determinant residue cells.

Splicing this estimate with the large-target-content theorem of the
preceding paper removes the auxiliary restriction $c\le Z$.  If
$I$ is any translated interval of length $W$ and $a\pmod q$ is one
residue class, then for any splitting threshold $1\le C\ll Q$ the
full physical cell satisfies
\[
 \left|\cS\bigl(\Delta^\#\in I,
 \ \Delta^\#\equiv a\!\pmod q\bigr)\right|
 \ll X^\eps XQ\left[
 J^{-1}+C^{-1}
 +\left(1+\frac Wq\right)
 \left(\frac CX+\frac1Q\right)
 \right].
\]
Consequently, if $1+W/q\le X^{s+o(1)}$ with $s\ge0$ and $s<\beta$,
every fixed saving exponent below
\[
 \min\{1-\beta,\,\beta-s\}
\]
is available after optimizing $C$.  For one residue class over the
entire determinant range, the relaxed saving is
$\min\{1-\beta,\beta,\rho\}$ when $q=X^{\rho+o(1)}$.

At $\beta=267/400$, an arbitrary translated $J$-window or a single
class modulo $q\asymp J$ has every fixed saving below $133/400$ after
the all-content splice.  If the $J$-window is centered at
$|\Delta^\#|\asymp Q$, its content is automatically bounded and the
margin improves to $67/200$.  A translated window of width
$X^{1/2+o(1)}$ has every fixed saving below $67/400$.

The result is cellwise.  Summing all determinant cells absolutely
recovers the original row family, and an exact finite Fourier formula
shows that the unweighted reassembly is the $r=0$ coefficient of an
auxiliary residue-cell transform.  Nonzero cell energy alone therefore
does not close the residual.  A candidate next route must restore the
prime--M\"obius core while retaining the fixed residue factors, pair
mask, and matched cutoff difference, and then estimate this coefficient.
No such dispersion theorem,
prime-pair asymptotic, positivity result, or breach of sieve parity is
claimed here.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; canonical
normalized determinant; support cardinality; translated determinant
window; residue cell; Schur bound; dispersion gate.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary 11B25.

\input{sections/introduction}
\input{sections/physical-interface}
\input{sections/canonical-determinant}
\input{sections/row-graph-entropy}
\input{sections/small-content-transfer}
\input{sections/all-content-splice}
\input{sections/high-beta-ledger}
\input{sections/fourier-zero-mode}
\input{sections/comparison-next-gate}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
