\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\e}{\mathrm e}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rank}{\operatorname{rank}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\diag}{\operatorname{diag}}

\hypersetup{
  pdftitle={Canonical Mellin Quotient Frames: Finite-Sampling Kernels, Interior Stability, and the Boundary of Signed TPC Reassembly},
  pdfauthor={Liang Wang},
  pdfsubject={Sharp continuous-frame obstructions and positive quotient frames for canonical Mellin reassembly},
  pdfkeywords={Mellin inversion, quotient frame, finite sampling, condition number, prime squarefree rows, static mask, parity problem}
}

\title{\bfseries Canonical Mellin Quotient Frames:\\
Finite-Sampling Kernels, Interior Stability,\\
and the Boundary of Signed TPC Reassembly}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The preceding twin-prime-correlation reduction left a signed Mellin
reassembly between fixed-complexity cell survival and the full
projective profile.  We determine exactly which frame statement is
available.  If a continuous Mellin dictionary is allowed arbitrary
signed coefficient densities, no lower frame can hold: every synthesis
into a finite-dimensional physical Hilbert space has a nonzero smooth
kernel.  For the phase dictionary at logarithmic samples
\(y_1,\ldots,y_N\), the kernel is explicit,
\[
 g(t)=\prod_{n=1}^{N}\left(\frac d{dt}+iy_n\right)\rho(t),
 \qquad \rho\in C_c^\infty(\R),
\]
and neighboring continuous atoms have arbitrarily large
total-variation-to-output condition number.  Thus a raw continuous
Riesz bound is not merely unproved; it is false.

One provenance-fixed scalar Mellin direction is different at the exact
algebraic level.  For a fixed smooth shape \(W\), positive samples
\(x_n\), and coefficients
\(c_n\), Mellin inversion gives the exact identities
\[
 \cE_B(W;c)=A_B(W)\|c\|_2,
 \qquad
 \|\cS_Wc\|_2^2=\sum_n|c_nW(x_n)|^2,
\]
where \(A_B(W)\) is a polynomially weighted Wiener--Mellin mass.
Consequently, on a declared sample set on which
\(\inf_n|W(x_n)|\geq\eta>0\), the canonical condition number is
\(O_{B,W,\eta}(1)\).  Coordinate samples approaching a zero of the
physical cutoff give quantified polynomial, or even super-polynomial,
obstructions.  For a fixed finite scalar family we bound the quotient
condition number in terms of its normalized sampled Gram matrix.  Weak
convergence of the sample measures and linear independence of the
limiting shapes then give an \(O(1)\) quotient frame for that abstract
fixed-family problem.

We apply this criterion to the prime--squarefree dyadic row universe.
Its normalized logarithmic sample measure converges to the measure with
density \(e^{x+y}\) on \([0,\log2]^2\).  Uniformly for a log-Fourier
bank of degree at most a fixed power of \(\log X\), the sampled Gram is
bounded above and below.  The literal TPC static mask changes its lower
frame bound by at most
\[
 O\!\left(\epsilon_X(2K+1)^2\right),
 \qquad
 \epsilon_X\ll
 L^{-1+o(1)}+D^{-1+o(1)}+X^{-\kappa_0+o(1)}.
\]
Hence every declared fixed finite scalar family, and every retained
finite log-Fourier bank in the stated range, has zero polynomial
sampling-and-mask cost at the inherited numerical endpoint.  Passing
from this theorem to the actual TPC provenance requires an additional
bridge: the genuine orbit-translate family is \(X\)-dependent and
Hilbert-valued, and its weighted continuous Mellin envelope must be
compared with the sampled Hilbert energy.  Those uniform Gram or
relative-tail and norm-comparison hypotheses are formulated here but
are not verified.  This bridge therefore remains open before coherent
prime summation, residual grouping, physical-shift localization, and
native-Gram identification.  No fixed-shift prime-pair estimate, parity
breach, or twin-prime conclusion is claimed.
\end{abstract}

\noindent\textbf{Keywords:} Mellin inversion; quotient frame; finite
sampling; condition number; prime--squarefree rows; static mask;
projective reassembly; sieve parity.

\medskip
\noindent\textbf{Convention.}
All Hilbert spaces are complex.  Continuous synthesis is understood as
a Bochner integral.  A ``canonical'' measure always means the fixed
real-axis Mellin measure supplied by the physical smooth shapes, before
any projective decomposition of the static mask.  Constants may depend
on the fixed shapes, residue moduli, and derivative order, but not on
\(X\).  We write \(\e^z:=\exp z\),
\(\e(z):=\exp(2\pi i z)\), and
\(\e_q(z):=\e(z/q)\).

\medskip
\noindent\textbf{MSC 2020:} Primary 42A38, 46C05; Secondary 11N35,
42B35, 15A18.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/continuous-kernels}
\input{sections/canonical-direction}
\input{sections/quotient-frames}
\input{sections/arithmetic-sampling}
\input{sections/mask-robustness}
\input{sections/endpoint-boundaries}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
