\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\E}{\mathbb E}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\cD}{\mathcal D}
\newcommand{\cF}{\mathcal F}
\newcommand{\cP}{\mathcal P}
\newcommand{\one}{\mathbf 1}
\newcommand{\Pminus}{P^{-}}
\newcommand{\Pplus}{P^{+}}
\newcommand{\QZ}{\mathbb Q_Z}

\hypersetup{
  pdftitle={Robust Small-Prime Freezing at the Four-Mobius Gate: Walsh-Face Compression, Exact Prime Descent, and the High-Prime Drift Barrier},
  pdfauthor={Liang Wang},
  pdfsubject={Partial de-randomization of the Mobius Walsh corner through low-prime projection complexity and exact coefficient descent},
  pdfkeywords={Mobius function, Walsh spectrum, random multiplicative function, prime filtration, parity problem, Type II estimate}
}

\title{\bfseries Robust Small--Prime Freezing at the Four--M\"obius Gate:\\
Walsh--Face Compression, Exact Prime Descent,\\
and the High--Prime Drift Barrier}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
TPC--43 represented the surviving equality energy at the four--M\"obius
gate as a nonnegative Walsh polynomial whose all--minus prime corner is
the physical M\"obius value.  Its annealed theorem controlled almost
every prime--sign environment but did not select that corner.  We prove
a partial de--randomization.  Split every squarefree row label at
a cutoff \(z\), and let \(\nu_z\) be the number of distinct small--prime
parts occurring in the actual packet.  A Hilbert--space grouping and one
Cauchy--Schwarz inequality give
\[
 \Pp_{>z}\!\left(
  \sup_{\sigma_{p\le z}}Z_0(\sigma,\varepsilon_{>z})
  >L\nu_z\cD_0\right)\le L^{-1}.
\]
Thus one high--prime environment controls every small--prime face
simultaneously.  At the inherited endpoint, a Rankin bound for the
projected labels gives
\(
 \nu_z\le X^{62549/26302500+o(1)}
\)
for \(z=(\log X)^{501/500}\), strictly below the available
\(K_B=X^{1/400+o(1)}\) budget.  Consequently a density \(1-o(1)\) set of
high--prime environments remains admissible after all signs
\(p\le z\) are overwritten arbitrarily, in particular by the physical
all--minus values.  We also give two exact prime--by--prime transports.
The coefficient restriction energy satisfies
\[
 |Z_0(-\one)-\cD_0|^2
 =\operatorname{Var}(Z_0)
   \prod_p(1-\theta_p),
 \qquad -1\le\theta_p\le1,
\]
while conditional face energies give an exact likelihood product in an
energy--biased measure.  A degree--two, entirely \(z\)-rough Gram
example has vanishing relative variance, vanishing normalized
influences, and vanishing prime--toggle quadratic variation, yet its
all--minus amplification diverges.  Hence variance, fixed moments,
rough support, or small local defects cannot finish the deterministic
endpoint.  What remains is a coefficient--specific high--prime
cumulative correlation estimate, naturally of bilinear/Type--II type;
no parity breach or prime--pair theorem is claimed.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius correlation; Walsh face; random
multiplicative function; small--prime freezing; reverse martingale;
coefficient descent; sieve parity.

\medskip
\noindent\textbf{Convention.}
All prime sets and Walsh polynomials at a fixed scale are finite.  Empty
coefficient energies are handled by continuity, so normalized
correlations are defined only when their denominators are positive.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 42C10; Secondary 60E15,
11N36, 11K65.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/prime-martingales}
\input{sections/robust-face}
\input{sections/quantitative-cutoff}
\input{sections/coefficient-descent}
\input{sections/face-transport}
\input{sections/sharp-obstruction}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
