\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Factor-Scale Localization of a Prime-Target Residual: Hard-Edge Bulk Persistence, Type-I Resolution, and Finite-Mellin Minimax Barriers},
 pdfauthor={Liang Wang},
 pdfsubject={Rigorous positive and negative scale-localization results for a fixed-shift prime-target residual},
 pdfkeywords={Bombieri--Vinogradov theorem, Mellin transform, optimal recovery, Selberg sieve, fixed-shift prime-pair boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cI}{\mathcal I}
\newcommand{\cM}{\mathcal M}
\newcommand{\cN}{\mathcal N}
\newcommand{\cP}{\mathcal P}
\newcommand{\cS}{\mathcal S}
\newcommand{\TV}{\mathrm{TV}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\Ran}{\operatorname{Ran}}
\newcommand{\supp}{\operatorname{supp}}

\title{\textbf{Factor-Scale Localization of a Prime-Target Residual:}\\
\textbf{Hard-Edge Bulk Persistence, Type-I Resolution,}\\
\textbf{and Finite-Mellin Minimax Barriers}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Fix $h\ne0$ and a real-valued $W\in C_c^1((0,\infty))$.  We attach to the
prime-target residual the signed factor-scale measure
\[
 \nu_{X,h}=\sum_{m,n\geq1}(\Lambda(n)-1)\Lambda(mn+h)W(mn/X)
 \delta_{\log(n/m)}.
\]
Its total mass, the zero Mellin mode, was evaluated previously by the
identity $\sum_{n\mid r}(\Lambda(n)-1)=\log r-\tau(r)$.  The present paper
asks how much localization in $\log(n/m)$ can be recovered rigorously.

There are two positive answers.  Write
\[
 I_0(W)=\int_0^\infty W(u)\,du,\qquad
 C_h=\prod_{p\mid h}(1-p^{-1})
     \prod_{p\nmid h}\left(1+\frac1{p(p-1)}\right).
\]
If both factors are restricted by $m,n>Y$, then, uniformly for
$2\leq Y\leq X^{1/3}$,
\[
 \sum_{m,n>Y}(\Lambda(n)-1)\Lambda(mn+h)W(mn/X)
 =(1-C_h)I_0(W)X\log X+O_{h,W}(X\log(2Y)).
\]
The analogous $\Lambda(n)$ form has leading coefficient $I_0(W)$.  Thus
the complete leading coefficient survives after every fixed,
polylogarithmic, or more generally $\log(2Y)=o(\log X)$ hard edge is removed
from both factor coordinates.  This is coarse bulk persistence, not a
fixed-ratio Type~II estimate.  Second, maximal Bombieri--Vinogradov gives
an asymptotic for every fixed smooth log-scale window in the Type~I range.
For $D\leq X^{1/2}(\log X)^{-B}$, it evaluates the insertion
$V(\log(n/m)-s)$ uniformly in every center $s\in\R$.

We then give an exact boundary for deductions from finitely many Mellin
samples or Taylor jets.  On a total-variation ball, the minimax error for a
window $V$ equals its uniform distance from the exponential-polynomial
space generated by the observed samples.  Geometric divisor nodes
$r=p^D$ produce explicit null profiles.  At the prime-target row
$3^4+2=83$, two adversarial, non-arithmetic probability profiles on genuine
divisor nodes have identical jets through order three but different local
window masses.  On expanding log-scale intervals, any fixed finite
sample/jet set
that includes the zero-frequency value has limiting risk equal to the
trivial midpoint risk.  Resolving a fixed-width interior window from
zero-frequency jets costs order $\log X$ jets at the information level.

Finally, the first Taylor interfaces are computed exactly.  The first two
nonconstant coefficients already contain convolutions of two von
Mangoldt factors.  A two-variable Mellin demodulation followed by an
all-frequency sinc-squared kernel isolates the $m=1$ layer exactly; its
predicted asymptotic is precisely the corresponding single-weight
fixed-shift Hardy--Littlewood assertion.  No complete-tail localized asymptotic,
fixed-shift prime-pair theorem, twin-prime lower bound, new distribution
level, or breach of the parity barrier is claimed.
\end{abstract}

\noindent\textbf{Keywords:} prime-target residual; factor-scale
localization; Bombieri--Vinogradov theorem; Selberg upper-bound sieve;
Mellin data; optimal recovery; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N13, 11N36; Secondary 11M06,
41A10, 41A65.

\input{sections/introduction-scope}
\input{sections/scale-bulk}
\input{sections/type-i-localization}
\input{sections/minimax-recovery}
\input{sections/geometric-certificates}
\input{sections/taylor-selector-boundary}
\input{sections/conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
