\begin{abstract}
TPC--61 identifies the exact normalized Gram of the literal missing-native
map at a fixed nonzero shift, while TPC--62 shows that support degree and
entrywise magnitudes alone lead only to phase-blind Schur certificates.  We
develop the complementary signed-operator route without selecting a minor,
deleting a difficult row, or replacing a complete native output by a
reduced collision cell.

Before erasure the normalized residual Gram is
\(I+\Xi_{=s}\), not generally the identity.  Native erasure adds the new
unequal-residual gate \(\Xi_{\ne s}\), so the full defect is
\(H=\Xi_{=s}+\Xi_{\ne s}=\Xi_{\ne p}\).  After the common residual
M\"obius gauge is calibrated, every off-diagonal entry of this full defect
is exactly a normalized two-affine sum with sign
\(\mu(mj+h_0)\mu(nj+h_0)\).  The gauge change is spectrally inert; it is
not a cancellation estimate.  We prove six finite-dimensional layers.
First, the missing-native norm and lower frame are the extremal eigenvalues
of \(I+H\), where \(H\) is a Hermitian zero-diagonal signed alias operator.
Second, sign-reversing partial matchings give exact pair-defect bounds for
complex literal weights.  Third, the maximum row \(\ell^2\)-star \(s_*\)
satisfies
\[
 s_*\le\|H\|\le\sqrt{\Delta}\,s_*,
\]
and a local extremizer shows why a scalar signed row sum cannot replace the
star norm.  Fourth, every entrywise pair majorant \(P\) gives the optimal
weighted-Schur certificate \(\|H\|\le\rho(P)\).  Fifth, even operator
walks and traces give
\[
 \|H\|\le
 \left(\max_m\sum_n|(H^{2q})_{mn}|\right)^{1/(2q)}
 \quad\text{and}\quad
 \|H\|\le(\tr H^{2q})^{1/(2q)}.
\]
Their literal expansions retain unequal-residual and complex-phase
closed-walk cancellation that an entrywise majorant discards; on a pure
same-residual walk the target signs telescope to one.  Sixth, these
estimates form a certificate lattice for both extremal eigenvalues of the
missing-native Gram.

For the full represented-plus-missing map we retain the nuisance space
\(\Ker A\).  An exact shorted-Gram corollary separates the direct
canonical Gram defect from a positive shorting penalty; control of the
missing-native Gram alone does not control that penalty.  Five explicit
countermodels distinguish coordinate gauge, pair, star, support-phase, and
nuisance obstructions.  All operator identities are L0 and their
specialization to the complete fixed-\(h_0\) carrier is L1.  Uniform
pairing defects, star savings, growing operator-walk estimates, missing-mass
savings, and shorting control are stated only as unproved L2 premises.  No
parity, prime-pair, or twin-prime conclusion is claimed.
\end{abstract}
