\section{Literal pair cancellation after gauge removal}
\label{sec:tpc68-gauge-pairing}

Because \(H\) and \(\widetilde H\) are unitarily equivalent, we work with
the gauged matrix and drop the tilde in this and the next three sections.
Thus every off-diagonal entry has the exact form
\eqref{eq:tpc68-two-affine-entry}.

\subsection{Signed complex pair lists}

Fix distinct active rows \(m,n\).  Let
\[
 \mathcal C_{mn}
 :=
 \{(w,w')\in\mathcal W_M^2:
 m(w)=m,\ m(w')=n,\ i(w)=i(w')\}
\]
be their complete native collision list.  For
\(\xi=(w,w')\in\mathcal C_{mn}\), define
\begin{align}
 \varepsilon_\xi^{mn}
 &:=
 \mu(mj(w)+h_0)\mu(nj(w')+h_0)\in\{-1,1\},
 \label{eq:tpc68-pair-sign}\\
 v_\xi^{mn}
 &:=
 \frac{\overline{\beta_w}\beta_{w'}}
 {\sqrt{W_M(m)W_M(n)}}\in\mathbb C.
 \label{eq:tpc68-pair-complex-weight}
\end{align}
Then
\begin{equation}
 H_{mn}=\sum_{\xi\in\mathcal C_{mn}}
 \varepsilon_\xi^{mn}v_\xi^{mn}.
 \label{eq:tpc68-literal-pair-list}
\end{equation}
The coefficient \(v_\xi^{mn}\) is complex and literal.  Replacing it by its
magnitude before pairing would discard physical phase information.

Write
\[
 \mathcal C_{mn}^{\pm}
 :=\{\xi\in\mathcal C_{mn}:\varepsilon_\xi^{mn}=\pm1\}.
\]

\begin{definition}[Admissible sign-reversing matching]
\label{def:tpc68-admissible-pairing}
An admissible matching for the row pair \((m,n)\) is a bijection
\[
 \tau:A\longrightarrow B
\]
between subsets \(A\subseteq\mathcal C_{mn}^{+}\) and
\(B\subseteq\mathcal C_{mn}^{-}\).  The matching may depend on the fixed
literal carrier, the row pair, and all literal coefficients
\(v_\xi^{mn}\).  It may not depend on a coefficient vector subsequently
inserted into the row space or on an extremizing eigenvector of \(H\).
\end{definition}

\begin{theorem}[Complex sign-reversing pair certificate]
\label{thm:tpc68-pair-certificate}
For every admissible matching \(\tau:A\to B\),
\begin{equation}
 |H_{mn}|
 \le
 \sum_{\xi\in A}|v_\xi^{mn}-v_{\tau(\xi)}^{mn}|
 +\sum_{\xi\in\mathcal C_{mn}\setminus(A\cup B)}
 |v_\xi^{mn}|.
 \label{eq:tpc68-pair-matching-bound}
\end{equation}
Consequently the literal pair defect
\begin{equation}
 P_{mn}
 :=
 \min_{\tau\ {\rm admissible}}
 \left\{
 \sum_{\xi\in\operatorname{dom}\tau}
 |v_\xi^{mn}-v_{\tau(\xi)}^{mn}|
 +
 \sum_{\xi\ {\rm unmatched}}|v_\xi^{mn}|
 \right\}
 \label{eq:tpc68-optimal-pair-defect}
\end{equation}
is well defined, symmetric after setting \(P_{nm}=P_{mn}\), satisfies
\begin{equation}
 |H_{mn}|\le P_{mn},
 \label{eq:tpc68-entry-below-defect}
\end{equation}
and is computable from the finite literal coefficient array.  If
\(P_{mn}=0\), then \(H_{mn}=0\).
\end{theorem}

\begin{proof}
Every matched positive-negative pair contributes
\[
 (+1)v_\xi^{mn}+(-1)v_{\tau(\xi)}^{mn}
 =v_\xi^{mn}-v_{\tau(\xi)}^{mn}.
\]
The remaining terms are unmatched.  The triangle inequality gives
\eqref{eq:tpc68-pair-matching-bound}.  There are finitely many partial
matchings, including the empty one, so the minimum exists.  Swapping
\((m,n)\) conjugates every weight and leaves all absolute defects
unchanged; hence the symmetric convention is consistent.
\end{proof}

\begin{remark}[Exact orthogonality is stronger than sign balance]
Equal cardinalities
\(|\mathcal C_{mn}^{+}|=|\mathcal C_{mn}^{-}|\) do not imply
\(P_{mn}=0\).  Exact cancellation also requires a matching of the
\emph{complex literal weights}.  Conversely, unequal cardinalities do not
preclude \(H_{mn}=0\), because several complex terms may cancel without a
pairwise equality.  Thus \(P_{mn}\) is a sufficient certificate, not an
exact formula for \(|H_{mn}|\).
\end{remark}

\subsection{An ordered partial-sum certificate}

Some arithmetic decompositions supply an order on the collision list
rather than a literal matching.  The following exact Abel certificate
records what such an order would need to control.

\begin{proposition}[Complex Abel certificate]
\label{prop:tpc68-Abel-certificate}
If \(\mathcal C_{mn}=\varnothing\), then \(H_{mn}=0\).  Otherwise let
\(\xi_1,\ldots,\xi_N\), with \(N\ge1\), be any fixed ordering of
\(\mathcal C_{mn}\), and abbreviate
\[
 \varepsilon_k:=\varepsilon_{\xi_k}^{mn},
 \qquad v_k:=v_{\xi_k}^{mn},
 \qquad A_t:=\sum_{k\le t}\varepsilon_k.
\]
Then
\begin{equation}
 |H_{mn}|
 \le
 \max_{1\le t\le N}|A_t|
 \left(
 |v_N|+\sum_{k=1}^{N-1}|v_{k+1}-v_k|
 \right).
 \label{eq:tpc68-Abel-bound}
\end{equation}
\end{proposition}

\begin{proof}
The empty-list assertion follows from
\eqref{eq:tpc68-literal-pair-list}.  For \(N\ge1\), summation by parts
gives the exact identity
\[
 \sum_{k=1}^{N}\varepsilon_kv_k
 =A_Nv_N+\sum_{k=1}^{N-1}A_k(v_k-v_{k+1}).
\]
Taking absolute values proves \eqref{eq:tpc68-Abel-bound}, with no
restriction that the complex weights lie on one ray.
\end{proof}

Neither the partial sums \(A_t\) nor the variation of the actual physical
weights are estimated here.  Choosing an order after inspecting a later
extremizing vector would violate the L1 quantifier; choosing it from the
fixed carrier and literal pair coefficients is allowed.

\subsection{Pair certificates and their limit}

The matrix
\[
 P=(P_{mn})_{m,n\in\mathcal M_M},
\qquad P_{mm}:=0,
\]
is a symmetric nonnegative majorant of \(|H|\).  It contains more signed
information than the raw support degree, but it has already taken an
absolute value at the level of each completed row pair.  Therefore it
cannot see cancellation between different edges in a row star or between
different complete operator walks.  The next two sections distinguish
these levels.
