\section{Introduction}
\label{sec:tpc68-introduction}

The missing-high reassembly problem contains two different questions.  The
first asks how much a family of literal missing atoms can amplify after its
residual labels are erased and its contributions are coherently returned to
native outputs.  The second asks whether the resulting missing map can
cancel a represented map along coefficient directions invisible to the
represented denominator.  The first is a signed native-Gram problem.  The
second is a shorted-operator problem.  Conflating them turns a useful
restricted norm estimate into a false uniform reassembly statement.

TPC--60 defined the physical missing-high map and proved exact nuisance
elimination by a shorted Gram \citep{WangTPC60}.  TPC--61 then fixed the
complete missing carrier before the coefficient vector, factored the map
through residual coordinates, and identified its optimal normalized native
Gram \citep{WangTPC61}.  TPC--62 supplied inverse localization and
phase-blind Schur bounds: a large operator norm leaves a row, cell, and pair
witness, whereas a uniform pair estimate must still beat the actual
collision degree \citep{WangTPC62}.  TPC--67 pursued a different door,
using all-row full-output minors, matching holonomy, and determinant mass
to certify a lower frame \citep{WangTPC67}.  The present paper returns to
the direct operator door advertised there.

\subsection{The narrow object of this paper}

The main arithmetic object is only the \emph{literal missing-native map}
\[
 M_X:\ell^2(\mathcal M_X)\longrightarrow\ell^2(\mathcal I_X^{\rm nat})
\]
from the TPC--61 very-high missing carrier.  Its source rows, atoms,
external blocks, side labels, orbit labels, residual labels, native labels,
masks, profiles, and coefficients are frozen before a coefficient vector is
chosen.  We neither extend the TPC--61 entry formula to the entire prime
packet nor assert that it already describes the cross terms of the full
represented-plus-missing Gram.

There are two output levels.  Before erasure the residual output is
\((i,s)\); after erasure the native output is \(i\).  Every still-orthogonal
physical label, including side, external block, opposite row, the
\(\gamma\)-label, and orbit time \(j\), remains inside \(i\).  Only the
residual label \(s\) is summed out, because only that erasure occurs in the
physical construction.  This is stricter than replacing \(i\) by a
reduced arithmetic collision cell.  The pre-erasure normalized Gram is
not assumed to be the identity: its same-residual defect remains part of
the full native operator.

\subsection{The six exact layers}

After physical row normalization, write
\[
 K=F^*F=I+H.
\]
The six finite-dimensional layers proved below are:
\begin{enumerate}[label=\textup{(\Alph*)},leftmargin=3em]
 \item an exact gauge-to-genuine-sign identity for \(H\);
 \item complex-weight sign-reversing pair certificates;
 \item exact star-norm bounds and their local sharpness;
 \item an entrywise pair majorant and its Perron/weighted-Schur optimum;
 \item even operator-walk and trace certificates that retain cancellation
       between complete walks; and
 \item a certificate lattice converting any of these estimates into upper
       and lower eigenvalue bounds for \(K\).
\end{enumerate}
These layers are deterministic.  They do not assume random signs,
independence, generic phases, or an average over shifts.

\subsection{Why operator walks are a genuinely different door}

A pair majorant first takes an absolute value of every off-diagonal entry.
Once that is done, cancellation between different row pairs is lost.
By contrast, \(H^{2q}\) expands into complete row walks.  Products of the
row gauges telescope on closed walks, while unequal-residual target signs
and literal complex phases remain.  Pure same-residual target signs also
telescopically trivialize, a limitation made explicit below.  An arithmetic
estimate for a whole decorated walk sum could
therefore succeed even when every pair-majorant bound is too expensive.
This is a logical possibility, not a theorem that such an estimate exists.

\subsection{Claim levels and nonclaims}

We use the following hierarchy throughout.
\begin{itemize}
 \item \textbf{L0:} exact finite-dimensional linear algebra for a fixed
       coefficient array.
 \item \textbf{L1:} identification of that array with the complete literal
       fixed-\(h_0\) missing carrier and its physical atomic normalization.
 \item \textbf{L2:} any new uniform cancellation or saving for the
       two-affine M\"obius sums, their stars, or their operator walks.
\end{itemize}
The paper proves L0 and records the L1 crosswalk.  It does not prove the L2
premises needed for a subpower native norm, an endpoint reassembly
inequality, a parity improvement, a prime-pair estimate, or a twin-prime
result.  In particular, all statements hold for an arbitrary fixed
nonzero \(h_0\); none is specialized to \(h_0=2\).

\subsection{Organization}

\Cref{sec:tpc68-literal-interface} freezes the physical carrier and derives
the signed Gram.  \Cref{sec:tpc68-gauge-pairing} gives pair certificates.
\Cref{sec:tpc68-star-perron} proves star and Perron bounds, and
\cref{sec:tpc68-operator-walks} gives the walk route.
\Cref{sec:tpc68-certificate-lattice} assembles the exact certificate
lattice.  \Cref{sec:tpc68-shorted-reassembly} restores the nuisance
directions of the full reassembly problem.
\Cref{sec:tpc68-countermodels} gives five separating examples.
\Cref{sec:tpc68-conditional-arithmetic,sec:tpc68-claim-boundary} state the
conditional arithmetic targets, kill criteria, and precise stopping line.
