\section{The complete literal missing-native interface}
\label{sec:tpc68-literal-interface}

This section specializes the TPC--61 construction without changing its
carrier.  It is included to make the quantifiers and the place where signs
become physical completely explicit.

\subsection{Frozen carrier and complete output labels}

Fix a scale \(X\), a nonzero integer \(h_0\), one direct side, one external
block, all source and opposite-row blocks, residue and orbit classes,
masks, profiles, endpoint restrictions, and the very-high cutoff before
choosing a coefficient vector.  The opposite direct side is included by
orthogonal direct sum.  Let \(\mathcal W_M\) be the complete set of actual
nonzero missing-high atoms in this scope.  Let \(\mathcal M_X\) be the
complete declared physical row set and
\begin{equation}
 \mathcal K_X:=\ell^2(\mathcal M_X)
 \label{eq:tpc68-full-coefficient-space}
\end{equation}
the full coefficient space.

Every \(w\in\mathcal W_M\) canonically recovers
\[
 m=m(w)=d_m\ell_m,\qquad
 j=j(w),\qquad
 n(w)=m(w)j(w)+h_0,
\]
its largest prime \(p(w)>y\), cofactor \(r(w)=n(w)/p(w)\), and residual
label
\[
 s(w)=d_{m(w)}r(w).
\]
The squarefree physical support gives
\[
 \mu(s(w))=\mu(d_{m(w)})\mu(r(w)).
\]
The complete native key is denoted by \(i(w)\).  It retains the side,
external block, opposite row, \(\gamma\)-coordinate, orbit time \(j\), and
every other label that remains orthogonal after native reassembly.  Thus
\[
 i(w)=i(w')\quad\Longrightarrow\quad j(w)=j(w'),
\]
but the residual labels \(s(w)\) and \(s(w')\) may differ.

The literal atom driven by row coefficient \(\zeta_m\) is
\[
 \beta_w\zeta_{m(w)},
\]
where \(\beta_w\ne0\) retains every physical source shape, mask, multiplier,
opposite-row factor, profile, and terminal weight.  There is no freely
chosen atomwise phase.  The TPC--61 singleton incidence says that, for a
fixed pair \((i,m)\), at most one atom of \(\mathcal W_M\) occurs.  Define
\[
 \mathcal M_M
 :=\{m:\text{some }w\in\mathcal W_M\text{ has }m(w)=m\}.
\]
Rows in \(\mathcal M_X\setminus\mathcal M_M\) have identically zero
missing mass.  They remain in \(\mathcal K_X\) and in the represented map;
only the normalized missing Gram will be restricted to its active range.

\subsection{Residual map, erasure, and native map}

Set
\begin{equation}
 c_w:=-\mu(s(w))\beta_w,
 \qquad
 (L_X\zeta)_w:=c_w\zeta_{m(w)}
 \qquad(\zeta\in\mathcal K_X).
 \label{eq:tpc68-atomic-lift}
\end{equation}
The physical high-character and residual M\"obius sign occur exactly once
in \(c_w\).  Put
\begin{align}
 (T_X\zeta)_{i,s}
 &:=
 \sum_{\substack{w\in\mathcal W_M\\
                 i(w)=i,\ s(w)=s}}
 c_w\zeta_{m(w)},
 \label{eq:tpc68-residual-map}\\
 (\mathsf Ez)_i&:=\sum_s z_{i,s}.
 \label{eq:tpc68-erasure-map}
\end{align}
Then the literal missing-native map is exactly
\begin{equation}
 \boxed{M_X=\mathsf E T_X.}
 \label{eq:tpc68-missing-native-factorization}
\end{equation}
This is the TPC--61 sign convention.  In particular, inserting a second
M\"obius sign after \eqref{eq:tpc68-erasure-map} would change the physical
map.

Before erasure, multiplication by
\[
 (U_\mu z)_{i,s}:=\mu(s)z_{i,s}
\]
is unitary on the residual space.  This fact says only that storing the
common residual sign in the input or in a signed erasure is a coordinate
choice.  It does \emph{not} say that the sign disappears from
\(\mathsf EU_\mu\): after \(s\) is erased, different residual coordinates
meet and their relative signs are genuine.

\subsection{Physical atomic normalization}

For every row \(m\in\mathcal M_X\), set
\begin{equation}
 W_M(m)
 :=
 \sum_{\substack{w\in\mathcal W_M\\m(w)=m}}|\beta_w|^2\ge0,
 \qquad
 D_M:=\diag\bigl(W_M(m)\bigr)_{m\in\mathcal M_X}.
 \label{eq:tpc68-row-missing-mass}
\end{equation}
This is raw counting-measure atomic mass.  No output-fiber degree or
collision multiplicity is divided out; equivalently,
\[
 D_M=L_X^*L_X
\]
on the full coefficient space.  Let
\begin{equation}
 S_M:=\Ran D_M=(\Ker D_M)^\perp
     =\ell^2(\mathcal M_M).
 \label{eq:tpc68-active-missing-range}
\end{equation}
If \(S_M=\{0\}\), then \(\mathcal W_M=\varnothing\) and \(M_X=0\); the
missing-native analysis is vacuous.  Henceforth assume
\(S_M\ne\{0\}\).

Define the normalized missing-native incidence
\begin{equation}
 F:=M_XD_M^{\dagger/2}\big|_{S_M}:
 S_M\longrightarrow
 \ell^2(\mathcal I_X^{\rm nat}).
 \label{eq:tpc68-normalized-F}
\end{equation}
Thus zero missing rows remain in \(\mathcal K_X\), while the normalized
Gram acts only on the support of the physical missing diagonal.

Define also the normalized residual incidence
\begin{equation}
 F_{\rm res}:=T_XD_M^{\dagger/2}\big|_{S_M}.
 \label{eq:tpc68-normalized-residual}
\end{equation}
The TPC--61 residual/native split gives Hermitian zero-diagonal operators
\begin{equation}
 H_{\rm res}:=\Xi_{=s},
 \qquad
 H_{\rm erase}:=\Xi_{\ne s},
 \label{eq:tpc68-res-erase-defects}
\end{equation}
such that
\begin{align}
 F_{\rm res}^*F_{\rm res}
 &=I_{S_M}+H_{\rm res},
 \label{eq:tpc68-residual-Gram-split}\\
 F^*F
 &=I_{S_M}+H_{\rm res}+H_{\rm erase}
 =I_{S_M}+\Xi_{\ne p}.
 \label{eq:tpc68-native-Gram-split}
\end{align}
In particular, the residual Gram in
\eqref{eq:tpc68-residual-Gram-split} is not generally \(I\).
Multiplication by \(U_\mu\) leaves it unchanged, because two contributions
meeting at one residual output have the same \(s\).  The operator
\(H_{\rm erase}\) consists exactly of the new cross terms created by
erasing unequal residual labels.

\begin{proposition}[Normalized signed alias Gram]
\label{prop:tpc68-normalized-signed-Gram}
One has
\begin{equation}
 K:=F^*F=I_{S_M}+H,
 \label{eq:tpc68-K-IH}
\end{equation}
where
\begin{equation}
 H=H_{\rm res}+H_{\rm erase}=\Xi_{\ne p}
 \label{eq:tpc68-full-H-split}
\end{equation}
is Hermitian and has zero diagonal.  Moreover
\begin{align}
 \kappa_M
 &:=\sup_{\substack{\zeta\in\mathcal K_X\\
                    \langle D_M\zeta,\zeta\rangle>0}}
   \frac{\|M_X\zeta\|^2}{\langle D_M\zeta,\zeta\rangle}
   =\lambda_{\max}(K)
   =1+\lambda_{\max}(H),
 \label{eq:tpc68-upper-native-eigenvalue}\\
 \alpha_M
 &:=\inf_{\substack{\zeta\in\mathcal K_X\\
                    \langle D_M\zeta,\zeta\rangle>0}}
   \frac{\|M_X\zeta\|^2}{\langle D_M\zeta,\zeta\rangle}
   =\lambda_{\min}(K)
   =1+\lambda_{\min}(H)\ge0.
 \label{eq:tpc68-lower-native-eigenvalue}
\end{align}
\end{proposition}

\begin{proof}
For a fixed \(m\in\mathcal M_M\), the \((i,m)\)-singleton property makes distinct missing
atoms occupy distinct native coordinates within that column.  Hence
\[
 \|Fe_m\|^2
 =\frac1{W_M(m)}
   \sum_{\substack{w\in\mathcal W_M\\m(w)=m}}|\beta_w|^2
 =1.
\]
Thus \(K=F^*F\) is positive semidefinite with unit diagonal.  Therefore
\(H=K-I\) is Hermitian with zero diagonal.  Substituting
\(x=D_M^{1/2}\zeta\in S_M\) into the two Rayleigh quotients gives the
extremal eigenvalue identities.  The map \(M_X\) vanishes on
\(\Ker D_M\), so retaining zero missing rows in \(\mathcal K_X\) does not
change either quotient.
\end{proof}

\begin{remark}[Notation]
The symbol \(\alpha_M\) in
\eqref{eq:tpc68-lower-native-eigenvalue} is the lower eigenvalue of the
atomic-normalized missing-native Gram.  It is not the restricted erasure
upper norm denoted by \(\beta_M\) in TPC--61.
\end{remark}

\subsection{Exact removal of the row gauge}

Define the diagonal row gauge
\begin{equation}
 U_d:=\diag\bigl(\mu(d_m)\bigr)_{m\in\mathcal M_M}.
 \label{eq:tpc68-row-gauge}
\end{equation}
It is a self-adjoint unitary on the squarefree active support.

\begin{theorem}[Gauge-to-genuine-sign identity]
\label{thm:tpc68-gauge-to-sign}
Put \(\widetilde H:=U_dHU_d\).  Then \(\widetilde H\) is unitarily
equivalent to \(H\), has the same zero diagonal, spectrum, entry
magnitudes, star norms, and collision graph, and for \(m\ne n\),
\begin{equation}
 \boxed{
 \widetilde H_{mn}
 =
 \frac1{\sqrt{W_M(m)W_M(n)}}
 \sum_{\substack{w,w'\in\mathcal W_M\\
                 m(w)=m,\ m(w')=n\\
                 i(w)=i(w')}}
 \mu(mj(w)+h_0)\mu(nj(w')+h_0)
 \overline{\beta_w}\beta_{w'}.}
 \label{eq:tpc68-two-affine-entry}
\end{equation}
Every label summed in \eqref{eq:tpc68-two-affine-entry} is an actual
complete native output; no reduced collision cell has been substituted.
\end{theorem}

\begin{proof}
The normalized matrix entry is
\[
 K_{mn}
 =
 \frac1{\sqrt{W_M(m)W_M(n)}}
 \sum_{\substack{w,w'\in\mathcal W_M\\
                 m(w)=m,\ m(w')=n\\
                 i(w)=i(w')}}
 \mu(s(w))\mu(s(w'))
 \overline{\beta_w}\beta_{w'}.
\]
The two minus signs in the definition of \(M_X\) cancel.  For \(m\ne n\),
this is \(H_{mn}\).  Multiplication by the row gauges replaces
\(\mu(s(w))\) by
\[
 \mu(d_m)\mu(s(w))
 =\mu(r(w)).
\]
Since \(mj(w)+h_0=p(w)r(w)\) is squarefree and
\(p(w)\nmid r(w)\),
\[
 \mu(mj(w)+h_0)=-\mu(r(w)).
\]
The two extra minus signs again cancel in the product for \(m,n\), giving
\eqref{eq:tpc68-two-affine-entry}.  Unitary conjugation proves every
spectral and magnitude assertion.
\end{proof}

\subsection{Direct-cell formula and the orthogonal second side}

Assume in this subsection the identical-support direct-cell specialization
of TPC--61: after the literal mask and opposite-row factors are retained,
the high and missing tests depend on \((m,j)\) and not on the surviving
\(\gamma\)-coordinate.  On the displayed left direct cell, write the unique atom as
\(w=(m,j,\gamma)\), extending its coefficient by zero when the declared
literal support fails, and factor
\begin{equation}
 \beta_{m,j,\gamma}
 =a_m(j)K_{m\gamma}q_\gamma(j).
 \label{eq:tpc68-direct-cell-factorization}
\end{equation}
Here \(a_m(j)\) contains the source and terminal shapes,
\(q_\gamma(j)\) contains the opposite-row shape and its fixed output phase,
and \(K_{m\gamma}\in\{0,1\}\) is the literal static mask.  Define the
actual missing-time indicator
\begin{equation}
 \mathfrak m_m(j)
 :=
 \mathbf1_{\{(m,j,\gamma)\in\mathcal W_M
                 \text{ for some }\gamma\}},
 \label{eq:tpc68-missing-time-indicator}
\end{equation}
where coefficient zeros caused only by \(K_{m\gamma}\) or
\(q_\gamma(j)\) remain inside those factors.  Put
\begin{equation}
 \Gamma_{m,n}(j)
 :=
 \sum_\gamma
 K_{m\gamma}K_{n\gamma}|q_\gamma(j)|^2.
 \label{eq:tpc68-Gamma-overlap}
\end{equation}

\begin{corollary}[Literal direct-cell two-affine formula]
\label{cor:tpc68-direct-cell-formula}
For distinct active rows \(m,n\), the left direct-cell contribution is
\begin{equation}
 \boxed{
 \begin{aligned}
 \widetilde H^{\,L}_{mn}
 ={}&
 \frac1{\sqrt{W_M(m)W_M(n)}}
 \sum_j
 \mathfrak m_m(j)\mathfrak m_n(j)\\
 &\times
 \mu(mj+h_0)\mu(nj+h_0)
 \overline{a_m(j)}a_n(j)\Gamma_{m,n}(j).
 \end{aligned}}
 \label{eq:tpc68-direct-cell-two-affine}
\end{equation}
The right direct slice has the symmetric formula with the two row systems
exchanged.  Its output range is orthogonal to the left slice, so
\[
 K=F_L^*F_L+F_R^*F_R.
\]
Consequently, for \(m\ne n\),
\[
 H_{mn}=H^L_{mn}+H^R_{mn},
\]
with no cross-slice Gram term.
\end{corollary}

\begin{proof}
A common complete native output on the left fixes the same pair
\((\gamma,j)\).  Substitute
\eqref{eq:tpc68-direct-cell-factorization} into
\eqref{eq:tpc68-two-affine-entry}, retain the two actual missing
indicators, and sum over \(\gamma\).  Orthogonality of the declared side
labels gives the final assertion.
\end{proof}

Outside the declared identical-support specialization, the compressed
\(\Gamma_{m,n}(j)\)-formula need not be valid.  One must either retain the
general literal pair sum \eqref{eq:tpc68-two-affine-entry}, or replace
\(\mathfrak m_m(j)\) by the full \(\gamma\)-dependent first-failure
indicator inside the \(\gamma\)-sum.  No later theorem requires the
compressed formula.

\begin{corollary}[Full versus erasure-only certificates]
\label{cor:tpc68-full-versus-erasure}
Every certificate developed below applies directly to the full defect
\[
 H=H_{\rm res}+H_{\rm erase}.
\]
The row gauge \(U_d\) conjugates both summands separately, so the same
decomposition holds in the gauged coordinates used below.
Alternatively, it may be applied separately to the two summands, followed
by
\begin{equation}
 \|H\|\le\|H_{\rm res}\|+\|H_{\rm erase}\|.
 \label{eq:tpc68-res-erase-triangle}
\end{equation}
A certificate for \(H_{\rm erase}\) alone does not bound
\(\kappa_M\) unless \(H_{\rm res}\) is controlled separately.
\end{corollary}

\begin{proof}
The first statement is definitional, and the second is the operator
triangle inequality combined with
\eqref{eq:tpc68-full-H-split}.
\end{proof}

\begin{proposition}[Same-residual target signs are frozen]
\label{prop:tpc68-same-residual-sign-freeze}
Fix distinct rows \(m,n\).  If a common-output pair
\((w,w')\) also satisfies
\[
 s(w)=s(w')=:s,
\]
then its gauged target sign is
\begin{equation}
 \boxed{
 \mu(mj(w)+h_0)\mu(nj(w')+h_0)
 =\mu(d_m)\mu(d_n),}
 \label{eq:tpc68-same-residual-frozen-sign}
\end{equation}
which is independent of the collision pair.  Thus \(H_{\rm res}\) has no
intra-pair oscillation coming from the two target M\"obius signs.  Any
cancellation there must come from the literal complex weights; new
residual-sign interference occurs in \(H_{\rm erase}\), or in cancellation
between the two completed operators.
\end{proposition}

\begin{proof}
Squarefreeness gives
\[
 \mu(s)=\mu(d_m)\mu(r(w))
       =\mu(d_n)\mu(r(w')).
\]
Since each row gauge is a sign,
\[
 \mu(mj(w)+h_0)
 =-\mu(r(w))
 =-\mu(d_m)\mu(s),
\]
and similarly for \(n,w'\).  Multiplying the two identities proves
\eqref{eq:tpc68-same-residual-frozen-sign}.  Before the row gauge, the two
residual signs at the same \((i,s)\) multiply to \(\mu(s)^2=1\).
\end{proof}

\begin{remark}[What the identity does not prove]
\label{rem:tpc68-gauge-not-cancellation}
The theorem exposes the exact signs on which new arithmetic would have to
act.  It supplies no saving for their sum.  The output gauge \(U_\mu\) and
the source-row gauge \(U_d\) act on different spaces and must not be
identified.  Either diagonal gauge can reveal a useful formula, but
neither can reduce an operator norm.
\end{remark}

\subsection{Six-item L1 audit}

The literal specialization satisfies the following audit.
\begin{enumerate}[label=\textup{(L1.\arabic*)},leftmargin=4em]
 \item The entries are the actual coefficients
       \(-\mu(s(w))\beta_w\), with no free atomwise phase.
 \item Every target is \(mj+h_0\) for one fixed physical \(h_0\ne0\).
 \item The full diagonal \(D_M\) is raw physical atomic mass; its zero
       rows are retained in \(\mathcal K_X\).
 \item Source rows and every retained output label are canonical; only the
       residual label is erased.
 \item The carrier, active rows, complete native outputs, collision graph,
       and every certificate family below are fixed before the later
       coefficient vector or extremizer.
 \item The exact identities cost no endpoint exponent.  Every eventual
       arithmetic estimate must still fit the total strict \(1/400\)
       endpoint ledger.
\end{enumerate}
