\begin{abstract}
We isolate the first genuinely arithmetic obstruction behind
determinant-energy survival in the fixed-shift matched cutoff shell.
The literal coefficient is written as a sum of native triplet weights
\(u_t\) over normalized-determinant fibers \(F_n\).  For prescribed
fiber moduli \(r_i\), we prove that the complete interval of attainable
resultant magnitudes in the unrestricted free-phase comparison class
is
\[
 \bigl[(2r_{\max}-\sum_i r_i)_+,\ \sum_i r_i\bigr].
\]
This gives the sharp phase-blind lower envelope
\[
 \sum_n(2r_{\max,n}-R_n)_+
\]
for the post-bin \(\ell^1\) mass.  It can vanish even when the raw
absolute mass is natural, so a raw lower bound and a fiber-survival
theorem are logically distinct.  The extremizing free phases need not
be realizable by the coupled phases of the literal physical packet.

We then prove the exact identity
\[
 D=E_{\rm trip}+C_{\rm eq}
\]
between determinant energy, the native triplet diagonal, and the
ordered off-diagonal equal-determinant correlation.  The literal
TPC-32 packet bounds, imported on the high-\(\beta\) physical domain
\(C=\lfloor J\rfloor\ll Q\), imply
\[
 E_{\rm trip}\ll_\varepsilon X^\varepsilon JQ^2
 \asymp X^{-1+\varepsilon}Q^3J^2.
\]
Hence any energy lower bound with fixed loss smaller than \(1\)
requires a positive off-diagonal term of asymptotically the same size.
This is a conditional positive-coherence gate: no such lower bound is
proved here.

Finally, we give an exponent ledger and an audit-ready proposed
native-key census schema.  A raw-mass loss \(\lambda_R\) followed by a
fiber-survival loss \(\lambda_{\rm fib}\) certifies energy loss
\(2(\lambda_R+\lambda_{\rm fib})\) under the verified \(O(Q)\) support
bound.  Candidate duplicate, symmetry, and shared-divisor pairings are
classified without assigning them an unproved main term.  The
proposed implementation aggregates exact determinant keys by
streaming or external sort and obtains
\(C_{\rm eq}=D-E_{\rm trip}\) without enumerating all pairs.  No
census is executed and no archive or data are supplied.  The finite
identities close an algebraic \(\mathrm{L0}\) gate; the TPC-32
diagonal comparison, the derived conditional coherence gate, and the
proposed schema are \(\mathrm{L1}\) interfaces, not the missing
growing-scale \(\mathrm{L2}\) arithmetic lower bound.
\end{abstract}
