\section{An audit-ready proposed native-key census schema}
\label{sec:census-protocol}

The proposed computation is not a search over rounded determinant
bins.  This section specifies an audit-ready schema and a scalable
execution design for a future census of the literal coefficient.
No census is executed in this paper, and no native archive, parameter
manifest, machine-readable schema, code, or census output is supplied.
Thus the word ``proposed'' is essential: the requirements below are
not themselves a reproducibility claim.  Every listed field is needed
either to reconstruct \(u_t\), to prove determinant equality, or to
prevent a change of normalization.

\subsection{Archive schema}

For each fixed \(X\), fixed \(h_0\), and fixed packet, a future
implementation should archive:
\begin{enumerate}[leftmargin=2.2em]
 \item \textbf{Experiment identity:} code revision, parameter file,
 fixed \(h_0\), smooth-support identifiers, residue data, and
 random-seed field if any.  The typed packet-scale tuple is
 \[
 (L,D_{\rm row},Q,J,R_{\rm cut},T,U_0,C).
 \]
 \item \textbf{Native row keys:} complete \(\alpha,\gamma\), row
 slopes \(m_\alpha,m_\gamma\), row provenance, literal complex
 coefficients \(\gamma_\alpha^{(1)},\gamma_\gamma^{(2)}\), and row
 orientation.
 \item \textbf{Orbit and targets:} \(j\), exact integers
 \(N_\alpha(j),N_\gamma(j)\), their gcd \(c_t\), and every active
 support flag.
 \item \textbf{Determinant data:} numerator
 \(m_\alpha-m_\gamma\), exact signed quotient
 \(\nu_t=(m_\alpha-m_\gamma)/c_t\), and a proof flag for exact
 divisibility.
 \item \textbf{Expansion-tree data:} parent native-triplet key,
 matched-shell channel, \(Y\in\{U_0,T\}\), cutoff sign
 \(\epsilon_Y\), orientation label, and inverse aggregation map.
 These child records do not enlarge the native triplet multiset.
 \item \textbf{Divisor expansion data:} exact \(u,v\), divisor witnesses,
 \(b_R(u),b_R(v)\), squarefree and coprimality flags, and any
 exact-content inversion variable kept as a separate field.
 \item \textbf{Joint multiplier:} literal
 \(\mathfrak A_{\alpha,\gamma}(j)\), its mask, periodic and smooth
 factors, and a provenance hash.
 \item \textbf{Aggregation data:} physical multiplicity,
 computational expansion multiplicity, aggregation multiplier, and
 the final exact or certified-interval value of \(u_t\).
\end{enumerate}

The complete native key is a tuple of these identity fields.  A future
implementation must fix a canonical serialization, hash algorithm,
schema version, and precision policy.  A hash then supplies a
reproducibility check, not a mathematical proof of equality.  None of
those machine-readable choices is frozen in this paper.

\subsection{Fiber statistics}

After exact aggregation, the proposed output records for every
determinant \(n\):
\begin{equation}
\begin{aligned}
 m_n&=\#F_n,&
 R_n&=\sum_{t\in F_n}|u_t|,\\
 r_{\max,n}&=\max_{t\in F_n}|u_t|,&
 d_n&=(2r_{\max,n}-R_n)_+,\\
 A(n)&=\sum_{t\in F_n}u_t,&
 D_n&=|A(n)|^2.
\end{aligned}
\label{eq:fiber-census-fields}
\end{equation}
Global checks are
\begin{equation}
\begin{aligned}
 R&=\sum_nR_n,
 &M_{\min}^{\rm mag}&=\sum_nd_n,
 &M&=\sum_n|A(n)|,\\
 D&=\sum_nD_n,
 &E_{\trip}&=\sum_t|u_t|^2,
 &C_{\eqc}&=D-E_{\trip}.
\end{aligned}
\label{eq:global-census-checks}
\end{equation}
\subsection{Scalable determinant aggregation}

Let \(N_{\rm rec}=\#\cT\) be the number of native records after inverse
aggregation to parent triplets, and let \(B\) be an available-memory
record budget.  The proposed exact-key pipeline is:
\begin{enumerate}[leftmargin=2.2em]
 \item stream the expansion records, verify inverse multiplicities,
 aggregate them to native parent keys, emit
 \((\nu(t),t,u_t)\), and accumulate \(E_{\trip}\);
 \item stable-sort the emitted records by the exact integer
 determinant key \(\nu(t)\), using bounded in-memory runs and an
 external merge when \(N_{\rm rec}>B\);
 \item scan each determinant fiber once to compute
 \(m_n,R_n,r_{\max,n},A(n),D_n\), and then sum \(R,M,D\);
 \item compute the total off-diagonal correlation by the exact
 identity
 \[
  C_{\eqc}=D-E_{\trip},
 \]
 rather than by forming all ordered pairs.
\end{enumerate}
With comparison sorting this requires
\(O(N_{\rm rec}\log N_{\rm rec})\) comparisons,
\(O(N_{\rm rec})\) disk storage, and \(O(B)\) working memory, apart
from the standard external-merge pass count.  When the exact keys fit
in memory, deterministic sorting has the same comparison bound and
hash aggregation has expected \(O(N_{\rm rec})\) work.  Exact or
directed-interval accumulators must be used throughout; the final
subtraction returns an exact value or a certified interval.

\subsection{Compressed class joins}

Class totals should also avoid a global pair table.  Exact duplicates
are obtained by sorting or hashing the complete physical-atom key and
using group sums and multiplicities.  For a fixed registry of
\(K\) determinant-preserving maps, symmetry candidates are obtained
by \(K\) indexed key lookups.  Shared-target and shared-divisor
candidates are produced by exact sort-merge joins on their declared
integer relation keys.  Their nominal costs are, respectively,
\[
 O(N_{\rm rec}\log N_{\rm rec}),\qquad
 O(KN_{\rm rec}\log N_{\rm rec}),\qquad
 O(N_{\rm rec}\log N_{\rm rec}+Z),
\]
where \(Z\) is the join-output size; hash indexes may replace the
logarithmic lookup factors in expected time.

The quantity \(Z\) can be quadratic.  Whenever a class contribution
factorizes over a relation-key group, the implementation must store
compressed group sums, squared norms, counts, and formally verified
inverse multiplicities instead of materializing its pairs.  The
unpaired remainder is then computed by subtracting the disjoint
certified class totals from \(C_{\eqc}\).  A full ordered-pair table
is permitted only for a declared bounded exploratory run.  A class
whose relation does not admit certified compression must report its
output-sensitive cost and is not called scalable merely because the
global determinant aggregation is scalable.

\subsection{Classification fields}

Every pair materialized in a bounded run, and every compressed class
join representing such pairs, carries:
\begin{enumerate}[leftmargin=2.2em]
 \item an exact equal-determinant witness;
 \item a class label from \cref{sec:pairing-classification} and the
 declared priority-rule and registry versions;
 \item duplicate, symmetry, shared-target, and shared-divisor flags,
 each accompanied by the exact equations used;
 \item coefficient product \(u_t\overline{u_{t'}}\), or a rigorous
 complex interval enclosing it;
 \item physical multiplicity and expansion multiplicity separately;
 \item a conjugate-partner identifier, ensuring each reported class
 is real;
 \item the contribution to the chosen candidate main term and to its
 complement.
\end{enumerate}

\subsection{Exactness and support rules}

Integer targets, gcds, divisors, determinants, and M\"obius signs are
computed exactly.  Rational algebraic coefficients are stored
exactly when possible; otherwise directed interval arithmetic must
certify all signs and inequalities used in a theorem.  Floating-point
phase proximity is exploratory evidence only.  Overlapping numerical
intervals do not prove exact coefficient equality: Class \(1\)
requires a symbolic identity, a shared canonical provenance proof, or
another exact equality certificate.  Otherwise the pair remains
outside the duplicate class.

The active support is
\[
 \{n:A(n)\ne0\}
\]
after complete aggregation.  It may not be replaced by the available
determinant interval, a thresholded support, or the set of raw fiber
labels.  If numerical precision cannot decide whether \(A(n)=0\), the
bin is marked unresolved and no exact support count is reported.

\subsection{Scaling tests}

For a growing sequence of \(X\), a future census should report the
nonnegative loss diagnostics
\begin{align}
 \lambda_R(X)&=
 \frac{[\log(N_0/R)]_+}{\log X},
\label{eq:empirical-raw-loss}\\
 \lambda_{\rm fib}(X)&=
 \frac{[\log(R/M)]_+}{\log X},
\label{eq:empirical-fiber-loss}\\
 \lambda_D(X)&=
 \frac{[\log(Q^3J^2/D)]_+}{\log X},
\label{eq:empirical-energy-loss}
\end{align}
where \([y]_+=\max\{y,0\}\), whenever the displayed ratios are
defined.  The report also includes the untruncated raw ratios,
uncertainty intervals, and local slopes.  These quantities are
diagnostics, not asymptotic exponents until a theorem controls their
limits.

The following residual checks detect normalization errors:
\begin{equation}
 0\le M_{\min}^{\rm mag}\le M\le R,\qquad
 \frac{M^2}{S}\le D\le LM,\qquad
 D-E_{\trip}=C_{\eqc}.
\label{eq:census-invariants}
\end{equation}
where the middle lower bound is asserted only when \(A\ne0\).
Every future run must record the original global \(N_0=JQ^2\); no
per-fiber or per-triplet renormalization is permitted.

\begin{remark}[Sampling is not a completed census]
A sampled pair table can estimate which classes deserve attention,
but it cannot prove multiplicity, support, or a signed remainder
bound.  A publishable \(\Lone\) computation may use the compressed
exact joins above, provided the serialization, registry, compression
map, inverse multiplicities, manifests, and output checksums are
versioned and formally verified.  Those implementation artifacts
remain future work.
\end{remark}
