\section{Claim boundary and conclusion}
\label{sec:claim-boundary}

\subsection{Level ledger}

The results of this paper have three deliberately separate levels:
\begin{description}[leftmargin=2.4em,style=nextline]
 \item[\(\Lzero\): exact algebra and finite geometry.]
 The complete resultant interval, the sharp global magnitude
 envelope, the raw--fiber--energy exponent transfer, and
 \(D=E_{\trip}+C_{\eqc}\) are rigorous finite-dimensional results.

 \item[\(\Lone\): typed physical interface.]
 On the high-\(\beta\) domain \(C=\lfloor J\rfloor\ll Q\), the
 imported TPC-32 support, singleton, and triplet-diagonal bounds put
 \(E_{\trip}\) at most on the loss-one scale, so it loses at least one
 power relative to natural energy, up to soft factors; the conditional
 positive-coherence gate derived from that import is also \(\Lone\).
 The native-key schema, scalable aggregation design, pairing
 classification, invariants, and success/kill criteria specify an
 audit-ready proposed interface for the actual fixed-shift packet.
 No census has been executed and no archive or data are supplied.

 \item[\(\Ltwo\): growing arithmetic theorem.]
 A uniform lower bound for the literal \(R\), \(M\), or positive
 \(C_{\eqc}\) at growing \(X\) is not proved.  This remains the next
 arithmetic gate.
\end{description}

\subsection{What is proved}

Magnitude data have exactly one universal way to force fiber
survival: a dominant native term.  Its sharp contribution is
\((2r_{\max,n}-R_n)_+\).  Separately, if an energy theorem below loss
one is proved, the imported diagonal upper bound forces its main scale
to come from positive off-diagonal equal-determinant coherence.  These
two facts sharply narrow the search: either enough fibers are
magnitude-dominant, or a structured signed pairing must be found and
its remainder controlled.

\subsection{What is not proved}

We do not prove:
\begin{itemize}[leftmargin=2em]
 \item a lower bound for the actual raw or post-bin mass;
 \item a positive asymptotic for any unverified pairing class;
 \item a fixed-\(2\) estimate or a theorem uniform in a way that can
 be specialized to it;
 \item unweighted two-point Chowla;
 \item a breach of the parity barrier;
 \item the Hardy--Littlewood prime-pair asymptotic;
 \item infinitude of twin primes.
\end{itemize}
No numerical census, regardless of range, upgrades an \(\Lone\)
pattern to an \(\Ltwo\) theorem without uniform error control.

\subsection{Conclusion}

TPC-83 identifies post-bin mass as the energy-survival variable.
The present paper opens that variable one level deeper.  It proves the
optimal phase-blind certificate and isolates a conditional
positive-coherence gate: any future determinant-energy lower bound
with loss below one would force a same-scale positive off-diagonal
correlation.  It does not prove that lower bound or exhibit such a
correlation.  The proposed audit schema concentrates the remaining
uncertainty in a finite list of literal pairing mechanisms and a
precisely defined unpaired remainder, but those class totals have not
been computed.

This is forward progress in the sense appropriate to the fixed-shift
program: an algebraic ambiguity has been closed, an arithmetic gate
has been isolated, and every route through that gate carries an
explicit exponent and endpoint audit.  It is not a prime-pair
conclusion.
