\section{Introduction}
\label{sec:introduction}

The matched-shell determinant coefficient of TPC-32 is a signed sum.
TPC-83 shows that its natural determinant energy is equivalent, at
subpower resolution, to survival of the \emph{post-bin} \(\ell^1\)
mass \citep{WangTPC32,WangTPC83}.  That equivalence is exact and useful,
but it moves rather than removes the next obstruction: why should
literal contributions landing in the same determinant bin fail to
cancel?

This paper resolves the finite-dimensional part of that question and
then states the remaining arithmetic task in an audit-ready form.
There are two separate losses:
\begin{enumerate}[leftmargin=2.1em]
 \item the literal native packet may have too little raw absolute mass;
 \item even if that mass is natural, equal-determinant aggregation may
 cancel it.
\end{enumerate}
Neither loss is controlled by the upper-bound axioms presently
available.  In particular, bounded row multipliers are allowed to
vanish, and all native coefficients can be rescaled down while
preserving those axioms.

\subsection{The three conclusions}

Our first conclusion is a sharp phase-envelope theorem.  In one fiber,
knowledge of the moduli alone forces a nonzero resultant exactly when
one term dominates the sum of all the others.  Summed over fibers this
produces a computable, optimal lower certificate for the post-bin
mass.  If this certificate vanishes on most of the raw mass, the
failure is conclusive for every phase-blind argument, but says nothing
against a signed arithmetic mechanism.

Our second conclusion is structural.  The determinant energy is not
primarily a diagonal quantity at its natural scale.  If
\[
 N_0=JQ^2,\qquad QJ\asymp X,
\]
then the natural energy is
\[
 \frac{N_0^2}{Q}=Q^3J^2,
\]
whereas the literal triplet diagonal is at most
\[
 X^{o(1)}JQ^2
 \asymp X^{-1+o(1)}Q^3J^2.
\]
Thus a successful energy theorem with any fixed loss
\(\lambda_D<1\) would have to prove \emph{positive aggregate
coherence} among distinct native terms with equal determinant.  The
present paper proves this conditional \(\Lone\) necessity statement,
not its energy-lower-bound hypothesis.

Our third conclusion is methodological.  We specify an audit-ready
schema for a future native archive and census.  The proposed
classification distinguishes literal diagonal terms, exact duplicate
atoms, determinant-preserving symmetries, shared-target/shared-divisor
pairings, and an unpaired remainder.  No census is executed here, and
no asymptotic size is assigned to the last four classes without exact
key data and a proof.

\subsection{What is new and what is not}

The phase envelope, the energy decomposition, and the conditional
mass-to-energy transfer are finite \(\Lzero\) results.  The diagonal
upper bound and support statement are \(\Lone\) physical imports from
TPC-32, used only in its high-\(\beta\) domain
\(C=\lfloor J\rfloor\ll Q\).  Together they convert a vague
``cancellation problem'' into a conditional signed lower-correlation
gate.  The proposed archive and census schema are an \(\Lone\)
interface, not a completed computation.

The missing \(\Ltwo\) theorem is still substantial: one must prove a
growing-scale lower bound for the actual raw mass, the actual
post-bin mass, or a positive family of off-diagonal equal-determinant
pairings.  General results on multiplicative functions, including
short-interval and logarithmically averaged theorems
\citep{MatomakiRadziwill2016,Tao2016}, do not automatically apply to
the restricted high-row geometry and its literal weights.

\subsection{Fixed-shift and endpoint discipline}

All statements are made at one fixed \(h_0\ne0\).  No averaging over
shifts, determinant frequencies, row slopes, or masks may replace the
physical coefficient.  The full route also has a strict endpoint
budget: every accumulated fixed-power loss must be
\[
 \boxed{\text{strictly smaller than }1/400.}
\]
Equality is not reserve and is a stopping point.  This paper neither
identifies \(h_0\) with \(2\) nor asserts any prime-pair consequence.
The determinant-energy interface and the physical endpoint loss are
kept as independent ledgers; an energy exponent is not automatically
added to the latter without a proved crosswalk.

\subsection{Organization}

\Cref{sec:native-packet} fixes the literal objects.
\Cref{sec:phase-envelope} proves the sharp fiber theorem.
\Cref{sec:loss-ledger} transfers raw and fiber losses to energy.
\Cref{sec:correlation-decomposition} isolates the conditional
positive-coherence gate.  \Cref{sec:opened-arithmetic} opens the
M\"obius variables and marks the Chowla boundary.
\Cref{sec:pairing-classification,sec:census-protocol} classify and
specify the proposed census schema.
\Cref{sec:decision-rules,sec:claim-boundary}
give success, kill, and claim rules.
