\section{The raw--fiber--energy loss ledger}
\label{sec:loss-ledger}

We now translate the two survival stages into the determinant-energy
exponent needed by the fixed-shift route.  The notation
\(X^{-\lambda+o(1)}\) records a fixed loss exponent \(\lambda\);
all soft factors are taken only after the fixed margins have been
chosen.

\begin{definition}[Two losses]
\label{def:two-losses}
A \emph{raw nondegeneracy certificate} of loss \(\lambda_R\ge0\) is
\begin{equation}
 R\ge X^{-\lambda_R+o(1)}N_0.
\label{eq:raw-certificate}
\end{equation}
A \emph{fiber-survival certificate} of loss
\(\lambda_{\rm fib}\ge0\) is
\begin{equation}
 M\ge X^{-\lambda_{\rm fib}+o(1)}R.
\label{eq:fiber-certificate}
\end{equation}
The second certificate may come either from the sharp magnitude
envelope
\[
 M_{\min}^{\rm mag}
 \ge X^{-\lambda_{\rm fib}+o(1)}R
\]
or from a stronger theorem using the actual signed arithmetic.
\end{definition}

\begin{theorem}[Certified energy loss]
\label{thm:certified-energy-loss}
Assume \eqref{eq:raw-certificate} and
\eqref{eq:fiber-certificate}.  If the actual postaggregation support
satisfies
\begin{equation}
 S\le X^{\lambda_S+o(1)}Q,
\label{eq:support-loss}
\end{equation}
then
\begin{equation}
 D\ge
 X^{-\lambda_D^{\rm cert}+o(1)}Q^3J^2,
\qquad
 \lambda_D^{\rm cert}
 =2\lambda_R+2\lambda_{\rm fib}+\lambda_S.
\label{eq:general-energy-ledger}
\end{equation}
For the verified TPC-32 support bound \(S\ll Q\), this specializes to
\begin{equation}
 \boxed{
 \lambda_D^{\rm cert}=2(\lambda_R+\lambda_{\rm fib}).}
\label{eq:special-energy-ledger}
\end{equation}
\end{theorem}

\begin{proof}
Cauchy--Schwarz on the actual nonzero determinant bins gives
\[
 M^2
 =\left(\sum_{A(n)\ne0}|A(n)|\right)^2
 \le S\sum_n|A(n)|^2
 =SD.
\]
The two survival hypotheses imply
\[
 M\ge
 X^{-(\lambda_R+\lambda_{\rm fib})+o(1)}N_0.
\]
Together with \eqref{eq:support-loss},
\[
 D\ge\frac{M^2}{S}
 \ge
 X^{-2\lambda_R-2\lambda_{\rm fib}-\lambda_S+o(1)}
 \frac{N_0^2}{Q}.
\]
Since \(N_0=JQ^2\),
\[
 \frac{N_0^2}{Q}=Q^3J^2,
\]
which proves the theorem.
\end{proof}

\begin{remark}[Why the fiber loss is doubled]
The exponent \(2\lambda_{\rm fib}\) is not an artifact of an
estimate: energy is quadratic in the surviving post-bin mass.  The
equal-amplitude construction in TPC-83 makes the
\(M^2/S\) inequality sharp, so no universal improvement is possible
without using more than mass and support \citep{WangTPC83}.
\end{remark}

\subsection{Compatibility with a zero-mode gain}

Suppose a later transfer theorem supplies a fixed zero-mode gain
\(\eta_Z\) and requires
\begin{equation}
 \lambda_D\le2\eta_Z.
\label{eq:zero-mode-requirement}
\end{equation}
Then the present route is sufficient provided
\begin{equation}
 \lambda_R+\lambda_{\rm fib}
 +\frac{\lambda_S}{2}
 \le\eta_Z.
\label{eq:zero-mode-ledger}
\end{equation}
With the literal \(S\ll Q\) support bound, this becomes
\[
 \lambda_R+\lambda_{\rm fib}\le\eta_Z.
\]
Equality in \eqref{eq:zero-mode-ledger} leaves no reserve for any other
fixed-power loss.  It is therefore an interface equality, not a
successful end-to-end budget.

\subsection{The inherited reverse direction}

The literal post-bin singleton bound at \(C=\lfloor J\rfloor\) gives
\begin{equation}
 L:=\max_n|A(n)|
 \ll X^{o(1)}\frac{N_0}{Q}.
\label{eq:L-upper}
\end{equation}
Because \(D\le LM\), any certificate
\begin{equation}
 D\ge X^{-\lambda_D+o(1)}\frac{N_0^2}{Q}
\label{eq:D-certificate}
\end{equation}
forces
\begin{equation}
 M\ge X^{-\lambda_D+o(1)}N_0.
\label{eq:D-to-M}
\end{equation}
Together with \cref{thm:certified-energy-loss}, this recovers the
sharp TPC-83 interval: a post-bin mass loss \(\lambda_M\) certifies
energy loss \(2\lambda_M\), whereas energy loss \(\lambda_D\) forces
post-bin mass loss no worse than \(\lambda_D\).  Neither direction
provides the missing lower bound by itself.

\subsection{Independent energy and physical endpoint ledgers}

The determinant-energy certificate and the end-to-end physical loss
are separate accounting objects.  The first must meet the transfer
interface
\begin{equation}
 \boxed{\lambda_D^{\rm cert}\le2\eta_Z.}
\label{eq:energy-interface-ledger}
\end{equation}
Let \(\Lambda_{\rm phys}\) denote the sum of fixed-power degradations
that a complete physical transfer theorem proves must be paid, with
no duplicated slack and no absorption into \(o(1)\).  Independently,
the endpoint requires
\begin{equation}
 \boxed{\Lambda_{\rm phys}<\frac1{400}.}
\label{eq:strict-endpoint}
\end{equation}
We do not assert any formula that automatically adds
\(\lambda_D^{\rm cert}\) to previously incurred physical losses.
Such a formula would require a term-by-term crosswalk proving that a
determinant-energy loss survives as a new physical degradation rather
than already being encoded in the zero-mode interface or another
transfer factor.  Without that crosswalk, adding the two ledgers may
double count.

Equality in \eqref{eq:strict-endpoint} is a stop.  Equality in
\eqref{eq:energy-interface-ledger} meets that interface but leaves no
energy reserve and is not by itself end-to-end success.  Averaging
over \(h\), frequencies, or alternative packets does not repair a
failure of either ledger for the literal fixed-\(h_0\) coefficient.
