\section{Literal native packet and determinant fibers}
\label{sec:native-packet}

Fix \(h_0\in\Z\setminus\{0\}\).  We use the one-packet notation of
TPC-32 and suppress \(X\) from symbols when no ambiguity is possible.
The row and orbit scales obey
\begin{equation}
 QJ\asymp_{\mathscr D}X,\qquad
 N_0:=JQ^2,
\label{eq:scales}
\end{equation}
and the content cutoff is \(C=\lfloor J\rfloor\).  We work only in the
inherited high-\(\beta\) regime
\begin{equation}
 J\ll_{\mathscr D}Q,\qquad
 C=\lfloor J\rfloor\ll_{\mathscr D}Q,
\label{eq:high-beta-domain}
\end{equation}
which is the theorem domain required by the TPC-32 estimates imported
below.  No proposition in this paper imports those estimates outside
\eqref{eq:high-beta-domain}.  The symbol \(\mathscr D\) collects fixed
supports, residue conditions, smooth weights, and positive margins.

The symbol \(R\) below denotes raw absolute mass.  When the inherited
divisor coefficient \(b_R\) is used in \cref{sec:opened-arithmetic},
its subscript denotes the typed TPC-32 sieve cutoff
\(R_{\rm cut}\), not the raw mass.  We retain the historical notation
\(b_R\) only to make comparison with TPC-32 immediate.

\subsection{Native triplets}

A native triplet is the physical key
\[
 t=(\alpha,\gamma,j)
\]
after the three shell channels have been recombined pointwise.  Its
archive record also stores content, orientation, and coefficient
provenance, but these metadata do not create additional copies of
\(t\).
Its row targets are
\[
 N_\alpha(j)=m_\alpha j+h_0,\qquad
 N_\gamma(j)=m_\gamma j+h_0.
\]
The normalized determinant label is
\begin{equation}
 \nu(t)=\Delta^\#_{\alpha,\gamma}(j)
 :=\frac{m_\alpha-m_\gamma}
 {(N_\alpha(j),N_\gamma(j))}\in\Z\setminus\{0\}.
\label{eq:determinant-label}
\end{equation}
All channel terms are first recombined into the exact matched shell.
At that level a convenient triplet weight is
\begin{equation}
 u_t=
 \gamma_\alpha^{(1)}\gamma_\gamma^{(2)}
 \mathfrak A_{\alpha,\gamma}(j)
 \cK_{\alpha,\gamma}^{\rm sh}(j)
 \one_{c_t\le C},
\qquad
 c_t=(N_\alpha(j),N_\gamma(j)).
\label{eq:triplet-weight}
\end{equation}
If an implementation opens channel, cutoff, divisor, or provenance
fields further, every expansion record retains its parent-triplet
identifier and literal aggregation multiplier.  Expansion records are
not additional native triplets.  This prevents a formal opening from
silently changing \(E_{\trip}\), multiplicity, or normalization.

\begin{definition}[Fibers and masses]
\label{def:fibers}
Let \(\cT\) be the finite multiset of native keys, retaining distinct
keys even if their displayed numerical fields happen to coincide.
For \(n\in\Z\), put
\begin{equation}
 F_n=\{t\in\cT:\nu(t)=n\},\qquad
 A(n)=\sum_{t\in F_n}u_t .
\label{eq:fiber-coefficient}
\end{equation}
Define
\begin{align}
 R&=\sum_{t\in\cT}|u_t|,
 &M&=\sum_n|A(n)|,\label{eq:raw-post-masses}\\
 D&=\sum_n|A(n)|^2,
 &E_{\trip}&=\sum_{t\in\cT}|u_t|^2.
\label{eq:energies}
\end{align}
The exact active support is
\[
 S=\#\{n:A(n)\ne0\}.
\]
\end{definition}

The distinction between \(R\) and \(M\) is fundamental.  The triangle
inequality gives
\begin{equation}
 0\le M\le R,
\label{eq:M-le-R}
\end{equation}
but gives no reverse inequality.  The global normalizer in
\eqref{eq:scales} is not divided by the number of fibers, channels,
or native records.

\subsection{Inherited upper bounds}

\begin{proposition}[\(\Lone\) imported one-sided information]
\label{prop:available-upper}
For the literal TPC-32 packet in
\eqref{eq:high-beta-domain} at \(C=\lfloor J\rfloor\),
\begin{align}
 R&\ll_{\varepsilon,h_0,\mathscr D}X^\varepsilon N_0,
\label{eq:R-upper}\\
 M&\le R,\label{eq:M-upper}\\
 S&\ll_{\mathscr D}Q,\label{eq:S-upper}\\
 D&\ll_{\varepsilon,h_0,\mathscr D}
 X^\varepsilon Q^3J^2.
\label{eq:D-upper}
\end{align}
None of these statements is a lower bound for \(R\) or \(M\).
\end{proposition}

\begin{proof}
The TPC-32 physical absolute-mass interface bounds the sum of the
absolute values of complete matched summands by
\(X^\varepsilon JQ^2\).  This gives \eqref{eq:R-upper}; then
\eqref{eq:M-upper} is \eqref{eq:M-le-R}.  The determinant labels lie
in an interval of length \(O_{\mathscr D}(Q)\), giving
\eqref{eq:S-upper}.  Finally, the inherited singleton bound and raw
absolute mass yield \eqref{eq:D-upper}; equivalently one may use the
post-bin \(\ell^\infty\)-by-\(\ell^1\) estimate from TPC-32
\citep{WangTPC32,WangTPC83}.
\end{proof}

\begin{remark}[Why the lower bound is absent]
\label{rem:no-lower-from-axioms}
The permitted joint multiplier
\(\mathfrak A_{\alpha,\gamma}(j)\) is only bounded above and may
vanish.  Multiplying every row or mask coefficient by
\(X^{-B}\) preserves all stated upper axioms while making \(R\)
arbitrarily small on the natural scale.  Therefore no uniform lower
bound for \(R\), \(M\), or \(D\) follows from those axioms alone.
\end{remark}
