\section{Opening the arithmetic and locating the correlation boundary}
\label{sec:opened-arithmetic}

The exact matched shell is a difference of two quadratic prefixes.
For \(Y\in\{U_0,T\}\), write
\[
 \epsilon_{U_0}=1,\qquad \epsilon_T=-1,
\]
and recall
\[
 b_R(w)=-\mu(w)w_R(w)
\]
on its squarefree support, with \(w_R(w)>0\).  The native weight may
be opened as
\begin{equation}
\begin{split}
 u_t={}&
 \sum_{Y\in\{U_0,T\}}\epsilon_Y
 \gamma_\alpha^{(1)}\gamma_\gamma^{(2)}
 \mathfrak A_{\alpha,\gamma}(j)\\
 &\quad\times
 \sum_{\substack{u,v\le Y\\
 u\mid N_\alpha(j),\ v\mid N_\gamma(j)}}
 b_R(u)b_R(v)\,
 \one_{c_t\le C}.
\end{split}
\label{eq:fully-opened-atom}
\end{equation}
Every cutoff sign, row orientation, content restriction, and
aggregation multiplier is part of the native reconstruction record,
but its expansion children remain attached to the same parent
triplet.

\subsection{Four M\"obius factors after crossing}

The row provenance contains \(\mu(d_\alpha)\) and
\(\mu(d_\gamma)\).  Target primitivity gives
\((d_\alpha,u)=(d_\gamma,v)=1\) on contributing terms, so on the two
legs
\begin{equation}
 \mu(d_\alpha)b_R(u)
 =-\mu(d_\alpha u)w_R(u),\qquad
 \mu(d_\gamma)b_R(v)
 =-\mu(d_\gamma v)w_R(v).
\label{eq:sign-fusion}
\end{equation}
Squaring \eqref{eq:fully-opened-atom}, or crossing two distinct native
atoms in one determinant fiber, therefore produces structured
correlations containing four M\"obius factors, together with positive
divisor weights and literal smooth, residue, cutoff, and mask
coefficients.  Schematically, one encounters
\begin{equation}
 \mu(d_\alpha u)\mu(d_\gamma v)
 \mu(d_{\alpha'}u')\mu(d_{\gamma'}v')
 \one_{\nu(t)=\nu(t')},
\label{eq:four-mobius-schematic}
\end{equation}
not an unweighted generic four-point correlation.

\begin{remark}[Do not over-fuse]
Any M\"obius factor introduced by exact-content inversion may share a
prime factor with \(u\) or \(v\).  It cannot be fused into
\eqref{eq:sign-fusion} unless the requisite coprimality has been
proved for the literal key.  A future census must store such factors
separately.
\end{remark}

\subsection{The Chowla boundary}

A theorem uniform over a broad affine family must be tested against
its smallest specializations.  For example, if its admissible
parameters include \(a=s=h=1\), so that consecutive unit-scale
targets are allowed, then a specialization can contain
\begin{equation}
 \sum_{t\le x}\mu(t)\mu(t+1),
\label{eq:chowla-specialization}
\end{equation}
the classical unweighted two-point Chowla correlation.  An
unconditional theorem uniform enough to imply cancellation in
\eqref{eq:chowla-specialization} would include a currently unproved
special case.  Logarithmically averaged variants are known
\citep{Tao2016}, but they are not literal substitutes for the
unweighted high-row packet.

This observation is a stress test, not an equivalence theorem.  The
actual family here has large structured rows, fixed support
restrictions, determinant equality, divisor weights, and coupled
targets.  We do \emph{not} prove that its correlation problem is
equivalent to classical Chowla.  A localization, completion, or
pairing mechanism may exploit precisely those restrictions.

\subsection{Why a positive term is plausible but unproved}

Equation \eqref{eq:four-mobius-schematic} shows two competing
features:
\begin{enumerate}[leftmargin=2.1em]
 \item generic off-diagonal terms have genuinely oscillatory
 M\"obius signs;
 \item exact repeated targets, divisors, or native atoms can pair
 those signs and leave positive weights.
\end{enumerate}
Theorem \ref{thm:positive-coherence-necessary} says conditionally
that the second feature would have to dominate at the desired scale.
It does not say which pairings occur or how many survive.  The
proposed schema organizes the arithmetic census gate still missing.

\begin{proposition}[No lower bound from the opened formula alone]
\label{prop:no-lower-opened}
The representation \eqref{eq:fully-opened-atom}, together with the
current boundedness and support axioms, does not imply a positive
fixed-power lower bound for \(R\), \(M\), or \(C_{\eqc}\).
\end{proposition}

\begin{proof}
As in \cref{rem:no-lower-from-axioms}, the allowed literal
multipliers can vanish or be uniformly rescaled.  Moreover,
\eqref{eq:fully-opened-atom} is a signed difference between two cutoff
levels.  An identity and upper envelopes for its summands cannot
exclude cancellation within a native atom, within a determinant
fiber, or across the ordered correlation sum.
\end{proof}
