\section{A literal classification of candidate positive pairings}
\label{sec:pairing-classification}

The identity \(D=E_{\trip}+C_{\eqc}\) makes candidate pairings worth
examining only after determinant equality and literal coefficients
have been checked.  The following hierarchy prevents the same pair
from being counted twice.  It is a classification protocol, not an
asymptotic theorem.

The proposed precedence is explicit: after removing the diagonal,
Class \(1\) (proved exact duplicate) takes priority over Class \(2\)
(a registered determinant-preserving symmetry), which takes priority
over Class \(3\) (a registered shared-target or shared-divisor
relation); every remaining ordered pair is Class \(4\).  A future
executable census must freeze this precedence and the finite lists of
allowed symmetry and shared-relation tests in a versioned registry.
No such machine-readable registry is supplied here, so the class
totals below are proposed \(\Lone\) outputs, not computed results.

\subsection{Class 0: the literal diagonal}

Pairs with \(t=t'\) contribute exactly
\[
 E_{\trip}=\sum_t|u_t|^2.
\]
They are nonnegative, and the imported upper bound places their total
at least one full power below natural determinant energy, up to soft
factors, by \cref{prop:triplet-diagonal-upper}.  Treating an expanded
channel or divisor record as a new triplet would artificially inflate
this class; identity is determined by the parent triplet
\((\alpha,\gamma,j)\), not by a row in a flattened expansion table.

\subsection{Class 1: exact duplicate physical atoms}

Distinct native keys \(t\ne t'\) are \emph{exact duplicates} only if
the archive proves equality of the complete physical atom data:
\begin{equation}
 \nu(t)=\nu(t'),\qquad
 u_t=u_{t'},
\label{eq:duplicate-condition}
\end{equation}
including cutoff sign, row coefficients, mask, orientation, content,
divisor provenance, and aggregation multiplier.  Such an ordered pair
contributes \(|u_t|^2\ge0\), and the contribution is strictly positive
only when \(u_t\ne0\).  A numerical equality after floating-point
rounding is not a proof of \eqref{eq:duplicate-condition}.

If a physical atom occurs with literal multiplicity \(m\), its
within-copy energy is \(m^2|u|^2\): \(m|u|^2\) is diagonal and
\(m(m-1)|u|^2\) is nonnegative off-diagonal coherence.  Conversely,
records created solely by a computational expansion do not acquire
physical multiplicity.

\subsection{Class 2: determinant-preserving symmetries}

A map \(\sigma:t\mapsto\sigma t\) is a candidate symmetry pairing
only after proving
\begin{equation}
 \nu(\sigma t)=\nu(t)
\label{eq:symmetry-det-preserve}
\end{equation}
and tracking the exact coefficient ratio
\[
 u_{\sigma t}/u_t.
\]
Positivity requires the real part of
\(u_t\overline{u_{\sigma t}}\) to have a controlled positive sign
after summation.

The most tempting permutation fails the first test.  Exchanging the
two rows gives
\begin{equation}
 \Delta^\#_{\gamma,\alpha}(j)
 =-\Delta^\#_{\alpha,\gamma}(j).
\label{eq:row-swap-sign}
\end{equation}
Since the off-diagonal mask removes determinant \(0\), plain row
exchange maps \(F_n\) to \(F_{-n}\), not \(F_n\), and contributes
nothing to \(C_{\eqc}\) as defined.  It becomes relevant only if an
additional archived transformation restores the determinant sign and
preserves all other physical orientations.

\subsection{Class 3: shared-target or shared-divisor pairings}

Two distinct keys may satisfy exact relations such as
\begin{equation}
 N_\alpha(j)=N_{\alpha'}(j'),\qquad
 N_\gamma(j)=N_{\gamma'}(j'),
\label{eq:shared-target}
\end{equation}
or may share selected divisor variables after
\eqref{eq:fully-opened-atom} is expanded.  Such equalities can pair
M\"obius factors and leave positive weights.  They are candidates
only if all of the following are verified:
\begin{enumerate}[leftmargin=2.2em]
 \item the exact target or divisor equations;
 \item the determinant identity \(\nu(t)=\nu(t')\);
 \item the literal cutoff signs and orientations;
 \item the true multiplicity after inverse aggregation;
 \item the sign of the complete coefficient product.
\end{enumerate}
Sharing a target residue class, a content value, or a divisor bound is
not the same as sharing the literal target or divisor.

\subsection{Class 4: genuinely unpaired remainder}

After Classes 1--3 are removed in the declared order above, all
remaining ordered pairs form the unpaired remainder.  Its total may
be positive or negative.  Bounding each term absolutely is generally
too expensive; proving uniform cancellation over an enlarged affine
family may cross the Chowla boundary described in
\cref{sec:opened-arithmetic}.  A viable theorem may instead localize
the remainder by content, determinant multiplicity, or a
geometry-specific completion.

\begin{proposition}[What the classification proves]
\label{prop:classification-scope}
For any conjugation-closed priority partition of the ordered
equal-determinant pairs,
\begin{equation}
 C_{\eqc}
 =C_{\rm dup}+C_{\rm sym}+C_{\rm share}+C_{\rm rem}.
\label{eq:Ceq-class-sum}
\end{equation}
The duplicate term is nonnegative when
\eqref{eq:duplicate-condition} is proved.  No sign or asymptotic size
for the other three terms follows from the classification alone.
\end{proposition}

\begin{proof}
The equality is a disjoint partition of the finite ordered sum
\eqref{eq:Ceq-definition}.  Conjugation closure makes every class
sum real.  Exact duplicates have
\(u_t\overline{u_{t'}}=|u_t|^2\).  The remaining assertions require
additional arithmetic information not contained in their labels.
\end{proof}

\begin{remark}[A positive main-term route]
A successful alternative to the mass ledger would identify a
conjugation-closed family \(\cP\) with
\[
 \sum_{(t,t')\in\cP}
 u_t\overline{u_{t'}}
 \ge X^{-\lambda_P+o(1)}Q^3J^2
\]
and prove that the complement is smaller.  This is a positive-pairing
theorem, not an assertion that every off-diagonal pair is positive.
\end{remark}
