\section{Sharp phase envelopes inside determinant fibers}
\label{sec:phase-envelope}

The first question is purely geometric.  How much of a fiber's
absolute mass survives if only its moduli are known?

\begin{theorem}[Complete resultant interval]
\label{thm:resultant-interval}
Let \(m\ge1\), let \(r_1,\ldots,r_m\ge0\), and set
\[
 R_f=\sum_{i=1}^m r_i,\qquad
 r_{\max}=\max_{1\le i\le m}r_i,
\]
and allow arbitrary phases \(\theta_i\in\R\).  Then
\begin{equation}
 \left\{
 \left|\sum_{i=1}^m r_i e^{i\theta_i}\right|:
 \theta_1,\ldots,\theta_m\in\R
 \right\}
 =
 \left[(2r_{\max}-R_f)_+,\,R_f\right].
\label{eq:complete-resultant-interval}
\end{equation}
Both endpoints, and every magnitude between them, are attained.
\end{theorem}

\begin{proof}
We prove by induction that the attainable magnitudes form the stated
closed interval.  The assertion is immediate for \(m=1\).

Suppose the first \(m-1\) lengths have attainable interval
\([L',R']\), where
\[
 R'=\sum_{i<m}r_i,\qquad
 L'=(2r'_{\max}-R')_+.
\]
Write \(r=r_m\).  If a partial resultant has magnitude \(s\), adding
the last vector produces every magnitude in
\([|s-r|,s+r]\), by varying the angle between the two vectors.  As
\(s\) runs continuously through \([L',R']\), these intervals overlap
and their union is an interval.  Its upper endpoint is \(R'+r\), and
its lower endpoint is the distance from \(r\) to \([L',R']\):
\begin{equation}
 \min_{s\in[L',R']}|s-r|
 =\max\{L'-r,\ r-R',\ 0\}.
\label{eq:distance-interval}
\end{equation}
If \(r\ge r'_{\max}\), the right side of
\eqref{eq:distance-interval} equals
\((2r-(R'+r))_+\).  If \(r<r'_{\max}\), then
\(L'-r=(2r'_{\max}-(R'+r))_+\) whenever it is positive, while
\(r-R'\le0\) because \(R'\ge r'_{\max}>r\).  Thus in both cases the
new lower endpoint is
\[
 \bigl(2\max\{r'_{\max},r\}-(R'+r)\bigr)_+.
\]
This is exactly the claimed formula for \(m\) lengths.  The induction
also proves that every intermediate magnitude is attained.
\end{proof}

\begin{remark}[Polygon interpretation]
The lower endpoint is zero precisely when the longest segment is no
longer than the sum of the remaining segments.  This is the polygon
closure condition.  When one segment dominates, placing all other
segments directly opposite it attains the positive defect
\(2r_{\max}-R_f\).  The theorem is the sharp form of the polygon
inequality \citep{HardyLittlewoodPolya1952}.
\end{remark}

For the actual fiber \(F_n\), define
\begin{equation}
 R_n=\sum_{t\in F_n}|u_t|,\qquad
 r_{\max,n}=\max_{t\in F_n}|u_t|,
\qquad
 d_n=(2r_{\max,n}-R_n)_+,
\label{eq:fiber-defect}
\end{equation}
with all three quantities zero for an empty fiber.

\begin{corollary}[Sharp global magnitude certificate]
\label{cor:sharp-global-envelope}
For every choice of phases consistent with the fiber moduli,
\begin{equation}
 \boxed{
 M=\sum_n|A(n)|
 \ge M_{\min}^{\rm mag}:=\sum_n d_n.}
\label{eq:global-mag-lower}
\end{equation}
Moreover,
\begin{equation}
 M_{\min}^{\rm mag}
 \le M\le R=\sum_nR_n,
\label{eq:global-envelope}
\end{equation}
and both global endpoints are attainable by independent choices of
phases within the unrestricted free-phase comparison class.  Hence no
lower bound depending only on the multiset of fiber moduli can improve
\eqref{eq:global-mag-lower}.
\end{corollary}

\begin{proof}
Apply \cref{thm:resultant-interval} separately to every nonempty
fiber.  The determinant fibers are disjoint, so their phases may be
chosen independently in the free-phase comparison class.  Choosing a
minimizing configuration in every fiber attains the sum of lower
endpoints; aligning every fiber attains \(\sum_nR_n=R\).
\end{proof}

\begin{remark}[Free-phase sharpness versus physical realizability]
\label{rem:free-phase-sharpness}
The lower bound \eqref{eq:global-mag-lower} applies to the literal
coefficient because it uses only its actual moduli.  The endpoint
attainability statement is sharper in a different sense: it is
optimal over all complex packets having the same fiber partition and
moduli while allowing the phases to vary independently.  Literal
phases may be coupled through shared rows, masks, smooth factors, or
orientations, so an extremizing free-phase assignment need not be
realizable by the physical packet.  The corollary therefore proves
optimality for modulus-only arguments, not the existence of a
physical cancellation or coherence configuration.
\end{remark}

\begin{definition}[Raw and fiber survival]
\label{def:survival}
When \(R>0\), define the actual fiber-survival ratio and its
phase-blind certificate by
\begin{equation}
 \vartheta_{\rm fib}=\frac{M}{R},\qquad
 \underline\vartheta_{\rm mag}
 =\frac{M_{\min}^{\rm mag}}{R}.
\label{eq:survival-ratios}
\end{equation}
Then \(0\le\underline\vartheta_{\rm mag}
\le\vartheta_{\rm fib}\le1\).
\end{definition}

\begin{remark}[What a zero envelope means]
\label{rem:zero-envelope}
It is possible that \(d_n=0\) in every fiber while \(R\) is arbitrarily
large.  Thus a zero phase-blind certificate kills the
\emph{magnitude-only route}, not the actual signed coefficient.  A
positive arithmetic pairing can still force a large resultant.  The
proposed census schema in \cref{sec:census-protocol} is designed to
distinguish these two outcomes in a future executed audit.
\end{remark}

\begin{example}[Sharpness at both extremes]
If every fiber is a singleton, then \(d_n=R_n\), so \(M=R\)
independently of phase.  If one fiber contains two equal moduli, then
its lower envelope is zero and opposite phases attain complete
cancellation.  No interpolation inequality can distinguish those
cases without the actual fiber multiplicities and moduli.
\end{example}
