\section{Exact certificate and scope ledger}
\label{sec:tpc32-certificate}

The companion script
\begin{center}
\texttt{experiments/tpc32\_certificate.py}
\end{center}
is a standard-library Python regression certificate for the finite algebra
and rational bookkeeping used in this paper.  Run from the paper directory
with Python 3.10 or later:
\begin{verbatim}
python experiments/tpc32_certificate.py
python -O experiments/tpc32_certificate.py
\end{verbatim}
Both modes use exception-based checks rather than \texttt{assert}, perform
exactly
\begin{equation}
 \boxed{488{,}845}
 \label{eq:tpc32-certificate-count}
\end{equation}
recorded checks, and regenerate byte-identical JSON.

The check families are:
\begin{center}
\begin{tabular}{@{}lr@{}}
\toprule
Finite check family & Recorded checks \\
\midrule
Matched shell, rank at most two, and polarization & $4{,}017$ \\
Exact content inversion and the \(\lambda_C\) projector & $410{,}980$ \\
Canonical phase splitting, including \((c,q)>1\) & $22{,}850$ \\
Primitive prime--M\"obius sign fusion & $22{,}254$ \\
Exact Parseval and the flat-signal zero-frequency model & $8{,}490$ \\
\(\ell^2\)-versus-\(\ell^1\ell^\infty\) inequality & $19{,}530$ \\
High-\(\beta\) rational ledger and the \(1/400\) threshold & $20$ \\
Coherent matrices and the primitive finite witness & $566$ \\
\(\lambda'_{12}(1)\) and formal prime-log polynomials & $110$ \\
Scope flags & $28$ \\
\midrule
Total & $488{,}845$ \\
\bottomrule
\end{tabular}
\end{center}

The certificate uses integers and \texttt{fractions.Fraction}.  Finite
character orthogonality is represented in exact cyclotomic coordinates,
not by floating-point roots of unity.  In particular, it checks:
\begin{enumerate}[label=\textup{(\alph*)}]
 \item the scalar and matrix matched-shell identities, symmetric
 polarization, and rank bound;
 \item exact gcd inversion, the cumulative content projector, and
 \(\lambda_C(t)=0\) for \(2\le t\le C\) and
 \(\lambda_C(t)=-1\) for \(C<t\le2C\);
 \item the canonical phase lift to modulus \(cq\) in cases with
 \((c,q)>1\), without introducing an inverse of \(c\bmod q\);
 \item primitive target-divisor coprimality and both prime--M\"obius
 fusion identities;
 \item no-wrap character orthogonality, exact Parseval, and a constant
 signal whose nonzero Fourier coefficients all vanish;
 \item the exact high-\(\beta\) identities
 \[
  1-\frac{267}{400}=\frac{133}{400},\qquad
  3\frac{267}{400}-2=\frac1{400};
 \]
 \item the spectrum and stable rank of \(\mathbf J_M-I_M\), including the
 nine-row primitive realization;
 \item
 \(\lambda'_{12}(1)=113/30\) and the nonzero formal coefficient of
 \(\log p_i\log p_j\) in the three-channel witness.
\end{enumerate}

Reproducibility values are:
\begin{align}
 \text{normalized certificate-script source SHA-256}\qquad
 &\texttt{9ccb7e40d31b4bd23b79df09336fcee6}\notag\\[-0.2em]
 &\texttt{230d95c7a9f1a85da0324fb6eb807d1e},
 \label{eq:tpc32-source-hash}\\
 \text{JSON SHA-256}\qquad
 &\texttt{77ac56e2f4f3543224876e8a0374564}\notag\\[-0.2em]
 &\texttt{c81c1b4a9f17800f18ca5249e12954d36},
 \label{eq:tpc32-json-hash}\\
 \text{certificate digest}\qquad
 &\texttt{a890734f5450cda4a7a400f5e1d63796}\notag\\[-0.2em]
 &\texttt{83eb4b9e53a05c8497f256edfdc82c78}.
 \label{eq:tpc32-certificate-digest}
\end{align}

\subsection{Claim boundary}

The unconditional mathematical statements established in this paper are:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the exact matched cutoff shell, its rank-two divisor tensor, and its
 calibrated drift boundary;
 \item exact canonical-content inversion, determinant-phase splitting, and
 the retained-multiplier bilinear representation;
 \item the prime--M\"obius one-leg fusion and the explicit separation
 boundary for a generic pair mask;
 \item determinant \(\ell^1\), \(\ell^\infty\), and \(\ell^2\) bounds
 inherited from the physical singleton-cell theorem;
 \item no-wrap Parseval, exceptional-frequency compression, and the
 classical Farey large-sieve estimate;
 \item the exact equivalence of the auxiliary zero coefficient and the full
 matched raw shell modulo the previously bounded large-content contribution;
 \item the high-\(\beta\) almost-all-frequency proportion and the two sharp
 finite interface obstructions.
\end{enumerate}
The flatness transfer theorem is a proved implication whose premise
\[
 |\widehat A_{C,q}(0)|^2
 \le X^{\chi+o(1)}\sum_n|A_C(n)|^2
\]
is explicitly additional.  The paper does not prove this premise, does not
show that \(r=0\) is a typical determinant frequency, and does not assert
that the generic pair mask has bounded projective norm.

Neither the certificate nor the analytic theorems prove:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item signed cancellation of the complete M\"obius-tail residual;
 \item an improved level of distribution for primes;
 \item a Hardy--Littlewood prime-pair asymptotic or positivity statement;
 \item the twin-prime conjecture; or
 \item a breach of the sieve parity barrier.
\end{enumerate}
The finite prime-row witness is an exact algebraic regression test only.
The negative JSON scope flags make any future promotion of that witness, or
of the conditional \(1/400\) gate, into an unconditional prime-pair claim
detectable during review.
