\section{Introduction and route ledger}
\label{sec:tpc32-introduction}

The primitive M\"obius-tail programme has reached a sharply localized
analytic question.  The preceding reductions first preserved the four
prime/model channels long enough to recombine their divisor coefficients,
then returned from a selected cutoff to the full physical cutoff, and
finally removed target pairs with large common content
\citep{WangTPC19,WangTPC20,WangTPC25,WangTPC29,WangTPC30}.  TPC-31
introduced the factorization-independent coordinates
\begin{equation}
 N_m(j)=mj+h,
 \qquad
 c=(N_m(j),N_n(j)),
 \qquad
 \Delta^\#=\frac{m-n}{c},
 \label{eq:tpc32-intro-canonical}
\end{equation}
and proved fixed-power estimates for individual translated windows and
residue cells of $\Delta^\#$ \citep{WangTPC31}.  Absolute reassembly of all
cells, however, returns the original shell.  Equivalently, the untwisted
sum is the zero coefficient of an auxiliary finite Fourier transform.

The purpose of this paper is to determine exactly how much of that Fourier
problem follows from the available physical estimates, and exactly what
new input is still missing.  Three features must remain visible at the
same time:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the two mixed cutoff channels and the both-ultra channel have to be
 matched before absolute values are taken;
 \item the outer M\"obius sign on an opened row has to be fused with the
 reflected divisor sign;
 \item the auxiliary determinant phase may be separated row by row, but
 the actual pair mask must remain a joint multiplier unless a controlled
 projective decomposition has been proved.
\end{enumerate}
Keeping these three points produces a rank-two algebraic core and an exact
determinant-frequency representation.  The resulting mean-square theorem
is strong enough on average, and at every frequency outside a power-small
exceptional set.  What remains is a single distinguished coefficient.

\subsection{The unconditional results}

Write
\begin{equation}
 Q=X^{\beta+o(1)},
 \qquad
 J=X^{1-\beta+o(1)},
 \qquad
 QJ\asymp X,
 \qquad
 N_0=JQ^2\asymp XQ.
 \label{eq:tpc32-intro-scales}
\end{equation}
The inherited prefix $\mathsf A_{m,T}$ and ultra increment $C_m$ obey
the exact pointwise recombination
\begin{equation}
 \mathsf A_{m,T}C_n+C_m\mathsf A_{n,T}+C_mC_n
 =\mathsf A_{m,U_0}\mathsf A_{n,U_0}
  -\mathsf A_{m,T}\mathsf A_{n,T}.
 \label{eq:tpc32-intro-shell}
\end{equation}
Thus the divisor-coefficient matrix is the difference of two rank-one
tensors.  This low rank is an exact matching statement, not a cancellation
estimate: a rank-one tensor may carry the entire coherent mass.

There is also an exact arithmetic factorization.  For every $C,q\ge1$ and
$r\pmod q$,
\begin{align}
 &\one_{(N_m,N_n)\le C}
 e_q\!\left(-r\frac{m-n}{(N_m,N_n)}\right)
 \notag\\
 &\qquad=
 \sum_{c\le C}\sum_{k\ge1}\mu(k)
 \one_{ck\mid N_m}\one_{ck\mid N_n}
 e_{cq}\!\left(-r(m-n)\right).
 \label{eq:tpc32-intro-content-factorization}
\end{align}
The sum is finite.  Its phase splits as
$e_{cq}(-rm)e_{cq}(rn)$, with no assumption that $(c,q)=1$.
Together with \eqref{eq:tpc32-intro-shell}, this gives a factorable row
core with the full joint physical multiplier retained.

Let $A_C(n)$ be the signed amplitude of the matched three-channel shell
with canonical content at most $C$ and normalized determinant $n$.  The
TPC-31 singleton-cell estimate and total absolute mass imply, for
$C\le J$ and $C\ll_{\mathscr D}Q$,
\begin{equation}
 \|A_C\|_1\ll X^\eps N_0,
 \qquad
 \|A_C\|_\infty\ll X^\eps Q(C+J),
 \qquad
 \|A_C\|_2^2\ll X^\eps\frac{N_0^2}{Q}.
 \label{eq:tpc32-intro-norms}
\end{equation}
A prime modulus larger than the determinant span eliminates residue
collisions, so Parseval is an identity for the physical determinant
amplitudes, not merely for grouped residue classes.  It follows that
\begin{equation}
 \#\{r\pmod q:|\widehat A_{C,q}(r)|>N_0X^{-\sigma}\}
 \ll X^{2\sigma+\eps}.
 \label{eq:tpc32-intro-exceptional}
\end{equation}
The classical additive large sieve gives the analogous statement over
reduced rational frequencies.  No spectral large sieve or unproved
M\"obius hypothesis enters these conclusions.

\subsection{The distinguished zero-frequency gate}

Define
\begin{equation}
 \lambda_C(t)=\sum_{\substack{c\mid t\\c\le C}}\mu(t/c).
 \label{eq:tpc32-intro-projector}
\end{equation}
Then
\begin{equation}
 \one_{(N_m,N_n)\le C}
 =\sum_{t\mid N_m,\ t\mid N_n}\lambda_C(t),
 \label{eq:tpc32-intro-projector-identity}
\end{equation}
while $\lambda_C(1)=1$ and, for $g=(N_m,N_n)$,
\begin{equation}
 \sum_{\substack{t\mid g\\t>1}}\lambda_C(t)
 =-\one_{g>C}.
 \label{eq:tpc32-intro-projector-reassembly}
\end{equation}
Thus the unit-divisor term is the untwisted full-content shell, and every
nonunit projector term together is exactly minus the large-content
correction already treated in TPC-30.  The cell decomposition does not
center the coefficient needed by the original problem.

To quantify the remaining input, we introduce a zero-frequency flatness
exponent $\chi$ through
\begin{equation}
 |\widehat A_{C,q}(0)|^2
 \le X^{\chi+o(1)}\sum_n|A_C(n)|^2.
 \label{eq:tpc32-intro-flatness}
\end{equation}
This is a hypothesis, not a conclusion of the paper.  If
$C=X^{\kappa+o(1)}\le J$ and $C\ll_{\mathscr D}Q$, the exact transfer theorem
gives every saving exponent strictly below
\begin{equation}
 \min\left\{1-\beta,\ \kappa,\ \frac{\beta-\chi}{2}\right\}.
 \label{eq:tpc32-intro-transfer-margin}
\end{equation}
At
\begin{equation}
 \beta=\frac{267}{400},
 \qquad
 C=\lfloor J\rfloor=X^{133/400+o(1)},
 \label{eq:tpc32-intro-high-beta}
\end{equation}
the precise threshold for recovering every saving below $133/400$ is
\begin{equation}
 \boxed{\chi\le\frac1{400}.}
 \label{eq:tpc32-intro-one-over-four-hundred}
\end{equation}
Unconditionally, all but an $X^{-1/400+o(1)}$ proportion of determinant
frequencies already meet the target scale.  The theorem needed by the
remaining hard raw component of the original calibrated residual is the
assertion that the special frequency $r=0$ is not in that exceptional set,
after the inherited large-content and drift terms are separated.

\subsection{Why this is a genuine new gate}

The interface obstruction is sharp.  A constant signal on one complete
residue system has the norm bounds in \eqref{eq:tpc32-intro-norms}, has
zero Fourier transform at every nonzero frequency, and nevertheless has
maximal zero coefficient.  Likewise, the small-content projector on
pairwise coprime targets is the matrix $\mathbf J-I$; it retains the
constant-row direction with eigenvalue of order the number of rows.
Therefore support length, $\ell^1/\ell^\infty/\ell^2$ control, low rank,
and nonzero-frequency cancellation cannot by themselves prove
\eqref{eq:tpc32-intro-one-over-four-hundred}.

Opening one reflected ultra leg exposes the next arithmetic object.  A
divisibility condition parametrizes the row variable by one progression,
and the two M\"obius signs become a correlation of two nonproportional
affine forms.  Classical one-frequency M\"obius estimates do not estimate
that correlation, while known logarithmically averaged two-point results
do not provide the uniform polynomial-scale physical estimate required
here.  This identifies a concrete next problem without asserting that an
existing theorem closes it.

The conclusions of this paper are therefore deliberately asymmetric.  We
prove the matched factorization, the almost-all-frequency theorem, the
exact zero-frequency transfer, and the sharp no-go models.  We do not prove
the flatness hypothesis, a full residual estimate, a Hardy--Littlewood
main term, positivity of a prime-pair count, the twin-prime conjecture, or
a breach of the sieve parity barrier \citep{HeathBrown1982Parity}.

\subsection{Organization}

The inherited packet and exact cutoff shell are recorded in
\cref{sec:tpc32-physical-shell}.  Exact content factorization and the
content projector are developed in \cref{sec:tpc32-canonical-factorization}.
The actual prime--M\"obius sign and the joint-mask boundary are treated in
\cref{sec:tpc32-prime-mobius}.  Determinant dispersion and zero-frequency
transfer occupy
\cref{sec:tpc32-determinant-dispersion,sec:tpc32-zero-frequency-gate},
followed
by the high-$\beta$ ledger.  The two sharp interface models and the
primitive finite witness appear in \cref{sec:tpc32-obstructions}.
We finish with the next affine-M\"obius gate and the exact certificate.
