\section{Sharp interface obstructions and a primitive witness}
\label{sec:tpc32-obstructions}

The preceding mean-square estimate is nearly sufficient numerically, but
it cannot select the coefficient $r=0$.  We give two exact models showing
that this failure is structural at the current interface rather than an
artifact of a loose inequality.

\subsection{A flat determinant signal}

\begin{proposition}[Perfect nonzero-frequency cancellation does not control
zero]
\label{prop:tpc32-flat-signal}
Let $q$ be prime and let $I$ consist of $q$ consecutive integers.  Define
\begin{equation}
 A(n)=\frac{N_0}{q}\one_{n\in I}.
 \label{eq:tpc32-flat-signal}
\end{equation}
Then
\begin{equation}
 \|A\|_1=N_0,
 \qquad
 \|A\|_\infty=\frac{N_0}{q},
 \qquad
 \|A\|_2^2=\frac{N_0^2}{q},
 \label{eq:tpc32-flat-signal-norms}
\end{equation}
but its $q$-point determinant transform satisfies
\begin{equation}
 |\widehat A(0)|=N_0,
 \qquad
 \widehat A(r)=0\quad(1\le r<q).
 \label{eq:tpc32-flat-signal-dft}
\end{equation}
\end{proposition}

\begin{proof}
The norm formulas are immediate.  The consecutive integers in $I$ form a
complete residue system modulo $q$, so
\[
 \widehat A(r)=\frac{N_0}{q}
 e_q(-rn_0)\sum_{a=0}^{q-1}e_q(-ra).
\]
The geometric sum is $q$ for $r=0$ and zero otherwise.
\end{proof}

Taking $q\asymp Q$, \eqref{eq:tpc32-flat-signal-norms} saturates the
$\ell^1$, $\ell^\infty$, and $\ell^2$ scales available for $A_C$.  Thus
those three norms, the support length, and even exact vanishing of every
nonzero Fourier coefficient cannot imply any positive flatness saving at
zero.  This is an abstract interface countermodel; it is not a lower bound
for the physical M\"obius shell.

\subsection{The coherent mode of the content projector}

For positive integers $N_1,\ldots,N_M$, define
\begin{equation}
 P_C(i,j)=\one_{(N_i,N_j)\le C}.
 \label{eq:tpc32-content-matrix}
\end{equation}
The content-projector identity gives the exact signed rank-one expansion
\begin{equation}
 P_C=\sum_{t\ge1}\lambda_C(t)v_tv_t^{\mathsf T},
 \qquad
 v_t(i)=\one_{t\mid N_i}.
 \label{eq:tpc32-content-rank-one-expansion}
\end{equation}
The coefficients are signed, so this is not a positive-semidefinite
decomposition.

\begin{proposition}[A coherent constant-row mode]
\label{prop:tpc32-coherent-content}
If the $N_i$ are pairwise coprime and $N_i>C$ for every $i$, then
\begin{equation}
 P_C=\mathbf J_M-I_M.
 \label{eq:tpc32-J-minus-I}
\end{equation}
Its spectrum is
\begin{equation}
 M-1,\qquad -1\ \text{with multiplicity }M-1,
 \label{eq:tpc32-J-minus-I-spectrum}
\end{equation}
and
\begin{equation}
 \|P_C\|_{2\to2}=M-1,
 \qquad
 \operatorname{srank}(P_C)
 :=\frac{\|P_C\|_{F}^{2}}{\|P_C\|_{2\to2}^{2}}
 =\frac{M}{M-1}.
 \label{eq:tpc32-J-minus-I-stable-rank}
\end{equation}
\end{proposition}

\begin{proof}
For $i\ne j$, pairwise coprimality gives $(N_i,N_j)=1\le C$; on the
diagonal $(N_i,N_i)=N_i>C$.  This proves \eqref{eq:tpc32-J-minus-I}.
The all-ones vector has eigenvalue $M-1$, and its orthogonal complement has
eigenvalue $-1$.  Finally,
$\|P_C\|_F^2=M(M-1)$, giving
\eqref{eq:tpc32-J-minus-I-stable-rank}.
\end{proof}

The stable rank being close to one is not a gain here: it records that one
coherent direction dominates the operator.  In particular, restricting to
small canonical content is not a row-centering operation.

\subsection{A finite primitive realization}

The coherent model occurs inside the actual arithmetic interface.  Take
\begin{equation}
 h=2,
 \quad j=1,
 \quad d=1,
 \quad R=12,
 \quad T=50,
 \quad U_0=200,
 \quad C=30,
 \label{eq:tpc32-witness-parameters}
\end{equation}
and the prime rows
\begin{equation}
 59,71,101,107,137,149,179,191,197.
 \label{eq:tpc32-witness-rows}
\end{equation}
Their targets $m+2$ are respectively
\begin{equation}
 61,73,103,109,139,151,181,193,199,
 \label{eq:tpc32-witness-targets}
\end{equation}
which are distinct primes exceeding $C$.  Hence the $9\times9$ content
matrix is $\mathbf J_9-I_9$, with spectrum $8,-1,\ldots,-1$ and stable
rank $9/8$.

For completeness, the finite Ramanujan-model divisor coefficient is
\begin{equation}
 \lambda'_R(u)
 =u\sum_{b\le R/u}\frac{\mu(ub)\mu(b)}{\varphi(ub)}
 \qquad(u\le R).
 \label{eq:tpc32-lambda-prime}
\end{equation}
At $R=12$,
\begin{equation}
 \lambda'_{12}(1)
 =\sum_{b\le12}\frac{\mu(b)^2}{\varphi(b)}
 =\frac{113}{30}.
 \label{eq:tpc32-lambda-113}
\end{equation}
Since each target in \eqref{eq:tpc32-witness-targets} is prime and lies in
$(T,U_0]$, its prefix and ultra increment are
\begin{equation}
 \mathsf A_{m,50}=-\frac{113}{30},
 \qquad
 C_m=\log(m+2).
 \label{eq:tpc32-witness-prefix-tail}
\end{equation}
For two distinct witness rows with targets $p_i,p_j$, the sum of the three
raw channels is therefore the formal prime-log polynomial
\begin{equation}
 \boxed{
 \log p_i\log p_j
 -\frac{113}{30}(\log p_i+\log p_j).}
 \label{eq:tpc32-witness-polynomial}
\end{equation}
Its coefficient of $\log p_i\log p_j$ is one, so there is no universal
algebraic annihilation among the three channels.

This finite realization certifies the algebraic interface only.  Although
the displayed rows happen to be members of a finite list of prime pairs at
gap two, their presence proves neither a growing lower bound nor any
asymptotic statement about twin primes.  It also does not prove that the
physical shell has a coherent main term; cancellation from the remaining
row coefficients and phases is still possible.

\subsection{The arbitrary-mask obstruction}

Low rank in divisor variables does not survive an uncontrolled conclusion
about the row operator.  Given any finite kernel $K_{\alpha,\gamma}$, an
entrywise bounded mask may be chosen to align its phases, for example
\begin{equation}
 \mathfrak m(\alpha,\gamma)=
 \begin{cases}
  \overline{K_{\alpha,\gamma}}/|K_{\alpha,\gamma}|,
    &\alpha\ne\gamma\text{ and }K_{\alpha,\gamma}\ne0,\\
  0,&\alpha=\gamma\text{ or }K_{\alpha,\gamma}=0.
 \end{cases}
 \label{eq:tpc32-sign-mask}
\end{equation}
Then the masked off-diagonal scalar sum is
$\sum_{\alpha\ne\gamma}|K_{\alpha,\gamma}|$.  Therefore no
theorem uniform over all entrywise bounded pair masks can deduce signed
cancellation from the matched rank-two identity alone.  The actual mask
may have additional structure, but that structure must be stated and
quantified rather than inferred from \eqref{eq:tpc32-mask-bound}.
