\begin{abstract}
The primitive cofactor plane was previously attached to a four-corner
coefficient in the first mixed trace of a fixed-shift normalized
missing-native Gram.  That
representation preserves arithmetic signs but does not control a matrix
entry or operator norm.  We remove this object mismatch.  For two active
rows \(m<n\), every complete common-output key fixes one time \(j\) and two
squarefree targets
\[
 mj+h_0=Q_mS_m,\qquad nj+h_0=Q_nS_n.
\]
Writing
\[
 q=(S_m,S_n),\qquad S_m=qu,\qquad S_n=qv
\]
gives pairwise coprime squarefree coordinates \(q,u,v\),
\(q\mid |h_0(n-m)|\), and an exact affine solution lattice containing
every realized prime key.  Without assuming row--shift coprimality its
spacing is
\[
\operatorname{lcm}\left(\frac{qu}{(m,qu)},\frac{qv}{(n,qv)}\right);
\]
the proved primitive-row property of the inherited physical carrier
reduces it to \(quv\).
After the inherited unitary row gauge, the target sign at every key is
\(\mu(u)\mu(v)\).

Let \(d_m=ga\), \(d_n=gb\), \((a,b)=1\).  We prove that the residual labels
are equal if and only if
\[
 (u,v)=(b,a).
\]
Thus the same-residual part is one distinguished primitive direction for
each row pair, while every other primitive direction is the erasure part.
Defining a literal kernel \(L_{mn,q}(u,v)\) by summing
\(\overline{\beta_{i,m}}\beta_{i,n}/\sqrt{W_mW_n}\) over complete keys with
the indicated coordinates, and aggregating the divisor-many \(q\)-slices,
we obtain the exact formulas
\[
 \widetilde H_{mn}
 =\sum_{(u,v)=1}\mu(u)\mu(v)L_{mn}(u,v),
\]
\[
 \widetilde R_{mn}
 =\mu(a)\mu(b)L_{mn}(b,a),\qquad
 \widetilde E_{mn}
 =\sum_{\substack{(u,v)=1\\(u,v)\ne(b,a)}}
 \mu(u)\mu(v)L_{mn}(u,v).
\]
Hermitian reversal becomes
\(L_{nm,q}(v,u)=\overline{L_{mn,q}(u,v)}\).

The support-faithful entry kernels are primitive-supported, so their
auxiliary diagonal tails vanish and ordinary two-dimensional Abel
summation gives exact location-sensitive entry majorants.  Collecting
these majorants in a symmetric nonnegative matrix \(P\) yields
\(\|H\|\le\rho(P)\), together with weighted Schur and row-star
certificates.  These are genuine operator carriers because they retain
all entries, but no arithmetic estimate showing that \(\rho(P)\) is small
is proved.  Countermodels separate direct entries from mixed traces,
fixed-pair decay from operator control, and general complete-key formulas
from direct-cell compressions.  No fixed-\(2\), parity-breaking, or
prime-pair conclusion is drawn.
\end{abstract}
