\section{Claim ledger and conclusion}
\label{sec:claim-boundary}

\subsection{Exact conclusions}

The paper proves:
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item canonical primitive coordinates for every actual complete
       two-corner key;
 \item the divisor condition \(q\mid|h_0(n-m)|\), the exact linear
       Diophantine identity, and the general least-common-multiple
       solution lattice, with \(quv\) on the inherited physical carrier;
 \item the frozen direct-entry sign \(\mu(u)\mu(v)\);
 \item equivalence between equal residuals and the single direction
       \((u,v)=(b,a)\);
 \item exact literal formulas for every entry of
       \(\widetilde H,\widetilde R,\widetilde E\);
 \item reversed-pair conjugacy and therefore Hermitian compatibility;
 \item tail-free Abel identities for the support-faithful entry kernels;
       and
 \item entrywise, Schur, row-star, weighted Collatz, and Perron operator
       certificates for the complete literal matrix.
\end{enumerate}

\subsection{Statements not proved}

The paper does not prove:
\begin{itemize}
 \item that a physical entry has cancellation relative to its literal
       mass;
 \item that \(\cC_\square(L_{mn}^{0})\) is small uniformly in a growing
       row-pair family;
 \item that \(\rho(P_X^H)\), \(\rho(P_X^E)\), or
       \(\rho(P_X^R)\) has any desired asymptotic saving;
 \item a uniformly controlled low-cost analytic completion;
 \item cancellation in the same-residual sector from target M\"obius
       signs;
 \item closure of terminal activation, represented lower frame,
       missing-mass comparison, nuisance shorting, endpoints, or final
       boundary reconstruction;
 \item the strict \(1/400\) endpoint inequality for one complete physical
       chain;
 \item a statement special to \(h_0=2\); or
 \item a parity-breaking, prime-pair, or twin-prime theorem.
\end{itemize}

\subsection{Audit levels}

\begin{center}
\begin{tabular}{@{}
 >{\raggedright\arraybackslash}p{0.28\textwidth}
 >{\raggedright\arraybackslash}p{0.48\textwidth}
 >{\raggedright\arraybackslash}p{0.13\textwidth}@{}}
\toprule
Result & Scope & Level\\
\midrule
General least-common-multiple ray and matrix comparison &
Finite arithmetic triples and finite matrices & L0\\
Physical \(quv\) ray specialization &
Sufficiently large TPC--61 missing-high carrier & L1\\
Direct-entry primitive representation &
Complete literal fixed-\(h_0\) missing-high carrier & L1\\
Same-residual direction and Hermitian reversal &
Every actual active row pair & L1\\
Mass-normalized entry saving &
Complete growing literal key family & Open L2\\
Perron/row-star saving &
Complete growing active-row matrix & Open L2\\
Physical reassembly &
One common carrier and coefficient scope & Open\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Conclusion}

The primitive cofactor plane is no longer confined to a four-corner mixed
trace.  It represents every literal off-diagonal entry of the normalized
missing-native Gram directly:
\[
 \widetilde H_{mn}
 =
 \sum_{(u,v)=1}\mu(u)\mu(v)L_{mn}(u,v).
\]
For each ordered row pair, the same-residual entry is its unique
pair-dependent direction \((b_{mn},a_{mn})\); the erasure entry is the
remaining primitive plane.  This is a genuine L1 operator-carrier advance
because no entry, complete key, literal coefficient, or raw normalization
is discarded.

The hard question has consequently become sharper, not solved.  One must
control the weighted plaquette or completion cost for all actual row
pairs and then prove that the resulting Perron matrix is small at the
physical scale.  TPC--75 will test that certificate on the literal
carrier.  If it fails by an actual obstruction, the fallback is a signed
moment or hybrid direct/anchor architecture, not a claim that arithmetic
cancellation itself has failed.
