\section{Countermodels and non-substitution laws}
\label{sec:countermodels}

\subsection{A literal orphan erasure edge}

Take the finite fixed-shift interface
\[
 m=2,\qquad n=3,\qquad h_0=1,\qquad d_m=d_n=1,
\]
with one complete common-output key at time \(j=3\).  Its targets are
\[
 2j+1=7=7\cdot1,\qquad
 3j+1=10=5\cdot2.
\]
Thus
\[
 q=1,\qquad (u,v)=(1,2),\qquad (b,a)=(1,1).
\]
The residuals \(1\) and \(2\) are unequal.  Choose one literal coefficient
at each row, both equal to \(1\); then \(W_m=W_n=1\).  With a finite high
threshold below \(5\), the largest-prime labels are literal and all target
and residual M\"obius values are nonzero.  The exact matrices are
\[
 R=0,\qquad
 E=H=
 \begin{pmatrix}
 0&-1\\
 -1&0
 \end{pmatrix}.
\]
Indeed,
\[
 L_{mn,1}(1,2)=1,\qquad
 \mu(1)\mu(2)=-1.
\]

Every four-corner \(ER\) anchor coefficient vanishes because \(R=0\),
whereas the direct erasure entry and its operator norm are nonzero.  This
is a literal finite-interface witness that the anchored primitive plane
cannot substitute for the direct plane.  It does not assert that orphan
edges carry nonnegligible mass in the full asymptotic carrier.

\subsection{A literal same-residual direction}

Take
\[
 m=2,\qquad n=3,\qquad h_0=1,\qquad d_m=2,\qquad d_n=3,
\]
so \(g=1\), \(a=2\), and \(b=3\).  At time \(j=7\),
\[
 2j+1=15=5\cdot3,\qquad
 3j+1=22=11\cdot2.
\]
Thus
\[
 q=1,\qquad (u,v)=(3,2)=(b,a),
\]
and the two residual labels agree:
\[
 d_mS_m=2\cdot3=6=3\cdot2=d_nS_n.
\]
This finite arithmetic key checks the distinguished \(R\)-direction.
Entry into a particular asymptotic physical family still requires all
of that family's literal masks and endpoint conditions.

\subsection{The same-residual point need not cancel}

Let the only nonzero direction for one row pair be
\[
 L_{mn}^{0}=ce_{b,a}.
\]
Then
\[
 \widetilde R_{mn}=\mu(a)\mu(b)c,\qquad
 \widetilde E_{mn}=0.
\]
The full magnitude is \(|c|\).  Primitive support, affine-ray structure,
and the divisor bound on \(q\) do not create M\"obius cancellation inside
the distinguished direction.  Literal phases across keys are a separate
possible mechanism.

\subsection{One common key does not have unit normalized weight}

Let each of two rows carry \(T\) literal unit coefficients, but let only
one complete output key be common to the rows.  Then
\[
 W_m=W_n=T
\]
and the common key contributes
\[
 \frac{\overline{\beta_{i,m}}\beta_{i,n}}{\sqrt{W_mW_n}}
 =\frac1T,
\]
not \(1\).  Neither the singleton property nor equality of the common
key permits replacing the raw row masses by collision degrees.  This
also illustrates why the entry audit
\eqref{eq:atomic-entry-l1-audit} is a normalization bound rather than a
uniform saving.

\subsection{Mixed-trace cancellation does not control an entry}

Consider the abstract Hermitian zero-diagonal matrices
\[
 R=
 \begin{pmatrix}
 0&1\\
 1&0
 \end{pmatrix},
 \qquad
 E=
 \begin{pmatrix}
 0&i\\
 -i&0
 \end{pmatrix}.
\]
Then \(ER\ne0\), but
\[
 \tr(ER)=0,\qquad \|E\|=\|R\|=1.
\]
Thus even cancellation of a nonzero first mixed carrier does not bound
either factor.  The direct-entry theorem is a new object interface, not a
corollary of a scalar trace estimate.

\subsection{Fixed-pair decay does not control the operator}

For \(N\ge2\), let \(A_N\) be the \(N\)-by-\(N\) matrix with zero diagonal
and every off-diagonal entry equal to \(1/(N-1)\).  For each fixed pair,
\[
 (A_N)_{mn}\longrightarrow0,
\]
while
\[
 \|A_N\|=1
\]
because the all-ones vector is an eigenvector.  Hence fixed-pair
little-oh notation for
\(\cC_\square(L_{mn}^{0})\) is insufficient.  A row, weighted Schur, or
Perron estimate over the complete growing pair family is necessary.

\subsection{Pre-aggregation costs can lose literal cancellation}

In the ambient finite-kernel class, two content slices \(F\) and \(-F\)
have
\[
 L_{mn}=F+(-F)=0,
\]
although their separate weighted costs are positive.  Therefore
\[
 \cC_\square\!\left(\sum_qL_{mn,q}\right)
 \le
 \sum_q\cC_\square(L_{mn,q})
\]
is valid but may be strict.  This model does not assert that exact
cancellation occurs in every physical family; it fixes the legal order of
operations.

\subsection{A time-only compression can change the carrier}

Equality of complete native outputs implies equality of time, but the
converse fails.  Two atoms at the same time with different side,
\(\gamma\), block, or remaining output labels do not form a Gram
collision.  Replacing \(\cI_{mn}\) in
\eqref{eq:q-slice-entry-kernel} by a time set may therefore create
spurious two-corner products.  The compressed direct-cell
\(\Gamma_{m,n}(j)\) formula is legal only under its identical-support
hypothesis.

\subsection{Failure of the majorant is not failure of cancellation}

A large value of \(\rho(P^H)\) proves only that the present
absolute-value certificate is inconclusive.  The signed matrix \(H\) may
still be small because of cancellations between plaquettes, row pairs,
contents, sides, or literal phases discarded by \(P^H\).  To close the
Abel--Perron route negatively, one needs an actual-carrier lower
obstruction for every declared admissible completion or for the exact
majorant architecture, at a nonnegligible physical mass scale.
