\section{Introduction}
\label{sec:introduction}

The fixed-shift missing-native Gram has the atomic-normalized form
\[
 G_{\rm nat}=I+H,\qquad H=R+E,
\]
where \(R\) contains same-residual collisions and \(E\) contains
unequal-residual collisions created by erasure
\citep{WangTPC61,WangTPC68}.  The exact source-row gauge of TPC--68 turns
every off-diagonal entry into a signed two-affine sum, while preserving
the spectrum, entry magnitudes, row stars, and collision graph
\citep{WangTPC68}.  Consequently, a direct arithmetic representation of
those gauged entries would be a genuine operator interface.

TPC--70 instead begins with the first mixed trace \(\tr(ER)\).  A
same-residual key and an erasure key form a four-corner rectangle.  The
same-residual key freezes two signs, and the remaining erasure key is
reindexed by primitive cofactor coordinates
\[
 q=(S_m,S_n),\qquad S_m=qu,\qquad S_n=qv
\]
\citep{WangTPC70}.  TPC--71 gives a divisor-lifted Abel certificate for
the resulting plane \citep{WangTPC71}.  TPC--73 then observes that the
support-faithful zero extension is already primitive-supported; its
auxiliary high-diagonal tail is identically zero
\citep{WangTPC73}.

That chain is exact but remains attached to a four-corner scalar.  Even a
perfect estimate for \(\tr(ER)\) does not bound \(E_{mn}\), a row star, or
\(\|H\|\).  The present paper returns to the two-corner formula of
TPC--68 and applies the cofactor coordinates to the actual common-output
key itself.  No same-residual anchor is needed to define the coordinates.
The row divisors still identify one direction:
\[
 d_mS_m=d_nS_n
 \quad\Longleftrightarrow\quad
 (u,v)=(b,a),
\]
where \(d_m=ga\), \(d_n=gb\), and \((a,b)=1\).  The point \((b,a)\)
therefore is not deleted from the full plane.  It is exactly \(R_{mn}\);
the punctured plane is exactly \(E_{mn}\).

\subsection{Main results}

The paper proves the following finite, literal statements.
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item Every actual complete common-output key determines canonical
       squarefree, pairwise coprime coordinates \(q,u,v\), with
       \(q\mid|h_0(n-m)|\).
 \item Fixed \((q,u,v)\) keys lie in an exact affine solution lattice
       with a general least-common-multiple spacing; the proved
       primitive-row property of the inherited physical carrier
       simplifies it to \(quv\).
       Their gauged M\"obius sign is the frozen value
       \(\mu(u)\mu(v)\).
 \item Same residual is equivalent to the unique primitive direction
       \((b,a)\).
 \item The complete gauged matrices \(\widetilde H,\widetilde R,\widetilde
       E\) have exact entry formulas in the literal kernels
       \(L_{mn,q}\), with normalization \(1/\sqrt{W_mW_n}\).
 \item Reversing the row pair swaps \(u,v\) and conjugates the kernel, so
       the representation is manifestly Hermitian.
 \item Primitive support removes the auxiliary diagonal tail from every
       entry kernel.  Weighted plaquette costs give explicit entry
       majorants.
 \item A symmetric nonnegative matrix of these majorants controls the
       operator norm through its Perron radius.  This is an exact carrier
       theorem, not a saving for that radius.
\end{enumerate}

\subsection{Logical level}

The coordinate and matrix identities are L1: they retain the same fixed
\(h_0\), raw masses, complete keys, literal coefficients, actual support,
and unitary gauge as the physical Gram.  The finite-matrix comparison
principles are L0.  Estimating the complete growing majorant matrix is the
new L2 arithmetic gate.  In particular, one fixed pair, one side, a
direct-cell compression, or the first mixed trace cannot be substituted
for that gate.

\subsection{Organization}

\Cref{sec:literal-entry} fixes the complete-key native entry.
\Cref{sec:primitive-coordinates} constructs its primitive coordinates,
and \cref{sec:rays-signs} proves the ray and sign theorems.
\Cref{sec:exact-representation} gives the exact \(R/E/H\) entry formulas
and Hermitian reversal.  \Cref{sec:operator-certificates} builds
entry-to-operator majorants.  Countermodels and non-substitution laws
appear in \cref{sec:countermodels}.  The remaining physical gates and
claim ledger are in \cref{sec:physical-gates,sec:claim-boundary}.
