\section{The complete literal two-corner entry}
\label{sec:literal-entry}

\subsection{Frozen physical carrier}

Fix a finite scale \(X\), one nonzero integer shift \(h_0\), one external
block, one direct side, all source and opposite-row blocks, orbit classes,
masks, profiles, endpoint restrictions, and the very-high cutoff before
any coefficient vector is selected.  The opposite direct side is included
only by the orthogonal direct sum proved in TPC--68.  Let \(\cW_M\) be
the complete set of actual nonzero missing-high atoms in this exact scope,
\(\cM_X\) the declared source-row set, and
\[
 \cI_X=\{i(w):w\in\cW_M\}
\]
the set of actual complete native output keys.  A key \(i(w)\) retains
the side, fixed external block, opposite row, \(\gamma\)-coordinate,
physical time \(j(w)\), and every remaining orthogonal output label.

Every \(w\in\cW_M\) has a canonical source row \(m(w)\), literal
coefficient \(\beta_w\), target, largest prime, cofactor, and residual
label
\begin{equation}
 N_w=m(w)j(w)+h_0=Q_wS_w,
 \qquad
 s(w)=d_{m(w)}S_w.
 \label{eq:key-target-residual}
\end{equation}
Here \(\beta_w\) is the stripped TPC--68 literal coefficient: it retains
all physical shapes, masks, phases, profiles, and terminal weights, but
not a second residual M\"obius sign.  The signed atomic coefficient is
\(c_w=-\mu(s(w))\beta_w\), as recorded below.
The TPC--61 singleton property says that at most one \(w\) occurs at a
fixed pair \((i,m)\).  Hence define
\[
 \beta_{i,m}=
 \begin{cases}
  \beta_w,&i(w)=i,\ m(w)=m,\\
  0,&\text{if that corner is absent},
 \end{cases}
\]
and use \(N_{i,m},Q_{i,m},S_{i,m},s_{i,m}\) for the corresponding
quantities whenever \(\beta_{i,m}\ne0\).
More explicitly, the side decomposition is
\[
 \cW_M=\cW_M^+\sqcup\cW_M^-,
 \qquad
 W_m^\sigma
 =\sum_{\substack{w\in\cW_M^\sigma\\m(w)=m}}|\beta_w|^2,
 \qquad
 W_m=W_m^++W_m^-,
\]
where the union is an orthogonal output union, not a cross-side collision
set.
The raw atomic row mass is
\begin{equation}
 W_m
 =\sum_{\substack{w\in\cW_M\\m(w)=m}}|\beta_w|^2
 =\sum_{i\in\cI_X}|\beta_{i,m}|^2.
 \label{eq:raw-row-mass}
\end{equation}
No output degree or collision multiplicity divides this mass.

Let
\[
 \cM_M=\{m\in\cM_X:W_m>0\}.
\]
Assume \(\cM_M\ne\varnothing\); otherwise the missing-native analysis is
vacuous.
All normalized matrices below act on
\(\ell^2(\cM_M)\).  Every active target and residual label is on the
inherited squarefree carrier:
\begin{equation}
 \mu(N_{i,m}),\ \mu(s_{i,m})\in\{-1,1\}
 \qquad(\beta_{i,m}\ne0).
 \label{eq:squarefree-key-carrier}
\end{equation}
The inherited row divisors satisfy
\begin{equation}
 d_m\mid m.
 \label{eq:row-divisor-condition}
\end{equation}
The direct coordinate and entry theorems below do not need a coprimality
assumption between a source row and \(h_0\).  We therefore prove the
general ray lattice first.  For sufficiently large \(X\), the actual
TPC--61 missing-high carrier additionally satisfies
\begin{equation}
 (m,h_0)=1
 \label{eq:physical-row-primitivity}
\end{equation}
for every realized source row \citep{WangTPC61}; this proved property,
rather than a new hypothesis, simplifies the physical ray spacing.

\subsection{Normalized missing-native Gram and row gauge}

Set
\[
 c_w=-\mu(s(w))\beta_w,\qquad
 (M_X\zeta)_i
 =\sum_{\substack{w\in\cW_M\\i(w)=i}}
 c_w\zeta_{m(w)},
 \qquad
 D_M=\diag(W_m).
\]
On \(S_M=\ell^2(\cM_M)=\Ran D_M\), the atomic-normalized
missing-native incidence is
\[
 F=M_XD_M^{\dagger/2}\big|_{S_M}.
\]
Its normalized missing-native Gram is
\[
 G_{\rm nat}=F^*F=I+H,\qquad H=R+E,
\]
where all three displayed matrices are Hermitian, \(H,R,E\) have zero
diagonal, \(R\) sums common-output pairs with equal residual labels, and
\(E\) sums those with unequal residual labels
\citep{WangTPC68}.

Define the self-adjoint unitary row gauge
\begin{equation}
 U_d=\diag\bigl(\mu(d_m)\bigr)_{m\in\cM_M},
 \qquad
 \widetilde H=U_dHU_d,
 \quad
 \widetilde R=U_dRU_d,
 \quad
 \widetilde E=U_dEU_d.
 \label{eq:row-gauge}
\end{equation}
For \(m\ne n\), put
\[
 \cI_{mn}=\{i\in\cI_X:\beta_{i,m}\beta_{i,n}\ne0\}.
\]
The exact TPC--68 two-affine formula is
\begin{equation}
 \boxed{
 \widetilde H_{mn}
 =
 \frac1{\sqrt{W_mW_n}}
 \sum_{i\in\cI_{mn}}
 \mu(N_{i,m})\mu(N_{i,n})
 \overline{\beta_{i,m}}\beta_{i,n}.}
 \label{eq:literal-gauged-entry}
\end{equation}
Equality of complete keys fixes one common time \(j(i)\).  Thus
\eqref{eq:literal-gauged-entry} is a literal two-corner sum, not a
time-only surrogate and not the four-corner coefficient of
\(\tr(ER)\).

\begin{remark}[Sides and global row mass]
\label{rem:sides-global-mass}
The side is part of the complete output key, so atoms on different sides
never form a Gram pair.  If
\(W_m=W_m^{+}+W_m^{-}\), however, the normalization in
\eqref{eq:literal-gauged-entry} is still the global \(W_m\).  The
diagonal contribution of one side alone is \(W_m^\pm/W_m\), not
automatically \(1\).  Orthogonality across sides therefore does not
license a separate identity-diagonal normalization on each side.
\end{remark}

\subsection{Six-item audit}

Every reindexing below retains:
\begin{enumerate}[label=\textup{(L1.\arabic*)},leftmargin=4em]
 \item the literal coefficients
       \(\overline{\beta_{i,m}}\beta_{i,n}\);
 \item one fixed nonzero shift \(h_0\) in both targets;
 \item the raw normalization \(1/\sqrt{W_mW_n}\);
 \item canonical rows and equality of complete native output keys;
 \item the complete actual squarefree support, including sides, masks,
       endpoints, and absent-corner zeros; and
 \item zero structural exponent loss for the exact identities, with every
       later estimate subject to the strict \(1/400\) endpoint ledger.
\end{enumerate}
