\section{The new physical gate and the adaptive next door}
\label{sec:physical-gates}

Let \(X\to\infty\) through one declared physical family.  All active row
sets, complete keys, kernels, and majorants now depend on \(X\); the index
is suppressed unless needed.  Every asymptotic statement below uses the
same fixed \(h_0\), literal coefficient class, raw atomic normalization,
and actual support.

\subsection{What the exact carrier has closed}

TPC--73 left open whether a primitive plane could be attached to a
two-corner matrix entry.  \Cref{thm:exact-two-corner-planes} answers this
affirmatively:
\[
 \text{every off-diagonal entry}
 \quad\longleftrightarrow\quad
 \text{one literal primitive plane}.
\]
For each ordered row pair, the same-residual entry is its pair-dependent
distinguished direction \((b_{mn},a_{mn})\), and the erasure entry is the
primitive complement.  Consequently, no anchor-observability
hypothesis is needed to see an erasure edge, and orphan edges are included
automatically.

This closes an L1 object mismatch.  It does not close any of the following
L2 estimates.

\subsection{Four remaining operator gates}

\paragraph{Gate A: mass-normalized plaquette or completion control.}
One must estimate the actual kernels
\[
 \cC_\square(L_{mn}^{0})
\]
or the full divisor--variation cost of one declared nonprimitive
completion.  Smooth envelopes, time-only kernels, and support counts do
not replace the literal complex amplitudes.

\paragraph{Gate B: complete pair aggregation.}
The desired conclusion must control the complete matrix, for example
\[
 \rho(P_X^H)\le\eta_X
\]
at the declared physical scale.  Fixed-pair cancellation, density-one
rows, or one side do not imply this estimate.  Weighted Perron vectors are
allowed only when fixed before the later coefficient extremizer.

\paragraph{Gate C: the same-residual sector.}
The full Gram requires \(H=R+E\).  The target M\"obius sign of \(R\) is
frozen.  Any saving there must come from literal phases, sparsity,
geometry, or a separate deterministic mass bound.  An estimate for \(E\)
alone is not an estimate for \(H\).

\paragraph{Gate D: physical reassembly.}
Even a complete operator estimate must be combined with terminal
activation, a represented lower frame, missing-mass comparison, nuisance
shorting, geometric endpoints, and final packet boundaries on the same
carrier and coefficient scope.

\subsection{Exact stop rules}

\begin{enumerate}[label=\textup{(G\arabic*)},leftmargin=3.2em]
 \item If the canonical \(P_X^H\) is too large by a proved lower
       obstruction, only the canonical zero-extension Abel--Perron
       certificate is closed.
 \item To close completion-based entry certificates, the obstruction must
       cover every admissible completion rule or the corresponding
       completion infimum, with Hermitian and uniform-quantifier
       constraints retained.
 \item If orphan edges carry nonnegligible operator mass, that closes an
       anchor-only observability route but not the direct-entry route.
 \item If the same-residual majorant is too large, erasure cancellation
       cannot repair the triangle estimate automatically; one may need a
       signed full-\(H\) moment rather than separate \(R/E\) norms.
 \item If the actual total fixed-power loss reaches \(1/400\), including
       equality, the current endpoint implication is closed.
 \item None of these outcomes is a theorem about the special shift
       \(h_0=2\), the sieve parity barrier, prime pairs, or twin primes.
\end{enumerate}

\subsection{TPC--75 decision}

The direct carrier changes the priority of the next plane paper.  TPC--75
will compare two coefficient-faithful entry certificates:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item the canonical primitive zero extension, whose auxiliary diagonal
       tail is zero; and
 \item a \(q\)-compatible nonprimitive completion that moves common
       coordinate factors into existing literal content slices.
\end{enumerate}
The target is a complete physical census of weighted plaquettes,
large-content mass, row stars, and the resulting Perron matrix.  A positive
result must bound the actual growing matrix.  A negative result must
exhibit a nonnegligible actual-carrier obstruction, not merely a rough
ambient upper bound.  TPC--76 will then quantify what four-corner anchors
observe and isolate the orphan complement, providing a hybrid fallback
rather than replacing the direct representation.
