\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Radial Completion of Factor-Ray Dynamics: A GCD-Mellin Joint Spectrum, Exact Anisotropic Dephasing, and the Fixed-Shift Boundary},
 pdfauthor={Liang Wang},
 pdfsubject={A two-coordinate spectral completion of factor-ray dynamics and its arithmetic boundary},
 pdfkeywords={factor rays, Mellin transform, gcd coordinate, anisotropic dephasing, primes in short intervals, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cH}{\mathcal H}
\newcommand{\cM}{\mathcal M}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\arsinh}{\operatorname{arsinh}}
\newcommand{\rad}{\mathrm{rad}}
\newcommand{\raw}{\mathrm{raw}}

\title{\textbf{Radial Completion of Factor-Ray Dynamics:}\\
\textbf{A GCD--Mellin Joint Spectrum, Exact Anisotropic}\\
\textbf{Dephasing, and the Fixed-Shift Boundary}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Put $u(n)=\Lambda(n)-1$, let $W\in C_c^1((0,\infty);\R)$ with
$\supp W\subset[\alpha,\beta]\subset(0,\infty)$, and consider
the two-coordinate residual
\[
 \cR^{\rad}_{h,D}(X;t,s)=
 \sum_{\substack{n>D\\m\geq1}}
 u(n)(\Lambda(mn+h)-1)W(mn/X)
 (n/m)^{it}(m,n)^{is}.
\]
Writing $n=ak$, $m=bk$, $(a,b)=1$, turns its joint frequency into
$(\log(a/b),\log k)$.  Unlike the previous ratio-only Mellin signal,
this GCD--Mellin lift separates every factor pair.  We formulate the lift
as a commuting two-parameter unitary action and prove exact coefficient
recovery, a tensor Fej\'er Parseval identity, and a rectangular
Montgomery--Vaughan estimate.
The lift is a ray-adapted coordinate system, not an information-theoretic
enlargement of the full ratio--product two-Mellin continuum used in
TPC-10.

On a sector $R\leq ab<2R$, the two frequency gaps are bounded below by
\[
 \delta_{\rm ray}=2\arsinh(1/(4R)),\qquad
 \delta_{\rm rad}=\log\!\left(1+\sqrt{R/(\beta X)}\right).
\]
Consequently exact tensor-Fej\'er dephasing occurs at the separate scale
parameters
$T_{\rm ray}\asymp R$ and
$T_{\rm rad}\asymp\sqrt{X/R}$.  Both scales are sharp up to constants
along populated interior sector families; their sectorwise invariant is
$T_{\rm ray}T_{\rm rad}^2\asymp X$.  This is not a single global
bandwidth law: the undecomposed signal has the worse simultaneous scales
$X$ and $\sqrt X$.
Hard rectangles are asymptotic only when both side lengths exceed the
corresponding reciprocal gaps by unbounded factors.

The fully dephased energy is exactly
\[
 \cF_{h,D}(X)=
 \sum_{\substack{n>D\\m\geq1}}
 u(n)^2(\Lambda(mn+h)-1)^2|W(mn/X)|^2.
\]
Let $G\in C_c^1((0,\infty))$ be nonnegative and nonzero, and put
$I_0(G)=\int_0^\infty G(v)\,dv$ and
$I_2(W)=\int_0^\infty|W(v)|^2\,dv$.
Using the weighted exceptional-set transfer from TPC-12, for fixed
$0<\eps<13/15$ and $0<\eta<1$, uniformly in
$X^{2/15+\eps}\leq H\leq X$ and $1\leq D\leq X^{1-\eta}$, we prove
\begin{align*}
 \sum_hG(h/H)\cF_{h,D}(X)
 ={}&\frac12HX I_0(G)I_2(W)\log X
 \bigl((\log X)^2-(\log D)^2\bigr)\\
 &+O\bigl(HX(\log X)^2\bigr).
\end{align*}
The same result holds for the raw target.  Radial dephasing removes the
same-ray off-diagonal and hence the $\log\log X$ loss in TPC-12.  The
unnormalized parity-centered sum over even shifts has coefficient $1/4$.

The added coordinate repairs geometric information loss, not the fixed-
shift arithmetic.  We prove that the $m=1$ endpoint of the dephased
energy is, up to $O(X\log X)$, $(\log X)^2$ times the weighted
Hardy--Littlewood prime-pair correlation.  Thus its predicted fixed-even-
shift asymptotic is equivalent to that open correlation; for $h=2$ it
is the weighted Hardy--Littlewood twin-prime asymptotic, which is
strictly stronger than mere infinitude of twin primes.  No fixed-shift prime-pair asymptotic,
twin-prime lower bound, new level of distribution, or breach of sieve
parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} factor-ray dynamics; GCD--Mellin spectrum;
anisotropic dephasing; primes in almost all short intervals; prime-pair
boundary; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N05, 11N35; Secondary
11N32, 42A05.

\input{sections/introduction-scope}
\input{sections/joint-dynamics}
\input{sections/sector-geometry}
\input{sections/two-dimensional-dephasing}
\input{sections/arithmetic-transfer}
\input{sections/short-shift-spectrum}
\input{sections/even-shifts}
\input{sections/fixed-shift-boundary}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
