\section{Exact certificate, scope, and conclusion}
\label{sec:tpc25-certificate-scope}

The analytic input in this paper is symbolic: Chebyshev's upper bound,
the TPC-24 endpoint calibration theorem, and the previously established
nonzero-conductor estimates.  A deterministic finite certificate is
included to audit the exact divisor and row-space identities that are
most vulnerable to normalization, diagonal, or shared-factor errors.

\subsection{Certificate}

The standard-library script
\begin{center}
 \texttt{experiments/tpc25\_certificate.py}
\end{center}
uses \texttt{fractions.Fraction} throughout.  Logarithms are represented
as formal prime variables, so no floating-point comparison enters the
kernel tests.  It verifies:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item the direct physical zero kernel against its exact congruence-
 skeleton expansion on three finite prime-row families, including
 nontrivial fixed target radicals;
 \item the identity
 \(K^0_{2,3}=((\log2-2)\log3)/6\) on every off-diagonal entry of a
 five-row model;
 \item the principal and contrast eigenvector relations for the exact
 rank-one-plus-diagonal matrix;
 \item the rank of each congruence matrix
 \(A_g=(\one_{m\equiv n\pmod g})\), compared with the number of
 occupied residue classes and the upper bound \(\rank A_g\le g\);
 \item a rational finite saturation model for the energy-only
 counterexample; and
 \item the rational crossing sample and all three entries of the
 asymmetric exponent ledger.
\end{enumerate}

Independent ordinary and \texttt{python -O} runs perform the same exact
checks and are required to generate byte-identical JSON.  The archived
JSON records false flags for asymptotic M\"obius evidence, full residual
closure, Hardy--Littlewood, twin primes, and a general parity
breakthrough.  Hashes are recorded in the repository README after the
final source audit.

The certificate does not test Chebyshev's theorem, the classical
zero-free region, or any asymptotic cancellation statement.  Its role
is regression control for finite algebra, not numerical evidence.

\subsection{What is unconditional and what is inherited}

Within one actual opened-\(d\) packet, the following statements are
finite or elementary and unconditional:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the row-provenance factorization and the \(O(Q)\) one-row
 absolute mass;
 \item extraction of physical frequency zero before smooth separation;
 \item the resulting \(O(Q^2)\) zero-frequency pair mass;
 \item the soft-energy countermodel and the finite exact M\"obius
 principal mode; and
 \item the congruence-skeleton and deflated operator identities in the
 stated prime-row model.
\end{enumerate}
The arbitrary-logarithmic pointwise shell bound is imported from
TPC-24; it ultimately uses the classical zero-free region for
\(\zeta(s)\) in a uniform M\"obius calibration
\citep{WangTPC24,IwaniecKowalski2004}.  The nonzero-frequency closure
also imports the TPC-24 no-wrap, polynomial Fourier-tail, and
exact-conductor hypotheses.  The present paper removes only the
independent fixed-projective-mass condition for the actual physical
packet.

The operator obstruction must be read with equal precision.  It proves
that the abstract soft interfaces do not logically imply a row-averaged
saving and that the coherent direction occurs in exact finite M\"obius
algebra.  It does not prove a lower bound for the intended growing
shell, and therefore it does not show that a deeper arithmetic row-
average theorem is false.

\subsection{Conclusion and next gate}

TPC-24 left the physical zero mode at a clean but mass-sensitive
boundary.  Returning to the pre-separated packet resolves that boundary
for the actual one-sided opened-\(d\) correlation.  A direct
provenance proof is obtained in the following order:
\begin{equation}
 \boxed{
 \begin{gathered}
 \text{extract physical zero frequency}
 \ \longrightarrow\ \text{use row provenance}\\
 \longrightarrow\ \text{separate only the nonzero spectrum}
 \end{gathered}}
 \label{eq:tpc25-order-of-operations}
\end{equation}
This yields arbitrary logarithmic saving for a general nonzero-mean
fixed smooth test in the factorable provenance class throughout the
existing positive asymmetric-conductor region,
without assuming a fixed projective norm that was not proved in
TPC-24.

The energy audit also prevents a false shortcut.  Entrywise
arbitrary-logarithmic decay and soft \(L^2\) row energy cannot be fed
into a black-box Hilbert--Schmidt estimate: the shared-factor block
\(g=1\) contains a coherent principal row mode.  In the prime-row
model the remaining small-\(g\) directions are exactly the
residue-class constant spaces.  A future operator approach must
therefore center those projections while keeping the actual generic
Schur mask and the local coprimality multipliers inside the argument.

The next analytic component is the both-new square
\(L_{m;S,T}L_{n;S,T}\).  It lacks the calibrated short prefix whose two
endpoint constants cancel in the one-sided argument.  One possible
route is a row-space projection theorem for its low-\(g\) congruence
skeleton followed by a nonprincipal additive large sieve.  A second is
to exploit a different exact recombination before either divisor leg is
estimated.  Failure of either route would still yield a precise
operator or arithmetic obstruction; success would close only another
residual component.

Even after such a step, the ultra-long complement fibers, global
endpoint reassembly, positivity, and the prime-pair main term remain.
Accordingly this paper makes no Hardy--Littlewood, twin-prime, or
general parity-breaking claim.
