\section{The congruence skeleton and a deflated row estimate}
\label{sec:tpc25-congruence-skeleton}

The principal-mode obstruction identifies what a genuine row-space
argument must remove.  In this section we make that geometry exact in a
prime-row model.  The model is deliberately narrower than the physical
opened-\(d\) packet used in the positive theorem: it has no small row
factor and no additional generic Schur pruning.  Its purpose is to
identify the exceptional row subspaces, not to replace the provenance
argument of \cref{sec:tpc25-zero-first}.

Fix \(H\ge1\), let \(R\le S<T<L/2\), and take a finite set
\begin{equation}
 \cP_L\subset
 \{p\in[L/2,2L]:p\text{ is prime},\ (p,H)=1\}.
 \label{eq:tpc25-prime-row-set}
\end{equation}
In particular every row prime is larger than every divisor variable in
the shell.  For \(1\le g\le S\), define
\begin{align}
 \omega_g
 :={}&\frac1g
 \sum_{\substack{c\le S/g\\(gc,H)=1}}
 \frac{b_R(gc)}c
 \sum_{\substack{S/g<d\le T/g\\(d,gcH)=1}}
 \frac{a(gd)}d,
 \label{eq:tpc25-omega-g}
\end{align}
with the convention that ineffective nonsquarefree terms vanish.  Also
let \(A_g\) be the congruence matrix on \(\ell^2(\cP_L)\),
\begin{equation}
 A_g(m,n)=\one_{m\equiv n\pmod g}.
 \label{eq:tpc25-congruence-matrix}
\end{equation}

\begin{theorem}[Exact prime-row congruence skeleton]
\label{thm:tpc25-exact-congruence-skeleton}
Let \(\mathbf K^0_{S,T}\) be the matrix whose off-diagonal entries are
the physical zero kernel \eqref{eq:tpc25-zero-kernel} and whose diagonal
entries are zero.  Then
\begin{equation}
 \boxed{
 \mathbf K^0_{S,T}
 =\sum_{g\le S}\omega_g(A_g-I).}
 \label{eq:tpc25-kernel-skeleton}
\end{equation}
For
\begin{equation}
 v_{g,r}(m)=\one_{m\equiv r\pmod g},
 \qquad r\bmod g,
 \label{eq:tpc25-residue-vector}
\end{equation}
one has
\begin{equation}
 A_g=\sum_{r\bmod g}v_{g,r}v_{g,r}^{*},
 \qquad
 \rank A_g=\#\{m\bmod g:m\in\cP_L\}\le g.
 \label{eq:tpc25-Ag-factorization}
\end{equation}
Moreover,
\begin{equation}
 \|A_g\|_{2\to2}
 =\max_{r\bmod g}\#\{m\in\cP_L:m\equiv r\pmod g\}
 \ll\frac Lg.
 \label{eq:tpc25-Ag-operator}
\end{equation}
Thus the correlated part of every \(g\)-layer lies exactly in the
residue-class constant space modulo \(g\).
\end{theorem}

\begin{proof}
Because every row prime exceeds \(T\), the row coprimality conditions
in \eqref{eq:tpc25-zero-kernel} reduce to coprimality with \(H\).  Put
\(g=(u,v)\), \(u=gc\), and \(v=gd\).  Squarefree support makes
\(g,c,d\) pairwise coprime on every effective term.  The exact gcd
reparametrization becomes, for \(m\ne n\),
\[
 K^0_{S,T}(m,n)
 =\sum_{\substack{g\le S\\g\mid m-n}}\omega_g.
\]
The matrix \(A_g-I\) has precisely the off-diagonal entries
\(\one_{g\mid m-n}\) and zero diagonal, proving
\eqref{eq:tpc25-kernel-skeleton}.

The first identity in \eqref{eq:tpc25-Ag-factorization} follows by
partitioning the rows by their residue class.  After this partition,
\(A_g\) is a direct sum of all-ones blocks, one for each occupied class.
Each nonempty block has rank one and its only nonzero eigenvalue is its
cardinality.  This proves the rank formula and the first equality in
\eqref{eq:tpc25-Ag-operator}.  An interval of length \(O(L)\) contains
\(O(L/g+1)=O(L/g)\) integers in one class because
\(g\le S<L/2\), proving the final estimate.
\end{proof}

The scalar diagonal in \eqref{eq:tpc25-kernel-skeleton} is harmless at
the row-pair scale, but it must not be silently dropped.  Put
\begin{equation}
 \Omega_{S,T}=\sum_{g\le S}\omega_g,
 \qquad
 \cV_G=\operatorname{span}
 \{v_{g,r}:1\le g\le G,\ r\bmod g\}.
 \label{eq:tpc25-deflation-space}
\end{equation}
Then
\[
 \mathbf K^0_{S,T}
 =\sum_{g\le S}\omega_gA_g-\Omega_{S,T}I.
\]

\begin{lemma}[Coefficient mass of one skeleton layer]
\label{lem:tpc25-omega-bound}
Uniformly for \(g\le S\),
\begin{equation}
 |\omega_g|\ll_{C_T,H}\frac{(\log(2X))^6}{g},
 \qquad
 |\Omega_{S,T}|\ll_{C_T,H}(\log(2X))^7,
 \label{eq:tpc25-omega-bound}
\end{equation}
provided \(T\le X^{C_T}\).
\end{lemma}

\begin{proof}
The prefix cofactor estimate of TPC-24 gives
\[
 \sum_{c\le S/g}\frac{|b_R(gc)|}{c}
 \ll(\log(2X))^4,
\]
uniformly in squarefree \(g\).  The corresponding harmonic bound for
the long coefficient is
\[
 \sum_{d\le T/g}\frac{|a(gd)|}{d}
 \ll(\log(2X))^2.
\]
Insert these estimates into \eqref{eq:tpc25-omega-g}.  Summing
\(1/g\) for \(g\le S\) proves the second assertion.
\end{proof}

\begin{theorem}[Deflated operator estimate]
\label{thm:tpc25-deflated-operator}
Let \(1\le G<S\).  If \(x\in\ell^2(\cP_L)\) satisfies
\begin{equation}
 x\perp\cV_G,
 \label{eq:tpc25-exact-row-balance}
\end{equation}
then for every \(y\in\ell^2(\cP_L)\),
\begin{equation}
 \boxed{
 |\langle x,\mathbf K^0_{S,T}y\rangle|
 \ll_{C_T,H}
 \left\{
 \frac{L(\log(2X))^6}{G}
 +(\log(2X))^7
 \right\}\|x\|_2\|y\|_2.}
 \label{eq:tpc25-deflated-operator}
\end{equation}
The same conclusion holds if the balance condition is imposed on
\(y\) instead.
\end{theorem}

\begin{proof}
For \(g\le G\), the range of \(A_g\) is contained in \(\cV_G\), so
\(\langle x,A_gy\rangle=0\).  By
\cref{thm:tpc25-exact-congruence-skeleton,lem:tpc25-omega-bound},
\begin{align*}
 |\langle x,\mathbf K^0_{S,T}y\rangle|
 &\le
 \left(
 \sum_{g>G}|\omega_g|\|A_g\|_{2\to2}
 +|\Omega_{S,T}|
 \right)\|x\|_2\|y\|_2\notag\\
 &\ll
 \left(
 L(\log(2X))^6\sum_{g>G}\frac1{g^2}
 +(\log(2X))^7
 \right)\|x\|_2\|y\|_2,
\end{align*}
which is \eqref{eq:tpc25-deflated-operator}.  Symmetry gives the last
statement.
\end{proof}

For instance, if \(L=X^{\lambda+o(1)}\),
\(G=X^{\gamma+o(1)}\) with \(0<\gamma<\min\{s,\lambda/2\}\), and
\(\|x\|_2\|y\|_2\ll LX^\eps\), then
\eqref{eq:tpc25-deflated-operator} is
\begin{equation}
 \ll L^2X^{-\gamma+\eps+o(1)}
   +LX^{\eps+o(1)},
 \label{eq:tpc25-deflated-power-saving}
\end{equation}
a fixed-power saving from the prime-row pair scale \(L^2\) after
choosing \(\eps\) below the fixed margins.  This is a genuine
row-averaged theorem, but its balance hypothesis is strong and
explicit: since \(v_{1,0}=\mathbf1\), it first removes the principal
row mode, and it then removes every residue-class constant mode up to
\(G\).

The balance space is nonvacuous for the full dyadic prime-row family:
indeed \(\dim\cV_G\le\sum_{g\le G}g\ll G^2\), while the prime number
theorem gives \(\#\cP_L\asymp L/\log L\).  Thus the displayed strict
condition \(2\gamma<\lambda\) leaves a nonzero orthogonal complement
for all sufficiently large \(X\).  For an arbitrary sparse subset
\(\cP_L\), \eqref{eq:tpc25-deflated-operator} remains valid but the
existence of a nonzero balanced vector must be checked separately.

\begin{remark}[Why this is not the physical closure theorem]
\label{rem:tpc25-skeleton-scope}
The actual opened row is \(m=\ell d_0\).  Local coprimality inserts
diagonal row multipliers, and for fixed \(d_0\) the exceptional spaces
become residue-class constant spaces inside each \(d_0\)-block.  A
global mean-zero condition need not center every such block.  Moreover,
the near-determinant and row-gcd conditions form a Schur mask;
entrywise masking does not preserve the exact ranges in
\eqref{eq:tpc25-Ag-factorization}.  One must either enlarge
\(\cV_G\) to include those blockwise multipliers and control the mask
as a sparse operator perturbation, or use the zero-before-separation
absolute-mass route.  The present paper takes the latter route for the
one-sided physical packet.  No deflated estimate for the both-new
physical square is claimed here.
\end{remark}
