\section{The principal row mode and the energy boundary}
\label{sec:tpc25-energy-boundary}

This section records a sharp limitation of the soft row interface.  The
physical zero kernel may be very small at every individual row pair and
still possess a coherent row direction whose singular value is the row
cardinality times the pointwise size.  Consequently, the soft
\(QX^{o(1)}\) row-energy interface, together with the
Hilbert--Schmidt bound obtained only from entrywise control, cannot
replace the absolute row-pair mass.  The obstruction already occurs in the
shared-factor block \(g=1\), where compatibility supplies no oscillation
in the row variables.

\subsection{An abstract soft-energy saturation theorem}

Let \(Q=X^{\beta+o(1)}\) for some fixed \(\beta>0\), and let
\(\mathcal R_X\) be a row set of cardinality
\begin{equation}
 N=N_X=\left\lfloor\frac{Q}{\log(2Q)}\right\rfloor.
 \label{eq:tpc25-row-cardinality}
\end{equation}
Write \(\mathbf 1\) for the constant vector on \(\mathcal R_X\), and
put
\begin{equation}
 \rho_X=\exp\{-\sqrt{\log X}\}.
 \label{eq:tpc25-rho}
\end{equation}
Thus \(\rho_X^{-1}=X^{o(1)}\), while for every fixed \(A>0\),
\begin{equation}
 \rho_X\ll_A(\log X)^{-A}.
 \label{eq:tpc25-rho-log}
\end{equation}

\begin{theorem}[Soft \(\ell^2\) energy does not close a dense zero mode]
\label{thm:tpc25-soft-energy-no-go}
There are a divisor-independent off-diagonal row mask, a real kernel,
and row weights satisfying
\begin{equation}
 \|x\|_\infty+\|y\|_\infty\ll_\epsilon X^\epsilon,
 \qquad
 \|x\|_2^2+\|y\|_2^2\ll_\epsilon QX^\epsilon
 \label{eq:tpc25-soft-row-interface}
\end{equation}
for every fixed \(\epsilon>0\), such that the kernel obeys the
arbitrary-logarithmic pointwise bound
\begin{equation}
 \sup_{m,n\in\mathcal R_X}|K_X(m,n)|
 \ll_A(\log X)^{-A}
 \label{eq:tpc25-pointwise-superlog}
\end{equation}
for every fixed \(A>0\), but
\begin{equation}
 \sum_{m,n\in\mathcal R_X}
 x_my_n\mathfrak m_X(m,n)K_X(m,n)
 =Q^2\{1+o(1)\}.
 \label{eq:tpc25-natural-scale-saturation}
\end{equation}
In particular, the three properties in
\eqref{eq:tpc25-soft-row-interface}--
\eqref{eq:tpc25-pointwise-superlog} do not imply either a fixed-power
saving or an arbitrary-logarithmic saving from the natural row scale
\(Q^2\).
\end{theorem}

\begin{proof}
Take
\begin{equation}
 \mathfrak m_X(m,n)=\mathbf 1_{\{m\ne n\}},
 \qquad
 K_X(m,n)=\rho_X,
 \qquad
 x_m=y_m=\frac{Q}{N\sqrt{\rho_X}}.
 \label{eq:tpc25-saturating-data}
\end{equation}
The mask is bounded, off-diagonal, and independent of every divisor
variable.  Equations \eqref{eq:tpc25-rho} and
\eqref{eq:tpc25-row-cardinality} give
\begin{align}
 \|x\|_\infty=\|y\|_\infty
 &=\frac{Q}{N\sqrt{\rho_X}}=X^{o(1)},
 \label{eq:tpc25-saturating-linfty}\\
 \|x\|_2^2+\|y\|_2^2
 &=\frac{2Q^2}{N\rho_X}=QX^{o(1)}.
 \label{eq:tpc25-saturating-ltwo}
\end{align}
This proves \eqref{eq:tpc25-soft-row-interface}, while
\eqref{eq:tpc25-pointwise-superlog} is
\eqref{eq:tpc25-rho-log}.  Finally,
\[
 \sum_{m,n}x_my_n\mathfrak m_X(m,n)K_X(m,n)
 =\frac{Q^2}{N^2\rho_X}\rho_X N(N-1)
 =Q^2\left(1-\frac1N\right),
\]
which proves \eqref{eq:tpc25-natural-scale-saturation}.
\end{proof}

For any fixed finite divisor set, or in the prime-row regime in which
all rows exceed the divisor horizon, the construction can be placed on
primitive rows coprime to every divisor variable under consideration.
In the \(g=1\) block the
compatibility condition is automatic, so target primitivity merely
deletes inadmissible one-row factors; it does not create cancellation
between different rows.  The theorem is intentionally an interface
countermodel: \(K_X\) is not asserted to be the actual M\"obius shell
kernel.

\subsection{Operator norm, Hilbert--Schmidt norm, and stable rank}

The masked matrix in the preceding proof is
\begin{equation}
 A_X=\rho_X(\mathbf1\mathbf1^{\mathsf T}-I_N).
 \label{eq:tpc25-rank-one-plus-diagonal}
\end{equation}
The constant vector has eigenvalue \(\rho_X(N-1)\), while its
orthogonal complement has eigenvalue \(-\rho_X\).  Hence
\begin{align}
 \|A_X\|_{2\to2}
 &=\rho_X(N-1),
 \label{eq:tpc25-op-norm}\\
 \|A_X\|_{\mathrm{HS}}
 &=\rho_X\sqrt{N(N-1)},
 \label{eq:tpc25-hs-norm}\\
 \operatorname{srank}(A_X)
 :=\frac{\|A_X\|_{\mathrm{HS}}^2}
 {\|A_X\|_{2\to2}^2}
 &=\frac{N}{N-1}\longrightarrow1.
 \label{eq:tpc25-stable-rank}
\end{align}
Thus the Hilbert--Schmidt norm has the same order as the operator norm.
There is no square-root row gain to extract: after diagonal removal the
dangerous matrix is rank one plus a scalar diagonal correction.

More generally, for arbitrary row weights,
\begin{equation}
 x^{\mathsf T}(\mathbf1\mathbf1^{\mathsf T}-I_N)y
 =\left(\sum_mx_m\right)\left(\sum_ny_n\right)
 -\sum_mx_my_m.
 \label{eq:tpc25-principal-row-identity}
\end{equation}
The off-diagonal mask removes only the second, diagonal expression.  It
does not center either row sequence against the constant vector.

\subsection{A finite exact M\"obius certificate}

The coherent geometry above is present in the exact divisor algebra,
not only in the abstract countermodel.  Recall
\begin{equation}
 a(w)=-\mu(w)\log w,
 \qquad
 \lambda'_R(w)
 =w\sum_{b\le R/w}
 \frac{\mu(wb)\mu(b)}{\varphi(wb)},
 \qquad
 b_R(w)=a(w)-\lambda'_R(w).
 \label{eq:tpc25-divisor-coefficients}
\end{equation}

\begin{proposition}[An exact constant zero kernel]
\label{prop:tpc25-finite-constant-kernel}
Take
\begin{equation}
 H=1,\qquad R=S=2,\qquad T=3,
 \label{eq:tpc25-finite-scales}
\end{equation}
and let the two row variables range over any finite set
\(\mathcal R\) of at least two primes greater than \(3\).  Then for
every distinct pair \(m,n\in\mathcal R\), the full physical zero
kernel equals
\begin{equation}
 K^0_{2,3}(m,n)
 =\kappa_0,
 \qquad
 \boxed{\kappa_0=
 \frac{(\log2-2)\log3}{6}\ne0.}
 \label{eq:tpc25-kappa-zero}
\end{equation}
Consequently, after applying
\(\mathfrak m(m,n)=\mathbf 1_{\{m\ne n\}}\), its matrix is exactly
\begin{equation}
 \kappa_0(\mathbf1\mathbf1^{\mathsf T}-I_N).
 \label{eq:tpc25-exact-mobius-matrix}
\end{equation}
Its operator norm, Hilbert--Schmidt norm, and stable rank are obtained
from \eqref{eq:tpc25-op-norm}--\eqref{eq:tpc25-stable-rank} by replacing
\(\rho_X\) with \(|\kappa_0|\).
\end{proposition}

\begin{proof}
Here \(u\in\{1,2\}\) and the long shell contains only \(v=3\).
Thus \((u,v)=1\) for every effective divisor pair.  Since the rows are
primes greater than \(3\), all target-primitivity restrictions are
automatic, and the compatibility indicator is identically one.
Directly from \eqref{eq:tpc25-divisor-coefficients},
\begin{align*}
 \lambda'_2(1)&=2,
 &\lambda'_2(2)&=-2,\\
 b_2(1)&=-2,
 &b_2(2)&=\log2+2,
 &a(3)&=\log3.
\end{align*}
Therefore
\begin{align*}
 K^0_{2,3}(m,n)
 &=\frac{a(3)}3
 \left(b_2(1)+\frac{b_2(2)}2\right)\\
 &=\frac{\log3}{3}
 \left(-2+\frac{\log2+2}{2}\right)
 =\frac{(\log2-2)\log3}{6}.
\end{align*}
The constant is negative, hence nonzero, because \(\log2<2\).  The
matrix assertion follows by deleting its diagonal.
\end{proof}

\begin{remark}[What the finite certificate proves]
\label{rem:tpc25-finite-certificate-scope}
The proposition proves that the principal row direction is compatible
with the genuine M\"obius coefficients, exact target primitivity, and
exact shared-factor compatibility.  It also proves that diagonal
deletion is not row centering.  It does not provide an asymptotic lower
bound for a growing wide shell and therefore is not a counterexample to
an eventual power-saving estimate for the actual TPC shell.
\end{remark}

\subsection{Interface obstruction versus number-theoretic obstruction}

The preceding results have two deliberately different logical levels.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item \Cref{thm:tpc25-soft-energy-no-go} is a black-box
 non-implication theorem.  It proves that soft \(X^{o(1)}\) row energy,
 pointwise arbitrary-logarithmic decay, divisor independence of the
 mask, and target primitivity do not by themselves imply a useful
 bilinear estimate.
 \item \Cref{prop:tpc25-finite-constant-kernel} is exact arithmetic.  It
 proves that the coherent spectral geometry occurs in an actual finite
 M\"obius shell.
 \item Neither result says that the zero kernel in the intended growing
 shell is large.  A genuine asymptotic counterexample would require a
 quantitative lower bound along those growing shells and row weights
 that arise in the original decomposition.  No such lower bound is
 asserted here.
\end{enumerate}

There is a second black-box obstruction if a theorem is stated for
every bounded row-pair mask.  Given any real off-diagonal matrix
\(K(m,n)\), the row-only choice
\(\mathfrak m(m,n)=\operatorname{sgn}K(m,n)\) converts its bilinear sum
with positive constant weights into \(\sum_{m\ne n}|K(m,n)|\).  It is
still independent of the individual divisor variables.  Therefore a
positive row-cancellation theorem must either retain and analyze the
actual generic mask or impose a quantitative structural norm on the
class of masks; the entrywise bound \(|\mathfrak m|\le1\) is not enough.

\subsection{Minimal additional inputs}

The obstruction isolates three viable forms of extra information.

\paragraph{Principal-row balance.}
For the exact model \(\kappa(\mathbf1\mathbf1^{\mathsf T}-I_N)\),
\eqref{eq:tpc25-principal-row-identity} shows that the minimal new datum
is cancellation of at least one row sequence against the constant
vector.  A quantitative form is
\begin{equation}
 \frac{|\langle x,\mathbf1\rangle|}
 {\sqrt N\|x\|_2}
 \frac{|\langle y,\mathbf1\rangle|}
 {\sqrt N\|y\|_2}
 \ll X^{-\sigma}
 \label{eq:tpc25-principal-balance}
\end{equation}
for some fixed \(\sigma>0\); exact mean zero on either side is a
stronger sufficient condition.  The remaining diagonal term is bounded
by \(|\kappa|\|x\|_2\|y\|_2\), with no factor \(N\).

For a shared factor \(g>1\), the analogous coherent subspace is spanned
by the indicators of the admissible residue classes modulo \(g\), with
the local coprimality multipliers included.  Thus a general positive
theorem needs a uniform bound for the projections of the actual row
weights onto these residue-class constant spaces.  Additive large-sieve
energy may then be applied to the complementary, nonprincipal row
frequencies.  It cannot treat \(g=1\), because that block has no
nonprincipal row frequency.

\paragraph{Structured-mask control.}
Principal balance must be preserved after inserting the actual mask.
One sufficient interface is a separated representation
\begin{equation}
 \mathfrak m(m,n)=\sum_\nu\alpha_\nu(m)\beta_\nu(n),
 \qquad
 \sum_\nu\|\alpha_\nu\|_\infty
 \|\beta_\nu\|_\infty\ll(\log X)^C,
 \label{eq:tpc25-mask-projective-control}
\end{equation}
together with \eqref{eq:tpc25-principal-balance} for every twisted pair
\(x\alpha_\nu,y\beta_\nu\).  Alternatively one may work directly with
the specific generic mask and prove that its exceptional part has a
power-saving operator norm.  A generic bounded Schur mask cannot simply
be discarded before taking the nonlinear norm.

\paragraph{Fixed-polylogarithmic row energy.}
There is also a simpler sufficient hypothesis which does not exploit
row cancellation.  If \(\#\mathcal R_X\ll Q\) and
\begin{equation}
 \|x\|_2\|y\|_2\ll Q(\log X)^C,
 \label{eq:tpc25-polylog-ltwo}
\end{equation}
then a pointwise bound
\(\sup|K|\ll_A(\log X)^{-A}\) gives
\[
 |x^{\mathsf T}(\mathfrak m\circ K)y|
 \le \|x\|_2\|y\|_2
 \|\mathfrak m\circ K\|_{2\to2}
 \ll_A Q^2(\log X)^{C-A}.
\]
Choosing \(A\) after the desired logarithmic saving closes the term.
For a projective sum of row packets, the corresponding sum of the
\(\ell^2\)-norm products must satisfy
\eqref{eq:tpc25-polylog-ltwo}.  This route is rigorous but is a
fixed-polylogarithmic mass input in another norm; it is not a consequence
of the soft \(QX^\epsilon\) energy estimate.

Absent a fixed-polylogarithmic mass input, a genuinely
cancellation-based route is therefore not ``apply the entrywise
Hilbert--Schmidt bound once more.''  It must isolate the principal row
projections, prove a balance statement for the actual weights and mask,
and only then use large-sieve energy on the complementary row spectrum.
