\section{Closure of the actual one-sided mixed increment}
\label{sec:tpc25-one-sided-closure}

We now splice the physical zero-frequency estimate into the nonzero
exact-conductor result of TPC-24.  This section introduces no new
conductor estimate.  Its role is to state precisely which former
hypothesis has been discharged and which inherited interfaces remain.

Write
\begin{equation}
 Q=X^{\beta+o(1)},\qquad J=X^{1-\beta+o(1)},
 \qquad S=X^{s+o(1)},\qquad T=X^{t+o(1)},
 \label{eq:tpc25-closure-exponents}
\end{equation}
where \(0<s\le t\), \(QJ\asymp X\), and put
\begin{equation}
 \eta_{\rm asym}(\beta;s,t)
 :=\min\left\{
 1-\frac{3\beta}{2},
 \frac{\beta+1-2s-2t}{2},
 \frac{3-\beta-s-5t}{4}
 \right\}.
 \label{eq:tpc25-eta-asym}
\end{equation}
The three entries are respectively the two-low-conductor, two-high-
conductor, and mixed-conductor faces of the asymmetric rectangle.

Let \(P_{m,W}\) denote the calibrated prefix of TPC-24 and set
\[
 L_{m;S,T}=P_{m,T}-P_{m,S}.
\]
For one actual primitive opened-\(d\) packet, with its original smooth
row--orbit weight retained until after physical frequency zero is
extracted, let \(\Xi_{\alpha,\gamma}(j)\) be its bounded periodic
factor of fixed period \(H_0=|h|\), and write
\begin{equation}
 \cI^{\rm phys}_{S,T}
 =\sum_{\alpha,\gamma}
 \gamma^{(1)}_\alpha\gamma^{(2)}_\gamma
 \mathfrak m(\alpha,\gamma)
 \sum_{\substack{j\in\Z\\(j,H)=1}}
 \Xi_{\alpha,\gamma}(j)\cW_{\alpha,\gamma}(j/J)
 P_{m_\alpha,S}(j)L_{m_\gamma;S,T}(j).
 \label{eq:tpc25-physical-increment}
\end{equation}
Here \(\gamma^{(1)},\gamma^{(2)}\), the rows, the mask, and the
uniformly smooth amplitude are exactly those of the factorable
provenance class in \cref{sec:tpc25-provenance}.  Equivalently, one may
first split the \(O_h(1)\) classes modulo \(H_0\).

\begin{lemma}[Transfer to the separated nonzero interface]
\label{lem:tpc25-interface-transfer}
The continuous Mellin representation
\eqref{eq:tpc25-continuous-projective-representation} transfers
\eqref{eq:tpc25-physical-increment}, restricted to nonzero additive
frequencies, to the separated packet interface of TPC-24.  More
precisely:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item every Mellin component satisfies
 \(\|x\|_\infty+\|y\|_\infty\ll\log(2L)\) and
 \(\|x\|_2^2+\|y\|_2^2\ll Q\log(2L)\);
 \item the actual generic mask is unchanged, remains outside the
 Mellin integral, and is independent of every divisor and conductor
 variable;
 \item every fixed orbit seminorm grows at most polynomially in the
 Mellin variables, and its weighted total variation is finite; and
 \item the TPC-24 discrepancy, principal-mean, and Fourier-tail bounds
 may be integrated componentwise and restored by dominated
 convergence.
\end{enumerate}
The row scales and hence the no-wrap inequalities are unchanged.
\end{lemma}

\begin{proof}
Part (i) is \cref{lem:tpc25-row-energy}; the Mellin row phases have
modulus one.  Part (ii) holds because smooth separation acts only on
the original row--orbit amplitude.  Differentiating the orbit phases
introduces a polynomial in \(\boldsymbol\tau\), so (iii) follows from
the Schwartz moments in
\cref{eq:tpc25-weighted-projective-mass,eq:tpc25-weighted-energy-reassembly}.
The underlying nonzero-frequency packet is linear.  After the triangle
inequality and Tonelli's theorem are applied to the Mellin
representation, the reassembled Fourier tail is bounded by the
integral of the component tail masses.  The same Schwartz moments
dominate that integral and the polynomial constants in the inherited
nonzero packet estimates.  Finite Riemann sums therefore obey those
estimates uniformly, and dominated convergence proves (iv).  Splitting
the fixed \(H_0\)-periodic factor costs only \(O_h(1)\).
\end{proof}

Let \(\mathscr D\) denote the fixed data consisting of \(h,\delta,C_T\),
the positive row, no-wrap, Fourier-tail, and conductor margins, and the
fixed smooth and residue families.

\begin{theorem}[Actual one-sided closure]
\label{thm:tpc25-actual-one-sided-closure}
Assume the primitive row and target-coprimality conditions of TPC-24,
its divisor-independent off-diagonal generic mask, its no-wrap and
polynomial Fourier-tail interfaces, and \(L\ge X^{\lambda_0}\) for a
fixed \(\lambda_0>0\).  Suppose
\begin{equation}
 R\le S<T\le U,\qquad T\le X^{C_T},
 \label{eq:tpc25-shell-range}
\end{equation}
and
\begin{equation}
 \eta_{\rm asym}(\beta;s,t)>0
 \label{eq:tpc25-positive-conductor-margin}
\end{equation}
with a fixed margin.  Then for every fixed \(B>0\),
\begin{equation}
 \boxed{
 \cI^{\rm phys}_{S,T}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}.}
 \label{eq:tpc25-actual-closure}
\end{equation}
The same estimate holds for the transpose packet and for a general
nonzero-mean fixed smooth test within this factorable provenance
class.  No separate fixed-projective-mass hypothesis and no mean-zero
hypothesis on the fixed physical test are required.
\end{theorem}

\begin{proof}
The exact calibrated-prefix identity of TPC-24 writes the product in
\eqref{eq:tpc25-physical-increment} as the joint short--long divisor
lattice minus the explicit row drift.  Treat the joint physical zero
frequency before smooth separation.  The zero-before-separation
theorem in \cref{sec:tpc25-zero-first} bounds it by
\begin{equation}
 XQ\left\{(\log X)^{-A}
       +X^{-s+\kappa+o(1)}\right\}
 \label{eq:tpc25-zero-in-closure}
\end{equation}
for every fixed \(A>0\) and \(0<\kappa<s\).  Fixed bounded-overlap
reassembly costs only \((\log X)^{O(1)}\), so \(A\) may be chosen
after \(B\).  The second term has a fixed power saving.

For nonzero additive frequencies, apply
\cref{lem:tpc25-interface-transfer} and the asymmetric exact-conductor
estimate of TPC-24 \citep{WangTPC24}.  Positivity of
\eqref{eq:tpc25-eta-asym} with fixed margin gives a fixed-power saving
after all dyadic and divisor multiplicities.  The global principal
conductor cell is \(O(Q^2X^\eps)\), hence has a fixed-power saving
relative to \(Q^2J=XQ\) because \(J=X^{1-\beta+o(1)}\) has a fixed
positive exponent in the stated region.  The polynomial Fourier tail
is made smaller than any prescribed fixed power by choosing its
integration-by-parts order after its polynomial mass.

Finally, the calibrated row drift contributes
\(O(JQ^2L^{-1}X^\eps)\).  Choose the auxiliary \(\eps\) smaller than
the fixed \(L\)-margin.  Every term other than
\eqref{eq:tpc25-zero-in-closure} then has a fixed-power saving, and the
calibration exponent in that display supplies the requested arbitrary
logarithmic saving.
\end{proof}

\begin{remark}[What was removed]
\label{rem:tpc25-removed-hypothesis}
TPC-24 proves the same conclusion for an abstract separated packet
under the additional bound
\(\sum_\nu\|x^{(\nu)}\|_1\|y^{(\nu)}\|_1
 \ll Q^2(\log X)^K\).
\Cref{thm:tpc25-actual-one-sided-closure} removes that as an
\emph{independent} hypothesis only for the actual opened-\(d\)
provenance class.  The no-wrap, polynomial Fourier-tail, row geometry,
and positive conductor-margin assumptions have not been removed.
\end{remark}

\subsection{The strict crossing window}

For a genuine crossing of the old Poisson face, impose
\begin{equation}
 s<1-\beta<t.
 \label{eq:tpc25-poisson-crossing}
\end{equation}
The positivity conditions in \eqref{eq:tpc25-eta-asym} give
\begin{equation}
 1-\beta<t<
 \min\left\{
 \frac{\beta+1}{2}-s,
 \frac{3-\beta-s}{5}
 \right\},
 \label{eq:tpc25-general-passage}
\end{equation}
together with \(\beta<2/3\) and \(s<1-\beta\), all with fixed
margins.

At the baseline cutoff
\begin{equation}
 S=R=X^{1/2-\delta+o(1)},\qquad
 T=RX^{\xi+o(1)},
 \label{eq:tpc25-baseline}
\end{equation}
the saving becomes
\begin{equation}
 \eta_{\rm asym}(\beta,\delta,\xi)
 =\min\left\{
 1-\frac{3\beta}{2},
 \frac{\beta+4\delta-1}{2}-\xi,
 \frac{6\delta-\beta-5\xi}{4}
 \right\}.
 \label{eq:tpc25-special-eta}
\end{equation}
The strict passage \(R<J<T\) is certified when
\begin{equation}
 \boxed{
 \frac12+\delta-\beta<\xi<
 \min\left\{
 \frac{\beta+4\delta-1}{2},
 \frac{6\delta-\beta}{5}
 \right\},}
 \label{eq:tpc25-special-window}
\end{equation}
with \(\beta<2/3\) and \(\beta<1/2+\delta\).  For example,
\begin{equation}
 \delta=\frac3{20},\qquad
 \beta=\frac{31}{50},\qquad
 \xi=\frac1{25}
 \label{eq:tpc25-rational-sample}
\end{equation}
gives
\(R=X^{7/20}\), \(J=X^{19/50}\),
\(T=X^{39/100}>J\), and nonzero-conductor saving \(1/50\).
The new content is not a larger exponent window; it is that the
physical packet now satisfies the general-mean conclusion throughout
that window without an unverified projective-mass assumption.
