\section{The actual opened-row provenance}
\label{sec:tpc25-provenance}

The logarithmic zero-mode loss in the abstract separated interface is
not present in the packet from which that interface was obtained.  The
point is elementary but order-sensitive: the original opened row has
an explicit prime--M\"obius weight whose \(\ell^1\)-mass is \(O(Q)\).
We record the provenance before taking any Mellin--Fourier separation.

Fix \(h\in\mathbb Z\setminus\{0\}\), put
\begin{equation}
 H=\rad|h|,\qquad H_0=|h|,
 \label{eq:tpc25-two-fixed-periods}
\end{equation}
and fix one dyadic opened-\(d\) slice.  Here \(H\) controls
primitivity, while the fixed period \(H_0\) retains the full residue
masks inherited from TPC-18.  Put
\begin{equation}
 R=X^{1/2-\delta+o(1)},\qquad V=R^{1/2+o(1)},
 \qquad Q=LD,\qquad J=K/D,\qquad QJ\asymp X,
 \label{eq:tpc25-row-scales}
\end{equation}
and assume
\begin{equation}
 L>\max\{2R,2|h|\}.
 \label{eq:tpc25-large-prime-separation}
\end{equation}
Its rows are
\begin{equation}
 \begin{gathered}
 \alpha=(\ell,d),\qquad
 \ell\in[L/2,2L]\ \text{prime},\qquad m_\alpha=\ell d,\\
 d\in[D,2D]\cap[1,V],\qquad
 d\text{ squarefree},\qquad(d,H)=1.
 \end{gathered}
 \label{eq:tpc25-row-family}
\end{equation}
The size separation makes the integer row \(m_\alpha\) determine its
label uniquely.  A typical one-row coefficient is
\begin{equation}
 \gamma_\alpha
 =\mu(d)(\log\ell)\omega_D(d)\psi_L(\ell/L)\zeta_\alpha,
 \qquad |\zeta_\alpha|\le C,
 \label{eq:tpc25-row-coefficient}
\end{equation}
where \(\omega_D\) and \(\psi_L\) range over fixed bounded smooth
families.  The harmless factor \(\zeta_\alpha\) permits fixed residue
characters and unit-modulus phases.  The two sides of a bilinear packet
may carry different coefficients \(\gamma_\alpha^{(1)}\) and
\(\gamma_\alpha^{(2)}\) of this form.

The orbit amplitude before separation is a product of fixed smooth
factors such as
\begin{equation}
 W(m_\alpha j/X)\,\Psi(dj/K)
 \label{eq:tpc25-one-row-smooth-weight}
\end{equation}
and a mask \(\xi(d,j)\) depending on \((d,j)\bmod H_0\).  After the
quadratic expansion, the generic Schur mask
\(\mathfrak m(\alpha_1,\alpha_2)\) is imposed on the row pair.  We use
only
\begin{equation}
 |\mathfrak m(\alpha_1,\alpha_2)|\le1,
 \qquad
 \mathfrak m(\alpha_1,\alpha_2)=0
 \quad\text{whenever }m_{\alpha_1}=m_{\alpha_2}.
 \label{eq:tpc25-mask-properties}
\end{equation}
In particular, the mask never increases an absolute row-pair mass.

\subsection{Chebyshev row mass}

\begin{lemma}[Actual one-row \(\ell^1\)-mass]
\label{lem:tpc25-row-l1}
For each fixed opened slice and each of the two row factors,
\begin{equation}
 \boxed{\quad
 \sum_{\alpha}|\gamma_\alpha^{(i)}|\ll Q,
 \qquad i=1,2.
 \quad}
 \label{eq:tpc25-row-l1}
\end{equation}
The implied constant depends only on the fixed smooth and residue
families.  No prime number theorem in an arithmetic progression is
used.
\end{lemma}

\begin{proof}
Chebyshev's estimate and boundedness of the source cutoff give
\begin{equation}
 \sum_{\substack{\ell\in[L/2,2L]\\ \ell\ {\rm prime}}}
 (\log\ell)|\psi_L(\ell/L)|\ll L.
 \label{eq:tpc25-Chebyshev}
\end{equation}
Also
\begin{equation}
 \sum_{d\in[D,2D]}|\mu(d)\omega_D(d)|\ll D.
 \label{eq:tpc25-d-mass}
\end{equation}
Multiplication and \(LD=Q\) prove
\eqref{eq:tpc25-row-l1}.  Notice that the factor \(\log\ell\) has
already been summed by \eqref{eq:tpc25-Chebyshev}; replacing it by a
generic \(X^\varepsilon\) bound at this point would lose genuine
information.
\end{proof}

\begin{lemma}[Actual one-row energy]
\label{lem:tpc25-row-energy}
For each row factor in \eqref{eq:tpc25-row-coefficient},
\begin{equation}
 \|\gamma^{(i)}\|_\infty\ll\log(2L),
 \qquad
 \|\gamma^{(i)}\|_2^2\ll Q\log(2L),
 \qquad i=1,2.
 \label{eq:tpc25-row-energy}
\end{equation}
\end{lemma}

\begin{proof}
The first estimate is immediate.  For the second, Chebyshev's estimate
and \((\log\ell)^2\le\log(2L)\log\ell\) give
\[
 \sum_\alpha|\gamma^{(i)}_\alpha|^2
 \ll D\sum_{\substack{\ell\asymp L\\\ell\ {\rm prime}}}
 (\log\ell)^2
 \ll DL\log(2L)=Q\log(2L).
\]
\end{proof}

\begin{corollary}[Actual pair mass]
\label{cor:tpc25-pair-mass}
Uniformly for every bounded row-pair mask,
\begin{equation}
 \sum_{\alpha_1,\alpha_2}
 |\gamma_{\alpha_1}^{(1)}\gamma_{\alpha_2}^{(2)}
   \mathfrak m(\alpha_1,\alpha_2)|
 \ll Q^2.
 \label{eq:tpc25-pair-mass}
\end{equation}
The same conclusion holds after multiplication by any uniformly
bounded scalar depending on the row pair.
\end{corollary}

\begin{proof}
Delete the mask in absolute value and apply
\cref{lem:tpc25-row-l1} to the two factors.
\end{proof}

\subsection{Smooth and finite-residue provenance}

There are two different facts here.  The first, which is all that the
physical zero frequency needs, is that the row-dependent smooth orbit
weight has a uniformly bounded integral.  Indeed, on
\eqref{eq:tpc25-row-scales}--\eqref{eq:tpc25-row-family},
\begin{equation}
 \frac{m_\alpha J}{X}\asymp1,
 \qquad
 \frac{dJ}{K}\asymp1.
 \label{eq:tpc25-scaled-arguments}
\end{equation}
Consequently every product of the factors
\eqref{eq:tpc25-one-row-smooth-weight}, written as a function of
\(t=j/J\), belongs to a fixed bounded subset of
\(C_c^\infty(\mathbb R)\).  In particular, if it is denoted by
\(F_{\alpha_1,\alpha_2}(t)\), then
\begin{equation}
 \sup_{\alpha_1,\alpha_2}
 \left|\widehat F_{\alpha_1,\alpha_2}(0)\right|
 \le
 \sup_{\alpha_1,\alpha_2}\int_{\mathbb R}
 |F_{\alpha_1,\alpha_2}(t)|\,dt
 \ll1.
 \label{eq:tpc25-zero-functional-bound}
\end{equation}

The fixed residue mask introduces no growing complexity.  For example,
Fourier inversion on \((\mathbb Z/H_0\mathbb Z)^2\) writes
\begin{equation}
 \xi(d,j)=
 \sum_{a,b\bmod H_0}\widehat\xi_{H_0}(a,b)e_{H_0}(ad+bj),
 \qquad
 \sum_{a,b\bmod H_0}|\widehat\xi_{H_0}(a,b)|\ll_h1.
 \label{eq:tpc25-finite-residue-separation}
\end{equation}
Equivalently, one may first split the \(O_h(1)\) residue cells.  In
either description, the physical zero coefficient acquires only a
bounded local factor.

For completeness, the usual smooth separation also has no intrinsic
\(X^\varepsilon\) projective loss.  If
\begin{equation}
 \widetilde W(\tau)=
 \int_0^\infty W(z)z^{-i\tau}\frac{dz}{z},
 \label{eq:tpc25-log-Mellin-transform}
\end{equation}
then \(\widetilde W\) is Schwartz and Mellin inversion separates
\(W(mj/X)\) into a row phase and an orbit phase, both of modulus one
on the positive support.  Applying this to the four smooth factors in
a two-row packet gives a continuous projective representation
\[
 \boldsymbol\tau=(t_1,s_1,t_2,s_2),\qquad
 d\nu(\boldsymbol\tau)
 =(2\pi)^{-4}\widetilde W(t_1)\widetilde\Psi(s_1)
   \widetilde W(t_2)\widetilde\Psi(s_2)\,
   d\boldsymbol\tau,
\]
with the evident replacement when the two sides carry different fixed
smooth functions.  The row phases and fixed coefficients are denoted
by \(x_{\boldsymbol\tau},y_{\boldsymbol\tau}\), while all orbit phases
are placed in \(\Phi_{\boldsymbol\tau}\).  Thus
\begin{equation}
 \gamma_{\alpha_1}^{(1)}\gamma_{\alpha_2}^{(2)}
 F_{\alpha_1,\alpha_2}(j/J)
 =\int_{\mathbb R^4}
 x_{\boldsymbol\tau}(\alpha_1)
 y_{\boldsymbol\tau}(\alpha_2)
 \Phi_{\boldsymbol\tau}(j/J)\,
 d\nu(\boldsymbol\tau),
 \label{eq:tpc25-continuous-projective-representation}
\end{equation}
after the fixed row coefficients have been included in \(x\) and
\(y\).  For every fixed integer \(M\ge0\), Schwartz decay and
\cref{lem:tpc25-row-l1} give
\begin{equation}
 \int_{\mathbb R^4}(1+|\boldsymbol\tau|)^M
 \|x_{\boldsymbol\tau}\|_1
 \|y_{\boldsymbol\tau}\|_1\,d|\nu|(\boldsymbol\tau)
 \ll_M Q^2.
 \label{eq:tpc25-weighted-projective-mass}
\end{equation}
The residue expansion \eqref{eq:tpc25-finite-residue-separation}
changes only the implied constant.  Formula
\eqref{eq:tpc25-continuous-projective-representation} may be replaced
by finite Riemann sums and passed to the limit by dominated
convergence.  Thus there is no hidden infinite projective norm.

The same representation supplies the nonzero-frequency norm interface
used later.  Unit-modulus Mellin phases do not change
\eqref{eq:tpc25-row-energy}, and Schwartz decay gives, for every fixed
integer \(M\ge0\),
\begin{equation}
 \int_{\mathbb R^4}(1+|\boldsymbol\tau|)^M
 \|x_{\boldsymbol\tau}\|_2
 \|y_{\boldsymbol\tau}\|_2
 \,d|\nu|(\boldsymbol\tau)
 \ll_M Q\log(2L).
 \label{eq:tpc25-weighted-energy-reassembly}
\end{equation}
Thus a separated estimate whose constant is polynomial in finitely
many orbit seminorms may be integrated term by term.  The fixed
\(H_0\)-residue expansion costs only \(O_h(1)\), and dominated
convergence restores the complete smooth packet.

The frequently used statement that one may truncate Mellin variables
at \(X^\varepsilon\) with power accuracy is a convenient coarse
interface, not a lower bound for the projective mass.  For a requested
logarithmic accuracy one may either keep the absolutely convergent
integral, as above, or truncate at a power of \(\log X\); the omitted
tail is then arbitrarily logarithmically small by
\eqref{eq:tpc25-weighted-projective-mass}.  More importantly, the next
section shows that the physical zero frequency should be taken before
any such separation.
