\section{The physical zero frequency before smooth separation}
\label{sec:tpc25-zero-first}

We now apply the provenance of \cref{sec:tpc25-provenance} to the
one-sided primitive M\"obius shell of TPC-24.  Put
\begin{equation}
 a(v)=-\mu(v)\log v,
 \label{eq:tpc25-a-coefficient}
\end{equation}
and let \(b_R(u)\) be the calibrated prefix coefficient.  For an
off-diagonal row pair \(m_1\ne m_2\), define its physical zero kernel
by
\begin{align}
 K^0_{S,T}(m_1,m_2)
 :={}&
 \sum_{\substack{u\le S,\ S<v\le T\\
                  (u,m_1H)=(v,m_2H)=1}}
 \frac{b_R(u)a(v)}{uv}(u,v)
 \mathbf 1_{(u,v)\mid m_1-m_2}.
 \label{eq:tpc25-zero-kernel}
\end{align}
The pointwise shell theorem of TPC-24 states that, if
\(R\le S<T\le U\), \(S=X^{s+o(1)}\), \(T\le X^{C_T}\), and
\(0<\kappa<s\), then for
every fixed \(A>0\), uniformly over the retained off-diagonal rows,
\begin{equation}
 K^0_{S,T}(m_1,m_2)
 \ll_{A,\kappa,C_T,h}
 (\log X)^{-A}+X^{-s+\kappa+o(1)}.
 \label{eq:tpc25-imported-pointwise-zero}
\end{equation}
Its small-shared-factor term uses cancellation between the two complete
endpoints \(S/(u,v)\) and \(T/(u,v)\); its large-shared-factor term
uses divisibility of the nonzero row determinant.  We do not replace
\eqref{eq:tpc25-imported-pointwise-zero} by a fixed-modulus
calibration assertion.

\subsection{Exact zero coefficient of the actual packet}

Let \(F_{\alpha_1,\alpha_2}\) be the row-dependent smooth orbit
amplitude before Mellin separation, and let
\(\Xi_{\alpha_1,\alpha_2}(j)\) be its bounded real periodic factor of
period \(H_0=|h|\).  Define
\begin{equation}
 \vartheta_{H_0}(\alpha_1,\alpha_2)
 =\frac1{H_0}\sum_{r\bmod H_0}
 \mathbf 1_{(r,H)=1}
 \Xi_{\alpha_1,\alpha_2}(r).
 \label{eq:tpc25-local-zero-factor}
\end{equation}
In the opened TPC-18 square one has, in particular,
\(\Xi_{\alpha_1,\alpha_2}(r)=\xi(d_1,r)\xi(d_2,r)\).
For a Hermitian convention the second factor is conjugated; the
absolute estimate below is unchanged.  A general fixed finite family
is handled cell by cell.  In every case
\begin{equation}
 |\vartheta_{H_0}(\alpha_1,\alpha_2)|\ll_h1.
 \label{eq:tpc25-local-zero-bound}
\end{equation}
Poisson summation on each progression modulo \(H_0[u,v]\) shows that the
physical zero contribution of one opened dyadic packet is exactly
\begin{align}
 \mathcal Z^0_{S,T}
 ={}&J
 \sum_{\alpha_1,\alpha_2}
 \gamma^{(1)}_{\alpha_1}\gamma^{(2)}_{\alpha_2}
 \mathfrak m(\alpha_1,\alpha_2)
 \vartheta_{H_0}(\alpha_1,\alpha_2)
 \widehat F_{\alpha_1,\alpha_2}(0)
 K^0_{S,T}(m_{\alpha_1},m_{\alpha_2}).
 \label{eq:tpc25-actual-zero-packet}
\end{align}
On the primitive row support \((d_i,H)=1\), the pure primitive mask
gives the local factor
\(\varphi(H_0)/H_0=\varphi(H)/H\), recovering the normalization in
TPC-24.  Formula \eqref{eq:tpc25-actual-zero-packet}
is taken before the smooth row--orbit weight is decomposed.  This is
legitimate because evaluation at Fourier frequency zero is the bounded
linear functional \(F\mapsto\widehat F(0)=\int F\).

\begin{theorem}[Zero before separation]
\label{thm:tpc25-zero-before-separation}
Assume \(R\le S<T\le U\), \(T\le X^{C_T}\), the actual opened-row provenance
\eqref{eq:tpc25-row-scales}--\eqref{eq:tpc25-one-row-smooth-weight},
the bounded off-diagonal mask \eqref{eq:tpc25-mask-properties}, and the
pointwise shell estimate \eqref{eq:tpc25-imported-pointwise-zero}.
Then, for every fixed \(A>0\) and \(0<\kappa<s\),
\begin{equation}
 \boxed{
 |\mathcal Z^0_{S,T}|
 \ll_{A,\kappa,C_T,h}
 JQ^2\left\{(\log X)^{-A}
 +X^{-s+\kappa+o(1)}\right\}.}
 \label{eq:tpc25-zero-first-bound}
\end{equation}
Since \(QJ\asymp X\), this is
\begin{equation}
 |\mathcal Z^0_{S,T}|
 \ll XQ\left\{(\log X)^{-A}
 +X^{-s+\kappa+o(1)}\right\}.
 \label{eq:tpc25-zero-first-natural-scale}
\end{equation}
In particular, for every fixed \(B>0\),
\begin{equation}
 \boxed{\mathcal Z^0_{S,T}
 \ll_{B,C_T,h}XQ(\log X)^{-B}.}
 \label{eq:tpc25-zero-first-log-closure}
\end{equation}
No fixed-projective-mass hypothesis is required in addition to the
actual TPC-18 opened-row provenance.
\end{theorem}

\begin{proof}
By \eqref{eq:tpc25-zero-functional-bound} and
\eqref{eq:tpc25-local-zero-bound}, the scalar multiplying
\(\gamma^{(1)}_{\alpha_1}\gamma^{(2)}_{\alpha_2}
\mathfrak m(\alpha_1,\alpha_2)\) in
\eqref{eq:tpc25-actual-zero-packet}, apart from the zero kernel, is
uniformly bounded.  Hence \cref{cor:tpc25-pair-mass} gives
\begin{equation}
 \sum_{\alpha_1,\alpha_2}
 \left|
 \gamma^{(1)}_{\alpha_1}\gamma^{(2)}_{\alpha_2}
 \mathfrak m(\alpha_1,\alpha_2)
 \vartheta_{H_0}(\alpha_1,\alpha_2)
 \widehat F_{\alpha_1,\alpha_2}(0)
 \right|
 \ll_h Q^2.
 \label{eq:tpc25-weighted-zero-mass}
\end{equation}
Insert \eqref{eq:tpc25-imported-pointwise-zero} into
\eqref{eq:tpc25-actual-zero-packet} and use
\eqref{eq:tpc25-weighted-zero-mass}.  This proves
\eqref{eq:tpc25-zero-first-bound};
\eqref{eq:tpc25-zero-first-natural-scale} follows from \(QJ\asymp X\).
For \eqref{eq:tpc25-zero-first-log-closure}, first fix, for example,
\(\kappa=s/2\).  The second term then has a fixed power saving and is
smaller than every prescribed negative power of \(\log X\).  Choose
the calibration exponent \(A\) after \(B\).
\end{proof}

\begin{remark}[Why the order removes the apparent \(X^\varepsilon\)]
\label{rem:tpc25-order-of-zero}
If one first truncates a generic Mellin superposition at
\(X^\varepsilon\), counts all separated terms, and only then takes
absolute values at frequency zero, the coarse bookkeeping can produce
\(Q^2X^\varepsilon\).  Multiplication by an arbitrarily logarithmic
pointwise error does not close that expression.  In
\eqref{eq:tpc25-actual-zero-packet}, by contrast, the zero functional
is applied directly to the uniformly smooth row-dependent amplitude;
then Chebyshev summation gives the exact scale \(Q^2\).  No
cancellation between rows is asserted or needed.
\end{remark}

\subsection{Polylogarithmic reassembly}

The conclusion survives the finite bookkeeping used to return from an
opened slice.  Suppose the original packet is the sum of dyadic,
content, sign, and fixed-residue cells \(\mathfrak b\), with total
complexity \(O((\log X)^{C_{\rm cell}})\).  Let the scale in cell
\(\mathfrak b\) be \((Q_{\mathfrak b},J_{\mathfrak b})\), with
\(Q_{\mathfrak b}J_{\mathfrak b}\asymp X\), and suppose the bounded
partition coefficients have total variation
\(O((\log X)^{C_{\rm cell}})\).  Summing
\eqref{eq:tpc25-zero-first-bound} gives, for every \(B>0\),
\begin{equation}
 \sum_{\mathfrak b}|\mathcal Z^0_{S,T}(\mathfrak b)|
 \ll_B
 (\log X)^{-B}
 \sum_{\mathfrak b}XQ_{\mathfrak b},
 \label{eq:tpc25-polylog-reassembly}
\end{equation}
after choosing the calibration exponent beyond
\(B+C_{\rm cell}\).  Equivalently, comparison with the largest cell
costs only another fixed power of \(\log X\).  Prime-power removal and
the degenerate row channels retain their previously proved fixed-power
margins and are not part of the logarithmic zero-mode ledger.

\subsection{Exact scope}

The theorem concerns the actual opened TPC packet, not every object in
the later abstract interface.  In particular:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item An arbitrary matrix \(z_{\alpha_1,\alpha_2}\) satisfying only
 \(|z_{\alpha_1,\alpha_2}|\ll X^\varepsilon\) need not obey
 \eqref{eq:tpc25-pair-mass}.  The conclusion cannot be transferred to
 such a matrix by deleting its provenance.
 \item An arbitrary uniformly smooth family
 \(F_{\alpha_1,\alpha_2}\) does not by itself force the pair
 coefficient to be a prime--M\"obius rank-one weight.  What is used is
 the combination of the actual row factors
 \eqref{eq:tpc25-row-coefficient}, the bounded zero functional
 \eqref{eq:tpc25-zero-functional-bound}, and \(|\mathfrak m|\le1\).
 \item The argument closes the physical zero frequency.  The nonzero
 conductor cells still use the TPC-24 large-sieve, no-wrap, and Fourier
 tail interfaces.  Their fixed-power margin is compatible with the
 conventional \(X^\varepsilon\) smooth-separation loss.
 \item Nothing here estimates the both-new square, the remaining
 complementary residual legs, or a prime-pair main term.  In
 particular, it is not a Hardy--Littlewood asymptotic, a twin-prime
 lower bound, or a claim to cross the general sieve parity barrier.
\end{enumerate}

Thus the fixed-projective-mass condition in the abstract TPC-24
corollary remains a valid sufficient hypothesis for arbitrary
separated inputs, while \cref{thm:tpc25-zero-before-separation} proves
that it is automatic---and can in fact be bypassed---for the physical
zero mode of the packet that actually arises from the opened-\(d\)
construction.
