\section{Finite certificate and conclusion}
\label{sec:computation}

The accompanying script
\texttt{experiments/tpc18\_certificate.py} performs exact finite checks
of the algebraic layer.  It verifies:

\begin{enumerate}
\item the lcm transform \eqref{eq:lcm-transform}, its M\"obius
inversion, and the $g,a,b$ parameterization;
\item the Gram identity \eqref{eq:Gram-factorization} using rational
arithmetic and the exact finite-box identity
\[
 \sum_{k\le K}\beta_I(k)^2
 =\sum_q\Gamma_I(q)\left\lfloor\frac Kq\right\rfloor;
\]
\item the terminal-octave lower bound and a numerical partial Euler
product for $C_{\mathrm{sf}}$;
\item endpoint collapse for several nonprimitive contents;
\item the three CRT compatibility conditions by exhaustive residue
enumeration;
\item a finite matrix $TT^*$ identity and elementary tuple counts for
the same-source, near-determinant, and large-gcd channels.
\end{enumerate}

The generated JSON file records all parameters and results.  These
checks are deterministic regression tests for exact identities.  They
are not numerical evidence for a prime-pair asymptotic, for
\eqref{eq:DD}, or for the twin-prime conjecture.

\subsection{What moved forward}

TPC-17 ended with a sharp M\"obius tail but no quadratic form adapted
to that coefficient.  The present paper supplies two such forms and
proves that they reveal different, compatible information:
\begin{equation}
 \begin{array}{ccl}
 \text{same-$k$ square}
 &\Longrightarrow& q=[d_1,d_2]\le V^2\le R,
 \quad\text{explicit lcm/CRT cells},\\[0.3em]
 \text{$d$-first square}
 &\Longrightarrow& m_i=\ell_i d_i>R,
 \quad h(m_1-m_2),\ \text{generic determinant channel}.
 \end{array}
 \label{eq:two-quadraticizations-summary}
\end{equation}
The first route also proves a coefficient no-go result: the terminal
octave carries nonvanishing Gram mass.  The second route removes three
large but elementary degeneracies.  The content split then shows that
nonprimitive sectors are not simply smaller copies of the primitive
problem: their interior tail cancels exactly and their target-prime
terms collapse to sparse prime powers.

The remaining primitive large-determinant/low-gcd correlation is a
sharper and more testable gate than the undifferentiated tail.  It is
also honestly hard: a uniform bound at all necessary row exponents,
combined with the preceding papers, reaches the fixed-shift
Hardy--Littlewood asymptotic.  Future progress can therefore proceed in
three falsifiable directions:
\begin{itemize}
\item exploit additional factor shapes inside the generic channel
without claiming coverage of the sharp tail as a whole;
\item transform the variable determinant through dispersion,
reciprocity, Poisson summation, and a Kuznetsov-type spectral step, with
every incomplete-period error retained;
\item first prove an averaged-shift or restricted-determinant theorem,
then state precisely what extra uniformity is missing at fixed $h$.
\end{itemize}

Any one of these may yield a partial positive theorem or a rigorous
no-go result.  What has been gained here is a stable junction at which
such alternatives no longer conceal one another.  No parity barrier has
been broken, but a broad unresolved packet has been reduced to two
explicit and structurally different obstructions.
