\section{Introduction and claim ledger}
\label{sec:introduction}

The parity problem is not merely a shortage of numerical cancellation.
It is a structural failure of ordinary sieve information to distinguish
integers with an odd or even number of prime factors; see Selberg's
classical discussion and modern sieve treatments
\citep{Selberg1952Parity,FI2010}.  The fixed-shift prime-pair problem
therefore provides a useful stress test for any proposed spectral or
dynamical reformulation: an attractive change of variables is valuable
only if every discarded term and every imported distribution theorem
is made explicit.

TPC-15--TPC-17 follow this discipline for the finite Ramanujan model
\citep{WangTPC15,WangTPC16,WangTPC17}
\[
 \Lambda_R(n)=\sum_{q\le R}\frac{\mu(q)}{\varphi(q)}c_q(n),
 \qquad r_R(n)=\Lambda(n)-\Lambda_R(n).
\]
TPC-17 proves cancellation for an assembled initial divisor segment
and leaves, on certain symmetric Heath--Brown blocks, the exact
coefficient
\[
 \beta_I(k)=\sum_{\substack{d\mid k\\d\in I}}\mu(d),
 \qquad I=(D_0,V].
\]
It also proves a $TT^*$ stopping theorem for a different, asymmetric
square-root packet.  The two statements are not interchangeable: the
asymmetric packet has no factor $\beta_I(k)$, while squaring the latter
changes both its row geometry and its coefficient class.  The first
purpose of this paper is to construct the correct quadratic forms
directly from the symmetric tail.

\subsection{What is proved}

There are four unconditional structural statements within the TPC
interface.

\begin{enumerate}[label=\textup{(\roman*)}]
\item The square of the sharp divisor tail has an exact lcm expansion.
Since $V^2\le R$, its new row label lies back inside the finite-model
cutoff.  We call this \emph{lcm cutoff return}.

\item If $D_0<V/2$, the associated divisor Gram form has an explicit
positive lower bound coming from $r\in(V/2,V]$.  When
$K/V^2\to\infty$, as in the two
explicit TPC-17 profiles, this yields natural $k$-space $L^2$ mass.
Thus neither Cauchy--Schwarz nor a claim that the tail coefficient is
$L^2$-small can remove those remaining packets.  The Gram identity and
terminal-octave mechanism are classical;
our contribution is to place them exactly at the TPC-17 stopping gate.

\item A different, $d$-first $TT^*$ expansion produces row moduli
$m=\ell d$ and determinant $h(m_1-m_2)$.  We remove three degenerate
families without any distribution theorem.  A failed slice must
therefore concentrate in the generic channel
\[
 \ell_1\ne\ell_2,\qquad
 |m_1-m_2|>QX^{-\kappa},\qquad
 (d_1,d_2)\le X^\kappa.
\]

\item Splitting by $(k,h)$ reveals an exact asymmetry.  In the primitive
sector the two target values have gcd dividing $\ell_1-\ell_2$.  In
every nonprimitive sector the interior M\"obius interval cancels
pointwise and only fixed-ratio endpoint bands remain.  Terms containing
a target von Mangoldt factor reduce to prime powers, so the surviving
correlation is, up to a power-saving error at the relevant scale, a
finite-model correlation with an exact CRT kernel.
\end{enumerate}

The individual lcm, Gram, and inclusion--exclusion identities are
classical or elementary.  The contribution claimed here is their exact
coupling to the TPC-17 tail and the resulting stopping decomposition.
The combined conclusion is a stopping theorem, not an asymptotic
formula.  It converts a failed symmetric tail block into either a
primitive large-determinant/low-gcd residual witness or a nonprimitive
endpoint finite-model witness.

\subsection{What is not proved}

We do not prove any of the following:

\begin{itemize}
\item a fixed-$h$ Hardy--Littlewood asymptotic or infinitely many twin
primes;
\item cancellation of the primitive generic determinant correlation;
\item a new level of distribution for primes;
\item that the sharp M\"obius interval coefficient is well-factorable;
\item that an exponent appearing in an existing one-prime progression
theorem can be transplanted to the two-residual correlation here.
\end{itemize}

Indeed, the last sections explain that a uniform estimate strong enough
to remove every relevant generic slice, combined with TPC-16 and
TPC-17, would deliver the fixed-shift Hardy--Littlewood conclusion.
This is why the remaining statement is recorded as a conditional input
rather than advertised as a routine consequence of current dispersion
technology.

\subsection{Relation to classical and current work}

The lcm Gram form belongs to the Selberg-sieve tradition.  Closely
related M\"obius double sums were studied by
\citet{DressIwaniecTenenbaum1983} and
\citet{deLaBretecheDressTenenbaum2020}; smoothing and factorization issues
are developed systematically by \citet{GranvilleKoukoulopoulosMaynard2021}.
A recent preprint of \citet{RamareZunigaAlterman2026v3} makes the same
terminal-octave obstruction especially transparent.  We therefore make
no novelty claim for the bare Gram identity or its endpoint floor.

For distribution beyond the square-root barrier, the relevant lesson
from Maynard's published fixed-residue and well-factorable theorems
\citep{Maynard2025I,Maynard2025II}, and from the more recent preprints
of \citet{Lichtman2023} and \citet{Li2026v6}, is that coefficient shape
matters as much as the numerical exponent.  The sharp interval
$\mu(d)\one_I(d)$ contains isolated large primes and is not covered by
their balanced factorization hypotheses.  Moreover, their conclusions
concern one prime in progressions; the object left here is a correlation
of two residual affine forms.  Kloosterman-fraction estimates such as
\citet{BettinChandee2018} are important ingredients in dispersion
arguments but do not, without a new reduction, estimate our
variable-determinant form.

\subsection{Organization}

\Cref{sec:interface} fixes the inherited block and separates it from
TPC-17's asymmetric packet.  \Cref{sec:lcm} proves cutoff return.
\Cref{sec:gram} proves the coefficient no-go theorem.
\Cref{sec:same-k} develops the first $TT^*$ witness.
\Cref{sec:opened-d} proves the generic determinant theorem.
\Cref{sec:content} gives the primitive/nonprimitive split and endpoint
collapse.  \Cref{sec:crt} derives the finite-model CRT kernel.
\Cref{sec:stopping} assembles the stopping theorem and states the exact
conditional closure gate.  \Cref{sec:computation} describes the finite
certificate and summarizes the boundary.
