\section{Exact certificate and formal claim boundary}
\label{sec:tpc38-certificate-claims}

The accompanying standard--library program is
\begin{center}
 \texttt{experiments/tpc38\_certificate.py}.
\end{center}
It writes the canonical archive
\begin{center}
 \texttt{experiments/tpc38\_certificate.json}.
\end{center}
The same suite is run with ordinary Python and with optimization enabled:
\begin{center}
\begin{minipage}{0.58\textwidth}
\ttfamily
python experiments/tpc38\_certificate.py\\
python -O experiments/tpc38\_certificate.py
\end{minipage}
\end{center}
No check depends on \texttt{assert} semantics.

\subsection{Finite identities checked}

The certificate uses integers and rational numbers only.  It checks:
\begin{enumerate}[label=(\roman*)]
 \item the local and CRT full/proper face definitions and exact
 recombination \(C_N+P_N=\one_{M\mid F}\);
 \item fixed--target one--period squared norms;
 \item the local and CRT target--row Gram formulas;
 \item the local target--synthesis eigenvalues and the global tensor
 product ledger;
 \item the exact ratio--fiber multiplicity \(d_M(F)\) on every determinant
 stratum for several small prime packets;
 \item the fixed--determinant full/proper target masses;
 \item the four--modulus no--wrap threshold on a finite interval;
 \item offjoint full/proper cancellation; and
 \item the sharp \(K_B\)-loss rank--one alias witness and the two--column
 equality--nonrecoverability witness.
\end{enumerate}
Finite enumeration verifies the displayed algebra on the archived test
families.  It is not evidence for an asymptotic M\"obius or Gram estimate.

\subsection{Reproducibility record}

The final JSON records per--family check counts, byte--for--byte SHA--256
hashes of the tracked sources, and a digest of the canonical certificate
payload.  For the archived run:
\begin{center}
\begin{minipage}{0.96\linewidth}
\small
\textbf{Certificate source SHA--256.}\par
{\scriptsize\ttfamily
1f2f479b8ff1891eebd379f1357d9fc03009dfe2583b68a982ea20d28409dc42\par}
\smallskip
\textbf{JSON SHA--256.}\par
{\scriptsize\ttfamily
9750d268eec35885d034ce12b0be52c83e9008f9a8a515d49ad0a72bc967c3d6\par}
\smallskip
\textbf{Certificate digest.}\par
{\scriptsize\ttfamily
f7a09acd95d4e5ff4420da353c04daded1c679b1c43da6e1b3bc6492da0c8f2a\par}
\end{minipage}
\end{center}
These values were inserted after the hashed manuscript sources and
certificate were frozen.  The certificate hashes do not promote finite enumeration to a
proof of the analytic reductions.

\subsection{Unconditional conclusions}

Under the hypotheses stated in the corresponding results (and using the
inherited notation only when physical scales are mentioned), this paper
proves:
\begin{enumerate}[label=(\roman*)]
 \item the exact target--coupled character expansion of every CRT face for
 unit targets;
 \item full/proper recombination and the elimination of all nonjoint
 ghosts in the regular CRT completion before estimation;
 \item fixed--target Parseval and the shifted Jacobi cross--target Gram;
 \item Hilbert--valued ratio Parseval and the exact determinant multiplicity
 \(d_M(F)\), hence the scale ladder \(1,J,J^2,J^3\) when
 \(q_i\asymp J\);
 \item exact fixed--determinant target masses;
 \item the complete scalar target--synthesis spectra of the full and
 proper fields;
 \item character blindness on the joint--alias identity bucket;
 \item the sharp coefficient--free \(K_B\) Cauchy loss for coherent alias
 columns;
 \item nonrecoverability of the exact equality column from the completed
 alias sum or the two completed fixed face fields;
 \item strict non--equivalence between separate face estimates and their
 recombined output;
 \item the equality--face embedding and the strength of a hereditary
 all--field operator estimate; and
 \item the exact terminal alias autocorrelation identity and the displayed
 four--M\"obius factor contained in the physical row kernel.
\end{enumerate}

\subsection{What is not proved}

Neither the manuscript nor the certificate proves:
\begin{enumerate}[label=(\roman*)]
 \item the uniform full alias--column bound
 \eqref{eq:tpc38-moving-shift-diagonal};
 \item the joint--alias Gram estimate
 \eqref{eq:tpc38-joint-alias-Gram-gate} or its one--vector weakening;
 \item the two fixed physical face--field estimates
 \eqref{eq:tpc38-interface-two-field-input};
 \item the nonzero--alias recovery estimate
 \eqref{eq:tpc38-nonzero-alias-recovery-gate}, or any other recovery of
 \(\mathscr Z_0\) from the completed face outputs;
 \item a hereditary target--coupled all--field operator theorem;
 \item the full physical orbit gate
 \(V_L+V_R\ll X^{o(1)}Q^3/J\);
 \item cancellation in the M\"obius progression
 \(N+kM\), pointwise or on average;
 \item an affine Chowla theorem or a new M\"obius--disjointness theorem;
 \item failure of sieve parity or positivity;
 \item a Hardy--Littlewood prime--pair asymptotic; or
 \item infinitely many twin primes.
\end{enumerate}

The advance is an exact reduction and a corrected logical gate.  The finite
unit--target CRT dependence and regular nonjoint face geometry have been resolved; the
remaining physical identity bucket has a target--scale recovery route, a
nested stronger alias--Gram route, and a sharp coefficient--free loss.
