\section{Inherited physical interface and normalizations}
\label{sec:tpc38-interface}

The finite CRT statements later in the paper are unconditional.  Their
application to the orbit--sliced prime--M\"obius packet uses only the
interface below, inherited from TPC--34--TPC--37
\citep{WangTPC34,WangTPC35,WangTPC36,WangTPC37}.

\subsection{Rows, targets, and the orbit gate}

Fix \(h\in\Z\setminus\{0\}\), put \(H=\rad|h|\), and work on one retained
dyadic packet with
\begin{equation}
 Q=LD,\qquad QJ\asymp X,\qquad R\le T<U_0\asymp X.
 \label{eq:tpc38-interface-scales}
\end{equation}
A physical row is
\begin{equation}
 \alpha=(\ell_\alpha,d_\alpha),\qquad
 m_\alpha=\ell_\alpha d_\alpha\asymp Q,
 \label{eq:tpc38-interface-row}
\end{equation}
where \(\ell_\alpha\asymp L\) is prime and \(d_\alpha\asymp D\) is
squarefree.  Source separation makes \(m_\alpha\) determine the row.
There are \(O(QX^{o(1)})\) rows.  The two physical coefficient systems
satisfy
\begin{align}
 \sum_\alpha|\gamma_\alpha^{(i)}|
 &\ll X^{o(1)}Q,
 \label{eq:tpc38-row-l1}\\
 \sum_\alpha|\gamma_\alpha^{(i)}|^2
 &\ll X^{o(1)}Q,
 \qquad i=1,2.
 \label{eq:tpc38-row-l2}
\end{align}
They contain the actual squarefree M\"obius and prime von--Mangoldt
provenance; they are not arbitrary bounded row vectors.

For \(j\) in a positive interval \(\cJ\) of \(O(J)\) integers, put
\begin{equation}
 N_\alpha(j)=m_\alpha j+h\asymp X.
 \label{eq:tpc38-interface-target}
\end{equation}
Choose the distinct auxiliary primes \(q_i\asymp J\) under the inherited
zero--face hypotheses
\begin{equation}
 \max\cJ<q_i,
 \qquad
 \max_\alpha d_\alpha<q_i<\min_\alpha\ell_\alpha,
 \qquad
 q_i\nmid h,
 \label{eq:tpc38-interface-auxiliary-prime-hypotheses}
\end{equation}
and put \(M=\prod_iq_i\).  Let \(\cN_{\rm reg}\) be the subpacket on which
\begin{equation}
 (N_\alpha(j),M)=1.
 \label{eq:tpc38-interface-regular-target}
\end{equation}
The zero--face estimates of TPC--37 place the complementary target rows at
the inherited acceptable scale.  From this point onward, all shifted
outputs and the symbols \(V_L,V_R\) refer to this regular subpacket.  Thus
the character and ratio calculations below are applied only where their
unit hypotheses hold; adjoining the already controlled complement recovers
the full packet ledger.

The ultra increment is
\begin{equation}
 C_m(j)=\sum_{\substack{T<u\le U_0\\u\mid mj+h}}
 -\mu(u)\log u.
 \label{eq:tpc38-interface-ultra}
\end{equation}
On the physical support,
\begin{equation}
 (u,mjH)=1
 \label{eq:tpc38-interface-primitivity}
\end{equation}
for every divisor in this sum.

The actual retained multiplier has the form
\begin{equation}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)
 =\mathfrak m_{\rm act}(\alpha,\gamma)
  \Xi_{\alpha,\gamma}(j)
  \cW_{\alpha,\gamma}(j/J),
 \label{eq:tpc38-interface-multiplier}
\end{equation}
where the static mask is
\begin{equation}
 \mathfrak m_{\rm act}(\alpha,\gamma)
 =\one_{\ell_\alpha\ne\ell_\gamma}
  \one_{|m_\alpha-m_\gamma|>\Delta}
  \one_{(d_\alpha,d_\gamma)\le G}.
 \label{eq:tpc38-interface-static-mask}
\end{equation}
TPC--36 proves an \(X^{o(1)}\) signed projective reassembly for this mask
and the fixed residue and smooth orbit factors.  It does not prove an
arithmetic Gram estimate for the resulting divisor sums.

Define
\begin{align}
 Y_{\gamma,j}^L
 &=\sum_\alpha\gamma_\alpha^{(1)}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\alpha}(j),
 \qquad
 V_L=\sum_{\gamma,j}|Y_{\gamma,j}^L|^2,
 \label{eq:tpc38-interface-left}\\
 Y_{\alpha,j}^R
 &=\sum_\gamma\gamma_\gamma^{(2)}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)C_{m_\gamma}(j),
 \qquad
 V_R=\sum_{\alpha,j}|Y_{\alpha,j}^R|^2.
 \label{eq:tpc38-interface-right}
\end{align}
The inherited scalar remainder closes once
\begin{equation}
 \boxed{V_L+V_R\ll X^{o(1)}\frac{Q^3}{J}.}
 \label{eq:tpc38-interface-gate}
\end{equation}
The proved input--copy diagonal is
\begin{equation}
 V_{L,\Delta}+V_{R,\Delta}
 \ll X^{o(1)}Q^2J.
 \label{eq:tpc38-interface-diagonal}
\end{equation}
This diagonal is attached to the original fixed shift \(h\).

\subsection{Shifted determinant fibers}

Opening one ultra divisor and its complementary factor gives
\begin{equation}
 su=N_\alpha(j)=\ell_\alpha d_\alpha j+h.
 \label{eq:tpc38-interface-reflection}
\end{equation}
After dyadic and projective separation, a layer has the schematic integer
form
\begin{equation}
 \sum_{\ell,d,u,s}b(\ell)f(d)g(u)w(s)
 \one_{su=\ell jd+h},
 \label{eq:tpc38-interface-integer-core}
\end{equation}
with the physical ultra coefficient
\begin{equation}
 g(u)=-\mu(u)\log u\,\Phi_U(u).
 \label{eq:tpc38-interface-physical-ultra}
\end{equation}

For a shifted determinant \(F\), replace
\eqref{eq:tpc38-interface-reflection} by
\begin{equation}
 su=N_\alpha(j)+F
 =\ell_\alpha d_\alpha j+h+F.
 \label{eq:tpc38-interface-shifted-fiber}
\end{equation}
Let
\begin{equation}
 \cH_{\rm phys}
 =\ell^2\{(L,\gamma,j)\}
 \oplus\ell^2\{(R,\alpha,j)\}
 \label{eq:tpc38-interface-Hphys}
\end{equation}
be the retained left/right output space.  We write \(\mathscr Z_F[\kappa]\)
for the Hilbert--valued shifted output in which an atom with target \(N\)
is multiplied by \(\kappa_N(F)\) before the row sum.  This notation
contains the already proved \(X^{o(1)}\) projective reassembly cost.
Write
\begin{equation}
 \mathscr R_F:=\mathscr Z_F[\mathbf1]
 \label{eq:tpc38-interface-raw-shifted-output}
\end{equation}
for the raw shifted column.  The original regular--subpacket output is
\(\mathscr R_0\), and
\begin{equation}
 \|\mathscr R_0\|_2^2=V_L+V_R
 \label{eq:tpc38-interface-original-output}
\end{equation}
at the packet level, with the declared reassembly convention.

The TPC--37 continuation was the pair of fixed--field estimates
\begin{equation}
 \left\|\sum_{|F|\ll X}\mathscr Z_F[\kappa]\right\|_2^2
 \ll X^{o(1)}Q^2J
 \sup_N\sum_{|F|\ll X}|\kappa_N(F)|^2,
 \qquad \kappa=C,P.
 \label{eq:tpc38-interface-two-field-input}
\end{equation}
It was proposed there as a sufficient conditional input.  The present
paper does not assume it and refines its logical scope: the displayed
estimate controls a face--weighted congruence completion.  Recovering
\(\mathscr R_0\) from that completion requires an additional statement.
We determine the exact coefficient--free information available for its two
fields, prove the recovery obstruction, and distinguish
\eqref{eq:tpc38-interface-two-field-input} from an operator inequality valid
for arbitrary \(\kappa\).

\subsection{Endpoint ledger}

At the endpoint,
\begin{equation}
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
 \label{eq:tpc38-interface-endpoint}
\end{equation}
so \(QJ=X^{1+o(1)}\).  Three pairwise coprime orbit--scale primes give
\begin{equation}
 M=q_1q_2q_3=X^{399/400+o(1)},
 \qquad
 \cK_X:=1+\frac XM=X^{1/400+o(1)}.
 \label{eq:tpc38-interface-M-K}
\end{equation}
The key identity is
\begin{equation}
 Q^2J\cK_X
 =Q^2J\frac Q{J^2}X^{o(1)}
 =X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc38-interface-key-ledger}
\end{equation}
Four orbit--scale primes have product \(J^4>X^{1+o(1)}\) and eliminate
nonzero joint aliases.  As shown later, they do not weaken the full face
on the equality \(F=0\).
