\section{Full/proper recombination and the joint--alias Gram}
\label{sec:tpc38-recombined-gate}

The preceding sections show why estimating the two face families
separately is expensive.  The CRT congruence--completed kernel contains
their exact sum, so one should recombine before applying an inequality.

\subsection{Strict face--splitting obstruction}

Let \(E\subset\Z/M\Z\) be a nonempty set of nonjoint residues on which
\(C_N(F)\ne0\).  Fix a unit vector \(v\) in a Hilbert space and set
\begin{equation}
 z_F=\frac{\overline{C_N(F)}}{|C_N(F)|}v,
 \qquad F\in E.
 \label{eq:tpc38-offjoint-witness}
\end{equation}

\begin{proposition}[Separate faces are strictly stronger]
\label{prop:tpc38-face-splitting-obstruction}
For the family \eqref{eq:tpc38-offjoint-witness},
\begin{equation}
 \sum_{F\in E}C_N(F)z_F
 =\left(\sum_{F\in E}|C_N(F)|\right)v,
 \label{eq:tpc38-large-full-output}
\end{equation}
and
\begin{equation}
 \sum_{F\in E}P_N(F)z_F
 =-\left(\sum_{F\in E}|C_N(F)|\right)v.
 \label{eq:tpc38-large-proper-output}
\end{equation}
Their recombined output is zero.  Hence no abstract estimate can recover
separate full and proper outputs from their sum.
\end{proposition}

\begin{proof}
Use \(P_N(F)=-C_N(F)\) for \(M\nmid F\).  The definition of \(z_F\)
aligns every full--face summand.
\end{proof}

This proposition is not a counterexample to either fixed physical field
estimate in \eqref{eq:tpc38-interface-two-field-input}: its vectors were
chosen adversarially.  It proves a logical point.  Separate--face
control is sufficient, but it is not necessary for the recombined
physical kernel and may destroy an exact cancellation before arithmetic
coefficients are used.

\subsection{The identity bucket}

Let \(B\ll X\) bound the determinant range and put
\begin{equation}
 \cI_B=\{k\in\Z:|kM|\le B\},
 \qquad K_B=|\cI_B|=2\left\lfloor\frac BM\right\rfloor+1.
 \label{eq:tpc38-alias-index-set}
\end{equation}
Let
\begin{equation}
 \mathscr Z_k:=\mathscr R_{kM}\in\cH_{\rm phys},
 \qquad k\in\cI_B,
 \label{eq:tpc38-Zk}
\end{equation}
be the raw shifted columns associated with
\begin{equation}
 su=N+kM.
 \label{eq:tpc38-joint-shifted-equality}
\end{equation}
Define the two completed face outputs by
\begin{equation}
 \mathscr Y_C:=\sum_{|F|\le B}\mathscr Z_F[C],
 \qquad
 \mathscr Y_P:=\sum_{|F|\le B}\mathscr Z_F[P].
 \label{eq:tpc38-completed-face-outputs}
\end{equation}
Linearity and \eqref{eq:tpc38-face-recombination} give the exact identity
\begin{equation}
 \boxed{
 \mathscr Y_C+\mathscr Y_P
 =\sum_{k\in\cI_B}\mathscr Z_k
 =:\mathscr Y_{\rm alias}.}
 \label{eq:tpc38-joint-output}
\end{equation}
By contrast, the original equality output of the retained regular subpacket is
\begin{equation}
 \boxed{\mathscr Y_{\rm phys}=\mathscr Z_0=\mathscr R_0.}
 \label{eq:tpc38-original-versus-alias-output}
\end{equation}
Thus face recombination produces an exact congruence completion of the
original equality; it does not identify the completion with its zero
column.

\begin{proposition}[Character blindness on the identity bucket]
\label{prop:tpc38-character-blindness}
For every unit target \(N\), every \(k\in\cI_B\), and every character
\(\chi\bmod M\),
\begin{equation}
 \chi(N+kM)\overline{\chi(N)}=1.
 \label{eq:tpc38-character-phase-one}
\end{equation}
Thus every joint alias belongs to the single ratio bucket \(r=1\), and the
multiplicative character Gram on that bucket is rank one.
\end{proposition}

\begin{proof}
Modulo \(M\), one has \(N+kM=N\), and \(N\) is a unit.
\end{proof}

No additional multiplicative character decomposition can separate the
vectors in \eqref{eq:tpc38-joint-output}.  The completion is governed by
their ordinary Hilbert Gram matrix
\begin{equation}
 \mathsf G_B=(\langle\mathscr Z_k,\mathscr Z_{k'}\rangle)_{k,k'\in\cI_B}.
 \label{eq:tpc38-alias-Gram-matrix}
\end{equation}

\subsection{Alias completion does not recover exact equality}

\begin{theorem}[Sharp equality--recovery obstruction]
\label{thm:tpc38-equality-recovery-obstruction}
Assume \(K_B>1\).  In the unrestricted Hilbert column class, neither
\(\mathscr Y_{\rm alias}\) nor the pair
\((\mathscr Y_C,\mathscr Y_P)\) controls \(\mathscr Z_0\).  More precisely,
for every \(T>0\) there are columns for which
\begin{equation}
 \mathscr Y_C=\mathscr Y_P=\mathscr Y_{\rm alias}=0,
 \qquad
 \|\mathscr Z_0\|_2=T.
 \label{eq:tpc38-equality-recovery-witness-output}
\end{equation}
\end{theorem}

\begin{proof}
Choose \(k_1\in\cI_B\setminus\{0\}\) and a unit vector \(v\).  Set
\begin{equation}
 \mathscr Z_0=Tv,
 \qquad
 \mathscr Z_{k_1}=-Tv,
 \qquad
 \mathscr Z_k=0\quad(k\ne0,k_1),
 \label{eq:tpc38-equality-recovery-witness}
\end{equation}
and set every nonjoint target atom in every shifted output to zero.  On a joint alias,
\(C_N(kM)=A\) and \(P_N(kM)=1-A\), independently of \(N\).  Hence
\(\mathscr Y_C=A(\mathscr Z_0+\mathscr Z_{k_1})=0\) and
\(\mathscr Y_P=(1-A)(\mathscr Z_0+\mathscr Z_{k_1})=0\), while
\(\|\mathscr Z_0\|_2=T\).
\end{proof}

The witness is coefficient--blind and artificial.  It does not assert
that the physical M\"obius columns cancel in this way.  It proves that an
estimate for the two completed fixed fields needs a new physical recovery
argument before it can bound \eqref{eq:tpc38-interface-gate}.

\subsection{Localized columns, the alias Gram, and the sharp Cauchy loss}

Put
\begin{equation}
 B_0=Q^2J.
 \label{eq:tpc38-B0}
\end{equation}
The following strong localized input is useful for calibrating possible
positive theorems.

\begin{assumption}[Uniform full alias--column bound]
\label{ass:tpc38-moving-shift-diagonal}
Uniformly for \(k\in\cI_B\),
\begin{equation}
 \|\mathscr Z_k\|_2^2\ll X^{o(1)}B_0.
 \label{eq:tpc38-moving-shift-diagonal}
\end{equation}
\end{assumption}

At \(k=0\), \cref{ass:tpc38-moving-shift-diagonal} already gives
\begin{equation}
 \|\mathscr Y_{\rm phys}\|_2^2
 \ll X^{o(1)}Q^2J,
 \label{eq:tpc38-moving-diagonal-already-strong}
\end{equation}
which is stronger than the inherited target \(X^{o(1)}Q^3/J\), since
\(Q^2J\cK_X=X^{o(1)}Q^3/J\).
It is therefore not a preliminary consequence of the proved input--copy
diagonal; it is itself a stronger coefficient theorem for the raw output.

\begin{assumption}[Joint--alias Gram almost--orthogonality]
\label{ass:tpc38-joint-alias-Gram}
The Gram matrix in \eqref{eq:tpc38-alias-Gram-matrix} satisfies
\begin{equation}
 \boxed{\|\mathsf G_B\|_{\op}\ll X^{o(1)}B_0.}
 \label{eq:tpc38-joint-alias-Gram-gate}
\end{equation}
\end{assumption}

\begin{proposition}[What the strong Gram gate implies]
\label{prop:tpc38-reduced-gate-suffices}
Under \cref{ass:tpc38-joint-alias-Gram},
\begin{equation}
 \left\|\sum_{k\in\cI_B}\mathscr Z_k\right\|_2^2
 \ll X^{o(1)}B_0K_B.
 \label{eq:tpc38-reduced-gate-output}
\end{equation}
At the physical endpoint \(B\asymp X\), the right side has scale
\begin{equation}
 X^{o(1)}B_0K_B
 \asymp X^{o(1)}Q^2J\cK_X
 =X^{o(1)}\frac{Q^3}{J}.
 \label{eq:tpc38-reduced-gate-endpoint}
\end{equation}
Moreover,
\begin{equation}
 \|\mathscr Z_k\|_2^2
 \le \|\mathsf G_B\|_{\op}
 \ll X^{o(1)}B_0
 \qquad(k\in\cI_B).
 \label{eq:tpc38-Gram-implies-columns}
\end{equation}
In particular, the Gram gate implies
\cref{ass:tpc38-moving-shift-diagonal} and the stronger equality bound
\eqref{eq:tpc38-moving-diagonal-already-strong}.
\end{proposition}

\begin{proof}
The left side of \eqref{eq:tpc38-reduced-gate-output} is
\(\langle\mathsf G_B\mathbf1,\mathbf1\rangle\).  Bound it by
\(\|\mathsf G_B\|_{\op}\|\mathbf1\|_2^2\).
The diagonal entries of a positive semidefinite Gram matrix are bounded by
its operator norm, proving \eqref{eq:tpc38-Gram-implies-columns}.
\end{proof}

For the alias--completed vector alone, the operator--norm gate is stronger
than necessary.  Given the diagonal trace bound, a weaker sufficient
one--vector condition is
\begin{equation}
 \operatorname{Re}\sum_{k\ne k'}
 \langle\mathscr Z_k,\mathscr Z_{k'}\rangle
 \ll X^{o(1)}B_0K_B,
 \label{eq:tpc38-one-vector-offdiagonal-gate}
\end{equation}
together with the diagonal trace of the same size.  We retain
\eqref{eq:tpc38-joint-alias-Gram-gate} because it is the genuine Bessel
form.

\begin{proposition}[Sharp coefficient--free alias loss]
\label{prop:tpc38-sharp-alias-loss}
Suppose only the diagonal trace estimate
\begin{equation}
 \sum_{k\in\cI_B}\|\mathscr Z_k\|_2^2
 \ll X^{o(1)}B_0K_B.
 \label{eq:tpc38-alias-diagonal-trace}
\end{equation}
Then Cauchy gives
\begin{equation}
 \left\|\sum_{k\in\cI_B}\mathscr Z_k\right\|_2^2
 \ll X^{o(1)}B_0K_B^2.
 \label{eq:tpc38-Cauchy-alias-loss}
\end{equation}
The factor \(K_B\) relative to
\eqref{eq:tpc38-reduced-gate-output} is optimal for the abstract Hilbert
column class.
\end{proposition}

\begin{proof}
Cauchy proves \eqref{eq:tpc38-Cauchy-alias-loss}.  For sharpness, let \(v\)
be a unit vector and take
\begin{equation}
 \mathscr Z_k=\sqrt{B_0}\,v
 \qquad(k\in\cI_B).
 \label{eq:tpc38-rank-one-alias-witness}
\end{equation}
Then the diagonal trace is \(B_0K_B\), while the squared sum is
\(B_0K_B^2\).
\end{proof}

At \(B\asymp X\), the exact finite loss in
\cref{prop:tpc38-sharp-alias-loss} is \(K_B\), and
\begin{equation}
 \boxed{
 K_B\asymp\cK_X:=1+\frac XM
 =\frac X{J^3}X^{o(1)}
 =\frac Q{J^2}X^{o(1)}
 =X^{1/400+o(1)}.}
 \label{eq:tpc38-missing-KX}
\end{equation}
This is much smaller than the earlier \(J\)-scale face losses, but it is a
fixed power and cannot be hidden in \(X^{o(1)}\).

\begin{remark}[The old diagonal is a different object]
\label{rem:tpc38-moving-diagonal-not-inherited}
Equation \eqref{eq:tpc38-interface-diagonal} proves the input--copy
diagonal, not \(\|\mathscr R_0\|_2^2\).  For \(k\ne0\), the affine shift is
\(h+kM\), which may be of size \(X\), and the fixed--\(h\) primitivity and
incidence hypotheses are not automatically uniform.  Thus
\cref{ass:tpc38-moving-shift-diagonal} is both arithmetically new and, at
\(k=0\), already stronger than the inherited physical target.
\end{remark}

\subsection{A target--scale recovery formulation}

The original gate can be recovered without a full Gram theorem if one can
control two particular vectors rather than every alias coefficient.

\begin{proposition}[Two--sum equality recovery]
\label{prop:tpc38-two-sum-recovery}
Suppose
\begin{align}
 \|\mathscr Y_{\rm alias}\|_2^2
 &\ll X^{o(1)}B_0K_B,
 \label{eq:tpc38-alias-total-target-bound}\\
 \left\|\sum_{\substack{k\in\cI_B\\k\ne0}}\mathscr Z_k\right\|_2^2
 &\ll X^{o(1)}B_0K_B.
 \label{eq:tpc38-nonzero-alias-recovery-gate}
\end{align}
Then
\begin{equation}
 \|\mathscr Z_0\|_2^2\ll X^{o(1)}B_0K_B.
 \label{eq:tpc38-two-sum-recovered-output}
\end{equation}
At the endpoint, this is the inherited scale \(X^{o(1)}Q^3/J\).
\end{proposition}

\begin{proof}
Subtract the nonzero--alias sum from \(\mathscr Y_{\rm alias}\) and use
\(\|x-y\|^2\le2\|x\|^2+2\|y\|^2\).
\end{proof}

If the two fixed--field estimates
\eqref{eq:tpc38-interface-two-field-input} were proved, their period
ledgers and \eqref{eq:tpc38-joint-output} would imply
\eqref{eq:tpc38-alias-total-target-bound}.  They do not imply
\eqref{eq:tpc38-nonzero-alias-recovery-gate}, because the fixed fields are
not assumed to be stable under deleting \(F=0\).  This is the precise
additional recovery gate missing from the earlier sufficient--input claim.

\subsection{A fourth modulus removes aliases but not the equality gate}

Choose four pairwise coprime primes \(q_i\asymp J\) and put
\(M_4=\prod_{i=1}^4q_i\).  Then \(M_4>X\) at the endpoint, so
\begin{equation}
 \one_{M_4\mid F}=\one_{F=0}
 \qquad(|F|\ll X).
 \label{eq:tpc38-four-modulus-no-wrap}
\end{equation}
This removes every nonzero joint alias.  However, on \(F=0\) the
four--coordinate full face has scalar value
\begin{equation}
 A_4=\prod_{i=1}^4\left(1-\frac1{q_i-1}\right)
 =1-O(J^{-1}).
 \label{eq:tpc38-four-modulus-full-value}
\end{equation}

\begin{corollary}[Four--modulus loopback]
\label{cor:tpc38-four-modulus-loopback}
Adding a fourth orbit--scale modulus eliminates the alias Gram but returns
the full face, up to the scalar \(A_4\), to the original equality operator.
It supplies no coefficient--free power saving for the full physical gate.
\end{corollary}

This is not a negative result about the physical coefficient.  It shows
that the alias problem and the equality coefficient problem are distinct:
more CRT coordinates solve the former and leave the latter unchanged.
