\section{Terminal embeddings and sparse M\"obius progressions}
\label{sec:tpc38-terminal-boundary}

The identity bucket has an explicit arithmetic submodel.  We record it to
calibrate the strength of possible operator formulations, not to assert a
new M\"obius estimate.

\subsection{Terminal aliases}

On the terminal factorization \(s=1\), the \(k\)-th joint alias has
\begin{equation}
 u=N+kM.
 \label{eq:tpc38-terminal-alias}
\end{equation}
For a smooth terminal cutoff \(\Phi_0\), define
\begin{equation}
 a_N(k)
 =-\mu(N+kM)\log(N+kM)\Phi_0(N+kM).
 \label{eq:tpc38-terminal-alias-sequence}
\end{equation}
For every finite interval \(I\) of admissible \(k\)'s,
\begin{align}
 \left|\sum_{k\in I}a_N(k)\right|^2
 &=\sum_{k\in I}|a_N(k)|^2
 \notag\\
 &\quad+2\operatorname{Re}
 \sum_{r\ge1}
 \sum_{\substack{k,k+r\in I}}
 a_N(k+r)\overline{a_N(k)}.
 \label{eq:tpc38-terminal-autocorrelation}
\end{align}
The off--diagonal terms contain
\begin{equation}
 \mu(N+kM)\mu(N+(k+r)M)
 \label{eq:tpc38-M-spaced-Mobius}
\end{equation}
at shifts \(rM\).  The progression has modulus
\(M=X^{399/400+o(1)}\) and length only
\(\cK_X=X^{1/400+o(1)}\).

\begin{proposition}[Exact arithmetic content of the terminal alias Gram]
\label{prop:tpc38-terminal-alias-content}
The same--target part of the joint--alias Gram contains the autocorrelation
\eqref{eq:tpc38-terminal-autocorrelation}.  Restoring the physical row
\(\alpha=(\ell,d)\) and target \(N_\alpha(j)=\ell dj+h\), the cross--row
terms contain weights of the form
\begin{align}
 &\mu(d_\alpha)\mu(d_\beta)
 (\log\ell_\alpha)(\log\ell_\beta)
 \notag\\[-0.2em]
 &\qquad\times
 \mu(N_\alpha(j)+kM)
 \mu(N_\beta(j)+k'M),
 \label{eq:tpc38-four-Mobius-row-kernel}
\end{align}
multiplied by the actual masks and smooth factors.
\end{proposition}

\begin{proof}
Insert \eqref{eq:tpc38-terminal-alias-sequence} into the Gram expansion.
The physical row coefficient contains \(\mu(d)\log\ell\); pairing two rows
gives \eqref{eq:tpc38-four-Mobius-row-kernel}.
\end{proof}

Equation \eqref{eq:tpc38-four-Mobius-row-kernel} is the shifted version of
the affine four--M\"obius terminal boundary in TPC--34.  The required
physical theorem would average it over rows, orbit times, opposite rows,
aliases, and projective layers.  It is therefore not logically equivalent
to proving
\(\sum_{k<K}\mu(N+kM)=o(K)\) for every \(N\).  Conversely, it cannot be
deduced from character orthogonality because all joint aliases have ratio
one.

\subsection{Prescribed fields versus a hereditary all--field estimate}

Let \(\cK\) be a coefficient Hilbert space containing the two prescribed
fields \(C,P\), and let \(\mathfrak T:\cK\to\cH_{\rm phys}\) be the linear
synthesis map
\begin{equation}
 \boldsymbol\kappa\longmapsto
 \sum_F\mathscr Z_F[\boldsymbol\kappa].
 \label{eq:tpc38-formal-synthesis-map}
\end{equation}
The TPC--37 continuation asks only for bounds at the two fields \(C\) and
\(P\).  An all--field estimate of the same normalization would assert
\begin{equation}
 \left\|\sum_F\mathscr Z_F[\boldsymbol\kappa]\right\|_2^2
 \ll X^{o(1)}B_0
 \sup_N\sum_F|\kappa_N(F)|^2
 \label{eq:tpc38-all-field-estimate}
\end{equation}
for every admissible field \(\boldsymbol\kappa\).  We call it hereditary if
the same bound remains valid after multiplying the field by indicators of
determinant fibers or factorization layers.  This norm is the one appearing
in the earlier prescribed--field input; no Hilbert structure for the
right--hand side is being asserted.

\begin{proposition}[Two tests do not determine an operator norm]
\label{prop:tpc38-two-test-dichotomy}
Bounds for \(\mathfrak T C\) and \(\mathfrak T P\) alone give no bound for
\(\|\mathfrak T\|_{\op}\) on the orthogonal complement of their span in
\(\cK\).
Moreover, a small recombined value
\(\mathfrak T(C+P)\) gives no bound for either separate value.
\end{proposition}

\begin{proof}
The first statement is elementary finite--dimensional linear algebra: an
operator may vanish on two prescribed vectors and have arbitrary norm on
their orthogonal complement.  For the second, take
\(\mathfrak T C=v\) and \(\mathfrak T P=-v\), or use the explicit
offjoint construction in
\cref{prop:tpc38-face-splitting-obstruction}.
\end{proof}

In addition, \cref{thm:tpc38-equality-recovery-obstruction} shows that the
two completed test values do not recover their \(F=0\) column.  This is
logically distinct from their failure to determine the operator norm.
The distinction becomes arithmetic on the equality face.  Heredity under
\(F=0\) would in particular give the explicit restricted input
\begin{equation}
 \|\mathscr Z_0[\boldsymbol\kappa]\|_2^2
 \ll X^{o(1)}B_0\sup_N|\kappa_N(0)|^2
 \label{eq:tpc38-hereditary-F0-input}
\end{equation}
for every field supported on \(F=0\).

\begin{theorem}[Equality--face embedding]
\label{thm:tpc38-equality-face-embedding}
Assume \eqref{eq:tpc38-hereditary-F0-input}, and let
\(\mathscr R_0:=\mathscr Z_0[\mathbf1]\) be the raw regular--subpacket
output on \(F=0\).  Then
\begin{equation}
 \boxed{
 \mathscr Z_0[C]=A\mathscr R_0,
 \qquad
 \mathscr Z_0[P]=(1-A)\mathscr R_0.}
 \label{eq:tpc38-equality-face-embedding}
\end{equation}
Consequently, the hereditary all--field estimate at normalization
\(B_0=Q^2J\) implies
\begin{equation}
 \|\mathscr R_0\|_2^2\ll X^{o(1)}Q^2J.
 \label{eq:tpc38-hereditary-equality-bound}
\end{equation}
This is stronger than the inherited target \(Q^3/J\) by a factor of order
\(\cK_X=(Q/J^2)X^{o(1)}\).
\end{theorem}

\begin{proof}
The identities follow from \(C_N(0)=A\) and \(P_N(0)=1-A\), which are
independent of \(N\).  Apply the hereditary estimate to
\(C_N(F)\one_{F=0}\) and divide by \(A^2=1-O(J^{-1})\).  Finally,
\(Q^2J\cK_X=X^{o(1)}Q^3/J\) by
\eqref{eq:tpc38-interface-key-ledger}.
\end{proof}

If the hereditary all--field estimate is also stable under the terminal restriction
\(s=1\), then \eqref{eq:tpc38-hereditary-equality-bound} applies to the
affine terminal operator whose square expands into
\eqref{eq:tpc38-four-Mobius-row-kernel} with \(k=k'=0\).

\begin{corollary}[Terminal hereditary all--field implication]
\label{cor:tpc38-terminal-hereditary-implication}
An all--field estimate hereditary under \(F=0,s=1\) implies a diagonal--scale
bound for the terminal affine--M\"obius operator isolated in TPC--34.
\end{corollary}

This corollary does not say that the two prescribed--field inputs
\eqref{eq:tpc38-interface-two-field-input} implies affine Chowla.  By
itself that input does not even recover the equality column from its alias
completion, and it may also use cancellation between equality, proper
divisors, terminal atoms, and nonzero aliases.  The implication applies
only to the stronger, localizable operator theorem.

\subsection{What the sharp examples do not prove}

The rank--one witness \eqref{eq:tpc38-rank-one-alias-witness}, the
offjoint witness \eqref{eq:tpc38-offjoint-witness}, and the principal target
mode in \cref{sec:tpc38-target-spectrum} are artificial coefficient
choices.  They establish optimal losses in broad abstract classes.  They
do not prove that the actual M\"obius vectors align, that
\cref{ass:tpc38-joint-alias-Gram} is false, or that a M\"obius
autocorrelation is large.  Their role is to identify precisely which new
arithmetic information a positive theorem must use.
