\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={The Zero Mellin Mode of a Prime-Target Residual: Fixed-Shift Titchmarsh Closure, a Large-Factor Subtraction Formula, and the Scale-Localization Boundary},
 pdfauthor={Liang Wang},
 pdfsubject={A fixed-shift Titchmarsh evaluation and a large-factor subtraction formula for a fully scale-aggregated prime residual},
 pdfkeywords={Titchmarsh divisor problem, von Mangoldt function, Bombieri--Vinogradov theorem, Mellin localization, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cE}{\mathcal E}
\newcommand{\cI}{\mathcal I}
\newcommand{\cM}{\mathcal M}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\supp}{\operatorname{supp}}

\title{\textbf{The Zero Mellin Mode of a Prime-Target Residual:}\\
\textbf{Fixed-Shift Titchmarsh Closure,}\\
\textbf{a Large-Factor Subtraction Formula,}\\
\textbf{and the Scale-Localization Boundary}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let $h\ne0$ be fixed and let $W\in C_c^1((0,\infty))$.  We study the
prime-target residual aggregated over all factor scales,
\[
 \cA_h(X;W)=
 \sum_{m,n\geq1}(\Lambda(n)-1)\Lambda(mn+h)W(mn/X),
\]
and its large-factor portion $\cA_{h,>D}$ obtained by imposing $n>D$.
Although $\Lambda-1$ has $L^2$ energy of order $N\log N$ on a dyadic
interval, the complete factor aggregation has the exact collapse
\[
 \sum_{n\mid r}(\Lambda(n)-1)=\log r-\tau(r).
\]
Consequently $\cA_h$ is a difference of a shifted prime number theorem and
a Titchmarsh divisor sum.

Write
\[
 C_h(s)=
 \prod_{p\mid h}(1-p^{-s-1})
 \prod_{p\nmid h}\left(1+\frac1{(p-1)p^{s+1}}\right),
 \qquad C_h=C_h(0).
\]
Using the uniform Titchmarsh theorem of Assing--Blomer--Li, we obtain a
fixed-$h$ asymptotic with arbitrary logarithmic saving.  Classical maximal
Bombieri--Vinogradov then evaluates the whole range $n\leq D$, uniformly for
\[
 D\leq X^{1/2}(\log X)^{-B}.
\]
Subtracting gives an explicit asymptotic for the complementary range
$n>D$, even though most of that range lies beyond the direct
arithmetic-progression reduction.  When $D=D(X)\to\infty$, its logarithmic
leading term is
\[
 (1-C_h)X\log(X/D)\int_0^\infty W(u)\,du.
\]
Whenever $(1-C_h)I_0(W)\ne0$, its $X\log X$ coefficient at the
square-root cutoff is one half of the complete-sum coefficient.  For $h=2$,
\[
 C_2=\frac13\frac{\zeta(2)\zeta(3)}{\zeta(6)}
 =0.647865\ldots,
\]
so the coefficient is explicitly nonzero.

The result is a scale-aggregation theorem, not a new Titchmarsh,
Bombieri--Vinogradov, dispersion, or Type~II estimate.  The factor collapse
is the zero Mellin mode of the multiplicative scale variable.  Nonzero
Mellin modes do not reduce to $\log r-\tau(r)$, and a single factor layer
already contains fixed-shift prime-pair covariance.  In particular, the
paper proves no fixed prime-pair asymptotic, twin-prime lower bound, or
breach of the parity barrier.
\end{abstract}

\noindent\textbf{Keywords:} prime-target residual; Titchmarsh divisor
problem; Bombieri--Vinogradov theorem; factor-scale aggregation; Mellin
localization; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N13, 11N36; Secondary 11N35, 11M06.

\input{sections/introduction-scope}
\input{sections/zero-mellin-closure}
\input{sections/small-factor-transfer}
\input{sections/tail-mellin-boundary}
\input{sections/certificate-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
