\begin{abstract}
We audit the ten-paper block TPC--63 through TPC--72, using the completed
results of TPC--63 through TPC--71 as input.  The purpose is not to promote
interface theorems into arithmetic conclusions, but to determine exactly
which dependencies are closed, which proof mechanisms have failed, and
which literal estimates remain necessary before a fixed-shift endpoint can
be claimed.

The represented branch now has an exact chain from canonical cofactor
provenance through terminal activation, activated-range Grams, actual
pair-codegree geometry, and componentwise determinant mass.  TPC--68 gives
exact abstract certificates for the complete signed missing-native
operator.  TPC--69--TPC--71 then isolate one mixed scalar sector and reduce
its anchored four-corner contributions through erasure-boundary words,
primitive cofactor coordinates, and a divisor-lifted two-dimensional Abel
certificate.  In particular, the first cross-key sign becomes
\(\mu(a)\mu(b)\mu(u)\mu(v)\), is constant along each affine prime ray, and
leaves a primitive-plane kernel.  The identity
\[
 \one_{(u,v)=1}\mu(u)\mu(v)=\mu(uv)
\]
and a diagonal divisor lift reduce regular kernels to restricted Mertens
sums.  Fixed-divisor prime number theory then gives cancellation when every
fixed-\(d\) mixed variation is
\(O_d(\|K\|_\infty)\).  It does not give the mass-normalized variation or
divisor tail required by the actual physical kernel.

The audit also closes a tempting but type-incorrect physical promotion of
this certificate.  The TPC--70 primitive-plane target is an anchored
four-corner scalar contributing to \(\tr(ER)\), not a two-corner matrix
entry of the erasure operator \(E\).  Consequently, even a sharp bound for
every audited primitive-plane target does not by itself imply an entrywise
majorant, a row-star estimate, a Perron bound, or an operator norm estimate.
The literal anchor multiplicity must be retained, and the four-corner
normalization must not be applied a second time.

We prove a dependency theorem for the audited chain, reconcile its exponent
notations into one no-double-charge ledger, and state exact kill criteria.
Algebraic identities and isometric or subpower-conditioned relabelings have
zero fixed-power cost.  Every non-isometric physical comparison exposed by
them must be charged exactly once in a total strictly below \(1/400\).
The missing-native perturbative gate
\(\sigma_M>\nu_M+\lambda_{\rm rep}\) and the nuisance condition
\(\|C_N\|=o(1)\) remain separate.  As of TPC--71 there is no completed
\(\Ltwo\) estimate satisfying the full fixed-shift quantifier.  The next
stage may estimate the physical primitive-plane variation and tail to
control the first mixed trace, but an operator theorem additionally needs
one of three new bridges: a direct two-corner representation, row-local
anchored bounds dominating the relevant stars, or uniformly controlled
complete decorated moments.  Terminal activation and the represented lower
frame must advance in parallel.  No
fixed-\(2\), parity-breaking, prime-pair, or twin-prime conclusion is drawn.
\end{abstract}
