\section{Audit levels and invariant physical data}
\label{sec:audit-rules}

\subsection{The three levels}

\begin{definition}[Audit levels]
\label{def:audit-levels}
We use the following labels.
\begin{enumerate}[label=\textup{\Lzero},leftmargin=4em]
 \item[\(\Lzero\)] A finite-dimensional, combinatorial, or abstract analytic
       theorem valid for the declared object, before specialization to the
       literal growing physical family.
 \item[\(\Lone\)] An exact identification or unconditional support statement
       on the literal fixed-\(h_0\) carrier, retaining its coefficients,
       labels, support, and normalization, but not proving the required
       signed asymptotic saving.
 \item[\(\Ltwo\)] A uniform arithmetic estimate for the actual physical
       coefficients in the fixed-shift growing family, with sufficient
       strength and quantifiers to enter the endpoint chain.
\end{enumerate}
\end{definition}

An \(\Lone\) upper count can use number theory and still remain \(\Lone\)
when it controls support geometry rather than the required signed operator.
Conversely, a theorem need not solve the final problem to be \(\Ltwo\); a
fixed-power saving on one literal endpoint arrow is already an arithmetic
advance if its scope matches the physical chain.

\subsection{The six invariant checks}

Every proposed promotion to \(\Ltwo\) is tested against:
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3.6em]
 \item the literal physical coefficients;
 \item one prescribed fixed nonzero shift \(h_0\);
 \item raw physical atomic normalization;
 \item a canonical or explicitly justified representation;
 \item the actual active support, with no coefficient-dependent deletion;
 \item the complete endpoint loss, strictly below \(1/400\).
\end{enumerate}
Dropping any check changes either the object, the norm, or the quantifier.

\subsection{Three kinds of progress}

\begin{definition}[Counted progress]
\label{def:counted-progress}
A result counts as forward proof progress in this audit if it does at least
one of the following:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item improves a concrete exponent for literal physical coefficients;
 \item closes a necessary interface in the dependency chain; or
 \item rules out a route by an exact physical obstruction or a sharp
       non-implication theorem.
\end{enumerate}
\end{definition}

The definition recognizes structural progress without relabeling it as
arithmetic cancellation.  Numerical stability, generic phases, randomized
signs, or finite fixed-dimensional experiments do not satisfy
\cref{def:counted-progress} unless they yield an exact certificate.

\subsection{Uniform and distinguished scopes}

Several papers admit two honest coefficient scopes.
\begin{itemize}
 \item A \emph{uniform} theorem holds for every vector in the declared
       coefficient class and therefore requires rowwise or operator
       control.
 \item A \emph{distinguished} theorem holds for one fixed physical vector
       chosen independently of the later estimate.
\end{itemize}
The second cannot be entered as the first.  Likewise, a fixed-pair estimate,
a density-one family, or an average over shifts cannot be substituted for
the complete fixed-\(h_0\) growing-row statement.

\begin{proposition}[Audit monotonicity]
\label{prop:audit-monotonicity}
An exact \(\Lzero\) identity plus an \(\Lone\) crosswalk does not imply an
\(\Ltwo\) estimate without a quantitative arithmetic input on the crosswalked
object.
\end{proposition}

\begin{proof}
Take any finite incidence or matrix identity in the audited chain and fill
the same support with two coefficient systems having different phases.
TPC--65--TPC--69 contain explicit cycle, row-capacity, star, and holonomy
countermodels showing that the same structural data can yield incompatible
spectral or cancellation behavior
\citep{WangTPC65,WangTPC66,WangTPC67,WangTPC68,WangTPC69}.
Therefore the structural identity and physical dictionary do not determine
the missing quantitative estimate.
\end{proof}
