\section{Claim ledger and status line}
\label{sec:claim-ledger}

\subsection{Exact conclusions of this audit}

This paper proves the following statements about the audited architecture.
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item TPC--63--TPC--71 form two logically distinct branches, represented
       and missing-native, which meet only at physical reassembly.
 \item Every completed theorem in the block is classified as
       \(\Lzero\), \(\Lone\), or an explicitly conditional \(\Ltwo\)
       premise.
 \item The inherited single-band certificate, same-residual sign route,
       one-key mixed route, negative quadratic correction, and ray-sign
       route are closed by exact obstructions.
 \item The first surviving signed coefficient is the primitive-plane sum
       \eqref{eq:tpc72-physical-plane}.
 \item TPC--71 gives the exact certificate
       \eqref{eq:tpc72-master-plane-certificate} and unconditional
       cancellation for regular kernels, but not for the actual
       mass-normalized physical kernel.
 \item The physical primitive-plane target is the anchored four-corner
       scalar \(\mathfrak X_{\mathfrak a}\), and the valid aggregate
       conclusion is \eqref{eq:tpc72-correct-trace-majorant}.  It is not an
       entrywise erasure majorant.
 \item The complete endpoint requires every item of
       \cref{thm:dependency}; no audited theorem supplies the full
       conjunction.
 \item The common no-double-charge ledger is
       \eqref{eq:tpc72-global-ledger}, with strict gate
       \eqref{eq:tpc72-strict-budget}.
\end{enumerate}

\subsection{Statements not proved}

This paper does not prove:
\begin{itemize}
 \item a positive uniform terminal activation exponent;
 \item a polynomial lower frame for the physical unlabelled represented map;
 \item endpoint-quality determinant mass on the worst actual component;
 \item a mass-normalized mixed-variation bound for the physical
       primitive-plane kernel;
 \item a complete endpoint-quality bound for \(\tr(ER)\);
 \item a direct two-corner pair/star/Perron majorant, a row-local
       anchored-star bridge, or a complete growing-moment saving;
 \item \(\|R+E\|=X^{o(1)}\), much less \(o(1)\);
 \item the missing-mass estimate
       \eqref{eq:tpc72-missing-mass};
 \item the nuisance estimate \(\|C_N\|=o(1)\);
 \item the strict endpoint inequality for one completed physical chain;
 \item any estimate using a property special to \(h_0=2\); or
 \item a parity-breaking, prime-pair, or twin-prime theorem.
\end{itemize}

\subsection{Ten-paper result table}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.09\textwidth}
                  >{\raggedright\arraybackslash}p{0.51\textwidth}
                  >{\raggedright\arraybackslash}p{0.27\textwidth}}
\toprule
Paper & Exact advance & Honest status\\
\midrule
\endfirsthead
\toprule
Paper & Exact advance & Honest status\\
\midrule
\endhead
TPC--63
& Canonical provenance and single-band support-certificate no-go.
& \(\Lzero/\Lone\); no \(\Ltwo\)\\
\addlinespace
TPC--64
& True activation, parent inflation, and sharp capacity law.
& \(\Lzero/\Lone\); arithmetic activation open\\
\addlinespace
TPC--65
& Activated-range represented Gram and compatible three-stage product.
& \(\Lzero/\Lone\); physical gap open\\
\addlinespace
TPC--66
& Unit diagonal and critical reduced pair codegree \(X^{o(1)}\).
& Genuine \(\Lone\) support theorem; no operator saving\\
\addlinespace
TPC--67
& Componentwise determinant mass converts to represented gap.
& \(\Lzero/\Lone\); actual mass lower bound open\\
\addlinespace
TPC--68
& Signed native pair/star/walk certificates and exact shorting.
& \(\Lzero/\Lone\); all arithmetic premises open\\
\addlinespace
TPC--69
& Cross-key mixed holonomy, odd residual boundary, quadratic positivity.
& \(\Lzero/\Lone\); linear saving open\\
\addlinespace
TPC--70
& Primitive cofactor-plane and frozen affine prime rays.
& \(\Lzero/\Lone\); no cancellation\\
\addlinespace
TPC--71
& Divisor lift, two-dimensional Abel certificate, regular-kernel
  cancellation, and anchored mixed-trace crosswalk.
& \(\Lzero/\Lone\); direct operator promotion unavailable\\
\addlinespace
TPC--72
& Dependency theorem, four-corner type boundary and non-substitution
  theorem, unified ledger, revised routes.
& Audit closure; no new arithmetic saving\\
\bottomrule
\end{longtable}

\subsection{Status line}

The ten-paper block moves the program from an ambiguous cofactor-support
picture to a falsifiable primitive-plane frontier.  It has closed necessary
interfaces and eliminated several false sources of cancellation.  As of
TPC--72, however, the \(\Ltwo\) arithmetic column required by the endpoint
remains empty.  The next advance must control the literal physical
primitive-plane variation and tail strongly enough to bound the full
anchored mixed trace.  A separate advance must then construct a genuine
two-corner, row-local anchored-star, or complete-moment operator carrier,
while terminal activation and the represented lower frame are advanced in
parallel.  This is progress in proof architecture, not evidence that the
parity barrier has been broken.
