\section{Closed interfaces, failed mechanisms, and open doors}
\label{sec:closed-open}

The word ``closed'' has two meanings.  An interface may be solved positively,
or a proposed route may be ruled out.  Mixing these meanings obscures the
remaining work.

\subsection{Positively closed interfaces}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.19\textwidth}
                  >{\raggedright\arraybackslash}p{0.60\textwidth}
                  >{\raggedright\arraybackslash}p{0.10\textwidth}}
\toprule
Interface & Exact closure & Level\\
\midrule
\endfirsthead
\toprule
Interface & Exact closure & Level\\
\midrule
\endhead
Provenance
& Minimal faithful pair relation when it exists; literal hypergraph
  fallback when it does not; three separate faithfulness tests.
& \(\Lzero/\Lone\)\\
\addlinespace
Activation calculus
& Exact \(P_m,H_m,T_m\), parent inflation, hybrid repair, and sharp capacity
  certificate.
& \(\Lzero/\Lone\)\\
\addlinespace
Represented range
& Exact activated row Gram, repair invariance, kernel fusion, and
  label-erasure boundary.
& \(\Lzero/\Lone\)\\
\addlinespace
Pair support
& Unit diagonal and critical fixed-row-pair reduced codegree
  \(X^{o(1)}\).
& \(\Lone\)\\
\addlinespace
Determinant conversion
& Peeling, cycle activity, Cauchy--Binet mass, and the componentwise
  determinant-to-gap inequality.
& \(\Lzero/\Lone\)\\
\addlinespace
Native operator
& Exact pair, star, Perron, moment, and shorted-Gram certificates on the
  complete missing carrier.
& \(\Lzero/\Lone\)\\
\addlinespace
Mixed sectors
& Key-local vanishing, cyclic erasure-count formula, odd residual boundary,
  and nonnegative quadratic erasure response.
& \(\Lzero/\Lone\)\\
\addlinespace
Primitive plane
& Exact divisor and affine-ray parametrization of the first cross-key
  coefficient.
& \(\Lzero/\Lone\)\\
\addlinespace
Variation certificate
& Exact diagonal divisor lift, two-dimensional Abel formula, tail bound,
  and smooth-kernel cancellation.
& \(\Lzero/\Lone\)\\
\bottomrule
\end{longtable}

\subsection{Mechanisms closed by obstruction}

\begin{enumerate}[label=\textup{(F\arabic*)},leftmargin=3.5em]
 \item \textbf{Inherited single band.}
       The old freezing certificate misses the critical face, and its
       retuning already exceeds \(1/400\).
 \item \textbf{Label-count dilution.}
       \(O(\log X)\) labels give bookkeeping economy, not a lower bound after
       coherent erasure.
 \item \textbf{Capacity transport.}
       Row capacity does not imply spectral capacity without a reducing or
       basis-transport theorem.
 \item \textbf{Support-only Gram closure.}
       Low pair codegree does not control \(\gamma\)-multiplicity, energy
       diffuseness, or cycle holonomy.
 \item \textbf{Same-residual randomness.}
       Its target sign is a removable row gauge on closed walks.
 \item \textbf{One-key mixed cancellation.}
       \(\tr(E_iR_i^a)=0\) identically.
 \item \textbf{Negative quadratic correction.}
       The full \(S_{2q,2}\) is nonnegative.
 \item \textbf{Prime-ray M\"obius oscillation.}
       The primitive sign is constant along the affine ray parameter.
 \item \textbf{Bounded-amplitude variation.}
       Hard sign-selected masks show that \(\|K\|_\infty\) alone does not
       control the primitive-plane sum.
 \item \textbf{Four-corner-to-entry promotion.}
       An anchored primitive-plane target contributes to \(\tr(ER)\); it is
       not a matrix entry of \(E\), and cannot be inserted directly into a
       pair, star, or Perron operator certificate.
\end{enumerate}

Each failure is local to the named mechanism.  None is evidence that the
twin-prime conjecture is false.

\subsection{Open doors}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.22\textwidth}
                  >{\raggedright\arraybackslash}p{0.49\textwidth}
                  >{\raggedright\arraybackslash}p{0.18\textwidth}}
\toprule
Door & Required theorem & Current status\\
\midrule
\endfirsthead
\toprule
Door & Required theorem & Current status\\
\midrule
\endhead
Terminal activation
& \eqref{eq:tpc72-uniform-activation-target} or the exact distinguished
  capacity target in the same downstream scope.
& Open \(\Ltwo\)\\
\addlinespace
Represented frame
& Physical unlabelled Gram lower bound, for example an endpoint-quality
  worst-component determinant mass.
& Open \(\Ltwo\)\\
\addlinespace
Primitive variation
& Mass-normalized mixed variation and diagonal tail for the actual
  aggregated kernel \(\cK_{\mathfrak a}^{\circ}(u,v)\).
& Open \(\Ltwo\)\\
\addlinespace
Anchored mixed trace
& Mass-normalized variation and tail, followed by the complete sum over
  divisors, anchors, row pairs, keys, and blocks in
  \eqref{eq:tpc72-correct-trace-majorant}.
& Open \(\Ltwo\)\\
\addlinespace
Operator carrier
& A direct two-corner representation of \(E_{mn}\), row-local anchored
  bounds dominating the relevant stars, or complete decorated-moment
  estimates for the full missing-native operator.
& Open \(\Ltwo\)\\
\addlinespace
Missing mass
& \eqref{eq:tpc72-missing-mass} in the same reference form as the
  represented lower bound.
& Open \(\Ltwo\)\\
\addlinespace
Nuisance shorting
& \(\|C_N\|=o(1)\), or an explicitly charged nonzero loss.
& Open \(\Ltwo\)\\
\addlinespace
Boundary and tail
& Reconnection of the certified physical packet to the endpoint target,
  with all remaining losses recorded.
& Open \(\Ltwo\)\\
\bottomrule
\end{longtable}

\begin{theorem}[No completed arithmetic column]
\label{thm:no-L2-column}
No theorem among TPC--63--TPC--71 proves one of the open doors above with
all six physical invariants of \cref{sec:audit-rules} and simultaneously
closes the endpoint chain.
\end{theorem}

\begin{proof}
TPC--63--TPC--65 explicitly leave activation and unlabelled representation
open.  TPC--66 proves support codegree but not a Gram gap.  TPC--67 leaves
actual determinant mass open.  TPC--68--TPC--69 state their pair, star,
walk, missing-mass, and nuisance premises conditionally.  TPC--70 gives an
exact reindexing without cancellation.  TPC--71 proves regular-kernel
cancellation but explicitly leaves physical mass-normalized variation,
tail, and complete anchor summation open.  Its four-corner scalar target
cannot be used as an entrywise operator majorant by
\cref{prop:four-corners-not-entry}.  Thus no audited theorem satisfies the
stated conjunction.
\end{proof}
