\section{The strict endpoint ledger}
\label{sec:endpoint-ledger}

\subsection{One global accounting}

The complete inherited fixed-power loss is
\begin{equation}
 \boxed{
 \begin{aligned}
 \Lambda_{\rm tot}:={}&
 \lambda_{\rm sel}
 +\lambda_{\rm occ}
 +\lambda_{\rm blk}
 +\lambda_{\rm term}^{\rm eff}
 +\lambda_{\rm sing}\\
 &+\lambda_H+\lambda_{\rm aff}
 +\lambda_{\rm reasm}
 +\lambda_{\rm bdry}
 +\lambda_{\rm tail}.
 \end{aligned}}
 \label{eq:tpc72-global-ledger}
\end{equation}
Every symbol in \eqref{eq:tpc72-global-ledger} denotes the nonnegative
optimal fixed-power loss of one distinct physical comparison in the
declared scope; it is \(+\infty\) when a mandatory comparison constant
vanishes infinitely often.  The dictionary is:
\begin{description}[leftmargin=3.4em,style=nextline]
 \item[\(\lambda_{\rm sel}\)]
       canonical selection from the parent input energy;
 \item[\(\lambda_{\rm occ}\)]
       retention of the required occupied or activated support;
 \item[\(\lambda_{\rm blk}\)]
       localization to the actual compatible block or component;
 \item[\(\lambda_{\rm term}^{\rm eff}\)]
       true terminal activation;
 \item[\(\lambda_{\rm sing}\)]
       the weighted singleton-occupancy comparison;
 \item[\(\lambda_H\)]
       native residual-label erasure on the represented image;
 \item[\(\lambda_{\rm aff}\)]
       base--represented-high affine transversality;
 \item[\(\lambda_{\rm reasm}\)]
       physical label erasure and shorted reassembly;
 \item[\(\lambda_{\rm bdry},\lambda_{\rm tail}\)]
       final boundary restriction and tail reconstruction.
\end{description}
The endpoint gate is
\begin{equation}
 \boxed{\Lambda_{\rm tot}<\frac1{400}.}
 \label{eq:tpc72-strict-budget}
\end{equation}
Equality is not accepted by the exponent-only route.

The terminal loss satisfies
\begin{equation}
 \lambda_{\rm term}^{\rm eff}
 \le
 \min\{
 \lambda_{\rm term}^{\rm lit}+\lambda_{\rm infl},
 \lambda_{\rm cap}
 \},
 \label{eq:tpc72-terminal-loss}
\end{equation}
when the two TPC--64 certificates are available.  No equality is asserted;
a direct terminal theorem can be better.  The two certificates in the
minimum must hold in the same declared coefficient and quantifier scope.

\subsection{Coarse and fine notations}

TPC--65 compresses part of the chain to
\begin{equation}
 \Gamma_X\ge\tau_X\beta_X\delta_X,
 \qquad
 \Gamma_X
 \ge
 X^{-(\lambda_{\rm act}+\lambda_{\rm rep}
       +\lambda_{\rm reasm})+o(1)}.
 \label{eq:tpc72-coarse-ledger}
\end{equation}
This is not an additional loss on top of
\eqref{eq:tpc72-global-ledger}.  It is a coarser grouping of some of its
arrows.  Here \(\lambda_{\rm act}\) is the aggregate of the distinct
selection, occupancy, block, terminal, and singleton arrows actually used
on the activation side; \(\lambda_{\rm rep}\) is the represented lower
comparison; and \(\lambda_{\rm reasm}\) is the physical shorted-reassembly
arrow.  The represented comparison equals or is bounded using
\(\lambda_H+\lambda_{\rm aff}\) only when those are the same physical
arrows in the same scope.  In particular:
\begin{itemize}
 \item parent inflation belongs to activation;
 \item a represented exponent belongs to the represented arrow once;
 \item physical label erasure and missing-native perturbation belong to
       reassembly;
 \item exact coordinate relabeling costs zero only when it is unitary or
       has \(X^{o(1)}\) condition number.
\end{itemize}
Two inherited no-double-charge rules are especially easy to violate.
If selection, occupancy, or block losses were already used inside a direct
terminal ratio \(T/\widetilde P\), they are removed from the pre-terminal
sum.  If the represented comparison \(\lambda_{\rm rep}\) merely
repackages the physical arrow already encoded by
\(\lambda_H+\lambda_{\rm aff}\), it is not charged again through
\(\lambda_{\rm reasm}\).

\subsection{Mass-degree feasibility is not a second ledger}

Let \(A_X\) and \(M_X\) be the represented and missing-native maps on the
same raw physical coefficient space \(\cK_X\).  With missing atoms
\(\mathcal W_M\), define
\begin{equation}
 W_M(m)
 :=
 \sum_{\substack{w\in\mathcal W_M\\m(w)=m}}|\beta_w|^2,
 \qquad
 D_M:=\operatorname{diag}(W_M(m)),
 \qquad
 S_M:=\operatorname{Ran}D_M.
 \label{eq:tpc72-physical-missing-diagonal}
\end{equation}
Thus \(D_M\) uses raw physical atomic mass.  The missing-native synthesis
\(M_X\) is built from the same atoms, so, with \(P_{S_M}\) the orthogonal
projection onto \(S_M\),
\begin{equation}
 M_X(I-P_{S_M})=0.
 \label{eq:tpc72-missing-kernel-compatibility}
\end{equation}
If \(S_M\ne\{0\}\), set
\begin{equation}
 \kappa_M
 :=
 \sup_{\substack{z\in\cK_X\\
                 \langle D_Mz,z\rangle>0}}
 \frac{\|M_Xz\|^2}{\langle D_Mz,z\rangle}
 =
 \left\|
 M_XD_M^{\dagger/2}\big|_{S_M}
 \right\|^2;
 \label{eq:tpc72-kappa-Rayleigh}
\end{equation}
set \(\kappa_M=0\) when the missing carrier is empty.  In particular,
\begin{equation}
 \|M_Xz\|^2
 \le
 \kappa_M\langle D_Mz,z\rangle.
 \label{eq:tpc72-Rayleigh-domination}
\end{equation}
This is the restricted physical Rayleigh constant, not an ambient degree,
\(\|M_X\|^2\), or a quotient for a vector selected after the estimate.

Let \(\cD_{\rm ref}\) be one nonnegative reference form.  Fix either the
uniform represented scope \(z\in(\ker A_X)^\perp\) or one predeclared
distinguished vector.  In the distinguished case one may use the
corresponding fixed-vector Rayleigh quotient, but it must not be reported
as the uniform \(\kappa_M\).  Suppose, throughout the chosen scope,
\begin{align}
 \kappa_M
 &\le X^{\nu_M+o(1)},
 \label{eq:tpc72-native-exponent}\\
 \langle D_Mz,z\rangle
 &\le
 X^{-\sigma_M+o(1)}\cD_{\rm ref}(z),
 \label{eq:tpc72-missing-mass}\\
 \|A_Xz\|^2
 &\ge
 X^{-\lambda_{\rm rep}+o(1)}\cD_{\rm ref}(z).
 \label{eq:tpc72-represented-comparison}
\end{align}
Then
\begin{equation}
 \frac{\|M_Xz\|^2}{\|A_Xz\|^2}
 \le
 X^{\nu_M+\lambda_{\rm rep}-\sigma_M+o(1)}
 \label{eq:tpc72-relative-missing}
\end{equation}
 whenever \(A_Xz\ne0\).  Thus
\begin{equation}
 \boxed{\sigma_M>\nu_M+\lambda_{\rm rep}}
 \label{eq:tpc72-zero-cost-reassembly}
\end{equation}
makes the missing perturbation \(o(1)\).

When \eqref{eq:tpc72-native-exponent}--%
\eqref{eq:tpc72-represented-comparison} are used only to prove
\eqref{eq:tpc72-zero-cost-reassembly}, their exponents are diagnostic inputs
to \(\lambda_{\rm reasm}\); they are not added a second time to
\eqref{eq:tpc72-global-ledger}.  If the comparison gives a genuine nonzero
loss instead, that resulting physical loss is charged once.

The nuisance condition
\begin{equation}
 \|C_N\|=o(1)
 \label{eq:tpc72-nuisance-small}
\end{equation}
remains separate.

\begin{proposition}[No-double-charge law]
\label{prop:no-double-charge}
Choose one decomposition of the actual physical chain into composable
arrows.  Algebraic identities and isometric or \(X^{o(1)}\)-conditioned
relabelings cost zero.  The fixed-power loss of each non-isometric physical
arrow is entered exactly once.  Any refined exponents used only to certify
one arrow are not added again.
\end{proposition}

\begin{proof}
Successive lower comparisons multiply, so their logarithmic losses add.
Factoring one arrow internally and then adding both its internal losses and
its already-derived external loss counts the same ratio twice.  Conversely,
omitting a distinct non-isometric arrow removes a necessary comparison.
This proves the stated accounting rule.
\end{proof}

\subsection{Current endpoint status}

The algebraic identities and isometric or subpower-conditioned relabelings
in TPC--63--TPC--71 cost zero.  Their non-isometric physical comparisons,
including parent inflation when used, must be charged once.  The block does
not assign endpoint-quality values simultaneously to
\(\lambda_{\rm term}^{\rm eff}\), \(\lambda_{\rm rep}\),
\(\nu_M,\sigma_M\), the nuisance term, and the downstream boundary and tail.
Therefore \eqref{eq:tpc72-strict-budget} has not been verified.
