\section{Introduction}
\label{sec:introduction}

A long proof program can accumulate exact lemmas while losing track of the
quantifier needed at its endpoint.  This danger is particularly acute in a
fixed-shift parity problem.  A theorem for an abstract sign matrix, a fixed
row pair, an averaged shift, or a smoothed coefficient family can be correct
without estimating the literal growing operator.  Likewise, an exact
coordinate identity can remove a modeling ambiguity without producing any
arithmetic saving.

TPC--63 through TPC--71 were designed to separate these roles
\citep{WangTPC63,WangTPC64,WangTPC65,WangTPC66,WangTPC67,WangTPC68,WangTPC69,WangTPC70,WangTPC71}.
They form two chains.  The first follows the represented packet:
\[
\text{provenance}
\longrightarrow
\text{activation}
\longrightarrow
\text{represented Gram}
\longrightarrow
\text{collision geometry}
\longrightarrow
\text{determinant mass}.
\]
The second begins with the complete missing-native packet and then follows
one mixed scalar sector:
\[
\begin{aligned}
\text{signed native operator}
&\longrightarrow
\text{first mixed trace}
\longrightarrow
\text{primitive cofactor plane}\\
&\longrightarrow
\text{two-dimensional variation}.
\end{aligned}
\]
The represented branch and the complete missing-native operator meet only
at physical reassembly.  The descendant primitive-plane chain does not
itself return from a scalar trace sector to the missing-native operator.
A result on one branch does not silently supply a missing hypothesis on
the other.

\subsection{Why the present audit is necessary}

Three developments make a route audit timely.

First, TPC--63 proves that the inherited single-band freezing certificate
cannot reach the critical high face within the endpoint budget
\citep{WangTPC63}.  The failure concerns a proof mechanism, not the actual
weighted mass.  Second, TPC--66 gives a genuine fixed-shift arithmetic
support theorem: the reduced codegree of every fixed row pair is subpower
on the critical block \citep{WangTPC66}.  Yet TPC--67 shows why pair
sparsity is not a represented lower-frame theorem: long cores and phase
holonomy remain \citep{WangTPC67}.  Third, TPC--68--TPC--71 progressively
remove false sources of M\"obius randomness.  Same-residual signs freeze,
one-key mixed traces vanish, the complete quadratic erasure response is
nonnegative, and the surviving primitive sign is constant along each
prime ray \citep{WangTPC68,WangTPC69,WangTPC70}.  TPC--71 nevertheless
opens a new positive door: regular primitive-plane kernels cancel by an
exact divisor lift and two-dimensional Abel summation
\citep{WangTPC71}.

There is also a necessary type boundary.  The primitive-plane object inherited
from TPC--70 contains one erasure edge and one same-residual anchor.  It is
therefore a four-corner contribution to \(\tr(ER)\), whereas an entry of
\(E\) is a two-corner sum.  Treating the former as an entrywise majorant for
the latter changes the mathematical object, loses the anchor index, and
can apply the row normalization twice.  TPC--71 correctly retains the
anchored trace target.  The present audit promotes that boundary to an
explicit non-substitution law: the direct primitive-plane-to-star/Perron
promotion is unavailable.

These are real advances, but of different logical types.  The present paper
classifies them before a local improvement is mistaken for an endpoint
theorem.

\subsection{Main conclusions}

The audit has seven conclusions.
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item TPC--63--TPC--71 close a sequence of necessary \(\Lzero/\Lone\)
       interfaces.  No paper in the block proves a complete \(\Ltwo\)
       cancellation estimate.
 \item The represented and missing-native branches are logically
       independent until shorted reassembly.  Determinant mass does not
       bound the missing-native defect, and primitive-plane cancellation
       does not prove a represented lower frame.
 \item Several routes are permanently closed: the inherited single-band
       support certificate, same-residual M\"obius randomness, the one-key
       mixed trace, and a negative quadratic erasure correction.
 \item TPC--71 proves cancellation relative to ambient area for regular
       kernels.  The physical denominator is actual atomic mass, so the
       mass-normalized mixed variation and diagonal tail are new
       hypotheses, not corollaries.
 \item The primitive-plane target is an anchored contribution to
       \(\tr(ER)\), not an entry of \(E\).  A separate direct two-corner
       representation, row-local anchored-star bridge, or complete-moment
       argument is required before an operator theorem can be invoked.
 \item Algebraic identities and isometric or subpower-conditioned
       relabelings cost zero fixed power.  Every non-isometric physical
       comparison must be charged once in a common ledger strictly below
       \(1/400\).
 \item The next routes have explicit success and failure tests.  One route
       controls the literal anchored primitive-plane kernel strongly enough
       to bound the complete first mixed trace.  The other constructs a
       genuine operator-level carrier through direct entries, row-local
       anchored stars, or complete moments.  A global-trace estimate alone
       is insufficient.
\end{enumerate}

\subsection{Organization}

\Cref{sec:audit-rules} defines the audit levels and physical invariants.
\Cref{sec:provenance-activation,sec:represented-support,sec:native-mixed}
audit TPC--63--TPC--69.
\Cref{sec:primitive-frontier} records the TPC--70--TPC--71 frontier.
\Cref{sec:dependency-graph} proves the dependency theorem.
\Cref{sec:endpoint-ledger} reconciles exponent bookkeeping.
\Cref{sec:closed-open,sec:kill-criteria} separate closed doors from local
certificate failures.  The revised route and final claim ledger appear in
\cref{sec:revised-routes,sec:claim-ledger}.
