\section{Kill criteria and their logical strength}
\label{sec:kill-criteria}

\subsection{Object and quantifier stops}

\begin{enumerate}[label=\textup{(K\arabic*)},leftmargin=3.6em]
 \item \textbf{Wrong object.}
       Removing side, external block, opposite row, \(\gamma\), physical
       time, or another still-orthogonal native label estimates a different
       operator.
 \item \textbf{Wrong support.}
       Replacing actual active support by a terminal image, reduced cell, or
       coefficient-dependent subset changes the carrier.
 \item \textbf{Wrong norm.}
       Fiber-normalized atoms cannot replace raw atomic normalization.
 \item \textbf{Wrong quantifier.}
       A fixed row pair, density-one family, averaged shift, smoothed family,
       or partition chosen after the coefficient vector is known does not
       prove the uniform fixed-\(h_0\) statement.
 \item \textbf{Wrong denominator.}
       A lower bound relative to ambient area, a repaired parent, or a
       labelled norm cannot be inserted relative to physical mass without
       an exact comparison.
\end{enumerate}
These failures invalidate the proposed proof or promotion.  They are not
evidence that the underlying physical quantity is large or that every
route to it fails.

\subsection{Hard structural stops}

\begin{enumerate}[label=\textup{(H\arabic*)},leftmargin=3.6em]
 \item If a required row has \(T_m=0<\widetilde P_m\), the uniform terminal
       activation route is dead on any class containing that row.
 \item If the represented map restricted to the declared activated domain
       or quotient has a kernel, its uniform lower-frame constant there is
       zero.  A kernel outside that domain is irrelevant, and a
       distinguished vector remains a different question.
 \item If a full-output collision component has genuine rank deficiency,
       its determinant mass is zero.
 \item If the actual shorted Gram has a kernel, uniform reassembly through
       the declared architecture is impossible.
 \item If the complete physical loss is at least \(1/400\), including
       equality, the present exponent-only endpoint implication stops.  A
       different constant-sensitive theorem would be a new argument.
\end{enumerate}

\subsection{Certificate-local stops}

The next failures are weaker.
\begin{enumerate}[label=\textup{(C\arabic*)},leftmargin=3.6em]
 \item A pair majorant with \(\tau<\delta\) fails to produce a subpower
       pair/Perron bound by that certificate.  The positive exponent
       \(\delta-\tau\) may still be absorbed by
       \eqref{eq:tpc72-zero-cost-reassembly}, and a later star or moment
       route remains open.
 \item A star saving with \(\sigma<\delta/2\) fails to produce a subpower
       direct-star bound.  The exponent \(\delta/2-\sigma\) may still be
       compatible with the mass-degree gate, and complete walks remain
       open.
 \item Failure at one moment length does not kill other lengths; a
       fixed-\(q\) estimate with uncontrolled constants does not prove a
       growing-\(q\) theorem.
 \item Matching activity at least one kills the phase-uniform dominant
       matching certificate, not necessarily the minor.
 \item A superpolynomially small product over many orthogonal components
       does not kill the represented gap.  The relevant obstruction is the
       actual worst component.
 \item Large mixed variation kills the TPC--71 Abel certificate at the
       required scale, not necessarily the literal signed sum.
 \item A large diagonal tail for one cutoff \(D\) kills that truncation
       choice; it does not rule out a different exact decomposition.
 \item If
       \(\sigma_M\le\nu_M+\lambda_{\rm rep}\), the phase-blind mass-degree
       certificate does not prove a small perturbation in that scope.  It
       does not prove that the actual missing perturbation is large.
 \item Infinite parent inflation or new-only parent rows kill the
       literal-to-repaired inflation transfer.  A direct capacity or
       literal-hypergraph activation route can remain; the hard uniform
       stop is \(T_m=0<\widetilde P_m\) on a required row.
 \item Small global \(\tr(ER)\) does not certify any uniform local star.
 \item Small anchored four-corner targets do not bound the two-corner
       entries of \(E\); using them as such is a wrong-object failure, not
       an insufficient exponent.
\end{enumerate}

\subsection{Primitive-plane route stops}

The current narrow route has five specific tests.
\begin{enumerate}[label=\textup{(P\arabic*)},leftmargin=3.6em]
 \item The complete divisor and native-key census must have only controlled
       multiplicity.  Compressing keys before the census is forbidden.
 \item The zero-extended mixed variation must include every interior, edge,
       and corner jump.  Omitting boundary jumps invalidates the Abel
       identity.
 \item The exact tail \(\cT_D(K)\) must be small relative to actual mass.
       Failure of the ambient specialization
       \(\|K\|_\infty UV/D\) kills only that ambient majorant, not the exact
       support tail or another decomposition.
 \item The anchor bounds must survive the complete sum in
       \eqref{eq:tpc72-correct-trace-majorant}.  Even if they do, the output
       is a mixed-trace theorem, not an operator theorem.  Failure after
       anchorwise triangle summation kills that aggregation; it does not
       exclude cancellation across anchors or a complete-moment route.
 \item The four-corner normalization \(1/(W_mW_n)\) must be retained
       literally and charged once.  A further division by
       \(\sqrt{W_mW_n}\) changes the scale.
\end{enumerate}
Tests P1, P2, and P5 validate the object and identity; violating them changes
the theorem rather than proving a negative result.  P3 and P4 are
certificate-local quantitative gates.

\begin{proposition}[Meaning of a route obstruction]
\label{prop:route-obstruction}
A sharp obstruction or non-implication theorem for the actual declared
certificate is a publishable negative theorem about that proof mechanism.
Mere failure to prove a sufficient estimate is an unresolved gate.  Neither
statement is a parity theorem or has any implication for the truth of a
prime-pair conjecture.
\end{proposition}

\begin{proof}
Each certificate uses a sufficient inequality obtained by discarding some
literal information.  Failure to establish it does not imply failure of the
underlying quantity.  A genuine negative result requires a lower
obstruction, an exact type mismatch, or an extremal theorem proving
necessity.  The audited papers supply countermodels separating these
implications.
\end{proof}
