\section{TPC--68--TPC--69: signed native operators and mixed words}
\label{sec:native-mixed}

\subsection{TPC--68: the complete missing-native defect}

TPC--68 retains every missing-active row and every still-orthogonal native
label \citep{WangTPC68}.  Physical atomic normalization gives
\begin{equation}
 K_M=I+H,
 \qquad
 H=H^*,
 \qquad
 H_{mm}=0.
 \label{eq:tpc72-native-gram}
\end{equation}
The residual split is
\[
 H=R+E,
\]
where \(R\) contains same-residual collisions and \(E\) contains
unequal-residual erasure edges.

After a unitary row gauge, a literal off-diagonal entry exposes target signs
\[
 \mu(mj+h_0)\mu(nj+h_0).
\]
On a same-residual collision this product reduces to a row gauge
\(\mu(d_m)\mu(d_n)\).  Every pure \(R\)-closed walk therefore has target-sign
product one.  New signed information must use an \(E\)-edge or a literal
complex phase.

TPC--68 proves exact pair, star, Perron, and even-walk certificates.  If
\(\Delta_P\le X^{\delta+o(1)}\) and each pair majorant is at most
\(X^{-\tau+o(1)}\), then
\begin{equation}
 \|H\|\le X^{\delta-\tau+o(1)}.
 \label{eq:tpc72-pair-route}
\end{equation}
If instead the maximal \(\ell^2\)-star is
\(X^{-\sigma+o(1)}\), then
\begin{equation}
 \|H\|\le X^{\delta/2-\sigma+o(1)}.
 \label{eq:tpc72-star-route}
\end{equation}
For a growing even moment,
\begin{equation}
 \tr H^{2q_X}
 \le
 X^{2q_X\nu+o(q_X\log X)}
 \quad\Longrightarrow\quad
 \|H\|\le X^{\nu+o(1)}.
 \label{eq:tpc72-walk-route}
\end{equation}
The displayed premises are \(\Ltwo\) targets and are not proved there.

\subsection{TPC--69: the first exact cross-key holonomy}

TPC--69 refines the split by complete native key:
\begin{equation}
 R=\sum_iR_i,
 \qquad
 E=\sum_iE_i.
 \label{eq:tpc72-key-decomposition}
\end{equation}
Relative to the residual partition of key \(i\), \(R_i\) is block diagonal
and \(E_i\) is off block.  Hence, for every polynomial \(P\),
\begin{equation}
 \tr(E_iP(R_i))=0.
 \label{eq:tpc72-one-key-vanishing}
\end{equation}
The first mixed half-sector is therefore necessarily cross-key:
\begin{equation}
 S_{2,1}=2\tr(ER),
 \qquad
 \tr(ER)=\sum_{i\ne j}\tr(E_iR_j).
 \label{eq:tpc72-cross-key-first}
\end{equation}
Each term is a genuine four-corner rectangle, invariant under independent
row and key unit gauges.

For
\[
 \tr(R+tE)^k=\sum_{b=0}^kt^bS_{k,b},
\]
the exact cyclic sector formula is
\begin{equation}
 S_{k,b}
 =
 \frac{k}{b}
 \sum_{\substack{a_1+\cdots+a_b=k-b\\a_\ell\ge0}}
 \tr(ER^{a_1}\cdots ER^{a_b}).
 \label{eq:tpc72-cyclic-sector}
\end{equation}
On the squarefree physical carrier, source-row signs telescope around a
closed decorated walk.  The surviving target sign is the product of
\(\mu(s)\) over residual labels of odd erasure degree.

The complete two-erasure sector has a further obstruction.  If
\(\lambda_\alpha\) are the eigenvalues of \(R\), then
\begin{equation}
 S_{2q,2}
 =
 q\sum_{\alpha,\beta}
 |E_{\alpha\beta}|^2
 \frac{\lambda_\alpha^{2q-1}-\lambda_\beta^{2q-1}}
      {\lambda_\alpha-\lambda_\beta}
 \ge0,
 \label{eq:tpc72-quadratic-positive}
\end{equation}
with the derivative value on the diagonal.  The inequality follows because
the odd power \(x^{2q-1}\) is increasing.

\begin{corollary}[Signed-door reduction]
\label{cor:signed-door-reduction}
The following proposed sources of negative compensation are closed:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item M\"obius randomness internal to pure same-residual walks;
 \item one-key cancellation in the first mixed sector; and
 \item the complete quadratic erasure sector as a negative correction.
\end{enumerate}
The shortest remaining signed object is the cross-key rectangle in
\eqref{eq:tpc72-cross-key-first}.
\end{corollary}

\begin{proof}
The first statement follows from row-gauge telescoping; the second from
\eqref{eq:tpc72-one-key-vanishing}; the third from
\eqref{eq:tpc72-quadratic-positive}.
\end{proof}

A small global \(\tr(ER)\) is not a row-star estimate.  Even a complete
linear-sector saving does not bound the full moment unless all remaining
sectors are controlled at the correct scale.
