\section{TPC--70--TPC--71: the primitive-plane frontier}
\label{sec:primitive-frontier}

\subsection{TPC--70: exact cofactor coordinates}

Fix distinct physical rows \(m,n\), one nonzero shift \(h_0\) satisfying
\((mn,h_0)=1\), and one full same-residual anchor \(\mathfrak a\).  Put
\begin{equation}
 H=h_0(n-m).
 \label{eq:tpc72-H}
\end{equation}
At a same-residual anchor, TPC--70 writes
\begin{equation}
 d_m=ga,\qquad d_n=gb,\qquad(a,b)=1.
 \label{eq:tpc72-anchor-primitive}
\end{equation}
Equality of residuals forces the complementary cofactors to have the form
\begin{equation}
 R_m=bt,\qquad R_n=at,\qquad t\mid |H|.
 \label{eq:tpc72-anchor-cofactors}
\end{equation}
For fixed data, the anchor times lie on an affine ray
\begin{equation}
 j_R=j_{R,0}+abt\,z.
 \label{eq:tpc72-anchor-ray}
\end{equation}

At an erasure edge, write
\begin{equation}
 S_m=qu,\qquad S_n=qv,\qquad(u,v)=1.
 \label{eq:tpc72-erasure-primitive}
\end{equation}
The determinant relation forces \(q\mid |H|\), and admissible erasure times
lie on
\begin{equation}
 j_E=j_{E,0}+quv\,z.
 \label{eq:tpc72-erasure-ray}
\end{equation}
The erased residuals are unequal exactly when
\begin{equation}
 (u,v)\ne(b,a).
 \label{eq:tpc72-excluded-anchor}
\end{equation}

On the squarefree physical carrier, the four-corner target sign collapses
to
\begin{equation}
 \mu(d_mS_m)\mu(d_nS_n)
 =
 \mu(a)\mu(b)\mu(u)\mu(v).
 \label{eq:tpc72-primitive-sign}
\end{equation}
The common contents \(g\) and \(q\) disappear.  More importantly,
\eqref{eq:tpc72-primitive-sign} is constant in the affine parameter \(z\).
The prime ray contributes masks, endpoints, native constraints, and complex
amplitudes, but no new M\"obius oscillation.

Let \(\cK_{\mathfrak a,q}(u,v)\) be the complete ray sum for the fixed full
anchor \(\mathfrak a\), with every physical
coefficient and native label retained and with absent rays assigned zero.
Aggregate the divisor slices before taking absolute values and impose the
literal unequal-residual condition by setting
\begin{equation}
 \cK_{\mathfrak a}^{\circ}(u,v)
 :=
 \one_{(u,v)\ne(b,a)}
 \sum_{q\mid |H|}\cK_{\mathfrak a,q}(u,v).
 \label{eq:tpc72-aggregate-erasure-kernel}
\end{equation}
The literal contribution of that anchor is exactly
\begin{equation}
 \mathfrak X_{\mathfrak a}
 =
 \mu(a)\mu(b)
 \sum_{\substack{u,v\ge1\\(u,v)=1}}
 \mu(u)\mu(v)\cK_{\mathfrak a}^{\circ}(u,v).
 \label{eq:tpc72-physical-plane}
\end{equation}
The complete \(\tr(ER)\) is obtained only after summing these anchored
contributions over the actual rows and full same-residual anchors.
The divisor sum should be aggregated before absolute values whenever the
literal phases allow it.

\subsection{The physical type check}

Write
\[
 \alpha_{\iota,m}
 =
 \frac{\beta_{\iota,m}}{\sqrt{W_m}}
\]
for the complete signed and phased coefficient of native key \(\iota\) in
row \(m\), including atomic normalization.  An off-diagonal erasure entry
is the two-corner object
\begin{equation}
 E_{mn}
 =
 \sum_{\iota_E}
 \overline{\alpha_{\iota_E,m}}\alpha_{\iota_E,n},
 \label{eq:tpc72-two-corner-entry}
\end{equation}
with the unequal-residual restriction understood.  By contrast, fixing a
same-residual anchor \(\mathfrak a=\iota_R\) gives the four-corner scalar
\begin{equation}
 \mathfrak X_{\mathfrak a}
 =
 \sum_{\iota_E}
 \overline{\alpha_{\iota_E,m}}\alpha_{\iota_E,n}
 \overline{\alpha_{\iota_R,n}}\alpha_{\iota_R,m},
 \label{eq:tpc72-four-corner-scalar}
\end{equation}
which is the literal quantity parametrized in
\eqref{eq:tpc72-physical-plane}.  Hence
\begin{equation}
 \tr(ER)
 =
 2\Re
 \sum_{m<n}
 \sum_{\mathfrak a\in\mathcal R_{m,n}}
 \mathfrak X_{\mathfrak a}.
 \label{eq:tpc72-anchored-trace}
\end{equation}
In terms of the unnormalized coefficients \(\beta\), the four-corner
amplitude in \eqref{eq:tpc72-four-corner-scalar} already contains
\(1/(W_mW_n)\).

\begin{proposition}[Four corners are not an erasure entry]
\label{prop:four-corners-not-entry}
Suppose
\(
 |\mathfrak X_{\mathfrak a}|
 \le \mathcal B_{\mathfrak a}
\)
for every literal anchor.  Then
\begin{equation}
 |\tr(ER)|
 \le
 2\sum_{m<n}
 \sum_{\mathfrak a\in\mathcal R_{m,n}}
 \mathcal B_{\mathfrak a}.
 \label{eq:tpc72-correct-trace-majorant}
\end{equation}
This premise alone implies no entrywise bound for \(E_{mn}\), no row-star
bound, and no Perron or operator-norm bound for \(E\).  Dividing
\(\mathcal B_{\mathfrak a}\) again by \(\sqrt{W_mW_n}\) is a second,
unjustified normalization.
\end{proposition}

\begin{proof}
Equation \eqref{eq:tpc72-correct-trace-majorant} follows from
\eqref{eq:tpc72-anchored-trace} and the triangle inequality.  The remaining
claims follow already from the abstract example \(R=0\), \(E\ne0\):
every four-corner \(ER\) target vanishes, while \(E\) can have arbitrarily
large norm.  Thus no inequality involving only these targets can dominate
the entries or norm of \(E\).
\end{proof}

\begin{proposition}[No ray-sign door]
\label{prop:no-ray-sign-door}
No cancellation based only on changes of the M\"obius sign along \(z\) can
bound \eqref{eq:tpc72-physical-plane}.
\end{proposition}

\begin{proof}
For fixed \(a,b,q,u,v\), the sign in
\eqref{eq:tpc72-primitive-sign} is independent of \(z\).  Any cancellation
along the ray must therefore come from the literal complex amplitude, not
from a changing M\"obius factor.
\end{proof}

The divisor, determinant, and affine-ray algebra is \(\Lzero\).  Its exact
reindexing of the full native rectangle is \(\Lone\).  No cancellation is
asserted by TPC--70 \citep{WangTPC70}.

\subsection{TPC--71: abstract diagonal lift and two-dimensional Abel summation}

The primitive sign has the elementary but decisive identity
\begin{equation}
 \one_{(u,v)=1}\mu(u)\mu(v)=\mu(uv).
 \label{eq:tpc72-primitive-collapse}
\end{equation}
For a finitely supported kernel \(K\), M\"obius inversion of the
coprimality condition gives the exact diagonal divisor lift
\begin{equation}
 \sum_{\substack{u,v\ge1\\(u,v)=1}}
 \mu(u)\mu(v)K(u,v)
 =
 \sum_{d\ge1}\mu(d)
 \sum_{\substack{a,b\ge1\\(a,d)=(b,d)=1}}
 \mu(a)\mu(b)K(da,db).
 \label{eq:tpc72-diagonal-lift}
\end{equation}
Define the restricted Mertens function
\begin{equation}
 M_d(x)
 :=
 \sum_{\substack{n\le x\\(n,d)=1}}\mu(n).
 \label{eq:tpc72-restricted-Mertens}
\end{equation}
Extend \(K^{[d]}(a,b)=K(da,db)\) by zero outside its finite support, and put
\begin{equation}
 \cV_\square(K^{[d]})
 :=
 \sum_{a,b\ge1}
 |\Delta_1\Delta_2K^{[d]}(a,b)|.
 \label{eq:tpc72-mixed-variation}
\end{equation}
Two-dimensional Abel summation then gives the exact fixed-\(d\) identity
\begin{equation}
 \sum_{\substack{a,b\ge1\\(a,d)=(b,d)=1}}
 \mu(a)\mu(b)K(da,db)
 =
 \sum_{x,y\ge1}
 M_d(x)M_d(y)\Delta_1\Delta_2K^{[d]}(x,y).
 \label{eq:tpc72-double-Abel}
\end{equation}
Zero extension places the edge and corner terms inside the mixed
difference.  Omitting the boundary jumps would give a false certificate.

For
\[
 \mathfrak M_d(X)=\max_{1\le x\le X}|M_d(x)|,
\]
with \(\mathfrak M_d(X)=0\) when \(X<1\), define the exact diagonal tail
\begin{equation}
 \cT_D(K)
 :=
 \sum_{d>D}|\mu(d)|
 \sum_{x,y\ge1}
 |\mu(dx)\mu(dy)K(dx,dy)|.
 \label{eq:tpc72-exact-diagonal-tail}
\end{equation}
Truncation at \(d\le D\) yields
\begin{align}
 \left|
 \sum_{\substack{u\le U,\ v\le V\\(u,v)=1}}
 \mu(u)\mu(v)K(u,v)
 \right|
 \le{}&
 \sum_{d\le D}
 \mathfrak M_d(U/d)\mathfrak M_d(V/d)
 \cV_\square(K^{[d]})
 +\cT_D(K).
 \label{eq:tpc72-master-plane-certificate}
\end{align}
This tail retains the actual support and coefficients.  The ambient
specialization
\begin{equation}
 \cT_D(K)
 \le
 \|K\|_\infty
 \sum_{d>D}
 \left\lfloor\frac Ud\right\rfloor
 \left\lfloor\frac Vd\right\rfloor
 \le
 \|K\|_\infty\frac{UV}{D}
 \label{eq:tpc72-ambient-tail}
\end{equation}
is only an optional upper bound and may be much larger than the exact tail.

For every fixed \(d\), the prime number theorem gives
\begin{equation}
 M_d(x)=o_d(x).
 \label{eq:tpc72-fixed-d-PNT}
\end{equation}
Consequently, a bounded family satisfying
\[
 \cV_\square(K^{[d]})\ll_d\|K\|_\infty
\]
for every fixed \(d\) has
\begin{equation}
 \sum_{\substack{u\le U,\ v\le V\\(u,v)=1}}
 \mu(u)\mu(v)K(u,v)
 =
 o(\|K\|_\infty UV)
 \label{eq:tpc72-smooth-kernel-cancellation}
\end{equation}
as \(\min(U,V)\to\infty\).  In particular, the unweighted primitive
rectangle cancels unconditionally.  This use of prime number theory is
standard; see, for example, \citet{IwaniecKowalski2004}.

\subsection{Why the smooth theorem is not the physical theorem}

The physical denominator is not the ambient area
\(\|K\|_\infty UV\).  It is an actual anchored, trace-sector, or atomic
mass, and the kernel can contain hard prime-line masks.  Therefore the next
physical requirements are:
\begin{enumerate}[label=\textup{(V\arabic*)},leftmargin=3.5em]
 \item a mass-normalized bound for
       \(\cV_\square((\cK_{\mathfrak a}^{\circ})^{[d]})\), after the
       literal \(q\)-aggregation in
       \eqref{eq:tpc72-aggregate-erasure-kernel};
 \item the exact tail
       \(\cT_D(\cK_{\mathfrak a}^{\circ})\) small relative to the same
       physical mass;
 \item justified uniformity in the divisor cutoff and over anchors, blocks,
       rows, and complete keys;
 \item summation over every literal anchor and row pair to control the
       complete \(\tr(ER)\), without losing an unaffordable multiplicity;
       and
 \item for an operator theorem, either a new direct representation of the
       two-corner entries \eqref{eq:tpc72-two-corner-entry}, row-local
       anchored sums that dominate the relevant stars, or a separate
       expansion controlling complete decorated moments.
\end{enumerate}
Sign-selected hard masks show that bounded amplitude alone cannot imply
these conditions.

\begin{theorem}[Primitive-frontier classification]
\label{thm:primitive-frontier}
TPC--70 and TPC--71 close the algebraic reduction from a cross-key rectangle
to \eqref{eq:tpc72-master-plane-certificate} and prove cancellation for
regular kernels.  They do not prove a fixed-power or mass-normalized saving
for the actual physical kernel.  Their physical target is the anchored
mixed scalar \(\mathfrak X_{\mathfrak a}\), so the reduction does not
produce an erasure-entry, star, Perron, or operator certificate.
\end{theorem}

\begin{proof}
The exact reduction is
\eqref{eq:tpc72-physical-plane}--\eqref{eq:tpc72-master-plane-certificate}.
The regular-kernel corollary normalizes by \(\|K\|_\infty UV\).
No audited theorem bounds the actual kernel's mixed variation or tail
relative to the physical mass, nor sums all literal anchors and rows at an
endpoint-quality scale.  Moreover,
\cref{prop:four-corners-not-entry} rules out promotion of that scalar bound
to an entrywise operator majorant without a new representation.  The
missing implications are therefore new quantitative and type-correct
premises, not consequences of the regular-kernel theorem.
\end{proof}
