\section{TPC--63--TPC--64: provenance and true activation}
\label{sec:provenance-activation}

\subsection{TPC--63: the carrier cannot be repaired by declaration}

TPC--63 distinguishes a literal full incidence from its pair projection
\citep{WangTPC63}.  Three faithfulness questions are separate:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item preservation of the pre-terminal raw form;
 \item preservation of terminal atoms; and
 \item preservation of the grouped physical operator.
\end{enumerate}
An active spurious cross can pass one test and fail another.  When a
terminal-faithful pair completion exists, there is a unique least relation;
when it does not, the literal incidence hypergraph is the canonical faithful
object.

Let \(W_H(m)\) be native-high parent mass and \(W_A(m)\) the part aligned
with the terminal predicate.  Inside the aligned mass, let the declared
retained relation supply completion ratio \(c_{\rm comp}(m)\).  TPC--63
proves the exact factorization
\begin{equation}
 \frac{W_{\rm exposed}(m)}{W_H(m)}
 =
 \frac{W_A(m)}{W_H(m)}\,c_{\rm comp}(m)
 \label{eq:tpc72-exposure-factorization}
\end{equation}
whenever \(W_H(m)>0\).  Passing to the maximal eligible relation may make
\(c_{\rm comp}(m)=1\), but it cannot improve the alignment factor.

The same paper proves a negative \(\Lone\) result for the inherited
single-band mechanism.  The balanced band certified by the old freezing
inequality is eventually disjoint from the critical high face.  Retuning
that sufficient inequality to the critical cofactor scale already costs
more than the entire \(1/400\) allowance.  Even after an independently
justified retuning, a completely omitted dyadic block makes the inherited
support-cardinality/Brun--Titchmarsh certificate yield no positive
fixed-power saving.

\begin{proposition}[Scope of the TPC--63 no-go]
\label{prop:tpc63-no-go-scope}
The TPC--63 negative result closes the named single-band support certificate.
It does not imply that the actual omitted weighted mass is large.
\end{proposition}

\begin{proof}
The certificate replaces literal weights by support and harmonic
majorants.  Its failure shows only that those upper data cannot establish
the desired lower ratio.  A coefficient-sensitive weighted distribution
estimate or exact signed shorting uses information absent from that
certificate and is not contradicted.
\end{proof}

Orthogonally retaining all nonempty dyadic labels gives exact raw-energy
coverage at \(O(\log X)\) label complexity.  The later erasure of these
labels is a physical map, not a harmless relabeling.

\subsection{TPC--64: activation, inflation, and capacity}

TPC--64 defines, before the free row coefficient is chosen, the parent mass
\(P_m\), terminal-support mass \(H_m\), and shaped terminal energy \(T_m\)
\citep{WangTPC64}.  On a row where both denominators are nonzero,
\begin{equation}
 \frac{T_m}{P_m}
 =
 \frac{H_m}{P_m}\frac{T_m}{H_m}.
 \label{eq:tpc72-activation-factorization}
\end{equation}
The two factors are terminal-support alignment and terminal multiplier
intensity.

A parent-complete pair lift can add terminal-null coordinates.  Its repaired
parent is
\begin{equation}
 \widetilde P_m=P_m+\Delta_m,
 \qquad
 T_m\ \text{unchanged}.
 \label{eq:tpc72-parent-inflation}
\end{equation}
Thus a pair completion may preserve the numerator while diluting its
denominator by an arbitrary polynomial factor.  A newly created parent row
with \(P_m=0<\widetilde P_m\) makes uniform parent domination infinite.  The
literal-active-hypergraph baseline avoids this inflation exactly.

For \(g_m=T_m/\widetilde P_m\), let \(\delta_\eta\) be the repaired-parent
fraction on rows \(g_m\ge\eta\), and let \(\kappa_X\) measure the occupied
coefficient capacity.  TPC--64 proves the sharp lower certificate
\begin{equation}
 \frac{T(z)}{\widetilde P(z)}
 \ge
 \eta\left(1-\frac{1-\delta_\eta}{\kappa_X}\right)_+.
 \label{eq:tpc72-capacity-certificate}
\end{equation}
The right side is positive exactly when
\(\kappa_X>1-\delta_\eta\).

\subsection{The first unresolved arithmetic arrow}

There are two honest next inputs:
\begin{align}
 T_m
 &\ge
 X^{-\lambda_{\rm row}+o(1)}\widetilde P_m
 \quad\text{for every active row},
 \label{eq:tpc72-uniform-activation-target}\\
 \eta_X\left(
 1-\frac{1-\delta_{\eta_X}}{\kappa_X(z_*)}
 \right)_+
 &\ge
 X^{-\lambda_{\rm term,*}^{\rm eff}+o(1)}
 \quad\text{for one declared }z_*.
 \label{eq:tpc72-distinguished-activation-target}
\end{align}
Neither is proved in TPC--63 or TPC--64.  A row with
\(T_m=0<\widetilde P_m\) kills
\eqref{eq:tpc72-uniform-activation-target} on every coefficient class
containing that row, but it does not kill a separately justified
distinguished scope.

\begin{remark}[Audit classification]
The incidence factorizations, minimax constants, inflation laws, and
capacity extremizers are \(\Lzero\).  Their literal fixed-\(h_0\)
specialization is \(\Lone\).  Establishing either
\eqref{eq:tpc72-uniform-activation-target} or
\eqref{eq:tpc72-distinguished-activation-target} at endpoint strength would
be \(\Ltwo\).
\end{remark}
