\section{TPC--65--TPC--67: represented range, support, and determinants}
\label{sec:represented-support}

\subsection{TPC--65: the actual activated range}

Let \(L_X\) be the terminal map and
\[
 Y_X=\Ran L_X.
\]
TPC--65 places the represented comparison on \(Y_X\), rather than on a free
ambient atom space \citep{WangTPC65}.  If \(A_X:Y_X\to H_X\) is the
represented map, its exact lower constant is
\begin{equation}
 \beta_X
 =
 \inf_{0\ne y\in Y_X}
 \frac{\|A_Xy\|^2}{\|y\|^2}
 =
 \lambda_{\min}(K_X),
 \label{eq:tpc72-represented-gram}
\end{equation}
where \(K_X\) is the normalized activated row Gram with literal
residual-fiber entries.

Terminal-faithful canonical repair leaves downstream Grams unchanged when
both descriptions factor through the same terminal map.  Parent inflation
is therefore charged in the parent-to-terminal arrow, not again in
\(\beta_X\).

For orthogonally labeled blocks \(A_\nu\),
\begin{equation}
 \Ker\!\left(\bigoplus_\nu A_\nu\right)
 =
 \bigcap_\nu\Ker A_\nu.
 \label{eq:tpc72-kernel-fusion}
\end{equation}
Singular blocks can fuse into a positive global Gram.  Coherently erasing
their labels instead creates cross-block terms and requires a separate
fusion-angle theorem.  TPC--65 also gives a sharp counterexample to
transporting physical row capacity into spectral capacity.

On one common carrier, define activation, represented, and reassembly
constants \(\tau_X,\beta_X,\delta_X\).  The exact compatible product is
\begin{equation}
 \Gamma_X\ge\tau_X\beta_X\delta_X.
 \label{eq:tpc72-three-stage-product}
\end{equation}
This is a compatibility law, not a proof that any physical factor is
favorable.

\subsection{TPC--66: actual pair geometry}

TPC--66 opens the literal entries of \(K_X\) \citep{WangTPC66}.  A fixed
physical row contributes at most one terminal atom to a fixed residual
output key.  After row normalization,
\begin{equation}
 (K_X)_{mm}=1
 \label{eq:tpc72-unit-diagonal}
\end{equation}
for every active row.

For distinct literal rows \(m_1,m_2\), factor exchange and simultaneous CRT
give the reduced pair-codegree bound
\begin{equation}
 c^{\rm red}_{m_1,m_2}(R)
 \ll_{h_0}
 X^{o(1)}\left(1+\frac{J}{R}\right).
 \label{eq:tpc72-codegree}
\end{equation}
Consequently,
\begin{equation}
 c^{\rm red}_{m_1,m_2}(R)=X^{o(1)}
 \qquad(R\asymp J)
 \label{eq:tpc72-critical-codegree}
\end{equation}
uniformly over fixed active row pairs.

This is a genuine arithmetic support theorem at one fixed \(h_0\), but its
scope must be retained.  It counts reduced arithmetic cells, not the raw
\(\gamma\)-decorated intersection.  A right fiber may still have polynomial
degree.  The exact bridge
\begin{equation}
 |K_X(m,n)|
 \le
 C_{m,n}^{\rm red}(R)
 \sqrt{\rho_m(R)\rho_n(R)}
 \label{eq:tpc72-codegree-diffuseness}
\end{equation}
shows that a physical Gram estimate still needs row-energy diffuseness.

Private outputs, comparison matrices, weighted diagonal dominance, forest
gauges, star spectra, and unique-matching minors give exact lower-frame
certificates.  A cycle with fixed support, degree, codegree, and entry
magnitudes can nevertheless be singular or nonsingular according to its
holonomy.  Support sparsity alone is therefore not a lower-frame theorem.

\subsection{TPC--67: determinant mass on actual components}

TPC--67 factors every square actual minor by iterative degree-one peeling
\citep{WangTPC67}.  A residual core with no perfect matching has zero
determinant.  Relative to a declared core matching, all remaining terms are
vertex-disjoint alternating-cycle families.  Forest phases gauge away;
cycle holonomies remain.

If \(\cA_\phi\) is the total absolute activity relative to matching
\(\phi\), the phase-safe certificate has the form
\begin{equation}
 |\det T|
 \ge
 P_{\rm for}P_\phi(1-\cA_\phi)_+.
 \label{eq:tpc72-activity-certificate}
\end{equation}
The threshold one is sharp for information consisting only of total
activity.

For a synthesis matrix \(B\) with \(r\) unit columns and Gram \(K=B^*B\),
Cauchy--Binet yields
\begin{equation}
 \mathfrak D(B)
 :=
 \sum_{|I|=r}|\det B[I]|^2
 =
 \det K,
 \qquad
 \lambda_{\min}(K)\ge e^{-1}\mathfrak D(B).
 \label{eq:tpc72-determinant-gap}
\end{equation}
The actual full-support collision components are orthogonal, so the useful
bound is
\begin{equation}
 \beta_X
 \ge
 e^{-1}\min_{C\in\mathscr C_X}\mathfrak D_C,
 \label{eq:tpc72-componentwise-gap}
\end{equation}
not a product over unrelated components.

\begin{proposition}[Represented branch frontier]
\label{prop:represented-frontier}
The represented branch would close at fixed-power scale if one proved,
uniformly over actual full-support components,
\[
 \mathfrak D_C\ge X^{-\lambda_{\det}+o(1)}
\]
with an exponent compatible with the endpoint ledger.  TPC--66 does not
imply this premise.
\end{proposition}

\begin{proof}
\Cref{eq:tpc72-componentwise-gap} gives the implication.  TPC--66 controls
only reduced fixed-pair codegree.  It supplies neither a full-output Hall
matching, pivot lower bounds, long-cycle activity, nor
\(\gamma\)-multiplicity.  Hence its hypotheses do not determine
\(\mathfrak D_C\).
\end{proof}

All determinant conversions are \(\Lzero\), and the full-output
identification is \(\Lone\).  The displayed lower bound for the actual
worst component is an open \(\Ltwo\) target.
