\section{Exact certificate, dependency ledger, and scope}
\label{sec:tpc28-certificate-scope}

The proof has one new finite algebraic identity, one new analytic
full-rectangle theorem, and one exact rational sample.  We separate
these from imported interfaces and from statements that remain open.

\subsection{Exact finite certificate}

The standard-library script
\begin{center}
\texttt{experiments/tpc28\_certificate.py}
\end{center}
uses rational arithmetic and formal prime-log polynomials.  It checks:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the pointwise raw/drift product identity for finite opened rows;
 \item the direct connected double sum and complete-period raw,
 centered, and calibrated zero kernels, including
 \eqref{eq:tpc28-calibrated-zero-identity} and a case with
 $\rad|h|\ne|h|$;
 \item CRT compatibility and primitive complete-period densities for
 full-base divisor pairs, including pairs with one unit divisor;
 \item the two-route minimax lower bound on exact rational grids and
 the equality witnesses on every piece of
 \eqref{eq:tpc28-sharp-minimax};
 \item all rational source, Poisson-overrun, base, drift, and upper
 margins in \cref{tab:tpc28-high-ledger}.
\end{enumerate}
Every assertion uses an exception-based checker, so running Python with
optimization cannot delete a test.  The script writes a deterministic
JSON summary and hashes its normalized source and a canonical payload.
It checks finite algebra and rational bookkeeping only; it is not
numerical evidence for an asymptotic M\"obius or prime-pair claim.
Both ordinary and optimized Python complete $33{,}299$ exact checks
and regenerate byte-identical JSON.  The final hashes are
\begin{itemize}[leftmargin=2.2em]
 \item source SHA-256:
 \nolinkurl{c3ad5c993e1823a4752c5c31ef5e348342982607c078e8bc4343697d5dad9948};
 \item JSON SHA-256:
 \nolinkurl{e75a92e2eb78ce297fa305e5c8ea42eab0a6cec591e3ff989eb5566bd90ab6ec};
 \item certificate digest:
 \nolinkurl{3cb8458021bd05d8b04154137a92a068633944679a038db9c5e4f342dff563a3}.
\end{itemize}

\subsection{Dependency ledger}

\begin{table}[H]
\centering
\caption{Logical status of the ingredients used in TPC-28.}
\label{tab:tpc28-dependencies}
\begin{tabular}{@{}
 >{\raggedright\arraybackslash}p{0.31\textwidth}
 >{\raggedright\arraybackslash}p{0.13\textwidth}
 >{\raggedright\arraybackslash}p{0.46\textwidth}@{}}
\toprule
Ingredient & Status & Role \\
\midrule
Opened-row $\ell^1/\ell^2$ provenance
& Imported
& Gives physical row mass and continuous Mellin transfer; TPC-25.\\
Uniform prefix calibration $D=\delta+E$
& Imported
& Gives arbitrary-logarithmic $E_S(m)$; TPC-20 and TPC-27.\\
Ramanujan-square bound for $K_S^0$
& Imported
& Closes the connected physical zero mode for polynomial $S$; TPC-27.\\
Raw/centered calibrated zero identity
& New here
& Cancels the two $E_SZ_S$ zero legs exactly.\\
Full-base tensor energy and cell bound
& New here
& Extends the joint conductor mechanism to $u,v\le S$ without an annular lower cutoff.\\
Pointwise target-divisor drift bound
& New here
& Restores nonzero scalar legs with the fixed-power $L^{-1}$ factor.\\
Upper annular cutoff stability
& Imported
& Splices the newly closed base $S$ to $T$; TPC-26.\\
High-$\beta$ initial and upper values
& New here
& Closes the selected source-compatible truncated square.\\
\bottomrule
\end{tabular}
\end{table}

The full-base conductor proof uses the classical exact-conductor large
sieve, not an unproved distribution conjecture.  The zero theorem uses
the proved uniform M\"obius calibration and the exact finite
Ramanujan-square factorization.  Thus
\cref{thm:tpc28-base-closure,thm:tpc28-high-upper} require no unproved
conjecture beyond their explicitly stated physical packet hypotheses.

\subsection{Three invalid shortcuts}

The proof also identifies three tempting but invalid replacements:
\begin{enumerate}[label=\textup{(\arabic*)}]
 \item One cannot estimate nonzero $EZ$ by multiplying
 $E_S\ll_A(\log X)^{-A}$ with the soft bound $Z\ll X^\eps$.
 A fixed $X^\eps$ is not absorbed by choosing $A$.  The nonzero
 decomposition must use the power-small drift $\delta_H$.
 \item One cannot obtain the full-base theorem by formally setting the
 lower endpoint of an annular prefix theorem below $R$.  The full
 unit fibers, energy, principal mean, and reassembly must be defined
 directly, as in \cref{sec:tpc28-full-base,sec:tpc28-minimax}.
 \item One cannot conductor-project the coherent additive zero terms
 before their raw/centered recombination.  In particular $b_R(1)$ is
 generally nonzero.  The zero identity
 \eqref{eq:tpc28-calibrated-zero-identity} must be applied first.
\end{enumerate}

\subsection{What is new and what remains open}

The new conclusions are:
\begin{itemize}
 \item a full-rectangle nonzero conductor theorem governed by
 $M_\beta(s)$;
 \item calibrated base closure without $S<J$;
 \item closure of the particular source-compatible
 $\beta=267/400>2/3$ initial value;
 \item after importing TPC-26 cutoff stability, closure of the
 corresponding selected square through $T=X^{193/500+o(1)}$.
\end{itemize}

The following are not conclusions of this paper:
\begin{itemize}
 \item the ultra-long complement beyond $T$;
 \item the full TPC-18 residual or a complete original prime-pair
 correlation;
 \item a polynomially uniform affine two-point M\"obius theorem on the
 reflected surface \eqref{eq:tpc28-reflected-surface};
 \item positivity, a Hardy--Littlewood asymptotic, or a twin-prime
 lower bound;
 \item any general breach of the sieve parity barrier.
\end{itemize}

The next analytic gate is therefore cleaner than before: the selected
high-$\beta$ square no longer lacks an initial value.  What remains on
this branch is the reflected ultra-long complement, where the exact
surface \eqref{eq:tpc28-reflected-surface} must be combined with orbit
congruences, sparse incidence geometry, and genuine cancellation in
growing affine M\"obius coefficients.  A positive theorem, a precise
conditional reduction, or a sharp barrier theorem at that gate would
all be logically downstream of the present result.
