\section{The high-\texorpdfstring{\(\beta\)}{beta} initial value and upper splice}
\label{sec:tpc28-high-splice}

We now verify the exact source-compatible sample that was left with an
open initial value in TPC-26 and TPC-27.

\subsection{Source geometry}

Put
\begin{equation}
 \sigma=\frac1{10000},\qquad
 \lambda=\frac{10}{21}-\sigma
 =\frac{99979}{210000},\qquad
 \delta=\frac7{60}.
 \label{eq:tpc28-source-parameters}
\end{equation}
Take
\begin{equation}
 \beta=\frac{267}{400},\qquad
 s=\frac{23}{60},\qquad
 t=\frac{193}{500}.
 \label{eq:tpc28-high-sample}
\end{equation}
Then
\begin{equation}
 R=S=X^{23/60+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)}.
 \label{eq:tpc28-high-scales}
\end{equation}
The opened-$d$ exponent and its available endpoint are
\begin{equation}
 d_*=\beta-\lambda=\frac{10049}{52500},
 \qquad
 v_*=\frac14-\frac\delta2=\frac{23}{120},
 \label{eq:tpc28-dv-exponents}
\end{equation}
with
\begin{equation}
 v_*-d_*=\frac9{35000}>0.
 \label{eq:tpc28-dv-margin}
\end{equation}
In the notation of TPC-26, the source relations
$J=K/D$, $D_0<D\le V$, and $K>2V$ were verified for these exact
exponents \citep{WangTPC26}.  We also have
\begin{equation}
 \lambda-t=\frac{18919}{210000}>0,
 \label{eq:tpc28-L-above-T}
\end{equation}
so $L>2T\ge2S$ for all sufficiently large $X$.  The present proof
requires only the weaker fixed-power condition $L\ge X^{\lambda_0}$,
but \eqref{eq:tpc28-L-above-T} confirms the original source geometry.

The base lies strictly beyond the Poisson length:
\begin{equation}
 s-(1-\beta)
 =\frac{23}{60}-\frac{133}{400}
 =\frac{61}{1200}>0.
 \label{eq:tpc28-base-beyond-J}
\end{equation}
Thus the old Poisson-short base theorem cannot be invoked.

\subsection{Old and new base ledgers}

The three entries in the earlier centered base ledger are
\begin{equation}
 \left(
 1-\frac{3\beta}{2},
 \frac{\beta+1-4s}{2},
 \frac{3-\beta-6s}{4}
 \right)
 =\left(
 -\frac1{800},
 \frac{161}{2400},
 \frac{13}{1600}
 \right).
 \label{eq:tpc28-old-ledger-sample}
\end{equation}
The first face is negative.  This records the exact failure of the old
centered nonzero theorem; it is not a failure of the zero theorem.

For the full raw rectangle,
\begin{equation}
 \frac\beta2=\frac{267}{800}
 <s=\frac{23}{60}
 <\frac{3\beta-1}{2}=\frac{401}{800}.
 \label{eq:tpc28-base-branch}
\end{equation}
Therefore the third branch of
\eqref{eq:tpc28-sharp-minimax} applies and gives
\begin{equation}
 \boxed{
 M_{267/400}(23/60)
 =\frac{3-267/400-6(23/60)}4
 =\frac{13}{1600}.}
 \label{eq:tpc28-base-saving}
\end{equation}
The competing high--high face is $161/2400$, so the mixed witness is
the actual relaxed-box bottleneck.

The drift has the independent fixed-power factor $L^{-1}$.  At this
sample the source exponent is
\begin{equation}
 \lambda=\frac{99979}{210000}>0,
 \label{eq:tpc28-drift-source-saving}
\end{equation}
and \cref{prop:tpc28-drift-bound} applies after choosing its soft
$X^\eps$ loss below this fixed value.  In particular, no compensation
for the Poisson overrun $61/1200$ is required.

\begin{corollary}[Closed high-\(\beta\) initial value]
\label{cor:tpc28-high-base}
For the actual opened-row packet with the fixed primitive, mask,
no-wrap, smooth-transfer, and target-support interfaces above, the
parameters \eqref{eq:tpc28-source-parameters}--\eqref{eq:tpc28-high-sample}
satisfy
\begin{equation}
 \boxed{
 \cQ_S^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}}
 \label{eq:tpc28-high-base-closure}
\end{equation}
for every fixed $B>0$, although $S>J$.
\end{corollary}

\begin{proof}
The exact source relations give the physical row interface.
Equation \eqref{eq:tpc28-base-saving} supplies the positive
full-rectangle conductor margin, while
\eqref{eq:tpc28-drift-source-saving} supplies the existing fixed-power
row-prime margin.  Apply \cref{thm:tpc28-base-closure}.
\end{proof}

\subsection{Splicing to the upper cutoff}

TPC-26 proves annular cutoff stability between these same $S$ and
$T$ whenever $M_\beta(t)>0$.  Here
\begin{equation}
 \frac\beta2<t<\frac{3\beta-1}{2},
\end{equation}
and the two upper faces are
\begin{equation}
 \frac{\beta+1-4t}{2}=\frac{247}{4000},
 \qquad
 \frac{3-\beta-6t}{4}=\frac{33}{8000}.
 \label{eq:tpc28-upper-faces}
\end{equation}
Thus
\begin{equation}
 \boxed{M_{267/400}(193/500)=\frac{33}{8000}.}
 \label{eq:tpc28-upper-saving}
\end{equation}
Also $t-s=1/375>0$.  The imported theorem gives
\begin{equation}
 \cQ_T^{\rm phys}-\cQ_S^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}.
 \label{eq:tpc28-imported-annular}
\end{equation}
Its remaining hypotheses use the same physical packet, common weight,
mask, no-wrap, and source interfaces retained above.  Moreover
$1-\beta=133/400>0$, $S<T$, and \eqref{eq:tpc28-L-above-T} provide
the required fixed-power support and separation margins.

\begin{theorem}[Closed high-\(\beta\) selected truncated square]
\label{thm:tpc28-high-upper}
Under the physical interfaces above, the exact sample
\eqref{eq:tpc28-source-parameters}--\eqref{eq:tpc28-high-sample}
satisfies, for every fixed $B>0$,
\begin{equation}
 \boxed{
 \cQ_T^{\rm phys}
 \ll_{B,\mathscr D}XQ(\log X)^{-B}.}
 \label{eq:tpc28-high-upper-closure}
\end{equation}
\end{theorem}

\begin{proof}
Use the exact identity
\[
 \cQ_T^{\rm phys}
 =\cQ_S^{\rm phys}
 +(\cQ_T^{\rm phys}-\cQ_S^{\rm phys})
\]
and combine \cref{cor:tpc28-high-base} with
\eqref{eq:tpc28-imported-annular}.
\end{proof}

\begin{table}[t]
\centering
\caption{Exact margins in the high-\(\beta\) selected-square splice.}
\label{tab:tpc28-high-ledger}
\begin{tabular}{@{}lll@{}}
\toprule
Gate & Exact value & Status \\
\midrule
Poisson overrun $s-(1-\beta)$ & $61/1200$ & base is long \\
Old centered face $1-3\beta/2$ & $-1/800$ & old route fails \\
Full raw-base minimax $M_\beta(s)$ & $13/1600$ & closed here \\
Row-prime exponent $\lambda$ & $99979/210000$ & drift is power-small \\
Annular minimax $M_\beta(t)$ & $33/8000$ & imported from TPC-26 \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Exact scope of the splice}

The conclusion estimates one selected calibrated square truncated at
$T$.  It does not estimate the ultra-long complement
\begin{equation}
 \sum_{\substack{T<u\le U\\u\mid mj+h}}a(u),
 \label{eq:tpc28-ultra-long-complement}
\end{equation}
nor the products involving that complement.  Writing the reflected
quotient variables as
$mj+h=ur'$ and $nj+h=vs'$, divisor reflection there produces the
exact determinant surface
\begin{equation}
 n\,u\,r'-m\,v\,s'=h(n-m),
 \label{eq:tpc28-reflected-surface}
\end{equation}
together with orbit congruences and growing two-point M\"obius
coefficients.  No estimate for that surface is asserted here.  The
separate positivity/main-term stage is also untouched.
