\section{Introduction}
\label{sec:tpc28-introduction}

This paper addresses one precise initial-value gap in the primitive
M\"obius-tail program of TPC-18--27.  The target is not a prime-pair
asymptotic.  It is a cancellation estimate for one selected calibrated
quadratic packet that occurs before the ultra-long complement and
before any positivity argument.

The previous chain separates into two facts.  First, TPC-26 proves
cutoff stability
\begin{equation}
 \cQ_T^{\rm phys}-\cQ_S^{\rm phys}
 \ll_B XQ(\log X)^{-B}
 \label{eq:tpc28-intro-annular}
\end{equation}
in a sharp joint-conductor region that can contain $S>J$ and $T>J$
\citep{WangTPC26}.  Second, TPC-27 proves the matching initial value
\begin{equation}
 \cQ_S^{\rm phys}
 \ll_B XQ(\log X)^{-B}
 \label{eq:tpc28-intro-old-base}
\end{equation}
only when $S<J$ with a fixed power margin \citep{WangTPC27}.  The
logical difference matters: \eqref{eq:tpc28-intro-annular} alone does
not estimate either endpoint.

The high-$\beta$ sample recorded in TPC-26 has
\begin{equation}
 \beta=\frac{267}{400},\qquad
 J=X^{133/400+o(1)},\qquad
 S=X^{23/60+o(1)},\qquad
 T=X^{193/500+o(1)}.
 \label{eq:tpc28-intro-high-sample}
\end{equation}
Both cutoffs exceed $J$.  Its annular margin is positive, but its
initial value was therefore left open.

\subsection{Why the earlier base proof stops}

For a row $m=\ell d$, the calibrated prefix admits two exact
representations:
\begin{equation}
 P_{m,S}=Z_{m,S}+E_S(m)
 =\mathsf A_{m,S}-\delta_H(m).
 \label{eq:tpc28-two-representations}
\end{equation}
The first uses a centered divisor process and a calibration error
 $E_S(m)\ll_A(\log X)^{-A}$.  The second uses the raw divisor prefix
\(\mathsf A_{m,S}\) and the row drift
\(\delta_H(m)\ll X^\eps/L\).

TPC-27 uses the centered representation at every frequency.  Its
nonzero exact-conductor ledger is
\begin{equation}
 \eta_S(\beta,s)=
 \min\left\{
 1-\frac{3\beta}{2},
 \frac{\beta+1-4s}{2},
 \frac{3-\beta-6s}{4}
 \right\}.
 \label{eq:tpc28-old-centered-ledger}
\end{equation}
At \eqref{eq:tpc28-intro-high-sample}, its first entry is
$-1/800$.  Moreover, estimating $E_SZ_S$ by an orbitwise
\(\ell^1\) bound introduces $J+S$.  An error that is smaller than
every logarithmic power cannot absorb the fixed power $S/J$.

Neither obstruction occurs if the two representations in
\eqref{eq:tpc28-two-representations} are used at different additive
frequencies.  This is the central observation of the paper.

\subsection{The frequency-dependent recombination}

At additive frequency zero we keep the centered representation.  The
complete-period mean of $Z_{m,S}$ vanishes, so the zero kernel of
$P_{m,S}P_{n,S}$ is exactly
\begin{equation}
 K_S^0(m,n)+E_S(m)E_S(n).
 \label{eq:tpc28-intro-zero-result}
\end{equation}
The potentially dangerous $EZ$ and $ZE$ terms are absent by exact
algebra, not by an estimate.  TPC-27 already closes $K_S^0$ for every
polynomial $S\ge R$; its zero theorem never required $S<J$.

At nonzero frequency we instead expand
\begin{equation}
 \begin{aligned}
 P_{m,S}P_{n,S}
 ={}&\mathsf A_{m,S}\mathsf A_{n,S}
 -\delta_H(m)\mathsf A_{n,S}
 -\delta_H(n)\mathsf A_{m,S}
 +\delta_H(m)\delta_H(n).
 \end{aligned}
 \label{eq:tpc28-intro-raw-expansion}
\end{equation}
The coefficient-one term is one raw joint rectangle $u,v\le S$.
The other three terms contain the fixed-power row drift.  On the
physical target support, a divisor bound gives
\begin{equation}
 \mathsf A_{m,S}(j)\ll_\eps X^\eps,
 \label{eq:tpc28-intro-divisor-bound}
\end{equation}
uniformly in $S$.  Hence the full drift contribution is already
power-small from $L\ge X^{\lambda_0}$; no $J+S$ loss is needed.

For the raw joint rectangle we prove the full-base analogue of the
TPC-26 annular cell theorem.  The annular lower restriction was deleted
when enlarging the nonnegative tensor energy, but the full-base result
is not obtained merely by setting an endpoint to zero.  We define the
full fibers, their exact-conductor projections, principal mean, and
Fourier reassembly anew.  The resulting cell estimate is
\begin{equation}
 \cL^{\rm base}_{Y;S}(F_1,F_2)
 \ll_\eps QX^\eps
 \sqrt{\cK_Q(F_1)\cK_Q(F_2)}
 \min\{\sqrt{JY},F_1F_2\}.
 \label{eq:tpc28-intro-cell-bound}
\end{equation}
It gives the sharp relaxed-box margin $M_\beta(s)$, without the old
face $1-3\beta/2$.

\subsection{Main consequence}

Under the actual opened-row provenance, the divisor-independent
off-diagonal mask, the common physical weight, no-wrap, and fixed
Fourier-tail interfaces, we prove
\begin{equation}
 \boxed{
 M_\beta(s)>0
 \quad\Longrightarrow\quad
 \cQ_S^{\rm phys}
 \ll_B XQ(\log X)^{-B}}
 \label{eq:tpc28-intro-main}
\end{equation}
for every fixed $B>0$.  There is no condition $S<J$.  At the high
sample,
\begin{equation}
 M_{267/400}(23/60)=\frac{13}{1600}>0.
 \label{eq:tpc28-intro-base-margin}
\end{equation}
Combining \eqref{eq:tpc28-intro-main} with the TPC-26 annular margin
\begin{equation}
 M_{267/400}(193/500)=\frac{33}{8000}>0
 \label{eq:tpc28-intro-upper-margin}
\end{equation}
closes the selected calibrated truncated square through $T$.

The improvement is a recombination theorem inside a specific analytic
packet.  It does not estimate the complement beyond $T$, whose
divisor reflection exposes polynomial families of affine two-point
M\"obius correlations \citep{WangTPC23,WangTPC26}.  It also does not
produce a positive main term.  In particular, the result neither
implies twin primes nor claims a general breach of the sieve parity
barrier.

\subsection{Organization}

\Cref{sec:tpc28-interface-zero} fixes the physical interface and proves
the exact zero-frequency recombination.  \Cref{sec:tpc28-full-base}
constructs the full-rectangle exact-conductor cells and proves the two
cell estimates.  \Cref{sec:tpc28-minimax} optimizes and reassembles the
nonzero spectrum.  \Cref{sec:tpc28-drift-base} restores the drift and
proves the Poisson-long base theorem.  \Cref{sec:tpc28-high-splice}
checks the exact high-$\beta$ ledger and splices to TPC-26.
\Cref{sec:tpc28-certificate-scope} records the certificate, dependency
ledger, and scope.
