\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\hypersetup{
 pdftitle={Target-Coupled CRT Projectors and the Identity Bucket: Shifted Jacobi Grams, Alias Coherence, and the Equality-Recovery Obstruction},
 pdfauthor={Liang Wang},
 pdfsubject={Exact character projectors and the joint-alias boundary in an orbit-sliced Mobius gate},
 pdfkeywords={Mobius correlation, Dirichlet character, CRT projector, Jacobi sum, Bessel sequence, alias Gram, equality recovery, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\F}{\mathbb F}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cN}{\mathcal N}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cU}{\mathcal U}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\cX}{\mathcal X}
\newcommand{\cY}{\mathcal Y}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\op}{\operatorname{op}}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\rank}{\operatorname{rank}}

\title{\textbf{Target--Coupled CRT Projectors and the Identity Bucket:}\\
\textbf{Shifted Jacobi Grams, Alias Coherence,}\\
\textbf{and the Equality--Recovery Obstruction}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC--37 proposed a target--coupled shifted--fiber estimate as one possible
continuation of an orbit--sliced prime--M\"obius energy program.  We resolve
the coefficient--free part of that proposal exactly and identify an
additional equality--recovery step required by its physical application.

Let \(q_1,q_2,q_3\) be distinct orbit--scale primes,
\(M=q_1q_2q_3\), \(\Phi=\varphi(M)\), and let \(N\) be a unit modulo
\(M\).  If \(F=su-N\), every coordinate face has the exact expansion
\[
 K_{S,N}(F)=\frac1\Phi
 \sum_{\chi\in\mathfrak X_S}
 \chi(s)\chi(u)\overline{\chi(N)},
\]
where the local component of \(\chi\) is nonprincipal exactly on \(S\).
Zero extension makes this expansion valid even when \(N+F\) is a nonunit;
then every face vanishes in a killed local coordinate.  On the regular
support \(N+F\in(\Z/M\Z)^\times\), the finite CRT target dependence is
diagonalized by the unit--group ratio
\[
 r=(N+F)N^{-1}\pmod M.
\]
The full and proper face families are complementary character
projectors.  Their recombination is the target--independent identity
\[
 C_N(F)+P_N(F)=\one_{M\mid F}.
\]

On this regular support we prove a Hilbert--valued ratio Parseval identity.  For arbitrary vectors
\(z_{N,F}\), character orthogonality controls the sums of the coherent
ratio buckets, not the individual pairs \((N,F)\).  For fixed \(F\), the
ratio map has exact maximum multiplicity
\[
 d_M(F)=\prod_{q_i\mid F}(q_i-1).
\]
When \(q_i\asymp J\), the target collision scales are therefore
\(1,J,J^2,J^3\), according as \(F\) is divisible by zero, one, two, or
three auxiliary primes.  Generic
determinants are injective; the obstruction is concentrated on the
coordinate divisibility strata.

We also compute the complete one--period target--synthesis spectrum.  The
full--face operator has squared norm
\[
 \prod_{i=1}^3\frac{q_i(q_i-2)^2}{(q_i-1)^2}\asymp\Phi,
\]
whereas, for \(q_i\asymp J\), the proper operator has squared norm
\(\asymp\Phi/J\).  Both scalar spectra have a dominant global principal
target mode; fixed--target Parseval does not imply target--synthesis
orthogonality.

After full/proper recombination, every nonjoint ghost cancels exactly and
the completed output is the joint--alias sum over \(F=kM\).  At the endpoint
\[
 Q=X^{267/400+o(1)},\qquad J=X^{133/400+o(1)},\qquad
 M=X^{399/400+o(1)},
\]
their endpoint order is
\[
 \cK_X:=1+X/M=X^{1/400+o(1)}.
\]
All multiplicative character phases equal \(1\) on this identity bucket.
For the alias--completed sum, diagonal energy plus Cauchy loses the exact
finite alias count; at the endpoint this has order \(\cK_X\).  A
joint--alias Gram estimate removes that loss.

Crucially, the alias--completed sum is not the original equality output,
which is its \(k=0\) column.  There is no coefficient--free recovery:
two opposite alias columns make both fixed full/proper field outputs vanish
while leaving the equality column arbitrary.  Thus the shifted--fiber
estimate proposed in TPC--37 controls a congruence completion but, by
itself, does not imply the physical equality gate.  A full alias--Gram
bound implies the equality bound directly through its \(k=0\) diagonal
entry, at the stronger diagonal scale.  The terminal identity bucket expands into
M\"obius autocorrelations at shifts \(rM\), and the physical row expansion
contains the affine four--M\"obius boundary found earlier.

Finally, we distinguish two prescribed face--field estimates from an
all--field operator estimate of the same normalization that is stable under
restrictions.  The latter would be strictly stronger: its
\(F=0,s=1\) restriction implies a diagonal--scale estimate for the
terminal affine--M\"obius/four--M\"obius operator.  We prove no positive
physical equality--recovery estimate and no M\"obius estimate.  The results
are exact reductions, a correction of the
logical gate, and method obstructions---not a M\"obius lower bound, a
parity breach, a Hardy--Littlewood asymptotic, or a twin--prime theorem.
\end{abstract}

\noindent\textbf{Keywords:}
M\"obius correlation; Dirichlet character; CRT projector; Jacobi sum;
Bessel sequence; alias Gram; equality recovery; parity boundary.

\medskip
\noindent\textbf{MSC 2020:}
Primary 11N35, 11L40; Secondary 11N37, 15A18, 42C15.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/target-character-projectors}
\input{sections/ratio-parseval}
\input{sections/target-synthesis-spectrum}
\input{sections/recombined-alias-gate}
\input{sections/terminal-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
