\begin{abstract}
Let \(h_0\ne0\) be fixed.  In the matched prime--M\"obius cutoff
packet of TPC-32, the post-aggregation normalized-determinant
coefficient at the physical content cutoff \(C=\lfloor J\rfloor\) is
\[
 A_C(n),\qquad
 Z_X=\sum_nA_C(n),\qquad
 D_X=\sum_n|A_C(n)|^2.
\]
The off-diagonal row mask gives \(A_C(0)=0\), but this coefficient
identity does not imply that the finite Fourier value
\(\widehat A_{C,q}(0)=Z_X\) vanishes.  We give an exact
disintegration of that distinguished Fourier mode and prove three
normalization barriers.

First, under the strong physical no-wrap padding,
\[
 A_C=A_C^\circ+\frac{Z_X}{q}\mathbf 1,\qquad
 D_X=\|A_C^\circ\|_2^2+\frac{|Z_X|^2}{q}.
\]
Fourier inversion at the deleted determinant bin also gives
\[
 Z_X=-\sum_{r\ne0}\widehat A_{C,q}(r).
\]
Thus canonical centering alone extracts the unknown constant mode
rather than estimates it, while a coherent estimate for all nonzero
modes is an exact alternative interface.  Second, for a positive raw
atomic measure whose
determinant-fiber masses are \(M_n\), conditional expectation onto the
determinant sigma-algebra has squared norm
\[
 \sum_n\frac{|A_C(n)|^2}{M_n},
\]
not \(D_X\), and preserves the total integral \(Z_X\).  Unit mass per
bin is therefore a change of normalization, not a consequence of
conditional expectation.  Third, exact common-divisor inversion does
not center the packet: its \(t=1\) term is the unrestricted full
matched shell and its \(t>1\) terms reassemble to the negative
large-content shell.

We then trace the literal affine interface
\[
 \mu(d_0+sr)\mu(u_0+ar),\qquad su_0-ad_0=h_0,
\]
including growing slopes, short fibers, joint masks, and outer
reassembly.  This interface expands the raw hard coefficient; the
calibrated drift remains a separate downstream ledger item.  A
quantifier audit shows why fixed-form logarithmic
correlation theorems, shift averages, almost-all-scale results, and
almost-all short intervals do not by themselves control this
unweighted fixed-\(h_0\) packet.  An explicit dyadic sign sequence
proves that logarithmic cancellation cannot be converted to ordinary
cancellation by a structure-free Tauberian black box.  The example is
not multiplicative and asserts no obstruction to an argument using
M\"obius-specific structure.

All new finite identities and the explicit abstract countermodel are
\(\Lzero\) results, and their placement inside the physical packet is
an \(\Lone\) transfer diagnosis.  No new \(\Ltwo\) affine M\"obius
estimate, parity-breaking theorem, prime-pair lower bound, or
twin-prime conclusion is claimed.
\end{abstract}
