\section{Claim boundary and conclusion}
\label{sec:claim-boundary}

\subsection{What has been proved}

The paper proves the following unconditional statements.
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=2.5em]
 \item For the actual TPC-32 determinant coefficient at
 \(C=\lfloor J\rfloor\),
 \[
 A_C(0)=0
 \quad\text{and}\quad
 \widehat A_{C,q}(0)=Z_X
 \]
 are different assertions: the first does not by itself make the
 second vanish.
 \item Every no-wrap cyclic realization has the orthogonal
 decomposition
 \[
 D_X=\|A_C^\circ\|_2^2+\frac{|Z_X|^2}{q}.
 \]
 Under the strong physical padding, it also has the coherent
 reassembly
 \[
 Z_X=-\sum_{r\ne0}\widehat A_{C,q}(r).
 \]
 \item Conditional expectation onto determinant fibers has norm
 \(\sum_n|A_C(n)|^2/M_n\), preserves \(Z_X\), and cannot be identified
 with the post-bin energy without fiber-mass control.
 \item The cumulative content projector has full-shell \(t=1\) term
 and negative large-content \(t>1\) reassembly; it does not center the
 zero mode.
 \item The opened physical column has a fixed-determinant affine
 M\"obius interface, but its slopes grow, some fibers are bounded,
 and the complete joint-mask reassembly remains part of the gate.
 \item Logarithmic cancellation does not imply ordinary cancellation
 for arbitrary bounded sequences; the conversion needs additional
 structure.
\end{enumerate}

Items (1)--(4) are finite \(\Lzero\) identities, while item (6) is an
explicit structure-free \(\Lzero\) countermodel.  Their exact placement
in the literal matched packet, together with the theorem-quantifier
audit, is an \(\Lone\) diagnosis.  None is a new \(\Ltwo\)
M\"obius-correlation estimate.

\subsection{Explicit exclusions}

This paper does not prove:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.3em]
 \item a bound of the form
 \(|Z_X|\le X^{-\eta_Z+o(1)}Q^2\) with a new
 \(\eta_Z>0\);
 \item the physical determinant-energy lower bound for \(D_X\);
 \item a uniform Chowla or Elliott theorem for the growing affine
 family in \eqref{eq:affine-literal-correlation};
 \item a full-block cover or the downstream uniform remainder bounds
 of the original route \citep{WangTPC18};
 \item a fixed-\(h_0\) Hardy--Littlewood asymptotic;
 \item a breach of the general sieve parity barrier;
 \item a prime-pair lower bound or the twin-prime conjecture.
\end{enumerate}
No conclusion is specialized from a general fixed nonzero \(h_0\) to
\(h_0=2\).  The appearance of the two signs
\(\mu(D_r)\mu(U_r)\) identifies an arithmetic gate; it does not solve
that gate.  Sieve parity remains a genuine boundary
\citep{HeathBrown1982Parity,IwaniecKowalski2004}.

\subsection{Conclusion}

The distinguished zero mode is not hidden in the notation.  It is the
total mass of the literal determinant coefficient and, modulo the
known large-content error, the complete matched shell.  The three
most immediate reorganizations have exact outcomes:
\[
\begin{array}{ccl}
\text{Fourier centering}
&\longrightarrow&
\text{subtracts }(Z_X/q)\one,\\
\text{coherent nonzero-frequency reassembly}
&\longrightarrow&
\text{returns }-\sum_{r\ne0}\widehat A_{C,q}(r)=Z_X,\\
\text{conditional expectation}
&\longrightarrow&
\text{preserves }Z_X\text{ and inserts }M_n^{-1},\\
\text{content inversion}
&\longrightarrow&
\text{returns the full shell at }t=1.
\end{array}
\]
None creates cancellation.  The coherent Fourier identity does,
however, identify a valid alternative route: control the full
phase-sensitive sum of the nonzero modes, including every exceptional
nonzero mode.

The surviving positive interfaces are the coherent Fourier
reassembly \eqref{eq:constant-coherent-reassembly} and the
fixed-determinant affine correlation
\eqref{eq:affine-literal-correlation}.  The next arithmetic advance
must either prove a uniform estimate that survives one of these
literal reassemblies, isolate a rigorously controlled physical sector,
or establish a sharper impossibility theorem for a proposed transfer.
Whichever outcome occurs, it must retain the same \(h_0\), the actual
\(r=0\), \(C=\lfloor J\rfloor\), one global normalization, and the
strict loss rule \(\Lambda_{\rm phys}<1/400\).
