\section{Introduction}
\label{sec:introduction}

The determinant-frequency route of TPC-32 separates a literal signed
arithmetic packet into coefficients \(A_C(n)\) indexed by a normalized
row determinant \citep{WangTPC32}.  Parseval and the additive large
sieve control the family of determinant frequencies in mean, but the
physical reassembly selects one distinguished member:
\[
 \widehat A_{C,q}(0)=\sum_nA_C(n).
\]
An exceptional-frequency theorem is permitted to place this one
frequency in its exceptional set.  TPC-81 and TPC-82 therefore retain
the bound for this zero mode as an independent arithmetic premise
\citep{WangTPC81,WangTPC82}.

This paper asks whether three natural reorganizations can reduce that
premise: subtracting a mean, conditioning raw atoms on determinant
fibers, or expanding the small-content indicator by M\"obius
inversion.  Each operation is useful, but each has an exact limitation.
Centering subtracts the unknown zero mode itself.  Conditional
expectation preserves the total integral and changes the post-bin
energy by a fiber-mass factor.  Content inversion returns the full
shell in its principal term.  These are normalization statements, not
heuristic objections.

\subsection{The literal object and the scope of the audit}

Throughout, \(h_0\in\Z\setminus\{0\}\) is one fixed integer.  It is not
averaged, allowed to vary with \(X\), or specialized to \(2\).  The
content cutoff is always
\begin{equation}
 C=\lfloor J\rfloor.
 \label{eq:intro-physical-cutoff}
\end{equation}
The coefficient \(A_C\) is formed from the complete signed matched
atoms before any norm or Fourier estimate is taken.  In particular,
the actual row-pair mask, fixed residue factors, smooth weights, both
polarizations of the rank-two cutoff shell, and all native keys remain
inside the coefficient.  The energy
\[
 D_X=\sum_n|A_C(n)|^2
\]
is the physical post-aggregation energy, not raw atom energy, an
unsigned majorant, or a sum of pre-bin squares.
Here ``physical post-aggregation'' refers to the hard raw matched
coefficient of TPC-32.  The calibrated packet contains two additional
drift legs.  They are restored only after the raw estimate and are
charged in the downstream physical ledger; they are not silently
inserted into \(A_C\), \(Z_X\), or \(D_X\).

The audit has three levels.
\begin{definition}[Proof levels]
\label{def:proof-levels}
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.5em]
 \item \(\Lzero\) consists of finite identities in Fourier analysis,
 conditional expectation, divisor inversion, and affine
 parametrization, together with explicit structure-free
 countermodels that make a logical nonimplication exact.
 \item \(\Lone\) consists of a literal transfer or obstruction at the
 same fixed \(h_0\), with all physical keys and the global
 normalization retained.
 \item \(\Ltwo\) is a new asymptotic arithmetic estimate for the
 actual growing family, strong enough to save a fixed power after
 complete reassembly.
\end{enumerate}
\end{definition}
The theorems proved here are \(\Lzero\); their crosswalk to \(Z_X\) is
\(\Lone\).  No \(\Ltwo\) estimate is proved.

\subsection{Main results}

The first result is an orthogonal constant-mode identity.  After
embedding the determinant support injectively into a cyclic group of
order \(q\) using the strong physical padding,
\begin{equation}
 A_C^\circ=A_C-\frac{Z_X}{q}\one
 \label{eq:intro-centered-coefficient}
\end{equation}
satisfies
\begin{equation}
 \boxed{
 D_X=\|A_C^\circ\|_2^2+\frac{|Z_X|^2}{q}.}
 \label{eq:intro-constant-mode-energy}
\end{equation}
At the deleted determinant bin, Fourier inversion gives the
additional exact identity
\begin{equation}
 \boxed{
 Z_X=-\sum_{r\ne0}\widehat A_{C,q}(r).}
 \label{eq:intro-coherent-reassembly}
\end{equation}
Thus centering or mean-square information alone does not estimate the
removed constant coefficient, but a coherent estimate for the full
nonzero-frequency sum can do so.  A generic-frequency theorem must
return its exceptional nonzero modes and the coherent reassembly; it
need not separately state a pointwise theorem at \(r=0\).

The second result starts with a general finite positive atomic measure
\(\rho\), a signed density \(f\), and a bin map \(\nu\).  If
\[
 A(n)=\int_{\nu=n}f\,d\rho,\qquad
 M_n=\rho(\nu=n),
\]
then
\begin{equation}
 \boxed{
 \left\|\E_\rho(f\mid\sigma(\nu))\right\|_{L^2(\rho)}^2
 =\sum_{M_n>0}\frac{|A(n)|^2}{M_n}.}
 \label{eq:intro-conditional-energy}
\end{equation}
Moreover,
\[
 \int\E_\rho(f\mid\sigma(\nu))\,d\rho
 =\int f\,d\rho
 =\sum_nA(n).
\]
Thus conditioning neither produces \(D_X\) nor cancels \(Z_X\).

The third result applies the cumulative content projector
\[
 \eta_{\le C}(t)
 =\sum_{\substack{c\mid t\\c\le C}}\mu(t/c).
\]
For a target gcd \(G\),
\[
 \sum_{\substack{t\mid G\\t>1}}\eta_{\le C}(t)
 =-\one_{G>C}.
\]
Consequently the \(t=1\) term is exactly the unrestricted full shell,
and the remaining terms are exactly minus the large-content shell.
At \eqref{eq:intro-physical-cutoff}, the known large-content estimate
only gives the already recorded \(X^{o(1)}Q^2\) splice error
\citep{WangTPC30,WangTPC32}.

Finally, we trace the raw hard physical column reduction to two affine
M\"obius signs and compare its quantifiers with the available
correlation theorems.  The fixed-determinant equation is
\[
 su_0-ad_0=h_0,\qquad a=\ell jv,
\]
but \(s\) and \(a\) grow with \(X\), some fibers have bounded length,
and the column must be returned through a joint mask and an outer
sum.  Theorems for fixed affine forms, averaged shifts, almost-all
scales, or almost-all interval origins do not automatically supply
that package.  Content completion belongs to this raw reassembly,
whereas the calibrated drift is returned only afterward.

\subsection{A black-box Tauberian boundary}

We also give a deterministic sequence \(c_n\in\{-1,1\}\) such that,
for every \(1\le\omega(x)\le x\) with \(\omega(x)\to\infty\),
\[
 \sum_{x/\omega(x)<n\le x}\frac{c_n}{n}
 =o(\log\omega(x)),
\]
while \(\sum_{n\le X}c_n\) has size comparable to \(X\) along an
infinite dyadic subsequence.  This proves that no structure-free
Tauberian implication converts a Tao-shaped logarithmic estimate into
ordinary cancellation.  Because the constructed sequence is not
multiplicative, this statement does not rule out a conversion based
on additional M\"obius structure.

\subsection{Organization}

\Cref{sec:literal-zero-mode} fixes the literal coefficient and the
coefficient-value/Fourier-frequency distinction.
\Cref{sec:constant-mode} proves the no-wrap constant-mode
decomposition.  \Cref{sec:conditional-expectation} proves the
conditional-expectation barrier, and
\cref{sec:content-projector} proves the content-projector
reassembly.  \Cref{sec:affine-interface} records the exact affine
interface.  \Cref{sec:literature-quantifiers} audits the available
theorems, while \cref{sec:log-counterexample} gives the Tauberian
counterexample.  The endpoint ledger and claim boundary appear in
\cref{sec:endpoint-ledger,sec:claim-boundary}.
