\section{Quantifier audit of available correlation theorems}
\label{sec:literature-quantifiers}

The affine sequence \eqref{eq:affine-literal-correlation} resembles
several established multiplicative-correlation problems.  Resemblance
of the summand is not enough: the averaging measure, coefficient
range, selected shift, selected scale, interval length, and outer
reassembly are theorem hypotheses.

\subsection{Fixed-form logarithmic correlation}

For fixed \(a_1,a_2\in\N\) and
\(b_1,b_2\in\Z_{\ge0}\) with
\(a_1b_2-a_2b_1\ne0\), Tao proved the logarithmically averaged
two-point Chowla estimate
\begin{equation}
 \sum_{x/\omega(x)<n\le x}
 \frac{\lambda(a_1n+b_1)\lambda(a_2n+b_2)}{n}
 =o(\log\omega(x)),
 \label{eq:lit-tao-log}
\end{equation}
where \(1\le\omega(x)\le x\) and \(\omega(x)\to\infty\)
\citep{Tao2016LogChowla}.  The Elliott form of the theorem treats
more general bounded multiplicative functions under its
nonpretentiousness hypotheses and contains fixed-form M\"obius
analogues.

This is a genuine parity-breaking correlation theorem in its stated
logarithmic setting.  It does not, without additional arguments,
provide the physical estimate because:
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=2.3em]
 \item the slopes \(s\) and \(a=\ell jv\), and the intercepts, vary
 polynomially with \(X\);
 \item the required sum is dyadic or ordinary rather than weighted
 by \(1/n\);
 \item the packet contains many intervals, some of length \(O(1)\);
 \item fixed residue factors, growing auxiliary moduli, and the
 actual joint mask must be retained;
 \item all columns and both polarizations must be reassembled with a
 quantitative fixed-power budget.
\end{enumerate}
The entropy decrement argument is one mechanism in the proof of
\eqref{eq:lit-tao-log}; it is not a black-box rule that deletes the
logarithmic weight or supplies uniformity in growing affine
coefficients.

\subsection{Averaged shifts}

Matom\"aki, Radziwi{\l}{\l}, and Tao proved, for fixed \(k\) and
\(1\le H=H(X)\le X\) with \(H(X)\to\infty\),
\begin{equation}
 \sum_{h_1,\ldots,h_k\le H}
 \left|
 \sum_{n\le X}
 \lambda(n+h_1)\cdots\lambda(n+h_k)
 \right|
 =o(H^kX).
 \label{eq:lit-mrt-shift-average}
\end{equation}
See \citet{MatomakiRadziwillTao2015}.  This ordinary, unweighted
estimate is strong on average over shifts.  It does not select one
prescribed \(h_0\).  An exceptional shift may be the same \(h_0\) for
every \(X\) while \eqref{eq:lit-mrt-shift-average} remains true.
Nor does the theorem directly carry the growing two-slope geometry
and outer mask of \eqref{eq:affine-literal-correlation}.

\subsection{Almost-all scales}

Tao and Ter\"av\"ainen proved unweighted cases of Chowla and Elliott
at all scales outside a set of zero logarithmic density
\citep{TaoTeravainen2019}.  For fixed Liouville shifts, the stated
Chowla cases include odd \(k\) and \(k=2\).  In particular, their
binary result is much closer to the ordinary fixed-shift correlation than
\eqref{eq:lit-tao-log}.  The remaining quantifier is nevertheless
essential: a prescribed sparse family of physical scales may lie
inside a zero-logarithmic-density exceptional set.  A block theorem
that must hold at every selected scale cannot discard that family
without a separate scale-selection or interpolation argument.

\subsection{Almost-all short intervals}

The short-interval theory of Matom\"aki and Radziwi{\l}{\l} gives
mean-value control for multiplicative functions on almost all short
intervals \citep{MatomakiRadziwill2016}.  Such results are a central
input to later correlation theorems.  A literal affine fiber,
however, has a prescribed origin determined by
\((\ell,j,s,v,\widetilde d_0)\).  An exceptional set of interval
origins may contain that prescribed origin.  In addition, the bound
\(|I|=O(1)\) permitted by \eqref{eq:affine-fiber-length} supplies no
asymptotic short-interval parameter.

The same paper also proves a fixed-shift ordinary bound away from the
trivial extremum for the mean of
\(\lambda(n)\lambda(n+1)\): its absolute value is at most
\(1-\delta\) for some \(\delta>0\).  This is an important
nontrivial-correlation theorem, but it is not an \(o(X)\) cancellation
statement, a power-saving estimate, or a theorem uniform over the
growing affine family in \eqref{eq:affine-literal-correlation}.

\clearpage
\subsection{The quantifier table}

\begin{table}[ht]
\centering
\small
\renewcommand{\arraystretch}{1.18}
\begin{tabularx}{\textwidth}{
  >{\raggedright\arraybackslash}p{0.18\textwidth}
  >{\raggedright\arraybackslash}p{0.28\textwidth}
  >{\raggedright\arraybackslash}X}
\toprule
Result & Native strength & Missing literal input\\
\midrule
Tao 2016
& Fixed nonproportional affine forms; logarithmic weight; general
two-point Elliott form
& Ordinary/dyadic weight, uniform growing coefficients, short-fiber
and complete outer-reassembly bounds\\
\addlinespace
Matom\"aki--Radziwi{\l}{\l}--Tao 2015
& Ordinary correlations averaged over \(h_1,\ldots,h_k\)
& Selection of the prescribed \(h_0\), the physical two-slope
family, and the literal mask\\
\addlinespace
Tao--Ter\"av\"ainen 2019
& Unweighted correlations at scales outside a zero-log-density set
& Every prescribed physical scale, growing affine coefficients, and
a fixed-power reassembly rate\\
\addlinespace
Matom\"aki--Radziwi{\l}{\l} 2016
& Multiplicative mean values on almost all short intervals
& The prescribed fiber origin, two-sign affine product, and
\(O(1)\)-length fibers\\
\bottomrule
\end{tabularx}
\caption{The theorem may be strong in its native quantifiers while
still failing to imply the literal fixed-\(h_0\) packet estimate.}
\label{tab:quantifier-audit}
\end{table}

\subsection{Elementary localization barriers}

\begin{proposition}[Averages do not select a prescribed member]
\label{prop:lit-average-selection}
Let \(h_0\) be fixed.  A bound of the form
\[
 \frac1H\sum_{h\le H}|B_X(h)|=o(1)
\]
does not logically imply \(B_X(h_0)=o(1)\).  Likewise, a statement
holding outside a zero-logarithmic-density set of scales does not
logically imply the statement along a prescribed sparse sequence of
scales.
\end{proposition}

\begin{proof}
For the first assertion, set \(B_X(h_0)=1\) and \(B_X(h)=0\) for
\(h\ne h_0\).  The average is \(1/H=o(1)\), while the selected value
is one.  For the second, place every prescribed sparse scale in the
exceptional set.  For example, the set
\(\{2^k:k\ge0\}\) has zero logarithmic density since
\[
 \frac{1}{\log X}
 \sum_{\substack{2^k\le X}}\frac1{2^k}
 \longrightarrow0.
\]
The almost-all-scale assertion may therefore hold off that set while
failing at every selected dyadic scale.
\end{proof}

\begin{remark}[Logical countermodel versus arithmetic counterexample]
\Cref{prop:lit-average-selection} is a statement about quantifiers.
It does not assert that the actual M\"obius correlation is exceptional
at \(h_0\) or at dyadic scales.  It shows only that an additional
localization theorem is required before an averaged result can be
invoked for the literal packet.
\end{remark}

\begin{corollary}[What a callable theorem must match]
\label{cor:lit-callable-checklist}
To enter \eqref{eq:affine-global-interface} without an unreturned
average, an analytic theorem or a proved auxiliary transfer must
explicitly match:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.5em]
 \item the same fixed \(h_0\);
 \item the actual ranges of \(a,s,\widetilde d_0,\widetilde u_0\);
 \item the ordinary physical interval and its weight;
 \item long and bounded-length fibers;
 \item periodic, coprimality, and joint-mask factors;
 \item a uniform rate surviving the complete outer sum.
\end{enumerate}
Failure to match one item may still yield a valid frozen, averaged, or
restricted-sector theorem, but not the literal \(Z_X\) bound.
\end{corollary}
