\begin{abstract}
TPC--74 resolved every direct off-diagonal missing-native Gram entry into
literal primitive kernels \(L_{mn,q}(u,v)\), where the content
\(q\) divides the fixed-shift difference
\(\Delta_{mn}=h_0(n-m)\).  TPC--75 then made the cost of an arbitrary
nonprimitive completion exactly primal--dual.  The unrestricted optimum,
however, need not preserve any \(q\)-slice provenance and therefore does
not yet identify a physical construction rule.

This paper develops a provenance-compatible completion class for this
TPC chain.
For a fixed nonzero \(\Delta\), define the divisor-poset content lift
\[
 F^{\rm Z}(du,dv)
 =
 \sum_{d\mid q\mid|\Delta|}L_q(u,v),
 \qquad (u,v)=1.
\]
At \(d=1\) it equals the exact post-\(q\)-aggregation primitive datum, so
it is a legal analytic completion.  Its diagonal profiles are the zeta
transform on the divisor lattice.  We prove the exact inversion
\[
 L_q(u,v)
 =
 \sum_{q\mid d\mid|\Delta|}
 \mu(d/q)F^{\rm Z}(du,dv),
\]
so the lift retains, rather than smooths away, the complete content
decomposition.

The same formula gives an exact diagonal filtration.  If
\((x,y)=r\) and \(x=ru,y=rv\), then
\[
 (F^{\rm Z})^{[a]}(x,y)
 =
 \sum_{ar\mid q\mid|\Delta|}L_q(u,v).
\]
Consequently every auxiliary slice with \(a\nmid|\Delta|\) vanishes.
The high-diagonal tail is therefore supported only on actual divisors of
the fixed row-pair difference, although no smallness of its mass is
asserted.

We next introduce all provenance filters
\[
 F^W(du,dv)
 =
 \sum_{d\mid q\mid|\Delta|}w_{d,q}L_q(u,v),
 \qquad w_{1,q}=1.
\]
This affine class contains the primitive zero completion and the zeta
lift.  Its optimal full divisor--variation cost is attained and has the
reduced exact dual
\[
 \min_\theta\|A_D(F^0+B_L\theta)\|_1
 =
 \max_{\substack{\|z\|_\infty\le1\\B_L^*A_D^*z=0}}
 \operatorname{Re}\langle z,A_DF^0\rangle.
\]
Thus a provenance-compatible fill and a content-flow obstruction are
again exact alternatives.

The construction is attached to the complete literal fixed-\(h_0\)
carrier with its original raw normalization.  It proves neither that the
zeta lift improves the zero completion nor that the optimal provenance
matrix has small Perron radius.  No fixed-\(2\), parity-breaking,
prime-pair, or twin-prime conclusion is claimed.
\end{abstract}
