\section{Countermodels and exact comparison examples}
\label{sec:countermodels}

For this section write
\[
 M(x)=\sum_{n\le x}\mu(n),\qquad
 \Delta_{12}F(x,y)
 =
 F(x,y)-F(x+1,y)-F(x,y+1)+F(x+1,y+1),
\]
and retain the TPC--75 notation
\(\cC_D(F)=\|A_DF\|_1\) for the complete low-plaquette plus exact-tail
cost.

\subsection{The zeta lift can beat the zero completion}

Take \(U=V=4\), \(D=1\), and \(\Delta=12\).  Put all content in the
rectangle \(B=[1,4]^2\).  For every primitive
\((u,v)\in B\), set
\[
 t(u,v)=\left\lfloor\frac4{\max\{u,v\}}\right\rfloor,
 \qquad
 G_d(u,v)=\one_{d\mid12}\one_{d\le t(u,v)},
\]
and define the literal slices by the exact inverse transform
\[
 L_q(u,v)
 =
 \sum_{q\mid d\mid12}\mu(d/q)G_d(u,v).
\]
If \(L_q(u,v)\ne0\), then necessarily \(q\le t(u,v)\); hence every
inserted point \((du,dv)\), \(d\mid q\), still lies in \(B\).
Thus this is a full lift on the declared rectangle, not a truncation.
By construction its zeta profiles are the displayed \(G_d\), so the
zeta lift is the constant \(4\)-by-\(4\) rectangle:
\[
 F^{\rm Z}(x,y)=1
 \qquad(1\le x,y\le4).
\]
Its primitive aggregate is also identically \(1\) on the primitive
sites of \(B\).

For the zero completion, the \(d=1\) plaquette terms with nonzero cost
are
\[
\begin{array}{c|cccccccc}
(x,y)&(1,1)&(1,3)&(1,4)&(3,1)&(3,3)&(3,4)&(4,1)&(4,3)\\
\hline
|M(x)M(y)\Delta_{12}F^0(x,y)|
&1&1&1&1&2&1&1&1.
\end{array}
\]
Its higher diagonal tail vanishes, so
\[
 \cC_1(F^0)=9.
\]
For the constant zeta rectangle, only the terminal \(d=1\) plaquette
contributes, with cost \(1\).  Its exact tail has one unit contribution
at \(a=2\) and one at \(a=3\).  Hence
\[
 \cC_1(F^{\rm Z})=1+1+1=3<9.
\]
This is an exact example in the full cost, not merely a comparison of
\(d=1\) variation.

\subsection{The zero completion can beat the zeta lift}

Take \(D=1\), \(\Delta=2\), one primitive atom at \((1,1)\), and
\[
 L_1(1,1)=1,
 \qquad
 L_2(1,1)=-1.
\]
The aggregate primitive datum is zero, so \(F^0=0\) and
\(\cC_1(F^0)=0\).  But
\[
 F^{\rm Z}(2,2)=L_2(1,1)=-1.
\]
The tail coordinate \(a=2,x=y=1\) has unit weight, hence
\[
 \cC_1(F^{\rm Z})\ge1.
\]
Therefore neither distinguished completion universally dominates the
other.

\subsection{Zeta inversion is not smoothing}

If \(L_q(u_0,v_0)=1\) for every \(q\mid|\Delta|\) at one primitive
coordinate, then
\[
 G_d(u_0,v_0)
 =
 \#\{q:d\mid q\mid|\Delta|\}.
\]
The total absolute profile mass is
\[
 \sum_{d\mid|\Delta|}|G_d(u_0,v_0)|
 =
 \sum_{q\mid|\Delta|}\tau(q),
\]
whereas the literal slice mass is only \(\tau(|\Delta|)\).  The zeta
transform is an invertible provenance expansion, not a contraction.

\subsection{Few diagonal indices need not mean a small tail}

Take one large coefficient \(A\) at a prime content \(q>D\), supported
at the primitive coordinate \((1,1)\).  The
zeta lift places \(A\) on the layer \(d=q\).  The tail coordinate
\((d,x,y)=(q,1,1)\) then has weight
\[
 |\mu(q)\mu(q)\mu(q)|=1
\]
and contributes \(|A|\), even though only one high diagonal index need
be active.  Sparsity of divisor indices and smallness of normalized mass
are different statements.

\subsection{Optimizing after aggregation is broader}

The unrestricted gauge \(\gamma_D(k)\) sees only the aggregate primitive
datum \(k=\sum_qL_q\).  The provenance gauge also sees the decomposition
\((L_q)\).  Two slice families with the same aggregate can therefore
have the same unrestricted gauge but different provenance programs,
different zeta lifts, and different dual annihilators
\[
 B_{\boldsymbol L}^*A_D^*z=0.
\]
One may not use the cheaper decomposition unless it is the literal one
carried by the complete physical keys.

\subsection{A fill is not a new collision}

At \(d>1\), the number
\[
 F^W(du,dv)
\]
is an analytic copy of amplitudes already present at primitive
coordinates.  Counting it as an additional native key would change both
the Gram entry and the raw row mass.  The completion invariance theorem
allows the value only because the physical M\"obius functional samples
primitive sites.

\subsection{Pairwise filters are not a universal rule}

Let one shared real parameter \(t\) control two row pairs, with optimal
cost profiles
\[
 p_{12}(t)=|t|,
 \qquad
 p_{23}(t)=|1-t|.
\]
Each pair-dependent provenance optimum is zero, but a single filter pays
at least \(1/2\).  The exact independent factorization in
\cref{thm:provenance-factorization} cannot be re-labelled as a uniform
filter theorem.
