\section{The actual fixed-shift gate}
\label{sec:physical-gate}

\subsection{Literal specialization}

Fix one nonzero \(h_0\), one declared external block, both direct sides
through their proved orthogonal sum, and the complete TPC--74
missing-high key carrier.  For every active \(m<n\),
\[
 \Delta_{mn}=h_0(n-m)\ne0.
\]
The slices \(L_{mn,q}\) retain all complete native key labels and the raw
normalization
\[
 \frac1{\sqrt{W_M(m)W_M(n)}}.
\]
Here \(W_M(m)=W_m\) is the sum of the raw masses of all actual atoms on
both orthogonal direct sides in the declared TPC--74 block.  It is not
recomputed by side, degree, content, or support, and analytic copies at
\(d>1\) never enter \(W_m\).
They are aggregated in the physical primitive datum before any absolute
value:
\[
 k_{mn}=\sum_{q\mid|\Delta_{mn}|}L_{mn,q}.
\]

Choose \(B_{mn}\) to contain every actual primitive slice support and
every declared layer \(d\mid q\mid|\Delta_{mn}|\).  Fix \(D_{mn}\), with
transpose rectangle and equal cutoff on the reversed pair.  These choices
are made before the provenance optimization.

\subsection{What the divisor filtration closes}

The content lift now has three exact physical compatibilities:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.7em]
 \item every fill coefficient comes from an actual
       \(q\mid|h_0(n-m)|\) slice;
 \item every nonzero greatest-common-divisor layer satisfies
       \(d\mid|h_0(n-m)|\); and
 \item the entire lifted profile can be inverted back to the literal
       \(q\)-slices.
\end{enumerate}
No smooth ambient interpolation has these properties automatically.
They are L1 carrier statements because the \(L_{mn,q}\) are the actual
complete-key kernels of TPC--74.

\subsection{The remaining positive estimate}

Let \(Q^{\rm prov}_X\) be the complete matrix of optimal
provenance-filter costs on a growing physical family.  A positive
completion result requires an estimate such as
\[
 \rho(Q^{\rm prov}_X)\le\eta_X<1,
\]
or a fixed predeclared filter family with an equally strong complete
Perron bound.  Then TPC--75 gives the corresponding eigenvalue control
for the normalized missing-native Gram.

Neither
\[
 a\mid|h_0(n-m)|
 \qquad\text{nor}\qquad
 \tau(|h_0(n-m)|)=|h_0(n-m)|^{o(1)}
\]
proves that estimate.  The first is a support identity; the second is an
ambient divisor count.  The required quantity contains the actual
complex amplitudes, raw masses, row degrees, and restricted Mertens
weights.

\subsection{Negative outcomes}

There are three distinct stop rules.
\begin{enumerate}[label=\textup{(G\arabic*)},leftmargin=3.2em]
 \item If a dual content-flow matrix
       \(O_X^{\rm prov}\) has nonnegligible Perron radius, the entire
       declared provenance-filter class is too expensive at that scale.
 \item If the smaller actual absolute floor
       \(\rho(|\widetilde H_X|)\) is nonnegligible, every entrywise
       absolute completion architecture is blocked, including
       unrestricted completions.
 \item Neither obstruction lower-bounds the signed norm
       \(\|H_X\|\).  A signed phase, full-moment, or hybrid anchor/direct
       route remains logically open.
\end{enumerate}

\subsection{TPC--77 decision}

The next step is to exploit sparsity before attempting asymptotics.
For every actual row pair, form the bipartite incidence complex linking:
\[
 \text{free content weights}
 \longleftrightarrow
 \text{nonprimitive sites}
 \longleftrightarrow
 \text{plaquette/tail coordinates}.
\]
The next paper is planned to target exact component deletion and
primal/dual factorization, together with a certificate format in which
every finite census value is independently checked by matching fills and
charges.  Solver failure will not be called an obstruction, and finite
data will not be called L2 progress.

\subsection{Endpoint ledger}

Even a successful \(Q^{\rm prov}\) estimate does not close terminal
activation, represented-frame recovery, missing-mass comparison,
nuisance shorting, endpoint cells, or final packet reconstruction.  The
same strict endpoint rule remains: if total fixed-power loss reaches
\(1/400\), including equality, the current implication stops.
