\begin{abstract}
Let
\[
 S_N=\sum_{n\le N}a_n,\qquad
 L_N=\sum_{n\le N}\frac{a_n}{n},\qquad L_0=0.
\]
We isolate the exact discrete Tauberian interface between logarithmic
and ordinary cancellation.  Summation by parts gives the identity
\[
 \boxed{\quad
 S_N=NL_N-\sum_{m<N}L_m,\qquad
 \frac{S_N}{N}
 =L_N-\frac1N\sum_{m<N}L_m.
 \quad}
\]
Consequently ordinary cancellation is equivalent, with identical
rate, to the vanishing of the \emph{signed backward Ces\`aro defect}
of the unnormalized logarithmic primitive \(L\).  Convergence of
\(L_N\) is sufficient by Ces\`aro convergence, but boundedness is not.
Indeed, for
\[
 a_n=(-1)^k\qquad(2^k\le n<2^{k+1}),
\]
one has \(|a_n|=1\), \(L_N=O(1)\), and even
\[
 \frac{1}{\log\omega(x)}
 \sum_{x/\omega(x)<n\le x}\frac{a_n}{n}\longrightarrow0
\]
for every \(1\le\omega(x)\le x\) with \(\omega(x)\to\infty\), whereas
\(S_N/N\) has subsequential limits \(1/3\) and \(-1/3\).
Thus normalized logarithmic cancellation alone has no
structure-free implication for the ordinary mean.

We then give quantitative positive criteria.  The absolute Ces\`aro
oscillation dominates \(|S_N|/N\).  If
\[
 \omega_N(L):=
 \max_{\lfloor N/2\rfloor\le m\le N}|L_N-L_m|
\longrightarrow0,
\]
then \(S_N/N\to0\); a power bound
\(\omega_N(L)\ll N^{-\eta}\), \(0<\eta<1\), transfers with the same
power.  A second criterion uses the dyadic logarithmic variation
\[
 V_k=\sum_{2^k\le n<2^{k+1}}\frac{|a_n|}{n}.
\]
We prove an explicit geometrically weighted convolution bound, hence
\(V_k\to0\) also suffices.

Finally, we audit what these identities do and do not supply for the
literal growing fixed-\(h_0\) affine M\"obius packet.  The exact
Tauberian statements and countermodel are \(\Lzero\).  Their faithful
attachment to every physical fiber and the complete outer
reassembly is an \(\Lone\) certificate.  Establishing the required
uniform terminal cancellation for the actual growing affine family
is an unproved \(\Ltwo\) arithmetic problem.  No parity breach,
prime-pair lower bound, or twin-prime conclusion is claimed.
\end{abstract}
