\section{Quantifier audit of available arithmetic theorems}
\label{sec:literature-quantifiers}

The Tauberian identity is exact only after the same ordered
coefficient sequence has been fixed.  A theorem that changes the
forms, shift, scale, interval origin, or outer averaging measure does
not automatically control its signed Ces\`aro defect.

\subsection{Fixed-form logarithmic correlation}

For fixed \(a_1,a_2\in\N\) and
\(b_1,b_2\in\Z_{\ge0}\) with
\(a_1b_2-a_2b_1\ne0\), Tao proved
\begin{equation}
 \sum_{x/\omega(x)<n\le x}
 \frac{\lambda(a_1n+b_1)\lambda(a_2n+b_2)}n
 =o(\log\omega(x)),
\label{eq:tao-logarithmic}
\end{equation}
where \(1\le\omega(x)\le x\) and \(\omega(x)\to\infty\)
\citep{Tao2016LogChowla}.  This is a genuine two-point cancellation
theorem in its stated logarithmic setting.

Equation \eqref{eq:tao-logarithmic} does not by itself verify
\(\omega_N(L)\to0\).  Its ratio \(\omega(x)\) must grow, its
conclusion is normalized by \(\log\omega(x)\), and the affine
coefficients are fixed.  The literal packet instead contains
polynomially growing slopes and intercepts, fixed-ratio terminal
windows, actual masks, and a quantitative outer sum.  The dyadic
counterexample proves that this mismatch cannot be repaired for
arbitrary bounded sequences by a Tauberian black box alone.

\subsection{Averaged shifts, almost-all scales, and short intervals}

For fixed \(k\) and \(1\le H=H(X)\le X\) with \(H(X)\to\infty\),
Matom\"aki, Radziwi{\l}{\l}, and Tao proved
\begin{equation}
 \sum_{h_1,\ldots,h_k\le H}
 \left|
 \sum_{n\le X}\lambda(n+h_1)\cdots\lambda(n+h_k)
 \right|
 =o(H^kX)
\label{eq:mrt-averaged-shifts}
\end{equation}
\citep{MatomakiRadziwillTao2015}.  This is ordinary cancellation
averaged over shifts; it does not select one prescribed \(h_0\).

Tao and Ter\"av\"ainen proved unweighted Chowla and Elliott cases at
all scales outside a set of zero logarithmic density.  For fixed
Liouville shifts, their stated Chowla cases include odd order and
order two \citep{TaoTeravainen2019}.  A prescribed sparse sequence
of physical scales can lie inside the exceptional set, so an
additional scale-localization theorem is required.

Matom\"aki and Radziwi{\l}{\l} proved mean-value control for
multiplicative functions on almost all short intervals, including
M\"obius cancellation on almost all intervals whose length tends to
infinity arbitrarily slowly \citep{MatomakiRadziwill2016}.  A
physical affine fiber has a prescribed origin, and some literal
fibers have \(O(1)\) length.  Neither feature is selected by an
almost-all-origin theorem.  Moreover, the cited result concerns the
mean of one multiplicative function; it is not itself a theorem for
the two-sign affine product in
\eqref{eq:literal-affine-sequence}.

\subsection{Principal quantifier mismatches}

\begin{table}[htbp]
\centering
\small
\renewcommand{\arraystretch}{1.16}
\begin{tabularx}{\textwidth}{
 >{\raggedright\arraybackslash}p{0.18\textwidth}
 >{\raggedright\arraybackslash}p{0.28\textwidth}
 >{\raggedright\arraybackslash}X}
\toprule
Input & Native quantifiers & Missing literal certificate\\
\midrule
Tao 2016
& Fixed nonproportional forms; \(1/n\) weight; growing window ratio
& Fixed-ratio \(o(1)\) logarithmic increments, growing coefficients,
actual masks, outer rate\\
\addlinespace
MRT 2015
& Ordinary correlations averaged over \(h_1,\ldots,h_k\)
& Selection of the prescribed \(h_0\), growing two-slope forms,
actual masks and weights, and outer reassembly\\
\addlinespace
TT 2019
& Ordinary correlations outside a zero-log-density set of scales
& Every prescribed physical scale, growing forms, literal masks and
weights, outer reassembly, and a uniform fixed-power rate\\
\addlinespace
MR 2016
& One multiplicative function on almost all short-interval origins
& The two-sign affine product, prescribed origin, growing forms,
literal masks and weights, outer reassembly, and \(O(1)\)-length
fibers\\
\bottomrule
\end{tabularx}
\caption{A theorem can be strong in its native quantifiers without
controlling the literal signed Ces\`aro defect.}
\label{tab:quantifier-mismatch}
\end{table}

\begin{proposition}[Averages do not select a literal member]
\label{prop:average-selection}
An estimate
\[
 \frac1H\sum_{h\le H}|B_X(h)|=o(1)
\]
does not logically imply \(B_X(h_0)=o(1)\) for one prescribed
\(h_0\).  Likewise, a theorem outside a zero-logarithmic-density set
of scales does not logically imply its conclusion along a prescribed
sparse scale sequence.
\end{proposition}

\begin{proof}
For the first statement set \(B_X(h_0)=1\) and
\(B_X(h)=0\) otherwise.  For the second, put the prescribed sparse
sequence into the exceptional set.  For example,
\(\{2^k:k\ge0\}\) has zero logarithmic density because
\[
 \frac1{\log X}\sum_{2^k\le X}\frac1{2^k}\longrightarrow0.
\]
\end{proof}

\begin{remark}[Logical versus arithmetic countermodels]
\label{rem:quantifier-countermodel}
\Cref{prop:average-selection} classifies a quantifier gap.  It does
not assert that an actual M\"obius correlation is exceptional at
\(h_0\) or at the selected physical scales.
\end{remark}
