\section{The literal growing fixed-\texorpdfstring{\(h_0\)}{h0} interface}
\label{sec:physical-interface}

The exact Tauberian theorem is useful only after the physical
coefficient has been retained.  We therefore formulate the
crosswalk without claiming that its arithmetic hypothesis is known.

\subsection{The affine fibers}

After one physical column is opened, the literal TPC-33 affine
correlation has the schematic form
\begin{equation}
 \mathfrak a_{\theta,X}(r)
 =
 \mu(\widetilde d_{\theta,X}+s_{\theta,X}r)
 \mu(\widetilde u_{\theta,X}+\alpha_{\theta,X}r)
 M_{\theta,X}(r)W_{\theta,X}(r),
\label{eq:literal-affine-sequence}
\end{equation}
where \(M_{\theta,X}\) contains the actual coprimality, residue, and
joint masks, \(W_{\theta,X}\) contains the physical smooth and
logarithmic weights, and
\begin{equation}
 s_{\theta,X}\widetilde u_{\theta,X}
 -\alpha_{\theta,X}\widetilde d_{\theta,X}=h_0\ne0.
\label{eq:fixed-determinant}
\end{equation}
The parameter \(\theta\) also records the opposite row,
polarization, divisor layer, interval component, and native keys.
The slopes and intercepts may grow with \(X\).

For an ordered fiber of length \(N_{\theta,X}\), absorb every literal
local factor into a sequence \(b_{\theta,X}(n)\), \(1\le n\le
N_{\theta,X}\), and define
\begin{equation}
 S_{\theta,X}(N)=\sum_{n\le N}b_{\theta,X}(n),\qquad
 L_{\theta,X}(N)=\sum_{n\le N}\frac{b_{\theta,X}(n)}n.
\label{eq:fiber-primitives}
\end{equation}
This definition does not assert that an existing logarithmic
correlation theorem applies to \(b_{\theta,X}\).

\subsection{An exact conditional certificate}

\begin{theorem}[Literal Tauberian reassembly certificate]
\label{thm:literal-certificate}
Suppose the complete raw hard zero mode has an exact reassembly
\begin{equation}
 Z_X=
 \sum_{\theta\in\Theta_X}
 c_{\theta,X}
 S_{\theta,X}(N_{\theta,X})
 +E_{\mathrm{content},X},
\label{eq:literal-reassembly}
\end{equation}
with all native keys and both polarizations retained.  Then
\begin{equation}
 |Z_X|
 \le
 \sum_{\theta\in\Theta_X}
 |c_{\theta,X}|N_{\theta,X}
 \left|
 \cT_{N_{\theta,X}}(L_{\theta,X})
 \right|
 +|E_{\mathrm{content},X}|.
\label{eq:literal-defect-bound}
\end{equation}
The signed defect in \eqref{eq:literal-defect-bound} may be replaced
by the absolute oscillation \(\cA_N\), the right side of
\eqref{eq:geometric-local-global}, or the right side of
\eqref{eq:variation-convolution}.
\end{theorem}

\begin{proof}
By \cref{thm:sharp-criterion},
\[
 S_{\theta,X}(N_{\theta,X})
 =
 N_{\theta,X}
 \cT_{N_{\theta,X}}(L_{\theta,X}).
\]
Insert this identity into \eqref{eq:literal-reassembly}, then take
one triangle inequality after the complete reassembly.  The
alternative bounds follow from
\cref{cor:absolute-sufficient,thm:local-to-global,thm:variation-convolution}.
\end{proof}

\begin{remark}[What is exact and what is conditional]
\label{rem:exact-conditional}
The passage from \eqref{eq:literal-reassembly} to
\eqref{eq:literal-defect-bound} is finite \(\Lzero\) algebra.  The
claim that \eqref{eq:literal-reassembly} is the actual raw physical
packet, with no missing mask or renormalization, is an \(\Lone\)
verification.  A uniform power bound for the defects of the growing
M\"obius family \eqref{eq:literal-affine-sequence} is an \(\Ltwo\)
arithmetic estimate and is not proved here.
\end{remark}

\begin{remark}[Short fibers]
\label{rem:short-fibers}
The asymptotic condition \(\omega_N(L)\to0\) says nothing about a
fiber whose length stays \(O(1)\).  Such fibers must be returned by
an exact finite estimate or controlled after a separate outer
reassembly.  Their mere cardinality is not a cancellation theorem.
\end{remark}

\begin{remark}[Weights and origins]
\label{rem:weights-origins}
The harmonic factor \(1/n\) in \eqref{eq:fiber-primitives} is tied to
the chosen local ordering.  Partial summation can transfer some
smooth weights only when the required prefix estimates are uniform.
It cannot silently change the prescribed interval origin, delete the
joint mask, or freeze coefficients that grow with \(X\).
In particular, the \(1/n\) in a fixed-form logarithmic theorem is
attached to the original arithmetic variable.  After translating a
physical fiber with origin \(r_{\theta,X}\), the inherited weight is
\(1/(r_{\theta,X}+n)\), not \(1/n\).  Replacing one by the other
requires an exact change of variables or a uniform partial-summation
lemma for the same prefixes; it is not a formal relabeling.
\end{remark}

\subsection{Fixed-power and endpoint ledger}

The exact identity itself spends no fixed power.  A useful physical
application, however, must prove a rate that survives the full outer
sum.  For example, if
\[
 \omega_M(L_{\theta,X})
 \ll M^{-\eta+o(1)},\qquad 0<\eta<1,
\]
uniformly in every literal long fiber and every relevant prefix
\(2\le M\le N_{\theta,X}\), then
\cref{cor:power-transfer} gives the same per-fiber power.  Losses
from the number and size of fibers, masks, short-fiber treatment,
content completion, and calibrated downstream drift remain to be
charged separately.

At the critical physical scales
\[
 Q=X^{267/400+o(1)},\qquad J=X^{133/400+o(1)},
\]
the recorded two-exponent transfer takes the form
\begin{equation}
 |Z_X|\le X^{-\eta_Z+o(1)}Q^2,\qquad
 D_X\ge X^{-\lambda_D+o(1)}Q^3J^2
\label{eq:two-exponent-input}
\end{equation}
and yields
\begin{equation}
 \frac{|Z_X|^2}{D_X}
 \le X^{1/400+\lambda_D-2\eta_Z+o(1)}.
\label{eq:two-exponent-output}
\end{equation}
This is a sufficient ledger, not a claim that the displayed
exponents are optimal; see TPC-81 and TPC-82
\citep{WangTPC81,WangTPC82}.
Retaining the baseline exponent in
\eqref{eq:two-exponent-output} requires the determinant-flatness
compatibility
\begin{equation}
 \lambda_D\le 2\eta_Z.
\label{eq:determinant-flatness-ledger}
\end{equation}
This is one ledger: it compares the certified lower loss for \(D_X\)
with the certified cancellation gain for \(Z_X\).

\begin{definition}[Strict physical endpoint rule]
\label{def:strict-endpoint}
Let \(\Lambda_{\mathrm{phys}}\) be the sum of all fixed-power losses
actually incurred by localization, coefficient growth, masks,
short-fiber treatment, outer reassembly, content completion,
dictionary transfer, and downstream calibrated drift.  A proposed
route continues only if
\begin{equation}
 \boxed{\qquad \Lambda_{\mathrm{phys}}<\frac1{400}. \qquad}
\label{eq:strict-endpoint}
\end{equation}
Equality or excess is a stop condition.
This is a second, independent ledger.  A loss already included in
\(\lambda_D-2\eta_Z\) is not charged a second time; an interface or
downstream loss absent from those exponents must be entered in
\(\Lambda_{\mathrm{phys}}\).
\end{definition}

\begin{proposition}[Success checklist]
\label{prop:success-checklist}
A logarithmic-to-ordinary advance qualifies as a literal \(\Lone\)
or \(\Ltwo\) input only if it returns:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.5em]
 \item the same fixed \(h_0\) and actual growing affine forms;
 \item the ordinary physical fibers with their prescribed origins;
 \item all periodic, coprimality, residue, smooth-weight, and
 joint-mask factors;
 \item both polarizations and every native outer key;
 \item a separate exact or outer estimate for bounded-length fibers;
 \item a quantitative signed-defect or stronger local bound uniform
 over the active family and all prefixes used by the dyadic
 recursion;
 \item a complete fixed-power ledger satisfying
 \eqref{eq:strict-endpoint}.
\end{enumerate}
\end{proposition}

\begin{proof}
Items (i)--(v) ensure that the sequence in
\eqref{eq:fiber-primitives} is the literal coefficient rather than a
frozen or averaged substitute.  Item (vi) supplies the hypothesis of
\cref{thm:literal-certificate}; qualitative normalized logarithmic
cancellation alone is ruled out by
\cref{cor:black-box-failure}.  Item (vii) is the endpoint rule.
\end{proof}
