\section{A shifted-divisor square which removes the one-prime modes}
\label{sec:shifted-square-design}

This section isolates an algebraic point which is useful later and easy to
misstate.  An ordinary Selberg divisor square supported on the same primes
that define a rough set becomes constant on that rough set.  Moving the
divisor primes outside the roughness window avoids the collapse, but creates
a separate distribution interface.  A tensor product of nonconstant local
weights also cannot remove every one-prime Fourier mode.  We therefore use a
different object: a square built from the shifted divisibility events
$p\mid a-\rho$.  Its coefficients can be chosen so that its centered part has
exactly two-prime Fourier support.

The phrase \emph{shifted-divisor Selberg-form square} below refers only to
this quadratic shape.  It is not the standard same-window Selberg weight
$\bigl(\sum_{d\mid n}\lambda_d\bigr)^2$, and it is not a prime-detecting
weight.  All statements in this section are finite identities on residue
groups.

\subsection{Why an ordinary same-window divisor square collapses}
\label{subsec:same-window-collapse}

Let $\mathcal P$ be a finite set of primes and put
\begin{equation}
 Q=\prod_{p\in\mathcal P}p,
 \qquad
 G=(\mathbb Z/Q\mathbb Z)^\times.
 \label{eq:wt-Q-and-G}
\end{equation}
No asymptotic restriction on $\mathcal P$ is needed in the first three
results.

\begin{proposition}[Same-window collapse]
\label{prop:wt-same-window-collapse}
Let $(\lambda_d)_{d\mid Q}$ be arbitrary complex coefficients and set
\begin{equation}
 \nu_{\lambda,Q}(n)
 =\left|\sum_{\substack{d\mid Q\\d\mid n}}\lambda_d\right|^2.
 \label{eq:wt-ordinary-selberg-square}
\end{equation}
Then
\begin{equation}
 \nu_{\lambda,Q}(n)=|\lambda_1|^2
 \qquad\text{whenever }(n,Q)=1.
 \label{eq:wt-collapse-identity}
\end{equation}
Consequently, the restriction of $\nu_{\lambda,Q}$ to $G$ is constant and
its centered multiplicative Fourier transform is identically zero.  The
same conclusion holds if the divisor sum is further restricted by $d\le D$
for any $D\ge1$.
\end{proposition}

\begin{proof}
If $d\mid Q$, $d\mid n$, and $(n,Q)=1$, then $d=1$.  Thus only the
$d=1$ summand remains in \eqref{eq:wt-ordinary-selberg-square}.  A cutoff on
$d$ does not alter this observation.
\end{proof}

This is an exact support obstruction, not a failure to optimize the
coefficients $\lambda_d$.  In particular, a normalized choice
$\lambda_1=1$ gives the constant weight one on the $Q$-rough support and
cannot be tuned there to cancel selected nontrivial characters.

There is a legitimate off-window alternative, but it changes the analytic
problem.  The following elementary identity makes the interface explicit.

\begin{lemma}[Off-window interface]
\label{lem:wt-off-window-interface}
Let $R$ be squarefree and define
\begin{equation}
 R_{\mathrm{off}}
 =\frac{R}{(R,Q)}
 =\prod_{\substack{\ell\mid R,\ \ell\ \mathrm{prime}\\ \ell\nmid Q}}\ell,
 \label{eq:wt-off-window-modulus}
\end{equation}
For arbitrary coefficients
$(\lambda_d)_{d\mid R}$ and every $(n,Q)=1$,
\begin{equation}
 \left|\sum_{\substack{d\mid R\\d\mid n}}\lambda_d\right|^2
 =
 \left|\sum_{\substack{d\mid R_{\mathrm{off}}\\d\mid n}}
       \lambda_d\right|^2.
 \label{eq:wt-off-window-reduction}
\end{equation}
In particular, only primes outside $\mathcal P$ can make this ordinary
divisor square vary on the $Q$-rough set.

Moreover, if the right side of \eqref{eq:wt-off-window-reduction} is denoted
by $\nu_{\mathrm{off}}(n)$, then for every $F:G\to\mathbb C$,
\begin{align}
 &\frac{1}{\varphi(Q)R_{\mathrm{off}}}
  \sum_{\substack{n\bmod QR_{\mathrm{off}}\\(n,Q)=1}}
  F(n\bmod Q)\nu_{\mathrm{off}}(n) \notag\\
 &\qquad=
 \left(\frac1{\varphi(Q)}\sum_{a\in G}F(a)\right)
 \left(\frac1{R_{\mathrm{off}}}
       \sum_{x\bmod R_{\mathrm{off}}}\nu_{\mathrm{off}}(x)\right).
 \label{eq:wt-complete-crt-factorization}
\end{align}
\end{lemma}

\begin{proof}
A divisor of $n$ cannot contain a prime which divides $Q$, proving
\eqref{eq:wt-off-window-reduction}.  Since
$(Q,R_{\mathrm{off}})=1$, the Chinese remainder theorem identifies the
summation set in \eqref{eq:wt-complete-crt-factorization} with
$G\times\mathbb Z/R_{\mathrm{off}}\mathbb Z$, on which the two factors of
the summand depend on separate coordinates.
\end{proof}

Thus an off-window divisor square has a nontrivial role only after one
controls the joint distribution of the observation interval in the
$Q$-coordinate and the $R_{\mathrm{off}}$-coordinate.  Over the complete
CRT product it is independent of every centered function of the
$Q$-coordinate.  On an incomplete interval the difference from
\eqref{eq:wt-complete-crt-factorization} is a genuine discrepancy or
character-sum problem; it is not supplied by the Selberg-form algebra.

\subsection{A tensor-product no-go statement}
\label{subsec:tensor-no-go}

Write $G\cong\prod_{p\in\mathcal P}\mathbb F_p^\times$ and use normalized
counting measure on every factor.  For $f:G\to\mathbb C$ our Fourier
convention is
\begin{equation}
 \widehat f(\chi)
 =\mathbb E_{a\in G}f(a)\overline{\chi(a)},
 \qquad
 f(a)=\sum_{\chi\in\widehat G}\widehat f(\chi)\chi(a).
 \label{eq:wt-fourier-convention}
\end{equation}
The support of $\chi=\bigotimes_p\chi_p$ is
\begin{equation}
 \operatorname{supp}(\chi)
 =\{p\in\mathcal P:\chi_p\ne\mathbf1\}.
 \label{eq:wt-character-support}
\end{equation}
A one-prime mode is a character whose support has cardinality one.

\begin{proposition}[Tensor-product no-go]
\label{prop:wt-tensor-no-go}
For each $p\in\mathcal P$, let
$v_p:\mathbb F_p^\times\to\mathbb R_{\ge0}$ have positive mean $m_p$, and put
\begin{equation}
 V(a)=\prod_{p\in\mathcal P}v_p(a_p),
 \qquad
 m=\mathbb E_G V=\prod_{p\in\mathcal P}m_p,
 \qquad
 V^\circ=V/m-1.
 \label{eq:wt-product-weight}
\end{equation}
If every one-prime Fourier coefficient of $V^\circ$ vanishes, then every
$v_p$ is constant.  Hence a nonconstant tensor-product local weight cannot
annihilate all one-prime modes.
\end{proposition}

\begin{proof}
If $\chi$ is nontrivial only at $p$, Fourier factorization gives
\begin{equation}
 \widehat{V^\circ}(\chi)
 =\frac{\widehat v_p(\chi_p)}{m_p}.
 \label{eq:wt-product-one-prime-coefficient}
\end{equation}
The assumed vanishing therefore removes every nontrivial Fourier
coefficient of every $v_p$.  Fourier inversion on
$\mathbb F_p^\times$ makes each $v_p$ constant.
\end{proof}

For example, for any residue vector $\rho$, the raw local avoidance indicator
$\prod_p(1-\mathbf1_{a_p=\rho_p})$ is a nonconstant tensor product and retains
one-prime modes.  Cross-prime terms are therefore necessary for the exact
annihilation sought here.

\subsection{The shifted-divisor quadratic design}
\label{subsec:shifted-quadratic-design}

Assume from now on that every $p\in\mathcal P$ is at least $5$.  Fix a unit
residue vector $\rho=(\rho_p)_{p\in\mathcal P}\in G$ and define
\begin{equation}
 X_{p,\rho}(a)=\mathbf1_{a_p=\rho_p}
            =\mathbf1_{p\mid a-\rho},
 \qquad
 \theta_p=\mathbb E_G X_{p,\rho}=\frac1{p-1},
 \qquad
 Y_{p,\rho}=X_{p,\rho}-\theta_p.
 \label{eq:wt-X-theta-Y}
\end{equation}
In the divisibility notation, $\rho$ denotes any CRT lift of the residue
vector.  Set
\begin{equation}
 A=\sum_{p\in\mathcal P}\frac1{p-3},
 \qquad
 C=\frac2{1+2A},
 \qquad
 t_p=C\frac{p-1}{p-3},
 \label{eq:wt-designed-coefficients}
\end{equation}
and introduce the nonnegative square
\begin{equation}
 W_\rho(a)=\left(1-\sum_{p\in\mathcal P}t_pX_{p,\rho}(a)\right)^2.
 \label{eq:wt-shifted-square}
\end{equation}
It is a local majorant for the finite residue-avoidance event:
\begin{equation}
 W_\rho(a)\ge
 \prod_{p\in\mathcal P}\bigl(1-X_{p,\rho}(a)\bigr).
 \label{eq:wt-local-majorant}
\end{equation}
Indeed, both sides equal one when every $X_{p,\rho}$ is zero, while otherwise
the right side is zero and the left side is a square.  This observation is
only about avoidance of one residue modulo each $p$; it does not majorize or
detect the primes.

\begin{theorem}[Exact pair-only coordinate decomposition]
\label{thm:wt-pair-only-decomposition}
Let
\begin{equation}
 \mu=\mathbb E_G W_\rho
 =\frac{C^2}{4}
  +\sum_{p\in\mathcal P}t_p^2\theta_p(1-\theta_p)>0
 \label{eq:wt-mean-mu}
\end{equation}
and $U_\rho=W_\rho/\mu-1$.  Then the pointwise identities
\begin{align}
 W_\rho-\mu
&=2\sum_{\substack{p,q\in\mathcal P\\p<q}}
       t_pt_qY_{p,\rho}Y_{q,\rho},
 \label{eq:wt-exact-hoeffding}\\
 U_\rho
 &=\frac2\mu\sum_{p<q}t_pt_qY_{p,\rho}Y_{q,\rho}
 \label{eq:wt-normalized-hoeffding}
\end{align}
hold.  In particular,
\begin{equation}
 \mathbb E_G(U_\rho\mid a_p)=0
 \quad\text{for every }p\in\mathcal P,
 \label{eq:wt-one-coordinate-annihilation}
\end{equation}
so the constant and all one-prime coordinate components vanish.

More precisely, with the convention \eqref{eq:wt-fourier-convention},
\begin{equation}
 \widehat U_\rho(\chi)=
 \begin{cases}
 \displaystyle
 \frac{2t_pt_q}{\mu(p-1)(q-1)}
 \overline{\chi_p(\rho_p)\chi_q(\rho_q)},
 &\operatorname{supp}(\chi)=\{p,q\},\ p<q,\\[1.1em]
 0,&|\operatorname{supp}(\chi)|\ne2.
 \end{cases}
 \label{eq:wt-exact-fourier-support}
\end{equation}
Thus the Fourier support is exactly on two-prime characters whenever
$|\mathcal P|\ge2$.
\end{theorem}

\begin{proof}
Put $m=\sum_pt_p\theta_p$.  From
\eqref{eq:wt-designed-coefficients},
\begin{equation}
 m=CA,
 \qquad
 C=2(1-m).
 \label{eq:wt-C-relation}
\end{equation}
For a Bernoulli variable of mean $\theta_p$,
\begin{equation}
 Y_{p,\rho}^2
 =\theta_p(1-\theta_p)+(1-2\theta_p)Y_{p,\rho}.
 \label{eq:wt-bernoulli-square}
\end{equation}
Expanding $W_\rho=(1-m-\sum_pt_pY_{p,\rho})^2$, and then using
\eqref{eq:wt-bernoulli-square}, gives
\begin{align}
 W_\rho
 &= (1-m)^2+\sum_p t_p^2\theta_p(1-\theta_p) \notag\\
 &\quad+
 \sum_p t_p\bigl[-2(1-m)+t_p(1-2\theta_p)\bigr]Y_{p,\rho}
 +2\sum_{p<q}t_pt_qY_{p,\rho}Y_{q,\rho}.
 \label{eq:wt-hoeffding-before-design}
\end{align}
Now
\begin{equation}
 t_p(1-2\theta_p)
 =C\frac{p-1}{p-3}\frac{p-3}{p-1}=C=2(1-m),
 \label{eq:wt-linear-cancellation}
\end{equation}
so every linear coefficient vanishes.  Also $(1-m)^2=C^2/4$,
which identifies the constant in \eqref{eq:wt-hoeffding-before-design} with
$\mu$ and proves \eqref{eq:wt-exact-hoeffding}.

Independence and $\mathbb E Y_{p,\rho}=0$ give
\eqref{eq:wt-one-coordinate-annihilation}.  Finally, for a local character
$\chi_p$,
\begin{equation}
 \widehat{Y_{p,\rho}}(\chi_p)
 =\begin{cases}
 0,&\chi_p=\mathbf1,\\
 (p-1)^{-1}\overline{\chi_p(\rho_p)},&\chi_p\ne\mathbf1.
 \end{cases}
 \label{eq:wt-local-Y-transform}
\end{equation}
Taking the product of the two local transforms in
\eqref{eq:wt-normalized-hoeffding} proves
\eqref{eq:wt-exact-fourier-support}.
\end{proof}

\begin{remark}[Why this is not the collapsed weight]
\label{rem:wt-not-standard-same-window}
If the components of $\rho$ come from one integer, then
$X_{p,\rho}(a)=\mathbf1_{p\mid a-\rho}$.  Thus
\eqref{eq:wt-shifted-square} uses shifted divisors of $a-\rho$, whereas
\cref{prop:wt-same-window-collapse} concerns divisors of the already
$Q$-rough integer $a$.  This shift is precisely why the new square is not
constant on $G$.  Calling it ``Selberg-form'' records the square of a linear
divisor sum; it does not import the prime-detection properties of a sieve.
\end{remark}

\subsection{An exact certificate at \texorpdfstring{$Q=385$}{Q=385}}
\label{subsec:wt-385-certificate}

Take $\mathcal P=\{5,7,11\}$, $Q=385$, and $\rho=1$.  Then
\begin{equation}
 A=\frac78,
 \qquad
 C=\frac8{11},
 \qquad
 (t_5,t_7,t_{11})
 =\left(\frac{16}{11},\frac{12}{11},\frac{10}{11}\right),
 \qquad
 \mu=\frac{93}{121}.
 \label{eq:wt-385-parameters}
\end{equation}
If $S(a)=\{p:X_{p,1}(a)=1\}$, the value of $W_1(a)$ and the number of
residues in $G$ with a given pattern are as follows.
\begin{center}
\begin{tabular}{c@{\qquad}r@{\qquad}c}
\toprule
$S(a)$ & multiplicity & $W_1(a)$\\
\midrule
$\varnothing$ & $135$ & $1$\\
$\{5\}$ & $45$ & $25/121$\\
$\{7\}$ & $27$ & $1/121$\\
$\{11\}$ & $15$ & $1/121$\\
$\{5,7\}$ & $9$ & $289/121$\\
$\{5,11\}$ & $5$ & $225/121$\\
$\{7,11\}$ & $3$ & $1$\\
$\{5,7,11\}$ & $1$ & $729/121$\\
\bottomrule
\end{tabular}
\end{center}
The multiplicities sum to $\varphi(385)=240$, and their weighted average is
$93/121$.  The pointwise centered identity is
\begin{equation}
 W_1-\frac{93}{121}
 =\frac{384}{121}Y_{5,1}Y_{7,1}
  +\frac{320}{121}Y_{5,1}Y_{11,1}
  +\frac{240}{121}Y_{7,1}Y_{11,1}.
 \label{eq:wt-385-pointwise-identity}
\end{equation}
Since every character takes the value one at $\rho=1$, the nonzero Fourier
coefficients of $U_1=W_1/\mu-1$ are exactly
\begin{equation}
 \widehat U_1(\chi)=
 \begin{cases}
 16/93,&\operatorname{supp}(\chi)=\{5,7\},\\
 8/93,&\operatorname{supp}(\chi)=\{5,11\},\\
 4/93,&\operatorname{supp}(\chi)=\{7,11\}.
 \end{cases}
 \label{eq:wt-385-fourier-coefficients}
\end{equation}
There are respectively $15$, $27$, and $45$ characters of these three
types.  Parseval therefore gives the exact check
\begin{align}
 \mathbb E_G|U_1|^2
 &=15\left(\frac{16}{93}\right)^2
   +27\left(\frac8{93}\right)^2
   +45\left(\frac4{93}\right)^2
 =\frac{2096}{2883}.
 \label{eq:wt-385-parseval}
\end{align}
In addition, for every $p\in\{5,7,11\}$ and every
$x\in\mathbb F_p^\times$,
\begin{equation}
 \sum_{\substack{a\in G\\a_p=x}}U_1(a)=0.
 \label{eq:wt-385-fiber-certificate}
\end{equation}
Equations \eqref{eq:wt-385-parameters}--\eqref{eq:wt-385-fiber-certificate}
are rational identities.  The accompanying exact-arithmetic program and
JSON file reproduce the pattern table, the fiber sums, and Parseval mass.
They are finite consistency certificates, not numerical evidence for a
prime-pair assertion.

\subsection{Pairing with the centered local kernel}
\label{subsec:wt-kernel-pairing}

We finally quantify the gain produced by removing the one-prime modes.  For
an integer $h$, let
\begin{equation}
 \mathcal P_h=\{p\in\mathcal P:p\nmid h\},
 \qquad
 \kappa_h=\prod_{p\in\mathcal P_h}\frac{p-2}{p-1},
 \label{eq:wt-active-primes-kappa}
\end{equation}
and, for $a,b\in G$, define
\begin{equation}
 K_h^\circ(a,b)
 =\kappa_h^{-1}
  \prod_{p\in\mathcal P_h}\mathbf1_{a_pb_p\ne-h\bmod p}-1.
 \label{eq:wt-centered-local-kernel}
\end{equation}
The empty product convention makes $K_h^\circ=0$ when
$\mathcal P_h=\varnothing$.  Let
\begin{equation}
 (T_hf)(a)=\mathbb E_{b\in G}K_h^\circ(a,b)f(b).
 \label{eq:wt-centered-local-operator}
\end{equation}
We use the Hermitian convention
$\langle f,g\rangle_G=\mathbb E_G f\overline g$.  Since $U_\rho$, $U_\sigma$, and
$K_h^\circ$ are real-valued, the bilinear average below equals the indicated
inner product:
\begin{equation}
 \mathcal C_h(\rho,\sigma)
 =\mathbb E_{a,b\in G}
   U_\rho(a)U_\sigma(b)K_h^\circ(a,b)
 =\langle U_\rho,T_hU_\sigma\rangle_G.
 \label{eq:wt-pairing-definition}
\end{equation}

\begin{theorem}[Pair-only kernel bound]
\label{thm:wt-pair-only-kernel-bound}
For all $\rho,\sigma\in G$ and all integers $h$,
\begin{align}
 |\mathcal C_h(\rho,\sigma)|
 &\le \frac4{\mu^2}
  \sum_{\substack{p<q\\p,q\in\mathcal P_h}}
  t_p^2t_q^2\theta_p^2\theta_q^2
 \label{eq:wt-exact-pairing-bound}\\
 &\le 32\left(\sum_{p\in\mathcal P_h}\frac1{(p-3)^2}\right)^2.
 \label{eq:wt-elementary-pairing-bound}
\end{align}
In particular, if
\begin{equation}
 \mathcal P=\{p:w<p\le w^2\},
 \label{eq:wt-quadratic-prime-window}
\end{equation}
then, as $w\to\infty$,
\begin{equation}
 \sup_{h\in\mathbb Z}\sup_{\rho,\sigma\in G}
 |\mathcal C_h(\rho,\sigma)|
 \ll \frac1{(w\log w)^2}.
 \label{eq:wt-wlogw-pairing-bound}
\end{equation}
The implied constant is absolute.
\end{theorem}

\begin{proof}
The multiplicative-character expansion of
\eqref{eq:wt-centered-local-kernel} contains only characters which are
trivial outside $\mathcal P_h$.  A character with support $S\ne\varnothing$
has coefficient of magnitude
\begin{equation}
 \prod_{p\in S}\frac1{p-2}.
 \label{eq:wt-kernel-coefficient-magnitude}
\end{equation}
By \eqref{eq:wt-exact-fourier-support}, only supports $S=\{p,q\}$ can
contribute to \eqref{eq:wt-pairing-definition}.  For a fixed pair $p<q$
there are $(p-2)(q-2)$ such characters.  Each kernel coefficient has
magnitude $((p-2)(q-2))^{-1}$, while each of the two weight coefficients has
magnitude
\begin{equation}
 \frac{2t_pt_q\theta_p\theta_q}{\mu}.
 \label{eq:wt-pair-weight-coefficient}
\end{equation}
The character count and the kernel denominator therefore cancel exactly.
The triangle inequality, summed over active pairs, proves
\eqref{eq:wt-exact-pairing-bound}.  This calculation also fixes the Fourier
normalization: no factor $|G|$ occurs because every average and Fourier
coefficient is normalized as in \eqref{eq:wt-fourier-convention}.

From \eqref{eq:wt-designed-coefficients} and
$\theta_p=(p-1)^{-1}$,
\begin{equation}
 t_p^2\theta_p^2=\frac{C^2}{(p-3)^2}.
 \label{eq:wt-t-theta-simplification}
\end{equation}
Also \eqref{eq:wt-mean-mu} gives $\mu\ge C^2/4$.  Hence
\begin{align}
 \frac4{\mu^2}\sum_{p<q}t_p^2t_q^2\theta_p^2\theta_q^2
 &\le \frac{2C^4}{\mu^2}
       \left(\sum_p\frac1{(p-3)^2}\right)^2 \notag\\
 &\le32\left(\sum_p\frac1{(p-3)^2}\right)^2,
 \label{eq:wt-constant-32-check}
\end{align}
which proves \eqref{eq:wt-elementary-pairing-bound}.  Finally, the standard
upper bound $\pi(x)\ll x/\log x$, followed by partial summation, yields
\begin{equation}
 \sum_{w<p\le w^2}\frac1{(p-3)^2}
 \ll\frac1{w\log w}.
 \label{eq:wt-prime-reciprocal-square-sum}
\end{equation}
Substitution in \eqref{eq:wt-elementary-pairing-bound} proves
\eqref{eq:wt-wlogw-pairing-bound}.
\end{proof}

\begin{remark}[Scope of the suppression]
\label{rem:wt-scope-of-suppression}
The saving in \eqref{eq:wt-wlogw-pairing-bound} is an exact finite Fourier
pairing estimate for two deliberately designed residue weights and the
centered local kernel.  It does not estimate von Mangoldt correlations,
does not resolve the sieve parity problem, and does not give a lower bound
for any prime-pair count.  Its role is narrower: within the local model it
removes the entire one-prime obstruction and measures the remaining
two-prime contribution without suggesting that the same cancellation holds
for primes.
\end{remark}
