\section{Exact finite certificate}
\label{sec:tpc52-certificate}

The analytic arguments do not depend on floating-point experiments.
The accompanying standard-library Python program
\begin{center}
 \texttt{experiments/tpc52\_certificate.py}
\end{center}
is a deterministic regression test for their finite algebra.  It uses
exact rational arithmetic and performs \(4{,}372\) assertions in six
groups:
\begin{enumerate}[label=\textup{(C\arabic*)},leftmargin=3.2em]
 \item \(3{,}612\) clustered finite-difference moment identities;
 \item \(128\) orthogonal orbit-lift energy identities;
 \item \(370\) finite diagonal-multiplier overlap ledgers;
 \item \(160\) arbitrary nonnegative weight-transfer checks;
 \item \(99\) good/bad overlap threshold inequalities; and
 \item three exact endpoint fraction identities.
\end{enumerate}
The normalized source SHA-256 is
\begin{center}
{\small\texttt{3d6244dd53736436539c4842b732731919539164d001d1f41e8f886d80702ee4}},
\end{center}
the semantic payload SHA-256 is
\begin{center}
{\small\texttt{0fc0c178543beddd5ba86120d235fd28cd135ffdd84893cdda12cd296ca54bf9}},
\end{center}
and the certificate-core SHA-256 is
\begin{center}
{\small\texttt{2e136caf81b9ce92f8dccd55d834c78cf4eeedc5c559d283f483e5d333177065}}.
\end{center}
The committed output is
\texttt{experiments/tpc52\_certificate\_output.txt}.  Running
\begin{center}
\texttt{python experiments/tpc52\_certificate.py
        --output experiments/tpc52\_certificate\_output.txt}
\end{center}
reproduces it byte for byte when the normalized source is unchanged.

The certificate catches sign errors in the moment-annihilating
coefficients, accidental reintroduction of scalar cross terms, inversion
of the overlap ratio, failure of fiberwise lower bounds under arbitrary
nonnegative concentration, and arithmetic mistakes in the endpoint
ledger.  It does not prove uniform prime--squarefree sampling, Sobolev
tail estimates, flat-boundary asymptotics, or the physical profile
nondegeneracy assumption.  It does not enumerate a coherent prime sum
and cannot certify a fixed-shift prime-pair statement.  Its scope is
finite L0 algebra supporting the stated L1 interface, with no L2 or
parity-sensitive conclusion.
