\section{Endpoint ledger and claim boundary}
\label{sec:tpc52-endpoint}

This section records exactly what the preceding theorems purchase in the
fixed-shift reduction.  It is deliberately stated as an operator ledger,
not as a prediction about primes.

\subsection{Condition-number expenditure}

For one direct cell and a sequence of nonzero coefficient vectors \(c_X\),
put \(\Theta_X:=\Theta(\mathbf W;c_X)\).  The diagonal identity of
\cref{thm:tpc52-diagonal-ledger} then assigns the scale-dependent cost
\begin{equation}
 \kappa_{\rm can,B}(X)
 =\frac{A_B(\mathbf W)^2}{\Theta_X}.
 \label{eq:tpc52-endpoint-exact-cost}
\end{equation}
The Mellin factor \(A_B(\mathbf W)\) is fixed once the shapes, the
number of factors, and \(B\) are fixed.  Consequently:
\begin{align}
 \Theta_X&\gg 1
   &&\Longrightarrow& \kappa_{\rm can,B}(X)&=O(1),
 \label{eq:tpc52-endpoint-constant-cost}\\
 \Theta_X&\ge X^{-o(1)}
   &&\Longrightarrow& \kappa_{\rm can,B}(X)&=X^{o(1)},
 \label{eq:tpc52-endpoint-subpower-cost}\\
 \Theta_X&\ge X^{-\lambda+o(1)}
   &&\Longrightarrow& \kappa_{\rm can,B}(X)&\ll X^{\lambda+o(1)}.
 \label{eq:tpc52-endpoint-power-cost}
\end{align}
Here \(\kappa_{\rm can,B}\) is a squared norm ratio.  No square root is
silently inserted into the exponent ledger.

The inherited endpoint reserves at most \(1/400\) of polynomial
exponent for this interface.  The formal exponent ledger therefore requires
\begin{equation}
 \lambda\le \frac1{400}.
 \label{eq:tpc52-endpoint-budget}
\end{equation}
In an application carrying unspecified \(X^{o(1)}\) factors, operational
viability uses the strict inequality \(\lambda<1/400\); equality is a
boundary case requiring a separate sharp endpoint estimate.
Uniform activity has \(\lambda=0\).  By contrast, the grazing example
in \cref{sec:tpc52-grazing} violates every fixed polynomial budget.
These statements concern only this coefficientwise interface; unused
budget here cannot be counted as progress at a downstream gate.

\subsection{The precise forward step}

The logical dependency is
\begin{equation}
 \begin{gathered}
 \text{TPC--50: a fixed-complexity direct cell survives the literal mask}
 \\
 \Downarrow
 \\
 \text{TPC--51: fixed scalar quotient frames and sampled row-log banks}
 \\
 \Downarrow
 \\
 \boxed{\text{TPC--52: a conditional pre-terminal Mellin criterion}}
 \\
 \boxed{\text{on exact-dictionary, complete-row, uniformly active cells.}}
 \end{gathered}
 \label{eq:tpc52-dependency}
\end{equation}
The new point is that the physical orbit label is retained.  The false
scalar Gram is allowed to saturate, while the actual coefficient vector
is treated by a diagonal multiplier and a nonnegative overlap ratio.
Under the exact-profile dictionary, complete-row hypotheses
\textup{(S1)}--\textup{(S3)}, and \(\rho_*>0\), this verifies the
actual-direction part of the narrow TPC--51 bridge and its row-log
relative-tail branch on the declared retained field.  Those hypotheses are
not proved here for every inherited packet.  The result is therefore a
conditional L1 interface theorem and a finite, checkable reduction of the
remaining provenance work.

\subsection{Operations not licensed by the theorem}

The following arrows remain absent:
\begin{enumerate}[label=\textup{(O\arabic*)},leftmargin=3.2em]
 \item a lower square after the terminal coherent sum over primes \(p\);
 \item stability after identifying equal residual labels
       \(s=d(m)r\);
 \item passage from the frozen shift family to the single physical
       shift \(h_0\);
 \item identification of the coefficientwise quadratic form with the
       native affine physical Gram;
 \item reverse Minkowski control for the full signed projective profile
       used in TPC--48; and
 \item an estimate for any fixed-shift prime-pair correlation.
\end{enumerate}
The diagonal proof would be invalid if applied after any operation that
creates cross terms among \((m,r,j,\gamma)\).  In particular, it cannot
be moved through the coherent prime map merely by citing positivity of
the pre-terminal energy.

\subsection{Claim table}

\begin{center}
\small
\begin{tabular}{@{}
 >{\raggedright\arraybackslash}p{0.16\textwidth}
 >{\raggedright\arraybackslash}p{0.48\textwidth}
 >{\raggedright\arraybackslash}p{0.25\textwidth}@{}}
\toprule
Level & Established here & Explicitly not established\\
\midrule
L0 & Scalar cluster saturation; orthogonal lift; exact multi-factor
Mellin ledger; support-grazing obstruction. & A lower frame for every
signed Mellin density.\\
L1 & Conditional actual-direction stability and polylogarithmic row-log
tail on exact-dictionary, complete-row, profile-nondegenerate direct cells.
& Verification of those hypotheses for every inherited packet; coherent
prime lower square, residual grouping, physical-shift localization, and
native-Gram comparison.\\
L2 & Nothing. & Hardy--Littlewood asymptotics, a parity-barrier breach,
or any twin-prime conclusion.\\
\bottomrule
\end{tabular}
\end{center}

Thus TPC--52 closes the analytic part of a declared interior subgate
conditional on a finite actual-profile dictionary and sharpens the next
decision.  One must first verify that dictionary and uniform overlap for the
packet in use; one may then test whether the later coherent-prime operator
preserves enough of this retained-label energy, or prove that it does
not.  Boundary packets with vanishing overlap must be budgeted,
discarded with a quantified physical error, or treated by additional
structure; they are not covered by the interior theorem.
