\section{Support grazing: a sharp actual-direction obstruction}
\label{sec:tpc52-grazing}

The positive profile-overlap hypothesis cannot be replaced by bounded
smoothness, common compact support, or dyadic comparability of the
scale parameters.  We now give a fixed-shape example in which the
carrier remains macroscopically nonzero while the physical profile
collapses faster than every power.  The construction concerns the
provenance-fixed actual direction itself; it is not obtained by
choosing an arbitrary Mellin coefficient density.

\subsection{Two fixed flat bumps}

Let
\begin{equation}
 \vartheta(u):=
 \begin{cases}
  \exp(-1/u),&u>0,\\
  0,&u\leq0,
 \end{cases}
 \label{eq:tpc52-flat-half-bump}
\end{equation}
and fix the two nonzero shapes
\begin{equation}
 U(t):=\vartheta(t-1)\vartheta(2-t),
 \qquad
 V(t):=\vartheta(t-1)\vartheta(2-t).
 \label{eq:tpc52-fixed-flat-bumps}
\end{equation}
Both functions belong to \(C_c^\infty(\R)\), are supported on
\([1,2]\), are positive on \((1,2)\), and are flat at both endpoints.
In particular, they belong to \(C_c^\infty((0,\infty))\), as required
by real-axis Mellin inversion.  For \(1<c<2\), define the carrier and
the physical profile by
\begin{equation}
 R_c(t):=U(t),
 \qquad
 F_c(t):=U(t)V(ct).
 \label{eq:tpc52-grazing-carrier-profile}
\end{equation}
The carrier does not depend on \(c\).  The two supports overlap only on
\begin{equation}
 1<t<\frac2c,
 \qquad
 \frac2c-1=\frac{2-c}{c}.
 \label{eq:tpc52-grazing-overlap-interval}
\end{equation}

\begin{proposition}[Every-power overlap collapse]
\label{prop:tpc52-every-power-grazing}
Put
\begin{equation}
 \rho(c):=
 \frac{\displaystyle\int_\R|F_c(t)|^2\,dt}
      {\displaystyle\int_\R|R_c(t)|^2\,dt}.
 \label{eq:tpc52-grazing-overlap-ratio}
\end{equation}
For every \(N>0\), there is \(C_N<\infty\) such that
\begin{equation}
 0\leq\rho(c)\leq C_N(2-c)^N
 \qquad(1<c<2).
 \label{eq:tpc52-every-power-overlap-bound}
\end{equation}
More precisely, there are absolute constants \(C,c_0>0\) such that
\begin{equation}
 \rho(c)\leq C(2-c)\exp\!\left(-\frac{c_0}{2-c}\right).
 \label{eq:tpc52-exponential-grazing-bound}
\end{equation}
\end{proposition}

\begin{proof}
Write \(\delta=2-c\) and \(t=1+s\).  On the overlap interval,
\(0<s<\delta/c\), and
\begin{equation}
 2-ct=\delta-cs.
 \label{eq:tpc52-two-flat-distances}
\end{equation}
All factors in \eqref{eq:tpc52-fixed-flat-bumps} are at most one.
Using only the two flat factors facing the grazing endpoints gives
\[
 |U(1+s)V(c(1+s))|^2
 \leq
 \exp\!\left(-\frac2s-\frac2{\delta-cs}\right).
\]
Since \(s<\delta/c\) and \(0<\delta-cs<\delta\), the right side is at
most \(\exp(-c_0/\delta)\) for an absolute \(c_0>0\).  The interval has
length \(\delta/c\).  The denominator in
\eqref{eq:tpc52-grazing-overlap-ratio} is one fixed positive number, so
\eqref{eq:tpc52-exponential-grazing-bound} follows.  Finally,
\(e^{-c_0/\delta}\ll_N\delta^N\) for every \(N\), which proves
\eqref{eq:tpc52-every-power-overlap-bound}.
\end{proof}

Taking \(c_X=2-X^{-\sigma}\), with fixed \(\sigma>0\), gives
\begin{equation}
 \rho(c_X)\ll_M X^{-M}
 \qquad\text{for every fixed }M>0.
 \label{eq:tpc52-superpolynomial-overlap-collapse}
\end{equation}
The shapes \(U,V\) have not changed with \(X\); only the legitimate
scale parameter \(c_X\) approaches the grazing boundary.

\subsection{The distinguished Mellin direction becomes a near-kernel}

Let \(\widetilde V\) be the real-axis Mellin transform of \(V\), and
write
\begin{equation}
 A_B(V):=\frac1{2\pi}\int_\R
 (1+|\tau|)^B|\widetilde V(\tau)|\,d\tau.
 \label{eq:tpc52-grazing-Wiener-mass}
\end{equation}
This is a fixed positive finite number.  On positive samples
\(t_1,\ldots,t_N\), take the carrier coefficients
\(b_n=U(t_n)\) and the physical samples \(x_n=ct_n\).  The canonical
Mellin direction fixed by \(V\) is
\begin{equation}
 \frac1{2\pi}\int_\R\widetilde V(\tau)
 (b_nx_n^{i\tau})_{n=1}^N\,d\tau
 =(U(t_n)V(ct_n))_{n=1}^N.
 \label{eq:tpc52-grazing-actual-direction}
\end{equation}
Its envelope and output obey the exact ledger
\begin{align}
 \cE_B^{\rm gr}(c)&=A_B(V)
  \left(\sum_n|U(t_n)|^2\right)^{1/2},
 \label{eq:tpc52-grazing-envelope}\\
 \|\cS_V^{\rm gr}(c)\|_2^2
 &=\sum_n|U(t_n)V(ct_n)|^2.
 \label{eq:tpc52-grazing-output}
\end{align}
Thus support grazing shrinks the physical profile but not the carrier
size seen by the canonical layer envelope.

The identical calculation on the Hilbert space
\(L^2((0,\infty),dt)\), with carrier \(U(t)\), gives the continuum
condition number
\begin{equation}
 \frac{\cE_B^{\rm gr}(c)^2}{\|\cS_V^{\rm gr}(c)\|_2^2}
 =\frac{A_B(V)^2}{\rho(c)}.
 \label{eq:tpc52-grazing-condition-number}
\end{equation}
Consequently \eqref{eq:tpc52-superpolynomial-overlap-collapse}
produces a condition number larger than every fixed power of \(X\).
This is a near-kernel for the one density \(\widetilde V\) prescribed by
the physical shape.  It is therefore different from the universal
kernel obtained by allowing an arbitrary signed Mellin density.

\subsection{Exact zero on a physical grid}

The discrete obstruction can be stronger.  Let \(t_j=j/J\), and
suppose the carrier window contains the grid points in \([1,2]\).  If
\begin{equation}
 0<\delta=2-c<\frac cJ,
 \label{eq:tpc52-grid-grazing-condition}
\end{equation}
then
\[
 0<\frac2c-1=\frac\delta c<\frac1J.
\]
The open overlap interval \((1,2/c)\) contains no grid point: \(t=1\)
is an endpoint where \(U(1)=0\), and the next grid point is
\(1+J^{-1}\geq2/c\).  Hence
\begin{equation}
 U(t_j)V(ct_j)=0
 \quad\text{for every }j,
 \qquad
 \sum_j|U(t_j)|^2>0
 \label{eq:tpc52-exact-grid-zero}
\end{equation}
for all sufficiently large \(J\).  The sampled physical output is then
exactly zero although the canonical carrier envelope is positive.
This example does not depend on an arithmetic sampling accident; it
already occurs on the regular orbit grid.
For example, \(c_J=2-J^{-2}\) satisfies
\eqref{eq:tpc52-grid-grazing-condition} for large \(J\) and gives both
the exact grid zero and an every-power continuum overlap collapse.

\subsection{A representation-free good--bad tradeoff}

The correct energy selection is made on the unseparated physical
profile, not on signed Mellin layers.  Let \(R\) be a nonzero carrier,
\(P\) a bounded physical multiplier, and
\begin{equation}
 d\sigma:=|R|^2\,d\varpi,
 \qquad
 \operatorname{Bad}_\eta(P;R)
 :=\frac{\sigma(\{|P|<\eta\})}{\sigma(\Omega)},
 \qquad \eta>0.
 \label{eq:tpc52-bad-carrier-fraction}
\end{equation}
Then the profile-to-carrier ratio satisfies
\begin{equation}
 \frac{\int_\Omega|R|^2|P|^2\,d\varpi}
      {\int_\Omega|R|^2\,d\varpi}
 \geq
 \eta^2\bigl(1-\operatorname{Bad}_\eta(P;R)\bigr).
 \label{eq:tpc52-good-bad-lower-tradeoff}
\end{equation}
Conversely,
\begin{equation}
 \frac{\int_\Omega|R|^2|P|^2\,d\varpi}
      {\int_\Omega|R|^2\,d\varpi}
 \leq
 \eta^2+\|P\|_\infty^2
 \frac{\sigma(\{|P|\geq\eta\})}{\sigma(\Omega)}.
 \label{eq:tpc52-good-bad-upper-tradeoff}
\end{equation}
These inequalities are immediate by splitting the integral into the
good and bad sets.  They show exactly what an energy-selected boundary
argument would need: a level \(\eta=\eta_X\) for which the good set
retains enough carrier mass and \(\eta_X\) itself does not introduce a
forbidden polynomial loss.  In the grazing example, the good carrier
mass tends to zero for every fixed \(\eta>0\), and the best useful
\(\eta_X\) is super-polynomially small.

The split in \eqref{eq:tpc52-bad-carrier-fraction} is intrinsic to the
physical multiplier \(P\).  It neither chooses a favorable term from a
signed Mellin representation nor changes the distinguished coefficient
density.

\subsection{Scope of the obstruction}

The construction proves sharpness of the positive-overlap assumption:
uniform \(C^B\) bounds and compact scale control alone do not yield a
uniform actual-direction condition number.  It does \emph{not} assert
that the inherited TPC packet approaches this grazing configuration.
That is decided only by inspecting its declared fixed cutoffs and
normalized scale cell.  Nor does the example involve coherent prime
summation, residual grouping, localization to \(h_0\), a
parity-sensitive correlation, or a prime-pair conclusion.  It is a
sharp analytic obstruction at the coefficientwise pre-terminal Mellin
interface and nothing beyond that interface.
