\section{Introduction}
\label{sec:tpc52-introduction}

The smooth row--orbit factors in the opened fixed-shift packet are not a
fixed scalar family.  They contain expressions such as
\begin{equation}
 W(mj/X),\qquad \Psi(dj/K),
 \label{eq:tpc52-physical-shapes-preview}
\end{equation}
and therefore generate more and more log translates as the orbit length
\(J\) grows.  TPC--51 proved that distinct compactly supported log
translates are linearly independent and consequently cannot be replaced
by a fixed-rank scalar family merely by relabelling
\citep{WangTPC51}.  It also proved stable sampled quotient frames for
every declared fixed finite family and for polylogarithmic row-log
Fourier banks.  The missing step was to connect those model results to
the actual coefficientwise operator.

There are two traps at this point.  First, linear independence is not a
uniform lower-frame theorem.  Nearby translates are almost parallel,
and their scalar Gram matrix is extremely ill-conditioned.  Second, the
physical operator never forms that scalar Gram: before coherent prime
summation it retains the orbit coordinate \(j\), together with source,
cofactor, opposite-row, and residual labels.  Those labels are
orthogonal.  Forgetting them manufactures cross terms that are absent
from the physical coefficient space.

This paper separates the two issues.  We give a quantitative saturation
theorem for the false scalar collapse, then prove a diagonal theorem for
the label-preserving actual direction.  The latter does not assert a
lower frame on every signed Mellin density.  It uses the one coefficient
density fixed by provenance and reduces its condition number to a
nonnegative physical overlap ratio.

\subsection{Main results}

The conclusions are organized by the operator on which they hold.

\begin{enumerate}[label=\textup{(R\arabic*)},leftmargin=3.2em]
 \item \textbf{Scalar saturation.}
 Let \(a\mapsto g(a)\) be a normalized \(C^\infty\) Hilbert-valued
 curve.  If \(r+1\) sampling parameters lie in an interval of length
 \(O_r(J^{-1})\), then their scalar Gram matrix has
 \begin{equation}
  \lambda_{\min}\le C_rJ^{-2r}.
  \label{eq:tpc52-intro-saturation}
 \end{equation}
 For interior log translates with no exact relation, this persists on
 the exact span.  Their dimension is of order \(J\), so an exact or
 uniform-relative scalar reduction needs rank of order \(J\), not a
 fixed or polylogarithmic rank.

 \item \textbf{Orthogonal orbit lift.}
 For arbitrary vectors \(f_j\), the label-preserving synthesis
 \(c\mapsto\bigoplus_jc_jf_j e_j\) has diagonal Gram
 \begin{equation}
  \left\|\bigoplus_jc_jf_je_j\right\|^2
  =\sum_j|c_j|^2\|f_j\|^2.
  \label{eq:tpc52-intro-orthogonal-lift}
 \end{equation}
 Thus scalar saturation is not a physical obstruction while \(j\)
 remains an output coordinate.

 \item \textbf{Exact multi-factor Mellin ledger.}
 For one direct residue cell and one provenance-fixed coefficient
 vector, multidimensional Mellin inversion gives
 \begin{equation}
  \frac{\cE_B(\mathbf W;c)^2}
       {\|\cS_{\mathbf W}c\|_2^2}
  =\frac{A_B(\mathbf W)^2}{\Theta(\mathbf W;c)}.
  \label{eq:tpc52-intro-exact-ledger}
 \end{equation}
 The numerator contains only the fixed weighted Wiener--Mellin mass;
 all scale dependence is in the explicit profile-overlap
 \(\Theta\).  This is an identity, not a numerical conditioning
 heuristic.

 \item \textbf{Uniformly active actual cells.}
 Normalize an opposite row by
 \(x=\log(\ell/L)\), \(y=\log(d/D)\), and the orbit by \(t=j/J\).
 For a source-scale parameter \(\beta\), let \(B_\beta\) be the carrier
 and \(F_\beta\) the unseparated physical profile.  Define
 \begin{equation}
 \rho_*
  :=\inf_{\beta\in\mathfrak B}
  \frac{\displaystyle\int|F_\beta(x,y,t)|^2
                       e^{x+y}\,dx\,dy\,dt}
       {\displaystyle\int|B_\beta(x,y,t)|^2
                       e^{x+y}\,dx\,dy\,dt}.
  \label{eq:tpc52-intro-overlap}
 \end{equation}
 A single strict overlap point yields a nonempty compact uniformly active
 subcell; on such a cell, \(\rho_*>0\).  Conditional on the named packet
 also satisfying the exact actual-to-profile coordinate dictionary and
 complete-row hypotheses, the prime--squarefree row sampler, the orbit
 Riemann sum, and the literal mask imply
 \(\Theta_X^{\rm act}\ge\rho_*/2\), uniformly for arbitrary source
 concentration and arbitrary finite retained cofactor support.  Hence that
 declared coefficientwise pre-terminal
 direction has condition number \(O(1)\).  The paper does not infer this
 dictionary or uniform overlap for every inherited packet.

 \item \textbf{Conditional row-log compression.}
 A tensor cosine bank of degree \(K_{\rm F}\) has squared approximation tail
 \(O(K_{\rm F}^{-2})\) for a retained Hilbert-valued orbit field with controlled
 row-log regularity.  If that regularity is bounded by the carrier energy
 and the projected reference energy has a fixed lower bound, then
 \(K_{\rm F}=(\log X)^A\), arithmetic sampling, and sparse mask deletion
 give an \(o(1)\) relative tail.  Under the exact-profile dictionary and
 \(\rho_*>0\), the required normalizations are verified for the declared
 retained actual field.  The projection compresses row-log frequency, not
 the orbit label.

 \item \textbf{Grazing is a sharp boundary.}
 Two fixed \(C_c^\infty\) bumps can have scaled supports whose overlap
 approaches a common flat endpoint.  At distance
 \(\delta_X=X^{-\sigma}\), the physical overlap is smaller than every
 power of \(X\) while the Mellin carrier stays nonzero.  The
 distinguished actual direction then has a super-polynomial condition
 number.  Thus bounded smoothness and dyadic scale comparability do not
 replace the positive-overlap hypothesis.
\end{enumerate}

\subsection{What advances and what does not}

We use the same three-level ledger as the preceding reduction.

\begin{description}[leftmargin=3.2em,style=nextline]
 \item[Level L0: exact algebra and boundary analysis.]
 Scalar saturation, the orthogonal-lift identity, the multi-factor
 Mellin ledger, and the grazing construction are exact analytic
 statements.
 \item[Level L1: physical coefficient interface.]
 Under the exact-profile and complete-row hypotheses, the overlap theorem
 keeps the literal source coefficient, direct
 residue cell, orbit label, opposite row, residual label, real-axis
 Mellin normalization, and static mask in their inherited order.  It
 gives a conditional actual-direction Mellin bridge on uniformly active
 direct cells.  Verifying those hypotheses for every inherited packet is
 not part of the theorem.
 \item[Level L2: arithmetic target.]
 A coherent prime square, fixed-shift target correlation, or parity
 estimate.  No statement at this level is proved here.
\end{description}

The L1 conclusion is a strict subgate.  It is not the full TPC--48
profile envelope: that object takes a Hilbert norm after coherent prime
summation and before the outer signed projective integral.  Nor does the
present theorem group \(s=d(m)r\), localize a frozen family to the
physical \(h_0\), or identify the residual Gram with the native affine
physical Gram.  In particular, no fixed-shift prime-pair lower bound,
Hardy--Littlewood asymptotic, parity-barrier breach, or twin-prime
conclusion is asserted.

\subsection{Organization}

\Cref{sec:tpc52-interface} reconstructs the exact coefficientwise
operator.  \Cref{sec:tpc52-scalar-saturation} proves scalar saturation
and the orthogonal-lift identity.  The diagonal Mellin ledger is
\cref{sec:tpc52-diagonal-mellin}.  The continuous and sampled overlap
theorems are established in \cref{sec:tpc52-profile-overlap}, and their
actual TPC consequence in \cref{sec:tpc52-actual-bridge}.
 \Cref{sec:tpc52-fourier-compressibility} proves the corresponding
 conditional polylogarithmic relative-tail theorem.  The sharp grazing obstruction and the endpoint
claim ledger are given in \cref{sec:tpc52-grazing,sec:tpc52-endpoint}.
The exact finite certificate is described in
\cref{sec:tpc52-certificate}.
