\section{Exact certificate and scope ledger}
\label{sec:tpc31-certificate}

The companion script
\begin{center}
\texttt{experiments/tpc31\_certificate.py}
\end{center}
is a standard-library Python certificate for the finite algebra,
graph inequalities, and rational exponent ledger used in this paper.
Run from the paper directory with Python 3.10 or later:
\begin{verbatim}
python experiments\tpc31_certificate.py
python -O experiments\tpc31_certificate.py
\end{verbatim}
Both modes perform exactly
\begin{equation}
 \boxed{876{,}320}
 \label{eq:tpc31-certificate-count}
\end{equation}
recorded checks and regenerate byte-identical JSON.

The checks are divided as follows:
\begin{center}
\begin{tabular}{@{}lr@{}}
\toprule
Finite check family & Recorded checks \\
\midrule
Primitive content and canonical reduced-target identities & $566{,}738$ \\
Selected-divisor multiplier $d\mid c$ and determinant dilation & $206{,}203$ \\
Determinant-cell degree calculations & $5{,}939$ \\
Integer-weight Schur inequalities & $78{,}746$ \\
Exact-content orbit occupancy & $1{,}662$ \\
Residue partition and absolute reassembly & $301$ \\
Rational splice and high-$\beta$ ledgers & $16{,}705$ \\
Scope and nonoverlap flags & $26$ \\
\midrule
Total & $876{,}320$ \\
\bottomrule
\end{tabular}
\end{center}

The finite identity sweep verifies
\[
 c=(N_m,N_n),\quad c\mid m-n,\quad (c,mnh)=1,
\]
the coprimality of the reduced targets, and
$mV-nU=h\Delta^\#$.  Over selected divisors it verifies
$d=(r,s)\mid c$ and
\[
 \frac{m-n}{d}=\frac cd\Delta^\#.
\]
The graph tests cover positive, negative, crossing-zero, and
macro-translated windows; $q=1$; noncoprime $c,q$; content-scaled
moduli $cq$ beyond the row span (equivalently, $q$ beyond the
normalized-determinant span); full residue cells; and window--residue
intersections.  Exhaustive and deterministic integer weights verify
the squared two-sided Schur inequality, including sharp $+1$ cases.

The orbit tests compare direct exact-content counts with their finite
M\"obius inversion and verify the one-class occupancy bound.  The
partition tests check that the residue cells exactly reassemble the
whole determinant layer and include signed cancellation witnesses,
while making no claim about the asymptotic physical coefficient.  All
exponent calculations use \texttt{fractions.Fraction}; no
floating-point comparison is used in the high-$\beta$ or threshold
optimization ledger.

Reproducibility values are:
\begin{align}
 \text{normalized certificate-script source SHA-256}\qquad
 &\texttt{7b4c984620ce733e7741d00b3c4b547e}\notag\\[-0.2em]
 &\texttt{7d62efb05947902d91fc9dc54e133ff7},
 \label{eq:tpc31-source-hash}\\
 \text{JSON SHA-256}\qquad
 &\texttt{5776b4310c04df512c47f940924253d4}\notag\\[-0.2em]
 &\texttt{75ab51a2da3c8058a52201a643479fea},
 \label{eq:tpc31-json-hash}\\
 \text{certificate digest}\qquad
 &\texttt{cd48ae70d7d5a39b54d128a28c695557}\notag\\[-0.2em]
 &\texttt{f440de37582c7c3cec6405713eae0ab4}.
 \label{eq:tpc31-certificate-digest}
\end{align}

The certificate is a regression check, not a computer-assisted proof
of an asymptotic estimate.  In particular, it does not certify
M\"obius cancellation, cancellation of the auxiliary residue-cell zero
coefficient, a prime-pair main term, or the existence of infinitely
many prime pairs.

\subsection{Claim boundary}

The proved statements in this paper are exactly:
\begin{enumerate}[label=\textup{(\alph*)}]
 \item canonical reduced-target algebra;
 \item deterministic row-graph and Schur estimates;
 \item absolute cellwise transfer to the three retained raw channels;
 \item the TPC-30 large-content splice;
 \item rational exponent consequences;
 \item residue-cell energy and exceptional-frequency compression;
 \item the exact auxiliary residue-cell zero-coefficient and
 absolute-reassembly identities.
\end{enumerate}
\par\medskip\noindent
They do not imply:
\begin{enumerate}[label=\textup{(\alph*)}]
 \item cancellation of the full coprime determinant spectrum;
 \item smallness of the auxiliary residue-cell zero coefficient in
 \eqref{eq:tpc31-zero-mode};
 \item a complete M\"obius-tail estimate;
 \item a Hardy--Littlewood asymptotic or positive prime-pair lower
 bound;
 \item the twin-prime conjecture or a breach of the sieve parity
 barrier.
\end{enumerate}

The scope flags in the JSON archive encode these negative statements
explicitly, making any future promotion of a finite certificate or a
cellwise estimate into a global number-theoretic claim detectable in
regression review.
