\section{Comparison, sharpness, and the next gate}
\label{sec:tpc31-comparison}

\subsection{What is inherited and what is new}

The Euclidean identity
\[
 (mj+h,nj+h)\mid m-n
\]
and the single exact-content orbit class are inherited from TPC-30,
with their earlier geometric origin in TPC-18
\citep{WangTPC18,WangTPC30}.  TPC-19 already constructed determinant
Fourier normal forms for an earlier centered model, and TPC-29 already
computed the affine determinant associated with a selected reflected
divisor pair \citep{WangTPC19,WangTPC29}.  We claim none of those
identities as new.

The additions here are:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the factorization-independent reduced pair
 $(U,V)$ and its canonical determinant
 $mV-nU=h\Delta^\#$;
 \item the two-sided degree and Schur bounds for arbitrary canonical
 determinant spectra $\Omega_c$;
 \item their transfer to all three unexpanded ultra-long raw channels;
 \item translated-window, residue-cell, and window--residue bounds on
 the complete small-content family;
 \item the splice with TPC-30, producing all-content single-cell
 estimates with optimized fixed-power margins;
 \item the residue-cell energy and exceptional-frequency compression;
 \item the exact identification of the small-content residue-cell
 reassembly as the $r=0$ coefficient of an auxiliary residue-label
 DFT.
\end{enumerate}

The word ``determinant'' here refers to the elementary $2\times2$
identity \eqref{eq:tpc31-canonical-determinant-identity}.  The method
is not the determinant method for counting rational or integral points
on algebraic varieties \citep{HeathBrown2002Determinant}.  Its counting
input is only the injectivity of $n=m-c\delta$ and a bipartite Schur
estimate.

\subsection{Why the regions are genuinely different}

TPC-18 deleted a neighborhood of the row diagonal.  The present
windows are translation-invariant and may be centered where
$|m-n|\asymp Q$.  TPC-29 works after selecting divisor variables and
uses their gcd and lcm.  The present cell is defined before divisor
selection and remains meaningful for the whole raw kernel.  TPC-30
deletes large full target content; the fully coprime layer $c=1$ is
the sharp model for the new theorem.

The all-content splice does overlap TPC-30 on $c>C$ by design.  Its
new input is the low-complexity determinant estimate on $c\le C$; neither
half alone yields \cref{thm:tpc31-all-content-cell}.  On expanded
divisor subfamilies there may also be overlap with one of TPC-29's
sparse wedges.  The theorem does not assert disjointness from every
such subfamily.  It asserts a uniform raw-kernel bound requiring none
of their selected-divisor hypotheses.

\subsection{Sharp deterministic floors}

The $Q^{-1}$ term in a residue cell comes from one possible row match
per left row.  It cannot be removed from a theorem assuming only row
uniqueness and $\ell^2$ control.  For example, take consecutive
abstract row sets and the graph $m-n=1$.  Its degree is one, and
constant nonnegative row weights attain the order of the Schur bound.
In the physical target geometry, the same difference has exact content
one at every primitive orbit point, because the target gcd divides
$|m-n|=1$.

Likewise, a translated window containing $K$ integer determinants can
have degree $K$ on an interval of consecutive rows.  The cardinality
factor in \eqref{eq:tpc31-row-entropy-bound} is therefore optimal under
the abstract physical interface up to support edges and logarithmic
normalization.  This is not an optimality theorem for the signed
opened-row coefficients; their arithmetic provenance has not yet been
used.

\subsection{The refined route after TPC-31}

The Fourier calculation in \cref{sec:tpc31-zero-mode} refines the
phrase ``signed dispersion across determinant cells.''  Even the
few-large-frequency estimate does not control the original sum,
because that sum is exactly the $r=0$ coefficient $\widehat S(0)$ of
the auxiliary residue-label transform.  The next stage must make this
coefficient non-generic by using structure suppressed in the Schur
majorant.

The resulting staged route is:
\begin{enumerate}[label={\textup{TPC-\arabic*:}},start=32]
 \item construct a factorable representation of the prime--M\"obius
 coefficient, incorporating
 $\mu(d)(\log\ell)\omega_D(d)\psi_L(\ell/L)$ inside the canonical
 determinant coefficient while retaining the fixed residue factors,
 the bounded pair mask, and the remaining physical weights; derive a
 matched $TT^*$ or spectral dispersion form without separating the two
 mixed channels from the both-ultra channel;
 \item prove cancellation of the auxiliary zero coefficient or a deconcentration inequality
 strong enough to retain a fixed part of the cellwise margin;
 \item reassemble the exact cutoff difference and propagate the
 estimate uniformly over the physical parameter box;
 \item return to the complete TPC-18 residual and endpoint packets
 only after the preceding uniformity is proved.
\end{enumerate}

The exact matched-channel identity of TPC-20 is a natural algebraic
interface for the first step \citep{WangTPC20}.  Classical large-sieve
technology and modern Kloosterman-fraction or exceptional-spectrum
estimates provide benchmarks
\citep{IwaniecKowalski2004,DukeFriedlanderIwaniec1997,
BettinChandee2018,Pascadi2026LargeSieve}.  They cannot be inserted
merely by analogy: the actual coefficient, parameter range, mask, and
auxiliary zero coefficient must first be reduced to the precise
hypotheses of one stated theorem.  No such transfer is used in the
present estimates.

\begin{center}
\begin{tabular}{>{\raggedright\arraybackslash}p{0.43\textwidth}
                >{\raggedright\arraybackslash}p{0.46\textwidth}}
\toprule
Object & Status \\
\midrule
Primitive target-gcd identity and exact-content orbit class
& Inherited from TPC-30. \\
\addlinespace
Canonical reduced targets and determinant $h\Delta^\#$
& Factorization-independent canonical packaging proved here. \\
\addlinespace
Arbitrary translated canonical determinant window
& Explicit cellwise bound; power saving under the stated support-count
condition, with a macro-centered sharpening. \\
\addlinespace
Individual normalized-determinant residue class
& Explicit small-content and all-content bounds; power saving for a
polynomially growing effective modulus. \\
\addlinespace
Residue-cell and determinant-frequency mean square
& Unconditional bound proved here; an exceptional-frequency estimate follows. \\
\addlinespace
Absolute reassembly over all windows or classes
& No saving; exact partition restores the full majorant. \\
\addlinespace
Signed auxiliary zero coefficient $\widehat S(0)$
& Open; not controlled by the nonzero-frequency mean square. \\
\addlinespace
Complete residual, positivity, prime-pair asymptotic, or parity breach
& Not proved and not implied. \\
\bottomrule
\end{tabular}
\end{center}
