\section{Cell energy, exceptional frequencies, and the auxiliary zero coefficient}
\label{sec:tpc31-zero-mode}

The cell theorems imply a useful mean-square statement, but they also
show exactly why that statement does not estimate the full residual.
Fix $C\ge1$, $q\ge1$, one raw channel $\nu$, and define the signed
small-content cell amplitudes
\begin{equation}
 S_a
 :=\cS_\nu(c_{\alpha,\gamma}(j)\le C,
             \ \Delta^\#_{\alpha,\gamma}(j)
                  \equiv a\!\pmod q),
 \qquad a\pmod q.
 \label{eq:tpc31-signed-cell-amplitudes}
\end{equation}
Let $A_a$ be the corresponding absolute majorant obtained from
\eqref{eq:tpc31-raw-channel} by replacing every coefficient, kernel,
mask, and weight by its absolute value.  Then
\begin{equation}
 |S_a|\le A_a.
 \label{eq:tpc31-cell-majorization}
\end{equation}

\begin{remark}[Zero-mode nomenclature]
\label{rem:tpc31-zero-mode-nomenclature}
The transform below is a finite Fourier transform in the auxiliary
residue label $a\pmod q$.  Its $r=0$ coefficient is not the Poisson
zero frequency in the orbit variable $j$, and it is not the centered
divisor-kernel zero mode of TPC-20.  We use ``residue-cell zero
coefficient'' when this distinction matters.
\end{remark}

Because residue classes partition the exact-content triples,
\begin{equation}
 \sum_{a\, (q)}A_a
 \ll_{\eps,h,\mathscr D}X^\eps JQ^2.
 \label{eq:tpc31-total-absolute-cell-mass}
\end{equation}
On the other hand, the proof of
\cref{cor:tpc31-small-residue} is an absolute proof and gives
\begin{equation}
 \max_{a\, (q)}A_a
 \ll_{\eps,h,\mathscr D}X^\eps JQ^2
 \left(\frac CX+\frac1Q+\frac1q\right).
 \label{eq:tpc31-maximum-cell-mass}
\end{equation}

\begin{proposition}[Residue-cell energy]
\label{prop:tpc31-cell-energy}
The signed cells in \eqref{eq:tpc31-signed-cell-amplitudes} satisfy
\begin{equation}
 \boxed{
 \sum_{a\, (q)}|S_a|^2
 \ll_{\eps,h,\mathscr D}X^\eps(JQ^2)^2
 \left(\frac CX+\frac1Q+\frac1q\right).}
 \label{eq:tpc31-cell-energy}
\end{equation}
If $C\ll J$, this simplifies to
\begin{equation}
 \sum_{a\, (q)}|S_a|^2
 \ll X^\eps(JQ^2)^2
 \left(\frac1Q+\frac1q\right).
 \label{eq:tpc31-cell-energy-C-below-J}
\end{equation}
\end{proposition}

\begin{proof}
By \eqref{eq:tpc31-cell-majorization},
\[
 \sum_a|S_a|^2
 \le\sum_aA_a^2
 \le(\max_aA_a)\sum_aA_a.
\]
Apply \eqref{eq:tpc31-total-absolute-cell-mass} and
\eqref{eq:tpc31-maximum-cell-mass}, each with $\eps/2$, and relabel the
resulting soft loss as $X^\eps$.  If $C\ll J$, then
$C/X\ll1/Q$ because $JQ\asymp X$.
\end{proof}

Define the unnormalized discrete Fourier transform
\begin{equation}
 \widehat S(r)
 :=\sum_{a\, (q)}S_a e_q(-ra),
 \qquad
 e_q(x)=\exp(2\pi i x/q).
 \label{eq:tpc31-cell-DFT}
\end{equation}
Since each triple lies in the class
$a\equiv\Delta^\#\pmod q$, this transform also has the exact physical
form
\begin{equation}
 \widehat S(r)
 =\cS_\nu(c\le C; e_q(-r\Delta^\#)),
 \label{eq:tpc31-physical-frequency}
\end{equation}
where the notation on the right means that the phase is inserted into
the raw summand.

\begin{corollary}[Mean-square frequency compression]
\label{cor:tpc31-frequency-compression}
If $C\ll J$, then
\begin{equation}
 \boxed{
 \frac1q\sum_{r\, (q)}|\widehat S(r)|^2
 \ll_{\eps,h,\mathscr D}X^\eps(JQ^2)^2
 \left(\frac1Q+\frac1q\right).}
 \label{eq:tpc31-frequency-mean-square}
\end{equation}
In particular, if $q\le Q$ and $\sigma>0$, then
\begin{equation}
 \#\{r\pmod q:|\widehat S(r)|>JQ^2X^{-\sigma}\}
 \ll_{\eps,h,\mathscr D}X^{2\sigma+\eps}.
 \label{eq:tpc31-exceptional-frequency-count}
\end{equation}
\end{corollary}

\begin{proof}
Parseval for \eqref{eq:tpc31-cell-DFT} gives
\[
 \frac1q\sum_r|\widehat S(r)|^2=\sum_a|S_a|^2.
\]
Use \eqref{eq:tpc31-cell-energy-C-below-J}.  If $q\le Q$, then
\[
 \sum_r|\widehat S(r)|^2
 \ll X^\eps(JQ^2)^2.
\]
Chebyshev's inequality gives
\eqref{eq:tpc31-exceptional-frequency-count}.
\end{proof}

More precisely, if $q=X^{\rho+o(1)}\le Q$ and
$0<\sigma<\rho/2$, then one may choose the soft-loss exponent with
$0<\eps<\rho-2\sigma$.  The exceptional set in
\eqref{eq:tpc31-exceptional-frequency-count} is then power-smaller
than the full set of $q$ frequencies.  This few-large-frequency bound
is not, however, a bound for the coefficient needed by the original
unweighted reassembly.

\begin{proposition}[The exact residue-cell zero coefficient]
\label{prop:tpc31-zero-mode}
With the preceding notation,
\begin{equation}
 \boxed{
 \widehat S(0)=\sum_{a\, (q)}S_a
 =\cS_\nu(c_{\alpha,\gamma}(j)\le C).}
 \label{eq:tpc31-zero-mode}
\end{equation}
Moreover, inversion gives
\begin{equation}
 S_a-\frac{\widehat S(0)}q
 =\frac1q\sum_{r=1}^{q-1}\widehat S(r)e_q(ra),
 \label{eq:tpc31-centered-cell-inversion}
\end{equation}
and hence
\begin{equation}
 \sum_{a\, (q)}
 \left|S_a-\frac{\widehat S(0)}q\right|^2
 =\frac1q\sum_{r=1}^{q-1}|\widehat S(r)|^2.
 \label{eq:tpc31-centered-cell-parseval}
\end{equation}
Control of the nonzero-frequency side alone places no upper bound on
$\widehat S(0)$.
\end{proposition}

\begin{proof}
The first equality is the $r=0$ case of
\eqref{eq:tpc31-cell-DFT}; the second follows because the residue cells
partition the event $c\le C$.  Fourier inversion proves
\eqref{eq:tpc31-centered-cell-inversion}, and Parseval proves
\eqref{eq:tpc31-centered-cell-parseval}.  Finally, a constant vector
$S_a=M/q$ has every nonzero Fourier coefficient equal to zero but has
$\widehat S(0)=M$.  Thus no inequality involving only the nonzero
 frequencies can control the residue-cell zero coefficient without an
 additional input.
\end{proof}

\subsection{Absolute reassembly is exactly lossless}

For the nonnegative majorants there is an even simpler obstruction:
\begin{equation}
 \boxed{
 \sum_{a\, (q)}A_a=A_{\rm all},}
 \label{eq:tpc31-absolute-residue-reassembly}
\end{equation}
where $A_{\rm all}$ is the absolute mass of the whole small-content
event.  Likewise, if a normalized-determinant interval is partitioned
into disjoint integer windows, the sum of their determinant
cardinalities equals the cardinality of the original interval.
Consequently the local gains $q^{-1}$ and $W/Q$ disappear when all
cells are recombined by the triangle inequality.  This is an exact
partition identity, not an assertion that the signed physical sum is
large.

The next analytic obligation is therefore sharper than ``prove that
most nonzero determinant frequencies are small.''  One candidate is
to construct a factorable representation of the prime--M\"obius
coefficient while retaining the fixed residue factors, pair mask, and
matched channel structure, and then control the residue-cell zero
coefficient or cancel it across the mixed and both-ultra channels
before separation.  The exact channel
recombination of TPC-20 and the coefficient gates isolated in TPC-19
provide relevant normal forms \citep{WangTPC19,WangTPC20}; the present
paper does not supply the required signed estimate.
