\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Matched-Spectrum Gates in a Primitive Mobius Tail: Exact Determinant-Divisor Normal Forms, CRT-Poisson Duality, and a Frequency-Concentration Gate},
 pdfauthor={Liang Wang},
 pdfsubject={Exact arithmetic and spectral normal forms for the primitive determinant obstruction in a fixed-shift prime-pair tail},
 pdfkeywords={Mobius tail, Ramanujan model, determinant spectrum, Chinese remainder theorem, Poisson summation, Kloosterman fractions, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{Conditional input}{Conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\ee}[1]{\exp(2\pi i #1)}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cW}{\mathcal W}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Matched-Spectrum Gates in a Primitive M\"obius Tail:}\\
\textbf{Exact Determinant--Divisor Normal Forms, CRT--Poisson Duality,}\\
\textbf{and a Frequency-Concentration Gate}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC-18 reduces a failed symmetric fixed-shift M\"obius tail block to a
primitive correlation of the Ramanujan residuals
\(r_R=\Lambda-\Lambda_R\) on two affine rows
\(m_i j+h\), where \(m_i=\ell_i d_i\), \(Q=LD\),
\(J=X/Q\), and the determinant is \(h(m_1-m_2)\).  We replace that
still-opaque correlation by exact divisor and spectral normal forms.

Writing
\[
 \Lambda_R(n)=\sum_{u\mid n}\lambda'_R(u),
\]
we prove that the actual residual, not merely the finite model, has the
identity
\[
 r_R(n)=-\sum_{\substack{u\mid n\\u\ \mathrm{squarefree}}}
 \mu(u)w_R(u),
 \qquad w_R(u)>0,
\]
with an explicit weight \(w_R\).  In the primitive sector put
\(H=\rad|h|\).  For a pair of target divisors
\(u=ga\), \(v=gb\), the integers \(g,a,b\) are pairwise coprime and
squarefree, the shared sign cancels exactly,
\[
 \mu(ga)\mu(gb)=\mu(a)\mu(b),
\]
and the simultaneous congruences are soluble precisely when
\(g\mid m_1-m_2\).  This gives an exact all-modulus
determinant--divisor expansion of the primitive residual correlation.

We next calibrate the prime and finite-model conditional row densities
on \((j,H)=1\).  Their difference is an explicit
\(O_{h,\eps}(L^{-1}X^\eps)\) bias, whose contribution has a fixed
power saving relative to the natural \(XQ\) scale.  The
centered finite-model covariance is
\[
 \sum_{u,v\le R}\frac{\lambda'_R(u)\lambda'_R(v)}{uv}
 \bigl((u,v)\one_{(u,v)\mid m_1-m_2}-1\bigr),
\]
with the natural coprimality restrictions.  Every coprime
\((u,v)\) term vanishes individually.  Moreover,
\[
 g\one_{g\mid\Delta}-1
 =\sum_{0<r<g}\ee{r\Delta/g},
\]
so the complete-period \(j\)-zero mode is supported entirely on
nonzero frequencies in the determinant \(\Delta\).

There are then two exact analytic interfaces.  For the bare dyadic,
separable determinant coefficient, Fourier grouping of
\(\ell_1d_1-\ell_2d_2\) produces a transform that factors into two
M\"obius exponential sums.  The full \(g,a,b\) masks and row-pair
weights still require a matched reduction.  Alternatively, Poisson
summation in the common \(j\)-class
completes every \(H[u,v]\le JX^{-\eta}\) term.  In the remaining
long-lcm range, the compatible joint residue has three coupled inverse
phases of Kloosterman type; the centered single terms must be retained
beside it.  We prove the corresponding short/long-lcm decomposition
and give the strict-margin sufficient range
\(Q\le X^{2\delta-\eta_0}\) on which the whole finite model is
completable.

Finally, an exact finite witness shows that one centered finite-model
row pair can have linear complete-period mass.  Thus centering alone
does not give rowwise cancellation in the four terms of
\(r_R(n_1)r_R(n_2)\).  A separate global estimate could still use
oscillation over the row variables; the matched-spectral route instead
keeps the four local spectra together.  Current
large-sieve theorems apply to smoother or differently factorable
coefficient classes and do not establish that matching for the sharp
M\"obius coefficient.  No determinant-dispersion estimate, fixed-shift
Hardy--Littlewood asymptotic, twin-prime theorem, or breach of sieve
parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius tail; Ramanujan residuals;
determinant spectrum; Chinese remainder theorem; Poisson summation;
Kloosterman fractions; frequency concentration; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11N05, 11L07, 11L20.

\input{sections/introduction}
\input{sections/primitive-interface}
\input{sections/divisor-normal-form}
\input{sections/primitive-centering}
\input{sections/finite-model-spectrum}
\input{sections/determinant-frequency}
\input{sections/crt-poisson}
\input{sections/componentwise-nogo}
\input{sections/euler-tail-gates}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
