\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{bm}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{array}
\usepackage[numbers,sort&compress]{natbib}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{assumption}[theorem]{Assumption}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\Pp}{\mathbb P}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Hh}{\mathcal H}
\newcommand{\cA}{\mathcal A}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cW}{\mathcal W}
\newcommand{\one}{\mathbf 1}
\newcommand{\pinf}{\|\cdot\|_{\pi,\infty}}
\newcommand{\e}{\mathrm e}

\hypersetup{
  pdftitle={Weighted Mask Survival and Sharp Projective-to-Atomic Distortion for Residual Determinant Packets},
  pdfauthor={Liang Wang},
  pdfsubject={Nuclear effective rank, specified representation efficiency, and the static row-mask interface},
  pdfkeywords={projective tensor norm, nuclear norm, Frobenius norm, effective rank, row mask, determinant equation, parity problem}
}

\title{\bfseries Weighted Mask Survival and Sharp\\
Projective-to-Atomic Distortion for\\
Residual Determinant Packets}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-2pt]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
The preceding twin-prime-correlation (TPC) reduction controls the
complete frozen actual-coefficient residual family by a signed
projective row-square envelope, whereas the inherited normalization is
the physical atomic diagonal.  We identify the exact finite-dimensional
distortion between these two geometries.  For a Hilbertized coefficient
tensor \(T\), the optimal rank-one projective envelope is its nuclear
norm and the atomic energy is its squared Frobenius norm.  The intrinsic
energy loss is therefore the nuclear participation rank
\[
 r_{\rm nuc}(T)
 =\frac{\|T\|_{S_1}^2}{\|T\|_{S_2}^2}.
\]
For a specified signed representation there is a second, independent
factor: its cancellation condition number.  We prove the exact product
formula for the two losses and show that cancelling layer pairs make
every comparison uniform over all exact representations impossible.

For a weighted row mask \(A=D_aKD_b\), the bounded projective norm used
in TPC--36 transfers sharply to the Hilbert geometry:
\[
 \|A\|_{S_1}
 \le \|K\|_{\pi,\infty}\|a\|_2\|b\|_2,
 \qquad
 r_{\rm nuc}(A)
 \le \min\!\left\{\operatorname{rank}A,
 \frac{\|K\|_{\pi,\infty}^2}{\delta_w}\right\},
\]
where \(\delta_w=\|A\|_{S_2}^2/
(\|a\|_2^2\|b\|_2^2)\) is the weighted survival parameter (the weighted
admitted fraction for a \(0\)-\(1\) mask).  Permutation
masks attain the density bound exactly, so bounded projective cost one
does not by itself imply any dimension-free atomic estimate.  Ferrers
masks, by contrast, have distortion
\((2/\pi^2)(\log n)^2+O(\log n)\).

We then study the complete-universe extension of the literal static TPC
mask formula.  Standard row counts show that every row and
column has admitted degree \((1-o(1))N\).  Combined with a specified
explicit TPC--36 projective representation, this gives only
\(X^{o(1)}\) energy loss for that complete formula model.  Nevertheless
the same admitted
support contains a perfect-matching permutation packet with distortion
\(N=X^{267/400+o(1)}\); it is a support-class witness, not the literal
physical coefficient.  Thus static mask geometry is soft on the full
row cell, while support information alone is provably insufficient.

If the entire TPC endpoint allowance is assigned to the isolated
Hilbertized face, its exact fixed-representation target is
\(c_{\mathscr R}^2r_{\rm nuc}\le X^{1/400+o(1)}\).
This is not an if-and-only-if criterion for full TPC--48 closure, whose
other gates may consume part or all of the same budget.
The paper does not identify the full Banach profile envelope with a
nuclear norm and does not compare the completed coherent prime square
with the fixed-\(h_0\) physical diagonal.  Weighted active-cell density,
representation-frame efficiency, coherent prime cancellation,
residual grouping, and shift localization remain separate gates.  No
parity-barrier breach or twin-prime conclusion is claimed.
\end{abstract}

\noindent\textbf{Keywords:} projective tensor norm; nuclear norm;
Frobenius norm; effective rank; determinant equation; row masks;
M\"obius correlation; parity problem.

\medskip
\noindent\textbf{Convention.}
All sets and matrices in the abstract theory are finite.  The Schatten
norms are denoted by \(\|\cdot\|_{S_1}\) and
\(\|\cdot\|_{S_2}\); the latter is the Frobenius norm.  Rank-one
tensors \(x\otimes\overline y\) are identified with operators
\(z\mapsto\langle z,y\rangle x\).  Constants may depend on the fixed
shift and dyadic support constants.

\medskip
\noindent\textbf{MSC 2020:} Primary 46B28, 47B10; Secondary 11N35,
15A18, 42A05.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/hilbert-projective-geometry}
\input{sections/weighted-mask-transfer}
\input{sections/actual-static-mask}
\input{sections/sharp-models}
\input{sections/endpoint-ledger}
\input{sections/boundaries-next-gate}
\input{sections/certificate-claims}

\begingroup
\small
\raggedright
\setlength{\bibsep}{4pt plus 1pt minus 1pt}
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
