\section{Fixed-shift dictionary, conclusions, and next gate}

\subsection{What is now exact}
On the literal TPC-64 terminal carrier, the following statements are proved
without asymptotics:
\begin{enumerate}[label=(\arabic*)]
\item the represented reference is the actual activated range \(Y_X\), not a
free ambient atom space;
\item a genuinely descending represented map is governed by the normalized
row Gram \eqref{eq:normalized-row-gram}, with exact kernel and dimension tests;
\item every Gram entry is the literal residual-fiber correlation
\eqref{eq:literal-gram};
\item terminal-faithful repair leaves downstream Grams unchanged when both
descriptions use the same factorization through the common terminal map; it
changes direct parent constants only through the parent metric;
\item labelled blocks can fuse complementary kernels according to
\eqref{eq:kernel-intersection}, while coherent label erasure requires a
separate fusion-angle estimate;
\item spectral capacity has a sharp projection law, but row capacity cannot be
transported to it without a reducing or basis-transport theorem;
\item activation, representation, and reassembly multiply compatibly on the
same vector, with each loss charged once.
\end{enumerate}

The prime-resolved construction of \citet{WangTPC55} gives a conditional
benchmark. Under its hypotheses \(h_0\ne0\), \(D=o(J)\), uniqueness of the
declared row labels, and sufficiently large \(X\), the refined key
\((\gamma,d(m)r,j,p)\) is injective on one declared source system. If this full
key and the external block label are retained, the represented map is a
coordinate relabelling and hence an isometry on its populated range. In that
labelled benchmark \(\beta_X^{\rm lab}=1\). This does not prove anything about
the physical map that forgets \(p\), erases other labels, or coherently
reassembles blocks: all unresolved cancellation is localized to those later
arrows.

\subsection{What remains unproved}
This paper does not establish:
\begin{itemize}
\item a favorable lower bound for the actual terminal activation ratio
\(\tau_{X,\nu}\);
\item injectivity, let alone a polynomial smallest singular value, for the
physical unlabelled represented map;
\item a positive physical fusion angle \(\theta_X\);
\item a reassembly or downstream lower bound with the literal arithmetic
coefficients;
\item a statement specialized to \(h_0=2\), a parity-breaking estimate, or a
twin-prime conclusion.
\end{itemize}

All exact matrix results are L0. The fixed-\(h_0\) identification is L1 only
because it preserves the literal carrier, coefficients, and support. An L2
arithmetic advance begins only when one controls the actual matrix
\(b_{y,m}\) uniformly or on a declared physical cone.

\subsection{The next smallest gate}
The row formula identifies the next paper's target. For each active row \(m\),
one must determine
\begin{enumerate}[label=(\roman*)]
\item the number and weight of actually exposed output fibers \(y\);
\item the physical collision degree between the supports of
\(b_{\cdot,m}\) and \(b_{\cdot,n}\);
\item whether the diagonal energy dominates the accumulated off-diagonal
correlations on the same fixed-shift carrier.
\end{enumerate}
Support degree alone cannot prove cancellation, but it can turn a subsequent
pair-correlation estimate into a Gram bound. This is the route pursued next:
actual exposure and collision geometry first, signed cancellation only after
the literal neighbor graph is known.
