\section{Terminal-faithful repair invariance and parent covariance}
\label{sec:tpc65-repair-invariance}

This section compares the literal-active-hypergraph carrier with the
canonical pair-repaired carrier.  The comparison is made after the typed
terminal operator, where both constructions take values in the same literal
terminal Hilbert space.  This placement is essential: a map acting on a
pre-terminal parent space may see repair-only coordinates which the terminal
operator annihilates.

\subsection{One terminal map from two parent carriers}

Retain the finite scale \(X\), the fixed nonzero shift \(h_0\), and the
coefficient space
\[
 Z_X=\mathbb C^{\mathcal M_X}.
\]
In the notation of \citet{WangTPC64}, define
\begin{align}
 L_X^{\mathrm{hyp}}
 &:=
 D_{X,h_0}^{\mathcal U^{\mathrm{pre},+}}
 C_X^{\mathrm{hyp}},
 \label{eq:tpc65-hypergraph-terminal-map}\\
 L_X^{\mathrm{rep}}
 &:=
 D_{X,h_0}^{\mathcal V^{\mathrm{hyb}}}
 C_X^{\mathrm{hyb}}.
 \label{eq:tpc65-repaired-terminal-map}
\end{align}
Both maps have codomain
\[
 \mathcal H_X^{\mathrm{term}}
 =
 \bigoplus_{k\in K_X}^{\perp}
 \ell^2(\mathcal U_{X,h_0,k}^{+}),
\]
the literal terminal atom space.  Their parent spaces are different, but
their displayed codomain is not.

\begin{theorem}[Common terminal map]
\label{thm:tpc65-common-terminal-map}
The hypergraph and canonical pair-repaired constructions
induce the same terminal map:
\begin{equation}
 \boxed{
 L_X^{\mathrm{hyp}}=L_X^{\mathrm{rep}}=:L_X.}
 \label{eq:tpc65-common-terminal-map}
\end{equation}
Moreover,
\begin{equation}
 \boxed{
 L_X^*L_X=T_X=\operatorname{diag}(T_m).}
 \label{eq:tpc65-common-terminal-gram}
\end{equation}
Consequently their activated ranges agree exactly:
\begin{equation}
 Y_X:=\Ran L_X^{\mathrm{hyp}}
     =\Ran L_X^{\mathrm{rep}}
     =\Ran L_X.
 \label{eq:tpc65-common-activated-range}
\end{equation}
\end{theorem}

\begin{proof}
Fix a literal terminal coordinate \((k,u)\), with
\(u\in\mathcal U_{X,h_0,k}^{+}\).  Both populated parent analyses assign
the value \(c_u z_{m(u)}\) to this coordinate, and both typed terminal
operators multiply it by the same literal multiplier \(t_{h_0}(u)\).
Thus
\[
 (L_X^{\mathrm{hyp}}z)(k,u)
 =
 t_{h_0}(u)c_u z_{m(u)}
 =
 (L_X^{\mathrm{rep}}z)(k,u)
\]
for every \(z\in Z_X\). The typed repaired terminal operator discards every
repair-only coordinate before entering the displayed literal terminal
codomain, so those coordinates contribute nothing. This proves
\eqref{eq:tpc65-common-terminal-map}.

Distinct row indices populate disjoint labelled terminal coordinates.
Hence the columns \(L_Xe_m\) are mutually orthogonal, and their squared
norms are precisely
\[
 \|L_Xe_m\|^2
 =
 \sum_{k\in K_X}
 \sum_{\substack{u\in\mathcal U_{X,h_0,k}^{+}\\m(u)=m}}
 |t_{h_0}(u)c_u|^2
 =T_m.
\]
This proves \eqref{eq:tpc65-common-terminal-gram}, and
\eqref{eq:tpc65-common-activated-range} follows immediately.
\end{proof}

\subsection{The exact represented Gram on the common range}

Let
\[
 A_X:Y_X\longrightarrow\mathcal H_X^{\mathrm{rep}}
\]
be one declared represented map on the common activated range.  This means
that the hypergraph and repaired descriptions use the same downstream map
after terminalization.  Assume \(Y_X\ne\{0\}\); when \(Y_X=\{0\}\), there is
no nonzero represented reference and no lower constant is assigned.  Define
\begin{equation}
 \beta_X
 :=
 \inf_{0\ne y\in Y_X}
 \frac{\|A_Xy\|^2}{\|y\|^2}.
 \label{eq:tpc65-beta-on-range}
\end{equation}

Put
\[
 \mathcal M_X^{T}:=\{m\in\mathcal M_X:T_m>0\},
 \qquad
 u_m:=\frac{L_Xe_m}{\sqrt{T_m}}
 \quad(m\in\mathcal M_X^{T}).
\]
By \eqref{eq:tpc65-common-terminal-gram},
\((u_m)_{m\in\mathcal M_X^{T}}\) is an orthonormal basis of \(Y_X\).
Define its represented row Gram by
\begin{equation}
 \mathsf G_X^{\mathrm{act}}(m,n)
 :=
 \langle A_Xu_m,A_Xu_n\rangle,
 \qquad m,n\in\mathcal M_X^{T}.
 \label{eq:tpc65-activated-row-gram}
\end{equation}

\begin{proposition}[Exact and repair-invariant represented constant]
\label{prop:tpc65-repair-invariant-beta}
One has
\begin{equation}
 \boxed{
 \beta_X
 =
 \lambda_{\min}\!\left(\mathsf G_X^{\mathrm{act}}\right)
 =
 \sigma_{\min}(A_X|_{Y_X})^2.}
 \label{eq:tpc65-beta-exact-eigenvalue}
\end{equation}
In particular,
\begin{equation}
 \boxed{
 \beta_X>0
 \quad\Longleftrightarrow\quad
 \Ker A_X\cap Y_X=\{0\}.}
 \label{eq:tpc65-beta-kernel-test}
\end{equation}
The matrix \(\mathsf G_X^{\mathrm{act}}\), the number \(\beta_X\), and
the kernel test are identical for the hypergraph and canonical repaired
descriptions.
\end{proposition}

\begin{proof}
The matrix in \eqref{eq:tpc65-activated-row-gram} is the matrix of
\(A_X^*A_X|_{Y_X}\) in the orthonormal basis \((u_m)\).  The Rayleigh
principle therefore gives
\[
 \inf_{0\ne y\in Y_X}
 \frac{\langle A_X^*A_Xy,y\rangle}{\|y\|^2}
 =
 \lambda_{\min}(\mathsf G_X^{\mathrm{act}}),
\]
which is \eqref{eq:tpc65-beta-exact-eigenvalue}.  In finite dimensions
the smallest eigenvalue is positive exactly when the restricted map is
injective, proving \eqref{eq:tpc65-beta-kernel-test}.  Repair invariance
then follows from \cref{thm:tpc65-common-terminal-map}: both constructions
have the same \(L_X\), the same range \(Y_X\), the same normalized row
basis, and the same declared map \(A_X\).
\end{proof}

\begin{remark}[What is and is not invariant]
\label{rem:tpc65-parent-versus-represented-gram}
The repair-invariant object is the represented Gram on \(Y_X\).  The
diagonal matrix with entries \(P_m/T_m\), when it is defined, is instead
the literal parent metric transported to \(Y_X\); replacing \(P_m\) by
\(\widetilde P_m\) changes that metric.  It must not be called the
represented Gram.
\end{remark}

\subsection{Direct closure relative to the two parents}

Let
\begin{equation}
 R_{X,\mathrm{hyp}}:=\operatorname{diag}(P_m),
 \qquad
 R_{X,\mathrm{rep}}:=\operatorname{diag}(\widetilde P_m).
 \label{eq:tpc65-two-parent-operators}
\end{equation}
For the canonical hybrid repair there are no new-only rows, so, provided
the literal parent is nonzero,
\begin{equation}
 R_{X,\mathrm{hyp}}
 \preceq R_{X,\mathrm{rep}}
 \preceq\mathfrak I_XR_{X,\mathrm{hyp}},
 \qquad
 1\le\mathfrak I_X<\infty,
 \label{eq:tpc65-parent-operator-order}
\end{equation}
and the two parent operators have the same kernel.  Let
\[
 B_X:Y_X\longrightarrow\mathcal H_X^{\mathrm{out}}
\]
be any fixed downstream map; it may be the represented map \(A_X\) or a
complete represented-plus-missing output.  For
\(\nu\in\{\mathrm{hyp},\mathrm{rep}\}\), define the direct parent-to-output
constant
\begin{equation}
 \Gamma_{X,\nu}(B_X)
 :=
 \inf_{\langle R_{X,\nu}z,z\rangle>0}
 \frac{\|B_XL_Xz\|^2}
      {\langle R_{X,\nu}z,z\rangle}.
 \label{eq:tpc65-direct-closure-constant}
\end{equation}

\begin{theorem}[Exact direct Gram and repair covariance]
\label{thm:tpc65-direct-repair-covariance}
Let
\[
 N_X:=\Ker R_{X,\mathrm{hyp}}
     =\Ker R_{X,\mathrm{rep}},
 \qquad
 S_X:=N_X^\perp.
\]
Then \(N_X\subseteq\Ker L_X\), and for each
\(\nu\in\{\mathrm{hyp},\mathrm{rep}\}\),
\begin{equation}
 \boxed{
 \Gamma_{X,\nu}(B_X)
 =
 \lambda_{\min}\!\left(
 R_{X,\nu,S}^{-1/2}
 L_{X,S}^*B_X^*B_XL_{X,S}
 R_{X,\nu,S}^{-1/2}
 \right).}
 \label{eq:tpc65-direct-generalized-gram}
\end{equation}
Its exact positivity test is
\begin{equation}
 \boxed{
 \Gamma_{X,\nu}(B_X)>0
 \quad\Longleftrightarrow\quad
 \Ker(B_XL_X)\subseteq\Ker R_{X,\nu}.}
 \label{eq:tpc65-direct-kernel-test}
\end{equation}
The two parent normalizations obey the sharp sandwich
\begin{equation}
 \boxed{
 \frac{1}{\mathfrak I_X}\,
 \Gamma_{X,\mathrm{hyp}}(B_X)
 \le
 \Gamma_{X,\mathrm{rep}}(B_X)
 \le
 \Gamma_{X,\mathrm{hyp}}(B_X).}
 \label{eq:tpc65-direct-repair-sandwich}
\end{equation}
\end{theorem}

\begin{proof}
The literal implication \(P_m=0\Rightarrow T_m=0\), together with
\eqref{eq:tpc65-common-terminal-gram}, gives
\(N_X\subseteq\Ker L_X\).  Consequently \(B_XL_X\) also annihilates
\(N_X\).  Every numerator and denominator in
\eqref{eq:tpc65-direct-closure-constant} therefore depends only on the
\(S_X\)-component of \(z\).  On \(S_X\), the parent operator is positive
definite.  The substitution
\[
 x=R_{X,\nu,S}^{1/2}z
\]
turns the quotient into the Rayleigh quotient of the matrix in
\eqref{eq:tpc65-direct-generalized-gram}.  This proves the exact formula.
Its smallest eigenvalue is positive precisely when \(B_XL_X\) has no
kernel vector outside \(N_X\), giving
\eqref{eq:tpc65-direct-kernel-test}.  This is the compatible-kernel case
of the general shorted formula of \citet{WangTPC62}; no nuisance-output
projection remains.

The common kernel in \eqref{eq:tpc65-parent-operator-order} makes the
admissible set of nonzero denominators the same for both parents.  For
every vector in this set,
\[
 \frac{1}{\mathfrak I_X}
 \frac{\|B_XL_Xz\|^2}
      {\langle R_{X,\mathrm{hyp}}z,z\rangle}
 \le
 \frac{\|B_XL_Xz\|^2}
      {\langle R_{X,\mathrm{rep}}z,z\rangle}
 \le
 \frac{\|B_XL_Xz\|^2}
      {\langle R_{X,\mathrm{hyp}}z,z\rangle}.
\]
Taking infima proves \eqref{eq:tpc65-direct-repair-sandwich}.
\end{proof}

\begin{example}[Sharpness of the repair charge]
\label{ex:tpc65-repair-sandwich-sharp}
Take \(Z_X=Y_X=\mathcal H_X^{\mathrm{out}}=\mathbb C\),
\(L_Xz=\sqrt a\,z\), \(B_X=I\),
\(R_{X,\mathrm{hyp}}=1\), and
\(R_{X,\mathrm{rep}}=\mathfrak I_X\), where
\(a>0\) and \(\mathfrak I_X\ge1\).  Then
\[
 \Gamma_{X,\mathrm{hyp}}=a,
 \qquad
 \Gamma_{X,\mathrm{rep}}=\frac{a}{\mathfrak I_X}.
\]
Thus the factor \(1/\mathfrak I_X\) cannot be improved.  The coefficient
one in the upper inequality is attained when the two parent forms agree
globally, in particular when \(\mathfrak I_X=1\).
\end{example}

Define the activation constants
\begin{equation}
 \tau_{X,\nu}
 :=
 \inf_{\langle R_{X,\nu}z,z\rangle>0}
 \frac{\|L_Xz\|^2}{\langle R_{X,\nu}z,z\rangle}.
 \label{eq:tpc65-two-activation-constants}
\end{equation}
Applying \eqref{eq:tpc65-beta-on-range} to \(y=L_Xz\) gives the useful
but generally non-exact staged certificate
\begin{equation}
 \Gamma_{X,\nu}(A_X)
 \ge \beta_X\tau_{X,\nu}.
 \label{eq:tpc65-staged-beta-activation}
\end{equation}
Here \(\beta_X\) is repair invariant; the parent repair is charged through
\(\tau_{X,\nu}\), or equivalently through the direct sandwich
\eqref{eq:tpc65-direct-repair-sandwich}.  Charging
\(\mathfrak I_X\) once in activation and again in the represented Gram
would double-count the same parent enlargement.

\begin{remark}[Generic repairs with new-only rows]
\label{rem:tpc65-new-only-repair}
The finite lower comparison in
\eqref{eq:tpc65-direct-repair-sandwich} relies on the absence of a row
with \(P_m=0<\widetilde P_m\).  For a generic larger repair such a row has
\(T_m=0\), hence \(L_Xe_m=0\), while its repaired-parent energy is
positive.  It follows directly from
\eqref{eq:tpc65-direct-closure-constant} that
\(\Gamma_{X,\mathrm{rep}}(B_X)=0\) for every downstream \(B_X\).
Thus terminal faithfulness alone does not provide a finite repair charge;
the no-new-only property of the canonical hybrid carrier is substantive.
\end{remark}

\subsection{Why pre-terminal maps are not repair invariant}

\begin{example}[A terminal-null coordinate read before terminalization]
\label{ex:tpc65-preterminal-noninvariance}
Let \(Z=\mathbb C\) and embed both parent descriptions in
\(\mathcal H^{\mathrm{pre}}=\mathbb C^2\).  Put
\[
 C_{\mathrm{hyp}}z=(z,0),
 \qquad
 C_{\mathrm{rep}}z=(z,z),
 \qquad
 D(a,b)=a.
\]
Then
\[
 DC_{\mathrm{hyp}}z=z=DC_{\mathrm{rep}}z,
\]
so the terminal map and its activated range are identical.  The second
coordinate is repair-only and terminal-null.  For
\[
 Q_\lambda(a,b):=a+\lambda b
\]
one nevertheless has
\[
 Q_\lambda C_{\mathrm{hyp}}z=z,
 \qquad
 Q_\lambda C_{\mathrm{rep}}z=(1+\lambda)z.
\]
The two pre-terminal output Grams are therefore \(1\) and
\(|1+\lambda|^2\).  They can be separated arbitrarily, and the repaired
output even vanishes when \(\lambda=-1\).
\end{example}

The obstruction in \cref{ex:tpc65-preterminal-noninvariance} is exactly
failure of descent: when \(\lambda\ne0\),
\[
 \Ker D\nsubseteq\Ker Q_\lambda.
\]
Accordingly, repair invariance may be invoked only after proving a common
factorization through the literal terminal map,
\begin{equation}
 F_X^{\mathrm{hyp}}=A_XL_X^{\mathrm{hyp}},
 \qquad
 F_X^{\mathrm{rep}}=A_XL_X^{\mathrm{rep}},
 \label{eq:tpc65-common-downstream-factorization}
\end{equation}
with the same \(A_X\).  Equality of terminal norms alone does not imply
\eqref{eq:tpc65-common-downstream-factorization}.

\begin{remark}[L0/L1 claim boundary]
\label{rem:tpc65-repair-claim-boundary}
The abstract represented-Gram and repair-sandwich consequences are
finite-dimensional L0 statements for declared maps and carriers. Identifying
the two coordinatewise terminal maps with the literal TPC-64 fixed-shift
constructions is an L1 dictionary statement. Any arithmetic use
must retain one fixed nonzero shift \(h_0\), the literal coefficients and
terminal multiplier, the actual active support, every required external
label until its declared erasure, and the raw counting-measure atomic
norm.  The exact identities prove neither a favorable activation census
nor a polynomial bound for \(\mathfrak I_X\), \(\tau_{X,\nu}\),
\(\beta_X\), or \(\Gamma_{X,\nu}\).  Finite-scale injectivity can have a
superpolynomially small least singular value.  Nothing in this section
specializes \(h_0\) to \(2\), controls a parity-sensitive signed kernel,
or implies a prime-pair lower bound.
\end{remark}
