\section{The activated row Gram}

Assume \(Y_X\ne\{0\}\). Let \(A_X:Y_X\to H_X^{\rm rep}\) be a declared
represented map and set
\[
 F_X=A_XL_X:Z_X\to H_X^{\rm rep},\qquad
 G_X=F_X^*F_X.
\]
The exact represented-to-terminal constant is
\begin{equation}\label{eq:beta-definition}
 \beta_X
 :=\inf_{\Tform_X(z)>0}
 \frac{\|F_Xz\|^2}{\Tform_X(z)}.
\end{equation}

\begin{theorem}[Activated-range represented Gram]\label{thm:row-gram}
On \(S_T=(\Ker T_X)^\perp\), define
\begin{equation}\label{eq:normalized-row-gram}
 K_X=T_{X,S}^{-1/2}G_{X,S}T_{X,S}^{-1/2}.
\end{equation}
Then
\begin{equation}\label{eq:beta-eigenvalue}
 \boxed{\quad
 \beta_X=\lambda_{\min}(K_X)
 =\sigma_{\min}(A_X|_{Y_X})^2.
 \quad}
\end{equation}
Consequently the following are equivalent:
\begin{enumerate}[label=(\roman*)]
\item \(\beta_X>0\);
\item \(\Ker A_X\cap Y_X=\{0\}\);
\item \(\Ker F_X=\Ker L_X\);
\item the represented columns \(A_Xf_m\), \(T_m>0\), are linearly
independent.
\end{enumerate}
In particular, \(\dim Y_X>\dim H_X^{\rm rep}\) forces \(\beta_X=0\).
\end{theorem}

\begin{proof}
Every \(z=z_S+z_0\) with \(z_0\in\Ker T_X=\Ker L_X\) has the same numerator
and denominator as \(z_S\). With \(x=T_{X,S}^{1/2}z_S\), the quotient in
\eqref{eq:beta-definition} becomes
\(\langle K_Xx,x\rangle/\|x\|^2\). This proves the first equality. The map
\(U=L_XT_{X,S}^{-1/2}:S_T\to Y_X\) is unitary because \(U^*U=I\), and
\(K_X=U^*A_X^*A_XU\), proving the singular-value identity. The kernel
equivalences and dimension statement follow.
\end{proof}

\subsection{Literal residual-fiber formula}
Suppose the represented output has an orthonormal coordinate set
\(\mathcal Y_X\), and terminal atoms \(u\) are sent to output fibers
\(q(u)\in\mathcal Y_X\). Write the terminal coefficient contributed by row
\(m\) at atom \(u\) as \(a_u\). Thus, for a terminal atom generated by row
\(m(u)\), its coefficient in \(L_Xz\) is \(a_uz_{m(u)}\). Define the coherent
row--fiber column
\begin{equation}\label{eq:bym}
 b_{y,m}:=
 \sum_{\substack{u:\ q(u)=y\\m(u)=m}}a_u.
\end{equation}
Then
\begin{equation}\label{eq:fiber-output}
 (F_Xz)_y=\sum_m b_{y,m}z_m,
\end{equation}
and hence
\begin{equation}\label{eq:literal-gram}
 \boxed{\quad
 (G_X)_{m,n}
 =\sum_{y\in\mathcal Y_X}\overline{b_{y,m}}b_{y,n}.
 \quad}
\end{equation}

Formula \eqref{eq:literal-gram} is the concrete arithmetic target. Diagonal
entries measure represented row energy, while off-diagonal entries record
actual coherent collisions. An ambient atom-grouping operator can have a
large kernel without harming \(K_X\) if that kernel misses \(Y_X\). Conversely,
nonzero diagonal entries do not prevent a kernel among the row columns.

\begin{corollary}[Common output gauge cancels]\label{cor:gauge}
If \(b_{y,m}=\Omega_y\beta_{y,m}\), where \(\Omega_y\) is independent of \(m\),
then
\[
 (G_X)_{m,n}
 =\sum_y|\Omega_y|^2\overline{\beta_{y,m}}\beta_{y,n}.
\]
In particular, a common unit-modulus M\"obius or phase gauge on an output
fiber cannot by itself improve or degrade the represented Gram.
\end{corollary}

\subsection{When the map does not descend}
For completeness, let \(\widetilde F_X:Z_X\to H_X\) be a row-space map not
known to kill \(\Ker T_X\). Ordinary compression to \(S_T\) is then invalid.
The exact constant is the TPC-62 shorted Gram
\begin{equation}\label{eq:shorted-nondescending}
 \alpha_{T_X}(\widetilde F_X)
 =\lambda_{\min}\!\left(
 T_{X,S}^{-1/2}\widetilde F_{X,S}^*
 P_{\widetilde F_X(\Ker T_X)^\perp}
 \widetilde F_{X,S}T_{X,S}^{-1/2}
 \right),
\end{equation}
not the unprojected compression \citep{WangTPC62}. Equation
\eqref{eq:normalized-row-gram} is valid here precisely because the declared
map is \(A_XL_X\) and therefore annihilates \(\Ker T_X\).
