\section{Spectral capacity after exact nuisance elimination}
\label{sec:tpc65-spectral-capacity}

The general shorted-Gram formula and its kernel criterion belong to the
closure calculus developed in TPC-62; we do not reprove them here.  We begin
after exact nuisance elimination has produced a positive semidefinite
effective Gram \(Q\) on the reference-visible space \(S\), together with a
positive definite reference Gram \(R_{\mathrm{ref},S}\).  In normalized
coordinates,
\begin{equation}
  K_{\mathrm{eff}}
  :=
  R_{\mathrm{ref},S}^{-1/2}
  Q
  R_{\mathrm{ref},S}^{-1/2}
  \ge 0,
  \qquad
  x:=R_{\mathrm{ref},S}^{1/2}s,
  \label{eq:tpc65-effective-gram}
\end{equation}
the exact short implies that every represented/reference quotient with
visible coordinate \(s\) is bounded below by
\begin{equation}
  \frac{\langle K_{\mathrm{eff}}x,x\rangle}{\|x\|^2}.
  \label{eq:tpc65-effective-rayleigh}
\end{equation}
Thus the remaining question is finite-dimensional: when do structural
capacity constraints force a vector to place a definite fraction of its
energy in a spectrally good part of a fixed positive semidefinite Gram?

\subsection{Reducing blocks and structural spectral capacity}

\begin{definition}[Spectral-capacity data]
\label{def:tpc65-spectral-capacity}
Let \(\mathcal S\) be a finite-dimensional Hilbert space, let
\(K\colon\mathcal S\to\mathcal S\) be positive semidefinite, and fix an
orthogonal \(K\)-reducing decomposition over a finite index set
\(\mathcal J\), with every \(\mathcal S_j\ne\{0\}\):
\begin{equation}
  \mathcal S=\bigoplus_{j\in\mathcal J}\mathcal S_j,
  \qquad
  KP_j=P_jK,
  \label{eq:tpc65-reducing-decomposition}
\end{equation}
where \(P_j\) is the orthogonal projection onto \(\mathcal S_j\).
Assign a structural capacity weight \(w_j>0\) to each block and put
\[
  0<W:=\sum_{j\in\mathcal J}w_j<\infty.
\]
These weights are declared energy budgets; they need not equal block
dimensions, ranks, traces, or spectral multiplicities.

For a threshold \(\eta>0\), define
\begin{equation}
  \mathcal G_\eta
  :=
  \left\{
    j\in\mathcal J:
    K|_{\mathcal S_j}\ge \eta I_{\mathcal S_j}
  \right\},
  \qquad
  \delta_\eta
  :=
  \frac{\sum_{j\in\mathcal G_\eta}w_j}{W}.
  \label{eq:tpc65-good-blocks}
\end{equation}
Given \(C>0\) and \(0<\kappa\le 1\), a nonzero vector
\(x\in\mathcal S\) belongs to the corresponding spectral-capacity class if
\begin{equation}
  \|P_jx\|^2\le C^2w_j
  \quad (j\in\mathcal J),
  \qquad
  \|x\|^2\ge \kappa C^2W.
  \label{eq:tpc65-capacity-class}
\end{equation}
\end{definition}

\begin{theorem}[Sharp spectral-capacity lower bound]
\label{thm:tpc65-sharp-spectral-capacity}
For the data of \cref{def:tpc65-spectral-capacity}, every vector satisfying
\eqref{eq:tpc65-capacity-class} obeys
\begin{equation}
  \boxed{
  \frac{\langle Kx,x\rangle}{\|x\|^2}
  \ge
  \eta
  \left(
    1-\frac{1-\delta_\eta}{\kappa}
  \right)_+ ,
  }
  \qquad
  t_+:=\max\{t,0\}.
  \label{eq:tpc65-capacity-bound}
\end{equation}
In particular, the right-hand side is positive precisely when
\begin{equation}
  \kappa>1-\delta_\eta.
  \label{eq:tpc65-positive-threshold}
\end{equation}
The coefficient in \eqref{eq:tpc65-capacity-bound} is optimal if one knows
only \(\eta\), \(\delta_\eta\), \(\kappa\), the block caps, and the total
occupancy condition.
\end{theorem}

\begin{proof}
Orthogonality and the block caps give
\begin{equation}
  \sum_{j\notin\mathcal G_\eta}\|P_jx\|^2
  \le
  C^2\sum_{j\notin\mathcal G_\eta}w_j
  =
  C^2(1-\delta_\eta)W.
  \label{eq:tpc65-bad-energy-cap}
\end{equation}
Dividing this estimate by
\(\|x\|^2\ge\kappa C^2W\) shows that the fraction of the energy in the good
blocks is at least
\[
  \frac{\sum_{j\in\mathcal G_\eta}\|P_jx\|^2}{\|x\|^2}
  \ge
  \left(
    1-\frac{1-\delta_\eta}{\kappa}
  \right)_+.
\]
Because the decomposition is \(K\)-reducing, there are no cross terms between
distinct blocks.  Positivity of \(K\) on the remaining blocks and the
definition of \(\mathcal G_\eta\) therefore yield
\[
  \langle Kx,x\rangle
  =
  \sum_{j\in\mathcal J}
  \langle KP_jx,P_jx\rangle
  \ge
  \eta
  \sum_{j\in\mathcal G_\eta}\|P_jx\|^2.
\]
This proves \eqref{eq:tpc65-capacity-bound}, and
\eqref{eq:tpc65-positive-threshold} follows immediately.

It remains to prove optimality.  Normalize \(C=W=1\).  First suppose
\(0<\delta_\eta<1\), and take two one-dimensional reducing blocks with
weights
\[
  w_{\mathrm g}=\delta_\eta,
  \qquad
  w_{\mathrm b}=1-\delta_\eta,
\]
on which \(K\) acts by \(\eta\) and \(0\), respectively.  If
\(\kappa\le 1-\delta_\eta\), choose
\[
  \|x_{\mathrm g}\|^2=0,
  \qquad
  \|x_{\mathrm b}\|^2=\kappa.
\]
All caps hold, the total energy is \(\kappa\), and the Rayleigh quotient is
zero.  If \(\kappa>1-\delta_\eta\), choose instead
\[
  \|x_{\mathrm b}\|^2=1-\delta_\eta,
  \qquad
  \|x_{\mathrm g}\|^2=\kappa-1+\delta_\eta.
\]
The good-block cap holds because \(\kappa\le1\), and the resulting quotient is
\[
  \eta\,
  \frac{\kappa-1+\delta_\eta}{\kappa}
  =
  \eta
  \left(
    1-\frac{1-\delta_\eta}{\kappa}
  \right).
\]
For the endpoint \(\delta_\eta=0\), a single bad block with energy
\(\kappa\) gives quotient zero.  For \(\delta_\eta=1\), a single good block
on which \(K=\eta I\), again with energy \(\kappa\), gives quotient \(\eta\).
Thus equality is attained in every parameter regime.
\end{proof}

\begin{remark}[Actual occupancy]
\label{rem:tpc65-actual-occupancy}
For a fixed capped vector \(x\ne0\) and a fixed cap scale \(C\), the actual
occupancy is
\begin{equation}
  \kappa(x;C)
  :=
  \frac{\|x\|^2}{C^2W}
  \in(0,1].
  \label{eq:tpc65-actual-occupancy}
\end{equation}
Applying \cref{thm:tpc65-sharp-spectral-capacity} with this value, rather than
with a weaker a priori lower bound, gives
\[
  \frac{\langle Kx,x\rangle}{\|x\|^2}
  \ge
  \eta
  \left(
    1-\frac{1-\delta_\eta}{\kappa(x;C)}
  \right)_+.
\]
Combining this estimate with \eqref{eq:tpc65-effective-rayleigh} gives the
exact capacity consequence for the original quotient.  It applies once the
normalized effective Gram and a valid reducing capacity ledger have both been
identified.
\end{remark}

\subsection{Why physical row capacity does not transfer}

The reducing qualification in \cref{def:tpc65-spectral-capacity} is
indispensable.  Diagonal information in a physical row basis does not control
coherent off-diagonal cancellation.

\begin{proposition}[Sharp row-capacity non-transfer]
\label{prop:tpc65-row-capacity-nontransfer}
There is a positive semidefinite Gram for which every physical coordinate row
has unit diagonal gain and a vector has maximal row-capacity occupancy, while
the represented energy of that vector is zero.  Consequently, physical
row-capacity data alone imply no positive spectral-capacity lower bound.
\end{proposition}

\begin{proof}
Let
\begin{equation}
  \mathcal S=\mathbb C^2,
  \qquad
  A=\begin{pmatrix}1&-1\end{pmatrix},
  \qquad
  K=A^*A
  =
  \begin{pmatrix}
    1&-1\\
    -1&1
  \end{pmatrix}.
  \label{eq:tpc65-collision-gram}
\end{equation}
For the physical coordinate vectors \(e_1,e_2\),
\[
  \langle Ke_1,e_1\rangle
  =
  \langle Ke_2,e_2\rangle
  =1.
\]
Hence a ledger that treats the two physical coordinate rows as independent
good blocks at threshold \(\eta=1\) would record
\(\delta_{\mathrm{row}}=1\).  Give the rows weights
\(w_1=w_2=1\), take \(C=1\), and set
\[
  x=\begin{pmatrix}1\\1\end{pmatrix}.
\]
Both row caps are saturated, and the row occupancy is maximal:
\[
  \kappa_{\mathrm{row}}
  =
  \frac{\|x\|^2}{C^2(w_1+w_2)}
  =1.
\]
Nevertheless,
\[
  Ax=0,
  \qquad
  \langle Kx,x\rangle=0.
\]
The invalid scalar substitution
\((\eta,\delta,\kappa)=(1,1,1)\) into
\eqref{eq:tpc65-capacity-bound} would predict the lower bound \(1\), whereas
the true Rayleigh quotient is \(0\).

The spectral resolution explains the failure.  The eigenvalues of \(K\) are
\(0\) and \(2\), and its kernel is the coherent direction
\(\operatorname{span}\{(1,1)\}\).  The physical coordinate decomposition
\(\mathbb Ce_1\oplus\mathbb Ce_2\) does not reduce \(K\), so it is not an
admissible decomposition in \cref{def:tpc65-spectral-capacity}.  The
off-diagonal terms cancel two individually favorable diagonal gains. Both
diagonal gains and the occupancy saturate the chosen unit normalization, so no
strengthening based only on those scalar row data can repair the conclusion.
\end{proof}

\begin{remark}[Valid recovery routes]
\label{rem:tpc65-valid-recovery}
A physical row-capacity certificate can be transferred to
\cref{thm:tpc65-sharp-spectral-capacity} only after an additional structural
statement is proved.  Sufficient routes include:
\begin{enumerate}
  \item the physical one-row decomposition itself reduces \(K\) (equivalently,
  the relevant Gram is diagonal), or an explicitly declared row grouping gives
  a reducing block-diagonal decomposition;
  \item a quantitative basis-transport or coherence estimate converts the
  physical row caps into caps for a declared \(K\)-reducing decomposition; or
  \item the argument is formulated directly with the spectral projectors of
  the exact effective Gram.
\end{enumerate}
Without one of these bridges, no favorable capacity conclusion is asserted.
\end{remark}

\subsection{Claim boundary}

\Cref{thm:tpc65-sharp-spectral-capacity} and
\cref{prop:tpc65-row-capacity-nontransfer} are finite-dimensional L0
statements.  The operator \(K\), its reducing blocks, the weights, and the
capacity caps are declared data.  This section does not prove that a physical
TPC represented Gram has a favorable value of \(\delta_\eta\), a favorable
occupancy \(\kappa\), or a positive smallest eigenvalue.  It makes no L1
arithmetic identification, does not specialize to the fixed shift \(h_0=2\),
and yields no parity-breaking, prime-pair, or twin-prime conclusion.
