\begin{abstract}
For the literal fixed-shift packet, the terminal map first restricts the
full pre-terminal array to the exact prime equality support, multiplies a
surviving atom by its cofactor sign and shaped terminal logarithm, and then
sums distinct terminal primes inside a complete output fiber
\(y=(\gamma,d(m)r,j)\).  TPC--55 proved that adjoining the terminal prime
to the output key removes every collision on one declared source system.
The remaining internal gate is therefore the coherent square of one
explicit prime-indexed vector in each fiber.  That square can vanish even
when its terminal diagonal is positive.

We prove a universal lower-selection theorem for this exact gate.  Fix a
unit gauge on each output fiber and partition the gauge-normalized realized
nonzero amplitudes into \(M\ge3\) equal angular sectors.  One global sector
index in these normalized coordinates, used simultaneously on every fiber,
selects a coordinate subpacket
whose grouped energy is at least
\[
 \frac{\cos^2(\pi/M)}{M}
\]
times the full terminal diagonal energy.  In each fiber the selected atoms
lie, after its own fixed gauge, in the same relative cone of half-angle
\(\pi/M<\pi/2\).  The corresponding absolute cones may rotate with the
fiber, and the estimate is independent of the fiber cardinalities.  Among
equal finite sectorizations, \(M=5\) is
optimal and gives the exact constant
\((3+\sqrt5)/40\).  Allowing a continuously rotated angular window gives
the slightly larger constant
\(c_*=\theta_*\cos^2\theta_*/\pi=0.1311275\ldots\), where
\(2\theta_*\tan\theta_*=1\).  We also prove a quantitative phase-error
version.

For the literal physical vector, the common gauge is the exact product of
the residual M\"obius sign, opposite-row phase, orbit factor, and common
opposite-row profiles.  The terminal-prime bijection makes every selected
sector an unambiguous coordinate projection on the actual terminal
support.  Consequently, conditional on a separately established
terminal-activation ratio, the adaptive pentant subpacket has no positive
polynomial coherence loss at this selected grouping gate.  Relative to the
earlier rank-by-prime selection, it improves the retained-energy constant at
that gate, at the price of coefficient adaptivity: it retains a constant
fraction of the terminal diagonal without a maximal-multiplicity factor or
a balanced cofactor hypothesis.

The qualifier \emph{adaptive} is essential for the universal
all-coordinate guarantee.  We prove that any selector fixed independently
of the coefficient phases and retaining two coordinates in one fiber has a
nonzero collision-kernel direction on the unrestricted coordinate space.
The inherited class with only an upper bound on the complex source factor
can realize that cancellation locally on any nondegenerate two-atom literal
carrier; this is not promoted to a global literal-class no-go.
Thus the theorem is a fixed-\(h_0\), post-terminal selected-square result,
not a lower bound for the undeleted output.  It does not prove terminal
activation, a coefficient-independent pre-terminal phase realization,
frozen-shift localization, native-Gram comparison, a parity improvement,
or a twin-prime statement.
\end{abstract}
