\section{Adaptive necessity and the pre-terminal phase gate}
\label{sec:adaptive-boundary}

The constant in \cref{thm:tpc56-literal-pentant-extraction} does not come
from a lower singular value of the full grouping map.  It comes from using
the distinguished vector to choose a favorable coordinate cone.  We now
show exactly why that dependence is necessary for the universal
unrestricted-array guarantee, record the corresponding local fiberwise
obstruction in the bounded literal class, and state a sufficient condition
for replacing it by a finite fixed pre-terminal library.

\subsection{The sharp coefficient-independent alternative}

Let \(\Sigma\) be the abstract grouping map
\eqref{eq:tpc56-abstract-grouping}.  For a fixed set \(S\subseteq\cU\),
write \(P_S\) for its coordinate projection.  Here \(S\) is chosen from
the fiber geometry and is independent of the input vector.

The following is the unweighted specialization of the TPC--55
coordinate-transversal criterion, recalled here for comparison
\citep{WangTPC55}.

\begin{theorem}[Fixed-selector dichotomy]
\label{thm:tpc56-fixed-selector-dichotomy}
The following are equivalent:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.8em]
 \item There exists \(c>0\) such that
 \begin{equation}
  \|\Sigma P_Sx\|_2^2\ge c\|P_Sx\|_2^2
  \qquad(x\in\C^{\cU}).
  \label{eq:tpc56-fixed-selector-lower}
 \end{equation}
 \item Every fiber contains at most one selected coordinate:
 \begin{equation}
  |S\cap\cF_y|\le1\qquad(y\in\cY).
  \label{eq:tpc56-fixed-selector-transversal}
 \end{equation}
\end{enumerate}
When these conditions hold, \eqref{eq:tpc56-fixed-selector-lower} is an
identity with \(c=1\).  If they fail, the restricted map has a nonzero
two-coordinate kernel vector.
\end{theorem}

\begin{proof}
If \eqref{eq:tpc56-fixed-selector-transversal} holds, every selected output
is either zero or one input coordinate, hence
\(\|\Sigma P_Sx\|_2=\|P_Sx\|_2\).  Conversely, suppose
\(u,v\in S\cap\cF_y\) are distinct.  Take \(x_u=1\), \(x_v=-1\), and all
other coordinates zero.  Then \(P_Sx=x\ne0\) but \(\Sigma P_Sx=0\), so no
positive \(c\) is possible.
\end{proof}

Thus a single coefficient-independent selector with a uniform lower bound
on the unrestricted coefficient space is exactly a transversal.  The
pentant theorem escapes this dichotomy because its coordinate set changes
with the realized phases.  It retains a constant fraction of the energy
without claiming a lower bound for all vectors on the same selected set.

\subsection{Realization of the local collision in the literal class}

The abstract kernel direction is compatible with the source hypothesis
actually inherited by the literal packet.  Factor the remaining amplitude
\eqref{eq:tpc56-remaining-amplitude} as
\begin{equation}
 b_u=\kappa_u\zeta_{m_u},
 \label{eq:tpc56-baseline-times-zeta}
\end{equation}
where \(\kappa_u\) is the product of every displayed factor other than
\(\zeta_{m_u}\).  Call a terminal atom \emph{baseline nondegenerate} when
\(\Omega_{q(u)}\kappa_u\ne0\).

\begin{proposition}[Literal two-atom saturation]
\label{prop:tpc56-literal-two-atom-saturation}
Suppose \(C>0\) and one exact physical-capable fiber
\(\cF_y^{\rm term}\) contains two
distinct baseline-nondegenerate atoms \(u_1,u_2\).  In the inherited
coefficient class \(|\zeta_m|\le C\), there are coefficient choices for
which the restriction of that fiber to \(\{u_1,u_2\}\) has positive
terminal diagonal and zero coherent output.  More precisely, for a
sufficiently small \(t\ne0\), one may take
\begin{equation}
 \zeta_{m_{u_1}}=\frac{t}{\kappa_{u_1}},
 \qquad
 \zeta_{m_{u_2}}=-\frac{t}{\kappa_{u_2}},
 \label{eq:tpc56-cancelling-zeta-choice}
\end{equation}
and set the source factors belonging to every other row in this fiber to
zero.  Then
\begin{equation}
 D_y=2|\Omega_y t|^2>0,
 \qquad
 C_y=0.
 \label{eq:tpc56-literal-local-cancellation}
\end{equation}
Here \(D_y,C_y\) refer to the resulting fiber, with all its other rows
zeroed.
\end{proposition}

\begin{proof}
Distinct terminal atoms in a fixed fiber have distinct rows.  Indeed, the
row determines \(d\), and fixed \(s=dr\) then determines \(r\); fixed
\((j,\gamma)\) would otherwise give the same input.  Thus the two values of
\(\zeta_m\) in \eqref{eq:tpc56-cancelling-zeta-choice} are independent
coordinates.  Choose \(|t|\) small enough that both values have modulus at
most \(C\).  Equations \eqref{eq:tpc56-baseline-times-zeta} and
\eqref{eq:tpc56-physical-gauge-factorization} give terminal amplitudes
\(\Omega_yt\) and \(-\Omega_yt\), proving
\eqref{eq:tpc56-literal-local-cancellation}.
\end{proof}

The proposition is a no-go statement for a uniform \emph{fiberwise} lower
bound over the inherited bounded coefficient class.  It does not assert
that the distinguished inherited coefficients realize these choices, that
such a two-atom fiber carries global energy, or that other physical output
fibers vanish.  Those stronger conclusions would require additional
support information.

Prime-resolved injectivity, common M\"obius phase, a nonzero terminal
weight, and even multiplicity two therefore do not imply positive
coherence for arbitrary bounded source phases.  This is a coefficient
space obstruction, not a proof that the intended arithmetic vector
cancels.

\subsection{A finite fixed phase-provenance criterion}

There is a precise way in which the adaptive selector could become
compatible with an earlier source decomposition.  For an integer
\(M\ge2\), let
\begin{equation}
 \cU^{\rm pre}=\bigsqcup_{k=0}^{M-1}\cA_k
 \label{eq:tpc56-preterminal-phase-partition}
\end{equation}
be a partition chosen independently of terminal primality and independently
of the numerical values of the source coefficients.  Its coordinate
projections are fixed before \(D_{h_0}\) is applied.

\begin{theorem}[Pre-terminal phase-realization criterion]
\label{thm:tpc56-preterminal-phase-realization}
Let \(g\in\C^{\cU^{\rm pre}}\) and put \(x=D_{h_0}g\).  Suppose
\(0\le\theta<\pi/2\), and there are angles
\(\alpha_0,\ldots,\alpha_{M-1}\) and unit output gauges \(\omega_y\), all
fixed from coefficient-independent pre-terminal and output data before the
realized numerical source phases are seen.  In particular, neither the
angles nor the gauges may be chosen from the realized phases of \(x\).
Suppose every nonzero terminal amplitude in
\(\cA_k\cap\cF_y^{\rm term}\) satisfies
\begin{equation}
 \dist_{\T}
 \left(\Arg(\overline{\omega_y}x_u),\alpha_k\right)
 \le\theta.
 \label{eq:tpc56-preterminal-sector-hypothesis}
\end{equation}
Then one of the \emph{fixed} pre-terminal cells, chosen by the least-index
energy tie rule after terminal activation, satisfies
\begin{equation}
 \boxed{
 \|\Sigma D_{h_0}P_{\cA_{k_*}}g\|_2^2
 \ge\frac{\cos^2\theta}{M}\|D_{h_0}g\|_2^2.}
 \label{eq:tpc56-preterminal-sector-lower}
\end{equation}
The same statement holds after restriction to a declared output-fiber
family, relative to its terminal diagonal energy.
\end{theorem}

\begin{proof}
The fixed cells partition the full pre-terminal coordinates and hence their
terminal diagonal energies sum to \(\|D_{h_0}g\|_2^2\).  One cell retains
at least an \(M^{-1}\) fraction.  On each output fiber its surviving
amplitudes obey the acute-sector hypothesis
\eqref{eq:tpc56-preterminal-sector-hypothesis}.  The real-projection proof
of \eqref{eq:tpc56-fiber-sector-proof} gives a factor
\(\cos^2\theta\).
\end{proof}

This theorem separates two kinds of adaptivity.  Choosing one member of a
fixed finite library by energy pigeonhole is harmless at the exponent
level.  Defining the library itself from the realized terminal phases, as
in \cref{thm:tpc56-literal-pentant-extraction}, is a new post-terminal
operation.

The row provenance in TPC--25 permits fixed residue characters and
unit-modulus factors inside \(\zeta_m\) \citep{WangTPC25}.  The interface
inherited by TPC--53--55, however, records only \(|\zeta_m|\ll1\).  It does
not prove that the distinguished \(\zeta_m\) phases are determined by a
fixed finite residue partition.  Even if they are, one must also select
sign-stable cells for every source and profile factor in
\eqref{eq:tpc56-remaining-amplitude} and prove that those cells carry the
required terminal diagonal energy.  Geometric nonempty support alone is
insufficient by the concentration obstruction of TPC--54
\citep{WangTPC54}.

Accordingly, \cref{thm:tpc56-preterminal-phase-realization} is the exact
next positive criterion, not a property silently attributed to the current
packet.
