\section{Endpoint ledger, audit, and the next gate}
\label{sec:endpoint-claims}

\subsection{The selected coherence exponent}

The inherited endpoint scales are
\begin{equation}
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)},
 \qquad
 D=X^{10049/52500+o(1)},
 \label{eq:tpc56-endpoint-QJD}
\end{equation}
and hence
\begin{equation}
 L=Q/D=X^{99979/210000+o(1)}.
 \label{eq:tpc56-endpoint-L}
\end{equation}
The constant \(c_5=(3+\sqrt5)/40\) in
\eqref{eq:tpc56-literal-pentant-lower} is independent of every scale.
Therefore the adaptive selected grouping gate has
\begin{equation}
 \lambda_{\rm coh}^{\rm sec}=0
 \label{eq:tpc56-zero-sector-exponent}
\end{equation}
relative to terminal diagonal energy.  Unlike the coefficient-blind
prime-rank certificate in TPC--55, this statement has no factor
\(1+L/R\) and remains constant even at \(R\asymp J\).  Its price is
structural adaptivity, not a hidden polynomial exponent.

To place the theorem in the full prospective chain, suppose a parent
physical atomic energy is first restricted to a compatible packet and a
cofactor block at costs
\begin{equation}
 X^{-\lambda_{\rm sel}+o(1)},
 \qquad
 X^{-\lambda_{\rm blk}+o(1)}.
 \label{eq:tpc56-upstream-selection-losses}
\end{equation}
Suppose terminal activation and any restriction to a declared output-fiber
family cost
\begin{equation}
 X^{-\lambda_{\rm term}+o(1)},
 \qquad
 X^{-\lambda_{\rm fib}+o(1)}.
 \label{eq:tpc56-activation-coverage-losses}
\end{equation}
Then \cref{cor:tpc56-activation-coverage-transfer} gives the selected
fixed-shift residual-output exponent
\begin{equation}
 \lambda_{\rm sel}+\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm fib},
 \label{eq:tpc56-selected-ledger}
\end{equation}
with no added positive-power coherence cost.

Formula \eqref{eq:tpc56-selected-ledger} is valid only for the explicitly
adaptive terminal subpacket.  It may enter the eventual physical proof
chain only if later localization, Gram comparison, boundary truncation,
and tail reconstruction preserve that coordinate selection, or if the
selector is realized by the fixed pre-terminal criterion of
\cref{thm:tpc56-preterminal-phase-realization}.  This is a logical gate,
not an exponent silently set to zero.

For the undeleted physical output, one must instead prove
\begin{equation}
 \cG_{h_0}(g)
 \ge X^{-\lambda_{\rm coh}+o(1)}\cD_{h_0}(g).
 \label{eq:tpc56-full-coherence-hypothesis}
\end{equation}
The present paper does not prove \eqref{eq:tpc56-full-coherence-hypothesis}.
If a route uses a completed frozen shift family or signed projective
layers, it must also charge \(\lambda_{\rm loc}\) and
\(\lambda_{\rm reas}\) from estimates of the forms
\eqref{eq:tpc56-required-shift-localization} and
\eqref{eq:tpc56-required-lower-reassembly}.  The complete prospective
undeleted ledger is therefore
\begin{equation}
 \boxed{
 \begin{aligned}
 &\lambda_{\rm sel}+\lambda_{\rm blk}
 +\lambda_{\rm term}+\lambda_{\rm fib}+\lambda_{\rm coh}
 +\lambda_{\rm loc}+\lambda_{\rm reas}\\
 &\hspace{23mm}
 +\lambda_{\rm Gram}+\lambda_{\rm bdry}+\lambda_{\rm tail}
 \le\frac1{400}.
 \end{aligned}}
 \label{eq:tpc56-full-endpoint-budget}
\end{equation}
For a direct pointwise theorem at the already reassembled physical
\(h_0\), no localization or projective-reassembly gate is inserted.  At
equality in \eqref{eq:tpc56-full-endpoint-budget}, a further error of size
\(X^{-1/400+o(1)}\) need not be absorbable; strict slack or a closed
constant-level comparison remains the safe endpoint condition.

\subsection{Six-point physical audit}

The proof satisfies the following interface audit.
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3.2em]
 \item \emph{Literal coefficients.}
       The source weight, bounded complex factor, binary mask, four
       profiles, cofactor sign, and shaped terminal logarithm are all
       displayed in
       \eqref{eq:tpc56-source-coefficient}--
       \eqref{eq:tpc56-terminal-diagonal}.  Sector membership is formed
       from their product, not from a proxy coefficient.
 \item \emph{Fixed physical shift.}
       Every terminal equality uses the one specified \(h_0\).  Frozen
       intercepts appear only in the nonlocalization warning of
       \cref{sec:transport-boundaries}.
 \item \emph{Physical atomic normalization.}
       The pre-terminal, terminal diagonal, and grouped energies use raw
       counting measure in
       \eqref{eq:tpc56-preterminal-energy}--
       \eqref{eq:tpc56-grouped-energy}.  The terminal amplitude is not
       absorbed into a modified domain norm.
 \item \emph{Canonical representation.}
       The prime coordinate comes from the exact TPC--55 injection.  The
       pentants are the five fixed equal arcs, the common output gauge is
       \eqref{eq:tpc56-unit-output-gauge}, and ties use the least index.
       The support remains explicitly coefficient-adaptive; no projective
       layer is selected.
 \item \emph{Actual active support.}
       The full pre-terminal universe, terminal-admissible universe, and
       physically nonzero universe are distinct in
       \eqref{eq:tpc56-preterminal-universe},
       \eqref{eq:tpc56-terminal-universe}, and
       \eqref{eq:tpc56-physical-universe}.  Every selected prime belongs to
       the exact physical prime set \(\cP_y^{\rm phys}\).
 \item \emph{Endpoint budget.}
       The constant sector step has zero positive polynomial exponent only
       on the adaptive selected packet.  All activation, fiber coverage,
       localization, reassembly, Gram, boundary, and tail losses remain
       visible in \eqref{eq:tpc56-full-endpoint-budget}.
\end{enumerate}

\subsection{Claim table}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.29\textwidth}
                >{\raggedright\arraybackslash}p{0.60\textwidth}}
\toprule
Statement & Status \\
\midrule
Equal-sector compression and pentant constant
& Unconditional finite-dimensional theorem (L0). \\
Rotating-window and phase-error bounds
& Unconditional finite-dimensional refinements (L0). \\
Literal prime-indexed sector projection
& Exact on the fixed-\(h_0\) terminal support under the inherited
  prime-resolved injection (L1). \\
Constant-energy selected coherent square
& Exact post-terminal adaptive L1 selection; no multiplicity or balanced
  cofactor cost. \\
Fixed-selector dichotomy
& Exact L0 theorem; fixed uniform lower selectors are precisely
  transversals. \\
Literal two-atom saturation
& Local coefficient-class L1 no-go, conditional on a nondegenerate
  two-atom carrier; not a claim about the distinguished coefficients or
  global output. \\
Fixed pre-terminal phase realization
& Sufficient L0/L1 criterion; its phase and energy hypotheses are not
  verified for the inherited packet. \\
Terminal activation and energetic block occupancy
& Not proved. \\
Undeleted fixed-\(h_0\) coherent lower square
& Not proved; the five inter-sector channels may still cancel. \\
Frozen localization, native affine Gram, boundary, and tail
& Not proved. \\
Parity improvement or twin-prime consequence
& Not claimed. \\
\bottomrule
\end{tabular}
\end{center}

In particular, none of the following implications is permitted:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item a lower bound for one adaptive pentant does not lower-bound the sum
       of all five pentants;
 \item a constant selected fraction of terminal diagonal energy does not
       prove that terminal activation occurs;
 \item the common M\"obius gauge does not constrain the remaining
       \(\zeta_m\) and profile phases;
 \item a phase-defined terminal set is not automatically a fixed smooth or
       residue cell available before primality is tested;
 \item an average over frozen shifts or auxiliary Fourier phases does not
       select the prescribed physical coefficient;
 \item a favorable projective layer does not survive signed reassembly by
       a lower Minkowski inequality; and
 \item the residual grouped norm is not automatically the native affine
       physical Gram.
\end{enumerate}

\subsection{The next gate}

Complete within-sector cancellation is now uniformly excluded on a
constant-energy subpacket.  The next stage should investigate the
\emph{undeleted} five-channel problem by routes that are still pointwise in
\(h_0\).  Three concrete quantities are available.
\begin{enumerate}[label=\textbf{Door \Alph*.},leftmargin=3.8em]
 \item Measure the terminal diagonal carried by singleton fibers.  Their
       coherent square equals their diagonal without any phase hypothesis.
       Equivalently, bound the energy-weighted collision incidence of
       multiple fibers.
 \item Use the distinct terminal primes to form an auxiliary
       prime-modulated polynomial, compute its exact Parseval diagonal, and
       quantify the microscopic localization needed to return its average
       energy to the physical phase zero.
 \item Audit whether the actual \(\zeta_m\) and sign-stable source profiles
       admit the fixed finite phase partition in
       \cref{thm:tpc56-preterminal-phase-realization}; if not, prove a
       saturation theorem for every such fixed partition.
\end{enumerate}
Door A is phase-blind but needs arithmetic occupancy.  Door B has an exact
mean square but a pointwise localization barrier.  Door C would convert the
present adaptive theorem into a transportable pre-terminal selection.  A
negative theorem for any door remains useful and must retain its own label.

\paragraph{Conclusion.}
The literal coherent-prime gate admits a universal constant-energy escape
from its collision kernel: five gauge-normalized relative phase sectors
suffice, and one global normalized-sector index retains at least
\((3+\sqrt5)/40\) of the full terminal diagonal after grouping.  The
absolute windows may rotate with the fibers.  This removes every positive polynomial
multiplicity cost from the adaptive selected square.  The same theorem
also exposes its exact limitation.  On the unrestricted coordinate space,
uniform coefficient-independent lower selection is possible only on
collision-free transversals.  The literal two-atom result proves the
corresponding local fiberwise obstruction, not a global coefficient-class
no-go.  The undeleted five-channel interference, terminal
activation, fixed-shift localization, native-Gram comparison, boundary,
and tail gates remain open, strictly before any parity-sensitive or
twin-prime conclusion.
