\section{Introduction}
\label{sec:introduction}

The preceding three stages of this program separated three losses that
had previously been hidden inside one schematic prime square.  TPC--53
fixed the literal four-factor coefficient dictionary and the raw atomic
normalization \citep{WangTPC53}.  TPC--54 proved sharp pre-terminal energy
selection laws and showed that magnitude information cannot survive an
arbitrary many-to-one complex sum \citep{WangTPC54}.  TPC--55 then resolved
the complete fixed-shift output fiber \citep{WangTPC55}.  If
\[
 u=(m,r,j,\gamma),\qquad m=d\ell,
\]
survives the exact terminal restriction, then
\begin{equation}
 p_u=\frac{mj+h_0}{r}
 \label{eq:tpc56-intro-terminal-prime}
\end{equation}
is prime and the complete output is
\begin{equation}
 y=q(u)=(\gamma,s=d r,j).
 \label{eq:tpc56-intro-output-key}
\end{equation}
Under the inherited row geometry, adjoining \(p_u\) to the key is
injective.  Thus the only remaining collision is the deliberate operation
that forgets \(p\) and coherently adds all terminal primes in the same
\((\gamma,s,j)\)-fiber.

Write the terminalized amplitude indexed by that prime as
\begin{equation}
 x_{y,p}
 =\mu(r_{y,p})\Lambda(p r_{y,p})g_{u(y,p)}.
 \label{eq:tpc56-intro-literal-amplitude}
\end{equation}
The exact diagonal and grouped energies are
\begin{equation}
 \cD_{h_0}(g)=\sum_y\sum_{p\in\cP_y}|x_{y,p}|^2,
 \qquad
 \cG_{h_0}(g)=\sum_y\left|\sum_{p\in\cP_y}x_{y,p}\right|^2.
 \label{eq:tpc56-intro-two-energies}
\end{equation}
All sums in \eqref{eq:tpc56-intro-two-energies} are over the exact finite
terminal support; \(\cP_y\) is not an ambient interval of primes.  The
ratio \(\cG_{h_0}/\cD_{h_0}\) can be zero.  TPC--55 supplied two ways to
avoid that zero: impose an acute sector condition, or retain at most one
prime in each fiber.  The first was only a criterion.  The second was an
unconditional post-terminal construction, but on a cofactor block it
retained only the reciprocal of the maximal fiber multiplicity.

The present paper asks a narrower question:
\begin{quote}
Can one always extract a genuinely coherent terminal-prime subpacket while
retaining a constant fraction of the full terminal diagonal, independently
of the fiber sizes?
\end{quote}
The answer is yes if the selection is permitted to use the realized phases.
The proof is elementary, but its placement in the physical operator is
order-sensitive.  Split the complex plane into five equal sectors after
removing the common output gauge.  The five sectors partition the terminal
diagonal, so one of them carries at least one fifth of that energy.  Inside
one sector every amplitude has real projection at least
\(\cos(\pi/5)\) times its modulus.  Therefore the selected grouped square
is at least
\begin{equation}
 c_5\cD_{h_0}(g),
 \qquad
 c_5:=\frac{\cos^2(\pi/5)}5
      =\frac{3+\sqrt5}{40}.
 \label{eq:tpc56-intro-pentant-constant}
\end{equation}
Only one sector index is selected globally in the gauge-normalized phase
coordinates; it is not chosen separately for every output fiber.  The
corresponding absolute angular window is rotated by the canonical gauge of
that fiber.

This gives a real advance at the selected grouping gate.  No
\(X^{\varepsilon}\), divisor, or maximal-multiplicity factor appears.
If a pre-terminal packet satisfies the separate activation estimate
\begin{equation}
 \cD_{h_0}(g)\ge
 X^{-\lambda_{\rm term}+o(1)}\cE_{\rm pre}(g),
 \label{eq:tpc56-intro-activation}
\end{equation}
then the selected physical output satisfies
\begin{equation}
 \cG_{h_0}(P_*g)
 \ge c_5X^{-\lambda_{\rm term}+o(1)}\cE_{\rm pre}(g).
 \label{eq:tpc56-intro-selected-transfer}
\end{equation}
Thus the adaptive coherence exponent is zero.  In contrast with the
rank-by-prime transversal, no balanced condition such as \(R\gg L\) is
needed.

There is an equally important negative half.  The sets selected by the
five-sector rule depend on the phases of \(x_{y,p}\).  Once the realized
vector is fixed, each is an ordinary orthogonal coordinate projection;
as a rule on a coefficient class, however, the construction is nonlinear.
On the unrestricted coordinate space, if a coefficient-independent set
contains two coordinates of one fiber, the vector assigning opposite values
to those coordinates lies in the grouping kernel.  The inherited hypothesis
\(|\zeta_m|\ll1\) also realizes this cancellation \emph{inside} any
nondegenerate two-atom literal fiber by sufficiently small choices of the
two relevant source factors.  This proves failure of a uniform fiberwise
lower bound for such a selector.  It does not by itself disprove a global
lower bound over the coupled literal coefficient class, because the same
row coefficients may activate other fibers.  A global literal-class no-go
would require control or isolation of those additional outputs.

This dichotomy is useful for the route ahead:
\begin{equation}
 \boxed{
 \begin{array}{c}
 \text{adaptive terminal phases}\Rightarrow
 \text{constant-energy coherent subpacket},\\[2pt]
 \text{uniform selection on unrestricted arrays}\Rightarrow
 \text{at most one atom per fiber},
 \end{array}}
 \label{eq:tpc56-intro-dichotomy}
\end{equation}
It turns an unstructured prime-collision space into a five-channel phase
interface.  A future paper can now ask whether the five channels come from
fixed residue and sign-stable source cells, or whether every such attempted
pre-terminal realization meets a collision obstruction, with global
literal-class saturation requiring separate control of row couplings.

\subsection{Relation to the earlier coherent square}

The physical object in \eqref{eq:tpc56-intro-two-energies} must not be
identified with the projective/frozen square isolated in TPC--48
\citep{WangTPC48}.  That earlier object has the schematic form
\begin{equation}
 \sum_{m,r}
 \left\|\sum_p A_\omega(p,r,m)
 e(-pr\alpha)v_{\omega,p,r,m}\right\|^2,
 \label{eq:tpc56-intro-projective-square}
\end{equation}
before signed projective reassembly.  It keeps \((m,r)\) separate and
extends the physical coefficient field to frozen intercepts.  The present
square is already reassembled, uses one specified \(h_0\), and groups by
the complete literal output \((\gamma,d(m)r,j)\).  A lower estimate for an
average of \eqref{eq:tpc56-intro-projective-square} does not become a lower
estimate for \eqref{eq:tpc56-intro-two-energies} without separate lower
reassembly and fixed-shift localization theorems.

\subsection{Organization and claim level}

\Cref{sec:literal-interface} states the full physical coefficient and
support dictionary.  \Cref{sec:sector-theorem} proves the abstract
finite-sector theorem, its optimal equal-sector constant, the rotating
window refinement, and phase stability.  \Cref{sec:physical-specialization}
specializes it through the exact terminal-prime bijection.
\Cref{sec:adaptive-boundary} proves adaptive necessity and gives a
pre-terminal phase-realization criterion.  \Cref{sec:transport-boundaries}
records the frozen-average and signed-reassembly non-implications.
\Cref{sec:endpoint-claims} gives the endpoint ledger and six-point audit.

The sector theorem is unconditional finite-dimensional mathematics (L0).
Its use on the literal fixed-\(h_0\) terminal vector is an exact physical
interface result (L1).  Terminal activation and a pre-terminal realization
of the adaptive selector are not proved.  Nothing here improves a sieve
lower bound or crosses the parity boundary described in the classical
sieve literature \citep{FriedlanderIwaniec2010}; no prime-pair or
twin-prime conclusion is asserted.
