\section{Specialization to the literal terminal-prime square}
\label{sec:physical-specialization}

We now apply \cref{thm:tpc56-equal-sector-selection} to
\(x=D_{h_0}G_X^L\).  The specialization uses the exact physical support
twice: first to identify each coordinate with one terminal prime, and then
to remove the common fiber gauge without changing any phase difference.

\subsection{Prime-indexed pentants}

For an active output \(y\), let \(u(y,p)\) be the unique input associated
with \(p\in\cP_y^{\rm phys}\) by
\cref{prop:tpc56-prime-resolved-bijection}, and put
\begin{equation}
 x_{y,p}
 :=(D_{h_0}G_X^L)_{u(y,p)}
 =\mu(r_{y,p})\Lambda(p r_{y,p})
   [G_X^L]_{u(y,p)}.
 \label{eq:tpc56-prime-indexed-amplitude}
\end{equation}
Then
\begin{align}
 D_y&:=\sum_{p\in\cP_y^{\rm phys}}|x_{y,p}|^2,
 \label{eq:tpc56-fiber-diagonal}\\
 C_y&:=\left|\sum_{p\in\cP_y^{\rm phys}}x_{y,p}\right|^2.
 \label{eq:tpc56-fiber-coherent-square}
\end{align}
Empty fibers have \(D_y=C_y=0\).  A nonzero singleton fiber has
\(C_y=D_y\).  Globally,
\begin{equation}
 \cD_{h_0}(G_X^L)=\sum_yD_y,
 \qquad
 \cG_{h_0}(G_X^L)=\sum_yC_y.
 \label{eq:tpc56-global-prime-square}
\end{equation}

For \(D_y>0\), use the literal unit gauge \(\omega_y\) from
\eqref{eq:tpc56-unit-output-gauge}.  Equations
\eqref{eq:tpc56-physical-gauge-factorization} and
\eqref{eq:tpc56-prime-indexed-amplitude} show that
\begin{equation}
 \Arg(\overline{\omega_y}x_{y,p})
 =\Arg b_{u(y,p)}.
 \label{eq:tpc56-normalized-literal-phase}
\end{equation}
Partition these exact phases into the five fixed intervals
\(I_0,\ldots,I_4\) of \eqref{eq:tpc56-equal-sectors}.  Let
\begin{equation}
 \cP_{y,k}^{\rm sec}
 :=\{p\in\cP_y^{\rm phys}:
     \Arg b_{u(y,p)}\in I_k\},
 \label{eq:tpc56-prime-pentants}
\end{equation}
and pull this set back through the prime-resolved bijection.  This defines
an orthogonal coordinate projection \(P_k^{\rm sec}\) on the terminal
coordinate space.  Extend it by zero to the rest of \(\cU^{\rm pre}\).
For the fixed realized vector, diagonal coordinate projections commute
with the terminal diagonal:
\begin{equation}
 D_{h_0}P_k^{\rm sec}G_X^L
 =P_k^{\rm sec}D_{h_0}G_X^L.
 \label{eq:tpc56-selector-commutation}
\end{equation}

\begin{theorem}[Literal pentant extraction]
\label{thm:tpc56-literal-pentant-extraction}
Assume the hypotheses of
\cref{prop:tpc56-prime-resolved-bijection}.  Let \(k_*\) be the least
pentant index whose selected terminal diagonal energy is maximal.  Then
\begin{align}
 \cD_{h_0}(P_{k_*}^{\rm sec}G_X^L)
 &\ge\frac15\cD_{h_0}(G_X^L),
 \label{eq:tpc56-selected-diagonal-fraction}\\
 \boxed{
 \cG_{h_0}(P_{k_*}^{\rm sec}G_X^L)
 \ge\frac{3+\sqrt5}{40}\cD_{h_0}(G_X^L).}
 \label{eq:tpc56-literal-pentant-lower}
\end{align}
Both statements include the zero-energy case.  The selected support is an
exact subset of the physical terminal-prime support; no ambient prime has
been inserted.
\end{theorem}

\begin{proof}
If \(\cD_{h_0}(G_X^L)=0\), take the zero projection.  Otherwise apply
\cref{thm:tpc56-equal-sector-selection} to the finite terminalized vector
with the gauges \eqref{eq:tpc56-unit-output-gauge}.  The first conclusion
is the diagonal pigeonhole.  The second is
\eqref{eq:tpc56-universal-sector-lower} with \(M=5\), together with
\eqref{eq:tpc56-selector-commutation} and
\eqref{eq:tpc56-pentant-constant}.
\end{proof}

The theorem is more restrictive and canonical than selecting one pentant
separately in every fiber: remarkably, a single index \(k_*\) works in the
normalized phase coordinates after the fiber-dependent canonical gauges are
removed.  In absolute phase coordinates the five windows are rotated by
\(\omega_y\).  The partition itself uses the realized phases \(\Arg b_u\).

\subsection{Arbitrary fiber families and activation transfer}

Let \(\cY_*\subseteq\cY_{h_0}^{\rm term}\) be any declared family of
terminal output fibers, and let
\begin{equation}
 \cD_{h_0}(g;\cY_*)
 :=\sum_{y\in\cY_*}\sum_{u\in\cF_y^{\rm term}}
 |(D_{h_0}g)_u|^2.
 \label{eq:tpc56-fiber-family-diagonal}
\end{equation}
Apply the sector theorem after setting every terminalized coordinate
outside \(\cY_*\) to zero.

\begin{corollary}[Activation--coverage--sector transfer]
\label{cor:tpc56-activation-coverage-transfer}
Let \(g\) be a literal selected pre-terminal packet with
\(\cE_{\rm pre}(g)>0\).  Suppose
\begin{align}
 \cD_{h_0}(g)
 &\ge X^{-\lambda_{\rm term}+o(1)}\cE_{\rm pre}(g),
 \label{eq:tpc56-terminal-activation-hypothesis}\\
 \cD_{h_0}(g;\cY_*)
 &\ge X^{-\lambda_{\rm fib}+o(1)}\cD_{h_0}(g).
 \label{eq:tpc56-fiber-coverage-hypothesis}
\end{align}
Use any exact unit gauges on the active fibers; for the physical vector
they may be chosen as in \eqref{eq:tpc56-unit-output-gauge}.  Then an
adaptive pentant projection supported over \(\cY_*\) satisfies
\begin{equation}
 \boxed{
 \cG_{h_0}(P_*g)
 \ge c_5X^{-(\lambda_{\rm term}+\lambda_{\rm fib})+o(1)}
 \cE_{\rm pre}(g).}
 \label{eq:tpc56-activation-sector-transfer}
\end{equation}
For the family of all active fibers, one has \(\lambda_{\rm fib}=0\).
\end{corollary}

\begin{proof}
Apply \cref{thm:tpc56-equal-sector-selection} to the restriction of
\(D_{h_0}g\) over \(\cY_*\).  This gives
\(\cG_{h_0}(P_*g)\ge c_5\cD_{h_0}(g;\cY_*)\).  Substitute
\eqref{eq:tpc56-terminal-activation-hypothesis} and
\eqref{eq:tpc56-fiber-coverage-hypothesis}.
\end{proof}

The order of the hypotheses matters.  Terminal activation is measured on
the full declared pre-terminal packet before any phase selector is formed.
The phase selection then acts only on the surviving terminal coordinates.
No assertion that a convenient fiber is nonempty or energetically
representative is hidden in \eqref{eq:tpc56-fiber-coverage-hypothesis}.

\subsection{Cofactor blocks and comparison with rank selection}

For a cofactor interval \(\cB_R=[R,2R]\), put
\begin{equation}
 g_R=g\one_{r\in\cB_R}.
 \label{eq:tpc56-cofactor-block}
\end{equation}
The fibers of \(D_{h_0}g_R\) are simply intersections of the full fibers
with the block.  No new collision is created, so the sector theorem gives
\begin{equation}
 \cG_{h_0}(P_{*,R}g_R)
 \ge c_5\cD_{h_0}(g_R)
 \label{eq:tpc56-block-sector-lower}
\end{equation}
for every block, empty or nonempty.  Unlike the TPC--55 rank cover, this
does not require \(R\gg L\) or a bound for the maximal fiber size.

The two selectors solve different problems:
\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.25\textwidth}
                >{\raggedright\arraybackslash}p{0.31\textwidth}
                >{\raggedright\arraybackslash}p{0.31\textwidth}}
\toprule
Feature & Prime-rank transversal & Phase-sector selector \\
\midrule
Atoms retained per fiber
& At most one
& Arbitrarily many in one acute sector \\
Terminal diagonal retained
& At least reciprocal maximal multiplicity
& At least \(1/5\) globally \\
Grouped/diagonal ratio on selected packet
& Exactly one
& At least \(\cos^2(\pi/5)\) \\
Balanced cofactor input
& Needed for subpower loss
& Not needed \\
Dependence on coefficient phases
& None
& Essential under the current coefficient class \\
Pre-terminal smooth provenance
& Not automatic
& Not automatic \\
\bottomrule
\end{tabular}
\end{center}

Thus \eqref{eq:tpc56-literal-pentant-lower} improves the retained-energy
constant over rank selection at the \emph{adaptive selected} grouping gate,
at the price of coefficient adaptivity.  It removes the multiplicity cost
there, but does not return the deleted four pentants to the full physical
output.

\subsection{Five-channel form of the remaining cancellation}

For the physical vector define
\begin{equation}
 z_{y,k}:=
 \sum_{p\in\cP_{y,k}^{\rm sec}}x_{y,p}.
 \label{eq:tpc56-sector-channel}
\end{equation}
Then the original output and the phase-split energy satisfy the exact
relations
\begin{align}
 (\cT_{h_0}G_X^L)_y
 &=\sum_{k=0}^4z_{y,k},
 \label{eq:tpc56-five-channel-reassembly}\\
 \sum_y\sum_{k=0}^4|z_{y,k}|^2
 &\ge\cos^2(\pi/5)\cD_{h_0}(G_X^L).
 \label{eq:tpc56-five-channel-lower}
\end{align}
Accordingly, complete within-sector prime cancellation is uniformly
excluded, with the quantitative lower bound in
\eqref{eq:tpc56-five-channel-lower}.  The undeleted problem is now the explicit
five-channel interference in \eqref{eq:tpc56-five-channel-reassembly}.
The latter may still vanish by cancellation between different pentants.
