\section{Why averaged phases and projective layers do not close the gate}
\label{sec:transport-boundaries}

The sector theorem is pointwise in the one physical terminal vector.  Two
nearby routes produce legitimate positive averages but do not imply a lower
bound for the prescribed undeleted output.  We record the elementary
non-implications because both have appeared upstream in the TPC
decomposition.

\subsection{Shift averages do not select the prescribed shift}

Write \(e(t)=e^{2\pi i t}\), and give \(\T\) normalized Haar measure.
Let \(\mathscr H\subset\mathbb Z\) be a finite set of intercepts containing
\(h_0\), and
let \(F_h\) be vectors in an arbitrary Hilbert space.  A completed frozen
family may satisfy a lower estimate for
\(\sum_{h\in\mathscr H}\|F_h\|^2\), or equivalently for a Fourier integral.
That is not a pointwise estimate at \(h_0\).

\begin{proposition}[Sharp fixed-member nonlocalization]
\label{prop:tpc56-fixed-member-nonlocalization}
Assume \(|\mathscr H|\ge2\) and let \(w_h\ge0\) be weights with
\(w_{h_1}>0\) for some \(h_1\ne h_0\).  There is no positive constant
\(c\), depending only on the weights, such that
\begin{equation}
 \|F_{h_0}\|^2
 \ge c\frac{\sum_{h\in\mathscr H}w_h\|F_h\|^2}
              {\sum_{h\in\mathscr H}w_h}
 \label{eq:tpc56-false-average-localization}
\end{equation}
for all vector families.  The same failure holds when the right-hand side
is represented by Parseval as the \(L^2\)-energy of
\begin{equation}
 \widehat F_w(\alpha)
 =\sum_{h\in\mathscr H}\sqrt{w_h}\,F_he(h\alpha).
 \label{eq:tpc56-frozen-fourier-family}
\end{equation}
\end{proposition}

\begin{proof}
Take \(F_{h_0}=0\), choose \(F_{h_1}\ne0\), and set every other member to
zero.  The right-hand side of
\eqref{eq:tpc56-false-average-localization} is positive and the left-hand
side is zero.  Parseval gives
\begin{equation}
 \int_{\T}\|\widehat F_w(\alpha)\|^2\,d\alpha
 =\sum_{h\in\mathscr H}w_h\|F_h\|^2,
 \label{eq:tpc56-parseval-shift-average}
\end{equation}
so the Fourier formulation has the same counterexample.
\end{proof}

Consequently, a completed-family theorem transfers to the physical member
only if it is already uniform pointwise in \(h\), or if one separately
proves a localization estimate such as
\begin{equation}
 \|F_{h_0}\|^2
 \ge X^{-\lambda_{\rm loc}+o(1)}
 \frac{\sum_hw_h\|F_h\|^2}{\sum_hw_h}.
 \label{eq:tpc56-required-shift-localization}
\end{equation}
TPC--48 proves that its frozen coefficient equals the active coefficient
at the one original intercept \(h_0\) \citep{WangTPC48}.  For
\(h\ne h_0\), the support and coefficients remain frozen from \(h_0\);
they are algebraic extensions, not newly reconstructed physical packets.
Thus an average over that family is useful only with its frozen-family
label until \eqref{eq:tpc56-required-shift-localization} is supplied.

\subsection{Layerwise lower squares do not survive signed reassembly}

The projective representation also contains a signed or complex
reassembly over auxiliary layers.  Upper estimates pass through this
operation by Minkowski; lower estimates do not.

\begin{proposition}[Lower-reassembly obstruction]
\label{prop:tpc56-lower-reassembly-obstruction}
Let \(\nu\) be a nonzero finite complex measure on \(\Omega\) such that
\(\dim L^2(|\nu|)\ge2\), and let \(Z_\omega\) range in a nonzero Hilbert
space.  There is no positive constant \(c\), depending only on \(|\nu|\),
such that
\begin{equation}
 \left\|\int_\Omega Z_\omega\,d\nu(\omega)\right\|^2
 \ge c\int_\Omega\|Z_\omega\|^2\,d|\nu|(\omega)
 \label{eq:tpc56-false-lower-reassembly}
\end{equation}
for all layer fields.
\end{proposition}

\begin{proof}
Let \(\rho=d\nu/d|\nu|\), so \(|\rho|=1\) almost everywhere.  Since
\(\dim L^2(|\nu|)\ge2\), choose a nonzero
\(f\in L^2(|\nu|)\) orthogonal to the constants, and choose a nonzero vector
\(v\).  Put
\(Z_\omega=\overline{\rho(\omega)}f(\omega)v\).  Then
\[
 \int_\Omega Z_\omega\,d\nu(\omega)
 =v\int_\Omega f\,d|\nu|=0,
 \qquad
 \int_\Omega\|Z_\omega\|^2\,d|\nu|(\omega)>0.
\]
\end{proof}

A favorable projective layer, or even a lower square in every layer, is
therefore not a lower square for any signed physical reassembly with
\(\dim L^2(|\nu|)\ge2\).  A valid
transfer would require a separately proved lower frame estimate of the
form
\begin{equation}
 \left\|\int Z_\omega\,d\nu(\omega)\right\|^2
 \ge X^{-\lambda_{\rm reas}+o(1)}
 \int\|Z_\omega\|^2\,d|\nu|(\omega)
 \label{eq:tpc56-required-lower-reassembly}
\end{equation}
on the distinguished coefficient field or on a rigorously specified
subspace.  Such an estimate is not a consequence of bounded total
variation.

\subsection{The five selected channels still do not lower-bound their sum}

The same warning applies internally to
\eqref{eq:tpc56-five-channel-reassembly}.  The sector theorem proves
positive energy before the five channels are reassembled.  It does not
control the signed cross terms between them.  For example, two nonzero
channels with values \(v\) and \(-v\) in the same output coordinate have
positive split energy and zero sum.  This is compatible with the local
literal saturation of \cref{prop:tpc56-literal-two-atom-saturation}.

There are three honest ways to use the present result downstream:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.8em]
 \item retain the adaptive pentant as an explicitly selected physical
       subpacket and prove that every later operation respects that
       selection;
 \item verify the fixed pre-terminal phase partition of
       \cref{thm:tpc56-preterminal-phase-realization}; or
 \item estimate the five-channel cross terms and prove a lower-reassembly
       inequality for the undeleted distinguished vector.
\end{enumerate}
An average over auxiliary phases can help with the third route only after
a pointwise localization estimate identifies the physical phase.

\subsection{Parity boundary}

No step above supplies a lower-bound sieve for simultaneous primes.  The
terminal support is taken exactly as inherited; the sector theorem starts
after the primality restriction and after the terminal diagonal is formed.
It proves that a constant part of an already activated complex vector can
be selected into an acute cone.  It does not prove that the vector is
activated often, that the undeleted phases align, or that a fixed even gap
occurs infinitely often.  In particular, the result is compatible with the
classical parity obstruction \citep{FriedlanderIwaniec2010} and is not
reported as a parity-sensitive advance.
