\section{The canonical pre-mask cell interface}
\label{sec:tpc50-canonical-interface}

The weighted-survival parameter of TPC--49 is attached to a weighted
two-row mask.  It is therefore essential to define it before the static
mask is expanded into signed rank-one layers.  This section fixes that
order of operations, records the nondegeneracy inherited from the
physical packet, and states the exact transfer theorem available for one
specified cell.  In particular, a terminal projective parameter
\(\omega\) from TPC--47/48 is not declared to be a physical cell.

\subsection{The physical coefficient before projective expansion}

Fix the physical shift \(h_0\ne0\) and one source-compatible dyadic
packet.  Write \(\mathcal A_1\) and \(\mathcal A_2\) for the two row
systems.  A row is
\begin{equation}
 \rho=(\ell_\rho,d_\rho),
 \qquad m_\rho=\ell_\rho d_\rho\asymp Q,
 \label{eq:tpc50-physical-row}
\end{equation}
where \(\ell_\rho\) is prime, \(d_\rho\) is squarefree, and the inherited
separation makes \(m_\rho\) determine \(\rho\).  The literal static mask
on \(\mathcal A_1\times\mathcal A_2\) is
\begin{equation}
 K_{\alpha\gamma}
 :=\mathfrak m_{\rm act}(\alpha,\gamma)
 =\mathbf 1_{\ell_\alpha\ne\ell_\gamma}
  \mathbf 1_{|m_\alpha-m_\gamma|>\Delta}
  \mathbf 1_{(d_\alpha,d_\gamma)\le G},
 \label{eq:tpc50-literal-static-mask}
\end{equation}
with \(\Delta=QX^{-\kappa_0}\) and \(G=X^{\kappa_0}\).  The joint
multiplier is
\begin{equation}
 \mathfrak A_{\alpha,\gamma}^{\rm act}(j)
 =K_{\alpha\gamma}\,
  \Xi_{\alpha,\gamma}(j)
  \mathcal W_{\alpha,\gamma}(j/J).
 \label{eq:tpc50-joint-multiplier}
\end{equation}
Here \(\Xi\) is fixed-period in the orbit variable and \(\mathcal W\)
contains the inherited smooth factors.  The physical source coefficient
on the left has the form
\begin{equation}
 \gamma_\alpha^{(1)}
 =\mu(d_\alpha)(\log\ell_\alpha)
  \omega_D^{(1)}(d_\alpha)
  \psi_L^{(1)}(\ell_\alpha/L)\zeta_\alpha^{(1)},
 \label{eq:tpc50-left-source-weight}
\end{equation}
and the right coefficient \(\gamma_\gamma^{(2)}\) has the symmetric
form.  The inherited estimates are upper bounds only:
\begin{equation}
 \sum_{\rho\in\mathcal A_s}|\gamma_\rho^{(s)}|
 \ll QX^{o(1)},
 \qquad
 \sum_{\rho\in\mathcal A_s}|\gamma_\rho^{(s)}|^2
 \ll QX^{o(1)},
 \qquad s=1,2.
 \label{eq:tpc50-inherited-row-upper-bounds}
\end{equation}
No lower row count, lower \(\ell^2\)-mass, or pointwise lower bound is
part of this interface \citep{WangTPC36,WangTPC45,WangTPC47,WangTPC48}.

After large-prime descent, the literal left residual vector at \(h_0\)
is
\begin{equation}
 \mathcal F_{h_0}^{\rm act,L}
 =\sum_{\substack{\gamma,j,m,p,r\\pr-mj=h_0}}
 \gamma_m^{(1)}\mathfrak A_{m,\gamma}^{\rm act}(j)
 \mu(r)\Lambda(pr)e_{\gamma,d(m)r}\otimes e_j.
 \label{eq:tpc50-physical-residual-vector}
\end{equation}
Thus the two axes relevant to static-mask survival are the source row
\(m\) and the opposite row \(\gamma\).  The terminal factor, the
M\"obius phase, and the residual basis label are downstream data; they
are not additional entries of the row mask.

\subsection{Provenance-canonical residue/Mellin cells}

We now fix one representation rather than taking an infimum over all
algebraically equivalent ones.  First split the physical orbit into the
actual residue classes \(a\pmod {H_0}\).  On each class, apply the
specific finite Fourier and Mellin inversions supplied by the inherited
provenance construction, with their original normalizations and
cutoffs.  No zero pair, algebraic refactorization, or static-mask
Fourier expansion is inserted at this stage.  We call the resulting
specified decomposition the \emph{provenance-canonical pre-mask
cellization} and denote it by \(\mathscr C\).

Concretely, \(\mathscr C\) is the exact identity
\begin{align}
 &\gamma_\alpha^{(1)}
  \Xi_{\alpha,\gamma}(j)
  \mathcal W_{\alpha,\gamma}(j/J)
 \notag\\
 &\quad={}
 \sum_{a\bmod H_0}
 \mathbf 1_{j\equiv a\!\!\pmod {H_0}}
 \int_{\Theta_a}
 u_{a,\tau}^{L}(\alpha)v_{a,\tau}(\gamma)
 \phi_{a,\tau}(j/J)\,d\lambda_a(\tau).
 \label{eq:tpc50-canonical-pre-mask-cellization}
\end{align}
The source coefficient in \eqref{eq:tpc50-left-source-weight} is
absorbed into \(u_{a,\tau}^{L}\).  Equivalently, one may first separate
\(\Xi\mathcal W\) and then put
\(u_{a,\tau}^{L}(\alpha)=
\gamma_\alpha^{(1)}u_{a,\tau}(\alpha)\).  The right-side cellization is
obtained by absorbing \(\gamma_\gamma^{(2)}\) into the summation-row
factor on the right.

There is one fixed compact set \(I_0\subset\mathbb R\), independent of
\(X,a,\tau\), such that
\begin{equation}
 \phi_{a,\tau}\in C_c^\infty(I_0).
 \label{eq:tpc50-common-profile-support}
\end{equation}
The common cutoff used to obtain this support equals one throughout the
physical normalized orbit range.  Hence it does not alter a physical
coefficient.  For every fixed integer \(B\ge0\),
\begin{equation}
 \sum_{a\bmod H_0}\int_{\Theta_a}
 \|u_{a,\tau}^{L}\|_\infty
 \|v_{a,\tau}\|_\infty
 \|\phi_{a,\tau}\|_{C^B}
 \,d|\lambda_a|(\tau)
 \ll_{B,h_0}X^{o(1)}.
 \label{eq:tpc50-canonical-seminorm-mass}
\end{equation}
This is an upper projective-seminorm estimate.  It contains no lower
bound for either unary factor.  Identity
\eqref{eq:tpc50-canonical-pre-mask-cellization} is precisely the point
at which ``cell'' is defined in this paper: a cell is
\(c=(a,\tau)\) before \(K\) is decomposed.

\begin{definition}[Literal pre-mask cell tensor]
\label{def:tpc50-literal-cell}
For \(c=(a,\tau)\), put
\begin{equation}
 T_c^L(\alpha,\gamma)
 :=u_c^L(\alpha)K_{\alpha\gamma}v_c(\gamma).
 \label{eq:tpc50-literal-cell-tensor}
\end{equation}
The cell is called active when \(T_c^L\ne0\).  Define its nonnegative
unary weights by
\begin{equation}
 a_c^L(\alpha):=|u_c^L(\alpha)|,
 \qquad b_c(\gamma):=|v_c(\gamma)|.
 \label{eq:tpc50-cell-unary-weights}
\end{equation}
The right tensor and weights are defined symmetrically.
\end{definition}

Unary complex phases are harmless: diagonal unitary multiplication
does not change Frobenius, nuclear, or projective-envelope norms.  A
genuine common nonzero scalar multiplies both numerator and denominator
below and therefore cancels.  A source-dependent terminal or Mellin
modulus is instead absorbed into the weight \(a_c^L\), while its unit
phase still leaves survival unchanged.

\subsection{The exact weighted-survival parameter}

\begin{definition}[Physical row-mask survival of a cell]
\label{def:tpc50-cell-survival}
For an active left cell define
\begin{equation}
 \boxed{
 \delta_c^L
 :=\frac{\displaystyle
  \sum_{\alpha\in\mathcal A_1}
  \sum_{\gamma\in\mathcal A_2}
  a_c^L(\alpha)^2K_{\alpha\gamma}b_c(\gamma)^2}
 {\displaystyle
  \left(\sum_{\alpha\in\mathcal A_1}a_c^L(\alpha)^2\right)
  \left(\sum_{\gamma\in\mathcal A_2}b_c(\gamma)^2\right)}.}
 \label{eq:tpc50-exact-cell-survival}
\end{equation}
Define \(\delta_c^R\) by exchanging the two row systems.
\end{definition}

Equivalently,
\begin{equation}
 \delta_c^L
 =\frac{\|T_c^L\|_{S_2}^2}
 {\|a_c^L\|_2^2\|b_c\|_2^2}.
 \label{eq:tpc50-cell-survival-Frobenius}
\end{equation}
Because \(K\) is a zero--one mask, an active cell satisfies only the
qualitative inherited nondegeneracy
\begin{equation}
 0<\delta_c^L\le1.
 \label{eq:tpc50-qualitative-cell-nondegeneracy}
\end{equation}
There is no inherited lower bound by a power of \(X\).  In particular,
neither \eqref{eq:tpc50-inherited-row-upper-bounds} nor
\eqref{eq:tpc50-canonical-seminorm-mass} implies
\(\delta_c^L\ge X^{-1/400+o(1)}\).

The failure is already visible on a complete finite mask.  If one row
has a forbidden neighbor \(\gamma_0\) and an admitted neighbor
\(\gamma_1\), take \(a=e_\alpha\) and
\begin{equation}
 b=(1-\eta)^{1/2}e_{\gamma_0}
   +\eta^{1/2}e_{\gamma_1},
 \qquad 0<\eta<1.
 \label{eq:tpc50-concentrated-weight-model}
\end{equation}
Then \(\delta_w(K;a,b)=\eta\).  This is not asserted to be a physical
TPC cell.  It proves that upper norms, mask support, and bounded
projective complexity alone logically imply no quantitative survival.

\subsection{Why a terminal \texorpdfstring{\(\omega\)}{omega}-layer has no physical
survival parameter}

The order in \eqref{eq:tpc50-canonical-pre-mask-cellization} is forced
by the meaning of \(\delta_c\).  After the pre-mask cell is fixed,
TPC--36 expands
\begin{equation}
 K_{\alpha\gamma}
 =\int_{\Omega_{36}}p_\eta(\alpha)q_\eta(\gamma)
 \,d\nu_{36}(\eta).
 \label{eq:tpc50-specified-mask-representation}
\end{equation}
The final parameter used in TPC--47/48 combines \(c\), \(\eta\), and
the terminal Mellin variables into one symbol \(\omega\).  An
individual such layer contains the rank-one factor
\begin{equation}
 u_c^L(\alpha)p_\eta(\alpha),
 v_c(\gamma)q_\eta(\gamma),
 \label{eq:tpc50-terminal-rank-one-layer}
\end{equation}
not the weighted masked tensor \(D_{a_c}KD_{b_c}\).  The literal mask is
recovered only after the complete signed \(\eta\)-integral is taken.

Consequently, assigning
\(\delta_w(K;|u_cp_\eta|,|v_cq_\eta|)\) to a final \(\omega\)-layer
would multiply by \(K\) a second time and measure a tensor different
from the layer being reassembled.  There are three further obstructions:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item the signed projective representation is not unique;
 \item a cancelling null pair may be appended without changing the
       physical coefficient while changing every layerwise statistic;
 \item the TPC--48 layer also contains a profile seminorm, a coherent
       prime sum, and a residual Hilbert vector, so it is not a
       canonical two-axis matrix of the form \(D_aKD_b\).
\end{enumerate}
Thus no representation-independent ``physical \(\delta_\omega\)'' is
defined.  The pointwise infimum in TPC--48 may remove inefficient
representations at the level of the full envelope, but it does not turn
their individual layers into physical atoms.  Every survival assertion
below is therefore made for the fixed pre-mask cellization
\(\mathscr C\) and the specified mask representation
\(\mathscr R_{36}\), never for all exact signed representations.

\subsection{Specified \texorpdfstring{\(\mathscr R_{36}\)}{R36} transfer}

Let \(\mathscr R_{36}\) be the explicit representation
\eqref{eq:tpc50-specified-mask-representation} furnished by
same-source orthogonality, signed Ferrers separation, and global gcd
compression.  Its declared bounded-projective cost is
\begin{equation}
 P_{36}(K)
 :=\int_{\Omega_{36}}
 \|p_\eta\|_\infty\|q_\eta\|_\infty
 \,d|\nu_{36}|(\eta)
 \ll \log(2Q)(3+2\sqrt2)^{\omega_*}
 =X^{o(1)}.
 \label{eq:tpc50-R36-cost}
\end{equation}
For an active left cell define
\begin{equation}
 \mathcal E_{36,c}^L
 :=\int_{\Omega_{36}}
 \|D_{a_c^L}p_\eta\|_2
 \|D_{b_c}\overline{q_\eta}\|_2
 \,d|\nu_{36}|(\eta).
 \label{eq:tpc50-R36-cell-envelope}
\end{equation}

\begin{theorem}[Canonical-cell projective-to-atomic transfer]
\label{thm:tpc50-canonical-cell-transfer}
Every active pre-mask cell satisfies
\begin{align}
 \|T_c^L\|_{S_1}
 &\le \mathcal E_{36,c}^L
 \le P_{36}(K)\|a_c^L\|_2\|b_c\|_2,
 \label{eq:tpc50-cell-nuclear-transfer}\\
 \boxed{
 \frac{(\mathcal E_{36,c}^L)^2}
      {\|T_c^L\|_{S_2}^2}
 \le\frac{P_{36}(K)^2}{\delta_c^L}.}
 \label{eq:tpc50-cell-energy-transfer}
\end{align}
The same formulas hold on the right.
\end{theorem}

\begin{proof}
Insert \eqref{eq:tpc50-specified-mask-representation} into
\eqref{eq:tpc50-literal-cell-tensor}.  After removing unary phases this
is an exact Hilbert rank-one representation of
\(D_{a_c^L}KD_{b_c}\).  The triangle inequality for the nuclear norm
gives the first inequality in
\eqref{eq:tpc50-cell-nuclear-transfer}, while
\begin{equation}
 \|D_{a_c^L}p_\eta\|_2
 \|D_{b_c}\overline{q_\eta}\|_2
 \le
 \|a_c^L\|_2\|b_c\|_2
 \|p_\eta\|_\infty\|q_\eta\|_\infty
 \label{eq:tpc50-layer-supremum-transfer}
\end{equation}
gives the second.  Divide its square by
\eqref{eq:tpc50-cell-survival-Frobenius}.
\end{proof}

In particular, if a new arithmetic theorem proves
\begin{equation}
 \delta_c^L\ge X^{-\theta+o(1)},
 \label{eq:tpc50-cell-survival-target}
\end{equation}
then the specified cell representation loses at most
\begin{equation}
 \frac{(\mathcal E_{36,c}^L)^2}
      {\|T_c^L\|_{S_2}^2}
 \le X^{\theta+o(1)}.
 \label{eq:tpc50-cell-distortion-consequence}
\end{equation}
If the entire isolated coefficient-face allowance is assigned here,
\(\theta\le1/400\) is sufficient.  This allocation is not a ledger for
the complete TPC argument.

For comparison, on the complete-universe extension with \(N\) rows,
TPC--49 proves minimum degree \((1-\epsilon_X)N\), where
\begin{equation}
 \epsilon_X\ll
 L^{-1+o(1)}+D^{-1+o(1)}+X^{-\kappa_0+o(1)}.
 \label{eq:tpc50-complete-mask-defect}
\end{equation}
Writing
\begin{equation}
 \operatorname{Flat}(b):=
 \frac{N\|b\|_\infty^2}{\|b\|_2^2},
 \label{eq:tpc50-opposite-flatness}
\end{equation}
one then has the conditional bound
\begin{equation}
 \delta_w(K;a,b)
 \ge1-\epsilon_X\operatorname{Flat}(b).
 \label{eq:tpc50-degree-flatness-bound}
\end{equation}
Hence \(\epsilon_X\operatorname{Flat}(b_c)=o(1)\) would imply
\(\delta_c=1-o(1)\).  The compressed TPC--45/48 upper-only interface
does not identify its active row support with that complete universe
and does not itself contain such a flatness estimate.  In
\cref{prop:tpc50-direct-provenance-identification}, we therefore return
to the uncompressed TPC--25/36 pre-terminal provenance and identify the
direct fixed-complexity opposite-row factors for which the flatness
condition is a theorem.  Any independent downstream pruning of that
opposite row must still be checked through the concentration criterion
of \cref{thm:tpc50-exact-concentration}.

\subsection{Boundary of the cell theorem}

Theorem \ref{thm:tpc50-canonical-cell-transfer} is exactly a separated
row-mask statement.  It does not make any of the following
identifications:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item It does not compare the full TPC--48 Banach profile envelope
       \(\mathfrak S_{\mathscr R}(\alpha)\) with the fixed-shift physical
       atomic diagonal \(\mathcal D_0\).  Signed
       \(L^1(d|\lambda|)\) reassembly still needs a frame or
       no-cancellation theorem.
 \item It does not estimate the coherent prime square inside a fixed
       residual coordinate.  The \(p\)-sum remains inside the norm.
 \item It does not control collisions or grouping under
       \(s=d(m)r\).  The mask face is formed before that map.
 \item It does not unfold sparse determinant aliases, localize the
       completed frozen family back to \(h_0\), or identify the residual
       Gram route with the native affine physical face.
\end{enumerate}
Accordingly, even a subpower lower bound for every identified direct
canonical cell would close only the corresponding active-cell survival
subgate.  It would not prove a
fixed-shift Chowla estimate, cross the parity barrier, or imply any
prime-pair or twin-prime conclusion.
