\section{Deterministic certificate and reproducibility boundary}
\label{sec:tpc50-certificate}

The repository contains the exact-arithmetic script
\begin{center}
\texttt{experiments/tpc50\_certificate.py}.
\end{center}
It produces \texttt{experiments/tpc50\_certificate.json}.  The script
uses integers and rational numbers only: there is no floating-point
arithmetic, pseudorandom input, numerical optimizer, or tolerance-based
comparison.

The certificate performs the following deterministic checks.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item It enumerates every binary mask of size at most
       \(3\times3\) in the declared suite and all nonzero integer row
       weights with entries in \(\{0,1,2\}\).  It verifies the exact
       convex-combination identity
       \begin{equation}
        \delta_w(M;a,b)
        =\sum_i\frac{|a_i|^2}{\|a\|_2^2}s_b(i),
        \label{eq:tpc50-certificate-convex-identity}
       \end{equation}
       and checks
       \(\inf_{a\ne0}\delta_w(M;a,b)=1-\eta_M(b)\).  A basis vector at
       a minimizing row attains the value in every one of the
       \(15{,}884\) mask--right-weight cases.
 \item It exhausts all triples of \(2\times2\) binary forbidden-channel
       matrices and verifies both the three-channel union bound for
       \(\eta_M\) and the resulting survival inequality for every
       enumerated left and right weight.
 \item It checks the degree--flatness inequality exactly and verifies
       the energetic-cell lower bound and the aggregate nonenergetic
       energy estimate for \(132{,}864\) finite selection cases at
       \(\tau\in\{1/4,1/2,3/4\}\).
 \item It verifies invariance under independent nonzero integer scaling
       and under row, column, and supported-kernel phases in the exact
       Gaussian unit group \(\{1,-1,i,-i\}\).
 \item It constructs one explicit finite row universe containing a
       same-source block, a near-product block, and a large-gcd block.
       Each block has zero survival.  Adding one admitted neighbor gives
       the exact positive value \(1/(|S|+1)=1/3\) in each channel.
 \item It checks the rational endpoint ledger, including
       \begin{equation}
        \frac{99979}{210000}+\frac{10049}{52500}
        =\frac{267}{400},
        \qquad
        \frac{267}{400}-\frac1{400}=\frac{133}{200},
        \label{eq:tpc50-certificate-endpoint-identities}
       \end{equation}
       the interior-cutoff margin
       \(23/120-10049/52500=9/35000\), the canonical degree-defect exponent when
       \(\kappa_0=1/400\), and the zero-cost isolated-face budget
       identity.
\end{enumerate}

The committed record contains \(1{,}469{,}068\) exact checks.  Its
release digests are
\begin{center}
\small
\begin{tabular}{@{}ll@{}}
semantic & \nolinkurl{b01a3c4ede8b20090e904d7f93cd29174f2d8bb46b294f9fc02d988e398786cf}\\
source & \nolinkurl{8ad51dbe7dd900c993a616968111077ef9d55485e2d457239d314d31ee908915}\\
JSON & \nolinkurl{f4f7cd5abb63a8919f7594ecee2c23d189ea07109906f069aab2112411d9393b}
\end{tabular}
\end{center}
The semantic digest is taken from the canonical JSON serialization of
the result payload before hash metadata are added.  The source digest
normalizes line endings and trailing whitespace.  The JSON digest is
the SHA--256 hash of the committed generated record.

This computation is a finite regression certificate, not an
asymptotic proof.  In particular, it does not prove the fixed-modulus
prime number theorem, the squarefree progression asymptotic, the
complete-universe degree estimate, or the physical provenance of a
residue/Mellin cell.  It does not identify the abstract obstruction
weights with literal TPC coefficients, estimate the coherent prime
square, or test any prime-pair or twin-prime assertion.  Those logical
boundaries are part of the theorem statements, not empirical caveats.
