\section{Endpoint ledger and the boundary of the result}
\label{sec:tpc50-endpoint-boundaries}

\subsection{The isolated active-cell exponent}

At the inherited endpoint, write
\begin{equation}
 Q=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)},
 \qquad QJ=X^{1+o(1)},
 \label{eq:tpc50-endpoint-QJ}
\end{equation}
and use the finer row factorization
\begin{equation}
 L=X^{99979/210000+o(1)},
 \qquad
 D=X^{10049/52500+o(1)}.
 \label{eq:tpc50-endpoint-LD}
\end{equation}
The opened-divisor cutoff is genuinely inactive here.  Indeed, the
high-\(\beta\) source packet of TPC--28 has \citep{WangTPC28}
\begin{equation}
 R_{\rm src}=X^{23/60+o(1)},
 \qquad
 V=R_{\rm src}^{1/2+o(1)}=X^{23/120+o(1)},
 \label{eq:tpc50-endpoint-RV}
\end{equation}
and
\begin{equation}
 \frac{23}{120}-\frac{10049}{52500}
 =\frac9{35000}>0.
 \label{eq:tpc50-endpoint-interior-margin}
\end{equation}
Consequently \(2D\leq V\) for all sufficiently large \(X\), with a
fixed power margin.  Thus the actual high-\(\beta\) packet contains the
nondegenerate interior dyadic row blocks required in
\cref{prop:tpc50-direct-provenance-identification}; this is not an empty
support hypothesis.
Thus \eqref{eq:tpc50-mask-degree-defect} becomes
\begin{equation}
 \epsilon_X
 =O\!\left(X^{-\eta+o(1)}\right),
 \qquad
 \eta:=\min\left\{\kappa_0,\frac{10049}{52500}\right\}>0.
 \label{eq:tpc50-endpoint-degree-defect}
\end{equation}
The \(D^{-1}\) term dominates the \(L^{-1}\) term unless the fixed
pruning exponent \(\kappa_0\) is smaller.  In particular,
\begin{equation}
 \delta_w(M_X;a,b)
 =1-O\!\left(X^{-\eta+o(1)}\right)
 \label{eq:tpc50-endpoint-survival}
\end{equation}
for every fixed identified nondegenerate direct opposite-row cell and
every arbitrary nonzero weight on the other side.  The implied constant
may depend on that fixed cell.

Recall the isolated-face budget notation
\begin{equation}
 P_{\mathscr R}=X^{\varpi+o(1)},
 \qquad
 \delta_w=X^{-\theta+o(1)}.
 \label{eq:tpc50-budget-parameters}
\end{equation}
The fixed-representation sufficient condition at this endpoint is
\begin{equation}
 2\varpi+\theta\leq\frac1{400}.
 \label{eq:tpc50-isolated-budget-condition}
\end{equation}

\begin{corollary}[Zero polynomial cost for the canonical static face]
\label{cor:tpc50-endpoint-zero-cost}
For the representation \(\mathscr R_{36}\) and every identified
nondegenerate direct opposite-row pre-mask cell,
\begin{equation}
 \varpi=0,
 \qquad
 \theta=0.
 \label{eq:tpc50-zero-loss-exponents}
\end{equation}
Consequently this isolated static-mask face consumes no positive
polynomial portion of the \(X^{1/400+o(1)}\) allowance.
\end{corollary}

\begin{proof}
Equation \eqref{eq:tpc50-R36-projective-mass} gives \(\varpi=0\), and
\eqref{eq:tpc50-endpoint-survival} gives \(\theta=0\).  Substitute in
\eqref{eq:tpc50-isolated-budget-condition}.
\end{proof}

The phrase \emph{consumes no polynomial allowance} concerns exactly
the Hilbertized static row-output face in
\eqref{eq:tpc50-canonical-cell-atomic-transfer}.  It is not a statement
that the remaining \(1/400\) allowance closes the full determinant
packet.  If all remaining operations have total loss exponent
\(\lambda_{\rm other}\), the full multiplicative ledger would still
require
\begin{equation}
 \lambda_{\rm other}\leq\frac1{400}.
 \label{eq:tpc50-remaining-budget}
\end{equation}
No estimate for \(\lambda_{\rm other}\) is inferred here.

\subsection{What has and has not been proved}

The positive theorem removes one precise obstruction.  Even when the
source side is arithmetically sparse, the complete static mask deletes
only \(o(1)\) of the product \(\ell^2\)-mass of every identified
fixed-complexity opposite-row residue/Mellin cell covered by
\cref{prop:tpc50-direct-provenance-identification}.  Therefore
active-row sparsity by itself does not create a polynomial
projective-to-atomic loss in this canonical order of decomposition.

The following interfaces remain open and are not consequences of
\cref{thm:tpc50-canonical-cell-survival,cor:tpc50-canonical-cell-transfer}.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.6em]
 \item \textbf{Continuous Mellin frame efficiency.}
 The real Mellin phases preserve row flatness, and Schwartz variation
 gives finite weighted \(L^1\) mass, but two distinct Mellin layers are
 not automatically orthogonal in the physical coefficient Hilbert
 space.  Minkowski reassembly supplies an upper envelope; it does not
 supply a lower frame bound comparing that envelope with the squared
 norm of the signed, reassembled physical coefficient.  Selecting one
 favorable Mellin parameter by pigeonhole is invalid.

 \item \textbf{The full TPC--48 Banach profile envelope.}
 The quantity controlled in
 \eqref{eq:tpc50-canonical-cell-atomic-transfer} is one genuinely
 Hilbertized row-output face.  The TPC--48 envelope also carries the
 large-sieve profile constant and an outer signed Bochner integral.
 This paper does not identify that Banach profile envelope with a
 nuclear norm or with the physical diagonal.

 \item \textbf{The coherent prime square.}
 At fixed source \(m\) and cofactor \(r\), the prime sum is formed before
 taking the norm.  The exact orthogonality between distinct residual
 labels separates \(r\), but it does not separate the primes inside
 \begin{equation}
  \sum_p A_\omega(p,r,m)\mathrm e(-pr\alpha)
       v_{\omega,p,r,m}.
  \label{eq:tpc50-open-coherent-prime-sum}
 \end{equation}
 No prime exponential-sum cancellation, dispersion estimate, or
 pointwise large-sieve replacement is proved here.

 \item \textbf{Residual grouping.}
 The residual lift distinguishes the labels \(s=d(m)r\).  Returning to
 the grouped physical output applies a map whose squared norm is the
 maximal residual-fiber multiplicity.  The present row-mask theorem
 neither bounds that multiplicity by \(X^{o(1)}\) nor finds cancellation
 between labels in one fiber.

 \item \textbf{Frozen completion versus the physical shift.}
 The frozen family extends the coefficient field constructed at
 \(h_0\) to determinant equations with arbitrary intercept \(h\).  Only
 \(h=h_0\) has physical provenance.  A square estimate for the completed
 family need not have the same normalization as the one-slice atomic
 diagonal.  No completed-to-\(h_0\) localization theorem is supplied.

 \item \textbf{Residual and native affine Gram faces.}
 The large-prime residual synthesis is obtained after low-sign
 averaging.  Its cross-inner-product structure is not automatically
 the native affine physical Gram structure whose atomic diagonal is
 \(\mathcal D_0\).  The static survival theorem does not identify those
 two faces.

 \item \textbf{Slope collision and the remaining endpoint ledger.}
 The common-profile large sieve may still incur determinant-slope
 collision, and none of that cost is cancelled by
 \eqref{eq:tpc50-endpoint-survival}.  Such losses belong to
 \(\lambda_{\rm other}\) in \eqref{eq:tpc50-remaining-budget}.
\end{enumerate}

\subsection{Exact scope of the canonical hypothesis}

The proof applies unconditionally to the canonical terms produced by
direct finite Fourier decomposition of the stated fixed residue masks
and by real-axis Mellin inversion of fixed smooth shapes.  It does not
cover any of the following broadenings without a new argument:
\begin{itemize}
 \item a residue modulus growing with \(X\);
 \item an \(X\)-dependent smooth family whose nonzero support degenerates
       to a vanishing fraction of a dyadic row cell;
 \item a hard-cutoff boundary block failing
       \eqref{eq:tpc50-interior-cutoff-condition}, unless it is
       recellized and its fixed-shape or aggregate energy hypotheses are
       verified separately;
 \item a Mellin contour shift that introduces non-unit power weights;
       or
 \item an arbitrary bounded row coefficient substituted for the fixed
       character/phase provenance.
\end{itemize}
These exclusions are quantitative, not cosmetic: the construction in
\cref{prop:tpc50-abstract-interface-counterexample} gives zero survival
under the last broadening.

Accordingly, the theorem neither breaches the parity barrier nor proves
any fixed-shift prime-pair or twin-prime assertion.  Its contribution is
the sharper localization of the remaining gap: after the actual
fixed-complexity provenance is unpacked before the static mask, the
identified direct active-cell weighted-survival subdoor is open, while
the Mellin-frame, coherent-prime, residual-grouping, and
physical-localization doors remain.
