\section{Exact forbidden-mass concentration}
\label{sec:tpc50-exact-concentration}

The weighted-density condition of TPC--49 has an exact one-sided
formulation.  This formulation is useful here because the determinant
and terminal restrictions may concentrate the source weight, whereas
the opposite-row cell is the object whose provenance can still be
tested directly.

Let \(I,J\) be finite nonempty sets.  For an arbitrary kernel
\(K:I\times J\to\mathbb C\) and nonzero weights
\(a\in\mathbb C^I\), \(b\in\mathbb C^J\), put
\begin{equation}
 \delta_w(K;a,b)
 :=
 \frac{\displaystyle
       \sum_{i\in I}\sum_{j\in J}
       |a_i|^2|K(i,j)|^2|b_j|^2}
      {\|a\|_2^2\|b\|_2^2}.
 \label{eq:tpc50-general-weighted-survival}
\end{equation}
For the exact concentration theorem below, specialize to a binary mask
\(M:I\times J\to\{0,1\}\).
We allow the numerator in \eqref{eq:tpc50-general-weighted-survival} to be
zero.  Thus \(\delta_w=0\) when the product weight is supported
entirely on forbidden entries.  This is the continuous extension of
the TPC--49 definition to a zero weighted matrix.

For a nonzero right weight \(b\), define its forbidden-row
concentration by
\begin{equation}
 \eta_M(b)
 :=
 \max_{i\in I}
 \frac{\displaystyle
       \sum_{j\in J:\,M(i,j)=0}|b_j|^2}
      {\|b\|_2^2}.
 \label{eq:tpc50-exact-forbidden-concentration}
\end{equation}

\begin{theorem}[Exact one-sided survival criterion]
\label{thm:tpc50-exact-concentration}
For every nonzero \(b\in\mathbb C^J\),
\begin{equation}
 \boxed{
 \inf_{a\in\mathbb C^I\setminus\{0\}}
 \delta_w(M;a,b)
 =1-\eta_M(b).}
 \label{eq:tpc50-exact-infimum}
\end{equation}
Consequently,
\begin{equation}
 \bigl[\delta_w(M;a,b)\ge\delta_0
       \text{ for every }a\ne0\bigr]
 \quad\Longleftrightarrow\quad
 \eta_M(b)\le1-\delta_0
 \label{eq:tpc50-exact-uniform-equivalence}
\end{equation}
for every \(0\le\delta_0\le1\).
\end{theorem}

\begin{proof}
For \(i\in I\), set
\begin{equation}
 s_b(i)
 :=
 \frac{\sum_{j\in J}M(i,j)|b_j|^2}{\|b\|_2^2}
 =1-
 \frac{\sum_{j:\,M(i,j)=0}|b_j|^2}{\|b\|_2^2}.
 \label{eq:tpc50-row-survival-profile}
\end{equation}
Then
\begin{equation}
 \delta_w(M;a,b)
 =\sum_{i\in I}\frac{|a_i|^2}{\|a\|_2^2}s_b(i).
 \label{eq:tpc50-survival-convex-combination}
\end{equation}
The right side is a convex combination of the finitely many values
\(s_b(i)\).  Its infimum is their minimum, attained by a point mass at
any minimizing row.  By \eqref{eq:tpc50-row-survival-profile}, that
minimum is \(1-\eta_M(b)\).  This proves both assertions.
\end{proof}

We now specialize the criterion to the three deletions in the TPC
static mask.  Let rows be \(\alpha=(\ell_\alpha,d_\alpha)\), put
\(m_\alpha=\ell_\alpha d_\alpha\), and define
\begin{equation}
 M_X(\alpha,\gamma)
 :=
 \one_{\ell_\alpha\ne\ell_\gamma}
 \one_{|m_\alpha-m_\gamma|>\Delta}
 \one_{(d_\alpha,d_\gamma)\le G}.
 \label{eq:tpc50-three-channel-mask}
\end{equation}
For a nonzero opposite-row weight \(b\), introduce
\begin{align}
 \eta_{\rm src}(b)
 &:={}
 \max_{\ell}
 \frac{\displaystyle
       \sum_{\gamma:\,\ell_\gamma=\ell}|b_\gamma|^2}
      {\|b\|_2^2},
 \label{eq:tpc50-source-concentration}\\
 \eta_{\rm near}(b)
 &:={}
 \sup_{x\in\mathbb R}
 \frac{\displaystyle
       \sum_{\gamma:\,|m_\gamma-x|\le\Delta}|b_\gamma|^2}
      {\|b\|_2^2},
 \label{eq:tpc50-near-concentration}\\
 \eta_{\rm gcd}(b)
 &:={}
 \max_{d}
 \frac{\displaystyle
       \sum_{\gamma:\,(d,d_\gamma)>G}|b_\gamma|^2}
      {\|b\|_2^2}.
 \label{eq:tpc50-gcd-concentration}
\end{align}
The maxima range only over source and divisor labels that occur on the
left row set.  Enlarging those ranges can make the numerical upper
bound larger, but it does not invalidate any displayed inequality.

\begin{proposition}[Three-channel anti-concentration]
\label{prop:tpc50-three-channel-concentration}
For the mask \eqref{eq:tpc50-three-channel-mask},
\begin{equation}
 \eta_{M_X}(b)
 \le
 \eta_{\rm src}(b)
 +\eta_{\rm near}(b)
 +\eta_{\rm gcd}(b).
 \label{eq:tpc50-channel-union-bound}
\end{equation}
Hence every nonzero source weight \(a\) satisfies
\begin{equation}
 \boxed{
 \delta_w(M_X;a,b)
 \ge
 1-\eta_{\rm src}(b)
   -\eta_{\rm near}(b)
   -\eta_{\rm gcd}(b).}
 \label{eq:tpc50-channel-survival-bound}
\end{equation}
In particular, the endpoint target
\(\delta_w\ge X^{-1/400+o(1)}\), uniformly in \(a\), follows from
\begin{equation}
 \eta_{\rm src}(b)+\eta_{\rm near}(b)+\eta_{\rm gcd}(b)
 \le1-X^{-1/400+o(1)}.
 \label{eq:tpc50-minimal-checkable-endpoint}
\end{equation}
If the sum of the three concentrations is \(o(1)\), then the stronger
conclusion \(\delta_w=1-o(1)\) holds uniformly in \(a\).
\end{proposition}

\begin{proof}
For a fixed left row \(\alpha\), the forbidden opposite rows lie in
the union
\begin{equation}
 \{\gamma:\ell_\gamma=\ell_\alpha\}
 \cup
 \{\gamma:|m_\gamma-m_\alpha|\le\Delta\}
 \cup
 \{\gamma:(d_\alpha,d_\gamma)>G\}.
 \label{eq:tpc50-forbidden-union}
\end{equation}
The \(b^2\)-mass of the three sets, divided by \(\|b\|_2^2\), is at
most the respective quantities in
\eqref{eq:tpc50-source-concentration}--
\eqref{eq:tpc50-gcd-concentration}.  Take the maximum over \(\alpha\)
and apply \cref{thm:tpc50-exact-concentration}.
\end{proof}

\begin{remark}[Minimal versus decomposable conditions]
\label{rem:tpc50-minimal-versus-channel}
The single quantity \(\eta_{M_X}(b)\) is necessary and sufficient for
uniform one-sided survival.  The three channel quantities give a
slightly stronger but geometrically interpretable sufficient
condition.  The examples in \cref{sec:tpc50-obstructions} show
that each channel condition is individually sharp: none can be
discarded under the inherited upper-only interface.
\end{remark}
