\section{Introduction}
\label{sec:tpc50-introduction}

TPC--48 reduces the completed actual-coefficient determinant family to
a signed projective row-square envelope, while TPC--49 identifies the
exact finite-dimensional distortion between a Hilbertized projective
envelope and its atomic energy \citep{WangTPC48,WangTPC49}.  For a
weighted mask matrix
\begin{equation}
 T=D_aKD_b,
 \qquad
 \delta_w(K;a,b)
 =\frac{\sum_{\alpha,\gamma}|a_\alpha|^2
       |K_{\alpha\gamma}|^2|b_\gamma|^2}
       {\|a\|_2^2\|b\|_2^2},
 \label{eq:tpc50-intro-survival}
\end{equation}
that comparison gives
\begin{equation}
 \frac{\cE_{\mathscr R}(T)^2}{\|T\|_{S_2}^2}
 \le \frac{P_{\mathscr R}(K)^2}
          {\delta_w(K;a,b)}.
 \label{eq:tpc50-intro-transfer}
\end{equation}
Here \(P_{\mathscr R}\) is the bounded-projective cost of one specified
mask representation.  TPC--36 supplies a representation
\(\mathscr R_{36}\) with \(P_{\mathscr R_{36}}=X^{o(1)}\)
\citep{WangTPC36}.  The unresolved quantity was therefore the weighted
survival of the actual active cells.

The phrase ``actual active cell'' hides an order-of-operations issue.
The final parameter \(\omega\) in the TPC--47/48 representation already
combines fixed-residue and Mellin separation with the
Fourier--Ferrers--gcd decomposition of the static mask
\citep{WangTPC47,WangTPC48}.  It is not a canonical physical cell.
Null pairs can be appended to an exact signed representation, so no
nontrivial lower-mass statement can hold uniformly for every final
projective layer.  The static mask must instead be left intact while
the fixed-period and smooth factors are separated.  This produces a
specified \emph{pre-mask cell}; only then is
\eqref{eq:tpc50-intro-survival} the right quantity.

\subsection{The exact concentration criterion}

For a binary mask \(M\), define the largest forbidden proportion of a
right weight \(b\ne0\) by
\begin{equation}
 \eta_M(b)
 :=\max_\alpha
 \frac{\sum_{\gamma:M(\alpha,\gamma)=0}|b_\gamma|^2}
      {\|b\|_2^2}.
 \label{eq:tpc50-intro-eta}
\end{equation}
Our first main theorem is the exact identity
\begin{equation}
 \boxed{
 \inf_{a\ne0}\delta_w(M;a,b)=1-\eta_M(b).}
 \label{eq:tpc50-intro-exact}
\end{equation}
Thus a uniform statement over arbitrary pruning of the left row is
equivalent to one-sided anti-concentration of the right weight.  For
the literal TPC static mask
\begin{equation}
 M_X(\alpha,\gamma)
 =\one_{\ell_\alpha\ne\ell_\gamma}
  \one_{|m_\alpha-m_\gamma|>QX^{-\kappa_0}}
  \one_{(d_\alpha,d_\gamma)\le X^{\kappa_0}},
 \label{eq:tpc50-intro-mask}
\end{equation}
the single quantity \(\eta_{M_X}\) is bounded by the sum of three
transparent concentration coefficients: same-source, near-product,
and large-gcd mass.  This both refines the degree--flatness criterion
of TPC--49 and identifies the minimal one-sided repair of the inherited
upper-only interface.

\subsection{Restoring fixed-complexity provenance}

The physical opened row before static-mask decomposition has the form
\begin{equation}
 \mu(d)(\log\ell)\omega_D(d)\psi_L(\ell/L)\zeta_{\ell,d},
 \label{eq:tpc50-intro-row}
\end{equation}
where the smooth shapes and residue periods are fixed
\citep{WangTPC18,WangTPC25}.  Finite residue Fourier characters and
real-axis Mellin row factors have modulus one.  The identified direct
opposite-row factor uses \(e=0\); the restricted source-factor variant
with its physical prime logarithm uses \(e=1\).  Weighted prime and
squarefree counts give, for either displayed weight class,
\begin{equation}
 \|b\|_2^2\asymp LD(\log L)^{2e-1},
 \qquad
 \|b\|_\infty^2\ll(\log L)^{2e},
 \qquad e\in\{0,1\}.
 \label{eq:tpc50-intro-row-energy}
\end{equation}
Since the complete row universe has
\(N\asymp LD/\log L\), this proves
\begin{equation}
 \operatorname{Flat}(b)
 :=\frac{N\|b\|_\infty^2}{\|b\|_2^2}=O(1)
 \label{eq:tpc50-intro-flatness}
\end{equation}
uniformly in every real Mellin parameter.  Combining
\eqref{eq:tpc50-intro-flatness} with the complete-row degree theorem
of TPC--49 proves
\begin{equation}
 \boxed{
 \delta_w(M_X;a,b)
 =1-O\!\left(L^{-1+o(1)}+D^{-1+o(1)}
                  +X^{-\kappa_0+o(1)}\right)}
 \label{eq:tpc50-intro-positive}
\end{equation}
for every \(a\ne0\).  In particular, arbitrary terminal sparsity on
one side is harmless when the opposite side retains a canonical
fixed-complexity cell.

At the inherited endpoint,
\begin{equation}
 L=X^{99979/210000+o(1)},
 \qquad
 D=X^{10049/52500+o(1)},
 \label{eq:tpc50-intro-endpoint-LD}
\end{equation}
so \eqref{eq:tpc50-intro-positive} is \(1-o(1)\).  In the isolated
Hilbertized row-output face, its density exponent is therefore zero,
rather than the maximal allowed value \(1/400\).  This closes the
static survival subgate for the identified provenance-restored cells;
it does not close the full TPC--48 envelope comparison.

\subsection{Sharpness of the provenance requirement}

The preceding conclusion cannot be recovered from row-count and norm
upper bounds alone.  The three deletion channels in
\eqref{eq:tpc50-intro-mask} support correspondingly large concentrated
packets with
\begin{equation}
 \delta_w=0.
 \label{eq:tpc50-intro-zero}
\end{equation}
A near-product block and a large-gcd block can have
\(X^{267/400-\kappa_0+o(1)}\) rows.  Adding one admitted neighbor makes
the masked matrix nonzero but leaves survival equal to the inverse of
the packet size.  At \(\kappa_0=1/400\), this may be
\(X^{-133/200+o(1)}\), far below the isolated-face target.

These are exact logical counterexamples to the upper-only interface,
not models of the literal coefficient.  A same-source selector tracks
one prime as \(X\) varies, a near-product selector shrinks at relative
scale \(X^{-\kappa_0}\), and a gcd selector uses a growing modulus.
None is produced by a fixed-period residue expansion or by a
unit-modulus real Mellin phase.  The positive and negative theorems
therefore meet at a clean boundary: fixed complexity gives survival,
while growing concentration complexity must be estimated explicitly.

\subsection{Scope and organization}

The result proved here concerns one separated row-mask face.  It does
not identify the final TPC--48 parameter \(\omega\) with a physical
cell, replace a signed Mellin integral by an orthogonal frame, control
the coherent prime sum at fixed residual coordinate, compare the full
projective profile envelope with the literal atomic diagonal, group
the map \(s=d(m)r\), or recover the physical shift from the frozen
family.  These boundaries are structural, not disclaimers that can be
removed by relabeling a layer.

\Cref{sec:tpc50-canonical-interface} fixes the canonical order of
separation.  \Cref{sec:tpc50-exact-concentration} proves the exact
minimax criterion.  \Cref{sec:tpc50-frame-selection} treats general
subpower cell families.  \Cref{sec:tpc50-physical-cell-survival} proves the
fixed-provenance theorem.  \Cref{sec:tpc50-obstructions} gives sharp
concentration packets.  \Cref{sec:tpc50-endpoint-boundaries} records
the endpoint ledger and remaining gates, and
\cref{sec:tpc50-certificate} states the exact finite certificate.
