\section{Identified fixed-complexity physical cells survive the static mask}
\label{sec:tpc50-physical-cell-survival}

This section works \emph{before} the projective decomposition of the
static mask.  This order is essential.  The fixed residue selectors and
the smooth row--orbit factors are first put into canonical cells, while
the complete static mask remains one kernel.  The factors occurring in
a particular projective representation of that kernel are not absorbed
into the row weights.

\subsection{Canonical pre-mask row cells}

Set \(H=\rad|h_0|\), and fix an integer \(q=O_{h_0}(1)\).  We take \(q\) to be a
common multiple of all fixed row and orbit residue moduli in the packet,
including the period \(H_0\) used in
\eqref{eq:tpc50-canonical-pre-mask-cellization}, and let
\begin{equation}
 \mathcal R_X
 :=\left\{(\ell,d):
 L<\ell\leq2L,\ \ell\ {\rm prime},\
 D<d\leq2D,\ \mu^2(d)=1,\ (d,H)=1
 \right\}.
 \label{eq:tpc50-complete-row-universe}
\end{equation}
We assume \(L>4D\), \(L,D\to\infty\), and \(L,D\leq X^C\) for one
fixed \(C\).  Put \(N_X=|\mathcal R_X|\).  Then
\begin{equation}
 N_X\asymp_H\frac{LD}{\log L}.
 \label{eq:tpc50-complete-row-count}
\end{equation}
This follows from the prime number theorem and the elementary
squarefree count with fixed coprimality conditions
\citep{IwaniecKowalski2004}.

Let \(\mathcal A\subset(\mathbb Z/q\mathbb Z)^2\) be a fixed row-residue
cell.  We call it \emph{admissible} when it contains a residue pair for
which the prime progression and the squarefree progression in
\eqref{eq:tpc50-complete-row-universe} both have positive local density.
This is a finite, explicitly checkable condition.  Let
\(\psi,\omega\in C^\infty([1,2])\) be fixed nonzero shapes with
positive squared integrals.  This includes the constant shape one;
compactly supported interior shapes are also allowed.  Assume that
\(\mathcal A\) contains at least one locally admissible residue pair on
which the two shapes contribute positive density.  For
\(e\in\{0,1\}\), real \(t_1,t_2\), a fixed unit-modulus
periodic phase \(\chi\), and a scalar \(c\neq0\), define
\begin{equation}
 b_{\ell,d}
 :=c(\log\ell)^e\psi(\ell/L)\omega(d/D)
 \mathbf 1_{(\ell,d)\bmod q\in\mathcal A}
 \chi(\ell,d)\ell^{it_1}d^{it_2}.
 \label{eq:tpc50-canonical-cell-weight}
\end{equation}
The case \(e=1\) includes a physical prime-source logarithm; the case
\(e=0\) includes an unweighted opposite-row cell.  Additional
real-axis Mellin phases or fixed Fourier characters may be included in
\(\chi(\ell,d)\ell^{it_1}d^{it_2}\).

In the inherited opened-row notation, let
\(V=R_{\rm src}^{1/2+o(1)}\) be the hard upper cutoff on \(d\)
\citep{WangTPC25}.  We call a pre-terminal dyadic block
\emph{nondegenerate interior} when, after one of finitely many fixed
subdivisions and a rescaling of \(L,D\), its full divisor interval obeys
\begin{equation}
 2D\leq V
 \label{eq:tpc50-interior-cutoff-condition}
\end{equation}
for all sufficiently large \(X\), and its fixed unary shapes and
admissible residue support have positive squared density as specified
above.  Thus the phrase is a quantitative support condition, not merely
a name for a nonzero summand.

\begin{proposition}[Identification of the direct opposite-row factors]
\label{prop:tpc50-direct-provenance-identification}
Let \(\mathscr C_{\rm prov}:=\mathscr C\) be the pre-mask cellization obtained by
applying exactly the fixed-period Fourier expansion and the real-axis
Mellin inversion in the TPC--25 provenance formula, before applying any
TPC--36 Fourier--Ferrers--gcd representation of the static mask.
Every nonzero coefficient-free opposite-row factor on a nondegenerate
interior pre-terminal block of TPC--25/36, extended by zero to
\(\mathcal R_X\), is of the form
\eqref{eq:tpc50-canonical-cell-weight} with \(e=0\), up to replacing
\(\mathcal A\) by a fixed finite union of admissible residue pairs and
making one of finitely many fixed dyadic subdivisions of the inherited
row interval.
If a source factor contains the physical logarithm and its remaining
fixed residue coefficient is split into nonzero fixed values on
admissible cells, the same statement holds with \(e=1\).  A general
bounded coefficient satisfying only \(|\zeta_{\ell,d}|\ll1\) is not
covered by the \(e=1\) assertion and is instead retained in the
arbitrary weight on the other side.
\end{proposition}

\begin{proof}
Before separation, the inherited unary row coefficient is a product of
\(\mu(d)\), one possible factor \(\log\ell\), fixed smooth dyadic
cutoffs in \(\ell/L\) and \(d/D\), and a fixed-period residue factor
\citep{WangTPC25,WangTPC36}.  In the direct-cell implementation, residue
splitting gives a fixed set \(\mathcal A\) and one may take \(\chi=1\).
Equivalently, in the finite Fourier implementation, each summand carries
one fixed character \(\chi\), whose modulus is one on its admissible
support.
For the smooth row--orbit factors, real-axis Mellin inversion replaces
each occurrence of \(W(\ell dj/X)\) by a scalar transform coefficient,
an orbit phase, and row powers
\[
 (\ell d)^{it}d^{is}
 =\ell^{it}d^{i(t+s)}.
\]
These row powers have modulus one.  Products of the finitely many fixed
smooth shapes remain fixed smooth shapes, and all transform
coefficients may be placed in the nonzero scalar \(c\).  This is exactly
\eqref{eq:tpc50-canonical-cell-weight}; the M\"obius sign is another
unit phase on the squarefree support.

On a nondegenerate interior block, the zero extension is
coefficient-preserving because \(\mathcal R_X\) is the complete
prime--squarefree dyadic row universe for this pre-terminal packet:
condition \eqref{eq:tpc50-interior-cutoff-condition} removes the
inherited hard cutoff \(d\leq V\), while the fixed subdivision and
rescaling align the two dyadic intervals.  The omitted rows are
therefore precisely zeros of its fixed unary supports.  No static-mask
representation factor
\(p_\eta\) or \(q_\eta\) has yet been introduced.  An independently
pruned row subset created downstream is not covered by this
identification.  Any block failing
\eqref{eq:tpc50-interior-cutoff-condition} is outside the proposition,
whether its truncated support has positive or vanishing relative
density.  Only after a separate recellization and verification of the
fixed-shape or aggregate lower-energy hypotheses may
\cref{thm:tpc50-energy-selection} select its energetic cells; that
theorem does not by itself control their signed Mellin reassembly.
\end{proof}

\begin{corollary}[Location of downstream pruning]
\label{cor:tpc50-downstream-factor-location}
In the left physical residual route, fix a direct pre-mask residue and
Mellin layer and fixed downstream data \((j,p,r)\).  The modulus of the
unary factor indexed by the opposite row \(\gamma\), namely
\(|v_{a,\tau}(\gamma)|\), is the \(e=0\) weight identified in
\cref{prop:tpc50-direct-provenance-identification}.  The target
squarefreeness, terminal weight, prime/cofactor restrictions, and
source coefficient depend on the summation row \(m\) and downstream
variables, and may therefore be absorbed into the arbitrary weight
\(a\).  The right route is symmetric.
\end{corollary}

\begin{proof}
Inspect \eqref{eq:tpc50-physical-residual-vector}: after the fixed
factorization of \(\Xi\mathcal W\), the terminal and target data multiply
the source integer \(m\), whereas \(\gamma\) remains the opposite output
coordinate and carries only its separated pre-mask unary factor.  This
is a per-layer statement; it does not identify the signed reassembled
Mellin envelope with the physical atomic diagonal, nor may the
absorption be moved through the coherent downstream prime sum without a
new argument.
\end{proof}

\begin{theorem}[Fixed-complexity row energy]
\label{thm:tpc50-fixed-cell-energy}
For every fixed admissible cell as above, there are constants
\(\mathfrak c_{\rm cell},F_{\rm cell}\in(0,\infty)\) such that
\begin{equation}
 \sum_{(\ell,d)\in\mathcal R_X}|b_{\ell,d}|^2
 =\bigl(\mathfrak c_{\rm cell}+o(1)\bigr)
 |c|^2LD(\log L)^{2e-1}.
 \label{eq:tpc50-fixed-cell-l2-asymptotic}
\end{equation}
Moreover,
\begin{equation}
 \|b\|_\infty^2\ll_{\rm cell}|c|^2(\log L)^{2e}.
 \label{eq:tpc50-fixed-cell-linfty}
\end{equation}
Both statements are uniform in all real Mellin parameters and all
unit-modulus phases in \eqref{eq:tpc50-canonical-cell-weight}.
Consequently
\begin{equation}
 \boxed{
 \operatorname{Flat}_{\mathcal R_X}(b)
 :=\frac{N_X\|b\|_\infty^2}{\|b\|_2^2}
 \leq F_{\rm cell}.}
 \label{eq:tpc50-fixed-cell-flatness}
\end{equation}
\end{theorem}

\begin{proof}
Split the fixed set \(\mathcal A\) into its finitely many residue pairs.
For every prime-admissible class, the fixed-modulus weighted prime
number theorem gives \citep{IwaniecKowalski2004}
\begin{equation}
 \sum_{\substack{L<\ell\leq2L\\
                  \ell\ {\rm prime}\\
                  \ell\equiv a\pmod q}}
 (\log\ell)^{2e}|\psi(\ell/L)|^2
 =\bigl(c_{a,\psi}+o(1)\bigr)
 L(\log L)^{2e-1},
 \label{eq:tpc50-weighted-prime-energy}
\end{equation}
where \(c_{a,\psi}\geq0\).  Likewise, M\"obius inversion followed by
counting in a fixed progression gives
\begin{equation}
 \sum_{\substack{D<d\leq2D\\
                  d\equiv b\pmod q\\
                  \mu^2(d)=1,\ (d,H)=1}}
 |\omega(d/D)|^2
 =\bigl(c_{b,\omega,H}+o(1)\bigr)D,
 \label{eq:tpc50-weighted-squarefree-energy}
\end{equation}
with a nonnegative, explicitly determined local-density constant.
Admissibility and nontriviality of the fixed shapes make the sum of the
products \(c_{a,\psi}c_{b,\omega,H}\) over
\((a,b)\in\mathcal A\) strictly positive.  This proves
\eqref{eq:tpc50-fixed-cell-l2-asymptotic}.  Boundedness of the fixed
shapes gives \eqref{eq:tpc50-fixed-cell-linfty}.  The Mellin and Fourier
factors have modulus one, so none of these estimates depends on their
real parameters.  Finally combine
\eqref{eq:tpc50-complete-row-count},
\eqref{eq:tpc50-fixed-cell-l2-asymptotic}, and
\eqref{eq:tpc50-fixed-cell-linfty}.
\end{proof}

The hypothesis is not an unproved distribution conjecture.  For every
named fixed smooth and residue cell it is decided by a finite local check,
and the two asymptotics in the proof are standard fixed-modulus
theorems.  A zero or locally forbidden Fourier term is simply omitted.

\subsection{Weighted survival with arbitrary pruning on the other side}

On \(\mathcal R_X\times\mathcal R_X\), put
\begin{align}
 M_X(\alpha,\gamma)
 &:=
 \mathbf 1_{\ell_\alpha\ne\ell_\gamma}
 \mathbf 1_{|m_\alpha-m_\gamma|>\Delta}
 \mathbf 1_{(d_\alpha,d_\gamma)\leq G},
 \label{eq:tpc50-static-mask}\\
 m_\alpha&:=\ell_\alpha d_\alpha,
 \qquad
 \Delta:=LDX^{-\kappa_0},
 \qquad
 G:=X^{\kappa_0},
 \label{eq:tpc50-static-mask-scales}
\end{align}
where \(\kappa_0>0\) is fixed.  The complete-universe degree theorem
of TPC--49 \citep{WangTPC49}
gives, uniformly in every row on either side,
\begin{equation}
 \#\{\gamma:M_X(\alpha,\gamma)=0\}
 \leq\epsilon_XN_X,
 \qquad
 \epsilon_X\ll_H
 L^{-1+o(1)}+D^{-1+o(1)}+X^{-\kappa_0+o(1)}.
 \label{eq:tpc50-mask-degree-defect}
\end{equation}

For nonnegative weights \(a,b\), with neither identically zero, define
\begin{equation}
 \delta_w(M_X;a,b)
 :=\frac{\sum_{\alpha,\gamma}
 a_\alpha^2M_X(\alpha,\gamma)b_\gamma^2}
 {\left(\sum_\alpha a_\alpha^2\right)
  \left(\sum_\gamma b_\gamma^2\right)}.
 \label{eq:tpc50-complete-cell-weighted-survival}
\end{equation}

\begin{theorem}[Canonical-cell survival]
\label{thm:tpc50-canonical-cell-survival}
Let \(b\) be the modulus of a nonzero direct provenance factor from
\cref{prop:tpc50-direct-provenance-identification}; or, more generally,
let it be the modulus of a canonical cell weight
\eqref{eq:tpc50-canonical-cell-weight}.
For every nonzero weight \(a\)
on the other row system, with completely arbitrary support and
concentration,
\begin{equation}
 \boxed{
 \delta_w(M_X;a,b)
 \geq1-F_{\rm cell}\epsilon_X
 =1-o(1).}
 \label{eq:tpc50-canonical-survival}
\end{equation}
The conclusion is uniform in the real Mellin parameters and fixed
unit-modulus residue phases.  It also holds after exchanging the two
row systems.
\end{theorem}

\begin{proof}
For every fixed \(\alpha\), \eqref{eq:tpc50-mask-degree-defect} and the
definition of the supremum norm give
\begin{align}
 \sum_\gamma M_X(\alpha,\gamma)b_\gamma^2
 &\geq\|b\|_2^2-\epsilon_XN_X\|b\|_\infty^2
 \notag\\
 &\geq
 \bigl(1-F_{\rm cell}\epsilon_X\bigr)\|b\|_2^2,
 \label{eq:tpc50-rowwise-weighted-survival}
\end{align}
where the second line is
\eqref{eq:tpc50-fixed-cell-flatness}.  Multiply by \(a_\alpha^2\), sum
over \(\alpha\), and divide by the denominator in
\eqref{eq:tpc50-complete-cell-weighted-survival}.  No lower-density
information about \(a\) is used.
\end{proof}

This asymmetric formulation is useful for the physical residual
packet.  The arbitrary side may carry the squarefree target selector,
large-prime/cofactor restrictions, terminal weights, or any other
coefficient-specific pruning.  Only the opposite row cell needs the
fixed-complexity flatness proved above.  If a later reduction also
independently prunes that opposite row, the theorem is not automatic:
one must recheck the concentration quantities in
\eqref{eq:tpc50-source-concentration}--\eqref{eq:tpc50-gcd-concentration}.

\subsection{Transfer through the specified TPC--36 representation}

Let \(\mathscr R_{36}\) be the specified representation obtained from
same-source Fourier orthogonality, signed Ferrers separation, and the
global gcd compression.  As proved in TPC--36 and transferred through
the weighted interface in TPC--49, its bounded-projective mass satisfies
\citep{WangTPC36,WangTPC49}
\begin{equation}
 P_{\mathscr R_{36}}(M_X)=X^{o(1)}.
 \label{eq:tpc50-R36-projective-mass}
\end{equation}
Write \(\mathcal E_{\mathscr R_{36}}(M_X;a,b)\) for its weighted Hilbert
envelope.  The fixed-representation weighted transfer inequality is
\begin{equation}
 \frac{\mathcal E_{\mathscr R_{36}}(M_X;a,b)^2}
 {\|D_aM_XD_b\|_{S_2}^2}
 \leq
 \frac{P_{\mathscr R_{36}}(M_X)^2}
 {\delta_w(M_X;a,b)}.
 \label{eq:tpc50-fixed-representation-transfer}
\end{equation}

\begin{corollary}[Subpower atomic cost on an identified canonical cell]
\label{cor:tpc50-canonical-cell-transfer}
Under the hypotheses of
\cref{thm:tpc50-canonical-cell-survival},
\begin{equation}
 \boxed{
 \mathcal E_{\mathscr R_{36}}(M_X;a,b)^2
 \leq X^{o(1)}\|D_aM_XD_b\|_{S_2}^2.}
 \label{eq:tpc50-canonical-cell-atomic-transfer}
\end{equation}
The estimate is uniform in the canonical real Mellin and fixed residue
parameters.
\end{corollary}

\begin{proof}
Insert \eqref{eq:tpc50-canonical-survival} and
\eqref{eq:tpc50-R36-projective-mass} into
\eqref{eq:tpc50-fixed-representation-transfer}.
\end{proof}

The disjoint orbit classes \(j\bmod H_0\) are orthogonal output
subspaces and therefore reassemble by an exact square sum.  Disjoint
source-row residue cells reassemble exactly only at the atomic
Frobenius-diagonal level; after source summation they may contribute
coherently to the same physical output coordinate.  A finite character
expansion has an \(O_H(1)\) upper triangle/Bessel cost; Parseval is exact
only if its auxiliary residue label is retained in an enlarged space.
Real Mellin phases preserve \eqref{eq:tpc50-fixed-cell-flatness}, and
every polynomially weighted variation of a fixed smooth Mellin
transform is finite.  These facts give a constant or \(X^{o(1)}\)
\emph{upper} reassembly cost.  They do not assert that distinct
continuous Mellin layers are mutually orthogonal or supply a lower
frame bound for the signed physical coefficient.

\begin{proposition}[Why the older upper-bound interface is insufficient]
\label{prop:tpc50-abstract-interface-counterexample}
If the periodic/phase provenance in
\eqref{eq:tpc50-canonical-cell-weight} is replaced only by an arbitrary
coefficient \(\zeta_{\ell,d}\) satisfying
\(|\zeta_{\ell,d}|\leq1\), then no positive uniform lower bound for
\(\delta_w\) follows from the inherited upper norm bounds alone.
\end{proposition}

\begin{proof}
Fix a row \(\alpha_0=(\ell_0,d_0)\), put \(a\) on that row alone, and
put \(b\) on any nonempty subset of the opposite rows with source prime
\(\ell_0\).  The same-source factor in \eqref{eq:tpc50-static-mask}
vanishes on every pair in the resulting rectangle, so
\(D_aM_XD_b=0\) and \(\delta_w=0\).  The weights remain bounded and obey
all purely upper \(\ell^1\), \(\ell^2\), and support estimates.  What
excludes this example in
\cref{thm:tpc50-fixed-cell-energy} is the unpacked fixed-complexity
smooth/residue provenance, not an upper norm bound.
\end{proof}
