\section{Sharp concentration obstructions}
\label{sec:tpc50-obstructions}

The exact criterion of \cref{thm:tpc50-exact-concentration} cannot be
deduced from row-count and coefficient upper bounds.  We give one
large zero-survival block for each deletion in the literal static
mask, and then remove the apparent degeneracy caused by a zero weighted
matrix.

Fix \(H\ge1\), let \(L,D\to\infty\), and assume \(L>4D\).  Work on
the complete dyadic row universe
\begin{equation}
 \mathcal R_X
 :=
 \left\{(\ell,d):
 L<\ell\le2L,\ \ell\in\mathbb P,
 \ D<d\le2D,\ \mu^2(d)=1,\ (d,H)=1
 \right\}.
 \label{eq:tpc50-obstruction-universe}
\end{equation}
Put
\begin{equation}
 N:=|\mathcal R_X|
 \asymp_H\frac{LD}{\log L},
 \qquad
 Q:=LD,
 \qquad
 \Delta:=QX^{-\kappa_0},
 \qquad
 G:=X^{\kappa_0},
 \label{eq:tpc50-obstruction-scales}
\end{equation}
where \(\kappa_0>0\) is fixed.  We assume \(\Delta\to\infty\) and,
only for the gcd construction, \(G=o(D)\).  Let \(M_X\) be the mask
in \eqref{eq:tpc50-three-channel-mask} on
\(\mathcal R_X\times\mathcal R_X\).

\subsection{One sharp block for each deleted channel}

\begin{proposition}[Same-source zero-survival block]
\label{prop:tpc50-same-source-block}
For all sufficiently large \(X\), there is a prime
\(\ell_0\in(L,2L]\) such that
\begin{equation}
 S_{\rm src}
 :=\{(\ell_0,d)\in\mathcal R_X\}
 \label{eq:tpc50-source-block}
\end{equation}
satisfies
\begin{equation}
 |S_{\rm src}|\asymp_H D,
 \qquad
 M_X(\alpha,\gamma)=0
 \quad(\alpha,\gamma\in S_{\rm src}).
 \label{eq:tpc50-source-block-data}
\end{equation}
Consequently
\begin{equation}
 \delta_w(M_X;\one_{S_{\rm src}},\one_{S_{\rm src}})=0.
 \label{eq:tpc50-source-zero-survival}
\end{equation}
At the inherited endpoint,
\begin{equation}
 |S_{\rm src}|
 =X^{10049/52500+o(1)}.
 \label{eq:tpc50-source-block-endpoint}
\end{equation}
\end{proposition}

\begin{proof}
The prime number theorem supplies \(\ell_0\), and the elementary
squarefree count with the fixed coprimality condition gives
\(|S_{\rm src}|\asymp_H D\).  Every pair in the block has equal source
prime, so the first factor in \eqref{eq:tpc50-three-channel-mask}
vanishes.  The endpoint size is the inherited value of \(D\).
\end{proof}

\begin{proposition}[Near-row zero-survival block]
\label{prop:tpc50-near-block}
There is a set \(S_{\rm near}\subset\mathcal R_X\) such that
\begin{equation}
 |S_{\rm near}|
 \gg N X^{-\kappa_0},
 \qquad
 |m_\alpha-m_\gamma|\le\Delta
 \quad(\alpha,\gamma\in S_{\rm near}).
 \label{eq:tpc50-near-block-data}
\end{equation}
Therefore
\begin{equation}
 \delta_w(M_X;\one_{S_{\rm near}},\one_{S_{\rm near}})=0.
 \label{eq:tpc50-near-zero-survival}
\end{equation}
At the inherited endpoint,
\begin{equation}
 |S_{\rm near}|
 \ge X^{267/400-\kappa_0+o(1)}.
 \label{eq:tpc50-near-block-endpoint}
\end{equation}
In particular, if \(\kappa_0=1/400\), this is
\(X^{133/200+o(1)}\).
\end{proposition}

\begin{proof}
Every row product lies in \((Q,4Q]\).  Partition that interval into
half-open intervals of length at most \(\Delta\).  The number of
intervals is
\begin{equation}
 \left\lceil\frac{3Q}{\Delta}\right\rceil
 \ll X^{\kappa_0}.
 \label{eq:tpc50-near-bin-count}
\end{equation}
By pigeonhole, one interval contains at least
\(\gg NX^{-\kappa_0}\) row products.  Take the corresponding rows for
\(S_{\rm near}\).  Two products in the same half-open interval differ
by less than \(\Delta\), so the middle factor in
\eqref{eq:tpc50-three-channel-mask} vanishes.  Finally
\(N=X^{267/400+o(1)}\) at the endpoint.
\end{proof}

\begin{proposition}[Large-gcd zero-survival block]
\label{prop:tpc50-gcd-block}
Assume \(G=o(D)\).  For all sufficiently large \(X\), there is a prime
\(g\) satisfying
\begin{equation}
 G<g\le2G,
 \qquad (g,H)=1,
 \label{eq:tpc50-gcd-prime}
\end{equation}
and a set
\begin{equation}
 S_{\rm gcd}
 :=\{(\ell,ge)\in\mathcal R_X:
 D/g<e\le2D/g,\ \mu^2(e)=1,\ (e,gH)=1\}
 \label{eq:tpc50-gcd-block}
\end{equation}
such that
\begin{equation}
 |S_{\rm gcd}|\asymp_H\frac Ng
 =NX^{-\kappa_0+o(1)},
 \qquad
 M_X(\alpha,\gamma)=0
 \quad(\alpha,\gamma\in S_{\rm gcd}).
 \label{eq:tpc50-gcd-block-data}
\end{equation}
Thus
\begin{equation}
 \delta_w(M_X;\one_{S_{\rm gcd}},\one_{S_{\rm gcd}})=0.
 \label{eq:tpc50-gcd-zero-survival}
\end{equation}
At the inherited endpoint the block has size
\begin{equation}
 |S_{\rm gcd}|
 =X^{267/400-\kappa_0+o(1)}.
 \label{eq:tpc50-gcd-block-endpoint}
\end{equation}
\end{proposition}

\begin{proof}
The prime number theorem in the interval \((G,2G]\), with the finitely
many prime divisors of \(H\) deleted, gives \(g\).  Since \(D/g\to
\infty\), the squarefree count with the fixed coprimality restrictions
gives \(\asymp_H D/g\) choices of \(e\).  Multiplication by the
\(\asymp L/\log L\) source primes proves the cardinality statement.
For any two rows in the block, both divisor coordinates are divisible
by \(g>G\).  The last factor in
\eqref{eq:tpc50-three-channel-mask} therefore vanishes.
\end{proof}

The three constructions saturate the degree--flatness mechanism
channel by channel.  The source block has relative size
\(D/N=L^{-1+o(1)}\), while the near and gcd blocks have relative size
at least \(X^{-\kappa_0+o(1)}\); they may be thinned to that order while
retaining zero survival.  Their full-universe flatness factors are the
reciprocals of exactly those quantities.

\subsection{Nonzero packets with polynomially small survival}

The preceding examples have zero weighted matrices.  The next lemma
shows that their obstruction is not confined to that endpoint.

\begin{lemma}[One admitted neighbor]
\label{lem:tpc50-admitted-neighbor}
Let \(S\subset\mathcal R_X\) be any of
\(S_{\rm src},S_{\rm near},S_{\rm gcd}\), and fix
\(\alpha_0\in S\).  For all sufficiently large \(X\), there exists
\(x\in\mathcal R_X\setminus S\) with
\begin{equation}
 M_X(\alpha_0,x)=1.
 \label{eq:tpc50-admitted-neighbor}
\end{equation}
For
\begin{equation}
 a=e_{\alpha_0},
 \qquad
 b=\one_S+e_x,
 \label{eq:tpc50-one-neighbor-weights}
\end{equation}
one has the exact value
\begin{equation}
 \boxed{
 \delta_w(M_X;a,b)=\frac1{|S|+1}.}
 \label{eq:tpc50-one-neighbor-survival}
\end{equation}
\end{lemma}

\begin{proof}
TPC--49 proves that every row of the complete static-mask graph has
degree \((1-o(1))N\) \citep{WangTPC49}.  Hence \(\alpha_0\) has an
admitted neighbor for sufficiently large \(X\).  Every pair in
\(\{\alpha_0\}\times S\) is forbidden by the defining property of the
chosen block, so such a neighbor necessarily lies outside \(S\).
For \eqref{eq:tpc50-one-neighbor-weights}, the numerator of
\eqref{eq:tpc50-general-weighted-survival} is exactly one, while
\(\|a\|_2^2=1\) and \(\|b\|_2^2=|S|+1\).
\end{proof}

\begin{corollary}[Endpoint separation from the required density]
\label{cor:tpc50-tiny-positive-survival}
The same-source construction gives a nonzero weighted matrix with
\begin{equation}
 \delta_w
 =X^{-10049/52500+o(1)}.
 \label{eq:tpc50-source-tiny-endpoint}
\end{equation}
The near and gcd constructions give nonzero weighted matrices with
\begin{equation}
 \delta_w
 \le X^{-(267/400-\kappa_0)+o(1)}.
 \label{eq:tpc50-near-gcd-tiny-endpoint}
\end{equation}
When \(\kappa_0=1/400\), the latter exponent is \(133/200\), and all of
these displayed survival parameters are polynomially smaller than the
isolated TPC target \(X^{-1/400+o(1)}\).
\end{corollary}

\subsection{Why fixed provenance excludes these selectors}

\begin{proposition}[Unit-phase immunity]
\label{prop:tpc50-unit-phase-immunity}
Let \(u:I\to\mathbb C\), \(v:J\to\mathbb C\) have unit modulus and
let \(U:I\times J\to\mathbb C\) have unit modulus on the support of
\(M\).  Then
\begin{equation}
 \delta_w(M\odot U;u\odot a,v\odot b)
 =\delta_w(M;a,b).
 \label{eq:tpc50-unit-phase-invariance}
\end{equation}
In particular, row and orbit Mellin phases, M\"obius signs, and fixed
residue characters cannot reduce weighted survival.  A scalar Mellin
coefficient cancels from the normalized ratio when it is nonzero; a
zero scalar cell may be deleted.
\end{proposition}

\begin{proof}
Every term in \eqref{eq:tpc50-general-weighted-survival} depends only on the
absolute values of the two unary weights and of the kernel entry.
\end{proof}

\begin{remark}[Upper-only compatibility and physical incompatibility]
\label{rem:tpc50-obstruction-provenance-boundary}
The weights in
\cref{prop:tpc50-same-source-block,prop:tpc50-near-block,prop:tpc50-gcd-block,lem:tpc50-admitted-neighbor}
are bounded by one, have support at most \(N\), and obey all row-count,
pointwise, and \(\ell^2\) upper bounds inherited by TPC--45/48.  They
are therefore genuine countermodels to any deduction based only on
that upper interface.  They are not asserted to be the literal
physical coefficient.

More precisely, the same-source block selects one prime that moves
with \(X\); the near block requires a normalized cutoff of width
\(X^{-\kappa_0}\); and the gcd block requires divisibility by a modulus
\(g\asymp X^{\kappa_0}\).  None is generated by a nonzero fixed smooth
dyadic family, a fixed-period residue cell, or a unit-modulus Mellin
phase.  A power-narrow smooth selector would also violate the inherited
uniform normalized \(C^B\)-bounds.  Thus the examples prove the need
for an explicit no-concentration or fixed-provenance theorem; they do
not disprove survival for the literal fixed-complexity cells.

Finally, cancellation between different signed residue/Mellin layers
does not alter this conclusion.  Such cancellation changes the
representation condition number and belongs to the frame-efficiency
gate, not to the nonnegative survival ratio
\eqref{eq:tpc50-general-weighted-survival}.
\end{remark}
