\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Exceptional-Set Transfer for Short-Shift Factor-Ray Energies: The Two-Fifteenths Window, Parity Conditioning, and Fixed-Ray Obstructions},
 pdfauthor={Liang Wang},
 pdfsubject={Short-shift asymptotics and rigorous fixed-shift boundaries for factor-ray energies},
 pdfkeywords={primes in short intervals, exceptional sets, factor rays, Mellin spectrum, Selberg sieve, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cE}{\mathcal E}
\newcommand{\cL}{\mathcal L}
\newcommand{\cM}{\mathcal M}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cB}{\mathcal B}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\arsinh}{\operatorname{arsinh}}

\title{\textbf{Exceptional-Set Transfer for Short-Shift Factor-Ray Energies:}\\
\textbf{The Two-Fifteenths Window, Parity Conditioning,}\\
\textbf{and Fixed-Ray Obstructions}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Put $u(n)=\Lambda(n)-1$ and let $W\in C_c^1((0,\infty);\R)$.
For a fixed integer shift $h$ consider
\[
 \cR_{h,D}(X;t)=
 \sum_{\substack{n>D\\m\geq1}}
 u(n)\bigl(\Lambda(mn+h)-1\bigr)
 W(mn/X)(n/m)^{it}.
\]
Writing $n=ak$, $m=bk$, $(a,b)=1$, compresses equal Mellin
frequencies into primitive factor rays and defines the ray energy
$\cE_{h,D}(X)$ as the sum of the squared compressed coefficients.
Earlier long-shift arguments evaluate this energy after averaging over
$h$ on a scale $H\geq X$.  We lower that scale unconditionally.

The new input is a weighted exceptional-set transfer.  Guth and Maynard
proved a prime number theorem in intervals of length
$H\geq X^{2/15+\eps}$ for all but a stretched-exponentially sparse set
of integer centers.  The diagonal factor-product center $r=mn$ carries
the weight
\[
 A_D(r)=|W(r/X)|^2
 \sum_{\substack{n\mid r\\n>D}}(\Lambda(n)-1)^2.
\]
We prove $\sum_{r\asymp X}A_D(r)^2\ll X(\log X)^4$; hence every such
exceptional set has $A_D$-mass smaller than $X(\log X)^{-A}$ for every
$A>0$.  This rules out concentration of the short-interval exceptions
on the factor products relevant to the ray energy.

 Let $G\in C_c^1((0,\infty))$ be nonnegative and nonzero.  Fix
 $0<\eps<13/15$ and $0<\eta<1$.  Uniformly for
\[
 X^{2/15+\eps}\leq H\leq X,
 \qquad 1\leq D\leq X^{1-\eta},
\]
we prove
\begin{align*}
 \sum_hG(h/H)\cE_{h,D}(X)
 ={}&\frac12HX I_0(G)I_2(W)\log X\\
 &\times\bigl((\log X)^2-(\log D)^2\bigr)\\
 &+O\!\left(HX(\log X)^2\log\log(3X)\right).
\end{align*}
The same formula holds for the raw target energy.  The diagonal target
square supplies $\log X$; all same-ray off-diagonals use only a
two-linear-forms Selberg upper sieve.  The first-moment model and the
hard- and Fej\'er-band consequences extend to the same shift range.  A
parity-conditioned even-shift ensemble has the corresponding coefficient
$1/4$ and still selects no prescribed even shift.

 We also prove exact fixed-shift boundaries.  For nonnegative, nonzero
 $W$, at $h=2$ an explicit family of primitive rays (for example, those
 with $24\mid a$, $ab=o(X)$, and the stated inactive cutoff) is sign
 coherent and has coefficient of natural radial
 size, so uniform individual-ray cancellation is false.  On the
locally admissible ray $(a,b,h)=(6,1,1)$, coefficient evaluation is
algebraically equivalent to a weighted prime number theorem for
$6k^2+1$.  Finally, an exact minimax formula shows that one Mellin
coordinate observes only the sum of the radial coefficients on a ray.
These results explain why the growing-window theorem cannot be
specialized to $H=O(1)$.  No fixed-shift prime-pair asymptotic,
twin-prime lower bound, quadratic-prime theorem, new distribution level,
or breach of the parity barrier is claimed.
\end{abstract}

\noindent\textbf{Keywords:} primes in almost all short intervals;
exceptional-set transfer; factor-ray energy; Mellin spectrum; Selberg
upper-bound sieve; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N05, 11N13, 11N36; Secondary
11M06, 42A05.

\input{sections/introduction-scope}
\input{sections/setup-ledgers}
\input{sections/exceptional-transfer}
\input{sections/short-shift-moments}
\input{sections/energy-band}
\input{sections/even-shifts}
\input{sections/fixed-shift-boundary}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
