\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs,enumitem,microtype}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[nameinlink,capitalise,noabbrev]{cleveref}
\usepackage[numbers,sort&compress]{natbib}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\Z}{\mathbb Z}
\newcommand{\F}{\mathbb F}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\ee}{\mathrm e}
\newcommand{\Lzero}{\mathrm{L0}}
\newcommand{\Lone}{\mathrm{L1}}
\newcommand{\Ltwo}{\mathrm{L2}}

\title{\textbf{From a Deleted Bin to a Zero Arc:}\\
Stable Padded Fourier Reassembly and the
Low-Frequency Fixed-Shift Gate}
\author{Liang Wang\\
School of Artificial Intelligence and Automation\\
Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}
\maketitle

\begin{abstract}
Let \(A:\Z/q\Z\to\C\) have support \(S\), let
\(D=\sum_n|A(n)|^2\), and let
\(Z=\widehat A(0)=\sum_nA(n)\).  When \(A(0)=0\), Fourier inversion
gives the exact identity
\[
 Z=-\sum_{r\ne0}\widehat A(r).
\]
Thus the distinguished zero mode can be recovered from the nonzero
frequencies, but only as a coherent signed reassembly.  We prove a
stronger support-aware theorem.  If \(K=(\Z/q\Z)\setminus S\), then
every weight \(w\) supported on \(K\) with \(\sum_Kw=1\) gives
\[
 Z=-\sum_{r\ne0}m_w(r)\widehat A(r),\qquad
 m_w(r)=\sum_{k\in K}w(k)\ee^{2\pi i rk/q}.
\]
The unique minimum-\(\ell^2\) kernel among zero-set averages is
obtained by taking \(w\) uniform on \(K\).  Its squared norm is
\[
 \sum_{r\ne0}|m_K(r)|^2=\frac{|S|}{q-|S|},
\]
and Parseval then recovers exactly the sharp physical inequality
\[
 |Z|^2\le |S|D.
\]
Positive-density overpadding gives more.  A fixed \(k\)-fold
interval filter supported in the zero arc has Wiener norm \(O_k(1)\)
and multiplier decay
\[
 |m_k(r)|\ll_k d_q(r,0)^{-k}.
\]
For the literal TPC-32 packet this yields, unconditionally,
\[
 |Z_X|\ll_k
 \max_{0<d_q(r,0)\le R}|\widehat A_X(r)|
 +
 X^{o(1)}N_{0,X}R^{1/2-k}.
\]
At the critical row, the triangular case \(k=2\) reduces the full
\(q_X=X^{267/400+o(1)}\) frequency problem to the low window
\(R=X^{133/600+\varepsilon}\) for sufficiently small fixed
\(\varepsilon>0\).  We also derive an exact
multiplier-weighted exceptional-frequency budget and prove that
mean-square dispersion alone cannot improve the sharp support bound.
Applied at one fixed nonzero shift, the result corrects an overly
strong ``nonzero frequencies cannot see the zero mode'' formulation:
coherent nonzero-frequency control can close the zero-mode gate, but
generic frequency estimates and unweighted exceptional-set counts by
themselves cannot.
The Fourier theorems are \(\Lzero\), and their literal attachment is
\(\Lone\).  No new \(\Ltwo\) M\"obius-correlation estimate is proved.
\end{abstract}

\noindent\textbf{Keywords:} distinguished zero mode; finite Fourier
transform; coherent reassembly; exceptional frequencies; actual
support; fixed shift; determinant coefficient.

\medskip
\noindent\textbf{Convention.}
Every arithmetic application uses one prescribed \(h_0\ne0\), the
literal high-\(\beta\) TPC-32 coefficient after complete determinant
aggregation, its actual nonzero support, and its original global
normalization.  No assertion is specialized to \(h_0=2\).

\input{sections/introduction}
\input{sections/fourier-reconstruction}
\input{sections/optimal-kernel}
\input{sections/zero-arc-filter}
\input{sections/exceptional-budget}
\input{sections/physical-interface}
\input{sections/claim-boundary}

\begingroup
\sloppy
\hbadness=10000
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup
\end{document}
