\section{Exact certificate and claim boundary}
\label{sec:tpc34-certificate-scope}

The accompanying standard-library certificate is
\begin{center}
 \texttt{experiments/tpc34\_certificate.py}.
\end{center}
It uses integers, \texttt{Fraction}, and a hand-written
Gaussian-rational arithmetic.  It contains no floating-point calculation,
random input, or Python \texttt{assert} statement.  Running
\begin{verbatim}
python experiments/tpc34_certificate.py
python -O experiments/tpc34_certificate.py
\end{verbatim}
performs the same checks and regenerates byte-identical JSON.

\subsection{Finite checks}

The archived run performs \(213{,}976\) exact checks.

\begin{table}[H]
\centering
\caption{Exact finite checks in the TPC-34 certificate.}
\label{tab:tpc34-certificate-counts}
\begin{tabular}{@{}lr@{}}
\toprule
Check family & Count \\
\midrule
Complex \(TT^*\), Gram split, and slice identities & \(106\) \\
Opened gcd-projector and lcm incidence & \(3{,}368\) \\
Weighted target-collision fibers & \(255\) \\
Shared-ultra congruence and occupancy & \(2{,}379\) \\
Two-time gcd, modular returns, and lag counts & \(172{,}434\) \\
Orbit-sliced Cauchy and sharpness & \(80\) \\
Coherent zero-pair-diagonal model & \(35{,}340\) \\
High-\(\beta\) rational ledger & \(14\) \\
\midrule
Total & \(213{,}976\) \\
\bottomrule
\end{tabular}
\end{table}

Gaussian-rational tests verify the standard Gram convention
\begin{equation}
 \cG(\xi_1,\xi_2)
 =\sum_\gamma
 \overline{\Phi_\gamma(\xi_1)}\Phi_\gamma(\xi_2),
 \qquad
 E=\sum_{\xi_1,\xi_2}
 \overline{z(\xi_1)}z(\xi_2)\cG(\xi_1,\xi_2).
 \label{eq:tpc34-certificate-Gram-convention}
\end{equation}
This detects a conjugate or transpose error that real-valued examples
would miss.  The opened-projector tests compare the direct masked column
with the \((u,v)\)-expanded column and then compare their energies.  Since
\(\log u\) is not rational, the test specializes the arbitrary real
ultra coefficient to
\[
 a_{\rm test}(u)=-\mu(u)(u+1).
\]
This certifies the finite linear identity for one nontrivial exact
coefficient system; the proof in the text establishes it for the actual
logarithmic coefficients.

The collision suite verifies
\[
 \#\{m_1j_1=m_2j_2\}=\sum_pr(p)^2,\qquad r(p)\le\tau(p),
\]
including the weighted Cauchy inequality used in
\cref{prop:tpc34-target-collision}.  The shared-ultra suite checks both
fixed-row and fixed-time residue occupancy.  The two-time suite verifies
\eqref{eq:tpc34-two-time-gcd}, the modular-return equivalence
\eqref{eq:tpc34-modular-return}, and an explicit harmonic upper bound for
the divisor overcount in \cref{prop:tpc34-large-lag-content}.  The
coherent model is checked entry by entry rather than only through its
closed formula.

\subsection{Reproducibility values}

The archived outputs have:
\begin{align}
 \text{normalized source SHA-256}\quad
 &\texttt{92db9e309593faa815b1806cc4a656bf}
 \notag\\[-0.2em]
 &\texttt{c02b4ffab5eb1eb4f61c7b973a24168f},
 \label{eq:tpc34-source-hash}\\
 \text{JSON SHA-256}\quad
 &\texttt{50e7d0aefc9dd74f549831c8f70072fb}
 \notag\\[-0.2em]
 &\texttt{34be4788ae9d193e7acfac79753d8c34},
 \label{eq:tpc34-json-hash}\\
 \text{certificate digest}\quad
 &\texttt{da2a05161550265582a881a0b7017a3b}
 \notag\\[-0.2em]
 &\texttt{0be540c62df3cab187c58dbeaab9d9be}.
 \label{eq:tpc34-certificate-digest}
\end{align}
Line endings are normalized before the source hash is taken.  The
certificate digest hashes the canonical JSON payload before its digest
field is appended.

\subsection{What is not certified}

Finite enumeration verifies algebra, exact finite incidence, and rational
bookkeeping.  It does not prove:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item the asymptotic divisor or prefix \(X^\eps\) envelopes;
 \item the growing-parameter shared-ultra estimate;
 \item the off-diagonal operator bound
 \eqref{eq:tpc34-orbit-operator-gate};
 \item the orbit-sliced energy gate
 \eqref{eq:tpc34-orbit-energy-gate};
 \item the inherited \(Q^3\) column-energy gate;
 \item cancellation in an affine M\"obius or Chowla family;
 \item the distinguished zero-frequency flatness inequality;
 \item closure of every earlier residual packet;
 \item positivity or a Hardy--Littlewood main term;
 \item infinitely many twin primes; or
 \item a breach of sieve parity.
\end{enumerate}

The unconditional analytic results of this paper are the exact physical
Gram expansion, the lcm kernel bound, Gram-copy diagonal closure, target
collision estimate, shared-ultra pruning, two-time target-content and lag
count, orbit-sliced transfer and diagonal estimate, and the precisely
scoped envelope-only obstruction.  The next unproved analytic input is
\eqref{eq:tpc34-orbit-energy-gate}, or one of its sufficient operator
forms.
