\section{The high-\texorpdfstring{\(\beta\)}{beta} ledger and the next gate}
\label{sec:tpc34-high-beta}

The preceding estimates have different meanings: some cross the \(Q^3\)
threshold, some merely save a full structural factor, and some are
conditional reductions.  We collect them with a common exponent
denominator before choosing the next route.

\subsection{Exact endpoint comparison}

At
\[
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
\]
the exponent ledger is as follows.

\begin{table}[H]
\centering
\caption{Physical energy and orbit-sliced scales at the endpoint.}
\label{tab:tpc34-high-beta-ledger}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.34\textwidth}
>{\raggedright\arraybackslash}p{0.25\textwidth}
>{\raggedleft\arraybackslash}p{0.23\textwidth}@{}}
\toprule
Object & Bound or target & \(X\)-exponent \\
\midrule
Required column energy & \(Q^3\) & \(4005/2000\) \\
Absolute two-time baseline & \(Q^3J^2\) & \(5335/2000\) \\
Gram-copy diagonal & \(Q^2J^2\) & \(4000/2000\) \\
Exact target collision & \(Q^2J\) & \(3335/2000\) \\
Shared ultra divisor & \(Q^3J^2/T\) & \(4563/2000\) \\
Absolute orbit-sliced baseline & \(Q^3J\) & \(4670/2000\) \\
Sufficient orbit-sliced gate & \(Q^3/J\) & \(3340/2000\) \\
Orbit-sliced diagonal & \(Q^2J\) & \(3335/2000\) \\
Diagonal-scale orbit target & \(Q^2J\) & \(3335/2000\) \\
\bottomrule
\end{tabular}
\end{table}

The table has four immediate consequences.
\begin{enumerate}[label=\textup{(\roman*)}]
 \item The Gram-copy diagonal closes with margin
 \(5/2000=1/400\).
 \item The exact target collision lies \(670/2000=134/400\) below the
 energy target.
 \item Shared-ultra incidence saves the entire factor \(T\) from the
 absolute baseline, but still misses the energy gate by
 \(558/2000=279/1000\), which is \(J^2/T\).
 \item The orbit-sliced diagonal lies only \(5/2000=1/400\) below the
 allowed orbit energy.  Thus the new interface is quantitatively tight:
 it asks for a near-diagonal-scale row theorem, not a generic
 square-root estimate on each original column.
\end{enumerate}

\subsection{The remaining coefficient-specific form}

Write
\begin{equation}
 V_L+V_R
 =
 V_{L,\Delta}+V_{R,\Delta}
 +V_{L,\ne}+V_{R,\ne}.
 \label{eq:tpc34-V-full-split}
\end{equation}
The first two terms are controlled by
\cref{prop:tpc34-V-diagonal}.  A direct coefficient-specific sufficient
condition is therefore
\begin{equation}
 |V_{L,\ne}|+|V_{R,\ne}|
 \ll X^\eps\frac{Q^3}{J}.
 \label{eq:tpc34-coefficient-off-V-gate}
\end{equation}
The off-diagonal quantities are real but may have either sign; replacing
them by their termwise absolute values would return to the failed
sign-blind scale.

The uniform operator gate
\eqref{eq:tpc34-orbit-operator-gate} is stronger than
\eqref{eq:tpc34-coefficient-off-V-gate}.  Two standard sufficient
interfaces for it are
\begin{align}
 \sum_{\alpha_1\ne\alpha_2}
 |O_L^{\rm orb}(\alpha_1,\alpha_2)|^2
 &\ll X^\eps\frac{Q^4}{J^2},
 \label{eq:tpc34-HS-next-gate}\\
 \max_{\alpha_1}
 \sum_{\alpha_2\ne\alpha_1}
 |O_L^{\rm orb}(\alpha_1,\alpha_2)|
 &\ll X^\eps\frac{Q^2}{J},
 \label{eq:tpc34-Schur-next-gate}
\end{align}
with the analogous right-hand estimates.  The first is a
Hilbert--Schmidt second moment and the second a Schur row-sum bound.
Neither is proved here, and neither should be confused with a consequence
of the diagonal estimate.

\subsection{A route menu}

The exact reductions leave several nonexclusive ways forward.
\begin{enumerate}[label=\textup{Route \Alph*:},leftmargin=5.8em]
 \item \emph{Same-time projective energy.}  Apply the finite
 fixed-determinant Plancherel geometry of TPC-33 after orbit slicing,
 using several moduli or an integer large sieve so that the physical
 slope set is averaged without the single-modulus no-wrap conflict.
 The target is \eqref{eq:tpc34-HS-next-gate}, not pointwise cancellation
 on every affine line.

 \item \emph{Terminal/proper dispersion.}  Use
 \eqref{eq:tpc34-terminal-split}.  The proper-divisor layers retain a
 nontrivial complementary factor and may admit bilinear dispersion.
 The terminal layer requires control of the fused-sign correlation
 \(\mu(d)\mu(\ell dj+h)\), cancellation between this layer and the
 proper layers, or stronger arithmetic incidence not captured by the
 estimates proved here.

 \item \emph{Lag-content plus zero-lag analysis.}  Combine
 \cref{prop:tpc34-large-lag-content} with a dyadic decomposition in the
 modular-return divisor.  Large lag content is sparse; the zero-lag and
 small-content pieces must then be treated by a signed row-operator
 estimate or by additional arithmetic incidence beyond the bounds
 proved here.

 \item \emph{Restricted averaged Chowla input.}  Prove only the
 physically weighted family average in
 \eqref{eq:tpc34-coefficient-off-V-gate}.  This is weaker than a uniform
 theorem for every growing affine direction, but stronger than the
 sign-blind incidence currently available.
\end{enumerate}

The first route is the most compatible with the average projective
identity already proved; the second exposes most clearly where
parity-sensitive signs enter the present interface.  A failed attempt
along either route remains informative if it
produces a sharp operator obstruction or a quantitative range in which
one of the proper-divisor layers closes.

\subsection{Relation to the preceding chain}

TPC-28 closes selected truncated base packets before the present
ultra-long shell \citep{WangTPC28}.  TPC-30 supplies the two-row,
one-time target-content geometry \citep{WangTPC30}.  TPC-31 develops
determinant cells and proposes a matched \(TT^*\) route
\citep{WangTPC31}; it does not perform the Gram-copy closure above.
TPC-32 supplies the matched polarization and the distinguished
zero-frequency gate \citep{WangTPC32}.  TPC-33 defines the physical
column energies and proves their scalar transfer
\citep{WangTPC33}.  The new step is the exact Gram expansion of those
energies, unconditional closure of its copy diagonal and target
collision, the transposed two-time content theorem, and the
orbit-sliced reduction.

Modulo a divisor \(c\), the map \(j\mapsto mj+h\) is an affine traversal
with invertible step.  A simultaneous hit of the zero class at two times
is precisely the return condition \(c\mid j'-j\).  This is deterministic
modular recurrence geometry.  It is not a claim of mixing, spectral
decay, a logistic-orbit correspondence, or M\"obius disjointness.

Even a future proof of \eqref{eq:tpc34-orbit-energy-gate} would close only
the inherited matched residual packet.  Later reconstruction, main-term,
and positivity stages would remain.  None of the results above implies a
Hardy--Littlewood asymptotic or infinitely many twin primes.
