\section{Exact certificate and claim boundary}
\label{sec:tpc36-certificate}

The accompanying standard-library certificate is
\begin{center}
\texttt{experiments/tpc36\_certificate.py}.
\end{center}
It uses integers, \texttt{Fraction}, and symbolic finite-group
orthogonality.  It contains no floating-point calculation, random input,
true division, or Python \texttt{assert} statement.  Running
\begin{verbatim}
python experiments/tpc36_certificate.py
python -O experiments/tpc36_certificate.py
\end{verbatim}
performs the same checks and regenerates byte-identical JSON.

\subsection{Finite exact checks}

The archived run performs \(137{,}083\) checks.

\begin{table}[H]
\centering
\caption{Exact check families in the TPC-36 certificate.}
\label{tab:tpc36-certificate-checks}
\begin{tabular}{@{}lr@{}}
\toprule
Check family & Count \\
\midrule
Gcd projector and orthogonal compression & 120,116 \\
Source equality and inequality compression & 970 \\
Ferrers Fourier reconstruction and far-row endpoints & 1,671 \\
Triangular Gram, inverse, and eigen-polynomial identities & 42 \\
Product-phase Gram \(qI-J\) & 3,350 \\
Multiplicative permutation-kernel reconstruction & 7,286 \\
Coherent \(s\)-trace and sharpness example & 3,644 \\
Source constraints & 4 \\
\midrule
Total & 137,083 \\
\bottomrule
\end{tabular}
\end{table}

For the gcd suite, the script enumerates squarefree packets and cutoff
values, verifies \eqref{eq:tpc36-gcd-projector}, and then verifies the
Walsh analogue of \eqref{eq:tpc36-global-gcd-factorization} coefficient
by coefficient.  The source suite checks the normalized orthogonality
identity and its complement.  The Ferrers suite represents roots of unity
symbolically, reconstructs every prefix entry, and checks
\eqref{eq:tpc36-near-row-prefix} at both exact endpoints
\(m_\gamma-\Delta\) and \(m_\gamma+\Delta\).

The triangular suite constructs \(T_nT_n^*\), verifies its exact
first-difference inverse, and compares the inverse characteristic
polynomial with its recurrence for \(n\le7\).  The
product-phase suite counts exponent residues to verify
\eqref{eq:tpc36-product-phase-Gram}; the multiplication suite uses discrete
logarithms to check \eqref{eq:tpc36-multiplicative-product-delta}.  The
last suite enumerates centered finite-field data for
\eqref{eq:tpc36-complete-s-trace} and checks the nonprincipal construction
\eqref{eq:tpc36-sharp-f}--\eqref{eq:tpc36-sharp-T}.

\subsection{Reproducibility values}

Line endings are normalized before the source digest is taken.  The
archived values are
\begin{align}
 \text{normalized source SHA-256}\quad
 &\texttt{ed669550fbf29aecdc31062f98fc64463}
 \notag\\[-0.3em]
 &\texttt{67871505f46d6a4bf0e20d7625a7151},
 \label{eq:tpc36-source-hash}\\
 \text{JSON SHA-256}\quad
 &\texttt{9fbbc133d77ca53ed978e75461900917b}
 \notag\\[-0.3em]
 &\texttt{188bfdb9abf3bd436c1df5e4cfd09b6},
 \label{eq:tpc36-json-hash}\\
 \text{certificate digest}\quad
 &\texttt{4718f7216d8e67a87e84e3ebf6c550af}
 \notag\\[-0.3em]
 &\texttt{ca725c27c7980070f11ca6025ce7ff85}.
 \label{eq:tpc36-certificate-digest}
\end{align}
The certificate digest hashes the canonical payload before its digest
field is appended.

\subsection{What is proved}

The unconditional new results of this paper are:
\begin{enumerate}[label=(\roman*)]
 \item the exact global orthogonal compression
 \eqref{eq:tpc36-global-gcd-factorization} and soft gcd projective bound;
 \item the global actual-mask theorem
 \eqref{eq:tpc36-global-static-mask-bound};
 \item the fixed-column source--divisor representation
 \eqref{eq:tpc36-exact-column-Fourier} with logarithmic signed mass;
 \item the exact Ferrers singular values, the optimal signed logarithmic
 cost, and the exact nonnegative cost \(n\);
 \item the product-phase Gram and exact projective norm
 \eqref{eq:tpc36-product-phase-exact-cost};
 \item the cost-one multiplication kernel and the sharp loss for its
 termwise additive-frequency reassembly;
 \item the weighted coherent spectrum
 \eqref{eq:tpc36-weighted-coherent-spectrum}; and
 \item the complete \(s\)-trace, its residue-zero energy formula, and the
 sharp centered nonprincipal Cauchy example.
\end{enumerate}
The physical product-ready column theorem also uses the fixed
residue-cell split and Mellin separation already proved in TPC-25.  Its
dependence on that prior result is explicit rather than re-proved here.

\subsection{What is not proved}

Finite enumeration certifies algebra on the tested families; it does not
prove asymptotic analytic estimates.  Neither the manuscript nor the
certificate proves:
\begin{enumerate}[label=(\roman*)]
 \item an operator or Hilbert--Schmidt bound for the actual orbit-Gram
 off-diagonal;
 \item the coefficient-specific physical gate
 \(V_L+V_R\ll X^{o(1)}Q^3/J\);
 \item a complete integer-to-modular reassembly at \(q\asymp J\);
 \item control of one-modulus or three-modulus alias fibers at diagonal
 scale;
 \item a bound for the actual weighted coherent functional
 \eqref{eq:tpc36-coherent-gate-functional};
 \item vanishing of the actual centered residue-zero boundary \(g(0)\);
 \item cancellation of the terminal/proper-divisor cross terms;
 \item an affine Chowla estimate or M\"obius disjointness theorem;
 \item a breach of sieve parity, positivity, or a Hardy--Littlewood
 prime-pair asymptotic; or
 \item infinitely many twin primes.
\end{enumerate}

The precise advance is narrower and reusable: static physical-mask
complexity is no longer an unresolved polynomial obstruction.  Signed
reassembly places the real next gate at weighted coherent spectral overlap
and joint alias control.  A positive or negative theorem about that new
functional would be the next logically meaningful layer.
