\section{Introduction}
\label{sec:tpc36-introduction}

The matched residual chain has reached a useful separation of tasks.
TPC-32 keeps the exact rank--two cutoff polarization but leaves the joint
row multiplier inside a bilinear form.  TPC-33 opens one ultra divisor and
obtains a fixed-determinant affine column after the opposite row is fixed.
TPC-34 converts the distinguished shell to orbit--sliced row energies, and
TPC-35 identifies the coefficient-specific multiplicative spectrum that
would be available after complete product--slope reassembly
\citep{WangTPC32,WangTPC33,WangTPC34,WangTPC35}.

The inherited sufficient gate is
\begin{equation}
 V_L+V_R\ll X^{o(1)}\frac{Q^3}{J},
 \label{eq:tpc36-inherited-gate-intro}
\end{equation}
whereas the proved Gram-copy diagonal is
\begin{equation}
 V_{L,\Delta}+V_{R,\Delta}
 \ll X^{o(1)}Q^2J.
 \label{eq:tpc36-inherited-diagonal-intro}
\end{equation}
At the endpoint
\begin{equation}
 Q=X^{267/400+o(1)},\qquad
 J=X^{133/400+o(1)},\qquad
 T=X^{193/500+o(1)},
 \label{eq:tpc36-endpoint-intro}
\end{equation}
the allowance between \eqref{eq:tpc36-inherited-gate-intro} and
\eqref{eq:tpc36-inherited-diagonal-intro} is only
\begin{equation}
 \frac{Q}{J^2}=X^{1/400+o(1)}.
 \label{eq:tpc36-margin-intro}
\end{equation}
One cannot afford a new fixed power of \(X\).

TPC-35 therefore left a precise preliminary question: does the actual
physical multiplier admit a signed separable representation of soft cost,
or is the multiplier itself another polynomial obstruction?  The answer
is positive.  The more delicate conclusion is that this does not close
\eqref{eq:tpc36-inherited-gate-intro}; it relocates the gap to completion,
aliases, and coherent complementary-factor spectra.

\subsection{The static multiplier is softly projective}

For a kernel \(K\) on two finite sets, write \(\pinf(K)\) for its bounded
projective norm; see \cref{sec:tpc36-projective-toolkit}.  The physical
static mask has three factors:
\begin{equation}
 \mathfrak m_{\rm act}(\alpha,\gamma)
 =\one_{\ell_\alpha\ne\ell_\gamma}
  \one_{|m_\alpha-m_\gamma|>\Delta}
  \one_{(d_\alpha,d_\gamma)\le G},
 \qquad
 \Delta=QX^{-\kappa_0},\quad G=X^{\kappa_0}.
 \label{eq:tpc36-static-mask-intro}
\end{equation}
The same-source factor is compressed by source orthogonality.  The
near-row factor is a one-dimensional interval kernel.  The new step is a
global orthogonal compression of the row-gcd projector.  If
\(\omega_*=\max_\alpha\omega(d_\alpha)\), then
\begin{equation}
 \boxed{
 \pinf(\mathfrak m_{\rm act})
 \ll\log(2Q)(3+2\sqrt2)^{\omega_*}=X^{o(1)}.}
 \label{eq:tpc36-global-mask-intro}
\end{equation}
The equality \(X^{o(1)}\) uses only the standard fixed-base divisor
estimate \(C^{\omega(n)}\ll_{C,\eps}n^\eps\).  It is uniform in the
pruning threshold \(G\).

The distinction between layer count and projective mass is essential.
The exact finite representation may contain polynomially many layers, but
their normalized total variation is soft.  Every estimate uniform in the
bounded factors may therefore be integrated without paying for the raw
number of layers.

\subsection{Columnwise separation and its optimal cost}

The orbit energy first fixes the opposite row.  For
\(\gamma=(\ell_\gamma,e)\), the gcd cutoff in
\eqref{eq:tpc36-static-mask-intro} is then a unary \(d\)-weight.  Ordering
the physical \(d\)-values turns the near-row condition into the difference
of two prefix, or Ferrers, kernels.  After splitting the fixed
\(O_h(1)\) orbit residue cells, finite Fourier inversion gives the exact
representation
\begin{equation}
 \gamma_{(\ell,d)}^{(1)}
 \mathfrak A^{\rm act}_{(\ell,d),\gamma}(j)
 =\sum_{r\bmod H_0}\one_{j\equiv r\!\!\!\pmod{H_0}}
 \int\sum_\rho
 c_{\rho,\omega,\gamma,r}
 b_{\rho,\omega,\gamma,r}(\ell)
 f_{\rho,\omega,\gamma,r}(d)
 \eta_{\rho,\omega,\gamma,r}(j/J)\,d\nu_r(\omega),
 \label{eq:tpc36-product-ready-intro}
\end{equation}
with \(O(D)\) discrete layers and \(X^{o(1)}\) total signed
orbit-seminorm cost.  In particular \(b(\ell)\) is independent of \(j\)
and of the reflected complementary factor \(s\).  This proves the static
product-ready shape asked for in TPC-35.

The logarithm is not an artifact.  For the triangular Ferrers matrix
\begin{equation}
 T_n=(\one_{k\le r})_{1\le r,k\le n},
 \label{eq:tpc36-triangular-intro}
\end{equation}
we prove
\begin{equation}
 \pinf(T_n)\asymp\log(2n).
 \label{eq:tpc36-ferrers-optimal-intro}
\end{equation}
If every rank-one layer is required to be nonnegative, its exact cost is
instead \(n\).  Thus requiring every rectangle layer to be entrywise
nonnegative destroys the gain that signed Fourier orthogonality supplies.

\subsection{The cost of absolute additive-frequency separation}

The product slope is not another harmless smooth factor.  For prime \(q\)
and \(r\ne0\), put
\begin{equation}
 A_r(x,y)=e_q(rxy),\qquad x,y\in\F_q^\times.
 \label{eq:tpc36-product-phase-intro}
\end{equation}
Multiplicative characters give a flat singular-vector basis and the exact
projective norm
\begin{equation}
 \boxed{
 \pinf(A_r)=\frac{(q-2)\sqrt q+1}{q-1}.}
 \label{eq:tpc36-product-phase-cost-intro}
\end{equation}
On the other hand, \(K_a(x,y)=\one_{xy=a}\) is a permutation kernel and
\(\pinf(K_a)=1\).  The additive delta expansion of \(K_a\), followed by
termwise absolute reassembly of its nonzero frequencies, costs
\(\asymp\sqrt q\).  At \(q\asymp J\), this is exactly a factor \(J\) after
squaring.  Thus the additive-frequency expansion cannot be estimated at
the critical scale by summing its frequency costs separately.  The
multiplicative-character reconstruction keeps projective cost one.

\subsection{The coherent complementary-factor spectrum}

TPC-35 diagonalizes the complete square energy
\(\sum_{j,s}|(Tb)(j,s)|^2\).  The physical column first sums over the
complementary factor \(s\) and then squares.  We prove the corresponding
weighted identity.  For \(G_q=\F_q^\times\), any \(w:G_q\to\C\), and
\begin{equation}
 S_w(j)=\sum_{s\in G_q}w(s)(Tb)(j,s),
 \label{eq:tpc36-weighted-trace-intro}
\end{equation}
one has
\begin{equation}
 \boxed{
 \sum_j|S_w(j)|^2
 =\frac1{q-1}\sum_\chi
 |\widehat b(\bar\chi)|^2
 \left|\sum_sw(s)\widehat R_s(\chi)\right|^2.}
 \label{eq:tpc36-weighted-spectrum-intro}
\end{equation}
For the complete weight \(w=1\), additive centering gives the exact trace
\begin{equation}
 \sum_{s\in G_q}R_s(a)=qg(0)f(-h/a).
 \label{eq:tpc36-complete-trace-intro}
\end{equation}
Thus full \(s\)-coherence collapses to a residue-zero boundary term.  Yet
there are centered nonprincipal data for which \((Tb)(j,s)\) is independent
of \(s\), so the factor \(q-1\) from Cauchy in \(s\) is sharp.  A physical
gain must use the actual M\"obius-derived \(g\), the actual incomplete
weight \(w\), or joint alias cancellation.

\subsection{Claim boundary and organization}

The paper resolves a missing interface, not the twin-prime problem.  It
proves soft projective complexity of the actual static mask, an exact
columnwise product-ready decomposition, two sharp order-of-operations
obstructions, and coherent finite-field spectra.  It does not prove a
small physical Gram norm, the coefficient gate
\eqref{eq:tpc36-inherited-gate-intro}, a three-modulus alias theorem, an
affine Chowla estimate, positivity, or a Hardy--Littlewood asymptotic.

\Cref{sec:tpc36-physical-interface} fixes the inherited object.
\Cref{sec:tpc36-projective-toolkit} develops the projective tools.
\Cref{sec:tpc36-global-mask} proves \eqref{eq:tpc36-global-mask-intro}.
\Cref{sec:tpc36-fixed-column} proves the product-ready column theorem.
\Cref{sec:tpc36-optimality} gives the sharp Ferrers and product-phase
boundaries.  \Cref{sec:tpc36-coherent-spectrum} proves
\eqref{eq:tpc36-weighted-spectrum-intro}--
\eqref{eq:tpc36-complete-trace-intro}.  The last two sections record the
endpoint ledger, next gate, exact certificate, and formal claim boundary.
