\section{Endpoint ledger and the relocated coefficient gate}
\label{sec:tpc36-next-gate}

The static multiplier question is now resolved, but the physical energy
still requires integer-to-finite-field completion in the correct coherent
topology.  This section records exactly what the new theorems save and
what they do not.

\subsection{Complementary dyadic localization and a large-modulus realization}

By \eqref{eq:tpc36-target}, there are fixed constants
\(0<c_{\mathscr D}<C_{\mathscr D}\) such that
\begin{equation}
 c_{\mathscr D}X
 \le N_{\ell d}(j):=\ell dj+h
 \le C_{\mathscr D}X
 \label{eq:tpc36-target-support-constants}
\end{equation}
throughout the packet.  Partition \(T<u\le U_0\) into disjoint half-open
dyadic blocks
\begin{equation}
 \mathscr U:=\{2^kT:k\ge0,\ 2^kT<U_0\},
 \qquad
 \cU_U:=(U,2U]\cap(T,U_0],
 \qquad |\mathscr U|=O(\log X),
 \label{eq:tpc36-u-dyadic-blocks}
\end{equation}
and attach to each block the complementary interval
\begin{equation}
 \cS_U:=
 \left\{s\in\N:
 \frac{c_{\mathscr D}X}{2U}\le s
 \le\frac{C_{\mathscr D}X}{U}\right\}.
 \label{eq:tpc36-s-complementary-block}
\end{equation}
On an equality solution \(su=N_{\ell d}(j)\) with \(u\in\cU_U\), the
indicator of \(\cS_U\) is identically one.  Hence the exact kernel identity
\begin{equation}
 \one_{T<u\le U_0}\one_{su=N_{\ell d}(j)}
 =
 \sum_{U\in\mathscr U}
 \one_{u\in\cU_U}\one_{s\in\cS_U}
 \one_{su=N_{\ell d}(j)}
 \label{eq:tpc36-reciprocal-dyadic-identity}
\end{equation}
holds pointwise.  The new cutoffs are unary in \(u\) and \(s\), and
summing the \(O(\log X)\) blocks costs only \(X^{o(1)}\).

Now fix one such block and put
\begin{equation}
 F=s u-N_{\ell d}(j)=s u-\ell jd-h.
 \label{eq:tpc36-affine-determinant}
\end{equation}
On the full Cartesian support
\(u\in\cU_U\), \(s\in\cS_U\), one has
\begin{equation}
 su\le2C_{\mathscr D}X,
 \qquad
 |F|\le3C_{\mathscr D}X.
 \label{eq:tpc36-block-determinant-bound}
\end{equation}
Enlarge a fixed constant \(C_0\) so that
\(C_0\ge3C_{\mathscr D}\) and every individual physical variable is
smaller than \(C_0X\).  By Bertrand's postulate, for large \(X\) one may
choose a prime
\begin{equation}
 2C_0X<q<4C_0X,
 \label{eq:tpc36-large-modulus}
\end{equation}
and then
\begin{equation}
 F\equiv0\pmod q\quad\Longleftrightarrow\quad F=0.
 \label{eq:tpc36-large-modulus-no-alias}
\end{equation}
Thus, block by block, the modular product-slope layer is pointwise
identical to the integer layer after the physical variables are
zero-extended to \(\F_q\).  Summing the dyadic blocks preserves this exact
identity at soft cost.

This is an unconditional algebraic realization, not an efficient analytic
one.  In the standard completion route, the \(J\)-long orbit occupies only
a proportion
\begin{equation}
 \frac Jq\asymp\frac JX\asymp\frac1Q
 \label{eq:tpc36-large-modulus-coverage}
\end{equation}
of the large modulus.  Any argument that forgets this localization before
using a complete normalized estimate may pay the coverage scale \(Q\).
This is method-specific bookkeeping, not a universal lower bound for every
large-modulus method.

\subsection{Orbit-scale moduli and aliases}

On each reciprocal dyadic block, at the useful scale \(q\asymp J\), the
congruence \(F\equiv0\pmod q\) admits
\begin{equation}
 O(1+X/q)=O(Q)
 \label{eq:tpc36-one-modulus-aliases}
\end{equation}
integer aliases.  The \(O(\log X)\) blocks are absorbed into \(X^{o(1)}\).
TPC-35 proves the exact joint ladder: for pairwise
coprime \(q_i\asymp J\), \(1\le i\le r\), the alias count is
\begin{equation}
 O\!\left(1+\frac X{J^r}\right).
 \label{eq:tpc36-CRT-alias-ladder}
\end{equation}
In particular,
\begin{equation}
 \frac X{J^3}=\frac Q{J^2}=X^{1/400+o(1)},
 \label{eq:tpc36-three-modulus-margin}
\end{equation}
while four moduli give strict no-wrap.  Equality
\eqref{eq:tpc36-three-modulus-margin} is only an exponent-compatible
ledger.  Reassembling every three-modulus alias at the diagonal scale and
controlling all proper-coordinate character faces remain unproved.

On every block, the complementary factor has length at most
\begin{equation}
 S_0\ll X/T.
 \label{eq:tpc36-complementary-length}
\end{equation}
Reducing a bare interval of this length modulo \(q\asymp J\) gives maximum
residue multiplicity
\begin{equation}
 \ll1+\frac{S_0}{q}
 \ll1+\frac Q{T}
 =X^{563/2000+o(1)}.
 \label{eq:tpc36-s-residue-multiplicity}
\end{equation}
The actual weight is more structured than a bare interval, but
\eqref{eq:tpc36-s-residue-multiplicity} shows that completeness in \(s\)
cannot be treated as cost-free.

\subsection{Resolved and unresolved scales}

\begin{table}[H]
\centering
\caption{Status of the post-TPC-35 reassembly routes.}
\label{tab:tpc36-status-ledger}
\begin{tabular}{@{}
 >{\raggedright\arraybackslash}p{0.42\textwidth}
 >{\raggedright\arraybackslash}p{0.22\textwidth}
 >{\raggedright\arraybackslash}p{0.25\textwidth}@{}}
\toprule
Object or operation & Scale or cost & Status \\
\midrule
Actual static row mask
 & \(X^{o(1)}\) projective
 & proved here \\
Fixed-column source--\(d\) separation
 & \(O(D)\) layers, \(X^{o(1)}\) mass
 & proved here \\
Signed Ferrers separation
 & \(\Theta(\log D)\)
 & proved sharp here \\
Nonnegative Ferrers separation
 & \(D\)
 & proved sharp here; avoid \\
Termwise additive product-phase split
 & \(q^{1/2}\) amplitude
 & proved sharp for that route; avoid \\
Uniform complete-\(s\) Cauchy
 & \(q\) energy
 & proved sharp abstractly \\
Large-modulus standard coverage
 & \(q/J\asymp Q\)
 & valid but inefficient route \\
One orbit-scale modulus
 & \(X/q\asymp Q\) aliases
 & deterministic envelope; too many \\
Three orbit-scale moduli
 & \(X/J^3=Q/J^2\)
 & critical ledger; reassembly open \\
Actual weighted coherent spectrum
 & \eqref{eq:tpc36-coherent-character-gate}
 & exact object; estimate open \\
\bottomrule
\end{tabular}
\end{table}

Two formerly conflated questions are now separate.  The first asks whether
the mask can be put into signed product-ready form; the answer is yes.  The
second asks whether the resulting actual coefficient direction has small
weighted coherent character mass after aliases and incomplete ranges are
restored; that is the new gate.

\subsection{A coefficient-specific coherent target}

For one completed finite-field layer, define
\begin{equation}
 \cG_q(b,f,g;w)
 :=\frac1{q-1}\sum_\chi
 |\widehat b(\bar\chi)|^2
 \left|\sum_sw(s)\widehat R_s(\chi)\right|^2.
 \label{eq:tpc36-coherent-gate-functional}
\end{equation}
By \cref{thm:tpc36-weighted-coherent-spectrum}, this is exactly
\(\|S_w\|_2^2\), not a majorant.  The next physical theorem can therefore
be pursued through either of two nonexclusive routes:
\begin{enumerate}[label=(\alph*)]
 \item prove an aggregate bound for
 \eqref{eq:tpc36-coherent-gate-functional} over the actual reassembly
 layers and aliases; or
 \item prove a quantitative avoidance statement showing that the actual
 \(b,f,g,w\) have negligible overlap with the character pairs on which
 \eqref{eq:tpc36-coherent-character-gate} is large.
\end{enumerate}
Neither route asks for a maximum over all abstract coefficients.
Conversely, \cref{thm:tpc36-s-Cauchy-sharp} shows that centeredness and
 \(f(0)=0\) alone cannot prove the desired aggregate estimate.

\subsection{Route menu for the next layer}

The following routes are nonexclusive.

\begin{description}[style=nextline,leftmargin=2.4em]
 \item[Route A: residue-zero boundary extraction.]
 Split the complete \(s\)-trace
 \eqref{eq:tpc36-complete-s-trace} from the incomplete boundary weight.
 Determine whether the actual centered ultra coefficient has a small or
 diagonally absorbable \(g(0)\) component before estimating the remainder.

 \item[Route B: weighted two-character dispersion.]
 Expand the physical \(s\)-weight multiplicatively and estimate
 \(\sum_sw(s)\widehat R_s(\chi)\) by the actual M\"obius character support,
 rather than by Cauchy.  This is the closest continuation of the spectral
 route.

 \item[Route C: coherent three-modulus CRT.]
 Keep three orbit-scale moduli separate, center each coordinate face, and
 prove diagonal-scale reassembly simultaneously for principal, singleton,
 double, and full-coordinate modes.  Static mask complexity no longer adds
 a polynomial loss.

 \item[Route D: a scoped negative theorem.]
 If the physical coefficient family can be shown to concentrate on the
 saturating \(s\)-coherent mode, or if a proper-coordinate alias survives
 every admissible centering, that is a precise obstruction to this route.
 It would not be a lower bound for twin-prime correlations themselves.
\end{description}

The first two routes now have exact finite-model targets; the third has the
critical exponent budget.  Failure of any one route leaves the others
available without changing the results proved in this paper.

\subsection{Relation to the parity boundary}

The factor \(q\asymp J\) appears twice: as the energy cost of splitting a
product phase additively, and as the sharp uniform Cauchy cost in the
coherent \(s\)-variable.  Avoiding the first is an algebraic
order-of-operations theorem.  Avoiding the second requires arithmetic
information about the actual coefficient family.  No estimate here
supplies that information.

Accordingly, the soft mask theorem is a genuine advance in the proof
program, but it is not a parity-breaking theorem in the sense of classical
sieve theory \citep{HeathBrown1982Parity,IwaniecKowalski2004}.  It removes
one candidate obstruction and exposes the next one in an exact norm.
