\section{Exact certificate and claim boundary}
\label{sec:tpc33-certificate-scope}

The accompanying standard-library certificate is
\begin{center}
 \texttt{experiments/tpc33\_certificate.py}.
\end{center}
It uses integer and \texttt{Fraction} arithmetic and exception-based
checks.  No Python \texttt{assert} statement, floating-point root of unity,
or random input is used.  Running
\begin{verbatim}
python experiments/tpc33_certificate.py
python -O experiments/tpc33_certificate.py
\end{verbatim}
regenerates byte-identical JSON and identical standard output in both
modes.

\subsection{What is checked}

The certificate performs \(506{,}900\) exact checks, distributed as in
\cref{tab:tpc33-certificate-counts}.

\begin{table}[H]
\centering
\caption{Exact finite checks in the TPC-33 certificate.}
\label{tab:tpc33-certificate-counts}
\begin{tabular}{@{}lr@{}}
\toprule
Check family & Count \\
\midrule
Affine normal form, gcd identities, and M\"obius layers & \(248{,}914\) \\
Reduced and projected affine origins & \(83{,}646\) \\
Local squarefree root counts & \(9{,}853\) \\
Actual-mask gcd projector and coefficient mass & \(135{,}320\) \\
Projective second moment and product-slope lift & \(714\) \\
Quadratic-character coherent-line obstruction & \(27{,}790\) \\
Finite column Cauchy--Schwarz inequalities & \(630\) \\
High-\(\beta\) rational ledger & \(9\) \\
Scope flags & \(24\) \\
\midrule
Total & \(506{,}900\) \\
\bottomrule
\end{tabular}
\end{table}

The affine checks enumerate primitive coefficient triples and verify
\begin{equation}
 sU_t-aD_t=h,\qquad
 \binom ht=\begin{pmatrix}s&-a\\-y&x\end{pmatrix}\binom{U_t}{D_t},
 \label{eq:tpc33-certificate-affine}
\end{equation}
all four gcd identities, the nonprimitive M\"obius layer, and the
discriminant \(h^2\).  The local sieve checks enumerate complete residue
systems modulo \(p\) or \(p^2\) and verify the exact \(p-1\),
\(p^2-1\), and \(p^2-2\) allowed-class counts.

The mask checks verify
\eqref{eq:tpc33-row-gcd-projector} and
\eqref{eq:tpc33-row-gcd-projector-mass} on finite ranges.  The projective
checks evaluate both sides of
\eqref{eq:tpc33-projective-plancherel} directly over finite fields, without
approximating additive characters.  The coherent-line check uses the exact
quadratic-character autocorrelation
\begin{equation}
 \sum_x\chi(x)\chi(x+k)
 =\begin{cases}q-1,&k=0,\\-1,&k\ne0,
 \end{cases}
 \label{eq:tpc33-certificate-character-autocorrelation}
\end{equation}
which certifies Fourier magnitude \(\sqrt q\) through finite-character
orthogonality.

\subsection{Reproducibility values}

The archived run has:
\begin{align}
 \text{normalized source SHA-256}\quad
 &\texttt{a55c3d71c0851870ea0b9bbd1e9ef938}
 \notag\\[-0.2em]
 &\texttt{4e70885e5de1ddc685c309ec1ec12c67},
 \label{eq:tpc33-source-hash}\\
 \text{JSON SHA-256}\quad
 &\texttt{c7d08c9020590d81bc590a6caa7d0f36}
 \notag\\[-0.2em]
 &\texttt{ad3f553532e580fbdc03553638a0b3b5},
 \label{eq:tpc33-json-hash}\\
 \text{certificate digest}\quad
 &\texttt{e5a28b8dcac36154ff620c2e644eed7f}
 \notag\\[-0.2em]
 &\texttt{d163d00568fcd90d8e4443beafcfe37b}.
 \label{eq:tpc33-certificate-digest}
\end{align}
The normalized source hash replaces all line endings by line feeds before
hashing.  The certificate digest hashes the canonical JSON payload before
the digest field is appended.

\subsection{What is not certified}

Finite enumeration verifies algebra and exact bookkeeping, not an
asymptotic analytic estimate.  In particular, the certificate does not:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item certify the error term in
 \eqref{eq:tpc33-squarefree-asymptotic}; that term is proved in the text by
 a CRT sieve and a large-square tail;
 \item prove signed cancellation in any growing affine M\"obius family;
 \item prove the physical \(Q^3\) input
 \eqref{eq:tpc33-Q3-energy-input};
 \item prove the zero-frequency flatness ratio of TPC-32;
 \item close every residual packet in the earlier prime-pair reduction;
 \item prove positivity or a Hardy--Littlewood asymptotic;
 \item prove infinitely many twin primes; or
 \item break the sieve parity barrier.
\end{enumerate}

The proved statements are the integral normal form, its squarefree-support
theorem, the actual-mask column disintegration, the finite projective second
moment and its corollaries, the exact conditional \(Q^3\)-to-\(Q^2\)
transfer, and the sharp obstructions.  The remaining mathematical task is
\eqref{eq:tpc33-next-projective-energy}, together with all later positivity
 and reconstruction stages.  This delineates the proved, conditional, and
 open parts of the argument.
