\section{The high-\texorpdfstring{\(\beta\)}{beta} ledger and the next gate}
\label{sec:tpc33-high-beta-next-gate}

We now specialize the exact interfaces to the source-compatible endpoint
of TPC-28 \citep{WangTPC28}.  The purpose is to measure what one-fiber cancellation can and
cannot accomplish, and to state the next target without implying that it
has been proved.

\subsection{Physical exponents}

The row, orbit, prime-source, and opened-divisor exponents are
\begin{align}
 \beta&=\frac{267}{400},
 &Q&=X^{267/400+o(1)},
 &J&=X^{133/400+o(1)},
 \label{eq:tpc33-high-QJ}\\
 \lambda&=\frac{99979}{210000},
 &\ell&=X^{\lambda+o(1)},
 &d_*&=\frac{10049}{52500},
 \label{eq:tpc33-high-LD}\\
 D&=X^{d_*+o(1)},
 &T&=X^{193/500+o(1)}.
 \label{eq:tpc33-high-DT}
\end{align}
The exponent \(\lambda\) here is unrelated to the finite projector
coefficient \(\lambda_G(v)\) from
\cref{sec:tpc33-structured-mask}.
Here \(Q=LD\) and \(QJ\asymp X\).  In an unprojected affine column,
\begin{equation}
 \ell j
 =X^{\lambda+133/400+o(1)}
 =X^{42451/52500+o(1)}.
 \label{eq:tpc33-high-ellj}
\end{equation}
The reflected complement satisfies
\begin{equation}
 s\ll X/T=X^{307/500+o(1)}.
 \label{eq:tpc33-high-s-range}
\end{equation}
After the row-gcd projection, the second slope is
\begin{equation}
 a=\ell jv,\qquad v\mid e,\qquad
 a\le X^{1+o(1)},
 \label{eq:tpc33-high-projected-slope}
\end{equation}
because
\begin{equation}
 \frac{42451}{52500}+\frac{10049}{52500}=1.
 \label{eq:tpc33-high-slope-sum}
\end{equation}
The corresponding affine fiber has length
\begin{equation}
 |I|\ll1+X^{d_*+o(1)}/(sv).
 \label{eq:tpc33-high-fiber-length}
\end{equation}
Thus many slope layers are arithmetically nondegenerate but contain only
\(O(1)\) points.  Nonzero determinant alone does not create a long average.

\subsection{Why square root on every long fiber is still insufficient}

The longest possible affine fiber has length \(D\), attained only when the
product \(sv\) is bounded.  Suppose, optimistically, that every such fiber
could be bounded with square-root cancellation while all outer variables
were reassembled absolutely.  The largest relative saving visible to that
strategy would be
\begin{equation}
 D^{-1/2}
 =X^{-10049/105000+o(1)}.
 \label{eq:tpc33-single-fiber-sqrt-saving}
\end{equation}
Indeed, if the fiber lengths are \(n_i\le D\), then after absolute
reassembly the ratio of square-root bounds to trivial masses is a weighted
average of \(n_i^{-1/2}\), and hence cannot improve on \(D^{-1/2}\).
The required amplitude saving is
\begin{equation}
 J^{-1}=X^{-133/400+o(1)}.
 \label{eq:tpc33-required-J-saving}
\end{equation}
The exact missing exponent is
\begin{equation}
 \boxed{
 \frac{133}{400}-\frac{10049}{105000}
 =\frac{49727}{210000}
 =0.236795\ldots.}
 \label{eq:tpc33-single-fiber-gap}
\end{equation}

This is a limitation of a specified proof strategy, not a lower bound for
the actual M\"obius sum.  It proves that even a pointwise square-root theorem
for each longest fiber cannot close the endpoint if every remaining index
is treated by the triangle inequality.  The missing gain must use collective
averaging across some of
\begin{equation}
 \ell,\quad j,\quad s,\quad v,\quad
 \text{and the opposite row}.
 \label{eq:tpc33-outer-average-variables}
\end{equation}

\subsection{The restricted physical projective-energy problem}

The next analytic target is exactly
\begin{equation}
 \boxed{
 E_L+E_R\ll_{\eps,h,\mathscr D}X^\eps Q^3,}
 \label{eq:tpc33-next-projective-energy}
\end{equation}
with \(E_L,E_R\) defined in
\eqref{eq:tpc33-left-column-energy} and
\eqref{eq:tpc33-right-column-energy}, and with each inner column expanded
as in \cref{thm:tpc33-actual-mask-column}.  The estimate must retain:
\begin{enumerate}[label=\textup{(\alph*)}]
 \item both exact polarizations;
 \item the actual row coefficients and row-gcd projection;
 \item the fixed-period and smooth orbit factors;
 \item the \(+1\) occupancy in \eqref{eq:tpc33-high-fiber-length}; and
 \item the exceptional coefficient pairs allowed by determinant-fiber
 averaging.
\end{enumerate}

There are several nonexclusive routes to
\eqref{eq:tpc33-next-projective-energy}:
\begin{enumerate}[label=\textup{(\roman*)}]
 \item prove an integer restricted-projective large sieve directly for
 \(a=\ell jv\) and the physical \(s\)-range;
 \item use a multi-modulus delta/circle decomposition to separate no-wrap
 from slope coverage;
 \item expose a genuine second long variable and apply a correlation
 theorem in two variables before taking absolute values; or
 \item split long and sparse fibers and combine a \(TT^*\) estimate on the
 long range with an incidence-energy estimate on the \(O(1)\)-point range.
\end{enumerate}
Each route requires a new norm and conductor ledger.  The present paper
does not select one as already successful.

\subsection{Endpoint consequences if the gate is proved}

At \eqref{eq:tpc33-high-QJ},
\begin{equation}
 Q^2=N_0J^{-1}
 =N_0X^{-133/400+o(1)}.
 \label{eq:tpc33-high-Q2-saving}
\end{equation}
Thus \eqref{eq:tpc33-next-projective-energy}, together with
\cref{thm:tpc33-column-energy-transfer}, gives every strict saving below
\(133/400\) for the matched raw shell.  The large-content correction at
\(C=J\) has the same \(Q^2\) size.

The drift term is smaller still.  From
\eqref{eq:tpc33-high-QJ}--\eqref{eq:tpc33-high-LD},
\begin{equation}
 \frac{XQ/L}{Q^2}
 =\frac JL
 =X^{-15077/105000+o(1)}.
 \label{eq:tpc33-high-drift-ratio}
\end{equation}
Consequently the calibrated shell would also be
\(O(X^{o(1)}Q^2)\).

Even that conditional endpoint closes only the residual packet inherited
from the preceding reductions.  It does not supply the independent
positivity and main-term reconstruction needed for a prime-pair theorem.
The next gate is therefore substantial but sharply localized: it is a
restricted projective \(L^2\) estimate, not a disguised assertion that
the twin-prime conjecture has already been proved.
