\begin{abstract}
Let \(a=(a_\omega)_{\omega\in\Omega}\ne0\) be a complex coefficient
on its prescribed finite support, let \(S=\#\Omega\), and put
\[
 Z=\sum_{\omega\in\Omega}a_\omega,\qquad
 D=\sum_{\omega\in\Omega}|a_\omega|^2,\qquad
 \rho(a)=\frac{|Z|}{\sqrt{SD}}.
\]
Thus \(\rho(a)\) is the cosine of the projective angle between \(a\)
and the constant vector.  If
\[
 a=\frac{Z}{S}\one+a_\perp,
\]
then the exact orthogonal decomposition is
\[
 D=\frac{|Z|^2}{S}+\|a_\perp\|_2^2,\qquad
 \Flat(a):=\frac{|Z|^2}{D}=S\rho(a)^2.
\]

We determine the sharp perturbation law for this angle.  If
\(\|a-b\|_2\le\delta\|b\|_2\), \(0\le\delta<1\), and
\(r=\rho(b)\), then, for support dimension at least two,
\[
 L(r,\delta)\le\rho(a)\le U(r,\delta),
\]
where, with \(\alpha=\arccos r\) and
\(\gamma=\arcsin\delta\),
\[
 L(r,\delta)=\cos\!\bigl(\min\{\tfrac{\pi}{2},\alpha+\gamma\}\bigr),
 \qquad
 U(r,\delta)=\cos\!\bigl((\alpha-\gamma)_+\bigr).
\]
Both endpoints are attained.  In particular,
\[
 |\rho(a)-\rho(b)|\le\delta,
\]
with optimal constant \(1\).  The frequently obtained estimate
\[
 \rho(a)\le\frac{\rho(b)+\delta}{1-\delta}
\]
is valid, but is not sharp; its denominator is an artifact of
separately estimating the numerator and norm.

This exact stability law identifies a critical surrogate barrier.
To transfer an upper target \(\rho\ll J^{-1}\), relative
\(\ell^2\) error \(O(J^{-1})\) is sufficient and, uniformly over
surrogates, necessary in order.  Merely \(o(1)\) error is
insufficient: there are two-dimensional examples with
\(\rho(b_J)=0\), relative error \(\delta_J\to0\), and
\(\rho(a_J)=\delta_J\gg J^{-1}\).  Uniformly preserving a
two-sided \(\rho\asymp J^{-1}\) law from the norm hypothesis alone
additionally requires a fixed margin between the error constant and
the surrogate's lower constant.

Finally, we attach the theorem to the literal fixed-\(h_0\) TPC-32
determinant packet.  On its actual support \(S_X\ll Q_X\), a
same-frame surrogate satisfying
\[
 \rho(b_X)\le\frac{X^{o(1)}}{J_X},
 \qquad
 \frac{\|A_X-b_X\|_2}{\|b_X\|_2}
 \le\frac{X^{o(1)}}{J_X}
\]
would certify
\[
 \Flat(A_X)\le X^{1/400+o(1)}
\]
at the critical scales.  This is an exact \(\Lone\) stability
certificate, not a construction of such a surrogate and not a new
\(\Ltwo\) estimate.  The determinant-energy ledger
\(\lambda_D\le2\eta_Z\) and the independent physical-loss ledger
\(\Lambda_{\rm phys}<1/400\) are kept separate.
\end{abstract}
