\section{Claim boundary and next gate}
\label{sec:claim-boundary}

\begin{theorem}[Audited conclusion]
\label{thm:audited-conclusion}
Let \(a\ne0\) be a finite complex coefficient on its prescribed
support of size \(S\).  Then
\[
 D(a)=\frac{|Z(a)|^2}{S}+D_\perp(a),\qquad
 \Flat(a)=S\rho(a)^2.
\]
If \(a\) is approximated by \(b\ne0\) with
\[
 \|a-b\|_2\le\delta\|b\|_2,\qquad\delta<1,
\]
then the sharp envelope
\[
 L(\rho(b),\delta)\le\rho(a)\le
 U(\rho(b),\delta)
\]
holds, and in particular
\[
 |\rho(a)-\rho(b)|\le\delta.
\]
The constant is optimal.  Consequently,
\[
 \rho(b_J)=O(J^{-1}),\quad
 \delta_J=O(J^{-1})
\quad\Longrightarrow\quad
 \rho(a_J)=O(J^{-1}),
\]
and this order of relative accuracy is uniformly sharp.

For the literal fixed-\(h_0\) TPC-32 coefficient on its actual
support, the conditional same-frame hypotheses
\[
 \rho(b_X),\delta_X
 \le\frac{X^{o(1)}}{J_X}
\]
certify
\[
 \Flat_X\le X^{1/400+o(1)}.
\]
\end{theorem}

\begin{proof}
Combine
\cref{thm:orthogonal-decomposition,thm:sharp-envelope,cor:optimal-additive-stability,thm:sharp-accuracy-barrier,thm:literal-surrogate-certificate}.
\end{proof}

\paragraph{What is proved.}
The orthogonal decomposition, exact angle envelope, equality
constructions, padding law, \(J^{-1}\) accuracy barrier, and finite
countermodels are unconditional \(\Lzero\) results.  Their placement
on the actual fixed-\(h_0\) determinant support is an exact
\(\Lone\) stability certificate.

\paragraph{What is not proved.}
No same-frame surrogate for \(A_X\) is constructed.  No bound
\(\delta_X\le X^{o(1)}/J_X\) is proved.  No determinant-energy lower
bound, distinguished zero-mode estimate, growing fixed-shift
M{\"o}bius-correlation estimate, or full-block remainder estimate is
proved.  Thus there is no new \(\Ltwo\) arithmetic theorem.

\paragraph{Support rule.}
The angle must be computed on the actual post-bin support of the
literal coefficient.  Zero padding changes \(\rho\).  A surrogate
with a different grid or support is covered only after an exact map
places it on the literal bins.  Otherwise a separate union-frame
theorem is required and the present certificate does not apply.

\paragraph{Degenerate branches.}
If \(A_X=0\), one may set \(\Flat_X=0\) by convention, but
\(\rho_X\) is left undefined and no division by \(D_X\) is made.
This branch does not certify determinant-energy survival.  If
\(A_X\ne0\) and \(S_X=1\), then
\(\rho_X=\Flat_X=1\); the flatness upper target is numerically
automatic for large \(X\), while the nontrivial two-dimensional
sharpness constructions are inapplicable.

\paragraph{Accuracy rule.}
Relative error \(o(1)\) is sufficient to transfer a nonzero
determinant-energy scale, but not a \(J^{-1}\) principal-angle
scale.  For a one-sided upper target, \(O(J^{-1})\) is the sharp
uniform order.  For a two-sided \(\asymp J^{-1}\) statement, the
error constant must also remain strictly below the lower signal
constant.

\paragraph{Ledger rule.}
The determinant compatibility condition
\[
 \lambda_D\le2\eta_Z
\]
and the physical stop rule
\[
 \Lambda_{\rm phys}<1/400
\]
belong to different ledgers.  The surrogate error belongs to a
third stability interface.  None may be added to, subtracted from,
or substituted for another without a proved literal crosswalk.

\paragraph{Arithmetic claim boundary.}
Nothing here specializes the prescribed nonzero \(h_0\) to \(2\),
breaches the sieve parity barrier, proves a fixed-shift
Hardy--Littlewood asymptotic, gives a prime-pair lower bound, or
proves the twin-prime conjecture.  The critical-angle certificate
only states what an eventual surrogate theorem would have to
resolve.

\paragraph{Next gate.}
The most direct positive continuation is to construct a literal
same-frame surrogate \(b_X\) for which both
\[
 \rho(b_X)\le\frac{X^{o(1)}}{J_X}
\quad\text{and}\quad
 \|A_X-b_X\|_2
 \le\frac{X^{o(1)}}{J_X}\|b_X\|_2
\]
can be proved.  If only \(\delta_X=o(1)\) is accessible, a different
route must establish additional signed orthogonality of the error,
for example a direct improvement of
\[
 |Z(A_X-b_X)|
 \le\sqrt{S_X}\|A_X-b_X\|_2.
\]
Failure of both routes would itself identify a precise
nonidentifiability barrier, rather than evidence for a prime-pair
claim.
