\section{Separate determinant and physical ledgers}
\label{sec:separate-ledgers}

The same exponent \(1/400\) appears in several interfaces, but the
corresponding quantities are not interchangeable.  This section
records the ledgers explicitly.

\subsection{Determinant-energy and zero-mode ledger}

On a conditional natural-support branch, write
\begin{equation}
 S_X=X^{o(1)}Q_X,
\label{eq:ledger-support}
\end{equation}
and suppose the literal coefficient satisfies
\begin{align}
 |Z_X|
 &\le
 X^{-\eta_Z+o(1)}Q_X^2,
\label{eq:ledger-Z}\\
 D_X
 &\ge
 X^{-\lambda_D+o(1)}Q_X^3J_X^2.
\label{eq:ledger-D}
\end{align}
These are hypotheses, not results of the present paper.

\begin{proposition}[Principal-angle exponent dictionary]
\label{prop:angle-exponent-dictionary}
Under
\eqref{eq:ledger-support}--\eqref{eq:ledger-D},
\begin{equation}
 \rho_X
 \le
 \frac{
 X^{\lambda_D/2-\eta_Z+o(1)}
 }{J_X}.
\label{eq:angle-exponent-dictionary}
\end{equation}
Consequently, the recorded bounds certify the critical angle scale
\(\rho_X\le X^{o(1)}/J_X\) whenever
\begin{equation}
 \boxed{\lambda_D\le2\eta_Z.}
\label{eq:determinant-ledger}
\end{equation}
\end{proposition}

\begin{proof}
Insert \eqref{eq:ledger-support}--\eqref{eq:ledger-D} into
\[
 \rho_X=\frac{|Z_X|}{\sqrt{S_XD_X}}.
\]
The denominator has scale
\[
 \sqrt{S_XD_X}
 \ge
 X^{-\lambda_D/2-o(1)}Q_X^2J_X.
\]
This proves \eqref{eq:angle-exponent-dictionary}.  The exponent of
\(X\) outside \(J_X^{-1}\) is nonpositive precisely under
\eqref{eq:determinant-ledger}.
\end{proof}

\begin{remark}[A sufficient recorded-bounds condition]
The condition \(\lambda_D\le2\eta_Z\) is the TPC-81/TPC-82
compatibility ledger for these particular recorded bounds
\citep{WangTPC81,WangTPC82}.  It is not claimed to be necessary for
the physical packet if either estimate is nonoptimal.
\end{remark}

\subsection{Surrogate-accuracy ledger}

The surrogate parameter
\[
 \delta_X=\frac{\|a_X-b_X\|_2}{\|b_X\|_2}
\]
has two distinct jobs:
\begin{enumerate}[label=(\alph*),leftmargin=2.2em]
\item \(\delta_X=o(1)\) transfers the determinant-energy scale by
\eqref{eq:energy-transfer};
\item \(\delta_X\le X^{o(1)}/J_X\) transfers the critical
principal-angle scale by
\eqref{eq:literal-rho-stability}.
\end{enumerate}
The second is strictly stronger.  Neither hypothesis is presently
verified for a literal TPC-32 surrogate.

\subsection{Physical-loss ledger}

The complete physical reduction has its own fixed-power loss
\(\Lambda_{\rm phys}\).  The inherited endpoint rule is
\begin{equation}
 \boxed{\Lambda_{\rm phys}<\frac1{400}.}
\label{eq:physical-loss-ledger}
\end{equation}
Equality or excess is a stop condition.

\begin{table}[ht]
\centering
\small
\begin{tabularx}{\textwidth}{@{}
  >{\raggedright\arraybackslash}p{0.22\textwidth}
  >{\raggedright\arraybackslash}X
  >{\raggedright\arraybackslash}p{0.23\textwidth}@{}}
\toprule
Ledger & Certified comparison & Status here\\
\midrule
Determinant angle
&
\(\lambda_D\le2\eta_Z\) transfers the recorded \(Z_X,D_X\)
bounds to \(\rho_X\le X^{o(1)}/J_X\)
&
Conditional \(\Lone\); no \(Z_X\) or \(D_X\) estimate proved
\\
\addlinespace
Surrogate stability
&
\(\rho(b_X),\delta_X\le X^{o(1)}/J_X\) transfers the angle and
flatness target
&
Exact \(\Lone\) implication; no surrogate constructed
\\
\addlinespace
Physical reassembly
&
\(\Lambda_{\rm phys}<1/400\)
&
Independent inherited stop rule
\\
\bottomrule
\end{tabularx}
\caption{The three comparisons have different inputs and cannot be
merged without an explicit crosswalk.}
\label{tab:separate-ledgers}
\end{table}

\begin{proposition}[No automatic ledger conversion]
\label{prop:no-ledger-conversion}
The identities and perturbation inequalities of this paper do not
imply any of the following conversions:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item a determinant-energy loss \(\lambda_D\) is a physical
reassembly loss;
\item the approximation exponent in \(\delta_X\) is a saving in
\(\eta_Z\);
\item a numerical surrogate error may be subtracted from
\(\Lambda_{\rm phys}\);
\item the inequalities
\eqref{eq:determinant-ledger} and
\eqref{eq:physical-loss-ledger} may be added into one budget.
\end{enumerate}
\end{proposition}

\begin{proof}
The determinant ledger compares the literal post-bin zero mode with
literal post-bin energy.  The surrogate ledger compares two vectors
on that same coefficient space.  The physical ledger records losses
in the upstream and downstream arithmetic reassembly.  No theorem
above identifies any pair of these quantities.  Therefore no
conversion follows.
\end{proof}

\begin{remark}[What a valid crosswalk would require]
To enter a surrogate construction into the physical ledger, one
would need a literal theorem that tracks its approximation error
through every mask, determinant bin, polarization, and outer
normalization.  To enter determinant-energy loss into the physical
ledger, one would need a theorem expressing that loss as an
independent consumption of the final saving.  Until such statements
are proved, the ledgers remain separate and double counting is
forbidden.
\end{remark}
