\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Joint Before Centering at a Poisson-Long Base: Full-Rectangle Exact Conductors and High-Beta Initial-Value Closure},
 pdfauthor={Liang Wang},
 pdfsubject={Closure of a selected calibrated Poisson-long base packet in a primitive Mobius tail},
 pdfkeywords={Mobius tail, Poisson-long base, exact conductor, raw joint rectangle, additive zero mode, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cN}{\mathcal N}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cW}{\mathcal W}
\newcommand{\cond}{\operatorname{cond}}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Joint Before Centering at a Poisson-Long Base:}\\
\textbf{Full-Rectangle Exact Conductors and}\\
\textbf{High-\(\boldsymbol\beta\) Initial-Value Closure}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let $P_{m,S}$ be the calibrated divisor prefix in a primitive
opened row $m=\ell d$, and suppose that the base cutoff $S$ may
already exceed the orbit length $J\asymp X/Q$.  The centered
nonzero-spectrum theorem used previously requires $S<J$.  Treating
its scalar correction terms separately also incurs the polynomial loss
$1+S/J$.  We remove both appearances of that restriction by changing
the order of the decomposition.

Write
\[
 \mathsf A_{m,S}(j)=
 \sum_{\substack{u\le S\\u\mid mj+h}}b_R(u),
 \qquad P_{m,S}=\mathsf A_{m,S}-\delta_H(m).
\]
At additive frequency zero, the raw joint kernel, both drift legs, and
the constant term recombine exactly as
\[
 \cR_S^0(m,n)-\delta_H(m)D_{n,S}
 -\delta_H(n)D_{m,S}+\delta_H(m)\delta_H(n)
 =K_S^0(m,n)+E_S(m)E_S(n).
\]
Here $D_{m,S}=\delta_H(m)+E_S(m)$, while $K_S^0$ is the
Ramanujan-square connected kernel already known to have arbitrary
logarithmic physical saving.  Thus no Poisson-short hypothesis is
needed at zero frequency.

Away from zero, we prove a full-rectangle version of the symmetric
exact-conductor argument.  For $u,v\le S$, denominator
$[u,v]\asymp Y$, and coordinate conductors $F_1,F_2$, the raw joint
cell satisfies
\[
 \cL^{\rm base}_{Y;S}(F_1,F_2)
 \ll QX^\eps
 \sqrt{\cK_Q(F_1)\cK_Q(F_2)}
 \min\{\sqrt{JY},F_1F_2\},
 \qquad \cK_Q(F)=F+Q/F.
\]
The corresponding relaxed-box saving is the same piecewise function
$M_\beta(s)$ that occurs in the annular joint problem.  A pointwise
target-divisor bound gives
$\mathsf A_{m,S}(j)\ll_\eps X^\eps$, so the two remaining drift legs
are power-small from the existing row-prime condition
$L\ge X^{\lambda_0}$; no factor $1+S/J$ remains.  Consequently
$M_\beta(s)>0$, together with the physical row, no-wrap, Fourier-tail,
and fixed-margin interfaces, closes the selected calibrated base
packet even when $S>J$.

For the exact source-compatible sample
\[
 \beta=\frac{267}{400},\qquad
 s=\frac{23}{60},\qquad
 t=\frac{193}{500},
\]
the old centered ledger has the negative face $-1/800$, whereas the
full-rectangle base margin is $M_\beta(s)=13/1600$.  The row-prime
exponent is $99979/210000$, and the inherited annular margin to
$T=X^t$ is $33/8000$.  Hence the selected calibrated truncated square
closes at this particular $\beta>2/3$ sample.  The ultra-long complement,
positivity, a Hardy--Littlewood asymptotic, twin primes, and any general
breach of the parity barrier remain outside the result.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; Poisson-long
base; raw joint rectangle; exact conductor; additive zero mode; sieve
parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11L07, 11L40.

\input{sections/introduction}
\input{sections/interface-zero}
\input{sections/full-rectangle-conductor}
\input{sections/minimax-reassembly}
\input{sections/drift-base-theorem}
\input{sections/high-beta-splice}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
