\section{Introduction}
\label{sec:introduction}

The high-row fixed-shift route isolates the literal determinant
coefficient
\[
 A_X(n)=A_{\lfloor J_X\rfloor}(n)
\]
only after the three matched physical channels and every native
contribution in the determinant fiber have been aggregated.  Its
post-bin statistics are
\[
 Z_X=\sum_nA_X(n),\qquad
 M_X=\sum_n|A_X(n)|,\qquad
 D_X=\sum_n|A_X(n)|^2.
\]
TPC-32 asks for an upper bound on the normalized zero-frequency
concentration
\[
 \Flat_X=\frac{|Z_X|^2}{D_X},
\]
while TPC-83 shows that survival of the natural determinant energy
is equivalent, up to subpower factors, to survival of the literal
post-bin \(\ell^1\) mass \(M_X\)
\citep{WangTPC32,WangTPC83}.  These statements leave a useful
question:

\begin{quote}
Once post-bin mass and energy have survived, exactly how much
cancellation among determinant bins is still required?
\end{quote}

The answer is an identity rather than an estimate.  Write
\[
 \canc_X=\frac{|Z_X|}{M_X},
 \qquad
 \SeffX=\frac{M_X^2}{D_X}.
\]
Then
\[
 \Flat_X=\canc_X^2\SeffX.
\]
The two factors have different meanings.  The effective support
\(\SeffX\) depends only on the magnitudes
\((|A_X(n)|)\); the relative cancellation \(\canc_X\) records how
the complex phases reassemble.  Neither factor may be substituted
for the other.

This paper makes the split exact and performs the endpoint
arithmetic.  Its main contributions are:
\begin{enumerate}[label=(\roman*),leftmargin=2.2em]
\item an edge-safe definition covering both nonzero and identically
zero complex sequences;
\item the exact factorization
\(\Flat=\canc^2\Seff\);
\item sharp ranges and complete elementary equality cases;
\item for a nonzero coefficient, a joint lower edge
\((2-\Seff)_+\le\Flat\), showing what very concentrated magnitude
profiles force even under optimal phase opposition;
\item exact counterexamples showing that identical magnitude data
can produce maximal or complete zero-mode cancellation;
\item a literal crosswalk to the fixed-\(h_0\) TPC-32 coefficient;
\item a proof that natural post-bin mass implies
\(\SeffX=X^{o(1)}Q_X\);
\item the critical equivalence
\[
 \Flat_X\le X^{1/400+o(1)}
 \quad\Longleftrightarrow\quad
 \frac{|Z_X|}{M_X}\le\frac{X^{o(1)}}{J_X};
\]
and
\item a two-level exponent ledger that reproduces, without double
counting, the TPC-82 compatibility condition
\(2\eta_Z\ge\lambda_D\).
\end{enumerate}

The factorization does not create phase cancellation.  It identifies
its exact relative scale after the magnitude-spreading level has
been fixed.

\subsection{Audit levels}

We retain the established three-level terminology.  An \(\Lzero\)
statement is finite algebra or an abstract finite counterexample.  An
\(\Lone\) statement identifies the same quantities on the literal
fixed-\(h_0\) carrier with its original aggregation and
normalization.  An \(\Ltwo\) statement is a new growing-\(X\)
arithmetic estimate for that carrier.  The finite theorems in
\cref{sec:finite-factorization,sec:sharp-range} are \(\Lzero\).
The crosswalk and conditional exponent implications are \(\Lone\).
No \(\Ltwo\) input is asserted.
