\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Label-Preserving Signed Observables after Radial Completion: A Fixed-Shift Coprime-Shell Law, Uniform Short-Shift Masks, and the Type-II Gate},
 pdfauthor={Liang Wang},
 pdfsubject={Fixed-shift and short-shift theorems for signed GCD-Mellin label selectors},
 pdfkeywords={prime correlations, GCD-Mellin transform, unitary divisors, Titchmarsh divisor problem, Vaughan identity, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cC}{\mathcal C}
\newcommand{\cE}{\mathcal E}
\newcommand{\cH}{\mathcal H}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cN}{\mathcal N}
\newcommand{\cO}{\mathcal O}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\dist}{\operatorname{dist}}
\newcommand{\ran}{\operatorname{ran}}

\title{\textbf{Label-Preserving Signed Observables}\\
\textbf{after Radial Completion:}\\
\textbf{A Fixed-Shift Coprime-Shell Law, Uniform}\\
\textbf{Short-Shift Masks, and the Type-II Gate}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let $u(n)=\Lambda(n)-1$, let
$W\in C_c^1((0,\infty);\R)$ and $G\in C_c^1(\R;\R)$ be nonzero, and
write every factor pair uniquely as
$n=ak$, $m=bk$, $(a,b)=1$.  TPC-13 separated the joint labels
$(\log(a/b),\log k)$ and proved diagonal-energy laws together with
character-phase first moments.  Here we evaluate one fixed-shift aggregate
and close the short-shift first moment from character phases to the full
bounded-mask ball.

The first result is at a prescribed fixed nonzero shift.  The exact radial
shell $k=1$, with all primitive orientations retained, is
\[
 \cK_h(X)=
 \sum_{\substack{a>1,\ b\geq1\\(a,b)=1}}
 u(a)(\Lambda(ab+h)-1)W(ab/X).
\]
If
\[
 \beta_h=\prod_{p\mid h}
 \left(1-\frac{p}{p^2-p+1}\right),
\]
then the unitary-divisor Titchmarsh theorem of Biao Wang implies
\[
 \cK_h(X)=
 \left(\frac1{\zeta(2)}-\beta_h\right)
 XI_0(W)\log X+O_{h,W}(X).
\]
Thus a nontrivial signed GCD--Mellin radial shell is evaluated for every
fixed $h$, including $h=2$.  It still sums all primitive directions $b$;
it does not isolate the endpoint $b=1$ and gives no twin-prime conclusion.

The second result controls the full coefficient-space dual ball after a
growing short-shift average.  For
$X^{2/15+\eps}\leq H\leq X$ and every $A>0$, the Guth--Maynard
short-interval inputs give, provided all translated targets remain at
height comparable with $X$,
\[
 \left\|
 \frac1H\sum_qG(q/H)(\Lambda(\,\cdot+h_0+q)-1)
 \right\|_{\ell^2(r\asymp X)}
 \ll_{A,\eps,G}X^{1/2}(\log X)^{-A}.
\]
Consequently, uniformly for every $D\geq1$, every bounded,
shift-independent mask $|\omega(a,b,k)|\leq1$ satisfies
\[
 \begin{aligned}
 &\frac1H\sum_qG(q/H)
 \sum_{\substack{a,b,k\geq1,\ (a,b)=1\\ak>D}}
 \omega(a,b,k)u(ak)\\
 &\qquad{}\times
 (\Lambda(abk^2+h_0+q)-1)W(abk^2/X)
 \ll_A X(\log X)^{-A}.
 \end{aligned}
\]
uniformly in the mask.  Taking $D=1$, this includes the exact endpoint
$b=k=1$,
individual radial layers, primitive rays, and arbitrary signed unions.
It yields an averaged endpoint prime-pair asymptotic at the
two-fifteenths scale, but no selected shift.

After recentering on the factorized target variable, the same theorem
controls every bounded mask of Vaughan's hard packet under the short-shift
average.  Finally, an exact local-data minimax formula and a nearly sharp
square-root divisor-signature dichotomy exhibit a prime/semiprime null
direction.  A balanced bilinear factor row detects that direction exactly;
detecting it is an information test, not an estimate for the arithmetic
packet.  No fixed-shift prime-pair asymptotic, twin-prime lower bound, new
level of distribution, or breach of sieve parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} GCD--Mellin labels; unitary divisors;
Titchmarsh divisor problem; short-shift prime correlations; Vaughan
identity; Type-II information; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N05, 11N37; Secondary
11N35, 11N32, 42A05.

\input{sections/introduction-scope}
\input{sections/dual-label-selectors}
\input{sections/fixed-coprime-shell}
\input{sections/l2-short-shift-transfer}
\input{sections/endpoint-even-shifts}
\input{sections/masked-vaughan-packets}
\input{sections/local-typeii-gate}
\input{sections/fixed-shift-boundary}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
