\section{Claims, stops, and the next gate}
\label{sec:claim-boundary}

\subsection{L0 results proved here}

For four squarefree largest-prime targets attached to two primitive rows:
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item the five four-corner identities
       \eqref{eq:anchor-determinant}--\eqref{eq:cross-determinant};
 \item the same-residual normal form
       \[
       R_m=bt,\qquad R_n=at,\qquad t\mid |h_0(n-m)|;
       \]
 \item the primitive erasure normal form
       \[
       S_m=qu,\qquad S_n=qv,\qquad
       q\mid |h_0(n-m)|;
       \]
 \item the exact erasure criterion
       \[
       d_mS_m\ne d_nS_n
       \quad\Longleftrightarrow\quad
       (u,v)\ne(b,a);
       \]
 \item the anchor and erasure affine-ray parametrizations and their exact
       census bounds;
 \item the sign identity
       \[
       \mu(d_mS_m)\mu(d_nS_n)
       =\mu(a)\mu(b)\mu(u)\mu(v);
       \]
 \item the fact that this sign is frozen along every fixed
       \((q,u,v)\)-ray; and
 \item the exact finite primitive-plane partition of an anchored
       rectangle sum.
\end{enumerate}

\subsection{L1 identification}

The L0 coordinates are identified with the literal TPC two-key rectangle
by retaining:
\begin{itemize}
 \item the fixed nonzero \(h_0\) in every target;
 \item the actual largest prime and cofactor at all four corners;
 \item every complete native key and actual support condition;
 \item all four literal complex coefficients;
 \item raw atomic row normalization; and
 \item the full physical kernel \(K_{\mathfrak a,q}(u,v)\), with zero
       coefficient at every absent corner.
\end{itemize}
Consequently \eqref{eq:complete-primitive-plane-transform} is an exact L1
reindexing of \(\tr(ER)\), not a model average.

\subsection{L2 statements not proved}

This paper does not prove:
\begin{itemize}
 \item cancellation in one primitive cofactor box;
 \item a uniform two-dimensional Mertens or variation bound for the actual
       kernel;
 \item a saving after summing all \(q,t\), anchors, keys, or row pairs;
 \item a local-star bound or a complete mixed-moment bound;
 \item a subpower or vanishing bound for \(\|R+E\|\);
 \item missing-mass, represented-frame, or nuisance-shorting estimates;
 \item any fixed-\(h_0\) parity-breaking estimate;
 \item a prime-pair theorem, a twin-prime theorem, or a positive lower
       bound for prime pairs.
\end{itemize}

\subsection{Kill criteria}

\begin{enumerate}[label=\textup{(K\arabic*)},leftmargin=3.5em]
 \item \textbf{Nonprimitive rows.}  The exact ray spacings use
       \((mn,h_0)=1\).  Applying them outside that scope without extracting
       the additional gcd changes the parametrization.

 \item \textbf{Nonsquarefree support.}  The sign formula is a
       \(\{-1,1\}\)-identity on the active squarefree carrier.  Terms with
       vanishing M\"obius factors must be removed or treated separately.

 \item \textbf{Time-only compression.}  Replacing complete native keys by
       their times deletes orthogonal labels and estimates a different
       operator.

 \item \textbf{False ray randomness.}  The target M\"obius sign is constant
       on a fixed \((q,u,v)\)-ray.  Random-sign or time-oscillation
       heuristics cannot certify a saving there.

 \item \textbf{Divisor-count overclaim.}  Although \(t,q\mid H\), the
       primitive pair, ray points, and complete keys remain.  The number
       of rectangles is not bounded by \(\tau(H)^2\).

 \item \textbf{Silent rectangularization.}  Zero-extending the ragged
       support is allowed only if every new boundary and variation term is
       retained.

 \item \textbf{Unsigned-to-signed promotion.}  A Brun--Selberg upper bound
       is an absolute population estimate, not cancellation of
       \(\mu(u)\mu(v)\).

 \item \textbf{Trace-to-operator promotion.}  A small
       \(\tr(ER)\) does not imply a local-star, moment, or operator-norm
       bound.

 \item \textbf{Reassembly mismatch.}  A missing-native estimate does not
       prove the mass, represented-frame, or nuisance shorting gates.

 \item \textbf{Endpoint stop.}  Any combined literal loss at least
       \(1/400\) stops the present endpoint implication.
\end{enumerate}

\subsection{The next specified gate}

The next falsifiable question is not another coordinate change.  It is:
\begin{quote}
For the zero-extended literal kernels \(K_{\mathfrak a,q}\), can
two-dimensional summation by parts combine unconditional Mertens
cancellation with a uniformly subcritical boundary-and-variation total?
\end{quote}
A complete next step should:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item derive an exact discrete two-dimensional Abel identity;
 \item separate interior mixed variation from four edges and four corners;
 \item charge the primitive condition, the excluded point, ragged cofactor
       support, prime-line masks, and missing masks literally;
 \item compare the resulting certificate with
       \(\sum|K_{\mathfrak a,q}|\) in every dyadic box; and
 \item either prove a uniform saving or give an actual-kernel lower bound
       showing that the variation route cannot save.
\end{enumerate}
If the certificate succeeds only for smoothed, averaged, or frozen
kernels, that result must remain in its weaker scope.  If it fails because
hard physical masks have full variation, the failure is a publishable
negative boundary and the route should return to literal complex phases
or direct shorted reassembly.

\subsection{Status line}

TPC--70 compresses both common-content variables to divisors of the fixed
row-pair determinant and identifies the surviving sign as a primitive
two-dimensional M\"obius product.  It also proves that time-ray sign
oscillation is impossible.  This is a genuine L0/L1 advance and a sharper
analytic target.  It is not L2 cancellation and gives no evidence that
the parity barrier has been crossed.
