\section{The exact primitive cofactor-plane transform}
\label{sec:cofactor-plane}

We now group the literal rectangle sum without dropping any native label.

\subsection{Anchored rectangles}

Fix \(m<n\).  A \emph{same-residual anchor}
\(\mathfrak a\) consists of:
\[
 \mathfrak a
 =
 (m,n,\iota_R,j_R,P_m,P_n,R_m,R_n,t)
\]
together with its two literal corner coefficients.  Every entry is
recovered from an actual complete native key satisfying
\eqref{eq:same-residual-anchor}.  Let \(\cR_{m,n}\) be the finite set of
such anchors.

For a fixed anchor, let \(\cE(\mathfrak a)\) be the finite set of actual
erasure keys \(\iota_E\) completing the other two corners and satisfying
\eqref{eq:unequal-residual-erasure}.  Define the oriented anchored sum
\begin{equation}
 \mathfrak X_{\mathfrak a}
 :=
 \sum_{\iota_E\in\cE(\mathfrak a)}
 \mu(d_mS_m(\iota_E))
 \mu(d_nS_n(\iota_E))
 \cA(\iota_E,\iota_R;m,n).
 \label{eq:anchored-rectangle-sum}
\end{equation}
With the oriented convention of \cref{sec:physical-interface},
\begin{equation}
 \tr(ER)
 =
 2\operatorname{Re}
 \sum_{m<n}\sum_{\mathfrak a\in\cR_{m,n}}
 \mathfrak X_{\mathfrak a}.
 \label{eq:trace-by-anchors}
\end{equation}

\subsection{The literal ray kernel}

Fix \(\mathfrak a\), a positive divisor \(q\mid |H|\), and positive
coprime integers \(u,v\).  If an erasure ray with these coordinates is
nonempty, choose one arithmetic representative
\[
 (j_{E,0},Q_{m,0},Q_{n,0}).
\]
Every actual key in that fiber has the form
\[
 j_E=j_{E,0}+quv\,z,\qquad
 Q_m=Q_{m,0}+mv\,z,\qquad
 Q_n=Q_{n,0}+nu\,z.
\]
Define
\begin{equation}
\begin{aligned}
 K_{\mathfrak a,q}(u,v)
 &:=
 \sum_{z\in\Z}
 \ \sum_{\substack{\iota_E\in\cE(\mathfrak a)\\
                    j(\iota_E)=j_{E,0}+quv z\\
                    (S_m(\iota_E),S_n(\iota_E))=(qu,qv)}}
 \cA(\iota_E,\iota_R;m,n).
\end{aligned}
\label{eq:literal-ray-kernel}
\end{equation}
If no representative exists, set \(K_{\mathfrak a,q}(u,v)=0\).
This definition is independent of the chosen representative, since
changing it only translates \(z\).

The kernel in \eqref{eq:literal-ray-kernel} retains:
\begin{itemize}
 \item both affine primality and largest-prime conditions;
 \item all squarefree and coprimality conditions not displayed outside the
       kernel;
 \item the actual finite cofactor and time ranges;
 \item side, block, opposite-row, \(\gamma\), missing, first-failure, and
       endpoint masks;
 \item all four literal complex coefficients; and
 \item raw atomic normalization by \(W_mW_n\).
\end{itemize}
It is therefore a ragged, generally complex kernel.  No positivity,
smoothness, product structure, or low variation is assumed.

\begin{theorem}[Exact primitive-plane transform]
\label{thm:primitive-plane-transform}
For every same-residual anchor \(\mathfrak a\),
\begin{equation}
\boxed{
 \mathfrak X_{\mathfrak a}
 =
 \mu(a)\mu(b)
 \sum_{q\mid |H|}
 \ \sum_{\substack{u,v\ge1\\(u,v)=1\\(u,v)\ne(b,a)}}
 \mu(u)\mu(v)K_{\mathfrak a,q}(u,v).}
\label{eq:primitive-plane-transform}
\end{equation}
All sums are finite because the physical carrier is finite.
\end{theorem}

\begin{proof}
Every \(\iota_E\in\cE(\mathfrak a)\) has a unique triple
\[
 q=(S_m,S_n),\qquad u=S_m/q,\qquad v=S_n/q.
\]
By \cref{thm:erasure-divisor-line}, this triple satisfies
\[
 q\mid |H|,\qquad (u,v)=1,\qquad (u,v)\ne(b,a).
\]
Conversely, the kernel in \eqref{eq:literal-ray-kernel} contains exactly
the actual erasure keys with the displayed coordinates.  Thus the
right-hand side partitions \(\cE(\mathfrak a)\) without omission or
multiplicity.  Finally, \cref{thm:primitive-cofactor-sign} replaces the
residual sign on each part by
\(\mu(a)\mu(b)\mu(u)\mu(v)\).
\end{proof}

\begin{corollary}[Complete rectangle transform]
\label{cor:complete-rectangle-transform}
The first mixed trace has the exact expansion
\begin{equation}
\boxed{
\begin{aligned}
 \tr(ER)
 =2\operatorname{Re}
 \sum_{m<n}
 \sum_{\mathfrak a\in\cR_{m,n}}
 \mu(a)\mu(b)
 \sum_{q\mid |h_0(n-m)|}
 \sum_{\substack{(u,v)=1\\(u,v)\ne(b,a)}}
 \mu(u)\mu(v)K_{\mathfrak a,q}(u,v).
\end{aligned}}
\label{eq:complete-primitive-plane-transform}
\end{equation}
\end{corollary}

\subsection{The exact location of possible cancellation}

For a fixed primitive pair, \cref{cor:frozen-ray-sign} gives
\begin{equation}
\begin{aligned}
 &\left|
 \mu(a)\mu(b)\mu(u)\mu(v)
 K_{\mathfrak a,q}(u,v)
 \right|
 =
 |K_{\mathfrak a,q}(u,v)|.
\end{aligned}
\label{eq:fiber-absolute-value}
\end{equation}
Thus grouping or estimating the \(z\)-fiber cannot by itself create
M\"obius cancellation.  It may create complex-phase cancellation inside
\(K\), but the arithmetic sign is a scalar outside the fiber.

A genuine signed estimate must control a sum of the form
\begin{equation}
 \sum_{\substack{u\sim U,\ v\sim V\\(u,v)=1\\(u,v)\ne(b,a)}}
 \mu(u)\mu(v)K_{\mathfrak a,q}(u,v)
 \label{eq:dyadic-primitive-plane-target}
\end{equation}
uniformly over the actual growing family of rows, anchors, divisors,
blocks, and coefficient profiles.  Small or boundary values of \(u,v\)
are part of the physical support; the notation \(u\sim U,v\sim V\) is only
a possible later dyadic partition, not a hypothesis of this paper.

\begin{remark}[Zero extension and boundary cost]
\label{rem:zero-extension-boundary-cost}
One may extend \(K_{\mathfrak a,q}\) by zero to a rectangle in
\(\Z_{\ge1}^2\) and absorb the primitive and excluded-point indicators
into the kernel.  This is algebraically valid.  Analytically, every jump
created by the ragged support, hard prime-line conditions, or a missing
mask contributes to the two-dimensional boundary or variation.  Such
costs cannot be discarded in a later summation-by-parts argument.
\end{remark}

\subsection{A useful but unproved L2 target}

Let
\[
 \|K\|_{\ell^1(U,V)}
 :=
 \sum_{\substack{u\sim U\\v\sim V}}|K(u,v)|.
\]
A representative L2 input would be a number \(\eta_X=o(1)\) such that
\begin{equation}
 \left|
 \sum_{\substack{u\sim U,\ v\sim V\\(u,v)=1\\(u,v)\ne(b,a)}}
 \mu(u)\mu(v)K_{\mathfrak a,q}(u,v)
 \right|
 \le
 \eta_X\,
 \|K_{\mathfrak a,q}\|_{\ell^1(U,V)}
 \label{eq:unproved-plane-saving}
\end{equation}
in the required uniform physical scope.  No estimate of the form
\eqref{eq:unproved-plane-saving} is proved here.  It is displayed to make
the next arithmetic door falsifiable.
