\section{Existing-theorem boundary}
\label{sec:literature-boundary}

The primitive-plane transform changes the analytic shape of the problem.
It does not solve it.  We record which standard inputs are genuinely
available and which interfaces remain unmatched.

\subsection{Unconditional Mertens cancellation is available only through
the kernel}

The prime number theorem is equivalent to
\begin{equation}
 M(x):=\sum_{n\le x}\mu(n)=o(x).
 \label{eq:mertens-pnt}
\end{equation}
Consequently a sufficiently regular product-like kernel can be treated by
one- or two-dimensional summation by parts.  Formula
\eqref{eq:primitive-plane-transform} makes this possibility visible:
the variable sign is the separable product \(\mu(u)\mu(v)\).

However, \eqref{eq:mertens-pnt} does not control
\[
 \sum_{u,v}\mu(u)\mu(v)K(u,v)
\]
for an arbitrary bounded or sign-correlated kernel.  The literal
\(K_{\mathfrak a,q}\) includes prime-ray solvability, largest-prime
conditions, ragged cofactor ranges, missing masks, and complex weights.
A proof must charge the boundary and variation produced by these
features.  This is the precise reason the Mertens theorem is not silently
inserted into \cref{thm:primitive-plane-transform}.

\subsection{Nearby correlation theorems}

TPC--33 gives a detailed comparison between the physical fixed-determinant
families and existing Chowla--Elliott technology
\citep{WangTPC33}.  The relevant theorem forms include:
\begin{itemize}
 \item Tao's logarithmically averaged two-point theorem for fixed
       nonproportional affine forms \citep{Tao2016LogChowla};
 \item the Matom\"aki--Radziwi\l\l--Tao averaged Chowla theorem, which
       includes an additional averaging parameter
       \citep{MatomakiRadziwillTao2015}; and
 \item the Frantzikinakis--Host mean-zero theorem for fixed independent
       linear forms on a full multidimensional box
       \citep{FrantzikinakisHost2017}.
\end{itemize}
These results are strong precedents, but none is invoked here as a bound
for \eqref{eq:dyadic-primitive-plane-target}.  As stated in the cited
sources, they do not simultaneously supply all of:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item the actual finite, ragged \((u,v)\)-support;
 \item coefficients and ray slopes growing with the physical scale;
 \item the hard two-prime and largest-prime masks inside \(K\);
 \item every complete native block and literal complex weight; and
 \item the uniform row, anchor, and divisor scope needed by the operator
       ledger.
\end{enumerate}
This statement compares the displayed theorem forms with the present
interface; it is not a claim that no future combination or refinement of
those methods can apply.

\subsection{The classical parity boundary}

Brun--Selberg sieves provide the unsigned ray estimate in
\cref{prop:fixed-ray-sieve-boundary}.  They do not distinguish the two
values of \(\mu(u)\mu(v)\).  This is the familiar sign-sensitive boundary
of sieve theory; see the classical parity discussion in
\citep{HeathBrown1982Parity}.  Our coordinate change does not evade that
boundary.  It identifies the exact two-dimensional location at which an
additional input would have to act.

\begin{table}[H]
\centering
\caption{Available inputs and the remaining primitive-plane interface.}
\label{tab:literature-boundary}
\small
\begin{tabular}{@{}>{\raggedright\arraybackslash}p{0.22\textwidth}
>{\raggedright\arraybackslash}p{0.28\textwidth}
>{\raggedright\arraybackslash}p{0.40\textwidth}@{}}
\toprule
Input & What it controls & What remains here \\
\midrule
Prime number theorem
& \(M(x)=o(x)\)
& two-dimensional boundary and variation of the actual ragged kernel \\
Brun--Selberg upper bound
& population on one fixed prime ray
& sign is frozen on that ray; growing-family weighted uniformity \\
Two-point logarithmic Chowla
& fixed affine forms under logarithmic averaging
& physical dyadic kernel, growing slopes, native masks, and operator scope \\
Full-box multiplicative averages
& fixed independent forms on a full box
& determinant-coupled prime-ray kernel on a nonrectangular support \\
\bottomrule
\end{tabular}
\end{table}

\subsection{A precise positive route}

The literature boundary is not purely negative.  It suggests a concrete
test.  Zero-extend \(K_{\mathfrak a,q}\) on each dyadic cofactor box and
prove a two-dimensional Abel identity whose right-hand side contains:
\begin{enumerate}[label=\textup{(\arabic*)},leftmargin=3em]
 \item products of Mertens partial sums;
 \item mixed finite differences of \(K_{\mathfrak a,q}\);
 \item four edge terms and four corner terms; and
 \item explicit jumps created by primitive, prime-line, and missing
       indicators.
\end{enumerate}
If the resulting variation and boundary total is smaller than the
literal \(\ell^1\) mass in the required uniform scope, it yields a genuine
L2 saving.  If the hard masks force variation comparable to the full
mass, this route stops cleanly and the failure is itself a rigorous
boundary result.
