\section{The literal two-key interface}
\label{sec:physical-interface}

We isolate only the information used by the arithmetic reduction.  All
other physical labels remain attached to the coefficients.

\subsection{Rows, times, and four targets}

Fix a scale \(X\), one integer \(h_0\ne0\), and two distinct positive
source rows \(m,n\) satisfying
\begin{equation}
 (mn,h_0)=1.
 \label{eq:primitive-rows}
\end{equation}
The TPC carrier also assigns fixed squarefree row divisors
\[
 d_m\mid m,\qquad d_n\mid n.
\]
Choose two complete native keys.  Their physical times are denoted by
\(j_R\) and \(j_E\), where \(R\) indicates the same-residual key and \(E\)
the unequal-residual, or erasure, key.  Put
\begin{align}
 A_m&=mj_R+h_0=P_mR_m,&
 A_n&=nj_R+h_0=P_nR_n,
 \label{eq:anchor-targets}\\
 B_m&=mj_E+h_0=Q_mS_m,&
 B_n&=nj_E+h_0=Q_nS_n.
 \label{eq:erasure-targets}
\end{align}
Here
\[
 P_m=\Pplus(A_m),\quad P_n=\Pplus(A_n),\quad
 Q_m=\Pplus(B_m),\quad Q_n=\Pplus(B_n)
\]
are the literal largest-prime labels selected by the missing-high
carrier, and \(R_m,R_n,S_m,S_n\) are the corresponding cofactors.

Every active atom considered below lies in the squarefree physical
support.  Thus all four targets and all four residual labels have
nonvanishing M\"obius value:
\begin{equation}
 \mu(A_m),\ \mu(A_n),\ \mu(B_m),\ \mu(B_n),\
 \mu(d_mR_m),\ \mu(d_nR_n),\
 \mu(d_mS_m),\ \mu(d_nS_n)\in\{-1,1\}.
 \label{eq:squarefree-residuals}
\end{equation}
The residual relations defining the two keys are
\begin{align}
 d_mR_m&=d_nR_n,
 \label{eq:same-residual-anchor}\\
 d_mS_m&\ne d_nS_n.
 \label{eq:unequal-residual-erasure}
\end{align}

\begin{remark}[Why primitivity is the correct hypothesis]
\label{rem:primitive-gcd}
For every integer \(j\),
\[
 (m,mj+h_0)=(m,h_0)=1,\qquad
 (n,nj+h_0)=(n,h_0)=1.
\]
Thus each source row is coprime to every cofactor and largest-prime label
on its own side.  This elementary fact is what makes the ray spacings in
\cref{sec:rays-and-signs} exact.  No coprimality assumption between
\(m\) and \(n\) is required.
\end{remark}

\subsection{Complete keys and literal weights}

A complete native key contains the direct side, external block, opposite
row, \(\gamma\)-coordinate, physical time, and every other still
orthogonal output label.  Equality of complete keys fixes the time, but
equality of time alone need not fix the key.  We denote the two complete
keys by \(\iota_R\) and \(\iota_E\).

At a present key-row corner, let \(\beta_{\iota,r}\in\C\) be the literal
nonzero coefficient after every physical mask and profile has been
imposed.  Let \(W_r>0\) be the raw atomic mass of active row \(r\).  The
residual-sign-free rectangle amplitude is
\begin{equation}
 \cA(\iota_E,\iota_R;m,n)
 :=
 \frac{
 \overline{\beta_{\iota_E,m}}\beta_{\iota_E,n}
 \overline{\beta_{\iota_R,n}}\beta_{\iota_R,m}
 }{W_mW_n}.
 \label{eq:literal-rectangle-amplitude}
\end{equation}
It is defined to be zero if any corner is absent.  No sign, phase, or
normalization is averaged in this definition.

TPC--69 proves that the oriented rectangle contribution after the fixed
source-row gauge is
\begin{equation}
 \mu(d_mS_m)\mu(d_nS_n)
 \cA(\iota_E,\iota_R;m,n),
 \label{eq:rectangle-residual-sign}
\end{equation}
and that the full first mixed trace is twice the real part of the sum of
these oriented contributions over actual rectangles
\citep{WangTPC69}.  We shall reindex \eqref{eq:rectangle-residual-sign}
exactly.  Formula \eqref{eq:literal-rectangle-amplitude}, rather than a
time-only surrogate, is retained throughout.

\subsection{The six-item audit}

The specialization used below retains:
\begin{enumerate}[label=\textup{(L1.\arabic*)},leftmargin=4em]
 \item the literal physical coefficients at all four corners;
 \item the one fixed shift \(h_0\) in all four targets;
 \item raw atomic row masses \(W_m,W_n\);
 \item canonical source rows and complete native output keys;
 \item the actual active squarefree support, fixed before any extremizer is
       chosen; and
 \item zero structural exponent cost for all identities, with every future
       estimate still subject to the strict \(1/400\) endpoint ledger.
\end{enumerate}
The reduction does not replace complete keys by times.  It only groups
already existing keys according to arithmetic coordinates recovered from
their atoms.
