\section{Unsigned ray bounds and the sieve boundary}
\label{sec:sieve-boundary}

The affine rays expose two prime forms, so classical upper-bound sieve
technology can count candidate points.  This is useful support control,
but it is sign-blind.

\subsection{Nonproportional prime forms}

On a fixed anchor ray define
\[
 L_{m,R}(z)=P_{m,0}+ma\,z,\qquad
 L_{n,R}(z)=P_{n,0}+nb\,z.
\]
Equation \eqref{eq:anchor-prime-line} gives
\begin{equation}
 nbL_{m,R}(z)-maL_{n,R}(z)=H/t\ne0.
 \label{eq:anchor-form-determinant}
\end{equation}
Hence the forms are nonproportional.  They are primitive because
\((P_{m,0},ma)=(P_{n,0},nb)=1\), a consequence of
\eqref{eq:primitive-rows}.

Likewise, on a fixed erasure ray,
\[
 L_{m,E}(z)=Q_{m,0}+mv\,z,\qquad
 L_{n,E}(z)=Q_{n,0}+nu\,z,
\]
and
\begin{equation}
 nuL_{m,E}(z)-mvL_{n,E}(z)=H/q\ne0.
 \label{eq:erasure-form-determinant}
\end{equation}
These two forms need not be primitive a priori because, for example,
\(Q_{m,0}\) can divide the cross-cofactor \(v\).  If one form is
imprimitive, however, it assumes a positive prime value at most once.
Consequently every erasure ray containing two distinct simultaneous prime
points has two primitive forms; singleton rays are already covered by the
trivial census.

\begin{proposition}[Fixed-ray Brun--Selberg boundary]
\label{prop:fixed-ray-sieve-boundary}
Fix either pair of primitive, nonproportional affine forms above.  If the
pair is admissible, the upper-bound sieve gives, for an interval
\(\cI\subset\Z\) of length \(Z\),
\begin{equation}
 \#\{z\in\cI:L_1(z),L_2(z)\text{ are prime}\}
 \ll_{L_1,L_2}
 1+\frac{Z}{(\log(2+Z))^2}.
 \label{eq:fixed-ray-sieve-bound}
\end{equation}
If the pair has a fixed local obstruction, simultaneous prime values are
confined to \(O_{L_1,L_2}(1)\) exceptional points.
\end{proposition}

\begin{proof}
This is the standard dimension-two upper-bound sieve for a product of
two primitive, nonproportional affine forms; see, for example, the
Selberg sieve treatment in \citep{IwaniecKowalski2004}.  A fixed local
obstruction forces at least one form to equal one of finitely many local
primes at every simultaneous prime point.
\end{proof}

\begin{remark}[Uniformity is not supplied]
\label{rem:sieve-nonuniform}
The constant in \eqref{eq:fixed-ray-sieve-bound} is allowed to depend on
the ray data.  The physical coefficients \(m,n,a,b,u,v\) grow with \(X\),
the ray length can be as short as
\[
 Z\asymp \frac{J_R}{abt}
 \quad\text{or}\quad
 Z\asymp \frac{J_E}{quv},
\]
and the carrier contains additional largest-prime and hard-mask
conditions.  A uniform weighted bound over the complete family is a
separate theorem.
\end{remark}

\subsection{Why an upper-bound sieve does not move the sign}

Even a perfectly uniform version of \eqref{eq:fixed-ray-sieve-bound}
would estimate only the absolute population of one ray.  By
\cref{cor:frozen-ray-sign},
\begin{equation}
\begin{aligned}
 &\sum_{z}
 \mu(a)\mu(b)\mu(u)\mu(v)\,
 \cA_z\\
 &\qquad =
 \mu(a)\mu(b)\mu(u)\mu(v)\sum_z\cA_z.
\end{aligned}
\label{eq:sieve-sign-factor-out}
\end{equation}
If the amplitudes \(\cA_z\) are nonnegative, taking an upper-bound sieve
loses no arithmetic cancellation because none exists inside the fiber.
For complex amplitudes, any gain in \(\sum_z\cA_z\) is a phase theorem,
not a M\"obius theorem.

\begin{corollary}[Unsigned support gain is not parity progress]
\label{cor:unsigned-not-parity}
The divisor counts, ray spacings, and Brun--Selberg upper bounds in this
paper can reduce an unsigned majorant.  None of them proves cancellation
in \eqref{eq:dyadic-primitive-plane-target}; hence none is a fixed-shift
parity-breaking estimate.
\end{corollary}
