\section{Alias folding, local geometry, and fixed-shift localization}
\label{sec:tpc46-alias-localization}

The frozen shift variable has a useful Fourier theory because the
source--mask coefficient does not move with the intercept.  The two
shift families available from the inherited TPC construction have
opposite defects: the completed aliases range over a macroscopic
determinant window but are sampled on a very sparse progression, whereas
genuinely reconstructed local-shift packets can presently be placed in
one ambient geometry only on a much shorter interval.  This section
quantifies both statements and then records the sharp price of
localizing a weighted average back to one prescribed shift.

\subsection{The exact completed-alias fold}

Let \(M_{\rm al}\) and \(\cI_B\) be the inherited completion parameters,
so that
\begin{equation}
 M_{\rm al}=X^{399/400+o(1)},\qquad
 c_k=h_0+kM_{\rm al},\qquad
 K_B:=|\cI_B|=X^{1/400+o(1)}.
 \label{eq:tpc46-alias-scales}
\end{equation}
For a determinant atom
\[
 x=(p,r,m,j)
\]
write
\begin{equation}
 \Delta(x):=pr-mj.
 \label{eq:tpc46-determinant-value}
\end{equation}
The following identity is the exact form of alias folding; it uses no
estimate.

\begin{lemma}[Weighted alias selector]
\label{lem:tpc46-weighted-alias-selector}
For arbitrary weights \((\omega_k)_{k\in\cI_B}\) and any two integer
determinant values \(\Delta,\Delta'\),
\begin{align}
 &\sum_{k\in\cI_B}\omega_k
   \one_{\Delta=c_k}\one_{\Delta'=c_k}
 \notag\\
 &\qquad=
 \one_{\Delta=\Delta'}
 \one_{\Delta\equiv h_0\!\!\pmod {M_{\rm al}}}
 \one_{(\Delta-h_0)/M_{\rm al}\in\cI_B}
 \omega_{(\Delta-h_0)/M_{\rm al}}.
 \label{eq:tpc46-weighted-alias-selector}
\end{align}
Consequently, for every finitely supported coefficient field \(A(x)\),
\begin{align}
 &\sum_{k\in\cI_B}\omega_k
 \left|\sum_{\Delta(x)=c_k}A(x)\right|^2
 \notag\\
 &\quad=
 \sum_{\substack{x,x'\\
                  \Delta(x)=\Delta(x')\\
                  \Delta(x)\equiv h_0\!\!\pmod {M_{\rm al}}\\
                  (\Delta(x)-h_0)/M_{\rm al}\in\cI_B}}
 \omega_{(\Delta(x)-h_0)/M_{\rm al}}
 A(x)\overline{A(x')}.
 \label{eq:tpc46-alias-equal-determinant}
\end{align}
\end{lemma}

\begin{proof}
At most one \(k\) can satisfy \(\Delta=h_0+kM_{\rm al}\).  It contributes to the
left side of \eqref{eq:tpc46-weighted-alias-selector} precisely when the
two determinant values coincide, lie in the required residue class, and
their common quotient belongs to \(\cI_B\).  Expanding the square proves
\eqref{eq:tpc46-alias-equal-determinant}.
\end{proof}

Thus shift averaging does not turn the determinant form into its atomic
diagonal.  It replaces the fixed equation by an equal-determinant
quartic correlation, restricted to one sparse residue class.

There is an equivalent frequency statement.  For a finitely supported
sequence \(F:\Z\to\C\), define
\begin{equation}
 \widehat F(\alpha)=\sum_{c\in\Z}F(c)\e(-c\alpha),
 \qquad \alpha\in\T,
 \label{eq:tpc46-full-shift-transform}
\end{equation}
and sample \(G(k)=F(h_0+kM_{\rm al})\).  Then, for every
\(\beta\in\T\),
\begin{equation}
 \boxed{
 \widehat G(\beta)
 =\frac1{M_{\rm al}}\sum_{a=0}^{M_{\rm al}-1}
 \e\!\left(\frac{h_0(\beta+a)}{M_{\rm al}}\right)
 \widehat F\!\left(\frac{\beta+a}{M_{\rm al}}\right).}
 \label{eq:tpc46-exact-alias-fold}
\end{equation}
Indeed, insertion of \eqref{eq:tpc46-full-shift-transform} into the
right side gives
\[
 \sum_cF(c)\e\!\left(\frac{(h_0-c)\beta}{M_{\rm al}}\right)
 \frac1{M_{\rm al}}\sum_{a=0}^{M_{\rm al}-1}
 \e\!\left(\frac{(h_0-c)a}{M_{\rm al}}\right),
\]
and the inner average selects \(c=h_0+kM_{\rm al}\), leaving
\(\sum_kG(k)\e(-k\beta)\).  Multiplication by a finite alias window
\(\omega_k\) convolves the right side of
\eqref{eq:tpc46-exact-alias-fold} with \(\widehat\omega\).  It does not
unfold the \(M_{\rm al}\) frequency branches.

\begin{remark}[What the inherited alias family represents]
\label{rem:tpc46-alias-not-physical-shifts}
The common coefficient field in the alias family is exactly the one
proved in TPC--42 and TPC--43
\citep{WangTPC42,WangTPC43}.  Formula
\eqref{eq:tpc46-exact-alias-fold} is therefore an unconditional identity
for the completed determinant packet.  It is not the Fourier transform
of a family of prime-pair problems reconstructed at shifts
\(h_0+kM_{\rm al}\).  In particular, the row coprimality and fixed
residue masks
have not been recomputed at those integers.
\end{remark}

\subsection{Common embedding and a collision-free local range}

We now vary the physical shift itself.  Let
\begin{equation}
 \mathfrak H_X\subset\Z\setminus\{0\},\qquad
 H_*:=\max_{\nu\in\mathfrak H_X}|\nu-h_0|,
 \qquad
 \widetilde H_*:=|h_0|+H_*.
 \label{eq:tpc46-local-shift-set}
\end{equation}
Choose ambient geometric row systems
\(\cA_1^*,\cA_2^*\) containing every row in the relevant dyadic source
windows, without imposing shift-dependent coprimality.  The actual
packet at \(\nu\) is embedded by setting a row to zero unless
\((d_\rho,\nu)=1\), and by setting each terminal atom to zero off its
own support.  The same zero extension is made on the opposite-row output
coordinate.  This places all finite packets in a common coordinate
space; it does not make their coefficient values equal.

For \(\rho=(\ell_\rho,d_\rho)\), define the local equality label
\begin{equation}
 u_{\rho,j}^{(\nu)}
 :=d_\rho(\ell_\rho d_\rho j+\nu).
 \label{eq:tpc46-local-label}
\end{equation}
Let \(D_+\) be the largest ambient source divisor and \(J_-\) the
smallest orbit time.

\begin{lemma}[Uniform local-shift label rigidity]
\label{lem:tpc46-local-label-rigidity}
Suppose
\begin{equation}
 \widetilde H_*D_+<J_-.
 \label{eq:tpc46-local-rigidity-condition}
\end{equation}
For every fixed \((\nu,j)\in\mathfrak H_X\times\cJ\), two active rows
in the same source system satisfy
\begin{equation}
 u_{\rho,j}^{(\nu)}=u_{\sigma,j}^{(\nu)}
 \quad\Longrightarrow\quad \rho=\sigma.
 \label{eq:tpc46-local-label-injective}
\end{equation}
At the TPC endpoint, every fixed \(\epsilon>0\) permits
\begin{equation}
 H_*\le
 X^{29629/210000-\epsilon}.
 \label{eq:tpc46-local-shift-exponent}
\end{equation}
\end{lemma}

\begin{proof}
Writing \(\rho=(\ell,d)\) and \(\sigma=(\ell',e)\), equality of the
labels gives
\begin{equation}
 j(\ell d^2-\ell'e^2)=\nu(e-d).
 \label{eq:tpc46-local-collision-equation}
\end{equation}
If the integer in parentheses is nonzero, the left side has magnitude
at least \(j\ge J_-\), whereas the right side has magnitude at most
 \(\widetilde H_*D_+<J_-\).  Hence both sides vanish.  Since
 \(\nu\ne0\), first
\(d=e\), and then \(\ell=\ell'\).

For the exponent, use
\[
 \frac{133}{400}=\frac{69825}{210000},
 \qquad
 \frac{10049}{52500}=\frac{40196}{210000}.
\]
Their difference is \(29629/210000\).  Since \(h_0\) is fixed,
\(\widetilde H_*=H_*+O_{h_0}(1)\); the fixed \(\epsilon\) absorbs this
constant and the endpoint \(o(1)\)-terms.
\end{proof}

Since \eqref{eq:tpc46-local-shift-exponent} is \(o(X)\), common target
endpoints remain \(N_\pm^{\mathfrak H}=X^{1+o(1)}\) after harmless
dyadic enlargement.  A common large-prime band can therefore be defined
from the minimum and maximum over the entire local family.  The label
rigidity lemma also shows that zero extension itself creates no
same-coordinate collision.  It does not control the dependence of the
coefficient field on \(\nu\).

The support-only cofactor bound acquires an explicit dependence on the
window.  Suppose a touched target has \(n=pr\), residual label \(s=dr\),
and cofactor \(r\asymp R_0\).  For fixed \((\nu,j,s)\) and \(d\mid s\),
the source rows solve
\begin{equation}
 rp-dj\ell=\nu.
 \label{eq:tpc46-local-determinant-ladder}
\end{equation}
Putting \(g=(r,dj)\), one has \(g\mid\nu\).  The source-prime step in
the integral ladder is \(r/g\), so a source window of length \(O(L_0)\)
contains
\[
 O\!\left(1+\frac{gL_0}{r}\right)
 \le O\!\left(1+\frac{\widetilde H_*L_0}{R_0}\right)
\]
parameters.  Summation over \(d\mid s\) proves the uniform bound
\[
 \rho_{R_0,\mathfrak H}
 :=
 \max_{\substack{\nu\in\mathfrak H_X,\ j\in\cJ,\ s}}
 \#\left\{(d,\ell,p,r):
 \begin{array}{c}
 r\asymp R_0,\ dr=s,\\
 rp-dj\ell=\nu,\ \text{all packet supports hold}
 \end{array}\right\}
\]
\vspace{-4pt}
\begin{equation}
 \boxed{
 \rho_{R_0,\mathfrak H}
 \ll \tau(s)\left(1+\frac{\widetilde H_*L_0}{R_0}\right).}
 \label{eq:tpc46-local-fiber-bound}
\end{equation}
At the balanced scale \(R_0\asymp L_0\), the presently available
support-only bound therefore carries a polynomial factor for a
polynomial local window.  TPC--36 contains a
stronger primitivity statement at an earlier ultra-divisor interface,
but the terminal equality interface imported through TPC--43--TPC--45
does not state its preservation.  We consequently retain
\eqref{eq:tpc46-local-fiber-bound}; setting \(g=1\) would require a new
provenance lemma.

There is a second uniformity issue.  For each fixed \(\nu\), let
\(\mathfrak M_B(\nu;X)\) denote the least weighted projective mass in
the analogue of
\eqref{eq:tpc46-global-row-output-separation}.  The inherited statement
is only
\begin{equation}
 \mathfrak M_B(\nu;X)\ll_{B,\nu}X^{o(1)}
 \qquad\text{for every fixed \(\nu\)}.
 \label{eq:tpc46-fixed-shift-projective-only}
\end{equation}
It does not imply
\begin{equation}
 \sup_{\nu\in\mathfrak H_X}\mathfrak M_B(\nu;X)=X^{o(1)}
 \label{eq:tpc46-missing-uniform-projective}
\end{equation}
when \(\mathfrak H_X\) grows with \(X\).  The period
\(|\nu|\) of the fixed residue factor, the eligible rows, and the
source residue data all move with \(\nu\).  For a coherent weighted
average, the corresponding sufficient condition is
\[
 \sum_{\nu\in\mathfrak H_X}
 |\omega_\nu|\mathfrak M_B(\nu;X)=X^{o(1)}.
\]
Neither growing-family statement follows from TPC--36.  A fixed finite
set of physical shifts is harmless, but it supplies no mesoscopic shift
average.

\subsection{Why the proved collision-free range misses the Poisson scale}

The frozen determinant family has a clean shift transform.  For one
scalar product-ready layer, put
\begin{equation}
 F(c)=
 \sum_{p,r,m,j}
 a(p)b(r)c_0(m)w(j/J)
 \one_{pr-mj=c}.
 \label{eq:tpc46-frozen-shift-sequence}
\end{equation}
Its full shift Fourier transform contains the exact orbit kernel
\begin{align}
 \sum_{j\in\Z}w(j/J)\e(mj\alpha)
 &=J\sum_{k\in\Z}\widehat w\bigl(J(k-m\alpha)\bigr)
 \notag\\
 &=:K_m(\alpha).
 \label{eq:tpc46-Poisson-kernel}
\end{align}
Suppose, for clarity, that \(\widehat w\) is supported in a fixed
interval.  Since \(m\asymp Q\) and \(mJ\asymp X\), the zero Poisson
packet has width \(X^{-1+o(1)}\), while the first nonzero sampling
centers lie at distance \(Q^{-1+o(1)}\).  Thus the geometric gap is
\begin{equation}
 X^{-1+o(1)}
 <\|\alpha\|_{\T}<
 X^{-267/400+o(1)}.
 \label{eq:tpc46-Poisson-gap-scales}
\end{equation}

To see the required shift length concretely, take a standard modulated
weight
\begin{equation}
 W_{\mathsf H,\alpha_0}(c)
 =V\!\left(\frac{c-c_0}{\mathsf H}\right)\e(\alpha_0c).
 \label{eq:tpc46-modulated-shift-weight}
\end{equation}
Its Fourier multiplier has width \(\asymp\mathsf H^{-1}\) around
\(\alpha_0\).  Placing a fixed-shape multiplier inside the gap near its
coarse \(Q^{-1}\)-end requires
\begin{equation}
 \mathsf H\gg Q=X^{267/400+o(1)}.
 \label{eq:tpc46-Poisson-required-window}
\end{equation}
In contrast, the presently proved collision-free local-label range
reaches only
\[
 H_*\le X^{29629/210000-\epsilon}.
\]
The exponent deficit to the first Poisson scale is
\begin{equation}
 \frac{267}{400}-\frac{29629}{210000}
 =\frac{110546}{210000}
 =\frac{55273}{105000}>0.
 \label{eq:tpc46-Poisson-local-deficit}
\end{equation}
Hence the dense actual local family, under this rigidity argument, does
not reach the scale on which the first sampling aliases can be
spectrally resolved by this route.
The completed-alias family spans a determinant interval of order \(X\),
but its spacing is \(M_{\rm al}=X^{399/400+o(1)}\); the exact fold
\eqref{eq:tpc46-exact-alias-fold} shows why macroscopic span does not
replace dense sampling.  The frozen completed family is the only one of
the three current objects that simultaneously permits dense shifts on
the Poisson scale and retains one coefficient field, and it is not a
family of actual reconstructed TPC packets.

\subsection{Weighted grouping and the sharp localization price}

Shift averaging also does not improve the support norm merely by
renormalizing numerator and diagonal with the same weights.
\Cref{thm:tpc46-weighted-grouping-norm} proves that the exact grouping
norm remains the largest realized fiber: the common weight cancels on
each block.  An analytic averaged estimate may of course beat this
support norm by using coefficient cancellation.  A separate loss
appears when that average is localized back to one prescribed shift.

\begin{lemma}[Sharp weighted localization cost]
\label{lem:tpc46-weighted-localization}
Let \(E_\nu\ge0\), let \(\omega_\nu\ge0\), and suppose
\(\omega_{\nu_0}>0\).  Define
\begin{equation}
 \operatorname{Av}_\omega E
 :=\frac{\sum_\nu\omega_\nu E_\nu}
         {\sum_\nu\omega_\nu}.
 \label{eq:tpc46-weighted-average}
\end{equation}
Then
\begin{equation}
 \boxed{
 E_{\nu_0}
 \le
 \mathcal L_\omega(\nu_0)\operatorname{Av}_\omega E,
 \qquad
 \mathcal L_\omega(\nu_0)
 :=\frac{\sum_\nu\omega_\nu}{\omega_{\nu_0}}.}
 \label{eq:tpc46-localization-cost}
\end{equation}
The constant is sharp for arbitrary nonnegative data.
\end{lemma}

\begin{proof}
The term \(\omega_{\nu_0}E_{\nu_0}\) is bounded by the full weighted
sum, which proves the inequality.  Equality holds when every
\(E_\nu\) except \(E_{\nu_0}\) is zero.
\end{proof}

For \(K\) essentially equal weights,
\(\mathcal L_\omega(\nu_0)\asymp K\), independently of whether the
weights are normalized to have total mass one.  In particular, a
fixed-shape nonnegative smooth weight spread across \(K_B\) inherited
aliases, with central value bounded below, has
\begin{equation}
 \mathcal L_\omega(0)=X^{1/400+o(1)}
 \label{eq:tpc46-alias-localization-loss}
\end{equation}
when its central value is bounded below.  This is precisely the size of
the TPC endpoint allowance \(K_B\).  Therefore an alias-averaged
mean-square theorem at its averaged atomic scale does not, by positivity
alone, yield the physical \(k=0\) bound at the same scale.

\begin{remark}[Claim boundary]
\label{rem:tpc46-alias-localization-boundary}
The identities above prove four different facts: exact folding of the
completed aliases, a collision-free label range inside the common
zero-extended geometry, a strict mismatch between that rigidity range
and the Poisson resolution scale, and the sharp positivity cost of returning
from an average to one shift.  They do not show that localization is
impossible.  A maximal theorem, shift regularity, an amplifier, or a
coefficient-specific comparison between neighboring shifts could
reduce the loss.  None is supplied by TPC--36, TPC--42, TPC--43, or
TPC--45.  Accordingly, no averaged or frozen-family result in this
paper is asserted to close the physical fixed-shift TPC estimate, break
the parity barrier, or imply the twin-prime conjecture.
\end{remark}
