\section{Sharp atomic-normalization boundaries}
\label{sec:tpc46-atomic-boundaries}

This section shows why the valid tensor estimates in
\cref{sec:tpc46-tensor-closure,sec:tpc46-bohr} cannot be substituted for
the physical Bessel estimate.

\subsection{Averaging all shifts can retain a polynomial loss}

Take nonnegative unit coefficients on dyadic boxes and let
\begin{equation}
 N_h:=\#\{(p,r,m,j):pr-mj=h\}.
 \label{eq:tpc46-flat-count}
\end{equation}
Then \(\cT_h=N_h=\Delta_h\).  Suppose all differences occupy an
interval of \(O(X)\) integers.  If
\begin{equation}
 K_1:=\#(\cP\times\cR),
 \qquad
 K_2:=\#(\cM\times\cJ),
 \label{eq:tpc46-flat-cardinalities}
\end{equation}
then \(\sum_hN_h=K_1K_2\), and Cauchy--Schwarz gives
\begin{equation}
 \sum_h|\cT_h|^2
 =\sum_hN_h^2
 \gg\frac{(K_1K_2)^2}{X}.
 \label{eq:tpc46-global-flat-energy}
\end{equation}
Since \(\sum_h\Delta_h=K_1K_2\),
\begin{equation}
 \frac{\sum_h|\cT_h|^2}{\sum_h\Delta_h}
 \gg\frac{K_1K_2}{X}.
 \label{eq:tpc46-global-flat-ratio}
\end{equation}
At the endpoint, a prime \(p\)-box and three integer boxes have
\begin{equation}
 K_1=X^{1+o(1)}/\log X,
 \qquad
 K_2=X^{1+o(1)},
 \label{eq:tpc46-flat-endpoint-counts}
\end{equation}
so the ratio in \eqref{eq:tpc46-global-flat-ratio} is
\begin{equation}
 \gg X^{1-o(1)}.
 \label{eq:tpc46-flat-X-loss}
\end{equation}
Partitioning the difference range into intervals of any prescribed
length \(1\le H\ll X\) shows that at least one nonempty \(H\)-window
has ratio at least the global ratio.  Therefore no theorem for all
coefficient boxes and all shift windows can replace tensor energy by
the averaged atomic diagonal at subpolynomial cost.

\subsection{A prescribed-shift obstruction for arbitrary slots}

The following construction keeps the prime condition but is not
asserted to satisfy the actual TPC source factorization or M\"obius
weights.

\begin{proposition}[Fixed-shift coherent box]
\label{prop:tpc46-fixed-shift-box}
Fix \(h\ne0\).  Let \(p\asymp P\) range over primes, choose
\(j_0\in\N\) with \(j_0\asymp J\) and \(2J<P\), and let
\(R\ge J\) be an integer.  Work at a scale for which \(pR>|h|\) for
every selected prime, and choose the boxes so that
\(j_0<\min p\) over those primes.  For every
such \(p\), choose the unique
\begin{equation}
 r_p\in[R,R+j_0)
 \quad\text{with}\quad
 pr_p\equiv h\pmod{j_0},
 \label{eq:tpc46-rp-choice}
\end{equation}
and put
\begin{equation}
 m_p:=\frac{pr_p-h}{j_0}.
 \label{eq:tpc46-mp-choice}
\end{equation}
Let \(a,b,c\) be the indicators of the resulting \(p,r_p,m_p\) sets,
and let \(0\le\eta_j\le1\) with \(\eta_{j_0}=1\).  Then
\begin{equation}
 \frac{|\cT_h|^2}{\Delta_h}
 \ge \#\{p\asymp P:p\text{ prime}\}
 =P^{1-o(1)}.
 \label{eq:tpc46-fixed-shift-obstruction}
\end{equation}
\end{proposition}

\begin{proof}
Since \(p>j_0\), the prime \(p\) is invertible modulo \(j_0\), so
\eqref{eq:tpc46-rp-choice} has exactly one representative in the
declared half-open interval.  Every selected prime supplies the
solution
\(
 pr_p-m_pj_0=h
\).
The scale hypothesis gives \(m_p>0\).
All terms are nonnegative.  Since every coefficient has modulus at most
one, \(\Delta_h\le\cT_h\), while \(\cT_h\) is at least the number of
selected primes.  Hence
\(
 |\cT_h|^2/\Delta_h\ge\cT_h
\), proving the claim.
\end{proof}

At the TPC lengths
\(
 P=M=X^{267/400+o(1)}
\)
and
\(
 R=J=X^{133/400+o(1)}
\), this abstract obstruction has exponent \(267/400\), whereas the
endpoint budget is \(1/400\).  The gap is
\begin{equation}
 \frac{267}{400}-\frac1{400}
 =\frac{133}{200}.
 \label{eq:tpc46-fixed-box-gap}
\end{equation}
The construction rules out an arbitrary-three-slot black box at atomic
normalization.  It does not say that the actual TPC mask realizes the
coherent coefficients.

\subsection{Weighted shift averaging and exact grouping norms}

Let \(E\) be a finite atom set with maps
\(
 h:E\to\Z
\)
and
\(
 s:E\to S
\).
For nonnegative weights \(\omega_h\), define
\begin{equation}
 \|Gx\|_\omega^2
 :=\sum_{h_0,s_0}\omega_{h_0}
 \left|\sum_{\substack{e:h(e)=h_0\\s(e)=s_0}}x_e\right|^2,
 \qquad
 \|x\|_{\omega,E}^2
 :=\sum_e\omega_{h(e)}|x_e|^2.
 \label{eq:tpc46-weighted-grouping}
\end{equation}

\begin{theorem}[Averaging-invariant grouping norm]
\label{thm:tpc46-weighted-grouping-norm}
After discarding zero-weight fibers,
\begin{equation}
 \boxed{
 \sup_{x\ne0}\frac{\|Gx\|_\omega^2}{\|x\|_{\omega,E}^2}
 =\max_{\substack{h_0,s_0\\\omega_{h_0}>0}}
 \#\{e:h(e)=h_0,\ s(e)=s_0\}.}
 \label{eq:tpc46-weighted-grouping-norm}
\end{equation}
\end{theorem}

\begin{proof}
Fiberwise Cauchy--Schwarz gives the upper bound.  On a largest
positive-weight fiber, take \(x\) constant and nonzero and set it to
zero elsewhere.  The weight cancels from the quotient and equality is
attained.
\end{proof}

Thus dividing both numerator and atomic diagonal by the number of
shifts does not lower the exact support-only loss.  At the first
unbalanced TPC block \(R=J\), the available ambient fiber bound from
TPC--45 is
\begin{equation}
 1+\frac{L_0}{J}
 =X^{15077/105000+o(1)}.
 \label{eq:tpc46-unbalanced-ambient-frontier}
\end{equation}
It exceeds \(X^{1/400}\) by exponent
\begin{equation}
 \frac{15077}{105000}-\frac1{400}
 =\frac{29629}{210000}.
 \label{eq:tpc46-unbalanced-budget-deficit}
\end{equation}
The actual squared norm is the realized maximum fiber size, which can
be smaller than this ambient upper bound.  The theorem says only that
shift weights alone do not reduce that realized norm.
