\section{Exact certificate and claim ledger}
\label{sec:tpc46-certificate}

The reproducibility directory contains
\begin{center}
 \path{experiments/tpc46_certificate.py}.
\end{center}
It uses only the Python standard library.  Integer and Gaussian-integer
arithmetic is exact; rational exponent comparisons use
\texttt{fractions.Fraction}; and all pseudo-random trials use the fixed
seed \(4601\).  A successful run writes
\path{experiments/tpc46_certificate.json}.

The current certificate performs \(122232\) exact checks.  Its canonical
payload hash is
\begin{center}
\texttt{38287f0cbee8060ebfb73407f6a4cd0255490e64effefea4481ee67ec1adb4ea}.
\end{center}
The hash covers the canonical JSON report before the hash field is
appended.  The certificate checks:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item exact equality between the four-variable determinant synthesis
 and the additive correlation of the two product sequences, on \(640\)
 deterministic Gaussian-integer trials;
 \item exact disintegration of Cartesian tensor energy into the atomic
 diagonals over all shifts, together with the multiplicity-based scalar
 tensor bound;
 \item injectivity of the large-prime product map on a finite supported
 model;
 \item the residual collision identity and a finite Walsh
 scalarization of the squarefree physical labels \(s=d(m)r\);
 \item the exact weighted grouping norm and its maximizing fiber;
 \item the prescribed-shift coherent prime construction;
 \item exact finite-field DFT analogues of the orbit
 spectral-support theorem and alias-frequency folding, together with
 the sharp localization spike; and
 \item the principal rational endpoint, budget, coordinate, and scale
 differences listed in the generated report.
\end{enumerate}

The finite Walsh check uses squarefree residual labels, as at the
nonzero physical equality atoms; the analytic Bohr-torus theorem for
general integer labels is proved separately in the text.  The finite
cyclic spectral checks are algebraic finite-field DFT analogues; they
do not certify the continuous Poisson theorem.  Likewise, finite
large-prime injectivity does not certify an asymptotic prime-counting
statement.  Those facts are proved in the text from their explicit
hypotheses.  The certificate does not test M\"obius cancellation,
Fourier decay of the actual dual output, a growing-shift projective
decomposition, an anti-alias estimate, or a prime-pair asymptotic.

For clarity, the logical status of the main conclusions is as follows.
\begin{enumerate}[label=\textup{\arabic*.},leftmargin=2.2em]
 \item The physical large-prime determinant expansion and the exact
 pulled-back dual field in \cref{sec:tpc46-interface} are conditional
 only on the cited TPC coefficient packet and its declared dyadic
 support.  No new cancellation hypothesis is inserted.
 \item The scalar tensor closure, residual Fourier--Bohr closure,
 shift-kernel factorization, spectral gap, Poisson identities, grouping
 norm, alias fold, and localization inequality are unconditional
 theorems for the finite or smooth models stated in their hypotheses.
 \item The band-limited exact gap applies to a frozen packet whose
 Hilbert coefficient is independent of \(j\), or to a separately
 declared band-limited extension.  A fixed residue-class restriction
 preserves the endpoint exponents under the hypotheses of
 \cref{cor:tpc46-progression-shift-gap}.  For ordinary compactly supported
 smooth profiles, the conclusion is rapid decay on a shrunken band,
 not exact vanishing.
 \item The tensor bound is normalized by
 \(\cD_\otimes=\sum_h\Delta_h\).  It is not a bound at the physical
 atomic scale \(\Delta_{h_0}\).  The counterexamples concern arbitrary
 separated slots and do not assert that the actual TPC source/mask
 realizes their coherent phases.
 \item The completed alias bank is a common-coefficient auxiliary
 family, not a collection of reconstructed prime-pair problems at the
 sampled integers.  The local physical family always has a
 zero-extended common ambient coordinate space; only its
 collision-free label range is restricted by the displayed rigidity
 argument.  The inherited projective theorem is not asserted uniformly
 for a growing set of shifts.
 \item The external literature audit shows that the cited formulations
 do not directly supply the current coefficient and normalization
 interface.  This is not an impossibility theorem for every future
 analytic method.
 \item The doors in \cref{sec:tpc46-next-gate} are proposed next
 inputs.  None is assumed or proved here.
 \item No statement implies fixed-shift TPC closure, Chowla at a fixed
 shift, the Hardy--Littlewood prime-pair conjecture, a breach of the
 parity barrier, or the twin-prime conjecture.
\end{enumerate}

The positive advance is therefore exact but model-specific: the smooth
orbit slot creates a real mesoscopic gap in the completed shift
spectrum, while the tensor and Bohr calculations identify precisely
which energy they control.  The remaining physical transfer gaps are
displayed rather than promoted to hidden hypotheses.
