\section{A completed determinant model}
\label{sec:tpc46-model}

The analytic statements are most transparent for a completed family in
which the determinant value ranges over every integer.  This section
defines that family before any TPC specialization.

Let
\(
 \cP,\cR,\cM,\cJ\subset\N
\)
be finite sets.  The letter \(p\) is only an index in the abstract
model; primality will be imposed in the TPC application.  For
coefficient sequences \(a,b,c,\eta\), define
\begin{equation}
 \cT_h(a,b,c,\eta)
 :=\sum_{\substack{p\in\cP,r\in\cR,m\in\cM,j\in\cJ\\
                    pr-mj=h}}
 a_p b_r c_m\eta_j,
 \qquad h\in\Z.
 \label{eq:tpc46-scalar-packet}
\end{equation}
The corresponding Cartesian tensor energy and fixed-shift atomic
diagonal are
\begin{align}
 \cD_\otimes
 &:=
 \left(\sum_{p,r}|a_pb_r|^2\right)
 \left(\sum_{m,j}|c_m\eta_j|^2\right),
 \label{eq:tpc46-tensor-energy}\\
 \Delta_h
 &:=
 \sum_{pr-mj=h}|a_pb_rc_m\eta_j|^2.
 \label{eq:tpc46-atomic-diagonal}
\end{align}
Every Cartesian tuple has one and only one determinant value, and hence
\begin{equation}
 \boxed{\sum_{h\in\Z}\Delta_h=\cD_\otimes.}
 \label{eq:tpc46-diagonal-disintegration}
\end{equation}
This elementary identity is the normalization divide on which several
later conclusions turn.

For Hilbert-valued spectral statements it is useful to allow an
arbitrary coefficient on the three arithmetic variables.  Let
\(\Hh\) be a complex Hilbert space, let
\(z_{p,r,m}\in\C\), and let
\(v_{p,r,m}\in\Hh\).  For a profile \(w\) on \(\R\), put
\begin{equation}
 F_h
 :=\sum_{p,r,m}\sum_{j\in\Z}
 z_{p,r,m}w(j/J)v_{p,r,m}
 \one_{pr-mj=h}.
 \label{eq:tpc46-Hilbert-packet}
\end{equation}
The arithmetic supports in \(p,r,m\) remain finite, while the Schwartz
or compactly supported profile makes the \(j\)-sum absolutely
convergent.  The essential hypothesis in
\eqref{eq:tpc46-Hilbert-packet} is that the Hilbert vector is independent
of \(j\).  An arbitrary vector \(v_{p,r,m,j}\) can encode a different
orthogonal output at every orbit time and need not have any orbit
spectral gap.

When a multiplicative residual label is retained, fix a map
\begin{equation}
 d:\cM\longrightarrow\N
 \label{eq:tpc46-d-map}
\end{equation}
and define
\begin{equation}
 F(h,s)
 :=\sum_{\substack{pr-mj=h\\d(m)r=s}}
 a_pb_rc_m\eta_j.
 \label{eq:tpc46-residual-packet}
\end{equation}
At the physical TPC equality alias, \(d(m)\) is the source divisor in
the unique row \(m=\ell d(m)\), and coprimality gives the residual label
\(s=d(m)r\).  For nonzero completed aliases, the squarefree kernel may
replace this literal product; that distinction is treated in
\cref{sec:tpc46-alias-localization}.

Finally define the product-fiber multiplicities
\begin{align}
 \rho_{\cP,\cR}
 &:=
 \max_n\#\{(p,r)\in\cP\times\cR:pr=n\},
 \label{eq:tpc46-rho-pr}\\
 \rho_{\cM,\cJ}
 &:=
 \max_n\#\{(m,j)\in\cM\times\cJ:mj=n\}.
 \label{eq:tpc46-rho-mj}
\end{align}
For polynomially bounded integer supports,
\begin{equation}
 \rho_{\cM,\cJ}
 \le\max_{n\le X^{O(1)}}\tau(n)=X^{o(1)}.
 \label{eq:tpc46-divisor-multiplicity}
\end{equation}

At the optimized TPC endpoint the four principal lengths are
\begin{equation}
 P R=X^{1+o(1)},
 \qquad
 M=X^{267/400+o(1)},
 \qquad
 J=X^{133/400+o(1)},
 \qquad
 MJ=X^{1+o(1)}.
 \label{eq:tpc46-endpoint-boxes}
\end{equation}
The notation \(M\) in
\eqref{eq:tpc46-endpoint-boxes} is the source-variable length.  The
triple-prime alias modulus will always be written
\(M_{\rm al}\) to prevent a collision of notation.
