\section{The external analytic boundary}
\label{sec:tpc46-literature-boundary}

The deterministic reductions in this paper should not be conflated with an
available Kloosterman--fraction theorem.  The distinction is already visible
at the scalar level and becomes sharper after the physical Hilbert output is
restored.  We record the coefficient slots, the role of shift averaging, and
the normalization supplied by the relevant primary sources.

\subsection{Three Kloosterman sequences are not three determinant slots}
\label{subsec:tpc46-bc-slots}

Let \(\cA=[A/2,A]\), \(\cM=[M/2,M]\), and
\(\mathcal N=[N/2,N]\).  Bettin and Chandee's trilinear form is
\begin{equation}
 \cB(M,N,A)
 :=
 \sum_{\substack{a\in\cA,\ m\in\cM,\ n\in\mathcal N\\(m,n)=1}}
 \nu_a\alpha_m\beta_n
 \e\!\left(\vartheta\frac{a\overline m}{n}\right),
 \qquad \vartheta\ne0,
 \label{eq:tpc46-bc-form}
\end{equation}
where \(\overline m\) is the inverse of \(m\) modulo \(n\).  Their
Theorem~1 gives, for arbitrary complex sequences
\(\alpha,\beta,\nu\),
\begin{align}
 |\cB(M,N,A)|
 \ll {}&
 \|\alpha\|_2\|\beta\|_2\|\nu\|_2
 \left(1+\frac{|\vartheta|A}{MN}\right)^{1/2}
 \notag\\[-2pt]
 &\quad\times
 \left\{
 (AMN)^{7/20+\varepsilon}(M+N)^{1/4}
 +(AMN)^{3/8+\varepsilon}(AN+AM)^{1/8}
 \right\}.
 \label{eq:tpc46-bc-theorem}
\end{align}
Thus \eqref{eq:tpc46-bc-form} has three arbitrary sequences, but one
of them is a sequence in the \emph{Kloosterman numerator} \(a\).  This
is not the same assertion as allowing three arbitrary weights on
variables in a determinant equation \citep[Theorem~1]{BC2018}.

The distinction is explicit in the fixed-determinant consequence of the
same paper.  For
\begin{equation}
 \mathcal T_\Delta
 :=
 \sum_{\substack{m_i\in[M_i/2,M_i],\ n_i\in[N_i/2,N_i]\\
                   m_1n_2-m_2n_1=\Delta}}
 f(m_1)g(m_2)\alpha_{n_1}\beta_{n_2},
 \qquad \Delta\ne0,
 \label{eq:tpc46-bc-determinant}
\end{equation}
Corollary~1 assumes
\begin{equation}
 f^{(j)}\ll \eta^jM_1^{-j},
 \qquad
 g^{(j)}\ll \eta^jM_2^{-j}
 \qquad (j\ge0),
 \label{eq:tpc46-bc-smooth-slots}
\end{equation}
and places arbitrary sequences only on \(n_1,n_2\).  With
\begin{equation}
 R_*=\frac{M_1N_2}{M_2N_1}+\frac{M_2N_1}{M_1N_2},
 \label{eq:tpc46-bc-rstar}
\end{equation}
the conclusion is
\begin{align}
 \mathcal T_\Delta
 ={}&
 \sum_{\substack{n_i\in[N_i/2,N_i]\\(n_1,n_2)\mid\Delta}}
 \frac{(n_1,n_2)}{n_1n_2}\alpha_{n_1}\beta_{n_2}
 \int_{\R}
 f\!\left(\frac{x+\Delta}{n_2}\right)
 g\!\left(\frac{x}{n_1}\right)\,dx
 \notag\\
 &+O\!\left(
 (\eta R_*)^{3/2}\|\alpha\|_2\|\beta\|_2
 (N_1N_2)^{7/20}(N_1+N_2)^{1/4+\varepsilon}
 (M_1M_2)^\varepsilon
 \right).
 \label{eq:tpc46-bc-corollary}
\end{align}
Both smooth slots in \eqref{eq:tpc46-bc-smooth-slots} are part of the
hypothesis; they are not cosmetic remnants of the proof
\citep[Corollary~1]{BC2018}.

For the TPC equation
\begin{equation}
 pr-mj=h,
 \label{eq:tpc46-tpc-determinant-literature}
\end{equation}
one favorable identification is
\begin{equation}
 (m_1,n_2,m_2,n_1)=(p,r,j,m).
 \label{eq:tpc46-bc-slot-identification}
\end{equation}
It places the cofactor and source weights in the two arbitrary slots and
the orbit weight in one smooth slot, but it places the prime weight in
the other smooth slot.  Interchanging \(p\) and \(r\) merely replaces
the missing prime slot by a missing M\"obius slot.  Other identifications
put the nonsmooth source coefficient in a smooth slot.  Since one factor
from \(pr\) and one factor from \(mj\) must occupy the two smooth
positions, and only the envelope in \(j\) is intrinsically smooth,
every identification loses at least one of the three arithmetic
weights \(p,r,m\).  The actual fixed residue selector in \(j\), retained
in \cref{eq:tpc46-three-coefficient-layer}, only makes direct
applicability more restrictive.  This is
the exact coefficient-slot obstruction isolated geometrically in
TPC--45 \citep{WangTPC45}.

\subsection{What determinant-shift averaging actually buys}
\label{subsec:tpc46-bcr-averaging}

There is a genuine use of determinant-shift averaging in the work of
Bettin, Chandee, and Radziwi\l\l.  After their smooth decomposition and
Poisson summation, a relevant off-diagonal block contains, schematically,
\begin{equation}
 \sum_{n_1,n_2}
 \sum_{0<|\Delta|\le D/d}
 \sum_{0<k<H_d}
 a_{dn_1}\overline{a_{dn_2}}
 \e\!\left(-k\Delta\frac{\overline{n_1}}{n_2}\right)
 \cW_{k,\Delta,n_1,n_2},
 \label{eq:tpc46-bcr-offdiagonal}
\end{equation}
where \(\cW\) is supplied by the already smooth variables.  They set
\begin{equation}
 b=k\Delta,
 \qquad
 \nu_{x,y}(b)
 :=\sum_{k\Delta=b}
 \e\!\left(-kx+\frac{\Delta y}{2\pi}\right).
 \label{eq:tpc46-bcr-product-compression}
\end{equation}
Consequently
\begin{equation}
 |\nu_{x,y}(b)|\le \tau(|b|),
 \qquad
 \|\nu_{x,y}\|_2\ll B^{1/2+\varepsilon}
 \quad (|b|\ll B),
 \label{eq:tpc46-bcr-nu-norm}
\end{equation}
and the pair \((k,\Delta)\) becomes the single numerator sequence in
\eqref{eq:tpc46-bc-form}.  Bettin--Chandee cancellation is then
available in that numerator range \citep[Section~5, especially the
reduction preceding their small-frequency estimate]{BCR2017}.

This mechanism says exactly what the average provides: it lengthens and
structures the Kloosterman-numerator sequence.  It is available only
after Poisson summation has used smooth determinant variables.  It does
not replace either smooth hypothesis in
\eqref{eq:tpc46-bc-smooth-slots}, and it does not turn
\eqref{eq:tpc46-bc-corollary} into a determinant theorem with arbitrary
weights on \(p,r,m\).  An arbitrary external weight on \(\Delta\) can
also increase the multiplicative energy of the compressed sequence in
\eqref{eq:tpc46-bcr-product-compression}; its \(\ell^2\) norm must be
proved rather than silently identified with the product of two norms.

\subsection{Nearby dispersion estimates}
\label{subsec:tpc46-nearby-dispersion}

Fouvry and Radziwi\l\l{} study a different average.  For divisor-bounded
sequences \(\alpha_m,\beta_n\), they average the congruence discrepancy
\begin{equation}
 \sum_{q\asymp Q}
 \left|
 \sum_{mn\equiv a\, (\bmod q)}\alpha_m\beta_n
 -\frac1{\varphi(q)}
 \sum_{(mn,q)=1}\alpha_m\beta_n
 \right|
 \label{eq:tpc46-fr-discrepancy}
\end{equation}
over the modulus \(q\), while the residue \(a\ne0\) is fixed.  Their
first range, under the stated Siegel--Walfisz hypothesis on the short
sequence, is
\begin{equation}
 \exp((\log X)^\varepsilon)
 \le N
 \le Q^{-11/12}X^{17/36-\varepsilon}.
 \label{eq:tpc46-fr-range}
\end{equation}
Their prime-modulus variant removes that Siegel--Walfisz input in the
same power range \citep[Corollary~1.1 and Theorem~1.2]{FR2022}.
Wright's partially fixed-modulus theorem estimates
\begin{equation}
 \sum_{\substack{a\asymp A,\ m\asymp M,\ n\asymp N\\(m,nR)=1}}
 \nu_a\alpha_m\beta_n
 \e\!\left(\vartheta\frac{a\overline m}{nR}\right)
 \label{eq:tpc46-wright-form}
\end{equation}
and improves the resulting unbalanced-convolution ranges, including
\(N\le Q^{-33/28}X^{17/28-\varepsilon}\) in the first regime
\citep[Theorem~2.1 and Corollary~2.2]{Wright2026}.  These are genuine
advances for modulus dispersion and fixed denominator factors.  Neither
theorem averages the physical determinant shift in
\eqref{eq:tpc46-tpc-determinant-literature}, supplies the missing
determinant coefficient slot, or controls the inherited TPC masks after
successive physical restrictions.

\subsection{Why a scalar black box would still not prove the atomic estimate}
\label{subsec:tpc46-vector-boundary}

The external results above are scalar.  The TPC target inherited from
the projective and residual-fiber reductions is an atomic-energy
estimate for a Hilbert-valued synthesis, not merely a scalar count
\citep{WangTPC36,WangTPC42,WangTPC43,WangTPC45}.  Formally one may
write
\begin{equation}
 \left\|\sum_e x_e\right\|_{\Hh}
 =\sup_{\|v\|_{\Hh}=1}
 \left|\sum_e\langle x_e,v\rangle_{\Hh}\right|.
 \label{eq:tpc46-dual-scalarization}
\end{equation}
But the scalar coefficient \(\langle x_{p,r,m,j},v\rangle\) produced
by \eqref{eq:tpc46-dual-scalarization} generally couples all four
indices.  It need not factor into the separate sequences required by
\eqref{eq:tpc46-bc-form} or \eqref{eq:tpc46-bc-determinant}.  Uniformity
of \eqref{eq:tpc46-bc-theorem} over each of its three sequences does not
imply uniformity over such an entangled four-index tensor.

There is a second normalization mismatch.  Squaring a scalar estimate
and summing over ambient coordinates naturally returns a Cartesian
tensor energy, or after shift averaging the sum of diagonals over all
shifts.  The physical TPC denominator retains only the atomic diagonal
at the prescribed shift and after the actual projective identifications.
TPC--36 and TPC--42 show why these identifications and coherent defects
cannot be discarded; TPC--43 and TPC--45 show why physical sign
restriction and large-prime descent must be applied to one globally
consistent coefficient packet.  None of
\eqref{eq:tpc46-bc-theorem}, \eqref{eq:tpc46-bc-corollary},
\eqref{eq:tpc46-fr-discrepancy}, or \eqref{eq:tpc46-wright-form}
contains this atomic normalization or proves stability under those
restrictions.

We therefore use the cited literature only for comparison.  It does
not prove the vector atomic estimate studied here.  Conversely, the
slot and normalization mismatches are not impossibility theorems: a
future positive result could exploit the special prime/M\"obius packet,
prove a restriction-stable tensor estimate, or establish a separate
localization principle.  Such an input would be new and would have to
state these features explicitly.
