\section{Fixed-shift closure at tensor normalization}
\label{sec:tpc46-tensor-closure}

The third arithmetic coefficient is not, by itself, an obstruction to
a fixed-shift estimate.  The issue is the norm in which that estimate
is obtained.

Define multiplicative synthesis sequences
\begin{equation}
 A(n):=\sum_{pr=n}a_pb_r,
 \qquad
 C(n):=\sum_{mj=n}c_m\eta_j.
 \label{eq:tpc46-product-synthesis}
\end{equation}
Then
\begin{equation}
 \cT_h(a,b,c,\eta)=\sum_nA(n)C(n-h).
 \label{eq:tpc46-additive-correlation}
\end{equation}

\begin{theorem}[Scalar tensor closure]
\label{thm:tpc46-scalar-tensor-closure}
For every integer \(h\),
\begin{equation}
 \boxed{
 |\cT_h(a,b,c,\eta)|^2
 \le
 \rho_{\cP,\cR}\rho_{\cM,\cJ}\cD_\otimes.}
 \label{eq:tpc46-scalar-tensor-bound}
\end{equation}
\end{theorem}

\begin{proof}
Cauchy--Schwarz in \eqref{eq:tpc46-additive-correlation} gives
\(
 |\cT_h|^2\le\|A\|_2^2\|C\|_2^2
\).
On each product fiber, Cauchy--Schwarz gives
\begin{align*}
 \|A\|_2^2
 &\le\rho_{\cP,\cR}\sum_{p,r}|a_pb_r|^2,\\
 \|C\|_2^2
 &\le\rho_{\cM,\cJ}\sum_{m,j}|c_m\eta_j|^2.
\end{align*}
Multiplication proves the claim.
\end{proof}

The same proof is valid with one synthesized sequence Hilbert-valued.

\begin{corollary}[One-vector-slot closure]
\label{cor:tpc46-one-vector-slot}
Let \(x_{p,r}\in\C\) and \(y_{m,j}\in\Hh\), and put
\[
 G_h:=\sum_{pr-mj=h}x_{p,r}y_{m,j}.
\]
Then
\begin{equation}
 \|G_h\|_{\Hh}^2
 \le
 \rho_{\cP,\cR}\rho_{\cM,\cJ}
 \left(\sum_{p,r}|x_{p,r}|^2\right)
 \left(\sum_{m,j}\|y_{m,j}\|_{\Hh}^2\right).
 \label{eq:tpc46-one-vector-bound}
\end{equation}
\end{corollary}

\begin{proof}
Use Hilbert-space Cauchy--Schwarz after product synthesis; the
fiberwise inequality
\(
 \|\sum_{\nu=1}^k y_\nu\|^2\le k\sum_\nu\|y_\nu\|^2
\)
replaces its scalar counterpart.
\end{proof}

In the global large-prime range of TPC--45, product synthesis on the
left is actually injective.

\begin{lemma}[Large-prime product injectivity]
\label{lem:tpc46-large-prime-injectivity}
Suppose every \(p\in\cP\) is prime, \(p>\sqrt{N_+}\), and every
occurring product satisfies \(pr\le N_+\).  Then
\begin{equation}
 \rho_{\cP,\cR}=1.
 \label{eq:tpc46-rho-pr-one}
\end{equation}
\end{lemma}

\begin{proof}
If \(pr=p'r'\le N_+\) with distinct primes \(p,p'>\sqrt{N_+}\),
then \(pp'\) divides the common product, while \(pp'>N_+\), a
contradiction.
\end{proof}

Combining
\cref{thm:tpc46-scalar-tensor-closure,lem:tpc46-large-prime-injectivity}
with \eqref{eq:tpc46-divisor-multiplicity} gives
\begin{equation}
 |\cT_h|^2\le X^{o(1)}\cD_\otimes
 \label{eq:tpc46-fixed-h-tensor-endpoint}
\end{equation}
uniformly in \(h\).  This estimate retains an arbitrary prime
coefficient, an arbitrary cofactor coefficient, and an arbitrary source
coefficient.  It uses neither determinant-shift averaging nor a
Kloosterman-fraction estimate.

The conclusion is nevertheless not the TPC--45 Bessel target.  By
\eqref{eq:tpc46-diagonal-disintegration}, the right side of
\eqref{eq:tpc46-fixed-h-tensor-endpoint} is the total atomic energy over
\emph{all} determinant shifts.  TPC--45 requires the atomic diagonal
at the one physical shift and inside the actual output geometry.  The
size and sharpness of that mismatch are quantified in
\cref{sec:tpc46-atomic-boundaries}.
