\begin{abstract}
The native-affine interface at a fixed shift isolates a very-high-prime
face by imposing a cutoff \(p>y\).  Choosing
\(y=X^{267/400+\eta}\) with fixed \(\eta>0\) forces its target cofactor
into \(r\le X^{133/400-\eta+o(1)}\), apparently separating it from the
inherited \(R\asymp J=X^{133/400+o(1)}\) packet.  We prove that this
positive-power displacement is a feature of that convenient cutoff, not a
requirement of the literal very-high decomposition.  The exact cutoff
hypotheses already admit
\[
 y=C_{\rm vh}Q,
 \qquad Q=X^{267/400+o(1)},
\]
with a fixed support-dependent constant.  Writing \(\omega_X=y/Q\), the
safe and maximal cofactor scales are both
\(R\asymp J/\omega_X\).  Thus a critical cutoff
\(\omega_X\asymp1\) preserves the \(R\asymp J\) exponent, a subpower
cutoff shift has zero fixed-power cost, and only
\(\omega_X=X^{\eta+o(1)}\) creates the polynomial gap.

Geometric compatibility does not imply energy occupancy.  For the literal
pre-terminal lift, whose coefficient has no cofactor dependence, we compute
the optimal coefficient-uniform projection constant exactly:
\[
 \beta_{\cR}
 =\min_{m:B_mN(m)>0}\frac{N_{\cR}(m)}{N(m)}.
\]
It can vanish under the inherited hypotheses.  We give the analogous exact
terminal-activation minimax, a largest-prime census of the very-high face,
and an exact dyadic decomposition.  Conditional on nonzero very-high atomic
energy, one compatible dyadic block retains an
\(X^{-o(1)}\) fraction, so block localization has no positive polynomial
loss.  It does not prove parent-to-face occupancy.  The exact Walsh
decomposition also exposes high mass outside the represented terminal
image; restoring it is a separate nonmonotone reassembly gate.  Finally,
under the declared \(\Delta_M=O(Q)\) support information and among certified
fixed-power schedules, we show that the critical cutoff is support-optimal,
while all current support-only multiplicity and automatic-singleton bounds
remain far outside the \(1/400\) endpoint budget.  These are exact L0
results and an L1 fixed-shift interface advance; no parity improvement or
twin-prime conclusion is claimed.
\end{abstract}
