\section{The selected cofactor core and the undeleted singleton bridge}
\label{sec:tpc59-singleton}

The dyadic theorem localizes raw terminal energy, not a coherent output
norm.  We now connect one selected cell to the complete undeleted residual
vector by the full-fiber singleton bridge of TPC--57.  The distinction
between a very-high root and its full terminal fiber is essential: a
collision partner of a root with \(p>y\) need not itself remain on the
very-high face \citep{WangTPC57}.

\subsection{Core energy and full active multiplicity}

Let
\begin{equation}
 \cU_{h_0}^{\rm phys}(\zeta)
 :=\{u\in\cU_{h_0}^{\rm term}:x_u\ne0\},
 \qquad q(u)=(i(u),s(u)),
 \label{eq:tpc59-full-physical-terminal-set}
\end{equation}
and define the complete active degree of a residual fiber by
\begin{equation}
 n_a^{\rm phys}(\zeta)
 :=\bigl|q^{-1}(a)\cap\cU_{h_0}^{\rm phys}(\zeta)\bigr|.
 \label{eq:tpc59-full-physical-degree}
\end{equation}
The degree in \eqref{eq:tpc59-full-physical-degree} is computed in the
whole terminal vector, without imposing \(p>y\) or a cofactor block.
The complete undeleted residual energy is
\begin{equation}
 \cG_{\rm full}(\zeta)
 :=\sum_a\left|
      \sum_{\substack{u\in\cU_{h_0}^{\rm term}\\q(u)=a}}x_u
     \right|^2.
 \label{eq:tpc59-complete-grouped-energy}
\end{equation}
The high-only residual energy used by the TPC--58 high-column interface is
\begin{equation}
 \cG_H(y;\zeta)
 :=\sum_a\left|
      \sum_{\substack{u\in\cU_{h_0,>y}^{\rm term}\\q(u)=a}}x_u
     \right|^2.
 \label{eq:tpc59-high-only-grouped-energy}
\end{equation}
This is the same quantity as \(\cG_H\) in
\eqref{eq:tpc59-grouped-not-additive}.  The full degree below is deliberately
stronger than the active degree inside the high-only vector.

For a half-open cofactor core
\begin{equation}
 \cB_R(y)
 :=\{u\in\cU_{h_0,>y}^{\rm term}:R\le r_u<2R\},
 \label{eq:tpc59-very-high-core}
\end{equation}
put
\begin{align}
 \cD_R(y;\zeta)
 &:=\sum_{u\in\cB_R(y)}|x_u|^2,
 \label{eq:tpc59-core-terminal-diagonal}\\
 \cI_R^{\rm full}(y;\zeta)
 &:=\sum_{u\in\cB_R(y)\cap\cU_{h_0}^{\rm phys}(\zeta)}
       |x_u|^2\bigl(n_{q(u)}^{\rm phys}(\zeta)-1\bigr).
 \label{eq:tpc59-core-full-incidence}
\end{align}
Thus \(\cI_R^{\rm full}\) is a rooted, coefficient-weighted incidence,
not an unweighted pair count and not a multiplicity computed after
restricting the vector to \(\cB_R(y)\).

\begin{theorem}[Very-high core to high-only and full-output singleton bridge]
\label{thm:tpc59-core-full-singleton-bridge}
For every fixed \(h_0\ne0\), every admissible cutoff \(y\), every cofactor
scale \(R\), and every distinguished coefficient vector,
\begin{equation}
 \boxed{
 \min\{\cG_H(y;\zeta),\cG_{\rm full}(\zeta)\}
 \ge
 \bigl(\cD_R(y;\zeta)-\cI_R^{\rm full}(y;\zeta)\bigr)_+.}
 \label{eq:tpc59-core-full-singleton-floor}
\end{equation}
Consequently, if \(\cD_R(y;\zeta)>0\) and
\begin{equation}
 \cI_R^{\rm full}(y;\zeta)
 \le(1-\delta_R)\cD_R(y;\zeta),
 \qquad 0<\delta_R\le1,
 \label{eq:tpc59-core-incidence-criterion}
\end{equation}
then
\begin{equation}
 \boxed{
 \min\{\cG_H(y;\zeta),\cG_{\rm full}(\zeta)\}
 \ge\delta_R\cD_R(y;\zeta).}
 \label{eq:tpc59-core-positive-full-output}
\end{equation}
If \(R=2^{k_*}\) is the maximal-energy cell selected in
\cref{thm:tpc59-exact-dyadic-localization}, then
\begin{equation}
 \min\{\cG_H(y;\zeta),\cG_{\rm full}(\zeta)\}
 \ge\frac{\delta_R}{B_X(y)}\cD_H(y;\zeta)
 \label{eq:tpc59-selected-block-singleton-transfer}
\end{equation}
whenever \eqref{eq:tpc59-core-incidence-criterion} holds.
\end{theorem}

\begin{proof}
If \(n_a^{\rm phys}=1\), the unique active atom in the full fiber \(a\)
survives with exactly its atomic energy both in
\eqref{eq:tpc59-complete-grouped-energy} and, when it is a very-high root,
in \eqref{eq:tpc59-high-only-grouped-energy}.  Hence each of
\(\cG_H\) and \(\cG_{\rm full}\) dominates the energy of all core roots
whose full active degree is one.  A core root with full degree
at least two contributes at most
\(
 |x_u|^2(n_{q(u)}^{\rm phys}-1)
\)
to the energy removed from this singleton subcollection.  Summing over
core roots proves
\(
 \min\{\cG_H,\cG_{\rm full}\}\ge
 \cD_R-\cI_R^{\rm full}
\);
nonnegativity gives \eqref{eq:tpc59-core-full-singleton-floor}.
Equation \eqref{eq:tpc59-core-positive-full-output} follows from
\eqref{eq:tpc59-core-incidence-criterion}.  For the selected dyadic cell,
combine it with \eqref{eq:tpc59-dyadic-pigeonhole}.
\end{proof}

No comparison between the restricted grouped norm
\[
 \sum_a\left|
   \sum_{u\in q^{-1}(a)\cap\cB_R(y)}x_u
 \right|^2
\]
and either \(\cG_H(y;\zeta)\) or \(\cG_{\rm full}(\zeta)\) occurs in the
proof.  Restoring omitted coordinates can cancel a restricted coherent sum.
The theorem instead retains only roots that are singletons in the complete
active fiber system.  Those roots survive in particular in the high-only
residual vector needed by the downstream native-erasure map.

\subsection{Factor-exchange locality of every full partner}

Define the enlarged, unrestricted terminal neighborhood
\begin{equation}
 \cB_R^+
 :=\{v\in\cU_{h_0}^{\rm term}:R/2\le r_v<4R\}.
 \label{eq:tpc59-enlarged-full-terminal-block}
\end{equation}
Unlike \(\cB_R(y)\), this set does not impose \(p_v>y\).

\begin{proposition}[Every full partner is cofactor-local]
\label{prop:tpc59-full-partner-locality}
If \(u\in\cB_R(y)\) and
\(v\in\cU_{h_0}^{\rm term}\) satisfies \(q(v)=q(u)\), then
\begin{equation}
 \boxed{R/2\le r_v<4R.}
 \label{eq:tpc59-full-partner-range}
\end{equation}
Consequently, for every physical core root,
\begin{equation}
 n_{q(u)}^{\rm phys}(\zeta)
 =\bigl|q^{-1}(q(u))\cap
       \cU_{h_0}^{\rm phys}(\zeta)\cap\cB_R^+\bigr|,
 \label{eq:tpc59-full-degree-localized}
\end{equation}
and the exact incidence is
\begin{equation}
 \boxed{
 \cI_R^{\rm full}
 =\sum_{\substack{u\in\cB_R(y)\cap\cU_{h_0}^{\rm phys}(\zeta)\\
                   v\in\cB_R^+\cap\cU_{h_0}^{\rm phys}(\zeta)\\
                   v\ne u,\ q(v)=q(u)}}|x_u|^2.}
 \label{eq:tpc59-local-rooted-pair-identity}
\end{equation}
When \(R\) is dyadic, the enlarged range is the union of three adjacent
half-open dyadic cells, so localization of all partners has \(O(1)\)
covering cost.
\end{proposition}

\begin{proof}
Write the two source rows as \(m=d\ell\) and \(m'=d'\ell'\).  Equality of
the residual keys gives
\begin{equation}
 dr=d'r'.
 \label{eq:tpc59-partner-factor-exchange}
\end{equation}
Both source divisors belong to the same declared cell
\([D,2D]\).  Therefore
\[
 r'=\frac d{d'}r,
 \qquad \frac12\le\frac d{d'}\le2.
\]
Together with \(R\le r<2R\), this proves
\eqref{eq:tpc59-full-partner-range}.  Thus every full physical partner is
already present in \(\cB_R^+\), proving
\eqref{eq:tpc59-full-degree-localized}; expanding
\(n_{q(u)}^{\rm phys}-1\) then gives
\eqref{eq:tpc59-local-rooted-pair-identity}.
\end{proof}

The proposition is stronger than merely checking collisions inside the
selected very-high cell, but weaker than an occupancy estimate.  A carrier
made entirely of active doubletons obeys the same \(O(1)\) partner locality
and still has no singleton energy.  Thus bounded scale displacement does
not make \(\delta_R\) in
\eqref{eq:tpc59-core-incidence-criterion} positive.

\subsection{Critical compatibility does not create occupancy}

At the critical cutoff \(y=C_{\rm vh}Q\),
\cref{thm:tpc59-cutoff-cofactor-reciprocity} gives
\begin{equation}
 R_{\rm safe}(y)\asymp R_{\rm max}(y)\asymp J.
 \label{eq:tpc59-critical-singleton-compatible-scale}
\end{equation}
Hence the exponent \(R\asymp J\) is once again compatible with the
very-high dictionary.  This removes the fixed positive-power support gap
created by \(y=X^{267/400+\eta}\); it proves none of the following:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item that the fixed retained-pair carrier contains a cofactor in the
       critical window on every active row;
 \item that such a coordinate terminalizes or has nonzero physical energy;
 \item that the energy-rich dyadic cell \(k_*\) from
       \cref{thm:tpc59-exact-dyadic-localization} lies at scale \(J\); or
 \item that a positive weighted fraction of its full fibers are singletons.
\end{enumerate}
The first two failures are measured by the occupancy and terminal minimax
constants of \cref{sec:tpc59-occupancy}; the fourth is precisely
\eqref{eq:tpc59-core-incidence-criterion}.

For comparison, retain the fixed-power cutoff
\begin{equation}
 y=X^{267/400+\eta},
 \qquad \eta>0.
 \label{eq:tpc59-fixed-eta-singleton-face}
\end{equation}
Then every very-high atom satisfies
\begin{equation}
 r\le R_{\rm max}(y)
 =X^{133/400-\eta+o(1)},
 \label{eq:tpc59-fixed-eta-compatible-ceiling}
\end{equation}
whereas an inherited root with \(R\asymp J\) and every one of its
factor-exchange partners lie in a constant-factor neighborhood of \(J\).
Thus, for large \(X\),
\begin{equation}
 [R/2,4R)\cap[1,R_{\rm max}(y)]=\varnothing.
 \label{eq:tpc59-fixed-eta-factor-exchange-gap}
\end{equation}
The factor-exchange identity does not transport an old atom across this
polynomial gap: it only locates other atoms already sharing the same full
residual key.  In particular, it cannot turn geometric incompatibility
into cofactor occupancy or create terminal energy in a missing block.

\subsection{The remaining arithmetic door}

After high-face activation and dyadic localization, the exact remaining
singleton target is
\begin{equation}
 \boxed{
 \cI_{R_*}^{\rm full}(y;\zeta)
 \le(1-\delta_{R_*})\cD_{R_*}(y;\zeta),
 \qquad
 \delta_{R_*}\ge X^{-\lambda_{\rm sing}+o(1)},}
 \label{eq:tpc59-remaining-weighted-incidence-gate}
\end{equation}
for the distinguished energy-rich block \(R_*=2^{k_*}\), or a stronger
coefficient-uniform analogue on a fixed carrier.  By
\eqref{eq:tpc59-local-rooted-pair-identity}, this is a local, weighted
one-atom-versus-two-atom factor-exchange estimate retaining the literal
terminal coefficient and the one physical shift \(h_0\).  A support-only
upper bound for the maximal fiber degree does not imply it.

The bridge theorem and partner localization are unconditional
finite-dimensional and literal-support statements (L0/L1).  Positivity or
a polynomial lower bound for \(\delta_{R_*}\) is a new arithmetic input;
neither critical cutoff compatibility nor dyadic pigeonholing supplies it.
Only a quantitative proof of
\eqref{eq:tpc59-remaining-weighted-incidence-gate}, together with the
upstream activation and downstream transfers, could contribute to an L2
advance.  No undeleted asymptotic lower square, native-affine Gram transfer,
parity improvement, or twin-prime consequence is claimed here.
