\section{Largest-prime census and zero-cost dyadic localization}
\label{sec:tpc59-terminal}

The preceding minimax constants are exact but still refer to a terminal
indicator.  We now identify that indicator arithmetically and show that,
once very-high terminal energy exists, localizing it to one cofactor block
costs only a logarithm.

\subsection{The exact largest-prime face}

Adopt the convention \(\Pplus(1)=1\).  Let
\(\cU_{h_0}^{\rm term}\) be the complete literal terminal universe of
TPC--57, and define
\begin{equation}
 \cU_{h_0,>y}^{\rm term}
 :=\{u=(m,r,j,\gamma)\in\cU_{h_0}^{\rm term}:p_u>y\}.
 \label{eq:tpc59-very-high-terminal-universe}
\end{equation}

\begin{theorem}[Largest-prime census]
\label{thm:tpc59-largest-prime-census}
Assume \(y>\sqrt{N_+}\), and fix \((m,j,\gamma)\) with
\(n=mj+h_0\in[N_-,N_+]\).  There is at most one terminal atom over this
triple with \(p>y\).  Such an atom exists exactly when
\begin{equation}
 p_*:=\Pplus(n)>y,
 \qquad
 r_*:=\frac n{p_*},
 \qquad
 (m,r_*)\in\cI_X,
 \label{eq:tpc59-largest-prime-retained-test}
\end{equation}
and \((m,r_*,j,\gamma)\) satisfies the remaining inherited terminal masks,
squarefree conditions, coprimality conditions, and
\(\Lambda_X(n)\ne0\).  In that case
\begin{equation}
 p_u=p_* = \Pplus(mj+h_0),
 \qquad
 r_u=\frac{mj+h_0}{\Pplus(mj+h_0)}.
 \label{eq:tpc59-largest-prime-formula}
\end{equation}
\end{theorem}

\begin{proof}
If two distinct primes greater than \(y\) divided \(n\), their product
would exceed \(y^2>N_+\ge n\).  Thus a prime divisor above \(y\) is unique
and necessarily equals \(\Pplus(n)\).  The equality
\(p_ur=mj+h_0=n\) then forces \(r=r_*\).  The retained-pair and remaining
terminal conditions are plainly necessary.  Conversely, if all displayed
and inherited conditions hold, \(p_*\) is prime by definition of largest
prime factor, the equality \(p_*r_*=n\) holds, and the corresponding
coordinate belongs to \(\cU_{h_0,>y}^{\rm term}\).
\end{proof}

For the literal terminal amplitude
\begin{equation}
 x_u=\mu(r_u)\Lambda_X(p_ur_u)[G_X^L]_u,
 \label{eq:tpc59-literal-terminal-amplitude-repeat}
\end{equation}
define the very-high atomic diagonal
\begin{equation}
 \cD_H(y;\zeta)
 :=\sum_{u\in\cU_{h_0,>y}^{\rm term}}|x_u|^2.
 \label{eq:tpc59-very-high-terminal-diagonal}
\end{equation}
The theorem gives the exact weighted census
\begin{equation}
 \boxed{
 \cD_H(y;\zeta)
 =\sum_{m,j,\gamma}
   \one_{\rm vh}(m,j,\gamma;y)
   |\Lambda_X(mj+h_0)|^2
   |c_{m,j,\gamma}|^2|\zeta_m|^2,}
 \label{eq:tpc59-largest-prime-energy-census}
\end{equation}
where \(\one_{\rm vh}\) is precisely the test in
\cref{thm:tpc59-largest-prime-census}.  Under the sign calibration of
TPC--58, \(x_u=-\mu(d_mr_u)b_{i,d_mr_up_u}\), so
\begin{equation}
 |x_u|^2=|b_{i,d_mr_up_u}|^2.
 \label{eq:tpc59-terminal-Walsh-atomic-match}
\end{equation}
Thus every matched terminal/Walsh coordinate has the same raw atomic
weight on both sides of the dictionary \citep{WangTPC58}.  This coordinate
injection is not asserted to be surjective onto the full Walsh carrier.

The census is an identity, not a density theorem.  It permits
\(\cD_H(y;\zeta)=0\) while the parent or full Walsh diagonal is positive:
the targets may all be \(y\)-smooth, the required complementary cofactors
may be absent from \(\cI_X\), terminal masks may fail, or the distinguished
row coefficients may vanish on every surviving row.

\subsection{Exact dyadic partition}

Put
\begin{equation}
 R_+(y):=\frac{N_+}{y}.
 \label{eq:tpc59-dyadic-R-plus}
\end{equation}
If \(R_+(y)<1\), the very-high terminal face is empty.  Otherwise, for
integers
\begin{equation}
 0\le k\le K_X:=\left\lfloor\log_2R_+(y)\right\rfloor,
 \label{eq:tpc59-dyadic-index-range}
\end{equation}
define the half-open cofactor cells
\begin{equation}
 \cB_k(y)
 :=\{u\in\cU_{h_0,>y}^{\rm term}:2^k\le r_u<2^{k+1}\}
 \label{eq:tpc59-dyadic-terminal-cells}
\end{equation}
and their atomic energies
\begin{equation}
 \cD_k(y;\zeta):=\sum_{u\in\cB_k(y)}|x_u|^2.
 \label{eq:tpc59-dyadic-terminal-energy}
\end{equation}

\begin{theorem}[Exact dyadic localization]
\label{thm:tpc59-exact-dyadic-localization}
The cells \(\cB_k(y)\) form a disjoint partition of the very-high terminal
face and
\begin{equation}
 \boxed{
 \cD_H(y;\zeta)=\sum_{k=0}^{K_X}\cD_k(y;\zeta).}
 \label{eq:tpc59-dyadic-energy-partition}
\end{equation}
If \(\cD_H(y;\zeta)>0\), let \(k_*\) be the least index attaining the
maximum dyadic energy.  Then
\begin{equation}
 \boxed{
 \cD_{k_*}(y;\zeta)
 \ge\frac{\cD_H(y;\zeta)}{B_X(y)},
 \qquad
 B_X(y):=1+\left\lfloor\log_2R_+(y)\right\rfloor.}
 \label{eq:tpc59-dyadic-pigeonhole}
\end{equation}
For every admissible endpoint cutoff \(y\ge C_{\rm vh}Q\),
\begin{equation}
 B_X(y)=O(\log X)=X^{o(1)}.
 \label{eq:tpc59-dyadic-count-subpower}
\end{equation}
Hence dyadic localization inside an already activated very-high terminal
face has zero fixed-power loss.
\end{theorem}

\begin{proof}
Every very-high atom has positive integral \(r_u\le N_+/p_u<N_+/y\), so it
lies in exactly one half-open cell in the displayed index range.  Raw atomic
energy is additive across disjoint coordinate sets, proving
\eqref{eq:tpc59-dyadic-energy-partition}.  The maximum of \(B_X(y)\)
nonnegative numbers is at least their average.  Finally,
\(R_+(y)\le N_+/(C_{\rm vh}Q)=X^{133/400+o(1)}\), proving
\eqref{eq:tpc59-dyadic-count-subpower}.
\end{proof}

In the TPC--58 loss notation, the theorem proves
\begin{equation}
 \boxed{\lambda_{\rm blk}=0}
 \label{eq:tpc59-zero-block-exponent}
\end{equation}
conditional on a lower bound for \(\cD_H\).  It does not prove
a parent-to-high-face energy transfer: the ratio
\(\cD_H/\cE_{\rm par}\), or even \(\cD_H/\cD_0\), remains uncontrolled.

\subsection{The base/represented/missing decomposition and its limit}

Let \(\cW_0\) be the complete declared Walsh slice and define its raw
atomic diagonal by
\begin{equation}
 \cD_0:=\sum_{w\in\cW_0}|b_w|^2.
 \label{eq:tpc59-full-declared-Walsh-diagonal}
\end{equation}
Let \(\cW_H(y)\subseteq\cW_0\) be the set of high Walsh atoms in that
slice, namely those whose unique very-high prime exceeds \(y\), and let
\(\iota:\cU_{h_0,>y}^{\rm term}\to\cW_H(y)\) be the injective
terminal/Walsh coordinate map.  Its image retains exactly the
retained-pair and terminal-mask conditions in
\cref{thm:tpc59-largest-prime-census}.  Define
\begin{align}
 \cD_{\rm base}(y)
 &:=\sum_{w\in\cW_0\setminus\cW_H(y)}|b_w|^2,
 \label{eq:tpc59-base-Walsh-energy}\\
 \cD_{\rm miss}(y)
 &:=\sum_{w\in\cW_H(y)\setminus\Ran\iota}|b_w|^2.
 \label{eq:tpc59-missing-high-Walsh-energy}
\end{align}
The second term is the high Walsh mass whose complementary cofactor is
absent from the retained carrier or whose remaining terminal conditions
fail.  Unique very-high factorization and the atomic norm match
\eqref{eq:tpc59-terminal-Walsh-atomic-match} now give the exact
three-part decomposition
\begin{equation}
 \boxed{
 \cD_0
 =\cD_{\rm base}(y)+\cD_{\rm miss}(y)
  +\sum_{k=0}^{K_X}\cD_k(y).}
 \label{eq:tpc59-base-high-partition}
\end{equation}
In particular, with
\(\cD_{\rm off}(y):=\cD_{\rm base}(y)+\cD_{\rm miss}(y)\), either
\begin{equation}
 \cD_{\rm off}(y)\ge\frac12\cD_0
 \label{eq:tpc59-base-dominates}
\end{equation}
or some represented high cofactor block satisfies
\begin{equation}
 \cD_k(y)\ge\frac{\cD_0}{2B_X(y)}.
 \label{eq:tpc59-high-block-dominates}
\end{equation}
This dichotomy is unconditional, but its favorable alternative is not.
A proof requiring the represented high face cannot discard either the
base mass or the unrepresented high mass.  In particular, the possibility
\(\cD_{\rm miss}>0\) is exactly why the largest-prime census may vanish
while the full Walsh diagonal is positive.

\subsection{Why coherent energy is not a dyadic measure}

Let \(q(u)=(i,s(u))\) be the residual output key and define
\begin{equation}
 A_k(i,s)
 :=\sum_{\substack{u\in\cB_k(y)\\q(u)=(i,s)}}x_u.
 \label{eq:tpc59-dyadic-grouped-vector}
\end{equation}
The complete very-high residual vector is \(A_H=\sum_kA_k\), and therefore
\begin{equation}
 \cG_H=\left\|\sum_kA_k\right\|_2^2,
 \label{eq:tpc59-grouped-not-additive}
\end{equation}
not \(\sum_k\|A_k\|_2^2\).

There is nevertheless one exact locality statement.  If two atoms have the
same residual key, then
\begin{equation}
 d_mr=d_{m'}r',
 \qquad d_m,d_{m'}\in[D,2D],
 \qquad \frac12\le\frac{r'}r\le2.
 \label{eq:tpc59-factor-exchange-locality}
\end{equation}
Thus
\begin{equation}
 \langle A_k,A_\ell\rangle=0
 \qquad(|k-\ell|\ge2),
 \label{eq:tpc59-dyadic-orthogonality}
\end{equation}
and
\begin{equation}
 \boxed{
 \cG_H
 =\sum_k\|A_k\|_2^2
  +2\operatorname{Re}\sum_k\langle A_k,A_{k+1}\rangle.}
 \label{eq:tpc59-block-tridiagonal-grouping}
\end{equation}
Adjacent blocks can still cancel exactly.  After the native erasure
\((i,s)\mapsto i\), even this residual-label locality is lost because
different \(s\) values share the same native output.  Hence the atomic
pigeonhole theorem cannot be applied to a coherent norm without a new
lower-reassembly estimate.
