\section{Finite dynamical interpretation, exact certificate, and conclusion}
\label{sec:computation}

The term \emph{spectrum} here has a literal finite-dynamical meaning.
For each divisor pair, translation
\begin{equation}
 \tau:j\longmapsto j+1\qquad\text{on }\Z/T\Z,
 \quad T=H[u,v],
 \label{eq:cyclic-dynamics}
\end{equation}
is a finite measure-preserving dynamical system.  Its Koopman
eigenfunctions are \(e_T(rj)\).  The coefficients
\(\widehat K(r)\) in \eqref{eq:kernel-fourier} are therefore the exact
spectral coordinates of the centered local sieve observable.  The
direct identity \eqref{eq:determinant-fourier} diagonalizes the shared
determinant factor, whereas \eqref{eq:kernel-poisson} couples that
finite spectrum to the long orbit window.  The required four-channel
cancellation is consequently a matched-spectral statement; no claim
of a spectral realization of zeta zeros is involved.

\subsection{Exact computational certificate}

The standard-library Python certificate is located at
\begin{center}
\texttt{experiments/tpc19\_certificate.py}.
\end{center}
Run it from the paper directory with
\begin{verbatim}
python experiments/tpc19_certificate.py
python -O experiments/tpc19_certificate.py
\end{verbatim}
Both commands regenerate
\texttt{experiments/tpc19\_certificate.json}.  The proof layer uses
integers, \texttt{fractions.Fraction}, and formal prime-log
indeterminates.  In particular, it checks:
\begin{enumerate}[label=\textnormal{(\roman*)}]
 \item the Ramanujan definition of \(\Lambda_R\) against the divisor
 form in 540 exact cases, including squarefree support and
 \eqref{eq:lambda-positive-form};
 \item the primitive masked means, the covariance formula, and
 termwise cancellation of every \(g=1\) contribution;
 \item equality of a four-row direct complete-period Gram matrix and
 the CRT matrix, all 15 principal minors, and 625 integer-vector
 quadratic forms;
 \item the positive witness \(433/450\) and a separate negative
 covariance regression \(-259/900\);
 \item the full residual identity \eqref{eq:residual-divisor} for
 \(n\le360\), and direct/divisor/CRT formal-polynomial reassembly of a
 residual pair, including determinant support and common-\(g\) sign
 cancellation.
\end{enumerate}
The direct periodic side loops over the original \(q\)-truncated
Ramanujan model, whereas the comparison side assembles the
\(u\)-divisor and CRT forms.  These are independently looped
reorganizations, not wholly independent arithmetic libraries: the
Ramanujan-sum routine itself uses the standard divisor formula for
\(c_q(n)\).

At the version archived with this paper, the generated JSON has
SHA-256
\begin{center}
\texttt{B141ADC152C38CDABE46528BD872AA4622AFD7A8E9D1E8E719D283247AC05744},
\end{center}
and the script has SHA-256
\begin{center}
\texttt{60154632DB45B1DB023C8CF5BF6D4084481EEF9154851CD2121567C2DA96F61F}.
\end{center}
The optional prime-data diagnostics are isolated from every exact
check and explicitly serialize
\texttt{prime\_asymptotic\_evidence=false}.

\subsection{Conclusion}

TPC-19 advances the TPC chain by replacing an opaque variable-
determinant residual correlation with exact, reusable normal forms.
The actual residual has a positive-size squarefree divisor expansion
with transverse M\"obius signs.  Primitive CRT identifies the shared
divisor with the row determinant.  Exact centering removes a small row
drift.  The complete-period \(j\)-zero mode of the finite model is
supported on nonzero determinant frequencies, and CRT--Poisson duality
turns its long-period part into coupled inverse phases.

The negative theorem is equally informative: one local model channel
can have a nonzero complete-period mean, so rowwise orbit cancellation
is unavailable.  A future proof can seek extra oscillation over rows,
or preserve matched cancellation and then pass either the sharp
M\"obius frequency-concentration gate or the joint long-lcm
Kloosterman gate.  These are narrower targets than the TPC-18 residual
statement, but they remain open.  The paper therefore
delivers a rigorous step and an auditable route map, not a twin-prime
claim or a parity-barrier breakthrough.
