\section{A rowwise componentwise no-go theorem}
\label{sec:nogo}

The finite model has a nonzero connected spectrum even for a primitive,
distinct-source row pair.  The following exact example prevents a
common but invalid proof strategy.

\begin{theorem}[An exact nonzero model witness]
\label{thm:model-witness}
Take
\begin{equation}
 R=12,\qquad h=2,\qquad d_1=d_2=3,
 \qquad \ell_1=31,\qquad \ell_2=41.
 \label{eq:witness-data}
\end{equation}
Then \(H=2\), \(m_1=93\), \(m_2=123\), and all primitive centering
hypotheses hold.  The exact conditional covariance is
\begin{equation}
 \boxed{\qquad \kappa_{12}(93,123)=\frac{433}{450}.\qquad}
 \label{eq:witness-covariance}
\end{equation}
If \(P=\operatorname{lcm}(1,\ldots,12)=27720\), then for every
integer \(T\ge1\),
\begin{equation}
 \sum_{\substack{1\le j\le TP\\(j,2)=1}}
 M_{93}(j)M_{123}(j)
 =TP\,\frac{433}{900}.
 \label{eq:witness-linear-growth}
\end{equation}
Thus the centered finite-model component need not have logarithmic, or
even \(o(TP)\), cancellation along these repeated complete periods.
\end{theorem}

\begin{proof}
Insert \(R=12\), \(m_1=93\), \(m_2=123\), and
\(\Delta=-30\) in the finite rational sum
\eqref{eq:kappa-formula}.  Exact simplification gives \(433/450\).
The functions \(M_{93}\) and \(M_{123}\) are periodic modulo \(P\).
There are \(P/2\) odd classes, so the sum over one full period is
\((P/2)(433/450)=P(433/900)\).  Repetition proves
\eqref{eq:witness-linear-growth}.  The accompanying certificate
described in \cref{sec:computation} verifies both the divisor formula
and a direct complete-period Gram calculation using exact rational
arithmetic.
\end{proof}

\begin{corollary}[No rowwise componentwise substitute]
\label{cor:componentwise-nogo}
Complete-period centering alone does not force the \(MM\) channel to
have zero complete-period mean for every admissible finite primitive
distinct-source parameter choice.  Consequently a proof of
cancellation in
\begin{equation}
 Z_{m_1}Z_{m_2}
 =P_{m_1}P_{m_2}-P_{m_1}M_{m_2}
 -M_{m_1}P_{m_2}+M_{m_1}M_{m_2}
 \label{eq:centered-four-channel}
\end{equation}
cannot obtain the required saving separately for all four terms from
complete-period \(j\)-cancellation alone.
\end{corollary}

\begin{proof}
The \(MM\) assertion already fails by
\cref{thm:model-witness}.  Equation \eqref{eq:centered-four-channel}
is the expansion of \((P_{m_1}-M_{m_1})(P_{m_2}-M_{m_2})\).
Therefore a valid argument must either exploit additional cancellation
over the row variables or combine the nonzero local model spectrum with
the other channels before taking absolute values.
\end{proof}

\begin{remark}[What the witness does not prove]
The witness is finite and exact.  It disproves a proposed uniform
rowwise componentwise lemma; it does not show that the actual residual
correlation is large, that an asymptotic generic row family has a
positive main term, or that determinant dispersion is false.  The
other three terms in \eqref{eq:centered-four-channel} may cancel the
model spectrum.  Nor does the fixed-\(R\) example rule out a rowwise
asymptotic as \(R\to\infty\), or cancellation after averaging the
actual TPC row coefficients.  It proves only that complete-period
centering is not an algebraic rowwise annihilator.  Spectral matching
is one possible open route.
\end{remark}

There is also a structural reason not to recover positivity after
row-pair pruning.  The full matrix
\([\kappa_R(m_\alpha,m_\beta)]\) is a Gram matrix by
\cref{prop:model-psd}; removing diagonal, near-determinant, or
large-divisor-gcd entries is a Schur mask not known to preserve
positive semidefiniteness.  Hence neither positivity nor the witness
may be transferred automatically to the generic TPC-18 subgraph.

For orientation only, the certificate contains two deterministic
sharp-window diagnostics.  With the explicitly recorded finite windows
and normalization, the four locally calibrated channel values are
\begin{center}
\begin{tabular}{@{}lcc@{}}
\toprule
channel & \((R,L,D,J)=(30,70,3,80)\)
& \((60,130,4,100)\) \\
\midrule
\(PP\) & \(1.0313935\times10^{-2}\) & \(5.6077583\times10^{-2}\) \\
\(PM\) & \(7.4448828\times10^{-3}\) & \(5.7773558\times10^{-2}\) \\
\(MP\) & \(7.4448828\times10^{-3}\) & \(5.7773558\times10^{-2}\) \\
\(MM\) & \(3.5400940\times10^{-3}\) & \(5.8418970\times10^{-2}\) \\
\(PP-PM-MP+MM\) & \(-1.0357367\times10^{-3}\)
& \(-1.0505627\times10^{-3}\) \\
\bottomrule
\end{tabular}
\end{center}
These decimal data are regression tests for the implemented channel
bookkeeping, not asymptotic evidence.  The windows are sharp and are
not the smooth weights of the theorems.  In particular, the
machine-readable output sets
\texttt{prime\_asymptotic\_evidence=false}.
