\section{Direct determinant frequencies and the M\"obius concentration gate}
\label{sec:direct-frequency}

Write \(e_q(x)=\exp(2\pi i x/q)\).  The connected kernel in
\cref{eq:kappa-gab} has an elementary but useful exact spectrum.

\begin{proposition}[Only nonzero determinant frequencies remain]
\label{prop:determinant-fourier}
For every integer \(g\ge1\) and \(\Delta\in\Z\),
\begin{equation}
 g\one_{g\mid\Delta}-1
 =\sum_{r=1}^{g-1}e_g(r\Delta).
 \label{eq:determinant-fourier}
\end{equation}
Consequently
\begin{align}
 \kappa_R(m_1,m_2)
 ={}&\sum_{\substack{g,a,b\ \mathrm{pairwise\ coprime\ squarefree}\\
 ga,gb\le R\\(ga,m_1H)=(gb,m_2H)=1}}
 \frac{\lambda'_R(ga)\lambda'_R(gb)}{g^2ab}
 \sum_{r=1}^{g-1}e_g\!\bigl(r(m_1-m_2)\bigr).
 \label{eq:kappa-direct-spectrum}
\end{align}
In particular, centering removes every \(g=1\) contribution before
any estimate is made.
\end{proposition}

\begin{proof}
The complete additive-character sum is \(g\one_{g\mid\Delta}\).
Removing its \(r=0\) term proves \eqref{eq:determinant-fourier}; insertion
in \eqref{eq:kappa-gab} proves the second assertion.
\end{proof}

There is a second exact decomposition that separates genuine source
dispersion from a deterministic reduced-class bias.  If
\((g,\ell_1\ell_2d_1d_2)=1\), then
\begin{align}
 &g\one_{g\mid \ell_1d_1-\ell_2d_2}-1
 \notag\\
 &\quad={}
 g\left(
 \one_{\ell_1\equiv \ell_2d_2\overline{d_1}\ (\bmod g)}
 -\frac1{\varphi(g)}
 \right)
 +\left(\frac g{\varphi(g)}-1\right).
 \label{eq:source-bias-split}
\end{align}
Here and below a bar denotes an inverse in the displayed modulus.  The
first term in \eqref{eq:source-bias-split} is the discrepancy of the
prime source \(\ell_1\) in one reduced class.  The second term is a
fixed local bias.  It is not small for a fixed small \(g\), so the
model channel cannot be declared negligible from \(j\)-centering
alone.  A separate global estimate would have to use additional row
oscillation, or else retain the other three channels in
\eqref{eq:four-channel}.

We next isolate the bare dyadic M\"obius coefficient obtained by
grouping only the determinant difference.  The full TPC kernel also
contains the \(g,a,b\) restrictions, coprimality, generic pruning, and
spectral weights; those are not encoded in the following sequence.
Let \(\omega_D\) be a real smooth weight
supported in an interval of length at most \(D\) inside \([D,2D]\),
and let \(\ell_1\ne\ell_2\) be primes greater than \(2D\).  Define
\begin{equation}
 A_{\ell_1,\ell_2}(n)
 :=\sum_{\ell_1d_1-\ell_2d_2=n}
 \mu(d_1)\mu(d_2)\omega_D(d_1)\omega_D(d_2)
 \label{eq:difference-coefficient}
\end{equation}
and
\begin{equation}
 M_\ell(\alpha)
 :=\sum_d\mu(d)\omega_D(d)\ee{-\ell d\alpha}.
 \label{eq:mobius-frequency-sum}
\end{equation}

\begin{theorem}[Injective determinant geometry and exact transform]
\label{thm:difference-spectrum}
Under the preceding hypotheses, the map
\begin{equation}
 (d_1,d_2)\longmapsto \ell_1d_1-\ell_2d_2
 \label{eq:difference-map}
\end{equation}
is injective on the support of \(\omega_D\).  Therefore
\begin{equation}
 \sum_n|A_{\ell_1,\ell_2}(n)|^2
 =\left(\sum_d\mu(d)^2\omega_D(d)^2\right)^2.
 \label{eq:difference-l2}
\end{equation}
With the Fourier convention
\(\widehat A(\alpha)=\sum_nA(n)\ee{-n\alpha}\), one also has
\begin{equation}
 \boxed{\quad
 \widehat A_{\ell_1,\ell_2}(\alpha)
 =M_{\ell_1}(\alpha)\overline{M_{\ell_2}(\alpha)}.
 \quad}
 \label{eq:difference-factorization}
\end{equation}
\end{theorem}

\begin{proof}
A collision in \eqref{eq:difference-map} gives
\[
 \ell_1(d_1-d'_1)=\ell_2(d_2-d'_2).
\]
Thus \(\ell_2\mid d_1-d'_1\).  The support interval has length at
most \(D<\ell_2\), so \(d_1=d'_1\), and then \(d_2=d'_2\).
The \(\ell^2\)-identity follows by opening the square.  Finally,
Fourier inversion of the defining difference gives
\[
 \widehat A(\alpha)
 =\sum_{d_1,d_2}\mu(d_1)\mu(d_2)
 \omega_D(d_1)\omega_D(d_2)
 \ee{-\ell_1d_1\alpha}\ee{\ell_2d_2\alpha},
\]
which is \eqref{eq:difference-factorization} because the weights are
real.
\end{proof}

\begin{remark}[What \(\ell^2\) does and does not give]
Suppose \(|\omega_D|\ll1\) and, for some fixed \(c,c'>0\),
\(|\omega_D(d)|\ge c\) on at least \(c'D\) squarefree integers.  Then
\eqref{eq:difference-l2} is \(\asymp_{c,c'}D^2\).  Thus injectivity
gives an exact normalization, not a cancellation theorem.  Any gain
must come from where the mass of the product in
\eqref{eq:difference-factorization} lies in frequency, or from
cancellation against the other locally calibrated channels.
\end{remark}

If the factors \(\mu(d_i)\) in
\eqref{eq:difference-coefficient} are replaced by the permitted smooth
weights and phases, the resulting M\"obius-free difference coefficient
has the geometry covered by Pascadi's published large-sieve theorem
for smooth dispersion coefficients
\cite[Theorem~1.7]{Pascadi2026LargeSieve}, after dyadic and signed
splitting.  The general theorem is governed by a representing
measure for the \emph{pair sequence}
\(A_{\ell_1,\ell_2}\), through a frequency-concentration functional
\cite[Theorem~5.2]{Pascadi2026LargeSieve}.  It does not act separately
on the two factors \(M_{\ell_i}\).

\begin{remark}[Open sharp-M\"obius concentration gate]
\label{rem:mobius-concentration}
For the present coefficient, the representing measure for
\(A_{\ell_1,\ell_2}\) must encode the sharp factors \(\mu(d_i)\);
\eqref{eq:difference-factorization} identifies its Fourier density as
a product of two M\"obius exponential sums.  The required scale
parameter and rational-frequency windows depend on the preceding
matched Kuznetsov/dispersion reduction, which has not yet been
constructed.  We therefore do not state a numerical
frequency-concentration hypothesis in isolation.  The open gate is to
produce that matched reduction and then prove the exact
Theorem~5.2 concentration bound it requires, with sufficient saving for
\eqref{eq:residual-dd-target}.  This remark is a route specification,
not a conditional theorem.
\end{remark}

\begin{remark}[Two missing pieces, not one]
\Cref{rem:mobius-concentration} is not by itself a theorem about the
original residual.  One must first produce a Kuznetsov or dispersion
formula in which the \(PP,PM,MP,MM\) terms share the same spectral
kernel and remain combined.  Only then can a frequency-concentration
estimate be applied.  Current results for smooth dispersion
coefficients, triply well-factorable weights, or separated bilinear
divisor-bounded weights do not supply that matched reduction for the
sharp prime--M\"obius coefficient left by TPC-18
\citep{Pascadi2025Distribution,Li2026v6}.
\end{remark}
