\section{Introduction}
\label{sec:introduction}

The fixed-shift prime-pair problem may be written as a sequence of
normal-form and distribution gates.  TPC-15 through TPC-17 isolate and
assemble the factorable prefix of a symmetric Type-II packet
\citep{WangTPC15,WangTPC16,WangTPC17}.  TPC-18 proves that a surviving
M\"obius tail cannot be removed by coefficient smallness and that a
failed primitive slice forces a large two-row residual correlation with
distinct prime sources, large determinant, and low divisor gcd
\citep{WangTPC18}.  In the notation recalled below, its remaining
arithmetic object has the schematic form
\begin{equation}
 \sum_j\sum_{\alpha_1\ne\alpha_2}
 b_{\alpha_1,\alpha_2}(j)
 r_R(m_1j+h)r_R(m_2j+h),
 \qquad m_i=\ell_i d_i\asymp Q,
 \label{eq:opaque-correlation}
\end{equation}
with determinant \(h(m_1-m_2)\).  The point of the present paper is to
replace ``estimate a variable-determinant correlation'' by exact
arithmetic objects on which one can test a proposed dispersion input.

\subsection{Main advances}

The first advance is an exact divisor normal form for the actual
residual.  It is not a heuristic Ramanujan expansion.  It follows from
the finite divisor expansion of \(\Lambda_R\) and the classical identity
\(\Lambda(n)=-\sum_{u\mid n}\mu(u)\log u\).  The result has a fixed sign
pattern: a positive size \(w_R(u)\) multiplied by \(-\mu(u)\).  When a
pair \(u,v\) is written as
\[
 u=ga,\qquad v=gb,\qquad g=(u,v),
\]
the common factor \(g\) loses its M\"obius sign.  In a primitive affine
row pair, the Chinese remainder theorem then says exactly
\[
 \text{joint divisibility}\quad\Longleftrightarrow\quad
 g\mid m_1-m_2.
\]
Thus the parity-sensitive part is no longer hidden inside the values of
\(r_R\): the determinant content \(g\) is unsigned, while the transverse
variables retain the signs \(\mu(a)\mu(b)\).

The second advance is exact model centering and local prime
calibration.  On the allowed classes
\((j,H)=1\), \(H=\rad|h|\), the prime and finite-model local densities
are
\[
 \frac{H}{\varphi(H)}\frac{\ell d}{\varphi(\ell d)}
 \quad\text{and}\quad
 \frac{H}{\varphi(H)}\frac d{\varphi(d)},
\]
respectively.  Their difference is \(O(L^{-1}X^\eps)\), and we prove
that it is negligible at the \(XQ\) obstruction scale.  The remaining
problem is therefore a locally calibrated spectrum-matching problem,
not an unnoticed row drift; only the finite model has been proved to
have exact conditional mean zero.

The third advance is a pair of dual spectral interfaces.  For the
finite model, the connected complete density contains
\[
 g\one_{g\mid\Delta}-1,
 \qquad \Delta=m_1-m_2.
\]
Its direct Fourier expansion produces additive phases
\(\ee{r\ell d/g}\) and a determinant-difference coefficient.  Poisson
summation in the common \(j\)-progression instead produces inverse
phases in \(m_i\), hence a genuine Kloosterman-type interface.  These
are different routes and have different coefficient obstructions.

\subsection{A necessary negative result}

It is tempting to expand
\begin{equation}
 r_R(n_1)r_R(n_2)
 =\Lambda(n_1)\Lambda(n_2)
 -\Lambda(n_1)\Lambda_R(n_2)
 -\Lambda_R(n_1)\Lambda(n_2)
 +\Lambda_R(n_1)\Lambda_R(n_2)
 \label{eq:four-channel}
\end{equation}
and seek rowwise logarithmic saving from \(j\)-centering in all four
terms.  We show rigorously that this stronger strategy is false.  A
two-row finite example has centered
finite-model covariance \(433/450\); repeating its complete period
makes that component grow linearly.  Hence centering does not erase
the local \(MM\) spectrum.  One may either seek additional global
oscillation over the row variables or match the local spectra of all
four channels before absolute values are taken.  This does not
disprove the residual determinant-dispersion statement of TPC-18; it
rules out a stronger rowwise componentwise substitute for it.

\subsection{Relation to current large-sieve technology}

The M\"obius-free smooth analogue of the direct determinant
coefficient has the geometry treated by Pascadi's
frequency-concentrated exceptional-spectrum large sieve: a coefficient
\(
 \sum_{d_1\ell_1-d_2\ell_2=n}
 \Phi_1(d_1/D)\Phi_2(d_2/D)
 \ee{d_1\alpha_1+d_2\alpha_2}
\)
is covered by Theorem~1.7 of the published paper
\citep{Pascadi2026LargeSieve}, subject there to the spectral-level
condition \(q\gg L^2\).  That \(q\) is not the present row scale
\(Q=LD\); no parameter identification is valid before the missing
Kuznetsov reduction.  The coefficient here also contains the sharp
weights \(\mu(d_i)\omega_D(d_i)\).  Its Fourier transform factors
exactly, but the cited theorems do not supply the required
concentration estimate for those M\"obius weights.  Moreover, the reduction must
preserve the four-channel matching in \eqref{eq:four-channel}.

This distinction matters because the current numerical distribution
frontier alone is not the missing input.  Pascadi's more recent work
reaches level \(5/8-\eps\) for triply well-factorable prime weights
\citep{Pascadi2025Distribution}; Li's version-locked bilinear theorem
has the two monomial conditions used in TPC-17
\citep{Li2026v6}.  Neither coefficient class contains the sharp
prime--M\"obius row weight left here.  Classical and recent
Kloosterman-fraction estimates likewise act after a suitable inverse
phase has been produced \citep{DukeFriedlanderIwaniec1997,
BettinChandee2018,Wright2026}.  We construct that
phase algebraically, but do not assert that its three coupled moduli
satisfy an existing theorem's hypotheses.

\subsection{Scope and organization}

All unconditional statements in this paper are algebraic, elementary
analytic, or finite spectral identities.  We do not prove cancellation
of the primitive TPC-18 witness.  In particular, we prove no
fixed-shift Hardy--Littlewood asymptotic, no twin-prime lower bound, no
new exponent of distribution, and no violation of the parity barrier.

\Cref{sec:interface} fixes the primitive row geometry.
\Cref{sec:divisor-normal} derives the exact residual divisor form and
the \(g,a,b\) determinant expansion.  \Cref{sec:centering} removes the
local bias.  \Cref{sec:model-spectrum} computes the connected finite
model.  \Cref{sec:direct-frequency} gives the direct determinant
Fourier gate.  \Cref{sec:poisson} gives the CRT--Poisson and inverse
phase gate.  \Cref{sec:nogo} proves the rowwise componentwise no-go
theorem.
\Cref{sec:gates} records the high-prime local tail and the exact
remaining alternatives.  \Cref{sec:computation} describes the exact
certificate and concludes.
