\section{Hypercontractive moments and almost--sure dyadic closure}
\label{sec:tpc43-moments}

The first moment is enough for the endpoint statements above.  Fixed
higher moments give stronger tail bounds for a random prime--sign
environment, while still leaving open exceptional behavior at the
specified all--minus corner.  We use the standard Bonami--Beckner inequality on the
discrete cube \citep{Bonami1970,Beckner1975}; the weighted random
multiplicative form needed below is also recorded explicitly by
\citet[Probability Result~2.3]{Harper2019HighMoments}.

\begin{lemma}[One coordinate]
\label{lem:tpc43-one-coordinate-moment}
Let
\begin{equation}
 S(\varepsilon)=\sum_s A_s\chi_s(\varepsilon)
 \label{eq:tpc43-one-coordinate-polynomial}
\end{equation}
be any coordinate polynomial produced by the physical packet.  For each
fixed integer \(q\ge1\),
\begin{equation}
 \|S\|_{L^{2q}}^2
 \le
 \sum_s(2q-1)^{\omega(s)}|A_s|^2
 \le X^{o_q(1)}\sum_s|A_s|^2.
 \label{eq:tpc43-hypercontractive-coordinate}
\end{equation}
\end{lemma}

\begin{proof}
The first inequality is Bonami--Beckner hypercontractivity, decomposed by
Walsh degree.  Every label in the packet is at most \(X^{O(1)}\), so the
standard maximal-order bound gives
\begin{equation}
 \max_s\omega(s)\ll\frac{\log X}{\log\log X}.
 \label{eq:tpc43-max-omega}
\end{equation}
For fixed \(q\), the factor
\((2q-1)^{\omega(s)}\) is therefore \(X^{o_q(1)}\).
\end{proof}

\begin{theorem}[Fixed moments of the physical energies]
\label{thm:tpc43-fixed-moments}
For every fixed integer \(q\ge1\),
\begin{align}
 \E_\varepsilon Z_0(\varepsilon)^q
 &\le X^{o_q(1)}\cD_0^q,
 \label{eq:tpc43-zero-q-moment}\\
 \E_\varepsilon Z_{\rm tr}(\varepsilon)^q
 &\le X^{o_q(1)}\cD_{\rm tr}^q,
 \label{eq:tpc43-trace-q-moment}
\end{align}
where
\begin{equation}
 Z_{\rm tr}(\varepsilon)
 :=\sum_k
 \bigl(
  \|\mathscr T_{k,\varepsilon}^L\|^2
  +\|\mathscr T_{k,\varepsilon}^R\|^2
 \bigr).
 \label{eq:tpc43-trace-random-energy}
\end{equation}
In particular,
\begin{equation}
 \Pp_\varepsilon\bigl(
 Z_0(\varepsilon)>K_B\cD_0
 \bigr)
 \le X^{-q/400+o_q(1)}.
 \label{eq:tpc43-zero-high-moment-tail}
\end{equation}
\end{theorem}

\begin{proof}
For each output coordinate \(i\), write
\(S_i=\sum_sA_{i,s}\chi_s\) and let \(D_i\) be its atomic diagonal.
The fiber Cauchy estimate \eqref{eq:tpc43-fiber-Cauchy} gives
\begin{equation}
 \sum_s|A_{i,s}|^2\le\rho_XD_i.
 \label{eq:tpc43-coordinate-coefficient-l2}
\end{equation}
For \(k=0\), one may replace \(\rho_X\) by \(1\).  By
\cref{lem:tpc43-one-coordinate-moment},
\begin{equation}
 \bigl(\E|S_i|^{2q}\bigr)^{1/q}
 =\|S_i\|_{2q}^2
 \le X^{o_q(1)}D_i.
 \label{eq:tpc43-coordinate-Lq-square}
\end{equation}
Minkowski's inequality in \(L^q\) now gives
\begin{align}
 \bigl(\E Z^q\bigr)^{1/q}
 &=\left\|\sum_i|S_i|^2\right\|_{L^q}
 \le\sum_i\||S_i|^2\|_{L^q}
 \le X^{o_q(1)}\sum_iD_i.
 \label{eq:tpc43-Minkowski-moment}
\end{align}
This proves both moment estimates.  Apply Markov with threshold
\(K_B^q\cD_0^q\) when \(\cD_0>0\); if \(\cD_0=0\), the first moment
already gives \(Z_0=0\) almost surely.  Finally use
\(K_B=X^{1/400+o(1)}\) to obtain
\eqref{eq:tpc43-zero-high-moment-tail}.
\end{proof}

The field can be coupled across scales by choosing one sign for every
prime once and for all.

\begin{corollary}[Almost--sure closure on prescribed dyadic packets]
\label{cor:tpc43-almost-sure-dyadic}
Let \(X_r=2^r\), and for each \(r\) fix one deterministic inherited
TPC packet.  For almost every global prime--sign field, all sufficiently
large \(r\) satisfy
\begin{align}
 Z_0(X_r,\varepsilon)&\le K_B(X_r)\cD_0(X_r),
 \label{eq:tpc43-as-zero}\\
 Z_{\rm tr}(X_r,\varepsilon)&\le X_r^{o(1)}\cD_{\rm tr}(X_r).
 \label{eq:tpc43-as-trace}
\end{align}
Consequently both random--model endpoint estimates hold eventually on
that dyadic packet sequence.
\end{corollary}

\begin{proof}
The failure probabilities in
\eqref{eq:tpc43-zero-endpoint-probability} are summable at
\(X_r=2^r\).  For the trace, use
\eqref{eq:tpc43-rho-bound} and set
\begin{equation}
 L_X=\exp\!\left(\frac{\log X}{\sqrt{\log\log X}}\right)=X^{o(1)}.
 \label{eq:tpc43-summable-envelope}
\end{equation}
For sufficiently large \(X\), Markov and
\cref{thm:tpc43-annealed-trace} give a failure probability at most
\begin{equation}
 \Pp_\varepsilon\bigl(Z_{\rm tr}>L_X\cD_{\rm tr}\bigr)
 \le
 \frac{\rho_X}{L_X}
 \le\exp\!\left(-c\frac{\log X}{\sqrt{\log\log X}}\right),
 \label{eq:tpc43-summable-trace-tail}
\end{equation}
which is summable on the dyadic sequence.  The first Borel--Cantelli
lemma proves both assertions; no independence between scales is needed.
\end{proof}

The packet sequence in \cref{cor:tpc43-almost-sure-dyadic} is prescribed.
Uniformity over an additional family of packets requires an explicit
entropy or cardinality ledger and is not asserted.
