\section{Introduction}
\label{sec:tpc43-introduction}

The terminal TPC packet has reached a coefficient--specific arithmetic
gate.  TPC--41 closed the complete same--row alias sector and isolated a
cross--row form whose literal summands contain
\begin{equation}
 \mu(d_\alpha)\mu(d_\beta)
 \mu(m_\alpha j+h+kM)\mu(m_\beta j+h+k'M).
 \label{eq:tpc43-intro-four-mobius}
\end{equation}
TPC--42 then proved that integers within one residue fiber are already
orthogonal in the physical Hilbert coordinates.  The remaining operation
is coherent synthesis across distinct residue fibers, and projective mask
separation reduces each layer to a weighted orbit--slope energy.  Neither
a scalar progression theorem nor a small localization boundary controls
that synthesis \citep{WangTPC41,WangTPC42}.

The present paper asks a narrower question before attempting the
deterministic M\"obius estimate:
\begin{quote}
Does the endpoint fail for generic coefficient fields that preserve the
same squarefree support and the same prime--level multiplicative coupling
as the two physical M\"obius occurrences?
\end{quote}
The answer is no, in a strong exact sense.  Choose one independent sign
\(\varepsilon_p\in\{-1,1\}\) at every relevant prime and put
\begin{equation}
 F_\varepsilon(n)=\mu^2(n)\prod_{p\mid n}\varepsilon_p.
 \label{eq:tpc43-intro-rmf}
\end{equation}
We replace both \(\mu(d_\alpha)\) and
\(\mu(m_\alpha j+h+kM)\) by this same function.  This is not independent
row noise.  All occurrences sharing a prime share its sign, and the
actual M\"obius function is exactly the point
\(\varepsilon_p=-1\) for every prime.

\subsection{Main results}

The first result is a product--fiber theorem.  For a nonzero atom, let
\begin{equation}
 n_{\alpha,j,k}=\ell_\alpha d_\alpha j+h+kM,
 \qquad
 g_{\alpha,j,k}=(d_\alpha,n_{\alpha,j,k}),
 \label{eq:tpc43-intro-ng}
\end{equation}
and attach the squarefree Walsh label
\begin{equation}
 s_{\alpha,j,k}
 =\frac{d_\alpha n_{\alpha,j,k}}{g_{\alpha,j,k}^2}.
 \label{eq:tpc43-intro-label}
\end{equation}
At fixed \((j,k,s)\), choosing
\(g\mid h+kM\) and \(d\mid sg^2\) determines both
\(n=sg^2/d\) and
\begin{equation}
 \ell=\frac{n-h-kM}{dj}.
 \label{eq:tpc43-intro-row-recovery}
\end{equation}
Thus the fiber has divisor--type multiplicity \(X^{o(1)}\).  Walsh
orthogonality, followed by Cauchy--Schwarz only inside these fibers,
proves
\begin{equation}
 \E_\varepsilon
 \sum_k\left(
 \|\mathscr T_{k,\varepsilon}^L\|^2
 +\|\mathscr T_{k,\varepsilon}^R\|^2
 \right)
 \ll X^{o(1)}\cD_{\rm tr}
 \ll X^{o(1)}Q^2JK_B.
 \label{eq:tpc43-intro-trace-theorem}
\end{equation}
This is the full physical trace endpoint in the annealed multiplicative
model.  It retains all deterministic masks and bypasses projective
separation altogether.

The equality alias is exactly diagonal.  There
\((d_\alpha,n_{\alpha,j,0})=1\), so the label is the product
\begin{equation}
 u_{\alpha,j}
 =d_\alpha(\ell_\alpha d_\alpha j+h).
 \label{eq:tpc43-intro-fused-label}
\end{equation}
If two rows share that product, then
\begin{equation}
 j(\ell_\alpha d_\alpha^2-\ell_\beta d_\beta^2)
 =h(d_\beta-d_\alpha).
 \label{eq:tpc43-intro-rigidity-equation}
\end{equation}
The left side is either zero or has magnitude \(\gg J\), whereas the
right side is \(O_h(D_0)=o(J)\).  Hence the rows coincide.  It follows
that
\begin{equation}
 \boxed{
 \E_\varepsilon\left(
 \|\mathscr T_{0,\varepsilon}^L\|^2
 +\|\mathscr T_{0,\varepsilon}^R\|^2
 \right)=\cD_0.}
 \label{eq:tpc43-intro-exact-zero}
\end{equation}
Since \(K_B=X^{1/400+o(1)}\), all but a proportion
\(X^{-1/400+o(1)}\) of prime--sign environments meet the sufficient
equality endpoint.  Fixed Bonami--Beckner moments strengthen this to
\begin{equation}
 \Pp_\varepsilon(Z_0>K_B\cD_0)
 \le X^{-q/400+o_q(1)}
 \label{eq:tpc43-intro-high-tail}
\end{equation}
for every fixed \(q\).  Coupling the signs across scales and applying
Borel--Cantelli gives almost--sure eventual closure along any one fixed
prescribed dyadic packet sequence.

The third result identifies exactly what annealing removes.  For two
zero--alias labels, put
\begin{equation}
 \kappa_{\alpha,\beta,j}
 =\frac{u_{\alpha,j}u_{\beta,j}}
 {(u_{\alpha,j},u_{\beta,j})^2}.
 \label{eq:tpc43-intro-kernel}
\end{equation}
After grouping all deterministic masks and row representations into a
coefficient \(C(\kappa)\), the physical energy is
\begin{equation}
 \boxed{
 \|\mathscr T_0^L\|^2+\|\mathscr T_0^R\|^2
 =\cD_0+\sum_{\kappa>1}\mu(\kappa)C(\kappa).}
 \label{eq:tpc43-intro-corner-spectrum}
\end{equation}
This uses the literal identity
\begin{equation}
 \mu(d_\alpha)\mu(n_\alpha)
 \mu(d_\beta)\mu(n_\beta)
 =\mu(\kappa_{\alpha,\beta,j}).
 \label{eq:tpc43-intro-four-to-one}
\end{equation}
Thus the four signs have been compressed to one M\"obius value on a
squarefree symmetric--difference spectrum.  Randomizing only primes up
to \(z\) deletes exactly those terms whose kernel has a prime factor at
most \(z\), leaving an exact rough--kernel filtration.

Finally, the annealed--to--corner distinction is sharp.  On the divisor
Walsh system of a squarefree product with \(R\) divisors, one may have
mean energy \(R\) and all--minus energy \(R^2\), with the polynomial
vanishing at every other corner.  Hence a small exceptional set can be
concentrated entirely at the physical phase.  No measure selection can
replace a deterministic theorem for
\eqref{eq:tpc43-intro-corner-spectrum}.

\subsection{What has and has not moved}

The results close the generic multiplicative geometry, not the physical
M\"obius point.  In particular, they prove that the following features
do not by themselves force the \(J^2\) coherent loss:
\begin{enumerate}[label=(\roman*)]
 \item squarefree support;
 \item one globally coupled multiplicative sign field at source and
 target;
 \item the actual row masks and opposite--row Hilbert coordinates;
 \item the complete alias trace; and
 \item the endpoint aspect ratios of the triple--prime packet.
\end{enumerate}
What remains is a quenched theorem excluding the all--minus prime point
from a small, potentially structured exceptional set.  We do not call
\eqref{eq:tpc43-intro-trace-theorem} a M\"obius correlation estimate:
for generic prime signs, \(F_\varepsilon*\one=\delta_1\) is false, and
the actual point cannot be selected probabilistically.

\subsection{Organization}

\Cref{sec:tpc43-interface} records the exact inherited terminal object.
\Cref{sec:tpc43-prime-sign} defines the consistent multiplicative
deformation.  \Cref{sec:tpc43-product-fibers} proves the divisor fiber
bound, and \cref{sec:tpc43-annealed-trace} applies it to the full trace.
\Cref{sec:tpc43-zero-rigidity} proves singleton fibers at equality.
\Cref{sec:tpc43-moments} gives hypercontractive and almost--sure
extensions.  \Cref{sec:tpc43-Walsh-corner} derives the exact physical
kernel spectrum, while \cref{sec:tpc43-sharp-boundaries} proves its
sharp selection obstruction.  The final sections compare adjacent
literature, state the next deterministic gate, and delimit the exact
certificate.
