\section{Literature comparison and method boundary}
\label{sec:tpc43-literature}

Random multiplicative functions have a substantial literature.  In the
standard Rademacher model the prime values are independent signs and the
function is supported on squarefree integers; in the Steinhaus model the
prime values are independent Haar phases.  Their partial sums and moments
exhibit behavior very different from sums of independent integer--indexed
variables; see, for example,
\citet{HeapLindqvist2016,Harper2019HighMoments,Harper2020LowMoments}.
The present theorem is not a new general moment theorem for those models.
Its new input is the TPC--specific product--fiber calculation in
\cref{lem:tpc43-kernel-fiber-bound}, which permits one globally coupled
prime field to pass through the physical source and target simultaneously.
For integral \(q\), Probability Result~2.3 of
\citet{Harper2019HighMoments} gives the exact weighted inequality
\begin{equation}
 \E\left|\sum_{n\le N}a_nF_\varepsilon(n)\right|^{2q}
 \le\left(
  \sum_{n\le N}|a_n|^2d_{2q-1}(n)
 \right)^q.
 \label{eq:tpc43-Harper-weighted-moment}
\end{equation}
Here \(d_r\) denotes the \(r\)-fold divisor function.
On a squarefree kernel \(s\),
\(d_{2q-1}(s)=(2q-1)^{\omega(s)}\), so this is exactly the
coordinate estimate used in
\cref{lem:tpc43-one-coordinate-moment}.  Its underlying cube inequality
goes back to \citet{Bonami1970,Beckner1975}.  The subsequent
Hilbert--energy estimate is packet specific and follows by fiberwise
Cauchy--Schwarz and Minkowski; no asymptotic theorem for unweighted random
partial sums is imported.

\subsection{Why this is not another external phase bank}

TPC--39 used additive alias phases to recover the equality bucket, and
TPC--40 proved a sharp recovery--decorrelation uncertainty principle for
external row and alias frames \citep{WangTPC40}.  An independent sign on
each row, or a complete Dirichlet--character average separating distinct
row residues, would give an immediate diagonal second moment.  Such a
calculation is generic linear algebra and cannot recover the prescribed
untwisted column at low amplification.

Here the deformation instead replaces the two actual M\"obius occurrences
by the same squarefree--supported multiplicative field.  Prime factors
shared by different source and target integers therefore create genuine
dependencies.  The divisor fibers in
\eqref{eq:tpc43-kernel-fiber-divisor-bound}, and their exact collapse at
\(k=0\), are what make the annealed theorem work.  No recovery map is
applied, and \(F_{-\one}=\mu\) is one member of the coefficient family.
This places the result on the coefficient--specific side of the boundary
left open by TPC--40.

\subsection{Adjacent deterministic multiplicative correlations}

There are powerful deterministic results for averaged or fixed--complexity
systems of multiplicative functions.  The theorem of
\citet{MatomakiRadziwillTao2015} averages fixed--order correlations over
their additive shifts, including the two--point case.  Tao proved the
logarithmically averaged two--point Chowla and Elliott statements for
fixed affine forms \citep{Tao2016}.  Higher uniformity in short intervals
on average and applications to averaged polynomial patterns were
established by \citet{MRTTZ2023}.  More recently,
\citet{MatthiesenTeravainenWang2026} obtained arbitrary logarithmic
savings for a specified class of fixed polynomial systems satisfying
explicit degree--separation hypotheses, and
\citet{BanksShparlinski2026} obtained logarithmic savings for sums with
the factor \(\mu(n_1n_2n_3)\) constrained by one equation
\(f(n_1)+g(n_2)+\wp(n_3)=M\), under their injectivity, bounded--weight,
and scale hypotheses.

None of these theorems directly supplies the physical TPC estimate.
The averaged Chowla theorem does not select the fixed shift \(h\).
Tao's two--point theorem does allow fixed affine forms, but its orbit
average is logarithmically weighted and its coefficients are fixed as
the asymptotic parameter tends to infinity; it supplies no uniformity
for the \(X\)-dependent slopes \(m_\alpha,m_\beta\), nor for their
coherent weighted summation.  In the equality column those slopes satisfy
\begin{equation}
 m_\alpha\asymp Q
 =J^{267/133+o(1)},
 \label{eq:tpc43-moving-slope-size}
\end{equation}
and the target is a specific weighted quadratic form over many rows.
The results on polynomial patterns use fixed systems and average a
common translation.  The Banks--Shparlinski theorem has one separable
additive constraint and does not contain the two shared-\(j\) product
slopes in \eqref{eq:tpc43-intro-four-mobius}.  A theorem for each fixed
row pair would also not automatically survive the coherent row summation
at the required endpoint.

The exact kernel compression
\eqref{eq:tpc43-physical-kernel-spectrum} suggests a different comparison:
one now seeks M\"obius cancellation against the packet--generated
coefficient \(C(\kappa)\).  That coefficient is not presently known to
belong to any coefficient class controlled by the cited theorems---for
example, a fixed polynomial/nilsequence family or a family admitting a
bounded--complexity separable additive representation.  We therefore use
the cited results only to mark the current boundary, not as black boxes proving
\eqref{eq:tpc43-remaining-kernel-bound}.

\subsection{Scope of the probabilistic language}

``Annealed'' refers to expectation over the prime signs while keeping the
entire TPC packet fixed.  ``Almost surely along a prescribed dyadic
sequence'' refers to one global prime field and one fixed deterministic
packet at each scale.  No statement is made uniformly over all possible
packets or about the distinguished all--minus point.  The one--corner
extremizer in \cref{thm:tpc43-one-corner-extremizer} shows that these
qualifications cannot be dropped by measure theory alone.
