\section{The annealed--to--quenched gate}
\label{sec:tpc43-next-gate}

The preceding theorems separate two statements that were previously
mixed together.  The packet geometry is generically compatible with the
endpoint: a single multiplicative prime field diagonalizes the equality
alias exactly and controls the remaining aliases through subpolynomial
product fibers, so almost every such field closes the full trace.  The
physical M\"obius function is nevertheless
one specified point of that field, not a random draw that may be selected
after the energy is measured.

By \cref{thm:tpc43-four-to-one-compression}, the exact remaining
equality theorem is the one--sided bound
\begin{equation}
 \sum_{\kappa>1}\mu(\kappa)C(\kappa)
 \le X^{o(1)}K_BQ^2J,
 \label{eq:tpc43-remaining-kernel-bound}
\end{equation}
with \(C(\kappa)\) defined by the actual masks and row pairs in
\eqref{eq:tpc43-Walsh-spectrum-coefficient}.  The already controlled
diagonal \(\cD_0\) is harmless at this scale.  Formula
\eqref{eq:tpc43-remaining-kernel-bound} is a compression of the physical
four--M\"obius gate; it is not a known M\"obius orthogonality theorem,
because the coefficients aggregate growing affine slopes and may be
highly correlated with \(\kappa\).

Three precise continuations remain.
\begin{enumerate}[label=(\alph*)]
 \item \textbf{Rough--kernel descent.}
 Use \cref{cor:tpc43-rough-kernel-filtration} to estimate the spectrum
 with \(P^-(\kappa)>z\), then control the successive small--prime
 increments without paying their number absolutely.

 \item \textbf{Walsh spectral flatness.}
 Prove a coefficient estimate for
 \(C(\kappa)\), such as a sufficiently strong weighted \(\ell^2\) or
 divisor--fiber bound, and combine it with a M\"obius estimate adapted to
 the resulting kernel support.  Parseval
 \eqref{eq:tpc43-Walsh-Parseval} measures the exact annealed variance,
 but by \cref{thm:tpc43-one-corner-extremizer} variance alone is
 insufficient.

 \item \textbf{Prime--phase de--randomization.}
 Prove directly that the all--minus phase cannot lie in the coherent
 exceptional set for the actual TPC coefficient system.  Such a result
 must exploit arithmetic information beyond multiplicativity and
 squarefree support; an abstract selection from a measure--one set cannot
 identify a prescribed phase point.
\end{enumerate}

The first route is now the most concrete next layer: it turns a
four--sign row interaction into a single squarefree--kernel spectral sum
and exhibits an exact prime filtration.

\subsection{Claim boundary}

This paper does not prove \eqref{eq:tpc43-remaining-kernel-bound} at the
physical point.  It proves no fixed--shift Chowla estimate, no
deterministic orbit--slope Bessel theorem for the M\"obius coefficients,
no parity breach, no Hardy--Littlewood prime--pair asymptotic, and no
infinitude of twin primes.  ``Almost every prime--sign field'' never
means ``the M\"obius field'': the latter is the distinguished all--minus
point, and \cref{thm:tpc43-one-corner-extremizer} proves that this
logical distinction is sharp.
