\section{Sharp annealed--to--corner boundaries}
\label{sec:tpc43-sharp-boundaries}

The exceptional set in an annealed theorem can contain the specified
all--minus point.  This is not a technical possibility: Walsh systems
admit exact extremizers.

\begin{theorem}[A one--corner extremizer]
\label{thm:tpc43-one-corner-extremizer}
Let \(P=p_1\cdots p_s\) be squarefree and let
\(\cU=\{u:u\mid P\}\), so \(R:=|\cU|=2^s\).  Define
\begin{equation}
 Y(\varepsilon)
 :=\sum_{u\mid P}\mu(u)\chi_u(\varepsilon).
 \label{eq:tpc43-extremizer-sum}
\end{equation}
Then the labels are distinct and orthogonal,
\begin{align}
 Y(\varepsilon)
 &=\prod_{p\mid P}(1-\varepsilon_p),
 \label{eq:tpc43-extremizer-product}\\
 \E|Y|^2&=R,
 \label{eq:tpc43-extremizer-mean}\\
 |Y(-\one)|^2&=R^2,
 \label{eq:tpc43-extremizer-corner}
\end{align}
and \(Y\) vanishes at every other point of the \(s\)-dimensional sign
cube.  Thus the corner--to--annealed energy ratio is exactly \(R\), and
Markov's inequality is sharp on this multiplicative Walsh class.
\end{theorem}

\begin{proof}
Expanding \(\prod_{p\mid P}(1-\varepsilon_p)\) gives
\eqref{eq:tpc43-extremizer-sum}.  The orthogonality of its \(R\) Walsh
characters gives \(\E|Y|^2=R\).  At the all--minus point every factor is
two, so \(Y(-\one)=2^s=R\).  At any other point one factor vanishes.
\end{proof}

The same ratio is obtained from any \(R\) pairwise distinct squarefree
labels of the same M\"obius parity, with equal unit coefficients in one
coherent output coordinate.  In particular, the fused--label injectivity of
\cref{lem:tpc43-fused-label-injectivity} does not by itself control the
physical corner; it is exactly the property that makes the annealed
constant term diagonal.

\begin{remark}[No universal row theorem]
\label{rem:tpc43-no-universal-row-theorem}
The physical orbit matrix has only \(O(J)\) output times and polynomially
many source rows.  A Bessel inequality required for every row coefficient
direction must therefore pay the usual rank--trace lower bound.  This is
the dimension obstruction already isolated in TPC--40, and is why
TPC--42 restricted its proposed orbit--slope theorem to the actual
projective directions.  The present random theorem goes further in a
different direction: it retains the complete physical coefficient field
and proves that almost every consistent multiplicative prime environment
avoids the coherent mode.
\end{remark}

\begin{remark}[What the model does not preserve]
\label{rem:tpc43-random-convolution-boundary}
For generic \(\varepsilon\), one has
\(F_\varepsilon*\one\ne\delta_1\); only the distinguished all--minus
point recovers \(F_{-\one}=\mu\) and hence the M\"obius inversion
identity \(\mu*\one=\delta_1\).  Therefore
\cref{thm:tpc43-annealed-trace} is a theorem for the randomized terminal
interface, not a randomized proof about primes.  It preserves the exact
squarefree support, multiplicative coupling, masks, aliases, and Hilbert
geometry that occur at the final gate; it deliberately does not preserve
every special algebraic identity of the distinguished M\"obius point.
\end{remark}
