\begin{abstract}
The fixed-shift TPC packet now has exact coordinate, selection, prime-fiber,
native-alias, high-face, missing-reassembly, and cofactor-exposure interfaces,
but their conclusions carry different quantifiers and several are only
certificates for one proof architecture.  We give a quantifier-safe closure
calculus for this chain.

For a nonzero positive semidefinite parent form \(R\) and a final physical
map \(F\), let \(N=\Ker R\), \(S=N^\perp\), and \(W=F(N)\).  The optimal
coefficient-uniform transfer constant is exactly
\[
 \alpha(F;R)=
 \lambda_{\min}\!\left(
 R_S^{-1/2}F_S^*P_{W^\perp}F_SR_S^{-1/2}
 \right),
\]
and \(\alpha(F;R)>0\) if and only if
\(\Ker F\subseteq\Ker R\).  Using classical shorted-operator theory, with
self-contained finite-dimensional proofs, we apply transitivity on nested
retained spaces: sequential elimination of genuine nuisance directions
equals one master shorting, whereas ordinary compression can be strictly
wrong.
This separates mandatory kernel gates from sufficient certificates whose
failure proves nothing about the final map.

For a finite selector family \((S_a)\), we prove the strict quantifier gap
\[
 \sup_a\inf_{z\ne0}\frac{\|S_az\|^2}{\|z\|^2}
 \le
 \inf_{z\ne0}\sup_a\frac{\|S_az\|^2}{\|z\|^2}.
\]
Thus an adaptive good phase sector or dyadic block need not produce one
frozen selector with a uniform lower bound.  Retaining the selector label by
direct sum gives the exact uniform constant
\(\lambda_{\min}(\sum_aS_a^*S_a)\), but erasing that label is a new
reassembly problem.

We also order the reassembly certificates.  The master shorted constant
dominates every reverse-triangle lower certificate; the physical restricted
Gram dominates both residual-factor and ambient-degree relaxations, while
those two coarse relaxations are generally incomparable.  Finally, if the
unit-column missing Gram has \(\kappa_M\ge1+L\), then some row and one of
\(B\) literal correlation cells carry alias mass at least \(L/B\).  With at most
\(\Delta\) neighbors in that cell, one normalized pair has magnitude at
least \(L/(B\Delta)\).  Hence overlap degree
\(X^{\delta+o(1)}\) and pair correlation
\(X^{-\tau+o(1)}\) imply
\(\nu_M\le(\delta-\tau)_+\).  On the TPC--61 carrier these entries are the
explicit fixed-\(h_0\) two-affine M\"obius/determinant sums.  This localizes
a large alias obstruction; it does not estimate a M\"obius correlation.

A three-gate theorem closes only the declared truncated packet when the
represented-chain, reassembly, and downstream losses are proved in the same
scope and sum to less than \(1/400\).  We give sharp independence models and
kill/pivot rules.  No fixed-shift parity improvement, prime-pair lower bound,
or twin-prime consequence is asserted.
\end{abstract}
