\section{Adaptive selectors and the quantifier barrier}
\label{sec:tpc62-adaptive-selectors}

Several earlier TPC reductions locate, for each coefficient vector, a
sector, block, or face carrying a definite portion of its mass.  Such a
statement has the quantifier order
\[
 \text{for every }z\text{ there exists a label }a=a(z).
\]
It does not by itself provide one label which works for every coefficient
vector.  This section isolates that distinction as finite-dimensional
linear algebra.  No arithmetic input is used.

\subsection{The two selector constants}

Let \(\cK\ne\{0\}\) be a finite-dimensional complex Hilbert space, let
\(\cA\) be a finite nonempty label set, and let
\begin{equation}
 S_a:\cK\longrightarrow\cH_a
 \qquad(a\in\cA)
 \label{eq:tpc62-selector-family}
\end{equation}
be linear maps into finite-dimensional Hilbert spaces.  For \(z\ne0\),
put
\begin{equation}
 q_a(z):=\frac{\|S_az\|^2}{\|z\|^2}.
 \label{eq:tpc62-selector-Rayleigh}
\end{equation}
The adaptive and fixed-label lower constants are respectively
\begin{align}
 \lambda_{\rm ad}
 &:=\inf_{z\ne0}\max_{a\in\cA}q_a(z),
 \label{eq:tpc62-adaptive-constant}\\
 \lambda_{\rm fix}
 &:=\max_{a\in\cA}\inf_{z\ne0}q_a(z)
   =\max_{a\in\cA}\lambda_{\min}(S_a^*S_a).
 \label{eq:tpc62-fixed-constant}
\end{align}
The extrema exist because the unit sphere is compact and \(\cA\) is
finite.

\begin{theorem}[Quantifier-safe minimax inequality]
\label{thm:tpc62-selector-minimax}
For every family \eqref{eq:tpc62-selector-family},
\begin{equation}
 \boxed{
 \sup_{a\in\cA}\inf_{z\ne0}q_a(z)
 \quad\le\quad
 \inf_{z\ne0}\sup_{a\in\cA}q_a(z).}
 \label{eq:tpc62-minimax-order}
\end{equation}
Equivalently, \(\lambda_{\rm fix}\le\lambda_{\rm ad}\).  Consequently,
for any \(c>0\),
\begin{align}
 \lambda_{\rm ad}\ge c
 &\quad\Longleftrightarrow\quad
 (\forall z\ne0)(\exists a\in\cA):
 \|S_az\|^2\ge c\|z\|^2,
 \label{eq:tpc62-forall-exists}\\
 \lambda_{\rm fix}\ge c
 &\quad\Longleftrightarrow\quad
 (\exists a\in\cA)(\forall z\ne0):
 \|S_az\|^2\ge c\|z\|^2.
 \label{eq:tpc62-exists-forall}
\end{align}
The first statement does not imply the second.
\end{theorem}

\begin{proof}
For every fixed pair \((a,z)\),
\[
 \inf_{w\ne0}q_a(w)\le q_a(z)
 \le\sup_{b\in\cA}q_b(z).
\]
Taking the supremum over \(a\) in the left member and then the infimum
over \(z\) in the right member proves
\eqref{eq:tpc62-minimax-order}.  The two logical equivalences are merely
the definitions of the two constants, together with attainment of the
finite maximum and the compact-sphere minima.  The failure of the converse
is witnessed quantitatively by the next example.
\end{proof}

\begin{example}[Coordinate projections give a strict gap]
\label{ex:tpc62-coordinate-selector-gap}
Fix \(r\ge2\), take \(\cK=\C^r\), \(\cA=\{1,\ldots,r\}\), and let
\[
 S_a z=z_a\in\C.
\]
For every \(z\ne0\),
\[
 \max_{1\le a\le r}\frac{|z_a|^2}{\|z\|^2}\ge\frac1r,
\]
with equality at \(z=r^{-1/2}(1,\ldots,1)\).  Hence
\begin{equation}
 \lambda_{\rm ad}=\frac1r.
 \label{eq:tpc62-coordinate-adaptive}
\end{equation}
On the other hand, each \(S_a\) has a nonzero kernel, and therefore
\begin{equation}
 \lambda_{\rm fix}=0.
 \label{eq:tpc62-coordinate-fixed}
\end{equation}
Thus a label can always be chosen after seeing \(z\), but no single label
has any positive lower bound on all directions.  The gap is not a limiting
or measurability artifact: it occurs in a finite family of coordinate
projections in finite dimension.
\end{example}

The same example remains valid after multiplying every \(S_a\) by any
common scale.  It therefore obstructs not only a constant lower bound but
also any attempted fixed-power upgrade which preserves the same selector
family: an adaptive gain \(X^{-\lambda}\) does not produce a fixed label
with gain \(X^{-\lambda+o(1)}\).

\subsection{Uniformization by retaining the label}

There is a legitimate way to keep all adaptive alternatives without
reversing their quantifiers: retain the selector label as an orthogonal
output coordinate.  Define the labelled analysis map
\begin{equation}
 \mathsf S:\cK\longrightarrow
 \bigoplus_{a\in\cA}\cH_a,
 \qquad
 \mathsf Sz:=(S_az)_{a\in\cA}.
 \label{eq:tpc62-labelled-analysis-map}
\end{equation}

\begin{theorem}[Exact labelled direct-sum uniformization]
\label{thm:tpc62-labeled-uniformization}
The optimal coefficient-uniform constant for the label-retaining map is
\begin{equation}
 \boxed{
 \lambda_{\rm lab}
 :=\inf_{z\ne0}\frac{\|\mathsf Sz\|^2}{\|z\|^2}
 =\lambda_{\min}\!\left(\sum_{a\in\cA}S_a^*S_a\right).}
 \label{eq:tpc62-labelled-exact-constant}
\end{equation}
Moreover,
\begin{equation}
 \boxed{
 \lambda_{\rm ad}\le\lambda_{\rm lab}
 \le |\cA|\lambda_{\rm ad}.}
 \label{eq:tpc62-labelled-adaptive-comparison}
\end{equation}
In particular, an adaptive bound \(\lambda_{\rm ad}\ge c\) gives the
genuine uniform labelled inequality
\begin{equation}
 \sum_{a\in\cA}\|S_az\|^2\ge c\|z\|^2
 \qquad(z\in\cK).
 \label{eq:tpc62-labelled-uniform-lower}
\end{equation}
Conversely, \(\lambda_{\rm lab}\ge L\) implies only the adaptive bound
\(\lambda_{\rm ad}\ge L/|\cA|\) without further information.
\end{theorem}

\begin{proof}
Orthogonality of the labelled summands gives
\begin{align*}
 \|\mathsf Sz\|^2
 &=\sum_{a\in\cA}\|S_az\|^2\\
 &=\left\langle
     \left(\sum_{a\in\cA}S_a^*S_a\right)z,z
   \right\rangle.
\end{align*}
Rayleigh--Ritz proves \eqref{eq:tpc62-labelled-exact-constant}.  Pointwise
in \(z\ne0\),
\[
 \max_a q_a(z)
 \le\sum_a q_a(z)
 \le |\cA|\max_a q_a(z).
\]
Taking the infimum over \(z\) proves
\eqref{eq:tpc62-labelled-adaptive-comparison}, and the two consequences
follow immediately.
\end{proof}

For the coordinate family in
\cref{ex:tpc62-coordinate-selector-gap}, one has
\[
 \sum_{a=1}^rS_a^*S_a=I_{\C^r},
 \qquad
 \lambda_{\rm lab}=1,
\]
even though \(\lambda_{\rm fix}=0\).  Nothing contradictory has happened:
the direct sum retains all \(r\) labels, whereas a fixed selector retains
only one.

\subsection{Label retention is not physical reassembly}

The labelled theorem changes the output space.  A later map which erases
or recombines the label can restore the very cancellations that the direct
sum prevented.  This is an independent gate.

\begin{proposition}[Recombination requires a new lower certificate]
\label{prop:tpc62-recombination-new-gate}
Positivity of \(\lambda_{\rm lab}\) alone gives no universal positive
coefficient-uniform lower bound after an arbitrary linear recombination
\[
 \mathsf C:\bigoplus_{a\in\cA}\cH_a\longrightarrow\cH.
\]
Precisely, there exist a labelled map with \(\lambda_{\rm lab}>0\) and a
recombination \(\mathsf C\) for which \(\mathsf C\mathsf S\) has lower
constant zero.  There also exist a bounded-below represented map
\(A=\mathsf S\) and a missing map \(M\) for which \(A+M\) has lower
constant zero.
\end{proposition}

\begin{proof}
For the first assertion, take \(\cK=\C^2\),
\(S_1(z_1,z_2)=z_1\), \(S_2(z_1,z_2)=z_2\), and
\[
 \mathsf C(y_1,y_2)=y_1+y_2.
\]
Then \(\mathsf S=I_{\C^2}\) and \(\lambda_{\rm lab}=1\), while
\(\mathsf C\mathsf S(1,-1)=0\).  Thus the recombined map has lower
constant zero.

For the second assertion, on the labelled output space take
\(A=\mathsf S\) and \(M=-\mathsf S\).  Then \(A\) has lower constant
\(\lambda_{\rm lab}>0\), but \(A+M=0\).  Hence neither label retention
nor a represented lower bound controls signed reassembly without an
additional angle, defect, or exact shorted-Gram estimate.
\end{proof}

The correct scope statement is therefore
\begin{equation}
 \boxed{
 \text{adaptive selector}
 \;\Longrightarrow\;
 \text{uniform labelled direct sum}
 \;\not\Longrightarrow\;
 \text{uniform physical recombination}.}
 \label{eq:tpc62-selector-scope-chain}
\end{equation}
The first arrow is
\cref{thm:tpc62-labeled-uniformization}; the failed second arrow is
\cref{prop:tpc62-recombination-new-gate}.  To pass the second arrow one
must analyze the actual physical recombination and, when an undeleted
represented map \(A\) is perturbed by a missing contribution \(M\), the
actual map \(A+M\).  The exact shorted constant and its certificate
lattice are developed in the next section.

\subsection{Scope audit}

All results in this section are L0 finite-dimensional statements.  They
make three claims and no others.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=2.4em]
 \item An adaptive selector does not supply a fixed coefficient-uniform
       selector.
 \item Retaining the selector label gives a different, rigorously uniform
       direct-sum map with exact constant
       \(\lambda_{\min}(\sum_aS_a^*S_a)\).
 \item Dropping or recombining that label, or adding a missing signed map,
       requires a separate reassembly theorem.
\end{enumerate}
In particular, no sector, block, or label identified after inspecting a
coefficient vector is promoted here to one physical label valid for all
vectors.  No estimate for a fixed arithmetic shift, no parity
improvement, and no prime-pair lower bound follows from this section.
