\section{Result ledger, claim boundary, and the next theorem}
\label{sec:tpc62-claims-next}

TPC--62 turns the TPC--53--TPC--61 interfaces into an exact decision system.
It does not fill the remaining arithmetic inputs.  This final section
separates the two achievements.

\subsection{Result ledger}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.22\textwidth}
                >{\raggedright\arraybackslash}p{0.53\textwidth}
                >{\raggedright\arraybackslash}p{0.14\textwidth}}
\toprule
Object & Exact conclusion & Status\\
\midrule
Master transfer
& The optimal full-coefficient-space uniform constant from a nonzero
  semidefinite parent form to a final map is the projected shorted-Gram eigenvalue in
  \eqref{eq:tpc62-intro-master-eigenvalue}.
& L0 theorem\\
\addlinespace
Kernel criterion
& Positive finite-scale full-space uniform transfer holds exactly when
  \(\Ker F\subseteq\Ker R\).
& L0 iff test\\
\addlinespace
Nested nuisance elimination
& Shorting to nested retained spaces is transitive; sequential exact
  elimination equals one master shorting.
& L0 theorem\\
\addlinespace
Mandatory/certificate split
& A mandatory factor with a positive-energy kernel direction kills every
  final map factoring through it; a zero sufficient-certificate constant
  need not kill the physical map.
& L0 decision\\
\addlinespace
Selector quantifiers
& Frozen selector max--min is at most adaptive min--max, with a sharp
  coordinate-projection gap.
& L0 theorem\\
\addlinespace
Labeled uniformization
& Retaining all selector labels by direct sum has exact constant
  \(\lambda_{\min}(\sum_aS_a^*S_a)\); label erasure is a new map.
& L0 theorem\\
\addlinespace
Certificate order
& The exact shorted constant dominates valid reverse-triangle bounds;
  restricted \(\kappa_M\) dominates residual and ambient relaxations,
  which are generally incomparable.
& L0 partial order\\
\addlinespace
Alias localization
& \(\kappa_M\ge1+L\) forces a row of alias mass \(L\), a literal cell of
  mass \(L/B\), and a pair/star witness after a degree bound.
& L0 inverse theorem\\
\addlinespace
Degree--pair bridge
& Row degree \(X^{\delta+o(1)}\) and pair bound
  \(X^{-\tau+o(1)}\) imply
  \(\nu_M\le(\delta-\tau)_+\).
& L0 theorem; L1 target\\
\addlinespace
Literal alias entry
& Each TPC--61 entry is the fixed-\(h_0\) weighted two-affine M\"obius
  correlation, equivalently its determinant-cell sum.
& L1 identity\\
\addlinespace
Three-module closure
& Compatible represented, reassembly, and downstream lower constants
  multiply; exponents must sum strictly below \(1/400\).
& L0 theorem; fixed-\(h_0\) application conditional L1\\
\addlinespace
Independence models
& Small raw missing mass, prime-block isometry, or good upstream constants
  do not separately prevent exact coherent reassembly cancellation.
& L0 sharpness\\
\bottomrule
\end{tabular}
\end{center}

These statements reduce ambiguity.  They do not make an unproved input
positive.

\subsection{What is not proved}

The following conclusions are absent.
\begin{enumerate}[leftmargin=2.3em]
 \item The master arithmetic constant \(\alpha_X\) is not shown to be
       bounded below by \(X^{-\lambda+o(1)}\) for any
       \(\lambda<1/400\).
 \item The actual retained relation is not shown to have positive exposure
       on every active row, nor is the missing mass shown to save a fixed
       power in a uniform or distinguished scope.
 \item Critical-window occupancy, terminal activation, singleton survival,
       represented native transfer, boundary reconnection, and the tail
       estimate are not jointly established on one carrier.
 \item No frozen phase sector or dyadic block is shown to work uniformly for
       every coefficient vector.  Adaptive selection is not relabeled
       uniform.
 \item The actual normalized collision graph is not shown to have degree
       \(X^{\delta+o(1)}\) with a favorable \(\delta\).
 \item No new upper bound is proved for the weighted correlation
       \(\mu(mj+h_0)\mu(m'j+h_0)\), for its determinant form, or for a
       dyadic row-star.
 \item Consequently \(\kappa_M=X^{o(1)}\),
       \(\nu_M<\sigma_M-\lambda_{\rm rep}\), and
       \(\lambda_{\rm reasm}=0\) are not proved for the physical family.
 \item No positive fixed-shift parity estimate, prime-pair lower bound,
       prime-pair asymptotic, or twin-prime implication is obtained.
\end{enumerate}

In particular, \(h_0\) has not been specialized to \(2\).  Merely making
that substitution in an L1 identity would not supply the missing carrier,
correlation, reassembly, downstream, or target-identification theorems.

In particular, the phrase ``localized alias obstruction'' means that a
large eigenvalue must leave a literal witness.  It does not say that the
witness is small.  Likewise, the conditional closure theorem concludes a
lower bound only for the declared truncated packet form named in its
hypotheses.  Identifying that form with a number-theoretic target requires
the separately listed downstream theorem.

\subsection{The next arithmetic theorem}

The new calculus narrows the next useful theorem to a concrete alternative.

\begin{enumerate}[label=\textbf{Route \arabic*.},leftmargin=4.3em]
 \item \emph{Exposure first.}  Reopen the construction of the retained
       relation \(\cI_X\) and prove, in one declared scope,
       \begin{equation}
        \cD_M(z)
        \le X^{-\sigma_M+o(1)}\cD_{\rm ref}(z),
        \qquad \sigma_M>0.
        \label{eq:tpc62-next-exposure-target}
       \end{equation}
       Uniformly this requires every active row; distinguishedly it requires
       the exact weights \(W_H(m)|z_m|^2\).

 \item \emph{Represented reference in the same scope.}  Establish
       \begin{equation}
        \|A_Xz\|^2
        \ge X^{-\lambda_{\rm rep}+o(1)}
             \cD_{\rm ref}(z)
        \label{eq:tpc62-next-represented-target}
       \end{equation}
       after proving the actual critical occupancy and terminal activation
       used to define \(A_X\).

 \item \emph{Alias degree and cancellation.}  On literal dyadic
       determinant cells, prove either a pair/star estimate
       \begin{equation}
        |K_{m,n}|\le X^{-\tau+o(1)}\quad(m\ne n),
        \qquad
        \Delta_X\le X^{\delta+o(1)},
        \label{eq:tpc62-next-alias-target}
       \end{equation}
       strong enough that
       \begin{equation}
        \sigma_M>
        \lambda_{\rm rep}+(\delta-\tau)_+,
        \label{eq:tpc62-next-localized-threshold}
       \end{equation}
       or compute a large row/cell witness that closes this subroute and
       directs attention to exact shorting.

 \item \emph{Exact reassembly alternative.}  If the degree--pair route is
       too weak, estimate the master shorted Gram or the signed physical
       cross term directly.  Apply the kernel tests before any asymptotic
       eigenvalue analysis.

 \item \emph{Downstream theorem.}  Only after one reassembly route is
       quantified should the boundary and tail maps be reconnected and the
       full strict ledger \eqref{eq:tpc62-complete-ledger} be tested.
\end{enumerate}

The first two routes prevent a sophisticated alias estimate from being
spent on an unrepresented carrier.  The third turns every large operator
obstruction into an explicit determinant cell, so failure is informative
rather than merely numerical.

\subsection{Possible outcomes}

The next layer has three publishable outcomes with different strengths.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item A favorable exposure and alias estimate opens the restricted
       mass--degree route and supplies a zero-cost reassembly input.  It
       gives a conditional L1 packet lower bound only after the compatible
       represented and downstream modules also pass the strict ledger.
 \item A rank or kernel witness closes its matching architecture exactly;
       a localized-cell witness that violates the proposed norm hypothesis
       closes that narrower subroute and supplies an explicit pivot.
 \item A theorem valid only for adaptive selectors, averaged shifts, or a
       distinguished vector remains useful in that scope, provided it is
       not promoted to the uniform fixed-shift route.
\end{enumerate}

\paragraph{Conclusion.}
The TPC--53--TPC--61 sequence has not crossed the parity barrier.  It has
replaced a loosely connected heuristic with a literal packet, exact
finite-dimensional gates, sharp no-go tests, and one explicit remaining
alias kernel.  TPC--62 adds the master closure constant, quantifier calculus,
certificate order, and localization inverse theorem.  The surviving road is
therefore narrower and falsifiable: prove actual cofactor exposure, prove a
represented reference, and then control or exhibit one literal alias
row/cell strongly enough to pass the single reassembly gate.  That is a
precise next problem, not a claim that it has already been solved.
