\section{A three-module conditional closure theorem}
\label{sec:tpc62-conditional-closure}

The master constant in \cref{sec:tpc62-master-shorted} is the exact answer
for a complete finite-scale map.  A proof rarely estimates it in one step.
This section gives the precise modular statement that permits three lower
constants to be multiplied.  Its hypotheses include the carrier and
quantifier compatibility that is often suppressed in an informal ledger.

\subsection{Compatible form chains}

Let \(Z_X\subseteq\cH_X\) be either a declared coefficient class or the
singleton \(\{z_*(X)\}\).  Let
\begin{equation}
 \cQ_0,\quad \cQ_A,\quad \cQ_F,\quad \cQ_{\rm out}
 \label{eq:tpc62-four-forms}
\end{equation}
be nonnegative quadratic forms on the same original coefficient space.
Their intended meanings are parent input, represented output, full
represented-plus-missing output, and downstream reconnected output.

\begin{definition}[Compatible three-module chain]
\label{def:tpc62-compatible-three-module-chain}
The four forms in \eqref{eq:tpc62-four-forms} form a compatible chain on
\(Z_X\) if:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item every form is computed from the same initial vector \(z\);
 \item the output carrier and raw normalization used in one comparison are
       literally the input carrier and normalization used in the next;
 \item all maps and supports are fixed before \(z\), for a uniform chain;
 \item every adaptive label is retained in the next output, or else a
       separate proved reassembly inequality is inserted;
 \item no inequality is imported from a different shift, an averaged
       family, or an independently chosen coefficient vector.
\end{enumerate}
\end{definition}

\begin{theorem}[Three-module closure]
\label{thm:tpc62-three-module-closure}
Suppose the chain is compatible on \(Z_X\).  Let
\(c_A(X)\), \(\delta_{\rm reasm}(X)\), and \(c_{\rm out}(X)\) be finite
nonnegative constants, and suppose
\begin{align}
 \cQ_A(z)&\ge c_A(X)\cQ_0(z),
 \label{eq:tpc62-represented-module-lower}\\
 \cQ_F(z)&\ge \delta_{\rm reasm}(X)\cQ_A(z),
 \label{eq:tpc62-reassembly-module-lower}\\
 \cQ_{\rm out}(z)&\ge c_{\rm out}(X)\cQ_F(z)
 \label{eq:tpc62-downstream-module-lower}
\end{align}
for every \(z\in Z_X\).  Then
\begin{equation}
 \boxed{
 \cQ_{\rm out}(z)
 \ge c_{\rm out}(X)\delta_{\rm reasm}(X)c_A(X)\cQ_0(z)}
 \label{eq:tpc62-three-module-product}
\end{equation}
for every \(z\in Z_X\).

If \(Z_X\) is the full declared coefficient class, the conclusion is
uniform.  If \(Z_X=\{z_*(X)\}\), it is distinguished only.
\end{theorem}

\begin{proof}
If \(\cQ_0(z)=0\), or if any of the three constants is zero, the
right-hand side of \eqref{eq:tpc62-three-module-product} is zero and the
conclusion follows from nonnegativity of \(\cQ_{\rm out}\).  Otherwise all
three constants are positive.  The first lower bound then makes
\(\cQ_A(z)>0\), and the second makes \(\cQ_F(z)>0\).  The three
inequalities may therefore be applied successively to the actual
intermediate forms generated by the same \(z\).  Multiplication gives
\eqref{eq:tpc62-three-module-product}.  No quantifier changes in this
substitution.
\end{proof}

The compatibility conditions are necessary for this proof.  For example,
three statements of the form ``there exists a good vector'' need not concern
the same vector.  Likewise, a phase sector chosen after the first arrow need
not be the fixed input map assumed by the second.

\subsection{Exponent form and endpoint condition}

Suppose, in one compatible scope, that
\(\Lambda_A,\lambda_{\rm reasm},\Lambda_{\rm out}\ge0\), and that all
\(o(1)\) terms below are uniform over that declared scope:
\begin{align}
 c_A(X)&\ge X^{-\Lambda_A+o(1)},
 \label{eq:tpc62-cA-exponent}\\
 \delta_{\rm reasm}(X)&\ge X^{-\lambda_{\rm reasm}+o(1)},
 \label{eq:tpc62-reassembly-exponent}\\
 c_{\rm out}(X)&\ge X^{-\Lambda_{\rm out}+o(1)}.
 \label{eq:tpc62-cout-exponent}
\end{align}
Then
\begin{equation}
 \cQ_{\rm out}(z)
 \ge
 X^{-(\Lambda_A+\lambda_{\rm reasm}+\Lambda_{\rm out})+o(1)}
 \cQ_0(z).
 \label{eq:tpc62-three-module-exponent-product}
\end{equation}
The inherited endpoint comparison has room only under
\begin{equation}
 \boxed{
 \Lambda_A+\lambda_{\rm reasm}+\Lambda_{\rm out}
 <\frac1{400}.}
 \label{eq:tpc62-three-module-endpoint}
\end{equation}

This is a conditional closure of the declared truncated fixed-\(h_0\)
packet lower square.  It does not identify \(\cQ_{\rm out}\) with a
prime-pair counting function, prove a boundary/tail comparison, or establish
any of the three exponent inputs.

\subsection{Admissible reassembly inputs}

The middle constant in
\eqref{eq:tpc62-three-module-product} may be obtained in several honest
ways.

\paragraph{Master shorted-Gram input.}
Let \(R_A\) represent \(\cQ_A\), and let \(F=A_X+M_X\) represent
\(\cQ_F\).  If \(R_A\ne0\), then the optimal full-space uniform value is
the master constant
\begin{equation}
 \delta_{\rm sh}
 =\alpha(F;R_A)
 \label{eq:tpc62-delta-short-input}
\end{equation}
from \cref{thm:tpc62-master-shorted-gram}.  A quantitative lower bound for
\(\delta_{\rm sh}\) may be inserted directly as
\(\delta_{\rm reasm}\).  The kernel inclusion proves only positivity at
each finite scale, not a polynomial exponent.  Here ``optimal'' refers to
the full coefficient space, or to a homogeneous declared class containing a
nonzero scalar multiple of every coefficient direction.  On an arbitrary
restricted class the same full-space constant remains a valid lower bound,
but need not be optimal for that class.
If \(R_A=0\), then \(\cQ_A\) is identically zero, the middle comparison
has no positive denominator, and the reassembly arrow is vacuous; the
master constant is not invoked or assigned a value.

\paragraph{Restricted mass--degree input.}
On the same literal carrier, let
\(\sigma_M,\lambda_{\rm rep}\ge0\), suppose the effective growth exponent
\(\nu_M\) defined in \eqref{eq:tpc62-intro-alias-exponent} is finite, and
assume
\begin{equation}
 \cQ_A(z)=\|A_Xz\|^2,\qquad
 \cQ_F(z)=\|(A_X+M_X)z\|^2,\qquad
 \|M_Xz\|^2\le\kappa_M\cD_M(z),
 \label{eq:tpc62-closure-literal-reassembly-forms}
\end{equation}
together with
\begin{align}
 \cD_M(z)&\le X^{-\sigma_M+o(1)}\cD_{\rm ref}(z),
 \label{eq:tpc62-closure-missing-saving}\\
 \kappa_M&\le X^{\nu_M+o(1)},
 \label{eq:tpc62-closure-kappa-bound}\\
 \cQ_A(z)&\ge
 X^{-\lambda_{\rm rep}+o(1)}\cD_{\rm ref}(z)
 \label{eq:tpc62-closure-represented-reference}
\end{align}
in the same scope.  For vectors with \(\cQ_A(z)>0\), define
\begin{equation}
 q_X(z):=
 \frac{\kappa_M\cD_M(z)}{\cQ_A(z)}
 \le
 X^{\nu_M+\lambda_{\rm rep}-\sigma_M+o(1)}.
 \label{eq:tpc62-closure-effective-product}
\end{equation}
The strict condition
\begin{equation}
\boxed{\sigma_M>\nu_M+\lambda_{\rm rep}}
 \label{eq:tpc62-closure-strict-effective-product}
\end{equation}
therefore makes \(q_X(z)=o(1)\).  The reverse triangle inequality applied
to \eqref{eq:tpc62-closure-literal-reassembly-forms} shows that one may
take the lower certificate
\(\delta_{\rm reasm}(X)=1-o(1)\), and hence
\(\lambda_{\rm reasm}=0\).  Vectors with \(\cQ_A(z)=0\) impose no
condition on this middle lower bound.  This conclusion is uniform only if
all three inputs and their \(o(1)\) terms are uniform; replacing
\(\kappa_M\) by one Rayleigh quotient gives only a distinguished
statement.

At equality of fixed-power exponents, let \(a\ge0\).  If, uniformly over the same vectors
with \(\cQ_A(z)>0\),
\begin{equation}
 1-\sqrt{q_X(z)}\ge X^{-a+o(1)},
 \label{eq:tpc62-closure-critical-margin}
\end{equation}
then one may take
\(\delta_{\rm reasm}(X)\ge X^{-2a+o(1)}\), so
\(\lambda_{\rm reasm}\le2a\).  The endpoint requires
\begin{equation}
 \boxed{
 \Lambda_A+2a+\Lambda_{\rm out}<\frac1{400}.}
 \label{eq:tpc62-closure-critical-endpoint}
\end{equation}

\paragraph{Residual-factor input.}
On the critical cofactor block, TPC--61 leaves the conditional algebraic
window
\begin{equation}
 e+\mu_{\rm erase}+\lambda_{\rm rep}
 <\frac{39671}{210000}.
 \label{eq:tpc62-closure-residual-window}
\end{equation}
If the inherited residual certificate supplies the corresponding
same-scope missing-to-represented estimate on every one of the
\(O(\log X)\) blocks, if the global comparison loses at most this
logarithmic factor, and if
\eqref{eq:tpc62-closure-residual-window} holds with one fixed positive
margin uniformly over the blocks, then one may take
\(\lambda_{\rm reasm}=0\).  The logarithmic factor is subpower.  The
algebraic window by itself, or mere blockwise strictness with a margin
tending to zero, is not enough.

The numerical right side here is much larger than \(1/400\).  Passing this
test proves only that the middle reassembly exponent is zero.  It does not
place \(\lambda_{\rm rep}\), \(\Lambda_A\), or the downstream losses inside
the final endpoint budget; that independent check is still
\eqref{eq:tpc62-three-module-endpoint}.

\paragraph{Signed distinguished input.}
For one physical vector, an exact lower estimate of
\begin{equation}
 2\operatorname{Re}\langle A_Xz_*,M_Xz_*\rangle
 +\|M_Xz_*\|^2
 \label{eq:tpc62-closure-signed-input}
\end{equation}
may prove a favorable distinguished reassembly ratio even when every
uniform certificate is silent.  It may not be entered as
\(\delta_{\rm reasm}\) for the full coefficient class.

\subsection{No double charging}

The exponents \(\sigma_M\), \(\nu_M\),
\(\mu_{\rm erase}\), \(e\), and \(\lambda_{\rm rep}\) in the
preceding tests decide the single middle exponent
\(\lambda_{\rm reasm}\).  They are not five additional arrows.
Moreover, if \(\lambda_{\rm rep}\) is assembled from represented-chain
losses already contained in \(\Lambda_A\), it is used in
\eqref{eq:tpc62-closure-strict-effective-product} but is not added to
\(\Lambda_A\) a second time.  The same rule applies to every diagnostic
capacity exponent.

Exact coordinate changes, a fixed large support constant in
\(y=C_{\rm vh}Q\), Moore--Penrose restriction to an actual active support,
and finite or logarithmic diagnostic partitions have zero fixed-power cost.
