\section{The literal dependency graph and quantifier signatures}
\label{sec:tpc62-dependency-graph}

Historical paper numbers record discovery order, not a license to multiply
all displayed constants.  This section extracts the logical order needed by
a lower-bound proof and assigns a quantifier signature to every arrow.

\subsection{Four signatures}

Let \(Z_X\) be a coefficient class fixed before any vector is chosen.
Whenever a uniform generalized eigenvalue or kernel equivalence is used,
the declared class is understood to be its full linear coefficient space,
or a degree-zero direction-complete class containing a nonzero scalar
multiple of every direction.  For a proper nonlinear subset, the infimum
must instead be restricted to that subset, and a full-space kernel vector
outside the subset does not kill the restricted statement.

\begin{definition}[Quantifier signature]
\label{def:tpc62-quantifier-signature}
A lower statement has one of the following signatures.
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item \(\mathsf U\) (uniform): one fixed carrier and one fixed map satisfy
       the bound for every \(z\in Z_X\);
 \item \(\mathsf D\) (distinguished): the bound is asserted only for one
       declared physical vector \(z_*(X)\);
 \item \(\mathsf A\) (adaptive): for every \(z\in Z_X\), at least one
       selector \(a=a(z)\) from a fixed family gives the bound;
 \item \(\mathsf G\) (averaged): only an average over vectors, shifts,
       selectors, or another external parameter is bounded.
\end{enumerate}
The carrier, map, atomic normalization, and reference form are part of the
signature.
\end{definition}

The signature is not a stylistic label.  It determines which implications
are valid.

\begin{proposition}[Safe signature rules]
\label{prop:tpc62-safe-signature-rules}
The following rules hold.
\begin{enumerate}[label=\textup{(\alph*)},leftmargin=3em]
 \item A \(\mathsf U\) statement may be evaluated at \(z_*\), producing a
       \(\mathsf D\) statement on the same carrier and map.
 \item Finitely many sequential \(\mathsf U\) inequalities compose when
       the output form of each arrow is literally the input form of the
       next.
 \item Sequential \(\mathsf D\) inequalities compose only when every arrow
       concerns the actual intermediate image generated by the same initial
       vector.
 \item Neither \(\mathsf D\), \(\mathsf A\), nor \(\mathsf G\) implies
       \(\mathsf U\) without an additional theorem.
 \item An \(\mathsf A\) statement composes as a labeled direct-sum
       statement if all selector outputs are retained orthogonally.  It does
       not automatically compose after their labels are erased.
 \item A kernel or generalized-eigenvalue statement on the full coefficient
       space applies to a restricted declared class as a lower certificate,
       but a kernel witness kills that restricted class only when the witness
       direction belongs to its homogeneous cone.
\end{enumerate}
\end{proposition}

\begin{proof}
Parts (a)--(c) are direct substitutions with their quantifiers unchanged.
The coordinate-projection example in
\cref{sec:tpc62-adaptive-selectors} proves the failure in part (d) for
\(\mathsf A\); one-vector and averaging examples prove the other two
failures.  Part (e) is the direct-sum identity proved in
\cref{thm:tpc62-labeled-uniformization}; erasing labels applies a further
linear map and can create cancellation.  Part (f) follows because an
infimum over the full space is no larger than the infimum over a subset,
whereas a zero quotient obstructs a subset only if that subset contains the
corresponding direction up to nonzero scaling.
\end{proof}

Changing one fixed nonzero shift into a shift average changes both the
carrier and the signature.  Likewise, dividing an atomic input norm by a
fiber size, choosing a coefficient-dependent support, or replacing a
uniform generalized eigenvalue by one Rayleigh quotient changes the
statement rather than proving it.

\subsection{The logical graph}

The fixed-shift route has the following logical skeleton:
\begin{equation}
\begin{aligned}
&\text{literal parent atoms}
 \longrightarrow \text{actual-energy selection}
 \longrightarrow \text{critical high-face activation}\\
&\longrightarrow \text{terminal prime-resolved fibers}
 \longrightarrow \text{represented residual/native output}\\
&\longrightarrow \text{represented plus missing reassembly}
 \longrightarrow \text{boundary/tail reconnection}.
\end{aligned}
\label{eq:tpc62-logical-skeleton}
\end{equation}
Each phrase abbreviates several exact objects.  The status inherited from
TPC--53--TPC--61 is summarized below.

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.15\textwidth}
                >{\raggedright\arraybackslash}p{0.26\textwidth}
                >{\raggedright\arraybackslash}p{0.34\textwidth}
                >{\raggedright\arraybackslash}p{0.12\textwidth}}
\toprule
Source & Logical object & Established conclusion & Closure status\\
\midrule
TPC--53
& Literal factor dictionary
& Canonical row/orbit/prime/cofactor coordinates, literal coefficients,
  raw atomic normalization, and an interior compatible cell.
& L1 interface\\
\addlinespace
TPC--54
& Actual-energy selection
& Sharp carrier-coverage and saturation laws.  Cofactor occupancy and a
  coefficient floor remain inputs.
& L0/L1 certificate\\
\addlinespace
TPC--59
& Critical high face
& The admissible cutoff may be \(y\asymp Q\); exact occupancy,
  activation, and dyadic localization constants are identified.
& L1 route correction\\
\addlinespace
TPC--55
& Prime-resolved terminal fibers
& Exact grouping SVD, common M\"obius gauge, pseudoinverse, and
  collision-free transversal on the declared terminal support.
& L0/L1 structure\\
\addlinespace
TPC--56
& Phase-sector extraction
& A constant-energy sector exists after a coefficient-adaptive choice.
  The sector is not one frozen linear output for all coefficients.
& \(\mathsf A\), not \(\mathsf U\)\\
\addlinespace
TPC--57
& Undeleted singleton route
& Exact collision moments and the sharp singleton floor.  A positive
  endpoint singleton fraction is not proved.
& \(\mathsf U\) certificate\\
\addlinespace
TPC--58
& Residual/native affine map
& Exact erasure quotient, dark-space test, and two-stage generalized
  Grams.  No endpoint lower constant is obtained.
& L0/L1 gate\\
\addlinespace
TPC--60
& High-face reassembly
& Exact represented/missing split, shorted Gram, kernel test, and
  mass--degree certificate.
& L0/L1 gate\\
\addlinespace
TPC--61
& Missing cofactor exposure and alias Gram
& Exact exposure measure, cofactor ladder, restricted \(\kappa_M\), and
  the two-affine M\"obius/determinant kernel.
& L0/L1 reduction\\
\bottomrule
\end{tabular}
\end{center}

The table is not a proof that all rows are simultaneously active.  In
particular, actual-energy selection does not prove critical terminal
activation; prime-resolved isometry does not prove erasure injectivity;
singleton incidence does not prove a positive singleton mass; and an exact
formula for the missing alias Gram does not bound its top eigenvalue.

\subsection{Branches that must not be spliced}

The terminal-prime layer has two useful but logically different branches.

\paragraph{Adaptive phase branch.}
TPC--56 proves that after inspecting a coefficient vector one can retain a
phase sector with a constant fraction of the already grouped fiber energy
\citep{WangTPC56}.  This is an \(\mathsf A\) statement.  If the goal is a
coefficient-uniform lower bound for one undeleted physical map, the selected
sector cannot be inserted as a fixed arrow.  It becomes uniform only on a
new labeled direct-sum output, after which reassembly to the physical output
is still open.

\paragraph{Undeleted singleton branch.}
TPC--57 stays on the undeleted output and gives an exact sufficient floor in
terms of singleton energy \citep{WangTPC57}.  This branch has the right
uniform carrier, but the singleton floor may vanish.  Such vanishing kills
that certificate, not the complete coherent output, because nonsingleton
fibers may still add favorably.

Thus the two branches cannot be combined by taking the positive part of
each: the first changes the selector with the vector, while the second keeps
the map fixed but may have zero certified mass.

\subsection{TPC--59 is logically upstream of the terminal endpoint}

TPC--58 inherited a cutoff displaced by a fixed positive power.  TPC--59
shows that the literal very-high conditions already permit
\begin{equation}
 y=C_{\rm vh}Q
 \label{eq:tpc62-critical-cutoff}
\end{equation}
for a sufficiently large support-dependent constant, reopening the
critical cofactor scale
\begin{equation}
 R\asymp J=X^{133/400+o(1)}.
 \label{eq:tpc62-critical-cofactor-scale}
\end{equation}
Accordingly, TPC--59 is historically later than TPC--55--TPC--58 but
logically upstream of any endpoint use of their terminal carrier.  The
cutoff correction is a feasibility statement.  It does not prove that the
actual retained relation occupies the reopened block.

\subsection{The surviving three modules}

After exact identities and zero-cost coordinate changes have been removed,
the prospective lower chain can be compressed into three modules.
\begin{enumerate}[label=\textbf{Module \Roman*.},leftmargin=4.5em]
 \item The \emph{represented chain}: actual selection, critical occupancy,
       terminal activation, and represented residual/native transfer produce
       a represented map \(A_X\).
 \item The \emph{reassembly gate}: the missing map \(M_X\) is restored and
       \(A_X+M_X\) is compared with \(A_X\), uniformly by shorting or in a
       declared distinguished scope.
 \item The \emph{downstream reconnection}: boundary, tail, and parent-target
       interfaces compare the complete slice output with the declared
       truncated packet target.
\end{enumerate}
The conditional theorem in \cref{sec:tpc62-conditional-closure} composes
these modules only after their carriers, normalizations, and signatures have
been matched.

\subsection{Six-item physical audit}

Every L1 specialization in this paper is subject to the following audit.
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3.2em]
 \item \emph{Literal coefficients.}  Atom amplitudes are the inherited
       physical coefficients; no favorable atom phases are chosen.
 \item \emph{Fixed shift.}  Every target is built from the same fixed
       nonzero \(h_0\), with no shift average substituted.
 \item \emph{Raw atomic norm.}  The input energy is raw counting measure,
       not a fiber-normalized surrogate.
 \item \emph{Canonical representation.}  Row, orbit, largest-prime,
       cofactor, residual, and native labels are recovered canonically; only
       identically inactive directions are removed.
 \item \emph{Actual support.}  Carriers and selector families are fixed
       before the coefficient vector, unless the conclusion is explicitly
       labeled adaptive.
 \item \emph{Endpoint budget.}  Structural identities cost zero; every
       proved lower loss is entered once in a strict total below \(1/400\).
\end{enumerate}

Passing this audit says that the correct physical object and quantifier have
been retained.  It does not supply any of the open arithmetic lower bounds.
Here \(h_0\) remains an arbitrary fixed nonzero shift.  Nothing in this
audit specializes it to \(h_0=2\), and no conclusion for that special shift
may be inferred without the missing arithmetic and downstream
identifications.
