\section{Endpoint arithmetic, kill tests, and pivot rules}
\label{sec:tpc62-endpoint-decisions}

The abstract theorems identify which constants are exact and which
certificates dominate others.  This section places the three numerical
comparisons inherited from TPC--60--TPC--61 into that decision structure.
They are route tests, not new arithmetic estimates.

\subsection{Three numerical comparisons}

At the critical cofactor scale,
\begin{equation}
 \theta_J=\frac{133}{400},
 \qquad
 \lambda_L=\frac{99979}{210000}.
 \label{eq:tpc62-endpoint-basic-exponents}
\end{equation}
The coefficient-blind residual determinant-ladder exponent is
\begin{equation}
 \lambda_L-\theta_J
 =\frac{15077}{105000}.
 \label{eq:tpc62-endpoint-residual-degree}
\end{equation}
Combined with the balanced cofactor saving, it leaves the conditional
residual window
\begin{equation}
 \boxed{
 2\theta_J-\lambda_L
 =\frac{39671}{210000}.}
 \label{eq:tpc62-endpoint-residual-window}
\end{equation}
Thus the residual mass--degree certificate can be perturbative if
\begin{equation}
 e+\mu_{\rm erase}+\lambda_{\rm rep}
 <\frac{39671}{210000}
 \label{eq:tpc62-endpoint-residual-condition}
\end{equation}
with one uniform fixed margin over the compatible dyadic blocks.
Since \(39671/210000\gg1/400\), this inequality is only a test for
zero-cost reassembly.  A value of \(\lambda_{\rm rep}\) may satisfy this
test and still make the represented-chain loss \(\Lambda_A\) too large for
the final endpoint.  It is charged in the final ledger exactly when it is
part of a represented-chain arrow, and never as a second reassembly arrow.

The direct ambient native-degree route has instead the positive gap
\begin{equation}
 \boxed{
 \frac{267}{400}-\frac{133}{400}
 =\frac{67}{200}.}
 \label{eq:tpc62-endpoint-ambient-gap}
\end{equation}
It cannot make the missing perturbation \(o(1)\) by combining the full
ambient degree with the strongest nonempty pure-cardinality saving.  By the
certificate order in \cref{sec:tpc62-certificate-lattice}, this closes only
that coarse ambient proof.  It neither lower-bounds the restricted
\(\kappa_M\) nor implies failure of the residual, signed, or shorted routes.

Finally, the localized-alias theorem gives a different conditional door.
Let \(\delta,\tau\ge0\).  If the actual normalized collision graph has row degree
\begin{equation}
 \Delta_X\le X^{\delta+o(1)}
 \label{eq:tpc62-endpoint-overlap-degree}
\end{equation}
and every off-diagonal literal normalized pair entry satisfies, uniformly
for colliding \(m\ne n\),
\begin{equation}
 |K_{m,n}|\le X^{-\tau+o(1)},
 \label{eq:tpc62-endpoint-pair-saving}
\end{equation}
then
\begin{equation}
 \nu_M\le(\delta-\tau)_+.
 \label{eq:tpc62-endpoint-kappa-from-pairs}
\end{equation}
The optimal restricted mass--degree certificate consequently has the strict
sufficient condition
\begin{equation}
 \boxed{
 \sigma_M>
 \lambda_{\rm rep}+(\delta-\tau)_+.}
 \label{eq:tpc62-endpoint-localized-condition}
\end{equation}
provided the degree, pair, missing-mass, and represented-reference estimates
all hold on the same literal carrier and in the same quantifier scope.
No favorable value of \(\delta\), \(\tau\), or \(\sigma_M\) is proved in
this paper.

\subsection{The complete physical ledger}

Expanding the represented and downstream modules gives the inherited loss
sum.  Every quantity denoted by \(\lambda\) below is a nonnegative loss
exponent:
\begin{equation}
 \boxed{
 \begin{aligned}
 \Lambda_{\rm tot}:={}&
 \lambda_{\rm sel}+\lambda_{\rm occ}
 +\lambda_{\rm blk}+\lambda_{\rm term}
 +\lambda_{\rm sing}\\
 &+\lambda_H+\lambda_{\rm aff}
 +\lambda_{\rm reasm}
 +\lambda_{\rm bdry}+\lambda_{\rm tail}.
 \end{aligned}}
 \label{eq:tpc62-complete-ledger}
\end{equation}
The endpoint condition is
\begin{equation}
 \boxed{\Lambda_{\rm tot}<\frac1{400}.}
 \label{eq:tpc62-strict-ledger}
\end{equation}
In the three-module notation,
\begin{equation}
 \Lambda_A=\lambda_{\rm sel}+\lambda_{\rm occ}
 +\lambda_{\rm blk}+\lambda_{\rm term}+\lambda_{\rm sing}
 +\lambda_H+\lambda_{\rm aff},
 \qquad
 \Lambda_{\rm out}=\lambda_{\rm bdry}+\lambda_{\rm tail}.
 \label{eq:tpc62-module-ledger-identification}
\end{equation}
Every displayed identity, exact gauge, canonical relabeling, and diagnostic
finite or logarithmic partition costs zero.  The quantities in
\eqref{eq:tpc62-endpoint-residual-condition} and
\eqref{eq:tpc62-endpoint-localized-condition} determine whether
\(\lambda_{\rm reasm}\) is zero or positive; they are not added separately
to \eqref{eq:tpc62-complete-ledger}.

For a distinguished chain, the reassembly loss is replaced consistently by
\(\lambda_{\rm reasm,*}\), and every upstream and downstream inequality
must concern the same physical vector.  Equality in
\eqref{eq:tpc62-strict-ledger} is rejected unless leading constants and all
remainders recover a strict final inequality.

\subsection{Exact kill and pivot table}

The word ``kill'' is reserved for a proved zero in the object actually
needed by the route.  The following table separates exact deaths from
certificate failures.

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.29\textwidth}
                >{\raggedright\arraybackslash}p{0.31\textwidth}
                >{\raggedright\arraybackslash}p{0.29\textwidth}}
\toprule
Observed event & What is killed & Honest pivot\\
\midrule
\(\Ker F_X\not\subseteq\Ker R_X\)
& The full-coefficient-space master transfer; its exact constant is zero.
& Change scope to a declared distinguished vector, or change the actual
  physical theorem.\\
\addlinespace
A mandatory factor \(T_X\) has a kernel vector of positive parent energy
& Every final map that genuinely factors through \(T_X\).
& None within the same mandatory factorization; reopen the physical map.\\
\addlinespace
An active row has \(W_R(m)=0<W_M(m)\), and its row direction lies in the
declared uniform class
& Uniform represented raw-mass transfer on that class.
& Reopen the retained-relation provenance, or use a distinguished vector
  known to avoid that row.\\
\addlinespace
\(\Ker(A_X+M_X)\not\subseteq\Ker A_X\)
& Full-coefficient-space uniform represented-to-full reassembly.
& A distinguished signed estimate may remain possible.\\
\addlinespace
The sharp singleton floor is zero
& The singleton sufficient certificate only.
& Estimate the complete coherent fiber or use another literal certificate.\\
\addlinespace
\(\eta_{\rm frozen}=0<\eta_{\rm adaptive}\)
& One frozen selector as a uniform map.
& Retain all selector labels by direct sum, or prove frozen-selector
  stability and then reassembly.\\
\addlinespace
\(\sigma_M<\nu_M+\lambda_{\rm rep}\), or equality holds without a proved
leading-constant margin
& The zero-fixed-power conclusion from the exponent-only restricted
  mass--degree test.
& Test the exact shorted Gram, a signed distinguished vector, or improve the
  exposure/alias inputs.\\
\addlinespace
The ambient gap is \(67/200\)
& The full ambient-degree phase-blind proof.
& Use the actual restricted Gram, residual quotient, or signed shorting.\\
\addlinespace
A necessary proved loss reaches \(1/400\)
& The stated endpoint exponent route without a constant-level recovery.
& Change the upstream architecture; do not hide the loss in an
  \(X^{o(1)}\) term.\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Operational order for the next arithmetic attack}

The preceding tests should be applied in the following order.
\begin{enumerate}[label=\textbf{Door \Alph*.},leftmargin=3.8em]
 \item \emph{Master kernels.}  Check the kernel inclusions for every
       mandatory map before estimating small eigenvalues.
 \item \emph{Literal exposure.}  Recover the actual retained relation and
       compute \(W_R(m)\), \(W_M(m)\), and their physical distinguished
       weighting.
 \item \emph{Represented chain.}  Prove critical occupancy, terminal
       activation, and represented native transfer in one declared scope.
 \item \emph{Alias localization.}  Compute actual row/cell degrees and
       either prove a pair/star estimate for the TPC--61 determinant kernel
       or exhibit a large obstruction witness.
 \item \emph{Reassembly decision.}  Apply the optimal restricted product
       test, the residual alternative, or the exact shorted/signed route.
 \item \emph{Downstream reconnection.}  Prove boundary and tail arrows and
       then audit the strict complete ledger.
\end{enumerate}

This order prevents a difficult parity estimate from being attempted on an
empty represented carrier and prevents an adaptive or distinguished success
from being promoted to a uniform map.

\subsection{Forbidden repairs}

None of the killed routes is repaired by replacing \(h_0\), averaging over
shifts, dividing raw atoms by fiber sizes, deleting coefficient-dependent
zeros, choosing atom phases, or substituting one favorable Rayleigh quotient
for a uniform generalized eigenvalue.  Those operations define different
objects.  They may be interesting in their own right, but their conclusions
cannot be entered into \eqref{eq:tpc62-complete-ledger} for the fixed carrier.
