\section{Exact independence models and scope counterexamples}
\label{sec:tpc62-independence-models}

The closure gates in this paper are logically distinct.  The following
finite-dimensional models show that raw missing mass, prime-block
isometries, a strong represented map, and successful reassembly cannot be
interchanged.  Every coefficient and every atomic norm below is literal.
The models are L0 interface examples; they are not asserted to arise from
the fixed-\(h_0\) arithmetic carrier and therefore are not L1 or L2
counterexamples.

\subsection{One output and N distinct prime blocks}

Fix \(N\ge2\).  Let the row coefficient space be \(\C^N\), let the native
output space be \(\C\), and define
\begin{equation}
 A_N\zeta:=\frac1N\sum_{m=1}^N\zeta_m.
 \label{eq:tpc62-one-output-represented-map}
\end{equation}
For each row \(m\), introduce one missing atom \(w_m\).  All \(N\) atoms
land at the same native output, their terminal-prime labels
\(p_1,\ldots,p_N\) are pairwise distinct, and their literal coefficients
are
\begin{equation}
 c_{w_m}=-\frac1N.
 \label{eq:tpc62-one-output-missing-coefficients}
\end{equation}
Thus the missing map and its raw atomic diagonal are
\begin{equation}
 M_N\zeta=-\frac1N\sum_{m=1}^N\zeta_m=-A_N\zeta,
 \qquad
 \mathbf D_M=\frac1{N^2}I_N.
 \label{eq:tpc62-one-output-missing-map}
\end{equation}

\begin{proposition}[Exact coherent missing model]
\label{prop:tpc62-exact-coherent-missing-model}
The model in \eqref{eq:tpc62-one-output-missing-map} satisfies the
fixed-\((i,p)\) singleton property and the exact prime-block identities
\begin{equation}
 M_{p_m}^*M_{p_m}=\mathbf D_{p_m},
 \qquad
 \sum_{m=1}^N\mathbf D_{p_m}=\mathbf D_M.
 \label{eq:tpc62-model-prime-block-identities}
\end{equation}
Nevertheless
\begin{equation}
 \boxed{
 F_M=M_N\mathbf D_M^{-1/2}
      =[\,-1\ \cdots\ -1\,],
 \quad
 \mathbf K_M=\boldsymbol 1\boldsymbol 1^*,
 \quad
 \kappa_M=N.}
 \label{eq:tpc62-model-coherent-gram}
\end{equation}
For the distinguished coefficient
\(\zeta_\star=\boldsymbol 1\),
\begin{equation}
 \|A_N\zeta_\star\|^2=1,
 \qquad
 \langle\mathbf D_M\zeta_\star,\zeta_\star\rangle=\frac1N,
 \qquad
 (A_N+M_N)\zeta_\star=0.
 \label{eq:tpc62-model-exact-cancellation}
\end{equation}
Thus a raw missing fraction \(1/N\) can coexist with complete reassembly
failure.
\end{proposition}

\begin{proof}
For a fixed terminal prime \(p_m\), the block map is
\[
 M_{p_m}\zeta=-\frac1N\zeta_m.
\]
There is exactly one atom at the pair consisting of the unique output and
\(p_m\).  Hence
\[
 M_{p_m}^*M_{p_m}
 =\frac1{N^2}e_me_m^*
 =\mathbf D_{p_m}.
\]
Summing over \(m\) proves
\eqref{eq:tpc62-model-prime-block-identities}.  Since
\(\mathbf D_M^{-1/2}=NI_N\), the normalized incidence matrix has \(N\)
unit columns, all equal to \(-1\).  Its Gram is
\(\boldsymbol 1\boldsymbol 1^*\), whose eigenvalues are \(N,0,\ldots,0\).
This proves \eqref{eq:tpc62-model-coherent-gram}.  The three identities in
\eqref{eq:tpc62-model-exact-cancellation} follow by direct substitution.
\end{proof}

The mass--degree product is exactly critical in this example:
\begin{equation}
 \frac{\kappa_M
 \langle\mathbf D_M\zeta_\star,\zeta_\star\rangle}
 {\|A_N\zeta_\star\|^2}=1.
 \label{eq:tpc62-model-critical-product}
\end{equation}
The reverse-triangle margin is therefore zero, and the actual operators
attain that worst case.  The example does not say that equality must cause
cancellation; it shows why a theorem based only on this certificate needs
a strict margin or additional phase information.

\subsection{A uniformly perfect represented map can still cancel}

The rank-one nature of \(A_N\) in the preceding example is not the source
of the obstruction.  Let both the coefficient and output spaces be
\(\C^N\), put
\begin{equation}
 v:=N^{-1/2}\boldsymbol 1,
 \qquad
 \widetilde A_N:=I_N,
 \qquad
 \widetilde M_N:=-vv^*=-\frac1N
 \boldsymbol 1\boldsymbol 1^*.
 \label{eq:tpc62-uniform-represented-model}
\end{equation}
Realize \(\widetilde M_N\) by one atom \(w_{i,m}\) of coefficient
\(-1/N\) for every output--row pair \((i,m)\).  Give the \(N^2\) atoms
pairwise distinct formal terminal-prime labels.  Then every
fixed-\((i,p)\) incidence is a singleton, each one-atom prime block is an
exact isometry relative to its atomic diagonal, and
\begin{equation}
 \widetilde{\mathbf D}_M=\frac1N I_N,
 \qquad
 \widetilde F_M=-\frac1{\sqrt N}
 \boldsymbol 1\boldsymbol 1^*,
 \qquad
 \widetilde{\mathbf K}_M=\boldsymbol 1\boldsymbol 1^*,
 \qquad
 \widetilde\kappa_M=N.
 \label{eq:tpc62-uniform-model-gram}
\end{equation}
The represented map is uniformly optimal:
\begin{equation}
 \|\widetilde A_N\zeta\|^2=\|\zeta\|^2
 \qquad(\zeta\in\C^N).
 \label{eq:tpc62-uniform-perfect-represented}
\end{equation}
Yet on the unit vector \(v\),
\begin{equation}
 \langle\widetilde{\mathbf D}_Mv,v\rangle=\frac1N,
 \qquad
 (\widetilde A_N+\widetilde M_N)v=0.
 \label{eq:tpc62-uniform-model-cancellation}
\end{equation}
Thus even a coefficient-uniform represented lower bound, literal raw
missing mass, and all singleton prime-block identities do not imply a
positive reassembled lower bound.  Control of the restricted native Gram
or of the signed cross term is an independent gate.

The same model also separates uniform and distinguished conclusions.  For
every \(\zeta\perp v\), one has
\begin{equation}
 \widetilde M_N\zeta=0,
 \qquad
 (\widetilde A_N+\widetilde M_N)\zeta=\zeta.
 \label{eq:tpc62-uniform-model-good-directions}
\end{equation}
Hence the large uniform value \(\widetilde\kappa_M=N\) does not prove
failure for a specified physical vector.  Conversely, good reassembly on
one such vector gives no uniform lower bound because the direction \(v\)
is still dark.  Quantifier scope cannot be changed in either direction.

\subsection{Pair decorrelation and collision degree are independent}

For \(0\le\rho\le1\), take orthonormal vectors
\(e_0,e_1,\ldots,e_N\) and define the unit columns
\begin{equation}
 f_m:=\sqrt{1-\rho}\,e_m+\sqrt\rho\,e_0
 \qquad(1\le m\le N).
 \label{eq:tpc62-equi-correlated-columns}
\end{equation}
Their Gram is
\begin{equation}
 \mathbf K_\rho=(1-\rho)I_N
 +\rho\boldsymbol 1\boldsymbol 1^*,
 \qquad
 \lambda_{\max}(\mathbf K_\rho)=1+(N-1)\rho.
 \label{eq:tpc62-equi-correlated-gram}
\end{equation}
Every pair correlation is only \(\rho\), but every row has \(N-1\)
neighbours.  If
\(N=X^{\delta+o(1)}\) and
\(\rho=X^{-\tau+o(1)}\), this family has exact Gram exponent
\begin{equation}
 \limsup_{X\to\infty}
 \frac{\log\lambda_{\max}(\mathbf K_\rho)}{\log X}
 = (\delta-\tau)_+.
 \label{eq:tpc62-equi-correlated-exponent}
\end{equation}
It therefore shows that the degree factor in
\cref{cor:tpc62-degree-pair-exponent} cannot be removed at the Gram level.
Small pair correlations and sparse collision support are separate inputs.

\subsection{What the models do and do not refute}

The examples establish exact logical independence at the finite-dimensional
operator interface:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item prime-block isometry does not control unequal-prime cross terms;
 \item small raw missing mass does not control native missing energy without
       the restricted factor \(\kappa_M\);
 \item a uniform represented lower bound does not prevent phase-aligned
       cancellation by the missing map;
 \item a large uniform \(\kappa_M\) does not force failure on a distinguished
       coefficient vector; and
 \item pairwise decorrelation does not imply an operator bound without an
       active collision-degree estimate.
\end{enumerate}
They do not violate the exact TPC--61 formulas.  Rather, they attain those
formulas in abstract incidence systems.  They also do not satisfy or refute
the full fixed-\(h_0\) two-affine determinant restrictions.  Consequently
they prove no negative theorem about the literal arithmetic packet and no
parity, prime-pair, or twin-prime conclusion.  Their role is narrower and
quantifier-safe: any successful physical closure theorem must use a
hypothesis that excludes the displayed coherent configurations in the same
scope as its conclusion.
