\section{Introduction}
\label{sec:tpc62-introduction}

The papers TPC--53--TPC--61 replace a long heuristic transfer by explicit
finite-dimensional objects on one fixed nonzero physical shift
\citep{WangTPC53,WangTPC54,WangTPC55,WangTPC56,WangTPC57,WangTPC58,
WangTPC59,WangTPC60,WangTPC61}.  They identify literal atom coefficients,
sharp selection constants, prime-resolved singular values, adaptive phase
sectors, undeleted singleton floors, residual and native alias Grams, a
critical very-high cutoff, missing-coordinate reassembly, realized cofactor
exposure, and finally a normalized two-affine M\"obius kernel.  Most of these
objects are exact.  That does not mean they form one proved lower-bound
chain.

There are three reasons.
\begin{enumerate}[leftmargin=2.3em]
 \item Some results are coefficient-uniform, some concern one distinguished
       physical vector, and some select a sector or block after seeing the
       vector.  Their quantifiers cannot be silently exchanged.
 \item Some maps are mandatory parts of the physical transformation, while
       other projections, singleton floors, and mass--degree estimates are
       only sufficient certificates.  Failure of a certificate does not
       imply failure of the physical map.
 \item The endpoint allows a total fixed-power loss strictly below
       \(1/400\).  A numerical difference used inside one certificate is
       not automatically an additive loss, and the same exponent may not be
       charged twice.
\end{enumerate}

The purpose of this paper is to put these distinctions into a theorem-level
closure calculus.  It is both a synthesis and a new finite-dimensional
layer.  The synthesis records the literal dependency graph.  The new layer
specializes classical shorted-operator theory to the exact master transfer
constant and nuisance spaces of this closure problem, and adds a strict
selector-quantifier obstruction, a partial order among reassembly
certificates, and an inverse theorem localizing every large missing-alias
eigenvalue to a row and a literal determinant cell.

\subsection{The master constant}

Let \(\cH_X\) be the original coefficient space, let
\(0\ne R_X\succeq0\) represent the parent energy to be preserved, and let
\(F_X:\cH_X\to\cY_X\) be the complete declared output map after every
mandatory transformation in scope.  Define
\begin{equation}
 \alpha_X
 :=\inf_{\langle R_Xz,z\rangle>0}
   \frac{\|F_Xz\|^2}{\langle R_Xz,z\rangle}.
 \label{eq:tpc62-intro-master-constant}
\end{equation}
If \(R_X=0\), the quotient has no admissible vector and the transfer
problem is vacuous; throughout the master theorem no eigenvalue or loss
exponent is assigned to that case.
Write
\begin{equation}
 N_X:=\Ker R_X,
 \qquad S_X:=N_X^\perp,
 \qquad W_X:=F_X(N_X).
 \label{eq:tpc62-intro-master-spaces}
\end{equation}
The vectors in \(N_X\) cost no parent energy, but their outputs can cancel
the output of a vector in \(S_X\).  Therefore the correct numerator is not
the compression \(F_{X,S}^*F_{X,S}\).  It is the shorted form
\begin{equation}
 F_{X,S}^*P_{W_X^\perp}F_{X,S}.
 \label{eq:tpc62-intro-shorted-numerator}
\end{equation}
We prove
\begin{equation}
 \boxed{
 \alpha_X=\lambda_{\min}\!\left(
  R_{X,S}^{-1/2}F_{X,S}^*P_{W_X^\perp}F_{X,S}
  R_{X,S}^{-1/2}
 \right),}
 \label{eq:tpc62-intro-master-eigenvalue}
\end{equation}
and the exact finite-scale criterion
\begin{equation}
 \boxed{
 \alpha_X>0
 \quad\Longleftrightarrow\quad
 \Ker F_X\subseteq\Ker R_X.}
 \label{eq:tpc62-intro-master-kernel}
\end{equation}
This extends the TPC--60 reassembly shorting from one represented/missing
split to the entire declared packet.  It does not assert that
\(\alpha_X\) has a polynomial lower bound for the arithmetic family.

\subsection{Quantifier order is a mathematical gate}

For a finite family of selector maps \(S_a\), two superficially similar
constants are
\begin{align}
 \eta_{\rm frozen}
 &:=\sup_a\inf_{z\ne0}
   \frac{\|S_az\|^2}{\|z\|^2},
 \label{eq:tpc62-intro-frozen}\\
 \eta_{\rm adaptive}
 &:=\inf_{z\ne0}\sup_a
   \frac{\|S_az\|^2}{\|z\|^2}.
 \label{eq:tpc62-intro-adaptive}
\end{align}
Always \(\eta_{\rm frozen}\le\eta_{\rm adaptive}\), and equality can
fail maximally.  Coordinate projections have a positive adaptive constant,
although every fixed projection has a nontrivial kernel and hence zero
uniform constant.  This is the precise obstruction behind the implication
\[
 \forall z\ \exists a=a(z)
 \quad\not\Longrightarrow\quad
 \exists a\ \forall z.
\]
It applies to every coefficient-adaptive sector or maximal block.  A legal
uniformization retains all selector labels by orthogonal direct sum; summing
those outputs back into one physical coordinate is another alias/reassembly
gate.

\subsection{From a global eigenvalue to a literal obstruction}

TPC--61 writes the missing native map after raw diagonal normalization as a
matrix \(F_M\) with unit columns.  Its Gram is
\begin{equation}
 K_M=F_M^*F_M=I+\Xi_{\ne p},
 \qquad
 \kappa_M=\lambda_{\max}(K_M).
 \label{eq:tpc62-intro-missing-gram}
\end{equation}
The off-diagonal entries are weighted correlations of
\begin{equation}
 \mu(mj+h_0)\mu(m'j+h_0),
 \label{eq:tpc62-intro-two-affine}
\end{equation}
equivalently signed sums on
\begin{equation}
 m'pr-mp'r'=h_0(m'-m).
 \label{eq:tpc62-intro-determinant}
\end{equation}
The operator norm is a global object, so a single pair estimate is not
enough.  Conversely, a large operator norm cannot remain completely
delocalized.  If \(\kappa_M\ge1+L\), the Schur bound forces one row to have
off-diagonal absolute mass at least \(L\).  Partitioning that row into
\(B\) literal correlation cells forces one cell to carry at least \(L/B\).  If that
cell contains at most \(\Delta\) neighbors, one normalized determinant sum
has size at least \(L/(B\Delta)\).  This is an inverse localization theorem:
it produces a concrete witness to a large alias norm, but no cancellation
estimate.

At exponent level, a row-overlap degree
\(X^{\delta+o(1)}\) and a uniform pair bound
\(X^{-\tau+o(1)}\) imply
\begin{equation}
 \boxed{
 \nu_M
 :=\limsup_{X\to\infty}
   \frac{\log\max\{1,\kappa_M\}}{\log X}
 \le(\delta-\tau)_+.}
 \label{eq:tpc62-intro-alias-exponent}
\end{equation}
The TPC--61 effective-product door would then open under
\begin{equation}
 \sigma_M>
 \lambda_{\rm rep}+(\delta-\tau)_+.
 \label{eq:tpc62-intro-localized-door}
\end{equation}
Neither \(\delta\) nor \(\tau\) is favorably estimated here on the
arithmetic carrier.

\subsection{Main conclusions and scope}

The paper proves the following.
\begin{enumerate}[leftmargin=2.3em]
 \item The master shorted-Gram formula
       \eqref{eq:tpc62-intro-master-eigenvalue} and kernel criterion
       \eqref{eq:tpc62-intro-master-kernel} are exact.
 \item Shorting is transitive on nested retained subspaces.  A sequence of
       genuine nuisance eliminations is therefore equivalent to one master
       elimination, whereas ordinary compression may overstate transfer.
 \item A mandatory map with a kernel direction of positive parent energy
       kills the route exactly.  A zero singleton, selection, mass--degree,
       or other sufficient-certificate constant kills only that certificate
       unless the final map actually factors through it.
 \item Adaptive and frozen selector constants obey a strict min--max gap.
       Orthogonal direct sum gives the exact uniformization on a labeled
       output space.
 \item Exact shorting dominates every valid reverse-triangle certificate;
       the restricted missing Gram dominates its residual and ambient
       relaxations.  Residual and ambient relaxations need not dominate one
       another.
 \item Every large missing-alias eigenvalue has a row/cell/pair witness, with
       the quantitative and exponent consequences above.
 \item If represented-chain, reassembly, and downstream lower bounds are
       proved on the same carrier and in the same quantifier scope, their
       exponents add.  A sum strictly below \(1/400\) closes only the
       declared truncated fixed-\(h_0\) packet lower square.
\end{enumerate}

The first six conclusions and the abstract multiplication statement in the
seventh are L0 finite-dimensional theorems.  The literal TPC coordinate
identification in the sixth conclusion, including
\eqref{eq:tpc62-intro-two-affine}--\eqref{eq:tpc62-intro-determinant}, is
L1.  The fixed-\(h_0\) application of the seventh conclusion is conditional
L1.  No theorem here proves
\(\kappa_M=X^{o(1)}\), a new M\"obius correlation estimate, a lower square
for one fixed prime pair, or any twin-prime statement.

The paper is organized as follows.
\Cref{sec:tpc62-dependency-graph} records the logical graph and quantifier
signatures.  \Cref{sec:tpc62-master-shorted,sec:tpc62-nested-gates} develop
the master closure calculus.
\Cref{sec:tpc62-adaptive-selectors,sec:tpc62-certificate-lattice} prove the
quantifier gap and certificate partial order.
\Cref{sec:tpc62-localized-alias} localizes the missing-alias obstruction.
The conditional closure theorem, independence models, endpoint decisions,
and next targets appear in
\cref{sec:tpc62-conditional-closure,sec:tpc62-independence-models,sec:tpc62-endpoint-decisions,sec:tpc62-claims-next}.
