\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Joint Before Separation in a Primitive Mobius Tail: Both-New Annuli, Sharp Symmetric Conductor Ledgers, and Cutoff Stability},
 pdfauthor={Liang Wang},
 pdfsubject={Annular cutoff stability in a primitive Mobius tail},
 pdfkeywords={Mobius tail, both-new square, Poisson boundary, exact conductor, cutoff stability, sieve parity}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cK}{\mathcal K}
\newcommand{\cL}{\mathcal L}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cT}{\mathcal T}
\newcommand{\cU}{\mathcal U}
\newcommand{\cW}{\mathcal W}
\newcommand{\cZ}{\mathcal Z}
\newcommand{\rad}{\operatorname{rad}}
\newcommand{\cond}{\operatorname{cond}}
\newcommand{\supp}{\operatorname{supp}}

\title{\textbf{Joint Before Separation in a Primitive M\"obius Tail:}\\
\textbf{Both-New Annuli, Sharp Symmetric Conductor Ledgers,}\\
\textbf{and Cutoff Stability}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Let \(P_{m,W}\) be the calibrated residual prefix in a primitive
opened-\(d\) row and let \(R\le S<T\).  TPC-23 closes a centered
selected square below the Poisson length, while TPC-24--25 close the two mixed
increments obtained by replacing one prefix at \(S\) by the new shell
\(L_{m;S,T}=P_{m,T}-P_{m,S}\).  The remaining component is the
both-new square \(L_{m;S,T}L_{n;S,T}\).  We treat a stronger object:
the whole quadratic cutoff increment

\[
 P_{m,T}P_{n,T}-P_{m,S}P_{n,S}.
\]

The decisive step is exact and precedes every smooth or spectral
separation.  Writing

\[
 P_{m,W}(j)=
 \sum_{\substack{u\le W\\u\mid mj+h}}b_R(u)-\delta_H(m),
\]

the cutoff difference is one raw annular joint divisor lattice,
together with two explicit row-drift terms.  The annulus contains both
mixed orientations and the both-new square, but no surviving
single-indicator Poisson channel.

For the new shell--shell physical zero kernel we prove, uniformly for
off-diagonal rows, \(S=X^{s+o(1)}\), every \(0<\kappa<s\), and every
fixed \(A>0\),

\[
 K^{\square,0}_{S,T}(m,n)
 \ll (\log X)^{-A}+X^{-s+\kappa+o(1)}.
\]

The small shared factors are controlled by cancellation between the
two endpoints of a complete M\"obius shell; the large shared factors
divide the nonzero determinant \(m-n\).  TPC-25's actual
prime--M\"obius row provenance supplies \(O(Q^2)\) absolute row-pair
mass, so the complete annular zero frequency has arbitrary
logarithmic saving for a general fixed nonzero-mean physical test.

At nonzero frequency we prove a symmetric exact-conductor box theorem.
If \(Q=X^{\beta+o(1)}\), \(J=X^{1-\beta+o(1)}\), and
\(T=X^{t+o(1)}\), the exact minimax saving over the relaxed conductor
rectangle is denoted by \(M_\beta(t)\).  In the Poisson-beyond region
\(t>1-\beta\),

\[
 M_\beta(t)=
 \begin{cases}
 \dfrac{3(1-\beta)-2t}{4},
 &1-\beta<t\le\beta/2,\\[5pt]
 \displaystyle\min\left\{
 \dfrac{\beta+1-4t}{2},
 \dfrac{3-\beta-6t}{4}\right\},
 &t\ge\beta/2.
 \end{cases}
\]

Thus the annular conductor argument has a nonempty beyond-Poisson
region for every \(3/5<\beta<1\); the former face
\(\beta<2/3\) came from a nonsharp low--low estimate.  Under the
inherited primitive, no-wrap, row-mask, and fixed-power interfaces,
and with \(M_\beta(t)>0\) by a fixed margin, the actual physical cutoff
increment is

\[
 \mathcal Q_T^{\rm phys}-\mathcal Q_S^{\rm phys}
 \ll_B XQ(\log X)^{-B}
\]

for every fixed \(B>0\).  A strict sample with \(S<J<T\) has saving
\(1/100\).  A second, narrower sample with \(\beta>2/3\) is compatible
with the published opened-\(d\) source geometry and has saving
\(33/8000\), but proves cutoff stability only: its base square is not
imported as closed.  If an independent matching calibrated \(S\)-cutoff
estimate is supplied, the result closes the selected calibrated square
through \(T>J\).  Such a calibrated base estimate is not deduced here
from the earlier centered-square results.  The paper does not estimate
the ultra-long \((T,U]\) complement,
prove positivity, produce a Hardy--Littlewood main term, imply twin
primes, or breach the general sieve parity barrier.
\end{abstract}

\noindent\textbf{Keywords:} primitive M\"obius tail; both-new shell;
Poisson boundary; exact conductor; cutoff stability; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11L07, 11L40.

\input{sections/introduction}
\input{sections/interface-recombination}
\input{sections/both-new-zero}
\input{sections/physical-zero}
\input{sections/symmetric-conductor}
\input{sections/sharp-ledger}
\input{sections/cutoff-stability}
\input{sections/certificate-scope}

\clearpage
\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
