\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array,float}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\hypersetup{
 pdftitle={Row-Diagonal Closure at the Moving Mobius Gate: Folded Alias Energies, Exact Four-Correlation Isolation, and Triple-Prime Progression Decorrelation},
 pdfauthor={Liang Wang},
 pdfsubject={Exact removal of the same-row alias gate and logarithmic Mobius decorrelation for almost all admissible triple-prime CRT moduli},
 pdfkeywords={Mobius correlation, arithmetic progression, alias Gram, folded Parseval, multiplicative large sieve, CRT modulus, parity boundary}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{conditional input}{conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\T}{\mathbb T}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cA}{\mathcal A}
\newcommand{\cB}{\mathcal B}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cF}{\mathcal F}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cJ}{\mathcal J}
\newcommand{\cK}{\mathcal K}
\newcommand{\cM}{\mathcal M}
\newcommand{\cO}{\mathcal O}
\newcommand{\cP}{\mathcal P}
\newcommand{\cR}{\mathcal R}
\newcommand{\cS}{\mathcal S}
\newcommand{\cT}{\mathcal T}
\newcommand{\cV}{\mathcal V}
\newcommand{\cW}{\mathcal W}
\newcommand{\cY}{\mathcal Y}
\newcommand{\op}{\operatorname{op}}
\newcommand{\Var}{\operatorname{Var}}
\newcommand{\cond}{\operatorname{cond}}
\newcommand{\ee}[1]{\exp(2\pi i #1)}

\title{\textbf{Row--Diagonal Closure at the Moving M\"obius Gate:}\\
\textbf{Folded Alias Energies, Exact Four--Correlation Isolation,}\\
\textbf{and Triple--Prime Progression Decorrelation}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
TPC--39 isolates a finite additive--alias energy whose terminal expansion
appears to contain both long--gap two--M\"obius correlations and cross--row
four--M\"obius correlations.  We prove that the first class is not an
arithmetic gate.  For an arbitrary unimodular alias bank with normalized
Gram \(H\), the complete same--row sector is bounded by
\[
 \cE_{\rm same}\le\lambda_{\max}(H)\cD,
 \qquad
 |\cE_{\rm same}-\cD|\le\|H-I\|_{\op}\cD,
\]
where \(\cD\) is the atomic diagonal.  The minimal \(q=L+1\) Fourier bank
has spectrum \(2,1,0\), hence its same--row sector is at most \(2\cD\) and
the absolute value of its complete signed off--alias two--M\"obius sector
is at most \(\cD\).  The full \(2L+1\)-point bank deletes that sector
exactly.  Since
TPC--39 already bounds \(\cD\) at the physical endpoint, every same--row
alias correlation is thereby closed at the required scale without any
M\"obius cancellation.

After this deletion the only unbounded sector inside the chosen minimal
folded terminal energy is an explicit cross--row form.  Its summands contain
\[
 \mu(d_\alpha)\mu(d_\beta)
 \mu(m_\alpha j+h+kM)\mu(m_\beta j+h+k'M),
 \qquad \alpha\ne\beta,
\]
with the actual masks and source weights.  We prove that the two affine
target forms are nonproportional for every retained row pair, give the
exact one--sided bound equivalent to closure of that folded terminal
energy, and compress each fixed--alias column into a Hilbert--valued
one--M\"obius correlation.  This
identifies precisely why a scalar completion cannot control the physical
row energy.

We also obtain a quantitative arithmetic specialization at the inherited
CRT scale.
Let \(Y=X^{133/400}\), choose three disjoint admissible prime intervals of
length comparable with \(Y\), and let \(M=q_1q_2q_3\asymp
X^{399/400}\).  For every fixed \(0<\theta<1/200\), all but a zero-density
subfamily of these triple--prime moduli satisfy the raw, uncentered bound
\[
 \sum_{a\bmod M}^{*}
 \left|\sum_{\substack{n\le X\\n\equiv a\pmod M}}\mu(n)\right|^2
 \ll \frac{X(X/M)}{(\log X)^\theta}.
\]
The proof combines the almost--all--moduli theorem of
Klurman--Mangerel--Ter\"av\"ainen with a maximal multiplicative large sieve
that removes the single pretentious character on average over the sparse
triple--prime family.  A bounded--variation transfer includes the smooth
terminal weight \(-\mu(n)\log n\,\Phi_0(n/X)\).  This is genuine
coefficient--specific logarithmic decorrelation from the scalar coherent
scale, but it remains a factor
\((X/M)/(\log X)^\theta\) above the atomic diagonal and does
not estimate the physical cross--row four--M\"obius form.  No parity
breach, Hardy--Littlewood asymptotic, or twin--prime conclusion is claimed.
\end{abstract}

\noindent\textbf{Keywords:}
M\"obius correlation; arithmetic progression; folded Parseval; alias
Gram; multiplicative large sieve; triple--prime CRT modulus; parity
boundary.

\medskip
\noindent\textbf{MSC 2020:}
Primary 11N35, 11L40; Secondary 15A18, 42A16, 11N36.

\input{sections/introduction}
\input{sections/inherited-interface}
\input{sections/row-diagonal-identity}
\input{sections/minimal-and-full-banks}
\input{sections/physical-four-mobius}
\input{sections/hilbert-compression}
\input{sections/triple-prime-variance}
\input{sections/weighted-transfer}
\input{sections/convolution-shadow}
\input{sections/literature-boundary}
\input{sections/next-gate}
\input{sections/certificate-claims}

\begingroup
\footnotesize
\bibliographystyle{plainnat}
\bibliography{references}
\endgroup

\end{document}
