\documentclass[11pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage{amsmath,amssymb,amsthm,mathtools,mathrsfs}
\usepackage{booktabs,array}
\usepackage{enumitem}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage[colorlinks=true,linkcolor=blue!55!black,citecolor=blue!55!black,urlcolor=blue!55!black]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}
\hypersetup{
 pdftitle={Two Quadraticizations of a Mobius Tail: LCM Cutoff Return, Generic Row Determinants, and Nonprimitive Endpoint Collapse},
 pdfauthor={Liang Wang},
 pdfsubject={A rigorous stopping theorem for the unresolved Mobius tail at a fixed-shift Type-II prime-pair gate},
 pdfkeywords={Mobius tail, Linnik dispersion, TT star, least common multiple, determinant, sieve parity, twin primes}
}

\setlength{\parindent}{1.4em}
\setlength{\parskip}{0.15em}
\setlist{itemsep=0.25em,topsep=0.35em}
\allowdisplaybreaks

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{assumption}[theorem]{Conditional input}
\crefname{assumption}{Conditional input}{Conditional inputs}
\Crefname{assumption}{Conditional input}{Conditional inputs}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\C}{\mathbb C}
\newcommand{\N}{\mathbb N}
\newcommand{\R}{\mathbb R}
\newcommand{\Z}{\mathbb Z}
\newcommand{\one}{\mathbf 1}
\newcommand{\eps}{\varepsilon}
\newcommand{\cC}{\mathcal C}
\newcommand{\cD}{\mathcal D}
\newcommand{\cE}{\mathcal E}
\newcommand{\cG}{\mathcal G}
\newcommand{\cH}{\mathcal H}
\newcommand{\cI}{\mathcal I}
\newcommand{\cM}{\mathcal M}
\newcommand{\cP}{\mathcal P}
\newcommand{\cQ}{\mathcal Q}
\newcommand{\cR}{\mathcal R}
\newcommand{\cT}{\mathcal T}
\newcommand{\cW}{\mathcal W}
\newcommand{\supp}{\operatorname{supp}}
\newcommand{\rad}{\operatorname{rad}}

\title{\textbf{Two Quadraticizations of a M\texorpdfstring{$\ddot{\mathrm{o}}$}{o}bius Tail:}\\
\textbf{LCM Cutoff Return, Generic Row Determinants,}\\
\textbf{and Nonprimitive Endpoint Collapse}}
\author{Liang Wang\\
\small School of Artificial Intelligence and Automation,\\[-0.2em]
\small Huazhong University of Science and Technology, Wuhan 430074, P.R. China\\
\small \texttt{wangliang.f@gmail.com}}
\date{July 2026}

\begin{document}

\maketitle

\begin{abstract}
Fix $h\ne0$.  TPC-17 reduces a family of symmetric fixed-shift
Type-II blocks to the sharp M\"obius tail
\[
 \beta_I(k)=\sum_{\substack{d\mid k\\D_0<d\le V}}\mu(d),
 \qquad I=(D_0,V],
\]
but its separate $TT^*$ theorem concerns an asymmetric packet and
cannot be spliced into this tail.  We construct two quadraticizations
inside the symmetric tail block itself.

The first is an exact least-common-multiple transform
\[
 \beta_I(k)^2=\sum_{q\mid k}\Gamma_I(q),
 \qquad
 \Gamma_I(q)=\sum_{[d_1,d_2]=q}\mu(d_1)\mu(d_2).
\]
Because $V^2\le R$, every squared-tail row returns to the original
Ramanujan cutoff $q\le R$.  If $D_0<V/2$, Selberg's classical divisor
Gram factorization gives a positive terminal-octave Gram floor and, when
$K/V^2\to\infty$ as in the explicit TPC-17 profiles, natural
$k$-space $L^2$ mass; coefficient smallness cannot close it.  The second
quadraticization first fixes $d\asymp D$, opens $k=dj$, and applies
$TT^*$ in $j$.  With $m=\ell d$, $Q=LD$, and $J=K/D$, the determinant
is $h(m_1-m_2)$.  We prove by elementary counting that the same-source,
small-determinant, and large-$(d_1,d_2)$ channels are all negligible.
Thus failure of a tail slice forces a quantitatively large correlation
with distinct prime sources, large determinant, and low divisor gcd.

There is a further exact split by $s=(k,h)$.  In every nonprimitive
sector $s>1$, writing $H=\rad(s)$ gives
\[
 \beta_I(k)=\sum_{\substack{e\mid k\\(e,H)=1}}\mu(e)
 \sum_{f\mid H}\mu(f)\one_{D_0<ef\le V},
\]
and the inner coefficient is supported only on
$(D_0/H,D_0]\cup(V/H,V]$.  Hence the whole interior tail cancels
pointwise.  Moreover, up to a negligible prime-power term, the
nonprimitive residual correlation is a finite-model--finite-model
correlation governed by three explicit Chinese-remainder conditions.

These results identify a sharper stopping point; they do not estimate
the remaining primitive generic correlation.  We state a conditional
determinant-dispersion input that would close the tail and explain why,
under an explicit all-block cover hypothesis for the previous normal form, it reaches
the fixed-shift Hardy--Littlewood problem.  No twin-prime theorem, new
level of distribution, or breach of sieve parity is claimed.
\end{abstract}

\noindent\textbf{Keywords:} M\"obius tail; fixed-shift prime
correlations; $TT^*$ dispersion; least common multiples; divisor Gram
forms; affine determinants; sieve parity.

\medskip
\noindent\textbf{MSC 2020:} Primary 11N35, 11N37; Secondary
11N05, 11N13, 11L07.

\input{sections/introduction}
\input{sections/tail-interface}
\input{sections/lcm-cutoff-return}
\input{sections/gram-floor}
\input{sections/same-k-ttstar}
\input{sections/opened-d-dispersion}
\input{sections/content-endpoints}
\input{sections/finite-model-crt}
\input{sections/stopping-closure}
\input{sections/computation-conclusion}

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}
