\section{Introduction and theorem ledger}
\label{sec:introduction}

The fixed-shift correlation
\begin{equation}
 \cP_h(X;W)=
 \sum_{n\ge1}\Lambda(n)\Lambda(n+h)W(n/X)
 \label{eq:prime-pair-form}
\end{equation}
has conjectural main term
$\mathfrak S(h)XI_0(W)$, where
\begin{equation}
 I_0(W)=\int_0^\infty W(t)\,dt
 \label{eq:I0-definition}
\end{equation}
and
\begin{equation}
 \mathfrak S(h)=
 \prod_p\frac{1-\nu_p(h)/p}{(1-1/p)^2},
 \qquad
 \nu_p(h)=\#\{a\pmod p:a(a+h)\equiv0\pmod p\}.
 \label{eq:pair-singular-series}
\end{equation}
For an odd $h$ the factor at $p=2$ vanishes.  For a nonzero even $h$ the
series is positive.  In particular, an asymptotic of the expected form at
$h=2$ and a nonnegative nonzero $W$ would imply infinitely many twin
primes.  This paper does not prove such an asymptotic.

TPC-15 \citep{WangTPC15} introduced the finite Heath--Brown Ramanujan
model
\begin{equation}
 \Lambda_R(n)=\sum_{q\le R}\frac{\mu(q)}{\varphi(q)}c_q(n),
 \qquad
 r_R(n)=\Lambda(n)-\Lambda_R(n),
 \label{eq:finite-model}
\end{equation}
and, for fixed $0<\delta<1/2$, took
\begin{equation}
 R=\left\lfloor X^{1/2-\delta}\right\rfloor,
 \qquad U=V=\left\lfloor R^{1/2}\right\rfloor.
 \label{eq:base-parameters}
\end{equation}
The resulting Vaughan coefficient is
\begin{equation}
 \beta_V(k)=\sum_{\substack{d\mid k\\d\le V}}\mu(d),
 \label{eq:betaV-intro}
\end{equation}
and the remaining packet is
\begin{equation}
 \cH^{\rm HB}_{h,R;U,V}(X)
 =\sum_{\substack{\ell>U\\k>V}}
 \Lambda(\ell)\beta_V(k)r_R(\ell k+h)W(\ell k/X).
 \label{eq:TPC15-hard-packet}
\end{equation}
TPC-15 proves
\begin{equation}
 \cP_h(X;W)=\mathfrak S(h)XI_0(W)
 -\cH^{\rm HB}_{h,R;U,V}(X)
 +O_A\bigl(X(\log X)^{-A}\bigr).
 \label{eq:TPC15-imported-reduction}
\end{equation}
The negative sign in \eqref{eq:TPC15-imported-reduction} will be retained
throughout.

The broad support
\[
 X^{1/4-\delta/2}<\ell,k
 \ll_W X^{3/4+\delta/2}
\]
is not yet a canonical description of the gate.  Two issues are hidden in
that display.  First, the finite model has an exact progression mean even
when the row modulus exceeds $R$; only its equality with the prime density
fails.  Second, after \eqref{eq:betaV-intro} is opened, the modulus seen by
prime-distribution theorems is $\ell d$, not $\ell$ or $k$.  The paper
resolves these two issues separately.

\subsection{Results}

The first result computes the missing row mean.  Define
\begin{equation}
 \rho_h(m)=\one_{(m,h)=1}\frac m{\varphi(m)},
 \qquad
 \rho_{h,R}(m)=
 \sum_{\substack{q\mid m\\q\le R}}
 \frac{\mu(q)c_q(h)}{\varphi(q)}.
 \label{eq:two-row-means-intro}
\end{equation}
The second quantity is the exact complete-period mean of
$j\mapsto\Lambda_R(mj+h)$ for every $m$.  Their difference is
\begin{equation}
 \Delta_{h,R}(m)=\rho_h(m)-\rho_{h,R}(m)
 =\sum_{\substack{q\mid m\\q>R}}
 \frac{\mu(q)c_q(h)}{\varphi(q)}.
 \label{eq:cutoff-drift-intro}
\end{equation}
Although it need not vanish for $m>R$, its weighted aggregate up to the
Bombieri--Vinogradov wall is $o(1)$ after the natural $1/m$ normalization.

Let
\begin{equation}
 M=M(X)=
 \left\lfloor X^{1/2}\exp(-\sqrt{\log X})\right\rfloor.
 \label{eq:near-square-root-M}
\end{equation}
The recentered row theorem in \cref{sec:recentered-typei} controls every
bounded row mask up to $M$.  Taking the asymmetric Vaughan parameters
$U=M,V=1$ gives
\begin{equation}
 \cP_h(X;W)=\mathfrak S(h)XI_0(W)
 -\cH^\sharp_{h,R;M}(X)
 +O_A\bigl(X(\log X)^{-A}\bigr),
 \label{eq:square-root-normal-form-intro}
\end{equation}
where
\begin{equation}
 \cH^\sharp_{h,R;M}(X)=
 \sum_{\substack{\ell>M\\k>1}}
 \Lambda(\ell)r_R(\ell k+h)W(\ell k/X).
 \label{eq:Hsharp-intro}
\end{equation}
This is the square-root normal form.  It closes the left source-factor
wing $\ell<X^{1/2-o(1)}$.  It does not close the opposite wing in which
$k$ is small and $\ell$ is large.

Returning to the symmetric packet, opening $\beta_V$ and grouping by the
row modulus $m=\ell d$ peels off all terms with $\ell d\le R$.  The
unresolved coefficient is therefore supported in the exact hyperbolic
wedge
\begin{equation}
 \ell d>R.
 \label{eq:invisible-hyperbola-intro}
\end{equation}
This three-scale formulation allows a genuine local advance.  A smoothed
form of \citet[Theorem~1.1]{Maynard2025I} controls fixed-residue prime
errors for moduli $q=q_1q_2$ when
\begin{equation}
 Q_1Q_2^2<X^{1-\eta},\qquad
 Q_1^{12}Q_2^7<X^{4-\eta},\qquad
 Q_1^{20}Q_2^{19}<X^{10-\eta}.
 \label{eq:Maynard-polytope-intro}
\end{equation}
With $q_1=d\asymp D$ and $q_2=\ell\asymp L$, this theorem, together with
the explicit drift \eqref{eq:cutoff-drift-intro}, proves that one smooth
hard subpacket near
\begin{equation}
 D=X^{1/21-o(1)},\qquad
 L=X^{10/21-o(1)},\qquad
 K=X^{11/21+o(1)}
 \label{eq:eleven-twenty-one-scales-intro}
\end{equation}
is $o(X)$.  This is an imported large-modulus estimate transferred to a
new packet; it is not a new level-of-distribution theorem.  Since $d$ is
resolved, the conclusion does not apply to the complete $(L,K)$ block.

The last part is spectral but uses only standard translation dynamics.
For nonnegative $F\in C_c^\infty((0,\infty))$,
\begin{equation}
 \sum_n r_R(n)^2F(n/X)
 =X\log(X/R)I_0(F)+O_{F,\delta}(X).
 \label{eq:energy-law-intro}
\end{equation}
Thus $r_R$ is correlation-calibrated but not small in $\ell^2$.  The
packet \eqref{eq:Hsharp-intro} is an exact matrix coefficient of the
integer translation and hence a specified Fourier coefficient of a
cross-spectrum.  The remaining condition is directional cancellation,
not decay of total residual energy.  Phase averaging proves strong
cancellation for generic factor phases, but not at the unmodulated phase.

\subsection{Claim ledger}

\begin{center}
\small
\begin{tabular}{p{0.43\textwidth}p{0.47\textwidth}}
\toprule
Proved here & Not proved here\\
\midrule
Exact finite-model row mean for every modulus
& A fixed-$h$ prime-pair asymptotic\\
Recentered Type-I closure up to $X^{1/2-o(1)}$
& Cancellation of the full right wing\\
Asymmetric square-root Vaughan normal form
& Cancellation of every dyadic block\\
Peeling of the region $\ell d\le R$
& A new Bombieri--Vinogradov or Maynard range\\
$o(X)$ on one Maynard-admissible $D$-resolved wedge
& $o(X)$ on the complete balanced $(L,K)$ block\\
Residual energy law and translation cross-spectrum identity
& A spectral gap for primes or a Riemann-zero realization\\
Phase-averaged factor-mask bounds
& Cancellation at the distinguished zero phase\\
\bottomrule
\end{tabular}
\end{center}

The distinction between substantial Type-I/II input and actual prime
detection is central to the parity problem; see
\citet{Selberg1952Parity,Polymath2014,FordMaynard2024}.  Nothing below
asserts that the parity barrier has been crossed.  The purpose is to
replace one broad unnamed remainder by a sharper sequence of positive
regions, exact drifts, and explicitly quantified gates.
