\section{Recentered Type-I closure at the square-root wall}
\label{sec:recentered-typei}

The row identity \eqref{eq:row-drift-error-leakage} separates the part
seen by Bombieri--Vinogradov from two elementary terms.  This permits the
row modulus to extend beyond the spectral cutoff $R$.

For $F\in C_c^1((0,\infty))$, write
\begin{equation}
 \cR_{m,h;R}(X;F)=
 \sum_{j\ge1}r_R(mj+h)F(mj/X).
 \label{eq:row-residual-definition}
\end{equation}

\begin{theorem}[Recentered full Type-I row ball]
\label{thm:recentered-TypeI}
Fix $h\ne0$, $0<\delta<1/2$, and
$F\in C_c^1((0,\infty))$.  Put
$R=\lfloor X^{1/2-\delta}\rfloor$.  For every $A>0$ there is
$B=B(A,h,F)>0$ such that, whenever
\begin{equation}
 M\le\frac{X^{1/2}}{(\log X)^B},
 \label{eq:BV-row-wall}
\end{equation}
one has uniformly over all $|\alpha_m|\le1$
\begin{align}
 &\left|
 \sum_{m\le M}\alpha_m
 \left(
 \cR_{m,h;R}(X;F)
 -\Delta_{h,R}(m)\frac Xm I_0(F)
 \right)
 \right|
 \notag\\
 &\qquad\ll_{A,h,F,\delta}
 X(\log X)^{-A}+MR(\log(2R))^2.
 \label{eq:recentered-TypeI-bound}
\end{align}
In particular, with $M$ as in \eqref{eq:near-square-root-M}, the right
side is $O_A(X(\log X)^{-A})$ for every $A>0$.
\end{theorem}

\begin{proof}
Suppose first that $(m,h)=1$.  Smooth maximal
Bombieri--Vinogradov gives
\begin{equation}
 \sum_{\substack{m\le M\\(m,h)=1}}|\cE_{m,h}(X;F)|
 \ll_{A,h,F}X(\log X)^{-A}
 \label{eq:smooth-maximal-BV}
\end{equation}
after increasing the requested logarithmic exponent.  This is the usual
fixed residue $h\pmod m$ application of the theorem
\citep{Bombieri1965,Vinogradov1965,MontgomeryVaughan2007}.

If $(m,h)>1$, a nonzero value $\Lambda(mj+h)$ forces $mj+h$ to be a
power of one of the finitely many primes dividing $h$.  On the fixed
multiplicative support of $F$, there are $O_{h,F}(1)$ relevant powers for
each such prime.  Summing over $m$ counts divisors of the finitely many
integers $p^a-h$, and therefore contributes
$O_{h,F,\eps}(X^\eps)$.  The local density $\rho_h(m)$ is zero on these
rows, so this is exactly the required treatment of
\eqref{eq:prime-row-error}; no reduced residue-class main term is used.

Insert \eqref{eq:row-drift-error-leakage}.  The prime errors are bounded
by \eqref{eq:smooth-maximal-BV} and the preceding prime-power argument.
The model leakage is uniform in $m$ and sums to
$O_F(MR(\log(2R))^2)$.  Taking the supremum over the masks is harmless
after the absolute sum over row errors.  This proves
\eqref{eq:recentered-TypeI-bound}.

For \eqref{eq:near-square-root-M}, one has
$M\le X^{1/2}(\log X)^{-B}$ for every fixed $B$ and all sufficiently
large $X$.  Also
\[
 MR(\log(2R))^2
 \ll X^{1-\delta}\exp(-\sqrt{\log X})(\log X)^2,
\]
which is $O_A(X(\log X)^{-A})$ for every fixed $A$.
Here and below this assertion is pointwise in each fixed $A$: the
Bombieri--Vinogradov exponent and the threshold in $X$ may depend on
$A$.  No estimate uniform in an unbounded parameter $A$ is intended.
\end{proof}

The drift itself remains negligible for the logarithmic coefficient
vectors produced by Vaughan's identity.

\begin{corollary}[Bounded-log uncentered rows]
\label{cor:bounded-log-rows}
Under the hypotheses of \cref{thm:recentered-TypeI}, take $M$ from
\eqref{eq:near-square-root-M}.  Uniformly for $|a_m|\le\log X$,
\begin{equation}
 \sum_{m\le M}a_m\cR_{m,h;R}(X;F)
 \ll_{A,h,F,\delta}X(\log X)^{-A}
 +\frac XR(\log X)^3\log\log X.
 \label{eq:bounded-log-raw-row-bound}
\end{equation}
Consequently the left side is $O_A(X(\log X)^{-A})$ for every $A>0$.
\end{corollary}

\begin{proof}
Divide $a_m$ by $\log X$ and apply
\cref{thm:recentered-TypeI} with one additional logarithmic saving.  By
\cref{lem:drift-bounds}, the removed means contribute at most
\[
 X\log X\sum_{m\le M}\frac{|\Delta_{h,R}(m)|}{m}
 \ll_h\frac XR(\log X)^2\log\log X.
\]
We recorded the slightly looser exponent in
\eqref{eq:bounded-log-raw-row-bound}.  Since
$R=X^{1/2-\delta+o(1)}$ and $\delta<1/2$, this power-saving term is
$O_A(X(\log X)^{-A})$ for every fixed $A$.
\end{proof}

\begin{remark}[What has been extended]
The finite model is exactly calibrated row by row only for $m\le R$.
The theorem does not change that fact.  It proves instead that the
explicit sum of missing local factors is harmless throughout the
classical averaged progression range.  This is why the analytic row wall
can move while the spectral cutoff remains fixed.
\end{remark}

We also need one elementary logarithmic row.  It is included for clarity
rather than hidden in the Vaughan proof.

\begin{lemma}[The modulus-one logarithmic row]
\label{lem:modulus-one-log-row}
For every $A>0$,
\begin{equation}
 \sum_{j\ge1}(\log j)r_R(j+h)W(j/X)
 \ll_{A,h,W,\delta}X(\log X)^{-A}.
 \label{eq:modulus-one-log-row}
\end{equation}
\end{lemma}

\begin{proof}
The prime number theorem with its classical zero-free-region error and
partial summation evaluate the $\Lambda(j+h)$ sum with continuous main
term $\int (\log t)W(t/X)\,dt$.  The complete-period mean of
$\Lambda_R(j+h)$ is $1$, and the logarithmic version of
\cref{lem:finite-row-leakage} has error
$O_W(R(\log(2XR))^3)$.  The two continuous main terms agree.  Since
$R=X^{1/2-\delta+o(1)}$, both remaining errors have arbitrary logarithmic
saving relative to $X$.
\end{proof}
