\section{Finite certificate and reproducibility}
\label{sec:computation}

The analytic asymptotic rests on the theorem of
\citet{GuthMaynard2026}, the weighted transfer proved here, and the
Selberg upper sieve.  A finite computation cannot verify those asymptotic
inputs.  The included deterministic certificate instead checks the exact
algebra and the explicit obstructions on which the interpretation rests.

The script \texttt{experiments/short\_shift\_certificate.py} performs the
following checks.

\begin{enumerate}[label=\textup{(\roman*)}]
 \item It enumerates a finite factor box, groups it by the product center
 $r=mn$, and verifies that the diagonal source mass equals
 $\sum_rA_D(r)$.

 \item It groups the same box by primitive rays and compares the direct
 Mellin transform with the compressed ray transform at several
 frequencies.

 \item For a synthetic exceptional subset, it records the actual
 $A_D$-mass and verifies the finite Cauchy--Schwarz transfer bound
 $\sum_{r\in E}A_D(r)\leq |E|^{1/2}(\sum_rA_D(r)^2)^{1/2}$.

 \item It verifies term by term the sign-coherent identity in
 \cref{thm:sign-coherent-family} and the exact quadratic identity in
 \cref{thm:quadratic-prime-ray}.

 \item It checks the Euclidean instance of the radial minimax formula by
 projecting a test vector onto the constant direction and its orthogonal
 complement.
\end{enumerate}

The companion unit tests repeat the checks at independent parameter
values.  Exact integer arithmetic is used for factorization, ray labels,
and divisibility; floating-point tolerances occur only in logarithms and
Fourier phases.  Reproduction requires only the Python standard library:
\begin{verbatim}
python experiments/short_shift_certificate.py
python -m unittest experiments.test_short_shift_certificate
\end{verbatim}
The saved JSON file is a regression certificate for these finite
identities.  It is not numerical evidence for a fixed-shift prime or
prime-pair asymptotic.

\section{Conclusion and next analytic interface}
\label{sec:conclusion}

TPC-11 separated primitive factor rays at fixed shift but used a shift
window of length at least $X$ to evaluate the squared ray coefficients.
The present paper fills the range
\[
 X^{2/15+\eps}\leq H\leq X.
\]
The exponent comes from the almost-all short-interval prime number
theorem of \citet{GuthMaynard2026}.  The factor-ray contribution is the
weighted exceptional-set transfer: the divisor-square ledger proves that
the sparse exceptional centers cannot carry significant diagonal source
mass.  Once this issue is closed, the same-ray off-diagonal remains within
the reach of a two-linear-forms upper sieve.  The resulting energy and
Mellin-band formulas are unconditional and retain explicit errors.

The gain is substantial but its quantifiers remain those of a growing
ensemble.  Any fixed finite collection of shifts has relative mass
$O(1/H)$ and may remain exceptional forever.  More strongly, the actual
coefficients exhibit sign-coherent locally obstructed rays for every
fixed $h_0\geq2$.  After that obstruction is removed, one admissible ray
already embeds the open weighted prime number theorem for $6k^2+1$.
The radial minimax identity shows why no increase in the existing Mellin
bandwidth can recover the missing $k$ coordinate without additional
structure.

Uniform shifted-divisor technology such as that of
\citet{AssingBlomerLi2021} controls divisor-weighted shadows of the ray
multiplicity.  It does not evaluate the $\Lambda^2$-weighted
large-prime-divisor component that appears when a fixed ray is opened.
Likewise, the quadratic averages of \citet{BaierZhao2009} and the
almost-prime theorem of \citet{Iwaniec1978} do not supply a fixed
quadratic-prime asymptotic.

The next honest spectral target is therefore a radial completion rather
than an extrapolation to $H=1$.  On a sector $ab\asymp R$, the original
ray-frequency spacing is of order $R^{-1}$, while the radial length is
of order $\sqrt{X/R}$.  A second Mellin coordinate attached to
$k=(m,n)$ would test the geometric resolution pair
\[
 T_{\mathrm{ray}}\asymp R,
 \qquad
 T_{\mathrm{radial}}\asymp\sqrt{X/R},
 \qquad
 T_{\mathrm{ray}}T_{\mathrm{radial}}^2\asymp X.
\]
That lift can separate radial indices, but evaluating its fixed-shift
diagonal still requires new arithmetic input.  The sign-coherent,
quadratic-prime, and endpoint reductions in
\cref{sec:fixed-boundary} provide the tests against which any such claim
must be measured.

No fixed-shift prime-pair asymptotic, twin-prime lower bound, prime number
theorem for a fixed quadratic polynomial, new level of distribution, or
violation of sieve parity has been obtained.
