\section{A parity-conditioned short even-shift ensemble}
\label{sec:even-shifts}

The positive theorem can be restricted to even shifts without selecting
one of them.  The correct first-moment model is
\begin{equation}
 \cM_D^{(2)}(X;t)
 :=2\sum_{\substack{n>D,\ m\geq1\\2\nmid mn}}
 u(n)W(mn/X)(n/m)^{it}.
 \label{eq:short-even-model}
\end{equation}
For even $h$, define
\begin{equation}
 \eta_r^{(2)}(h)=\Lambda(r+h)-2\one_{2\nmid r},
 \qquad
 \cR^{(2)}_{h,D}=\cT_{h,D}-\cM_D^{(2)}.
 \label{eq:short-even-residual}
\end{equation}
Its factor-ray coefficient is
\begin{equation}
 c^{(2)}_{a,b}(h;X,D)=
 \sum_{\substack{k\geq1\\ak>D}}
 u(ak)\eta_{abk^2}^{(2)}(h)W(abk^2/X),
 \label{eq:short-even-ray-coefficient}
\end{equation}
and $\cE^{(2)}_{h,D}$ denotes the corresponding squared ray energy.

\begin{proposition}[Short even-shift first moment]
\label{prop:short-even-first-moment}
Under \eqref{eq:main-short-range}, uniformly in $t\in\R$ and for every
$A>0$,
\begin{equation}
 \frac2H\sum_{h\equiv0\ (2)}G(h/H)\cT_{h,D}(X;t)
 =I_0(G)\cM_D^{(2)}(X;t)
 +O_{A,\eps,W,G}\bigl(X(\log X)^{-A}\bigr).
 \label{eq:short-even-first-moment}
\end{equation}
\end{proposition}

\begin{proof}
If $r$ is odd, then every prime target $r+h\asymp X$ has $h$ even, and
the smooth sum over even $h$ is therefore the full prime sum from
\eqref{eq:smooth-Lambda-moment}, apart from the irrelevant prime $2$.
It equals $HI_0(G)+O_A(H(\log X)^{-A})$ outside the same exceptional
set.  If $r$ is even, the target is even and its von Mangoldt weight is
supported on powers of two, giving a negligible contribution.  Group by
$r=mn$ and use the signed exceptional transfer exactly as in the proof of
\cref{thm:short-first-moment}.  The normalization $2/H$ produces the
factor two in \eqref{eq:short-even-model}.
\end{proof}

\begin{proposition}[Short even-shift ray energy]
\label{prop:short-even-energy}
Let $G\in C_c^1((0,\infty))$ be nonnegative and nonzero.  Under
\eqref{eq:nonempty-short-range}--\eqref{eq:main-short-range},
\begin{equation}
 \begin{aligned}
 \sum_{h\equiv0\ (2)}G(h/H)\cE^{(2)}_{h,D}(X)
 ={}&\frac14HX I_0(G)I_2(W)\log X\\
 &\times\bigl((\log X)^2-(\log D)^2\bigr)\\
 &+O_{\eps,\eta,W,G}\!\left(
 HX(\log X)^2\log\log(3X)\right).
 \end{aligned}
 \label{eq:short-even-energy}
\end{equation}
\end{proposition}

\begin{proof}
For $r\in[\alpha X,\beta X]$, the argument above and the transferred
target-square estimate give
\begin{equation}
 \sum_{h\equiv0\ (2)}G(h/H)|\eta_r^{(2)}(h)|^2
 =HI_0(G)\log X\,\one_{2\nmid r}+O(H)
 \label{eq:short-even-target-square}
\end{equation}
outside a stretched-exponentially sparse set.  The weighted exceptional
transfer removes that set after summation.  The source diagonal on odd
products is
\begin{equation}
 \begin{aligned}
 &\sum_{\substack{n>D,\ m\geq1\\2\nmid mn}}
 u(n)^2|W(mn/X)|^2\\
 &\qquad=\frac14XI_2(W)
 \bigl((\log X)^2-(\log D)^2\bigr)+O_W(X\log X).
 \end{aligned}
 \label{eq:short-even-source-diagonal}
\end{equation}
Indeed, the odd $m$ sum has half the continuous density.  Restricting
$n$ to odd integers leaves the quadratic logarithmic term in the
harmonic $u(n)^2$ sum unchanged and alters it by only $O(\log X)$; the
prime $2$ itself contributes a bounded amount.

For distinct target positions, two odd rows are handled by writing
$h=2j$ and applying the two-linear-forms upper sieve.  If either row is
even, its target weight is supported on powers of two, and the resulting
term is smaller.  Thus the even-shift analogue of
\eqref{eq:short-two-target-sieve} is
\[
 \sum_{h\equiv0\ (2)}G(h/H)
 |\eta_r^{(2)}(h)\eta_{r'}^{(2)}(h)|
 \ll_{\eps,W,G}H\log\log(3X).
\]
Now expand the squared ray coefficients, use
\eqref{eq:short-even-target-square}--\eqref{eq:short-even-source-diagonal}
on the diagonal and \eqref{eq:source-offdiagonal-bound} off it.
\end{proof}

The hard- and Fej\'er-band corollaries follow from
\eqref{eq:MV-ray-law} and \eqref{eq:exact-Fejer-law}, with every leading
coefficient exactly one half of its all-shift counterpart.

\begin{remark}[No prescribed even shift]
The support of $G(h/H)$ moves to infinity.  The proposition gives an
asymptotic for a parity-conditioned ensemble; it neither contains nor
selects any fixed even shift.  In particular, no conclusion about a
specified prime gap follows.
\end{remark}
