\begin{abstract}
TPC--60 reduces restoration of the missing very-high Walsh face to a raw
missing-mass estimate and an upper bound for the missing native grouping on
the actual row-coefficient image.  We identify both quantities exactly at
the critical cutoff \(y\asymp Q\) and one fixed nonzero shift.

Under the explicit identical-support specialization, each row \(m\) has a
largest-prime cofactor exposure measure \(\nu_m\).  Represented and missing
raw masses are precisely \(\nu_m(\cI_m)\) and
\(\nu_m(\cI_m^c)\).  The optimal coefficient-uniform missing fraction is
therefore the worst row defect, not an average cofactor density.  We prove
the fixed-shift cofactor ladder
\[
 j=j_0+rt,
 \qquad p=p_0+mt,
\]
and a Brun--Titchmarsh refinement.  It yields a harmonic weighted defect
certificate and shows why one omitted small cofactor can be more dangerous
than its global cardinality suggests.  Since the inherited interface leaves
\(\cI_X\) as an arbitrary retained relation, it does not imply any
nontrivial uniform missing-mass saving; this is a hypothesis-insufficiency
theorem, not a counterexample to a more specific upstream carrier.

For the native map \(M_X\), let
\(\mathbf D_M=\operatorname{diag}(W_M(m))\).  The optimal physical upper degree is
\[
 \kappa_M=
 \lambda_{\max}\!\left(
 \mathbf D_M^{\dagger/2}M_X^*M_X\mathbf D_M^{\dagger/2}
 \big|_{\operatorname{Ran}\mathbf D_M}\right),
\]
so \(\|M_X\zeta\|^2\le\kappa_M\cD_M(\zeta)\) sharply.  On a nonempty
missing carrier, fixed \((i,p)\) incidence gives an exact unit diagonal and
\(\kappa_M=1+\lambda_{\max}(\Xi_{\ne p})\); all excess comes from unequal
high primes.  After a fixed row gauge, the off-diagonal entries are weighted
two-affine-form M\"obius correlations of
\(\mu(mj+h_0)\mu(m'j+h_0)\), equivalently sums on
\(m'pr-mp'r'=h_0(m'-m)\).  This is the explicit missing-high parity
kernel.  We give graph, stable-rank, Schur-complement, and block certificates
for its positive spectrum and a residual-level endpoint wedge.  No bound
\(\kappa_M=X^{o(1)}\), missing-mass saving, parity improvement, prime-pair
lower bound, or twin-prime consequence is asserted.
\end{abstract}
