\section{Result ledger, claim boundary, and the next gate}
\label{sec:tpc61-claims-next}

TPC--61 replaces two coarse quantities from TPC--60 by literal arithmetic
objects.  The missing mass is the realized cofactor measure outside the
fixed retained relation, and the effective native degree is the largest
eigenvalue of the normalized physical row Gram.  The latter has now been
calibrated to a two-affine-form M\"obius kernel.  These are reductions and
certificates; the required exposure and spectral estimates remain open.

\subsection{Result ledger}

\begin{center}
\small
\begin{tabular}{>{\raggedright\arraybackslash}p{0.23\textwidth}
                >{\raggedright\arraybackslash}p{0.52\textwidth}
                >{\raggedright\arraybackslash}p{0.15\textwidth}}
\toprule
Object & Exact conclusion & Status\\
\midrule
Literal high carrier
& One fixed \(h_0\), the raw coefficient
  \(b_w=\beta_w\zeta_{m(w)}\), and the canonical decoding
  \(n=mj+h_0=pr\), \(p=\Pplus(n)>y\), \(s=d_mr\).
& L1 interface\\
\addlinespace
Realized cofactor measure
& The row measure \(\nu_m(r)\) gives exact identities
  \(W_R(m)=\nu_m(\cI_m)\) and
  \(W_M(m)=\nu_m(\cI_m^c)\), followed by the sharp rowwise minimax.
& L1 identity and L0 minimax\\
\addlinespace
Opaque-carrier test
& The inherited finite-relation hypotheses alone permit a missing-only
  active row, so they imply neither positive uniform exposure nor a
  fixed-power missing-mass saving.
& Interface no-go\\
\addlinespace
Cofactor ladder
& For fixed \(m,r\), all solutions are
  \(j=j_0+rt\), \(p=p_0+mt\); Brun--Titchmarsh gives the literal
  harmonic upper capacity.
& L1 arithmetic upper bound\\
\addlinespace
Harmonic defect
& \(\varepsilon_m\ll
  \mathfrak h_m(E_m)/H_m^{\rm eff}\), with the exact dyadic exponent
  law.  Its usefulness requires a small retained-relation complement
  and a lower effective-exposure bound.
& L1 conditional certificate\\
\addlinespace
Residual/native audit
& A positive critical residual wedge remains, whereas paying the full
  direct native degree has a fixed exponent deficit \(67/200\).
& Route-specific opening and closure\\
\addlinespace
Restricted native degree
& \(\kappa_M\) is the optimal generalized-Gram eigenvalue on the actual
  row-coefficient image, with
  \(1\le\kappa_M\le\min\{d_{\rm miss},\dim S_M\}\) when the carrier is
  nonempty.
& L0 theorem; L1 specialization\\
\addlinespace
Prime/residual alias split
& On a nonempty missing carrier, same-prime blocks are isometric and
  \(\kappa_M=1+\lambda_{\max}(\Xi_{\ne p})\); the latter splits into
  same- and unequal-residual alias operators.
& L0/L1 exact Gram\\
\addlinespace
Collision certificates
& Stable rank, weighted Schur, codegree, exact Schur-complement, and
  block certificates give falsifiable upper or lower tests for
  \(\kappa_M\).
& L0 theorems\\
\addlinespace
Parity calibration
& A fixed row gauge turns every off-diagonal alias into the weighted
  kernel
  \(\mu(mj+h_0)\mu(m'j+h_0)\); equivalently it is a signed sum on
  \(m'pr-mp'r'=h_0(m'-m)\).
& L1 identity\\
\addlinespace
Static-mask overlap
& On the complete nondegenerate direct cell, two rows retain
  \(1-o(1)\) of the same opposite-row mass.  The mask costs no positive
  power but does not diagonalize the parity kernel.
& L0 inequality and L1 consequence\\
\addlinespace
Reassembly
& If
  \(\sigma_M>\nu_M+\lambda_{\rm rep}\), the effective mass--degree
  certificate gives zero fixed-power reassembly loss in the matching
  uniform or distinguished scope.
& Conditional only\\
\bottomrule
\end{tabular}
\end{center}

\subsection{Six-item physical audit}

The statements above pass the interface audit in the following precise
sense.  Passing this audit verifies that the right physical object is being
studied; it does not prove a favorable exposure or spectral estimate.
\begin{enumerate}[label=\textup{(A\arabic*)},leftmargin=3.2em]
 \item \emph{Literal coefficients.}
       Every atom has the single inherited coefficient
       \(\beta_w\zeta_{m(w)}\).  The signs
       \(-\mu(s(w))\) in \(M_X\) are the physical high-character signs.
       The row gauge \(U_d\) is a fixed unitary change of coordinates,
       not a choice of favorable atom phases.
 \item \emph{Fixed physical shift.}
       Every occurrence of a target, cofactor ladder, gcd identity, and
       determinant equation comes from \(n=mj+h_0\) for the same fixed
       nonzero \(h_0\).  No shift average or frozen family is substituted.
 \item \emph{Physical atomic normalization.}
       The measures \(\nu_m\), the weights \(W_M(m)\), and the matrix
       \(\mathbf D_M\) use raw counting-measure atoms.  No division by a
       native fiber size is hidden in the input norm.
 \item \emph{Canonical active representation.}
       The row \(m=d_m\ell_m\), largest prime \(p=\Pplus(n)\), cofactor
       \(r=n/p\), residual label \(s=d_mr\), and native output \(i\) are
       canonically recovered.  Moore--Penrose normalization is restricted
       to \(S_M=\Ran\mathbf D_M\); only identically inactive rows disappear.
 \item \emph{Actual support.}
       The carriers \(\cW_H,\cW_R,\cW_M\) and the relation \(\cI_X\) are
       fixed before \(\zeta\) is chosen.  The identity
       \(w\in\cW_M\Longleftrightarrow r(w)\notin\cI_{m(w)}\) is used only
       under the explicitly declared identical-support specialization.
 \item \emph{Endpoint ledger.}
       Exact disintegration, gauge calibration, determinant reindexing,
       and finite/logarithmic partitions carry no fixed-power loss.  A
       proved critical-margin loss is charged only as
       \(\lambda_{\rm reasm}\), and every other arrow remains in the
       strict \(1/400\) sum.
\end{enumerate}

\subsection{What is not proved}

The following conclusions do not follow from this paper.
\begin{enumerate}[leftmargin=2.3em]
 \item The actual upstream relation \(\cI_X\) has not been shown to meet
       \(\supp\nu_m\) on every active row, nor has its harmonic complement
       been shown small.
 \item No coefficient-uniform or distinguished fixed-power bound
       \(\cD_M\le X^{-\sigma_M+o(1)}\cD_{\rm ref}\) is proved.
 \item No lower bound for the represented reference
       \(\|A_X\zeta\|^2\) is supplied; critical-window occupancy and
       terminal activation remain separate upstream gates.
 \item The exact parity target
       \(\rho_{\rm par}(X)=\lambda_{\max}(\Xi_{\ne p})\) is not shown to
       be \(X^{o(1)}\), or to satisfy any smaller fixed exponent than the
       available missing-mass saving.
 \item The gcd divisibility
       \(\gcd(mj+h_0,m'j+h_0)\mid h_0(m-m')\), the distinctness of the
       two high primes, and the determinant parametrization do not imply
       cancellation of the M\"obius product.
 \item The \(1-o(1)\) static-mask overlap is not an orthogonality theorem.
       In fact it shows that the opposite-row coordinate alone supplies
       no polynomial separation of two source rows.
 \item No bound for one row pair is promoted to an operator-norm bound
       over the polynomially growing row family.
 \item No positive physical shorted-Gram lower bound, no value
       \(\lambda_{\rm reasm}=0\), no fixed-shift parity improvement, no
       prime-pair lower bound, no prime-pair asymptotic, and no twin-prime
       implication is proved.
\end{enumerate}

In particular, treating \(\mu(mj+h_0)\) as an independent random sign
would be a new unproved hypothesis.  Likewise, a result for fixed
coefficients, a logarithmically averaged correlation, or an average over
shifts cannot be inserted into
\eqref{eq:tpc61-two-affine-mobius-kernel} without verifying the actual
growing-slope, physical-weight, and operator-norm quantifiers.

\subsection{The ordered next gate}

The next work should preserve the following order.  A favorable spectral
model cannot repair an empty represented carrier, while a favorable
distinguished Rayleigh quotient cannot be entered as a uniform constant.

\begin{enumerate}[label=\textbf{Door \Alph*.},leftmargin=3.8em]
 \item \emph{Recover the actual retained relation.}
       Reopen the provenance of \(\cI_X\) and evaluate the literal row
       intersections
       \begin{equation}
        W_R(m)=\nu_m(\cI_m),
        \qquad
        W_M(m)=\nu_m(\cI_m^c).
        \label{eq:tpc61-next-literal-row-census}
       \end{equation}
       The uniform route is killed immediately by an active row with
       \(W_R(m)=0<W_M(m)\).  Equal row multiplicities, equal dyadic
       capacities, or positive exposure on other rows do not repair it.
       A distinguished route must instead retain the weights
       \(W_H(m)|\zeta_m|^2\) exactly.

 \item \emph{Prove a missing-mass saving in one declared scope.}
       A uniform target has the form
       \begin{equation}
        \cD_M(\zeta)
        \le X^{-\sigma_M+o(1)}\cD_{\rm ref}(\zeta)
        \quad\text{for every declared }\zeta,
        \label{eq:tpc61-next-uniform-missing-saving}
       \end{equation}
       while the distinguished version is asserted only at
       \(\zeta=\zeta_*(X)\).  The harmonic theorem reduces this to a small
       \(\mathfrak h_m(E_m)\) and a lower \(H_m^{\rm eff}\), but proves
       neither input.  One omitted small cofactor can destroy a
       cardinal-density argument.

 \item \emph{Establish the represented reference in the same scope.}
       Prove
       \begin{equation}
        \|A_X\zeta\|^2
        \ge X^{-\lambda_{\rm rep}+o(1)}
             \cD_{\rm ref}(\zeta).
        \label{eq:tpc61-next-represented-reference}
       \end{equation}
       This step cannot absorb unproved critical-window occupancy,
       terminal activation, singleton survival, native erasure, or affine
       transversality into one unnamed exponent.  Their established losses
       must be stated before \(\lambda_{\rm rep}\) is used.

 \item \emph{Estimate the parity kernel, uniformly or pointwise.}
       The coefficient-uniform target is
       \begin{equation}
        \kappa_M
        =1+\lambda_{\max}(\Xi_{\ne p})
        \le X^{\nu_M+o(1)}.
        \label{eq:tpc61-next-uniform-parity-target}
       \end{equation}
       It may be attacked through the two-affine formula
       \eqref{eq:tpc61-two-affine-mobius-kernel}, the determinant form
       \eqref{eq:tpc61-determinant-parity-kernel}, or the exact collision
       certificates.  Pairwise correlation estimates must be upgraded to
       a Schur, block, stable-rank, or direct spectral bound.  For the
       distinguished route, replace \(\kappa_M\) only by the exact
       Rayleigh quotient \(\kappa_M(\zeta_*)\).

 \item \emph{Apply the strict effective-product test.}
       The zero-cost mass--degree door opens only when
       \begin{equation}
        \boxed{\sigma_M>\nu_M+\lambda_{\rm rep}.}
        \label{eq:tpc61-next-effective-product-test}
       \end{equation}
       At exponent equality one must prove the actual subpower margin
       \(1-\sqrt{q_X}\ge X^{-a+o(1)}\); it then costs
       \(\lambda_{\rm reasm}\le2a\).  If the inequality fails, this
       certificate is silent.  It does not prove that signed reassembly
       fails.

 \item \emph{Retain the shorted-Gram and signed fallbacks.}
       Independently test the TPC--60 uniform kernel condition
       \begin{equation}
        \Ker(A_X+M_X)\subseteq\Ker A_X.
        \label{eq:tpc61-next-shorted-kernel-test}
       \end{equation}
       An exact violation kills the uniform reassembly route.  If it is
       killed, the physical distinguished vector may still survive through
       a direct estimate of
       \begin{equation}
        2\operatorname{Re}
          \langle A_X\zeta_*,M_X\zeta_*\rangle
        +\|M_X\zeta_*\|^2.
        \label{eq:tpc61-next-signed-fallback}
       \end{equation}
       This fallback must not be relabeled coefficient-uniform.

 \item \emph{Close the complete endpoint ledger.}
       The final loss remains
       \begin{equation}
        \begin{aligned}
        \Lambda_{\rm tot}:={}&
        \lambda_{\rm sel}+\lambda_{\rm occ}
        +\lambda_{\rm blk}+\lambda_{\rm term}
        +\lambda_{\rm sing}\\
        &+\lambda_H+\lambda_{\rm aff}
        +\lambda_{\rm reasm}
        +\lambda_{\rm bdry}+\lambda_{\rm tail},
        \end{aligned}
        \label{eq:tpc61-final-complete-ledger}
       \end{equation}
       and the endpoint condition is
       \begin{equation}
        \boxed{\Lambda_{\rm tot}<\frac1{400}.}
        \label{eq:tpc61-final-endpoint-condition}
       \end{equation}
       The exponents \(\sigma_M\) and \(\nu_M\) are inputs to the
       reassembly test, not two additional losses to be double-counted.
       Paying the full coefficient-blind native degree is already closed
       by the \(67/200\) deficit; changing the normalization does not reopen
       it.
\end{enumerate}

\paragraph{Conclusion.}
TPC--60 reduced missing-high restoration to a shorted-Gram decision tree.
TPC--61 resolves three structural subquestions in that decision tree at
the L0/L1 level.  It identifies the
exact realized cofactor defect, proves explicit one-dimensional
cofactor-ladder and Brun--Titchmarsh harmonic certificates without assuming
cancellation, and replaces the ambient native degree by the optimal
restricted Gram.
The remaining unequal-prime alias is now the explicit fixed-\(h_0\)
two-affine M\"obius kernel
\eqref{eq:tpc61-two-affine-mobius-kernel}, equivalently the signed
determinant sum \eqref{eq:tpc61-determinant-parity-kernel}.  This is a
strict narrowing of the route, not a parity breakthrough.  The next
arithmetic theorem must control the actual retained-relation exposure and
then beat the normalized parity-kernel exponent in the same scope.
