\section{Weighted collision certificates and sharp tests}
\label{sec:tpc61-collision-certificates}

The constant \(\kappa_M\) is an exact spectral target, but a direct
eigenvalue computation is not always the best proof.  We now express it as
the Gram of a literal weighted incidence matrix and give several rigorous
certificates: collision-graph Schur tests, stable-rank obstructions, exact
Schur complements, and blockwise estimates.  These statements retain the
fixed physical coefficients.  Replacing their signed entries by support
cardinalities is explicitly identified as a sufficient relaxation.

\subsection{The normalized physical incidence matrix}

Let
\begin{equation}
 F_M:=M_X\mathbf D_M^{\dagger/2}|_{S_M}
 :S_M\longrightarrow\ell^2(\cI_{\rm out})
 \label{eq:tpc61-normalized-incidence-map}
\end{equation}
and write its matrix as
\begin{equation}
 f_{i,m}
 =\frac{1}{\sqrt{W_M(m)}}
   \sum_{\substack{w\in\cW_M\\i(w)=i,\ m(w)=m}}c_w
 \qquad(W_M(m)>0).
 \label{eq:tpc61-normalized-incidence-entry}
\end{equation}
The fixed-\((i,m)\) decoding discussed after
\cref{thm:tpc61-prime-block-identity} makes the sum in
\eqref{eq:tpc61-normalized-incidence-entry} either empty or a single
literal atom.  Define the row-collision Gram
\begin{equation}
 \mathbf K_M:=F_M^*F_M.
 \label{eq:tpc61-collision-gram}
\end{equation}
Then
\begin{equation}
 (\mathbf K_M)_{m,n}
 =\sum_i\overline{f_{i,m}}f_{i,n},
 \qquad
 \kappa_M=\lambda_{\max}(\mathbf K_M).
 \label{eq:tpc61-collision-gram-entries}
\end{equation}
Every off-diagonal summand represents two different source rows landing at
the same native output.  By the prime-block singleton, their terminal
primes are unequal.  According to whether their residual labels agree, the
same summand belongs to \(\Xi_{=s}\) or \(\Xi_{\ne s}\).

\begin{theorem}[Unit columns, stable rank, and dimension obstruction]
\label{thm:tpc61-stable-rank}
Let
\begin{equation}
 r_M:=\dim S_M,
 \qquad
 d_M^{\rm out}:=\rank F_M.
 \label{eq:tpc61-active-dimensions}
\end{equation}
If \(r_M>0\), then every column of \(F_M\) has norm one and
\begin{align}
 (\mathbf K_M)_{m,m}&=1
 \qquad(m\in\cM_M),
 \label{eq:tpc61-unit-gram-diagonal}\\
 \|F_M\|_{\rm HS}^2
 =\operatorname{tr}\mathbf K_M&=r_M,
 \label{eq:tpc61-gram-trace}\\
 \boxed{
 \kappa_M
 =\frac{r_M}{\srank(F_M)}
 \ge\frac{r_M}{d_M^{\rm out}},}
 \label{eq:tpc61-stable-rank-identity}\\
 \boxed{
 1\le\kappa_M\le\min\{d_{\rm miss},r_M\}.}
 \label{eq:tpc61-kappa-basic-range}
\end{align}
Moreover:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item \(\kappa_M=1\) if and only if the normalized physical row images
       are orthonormal;
 \item \(\kappa_M=r_M\) if and only if \(F_M\) has rank one.
\end{enumerate}
\end{theorem}

\begin{proof}
Fix an active source row \(m\).  Distinct atoms driven by \(m\) cannot
occupy the same native coordinate: \(i\) fixes \(j\), and \(m,j,h_0\) fix
\(n\), its unique very-high prime, its cofactor, and its residual label.
Therefore
\[
 \sum_i|f_{i,m}|^2
 =\frac{1}{W_M(m)}
   \sum_{\substack{w\in\cW_M\\m(w)=m}}|c_w|^2
 =1.
\]
This proves \eqref{eq:tpc61-unit-gram-diagonal} and
\eqref{eq:tpc61-gram-trace}.  By definition,
\[
 \srank(F_M)
 =\frac{\|F_M\|_{\rm HS}^2}{\|F_M\|^2}
 =\frac{r_M}{\kappa_M},
\]
and \(\srank(F_M)\le\rank F_M\), proving
\eqref{eq:tpc61-stable-rank-identity}.  The lower bound one follows from
the trace, the upper bound \(r_M\) follows because the largest eigenvalue
of a positive matrix is at most its trace, and the
\(d_{\rm miss}\)-bound is
\cref{cor:tpc61-kappa-below-degree}.  If the largest eigenvalue is one,
the trace forces all \(r_M\) eigenvalues to equal one, hence
\(\mathbf K_M=I\).  If it equals \(r_M\), every other eigenvalue is zero,
which is equivalent to rank one.
\end{proof}

\begin{corollary}[Asymptotic rank kill for a subpower degree]
\label{cor:tpc61-rank-kill}
Suppose
\begin{equation}
 r_M=X^{\rho_M+o(1)},
 \qquad
 d_M^{\rm out}\le X^{\omega_M+o(1)}.
 \label{eq:tpc61-rank-exponents}
\end{equation}
Then
\begin{equation}
 \boxed{
 \kappa_M\ge
 X^{(\rho_M-\omega_M)_++o(1)}.}
 \label{eq:tpc61-rank-exponent-lower}
\end{equation}
In particular, a proof of \(\kappa_M=X^{o(1)}\) requires the actual native
image rank to be within a subpower factor of the number of active missing
rows.
\end{corollary}

This is a kill test for the \emph{mass--degree certificate}, not for the
full reassembly problem.  A distinguished coefficient vector can avoid
the large-singular-value direction even when
\eqref{eq:tpc61-rank-exponent-lower} is polynomial.

\subsection{The weighted collision graph}

Let \(\mathscr G_M\) be the graph on active source rows with
\begin{equation}
 m\sim n
 \quad\Longleftrightarrow\quad
 m\ne n\ \text{ and }\ (\mathbf K_M)_{m,n}\ne0,
 \label{eq:tpc61-collision-graph}
\end{equation}
and attach the signed edge weight \((\mathbf K_M)_{m,n}\).  A larger
support graph may instead join two rows whenever they share some output;
the signed graph is obtained after all literal phases on the shared outputs
have been summed.

\begin{theorem}[Component reduction and weighted Schur certificate]
\label{thm:tpc61-graph-schur}
Let \(\mathscr C\) be the connected components of
\(\mathscr G_M\).  Then
\begin{equation}
 \boxed{
 \kappa_M
 =\max_{C\in\mathscr C}
   \lambda_{\max}\bigl((\mathbf K_M)_{C,C}\bigr).}
 \label{eq:tpc61-component-maximum}
\end{equation}
For every family of positive row weights \(t_m>0\),
\begin{equation}
 \boxed{
 \kappa_M
 \le
 \max_m\left\{
  1+\sum_{n\ne m}
  |(\mathbf K_M)_{m,n}|\frac{t_n}{t_m}
 \right\}.}
 \label{eq:tpc61-weighted-graph-schur}
\end{equation}
In particular, if
\begin{equation}
 \Delta_{\rm coh}
 :=\max_m\sum_{n\ne m}|(\mathbf K_M)_{m,n}|,
 \label{eq:tpc61-coherent-degree}
\end{equation}
then
\begin{equation}
 \kappa_M\le1+\Delta_{\rm coh}.
 \label{eq:tpc61-unweighted-coherent-degree}
\end{equation}
\end{theorem}

\begin{proof}
There is no matrix entry between different connected components, so
\(\mathbf K_M\) is their orthogonal direct sum, proving
\eqref{eq:tpc61-component-maximum}.  Entrywise absolute value and the
Schur test give
\[
 \|\mathbf K_M\|
 \le\bigl\||\mathbf K_M|\bigr\|
 \le
 \max_m\frac{1}{t_m}
 \sum_n|(\mathbf K_M)_{m,n}|t_n.
\]
Use the unit diagonal from
\eqref{eq:tpc61-unit-gram-diagonal}.  Taking \(t_m=1\) gives the last
claim.
\end{proof}

Thus a subpower bound for the \emph{weighted coherent degree}, rather than
the raw number of atoms in one output fiber, is sufficient for
\(\kappa_M=X^{o(1)}\).  The weights \(t_m\) permit exceptional rows with
small physical mass or asymmetric overlap to be handled without replacing
the physical atomic norm.

\subsection{A phase-blind overlap certificate}

For an active row \(m\), put
\begin{equation}
 I_m:=\{i:f_{i,m}\ne0\}.
 \label{eq:tpc61-row-output-support}
\end{equation}
For two distinct active rows define the directed weighted overlap
\begin{equation}
 \theta_{m\to n}
 :=\sum_{i\in I_m\cap I_n}|f_{i,m}|^2.
 \label{eq:tpc61-directed-overlap}
\end{equation}
By the unit-column identity, \(0\le\theta_{m\to n}\le1\).

\begin{proposition}[Weighted-codegree bound]
\label{prop:tpc61-weighted-codegree}
For distinct active rows,
\begin{equation}
 |(\mathbf K_M)_{m,n}|
 \le
 \sqrt{\theta_{m\to n}\theta_{n\to m}}.
 \label{eq:tpc61-codegree-cauchy}
\end{equation}
Consequently
\begin{equation}
 \boxed{
 \kappa_M
 \le
 1+\max_m\sum_{n\ne m}
 \sqrt{\theta_{m\to n}\theta_{n\to m}}.}
 \label{eq:tpc61-phase-blind-overlap-bound}
\end{equation}
\end{proposition}

\begin{proof}
Only the common outputs \(I_m\cap I_n\) occur in
\((\mathbf K_M)_{m,n}\).  Cauchy--Schwarz on that set gives
\eqref{eq:tpc61-codegree-cauchy}; insert it in
\eqref{eq:tpc61-unweighted-coherent-degree}.
\end{proof}

The overlap certificate is deliberately phase blind.  Its failure does
not prove that \(\kappa_M\) is large: the exact signed sum in
\((\mathbf K_M)_{m,n}\) may be much smaller than its Cauchy--Schwarz
envelope.

For completeness, the incidence matrix itself admits the following
rectangular Schur test.  If positive weights \(a_i,b_m\) and constants
\(A,B\) satisfy
\begin{equation}
 \sum_m|f_{i,m}|b_m\le A a_i,
 \qquad
 \sum_i|f_{i,m}|a_i\le B b_m,
 \label{eq:tpc61-rectangular-schur-hypothesis}
\end{equation}
then
\begin{equation}
 \boxed{\kappa_M=\|F_M\|^2\le AB.}
 \label{eq:tpc61-rectangular-schur}
\end{equation}
This form can be more convenient when row and output weights factor into
literal smooth profiles.

\subsection{Exact Schur-complement certification}

The preceding Schur bounds use absolute values.  The following criterion
retains all signed cancellations and is exact.  Split the active row space
as \(S_M=S_U\oplus S_V\) and write
\begin{equation}
 \mathbf K_M=
 \begin{pmatrix}
  K_{UU}&K_{UV}\\
  K_{VU}&K_{VV}
 \end{pmatrix}.
 \label{eq:tpc61-blocked-collision-gram}
\end{equation}

\begin{proposition}[Exact recursive upper certificate]
\label{prop:tpc61-exact-schur-complement}
If \(\Lambda>\lambda_{\max}(K_{VV})\), then
\begin{equation}
 \lambda_{\max}(\mathbf K_M)\le\Lambda
 \label{eq:tpc61-lambda-upper-target}
\end{equation}
if and only if
\begin{equation}
 \boxed{
 K_{UU}
 +K_{UV}(\Lambda I-K_{VV})^{-1}K_{VU}
 \preceq\Lambda I.}
 \label{eq:tpc61-strict-schur-certificate}
\end{equation}
At the boundary where
\(C:=\Lambda I-K_{VV}\) may be singular, the exact conditions are
\begin{align}
 C&\succeq0,
 \label{eq:tpc61-singular-schur-one}\\
 \Ran K_{VU}&\subseteq\Ran C,
 \label{eq:tpc61-singular-schur-two}\\
 \Lambda I-K_{UU}-K_{UV}C^\dagger K_{VU}&\succeq0.
 \label{eq:tpc61-singular-schur-three}
\end{align}
\end{proposition}

\begin{proof}
The target is equivalent to positivity of
\[
 \Lambda I-\mathbf K_M
 =
 \begin{pmatrix}
  \Lambda I-K_{UU}&-K_{UV}\\
  -K_{VU}&\Lambda I-K_{VV}
 \end{pmatrix}.
\]
The ordinary Schur complement gives
\eqref{eq:tpc61-strict-schur-certificate} when the lower-right block is
positive definite.  The Moore--Penrose positivity criterion for a
Hermitian block matrix gives
\eqref{eq:tpc61-singular-schur-one}--%
\eqref{eq:tpc61-singular-schur-three}.
\end{proof}

This certificate permits a dense exceptional core \(V\) to be eliminated
exactly while a large sparse part \(U\) is treated recursively.  A
floating-point positive gap at finitely many values of \(X\) is not such a
certificate; exact arithmetic or interval enclosures must also control its
scale dependence.

\subsection{Blockwise physical certificates}

Let the missing carrier have a fixed disjoint partition
\begin{equation}
 \cW_M=\bigsqcup_{b=1}^{B}\cW_{M,b},
 \qquad
 M_X=\sum_{b=1}^{B}M_b,
 \qquad
 \mathbf D_M=\sum_{b=1}^{B}\mathbf D_b,
 \label{eq:tpc61-missing-block-partition}
\end{equation}
where \(\mathbf D_b\) is the raw diagonal of the \(b\)-th block.  Put
\begin{equation}
 S_b:=\Ran\mathbf D_b,
 \qquad
 F_b:=M_b\mathbf D_b^{\dagger/2}|_{S_b},
 \qquad
 \kappa_b:=\|F_b\|^2.
 \label{eq:tpc61-block-normalized-maps}
\end{equation}

\begin{theorem}[Block reassembly upper bounds]
\label{thm:tpc61-block-upper}
For every fixed carrier partition,
\begin{equation}
 \boxed{\kappa_M\le\sum_{b=1}^{B}\kappa_b.}
 \label{eq:tpc61-sum-block-bound}
\end{equation}
More precisely, define
\begin{equation}
 a_{bc}:=\|F_b^*F_c\|,
 \label{eq:tpc61-block-cross-norm}
\end{equation}
where the maps are extended by zero between their active row spaces.  Then
\begin{equation}
 \boxed{
 \kappa_M\le
 \bigl\|[a_{bc}]_{1\le b,c\le B}\bigr\|_{\ell^2_B\to\ell^2_B}.}
 \label{eq:tpc61-block-cross-matrix-bound}
\end{equation}
In particular:
\begin{enumerate}[label=\textup{(\roman*)},leftmargin=3em]
 \item if \(\Ran F_b\perp\Ran F_c\) for \(b\ne c\), then
       \(\kappa_M\le\max_b\kappa_b\);
 \item without any cross-block orthogonality,
       \(a_{bc}\le\sqrt{\kappa_b\kappa_c}\), which recovers
       \eqref{eq:tpc61-sum-block-bound}.
\end{enumerate}
\end{theorem}

\begin{proof}
For \(\zeta\), set
\(x_b=\mathbf D_b^{1/2}\zeta\in S_b\).  Then
\[
 M_X\zeta=\sum_bF_bx_b,
 \qquad
 \sum_b\|x_b\|^2=\cD_M(\zeta).
\]
The triangle inequality followed by Cauchy--Schwarz gives
\[
 \left\|\sum_bF_bx_b\right\|^2
 \le
 \left(\sum_b\sqrt{\kappa_b}\|x_b\|\right)^2
 \le
 \left(\sum_b\kappa_b\right)
 \left(\sum_b\|x_b\|^2\right),
\]
which proves \eqref{eq:tpc61-sum-block-bound}.  On the orthogonal direct
sum \(\bigoplus_bS_b\), the Gram of the row operator
\((x_b)_b\mapsto\sum_bF_bx_b\) has blocks \(F_b^*F_c\).  The norm of a
block operator matrix is at most the norm of the scalar matrix of block
norms, proving \eqref{eq:tpc61-block-cross-matrix-bound}.  The two special
cases follow immediately.
\end{proof}

If the carrier is divided into \(B=O(\log X)\) dyadic cofactor blocks and
one proves
\begin{equation}
 \kappa_b=X^{o(1)}
 \quad\text{uniformly in }b,
 \label{eq:tpc61-subpower-block-hypothesis}
\end{equation}
then \eqref{eq:tpc61-sum-block-bound} gives
\begin{equation}
 \boxed{\kappa_M=X^{o(1)}}
 \label{eq:tpc61-subpower-global-kappa}
\end{equation}
without any cross-block orthogonality hypothesis.  What is not automatic
is \eqref{eq:tpc61-subpower-block-hypothesis}: on a compatible endpoint
block, the ambient determinant-ladder bound still contains the
positive-power factor \(1+L/R\).

\subsection{Sharp examples}

\begin{example}[Complete coherent incidence]
\label{ex:tpc61-coherent-incidence}
Take \(r\) source rows and one native output, with one atom of coefficient
one in every row.  Then
\begin{equation}
 \mathbf D_M=I_r,
 \qquad
 F_M=[\,1\ \cdots\ 1\,],
 \qquad
 d_{\rm miss}=r,
 \qquad
 \kappa_M=r.
 \label{eq:tpc61-coherent-example}
\end{equation}
Thus the ambient degree bound can be exactly sharp.
\end{example}

\begin{example}[Same support and magnitudes, Fourier cancellation]
\label{ex:tpc61-fourier-incidence}
Take \(r\) rows and \(r\) native outputs, with one atom at every pair
\((i,m)\), all of modulus \(r^{-1/2}\).  The raw row weights are one and
every native fiber has degree \(r\).  If all phases are equal, then
\[
 F_M=r^{-1/2}\one\one^{\mathsf T},
 \qquad
 \kappa_M=r.
\]
For the Fourier phases
\begin{equation}
 (F_M)_{i,m}
 =r^{-1/2}\exp(2\pi\mathrm i\,im/r),
 \label{eq:tpc61-fourier-matrix}
\end{equation}
\(F_M\) is unitary and
\begin{equation}
 \boxed{d_{\rm miss}=r,\qquad\kappa_M=1.}
 \label{eq:tpc61-fourier-saving}
\end{equation}
The two arrays have identical support, identical atomic magnitudes, and
identical native degrees.  Hence support and raw mass do not determine the
restricted native norm.  This is an abstract sharpness example; it does
not assert that the literal arithmetic phases form a Fourier matrix.
\end{example}

\begin{example}[Uniform and distinguished scopes separate sharply]
\label{ex:tpc61-uniform-distinguished}
For
\[
 F_M=[\,1\ \ 1\,]
\]
one has \(\kappa_M=2\).  The distinguished normalized coefficient
\(x=(1,-1)\) has pointwise ratio zero, whereas \(x=(1,1)\) attains the
uniform value two.  A good distinguished ratio therefore gives no
coefficient-uniform bound, while a large uniform norm does not prove that
the inherited physical vector occupies its top singular direction.
\end{example}

\begin{example}[Either stage of the residual quotient can carry the loss]
\label{ex:tpc61-two-stage-sharpness}
If \(T_M\) embeds \(r\) coefficient coordinates as the \(r\) residual
labels over one native output, then
\(\kappa_{\rm res}=1\), \(\beta_M=r\), and \(\kappa_M=r\).  Conversely,
if \(T_M\) coherently groups \(r\) row coordinates into one residual
coordinate and \(\mathsf E\) is the identity on that coordinate, then
\(\kappa_{\rm res}=r\), \(\beta_M=1\), and again \(\kappa_M=r\).
Thus neither factor in \eqref{eq:tpc61-two-stage-upper} can be omitted.
\end{example}

\subsection{Exponent consequence for the reassembly ledger}

Suppose, in a stated uniform or distinguished scope,
\begin{align}
 \kappa_M&\le X^{\nu_M+o(1)},
 \label{eq:tpc61-effective-degree-exponent}\\
 \cD_M(\zeta)
 &\le X^{-\sigma_M+o(1)}\cD_{\rm ref}(\zeta),
 \label{eq:tpc61-missing-mass-saving}\\
 \|A_X\zeta\|^2
 &\ge X^{-\lambda_{\rm rep}+o(1)}
       \cD_{\rm ref}(\zeta).
 \label{eq:tpc61-represented-reference-lower}
\end{align}
Then
\begin{equation}
 q_X(\zeta)
 :=\frac{\kappa_M\cD_M(\zeta)}
          {\|A_X\zeta\|^2}
 \le
 X^{\nu_M+\lambda_{\rm rep}-\sigma_M+o(1)}.
 \label{eq:tpc61-effective-product}
\end{equation}
Consequently
\begin{equation}
 \boxed{
 \sigma_M>\nu_M+\lambda_{\rm rep}
 \quad\Longrightarrow\quad
 \frac{\|(A_X+M_X)\zeta\|^2}{\|A_X\zeta\|^2}
 =1+o(1).}
 \label{eq:tpc61-zero-cost-effective-degree}
\end{equation}
The upper half of the last equality follows from the triangle inequality,
and the lower half from
\eqref{eq:tpc61-uniform-reassembly-certificate}.

At exponent equality one must retain the actual margin.  If
\begin{equation}
 1-\sqrt{q_X(\zeta)}\ge X^{-a+o(1)}
 \label{eq:tpc61-critical-margin}
\end{equation}
for some \(a\ge0\), then the certificate charges at most
\begin{equation}
 \lambda_{\rm reasm}\le2a
 \label{eq:tpc61-critical-reassembly-cost}
\end{equation}
in the matching scope.  This cost must be entered in the strict
\(1/400\) ledger.  If \(q_X\) is not bounded below one, the present
reverse-triangle certificate is silent; that does not prove failure of a
signed or shorted-Gram route.

The dimension obstruction
\eqref{eq:tpc61-rank-exponent-lower} gives the necessary lower scale
\[
 \nu_M\ge(\rho_M-\omega_M)_+.
\]
Thus a zero-cost mass--degree proof cannot follow from the available
savings unless
\begin{equation}
 \sigma_M>
 (\rho_M-\omega_M)_++\lambda_{\rm rep}.
 \label{eq:tpc61-rank-necessary-saving}
\end{equation}
Failure of \eqref{eq:tpc61-rank-necessary-saving} closes this particular
uniform certificate, not the distinguished signed route.

At the critical cutoff, the coefficient-blind residual capacity exponent
from TPC--60 is at least
\[
 \frac{15077}{105000}
 \approx0.143590,
\]
far above \(1/400\).  The new quantity \(\nu_M\) is not that ambient
capacity exponent.  A proof of
\(\Delta_{\rm coh}=X^{o(1)}\), of the weighted overlap condition in
\eqref{eq:tpc61-phase-blind-overlap-bound}, or of the block condition
\eqref{eq:tpc61-subpower-block-hypothesis} would instead give
\(\nu_M=0\).  None of those arithmetic estimates is asserted here.
