\section{Introduction}
\label{sec:tpc61-introduction}

The critical-cutoff correction of TPC--59 reopens the geometric cofactor
scale \(r\asymp J\), but it does not say that the terminal retained-pair
carrier meets the largest-prime cofactors actually exposed by the complete
Walsh face.  TPC--60 consequently splits that face into represented and
missing atoms and writes their physical native outputs on one row-coefficient
space.  If \(A_X\) is the base plus represented-high map and \(M_X\) is the
missing-high correction, the exact full map is
\begin{equation}
 B_X=A_X+M_X.
 \label{eq:tpc61-intro-full-map}
\end{equation}
Restoring the missing atoms is not monotone after grouping.  TPC--60 proves
the sharp pointwise certificate
\begin{equation}
 \frac{\|B_X\zeta\|^2}{\|A_X\zeta\|^2}
 \ge
 \left(
  1-\sqrt{
   \frac{d_{\rm miss}\cD_M(\zeta)}{\|A_X\zeta\|^2}}
 \right)_+^2,
 \label{eq:tpc61-intro-ambient-certificate}
\end{equation}
but its ambient degree \(d_{\rm miss}\) is far too expensive at the
endpoint.  The next task is therefore not another abstract lower angle.  It
is to determine, on the literal carrier,
\begin{enumerate}[leftmargin=2.3em]
 \item how much raw high mass lies outside the retained cofactor relation;
 \item how large the missing grouping is on the actual row-coefficient image.
\end{enumerate}

This paper answers both questions at the level of exact objects and sharp
finite-dimensional certificates.  It does not estimate the final arithmetic
constants.  The distinction matters: replacing an unknown quantity by its
correct formula is progress only if the formula produces new tests, new
closures, or a narrower surviving target.  Here it does all three.

\subsection{From cofactor counts to exposure matching}

On the very-high face, every target has the unique factorization
\begin{equation}
 mj+h_0=p_m(j)r_m(j),
 \qquad p_m(j)=\Pplus(mj+h_0)>y.
 \label{eq:tpc61-intro-largest-prime}
\end{equation}
For a row \(m\), we retain the complete literal weight of all opposite rows
and define the cofactor exposure \(\nu_m(r)\) at those orbit times for which
\(r_m(j)=r\).  Under identical Walsh and terminal supports, the retained set
\(\cI_m=\{r:(m,r)\in\cI_X\}\) captures exactly
\begin{equation}
 W_R(m)=\nu_m(\cI_m),
 \qquad
 W_M(m)=\nu_m(\cI_m^c).
 \label{eq:tpc61-intro-exposure-split}
\end{equation}
Thus the problem is a weighted matching problem between a deterministic
retained relation and a largest-prime exposure profile.  Marginal knowledge
of \(\#\cI_m\), or an average over rows, does not determine this match.

There is, however, new arithmetic structure inside one row.  The terminal
support forces \((m,r)=1\).  Fixing \((m,r)\) in
\eqref{eq:tpc61-intro-largest-prime} gives
\begin{equation}
 j=j_0+rt,
 \qquad
 p=p_0+mt.
 \label{eq:tpc61-intro-row-ladder}
\end{equation}
Consequently a fixed critical cofactor \(r\asymp J\) occurs at only
\(O(1)\) orbit times.  For smaller \(r\), the relevant defect is harmonic:
the candidate load is \(1+J/r\), with a logarithmic Brun--Titchmarsh
improvement.  A single omitted \(r=1\) may therefore have a length-\(J\)
candidate ladder even though it is a negligible fraction of the global
cofactor universe.

\subsection{The optimal physical upper degree}

The raw missing diagonal is a quadratic form on the row space:
\begin{equation}
 \cD_M(\zeta)=\langle\mathbf D_M\zeta,\zeta\rangle,
 \qquad
 \mathbf D_M=\operatorname{diag}(W_M(m)).
 \label{eq:tpc61-intro-DM}
\end{equation}
The least constant in
\begin{equation}
 \|M_X\zeta\|^2\le\kappa\cD_M(\zeta)
 \label{eq:tpc61-intro-kappa-inequality}
\end{equation}
is
\begin{equation}
 \kappa_M
 =\lambda_{\max}\!\left(
 \mathbf D_M^{\dagger/2}M_X^*M_X\mathbf D_M^{\dagger/2}
 \big|_{\Ran\mathbf D_M}\right).
 \label{eq:tpc61-intro-kappa}
\end{equation}
This is not the ambient native fiber degree.  It is the exact operator norm
after the atomic lift is restricted to the coupled physical row image.

The fixed-\((i,p)\) singleton incidence makes each prime block an isometry
relative to its raw diagonal.  When \(S_M\ne\{0\}\), normalization gives
\begin{equation}
 \mathbf D_M^{\dagger/2}M_X^*M_X\mathbf D_M^{\dagger/2}
 =I+\Xi_{\ne p},
 \qquad
 \kappa_M=1+\lambda_{\max}(\Xi_{\ne p}).
 \label{eq:tpc61-intro-prime-alias}
\end{equation}
All excess above one is therefore unequal-prime alias.  The matrix further
splits into same-residual determinant-ladder collisions and the new
unequal-residual alias created by native erasure.  Stable rank, weighted
collision graphs, Schur complements, and dyadic block decompositions give
rigorous ways either to certify a small positive spectrum or to kill that
possibility before attempting a delicate number-theoretic proof.

\subsection{The parity kernel is literal}

The remaining Gram is not an unnamed ``random-sign'' object.  Since
\(mj+h_0=p r\) is squarefree,
\begin{equation}
 -\mu(r)=\mu(mj+h_0).
 \label{eq:tpc61-intro-mu-n}
\end{equation}
The fixed factor \(\mu(d_m)\) can be removed by a diagonal unitary gauge.
For two distinct rows, the normalized Gram entry is then a weighted
correlation of
\begin{equation}
 \mu(mj+h_0)\mu(m'j+h_0)
 \label{eq:tpc61-intro-two-affine}
\end{equation}
on the simultaneous missing very-high support.  Writing
\(mj+h_0=pr\) and \(m'j+h_0=p'r'\), the common-orbit condition is exactly
\begin{equation}
 m'pr-mp'r'=h_0(m'-m).
 \label{eq:tpc61-intro-determinant}
\end{equation}
Thus the surviving route is an operator-norm problem for a truncated
two-affine-form M\"obius kernel, equivalently a signed determinant-surface
sum.  Known fixed-form or averaged cancellation cannot simply be inserted:
the slopes range with \(X\), the support includes a largest-prime cutoff and
cofactor mismatch, and the desired quantity is a matrix norm rather than a
single unrestricted average.

\subsection{Main consequences and boundary}

For \(A_X\zeta\ne0\), the exact replacement of
\eqref{eq:tpc61-intro-ambient-certificate} is
\begin{equation}
 \boxed{
 \frac{\|B_X\zeta\|^2}{\|A_X\zeta\|^2}
 \ge
 \left(
  1-\sqrt{
   \frac{\kappa_M\cD_M(\zeta)}{\|A_X\zeta\|^2}}
 \right)_+^2.}
 \label{eq:tpc61-intro-restricted-certificate}
\end{equation}
For a distinguished vector, \(\kappa_M\) may be replaced by its one-vector
Rayleigh quotient; that conclusion remains pointwise.  If
\begin{equation}
 \kappa_M\le X^{\nu_M+o(1)},
 \quad
 \cD_M(\zeta)\le X^{-\sigma_M+o(1)}
                   \cD_{\rm ref}(\zeta),
 \quad
 \|A_X\zeta\|^2\ge
 X^{-\lambda_{\rm rep}+o(1)}\cD_{\rm ref}(\zeta),
 \label{eq:tpc61-intro-three-exponents}
\end{equation}
then the strict condition
\begin{equation}
 \sigma_M>\nu_M+\lambda_{\rm rep}
 \label{eq:tpc61-intro-zero-cost-condition}
\end{equation}
gives zero fixed-power reassembly loss in the same declared scope.

What is proved here is the exposure disintegration, the row ladder, the
harmonic defect certificate, the optimal restricted Gram and its exact
parity-kernel representation.  What is not proved is a positive exposure
match, a subpower bound for \(\kappa_M\), or any lower square at one fixed
shift.  The result is L0/L1.  It neither claims nor hints at an L2 parity
advance, a prime-pair asymptotic, or a twin-prime consequence.

 The paper is organized as follows.  \Cref{sec:tpc61-physical-interface}
 freezes the literal carrier.
 \Cref{sec:tpc61-cofactor-exposure,sec:tpc61-cofactor-ladder,sec:tpc61-harmonic-defect}
 treat the missing-mass side.
 \Cref{sec:tpc61-restricted-gram,sec:tpc61-parity-kernel,sec:tpc61-collision-certificates}
 identify and test the restricted native
Gram.  The endpoint ledger and exact next gate appear in
\cref{sec:tpc61-endpoint-ledger,sec:tpc61-claims-next}.
